### 2019-07-07 Latex/tex/pr.tex
code add

\documentclass[onecolumn,draftcls]{IEEEtran}
%\documentclass[journal,twocolumn,10pt,letter]{IEEEtran}
%\documentclass[conference,10pt,twocolumn,letter]{IEEEtran}
%\documentclass[journal,onecolumn,11pt,draftcls,doublespace]{IEEEtran}
%\documentclass[journal,onecolumn,11pt,doublespace]{IEEEtran}
%\documentclass[journal,onecolumn,11pt,draftcls,doublespace]{IEEEtran}
%\documentclass[journal,onecolumn]{IEEEtran}
\IEEEoverridecommandlockouts
\ifCLASSINFOpdf
\else
\fi
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[cmex10]{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{amsbsy}
\usepackage{mathrsfs}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{psfrag}
\usepackage{newclude}
\usepackage[normalem]{ulem}
\usepackage{latexsym}
%\usepackage{tikz}
\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{bbm} % indicator function
\usepackage{filecontents}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\def\CE{\mathcal{E}}
\def\A{{A^n_\epsilon}}
\def\bS{{\boldsymbol{S}}}
\def\bs{{\boldsymbol{s}}}
\def\bz{{\boldsymbol{z}}}
\def\bu{{\boldsymbol{u}}}
\def\bv{{\boldsymbol{v}}}
\def\bU{{\boldsymbol{U}}}
\def\bx{{\boldsymbol{x}}}
\def\bX{{\boldsymbol{X}}}
\def\by{{\boldsymbol{y}}}
\def\bY{{\boldsymbol{Y}}}
\def\pr{{\text{P}}}
\def\c{{\mathcal{C}}}
%%%%%%%%%%%%%%%%% Define \doublehat
\usepackage{accents}
\usepackage[absolute]{textpos}
\newlength{\dhatheight}
\newcommand{\doublehat}[1]{%
    \settoheight{\dhatheight}{\ensuremath{\hat{#1}}}%
    \addtolength{\dhatheight}{-0.35ex}%
    \hat{\vphantom{\rule{1pt}{\dhatheight}}%
    \smash{\hat{#1}}}}
%%%%%%%%%%%%%%%%%%% Define Independent Symbol
\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\graphicspath{{figures/}}
\allowdisplaybreaks
\newcommand{\eqdef}{\overset{\mathrm{def}}{=\joinrel=}}
\hyphenation{op-tical net-works semi-conduc-tor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{"In the name of GOD" \\[2in] End to End Open RAN System } \author{\IEEEauthorblockN{\normalsize
     Mojdeh Karbalaee Motalleb}

    \vspace{2cm}
    }

\maketitle

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

 \emph{index Terms}-
\end{abstract}
\IEEEpeerreviewmaketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\tableofcontents
\newpage
\listoffigures
\listoftables
\newpage
\section{System Model}

\newpage
\bibliographystyle{ieeetr}
\bibliography{m}
 %%
\
\end{document}

### 2019-09-29 Latex/tex/pr.tex
add latex file

@@
-\documentclass[onecolumn,draftcls]{IEEEtran}
-%\documentclass[journal,twocolumn,10pt,letter]{IEEEtran}
-%\documentclass[conference,10pt,twocolumn,letter]{IEEEtran}
-%\documentclass[journal,onecolumn,11pt,draftcls,doublespace]{IEEEtran}
-%\documentclass[journal,onecolumn,11pt,doublespace]{IEEEtran}
-%\documentclass[journal,onecolumn,11pt,draftcls,doublespace]{IEEEtran}
-%\documentclass[journal,onecolumn]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 \IEEEoverridecommandlockouts
-\ifCLASSINFOpdf
-\else
-\fi
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage[cmex10]{amsmath}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{mathrsfs}
-\usepackage{amsbsy}
-\usepackage{mathrsfs}
-\usepackage{setspace}
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
 \usepackage{graphicx}
-\usepackage{caption}
-%\usepackage{subcaption}
-\usepackage{psfrag}
-\usepackage{newclude}
-\usepackage[normalem]{ulem}
-\usepackage{latexsym}
-%\usepackage{tikz}
-\usepackage[table]{xcolor}
-\usepackage{multirow}
-\usepackage{rotating}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{mathrsfs}
-\usepackage{bbm} % indicator function
-\usepackage{filecontents}
-\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
-\def\CE{\mathcal{E}}
-\def\A{{A^n_\epsilon}}
-\def\bS{{\boldsymbol{S}}}
-\def\bs{{\boldsymbol{s}}}
-\def\bz{{\boldsymbol{z}}}
-\def\bu{{\boldsymbol{u}}}
-\def\bv{{\boldsymbol{v}}}
-\def\bU{{\boldsymbol{U}}}
-\def\bx{{\boldsymbol{x}}}
-\def\bX{{\boldsymbol{X}}}
-\def\by{{\boldsymbol{y}}}
-\def\bY{{\boldsymbol{Y}}}
-\def\pr{{\text{P}}}
-\def\c{{\mathcal{C}}}
-%%%%%%%%%%%%%%%%% Define \doublehat
-\usepackage{accents}
-\usepackage[absolute]{textpos}
-\newlength{\dhatheight}
-\newcommand{\doublehat}[1]{%
-    \settoheight{\dhatheight}{\ensuremath{\hat{#1}}}%
-    \addtolength{\dhatheight}{-0.35ex}%
-    \hat{\vphantom{\rule{1pt}{\dhatheight}}%
-    \smash{\hat{#1}}}}
-%%%%%%%%%%%%%%%%%%% Define Independent Symbol
-\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
-\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\allowdisplaybreaks
-\newtheorem{remark}{Remark}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\graphicspath{{figures/}}
-\allowdisplaybreaks
-\newcommand{\eqdef}{\overset{\mathrm{def}}{=\joinrel=}}
-\hyphenation{op-tical net-works semi-conduc-tor}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{textcomp}
+\usepackage{xcolor}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 \begin{document}
 
-\title{"In the name of GOD" \\[2in] End to End Open RAN System } \author{\IEEEauthorblockN{\normalsize
-     Mojdeh Karbalaee Motalleb}
+\title{Joint Power Allocation and Network Slicing In an End to End O-RAN System
+}
 
-    \vspace{2cm}
+\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
+\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+\textit{Tehran University}\\
+Tehran, Iran \\
+mojdeh.karbalaee@ut.ac.ir}
+\and
+\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address}
+
 }
@@
 
-\newpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
 
- \emph{index Terms}-
 \end{abstract}
-\IEEEpeerreviewmaketitle
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\tableofcontents
-\newpage
-\listoffigures
-\listoftables
-\newpage
-\section{System Model}
 
-\newpage
-\bibliographystyle{ieeetr}
-\bibliography{m}
- %%
-\
+\begin{IEEEkeywords}
+component, formatting, style, styling, insert
+\end{IEEEkeywords}
+
+\section{Introduction}
+This document is a model and instructions for \LaTeX.
+Please observe the conference page limits.
+
+\section{System Model and Problem Formulation}
+In this section, first, we present the downlink (DL) of O-RAN System. Then we obtain achievable rate and delays.
+Afterward, the main problem is expressed.
+\subsection{System Model}
+Suppose that there are $S$ Slices Serving $V$ Services.
+Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service.
+Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $N_s$ PRBs.
+Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity.
+Also each RRH and PRB can serve more than one slice.
+It is considered that in BBU, the system has 2 processing layer consists of $M_1$ homogeneous VMs in first layer and $M_2$ homogeneous VMs in second layer.
+\subsection{Achievable Rate}
+In this subsection, the Achievable Rate is obtained as below.
+The achievable data rate for $i^{th}$ UE in $v^{th}$ service can be written as 
+\begin{equation}
+R_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}})
+\end{equation}
+where $\rho_{u(v,i)}$ is obtained from 
+\begin{equation}
+\rho_{u(v,i)} =  \frac{P_{u(v,i)}}{BN_0 + I_{u(v,i)}}
+\end{equation}
+
+\section*{References}
+
+Please number citations consecutively within brackets \cite{b1}. The 
+sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
+number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
+the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+
+Number footnotes separately in superscripts. Place the actual footnote at 
+the bottom of the column in which it was cited. Do not put footnotes in the 
+abstract or reference list. Use letters for table footnotes.
+
+Unless there are six authors or more give all authors' names; do not use 
+``et al.''. Papers that have not been published, even if they have been 
+submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
+that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
+Capitalize only the first word in a paper title, except for proper nouns and 
+element symbols.
+
+For papers published in translation journals, please give the English 
+citation first, followed by the original foreign-language citation \cite{b6}.
+
+\begin{thebibliography}{00}
+\bibitem{b1} G.
+Eason, B.
+Noble, and I.
+N.
+Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
+Trans.
+Roy.
+Soc.
+London, vol.
+A247, pp.
+529--551, April 1955.
+\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
+\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+\bibitem{b6} Y.
+Yorozu, M.
+Hirano, K.
+Oka, and Y.
+Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
+J.
+Magn.
+Japan, vol.
+2, pp.
+740--741, August 1987 [Digests 9th Annual Conf.
+Magnetics Japan, p.
+301, 1982].
+\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\end{thebibliography}
+\vspace{12pt}
+\color{red}
+IEEE conference templates contain guidance text for composing and formatting conference papers.
+Please ensure that all template text is removed from your conference paper prior to submission to the conference.
+Failure to remove the template text from your paper may result in your paper not being published.
+
 \end{document}

### 2019-10-01 124/124/20161125.tex
latex

%\documentclass[onecolumn,draftcls]{IEEEtran}
%\documentclass[journal,twocolumn,10pt,letter]{IEEEtran}
\documentclass[conference,10pt,twocolumn,letter]{IEEEtran}
%\documentclass[journal,onecolumn,12pt,doublespace]{IEEEtran}
%\documentclass[journal,onecolumn,11pt,draftcls,doublespace]{IEEEtran}
%\documentclass[journal,onecolumn]{IEEEtran}
\IEEEoverridecommandlockouts
\ifCLASSINFOpdf
\else
\fi
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[cmex10]{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{amsbsy}
\usepackage{mathrsfs}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{psfrag}
\usepackage{newclude}
\usepackage[normalem]{ulem}
\usepackage{latexsym}
%\usepackage{tikz}
\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{bbm} % indicator function
\usepackage{filecontents}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\def\CE{\mathcal{E}}
\def\A{{A^n_\epsilon}}
\def\bS{{\boldsymbol{S}}}
\def\bs{{\boldsymbol{s}}}
\def\bz{{\boldsymbol{z}}}
\def\bu{{\boldsymbol{u}}}
\def\bv{{\boldsymbol{v}}}
\def\bU{{\boldsymbol{U}}}
\def\bx{{\boldsymbol{x}}}
\def\bX{{\boldsymbol{X}}}
\def\by{{\boldsymbol{y}}}
\def\bY{{\boldsymbol{Y}}}
\def\pr{{\text{P}}}
\def\c{{\mathcal{C}}}
%%%%%%%%%%%%%%%%% Define \doublehat
\usepackage{accents}
\newlength{\dhatheight}
\newcommand{\doublehat}[1]{%
    \settoheight{\dhatheight}{\ensuremath{\hat{#1}}}%
    \addtolength{\dhatheight}{-0.35ex}%
    \hat{\vphantom{\rule{1pt}{\dhatheight}}%
    \smash{\hat{#1}}}}
%%%%%%%%%%%%%%%%%%% Define Independent Symbol
\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\graphicspath{{figures/}}
\allowdisplaybreaks
\newcommand{\eqdef}{\overset{\mathrm{def}}{=\joinrel=}}
\hyphenation{op-tical net-works semi-conduc-tor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{Optimal Power Allocation for Distributed MIMO C-RAN System with Limited Fronthaul Capacity} \author{\IEEEauthorblockN{\normalsize
     Mojdeh Karbalaee Motalleb, Amirreza Kabiri, Mohammad Javad Emadi}
  \IEEEauthorblockA{\small Electrical Engineering Department, Amirkabir University of Technology, Tehran, Iran\\
    E-mails: \{mkm1992, a.r.kabiri, mj.emadi\}@aut.ac.ir}
    \vspace{-.75cm}
    }
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
This paper investigates the optimal power allocation for the downlink of multiple-input multiple output (MIMO) cloud radio access network (C-RAN) with limited fronthaul capacity in terms of maximizing energy efficiency (EE). 
In the considered system, the compressed and precoded message generated by Central Unit (CU) is transmitted to Remote Radio Heads (RRHs) via a fronthaul link with limited capacity, and the RRHs and users equipments (UEs) are assumed to be clustered into $S$ cluster set.
Here, we used an iterative algorithm with Lagrangian function to optimize the EE.
%Karush-Kuhn-Tucker (KKT) conditions
 \emph{index Terms}- Coud Radio Access Network, Multiple-Input Multiple Output, Energy efficincy, Clusterization, Power allocation, Karush-Kuhn-Tucker (KKT) conditions.
\end{abstract}
\IEEEpeerreviewmaketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The growing demand of higher data rates led vendors to think of the next generation of wireless networks which will essentially provide higher throughputs and more coverage than the state-of-art technologies. There are some new concepts introduced to enhance 5G networks such as; Het-Net systems, mmWave communications, Large-scale MIMO systems, and Cloud-Radio Access Networks. Each of the above mentioned concepts fulfills different requirements of 5G networks. As the main focus of this paper is on the C-RAN technology, it is briefly introduced next. In C-RAN systems, in order to have a more efficient system in terms of computational resources, baseband processings, which may have high computational complexities, are transfered from base stations to control centers located in a cloud. In addition to managing computational resources, C-RAN technology can provide new concepts such as co-operation among RRHs, RRH clustering \cite{33,55}. To obtain both advantages of C-RAN and MIMO system, using MIMO C-RAN system simultaneously can enhance achievable rate and also EE \cite{33}. By using MIMO system, we can achieve higher data rates and even better EE compared to conventional systems by exploiting multiple number of antennas to transmit or receive data streams.

In order to consider feasible links between CU and RRHs, named as fronthaul, the capacities of these inks are assumed to be limited \cite{22,44,1111,66}. As a result of limited fronthaul the messages passed through these links need to be compressed \cite{22,44,1111,66} . One of the main problems that now has attracted the attention of researches in MIMO C-RAN systems is how to efficiently perform detections or precodings and compressions of messages before transmitting them to CU or RRHs. Deploying efficient resource allocations causes prevention of wasting energy and as a result leads to higher EE \cite{33,55,77}. In\cite{22,44,1111,66}, the authors investigated optimizing achievable rate according to the precoding and power matrix and quantization noise with fronthaul capacity constraint. In \cite{66}, the approach of CFE (Compress-Forward Estimate) in uplink (UL) and improving data rates is investigated by using ECF (Estimate-Compress-Forward) instead can reach better performance in system, where RRH, estimate CSIT in UL, compress message and forward it to CUs studied.

In this paper, the downlink of a MIMO C-RAN system is considered where CU precodes the message, compresses the resulting signals. The compressed version of signal is forwarded via the limited capacity fronthaul links to the RRHs. it is assumed that RRHs and UEs are clustered in a way that certain clusters RRHs serve certain groups of UEs. In such system the knowledge of Channel State Information at Transmitter side (CSIT) is needed to compute precoding matrices. Since CSIT is imperfectly obtained from uplink pilot transmissions we assume that the CSIT is obtained with a certain error. MMSE precoding is applied to reduce interference and enhance the performance of the system.

\begin{figure}
  \centering
    \includegraphics[width=8cm, height=8cm]{c1}
  \caption{Cooperative MIMO downlink C-RAN system.}
  \label{fig:c11}
\end{figure}

\section{System Model and Problem Formulation}

In this section, the system model, achievable rate and the main problem which is optimizing power allocation is expressed.

\subsection{System Model}

Downlink of a MIMO C-RAN system consists of $R$ RRHs serving $D$ single antenna user equipments (UE) is considered. It is assumed that RRHs and UEs are clustered in to $S$ cluster set in a way that the $v$-th cluster set, has $R_v$ RRHs serving ${D}_v$ UEs. Furhtermore, it is assumed that the $j$-th RRH in the $v$-th cluster is connected to CU via a optical fibers with limited capacity of $c_{r_{(v,j)}}$. Each user receives both intra-cluster and inter-cluster interferences. So we have
\begin{equation}
\begin{split}
\mathcal{R}_v= \{  r_{(v,i)} | 1 \leq i \leq {R}_v , i\in Z^+\}, \\
\mathcal{C}_{\mathcal{R}_v}= \{c_{r_{(v,j)}}| 1 \leq j \leq {R}_v , j\in Z^+\}, \\
\mathcal{D}_v= \{  d_{(v,k)} | 1 \leq k \leq {D}_v , k\in Z^+\},  \\
\end{split}
\end{equation}
where $\mathcal{R}_v$, $\mathcal{C}_{\mathcal{R}_v}$, and $\mathcal{D}_v$ respectively represent the RRH set, the capacity set and the UE set  for the $v$-th cluster set.
In CU we apply the approach of compressing after precoding and then forwarding.
\subsection{Achievable Rate Analysis}
In this subsection, the achievable data rate of the considered system is investigated. 
\begin{theorem}\label{t1}
The achievable data rate for UE $d_{(s,k)}$ is
\begin{equation}\label{e1}
\mathfrak{R}_{d_{(s,k)}} = B \log_2(1+\gamma_{d_{(s,k)}}),
\end{equation}
where, $B$ is the channel bandwidth and $\gamma_{d_{(s,k)}}$ is the received SINR for the $k$-th UE in the $s$-th cluster set formulated as follows
\begin{equation}\label{5}
\gamma_{d_{(s,k)}}= \frac{p_{d_{(s,k)}}|\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,k)}}|^2}{I_{d_{(s,k)}}+BN_0}.
\end{equation}
In \eqref{5}, $I_{d_{(s,k)}}$, denotes the power od interfering signals, $N_0$ represents the noise power, $\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}$ shows the channel gain vector between the $k$-th UE in the $s$-th cluster set and $\boldsymbol{w}_{\mathcal{R}_{s},d_{(s,k)}}$ indicates the precoding vector used in $s$-th cluster set for the $k$-th UE.
$p_{d_{(s,k)}}$ is the power RRHs that transmit to the $k$-th UE in the $s$-th cluster set.
\end{theorem}

\begin{proof}
%%%%%%%%%%%%%
Let $\boldsymbol{y}_{\mathcal{D}_s}$ be a $D_s \times 1$ vector denoting the received signals by the set of UEs in the $s$-th cluster which is demonstrated as 
\begin{equation} \label{1}
\boldsymbol{y}_{\mathcal{D}_s} = \sum_{v=1}^S \boldsymbol{H}^H_{\mathcal{R}_v,\mathcal{D}_s}\hat{\boldsymbol{x}}_{\mathcal{R}_v}+ \boldsymbol{z}_{\mathcal{D}_s},
\end{equation}
where $\hat{\boldsymbol{x}}_{ \mathcal{R}_v} = [\hat{x}_{ r_{(v,1)}},...,\hat{ x}_{ r_{(v,\mathcal{R}_v)}}]^T \in \mathbb{C}^{{R}_v } $ is the transmitted message vector for the $v$-th cluster set, $\boldsymbol{z_{\mathcal{D}_s}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{D}_s})$ shows the additive white Guassian noise with the power of $N_0$, and $\boldsymbol{H}_{\mathcal{R}_v,\mathcal{D}_s}=\left[\boldsymbol{h}_{\mathcal{R}_v,d_{(s,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_v,d_{(s,\mathcal{D}_s)}}\right]^T  \in \mathbb{C}^{{R}_v\times {D}_s}$ 
represents the channel matrix between RRH set $\mathcal{R}_v$ to UE set
$\mathcal{D}_s$. The channel vector from the RRH cluster $v$ to the $k$-th UE in the $s$-th cluster set $\boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}\in \mathbb{C}^{{R}_v}$ is modeled as follows
\begin{equation}
\boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_v,d_{(s,k)}} \boldsymbol{g}_{\mathcal{R}_v,d_{(s,k)}},
\end{equation}
% resizebox{0.3\hsize}{!}{$
where \resizebox{0.35\hsize}{!}{$\boldsymbol{g}_{\mathcal{R}_v,d_{(s,k)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{D}_s})$} represents the fast fading channel vector and \resizebox{0.75\hsize}{!}{$\boldsymbol{\beta}_{\mathcal{R}_v,d_{(s,k)}}=\text{diag}(a_{r_{(v,1),d_{(s,k)}}},\ldots,a_{r_{(v,\mathcal{R}_v),d_{(s,k)}}})$}
indicates the large scale fading matrix \cite{88}. In addition, the transmitted signal has the following form
\begin{equation}
\label{eq_pow1}
 \hat{\boldsymbol{x}}_{\mathcal{R}_v} = \tilde{\boldsymbol{x}}_{\mathcal{R}_v} + \boldsymbol{Q}_{\mathcal{R}_v},
\end{equation}
where, $\boldsymbol{Q}_{\mathcal{R}_v} = \left[ q_{r_{(v,1)}},\ldots,q_{r_{(v,R_v)}}\right]^T$,  is the quantization noise vector originating from compression made after precoding in the CU with element distribution of
$q_{M_{(t,i)}}\backsim \mathcal{N}(0,\sigma_{q_{(t,i)}}^2) $. Moreover,
$$\tilde{\boldsymbol{x}}_{\mathcal{R}_v} = \textbf{W}_{\mathcal{R}_v,\mathcal{D}_v} \textbf{P}_{\mathcal{D}_v}^{\frac{1}{2}} \boldsymbol{x}_{ \mathcal{D}_v},$$
denotes the precoded message before compression.

As mentioned before, channel vector is assumed to be known with errors, the imperfection of channel estimation is modeled as follows
\begin{equation*}
\hat{\boldsymbol{h}}_{\mathcal{R}_v,d_{(s,k)}} = \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}} + \Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}},
\end{equation*}
$\Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}$ denotes the estimation error vector with a Guassian distribution of
$$\Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}\backsim \mathcal{N}(0,\boldsymbol{\phi}_{\mathcal{R}_v,d_{(s,k)}}^2),$$
where 
$$\boldsymbol{\phi}_{\mathcal{R}_v,d_{(s,k)}} = \text{diag}(\phi_{r_{(v,1)},d_{(s,k)}},\ldots,\phi_{r_{(v,\mathcal{R}_v)},d_{(s,k)}}).$$

By using MMSE precoding, the precoding matrix is expressed as follows
\begin{equation}
\boldsymbol{W}_{\mathcal{R}_s,\mathcal{D}_s} = \hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}(\hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}^H \hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}+ \alpha \boldsymbol{I}_{{D}_s})^{-1},
\end{equation} 
where, $\alpha$ is the regularization factor.

Then the before mentioned $I_{d_{(s,k)}}$, denoting the interference power, can be written as follows
\begin{equation}\label{6}
\begin{split}
I_{d_{(s,k)}} &=  \underbrace{\sum_{\substack{l=1 \\ l\neq k}}^{{D}_s} |\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,l)}}|^2  p_{d_{(s,l)}}}_{\text{(intra-cluster interference)}}\\
&+\underbrace{\sum_{\substack{v=1 \\ v\neq s}}^{S} \sum_{l=1}^{{D}_s} |\boldsymbol{h}_{\mathcal{R}_v, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{v},d_{(v,l)}}|^2 p_{d_{(v,l)}}}_{\text{(inter-cluster interference)}}\\
& +\underbrace{ \sum_{v=1}^{S} \sum_{i=1}^{{R}_v} {\sigma_q}_{r_{(v,i)}}^2 \sum_{l=1}^{{D}_s} |\boldsymbol{h}_{r_{(v,i)}, d_{(v,l)}}^H|^2 }_{\text{(quantization noise interference)}}.
\end{split}
\end{equation}

 \end{proof}
\section{Optimizing Power Allocation}
Let the power of transmitted signal by the $i$-th RRH in the $s$-th cluster set indicated by
\begin{equation} \label{eq_pow2}
\bar{p}_{r_{(s,i)}} = \frac{1}{T} \mathit{E}[|| \hat{x}_{\mathcal{D}_v} ||^2] ,
\end{equation}
where $T$ is the symbol duration assumed to be 1 throughout the paper. By plugging eq (\ref{eq_pow1}) into eq (\ref{eq_pow2}), the power of transmitted signal has the following form
\begin{equation}
\bar{p}_{r_{(s,i)}} = \boldsymbol{w}_{r_{(s,i)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{D}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{D}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,i)},\mathcal{D}_{s}}^H + \sigma_{q_{(s,i)}}^2.
\end{equation}
As a result the achievable rate on the fronthual link between the CU and the $i$-th RRH in $t$-th cluster should be higher than
\begin{equation}
C_{R_{(t,i)}} = \log{(1+\frac{w_{r_{(s,i)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{D}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{D}_v}^{H \frac{1}{2}}   w_{r_{(s,i)},\mathcal{D}_{s}}^H }{ \sigma_{q_{(s,i)}}^2})},
\end{equation}
in order to be able to transmit the aforementioned signals via fronthual links.
\subsection{Problem Statement}
The ratio of the sum-rate of system to the total power transmitted by RRHs indicates one of the most pormising indicators for selecting new technologies, named as the energy efficiency of system and denoted by $\eta$, which can be formulated as
\begin{equation}\label{eta}
\eta(\boldsymbol{P}) := \frac{\sum\limits_{s=1}^{S} \sum\limits_{k=1}^{{D}_s}\mathfrak{R}_{d_{(s,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{R_{total}(\boldsymbol{P})}{P_{RRH}(\boldsymbol{P})},
\end{equation}
in which $ \boldsymbol{P} = \{ \boldsymbol{P}_{\mathcal{D}_s}|  1 \leq s \leq S, s \in \mathbb{Z}^{+} \}$ is a power allocation matrix.
In this paper, maximization of energy efficiency is investigated with the presence of following constraints, 
\begin{equation}\label{p1}
\begin{aligned}
\max\limits_{\boldsymbol{P}}   \quad &   \eta(\boldsymbol{P})\\
\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \qquad \forall s, \forall i,   \\
&\mathfrak{R}_{d_{(s,k)}} \geq  \mathfrak{R}_{d_{(s,k)}}^{th} && \qquad \forall s, \forall k, \\
&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{th}  &&\qquad \forall s, \forall i, \\
&p_{d_{(s,k)}}  \geq 0                                  &&\qquad \forall s, \forall k, \\
\end{aligned}			
\end{equation}
Since the problem is not a convex problem, an iterative algorithm is used to derive the optimal values for the maximization problem. 
\subsection{Proposed Method}
In this subsection, instead of maximizing eq \eqref{eta}, we solve an equivalent problem by using an iterative algorithm. 
\begin{theorem}\label{t2}
 $\eta^*$ can be obtained if and only if 
\begin{equation}\label{q2}
\begin{split}
&\max \limits_{\boldsymbol{P}} (R_{total}(\boldsymbol{P}) - \eta^* P_{RRH}(\boldsymbol{P}))=\\
& R_{total}(\boldsymbol{P}^*) - \eta^* P_{RRH}(\boldsymbol{P}^*) =0,
\end{split}
\end{equation}
where $\{\boldsymbol{P}\}$ would be a feasible solution of problem \eqref{p1}.
\end{theorem}
\begin{proof}
See Theorem (1) in \cite{11}.
\end{proof}

To solve this problem, we use Lagrangian function  by an iterative algorithm proposed in \cite{11}.
For simplicity, the upper bound for the interference is considered as follows
\begin{equation}
\begin{split}
\tilde{I}_{d_{(s,k)}} &= \sum_{v=1}^{S} P_{max}|| \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}} \boldsymbol{w}_{\mathcal{R}_v,d_{(s,k)}}||^2 ,\\
& +  \sum_{v=1}^{S} \sum_{i=1}^{{R}_v} {\sigma_q}_{r_{(v,i)}}^2 \sum_{l=1}^{{D}_s} |\boldsymbol{h}_{r_{(v,i)}, d_{(v,l)}}^H|^2.
\end{split}
\end{equation}
So the following lower band for eq \eqref{e1} is used for finding optimal values
\begin{equation}\label{e11}
\mathfrak{\tilde{R}}_{d_{(s,k)}} = B \log_2(1+\tilde{\gamma}_{d_{(s,k)}}),
\end{equation}
where $\tilde{\gamma}_{d_{(s,k)}}$ is
\begin{equation}\label{15}
\tilde{\gamma}_{d_{(s,k)}} =  \frac{p_{d_{(s,k)}}|\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{R_{s},d_{(s,k)}}|^2}{\tilde{I}_{d_{(s,k)}}+BN_0};
\end{equation}

As mentioned before an iterative algorithm is used for optimization which is based on the Lagrangian multiplier function shown as follow,
\begin{equation}
\begin{split}
\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\mu}, \boldsymbol{ \kappa}) & = \sum\limits_{s=1}^{S} \sum\limits_{k=1}^{\mathcal{D}_s}\mathfrak{\tilde{R}}_{d_{(s,k)}} 
- \eta \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
&+\sum\limits_{s=1}^{S} \sum\limits_{k=1}^{\mathcal{D}_s} \lambda_{d_{(s,k)}} (\mathfrak{\tilde{R}}_{d_{(s,k)}}-\mathfrak{R}_{d_{(s,k)}}^{th})\\
&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{\mathcal{R}_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{\mathcal{R}_s} \kappa_{r_{(s,i)}} (C_{r_{(s,i)}}-C_{r_{(s,i)}}^{th}).\\
\end{split}
\end{equation}
where $\boldsymbol{\lambda}, \boldsymbol{\mu}, \boldsymbol{\kappa} \geq 0$ are Lagrangian multipliers vector.\\
By applying KKT conditions, the optimal power allocation is derived as below,
\begin{equation}
p_{r_{(s,i)}}^* =[\frac{ B(1+\gamma_{d_{(s,k)}} )}{ln2 \times (\iota_{r_{(s,i)}}+ \chi_{r_{(s,i)}})} -\frac{\tilde{I}_{d_{(s,k)}} + BN_0}{\nu_{d_{(s,k)}} }]^+;
\end{equation} 
where $$\nu_{d_{(s,k)}} =|h_{\mathcal{R}_s, d_{(s,k)}}^H w_{R_{s},d_{(s,k)}}|^2,$$
 $$\iota_{r_{(s,i)}}=\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{\mathcal{R}_s} (\mu_{r_{(s,i)}}+1)(w_{r_{(s,i)},d_{(v,l)}} w_{r_{(s,i)},d_{(v,l)}}^*),$$
 $$\chi_{r_{(s,i)}} \approx  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{\mathcal{R}_s} \frac{\kappa_{r_{(s,i)}}}{ln2}\frac{(w_{r_{(s,i)},d_{(v,l)}} w_{r_{(s,i)},d_{(v,l)}}^*)}{ \sum\limits_{k=1}^{\mathcal{D}_s}P_{max}+\sigma_{q_{r_{(s,i)}}}^2}.$$
  The details of algorithm are described in \textbf{Algorithm} \eqref{alg}.  
\begin{algorithm}
\caption{Energy-Efficient Power Allocation}\label{alg}
\begin{algorithmic}[1]
\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
\State Set the iteration index $i = 1$ and begin the iteration (Outer
Loop).
\For {$ 1\leq i \leq  Imax$}
\State Solve the resource allocation problem with $\eta^{(i)}$ (Inner Loop);
\State Obtain $P^{(i)}, R_{total}^{(i)}, P_{RRH}^{(i)}$
\If {$ R_{total}(\boldsymbol{P}^{(i)}) - \eta^{(i)} P_{RRH}(\boldsymbol{P}^{(i)}) < \epsilon_{\eta} $} 
\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
\State break;
\Else
\State Set $\eta^{(i)}= \frac{R_{total}(\boldsymbol{P}^{(i))}}{P_{RRH}(\boldsymbol{P}^{(i))}}$ and $i= i+1$;
\EndIf 
\State \textbf{end if}
\EndFor 
\State \textbf{end for}
\end{algorithmic}
\end{algorithm}
\section{Numerical Result}
In Fig. \ref{fig:nem1},
EE for the iterative algorithm and equal power allocation with different numbers in each cluster are shown.
 As it is illustrated, iterative algorithm is much more better than equal power allocation. The increase in the number of RRHs, causes an enhancement in EE of the system.
 The parameters used in the simulations generating Fig. \ref{fig:nem1}, is shown in Table \ref{tab:title}.

 \begin{table}[H]
 \caption {Simulation Parameter} \label{tab:title} 
 \begin{center}
  \begin{tabular}{||c c ||} 
  \hline
  Parameter & Value \\ [0.5ex] 
  \hline\hline
  Number of cluster S & 4 \\ 
  \hline
  Noise power & -174dBm\\
  \hline
  Bandwidth & 10MHZ \\
  \hline
 Maxmimun transmit Power & 23dBm \\
  \hline
  Minimum data rate &  1Mbits/sec \\ [1ex] 
  \hline
 \end{tabular}
 \end{center}
 \end{table}

  \begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{n123}
  \caption{Energy efficiency vs number of RRH for Optimized and Equal Power Allocation, plotted for parameters given in Table I with $U_s=8$.}
  \label{fig:nem1}
\end{figure}

In Fig. \ref{fig:nem2}, EE of the proposed iterative algorithm and equal power allocation is depicted with different number of UE in each cluster. It is shown that the iterative algorithm outperforms  again.
Since by increasing the number of UE in each cluster, interference also increased. So the system performance is decreased according to the increase in number of UE.  
  \begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{ue}
  \caption{Energy efficiency vs number of UE for Optimized and Equal Power Allocation, plotted for parameters given in Table I with $M_s=30$.}
  \label{fig:nem2}
\end{figure}
%\bibliographystyle{ieeetr}
%\bibliography{bib1}
%\setLTRbibitems
\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{c}
  \caption{Energy efficiency vs ${C}^{th} $ constraint with $S =3.Ms= 20, U =3$ }
  \label{fig:nem3}
\end{figure}

In Fig. \ref{fig:nem3}, EE is depicted as a function of the maximum fronthaul link capacity constraint. In this simulation as the capacity  exceeds 12 (bits/s/Hz) , the EE tends to be saturated.
\section{Conclusion}
In this paper, we have focused on optimizing power allocation in downlink of MIMO C-RAN system with limited fronthaul capacity.
 The compressed messages are forwarded via the limited capacity fronthaul links to the RRHs which are clustered into $S$ cluster sets.
The system model is expressed and the problem of maximizing the EE is solved by using an iterative algorithm and Lagrangian function.
Simulation results demonstrate that by increasing the number of RRHs in each cluster, the performance of the system would be enhanced. 
On the other hand, by increasing the number of UE in each cluster, the system performance is reduced.

\bibliographystyle{ieeetr}
\bibliography{m}
 %%
\
\end{document}

### 2019-10-01 Latex/tex/pr.tex
latex

@@
 Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $N_s$ PRBs.
+All the RRHs in a slice that is mapped to a service, transmit signals to all the UEs in specific service.
 Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity.
@@
 The achievable data rate for $i^{th}$ UE in $v^{th}$ service can be written as 
-\begin{equation}
-R_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}})
+\begin{equation}\label{eq1}
+\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}})
 \end{equation}
-where $\rho_{u(v,i)}$ is obtained from 
-\begin{equation}
-\rho_{u(v,i)} =  \frac{P_{u(v,i)}}{BN_0 + I_{u(v,i)}}
+where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from 
+\begin{equation}\label{eq2}
+\rho_{u(v,i)} =  \frac{P_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}}
 \end{equation}
+Where, $P_{u(v,i)}$ represents the transmitted power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 
+$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
+In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the the transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
+More over, $BN_0$ denotes the power of guassian additive noise and $I_{u(v,i)}$ is the power of interfering signals.
+To obtain SNR as formulated in equation \eqref{eq2}, let $\bold{y}_{U_v}$ be the received signal's vector of all users in $v^{th}$ service which is given by equation \eqref{eq3}
+\begin{equation}\label{eq3}
+\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k}+ \boldsymbol{z}_{\mathcal{U}_v}
+\end{equation}
+where, $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
+Furthermore, $\zeta_{U_v,k} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks(PRB) to UE.
 

### 2019-10-03 Latex/tex/pr.tex
latex update 1

--- 2019-09-29 Latex/tex/pr.tex
@@
 \usepackage{cite}
+\usepackage{stackengine}
+\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
 \usepackage{amsmath,amssymb,amsfonts}
+\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
 \usepackage{algorithmic}
@@
 The achievable data rate for $i^{th}$ UE in $v^{th}$ service can be written as 
+\begin{equation}\label{eq1}
+\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}})
+\end{equation}
+where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from 
+\begin{equation}\label{eq2}
+\rho_{u(v,i)} =  \frac{P_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}}
+\end{equation}
+Where, $P_{u(v,i)}$ represents the transmitted power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 
+$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
+In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the the transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
+Moreover, $BN_0$ denotes the power of guassian additive noise and $I_{u(v,i)}$ is the power of interfering signals.
+To obtain SNR as formulated in equation \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service which is given by equation \eqref{eq3}
+\begin{equation}\label{eq3}
+\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k}+ \boldsymbol{z}_{\mathcal{U}_v}
+\end{equation}
+where $\boldsymbol{x}_{ \mathcal{R}_s} = [x_{ r_{(s,1)}},...,x_{ r_{(s,\mathcal{R}_s)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector for the $s$-th set of Network slice,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
+In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which is made from signal compression in BBU.
+\\
+Furthermore, $\zeta_{U_v,k} \delequal \{\zeta_{u(v,1),k},\zeta_{u(v,2),k},...,\zeta_{u(v,N_{U_v}),k}\}$,
+$\zeta_{u(v,i),k} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks(PRB) to UE.
+Also as defined before, $\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
+shows the channel matrix between RRH set $\mathcal{R}_s$ to UE set
+$\mathcal{U}_v$. 
+The channel vector from the RRH of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below
 \begin{equation}
-R_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}})
+\boldsymbol{h}_{\mathcal{R}_s,u_{(s,i)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_s,u_{(v,i)}} \boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}},
 \end{equation}
-where $\rho_{u(v,i)}$ is obtained from 
+where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(a_{r_{(s,1),u_{(v,i)}}},\ldots,a_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
+represents the large scale fading matrix.
+\\
+Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as follow
 \begin{equation}
-\rho_{u(v,i)} =  \frac{P_{u(v,i)}}{BN_0 + I_{u(v,i)}}
+\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}
 \end{equation}
-
+Hence, the interference power of $i^{th}$ UE in $v^{th}$ service can be represented as follow
+\begin{equation}
+\begin{split}
+ I_{u_{(v,i)}} &= 
+ \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{vs}\zeta_{u_(v,i),n}\zeta_{u_(v,l),n}}_{\text{(intra-service interference)}}\\
+&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{ys} \zeta_{u_(v,i),n}\zeta_{u_(y,l),n}}_{\text{(inter-service interference)}}\\
+&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{vs}}_{\text{(quantization noise interference)}}.
+\end{split}
+\end{equation}
+where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
+and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$.
+let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from $j^{th}$ RRH in $s^{th}$ slice.
+from equation \eqref{eq3} we have
+\begin{equation}
+\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{vs} + \sigma_{q_{r(s,j)}}^2.
+\end{equation}
+As a result the user data capacity on the fronthual link between BBU and the $j^{th}$ RRH in $s^{th}$ slice is formulated as below
+\begin{equation}
+C_{R_{(s,j)}} = \log{(1+\sum_{v=1}^{V}\frac{w_{r_{(s,j)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   w_{r_{(s,j)},\mathcal{U}_{v}}^H a_{vs}}{ \sigma_{q_{r(s,j)}}^2})},
+\end{equation}
+It is assumed that we have two processing layer in BBU of O-RAN system.
+as we mentioned before, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer.
+Each VM in both layers map to one or more slices.
+So in $s^{th}$ slice, there are $M_{s_1}$ VMs in first layer and $M_{s_2}$ VMs in second layer.
+Each VM in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively.
 \section*{References}

### 2019-10-03 Latex/tex/pr.tex
latex update 2

@@
 where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(a_{r_{(s,1),u_{(v,i)}}},\ldots,a_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
-represents the large scale fading matrix.
+represents the large scale fading matrix. Here, it is assumed we have perfect channel state information(CSI).
 \\
@@
 \end{equation}
-It is assumed that we have two processing layer in BBU of O-RAN system.
-as we mentioned before, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer.
+Suppose that we have two processing layer in BBU of O-RAN system.
+As it is mentioned before, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer.
 Each VM in both layers map to one or more slices.
@@
 Each VM in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively.
+\\
+Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for $i^{th}$ UE in $v^{th}$ service. 
+Therefore, the mean arrival data rate of UEs in $s^{th}$ slice is 
+$\alpha_s = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}\lambda_{u(v,i)}$.  
+It is assumed that there are dispatchers in each layer for each slice to divide the incoming traffic to VMs.
+Suppose the baseband processing of each VM is depicted as a M/M/1 processing queue.
+
 \section*{References}

### 2019-10-04 Latex/tex/pr.tex
latex part 3 or 4

@@
 \end{equation}
+\subsection{Mean Delay}
 Suppose that we have two processing layer in BBU of O-RAN system.
@@
 Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for $i^{th}$ UE in $v^{th}$ service. 
-Therefore, the mean arrival data rate of UEs in $s^{th}$ slice is 
-$\alpha_s = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}\lambda_{u(v,i)}$.  
+Therefore, the mean arrival data rate of UEs in $s^{th}$ slice in the first layer is 
+$\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}\lambda_{u(v,i)}$.  
+Furthermore, the mean arrival rate of second layer is approximately equal to the mean arrival rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the arrival packets of second layer which is processed in first layer is still Poisson with rate $\alpha_{s}$
 It is assumed that there are dispatchers in each layer for each slice to divide the incoming traffic to VMs.
 Suppose the baseband processing of each VM is depicted as a M/M/1 processing queue.
+Each packet is routed by one of VMs of slices. So the mean delay of slice $s$ which is related to incoming traffic rate routed to
+each VM in first layer can be written as follow
+\begin{equation}
+d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}}
+\end{equation}
+Also, the delay in $s^{th}$ slice in second layer can be formulated as below
+\begin{equation}
+d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}
+\end{equation}
+In addition, the arrival data rate to the queue of wireless transmission
+ is equal to the arrival data rate of dispatcher.
+Moreover, it is assumed that the service time of transmission queue for each slice $s$ has 
+ an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue. Therefore, 
+the mean delay of transmission layer is 
+\begin{equation}
+d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}}
+\end{equation}
+Where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}R_{u(v,i)}$.
+\subsection{Physical Resource}
+Assume that for simplicity, each VM is mapped to one virtual network function (VNF). Each VNF requires
+physical resources which contain RAM, Memory and CPU.
+Let, the required resources for VNF $f$ in slice $s$ is represented by
+\begin{equation}
+\Omega_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \}
+\end{equation} 
+Where, $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU.
+Also, in the Core Network(CN), there are $N_{D}$ data centers(DC), which served VNFs. Each DC contains several servers that supply VNF's needs.
+The amount of RAM, Memory and CPU is denoted respectively by $\tau_{R_{j}}, \tau_{M_{j}}$ and $\tau_{C_{j}} $ for $j^{th}$ DC.
+\subsection{Problem Formulation}
 

### 2019-10-06 Latex/tex/pr.tex
add latex

@@
 \usepackage{cite}
+\usepackage{mathtools} 
 \usepackage{stackengine}
@@
 \usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
-\usepackage{algorithmic}
 \usepackage{graphicx}
@@
 \usepackage{xcolor}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \begin{document}
@@
 Where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}R_{u(v,i)}$.
+We define a new parameter which indicates mean delay of each slice
+\begin{equation}
+D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s
+\end{equation} 
 \subsection{Physical Resource}
-Assume that for simplicity, each VM is mapped to one virtual network function (VNF). Each VNF requires
+Assume each VM is mapped to one virtual network function (VNF) for simplicity. Each VNF requires
 physical resources which contain RAM, Memory and CPU.
@@
 The amount of RAM, Memory and CPU is denoted respectively by $\tau_{R_{j}}, \tau_{M_{j}}$ and $\tau_{C_{j}} $ for $j^{th}$ DC.
-\subsection{Problem Formulation}
-
+\begin{equation*}
+\tau_j = \{\tau_{R_{j}}, \tau_{M_{j}}, \tau_{C_{j}} \}
+\end{equation*}
+\subsection{Problem Statement}
+One of the most important parameters to estimate the optimality of the system is energy efficiency which is represented as sum-rate to sum-power as follow
+\begin{equation}
+\eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{R_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_{r_{tot}}(\boldsymbol{P},\boldsymbol{A})},
+\end{equation}
+Assume the power consumption of baseband processing at each data center that is mapped to VMs of a slice is depicted as
+$\phi$. So the total power can be represented as  
+\begin{equation*}
+\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}x_{s,d}\phi
+\end{equation*} 
+Where, $x_{s,d}$ is a binary variable which indicates whether $d^{th}$ data-center is mapped to VNFs of $s^{th}$ slice or not.\\
+In this paper, the main goal is to simultaneously maximize sum-rate and minimize sum-power with the presence of constraints which is written as follow, 
+\begin{subequations}
+\begin{alignat}{4}
+\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{X} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{X})} \\
+\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
+&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
+&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{max} && \quad \forall v, \forall k, \\                                 
+&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \\
+&D_{s} \leq D_{s}^{th}  &&\quad \forall s, \\
+& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \\
+& \sum_{d=1}^{D_c}\sum_{v=1}^{V}x_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
+& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} x_{s,d} \tau_d                       && \quad \forall f, \forall s 
+\end{alignat}
+\label{constraints}
+\end{subequations}
+Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{vs}]  \forall v , \forall s $ and $\boldsymbol{X} =[x_{s,d}]  \forall s , \forall d $.
+The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem. The First and main problem is
+\begin{subequations}
+\begin{alignat}{4}
+\max\limits_{\boldsymbol{P}, \boldsymbol{A} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})\\
+\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
+&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
+&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{max} && \quad \forall v, \forall k, \\                                 
+&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \\
+&D_{s} \leq D_{s}^{th}  &&\quad \forall s
+\end{alignat}
+\label{constraints1}
+\end{subequations}
+and the second problem is 
+\begin{subequations}
+\begin{alignat}{4}
+\min\limits_{\boldsymbol{X} }   \quad &   \phi_{tot}(\boldsymbol{X})\\
+\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
+& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \\
+& \sum_{d=1}^{D_c}\sum_{v=1}^{V}x_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
+& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} x_{s,d} \tau_d                       && \quad \forall f, \forall s 
+\end{alignat}
+\label{constraints2}
+\end{subequations}
+\subsection{Proposed Method}
+In this subsection, the proposed method is applied to solve the optimization problem. 
+\subsubsection{First Sub-Problem}
+In this part, we want to solve \eqref{constraints1}. Since the problem is non-convex, iterative algorithm is applied.
+To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} to 
+two different part that iteratively solve. 
+Firstly, we want to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = \boldsymbol{P}_{max}$ in the problem \eqref{constraints1}.
+This part of problem is solved in two different method.
+The first method is using MOSEK and second method is a heuristic method.
+The details of heuristic algorithm are represented in \textbf{Algorithm} \eqref{alg}.  
+\begin{algorithm}
+\caption{Mapping Slice to Service}\label{alg}
+\begin{algorithmic}[1]
+\State Sort Services according to their priority and the number of Users in the services and their requirements.
+\State Sort Slices according to the number of PRBs and number of RRHs and VMs  and their max of Capacities of resources. 
+\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
+\State Set the iteration index $i = 1$ and begin the iteration (Outer
+Loop).
+\For {$ 1\leq i \leq  Imax$}
+\State Solve the resource allocation problem with $\eta^{(i)}$ (Inner Loop);
+\State Obtain $P^{(i)}, R_{total}^{(i)}, P_{RRH}^{(i)}$
+\If {$ R_{total}(\boldsymbol{P}^{(i)}) - \eta^{(i)} P_{RRH}(\boldsymbol{P}^{(i)}) < \epsilon_{\eta} $} 
+\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
+\State break;
+\Else
+\State Set $\eta^{(i)}= \frac{R_{total}(\boldsymbol{P}^{(i))}}{P_{RRH}(\boldsymbol{P}^{(i))}}$ and $i= i+1$;
+\EndIf 
+\State \textbf{end if}
+\EndFor 
+\State \textbf{end for}
+\end{algorithmic}
+\end{algorithm}
 \section*{References}

### 2019-10-06 Latex/tex/pr.tex
complete more for latex file of icc

@@
 \begin{equation}\label{eq3}
-\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k}+ \boldsymbol{z}_{\mathcal{U}_v}
+\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s}+ \boldsymbol{z}_{\mathcal{U}_v}
 \end{equation}
@@
 \\
-Furthermore, $\zeta_{U_v,k} \delequal \{\zeta_{u(v,1),k},\zeta_{u(v,2),k},...,\zeta_{u(v,N_{U_v}),k}\}$,
-$\zeta_{u(v,i),k} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks(PRB) to UE.
+Furthermore, $\zeta_{U_v,k,s} \delequal \{\zeta_{u(v,1),k,s},\zeta_{u(v,2),k,s},...,\zeta_{u(v,N_{U_v}),k,s}\}$,
+$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks(PRB) to UE.
 Also as defined before, $\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
@@
 \end{equation}
-where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(a_{r_{(s,1),u_{(v,i)}}},\ldots,a_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
+where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
 represents the large scale fading matrix. Here, it is assumed we have perfect channel state information(CSI).
@@
  I_{u_{(v,i)}} &= 
- \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{vs}\zeta_{u_(v,i),n}\zeta_{u_(v,l),n}}_{\text{(intra-service interference)}}\\
-&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{ys} \zeta_{u_(v,i),n}\zeta_{u_(y,l),n}}_{\text{(inter-service interference)}}\\
+ \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{vs}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
+&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{ys} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
 &+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{vs}}_{\text{(quantization noise interference)}}.
@@
 \begin{equation*}
-\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}x_{s,d}\phi
+\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi
 \end{equation*} 
-Where, $x_{s,d}$ is a binary variable which indicates whether $d^{th}$ data-center is mapped to VNFs of $s^{th}$ slice or not.\\
+Where, $y_{s,d}$ is a binary variable which indicates whether $d^{th}$ data-center is mapped to VNFs of $s^{th}$ slice or not.\\
 In this paper, the main goal is to simultaneously maximize sum-rate and minimize sum-power with the presence of constraints which is written as follow, 
@@
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{X} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{X})} \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{Y})} \\
 \text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
@@
 & \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \\
-& \sum_{d=1}^{D_c}\sum_{v=1}^{V}x_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
-& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} x_{s,d} \tau_d                       && \quad \forall f, \forall s 
+& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
+& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_d                       && \quad \forall f, \forall s 
 \end{alignat}
@@
 \end{subequations}
-Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{vs}]  \forall v , \forall s $ and $\boldsymbol{X} =[x_{s,d}]  \forall s , \forall d $.
+Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{vs}]  \forall v , \forall s $ and $\boldsymbol{Y} =[y_{s,d}]  \forall s , \forall d $.
 The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem. The First and main problem is
@@
 \begin{alignat}{4}
-\min\limits_{\boldsymbol{X} }   \quad &   \phi_{tot}(\boldsymbol{X})\\
+\min\limits_{\boldsymbol{y} }   \quad &   \phi_{tot}(\boldsymbol{Y})\\
 \text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
 & \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \\
-& \sum_{d=1}^{D_c}\sum_{v=1}^{V}x_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
-& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} x_{s,d} \tau_d                       && \quad \forall f, \forall s 
+& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
+& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_d                       && \quad \forall f, \forall s 
 \end{alignat}
@@
 \State Sort Slices according to the number of PRBs and number of RRHs and VMs  and their max of Capacities of resources. 
-\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
-\State Set the iteration index $i = 1$ and begin the iteration (Outer
-Loop).
+\State Set the maximum number of iterations $I_{max}$
 \For {$ 1\leq i \leq  Imax$}

### 2019-10-06 Latex/tex/pr.tex
comlete part of latex

@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\allowdisplaybreaks
+\newtheorem{remark}{Remark}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
 
@@
 \subsection{System Model}
-Suppose that there are $S$ Slices Serving $V$ Services.
+Suppose that there are $S$ slices Serving $V$ services.
 Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service.
@@
 Also each RRH and PRB can serve more than one slice.
-It is considered that in BBU, the system has 2 processing layer consists of $M_1$ homogeneous VMs in first layer and $M_2$ homogeneous VMs in second layer.
+It is considered that in BBU, the system has two processing layer consists of $M_1$ homogeneous VMs in first layer and $M_2$ homogeneous VMs in second layer.
 \subsection{Achievable Rate}
@@
 \subsection{Mean Delay}
-Suppose that we have two processing layer in BBU of O-RAN system.
+Suppose that we have two processing layer in BBU of O-RAN system. The lower layer is consist of PHY and MAC and the upper layer is consist of RLC, PDCP and SDAP.\newline   
 As it is mentioned before, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer.
@@
 \max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{Y})} \\
-\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
-&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
-&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{max} && \quad \forall v, \forall k, \\                                 
-&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \\
-&D_{s} \leq D_{s}^{th}  &&\quad \forall s, \\
-& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \\
-& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
-& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_d                       && \quad \forall f, \forall s 
+\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i, 
+ \label{c11} \\
+&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k,\label{c12} \\
+&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k,\label{c13} \\                                 
+&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \label{c14}\\
+&D_{s} \leq D_{s}^{th}  &&\quad \forall s,\label{c15} \\
+& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \label{c21} \\
+& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s,\label{c23} \\
+& \sum_{f=1}^{F_s}\Omega_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_d                      
+ && \quad \forall f, \forall s  \label{c22}
 \end{alignat}
@@
 Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{vs}]  \forall v , \forall s $ and $\boldsymbol{Y} =[y_{s,d}]  \forall s , \forall d $. 
+Equation \eqref{c11}, \eqref{c12} indicates respectively that the power of each RRH do not exceed the maximum power and power of each UE is a positive integer value.
+Also \eqref{c13} shows that the rate of each UE is more than a threshold.
+\eqref{c14} and \eqref{c15} depicts respectively that the capacity of fronthaul link is limited and the delay of receiving signal should be less than a threshold.
+Furthermore, \eqref{c21}
+ensure that each service is mapped to one or more slice.
+Also, \eqref{c23} guarantee that each slice (VNFs in two layers of slice) has been placed to one or more physical resources (DC). Moreover, in \eqref{c22}  $\mathfrak{z}\in \{M,R,C\}$, which supports 
+that we have enough physical resource for VNFs of each slice.\newline 
 The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem. The First and main problem is
@@
 &p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
-&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{max} && \quad \forall v, \forall k, \\                                 
+&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\                                 
 &C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \\
@@
 \end{subequations}
-\subsection{Proposed Method}
+\subsection{Proposed Method For Problem \eqref{constraints1}}
 In this subsection, the proposed method is applied to solve the optimization problem.
+We want to solve \eqref{constraints1}. Since the problem is non-convex, iterative algorithm is applied.
+To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} to 
+two different part that can be solved iteratively.  
 \subsubsection{First Sub-Problem}
-In this part, we want to solve \eqref{constraints1}. Since the problem is non-convex, iterative algorithm is applied.
-To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} to 
-two different part that iteratively solve. 
-Firstly, we want to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = \boldsymbol{P}_{max}$ in the problem \eqref{constraints1}.
-This part of problem is solved in two different method.
-The first method is using MOSEK and second method is a heuristic method.
+Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = \boldsymbol{P}_{max}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration.
+Two different method is applied to acquire $\boldsymbol{A}$.
+The first method is using MOSEK and second method is a heuristic algorithm.
 The details of heuristic algorithm are represented in \textbf{Algorithm} \eqref{alg}.  
@@
 \begin{algorithmic}[1]
-\State Sort Services according to their priority and the number of Users in the services and their requirements.
-\State Sort Slices according to the number of PRBs and number of RRHs and VMs  and their max of Capacities of resources. 
-\State Set the maximum number of iterations $I_{max}$
-\For {$ 1\leq i \leq  Imax$}
-\State Solve the resource allocation problem with $\eta^{(i)}$ (Inner Loop);
-\State Obtain $P^{(i)}, R_{total}^{(i)}, P_{RRH}^{(i)}$
-\If {$ R_{total}(\boldsymbol{P}^{(i)}) - \eta^{(i)} P_{RRH}(\boldsymbol{P}^{(i)}) < \epsilon_{\eta} $} 
-\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
-\State break;
+\State Sort services according to their priority, the number of UEs in it and their requirements in descending order.
+\State Sort slices according to the number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in descending order. 
+\For {$ 1\leq i \leq  S$}
+\For {$ 1\leq j \leq  V$}
+\State Set $a_{ij} = 1$
+\State Obtain Parameters of System
+\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} is not applied} 
+\State Set $a_{ij} = 0$;
 \Else
-\State Set $\eta^{(i)}= \frac{R_{total}(\boldsymbol{P}^{(i))}}{P_{RRH}(\boldsymbol{P}^{(i))}}$ and $i= i+1$;
+\State break from inner loop;
 \EndIf 
@@
 \State \textbf{end for}
+\EndFor 
+\State \textbf{end for}
 \end{algorithmic}
 \end{algorithm}
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\subsubsection{Second Sub-Problem}
+In this part, by assuming that $\boldsymbol{A}$ is fixed, the optimal power of UEs in each service is achieved.
+\begin{theorem}\label{t2}
+ $\eta^*$ which is the optimum energy efficiency can be achieved if
+\begin{equation}\label{q2}
+\begin{split}
+&\max \limits_{\boldsymbol{P}} (R_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=\\
+& R_{total}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
+\end{split}
+\end{equation}
+\end{theorem}
+Using Lagrangian function and iterative algorithm, can solve this subproblem. 
+%\section*{References}
 

### 2019-10-08 Latex/tex/pr.tex
latex continue

@@
 and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$.
+It is assumed that interference signal applied from UEs with same PRB.
 let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from $j^{th}$ RRH in $s^{th}$ slice.
@@
 In this subsection, the proposed method is applied to solve the optimization problem.
-We want to solve \eqref{constraints1}. Since the problem is non-convex, iterative algorithm is applied.
+We want to solve \eqref{constraints1}. Since the problem is non-convex and NP-Hard iterative algorithm is applied.
 To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} to 
@@
 \subsubsection{First Sub-Problem}
-Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = \boldsymbol{P}_{max}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration.
+Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration.
 Two different method is applied to acquire $\boldsymbol{A}$.
@@
 \end{theorem}
-Using Lagrangian function and iterative algorithm, can solve this subproblem. 
+This subproblem can  be solved using Lagrangian function and iterative algorithm. 
+Since, Interference is a function of power of UEs, for simplicity, we assume an upper bound for interference (the worst-case) as follow
+\begin{equation}
+\begin{split}
+ \bar{I}_{u_{(v,i)}} &= 
+ \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{max} a_{vs}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
+&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{max}   a_{ys} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
+&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{vs}}_{\text{(quantization noise interference)}}.
+\end{split}
+\end{equation}
+where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
+and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$.\newline
+Lagrangian function is written as follow
+\begin{equation}
+\begin{split}
+\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}} 
+- \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
+&+\sum\limits_{s=1}^{S} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{d_{(s,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
+&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
+&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (C_{r_{(s,i)}}-C_{r_{(s,i)}}^{max}).\\ 
+&- \sum\limits_{s=1}^{S}  \kappa_{r_{(s,i)}} (D_{s}-D_{s}^{max}).\\ 
+\end{split}
+\end{equation}
+
 %\section*{References}

### 2019-10-10 Latex/tex/pr.tex
paper prepare abstract

@@
 \usepackage[noend]{algpseudocode}
+\usepackage{amsthm}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{abstract}
-
+Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a global 'carrier-led' effort to bring greater transparency of Open-RAN 
+(O-RAN), to the next-generation of radio access network. \newline
+To increase energy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method in 5G in order to virtualize the common physical network into several logical end-to-end networks.
+Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to end network.
+\newline
+In this paper, we elaborates joint NS in RAN and Core of O-RAN system and investigate optimal power 
+of each User Equipment (UE) to jointly maximize Energy Efficiency and minimize consumption power of physical resources in a downlink channel.
+The problem is formulated as a mixed integer optimization problem that can be decompose into two independent sub-problems for RAN and Core.
+Heuristic algorithms is proposed to each of sub-problems to solved the first sub-problem in order to simultaneously map slices to services and optimize power and the second sub-problem in order to map slices to physical resources and minimize number of active Data Centers (DC).
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+O-RAN, Network Slicing, Energy Efficiency, Data Center
 \end{IEEEkeywords}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
 
@@
 \begin{equation}\label{eq2}
-\rho_{u(v,i)} =  \frac{P_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}}
+\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}}
 \end{equation}
-Where, $P_{u(v,i)}$ represents the transmitted power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 
+Where, $p_{u(v,i)}$ represents the transmitted power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 
 $\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
@@
 Furthermore, $\zeta_{U_v,k,s} \delequal \{\zeta_{u(v,1),k,s},\zeta_{u(v,2),k,s},...,\zeta_{u(v,N_{U_v}),k,s}\}$,
-$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks(PRB) to UE.
+$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks (PRB) to UE.
 Also as defined before, $\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
@@
 and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$.
-It is assumed that interference signal applied from UEs with same PRB.
+It is assumed that interference signal for each UE, is applied from UEs which are using same PRB.
+If we replace $p_{u_{(v,l)}}$ and $p_{u_{(y,l)}}$ by $P_{max}$, an upper bound $\bar{I}_{u_{(v,i)}}$ is obtained for $I_{u_{(v,i)}}$.
+Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in equation \eqref{eq1} and \eqref{eq2}.\newline
 let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from $j^{th}$ RRH in $s^{th}$ slice.
@@
 physical resources which contain RAM, Memory and CPU.
-Let, the required resources for VNF $f$ in slice $s$ is represented by
+Let, the required resources for VNF $f$ in slice $s$ is represented by a three dimensional vector as follow
 \begin{equation}
-\Omega_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \}
+\bar{\Omega}_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \}
 \end{equation} 
-Where, $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU.
-Also, in the Core Network(CN), there are $N_{D}$ data centers(DC), which served VNFs. Each DC contains several servers that supply VNF's needs.
+Where,$\bar{\Omega}_{(f,s)}\in \mathbb{C}^{3}$ and $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU.
+Moreover total amount of required RAM, Memory and CPU of all VNFs in a slice is a three dimension vector which is defined as
+\begin{equation}
+\bar{\Omega}_{s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{(f,s)}
+\end{equation}
+Where, $F_s = M_{s_1} + M_{s_2}$ is the total number of VNFs in slice $s$.
+\newline
+Also, in the Core Network (CN), there are $N_{D}$ data centers(DC), which served VNFs. Each DC contains several servers that supply VNF's needs.
 The amount of RAM, Memory and CPU is denoted respectively by $\tau_{R_{j}}, \tau_{M_{j}}$ and $\tau_{C_{j}} $ for $j^{th}$ DC.
@@
 \end{equation*}
+Also we define a weighted parameter of $\tau_j$ as follow
+\begin{equation}\label{wt}
+\begin{split}
+\hat{\Omega}_{s}^{tot} &= w_R \bar{\Omega}_{R_s}^{tot} + w_M \bar{\Omega}_{M_s}^{tot} + w_C \bar{\Omega}_{C_s}^{tot} \\
+\hat{\tau}_j &= w_R \tau_{R_{j}} + w_M \tau_{M_{j}} + w_C \tau_{C_{j}}
+\end{split}
+\end{equation}
+Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ are the weight of RAM, Memory and CPU.
 \subsection{Problem Statement}
@@
 \begin{equation}
-\eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{R_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_{r_{tot}}(\boldsymbol{P},\boldsymbol{A})},
+\eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_{r_{tot}}(\boldsymbol{P},\boldsymbol{A})},
 \end{equation}
-Assume the power consumption of baseband processing at each data center that is mapped to VMs of a slice is depicted as
+Assume the power consumption of baseband processing at each data center that is mapped to VNFs of a slice is depicted as
 $\phi$. So the total power can be represented as  
@@
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{Y})} \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{Y})} \\
 \text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i, 
@@
 &C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \label{c14}\\
-&D_{s} \leq D_{s}^{th}  &&\quad \forall s,\label{c15} \\
+&D_{s} \leq D_{s}^{max}  &&\quad \forall s,\label{c15} \\
 & \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \label{c21} \\
 & \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s,\label{c23} \\
-& \sum_{f=1}^{F_s}\Omega_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_d                      
- && \quad \forall f, \forall s  \label{c22}
+& \bar{\Omega}_{\mathfrak{z}(s)}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                      
+ && \quad \forall \mathfrak{z}, \forall s  \label{c22}
 \end{alignat}
@@
 that we have enough physical resource for VNFs of each slice.\newline 
-The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem. The First and main problem is
+The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem A and B. The problem A is introduced as bellow
 \begin{subequations}
@@
 &\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\                                 
-&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \\
-&D_{s} \leq D_{s}^{th}  &&\quad \forall s
+&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i,\label{cc14} \\
+&D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
+& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s
 \end{alignat} 
@@
 \end{subequations}
-and the second problem is 
+and the problem B is 
 \begin{subequations}
@@
 \min\limits_{\boldsymbol{y} }   \quad &   \phi_{tot}(\boldsymbol{Y})\\
-\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
-& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \\
-& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
-& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_d                       && \quad \forall f, \forall s 
+\text{subject to} \quad & \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
+&  \bar{\Omega}_{\mathfrak{z}(s)}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                      
+ && \quad \forall \mathfrak{z}, \forall s\label{eqomega}
 \end{alignat}
@@
 \end{subequations}
-\subsection{Proposed Method For Problem \eqref{constraints1}}
+\section{Proposed Method For Problem \eqref{constraints1}}
 In this subsection, the proposed method is applied to solve the optimization problem.
@@
 two different part that can be solved iteratively.  
-\subsubsection{First Sub-Problem}
+\subsection{First Part of Sub-Problem A}\label{firstsub}
 Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration.
@@
 \State Sort slices according to the number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in descending order. 
-\For {$ 1\leq i \leq  S$}
-\For {$ 1\leq j \leq  V$}
+\For {$i \gets 1$ to $S$}
+\For {$j \gets 1$ to $V$}
 \State Set $a_{ij} = 1$
@@
 \end{algorithm}
-\subsubsection{Second Sub-Problem}
+\subsection{Second Part of Sub-Problem A}\label{secondsub}
 In this part, by assuming that $\boldsymbol{A}$ is fixed, the optimal power of UEs in each service is achieved.
@@
 \begin{split}
-&\max \limits_{\boldsymbol{P}} (R_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=\\
-& R_{total}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
+&\max \limits_{\boldsymbol{P}} (\mathfrak{R}_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=\\
+& \mathfrak{R}_{tot}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
 \end{split}
@@
 \end{theorem}
-This subproblem can  be solved using Lagrangian function and iterative algorithm. 
-Since, Interference is a function of power of UEs, for simplicity, we assume an upper bound for interference (the worst-case) as follow
-\begin{equation}
-\begin{split}
- \bar{I}_{u_{(v,i)}} &= 
- \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{max} a_{vs}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
-&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{max}   a_{ys} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
-&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{vs}}_{\text{(quantization noise interference)}}.
-\end{split}
-\end{equation}
-where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
-and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$.\newline
+\begin{proof}
+See Appendix A
+\end{proof}
+The second subproblem can  be solved using Lagrangian function and iterative algorithm. 
+Since, Interference is a function of power of UEs, for simplicity, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference (the worst-case). 
+In order to make equation \eqref{constraints1} as a standard form of convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15}.
 Lagrangian function is written as follow
-\begin{equation}
+\begin{equation}\label{lagrang}
 \begin{split}
@@
 &- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
-&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (C_{r_{(s,i)}}-C_{r_{(s,i)}}^{max}).\\ 
-&- \sum\limits_{s=1}^{S}  \kappa_{r_{(s,i)}} (D_{s}-D_{s}^{max}).\\ 
+&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,j)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\ 
+&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{vs}.\\ 
 \end{split}
 \end{equation}
-
+Where,$\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$.
+Also, $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers which have non-zero positive elements.
+Optimal power is obtained from equation \eqref{lagrang} as follow
+\begin{equation}
+p_{u(v,i)}^{*} = \frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }
+\end{equation}
+where, $\mathfrak{y}_{u(v,i)}= (-\mu_{u(v,i)}+\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and 
+$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}$. Also 
+$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} (\xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$. 
+By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained. 
 %\section*{References}
-
+\subsection{Solving two part of Sub-problem A iteratively}
+In \eqref{firstsub} and \eqref{secondsub} the details of solving each part of subproblem is depicted. 
+Here, the algorithm of solving sub-problem A is shown in \textbf{Algorithm} \eqref{alg2}
+\begin{algorithm}
+\caption{Joint Network Slicing and Power Allocation}\label{alg2}
+\begin{algorithmic}[1]
+\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
+\State Set $\boldsymbol{P} = \boldsymbol{P}_{max}$
+\For {$counter \gets 1$ to $I_{max}$}
+\State Achieve $\boldsymbol{A}$ by applying Algorithm \eqref{alg}
+\State Obtain $\boldsymbol{P}$ by using sub-gradient method which is mentioned in \eqref{secondsub}.
+\If {$ \mathfrak{R}_{tot}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) - \eta^{(i)} P_{r_{tot}}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) < \epsilon_{\eta} $} 
+\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $, $\boldsymbol{A}^*= \boldsymbol{A}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
+\State break;
+\Else
+\State $i= i+1$, Setting $\boldsymbol{P} = \boldsymbol{P}^{(i)}$ ;
+\EndIf 
+\State \textbf{end if}
+\EndFor 
+\State \textbf{end for}
+\end{algorithmic}
+\end{algorithm}
+\subsection{Sub-Problem B}
+In this subsection, we want to solve equation \eqref{constraints2} which is the placement of virtual resources to physical resource in order to minimize the number of using DCs. 
+To achieve optimum $\boldsymbol{Y}$ heuristic algorithm and Mosek is applied.
+The details of heuristic algorithm is written in \textbf{Algorithm} \eqref{alg3}.
+In this algorithm, if a slice does not admit to a specific DC, it is remain for next placement.
+In next placement the residual slices, map to more than one DC according to their requirements.
+\begin{algorithm}
+\caption{Plecement of Physical resources into Virtual resources}\label{alg3}
+\begin{algorithmic}[1]
+\State Sort Slices according to $\hat{\Omega}_{s}^{tot} , \forall s$ in descending order.
+\State Sort DCs according to $\hat{\tau}_j , \forall j$ in descending order. 
+\State $\boldsymbol{Y} = \boldsymbol{0}$
+\For {$d \gets 1$ to $D_c$}
+\For {$s \gets 1$ to $S$}
+\If {$\sum_{d=1}^{D_c}y_{s,d}==0$ and $\bar{\Omega}_{\mathfrak{z}(s)}^{tot} \leq \tau_{\mathfrak{z}_j} \forall \mathfrak{z}, \forall s$  } 
+\State Set $y_{s,d} = 1$;
+\State {$\tau_j$ $\gets$ {$\tau_j - \bar{\Omega}_{s}^{tot}$}}
+\EndIf 
+\State \textbf{end if}
+\EndFor 
+\State \textbf{end for}
+\EndFor 
+\State \textbf{end for}
+\State  $\{ind_{residual} = s|({\sum_{d=1}^{D_c}y_{s,d}==0})\}$
+\State Sort residual amount of DCs same as before in descending order.
+\State Sort residual slices same as before in descending order.
+\For {$r \gets 1$ to $S_{residual}$}
+\For {$n \gets 1$ to $D_c$}
+\State Set $y_{s,d} = 1$;
+\State {$\bar{\Omega}_{s}^{tot}$ $\gets$ {$\bar{\Omega}_{s}^{tot}- \tau_j$}}
+\If {$\bar{\Omega}_{s}^{tot}==0$}
+\State Set $y_{s,d} = 1$;
+\State {$\tau_j$ $\gets$ {$\tau_j - \bar{\Omega}_{s}^{tot}$}}
+\State {break inner loop}
+\EndIf 
+\State \textbf{end if}
+\EndFor 
+\State \textbf{end for}
+\EndFor 
+\State \textbf{end for}
+\end{algorithmic}
+\end{algorithm}
+\section{Simulation}
+In this section, Simulation and numerical results for the main problem are depicted.
 \end{document}

### 2019-10-11 Latex/tex/pr.tex
introduction add

@@
 \section{Introduction}
-
+Recently, O-RAN which is the integration and expansion of C-RAN and xRAN is expected to be a key technology for 5G to enhance RAN performance and solve the challenges in a best way.  
+There are two main ideas here: According to real-time analytics which is used for artificial intelligence system is evolving the radio access networks to make them more open and smarter than previous generations.
+Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces.
+\newline
+The core idea driving C-RAN is to split radio remote head (RRH) and baseband unit (BBU).
+Several BBUs operating on a cloud server will create a BBU-pool, providing unified baseband signal processing with powerful computing capabilities.
+Moreover, in O-RAN technology, this separation is implemented.\newline
+xRAN technology has three fundamental feature.
+Control plane is decoupled from User plane.
+In addition, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
+Moreover, open north-bound and south-bound interfaces is introduced.
+\begin{figure}[H]
+  \centering
+    \includegraphics[scale=0.45]{c2}
+  \caption{Network sliced O-RAN system}
+  \label{fig:c11}
+\end{figure} 
+Responsibility of wireless systems of the fifth generation covers a wide range types of services.
+In order to provide the requirement of these services, Network Slicing (NS) is implemented to virtualize the common physical network into several logical end-to-end networks.
+\newline
+To communicate between BBU-pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity.
+Compression of message which is passed through these links, is a consequence of limited fronthaul capacity.\\
+In BBU-Pool, using cloud-computing, enhance performance of system by virtualizing resources
+into virtual machines (VMs).
+Each VM has a computing processor which is mapped to Virtual Network Functions (VNFs) which is processed arrival data. Also VNFs are mapped to physical resource through NS technique. \newline
+In this paper, in figure \eqref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
+their service requirements.
+Also RAN is decoupled to slices to provides services needs.
+Optimal power allocation and joint mapping slices to services is applied.
+In addition, mapping slices to physical resources is considered too.
 \section{System Model and Problem Formulation}

### 2019-10-13 codes/thirdPart/simulations/moreVM.m
add matlab code plot

@@ -1,0 +1,18 @@
+%% if service need more than one VM
+ %mapStatus = sum(mappingVar,2);
+ index_notMap = find(mapStatus == 1);
+ remain_source = sorting(resourceShare, N_resource, weight, N_server);
+ resourceShare1 = remain_source(:,2:4);
+ demand_service2= demand_service1(:,2:4);
+ for i=index_notMap
+    for j = N_server:-1:1
+        demand_service2(i,:) = -resourceShare1(j,:)+ demand_service2(i,:);
+        indMap = find(resourceShare1(j,1)==resourceShare(:,1));
+        mappingVar(i,indMap) = 1;
+        if all(demand_service2(i,:) <= 0)
+            j = 0;
+            break;
+        end
+        
+    end
+ end

### 2019-10-13 Latex/tex/pr.tex
add matlab code plot
add sth

@@
 their service requirements.
-Also RAN is decoupled to slices to provides services needs.
+Also RAN is decoupled to slices to provide services needs.
 Optimal power allocation and joint mapping slices to services is applied.
@@
 $\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}\lambda_{u(v,i)}$.  
-Furthermore, the mean arrival rate of second layer is approximately equal to the mean arrival rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the arrival packets of second layer which is processed in first layer is still Poisson with rate $\alpha_{s}$
+Furthermore, the mean arrival rate of second layer is approximately equal to the mean arrival rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the arrival packets of second layer which is processed in first layer is still Poisson with rate $\alpha_{s}$.
 It is assumed that there are dispatchers in each layer for each slice to divide the incoming traffic to VMs.
@@
 \newline
-Also, in the Core Network (CN), there are $N_{D}$ data centers(DC), which served VNFs. Each DC contains several servers that supply VNF's needs.
+Also, in the Core Network (CN), there are $D_c$ data centers (DC), which served VNFs. Each DC contains several servers that supply VNF's needs.
 The amount of RAM, Memory and CPU is denoted respectively by $\tau_{R_{j}}, \tau_{M_{j}}$ and $\tau_{C_{j}} $ for $j^{th}$ DC.
@@
 In this section, Simulation and numerical results for the main problem are depicted.
+\bibliographystyle{ieeetr}
+\bibliography{ref}
 \end{document}

### 2019-10-17 Latex/tex/pr.tex
mat file
add fig

@@
 of each User Equipment (UE) to jointly maximize Energy Efficiency and minimize consumption power of physical resources in a downlink channel.
-The problem is formulated as a mixed integer optimization problem that can be decompose into two independent sub-problems for RAN and Core.
+The problem is formulated as a mixed integer optimization problem that can be decompose into two independent sub-problems for RAN and Core since sub-problems are independent.
 Heuristic algorithms is proposed to each of sub-problems to solved the first sub-problem in order to simultaneously map slices to services and optimize power and the second sub-problem in order to map slices to physical resources and minimize number of active Data Centers (DC).
@@
 Recently, O-RAN which is the integration and expansion of C-RAN and xRAN is expected to be a key technology for 5G to enhance RAN performance and solve the challenges in a best way.  
-There are two main ideas here: According to real-time analytics which is used for artificial intelligence system is evolving the radio access networks to make them more open and smarter than previous generations.
-Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces.
+The Idea of O-RAN comes from two opinion.
+Firstly, according to real-time analytic used for artificial intelligence system, the radio access networks must be evolved to be more open and smarter than previous generations.
+Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}.
 \newline
@@
 Several BBUs operating on a cloud server will create a BBU-pool, providing unified baseband signal processing with powerful computing capabilities.
-Moreover, in O-RAN technology, this separation is implemented.\newline
-xRAN technology has three fundamental feature.
+Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
+To communicate between BBU-pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity.
+Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud}.
+In BBU-Pool, using cloud-computing, enhance performance of system by virtualizing resources
+into virtual machines (VMs).
+Each VM has a computing processor which is mapped to Virtual Network Functions (VNFs) which is processed arrival data.
+Also VNFs are mapped to physical resource through NS technique\cite{frdl,luong2018novel,luong2018novel1}.
+\newline
+xRAN technology ,released in April 2018 as a next generation of RAN, has three fundamental features.
 Control plane is decoupled from User plane.
 In addition, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
-Moreover, open north-bound and south-bound interfaces is introduced.
+Moreover, open north-bound and south-bound interfaces is introduced\cite{xran}.
 \begin{figure}[H]
   \centering
-    \includegraphics[scale=0.45]{c2}
+    \includegraphics[scale=0.55]{c2}
   \caption{Network sliced O-RAN system}
@@
 Responsibility of wireless systems of the fifth generation covers a wide range types of services.
-In order to provide the requirement of these services, Network Slicing (NS) is implemented to virtualize the common physical network into several logical end-to-end networks.
+In order to provide the requirement of these services, NS is implemented to virtualize the common physical network into several logical end-to-end networks.
+Three different types of NS is introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing.
+In Core-RAN Slicing, each slice of RAN is mapped to slices of Core.
 \newline
-To communicate between BBU-pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity.
-Compression of message which is passed through these links, is a consequence of limited fronthaul capacity.\\
-In BBU-Pool, using cloud-computing, enhance performance of system by virtualizing resources
-into virtual machines (VMs).
-Each VM has a computing processor which is mapped to Virtual Network Functions (VNFs) which is processed arrival data. Also VNFs are mapped to physical resource through NS technique. \newline
-In this paper, in figure \eqref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
+In this paper, as  mentioned in figure \eqref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
 their service requirements.
@@
 In this section, Simulation and numerical results for the main problem are depicted.
+\begin{figure}[H]
+  \centering
+    \includegraphics[scale=0.5]{fig1}
+  \caption{algorithm}
+  \label{fig:c11}
+\end{figure} 
 \bibliographystyle{ieeetr}

### 2019-10-17 Latex/tex/pr.tex
add fig1
add fig corrected

@@
 In Core-RAN Slicing, each slice of RAN is mapped to slices of Core.
+Each slice of RAN consists of RRHs, PRB
 \newline
-In this paper, as  mentioned in figure \eqref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
+
+In this paper, as  depicted in figure \eqref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
 their service requirements.
@@
   \centering
-    \includegraphics[scale=0.5]{fig1}
+    \includegraphics[width=\linewidth]{f1}
   \caption{algorithm}

### 2019-10-17 Latex/tex/pr.tex
pow.mat + latex updATE

@@
 The core idea driving C-RAN is to split radio remote head (RRH) and baseband unit (BBU).
-Several BBUs operating on a cloud server will create a BBU-pool, providing unified baseband signal processing with powerful computing capabilities.
+Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities.
 Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
-To communicate between BBU-pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity.
-Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud}.
-In BBU-Pool, using cloud-computing, enhance performance of system by virtualizing resources
-into virtual machines (VMs).
-Each VM has a computing processor which is mapped to Virtual Network Functions (VNFs) which is processed arrival data.
-Also VNFs are mapped to physical resource through NS technique\cite{frdl,luong2018novel,luong2018novel1}.
-\newline
+To communicate between BBU-Pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity.
+Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.\newline
 xRAN technology ,released in April 2018 as a next generation of RAN, has three fundamental features.
@@
 \end{figure} 
+To evolve servicing in 5G, separation of elements of software and hardware of network is deployed in network functions virtualization (NFV) technology.
+In this technology, the functionality of networks is virtualized and divided to blocks of virtual network function (VNF).
 Responsibility of wireless systems of the fifth generation covers a wide range types of services.
@@
 In Core-RAN Slicing, each slice of RAN is mapped to slices of Core.
-Each slice of RAN consists of RRHs, PRB
+Also, UEs classified to group of services according to their requirements.
+In addition, each service is connected to one or more Core-RAN slices base on the resource of slices.
+Using cloud-computing in BBU-Pool, enhance performance of system by virtualizing resources
+into virtual machines (VMs).
+Each VM has a computing processor mapped to Virtual Network Functions (VNFs) which processed arrival data.
+Also VNFs are mapped to physical resource through NS technique\cite{frdl,luong2018novel,luong2018novel1}.
 \newline  
-
-In this paper, as  depicted in figure \eqref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
+In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum rate.
+Moreover, in \cite{frdl,luong2018novel,luong2018novel1} minimization of cost obtained by power consumption and cloud processing is applied.
+Limited fronthaul capacity is considered.
+Also processing delay of each VM and wireless transmission delay is bounded.\newline
+In this paper, as  depicted in figure \ref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
 their service requirements.
 Also RAN is decoupled to slices to provide services needs.
-Optimal power allocation and joint mapping slices to services is applied.
-In addition, mapping slices to physical resources is considered too.
+Optimal power allocation and joint connecting slices to services is applied.
+In addition, mapping slices to physical resources is taken to account.
+
 \section{System Model and Problem Formulation}
@@
 Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service.
-Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $N_s$ PRBs.
-All the RRHs in a slice that is mapped to a service, transmit signals to all the UEs in specific service.
+Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $N_s$ Physical Resource Blocks (PRBs) as it is defined in standard of LTE that the bandwidth (BW) of channel is divided to PRBs in time series \cite{lee2018dynamic}.
+All RRHs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}.
 Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity.
-Also each RRH and PRB can serve more than one slice.
-It is considered that in BBU, the system has two processing layer consists of $M_1$ homogeneous VMs in first layer and $M_2$ homogeneous VMs in second layer.
+Suppose that we have two processing layer in BBU-Pool of O-RAN system. The lower layer is consist of PHY and MAC and the upper layer is consist of RLC, PDCP and SDAP.
+Assume, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer.
+for simplicity, suppose ach VM is connected to a VNF.
+Each VNF in both layers maps to one or more slices.
+So in $s^{th}$ slice, there are $M_{s_1}$ VNFs in first layer and $M_{s_2}$ VNFs in second layer.
+All VNFs in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively.
+Also RRHs and PRBs can serve more than one slices. 
 \subsection{Achievable Rate}
-In this subsection, the Achievable Rate is obtained as below.
 The achievable data rate for $i^{th}$ UE in $v^{th}$ service can be written as 
 \begin{equation}\label{eq1}
-\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}})
+\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}});
 \end{equation}
-where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from 
+Where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from 
 \begin{equation}\label{eq2}
-\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}}
+\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}};
 \end{equation}
-Where, $p_{u(v,i)}$ represents the transmitted power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 
+Where, $p_{u(v,i)}$ represents the transmition power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 
 $\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
 In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the the transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
-Moreover, $BN_0$ denotes the power of guassian additive noise and $I_{u(v,i)}$ is the power of interfering signals.
-To obtain SNR as formulated in equation \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service which is given by equation \eqref{eq3}
+Moreover, $BN_0$ denotes the power of Guassian additive noise and $I_{u(v,i)}$ is the power of interfering signals.
+To obtain SNR as formulated in \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service which is given by \eqref{eq3}
 \begin{equation}\label{eq3}
-\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s}+ \boldsymbol{z}_{\mathcal{U}_v}
+\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s}+ \boldsymbol{z}_{\mathcal{U}_v};
 \end{equation}
-where $\boldsymbol{x}_{ \mathcal{R}_s} = [x_{ r_{(s,1)}},...,x_{ r_{(s,\mathcal{R}_s)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector for the $s$-th set of Network slice,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
+Where $\boldsymbol{x}_{ \mathcal{R}_s} = [x_{ r_{(s,1)}},...,x_{ r_{(s,\mathcal{R}_s)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector for the $s$-th set of Network slice,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
 In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which is made from signal compression in BBU.
@@
 \subsection{Mean Delay}
-Suppose that we have two processing layer in BBU of O-RAN system. The lower layer is consist of PHY and MAC and the upper layer is consist of RLC, PDCP and SDAP.\newline   
-As it is mentioned before, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer.
-Each VM in both layers map to one or more slices.
-So in $s^{th}$ slice, there are $M_{s_1}$ VMs in first layer and $M_{s_2}$ VMs in second layer.
-Each VM in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively.
-\\
 Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for $i^{th}$ UE in $v^{th}$ service. 

### 2019-10-17 Latex/tex/pr.tex
fig2

@@
   \centering
-    \includegraphics[scale=0.55]{c2}
+    \includegraphics[scale=0.55]{c3}
   \caption{Network sliced O-RAN system}
@@
 Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service.
-Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $N_s$ Physical Resource Blocks (PRBs) as it is defined in standard of LTE that the bandwidth (BW) of channel is divided to PRBs in time series \cite{lee2018dynamic}.
+Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs) as it is defined in standard of LTE that the bandwidth (BW) of channel is divided to PRBs in time series \cite{lee2018dynamic}.
 All RRHs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}.
 Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity.
-Suppose that we have two processing layer in BBU-Pool of O-RAN system. The lower layer is consist of PHY and MAC and the upper layer is consist of RLC, PDCP and SDAP.
+Suppose we have two processing layer in BBU-Pool of O-RAN system. The lower layer is consist of high-PHY and MAC and the upper layer is consist of RLC, PDCP and SDAP.
 Assume, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer.
-for simplicity, suppose ach VM is connected to a VNF.
-Each VNF in both layers maps to one or more slices.
+For simplicity, suppose each VM is connected to a VNF.
+Each VNF in both layers connects to one or more slices.
 So in $s^{th}$ slice, there are $M_{s_1}$ VNFs in first layer and $M_{s_2}$ VNFs in second layer.
@@
 \begin{equation}\label{eq2}
-\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}};
+\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}};
 \end{equation}
@@
 \begin{equation}\label{eq3}
-\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s}+ \boldsymbol{z}_{\mathcal{U}_v};
+\bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s}+ \boldsymbol{z}_{\mathcal{U}_v};
 \end{equation}
-Where $\boldsymbol{x}_{ \mathcal{R}_s} = [x_{ r_{(s,1)}},...,x_{ r_{(s,\mathcal{R}_s)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector for the $s$-th set of Network slice,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
-In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which is made from signal compression in BBU.
-\\
+Where $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
+In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which is made from signal compression in BBU.\newline
 Furthermore, $\zeta_{U_v,k,s} \delequal \{\zeta_{u(v,1),k,s},\zeta_{u(v,2),k,s},...,\zeta_{u(v,N_{U_v}),k,s}\}$,
-$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks (PRB) to UE.
-Also as defined before, $\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
+$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter, demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
+$\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$ 
 shows the channel matrix between RRH set $\mathcal{R}_s$ to UE set
-$\mathcal{U}_v$. 
-The channel vector from the RRH of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below
+$\mathcal{U}_v$, besides. 
+%The channel vector from the RRH of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below
+%\begin{equation}
+%\boldsymbol{h}_{\mathcal{R}_s,u_{(s,i)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_s,u_{(v,i)}} \boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}},
+%\end{equation}
+%where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
+%represents the large scale fading matrix.
+What's more, it is assumed we have perfect channel state information(CSI).\newline
+Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as below
 \begin{equation}
-\boldsymbol{h}_{\mathcal{R}_s,u_{(s,i)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_s,u_{(v,i)}} \boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}},
-\end{equation}
-where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
-represents the large scale fading matrix. Here, it is assumed we have perfect channel state information(CSI).
-\\
-Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as follow
-\begin{equation}
-\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}
+\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}.
 \end{equation}
@@
  I_{u_{(v,i)}} &= 
- \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{vs}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
-&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{ys} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
-&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{vs}}_{\text{(quantization noise interference)}}.
+ \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{v,s}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
+&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
+&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}}.
 \end{split}
 \end{equation}
-where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
+Where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
 and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$.
-It is assumed that interference signal for each UE, is applied from UEs which are using same PRB.
+As it is clear, Interference signal for each UE is comming from UEs using the same PRB.
 If we replace $p_{u_{(v,l)}}$ and $p_{u_{(y,l)}}$ by $P_{max}$, an upper bound $\bar{I}_{u_{(v,i)}}$ is obtained for $I_{u_{(v,i)}}$.
-Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in equation \eqref{eq1} and \eqref{eq2}.\newline
+Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in  \eqref{eq1} and \eqref{eq2}.\newline
 let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from $j^{th}$ RRH in $s^{th}$ slice.
-from equation \eqref{eq3} we have
+from \eqref{eq3} we have,
 \begin{equation}
-\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{vs} + \sigma_{q_{r(s,j)}}^2.
+\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s} + \sigma_{q_{r(s,j)}}^2.
 \end{equation}
-As a result the user data capacity on the fronthual link between BBU and the $j^{th}$ RRH in $s^{th}$ slice is formulated as below
+As a result the rate of users on the fronthual link between BBU-Pool and the $j^{th}$ RRH in $s^{th}$ slice is formulated as 
 \begin{equation}
-C_{R_{(s,j)}} = \log{(1+\sum_{v=1}^{V}\frac{w_{r_{(s,j)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   w_{r_{(s,j)},\mathcal{U}_{v}}^H a_{vs}}{ \sigma_{q_{r(s,j)}}^2})},
+C_{R_{(s,j)}} = \log{(1+\sum_{v=1}^{V}\frac{w_{r_{(s,j)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   w_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s}}{ \sigma_{q_{r(s,j)}}^2})},
 \end{equation}
 \subsection{Mean Delay}
-Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for $i^{th}$ UE in $v^{th}$ service. 
-Therefore, the mean arrival data rate of UEs in $s^{th}$ slice in the first layer is 
-$\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}\lambda_{u(v,i)}$.  
+Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for $i^{th}$ UE of $v^{th}$ service. 
+Therefore, the mean arrival data rate of UEs connect to $s^{th}$ slice in the first layer is 
+$\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$.  
 Furthermore, the mean arrival rate of second layer is approximately equal to the mean arrival rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the arrival packets of second layer which is processed in first layer is still Poisson with rate $\alpha_{s}$.
-It is assumed that there are dispatchers in each layer for each slice to divide the incoming traffic to VMs.
-Suppose the baseband processing of each VM is depicted as a M/M/1 processing queue.
-Each packet is routed by one of VMs of slices. So the mean delay of slice $s$ which is related to incoming traffic rate routed to
-each VM in first layer can be written as follow
+It is assumed there are dispatchers in each layer for each slice to divide the incoming traffic to VNFs \cite{frdl,luong2018novel,luong2018novel1}.
+Suppose the baseband processing of each VNF is depicted as a M/M/1 processing queue.
+Each packet is routed by one of VNFs of slices. So the mean delay of slice $s$ which is related to incoming traffic rate routed to
+each VNF in first layer can be written as follow
 \begin{equation}
-d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}}
+d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}}.
 \end{equation}
-Also, the delay in $s^{th}$ slice in second layer can be formulated as below
+Also, the delay of $s^{th}$ slice in second layer is
 \begin{equation}
-d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}
+d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}.
 \end{equation}
-In addition, the arrival data rate to the queue of wireless transmission
- is equal to the arrival data rate of dispatcher.
+In addition, $d_{s_{tr}}$ is another delay for $s^{th}$ slice as a result of wireless transmission. The arrival data rate of wireless transmission
+ is equal to the arrival data rate of dispatchers for each slice that divide data rates and transmit divided rates to VNFs.
 Moreover, it is assumed that the service time of transmission queue for each slice $s$ has 
@@
 \begin{equation}
-d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}}
+d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
 \end{equation}
-Where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}R_{u(v,i)}$.
-We define a new parameter which indicates mean delay of each slice
+Where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$.
+Mean delay of each slice is
 \begin{equation}
-D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s
+D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s.
 \end{equation} 
-\subsection{Physical Resource}
-Assume each VM is mapped to one virtual network function (VNF) for simplicity. Each VNF requires
+\subsection{Physical Data Center Resource}
+Each VNF requires
 physical resources which contain RAM, Memory and CPU.
@@
 \begin{equation}
-\bar{\Omega}_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \}
+\bar{\Omega}_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \};
 \end{equation} 
-Where,$\bar{\Omega}_{(f,s)}\in \mathbb{C}^{3}$ and $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU.
-Moreover total amount of required RAM, Memory and CPU of all VNFs in a slice is a three dimension vector which is defined as
+Where,$\bar{\Omega}_{(f,s)}\in \mathbb{C}^{3}$ and $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU, respectively.
+Moreover total amount of required RAM, Memory and CPU of all VNFs of a slice is a three dimension vector which is defined as
 \begin{equation}
-\bar{\Omega}_{s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{(f,s)}
+\bar{\Omega}_{s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{(f,s)};
 \end{equation}
-Where, $F_s = M_{s_1} + M_{s_2}$ is the total number of VNFs in slice $s$.
-\newline
-Also, in the Core Network (CN), there are $D_c$ data centers (DC), which served VNFs. Each DC contains several servers that supply VNF's needs.
-The amount of RAM, Memory and CPU is denoted respectively by $\tau_{R_{j}}, \tau_{M_{j}}$ and $\tau_{C_{j}} $ for $j^{th}$ DC.
+Also, there are $D_c$ data centers (DC), which served VNFs. Each DC contains several servers that supply VNF's requirements.
+The amount of RAM, Memory and CPU is denoted by $\tau_{R_{j}}, \tau_{M_{j}}$and $\tau_{C_{j}} $ for $j^{th}$ DC, respectively .
 \begin{equation*}
-\tau_j = \{\tau_{R_{j}}, \tau_{M_{j}}, \tau_{C_{j}} \}
+\tau_j = \{\tau_{R_{j}}, \tau_{M_{j}}, \tau_{C_{j}} \};
 \end{equation*}
@@
 \hat{\Omega}_{s}^{tot} &= w_R \bar{\Omega}_{R_s}^{tot} + w_M \bar{\Omega}_{M_s}^{tot} + w_C \bar{\Omega}_{C_s}^{tot} \\
-\hat{\tau}_j &= w_R \tau_{R_{j}} + w_M \tau_{M_{j}} + w_C \tau_{C_{j}}
+\hat{\tau}_j &= w_R \tau_{R_{j}} + w_M \tau_{M_{j}} + w_C \tau_{C_{j}},
 \end{split}
 \end{equation}
-Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ are the weight of RAM, Memory and CPU.
+Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ are the weight of RAM, Memory and CPU that is used for Algorithm \ref{alg3}.
+In this system model the placement of physical data center resources to VNFs is considered.
+$y_{s,d}$ is a binary variable indicates whether $d^{th}$ data-center is connected to VNFs of $s^{th}$ slice or not.
 \subsection{Problem Statement}
-One of the most important parameters to estimate the optimality of the system is energy efficiency which is represented as sum-rate to sum-power as follow
+One of the most important parameters to estimate the optimality of the system is energy efficiency which is represented as a sum-rate to sum-power 
 \begin{equation}
@@
 \end{equation}
-Assume the power consumption of baseband processing at each data center that is mapped to VNFs of a slice is depicted as
+Assume the power consumption of baseband processing at each data center that is connected to VNFs of a slice is depicted as
 $\phi$. So the total power can be represented as  
 \begin{equation*}
-\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi
+\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi.
 \end{equation*} 
-Where, $y_{s,d}$ is a binary variable which indicates whether $d^{th}$ data-center is mapped to VNFs of $s^{th}$ slice or not.\\
 In this paper, the main goal is to simultaneously maximize sum-rate and minimize sum-power with the presence of constraints which is written as follow, 
@@
 &D_{s} \leq D_{s}^{max}  &&\quad \forall s,\label{c15} \\
-& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \label{c21} \\
-& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s,\label{c23} \\
+& \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s, \label{c21} \\
+& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} &&\quad \forall s,\label{c23} \\
 & \bar{\Omega}_{\mathfrak{z}(s)}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                      
@@
 \end{subequations}
-Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{vs}]  \forall v , \forall s $ and $\boldsymbol{Y} =[y_{s,d}]  \forall s , \forall d $. 
-Equation \eqref{c11}, \eqref{c12} indicates respectively that the power of each RRH do not exceed the maximum power and power of each UE is a positive integer value.
+Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{v,s}]  \forall v , \forall s $ and $\boldsymbol{Y} =[y_{s,d}]   \forall s ,  \forall d $. 
+\eqref{c11} and \eqref{c12} indicate that the power of each RRH do not exceed the maximum power and power of each UE is a positive integer value, respectively.
 Also \eqref{c13} shows that the rate of each UE is more than a threshold.
-\eqref{c14} and \eqref{c15} depicts respectively that the capacity of fronthaul link is limited and the delay of receiving signal should be less than a threshold.
+\eqref{c14} and \eqref{c15} depicts that the capacity of fronthaul link is limited and the delay of receiving signal should be less than a threshold, respectively.
 Furthermore, \eqref{c21}
-ensure that each service is mapped to one or more slice.
-Also, \eqref{c23} guarantee that each slice (VNFs in two layers of slice) has been placed to one or more physical resources (DC). Moreover, in \eqref{c22}  $\mathfrak{z}\in \{M,R,C\}$, which supports 
+ensures that each service is connected to one or more slices.
+Also, \eqref{c23} guarantees that each slice (VNFs in two layers of slices) has been placed to one or more physical resources of DCs. Moreover, \eqref{c22}  $\mathfrak{z}\in \{M,R,C\}$, supports 
 that we have enough physical resource for VNFs of each slice.\newline 
-The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem A and B. The problem A is introduced as bellow
+The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem A and B since the variables can be obtained independently.
+The problem A is defined as
 \begin{subequations}
@@
 &D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
-& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s
+& \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s
 \end{alignat} 
@@
 \min\limits_{\boldsymbol{y} }   \quad &   \phi_{tot}(\boldsymbol{Y})\\
-\text{subject to} \quad & \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
+\text{subject to} \quad & \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} &&\quad \forall s, \\
 &  \bar{\Omega}_{\mathfrak{z}(s)}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                      
@@
 In this subsection, the proposed method is applied to solve the optimization problem.
-We want to solve \eqref{constraints1}. Since the problem is non-convex and NP-Hard iterative algorithm is applied.
-To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} to 
+We want to solve \eqref{constraints1}. Since the problem is non-convex and NP-Hard, iterative algorithm is applied.
+To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} into 
 two different part that can be solved iteratively.  
@@
 \For {$j \gets 1$ to $V$}
-\State Set $a_{ij} = 1$
+\State Set $a_{i,j} = 1$
 \State Obtain Parameters of System
 \If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} is not applied} 
-\State Set $a_{ij} = 0$;
+\State Set $a_{i,j} = 0$;
 \Else
@@
 \begin{proof}
-See Appendix A
+See \cite{aaa}, Appendix A
 \end{proof}
@@
 Since, Interference is a function of power of UEs, for simplicity, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference (the worst-case). 
-In order to make equation \eqref{constraints1} as a standard form of convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15}.
+In order to make \eqref{constraints1} as a standard form of convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15}.
 Lagrangian function is written as follow
@@
 &- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,j)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\ 
-&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{vs}.\\ 
+&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.\\ 
 \end{split}
@@
 where, $\mathfrak{y}_{u(v,i)}= (-\mu_{u(v,i)}+\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and 
-$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}$. Also 
+$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. Also 
 $\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} (\xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$. 
@@
 In \eqref{firstsub} and \eqref{secondsub} the details of solving each part of subproblem is depicted. 
+Firstly, by fixing power of each UE, $\boldsymbol{A}$ is obtained using Algorithm \eqref{alg}.
+Then by using sub-gradient method, \eqref{secondsub} is solved and iteratively solve these problems until variables converge.
 Here, the algorithm of solving sub-problem A is shown in \textbf{Algorithm} \eqref{alg2}
@@
 \subsection{Sub-Problem B}
-In this subsection, we want to solve equation \eqref{constraints2} which is the placement of virtual resources to physical resource in order to minimize the number of using DCs. 
+In this subsection, we want to solve  \eqref{constraints2} which is the placement of virtual resources to physical resource in order to minimize the number of using DCs. 
 To achieve optimum $\boldsymbol{Y}$ heuristic algorithm and Mosek is applied.
 The details of heuristic algorithm is written in \textbf{Algorithm} \eqref{alg3}.
-In this algorithm, if a slice does not admit to a specific DC, it is remain for next placement.
-In next placement the residual slices, map to more than one DC according to their requirements.
+In this algorithm, firstly we sort slices and DCs according to their sum-weighted of their requirements.
+Secondly, we start mapping from the most needs slices to the DC which has the most physical resources.
+After mapping DCs to slices, if some slices are not admitted, we start admitting residual slices to more than one DCs.
+At the end, if DC with the lowest physical resources is free and can served instead of DC with highest physical resource, the slices remapped to new DC with lowest physical resource since it has lowest power consumption.
+if a slice does not admit to a specific DC, it is remain for next placement. In next placement the residual slices, map to more than one DC according to their requirements.
 \begin{algorithm}
@@
 \State \textbf{end for}
+\State Remapping DCs must be done to prevent wasting Energy
 \end{algorithmic}
@@
 \section{Simulation}
+ \begin{table}[H]
+ \caption {Simulation Parameter} \label{table:1} 
+ \begin{center}
+  \begin{tabular}{||c c ||} 
+  \hline
+  Parameter & Value \\ [0.5ex] 
+  \hline\hline
+  Noise power & -174dBm\\
+  \hline
+  Bandwidth & 10MHZ \\
+  \hline
+ Maxmimun transmit Power & 23dBm \\
+  \hline
+  Minimum data rate &  1Mbits/sec \\ [1ex] 
+  \hline
+ \end{tabular}
+ \end{center}
+ \end{table}
 In this section, Simulation and numerical results for the main problem are depicted.
+In fig.
+\ref{fig:f1}, the ratio of admitted slices that connected to just one DC is demonstrated for two different number of DCs with different number of slices (the parameters for simulation listed in table \ref{table:1}).
+When number of DCs are low, proposed method and optimal method have approximately same ratio of admitted slices.
 \begin{figure}[H]
@@
     \includegraphics[width=\linewidth]{f1}
-  \caption{algorithm}
-  \label{fig:c11}
+  \caption{Ratio of Admitted Slices connected to just one DC vs. Total slices}
+  \label{fig:f1}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=\linewidth]{f2}
+  \caption{Normalized resource consumption vs. Number of slices}
+  \label{fig:f1}
 \end{figure} 

### 2019-10-19 Latex/tex/pr.tex
try

@@
 In this algorithm, firstly we sort slices and DCs according to their sum-weighted of their requirements.
-Secondly, we start mapping from the most needs slices to the DC which has the most physical resources.
+Secondly, we start mapping from the most needed slices to the DC with the most physical resources.
 After mapping DCs to slices, if some slices are not admitted, we start admitting residual slices to more than one DCs.
@@
   \hline\hline
-  Noise power & -174dBm\\
+  Mean of CPU for DCs & 25.6GHz\\
   \hline
-  Bandwidth & 10MHZ \\
+  Mean of RAM for DCs & 128G\\
   \hline
- Maxmimun transmit Power & 23dBm \\
+ Mean of Memory for DCs & 10T \\
   \hline
-  Minimum data rate &  1Mbits/sec \\ [1ex] 
+   Mean of CPU for Slices & 3.2GHz\\
+  \hline
+  Mean of RAM for Slices & 16G\\
+  \hline
+ Mean of Memory for Slices & 1T \\ [1ex] 
   \hline
@@
 In this section, Simulation and numerical results for the main problem are depicted.
-In fig.
-\ref{fig:f1}, the ratio of admitted slices that connected to just one DC is demonstrated for two different number of DCs with different number of slices (the parameters for simulation listed in table \ref{table:1}).
-When number of DCs are low, proposed method and optimal method have approximately same ratio of admitted slices.
+In Fig.
+\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different number of DCs with different number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}).
+In this simulation, it is assumed that each slice can be served by just one DC and it is not admitted by more than one DC.
+Proposed method is based on Algorithm \ref{alg3} and optimal method is done by MOSEK toolbox.
+ \begin{table}[H]
+ \caption {Simulation Parameter} \label{table:2} 
+ \begin{center}
+  \begin{tabular}{||c c ||} 
+  \hline
+  Parameter & Value \\ [0.5ex] 
+  \hline\hline
+   $w_C$ & 320\\
+  \hline
+  $w_R$  & 64\\
+  \hline
+ $w_M$  & 1 \\ [1ex] 
+  \hline
+ \end{tabular}
+ \end{center}
+ \end{table}
+When we have two DCs, proposed method and optimal method have approximately same ratio of admitted slices. But by increasing the number of DCs to five, performance of proposed method reduced.
 \begin{figure}[H]
@@
   \caption{Normalized resource consumption vs. Number of slices}
-  \label{fig:f1}
+  \label{fig:f2}
 \end{figure} 

### 2019-10-20 Latex/tex/pr.tex
finish fig2 and 3

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage[T1]{fontenc}
 \usepackage{cite}
@@
 \section{Simulation}
- \begin{table}[H]
+In this section, Simulation and numerical results for the main problem are depicted.
+In Fig.
+\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different number of DCs with different number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}).
+In this simulation, it is assumed that each slice can be served by just one DC and it is not admitted by more than one DC.
+Proposed method is based on Algorithm \ref{alg3} and optimal method is done by MOSEK toolbox.
+ \begin{table}
  \caption {Simulation Parameter} \label{table:1} 
@@
  \end{table}
-In this section, Simulation and numerical results for the main problem are depicted.
-In Fig.
-\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different number of DCs with different number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}).
-In this simulation, it is assumed that each slice can be served by just one DC and it is not admitted by more than one DC.
-Proposed method is based on Algorithm \ref{alg3} and optimal method is done by MOSEK toolbox.
- \begin{table}[H]
+When we have two DCs, proposed method and optimal method have approximately same ratio of admitted slices.
+But by increasing the number of DCs to five, performance of proposed method reduced.
+Using five DCs, the difference between
+proposed method and optimal method in worst case (44 slices) is about $23$ percentage. 
+ \begin{table}
  \caption {Simulation Parameter} \label{table:2} 
@@
  \end{table}
-When we have two DCs, proposed method and optimal method have approximately same ratio of admitted slices. But by increasing the number of DCs to five, performance of proposed method reduced.
 \begin{figure}[H]
   \centering
-    \includegraphics[width=\linewidth]{f1}
+    \includegraphics[width=\linewidth]{f11}
   \caption{Ratio of Admitted Slices connected to just one DC vs. Total slices}
@@
 \end{figure} 
-
+In Fig.
+\ref{fig:f2}, the normalized resource consumption is depicted due to the number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}).
+In this simulation, it is assumed that number of DCs is completely enough to cover all slices.
+The optimality of placement of DCs to slices is measured.
+It is shown that how much resources of active DCs are not used.
+For ten slices, the difference between optimal solution and proposed solution is about $15$ percent.
 \begin{figure}[H]
   \centering
-    \includegraphics[width=\linewidth]{f2}
-  \caption{Normalized resource consumption vs. Number of slices}
+    \includegraphics[width=\linewidth]{fig2_last}
+  \caption{Normalized Resource Consumption vs. Number of Slices}
   \label{fig:f2}
 \end{figure} 
-\bibliographystyle{ieeetr}
+\bibliographystyle{IEEEtran}
 \bibliography{ref}

### 2019-10-20 codes/simple_one/update_var.m

@@ -1,7 +1,7 @@
-mu_step = 0.01*Pmax/sqrt(count_power);
+mu_step = 0.1*Pmax/sqrt(count_power);
 kr_step = .1*(2^C_thresh * var_q)/sqrt(count_power);
-lambdar_step = 0.01*Rt/sqrt(count_power);
-tr_step = 0.01*(1/(delay_max-mean(Delay_Slice))+lamda)/sqrt(count_power);
+lambdar_step = 0.1*Rt/sqrt(count_power);
+tr_step = 0.1*(1/(delay_max-mean(Delay_Slice))+lamda)/sqrt(count_power);
 Ut2Slice = Ut2Service*service2slice;
 for ki=1:N_Ut
     lambda_r(ki)= max(0,lambda_r(ki) - lambdar_step* (rate_UE(ki) - Rt));
@@ -16,5 +16,5 @@ for ki=1:N_Ut
 end
 
 for mi=1:N_rrh
-    Kr(mi) =  max(0,Kr(ki)-kr_step*(2^C_thresh * var_q - Prrh(mi)));
+    Kr(mi) =  max(0,Kr(mi)-kr_step*(2^C_thresh * var_q - Prrh(mi)));
 end

### 2019-10-20 codes/thirdPart/simulations/main_simulation.m

@@ -26,7 +26,7 @@ for count = 1: counter_max
         sum_ConsResource(:,kk,count) = resource_server1(:,2:4)'*makeone(sum(mappingVar))';
         sum_ResResource(:,kk,count) = resource_server1(:,2:4)'*(1-makeone(sum(mappingVar))');
         run mosekRun
-        %run remap_server1
+        run remap_server1
         NumServerEnd1(kk,count) = sum(mapvec(1:N_service*N_server));
         sum_vector12 = demand_service'*map1;
         sum_sumVec1(:,kk,count) =  sum(sum_vector12,2);

### 2019-10-21 Latex/tex/pr.tex
enhance code
enhance latex

@@
 \begin{equation}\label{eq2}
-\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}};
+\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}};
 \end{equation}
@@
 Moreover, $BN_0$ denotes the power of Guassian additive noise and $I_{u(v,i)}$ is the power of interfering signals.
+Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable illustrates whether slice $s$ is connected to service $v$ or not.
+If $a_{v,s} =1$ then, $v^{th}$ service is connected to $s^{th}$ slice; otherwise, it is not connected.
+\newline 
 To obtain SNR as formulated in \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service which is given by \eqref{eq3}
@@
 \end{equation}
+Where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is connected to service $v$ or not.
 \subsection{Mean Delay}
@@
 Assume the power consumption of baseband processing at each data center that is connected to VNFs of a slice is depicted as
-$\phi$. So the total power can be represented as  
+$\phi$. So the total power of system for all active DCs that are connected to slices can be represented as  
 \begin{equation*}
@@
 \end{equation*} 
-In this paper, the main goal is to simultaneously maximize sum-rate and minimize sum-power with the presence of constraints which is written as follow, 
+In this paper, the main goal is to simultaneously maximize sum-rate and minimize sum-power which is the total power of all RRHs and the total power consumption of baseband processing at all DCs with the presence of constraints which is written as follow,
 \begin{subequations}
@@
 \end{subequations}
-Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{v,s}]  \forall v , \forall s $ and $\boldsymbol{Y} =[y_{s,d}]   \forall s ,  \forall d $. 
+Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}]  \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]   \forall s ,  \forall d $ is a binary variable shown whether
+the a physical DC is connected to a VNFs of a slice or not. 
 \eqref{c11} and \eqref{c12} indicate that the power of each RRH do not exceed the maximum power and power of each UE is a positive integer value, respectively.
@@
 We want to solve \eqref{constraints1}. Since the problem is non-convex and NP-Hard, iterative algorithm is applied.
-To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} into 
+To solve the problem and obtain $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} into 
 two different part that can be solved iteratively.  
@@
 Two different method is applied to acquire $\boldsymbol{A}$.
-The first method is using MOSEK and second method is a heuristic algorithm.
 The details of heuristic algorithm are represented in \textbf{Algorithm} \eqref{alg}.  
@@
 \begin{algorithmic}[1]
-\State Sort services according to their priority, the number of UEs in it and their requirements in descending order.
-\State Sort slices according to the number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in descending order. 
+\State Sort services according to the number of UEs in it and their requirements in descending order.
+\State Sort slices according to the weighted linear combination of number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in descending order. 
 \For {$i \gets 1$ to $S$}
@@
 \State Set $a_{i,j} = 1$
-\State Obtain Parameters of System
+\State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RRHs)
 \If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} is not applied} 
@@
 \end{equation}
-where, $\mathfrak{y}_{u(v,i)}= (-\mu_{u(v,i)}+\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and 
+where, $\mathfrak{y}_{u(v,i)}= (\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and 
 $\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. Also 
-$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} (\xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$. 
+$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$. 
 By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained. 

### 2019-10-23 Latex/tex/pr.tex
change latex + add matlab .mat

@@
 Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a global 'carrier-led' effort to bring greater transparency of Open-RAN 
-(O-RAN), to the next-generation of radio access network. \newline
+(O-RAN), to the next-generation of radio access network.
+
 To increase energy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method in 5G in order to virtualize the common physical network into several logical end-to-end networks.
 Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to end network.
-\newline
-In this paper, we elaborates joint NS in RAN and Core of O-RAN system and investigate optimal power 
-of each User Equipment (UE) to jointly maximize Energy Efficiency and minimize consumption power of physical resources in a downlink channel.
-The problem is formulated as a mixed integer optimization problem that can be decompose into two independent sub-problems for RAN and Core since sub-problems are independent.
-Heuristic algorithms is proposed to each of sub-problems to solved the first sub-problem in order to simultaneously map slices to services and optimize power and the second sub-problem in order to map slices to physical resources and minimize number of active Data Centers (DC).
+
+In this paper, we elaborates joint NS in RAN and Core of O-RAN system to investigate power 
+of each User Equipment (UE), connect slices to services and physical Data Centers (DC) to slices to jointly maximize Energy Efficiency and minimize consumption power of physical resources in a downlink channel.
+The problem is formulated as a mixed integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent.
+Heuristic algorithms is proposed to each of sub-problems to solved the first sub-problem in order to simultaneously connect slices to services and optimize power and for the second sub-problem to connect slices to physical resources and minimize number of active DCs.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-O-RAN, Network Slicing, Energy Efficiency, Data Center
+O-RAN, Network Slicing, Energy Efficiency, Data Center (DC)
 \end{IEEEkeywords}
@@
 Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}.
-\newline
-The core idea driving C-RAN is to split radio remote head (RRH) and baseband unit (BBU).
+In innovative O-RAN system, the programmable RAN software is decoupled from hardware which can be simply run on any specific processing platforms, in order to be more flexible for mobile network operators (MNOs) specially for mobile virtual network operators (MVNOs)\cite{oran1}.
+
+The core idea of C-RAN is to split radio remote head (RRH) and baseband unit (BBU).
 Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities.
@@
 To communicate between BBU-Pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity.
-Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.\newline
+Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.
+
 xRAN technology ,released in April 2018 as a next generation of RAN, has three fundamental features.
@@
 In addition, each service is connected to one or more Core-RAN slices base on the resource of slices.
-Using cloud-computing in BBU-Pool, enhance performance of system by virtualizing resources
+Using cloud-computing in BBU-Pool, performance of system is enhanced by virtualizing resources
 into virtual machines (VMs).
 Each VM has a computing processor mapped to Virtual Network Functions (VNFs) which processed arrival data.
-Also VNFs are mapped to physical resource through NS technique\cite{frdl,luong2018novel,luong2018novel1}.
-\newline  
+Also VNFs are mapped to physical resources through NS techniques\cite{frdl,luong2018novel,luong2018novel1}.
+
+Compression of messages passed through fronthaul link due to the limited capacity of these link is considered in \cite{simeone2016cloud,1111}. 
 In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum rate.
-Moreover, in \cite{frdl,luong2018novel,luong2018novel1} minimization of cost obtained by power consumption and cloud processing is applied.
-Limited fronthaul capacity is considered.
-Also processing delay of each VM and wireless transmission delay is bounded.\newline
+Moreover, in \cite{frdl,luong2018novel,luong2018novel1} minimization of cost obtained by power consumption, also cloud processing and limited fronthaul capacity is considered.
+Furthermore, processing delay of each VM and wireless transmission delay is bounded.
+
 In this paper, as  depicted in figure \ref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
 their service requirements.
-Also RAN is decoupled to slices to provide services needs.
+Also RAN is decoupled to slices to provide requirements of services.
 Optimal power allocation and joint connecting slices to services is applied.
-In addition, mapping slices to physical resources is taken to account.
+In addition, connecting slices to physical resources is taken to account.
 
@@
 Suppose that there are $S$ slices Serving $V$ services.
-Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service.
+Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna user equipments (UEs) that require certain service.
 Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs) as it is defined in standard of LTE that the bandwidth (BW) of channel is divided to PRBs in time series \cite{lee2018dynamic}.

### 2019-10-23 codes/simulation1/plotWithNan.m

@@ -2,7 +2,7 @@ y = zeros(2,nr);
 for i =1:iter_max
     for j=1:nr
         if isnan(etha(j,i))==0
-            y(1,j)=y(1,nr)+etha(j,i);
+            y(1,j)=y(1,j)+etha(j,i);
             y(2,j)= y(2,j)+1;
         end
     end

### 2019-10-24 Latex/tex/pr.tex
change code for 2part

@@
 \begin{abstract}
-Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a global 'carrier-led' effort to bring greater transparency of Open-RAN 
-(O-RAN), to the next-generation of radio access network.
+Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a more flexible and openness radio access network which is the Open-RAN 
+(O-RAN) for the fifth generation of wireless technology.
 
-To increase energy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method in 5G in order to virtualize the common physical network into several logical end-to-end networks.
+To increase energy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks.
 Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to end network.
@@
 In this paper, we elaborates joint NS in RAN and Core of O-RAN system to investigate power 
-of each User Equipment (UE), connect slices to services and physical Data Centers (DC) to slices to jointly maximize Energy Efficiency and minimize consumption power of physical resources in a downlink channel.
+of each User Equipment (UE), connect slices to services and also connect physical Data Centers (DC) to slices to jointly maximize Energy Efficiency and minimize consumption power of RRHs and the cost of  physical resources in a downlink channel.
 The problem is formulated as a mixed integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent.
-Heuristic algorithms is proposed to each of sub-problems to solved the first sub-problem in order to simultaneously connect slices to services and optimize power and for the second sub-problem to connect slices to physical resources and minimize number of active DCs.
+Heuristic algorithms is proposed to each of sub-problems in order to simultaneously connect slices to services, optimize power consumption and connect slices to physical resources to minimize cost of active DCs.
 \end{abstract}
@@
 \section{Introduction}
-Recently, O-RAN which is the integration and expansion of C-RAN and xRAN is expected to be a key technology for 5G to enhance RAN performance and solve the challenges in a best way.  
+Recently, O-RAN which is the integration and expansion of C-RAN and xRAN is expected to be a key technology for 5G to enhance RAN performance and solve the part of challenges of mobile network operators (MNOs) in a best way.
 The Idea of O-RAN comes from two opinion.
-Firstly, according to real-time analytic used for artificial intelligence system, the radio access networks must be evolved to be more open and smarter than previous generations.
+Firstly, according to real-time analytic used for artificial intelligence system, the radio access networks must be evolved to be more intelligent and flexible than before.
 Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}.
-In innovative O-RAN system, the programmable RAN software is decoupled from hardware which can be simply run on any specific processing platforms, in order to be more flexible for mobile network operators (MNOs) specially for mobile virtual network operators (MVNOs)\cite{oran1}.
+In innovative O-RAN system, the programmable RAN software is decoupled from hardware which can be simply run on any specific processing platforms, in order to be more flexible for MNOs specially for mobile virtual network operators (MVNOs)\cite{oran1}.
 

### 2019-10-24 codes/simulEnd/simulation1/channel.m

@@ -9,7 +9,7 @@ for i=1:N_rrh
        var_fading = db2pow(10);
        N_Ute = lognrnd(0,var_fading);
        loss(i,j) = N_Ute*1/(distance(i,j)^3.8);
-       ChannelGain(i,j) = (loss(i,j)^0.5)/sqrt(2)*(randn(1)+1i*randn(1));
+       ChannelGain(i,j) = 100*(loss(i,j)^0.5)/sqrt(2)*(randn(1)+1i*randn(1));
     end
 end
 ChannelGain2 = ChannelGain;

### 2019-10-24 codes/simulEnd/simulation1/mapping1.m

@@ -1,84 +1,5 @@
-function milo1()
 clear prob
 %%
-R = 500;
-N_Service = 3;
-NumOfUtInService = randi([1 10],1, N_Service);
-N_Ut = sum(NumOfUtInService);
-N_Slice =  10;
-N_rrh = 10;
-BW = 120*1e3;  
-N_PRB = 10;
-n0 = -174; %dbm
-N0 = db2pow(n0)/1000;
-Pt = 30;
-Pmax = db2pow(Pt)/1000;
-Rt = .01*BW;%0.1*BW; 
-Popt = ones(1, N_Ut)*Pmax;
-var_q = 1e-8;
-C_thresh = 3000*Rt/BW;
-%% ut to service
-k = 1;
-Ut2Service = zeros(sum(NumOfUtInService),N_Service);
-for i=1:N_Service
-    Ut2Service(k:k+NumOfUtInService(i)-1,i) = 1;
-    k = k+NumOfUtInService(i);
-end
-%% rrh 2 slice
-rrh2slice = zeros(N_rrh, N_Slice);
-num_map = 0;
-while any(sum(rrh2slice,1)<1) || any(sum(rrh2slice,2)<1)
-    rrh2slice = randi([0 1],N_rrh, N_Slice);
-    num_map = num_map+1;
-    if num_map >10
-        rrh2slice = ones(N_rrh, N_Slice);
-    end
-end
-%% PRB 2 Slice
-PRB2Slice = randi([0 1],N_PRB, N_Slice);
-num_map = 0;
-while any(sum(PRB2Slice,1)<1) || any(sum(PRB2Slice,2)<1)
-    PRB2Slice = randi([0 1],N_PRB, N_Slice);
-    num_map = num_map+1;
-    if num_map >10
-        PRB2Slice = ones(N_PRB, N_Slice);
-    end
-end
-%%
-Ut_map = zeros(N_Ut, N_PRB);
-for i =1:N_Ut
-    if mod(i,N_PRB)==0
-       Ut_map(i,N_PRB)= 1;
-    else
-        Ut_map(i,mod(i,N_PRB)) =1 ;
-    end
-
-end
-
-%% channel 
-ChannelGain = zeros(N_rrh,N_Ut);
-for i=1:N_rrh
-    for j=1:N_Ut
-       distance(i,j)= randi(R,1,1);
-       if distance(i,j)==0
[…]

### 2019-10-24 codes/simulEnd/simulation1/parameter.m

@@ -1,0 +1,39 @@
+Intf = cvx(zeros(N_Ut,1));
+rrh2ut1 = rrh2slice *transpose(service2slice)*transpose(Ut2Service);
+rrh2Ut = modifiedMat(rrh2ut1);
+ChannelGain = ChannelGain .* rrh2Ut;
+for i = 1: N_Ut
+    if sum(rrh2Ut(:,i)) > 0
+        Intf(i) = Intf(i) + var_q*abs((ChannelGain(:,i)')*ChannelGain(:,i));
+        for j = 1:N_PRB
+            if Ut_map(i,j)==1 
+                for t = 1 : N_Ut
+                    if i~=t && Ut_map(t,j)==1 && sum(rrh2Ut(:,t)) > 0
+                        Intf(i) = Intf(i) + Pmax/(N_Ut)*abs((PrecodingMat(:,t)')*(ChannelGain(:,t).*rrh2Ut(:,t)))^2;
+                    end
+                end
+            end
+        end
+    end
+end
+
+
+
+rate_UE = cvx(zeros(1,N_Ut));
+for i = 1:N_Ut
+    rate_UE(i) = BW/log(2)* log(1 + (Popt(i)*abs((PrecodingMat(:,i)')*(ChannelGain(:,i).*rrh2Ut(:,i)))^2)/( BW*N0));
+end
+
+
+PrecodingMat = PrecodingMat.*rrh2Ut;
+Prrh = cvx(zeros(1,N_rrh));
+Popt1 = cvx(eye(N_Ut));
+for i=1:N_Ut
+   Popt1(i,i) = Popt(i); 
+end
+for i = 1:N_rrh
+    Prrh(i) = (abs(PrecodingMat(i,:)*Popt1*PrecodingMat(i,:).'))*+var_q;
+end
+R1 = sum(rate_UE);
+P1 = sum(Prrh);
+error =  R1 - eta0 * P1;

### 2019-10-24 Latex/tex/pr.tex
matlab .mat

@@
 
-To increase energy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks.
+To increase nergy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks.
 Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to end network.
 
-In this paper, we elaborates joint NS in RAN and Core of O-RAN system to investigate power 
-of each User Equipment (UE), connect slices to services and also connect physical Data Centers (DC) to slices to jointly maximize Energy Efficiency and minimize consumption power of RRHs and the cost of  physical resources in a downlink channel.
+In this paper, we elaborate joint NS in RAN and Core of O-RAN system to investigate power 
+of each User Equipment (UE), connect slices to services and also connect physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RRHs and the cost of  physical resources in a downlink channel.
 The problem is formulated as a mixed integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent.
-Heuristic algorithms is proposed to each of sub-problems in order to simultaneously connect slices to services, optimize power consumption and connect slices to physical resources to minimize cost of active DCs.
+Heuristic algorithms is proposed to each of sub-problems in order to simultaneously connect slices to services, optimize power consumption and connect slices to physical resources to minimize cost of total DCs.
 \end{abstract}
@@
 
-The core idea of C-RAN is to split radio remote head (RRH) and baseband unit (BBU).
+The core idea of C-RAN is to separate radio remote head (RRH) from baseband unit (BBU).
 Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities.
 Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
-To communicate between BBU-Pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity.
-Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.
+To communicate between BBU-Pool and RRHs, fronthaul fiber link interface is assumed with limited capacity.
+Compression of messages passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.
 
@@
 Responsibility of wireless systems of the fifth generation covers a wide range types of services.
-In order to provide the requirement of these services, NS is implemented to virtualize the common physical network into several logical end-to-end networks.
+In order to provide the requirements of these services, NS is implemented to virtualize the common physical network into several logical end-to-end networks.
 Three different types of NS is introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing.
@@
 Also, UEs classified to group of services according to their requirements.
-In addition, each service is connected to one or more Core-RAN slices base on the resource of slices.
+In addition, each service is connected to one or more Core-RAN slices based on the resource of slices.
 Using cloud-computing in BBU-Pool, performance of system is enhanced by virtualizing resources

### 2019-10-24 Latex/tex/pr.tex
change code for 2part1

@@
 
-To increase nergy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks.
-Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to end network.
+To increase enrgy efficiency and optimize the allocation of resources, Network Slicing (NS) is considered as the best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks.
+Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to-end network.
 
-In this paper, we elaborate joint NS in RAN and Core of O-RAN system to investigate power 
+In this paper, we elaborate joint NS in RAN and Core of O-RAN system to investigate the power 
 of each User Equipment (UE), connect slices to services and also connect physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RRHs and the cost of  physical resources in a downlink channel.
-The problem is formulated as a mixed integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent.
-Heuristic algorithms is proposed to each of sub-problems in order to simultaneously connect slices to services, optimize power consumption and connect slices to physical resources to minimize cost of total DCs.
+The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent.
+Heuristic algorithms are proposed to each of sub-problems in order to connect slices to services, optimize power consumption and connect slices to physical resources to minimize the cost of total DCs simultaneously.
 \end{abstract}
@@
 \section{Introduction}
-Recently, O-RAN which is the integration and expansion of C-RAN and xRAN is expected to be a key technology for 5G to enhance RAN performance and solve the part of challenges of mobile network operators (MNOs) in a best way.
-The Idea of O-RAN comes from two opinion.
-Firstly, according to real-time analytic used for artificial intelligence system, the radio access networks must be evolved to be more intelligent and flexible than before.
+Recently, O-RAN, which is the integration and expansion of C-RAN and xRAN, is expected to be a key technology for 5G to enhance RAN performance and solve the part of challenges of mobile network operators (MNOs) in the best way.
+The Idea of O-RAN comes from two opinions.
+Firstly, according to real-time analytic used for artificial intelligence systems, the radio access networks must be evolved to be more intelligent and flexible than before.
 Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}.
-In innovative O-RAN system, the programmable RAN software is decoupled from hardware which can be simply run on any specific processing platforms, in order to be more flexible for MNOs specially for mobile virtual network operators (MVNOs)\cite{oran1}.
+In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms, in order to be more flexible for MNOs especially for mobile virtual network operators (MVNOs)\cite{oran1}.
 
-The core idea of C-RAN is to separate radio remote head (RRH) from baseband unit (BBU).
+The core idea of C-RAN is to split the radio remote head (RRH) from baseband unit (BBU).
 Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities.
 Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
-To communicate between BBU-Pool and RRHs, fronthaul fiber link interface is assumed with limited capacity.
-Compression of messages passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.
+To communicate between BBU-Pool and RRHs, the fronthaul fiber link interface, is assumed with limited capacity.
+The compression of a message passed through these links is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.
 
-xRAN technology ,released in April 2018 as a next generation of RAN, has three fundamental features.
-Control plane is decoupled from User plane.
-In addition, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
-Moreover, open north-bound and south-bound interfaces is introduced\cite{xran}.
+xRAN technology, released in April 2018 as the next generation of RAN, has three fundamental features.
+The Control plane is decoupled from User plane.
+Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
+Moreover, open north-bound and south-bound interfaces are introduced\cite{xran}.
 \begin{figure}[H]
   \centering
-    \includegraphics[scale=0.55]{c3}
+    \includegraphics[scale=0.55]{c4}
   \caption{Network sliced O-RAN system}
@@
 To evolve servicing in 5G, separation of elements of software and hardware of network is deployed in network functions virtualization (NFV) technology.
-In this technology, the functionality of networks is virtualized and divided to blocks of virtual network function (VNF).
-Responsibility of wireless systems of the fifth generation covers a wide range types of services.
-In order to provide the requirements of these services, NS is implemented to virtualize the common physical network into several logical end-to-end networks.
-Three different types of NS is introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing.
+In this technology, the functionality of networks is virtualized and divided into blocks of virtual network function (VNF).
+The responsibility of wireless systems of the fifth generation covers wide range types of services.
+In order to provide the requirements of these services, NS is implemented to virtualize the shared physical network into several logical end-to-end networks.
+Three different types of NS are introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing.
 In Core-RAN Slicing, each slice of RAN is mapped to slices of Core.
-Also, UEs classified to group of services according to their requirements.
+Also, UEs classified into a group of services according to their requirements.
 In addition, each service is connected to one or more Core-RAN slices based on the resource of slices.
-Using cloud-computing in BBU-Pool, performance of system is enhanced by virtualizing resources
+Using cloud-computing in BBU-Pool, the performance of the system is enhanced by virtualizing resources
 into virtual machines (VMs).
-Each VM has a computing processor mapped to Virtual Network Functions (VNFs) which processed arrival data.
-Also VNFs are mapped to physical resources through NS techniques\cite{frdl,luong2018novel,luong2018novel1}.
+Each VM has a computing processor in order to be run by the Virtual Network Functions (VNFs) which processed arrival data.
+Also, VNFs are mapped to physical resources through NS techniques\cite{frdl,luong2018novel,luong2018novel1}.
 
-Compression of messages passed through fronthaul link due to the limited capacity of these link is considered in \cite{simeone2016cloud,1111}. 
+The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}. 
 In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum rate.
@@
 
-In this paper, as  depicted in figure \ref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
+In this paper, as  depicted in figure \ref{fig:c11}, the downlink of the O-RAN system is assumed. UEs are divided to different groups according to 
 their service requirements.
 Also RAN is decoupled to slices to provide requirements of services.
-Optimal power allocation and joint connecting slices to services is applied.
+Optimal power allocation and joint connecting slices to services are applied.
 In addition, connecting slices to physical resources is taken to account.
@@
 \section{System Model and Problem Formulation}
-In this section, first, we present the downlink (DL) of O-RAN System. Then we obtain achievable rate and delays.
+In this section, first, we present the downlink (DL) of the O-RAN System. Then we obtain achievable rates and delays.
 Afterward, the main problem is expressed.
 \subsection{System Model}
-Suppose that there are $S$ slices Serving $V$ services.
-Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna user equipments (UEs) that require certain service.
-Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs) as it is defined in standard of LTE that the bandwidth (BW) of channel is divided to PRBs in time series \cite{lee2018dynamic}.
-All RRHs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}.
+Suppose there are $S$ slices Serving $V$ services.
+Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single-antenna user equipments (UEs) that require certain service.
+Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs) as it is defined in the standard of LTE that the bandwidth (BW) of the channel is divided to PRBs in time series \cite{lee2018dynamic}.
+All RRHs in a slice that is connected to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}.
 Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity.
-Suppose we have two processing layer in BBU-Pool of O-RAN system. The lower layer is consist of high-PHY and MAC and the upper layer is consist of RLC, PDCP and SDAP.
-Assume, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer.
-For simplicity, suppose each VM is connected to a VNF.
+Suppose we have two processing layers in the BBU-Pool of O-RAN system. The lower layer is consist of high-PHY and MAC, and the upper layer is consist of RLC, PDCP and SDAP.
+Assume we have $M_1$ VMs in the first layer and $M_2$ VMs in the second layer for processing data .
+For simplicity, suppose each VNF run on a VM and there is a one-to-one connection between VNFs and VMs.
 Each VNF in both layers connects to one or more slices.
-So in $s^{th}$ slice, there are $M_{s_1}$ VNFs in first layer and $M_{s_2}$ VNFs in second layer.
-All VNFs in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively.
-Also RRHs and PRBs can serve more than one slices. 
+So in $s^{th}$ slice, there are $M_{s_1}$ VNFs in the first layer and $M_{s_2}$ VNFs in the second layer.
+All VNFs in first and second layer has the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
+Also, RRHs and PRBs can serve more than one slices. 
 \subsection{Achievable Rate}
@@
 \end{equation}
-Where, $p_{u(v,i)}$ represents the transmition power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 
-$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
-In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the the transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
-Moreover, $BN_0$ denotes the power of Guassian additive noise and $I_{u(v,i)}$ is the power of interfering signals.
-Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable illustrates whether slice $s$ is connected to service $v$ or not.
+Where $p_{u(v,i)}$ represents the transmission power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service, also, 
+$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
+In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
+Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals.
+Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is connected to service $v$ or not.
 If $a_{v,s} =1$ then, $v^{th}$ service is connected to $s^{th}$ slice; otherwise, it is not connected.
@@
 \begin{equation}\label{eq3}
-\bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s}+ \boldsymbol{z}_{\mathcal{U}_v};
+\bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v};
 \end{equation}
 Where $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
-In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which is made from signal compression in BBU.\newline
+In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which, is made from signal compression in BBU.
+Besides, $\boldsymbol{P}_{U_v} = diag(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})$.
+\newline
 Furthermore, $\zeta_{U_v,k,s} \delequal \{\zeta_{u(v,1),k,s},\zeta_{u(v,2),k,s},...,\zeta_{u(v,N_{U_v}),k,s}\}$,
@@
 %represents the large scale fading matrix.
-What's more, it is assumed we have perfect channel state information(CSI).\newline
+What's more, it is assumed we have perfect channel state information (CSI).\newline
 Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as below
@@
 Where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
-and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. 
+and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. Moreover,
+${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RRH in $s^{th}$ slice.
 As it is clear, Interference signal for each UE is comming from UEs using the same PRB.
@@
 \end{equation}
-Where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is connected to service $v$ or not.
+Where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is connected to service $v$ or not \cite{simeone2016cloud, 1111}.
 \subsection{Mean Delay}
@@
 $\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$.  
-Furthermore, the mean arrival rate of second layer is approximately equal to the mean arrival rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the arrival packets of second layer which is processed in first layer is still Poisson with rate $\alpha_{s}$.
+Furthermore, the mean arrival data rate of the second layer is approximately equal to the mean arrival data rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
 It is assumed there are dispatchers in each layer for each slice to divide the incoming traffic to VNFs \cite{frdl,luong2018novel,luong2018novel1}.
@@
 Each packet is routed by one of VNFs of slices. So the mean delay of slice $s$ which is related to incoming traffic rate routed to
-each VNF in first layer can be written as follow
+each VNF in the first layer can be written as follow
 \begin{equation}
@@
 \end{equation}
-Also, the delay of $s^{th}$ slice in second layer is
+Also, the delay of $s^{th}$ slice in the second layer is
 \begin{equation}
@@
 \end{equation}
-In addition, $d_{s_{tr}}$ is another delay for $s^{th}$ slice as a result of wireless transmission. The arrival data rate of wireless transmission
- is equal to the arrival data rate of dispatchers for each slice that divide data rates and transmit divided rates to VNFs.
+In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice as a result of wireless transmission. The arrival data rate of wireless transmission
+ is equal to the arrival data rate of dispatchers (used as a traffic divider) for each slice divide traffic data and transmit divided traffic to VNFs.
 Moreover, it is assumed that the service time of transmission queue for each slice $s$ has 
- an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue. Therefore, 
-the mean delay of transmission layer is 
+ an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1}. Therefore, 
+the mean delay of the transmission layer is 
 \begin{equation}

### 2019-10-24 Latex/tex/pr.tex
near to last

@@
 Each VNF requires
-physical resources which contain RAM, Memory and CPU.
-Let, the required resources for VNF $f$ in slice $s$ is represented by a three dimensional vector as follow
+physical resources that contain RAM, Memory, and CPU.
+Let, the required resources for VNF $f$ in slice $s$ is represented by a three-dimensional vector as follow
 \begin{equation}
@@
   \centering
-    \includegraphics[width=\linewidth]{f11}
+    \includegraphics[width=\linewidth]{f111}
   \caption{Ratio of Admitted Slices connected to just one DC vs. Total slices}

### 2019-10-24 Latex/tex/pr.tex
last version of paper

@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
+\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+\textit{Tehran University}\\
+Tehran, Iran \\
+vmansouri@ut.ac.ir}
+\and
+\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
+\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+\textit{Tehran University}\\
+Tehran, Iran \\
+salar.nouri@ut.ac.ir}
 
@@
   \centering
-    \includegraphics[scale=0.55]{c4}
+    \includegraphics[scale=0.55]{c5}
   \caption{Network sliced O-RAN system}
@@
 \end{equation} 
-Where,$\bar{\Omega}_{(f,s)}\in \mathbb{C}^{3}$ and $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU, respectively.
-Moreover total amount of required RAM, Memory and CPU of all VNFs of a slice is a three dimension vector which is defined as
+Where,$\bar{\Omega}_{(f,s)}\in \mathbb{C}^{3}$ and $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory, and CPU, respectively.
+Moreover total amount of required RAM, Memory, and CPU of all VNFs of a slice is a three-dimensional vector which is defined as
 \begin{equation}
@@
 Also, there are $D_c$ data centers (DC), which served VNFs. Each DC contains several servers that supply VNF's requirements.
-The amount of RAM, Memory and CPU is denoted by $\tau_{R_{j}}, \tau_{M_{j}}$and $\tau_{C_{j}} $ for $j^{th}$ DC, respectively .
+The amount of RAM, Memory, and CPU is denoted by $\tau_{R_{j}}, \tau_{M_{j}}$and $\tau_{C_{j}} $ for $j^{th}$ DC, respectively.
 \begin{equation*}
@@
 \end{equation}
-Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ are the weight of RAM, Memory and CPU that is used for Algorithm \ref{alg3}.
-In this system model the placement of physical data center resources to VNFs is considered.
-$y_{s,d}$ is a binary variable indicates whether $d^{th}$ data-center is connected to VNFs of $s^{th}$ slice or not.
+Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ is the weight of RAM, Memory, and CPU that is used for Algorithm \ref{alg3}.
+In this system model, the placement of physical DC resources to VNFs is considered. $y_{s,d}$ is a binary variable indicates whether $d^{th}$ DC is connected to VNFs of $s^{th}$ slice or not.
 \subsection{Problem Statement}
@@
 \end{equation}
-Assume the power consumption of baseband processing at each data center that is connected to VNFs of a slice is depicted as
-$\phi$. So the total power of system for all active DCs that are connected to slices can be represented as  
+Where, $\sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RRHs in all slices.
+Also, $\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services.
+Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
+$\phi_{s,d}$. So the total power of the system for all active DCs that are connected to slices can be represented as  
 \begin{equation*}
-\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi.
+\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
 \end{equation*} 
-In this paper, the main goal is to simultaneously maximize sum-rate and minimize sum-power which is the total power of all RRHs and the total power consumption of baseband processing at all DCs with the presence of constraints which is written as follow,
+In this paper, the main goal is to maximize sum-rate and minimize sum-power (the total power of all RRHs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,
 \begin{subequations}
@@
 & \bar{\Omega}_{\mathfrak{z}(s)}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                      
- && \quad \forall \mathfrak{z}, \forall s  \label{c22}
+ && \quad \forall \mathfrak{z}, \forall s; \label{c22}
 \end{alignat}
@@
 Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}]  \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]   \forall s ,  \forall d $ is a binary variable shown whether
-the a physical DC is connected to a VNFs of a slice or not. 
-\eqref{c11} and \eqref{c12} indicate that the power of each RRH do not exceed the maximum power and power of each UE is a positive integer value, respectively.
+the physical DC is connected to a VNFs of a slice or not. 
+\eqref{c11} and \eqref{c12} indicate that the power of each RRH do not exceed the maximum power, and the power of each UE is a positive integer value, respectively.
 Also \eqref{c13} shows that the rate of each UE is more than a threshold.
-\eqref{c14} and \eqref{c15} depicts that the capacity of fronthaul link is limited and the delay of receiving signal should be less than a threshold, respectively.
+\eqref{c14} and \eqref{c15} depicts that the capacity of the fronthaul link is limited, and the delay of receiving signal should be less than a threshold, respectively.
 Furthermore, \eqref{c21}
@@
 Also, \eqref{c23} guarantees that each slice (VNFs in two layers of slices) has been placed to one or more physical resources of DCs. Moreover, \eqref{c22}  $\mathfrak{z}\in \{M,R,C\}$, supports 
-that we have enough physical resource for VNFs of each slice.\newline 
-The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem A and B since the variables can be obtained independently.
-The problem A is defined as
+that we have enough physical resources for VNFs of each slice.\newline 
+The main optimizaiton problem which, is formulated as \eqref{constraints}, can be decomposed into two independent optimization problems A and B since the variables can be obtained independently.
+Problem A is defined as
 \begin{subequations}
@@
 &D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
-& \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s
+& \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s.
 \end{alignat} 
@@
 \end{subequations}
-and the problem B is 
+Problem B is 
 \begin{subequations}
@@
 &  \bar{\Omega}_{\mathfrak{z}(s)}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                      
- && \quad \forall \mathfrak{z}, \forall s\label{eqomega}
+ && \quad \forall \mathfrak{z}, \forall s. \label{eqomega}
 \end{alignat}
@@
 Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration.
-Two different method is applied to acquire $\boldsymbol{A}$.
-The details of heuristic algorithm are represented in \textbf{Algorithm} \eqref{alg}.  
+Two different methods are applied to acquire $\boldsymbol{A}$.
+The details of the heuristic algorithm are represented in \textbf{Algorithm} \eqref{alg}.  
 \begin{algorithm}
@@
 \begin{algorithmic}[1]
-\State Sort services according to the number of UEs in it and their requirements in descending order.
-\State Sort slices according to the weighted linear combination of number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in descending order. 
+\State Sort services according to the number of UEs in it and their requirements in the descending order.
+\State Sort slices according to the weighted linear combination of number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in the descending order. 
 \For {$i \gets 1$ to $S$}
@@
 \subsection{Second Part of Sub-Problem A}\label{secondsub}
-In this part, by assuming that $\boldsymbol{A}$ is fixed, the optimal power of UEs in each service is achieved.
+In this part, by assuming that $\boldsymbol{A}$ is fixed, the power of UEs in each service is achieved.
 \begin{theorem}\label{t2}
@@
 \end{proof}
-The second subproblem can  be solved using Lagrangian function and iterative algorithm. 
-Since, Interference is a function of power of UEs, for simplicity, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference (the worst-case). 
-In order to make \eqref{constraints1} as a standard form of convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15}.
-Lagrangian function is written as follow
+The second subproblem can  be solved using the Lagrangian function and iterative algorithm. 
+Since, Interference is a function of the power of UEs, for simplicity, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference (the worst-case). 
+In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15}.
+The Lagrangian function is written as follow
 \begin{equation}\label{lagrang}
@@
 \end{equation}
-Where,$\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$.
-Also, $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers which have non-zero positive elements.
+Where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$.
+Also, $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
 Optimal power is obtained from equation \eqref{lagrang} as follow
 \begin{equation}
-p_{u(v,i)}^{*} = \frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }
+p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
 \end{equation}
@@
 \subsection{Solving two part of Sub-problem A iteratively}
-In \eqref{firstsub} and \eqref{secondsub} the details of solving each part of subproblem is depicted. 
-Firstly, by fixing power of each UE, $\boldsymbol{A}$ is obtained using Algorithm \eqref{alg}.
-Then by using sub-gradient method, \eqref{secondsub} is solved and iteratively solve these problems until variables converge.
+In \eqref{firstsub} and \eqref{secondsub}, the details of solving each part of the subproblem are depicted. 
+Firstly, by the fixing power of each UE, $\boldsymbol{A}$ is obtained using Algorithm \eqref{alg}.
+Then by using the sub-gradient method, \eqref{secondsub} is solved and iteratively solves these problems until variables converge.
 Here, the algorithm of solving sub-problem A is shown in \textbf{Algorithm} \eqref{alg2}
@@
 \subsection{Sub-Problem B}
-In this subsection, we want to solve  \eqref{constraints2} which is the placement of virtual resources to physical resource in order to minimize the number of using DCs. 
-To achieve optimum $\boldsymbol{Y}$ heuristic algorithm and Mosek is applied.
-The details of heuristic algorithm is written in \textbf{Algorithm} \eqref{alg3}.
-In this algorithm, firstly we sort slices and DCs according to their sum-weighted of their requirements.
+In this subsection, we want to solve  \eqref{constraints2}, which is the placement of virtual resources to physical resources in order to minimize the number of using DCs. 
+To achieve optimum $\boldsymbol{Y}$ heuristic algorithm is applied.
+The details of the heuristic algorithm are written in \textbf{Algorithm} \eqref{alg3}.
+In this algorithm, firstly, we sort slices and DCs according to their sum weighted of their requirements.
 Secondly, we start mapping from the most needed slices to the DC with the most physical resources.
-After mapping DCs to slices, if some slices are not admitted, we start admitting residual slices to more than one DCs.
-At the end, if DC with the lowest physical resources is free and can served instead of DC with highest physical resource, the slices remapped to new DC with lowest physical resource since it has lowest power consumption.
-if a slice does not admit to a specific DC, it is remain for next placement. In next placement the residual slices, map to more than one DC according to their requirements.
+After mapping DCs to slices, if some slices are not admitted, we start admitting remaining slices to more than one DCs.
+In the end, if DC with the lowest physical resources is free and can be served instead of DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption.
+If a slice does not admit to a specific DC, it remains for the next placement. In next placement the remaining slices, map to more than one DC according to their requirements.
 \begin{algorithm}
@@
 \State \textbf{end for}
-\State  $\{ind_{residual} = s|({\sum_{d=1}^{D_c}y_{s,d}==0})\}$
-\State Sort residual amount of DCs same as before in descending order.
-\State Sort residual slices same as before in descending order.
-\For {$r \gets 1$ to $S_{residual}$}
+\State  $\{ind_{remaining} = s|({\sum_{d=1}^{D_c}y_{s,d}==0})\}$
+\State Sort remaining amount of DCs same as before in descending order.
+\State Sort remaining slices same as before in descending order.
+\For {$r \gets 1$ to $S_{remaining}$}
 \For {$n \gets 1$ to $D_c$}
@@
 \section{Simulation}
-In this section, Simulation and numerical results for the main problem are depicted.
+In this section, simulation and numerical results for the main problem are depicted.
+ \begin{table}
+ \caption {Simulation Parameter} \label{table:1a} 
+ \begin{center}
+  \begin{tabular}{||c c ||} 
+  \hline
+Parameter & Value \\ [0.5ex] 
+  \hline\hline
+  Noise power & -174dBm\\
+  \hline
+  Bandwidth & 120 KHZ \\
+  \hline
+ Maxmimun transmit Power & 30dBm \\
+  \hline
+  Minimum delay &  30msec \\
+  \hline
+  Minimum data rate &  1Mbits/sec \\ [1ex] 
+  \hline
+ \end{tabular}
+ \end{center}
+ \end{table}
 In Fig.
-\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different number of DCs with different number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}).
-In this simulation, it is assumed that each slice can be served by just one DC and it is not admitted by more than one DC.
-Proposed method is based on Algorithm \ref{alg3} and optimal method is done by MOSEK toolbox.
+\ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with the different mean number of UEs in each service (the parameters for simulation listed in table \ref{table:1a}).
+The optimal method is $0.016$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.011$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$.
+As it is shown, the Energy Efficiency is increased as mean number of UEs rises.
+\begin{figure}%[H]
+  \centering
+    \includegraphics[width=\linewidth]{figure11}
+  \caption{Energy Efficiency vs. Mean Number of UEs in each Service}
+  \label{fig:f1a}
+\end{figure} 
+In Fig.
+\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}).
+In this simulation, it is assumed that  just one DC can serve each slice, and it is not admitted by more than one DC.
+The proposed method is based on Algorithm \ref{alg3}, and optimal method is done by the MOSEK toolbox.
  \begin{table}
@@
  \end{table}
-When we have two DCs, proposed method and optimal method have approximately same ratio of admitted slices.
-But by increasing the number of DCs to five, performance of proposed method reduced.
-Using five DCs, the difference between
-proposed method and optimal method in worst case (44 slices) is about $23$ percentage. 
+When we have two DCs, the proposed method and optimal method have approximately the same ratio of admitted slices.
+But by increasing the number of DCs to five, the performance of the proposed method reduced.
+Using five DCs, the difference between the
+proposed method and the optimal method in worst case (44 slices) is about $23$ percentage. 
  \begin{table}
@@
  \end{table}
-\begin{figure}[H]
+\begin{figure}%[H]
   \centering
@@
 \ref{fig:f2}, the normalized resource consumption is depicted due to the number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}).
-In this simulation, it is assumed that number of DCs is completely enough to cover all slices.
-The optimality of placement of DCs to slices is measured.
+In this simulation, it is assumed that the number of DCs is entirely enough to cover all slices.
+The optimality of the placement of DCs to slices is measured.
 It is shown that how much resources of active DCs are not used.
-For ten slices, the difference between optimal solution and proposed solution is about $15$ percent.
-\begin{figure}[H]
+For ten slices, the difference between the optimal solution and the proposed solution is about $15$ percent.
+\begin{figure}%[H]
   \centering
@@
 \end{figure} 
+\section{Conclusion}
+In this paper, joint network slicing and power allocation is considered in an end to end O-RAN system.
+It is assumed that UEs are classified based on their service requirements.
+Also, there are number of slices served the services.
+Each slice, is consist of PRBs, RRHs, and VNFs that run on VMs.
+The limited fronthaul capacity is considered for the fiber links between RRHs and BBU-pool.
+The target is to maximize sum rate and minimize power consumption and energy cost of data centers simultaneously.
+The problem is decomposed into two sub-problems.
+Each sub-problems are solved separately by a heuristic algorithm.
+For the sub-problem A, energy efficiency vs.
+mean number of UEs in each service is depicted.
+The energy efficiency  exceeded by increasing mean number of UEs in each service.
+For the sub-problem B, two figures are shown.
+In the first one, the ratio of admitted slices that connect to just one DC, for different number of slices is denoted.
+In second figure, the normalized resource consumption of DCs is depicted.
+In each figure, heuristic algorithm is compared with the optimal method and the difference between them is discussed.
+
 \bibliographystyle{IEEEtran}

### 2019-10-25 Latex/tex/pr.tex
version last 1

@@
   \hline
- Maxmimun transmit Power & 30dBm \\
+ Maxmimun transmit Power of each RRH & 40dBm \\
   \hline
-  Minimum delay &  30msec \\
+   Maxmimun transmit Power of each UE & 30dBm \\
   \hline
-  Minimum data rate &  1Mbits/sec \\ [1ex] 
+  Minimum delay &  300usec \\
+  \hline
+  Maximum fronthaul capacity  & 20bits/sec/Hz \\ 
+   \hline
+  Minimum data rate &  120 kbits/sec \\ [1ex] 
   \hline
@@
 The optimal method is $0.016$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.011$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$.
-As it is shown, the Energy Efficiency is increased as mean number of UEs rises.
+As it is shown, the Energy Efficiency is increased as a mean number of UEs rises.
 \begin{figure}%[H]
@@
 In this simulation, it is assumed that  just one DC can serve each slice, and it is not admitted by more than one DC.
-The proposed method is based on Algorithm \ref{alg3}, and optimal method is done by the MOSEK toolbox.
+The proposed method is based on Algorithm \ref{alg3}, and the optimal method is done by the MOSEK toolbox.
  \begin{table}
@@
 Using five DCs, the difference between the
-proposed method and the optimal method in worst case (44 slices) is about $23$ percentage. 
+proposed method and the optimal method in the worst case (44 slices) is about $23$ percentage. 
  \begin{table}
@@
 It is assumed that UEs are classified based on their service requirements.
-Also, there are number of slices served the services.
+Also, there is a number of slices served the services.
 Each slice, is consist of PRBs, RRHs, and VNFs that run on VMs.
 The limited fronthaul capacity is considered for the fiber links between RRHs and BBU-pool.
-The target is to maximize sum rate and minimize power consumption and energy cost of data centers simultaneously.
+The target is to maximize the sum-rate and minimize the power consumption and energy cost of data centers simultaneously.
 The problem is decomposed into two sub-problems.
@@
 mean number of UEs in each service is depicted.
-The energy efficiency  exceeded by increasing mean number of UEs in each service.
+The energy efficiency  exceeded by increasing the mean number of UEs in each service.
 For the sub-problem B, two figures are shown.
-In the first one, the ratio of admitted slices that connect to just one DC, for different number of slices is denoted.
-In second figure, the normalized resource consumption of DCs is depicted.
-In each figure, heuristic algorithm is compared with the optimal method and the difference between them is discussed.
+In the first one, the ratio of admitted slices that connect to just one DC, for a different number of slices is denoted.
+In the second figure, the normalized resource consumption of DCs is depicted.
+In each figure, the heuristic algorithm is compared with the optimal method and the difference between them is discussed.
 

### 2019-10-27 Latex/tex/pr.tex
change latex1

@@
 \newtheorem{corollary}{Corollary}   
-
+\newcommand{\diag}{\mathop{\mathrm{diag}}}
 \begin{document}
@@
 In this paper, we elaborate joint NS in RAN and Core of O-RAN system to investigate the power 
-of each User Equipment (UE), connect slices to services and also connect physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RRHs and the cost of  physical resources in a downlink channel.
+of each User Equipment (UE), map slices to services and also map physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RRHs and the cost of  physical resources in a downlink channel.
 The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent.
-Heuristic algorithms are proposed to each of sub-problems in order to connect slices to services, optimize power consumption and connect slices to physical resources to minimize the cost of total DCs simultaneously.
+Heuristic algorithms are proposed to each of sub-problems in order to map slices to services, optimize power consumption and map slices to physical resources to minimize the cost of total DCs simultaneously.
 \end{abstract}
@@
 \section{Introduction}
-Recently, O-RAN, which is the integration and expansion of C-RAN and xRAN, is expected to be a key technology for 5G to enhance RAN performance and solve the part of challenges of mobile network operators (MNOs) in the best way.
-The Idea of O-RAN comes from two opinions.
+O-RAN, which is the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G Network, to enhance RAN performance.  
+The idea of O-RAN comes from two opinions.
 Firstly, according to real-time analytic used for artificial intelligence systems, the radio access networks must be evolved to be more intelligent and flexible than before.
-Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}.
-In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms, in order to be more flexible for MNOs especially for mobile virtual network operators (MVNOs)\cite{oran1}.
+Also O-RAN uses deep learning techniques to develop smarter layers in its architecture.
+ Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces.
+In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms, in order to be more flexible for mobile network operators MNOs especially for mobile virtual network operators (MVNOs)\cite{oran1}.
+Openness is the specific feature of O-RAN. Open interface is one of the most crucial properties for O-RAN to enable MNOs and MVNOs, to define their own services.
+The concept of software defined network (SDN), which is the separation of control plane (CP), from user plane (UP), is deployed in an intelligent O-RAN architecture.
+The seperation of CP/UP is developed  through the E1 interface.
+Moreover, this separation, promote RRM by defining Non-RT
+and Near-RT) RAN Intelligent Controller (RIC) with the A1 and E2 interfaces .
+O-RAN introduced interfaces such as open fronthaul interface that maps DU and RRU, an E2 interface, and an A1 interface between orchestration/NMS layer containing the non-real-time RIC
+(RIC non-RT) function and the eNB/gNB containing the near-real-time RIC
+(RIC near-RT) function.\cite{oranpaper}
 
 The core idea of C-RAN is to split the radio remote head (RRH) from baseband unit (BBU).
-Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities.
-Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
+Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1}.
 To communicate between BBU-Pool and RRHs, the fronthaul fiber link interface, is assumed with limited capacity.
@@
 Moreover, open north-bound and south-bound interfaces are introduced\cite{xran}.
-\begin{figure}[H]
+
+\begin{figure}
   \centering
-    \includegraphics[scale=0.55]{c5}
+    \includegraphics[scale=0.55]{c6}
   \caption{Network sliced O-RAN system}
@@
 The responsibility of wireless systems of the fifth generation covers wide range types of services.
-In order to provide the requirements of these services, NS is implemented to virtualize the shared physical network into several logical end-to-end networks.
+In order to provide the requirements of these services, network slicing (NS) is implemented to virtualize the shared physical network into several logical end-to-end networks.
+In the NS, a specific physical network hardware, run multiple virtual networks. Each virtual network is 
+defined as a slice of network \cite{lee2018dynamic}.
 Three different types of NS are introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing.
@@
 Also, UEs classified into a group of services according to their requirements.
-In addition, each service is connected to one or more Core-RAN slices based on the resource of slices.
+In addition, each service is mapped to one or more Core-RAN slices based on the resource of slices.
 Using cloud-computing in BBU-Pool, the performance of the system is enhanced by virtualizing resources
@@
 The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}. 
-In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum rate.
-Moreover, in \cite{frdl,luong2018novel,luong2018novel1} minimization of cost obtained by power consumption, also cloud processing and limited fronthaul capacity is considered.
-Furthermore, processing delay of each VM and wireless transmission delay is bounded.
+In \cite{motalleb2017optimal} power allocation in C-RAN architecture, with limited fronthaul capacity in clustered network is studied.
+In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum-rate.
+Also, two level network slicing (upper and lower level) is done.
+The admission of UEs is maximized using the heuristic algorithms.
+In addition, the allocation of BBU capacity to UEs is considered.\newline
+In \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting} minimization of cost obtained by power consumption, also cloud processing and limited power for each RRH is considered.
+Furthermore, the processing delay of each VM and wireless transmission delay taken account.
+In \cite{frdl}, the processing and transmission delay is modeled as
+a M/M/1 queue. In \cite{guo2016exploiting}, M/D/1 queue is modeled for transmission delay.
 
@@
 Also RAN is decoupled to slices to provide requirements of services.
-Optimal power allocation and joint connecting slices to services are applied.
-In addition, connecting slices to physical resources is taken to account.
+Optimal power allocation and joint mapping slices to services are applied.
+In addition, mapping slices to physical resources is taken to account.\newline
+In \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical resources is expressed.
+Also, problem statements is explained and decomposed to two
+different sub-problems. 
+In \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In \ref{simul}, numerical results, is depicted for the sub-problems.
 
-\section{System Model and Problem Formulation}
-In this section, first, we present the downlink (DL) of the O-RAN System. Then we obtain achievable rates and delays.
+\section{System Model and Problem Formulation}\label{systemmodel}
+In this section, first, we first present the system model, Then we obtain achievable rates and delays for the downlink (DL) of the O-RAN architecture.
 Afterward, the main problem is expressed.
@@
 Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single-antenna user equipments (UEs) that require certain service.
-Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs) as it is defined in the standard of LTE that the bandwidth (BW) of the channel is divided to PRBs in time series \cite{lee2018dynamic}.
-All RRHs in a slice that is connected to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}.
-Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity.
-Suppose we have two processing layers in the BBU-Pool of O-RAN system. The lower layer is consist of high-PHY and MAC, and the upper layer is consist of RLC, PDCP and SDAP.
-Assume we have $M_1$ VMs in the first layer and $M_2$ VMs in the second layer for processing data .
-For simplicity, suppose each VNF run on a VM and there is a one-to-one connection between VNFs and VMs.
+Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs).
+All RRHs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}.
+Each RRH $r \in \{1,2,...,R \}$ is mapped to BBU pool via an optical fiber link with limited fronthaul capacity.
+Suppose we have two processing layers in the BBU-Pool of O-RAN system which contain VNFs. The lower layer consist of high-PHY and MAC, and the upper layer consist of RLC, PDCP and SDAP.
+Assume we have $M_1$ VNFs in the first layer and $M_2$ VNFs in the second layer for processing data .
 Each VNF in both layers connects to one or more slices.
-So in $s^{th}$ slice, there are $M_{s_1}$ VNFs in the first layer and $M_{s_2}$ VNFs in the second layer.
+So in $s^{th}$ slice, there are $M_{s,1}$ VNFs in the first layer and $M_{s,2}$ VNFs in the second layer.
 All VNFs in first and second layer has the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
 Also, RRHs and PRBs can serve more than one slices. 
-\subsection{Achievable Rate}
-The achievable data rate for $i^{th}$ UE in $v^{th}$ service can be written as 
+\subsection{The Achievable Rate}
+The achievable data rate for the $i^{th}$ UE in the $v^{th}$ service can be written as 
 \begin{equation}\label{eq1}
-\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}});
+\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}}),
 \end{equation}
-Where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from 
+where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from 
 \begin{equation}\label{eq2}
-\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}};
+\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
 \end{equation}
-Where $p_{u(v,i)}$ represents the transmission power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service, also, 
+where $p_{u(v,i)}$ represents the transmission power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service, and 
 $\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
@@
 Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals.
-Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is connected to service $v$ or not.
-If $a_{v,s} =1$ then, $v^{th}$ service is connected to $s^{th}$ slice; otherwise, it is not connected.
+Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is mapped to service $v$ or not.
+If $a_{v,s} =1$ then, $v^{th}$ service is mapped to $s^{th}$ slice; otherwise, it is not mapped.
 \newline 
@@
 In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which, is made from signal compression in BBU.
-Besides, $\boldsymbol{P}_{U_v} = diag(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})$.
+Besides, $\boldsymbol{P}_{U_v} = \diag{(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})}$.
 \newline
-Furthermore, $\zeta_{U_v,k,s} \delequal \{\zeta_{u(v,1),k,s},\zeta_{u(v,2),k,s},...,\zeta_{u(v,N_{U_v}),k,s}\}$,
-$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter, demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
+Furthermore, $\zeta_{k,s}^{U_v} \delequal \{\zeta_{k,s}^{u(v,1)},\zeta_{k,s}^{u(v,2)},...,\zeta_{k,s}^{u(v,N_{U_v})}\}$,
+$\zeta_{k,s}^{u(v,i)} \in \{0,1\}$ is a binary parameter, which demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
 $\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$ 
@@
 \end{equation}
-Where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
+where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
 and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. Moreover,
@@
 \end{equation}
-As a result the rate of users on the fronthual link between BBU-Pool and the $j^{th}$ RRH in $s^{th}$ slice is formulated as 
+Nevertheless, the rate of users on the fronthual link between BBU-Pool and the $j^{th}$ RRH in $s^{th}$ slice is formulated as \cite{simeone2016cloud, 1111}
 \begin{equation}
@@
 \end{equation}
-Where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is connected to service $v$ or not \cite{simeone2016cloud, 1111}.
+where, $a_{v,s}$ is a binary variable denotes which the slice $s$ is mapped to service $v$ or not .
 \subsection{Mean Delay}
-Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for $i^{th}$ UE of $v^{th}$ service. 
-Therefore, the mean arrival data rate of UEs connect to $s^{th}$ slice in the first layer is 
-$\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$.  
-Furthermore, the mean arrival data rate of the second layer is approximately equal to the mean arrival data rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
-It is assumed there are dispatchers in each layer for each slice to divide the incoming traffic to VNFs \cite{frdl,luong2018novel,luong2018novel1}.
+Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service. 
+Therefore, the mean arrival data rate of UEs map to $s^{th}$ slice in the first layer of the O-RAN which contains SDAP, PDCP, and RLC is 
+$\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where, $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not. 
+Furthermore, the mean arrival data rate of the second layer which contains MAC and HY/PHY is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
+It is assumed there are dispatchers in each layer for each slice to divide the incoming traffic to VNFs equally.
+Each dispatcher first processes the incoming traffic and divides equally to each VNF  \cite{frdl,luong2018novel,luong2018novel1}.
 Suppose the baseband processing of each VNF is depicted as a M/M/1 processing queue.
-Each packet is routed by one of VNFs of slices. So the mean delay of slice $s$ which is related to incoming traffic rate routed to
-each VNF in the first layer can be written as follow
+Each packet is processed by one of the VNFs of slices. So the mean delay of the $s^{th}$ slice in the first layer which is modeled as M/M/1 queue from queuing theory is formulated as
 \begin{equation}
@@
 \end{subequations}
-\section{Proposed Method For Problem \eqref{constraints1}}
+\section{Proposed Method}\label{proposedmethod}
 In this subsection, the proposed method is applied to solve the optimization problem.
@@
 \end{algorithm}
-\section{Simulation}
+\section{Simulation}\label{simul}
 In this section, simulation and numerical results for the main problem are depicted.

### 2019-10-27 Latex/tex/pr.tex
change latex2

@@
 In addition, mapping slices to physical resources is taken to account.\newline
-In \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical resources is expressed.
+The contribution of the paper is expressed as follow:
+\begin{itemize}
+\item In this paper, joint RAN slicing and resource allocation is considered in an end to end O-RAN system.
+\item UEs are categorized into different class of services based on their service requirements.
+RAN which contains RRHs, PRBs, and VNFs ,in the two layer of processing, are classified into different group of slices.
+\item The problem is decomposed into two independent sub-problems. 
+\item Heuristic algorithms are applied for the sub-problems to efficiently obtain the solution.
+\end{itemize}
+
+The rest of the paper is organized as follows.
+In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical resources is expressed.
 Also, problem statements is explained and decomposed to two
 different sub-problems. 
-In \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In \ref{simul}, numerical results, is depicted for the sub-problems.
+In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results, is depicted for the sub-problems.
 
@@
 Suppose the baseband processing of each VNF is depicted as a M/M/1 processing queue.
-Each packet is processed by one of the VNFs of slices. So the mean delay of the $s^{th}$ slice in the first layer which is modeled as M/M/1 queue from queuing theory is formulated as
+Each packet is processed by one of the VNFs of slices.
+So the mean delay of the $s^{th}$ slice in the first and the second layer, which is modeled as M/M/1 queue from queuing theory, is formulated as follow
+,respectively
 \begin{equation}
-d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}}.
+\begin{split}
+d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}} \\
+d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}.
+\end{split}
 \end{equation}
-Also, the delay of $s^{th}$ slice in the second layer is
-\begin{equation}
-d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}.
-\end{equation}
+where, $\mu_1$ and $\mu_2$ is the computational capacity of the first and the second layer respectively.
 In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice as a result of wireless transmission. The arrival data rate of wireless transmission

### 2019-10-27 Latex/tex/pr.tex
12233

@@
 \newcommand{\diag}{\mathop{\mathrm{diag}}}
+\DeclareMathOperator{\E}{\mathbb{E}}
 \begin{document}
@@
 Moreover, this separation, promote RRM by defining Non-RT
-and Near-RT) RAN Intelligent Controller (RIC) with the A1 and E2 interfaces .
+and Near-RT) RAN Intelligent Controller (RIC) with the A1 and E2 interfaces.
 O-RAN introduced interfaces such as open fronthaul interface that maps DU and RRU, an E2 interface, and an A1 interface between orchestration/NMS layer containing the non-real-time RIC
 (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC
-(RIC near-RT) function.\cite{oranpaper}
+(RIC near-RT) function \cite{oranpaper}.
 
@@
 The rest of the paper is organized as follows.
-In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical resources is expressed.
+In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is expressed.
 Also, problem statements is explained and decomposed to two
@@
 In this section, first, we first present the system model, Then we obtain achievable rates and delays for the downlink (DL) of the O-RAN architecture.
-Afterward, the main problem is expressed.
+Afterward, we explained physical data center resources.
+Finally, the main problem is expressed.
 \subsection{System Model}
@@
 Each RRH $r \in \{1,2,...,R \}$ is mapped to BBU pool via an optical fiber link with limited fronthaul capacity.
-Suppose we have two processing layers in the BBU-Pool of O-RAN system which contain VNFs. The lower layer consist of high-PHY and MAC, and the upper layer consist of RLC, PDCP and SDAP.
+Suppose we have two processing layers in the BBU-Pool of O-RAN system which contain VNFs. The lower layer consist of high-PHY, MAC, and RLC, and the upper layer consist of RRC, PDCP and SDAP.
 Assume we have $M_1$ VNFs in the first layer and $M_2$ VNFs in the second layer for processing data .
@@
 \newline 
-To obtain SNR as formulated in \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service which is given by \eqref{eq3}
+To obtain SNR as formulated in \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service
 \begin{equation}\label{eq3}
@@
 \end{equation}
-where, $a_{v,s}$ is a binary variable denotes which the slice $s$ is mapped to service $v$ or not .
+where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .
 \subsection{Mean Delay}
@@
 It is assumed there are dispatchers in each layer for each slice to divide the incoming traffic to VNFs equally.
-Each dispatcher first processes the incoming traffic and divides equally to each VNF  \cite{frdl,luong2018novel,luong2018novel1}.
+The dispatcher processes the incoming traffic and divides it equally to processed by VNFs  \cite{frdl,luong2018novel,luong2018novel1}.
 Suppose the baseband processing of each VNF is depicted as a M/M/1 processing queue.
@@
 \begin{split}
-d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}} \\
-d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}.
+d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}} \\
+d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}.
 \end{split}
 \end{equation}
-where, $\mu_1$ and $\mu_2$ is the computational capacity of the first and the second layer respectively.
-In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice as a result of wireless transmission. The arrival data rate of wireless transmission
- is equal to the arrival data rate of dispatchers (used as a traffic divider) for each slice divide traffic data and transmit divided traffic to VNFs.
+where, $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layer respectively, due to the fact that the service time of each data packet has an exponential distribution for $\mu_i>\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
+In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice as a result of wireless transmission . The arrival data rate of wireless transmission
+ is equal to the arrival data rate of dispatchers (used as a traffic divider) for each slice \cite{frdl}.
 Moreover, it is assumed that the service time of transmission queue for each slice $s$ has 
- an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1}. Therefore, 
+ an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore, 
 the mean delay of the transmission layer is 
@@
 \end{equation}
-Where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$.
+where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
 Mean delay of each slice is
@@
 Each VNF requires
-physical resources that contain RAM, Memory, and CPU.
-Let, the required resources for VNF $f$ in slice $s$ is represented by a three-dimensional vector as follow
+physical resources that contain memory, storage and CPU.
+Let the required resources for VNF $f$ in slice $s$ is represented by a three-dimensional vector as follow
 \begin{equation}
-\bar{\Omega}_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \};
+\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \};
 \end{equation} 
-Where,$\bar{\Omega}_{(f,s)}\in \mathbb{C}^{3}$ and $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory, and CPU, respectively.
-Moreover total amount of required RAM, Memory, and CPU of all VNFs of a slice is a three-dimensional vector which is defined as
+where, $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, storage, and CPU, respectively.
+Moreover the total amount of required memory, storage and CPU of all VNFs of a slice is a three-dimensional vector which is defined as
 \begin{equation}
-\bar{\Omega}_{s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{(f,s)};
+\bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\};
 \end{equation}
-Also, there are $D_c$ data centers (DC), which served VNFs. Each DC contains several servers that supply VNF's requirements.
-The amount of RAM, Memory, and CPU is denoted by $\tau_{R_{j}}, \tau_{M_{j}}$and $\tau_{C_{j}} $ for $j^{th}$ DC, respectively.
+Also, there are $D_c$ data centers (DC), serving VNFs. Each DC contains several servers that supply VNF's requirements.
+The amount of memory, storage and CPU is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$and $\tau_{C_{j}} $ for $j^{th}$ DC, respectively.
 \begin{equation*}
-\tau_j = \{\tau_{R_{j}}, \tau_{M_{j}}, \tau_{C_{j}} \};
+\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \};
 \end{equation*}
@@
 \end{equation}
-Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ is the weight of RAM, Memory, and CPU that is used for Algorithm \ref{alg3}.
+Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ is the weight of memory, storage and CPU that is used for Algorithm \ref{alg3}.
 In this system model, the placement of physical DC resources to VNFs is considered. $y_{s,d}$ is a binary variable indicates whether $d^{th}$ DC is connected to VNFs of $s^{th}$ slice or not.
 \subsection{Problem Statement}
-One of the most important parameters to estimate the optimality of the system is energy efficiency which is represented as a sum-rate to sum-power 
+One of the most important parameters to measure the optimality of the system is energy efficiency which is represented as a sum-rate to sum-power 
 \begin{equation}
@@
 \end{equation}
-Where, $\sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RRHs in all slices.
+where, $\sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RRHs in all slices.
 Also, $\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services.
@@
 \begin{equation*}
-\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
+\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d} - \E{[\phi]}\sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} .
 \end{equation*} 
-In this paper, the main goal is to maximize sum-rate and minimize sum-power (the total power of all RRHs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,
+Our goal is to maximize sum-rate and minimize sum-power (the total power of all RRHs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,
 \begin{subequations}
@@
 \end{algorithm}
-\section{Simulation}\label{simul}
+\section{Numerical Results}\label{simul}
 In this section, simulation and numerical results for the main problem are depicted.

### 2019-10-27 Latex/tex/pr.tex
8 page

@@
 \DeclareMathOperator{\E}{\mathbb{E}}
+
 \begin{document}
@@
 \begin{itemize}
-\item In this paper, joint RAN slicing and resource allocation is considered in an end to end O-RAN system.
+\item In this paper, joint network slicing and resource allocation is considered in an end to end O-RAN system.
 \item UEs are categorized into different class of services based on their service requirements.
@@
 \begin{equation}\label{eq3}
-\bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v};
+\bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v} \
+\mathfrak{y}_{R_s}\zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v},
 \end{equation}
+where, $\mathfrak{y}_{R_s} = \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_s}$
 Where $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
@@
 where, $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layer respectively, due to the fact that the service time of each data packet has an exponential distribution for $\mu_i>\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
+Besides, $\alpha_{s}$ is the data arrival rate which is divided
+by dispatcher before arriving to VNFs. So the data arrival rate of each VNF in each layer of slice $s$ is $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
 In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice as a result of wireless transmission . The arrival data rate of wireless transmission
@@
 \end{equation*}
-Also we define a weighted parameter of $\tau_j$ as follow
-\begin{equation}\label{wt}
-\begin{split}
-\hat{\Omega}_{s}^{tot} &= w_R \bar{\Omega}_{R_s}^{tot} + w_M \bar{\Omega}_{M_s}^{tot} + w_C \bar{\Omega}_{C_s}^{tot} \\
-\hat{\tau}_j &= w_R \tau_{R_{j}} + w_M \tau_{M_{j}} + w_C \tau_{C_{j}},
-\end{split}
-\end{equation}
-Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ is the weight of memory, storage and CPU that is used for Algorithm \ref{alg3}.
 In this system model, the placement of physical DC resources to VNFs is considered. $y_{s,d}$ is a binary variable indicates whether $d^{th}$ DC is connected to VNFs of $s^{th}$ slice or not.
@@
 \begin{equation}
-\eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_{r_{tot}}(\boldsymbol{P},\boldsymbol{A})},
+\eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_r^{{tot}}(\boldsymbol{P},\boldsymbol{A})},
 \end{equation}
-where, $\sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RRHs in all slices.
-Also, $\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services.
+where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RRHs in all slices.
+Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services.
 Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
@@
 \begin{equation*}
-\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d} - \E{[\phi]}\sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} .
+\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
 \end{equation*} 
+Also, a cost function for the placement of VNFs into DCs is defined as 
+\begin{equation}\label{eqpsi}
+ \psi_{tot} = \phi_{tot} - \nu \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s}
+\end{equation}
+where, $\nu$ is a design variable to value between the first term of \eqref{eqpsi} which is the total power consumption of physical resources and the second term that is shown the amount of admitted slices to have physical resources.
 Our goal is to maximize sum-rate and minimize sum-power (the total power of all RRHs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,
@@
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{Y})} \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\psi_{tot}(\boldsymbol{Y})} \\
 \text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i, 
@@
 & \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} &&\quad \forall s,\label{c23} \\
-& \bar{\Omega}_{\mathfrak{z}(s)}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                      
- && \quad \forall \mathfrak{z}, \forall s; \label{c22}
+ &\bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                     
+ && \quad  \forall s, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}
 \end{alignat}
@@
 \end{subequations}
-Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}]  \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]   \forall s ,  \forall d $ is a binary variable shown whether
+where, $\boldsymbol{P} =[p_{u(v,k)}] \:\: \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}] \:\: \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
 the physical DC is connected to a VNFs of a slice or not. 
@@
 Also \eqref{c13} shows that the rate of each UE is more than a threshold.
-\eqref{c14} and \eqref{c15} depicts that the capacity of the fronthaul link is limited, and the delay of receiving signal should be less than a threshold, respectively.
+\eqref{c14} and \eqref{c15} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
 Furthermore, \eqref{c21}
-ensures that each service is connected to one or more slices.
-Also, \eqref{c23} guarantees that each slice (VNFs in two layers of slices) has been placed to one or more physical resources of DCs. Moreover, \eqref{c22}  $\mathfrak{z}\in \{M,R,C\}$, supports 
+ensures that each service is connected to at least one slice.
+Also, \eqref{c23}, guarantees that each slice (VNFs in two layers of slices) has been placed to one or more physical resources of DCs.
+Moreover, in \eqref{c22}  $\mathcal{E} = \{M,S,C\}$ and the constraint supports
 that we have enough physical resources for VNFs of each slice.\newline 
-The main optimizaiton problem which, is formulated as \eqref{constraints}, can be decomposed into two independent optimization problems A and B since the variables can be obtained independently.
-Problem A is defined as
+The optimizaiton problem in \eqref{constraints}, can be decomposed into two independent optimization problems A and B since the variables can be obtained independently and respectively. In problem A, 
+the variables $\boldsymbol{P}$ and $ \boldsymbol{A}$ is obtained. The problem A is as follow
 \begin{subequations}
@@
 \end{subequations}
-Problem B is 
+In problem B, $ \boldsymbol{Y}$ is obtained. The problem B is
 \begin{subequations}
 \begin{alignat}{4}
-\min\limits_{\boldsymbol{y} }   \quad &   \phi_{tot}(\boldsymbol{Y})\\
+\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
 \text{subject to} \quad & \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} &&\quad \forall s, \\
-&  \bar{\Omega}_{\mathfrak{z}(s)}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                      
- && \quad \forall \mathfrak{z}, \forall s. \label{eqomega}
+ &\bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                     
+ && \quad  \forall s, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
 \end{alignat}
@@
 \end{subequations}
-\section{Proposed Method}\label{proposedmethod}
+\section{Hueristic Method}\label{proposedmethod}
 In this subsection, the proposed method is applied to solve the optimization problem.
@@
 two different part that can be solved iteratively. 
+Firstly, in the first part of sub-problem A, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in the problem \eqref{constraints1}.
+Also we fixed $\eta = 0$.
+Afterward, by achieving $\boldsymbol{A}$, in the second part, we just need to acquire $\boldsymbol{P}$.
+This part of the problem can be approximated and converted to a convex problem, so the problem can be solved by convex methods.
+After solving $\boldsymbol{P}$, $\eta$ is updated.
+Then in the next iteration, with new $\boldsymbol{P}$
+and $\eta$ the two parts of the problems is solved until the algorithm converged. 
 \subsection{First Part of Sub-Problem A}\label{firstsub}
-Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration.
 Two different methods are applied to acquire $\boldsymbol{A}$. 
-The details of the heuristic algorithm are represented in \textbf{Algorithm} \eqref{alg}.  
+The details of the heuristic algorithm are represented in algorithm \ref{alg}.  
 \begin{algorithm}
@@
 \begin{proof}
-See \cite{aaa}, Appendix A
+See \cite[Appendix A]{aaa}
 \end{proof}
-The second subproblem can  be solved using the Lagrangian function and iterative algorithm. 
-Since, Interference is a function of the power of UEs, for simplicity, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference (the worst-case). 
-In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15}.
+The second sub-problem can  be solved using the Lagrangian function and iterative algorithm. 
+Since, Interference is a function of the power of UEs, to make it tractable, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference (the worst-case). 
+In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively ).
+Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
 The Lagrangian function is written as follow
@@
 &- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
-&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,j)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\ 
+&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,i)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\ 
 &+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.\\ 
@@
 \end{equation}
-Where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$.
-Also, $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
-Optimal power is obtained from equation \eqref{lagrang} as follow
+where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$. Optimal power is obtained from  \eqref{lagrang} 
 \begin{equation}
@@
 $\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$. 
-By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained. 
+By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained \cite{mimoCran}. 
 %\section*{References}
 \subsection{Solving two part of Sub-problem A iteratively}
-In \eqref{firstsub} and \eqref{secondsub}, the details of solving each part of the subproblem are depicted. 
-Firstly, by the fixing power of each UE, $\boldsymbol{A}$ is obtained using Algorithm \eqref{alg}.
-Then by using the sub-gradient method, \eqref{secondsub} is solved and iteratively solves these problems until variables converge.
-Here, the algorithm of solving sub-problem A is shown in \textbf{Algorithm} \eqref{alg2}
+In \eqref{firstsub} and \eqref{secondsub}, the details of solving each part of the sub-problem are depicted. 
+Firstly, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in the problem \eqref{constraints1} and using algorithm \eqref{alg}.
+Also we fixed $\eta = 0$.
+Afterward, by achieving $\boldsymbol{A}$, in the second part, we acquire $\boldsymbol{P}$ using the sub-gradient method.
+After solving $\boldsymbol{P}$, $\eta$ is updated.
+Then in the next iteration, with new $\boldsymbol{P}$
+and $\eta$ the two parts of the problems is solved until the algorithm converged. 
+Here, the algorithm of solving sub-problem A is shown in algorithm \eqref{alg2}
 \begin{algorithm}
@@
 \subsection{Sub-Problem B}
-In this subsection, we want to solve  \eqref{constraints2}, which is the placement of virtual resources to physical resources in order to minimize the number of using DCs. 
+In this subsection, we would like to solve  \eqref{constraints2}, which is the placement of virtual resources to physical resources in order to minimize the cost function $\psi_{tot}$. 
 To achieve optimum $\boldsymbol{Y}$ heuristic algorithm is applied.
-The details of the heuristic algorithm are written in \textbf{Algorithm} \eqref{alg3}.
-In this algorithm, firstly, we sort slices and DCs according to their sum weighted of their requirements.
-Secondly, we start mapping from the most needed slices to the DC with the most physical resources.
-After mapping DCs to slices, if some slices are not admitted, we start admitting remaining slices to more than one DCs.
-In the end, if DC with the lowest physical resources is free and can be served instead of DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption.
+The details of the heuristic algorithm are written in algorithm \eqref{alg3}.
+In this algorithm, firstly, we sort slices and DCs according to their sum-weighted of their requirements (line \ref{31} and line \ref{32} of algorithm \ref{alg3}).
+We define a weighted parameter for $\Omega_{\mathfrak{z},s}^{tot}$ and $\tau_j^\mathfrak{z}$ as follow
+\begin{equation}\label{wt}
+\begin{split}
+\hat{\Omega}_{s}^{tot} &= w_M \bar{\Omega}_{M,s}^{tot} + w_S \bar{\Omega}_{S,s}^{tot} + w_C \bar{\Omega}_{C,s}^{tot} \\
+\hat{\tau}_j &= w_M \tau_{{j}}^M + w_S \tau_{{j}}^S + w_C \tau_{{j}}^C,
+\end{split}
+\end{equation}
+where, $\boldsymbol{w} = \{w_M, w_S, w_C\}$ is the weight of memory, storage and CPU.
+Secondly, we start mapping from the most needed slices to the DC with the most physical resources (from line \ref{33} to line \ref{34} of algorithm \ref{alg3}).
+After mapping DCs to slices, if some slices are not admitted, we start admitting remaining slices to more than one DCs (from line \ref{35} to line \ref{36} of algorithm \ref{alg3}).
+At the end, if DC with the lowest physical resources is free and can be served instead of DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption (line \ref{37} of algorithm \ref{alg3}).
 If a slice does not admit to a specific DC, it remains for the next placement. In next placement the remaining slices, map to more than one DC according to their requirements.
@@
 \begin{algorithmic}[1]
-\State Sort Slices according to $\hat{\Omega}_{s}^{tot} , \forall s$ in descending order.
-\State Sort DCs according to $\hat{\tau}_j , \forall j$ in descending order. 
+\State Sort Slices according to $\hat{\Omega}_{s}^{tot} , \forall s$ in descending order.\label{31}
+\State Sort DCs according to $\hat{\tau}_j , \forall j$ in descending order. \label{32}
 \State $\boldsymbol{Y} = \boldsymbol{0}$
-\For {$d \gets 1$ to $D_c$}
+\For {$d \gets 1$ to $D_c$}\label{33}
 \For {$s \gets 1$ to $S$}
@@
 \State Set $y_{s,d} = 1$;
-\State {$\tau_j$ $\gets$ {$\tau_j - \bar{\Omega}_{s}^{tot}$}}
+\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
 \EndIf 
@@
 \EndFor 
-\State \textbf{end for}
-\State  $\{ind_{remaining} = s|({\sum_{d=1}^{D_c}y_{s,d}==0})\}$
+\State \textbf{end for} \label{34}
+\State  $ind_{rem} = \{s|({\sum_{d=1}^{D_c}y_{s,d}==0})\}$ \label{35}
 \State Sort remaining amount of DCs same as before in descending order.
 \State Sort remaining slices same as before in descending order.
-\For {$r \gets 1$ to $S_{remaining}$}
+\For {$r \gets 1$ to $S_{rem}$}
 \For {$n \gets 1$ to $D_c$}
 \State Set $y_{s,d} = 1$;
-\State {$\bar{\Omega}_{s}^{tot}$ $\gets$ {$\bar{\Omega}_{s}^{tot}- \tau_j$}}
+\State {$\bar{\Omega}_{{\mathfrak{z}},s}^{tot}$ $\gets$ {$\bar{\Omega}_{{\mathfrak{z}},s}^{tot}- \tau_j^{\mathfrak{z}}$}}
 \If {$\bar{\Omega}_{s}^{tot}==0$}
 \State Set $y_{s,d} = 1$;
-\State {$\tau_j$ $\gets$ {$\tau_j - \bar{\Omega}_{s}^{tot}$}}
+\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
 \State {break inner loop}
@@
 \EndFor 
-\State \textbf{end for}
-\State Remapping DCs must be done to prevent wasting Energy
+\State \textbf{end for} \label{36}
+\State Remapping DCs must be done to prevent wasting Energy \label{37}
 \end{algorithmic}
@@
 \ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with the different mean number of UEs in each service (the parameters for simulation listed in table \ref{table:1a}).
+The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$ and iteratively updates $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$.
 The optimal method is $0.016$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.011$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$.
@@
 In Fig.
-\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}).
+\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices (the parameters for simulation listed in table \ref{table:1} and also we set $w_C = 320$, $w_S = 100$, $w_M =1$).
 In this simulation, it is assumed that  just one DC can serve each slice, and it is not admitted by more than one DC.
 The proposed method is based on Algorithm \ref{alg3}, and the optimal method is done by the MOSEK toolbox.
+\begin{small}
  \begin{table}
@@
   \hline\hline
-  Mean of CPU for DCs & 25.6GHz\\
+  Mean of CPU for DCs & 320GHz\\
   \hline
-  Mean of RAM for DCs & 128G\\
+  Mean of Memory for DCs & 1T\\
   \hline
- Mean of Memory for DCs & 10T \\
+ Mean of Storage for DCs & 100T \\
   \hline
-   Mean of CPU for Slices & 3.2GHz\\
+   Mean of CPU for Slices & 32GHz\\
   \hline
-  Mean of RAM for Slices & 16G\\
+  Mean of Memory for Slices & 100G\\
   \hline
- Mean of Memory for Slices & 1T \\ [1ex] 
+ Mean of Storage for Slices & 10T \\ [1ex] 
   \hline
@@
  \end{table}
+\end{small}
 When we have two DCs, the proposed method and optimal method have approximately the same ratio of admitted slices.
@@
 proposed method and the optimal method in the worst case (44 slices) is about $23$ percentage. 
- \begin{table}
- \caption {Simulation Parameter} \label{table:2} 
- \begin{center}
-  \begin{tabular}{||c c ||} 
-  \hline
-  Parameter & Value \\ [0.5ex] 
-  \hline\hline
-   $w_C$ & 320\\
-  \hline
-  $w_R$  & 64\\
-  \hline
- $w_M$  & 1 \\ [1ex] 
-  \hline
- \end{tabular}
- \end{center}
- \end{table}
 \begin{figure}%[H]
@@
 In Fig.
-\ref{fig:f2}, the normalized resource consumption is depicted due to the number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}).
+\ref{fig:f2}, the normalized resource consumption is depicted due to the number of slices (the parameters for simulation listed in table \ref{table:1} and also we set $w_C = 320$, $w_S = 100$, $w_M =1$).
 In this simulation, it is assumed that the number of DCs is entirely enough to cover all slices.

### 2019-10-28 Latex/tex/pr.tex
last version for figures

@@
 
-\title{Joint Power Allocation and Network Slicing In an End to End O-RAN System
+\title{Joint Power Allocation and Network Slicing in an End-to-End O-RAN System
 }
@@
 
-To increase enrgy efficiency and optimize the allocation of resources, Network Slicing (NS) is considered as the best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks.
+To increase energy efficiency and optimize the allocation of resources, Network Slicing (NS) is considered as the best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks.
 Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to-end network.
@@
 In this paper, we elaborate joint NS in RAN and Core of O-RAN system to investigate the power
-of each User Equipment (UE), map slices to services and also map physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RRHs and the cost of  physical resources in a downlink channel.
+of each User Equipment (UE), map slices to services and also map physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RUs and the cost of  physical resources in a downlink channel.
 The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent.
@@
 \section{Introduction}
-O-RAN, which is the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G Network, to enhance RAN performance.  
-The idea of O-RAN comes from two opinions.
-Firstly, according to real-time analytic used for artificial intelligence systems, the radio access networks must be evolved to be more intelligent and flexible than before.
-Also O-RAN uses deep learning techniques to develop smarter layers in its architecture.
- Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces.
-In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms, in order to be more flexible for mobile network operators MNOs especially for mobile virtual network operators (MVNOs)\cite{oran1}.
-Openness is the specific feature of O-RAN. Open interface is one of the most crucial properties for O-RAN to enable MNOs and MVNOs, to define their own services.
+O-RAN, as the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G Networks to extensively enhance the RAN performance.
+The core idea of C-RAN is to split the radio remote head (RU) from baseband unit (BBU).
+Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1}.
+To communicate between BBU-Pool and RUs, the fronthaul fiber link interface, is assumed \cite{frdl,simeone2016cloud,motalleb2017optimal}.
+On the other hand, xRAN technology has three fundamental features.
+The control plane is decoupled from user plane.
+Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
+Moreover, open north-bound and south-bound interfaces are introduced \cite{xran}.
+
+O-RAN virtualizes the elements of the radio access networks, separate them and define appropriate open interfaces for connection of these elements.
+Moreover,O-RAN uses machine learning techniques to develop smarter RAN layers in its architecture.
+In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms \cite{oran1}.
+
+Openness is the specific feature of O-RAN. Open interface is one of the most crucial properties for O-RAN to enable mobile network operators (MNOs) to define their own services.
 The concept of software defined network (SDN), which is the separation of control plane (CP), from user plane (UP), is deployed in an intelligent O-RAN architecture.
-The seperation of CP/UP is developed  through the E1 interface.
-Moreover, this separation, promote RRM by defining Non-RT
-and Near-RT) RAN Intelligent Controller (RIC) with the A1 and E2 interfaces.
-O-RAN introduced interfaces such as open fronthaul interface that maps DU and RRU, an E2 interface, and an A1 interface between orchestration/NMS layer containing the non-real-time RIC
+Moreover, this separation promotes RRM to use non-realtime (RT) and near-realtime (NRT) RAN Intelligent Controller (RIC).
+In the O-RAN architecture, distributed unit (DU) is a logical node hosting RLC/MAC/High-PHY layer. 
+Moreover, central unit (CU) is a logical node hosting RRC, SDAP and PDCP.
+Also, radio unit (RU),  is a logical node hosting LOW-PHY layer and 
+RF processing \cite{oranpaper}.
+O-RAN introduces interfaces such as open fronthaul interface that maps DU and RRU, an E2 interface, and an A1 interface between orchestration/NMS layer containing the non-real-time RIC
 (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC
-(RIC near-RT) function \cite{oranpaper}.
-
-The core idea of C-RAN is to split the radio remote head (RRH) from baseband unit (BBU).
-Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1}.
-To communicate between BBU-Pool and RRHs, the fronthaul fiber link interface, is assumed with limited capacity.
-The compression of a message passed through these links is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.
-
-xRAN technology, released in April 2018 as the next generation of RAN, has three fundamental features.
-The Control plane is decoupled from User plane.
-Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
-Moreover, open north-bound and south-bound interfaces are introduced\cite{xran}.
+(RIC near-RT) function.
 
@@
   \centering
-    \includegraphics[scale=0.55]{c6}
+    \includegraphics[scale=0.55]{c6.pdf}
   \caption{Network sliced O-RAN system}
@@
 \end{figure}
-To evolve servicing in 5G, separation of elements of software and hardware of network is deployed in network functions virtualization (NFV) technology.
-In this technology, the functionality of networks is virtualized and divided into blocks of virtual network function (VNF).
-The responsibility of wireless systems of the fifth generation covers wide range types of services.
-In order to provide the requirements of these services, network slicing (NS) is implemented to virtualize the shared physical network into several logical end-to-end networks.
-In the NS, a specific physical network hardware, run multiple virtual networks. Each virtual network is 
-defined as a slice of network \cite{lee2018dynamic}.
-Three different types of NS are introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing.
-In Core-RAN Slicing, each slice of RAN is mapped to slices of Core.
-Also, UEs classified into a group of services according to their requirements.
-In addition, each service is mapped to one or more Core-RAN slices based on the resource of slices.
-Using cloud-computing in BBU-Pool, the performance of the system is enhanced by virtualizing resources
-into virtual machines (VMs).
-Each VM has a computing processor in order to be run by the Virtual Network Functions (VNFs) which processed arrival data.
-Also, VNFs are mapped to physical resources through NS techniques\cite{frdl,luong2018novel,luong2018novel1}.
 
-The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}. 
-In \cite{motalleb2017optimal} power allocation in C-RAN architecture, with limited fronthaul capacity in clustered network is studied.
+To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and is referred to as network functions virtualization (NFV).
+Virtual network function (VNF) are functional blocks of the system in this case.
+5G networks are expected to host several services with different requirements simultaneously.
+Network slicing is considered as a solution for such demand.
+A network slice is a logical end-to-end network which provide service with specific requirements.
+Multiple network slices run on the same physical network infrastructure which are managed and operate independently \cite{lee2018dynamic}.
+Slicing can be defined for the RAN, for the core or both of these networks \cite{ns1}.
+In core-RAN Slicing, each slice of RAN is attached to a slice of core.
+
+Based on their type of request, UEs are classified into various services where UEs in the same service has similar service requests.
+In addition, each service is mapped to one or more slices based on the resource of the slices.
+Each VNF of the ORAN is mapped to one or some virtual machines (VMs) in the data center.
+For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.
+
+%The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}.
+In \cite{oranT},  the evolution of RAN in the  5G network is described.
+The architecture of C-RAN and X-RAN is expressed and development of the O-RAN from C-RAN and X-RAN is explained.
+Also requirements of the network in terms of capacity and latency is taken account.
+In \cite{oran12},  the O-RAN architecture, is studied.
+The eight work groups include focus areas of O-RAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software is discussed.
+In \cite{motalleb2017optimal}, power allocation in C-RAN architecture, with limited fronthaul capacity in clustered network is studied.
 In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum-rate.
@@
 In addition, the allocation of BBU capacity to UEs is considered.\newline
-In \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting} minimization of cost obtained by power consumption, also cloud processing and limited power for each RRH is considered.
+In \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting} minimization of cost obtained by power consumption, also cloud processing and limited power for each RU is considered.
 Furthermore, the processing delay of each VM and wireless transmission delay taken account.
-In \cite{frdl}, the processing and transmission delay is modeled as
-a M/M/1 queue. In \cite{guo2016exploiting}, M/D/1 queue is modeled for transmission delay.
+In \cite{frdl}, the processing and transmission delay is modeled as a M/M/1 queue.
+In \cite{guo2016exploiting}, M/D/1 queue is modeled for transmission delay.
 
-In this paper, as  depicted in figure \ref{fig:c11}, the downlink of the O-RAN system is assumed. UEs are divided to different groups according to 
-their service requirements.
-Also RAN is decoupled to slices to provide requirements of services.
-Optimal power allocation and joint mapping slices to services are applied.
-In addition, mapping slices to physical resources is taken to account.\newline
+In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
+The RAN is divided to three layers including RU, DU, and CU with open interfaces.
+DU and CU are running on general purpose data centers.
+UEs are divided to different services according to their service requirements.
+RAN resources are decoupled to slices to provide requirements of services.
+Optimal power allocation and joint mapping of slices to services are applied.
+In addition, mapping slices to physical resources is taken to account.
 The contribution of the paper is expressed as follow:
@@
 \item UEs are categorized into different class of services based on their service requirements.
-RAN which contains RRHs, PRBs, and VNFs ,in the two layer of processing, are classified into different group of slices.
+RAN which contains RUs, PRBs, and VNFs ,in the two layer of processing, are classified into different group of slices.
 \item The problem is decomposed into two independent sub-problems.
@@
 In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is expressed.
-Also, problem statements is explained and decomposed to two
-different sub-problems. 
-In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results, is depicted for the sub-problems.
+Then, problem statement is explained and decomposed into two independent sub-problems.
+In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results are provided for the problem.
 
 \section{System Model and Problem Formulation}\label{systemmodel}
-In this section, first, we first present the system model, Then we obtain achievable rates and delays for the downlink (DL) of the O-RAN architecture.
-Afterward, we explained physical data center resources.
+In this section, first, we  present the system model.
+Then, we obtain achievable rates and delays for the downlink (DL) of the O-RAN system.
+Afterward, we discuss about assignment of physical data center resources.
 Finally, the main problem is expressed.
 \subsection{System Model}
-Suppose there are $S$ slices Serving $V$ services.
-Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single-antenna user equipments (UEs) that require certain service.
-Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs).
-All RRHs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}.
-Each RRH $r \in \{1,2,...,R \}$ is mapped to BBU pool via an optical fiber link with limited fronthaul capacity.
-Suppose we have two processing layers in the BBU-Pool of O-RAN system which contain VNFs. The lower layer consist of high-PHY, MAC, and RLC, and the upper layer consist of RRC, PDCP and SDAP.
+Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$
+single-antenna user equipments (UEs) that require certain service.
+Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ Physical Resource Blocks (PRBs).
+All RUs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}.
+Each RU $r \in \{1,2,...,R \}$ is mapped to DU via an optical fiber link with limited fronthaul capacity.
+Suppose we have two processing layers in the DU/CU of O-RAN system which contain VNFs. The lower layer consist of high-PHY, MAC, and RLC, and the upper layer consist of RRC, PDCP and SDAP.
 Assume we have $M_1$ VNFs in the first layer and $M_2$ VNFs in the second layer for processing data .
@@
 All VNFs in first and second layer has the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
-Also, RRHs and PRBs can serve more than one slices. 
+Also, RUs and PRBs can serve more than one slices.
 \subsection{The Achievable Rate}
@@
 \end{equation}
-where $p_{u(v,i)}$ represents the transmission power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service, and 
-$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
-In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
+where $p_{u(v,i)}$ represents the transmission power allocated by RUs to $i^{th}$ UE in $v^{th}$ service, and
+$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
+In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
 Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals.
@@
 Where $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
-In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which, is made from signal compression in BBU.
+In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which, is made from signal compression in DU.
 Besides, $\boldsymbol{P}_{U_v} = \diag{(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})}$.
@@
 $\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
-shows the channel matrix between RRH set $\mathcal{R}_s$ to UE set
+shows the channel matrix between RU set $\mathcal{R}_s$ to UE set
 $\mathcal{U}_v$, besides.
-%The channel vector from the RRH of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below
+%The channel vector from the RU of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below
 %\begin{equation}
@@
 and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. Moreover,
-${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RRH in $s^{th}$ slice.
+${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RU in $s^{th}$ slice.
 As it is clear, Interference signal for each UE is comming from UEs using the same PRB.
@@
 Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in  \eqref{eq1} and \eqref{eq2}.\newline
-let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from $j^{th}$ RRH in $s^{th}$ slice.
+let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from $j^{th}$ RU in $s^{th}$ slice.
 from \eqref{eq3} we have,
@@
 \end{equation}
-Nevertheless, the rate of users on the fronthual link between BBU-Pool and the $j^{th}$ RRH in $s^{th}$ slice is formulated as \cite{simeone2016cloud, 1111}
+Nevertheless, the rate of users on the fronthual link between DU and the $j^{th}$ RU in $s^{th}$ slice is formulated as \cite{simeone2016cloud, 1111}
 \begin{equation}
@@
 \end{equation}
-where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RRHs in all slices.
+where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RUs in all slices.
 Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services.
@@
 where, $\nu$ is a design variable to value between the first term of \eqref{eqpsi} which is the total power consumption of physical resources and the second term that is shown the amount of admitted slices to have physical resources.
-Our goal is to maximize sum-rate and minimize sum-power (the total power of all RRHs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,
+Our goal is to maximize sum-rate and minimize sum-power (the total power of all RUs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,
 \begin{subequations}
@@
 the physical DC is connected to a VNFs of a slice or not.
-\eqref{c11} and \eqref{c12} indicate that the power of each RRH do not exceed the maximum power, and the power of each UE is a positive integer value, respectively.
+\eqref{c11} and \eqref{c12} indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively.
 Also \eqref{c13} shows that the rate of each UE is more than a threshold.
@@
 \State Sort services according to the number of UEs in it and their requirements in the descending order.
-\State Sort slices according to the weighted linear combination of number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in the descending order. 
+\State Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs in two layers and the Capacity of their resources in the descending order.
 \For {$i \gets 1$ to $S$}
@@
 \State Set $a_{i,j} = 1$
-\State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RRHs)
+\State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RUs)
 \If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} is not applied}
@@
   \hline
- Maxmimun transmit Power of each RRH & 40dBm \\
+ Maxmimun transmit Power of each RU & 40dBm \\
   \hline
@@
   \hline
-  Maximum fronthaul capacity  & 20bits/sec/Hz \\ 
+  Maximum fronthaul capacity  & 200bits/sec/Hz \\
    \hline
-  Minimum data rate &  120 kbits/sec \\ [1ex] 
+  Minimum data rate &  10 bits/sec/Hz \\ [1ex]
   \hline
@@
 The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$ and iteratively updates $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$.
-The optimal method is $0.016$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.011$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$.
+The optimal method is $0.1$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.09$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$.
 As it is shown, the Energy Efficiency is increased as a mean number of UEs rises.
@@
   \centering
-    \includegraphics[width=\linewidth]{figure11}
+    \includegraphics[width=\linewidth]{fig1_last}
   \caption{Energy Efficiency vs. Mean Number of UEs in each Service}
@@
   \centering
-    \includegraphics[width=\linewidth]{f111}
+    \includegraphics[width=\linewidth]{f112}
   \caption{Ratio of Admitted Slices connected to just one DC vs. Total slices}
@@
   \centering
-    \includegraphics[width=\linewidth]{fig2_last}
+    \includegraphics[width=\linewidth]{fig22_last}
   \caption{Normalized Resource Consumption vs. Number of Slices}
@@
 Also, there is a number of slices served the services.
-Each slice, is consist of PRBs, RRHs, and VNFs that run on VMs.
-The limited fronthaul capacity is considered for the fiber links between RRHs and BBU-pool.
+Each slice, is consist of PRBs, RUs, and VNFs that run on VMs.
+The limited fronthaul capacity is considered for the fiber links between RUs and DU
 The target is to maximize the sum-rate and minimize the power consumption and energy cost of data centers simultaneously.

### 2019-10-28 Latex/tex/pr.tex
last version for figures1

@@
 In addition, each service is mapped to one or more slices based on the resource of the slices.
-Each VNF of the ORAN is mapped to one or some virtual machines (VMs) in the data center.
+Each VNF of the O-RAN is mapped to one or some virtual machines (VMs) in the data center.
 For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.
@@
  \label{c11} \\
-&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k,\label{c12} \\
+&  p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k,\label{c12} \\
+&  p_{u_{(v,k)}}  \leq P_{max}^U  &&\quad \forall v, \forall k,\label{c122} \\
 &\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k,\label{c13} \\
@@
 the physical DC is connected to a VNFs of a slice or not.
-\eqref{c11} and \eqref{c12} indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively.
+\eqref{c11}, \eqref{c12} and \eqref{c122} indicate that the power of each RU do not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE do not exceed maximum power, respectively.
 Also \eqref{c13} shows that the rate of each UE is more than a threshold.
@@
 &p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
+&  p_{u_{(v,k)}}  \leq P_{max}^U  &&\quad \forall v, \forall k,  \\
 &\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\
@@
 In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively ).
-Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
+Assume $\boldsymbol{\lambda}$, $\boldsymbol{\chi}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
 The Lagrangian function is written as follow
@@
 - \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
-&+\sum\limits_{s=1}^{S} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{d_{(s,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
+&+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
+&-\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \chi_{u_{(v,k)}} (p_{u_{(v,k)}}  - P_{max}^U)\\
 &- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
@@
 \begin{equation}
-p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
+p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }-\chi_{u_{(v,k)}}]^+
 \end{equation}

### 2019-10-28 Latex/tex/pr.tex
chi add

@@
 
-\title{Joint Power Allocation and Network Slicing in an End-to-End O-RAN System
+\title{Joint Power Allocation and Network Slicing in an End-to-End ORAN System \vspace{-.1cm}
 }
-
-\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
-\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
-\textit{Tehran University}\\
-Tehran, Iran \\
-mojdeh.karbalaee@ut.ac.ir}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
-\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
-\textit{Tehran University}\\
-Tehran, Iran \\
-vmansouri@ut.ac.ir}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
-\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
-\textit{Tehran University}\\
-Tehran, Iran \\
-salar.nouri@ut.ac.ir}
-
+%
+%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%mojdeh.karbalaee@ut.ac.ir}
+%\and
+%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%vmansouri@ut.ac.ir}
+%\and
+%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%salar.nouri@ut.ac.ir}
+%}
+  \author{
+    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-Mansouri, Salar Nouri Naghadeh}
+    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
+    Email: \{mojdeh.karbalaee, vmansouri,salar.nouri@ut.ac.ir\}@ut.ac.ir,
+    \vspace{-.2cm}
+  }
   }
@@
 Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a more flexible and openness radio access network which is the Open-RAN
-(O-RAN) for the fifth generation of wireless technology.
-
+(ORAN) for the fifth generation of wireless technology.
 To increase energy efficiency and optimize the allocation of resources, Network Slicing (NS) is considered as the best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks.
 Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to-end network.
-
-In this paper, we elaborate joint NS in RAN and Core of O-RAN system to investigate the power
+In this paper, we elaborate joint NS in RAN and Core of ORAN system to investigate the power
 of each User Equipment (UE), map slices to services and also map physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RUs and the cost of  physical resources in a downlink channel.
@@
 \begin{IEEEkeywords}
-O-RAN, Network Slicing, Energy Efficiency, Data Center (DC)
+ORAN, Network Slicing, Energy Efficiency, Data Center (DC)
 \end{IEEEkeywords}
@@
 \section{Introduction}
-O-RAN, as the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G Networks to extensively enhance the RAN performance.
-The core idea of C-RAN is to split the radio remote head (RU) from baseband unit (BBU).
-Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1}.
-To communicate between BBU-Pool and RUs, the fronthaul fiber link interface, is assumed \cite{frdl,simeone2016cloud,motalleb2017optimal}.
+Open RAN (ORAN), as the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G networks to extensively enhance the RAN performance.
+The core idea of C-RAN is to split the radio remote head (RRU) from the baseband unit (BBU).
+Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1,frdl,simeone2016cloud,motalleb2017optimal}.
 On the other hand, xRAN technology has three fundamental features.
@@
 
-O-RAN virtualizes the elements of the radio access networks, separate them and define appropriate open interfaces for connection of these elements.
-Moreover,O-RAN uses machine learning techniques to develop smarter RAN layers in its architecture.
-In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms \cite{oran1}.
-
-Openness is the specific feature of O-RAN. Open interface is one of the most crucial properties for O-RAN to enable mobile network operators (MNOs) to define their own services.
-The concept of software defined network (SDN), which is the separation of control plane (CP), from user plane (UP), is deployed in an intelligent O-RAN architecture.
+ORAN virtualizes the elements of the radio access networks, separate them and define appropriate open interfaces for connection of these elements.
+Moreover, ORAN uses machine learning techniques to develop smarter RAN layers in its architecture.
+In an innovative ORAN system, the programmable RAN software is decoupled from hardware \cite{oran1}.
+Open interface is one of the most crucial properties for ORAN to enable mobile network operators (MNOs) to define their own services.
+The concept of software defined network (SDN), which is the separation of control plane from user plane, is deployed in an intelligent ORAN architecture.
 Moreover, this separation promotes RRM to use non-realtime (RT) and near-realtime (NRT) RAN Intelligent Controller (RIC).
-In the O-RAN architecture, distributed unit (DU) is a logical node hosting RLC/MAC/High-PHY layer. 
-Moreover, central unit (CU) is a logical node hosting RRC, SDAP and PDCP.
-Also, radio unit (RU),  is a logical node hosting LOW-PHY layer and 
+In the ORAN architecture, distributed unit (DU) is a logical node hosting RLC/MAC/High-PHY layer.
+Moreover, central unit (CU) is a logical node hosting RRC, SDAP and PDCP. Also, radio unit (RU)  is a logical node hosting LOW-PHY layer and
 RF processing \cite{oranpaper}.
-O-RAN introduces interfaces such as open fronthaul interface that maps DU and RRU, an E2 interface, and an A1 interface between orchestration/NMS layer containing the non-real-time RIC
-(RIC non-RT) function and the eNB/gNB containing the near-real-time RIC
-(RIC near-RT) function.
-
-\begin{figure}
-  \centering
-    \includegraphics[scale=0.55]{c6.pdf}
-  \caption{Network sliced O-RAN system}
-  \label{fig:c11}
-\end{figure}
+ORAN introduces interfaces such as open fronthaul interface that connects DU and RU(i.e., E2 interface), and an A1 interface between orchestration/NMS layer containing the non-real-time RIC (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC (RIC near-RT) function.
 
@@
 Multiple network slices run on the same physical network infrastructure which are managed and operate independently \cite{lee2018dynamic}.
-Slicing can be defined for the RAN, for the core or both of these networks \cite{ns1}.
-In core-RAN Slicing, each slice of RAN is attached to a slice of core.
+Slicing can be defined for the RAN, for the core network or both of these networks \cite{ns1}.
 
-Based on their type of request, UEs are classified into various services where UEs in the same service has similar service requests.
-In addition, each service is mapped to one or more slices based on the resource of the slices.
-Each VNF of the O-RAN is mapped to one or some virtual machines (VMs) in the data center.
+Based on their type of request, UEs are classified into various services, where UEs in the same service have similar service requests.
+In addition, each service is mapped to one or more slices based on the resources of the slices.
+Each VNF of the ORAN is mapped to one or some virtual machines (VMs) in the data center.
 For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.
@@
 In \cite{oranT},  the evolution of RAN in the  5G network is described.
-The architecture of C-RAN and X-RAN is expressed and development of the O-RAN from C-RAN and X-RAN is explained.
-Also requirements of the network in terms of capacity and latency is taken account.
-In \cite{oran12},  the O-RAN architecture, is studied.
-The eight work groups include focus areas of O-RAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software is discussed.
+The architecture of C-RAN and X-RAN is expressed and development of the ORAN from C-RAN and X-RAN is explained.
+Also requirements of the network in terms of capacity and latency is taken into account.
+In \cite{oran12},  the ORAN architecture is studied.
+The eight work groups is discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software.
+To the best of our knowledge, there is not work in the literature to model ORAN systems.
+
+%We shortly review related works in the area of C-RAN and xRAN.
 In \cite{motalleb2017optimal}, power allocation in C-RAN architecture, with limited fronthaul capacity in clustered network is studied.
-In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum-rate.
+In \cite{lee2018dynamic}, dynamic network slicing is considered in heterogeneous CRAN (H-CRAN) to maximize the weighted sum-rate.
 Also, two level network slicing (upper and lower level) is done.
 The admission of UEs is maximized using the heuristic algorithms.
-In addition, the allocation of BBU capacity to UEs is considered.\newline
+In addition, the allocation of BBU capacity to UEs is considered.
 In \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting} minimization of cost obtained by power consumption, also cloud processing and limited power for each RU is considered.
-Furthermore, the processing delay of each VM and wireless transmission delay taken account.
+Furthermore, the processing delay of each VM and wireless transmission delay are taken into account.
 In \cite{frdl}, the processing and transmission delay is modeled as a M/M/1 queue.
-In \cite{guo2016exploiting}, M/D/1 queue is modeled for transmission delay.
+In \cite{guo2016exploiting}, M/D/1 queue is used to modeled the transmission delay.
 
-In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
+\begin{figure}
+  \centering
+    \includegraphics[scale=0.55]{c6.pdf}
+  \caption{Network sliced ORAN system}
+  \label{fig:c11}
+\end{figure}
+
+In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
 The RAN is divided to three layers including RU, DU, and CU with open interfaces.
@@
 \begin{itemize}
-\item In this paper, joint network slicing and resource allocation is considered in an end to end O-RAN system.
+\item In this paper, joint network slicing and resource allocation is considered in an end to end ORAN system.
 \item UEs are categorized into different class of services based on their service requirements.
@@
 \section{System Model and Problem Formulation}\label{systemmodel}
+
 In this section, first, we  present the system model.
-Then, we obtain achievable rates and delays for the downlink (DL) of the O-RAN system.
+Then, we obtain achievable rates and delays for the downlink (DL) of the ORAN system.
 Afterward, we discuss about assignment of physical data center resources.
@@
 \subsection{System Model}
-Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$
+Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
 single-antenna user equipments (UEs) that require certain service.
-Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ Physical Resource Blocks (PRBs).
-All RUs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}.
-Each RU $r \in \{1,2,...,R \}$ is mapped to DU via an optical fiber link with limited fronthaul capacity.
-Suppose we have two processing layers in the DU/CU of O-RAN system which contain VNFs. The lower layer consist of high-PHY, MAC, and RLC, and the upper layer consist of RRC, PDCP and SDAP.
-Assume we have $M_1$ VNFs in the first layer and $M_2$ VNFs in the second layer for processing data .
-Each VNF in both layers connects to one or more slices.
-So in $s^{th}$ slice, there are $M_{s,1}$ VNFs in the first layer and $M_{s,2}$ VNFs in the second layer.
-All VNFs in first and second layer has the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
+Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), {\color{red} one DU and one CU}.
+All RUs in a slice, that is mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}.
+Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.
+There are two processing layers one in the DU and one on the CU of ORAN system, each represented with a VNF.
+The lower layer (i.e., DU) consists of high-PHY, MAC, and RLC, and the upper layer (i.e., CU) consists of RRC, PDCP and SDAP.
+Assume we have $M_1$ VNFs in the DU layer and $M_2$ VNFs in the CU layer for processing data.
+Each VNF in both layers belongs to one or more slices.
+So, in the $s^{th}$ slice, there are $M_{s,1}$ VNFs in the DU layer and $M_{s,2}$ VNFs in the CU layer.
+The VNFs in the DU and CU layers have the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
 Also, RUs and PRBs can serve more than one slices.
@@
 \begin{equation}\label{eq3}
-\bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v} \
+\textstyle \bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v} \
 \mathfrak{y}_{R_s}\zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v},
 \end{equation}
-where, $\mathfrak{y}_{R_s} = \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_s}$
-Where $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
-In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which, is made from signal compression in DU.
+where $\mathfrak{y}_{R_s} = \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_s}$
+and $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
+In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise, which is made from signal compression in DU.
 Besides, $\boldsymbol{P}_{U_v} = \diag{(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})}$.
@@
 \begin{equation}
-\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}.
+\textstyle \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}.
 \end{equation}
@@
 &+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
-&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}}.
+&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}},
 \end{split}
 \end{equation}
-where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
+where $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
 and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. Moreover,
 ${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RU in $s^{th}$ slice.
-As it is clear, Interference signal for each UE is comming from UEs using the same PRB.
+Interference signal for each UE is coming from UEs using the same PRB.
 If we replace $p_{u_{(v,l)}}$ and $p_{u_{(y,l)}}$ by $P_{max}$, an upper bound $\bar{I}_{u_{(v,i)}}$ is obtained for $I_{u_{(v,i)}}$.
 Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in  \eqref{eq1} and \eqref{eq2}.\newline
-let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from $j^{th}$ RU in $s^{th}$ slice.
-from \eqref{eq3} we have,
+Let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from the $j^{th}$ RU in $s^{th}$ slice.
+From \eqref{eq3}, we have,
 \begin{equation}
@@
 where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .
+
 \subsection{Mean Delay}
-Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
-Therefore, the mean arrival data rate of UEs map to $s^{th}$ slice in the first layer of the O-RAN which contains SDAP, PDCP, and RLC is
-$\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where, $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not.
-Furthermore, the mean arrival data rate of the second layer which contains MAC and HY/PHY is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
-It is assumed there are dispatchers in each layer for each slice to divide the incoming traffic to VNFs equally.
-The dispatcher processes the incoming traffic and divides it equally to processed by VNFs  \cite{frdl,luong2018novel,luong2018novel1}.
-Suppose the baseband processing of each VNF is depicted as a M/M/1 processing queue.
-Each packet is processed by one of the VNFs of slices.
-So the mean delay of the $s^{th}$ slice in the first and the second layer, which is modeled as M/M/1 queue from queuing theory, is formulated as follow
-,respectively
-\begin{equation}
-\begin{split}
-d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}} \\
-d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}.
-\end{split}
-\end{equation}
-where, $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layer respectively, due to the fact that the service time of each data packet has an exponential distribution for $\mu_i>\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
-Besides, $\alpha_{s}$ is the data arrival rate which is divided
-by dispatcher before arriving to VNFs. So the data arrival rate of each VNF in each layer of slice $s$ is $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
-In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice as a result of wireless transmission . The arrival data rate of wireless transmission
+
+Assume the packet arrival of UEs follows  a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
+Therefore, the mean arrival data rate of UEs mapped to the $s^{th}$ slice in the CU layer is $\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not.
+Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
+It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
+Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
+Each packet is processed by one of the VNFs of a slice.
+So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as $d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}}$, and $d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}},$ respectively.
+where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.%, due to the fact that the service time of each data packet has an exponential distribution for $\mu_i>\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
+Besides, $\alpha_{s}$ is the  arrival rate which is divided
+by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
+In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice on the  wireless link. The arrival data rate of wireless link
  is equal to the arrival data rate of dispatchers (used as a traffic divider) for each slice \cite{frdl}.
@@
  an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
-the mean delay of the transmission layer is
-\begin{equation}
-d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
-\end{equation}
+the mean delay of the transmission layer is $d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};$
 where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
@@
 physical resources that contain memory, storage and CPU.
-Let the required resources for VNF $f$ in slice $s$ is represented by a three-dimensional vector as follow
+Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
 \begin{equation}
-\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \};
+\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \},
 \end{equation}
-where, $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, storage, and CPU, respectively.
-Moreover the total amount of required memory, storage and CPU of all VNFs of a slice is a three-dimensional vector which is defined as
+where $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, storage, and CPU, respectively.
+Moreover, the total amount of required memory, storage and CPU of all VNFs of a slice is defined as
 \begin{equation}
-\bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\};
+\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.
 \end{equation}
-Also, there are $D_c$ data centers (DC), serving VNFs. Each DC contains several servers that supply VNF's requirements.
-The amount of memory, storage and CPU is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$and $\tau_{C_{j}} $ for $j^{th}$ DC, respectively.
+Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
+The amount of memory, storage and CPU is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$and $\tau_{C_{j}} $ for the $j^{th}$ DC, respectively
 \begin{equation*}
-\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \};
+\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \},
 \end{equation*}
-In this system model, the placement of physical DC resources to VNFs is considered. $y_{s,d}$ is a binary variable indicates whether $d^{th}$ DC is connected to VNFs of $s^{th}$ slice or not.
+In this system model, the assignment of physical DC resources to VNFs is considered.
+Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is connected to the VNFs of $s^{th}$ slice or not.
 \subsection{Problem Statement}
-One of the most important parameters to measure the optimality of the system is energy efficiency which is represented as a sum-rate to sum-power
+An important criterion to measure the optimality of a system is energy efficiency represented as the sum-rate to sum-power
 \begin{equation}
-\eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_r^{{tot}}(\boldsymbol{P},\boldsymbol{A})},
+\textstyle \eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_r^{{tot}}(\boldsymbol{P},\boldsymbol{A})},
 \end{equation}
@@
 \begin{equation*}
-\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
+\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
 \end{equation*}
@@
 \begin{equation}\label{eqpsi}
- \psi_{tot} = \phi_{tot} - \nu \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s}
+\textstyle  \psi_{tot} = \phi_{tot} - \nu \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s}
 \end{equation}
@@
 \max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\psi_{tot}(\boldsymbol{Y})} \\
-\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,
+\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} \quad \forall s, \forall i,
  \label{c11} \\
-&  p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k,\label{c12} \\
-&  p_{u_{(v,k)}}  \leq P_{max}^U  &&\quad \forall v, \forall k,\label{c122} \\
-&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k,\label{c13} \\
-&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \label{c14}\\
-&D_{s} \leq D_{s}^{max}  &&\quad \forall s,\label{c15} \\
-& \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s, \label{c21} \\
-& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} &&\quad \forall s,\label{c23} \\
- &\bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}
- && \quad  \forall s, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}
+&p_{u_{(v,k)}}  \geq 0  \quad \forall v, \forall k,\label{c12} \\
+&  p_{u_{(v,k)}}  \leq P_{max}^U  \quad \forall v, \forall k,\label{c122} \\
+&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} \quad \forall v, \forall k,\label{c13} \\
+&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max} \quad \forall s, \forall i, \label{c14}\\
+&D_{s} \leq D_{s}^{max} \quad \forall s,\label{c15} \\
+& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 \quad \forall s, \label{c21} \\
+& \textstyle  \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s,\label{c23} \\
+ &\textstyle  \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}  \forall s, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}
 \end{alignat}
@@
 \end{subequations}
-where, $\boldsymbol{P} =[p_{u(v,k)}] \:\: \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}] \:\: \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
+where $\boldsymbol{P} =[p_{u(v,k)}] \:\: \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}] \:\: \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
 the physical DC is connected to a VNFs of a slice or not.
-\eqref{c11}, \eqref{c12} and \eqref{c122} indicate that the power of each RU do not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE do not exceed maximum power, respectively.
+\eqref{c11}, \eqref{c12} and \eqref{c122}, indicate that the power of each RU do not exceed the maximum power of RU, and the power of each UE is a positive integer value, and the power of each UE do not exceed maximum power of UE, respectively.
 Also \eqref{c13} shows that the rate of each UE is more than a threshold.
@@
 that we have enough physical resources for VNFs of each slice.\newline
-The optimizaiton problem in \eqref{constraints}, can be decomposed into two independent optimization problems A and B since the variables can be obtained independently and respectively. In problem A,
+The optimization problem in \eqref{constraints} can be decomposed into two independent optimization problems A and B since the variables can be obtained independently and respectively. In problem A,
 the variables $\boldsymbol{P}$ and $ \boldsymbol{A}$ is obtained. The problem A is as follow
@@
 &p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
-&  p_{u_{(v,k)}}  \leq P_{max}^U  &&\quad \forall v, \forall k,  \\
+&p_{u_{(v,k)}}  \leq P_{max}^U  &&\quad \forall v, \forall k,  \\
 &\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\
@@
 &D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
-& \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s.
+& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s.
 \end{alignat}
@@
 \min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
-\text{subject to} \quad & \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} &&\quad \forall s, \\
- &\bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}
- && \quad  \forall s, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
+\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
+ &\textstyle  \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}
+\forall s, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
 \end{alignat}
@@
 \end{subequations}
-\section{Hueristic Method}\label{proposedmethod}
-In this subsection, the proposed method is applied to solve the optimization problem.
-We want to solve \eqref{constraints1}. Since the problem is non-convex and NP-Hard, iterative algorithm is applied.
-To solve the problem and obtain $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} into
+\section{Heuristic Method}\label{proposedmethod}
+In this subsection, a heuristic  method is proposed to solve the problem in \eqref{constraints1} which is non-convex and computationally hard.
+To make it tractable, we divide problem \eqref{constraints1} into
 two different part that can be solved iteratively.
-Firstly, in the first part of sub-problem A, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in the problem \eqref{constraints1}.
-Also we fixed $\eta = 0$.
-Afterward, by achieving $\boldsymbol{A}$, in the second part, we just need to acquire $\boldsymbol{P}$.
+In the first part of sub-problem A, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in \eqref{constraints1}.
+Also, we set $\eta = 0$.
+Afterward, by achieving $\boldsymbol{A}$, in the second part, we find $\boldsymbol{P}$ by using \eqref{constraints1}.
 This part of the problem can be approximated and converted to a convex problem, so the problem can be solved by convex methods.
@@
 Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$ the two parts of the problems is solved until the algorithm converged.
+and $\eta$, the two parts of the problems are solved. We repeat this procedure until the algorithm is converged.
 \subsection{First Part of Sub-Problem A}\label{firstsub}
@@
 \begin{theorem}\label{t2}
- $\eta^*$ which is the optimum energy efficiency can be achieved if
+The optimum energy efficiency is achieved if
 \begin{equation}\label{q2}
-\begin{split}
-&\max \limits_{\boldsymbol{P}} (\mathfrak{R}_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=\\
-& \mathfrak{R}_{tot}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
-\end{split}
+%\begin{split}
+\max \limits_{\boldsymbol{P}} (\mathfrak{R}_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=
+ \mathfrak{R}_{tot}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
+%\end{split}
 \end{equation}
@@
 The second sub-problem can  be solved using the Lagrangian function and iterative algorithm.
-Since, Interference is a function of the power of UEs, to make it tractable, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference (the worst-case).
-In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively ).
-Assume $\boldsymbol{\lambda}$, $\boldsymbol{\chi}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
+Since, Interference is a function of the power of UEs, to make it tractable, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference.
+In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively).
+Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\chi}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
 The Lagrangian function is written as follow
@@
 \begin{split}
-\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
+\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\chi}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
 - \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
@@
   \hline
-  Maximum fronthaul capacity  & 200bits/sec/Hz \\
+  Maximum fronthaul capacity  & 200 bits/sec/Hz \\
    \hline
@@
 \section{Conclusion}
-In this paper, joint network slicing and power allocation is considered in an end to end O-RAN system.
-It is assumed that UEs are classified based on their service requirements.
-Also, there is a number of slices served the services.
-Each slice, is consist of PRBs, RUs, and VNFs that run on VMs.
-The limited fronthaul capacity is considered for the fiber links between RUs and DU
-The target is to maximize the sum-rate and minimize the power consumption and energy cost of data centers simultaneously.
+In this paper, joint network slicing and power allocation were considered in an ORAN system.
+It is assumed that UEs are classified based on their requirements into services.
+Also, there is a number of slices serving the services.
+Each slice consists of PRBs, RUs, and VNFs that support CU and DU.
+The limited fronthaul capacity is considered for the fiber links between RUs and DU.
+The target was to maximize the sum-rate and minimize the power consumption and energy cost of data centers simultaneously.
 The problem is decomposed into two sub-problems.
-Each sub-problems are solved separately by a heuristic algorithm.
-For the sub-problem A, energy efficiency vs.
+Each sub-problem is solved separately by a heuristic algorithm.
+Using numerical results, we validate the heuristic method and study the performance of the algorithms.
+%For the sub-problem A, energy efficiency vs.
 mean number of UEs in each service is depicted.

### 2019-10-28 Latex/tex/pr.tex
submit version

@@
 \DeclareMathOperator{\E}{\mathbb{E}}
-
+\usepackage[margin=0.7in]{geometry}
+\setlength{\columnsep}{11mm}
 \begin{document}
@@
   \centering
-    \includegraphics[scale=0.55]{c6.pdf}
+    \includegraphics[scale=0.55]{c7.pdf}
   \caption{Network sliced ORAN system}
@@
 single-antenna user equipments (UEs) that require certain service.
-Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), {\color{red} one DU and one CU}.
+Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
 All RUs in a slice, that is mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}.
@@
 Each packet is processed by one of the VNFs of a slice.
-So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as $d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}}$, and $d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}},$ respectively.
+So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as $d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},$ and $d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}$, respectively.
 where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.%, due to the fact that the service time of each data packet has an exponential distribution for $\mu_i>\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
@@
  an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
-the mean delay of the transmission layer is $d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};$
+the mean delay of the transmission layer is
+\begin{equation}
+ d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
+\end{equation}
 where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
@@
 &p_{u_{(v,k)}}  \geq 0  \quad \forall v, \forall k,\label{c12} \\
-&  p_{u_{(v,k)}}  \leq P_{max}^U  \quad \forall v, \forall k,\label{c122} \\
 &\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} \quad \forall v, \forall k,\label{c13} \\
@@
 the physical DC is connected to a VNFs of a slice or not.
-\eqref{c11}, \eqref{c12} and \eqref{c122}, indicate that the power of each RU do not exceed the maximum power of RU, and the power of each UE is a positive integer value, and the power of each UE do not exceed maximum power of UE, respectively.
+\eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively.
 Also \eqref{c13} shows that the rate of each UE is more than a threshold.
@@
 &p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
-&p_{u_{(v,k)}}  \leq P_{max}^U  &&\quad \forall v, \forall k,  \\
 &\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\
@@
 In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively).
-Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\chi}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
+Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
 The Lagrangian function is written as follow
@@
 &+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
-&-\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \chi_{u_{(v,k)}} (p_{u_{(v,k)}}  - P_{max}^U)\\
 &- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
@@
 \begin{equation}
-p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }-\chi_{u_{(v,k)}}]^+
+p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
 \end{equation}
@@
   \hline
-   Maxmimun transmit Power of each UE & 30dBm \\
-  \hline
   Minimum delay &  300usec \\

### 2019-10-28 Latex/tex/pr.tex
submit version1

@@
 Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice.
-So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as $d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},$ and $d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}$, respectively.
+Each packet is processed by one of the VNFs of a slice. So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
+\begin{equation}
+\begin{split}
+d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},\\
+d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}.
+\end{split}
+\end{equation}
 where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.%, due to the fact that the service time of each data packet has an exponential distribution for $\mu_i>\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.

### 2019-10-29 Latex/tex/pr.tex
last version -revised

@@
 of each User Equipment (UE), map slices to services and also map physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RUs and the cost of  physical resources in a downlink channel.
-The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent.
+The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems.
 Heuristic algorithms are proposed to each of sub-problems in order to map slices to services, optimize power consumption and map slices to physical resources to minimize the cost of total DCs simultaneously.
@@
 Moreover, this separation promotes RRM to use non-realtime (RT) and near-realtime (NRT) RAN Intelligent Controller (RIC).
-In the ORAN architecture, distributed unit (DU) is a logical node hosting RLC/MAC/High-PHY layer.
-Moreover, central unit (CU) is a logical node hosting RRC, SDAP and PDCP. Also, radio unit (RU)  is a logical node hosting LOW-PHY layer and
+In the ORAN architecture, distributed unit (DU) is a logical node having RLC/MAC/High-PHY layer.
+Moreover, central unit (CU) is a logical node having RRC, SDAP and PDCP. Also, radio unit (RU) is a logical node having LOW-PHY layer and
 RF processing \cite{oranpaper}.
-ORAN introduces interfaces such as open fronthaul interface that connects DU and RU(i.e., E2 interface), and an A1 interface between orchestration/NMS layer containing the non-real-time RIC (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC (RIC near-RT) function.
+ORAN introduces interfaces such as open fronthaul interface that connects DU and RU (i.e., E2 interface), and an A1 interface between orchestration/NMS layer containing the non-real-time RIC (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC (RIC near-RT) function.
 
-To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and is referred to as network functions virtualization (NFV).
+To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and referred as network functions virtualization (NFV).
 Virtual network function (VNF) are functional blocks of the system in this case.
@@
 In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
-The RAN is divided to three layers including RU, DU, and CU with open interfaces.
+The RAN is divided into three layers including RU, DU, and CU with open interfaces.
 DU and CU are running on general purpose data centers.
@@
 Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
+Slices can have shared resources.
 All RUs in a slice, that is mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}.
 Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.
-There are two processing layers one in the DU and one on the CU of ORAN system, each represented with a VNF.
+There are two processing layers one in the DU and one in the CU of ORAN system, each represented with a VNF.
 The lower layer (i.e., DU) consists of high-PHY, MAC, and RLC, and the upper layer (i.e., CU) consists of RRC, PDCP and SDAP.
@@
 \subsection{Mean Delay}
-
 Assume the packet arrival of UEs follows  a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
@@
 \end{equation}
-where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.%, due to the fact that the service time of each data packet has an exponential distribution for $\mu_i>\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
+where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.
 Besides, $\alpha_{s}$ is the  arrival rate which is divided
@@
 In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice on the  wireless link. The arrival data rate of wireless link
- is equal to the arrival data rate of dispatchers (used as a traffic divider) for each slice \cite{frdl}.
+ is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
 Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
@@
 where $\boldsymbol{P} =[p_{u(v,k)}] \:\: \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}] \:\: \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
-the physical DC is connected to a VNFs of a slice or not.
+the physical DC is mapped to a VNFs of a slice or not.
 \eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively.
@@
 Furthermore, \eqref{c21}
-ensures that each service is connected to at least one slice.
+ensures that each service is mapped to at least one slice.
 Also, \eqref{c23}, guarantees that each slice (VNFs in two layers of slices) has been placed to one or more physical resources of DCs.
@@
 that we have enough physical resources for VNFs of each slice.\newline
-The optimization problem in \eqref{constraints} can be decomposed into two independent optimization problems A and B since the variables can be obtained independently and respectively. In problem A,
-the variables $\boldsymbol{P}$ and $ \boldsymbol{A}$ is obtained. The problem A is as follow
+The optimization problem in \eqref{constraints} can be decomposed into two independent optimization problems A and B since the variables can be obtained independently and respectively.
+Firstly we need to solve problem A.
+After obtaining $\boldsymbol{P}$ and $ \boldsymbol{A}$, problem B can be solved by having the value of $ \boldsymbol{A}$.
+The problem A is as follow
 \begin{subequations}
@@
 Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$, the two parts of the problems are solved. We repeat this procedure until the algorithm is converged.
+and $\eta$, the two parts of the problems are solved. We repeat this procedure until the algorithm  converges.
 \subsection{First Part of Sub-Problem A}\label{firstsub}
@@
 \State Sort services according to the number of UEs in it and their requirements in the descending order.
-\State Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs in two layers and the Capacity of their resources in the descending order.
+\State Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs in two layers and the capacity of their resources in the descending order.
 \For {$i \gets 1$ to $S$}
@@
 The Lagrangian function is written as follow
-\begin{equation}\label{lagrang}
-\begin{split}
+\begin{subequations}\label{lagrang}
+\begin{alignat}{4}
 \mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\chi}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
@@
 &- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,i)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\
-&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.\\
-\end{split}
-\end{equation}
+&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.
+\end{alignat}
+\end{subequations}
 where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$. Optimal power is obtained from  \eqref{lagrang}
@@
 Also we fixed $\eta = 0$.
-Afterward, by achieving $\boldsymbol{A}$, in the second part, we acquire $\boldsymbol{P}$ using the sub-gradient method.
+Afterward, $\boldsymbol{A}$ is achieved from algorithm \ref{alg}.
+Then, in the second part, we acquire $\boldsymbol{P}$ using the sub-gradient method.
 After solving $\boldsymbol{P}$, $\eta$ is updated.
 Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$ the two parts of the problems is solved until the algorithm converged.
+and $\eta$ the two parts of the problems is solved until the algorithm converges.
 Here, the algorithm of solving sub-problem A is shown in algorithm \eqref{alg2}
@@
 Secondly, we start mapping from the most needed slices to the DC with the most physical resources (from line \ref{33} to line \ref{34} of algorithm \ref{alg3}).
-After mapping DCs to slices, if some slices are not admitted, we start admitting remaining slices to more than one DCs (from line \ref{35} to line \ref{36} of algorithm \ref{alg3}).
-At the end, if DC with the lowest physical resources is free and can be served instead of DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption (line \ref{37} of algorithm \ref{alg3}).
-If a slice does not admit to a specific DC, it remains for the next placement. In next placement the remaining slices, map to more than one DC according to their requirements.
+After mapping DCs to slices, If a slice does not admit to a specific DC, it remains for the next placement.
+In the next placement the remaining slices, map to more than one DC according to their requirements.
+(from line \ref{35} to line \ref{36} of algorithm \ref{alg3}).
+At the end, if DC with the lowest physical resources is free and can be served the slices of a DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption (line \ref{37} of algorithm \ref{alg3}).
 \begin{algorithm}
@@
 \ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices (the parameters for simulation listed in table \ref{table:1} and also we set $w_C = 320$, $w_S = 100$, $w_M =1$).
-In this simulation, it is assumed that  just one DC can serve each slice, and it is not admitted by more than one DC.
+In this simulation, the second term of \eqref{eqpsi}, is important and the designed parameter $\nu$ is supposed to be high.
+Also, it is assumed that just one DC can serve each slice, and each slice is not admitted by more than one DC. 
 The proposed method is based on Algorithm \ref{alg3}, and the optimal method is done by the MOSEK toolbox.
@@
 \ref{fig:f2}, the normalized resource consumption is depicted due to the number of slices (the parameters for simulation listed in table \ref{table:1} and also we set $w_C = 320$, $w_S = 100$, $w_M =1$).
-In this simulation, it is assumed that the number of DCs is entirely enough to cover all slices.
-The optimality of the placement of DCs to slices is measured.
+In this simulation, suppose the number of DCs is entirely enough to cover all slices and also, the designed parameter $\nu$ is assumed to be low, so we focused on the first term of \eqref{eqpsi}.
+However, if any slice remains, it can be served by more than one DCs.
+The optimality of the placement of DCs to slices is measured based on the power consumption of DCs.
 It is shown that how much resources of active DCs are not used.

### 2019-11-03 Latex/tehran-thesis/tex/faTitle.tex
thesis Add

% !TeX root=../main.tex
% در این فایل، عنوان پایان‌نامه، مشخصات خود، متن تقدیمی‌، ستایش، سپاس‌گزاری و چکیده پایان‌نامه را به فارسی، وارد کنید.
% توجه داشته باشید که جدول حاوی مشخصات پروژه/پایان‌نامه/رساله و همچنین، مشخصات داخل آن، به طور خودکار، درج می‌شود.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% دانشگاه خود را وارد کنید
\university{دانشگاه تهران}
% پردیس دانشگاهی خود را اگر نیاز است وارد کنید (مثال: فنی، علوم پایه، علوم انسانی و ...)
\college{پردیس دانشکده‌های فنی}
% دانشکده، آموزشکده و یا پژوهشکده  خود را وارد کنید
\faculty{دانشکدهٔ مهندسی برق و کامپیوتر}
% گروه آموزشی خود را وارد کنید (در صورت نیاز)
\department{گروه شبکه}
% رشته تحصیلی خود را وارد کنید
\subject{مهندسی برق}
% گرایش خود را وارد کنید
\field{مخابرات شبکه}
% عنوان پایان‌نامه را وارد کنید
\title{نوشتن پروژه، پایان‌نامه و رساله با استفاده از کلاس 
\lr{tehran-thesis}}
% نام استاد(ان) راهنما را وارد کنید
\firstsupervisor{دکتر راهنمای اول}
\firstsupervisorrank{استاد}
\secondsupervisor{دکتر راهنمای دوم}
\secondsupervisorrank{استادیار}
% نام استاد(دان) مشاور را وارد کنید. چنانچه استاد مشاور ندارید، دستورات پایین را غیرفعال کنید.
\firstadvisor{دکتر مشاور اول}
\firstadvisorrank{استادیار}
%\secondadvisor{دکتر مشاور دوم}
% نام داوران داخلی و خارجی خود را وارد نمایید.
\internaljudge{دکتر داور داخلی}
\internaljudgerank{دانشیار}
\externaljudge{دکتر داور خارجی}
\externaljudgerank{دانشیار}
\externaljudgeuniversity{دانشگاه داور خارجی}
% نام نماینده کمیته تحصیلات تکمیلی در دانشکده \ گروه
\graduatedeputy{دکتر نماینده}
\graduatedeputyrank{دانشیار}
% نام دانشجو را وارد کنید
\name{مژده}
% نام خانوادگی دانشجو را وارد کنید
\surname{کربلایی مطلب}
% شماره دانشجویی دانشجو را وارد کنید
\studentID{810893024}
% تاریخ پایان‌نامه را وارد کنید
\thesisdate{مرداد ۱۳۹۶}
% به صورت پیش‌فرض برای پایان‌نامه‌های کارشناسی تا دکترا به ترتیب از عبارات «پروژه»، «پایان‌نامه» و «رساله» استفاده می‌شود؛ اگر  نمی‌پسندید هر عنوانی را که مایلید در دستور زیر قرار داده و آنرا از حالت توضیح خارج کنید.
%\projectLabel{پایان‌نامه}

% به صورت پیش‌فرض برای عناوین مقاطع تحصیلی کارشناسی تا دکترا به ترتیب از عبارت «کارشناسی»، «کارشناسی ارشد» و «دکتری» استفاده می‌شود؛ اگر نمی‌پسندید هر عنوانی را که مایلید در دستور زیر قرار داده و آنرا از حالت توضیح خارج کنید.
%\degree{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% پایان‌نامه خود را تقدیم کنید! %%
\dedication
{
{\Large تقدیم به:}\\
\begin{flushleft}{
	\huge
	همسر و فرزندانم\\
	\vspace{7mm}
	و\\
	\vspace{7mm}
	پدر و مادرم
}
\end{flushleft}
}
%% متن قدردانی %%
%% ترجیحا با توجه به ذوق و سلیقه خود متن قدردانی را تغییر دهید.
\acknowledgement{
سپاس خداوندگار حکیم را که با لطف بی‌کران خود، آدمی را به زیور عقل آراست.

در آغاز وظیفه‌  خود  می‌دانم از زحمات بی‌دریغ اساتید  راهنمای خود،  جناب آقای دکتر ... و ...، صمیمانه تشکر و  قدردانی کنم که در طول انجام این پایان‌نامه با نهایت صبوری همواره راهنما و مشوق من بودند و قطعاً بدون راهنمایی‌های ارزنده‌ ایشان، این مجموعه به انجام نمی‌رسید.

از جناب آقای دکتر ... که  زحمت مشاوره‌، بازبینی و تصحیح این پایان‌نامه را تقبل فرمودند کمال امتنان را دارم.

%از همکاری و مساعدت‌های دکتر ... مسئول تحصیلات تکمیلی و سایر کارکنان دانشکده بویژه سرکار خانم ... کمال تشکر را دارم.

با سپاس بی‌دریغ خدمت دوستان گران‌مایه‌ام، خانم‌ها ... و آقایان ... در آزمایشگاه ...، که با همفکری مرا صمیمانه و مشفقانه یاری داده‌اند.

و در پایان، بوسه می‌زنم بر دستان خداوندگاران مهر و مهربانی، پدر و مادر عزیزم و بعد از خدا، ستایش می‌کنم وجود مقدس‌شان را و تشکر می‌کنم از خانواده عزیزم به پاس عاطفه سرشار و گرمای امیدبخش وجودشان، که بهترین پشتیبان من بودند.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%چکیده پایان‌نامه را وارد کنید
\fa-abstract{
این راهنما، نمونه‌ای از قالبِ پروژه، پایان‌نامه و رسالهٔ دانشگاه تهران می‌باشد که با استفاده از کلاس 
\lr{tehran-thesis}
و بستهٔ زی‌پرشین در \lr{\LaTeX}{} تهیه شده است. این قالب به گونه‌ای طراحی شده است که مطابق با دستورالعمل نگارش و تدوین پایان‌نامه کارشناسی ارشد و دکتری، مورخ ۹۳/۰۶/۰۳ پردیس دانشکده‌های فنی دانشگاه تهران باشد و حروف‌چینی بسیاری از قسمت‌های آن، مطابق با استاندارد قالب‌های فارسی پایان‌نامه در لاتک، به طور خودکار انجام می‌شود.

چکیده بخشی از پایان‌نامه است که خواننده را به مطالعه آن علاقمند می‌کند و یا از آن می‌گریزاند. چکیده باید ترجیحاً‌ در یک صفحه باشد. در نگارش چکیده نکات زیر باید رعایت شود. متن چکیده باید مزین به کلمه‌ها و عبارات سلیس، آشنا، بامعنی و روشن باشد. بگونه‌ای که با حدود ۳۰۰ تا ۵۰۰ کلمه بتواند خواننده را به خواندن پایان‌نامه راغب نماید. چکیده، جدای از پا‌یان‌نامه باید به تنهایی گویا و مستقل باشد. در چکیده باید از ذکر منابع، اشاره به جداول و نمودارها اجتناب شود.تمیز بودن مطلب، نداشتن غلط‌های املایی یا دستور زبانی و رعایت دقت و تسلسل روند نگارش چکیده از نکات مهم دیگری است که باید درنظر گرفته شود. در چکیده پایان‌نامه باید از درج مشخصات مربوط به پایان‌نامه خودداری شود.
چکیده باید منعکس‌کننده اصل موضوع باشد. در چکیده باید اهداف تحقیق مورد توجه قرار گیرد. تأکید روی اطلاعات تازه (یافته‌ها) و اصطلاحات جدید یا نظریه‌ها، فرضیه‌ها، نتایج و پیشنهادها متمرکز شود. اگر در پایان‌نامه روش نوینی برای اولین بار ارائه می‌شود و تا به حال معمول نبوده است، با جزئیات بیشتری ذکر شود. شایان ذکر است چکیده فارسی و انگلیسی باید حتماً به تأیید استاد راهنما رسیده باشد.

کلمات کلیدی در انتهای چکیده فارسی و انگلیسی آورده می‌شود. محتوای چکیده‌ها بر اساس موضوع و گرایش تحقیق طبقه‌بندی می‌شود و به همین جهت وجود کلمات شاخص و کلیدی، مراکز اطلاعاتی  را در طبقه‌بندی دقیق و سریع پایان‌نامه یاری می‌دهد. کلمات کلیدی، راهنمای نکات مهم موجود در پایان‌نامه هستند. بنابراین باید در حد امکان کلمه‌ها یا عباراتی انتخاب شود که ماهیت، محتوا و گرایش کار را به وضوح روشن نماید.
}
% کلمات کلیدی پایان‌نامه را وارد کنید
\keywords{حداکثر ۵ کلمه یا عبارت، متناسب با عنوان، قالب پایان‌نامه، لاتک}
% انتهای وارد کردن فیلد‌ها
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-11-03 Latex/tehran-thesis/tex/chapter1.tex
thesis2

\chapter{مقدمه}
\section{مقدمه ای بر ساختار \lr{ORAN}}
\lr{Open RAN}(\lr{ORAN})
تبسیط و ترکیبی از دو ساختار \lr{C-RAN} و \lr{xRAN} می باشد که انتظار می رود که در فناوری نسل پنجم مخابرات مورد استفاده قرار گرفته و منجر به بهبود عملکرد شبکه های دسترسی رادیویی \lr{RAN} گردد. 
ایده اصلی \lr{C-RAN} جداسازی بخش

### 2019-11-05 Latex/tehran-thesis/tex/chapter1.tex
latex update

@@
 تبسیط و ترکیبی از دو ساختار \lr{C-RAN} و \lr{xRAN} می باشد که انتظار می رود که در فناوری نسل پنجم مخابرات مورد استفاده قرار گرفته و منجر به بهبود عملکرد شبکه های دسترسی رادیویی \lr{RAN} گردد. 
-ایده اصلی \lr{C-RAN} جداسازی بخش
+ایده اصلی \lr{C-RAN} جداسازی بخش رادیویی (\lr{RRH}) 
+\LTRfootnote{Radio Remote Head}
+ از واحد پردازشی باند پایه (\lr{BBU})
+ \LTRfootnote{Baseband Unit}
+  است.
+از تجمیع \lr{BBU} ها بر روی سرور ابری، \lr{BBU-Pool} ایجاد می شود.
+این ساختار جدید جزو یکی از ساختارهایی است که در \lr{5G} امکان استفاده را دارد.در این ساختار جدید در راستای بهینه سازی عملکرد \lr{BBU}
+ ها در مواجهه باایستگاههای پایه پر ترافیک و کم ترافیک،
+ \lr{BBU}ها به صورت یک مجموعه ی واحد تحت عنوان 
+\lr{BBU Pool}
+ در آمده اند که این مجموعه بین چندین سلول 
+ به اشتراک گزارده شده و مطابق شکل زیر مجازی سازی
+می شود. 
+در توضیح بیشتر این ساختار می توان این گونه
+عنوان کرد که \lr{BBU Pool} به عنوان یک خوشه ی مجازی
+در نظر گرفته می شود که شامل پردازش گرهایی می باشد
+که پردازش های باند پایه را انجام می دهند. ارتباط بین
+  \lr{BBU}ها در ساختار های فعلی به شکل  $X_2$ برقرار می شود
+که در این ساختار ارتباط بین خوشه ها از فرم جدید $X_2$
+تحت عنوان  $X_2 +$برقرار می شود.
+\newline
+در شکل \ref{fig:C-RAN} ساختار کلی شبکه ی  \lr{C-RAN} در سیستم های
+\lr{ LTE}
+ نمایش داده شده است. همان طور که در شکل قابل
+مشاهده می باشد ساختار کلی شبکه  \lr{C-RAN} به دو بخش
+ \lr{backhaul} و \lr{fronthaul} تقسیم بندی شده است. بخش
+ \lr{fronthaul}شبکه به مرحله ی اتصال سایت های \lr{ RRH}به
+ به \lr{BBU Pool} به اتصال \lr{backhaul} و بخش \lr{BBU Pool}
+هسته ی شبکه ی سیار اطلاق می شود. همان گونه که قبلا
+ذکر شد  \lr{ RRH}ها در نزدیکی انتن نصب شده و از طریق
+لینک های انتقالی نوری با پهنای باند وسیع و تاخیر کم به
+پردازشگرهای قوی در  \lr{BBU}متصل می شوند. توسط این
+لینک های انتقالی است که سیگنال های دیجیتالی باند
+پایه از نوع \lr{IQ} بین \lr{RRH} و \lr{BBU} انتقال می یابند \cite{checko2015cloud}.
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=\textwidth]{./fig/CRAN}
+  \caption{ساختار شبکه ی \lr{C-RAN} \cite{checko2015cloud}}
+  \label{fig:C-RAN}
+\end{figure}
+\section{مزایای شبکه ی \lr{C-RAN}}
+
+در این بخش قصد داریم مزایای شبکه ی \lr{C-RAN} و هدف از استفاده ی آن در \lr{5G} را بیان کنیم.
+\newline
+در هر دو نوع سلولهای ماکرو و میکرو، می توان از ساختار \lr{C-RAN} بهره برد.
+در حالت ماکرو، متمرکز کردن \lr{BBU} ها به صورت \lr{BBU Pool}، منجر به استفاده ی بهینه از \lr{BBU} ها و کاهش هزینه ی ایستگاه پایه \LTRfootnote{base station} می شود.
+همچنین منجر به کاهش مصرف توان و فراهم کردن انعطاف پذیری بیشتر در شبکه و تطبیق آن با ترافیک غیر یکسان می شود.
+علاوه بر این، باعث تبدیل سیگنال تداخل به سیگنال مفید تبدیل می شود.
+در ادامه این مزایا به صورت گسترده تر بیان می گردد.

### 2019-11-05 Latex/tehran-thesis/tex/chapter1.tex
latex update1

@@
 تبسیط و ترکیبی از دو ساختار \lr{C-RAN} و \lr{xRAN} می باشد که انتظار می رود که در فناوری نسل پنجم مخابرات مورد استفاده قرار گرفته و منجر به بهبود عملکرد شبکه های دسترسی رادیویی \lr{RAN} گردد.
+\subsection{\lr{C-RAN}} 
 ایده اصلی \lr{C-RAN} جداسازی بخش رادیویی (\lr{RRH}) 
@@
 از تجمیع \lr{BBU} ها بر روی سرور ابری، \lr{BBU-Pool} ایجاد می شود.
-این ساختار جدید جزو یکی از ساختارهایی است که در \lr{5G} امکان استفاده را دارد.در این ساختار جدید در راستای بهینه سازی عملکرد \lr{BBU}
+در این ساختار، در راستای بهینه سازی عملکرد \lr{BBU}
  ها در مواجهه باایستگاههای پایه پر ترافیک و کم ترافیک،
@@
 \end{figure}
-\section{مزایای شبکه ی \lr{C-RAN}}
-
-در این بخش قصد داریم مزایای شبکه ی \lr{C-RAN} و هدف از استفاده ی آن در \lr{5G} را بیان کنیم.
-\newline
-در هر دو نوع سلولهای ماکرو و میکرو، می توان از ساختار \lr{C-RAN} بهره برد.
-در حالت ماکرو، متمرکز کردن \lr{BBU} ها به صورت \lr{BBU Pool}، منجر به استفاده ی بهینه از \lr{BBU} ها و کاهش هزینه ی ایستگاه پایه \LTRfootnote{base station} می شود.
-همچنین منجر به کاهش مصرف توان و فراهم کردن انعطاف پذیری بیشتر در شبکه و تطبیق آن با ترافیک غیر یکسان می شود.
-علاوه بر این، باعث تبدیل سیگنال تداخل به سیگنال مفید تبدیل می شود.
-در ادامه این مزایا به صورت گسترده تر بیان می گردد.
+\subsection{\lr{xRAN}}
+\lr{xRAN}
+در سال ۲۰۱۶ با هدف استانداردسازی یک جایگزین انعطاف پذیر و باز برای \lr{RAN}
+مبتنی بر سخت افزار سنتی بدست آمده است.
+ در این ساختار، سه حوزه ی مهم مورد بررسی قرار گرفته است.
+اولین حوزه ی مورد بررسی، جداسازی بخش \lr{control plane} از 
+\lr{user plane}
+می باشد. حوزه ی دوم،
+ساختن یک پشته نرم افزاری eNodeB مدولار که از سخت افزار COTS استفاده می کند، می باشد.
+حوزه ی سوم مورد بررسی، انتشار رابط های باز شمال و جنوب است
+\cite{xran}.
+\subsection{\lr{ORAN}}
+\lr{ORAN}، المانهای شبکه ی دسترسی رادیویی را مجازی می کند ، آنها را جدا کرده و رابط های باز مناسب را 
+برای اتصال این عناصر
+تعیین می کند. همچنین، 
+\lr{ORAN}
+از روشهای یادگیری ماشین برای هوشمندسازی لایه های 
+\lr{RAN}
+ استفاده می نماید. 
+ در ساختار نوآورانه ی 
+ \lr{ORAN}
+ نرم افزار قابل برنامه ریزی 
+ \lr{RAN}
+ از سخت افزار جدا می شود.
+  یکی از مهم ترین خصوصیات
+  \lr{ORAN}
+  رابط کاربری باز است که به اپراتورهای موبایل این قابلیت را می دهد تا بتوانند سرویس های مورد نیاز خود را تعریف نمایند.
+  مفهوم 
+  \lr{SDN}
+  \LTRfootnote{software defined network}
+  که مبنی بر جداسازی 
+  جداسازی بخش \lr{control plane} از 
+\lr{user plane}
+می باشد، در ساختار 
+\lr{ORAN}
+مورد بررسی قرار می گیرد.
+این جداسازی منجر به بهبود 
+\lr{RRM}
+برای استفاده از زمان غیر واقعی و زمان نزدیک به واقعی در کنترلگر هوشمند شبکه ی دسترسی رادیویی می گردد.
+در ساختار
+\lr{ORAN}،
+واحد توزیع شده \lr{DU}،
+نود منطقی می باشد که شامل لایه های 
+\lr{RLC}
+،
+\lr{MAC}،
+و
+\lr{High-PHY}
+است.
+علاوه بر این، واحد مرکزی 
+\lr{CU}
+نود منطقی است که شامل لایه های 
+\lr{RRC}،
+\lr{SDAP} 
+و 
+\lr{PDCP}
+می باشد.

### 2019-11-10 Latex/tehran-thesis/tex/chapter1.tex
latex update1
proposal continue

--- 2019-11-03 Latex/tehran-thesis/tex/chapter1.tex
@@
 تبسیط و ترکیبی از دو ساختار \lr{C-RAN} و \lr{xRAN} می باشد که انتظار می رود که در فناوری نسل پنجم مخابرات مورد استفاده قرار گرفته و منجر به بهبود عملکرد شبکه های دسترسی رادیویی \lr{RAN} گردد.
-ایده اصلی \lr{C-RAN} جداسازی بخش
+\subsection{\lr{C-RAN}} 
+ایده اصلی \lr{C-RAN} جداسازی بخش رادیویی (\lr{RRH}) 
+\LTRfootnote{Radio Remote Head}
+ از واحد پردازشی باند پایه (\lr{BBU})
+ \LTRfootnote{Baseband Unit}
+  است.
+از تجمیع \lr{BBU} ها بر روی سرور ابری، \lr{BBU-Pool} ایجاد می شود.
+در این ساختار، در راستای بهینه سازی عملکرد \lr{BBU}
+ ها در مواجهه باایستگاههای پایه پر ترافیک و کم ترافیک،
+ \lr{BBU}ها به صورت یک مجموعه ی واحد تحت عنوان 
+\lr{BBU Pool}
+ در آمده اند که این مجموعه بین چندین سلول 
+ به اشتراک گزارده شده و مطابق شکل زیر مجازی سازی
+می شود. 
+در توضیح بیشتر این ساختار می توان این گونه
+عنوان کرد که \lr{BBU Pool} به عنوان یک خوشه ی مجازی
+در نظر گرفته می شود که شامل پردازش گرهایی می باشد
+که پردازش های باند پایه را انجام می دهند. ارتباط بین
+  \lr{BBU}ها در ساختار های فعلی به شکل  $X_2$ برقرار می شود
+که در این ساختار ارتباط بین خوشه ها از فرم جدید $X_2$
+تحت عنوان  $X_2 +$برقرار می شود.
+\newline
+در شکل \ref{fig:C-RAN} ساختار کلی شبکه ی  \lr{C-RAN} در سیستم های
+\lr{ LTE}
+ نمایش داده شده است. همان طور که در شکل قابل
+مشاهده می باشد ساختار کلی شبکه  \lr{C-RAN} به دو بخش
+ \lr{backhaul} و \lr{fronthaul} تقسیم بندی شده است. بخش
+ \lr{fronthaul}شبکه به مرحله ی اتصال سایت های \lr{ RRH}به
+ به \lr{BBU Pool} به اتصال \lr{backhaul} و بخش \lr{BBU Pool}
+هسته ی شبکه ی سیار اطلاق می شود. همان گونه که قبلا
+ذکر شد  \lr{ RRH}ها در نزدیکی انتن نصب شده و از طریق
+لینک های انتقالی نوری با پهنای باند وسیع و تاخیر کم به
+پردازشگرهای قوی در  \lr{BBU}متصل می شوند. توسط این
+لینک های انتقالی است که سیگنال های دیجیتالی باند
+پایه از نوع \lr{IQ} بین \lr{RRH} و \lr{BBU} انتقال می یابند \cite{checko2015cloud}.
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=\textwidth]{./fig/CRAN}
+  \caption{ساختار شبکه ی \lr{C-RAN} \cite{checko2015cloud}}
+  \label{fig:C-RAN}
+\end{figure}
+\subsection{\lr{xRAN}}
+\lr{xRAN}
+در سال ۲۰۱۶ با هدف استانداردسازی یک جایگزین انعطاف پذیر و باز برای \lr{RAN}
+مبتنی بر سخت افزار سنتی بدست آمده است.
+ در این ساختار، سه حوزه ی مهم مورد بررسی قرار گرفته است.
+اولین حوزه ی مورد بررسی، جداسازی بخش \lr{control plane} از 
+\lr{user plane}
+می باشد. حوزه ی دوم،
+ساختن یک پشته نرم افزاری eNodeB مدولار که از سخت افزار COTS استفاده می کند، می باشد.
+حوزه ی سوم مورد بررسی، انتشار رابط های باز شمال و جنوب است
+\cite{xran}.
+\subsection{\lr{ORAN}}
+\lr{ORAN}، المانهای شبکه ی دسترسی رادیویی را مجازی می کند ، آنها را جدا کرده و رابط های باز مناسب را 
+برای اتصال این عناصر
+تعیین می کند. همچنین، 
+\lr{ORAN}
+از روشهای یادگیری ماشین برای هوشمندسازی لایه های 
+\lr{RAN}
+ استفاده می نماید. 
+ در ساختار نوآورانه ی 
+ \lr{ORAN}
+ نرم افزار قابل برنامه ریزی 
+ \lr{RAN}
+ از سخت افزار جدا می شود.
+  یکی از مهم ترین خصوصیات
+  \lr{ORAN}
+  رابط کاربری باز است که به اپراتورهای موبایل این قابلیت را می دهد تا بتوانند سرویس های مورد نیاز خود را تعریف نمایند.
+  مفهوم 
+  \lr{SDN}
+  \LTRfootnote{software defined network}
+  که مبنی بر جداسازی 
+   بخش \lr{control plane} از 
+\lr{user plane}
+می باشد، در ساختار 
+\lr{ORAN}
+مورد بررسی قرار می گیرد.
+این جداسازی منجر به بهبود 
+\lr{RRM}
+برای استفاده از زمان غیر واقعی و زمان نزدیک به واقعی در کنترلگر هوشمند شبکه ی دسترسی رادیویی می گردد.
+در ساختار
+\lr{ORAN}،
+واحد توزیع شده \lr{DU}،
+نود منطقی می باشد که شامل لایه های 
+\lr{RLC}
+،
+\lr{MAC}،
+و
+\lr{High-PHY}
+است.
+علاوه بر این، واحد مرکزی 
+\lr{CU}
+نود منطقی است که شامل لایه های 
+\lr{RRC}،
+\lr{SDAP} 
+و 
+\lr{PDCP}
+می باشد.
+نود منطقی واحد رادیویی
+\lr{RU}
+نیز، شامل لایه ی 
+\lr{LOW-PHY}
+و بخش پردازش رادیویی می باشد.
+\lr{ORAN}
+،
+رابطهایی از جمله رابط 
+\lr{fronthaul}
+باز را شامل می شود که بخش \lr{DU} را به \lr{RU} متصل می نماید
+(رابط 
+\lr{E2}). 
+همچنین
+ رابط \lr{A1}
+ بین لایه ی 
+  \lr{orchestration/NMS}
+  که شامل 
+  تابع غیر واقعی زمان است و 
+  \lr{eNB/qNB}
+  که شامل تابع نزدیک به زمان است. 
+\section{مجازی سازی توابع شبکه}
+برای بهبود سرویس دهی در نسل پنجم مخابرات، جداسازی المان های نرم افزاری و سخت افزاری شبکه صورت گرفته است و به عنوان 
+مجازی سازی توابع شبکه (\lr{NFV}) \LTRfootnote{network function virtualization}
+معرفی شده است.
+  حال توابع شبکه ی مجازی
+  \lr{VNF}
+  \LTRfootnote{Virtual network function} ،
+  بلوکهای توابع سیستم هستند.
+در نسل پنجم مخابرات 
+  انتظار می رود که
+   میزبان چندین سرویس
+   با نیازهای مختلف به طور همزمان
+    باشند.
+ \section{برش شبکه}
+ برش شبکه
+ \LTRfootnote{Network Slicing}
+به عنوان راه حلی برای چنین تقاضا در نظر گرفته شده است.
+یک برش شبکه، یک شبکه منطقی \lr{end-to-end} است که خدمات  با نیازهای خاص را ارائه می دهد.
+ چندین برش شبکه
+در یک زیرساخت یکسان
+  اجرا و مدیریت می شوند و
+به طور مستقل کار کنید.
+پیاده سازی های مختلفی از برش شبکه وجود دارد که شامل برش هسته ی شبکه، برش \lr{RAN} و برش هر دو بخش می باشد.
+در برش هسته ی شبکه، برش تنها در بخش هسته ی شبکه است و تمام واسط ها و فرآیندها، بدون تغییر باقی می مانند.
+در برش \lr{RAN}، 
+برش های \lr{RAN}، بر روی

### 2020-01-07 Latex/tex1/pr1.tex
latex

--- 2019-10-28 Latex/tex/pr.tex
@@
 
-\title{Joint Power Allocation and Network Slicing in an End-to-End ORAN System \vspace{-.1cm}
+\title{Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}
 }
@@
     \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
-    Email: \{mojdeh.karbalaee, vmansouri,salar.nouri@ut.ac.ir\}@ut.ac.ir,
+    Email: \{mojdeh.karbalaee, vmansouri, salar.nouri\}@ut.ac.ir,
     \vspace{-.2cm}
@@
 \begin{abstract}
-Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a more flexible and openness radio access network which is the Open-RAN
-(ORAN) for the fifth generation of wireless technology.
-To increase energy efficiency and optimize the allocation of resources, Network Slicing (NS) is considered as the best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks.
-Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to-end network.
-In this paper, we elaborate joint NS in RAN and Core of ORAN system to investigate the power
-of each User Equipment (UE), map slices to services and also map physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RUs and the cost of  physical resources in a downlink channel.
-The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent.
-Heuristic algorithms are proposed to each of sub-problems in order to map slices to services, optimize power consumption and map slices to physical resources to minimize the cost of total DCs simultaneously.
+
 \end{abstract}
@@
 \begin{IEEEkeywords}
-ORAN, Network Slicing, Energy Efficiency, Data Center (DC)
+
 \end{IEEEkeywords}
 
-\section{Introduction}
-Open RAN (ORAN), as the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G networks to extensively enhance the RAN performance.
-The core idea of C-RAN is to split the radio remote head (RRU) from the baseband unit (BBU).
-Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1,frdl,simeone2016cloud,motalleb2017optimal}.
-On the other hand, xRAN technology has three fundamental features.
-The control plane is decoupled from user plane.
-Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
-Moreover, open north-bound and south-bound interfaces are introduced \cite{xran}.
-
-ORAN virtualizes the elements of the radio access networks, separate them and define appropriate open interfaces for connection of these elements.
-Moreover, ORAN uses machine learning techniques to develop smarter RAN layers in its architecture.
-In an innovative ORAN system, the programmable RAN software is decoupled from hardware \cite{oran1}.
-Open interface is one of the most crucial properties for ORAN to enable mobile network operators (MNOs) to define their own services.
-The concept of software defined network (SDN), which is the separation of control plane from user plane, is deployed in an intelligent ORAN architecture.
-Moreover, this separation promotes RRM to use non-realtime (RT) and near-realtime (NRT) RAN Intelligent Controller (RIC).
-In the ORAN architecture, distributed unit (DU) is a logical node hosting RLC/MAC/High-PHY layer.
-Moreover, central unit (CU) is a logical node hosting RRC, SDAP and PDCP. Also, radio unit (RU)  is a logical node hosting LOW-PHY layer and
-RF processing \cite{oranpaper}.
-ORAN introduces interfaces such as open fronthaul interface that connects DU and RU(i.e., E2 interface), and an A1 interface between orchestration/NMS layer containing the non-real-time RIC (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC (RIC near-RT) function.
-
-To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and is referred to as network functions virtualization (NFV).
-Virtual network function (VNF) are functional blocks of the system in this case.
-5G networks are expected to host several services with different requirements simultaneously.
-Network slicing is considered as a solution for such demand.
-A network slice is a logical end-to-end network which provide service with specific requirements.
-Multiple network slices run on the same physical network infrastructure which are managed and operate independently \cite{lee2018dynamic}.
-Slicing can be defined for the RAN, for the core network or both of these networks \cite{ns1}.
-
-Based on their type of request, UEs are classified into various services, where UEs in the same service have similar service requests.
-In addition, each service is mapped to one or more slices based on the resources of the slices.
-Each VNF of the ORAN is mapped to one or some virtual machines (VMs) in the data center.
-For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.
-
-%The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}.
-In \cite{oranT},  the evolution of RAN in the  5G network is described.
-The architecture of C-RAN and X-RAN is expressed and development of the ORAN from C-RAN and X-RAN is explained.
-Also requirements of the network in terms of capacity and latency is taken into account.
-In \cite{oran12},  the ORAN architecture is studied.
-The eight work groups is discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software.
-To the best of our knowledge, there is not work in the literature to model ORAN systems.
-
-%We shortly review related works in the area of C-RAN and xRAN.
-In \cite{motalleb2017optimal}, power allocation in C-RAN architecture, with limited fronthaul capacity in clustered network is studied.
-In \cite{lee2018dynamic}, dynamic network slicing is considered in heterogeneous CRAN (H-CRAN) to maximize the weighted sum-rate.
-Also, two level network slicing (upper and lower level) is done.
-The admission of UEs is maximized using the heuristic algorithms.
-In addition, the allocation of BBU capacity to UEs is considered.
-In \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting} minimization of cost obtained by power consumption, also cloud processing and limited power for each RU is considered.
-Furthermore, the processing delay of each VM and wireless transmission delay are taken into account.
-In \cite{frdl}, the processing and transmission delay is modeled as a M/M/1 queue.
-In \cite{guo2016exploiting}, M/D/1 queue is used to modeled the transmission delay.
-
-\begin{figure}
-  \centering
-    \includegraphics[scale=0.55]{c7.pdf}
-  \caption{Network sliced ORAN system}
-  \label{fig:c11}
-\end{figure}
-
-In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
-The RAN is divided to three layers including RU, DU, and CU with open interfaces.
-DU and CU are running on general purpose data centers.
-UEs are divided to different services according to their service requirements.
-RAN resources are decoupled to slices to provide requirements of services.
-Optimal power allocation and joint mapping of slices to services are applied.
-In addition, mapping slices to physical resources is taken to account.
-The contribution of the paper is expressed as follow:
-\begin{itemize}
-\item In this paper, joint network slicing and resource allocation is considered in an end to end ORAN system.
-\item UEs are categorized into different class of services based on their service requirements.
-RAN which contains RUs, PRBs, and VNFs ,in the two layer of processing, are classified into different group of slices.
-\item The problem is decomposed into two independent sub-problems.
-\item Heuristic algorithms are applied for the sub-problems to efficiently obtain the solution.
-\end{itemize}
-
-The rest of the paper is organized as follows.
-In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is expressed.
-Then, problem statement is explained and decomposed into two independent sub-problems.
-In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results are provided for the problem.
-
 \section{System Model and Problem Formulation}\label{systemmodel}
-
-In this section, first, we  present the system model.
-Then, we obtain achievable rates and delays for the downlink (DL) of the ORAN system.
-Afterward, we discuss about assignment of physical data center resources.
-Finally, the main problem is expressed.
-\subsection{System Model}
-Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
-single-antenna user equipments (UEs) that require certain service.
-Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
-All RUs in a slice, that is mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}.
-Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.
-There are two processing layers one in the DU and one on the CU of ORAN system, each represented with a VNF.
-The lower layer (i.e., DU) consists of high-PHY, MAC, and RLC, and the upper layer (i.e., CU) consists of RRC, PDCP and SDAP.
-Assume we have $M_1$ VNFs in the DU layer and $M_2$ VNFs in the CU layer for processing data.
-Each VNF in both layers belongs to one or more slices.
-So, in the $s^{th}$ slice, there are $M_{s,1}$ VNFs in the DU layer and $M_{s,2}$ VNFs in the CU layer.
-The VNFs in the DU and CU layers have the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
-Also, RUs and PRBs can serve more than one slices.
-\subsection{The Achievable Rate}
-The achievable data rate for the $i^{th}$ UE in the $v^{th}$ service can be written as
-\begin{equation}\label{eq1}
-\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}}),
-\end{equation}
-where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from
-\begin{equation}\label{eq2}
-\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
-\end{equation}
-where $p_{u(v,i)}$ represents the transmission power allocated by RUs to $i^{th}$ UE in $v^{th}$ service, and
-$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
-In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
-Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals.
-Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is mapped to service $v$ or not.
-If $a_{v,s} =1$ then, $v^{th}$ service is mapped to $s^{th}$ slice; otherwise, it is not mapped.
-\newline
-To obtain SNR as formulated in \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service
-\begin{equation}\label{eq3}
-\textstyle \bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v} \
-\mathfrak{y}_{R_s}\zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v},
-\end{equation}
-where $\mathfrak{y}_{R_s} = \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_s}$
-and $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
-In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise, which is made from signal compression in DU.
-Besides, $\boldsymbol{P}_{U_v} = \diag{(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})}$.
-\newline
-Furthermore, $\zeta_{k,s}^{U_v} \delequal \{\zeta_{k,s}^{u(v,1)},\zeta_{k,s}^{u(v,2)},...,\zeta_{k,s}^{u(v,N_{U_v})}\}$,
-$\zeta_{k,s}^{u(v,i)} \in \{0,1\}$ is a binary parameter, which demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
-$\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
-shows the channel matrix between RU set $\mathcal{R}_s$ to UE set
-$\mathcal{U}_v$, besides.
-%The channel vector from the RU of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below
-%\begin{equation}
-%\boldsymbol{h}_{\mathcal{R}_s,u_{(s,i)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_s,u_{(v,i)}} \boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}},
-%\end{equation}
-%where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
-%represents the large scale fading matrix.
-What's more, it is assumed we have perfect channel state information (CSI).\newline
-Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as below
-\begin{equation}
-\textstyle \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}.
-\end{equation}
-Hence, the interference power of $i^{th}$ UE in $v^{th}$ service can be represented as follow
-\begin{equation}
-\begin{split}
- I_{u_{(v,i)}} &=
- \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{v,s}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
-&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
-&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}},
-\end{split}
-\end{equation}
-where $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
-and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. Moreover,
-${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RU in $s^{th}$ slice.
-Interference signal for each UE is coming from UEs using the same PRB.
-If we replace $p_{u_{(v,l)}}$ and $p_{u_{(y,l)}}$ by $P_{max}$, an upper bound $\bar{I}_{u_{(v,i)}}$ is obtained for $I_{u_{(v,i)}}$.
-Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in  \eqref{eq1} and \eqref{eq2}.\newline
-Let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from the $j^{th}$ RU in $s^{th}$ slice.
-From \eqref{eq3}, we have,
-\begin{equation}
-\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s} + \sigma_{q_{r(s,j)}}^2.
-\end{equation}
-Nevertheless, the rate of users on the fronthual link between DU and the $j^{th}$ RU in $s^{th}$ slice is formulated as \cite{simeone2016cloud, 1111}
-\begin{equation}
-C_{R_{(s,j)}} = \log{(1+\sum_{v=1}^{V}\frac{w_{r_{(s,j)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   w_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s}}{ \sigma_{q_{r(s,j)}}^2})},
-\end{equation}
-where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .
-
-\subsection{Mean Delay}
-
-Assume the packet arrival of UEs follows  a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
-Therefore, the mean arrival data rate of UEs mapped to the $s^{th}$ slice in the CU layer is $\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not.
-Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
-It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
-Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice.
-So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as $d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},$ and $d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}$, respectively.
-where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.%, due to the fact that the service time of each data packet has an exponential distribution for $\mu_i>\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
-Besides, $\alpha_{s}$ is the  arrival rate which is divided
-by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
-In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice on the  wireless link. The arrival data rate of wireless link
- is equal to the arrival data rate of dispatchers (used as a traffic divider) for each slice \cite{frdl}.
-Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
- an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
-the mean delay of the transmission layer is
-\begin{equation}
- d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
-\end{equation}
-where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
-Mean delay of each slice is
-\begin{equation}
-D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s.
-\end{equation}
-\subsection{Physical Data Center Resource}
-Each VNF requires
-physical resources that contain memory, storage and CPU.
-Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
-\begin{equation}
-\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \},
-\end{equation}
-where $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, storage, and CPU, respectively.
-Moreover, the total amount of required memory, storage and CPU of all VNFs of a slice is defined as
-\begin{equation}
-\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.
-\end{equation}
-Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
-The amount of memory, storage and CPU is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$and $\tau_{C_{j}} $ for the $j^{th}$ DC, respectively
-\begin{equation*}
-\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \},
-\end{equation*}
-In this system model, the assignment of physical DC resources to VNFs is considered.
-Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is connected to the VNFs of $s^{th}$ slice or not.
-\subsection{Problem Statement}
-An important criterion to measure the optimality of a system is energy efficiency represented as the sum-rate to sum-power
-\begin{equation}
-\textstyle \eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_r^{{tot}}(\boldsymbol{P},\boldsymbol{A})},
-\end{equation}
-where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RUs in all slices.
-Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services.
-Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
-$\phi_{s,d}$. So the total power of the system for all active DCs that are connected to slices can be represented as
-\begin{equation*}
-\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
-\end{equation*}
-Also, a cost function for the placement of VNFs into DCs is defined as
-\begin{equation}\label{eqpsi}
-\textstyle  \psi_{tot} = \phi_{tot} - \nu \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s}
-\end{equation}
-where, $\nu$ is a design variable to value between the first term of \eqref{eqpsi} which is the total power consumption of physical resources and the second term that is shown the amount of admitted slices to have physical resources.
-Our goal is to maximize sum-rate and minimize sum-power (the total power of all RUs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,
-\begin{subequations}
-\begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\psi_{tot}(\boldsymbol{Y})} \\
-\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} \quad \forall s, \forall i,
- \label{c11} \\
-&p_{u_{(v,k)}}  \geq 0  \quad \forall v, \forall k,\label{c12} \\
-&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} \quad \forall v, \forall k,\label{c13} \\
-&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max} \quad \forall s, \forall i, \label{c14}\\
-&D_{s} \leq D_{s}^{max} \quad \forall s,\label{c15} \\
-& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 \quad \forall s, \label{c21} \\
-& \textstyle  \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s,\label{c23} \\
- &\textstyle  \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}  \forall s, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}
-\end{alignat}
-\label{constraints}
-\end{subequations}
-where $\boldsymbol{P} =[p_{u(v,k)}] \:\: \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}] \:\: \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
-the physical DC is connected to a VNFs of a slice or not.
-\eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively.
-Also \eqref{c13} shows that the rate of each UE is more than a threshold.
-\eqref{c14} and \eqref{c15} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
-Furthermore, \eqref{c21}
-ensures that each service is connected to at least one slice.
-Also, \eqref{c23}, guarantees that each slice (VNFs in two layers of slices) has been placed to one or more physical resources of DCs.
-Moreover, in \eqref{c22}  $\mathcal{E} = \{M,S,C\}$ and the constraint supports
-that we have enough physical resources for VNFs of each slice.\newline
-The optimization problem in \eqref{constraints} can be decomposed into two independent optimization problems A and B since the variables can be obtained independently and respectively. In problem A,
-the variables $\boldsymbol{P}$ and $ \boldsymbol{A}$ is obtained. The problem A is as follow
-\begin{subequations}
-\begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})\\
-\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
-&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
-&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\
-&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i,\label{cc14} \\
-&D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
-& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s.
-\end{alignat}
-\label{constraints1}
-\end{subequations}
-In problem B, $ \boldsymbol{Y}$ is obtained. The problem B is
-\begin{subequations}
-\begin{alignat}{4}
-\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
-\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
- &\textstyle  \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}
-\forall s, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
-\end{alignat}
-\label{constraints2}
-\end{subequations}
-\section{Heuristic Method}\label{proposedmethod}
-In this subsection, a heuristic  method is proposed to solve the problem in \eqref{constraints1} which is non-convex and computationally hard.
-To make it tractable, we divide problem \eqref{constraints1} into
-two different part that can be solved iteratively.
-In the first part of sub-problem A, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in \eqref{constraints1}.
-Also, we set $\eta = 0$.
-Afterward, by achieving $\boldsymbol{A}$, in the second part, we find $\boldsymbol{P}$ by using \eqref{constraints1}.
-This part of the problem can be approximated and converted to a convex problem, so the problem can be solved by convex methods.
-After solving $\boldsymbol{P}$, $\eta$ is updated.
-Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$, the two parts of the problems are solved. We repeat this procedure until the algorithm is converged.
-\subsection{First Part of Sub-Problem A}\label{firstsub}
-Two different methods are applied to acquire $\boldsymbol{A}$.
-The details of the heuristic algorithm are represented in algorithm \ref{alg}.
-\begin{algorithm}
-\caption{Mapping Slice to Service}\label{alg}
-\begin{algorithmic}[1]
-\State Sort services according to the number of UEs in it and their requirements in the descending order.
-\State Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs in two layers and the Capacity of their resources in the descending order.
-\For {$i \gets 1$ to $S$}
-\For {$j \gets 1$ to $V$}
-\State Set $a_{i,j} = 1$
-\State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RUs)
-\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} is not applied}
-\State Set $a_{i,j} = 0$;
-\Else
-\State break from inner loop;
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for}
-\end{algorithmic}
-\end{algorithm}
-\subsection{Second Part of Sub-Problem A}\label{secondsub}
-In this part, by assuming that $\boldsymbol{A}$ is fixed, the power of UEs in each service is achieved.
-\begin{theorem}\label{t2}
-The optimum energy efficiency is achieved if
-\begin{equation}\label{q2}
-%\begin{split}
-\max \limits_{\boldsymbol{P}} (\mathfrak{R}_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=
- \mathfrak{R}_{tot}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
-%\end{split}
-\end{equation}
-\end{theorem}
-\begin{proof}
-See \cite[Appendix A]{aaa}
-\end{proof}
-The second sub-problem can  be solved using the Lagrangian function and iterative algorithm.
-Since, Interference is a function of the power of UEs, to make it tractable, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference.
-In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively).
-Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
-The Lagrangian function is written as follow
-\begin{equation}\label{lagrang}
-\begin{split}
-\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\chi}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
-- \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
-&+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
-&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
-&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,i)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\
-&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.\\
-\end{split}
-\end{equation}
-where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$. Optimal power is obtained from  \eqref{lagrang}
-\begin{equation}
-p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
-\end{equation}
-where, $\mathfrak{y}_{u(v,i)}= (\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and
-$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. Also
-$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$.
-By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained \cite{mimoCran}.
-%\section*{References}
-\subsection{Solving two part of Sub-problem A iteratively}
-In \eqref{firstsub} and \eqref{secondsub}, the details of solving each part of the sub-problem are depicted.
-Firstly, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in the problem \eqref{constraints1} and using algorithm \eqref{alg}.
-Also we fixed $\eta = 0$.
-Afterward, by achieving $\boldsymbol{A}$, in the second part, we acquire $\boldsymbol{P}$ using the sub-gradient method.
-After solving $\boldsymbol{P}$, $\eta$ is updated.
-Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$ the two parts of the problems is solved until the algorithm converged.
-Here, the algorithm of solving sub-problem A is shown in algorithm \eqref{alg2}
-\begin{algorithm}
-\caption{Joint Network Slicing and Power Allocation}\label{alg2}
-\begin{algorithmic}[1]
-\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
-\State Set $\boldsymbol{P} = \boldsymbol{P}_{max}$
-\For {$counter \gets 1$ to $I_{max}$}
-\State Achieve $\boldsymbol{A}$ by applying Algorithm \eqref{alg}
-\State Obtain $\boldsymbol{P}$ by using sub-gradient method which is mentioned in \eqref{secondsub}.
-\If {$ \mathfrak{R}_{tot}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) - \eta^{(i)} P_{r_{tot}}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) < \epsilon_{\eta} $}
-\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $, $\boldsymbol{A}^*= \boldsymbol{A}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
-\State break;
-\Else
-\State $i= i+1$, Setting $\boldsymbol{P} = \boldsymbol{P}^{(i)}$ ;
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\end{algorithmic}
-\end{algorithm}
-\subsection{Sub-Problem B}
-In this subsection, we would like to solve  \eqref{constraints2}, which is the placement of virtual resources to physical resources in order to minimize the cost function $\psi_{tot}$.
-To achieve optimum $\boldsymbol{Y}$ heuristic algorithm is applied.
-The details of the heuristic algorithm are written in algorithm \eqref{alg3}.
-In this algorithm, firstly, we sort slices and DCs according to their sum-weighted of their requirements (line \ref{31} and line \ref{32} of algorithm \ref{alg3}).
-We define a weighted parameter for $\Omega_{\mathfrak{z},s}^{tot}$ and $\tau_j^\mathfrak{z}$ as follow
-\begin{equation}\label{wt}
-\begin{split}
-\hat{\Omega}_{s}^{tot} &= w_M \bar{\Omega}_{M,s}^{tot} + w_S \bar{\Omega}_{S,s}^{tot} + w_C \bar{\Omega}_{C,s}^{tot} \\
-\hat{\tau}_j &= w_M \tau_{{j}}^M + w_S \tau_{{j}}^S + w_C \tau_{{j}}^C,
-\end{split}
-\end{equation}
-where, $\boldsymbol{w} = \{w_M, w_S, w_C\}$ is the weight of memory, storage and CPU.
-Secondly, we start mapping from the most needed slices to the DC with the most physical resources (from line \ref{33} to line \ref{34} of algorithm \ref{alg3}).
-After mapping DCs to slices, if some slices are not admitted, we start admitting remaining slices to more than one DCs (from line \ref{35} to line \ref{36} of algorithm \ref{alg3}).
-At the end, if DC with the lowest physical resources is free and can be served instead of DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption (line \ref{37} of algorithm \ref{alg3}).
-If a slice does not admit to a specific DC, it remains for the next placement. In next placement the remaining slices, map to more than one DC according to their requirements.
-\begin{algorithm}
-\caption{Plecement of Physical resources into Virtual resources}\label{alg3}
-\begin{algorithmic}[1]
-\State Sort Slices according to $\hat{\Omega}_{s}^{tot} , \forall s$ in descending order.\label{31}
-\State Sort DCs according to $\hat{\tau}_j , \forall j$ in descending order. \label{32}
-\State $\boldsymbol{Y} = \boldsymbol{0}$
-\For {$d \gets 1$ to $D_c$}\label{33}
-\For {$s \gets 1$ to $S$}
-\If {$\sum_{d=1}^{D_c}y_{s,d}==0$ and $\bar{\Omega}_{\mathfrak{z}(s)}^{tot} \leq \tau_{\mathfrak{z}_j} \forall \mathfrak{z}, \forall s$  }
-\State Set $y_{s,d} = 1$;
-\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for} \label{34}
-\State  $ind_{rem} = \{s|({\sum_{d=1}^{D_c}y_{s,d}==0})\}$ \label{35}
-\State Sort remaining amount of DCs same as before in descending order.
-\State Sort remaining slices same as before in descending order.
-\For {$r \gets 1$ to $S_{rem}$}
-\For {$n \gets 1$ to $D_c$}
-\State Set $y_{s,d} = 1$;
-\State {$\bar{\Omega}_{{\mathfrak{z}},s}^{tot}$ $\gets$ {$\bar{\Omega}_{{\mathfrak{z}},s}^{tot}- \tau_j^{\mathfrak{z}}$}}
-\If {$\bar{\Omega}_{s}^{tot}==0$}
-\State Set $y_{s,d} = 1$;
-\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
-\State {break inner loop}
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for} \label{36}
-\State Remapping DCs must be done to prevent wasting Energy \label{37}
-\end{algorithmic}
-\end{algorithm}
-\section{Numerical Results}\label{simul}
-In this section, simulation and numerical results for the main problem are depicted.
- \begin{table}
- \caption {Simulation Parameter} \label{table:1a}
- \begin{center}
-  \begin{tabular}{||c c ||}
-  \hline
-Parameter & Value \\ [0.5ex]
-  \hline\hline
-  Noise power & -174dBm\\
-  \hline
-  Bandwidth & 120 KHZ \\
-  \hline
- Maxmimun transmit Power of each RU & 40dBm \\
-  \hline
-  Minimum delay &  300usec \\
-  \hline
-  Maximum fronthaul capacity  & 200 bits/sec/Hz \\
-   \hline
-  Minimum data rate &  10 bits/sec/Hz \\ [1ex]
-  \hline
- \end{tabular}
- \end{center}
- \end{table}
-In Fig.
-\ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with the different mean number of UEs in each service (the parameters for simulation listed in table \ref{table:1a}).
-The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$ and iteratively updates $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$.
-The optimal method is $0.1$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.09$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$.
-As it is shown, the Energy Efficiency is increased as a mean number of UEs rises.
-\begin{figure}%[H]
-  \centering
-    \includegraphics[width=\linewidth]{fig1_last}
-  \caption{Energy Efficiency vs. Mean Number of UEs in each Service}
-  \label{fig:f1a}
-\end{figure}
-In Fig.
-\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices (the parameters for simulation listed in table \ref{table:1} and also we set $w_C = 320$, $w_S = 100$, $w_M =1$).
-In this simulation, it is assumed that  just one DC can serve each slice, and it is not admitted by more than one DC.
-The proposed method is based on Algorithm \ref{alg3}, and the optimal method is done by the MOSEK toolbox.
-\begin{small}
- \begin{table}
- \caption {Simulation Parameter} \label{table:1}
- \begin{center}
-  \begin{tabular}{||c c ||}
-  \hline
-  Parameter & Value \\ [0.5ex]
-  \hline\hline
-  Mean of CPU for DCs & 320GHz\\
-  \hline
-  Mean of Memory for DCs & 1T\\
-  \hline
- Mean of Storage for DCs & 100T \\
-  \hline
-   Mean of CPU for Slices & 32GHz\\
-  \hline
-  Mean of Memory for Slices & 100G\\
-  \hline
- Mean of Storage for Slices & 10T \\ [1ex]
-  \hline
- \end{tabular}
- \end{center}
- \end{table}
-\end{small}
-When we have two DCs, the proposed method and optimal method have approximately the same ratio of admitted slices.
-But by increasing the number of DCs to five, the performance of the proposed method reduced.
-Using five DCs, the difference between the
-proposed method and the optimal method in the worst case (44 slices) is about $23$ percentage.
-\begin{figure}%[H]
-  \centering
-    \includegraphics[width=\linewidth]{f112}
-  \caption{Ratio of Admitted Slices connected to just one DC vs. Total slices}
-  \label{fig:f1}
-\end{figure}
-In Fig.
-\ref{fig:f2}, the normalized resource consumption is depicted due to the number of slices (the parameters for simulation listed in table \ref{table:1} and also we set $w_C = 320$, $w_S = 100$, $w_M =1$).
-In this simulation, it is assumed that the number of DCs is entirely enough to cover all slices.
-The optimality of the placement of DCs to slices is measured.
-It is shown that how much resources of active DCs are not used.
-For ten slices, the difference between the optimal solution and the proposed solution is about $15$ percent.
-\begin{figure}%[H]
-  \centering
-    \includegraphics[width=\linewidth]{fig22_last}
-  \caption{Normalized Resource Consumption vs. Number of Slices}
-  \label{fig:f2}
-\end{figure}
-\section{Conclusion}
-In this paper, joint network slicing and power allocation were considered in an ORAN system.
-It is assumed that UEs are classified based on their requirements into services.
-Also, there is a number of slices serving the services.
-Each slice consists of PRBs, RUs, and VNFs that support CU and DU.
-The limited fronthaul capacity is considered for the fiber links between RUs and DU.
-The target was to maximize the sum-rate and minimize the power consumption and energy cost of data centers simultaneously.
-The problem is decomposed into two sub-problems.
-Each sub-problem is solved separately by a heuristic algorithm.
-Using numerical results, we validate the heuristic method and study the performance of the algorithms.
-%For the sub-problem A, energy efficiency vs.
-mean number of UEs in each service is depicted.
-The energy efficiency  exceeded by increasing the mean number of UEs in each service.
-For the sub-problem B, two figures are shown.
-In the first one, the ratio of admitted slices that connect to just one DC, for a different number of slices is denoted.
-In the second figure, the normalized resource consumption of DCs is depicted.
-In each figure, the heuristic algorithm is compared with the optimal method and the difference between them is discussed.
+In this section, we consider the downlink of an ORAN system consisting of $V$ services served by an enterprise deploying $S$ slices.
+We denote $v\in \{1,2,...,V \} $ and $s \in \{1,2,...,S \}$ the set of
+services and slices, respectively.
+Each service $v$, contains $U_v$ single-antenna UEs.
+Moreover, each slice $s$, consists of $R_s$ multi-antenna RUs ,which contains $M$ antennas, $K_s$ physical resource blocks (PRBs), one DU and one CU.
+Each DU and CU consists of $$
 

### 2020-01-12 Latex/tex1/pr1.tex
change latex file

@@
 Moreover, each slice $s$, consists of $R_s$ multi-antenna RUs ,which contains $M$ antennas, $K_s$ physical resource blocks (PRBs), one DU and one CU.
-Each DU and CU consists of $$
+Each DU and CU consist of $M_{s,1}$ and $M_{s,2}$ VNFs, with the computational capacity
+of $\mu_1$ and $\mu_2$, respectively.
+\subsection{The Achievable Rate}
+Here, we want to obtain achievable data rate. The achievable data rate for the $j^{th}$ UE in $v^{th}$ service can be formulated as 
+\begin{equation}\label{eq1}
+\mathsf{R}_{u(v,j)} = B \log_2({1+ \rho_{u(v,j)}}),
+\end{equation}
+where, $\rho_{u(v,j)}$ is the SNR of $j^{th}$ UE in the $v^{th}$ service that is described as
+\begin{equation}\label{eq2}
+\rho_{u(v,j)} =  \frac{p_{u(v,j)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,j)}^H \bold{w}_{R_s,u(v,j)}|^2 a_{v,s}}{BN_0 + I_{u(v,j)}},
+\end{equation}
 

### 2020-02-04 Latex/tehran-thesis/tex/chapter3.tex
add latex

\chapter{تخصیص منابع در شبکه های \lr{Open RAN}}
در این فصل، هدف تخصیص منابع در شبکه های \lr{Open RAN} در لینک فروسو می باشد که شامل تخصیص توان و برش های شبکه است.
در این بخش فرض بر این است که شبکه ی نسل پنجم مخابرات با زیرساخت \lr{Open RAN} موجود است. این شبکه سرویس هایی از قبیل \lr{IoT}، سرویس تلفن، پیامک و ... در اختیار کاربران قرار می دهد. در اینجا از مفهوم برش شبکه استفاده شده است بدین صورت که به جای دیدن کاربران به صورت مجزا، کاربرانی که از یک سرویس خاص استفاده می نمایند در دسته ی آن سرویس قرار گرفته و دسته بندی می شوند. همچنین برش هایی از شبکه در اختیار کاربران هر سرویس خاص، قرار می گیرد که هر برش شبکه شامل تعدادی واحد رادیویی
\LTRfootnote{Radio Unit}
(\lr{RU}) 
،
بلوک های منبع فیزیکی
 \LTRfootnote{Physical Resource Block}
 (\lr{PRB})، 
 یک واحد توزیع شده
\LTRfootnote{Distributed Unit}
(\lr{DU}) 
 ، 
 یک واحد مرکزی
\LTRfootnote{Centralized Unit}
(\lr{CU})  
  می باشد که هر واحد توزیع شده و مرکزی شامل تعدادی توابع شبکه ی مجازی شده
  \LTRfootnote{Virtual Network Function}
(\lr{VNF}) 
می باشد. 
\section{مدل سیستم}
در این قسمت، سیستم مدل به صورت کامل مورد بررسی قرار می گیرد.
فرض می کنیم $S$ برش شبکه داریم که قرار است $V$ سرویس مختلف که شامل کاربرانی است که از سرویس خاص استفاده می نمایند را سرویس دهی نماید.
هر سرویس 
$v\in \{1,2,...,V \} $
شامل 
$U_v$
کاربر تک آنتنه می باشند که از سرویس خاصی را درخواست می نماید.
هر برش شبکه 
$s \in \{1,2,...,S \}$
شامل 
$R_s$
واحد رادیویی،
$K_s$
بلوک های منابع فیزیکی، یک واد توزیع شده و یک واحد مرکزی که شامل \lr{VNF} هایی می باشند.
همچنین برش های شبکه می توانند منابع مشترک داشته باشند.
تمام \lr{RU}هایی که به یک سرویس خاص خدمت رسانی می کنند به صورت مشارکتی سیگنال به تمام کاربران در آن سرویس ارسال می نمایند. 
\cite{motalleb2017optimal,mimoCran}
هر واحد رادیویی
$r \in \{1,2,...,R \}$
به یک واحد توزیع شده از طریق لینک فیبر نوری با ظرفیت \lr{fronthaul} 
محدود متصل می باشد.
در سیستم \lr{Open RAN}
دو لایه ی پردازشی که اولی در \lr{CU} و دومی در \lr{DU} قرار گرفته است که پردازش ها با \lr{VNF} ها صورت می گیرد.
لایه پایین تر (\lr{DU}) شامل 
\lr{high-PHY}
،
\lr{MAC}
و 
\lr{RLC}
می باشد و 
لایه ی بالاتر 
(\lr{CU})
شامل 
\lr{RRC}
،
\lr{PDCP}
و 
\lr{SDAP}
است.
فرض بر این است که $M_1$
\lr{VNF}
در \lr{DU}
و 
$M_2$
\lr{VNF}
در \lr{CU} قرار دارد.
هر \lr{VNF} به یک برش یا بیشتر تعلق دارد.
در $s^{th}$ امین برش شبکه $M_{s,1}$ 
\lr{VNF}
در \lr{DU}
و 
$M_{s,2}$
\lr{VNF}
دپر لایه ی \lr{CU} می باشد.
\lr{VNF}
های موجود در لایه ی \lr{DU} و \lr{VU} به ترتیب دارای ظرفیت محاسباتی 
$\mu_1$ 
و
 $\mu_2$
می باشند.
\subsection{نرخ قابل دسترس}
نرخ قابل دسترس برای $i^{th}$ امین کاربر در $v^{th}$امین سرویس به صورت زیر نوشته می شود
\begin{equation}\label{eq1}
\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}}),
\end{equation}
  که $B$ پهنای باند سیستم و 
  $\rho_{u(v,i)}$
  نسبت سیگنال به نویز $i^{th}$
  $i^{th}$ 
  امین کاربر در
   $v^{th}$
   امین سرویس
  می باشد 
  که از رابطه ی زیر بدست می آید
 \begin{equation}\label{eq2}
\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
\end{equation}
که   $p_{u(v,i)}$
نشان دهنده ی توان ارسالی توسط \lr{RU} به 
$i^{th}$ 
  امین کاربر در
   $v^{th}$
   امین سرویس
   است و 
 $\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$
 بردار کانال گین لینک وایرلس از \lr{RU} ها در 
$s^{th}$
امین برش شبکه می باشد.
 همچنین 
$\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$
نشان دهنده ی بردار بیم فرمینگ ارسالی برای \lr{RU}ها در $s$ امین برش شبکه به کاربر $i$ ام در سرویس $v$ ام می باشد.
   به علاوه، $BN_0$
   نشان دهنده ی توان نویز اضافه شونده ی گوسی می باشد و $I_{u(v,i)}$
   توان سیگنال تداخلی است.
همچنین $a_{v,s} \in \{0,1\}$
متغیر باینری است که نشان دهنده ی این است که برش شبکه ی $s$ به سرویس $v$ خدمات رسانی می کند یا نه.
درصورتی که 
 $a_{v,s} =1$
 برش شبکه ی $s$ به سرویس $v$ خدمات رسانی می کند. در غیر این صورت خدمت رسانی نمی کند.
\newline
برای بدست آوردن \lr{SNR} در فرمول \eqref{eq2}، 
فرض می شود که 
 $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $
 بردار سیگنال دریافتی از همه ی کاربران در سرویس $v$ می باشد 
\begin{equation}\label{eq3}
\textstyle \bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v} \
\mathfrak{y}_{R_s}\zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v},
\end{equation}
که $\mathfrak{y}_{R_s} = \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_s}$
و 
$\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $
نشان دهنده ی بردار سمبل ارسالی کاربران سرویس $v$ می باشد.
$\boldsymbol{z}_{U_v}$
نویز گوشی جمع شونده است و
$\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$
.
همچنین
$N_0$
توان نویز می باشد.
علاوه بر این
$\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $
نشان دهنده ی نویز کوانتیزاسیون می باشد که از فشرده سازی سیگنال  در واحد توزیع شده بدست آمده است.
$\boldsymbol{P}_{U_v} = \diag{(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})}$.

### 2020-02-06 Latex/tehran-thesis/tex/chapter3.tex
add latex

@@
 $\boldsymbol{P}_{U_v} = \diag{(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})}$.
+همچنین در اینجا، 
+$\zeta_{k,s}^{U_v} \delequal \{\zeta_{k,s}^{u(v,1)},\zeta_{k,s}^{u(v,2)},...,\zeta_{k,s}^{u(v,N_{U_v})}\}$
+و 
+$\zeta_{k,s}^{u(v,i)} \in \{0,1\}$
+پارامتر باینری می باشد که نشان دهنده ی این است که $i$ امین کابر در $v$امین سرویس امکان ارسال سیگنال خود را از طریق 
+\lr{PRB}
+$k$
+ام دارد یا نه، در ضمن این \lr{PRB} 
+ متعلق به برش $s$ ام می باشد و یا نه.
+ $\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
+نشان دهنده ی ماتریس کانال بین دسته واحد رادیویی 
+ $\mathcal{R}_s$
+ به دسته 
+ $\mathcal{U}_v$
+ کاربران می باشد.
+بردار کانال بین $s$امین برش و $i$امین کابر در $v$امین سرویس $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ به صورت زیر نشان داده شده است 
+\begin{equation}
+\boldsymbol{h}_{\mathcal{R}_s,u_{(s,i)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_s,u_{(v,i)}} \boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}},
+\end{equation} 
+که در اینجا 
+$\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$
+نشان دهنده ی بردار کانال فیدینگ سریع و تخت می باشد و
+ $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
+ نشان دهنده ی ماتریس فیدینگ مقیاس بزرگ می باشد.
+در اینجا فرض بر این است که اطلاعات حالت کانال \lr{CSI}، به صورت کامل می باشد.\newline
+ $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $
+ بردار بیم فرمینگ \lr{zero forcing}
+  می باشد که برای مینیمم کردن تداخل می باشد و بدین صورت است
+\begin{equation}
+\textstyle \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}.
+\end{equation}  
+توان تداخلی کابر $i$ام به سرویس $v$ام به صورت زیر بیان می شود
+\begin{equation}
+\begin{split}
+ I_{u_{(v,i)}} &=
+ \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{v,s}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
+&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
+&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}},
+\end{split}
+\end{equation}
+که 
+$\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
+و 
+$\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$.
+همچنین
+
+${\sigma_q}_{r_{(s,j)}}$
+واریانس نویز کوانتیزاسیون
+$j$
+امین 
+واحد رادیویی در برش $s$ می باشد.
+سیگنال تداخلی برای هر کاربر از سیگنالهای کاربرانی بدست می آید که از \lr{PRB} مشترکی استفاده نموده اند.
+درصورت قرار دادن $P_{max}$
+به جای 
+$p_{u_{(v,l)}}$
+و 
+$p_{u_{(y,l)}}$
+باند بالایی  
+$\bar{I}_{u_{(v,i)}}$
+برای 
+$I_{u_{(v,i)}}$
+بدست می آید
+بنابراین،
+$\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ 
+از قرار گرفتن 
+$\bar{I}_{u_{(v,i)}}$
+به جای 
+$I_{u_{(v,i)}}$
+در رابطه ی 
+\eqref{eq1} و \eqref{eq2}
+بدست می آید.
+\newline
+فرض کنید $\bar{p}_{r_{(s,j)}}$
+نشان دهنده ی سیگنال ارسالی از $j$ امین واحد رادیویی در $s$ امین برش می باشد.
+از رابطه ی \eqref{eq3} داریم
+\begin{equation}
+\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s} + \sigma_{q_{r(s,j)}}^2.
+\end{equation}
+در این صورت نرخ کاربران در لینک \lr{fronthaul} بین $j$امین واحد رادیویی در برش $s$ام با واحد توزیع شده ی موجود در این برش، بدین صورت می باشد  \cite{simeone2016cloud, 1111}
+\begin{equation}
+C_{R_{(s,j)}} = \log{(1+\sum_{v=1}^{V}\frac{w_{r_{(s,j)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   w_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s}}{ \sigma_{q_{r(s,j)}}^2})},
+\end{equation}
+که در اینجا 
+$a_{v,s}$
+متغیر باینری است که نشان دهنده ی این است که برش $s$ام به سرویس $v$ خدمات رسانی می کند یا نه.
+\subsection{میانگین تاخیر}
+فرض کنید ورود بسته های کاربران، فرآیند پوآسون با نرخ ورود 
+$\lambda_{u(v,i)}$
+برای $i$امین کاربر در سرویس $v$ ام می باشد.
+بنابراین، در لایه ی واحد مرکزی (\lr{CU})، میانگین نرخ ورود داده ی کاربری که از خدمات برش $s$ استفاده می نماید 
+$\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$
+می باشد. 
+همچنین، میانگین نرخ داده ی ورودی در لایه ی \lr{DU}، تقریبا مساوی میانگین نرخ داده ی ورودی لایه ی اول 
+$\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$
+می باشد.
+
+Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
+It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
+Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
+Each packet is processed by one of the VNFs of a slice. So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
+\begin{equation}
+\begin{split}
+d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},\\
+d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}.
+\end{split}
+\end{equation}
+where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.
+Besides, $\alpha_{s}$ is the  arrival rate which is divided
+by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
+In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice on the  wireless link. The arrival data rate of wireless link
+ is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
+Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
+ an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
+the mean delay of the transmission layer is
+\begin{equation}
+ d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
+\end{equation}
+where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
+Mean delay of each slice is
+\begin{equation}
+D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s.
+\end{equation}

### 2020-02-07 Latex/tehran-thesis/tex/chapter3.tex
tex

@@
 می باشد.
-
-Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
-It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
-Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice. So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
+میانگین نرخ داده ی ورودی در لایه ی \lr{DU}، تقریبا برابر میانگین نرخ داده ی ورودی در لایه ی \lr{CU} می باشد $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$.
+در اینجا فرض بر این است کهدر هر لایه متعادل کننده ی ترافیک موجود است که ترافیک ورودی را به طور مساوی بین \lr{VNF} ها تقسیم می نماید\cite{frdl,luong2018novel,luong2018novel1}.
+فرض کنید پردازش باند پایه هر \lr{VNF}، بوسیله ی پردازش صف \lr{M/M/1} نشان داده می شود.
+هر بسته بوسیله ی یکی از \lr{VNF}های برش شبکه، پردازش می شود.
+بنابراین، میانگین تاخیر برش $s$ در لایه ی اول و دوم با استفاده از مدل \lr{M/M.1} به این صورت نشان داده می شود
 \begin{equation}
@@
 \end{equation}
-where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.
-Besides, $\alpha_{s}$ is the  arrival rate which is divided
-by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
-In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice on the  wireless link. The arrival data rate of wireless link
- is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
-Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
- an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
-the mean delay of the transmission layer is
+در اینجا
+$1/\mu_1$ و $1/\mu_2$
+میانگین زمان سرویس دهی در لایه ی اول و دوم به ترتیب می باشند.
+$\alpha_{s}$
+نرخ ورودی است که توسط متعادل کننده ی ترافیک به طور مساوی بین \lr{VNF} ها تقسیم می شود.
+نرخ ورودی هر \lr{VNF} در هر لایه از برش \lr{s}، $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$ می باشد.
+$d_{s_{tr}}$
+تاخیر ارسال برای برش $s$ در لینک وایرلس می باشد.
+نرخ داده ی ورودی لینک وایرلس برابر نرخ داده ی ورودی متعادل کننده ی ترافیک برای هر برش است
+\cite{frdl}.
+همچنین زمان سرویس برای صف ارسال در هر برش $s$ دارای توزیع نمایی با میانگین $1/(R_{{tot}_s})$
+است و می توان به صورت صف \lr{M/M/1} مدل کرد  
+\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}.
+بنابراین میانگین تاخیر لایه ی ارسال بدین صورت است
 \begin{equation}
@@
 \end{equation}
-where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
-Mean delay of each slice is
+ $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ 
+ کل نرخ قابل دسترس در هر برش می باشد که به سرویس خاص، تخصیص داده است.
+میانگین تاخیر در هر برش نیز بدین صورت است
 \begin{equation}

### 2020-04-19 Latex/tehran-thesis/tex/chapter3.tex
ns

@@
 \end{equation}
+\subsection{مرکز داده ی فیزیکی}
+هر \lr{VNF}
+نیازمند منابع فیزیکی است که شامل حافظه، نگهدارنده و پردازشگر می باشد.
+فرض کنید منابع مورد نیاز برای $f$ امین \lr{VNF} در برش $s$ ام به صورت زیر می باشد
+ \begin{equation}
+\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \},
+\end{equation}
+که در اینجا 
+ $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$
+ و
+$\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$
+به ترتیب نشان دهنده ی مقدار حافظه، نگهدارنده و پردازشگر می باشد.
+همچنین مقدار کل حافظه، نگهدارنده و پردازشگر برای همه \lr{VNF} ها در یک برش به این صورت تعریف می شود
+\begin{equation}
+\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.
+\end{equation}
+همچنین $D_c$ مرکز داده برای سرویس دهی به \lr{VNF} ها می باشد. هر مرکز داده شامل تعدادی سرور برای سرویس دهی است.
+مقدار حافظه، نگهدارنده و پردازشگر به ترتیب با 
+$\tau_{M_{j}}, \tau_{S_{j}}$
+و
+$\tau_{C_{j}} $
+برای 
+$j^{th}$
+امین مرکز داده به ترتیب زیر می باشد.
+\begin{equation*}
+\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \},
+\end{equation*}
+در این مدل سیستم، 
+تخصیص منابع فیزیکی به \lr{VNF} ها در نظر کرفته شده است. 
+در اینجا فرض بر این است که $y_{s,d}$ متغیر صفر و یکی است که نشان میدهد مرکز داده ی $d$ ام به $s$ امین برش متصل است یا نه.
+\subsection{صورت مساله}
+یک معیار مهم برای سنجش بهینگی یک سیستم ، بهره وری انرژی است که نسبت نرخ کل به توان کل می باشد.
+\begin{equation}
+\textstyle \eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_r^{{tot}}(\boldsymbol{P},\boldsymbol{A})},
+\end{equation}
+که در اینجا، 
+ $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$
+ توان کل مصرفی تمام واحد های رادیویی در یک برشمی باشد.
+همچنین 
+ $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $
+ نرخ تمام کاربران مصرفی تمام سرویس ها می باشد.
+فرض کنید توان مصرفی پردازش باند پایه در هر مرکز داده ی $d$ که به \lr{VNF} های یک برش $s$ متصل می باشد با   
+$\phi_{s,d}$
+نشان داده شده است.
+بنابراین می توان توان کل سیستم را برای کلیه مرکز داده های فعال که به برش متصل هستند ،بدین صورت نشان داد
+\begin{equation*}
+\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
+\end{equation*}
+همچنین ، یک تابع هزینه برای قرار دادن \lr{VNF} ها در مرکز داده ها بدین عنوان تعریف شده است
+\begin{equation}\label{eqpsi}
+\textstyle  \psi_{tot} = \phi_{tot} - \nu \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s}
+\end{equation}
+که $\nu$
+متغیر طراحی برای ارزش بین اولین ترم 
+\eqref{eqpsi}
+ است که عبارت است از کل مصرف انرژی منابع فیزیکی و ترم دوم که مقدار برش های پذیرفته شده برای داشتن منابع فیزیکی نشان داده شده است.
+هدف ما این است که مجموع نرخ را به حداکثر رسانده و توان حاصل از کل (حداکثر توان تمام واحد های رادیویی و کل مصرف انرژی پردازش باند پایه را در کلیه مرکز داده ها) به طور همزمان و با وجود محدودیت هایی که به شرح زیر نوشته شده است ، به حداکثر برساند.
+\begin{subequations}
+\begin{alignat}{4}
+\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\psi_{tot}(\boldsymbol{Y})} \\
+\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} \quad \forall s, \forall i,
+ \label{c11} \\
+&p_{u_{(v,k)}}  \geq 0  \quad \forall v, \forall k,\label{c12} \\
+&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} \quad \forall v, \forall k,\label{c13} \\
+&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max} \quad \forall s, \forall i, \label{c14}\\
+&D_{s} \leq D_{s}^{max} \quad \forall s,\label{c15} \\
+& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 \quad \forall s, \label{c21} \\
+& \textstyle  \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s,\label{c23} \\
+ &\textstyle  \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}  \forall s, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}
+\end{alignat}
+\label{constraints}
+\end{subequations}

### 2020-04-19 Latex/tex/pr.tex
last
ns

@@
 \begin{abstract}
-Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a more flexible and openness radio access network which is the Open-RAN
-(ORAN) for the fifth generation of wireless technology.
-To increase energy efficiency and optimize the allocation of resources, Network Slicing (NS) is considered as the best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks.
-Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to-end network.
-In this paper, we elaborate joint NS in RAN and Core of ORAN system to investigate the power
-of each User Equipment (UE), map slices to services and also map physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RUs and the cost of  physical resources in a downlink channel.
+Open radio access network (ORAN) alliance which has been formed recently establishes a flexible,  open, and smart radio access network (RAN) by combing the ideas from xRAN and cloud RAN (C-RAN).
+ORAN divides the functions of the RAN into three parts, namely remote unit (RU), distributed unit (DU), and central unit (CU).
+While RU contains lower PHY functions, DU contains higher PHY, MAC, and RLC and CU contains RRC, PDCP, and SDAP.
+CU and DU are implemented as virtual network functions (VNFs) running on a cloud environment.
+Interfaces between RU, CU, and DU are open standard interfaces.
+Network slicing as a new concept in 5G systems is used to share the network resources between various services while the operation of one service does not affect another service.
+In this paper, we study the problem of RAN network slicing in an ORAN system.
+We formulate the problem of wireless link scheduling, mapping the slices to the services, and mapping the physical data centers resource to slices.
+The objective is to jointly maximize the energy efficiency and minimize power consumption of RUs and the cost of physical resources in a downlink channel.
 The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems.
-Heuristic algorithms are proposed to each of sub-problems in order to map slices to services, optimize power consumption and map slices to physical resources to minimize the cost of total DCs simultaneously.
+Heuristic algorithms are proposed for each of the sub-problems.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-ORAN, Network Slicing, Energy Efficiency, Data Center (DC)
+Open RAN (ORAN), network slicing, energy efficiency.
 \end{IEEEkeywords}
@@
 
-ORAN virtualizes the elements of the radio access networks, separate them and define appropriate open interfaces for connection of these elements.
+ORAN virtualizes the elements of the radio access networks, separates them and defines appropriate open interfaces for connection of these elements.
 Moreover, ORAN uses machine learning techniques to develop smarter RAN layers in its architecture.
@@
 
-To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and referred as network functions virtualization (NFV).
-Virtual network function (VNF) are functional blocks of the system in this case.
+To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and referred to as network functions virtualization (NFV).
+Virtual network functions (VNFs) are functional blocks of the system.
 5G networks are expected to host several services with different requirements simultaneously.
 Network slicing is considered as a solution for such demand.
-A network slice is a logical end-to-end network which provide service with specific requirements.
-Multiple network slices run on the same physical network infrastructure which are managed and operate independently \cite{lee2018dynamic}.
-Slicing can be defined for the RAN, for the core network or both of these networks \cite{ns1}.
+A network slice is a logical end-to-end network which provides service with specific requirements.
+Multiple network slices run on the same network infrastructure which are managed and operated independently \cite{lee2018dynamic}.
+Slicing can be defined for the RAN, for the core network or both of them \cite{ns1}.
 
-Based on their type of request, UEs are classified into various services, where UEs in the same service have similar service requests.
+Based on their type of service request, user equipments (UEs) are classified into various services, where UEs in the same service have similar service requests.
 In addition, each service is mapped to one or more slices based on the resources of the slices.
-Each VNF of the ORAN is mapped to one or some virtual machines (VMs) in the data center.
+Each VNF of the ORAN is mapped to one or more virtual machines (VMs) in the data center.
 For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.
@@
 In \cite{oranT},  the evolution of RAN in the  5G network is described.
-The architecture of C-RAN and X-RAN is expressed and development of the ORAN from C-RAN and X-RAN is explained.
+The architecture of C-RAN and xRAN is expressed and development of the ORAN from C-RAN and xRAN is explained.
 Also requirements of the network in terms of capacity and latency is taken into account.
 In \cite{oran12},  the ORAN architecture is studied.
-The eight work groups is discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software.
+The eight working groups are discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software.
 To the best of our knowledge, there is not work in the literature to model ORAN systems.
@@
 DU and CU are running on general purpose data centers.
-UEs are divided to different services according to their service requirements.
-RAN resources are decoupled to slices to provide requirements of services.
+UEs are divided to different services according to their requirements.
+RAN resources are partitioned into slices to provide requirements of services.
 Optimal power allocation and joint mapping of slices to services are applied.
-In addition, mapping slices to physical resources is taken to account.
-The contribution of the paper is expressed as follow:
+In addition, mapping slices to physical resources is taken into account.
+The contributions of the paper are as follows:
 \begin{itemize}
-\item In this paper, joint network slicing and resource allocation is considered in an end to end ORAN system.
-\item UEs are categorized into different class of services based on their service requirements.
-RAN which contains RUs, PRBs, and VNFs ,in the two layer of processing, are classified into different group of slices.
-\item The problem is decomposed into two independent sub-problems.
-\item Heuristic algorithms are applied for the sub-problems to efficiently obtain the solution.
+\item Joint network slicing and resource allocation is considered in an ORAN system.
+\item We formulate the problem of assigning UEs to services, services to slices, and physical wireless and data center resources to the slices as an optimization problem.
+\item Novel heuristic algorithms are applied for these sub-problems to efficiently obtain the solution.
 \end{itemize}
@@
 The rest of the paper is organized as follows.
-In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is expressed.
+In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is introduced.
 Then, problem statement is explained and decomposed into two independent sub-problems.
-In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results are provided for the problem.
+In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results are provided to investigate the performance of the algorithms.
 
@@
 Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
-single-antenna user equipments (UEs) that require certain service.
-Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
+single-antenna UEs that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
 Slices can have shared resources.
-All RUs in a slice, that is mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}.
+All RUs in a slice, that are mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}.
 Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.
@@
 The VNFs in the DU and CU layers have the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
-Also, RUs and PRBs can serve more than one slices.
+Also, RUs and PRBs can serve more than one slice.
 \subsection{The Achievable Rate}
@@
 where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
-Mean delay of each slice is
+Mean delay of each slice is obtained as below.
 \begin{equation}
@@
 where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RUs in all slices.
-Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services.
+Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the total rates of all UEs applied for all types of services.
 Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
@@
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\psi_{tot}(\boldsymbol{Y})} \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &  \eta(\boldsymbol{P},\boldsymbol{A})+ \varphi \frac{1}{\psi_{tot}(\boldsymbol{Y})} \\
 \text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} \quad \forall s, \forall i,
@@
 the physical DC is mapped to a VNFs of a slice or not.
+Also, $\varphi$ is weighted variable to value between first and second term of objective function.
 \eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively.
@@
 \State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RUs)
-\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} is not applied}
+\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} are not applied}
 \State Set $a_{i,j} = 0$;
@@
 \begin{algorithm}
-\caption{Plecement of Physical resources into Virtual resources}\label{alg3}
+\caption{Placement of Physical resources into Virtual resources}\label{alg3}
 \begin{algorithmic}[1]
@@
 \section{Numerical Results}\label{simul}
-In this section, simulation and numerical results for the main problem are depicted.
+In this section, numerical results for the main problem are depicted.
  \begin{table}
@@
   \hline
- Maxmimun transmit Power of each RU & 40dBm \\
+ Maximum transmit Power of each RU & 40dBm \\
   \hline
@@
 In Fig.
-\ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with the different mean number of UEs in each service (the parameters for simulation listed in table \ref{table:1a}).
-The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$ and iteratively updates $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$.
+\ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with different mean number of UEs in each service.
+The parameters of simulations are listed in Table \ref{table:1a}.
+The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$.
+They iteratively update $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$.
 The optimal method is $0.1$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.09$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$.
-As it is shown, the Energy Efficiency is increased as a mean number of UEs rises.
+As it is shown, the energy efficiency is increased as mean number of UEs rises.
 \begin{figure}%[H]
@@
 In Fig.
-\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices (the parameters for simulation listed in table \ref{table:1} and also we set $w_C = 320$, $w_S = 100$, $w_M =1$).
+\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices.
+The parameters of the simulation are listed in Table \ref{table:1}.
+We also set $w_C = 320$, $w_S = 100$, $w_M =1$.
 In this simulation, the second term of \eqref{eqpsi}, is important and the designed parameter $\nu$ is supposed to be high.
 Also, it is assumed that just one DC can serve each slice, and each slice is not admitted by more than one DC. 
-The proposed method is based on Algorithm \ref{alg3}, and the optimal method is done by the MOSEK toolbox.
+The proposed method is based on Algorithm \ref{alg3}, and the optimal method is obtained using MOSEK toolbox.
 \begin{small}
@@
 In Fig.
-\ref{fig:f2}, the normalized resource consumption is depicted due to the number of slices (the parameters for simulation listed in table \ref{table:1} and also we set $w_C = 320$, $w_S = 100$, $w_M =1$).
-In this simulation, suppose the number of DCs is entirely enough to cover all slices and also, the designed parameter $\nu$ is assumed to be low, so we focused on the first term of \eqref{eqpsi}.
+\ref{fig:f2}, the normalized resource consumption is depicted versus the number of slices.
+The parameters for simulation are listed in Table \ref{table:1}.
+We also set $w_C = 320$, $w_S = 100$, $w_M =1$).
+In this simulation, suppose the number of DCs is entirely enough to cover all slices and the designed parameter $\nu$ is assumed to be low, so we focused on the first term of \eqref{eqpsi}.
 However, if any slice remains, it can be served by more than one DCs.
-The optimality of the placement of DCs to slices is measured based on the power consumption of DCs.
-It is shown that how much resources of active DCs are not used.
+The optimality of the placement of DC resources to slices is measured based on the power consumption of DCs.
+It is shown the amount of resources of DCs which are not used.
 For ten slices, the difference between the optimal solution and the proposed solution is about $15$ percent.

### 2020-05-12 Latex/tex/pr.tex
add paper

@@
 \begin{equation}
-\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.
+\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.
 \end{equation}
+Where, $F_s = M_{s_1} + M_{s_2}$
 Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
@@
 & \textstyle  \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s,\label{c23} \\
- &\textstyle  \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}  \forall s, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}
+ &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}
 \end{alignat}
@@
 that we have enough physical resources for VNFs of each slice.\newline
-The optimization problem in \eqref{constraints} can be decomposed into two independent optimization problems A and B since the variables can be obtained independently and respectively.
-Firstly we need to solve problem A.
-After obtaining $\boldsymbol{P}$ and $ \boldsymbol{A}$, problem B can be solved by having the value of $ \boldsymbol{A}$.
-The problem A is as follow
+The optimization problem in \eqref{constraints} can be decomposed into two independent optimization sub-problems 1 and 2 since the variables can be obtained independently and respectively.
+Firstly we need to solve sub-problem 1.
+After obtaining $\boldsymbol{P}$ and $ \boldsymbol{A}$, sub-problem 2 can be solved by having the value of $ \boldsymbol{A}$.
+The sub-problem 1 is as follow
 \begin{subequations}
@@
 \end{subequations}
-In problem B, $ \boldsymbol{Y}$ is obtained. The problem B is
+In sub-problem 2, $ \boldsymbol{Y}$ is obtained. The sub-problem 2 is
 \begin{subequations}
@@
 \text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
- &\textstyle  \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}
-\forall s, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
+ &\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
 \end{alignat}
@@
 In this subsection, a heuristic  method is proposed to solve the problem in \eqref{constraints1} which is non-convex and computationally hard.
-To make it tractable, we divide problem \eqref{constraints1} into
+To make it tractable, we divide the problem \eqref{constraints1} into
 two different part that can be solved iteratively.
-In the first part of sub-problem A, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in \eqref{constraints1}.
+In the first part of sub-problem 1, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in \eqref{constraints1}.
 Also, we set $\eta = 0$.
 Afterward, by achieving $\boldsymbol{A}$, in the second part, we find $\boldsymbol{P}$ by using \eqref{constraints1}.
-This part of the problem can be approximated and converted to a convex problem, so the problem can be solved by convex methods.
+This part of the sub-problem can be approximated and converted to a convex problem, so the sub-problem can be solved by convex methods.
 After solving $\boldsymbol{P}$, $\eta$ is updated.
 Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$, the two parts of the problems are solved. We repeat this procedure until the algorithm  converges.
-\subsection{First Part of Sub-Problem A}\label{firstsub}
+and $\eta$, the two parts of the sub-problems are solved. We repeat this procedure until the algorithm  converges.
+\subsection{First Part of Sub-Problem 1}\label{firstsub}
 Two different methods are applied to acquire $\boldsymbol{A}$.
@@
 \end{algorithm}
-\subsection{Second Part of Sub-Problem A}\label{secondsub}
+\subsection{Second Part of Sub-Problem 1}\label{secondsub}
 In this part, by assuming that $\boldsymbol{A}$ is fixed, the power of UEs in each service is achieved.
@@
 %\section*{References}
-\subsection{Solving two part of Sub-problem A iteratively}
+\subsection{Solving two part of Sub-problem 1 iteratively}
 In \eqref{firstsub} and \eqref{secondsub}, the details of solving each part of the sub-problem are depicted.
@@
 Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$ the two parts of the problems is solved until the algorithm converges.
-Here, the algorithm of solving sub-problem A is shown in algorithm \eqref{alg2}
+and $\eta$ the two parts of the sub-problem is solved until the algorithm converges.
+Here, the algorithm of solving sub-problem 1 is shown in algorithm \eqref{alg2}
 \begin{algorithm}
@@
 \end{algorithm}
-\subsection{Sub-Problem B}
+\subsection{Sub-Problem 2}
 In this subsection, we would like to solve  \eqref{constraints2}, which is the placement of virtual resources to physical resources in order to minimize the cost function $\psi_{tot}$.

### 2020-05-25 Latex/tehran-thesis/tex/chapter1.tex
change proposal

@@
 \chapter{مقدمه}
+\subsection{مقدمه ای بر \lr{5G} }
+\lr{5G}،
+مخابرات نسل پنجم
+سیستم های بیسیم \LTRfootnote{Wireless} وشبکه های مخابراتی بعد از نسل چهارم می باشد که تکاملی از لایه ی فیزیکی در تکنولوژی شبکه های مخابراتی سیار همانند \lr{LTE} می باشد که نسبت به \lr{4G} سرعت و پوشش بهتری را فراهم می کند.
+\lr{5G}
+نوع جدیدی از شبکه را ایجاد می کند که به منظور اتصال تقریبا همه و همه چیز با هم از جمله ماشین ها، اشیاء و دستگاه ها ساخته شده است.
+\lr{5G}
+ فناوری بی سیم برای ارائه سرعت داده های چند گیگابیت بر ثانیه ، تأخیر فوق العاده کم ، قابلیت اطمینان بیشتر ، ظرفیت شبکه گسترده، افزایش در دسترس بودن و تجربه کاربری یکنواخت تر به کاربران بیشتر است.
+عملکرد بالاتر و بهره وری بهبود یافته باعث افزایش تجربیات کاربر جدید شده و صنایع جدیدی را به هم متصل می کند.
+
+تکنولوژی سیگنال  \lr{5G} برای پوشش فراگیرتر و بازدهی بهتر سیگنال ایجاد شده است.
+این پیشرفت ها منجر به تغییراتی از قبیل\lr{IOT} \LTRfootnote{Internet of Things} و \lr{Pervasive Computing} در آینده ی نزدیک خواهد شد.
+همچنین \lr{5G} منجر به توسعه و بهبود سرویس های مخابراتی و اینترنتی سیار و در ورای آن، ایجاد تجربه ی بهتری برای مصرف کنندگان خواهد شد.\newline
+برای توسعه ی اینترنت سیار و \lr{IOT}، نیاز داریم تا شبکه های\lr{5G}، معنای اولیه برای دسترسی شبکه برای ارتباط انسان ها با یکدیگر و ارتباط ماشین با انسان گردد.
+به طور کلی، 
+\lr{5G}
+ در سه نوع سرویس اصلی متصل از جمله پهن باند تلفن همراه ، ارتباطات مهم برای ماموریت و IoT عظیم استفاده می شود.
+
+ از آنجا که
+\lr{5G}
+ تکامل می یابد و کمتر به زیرساخت های \lr{4G} وابسته می شود و طیف بیشتری در دسترس قرار می گیرد،
+ تخمین ها سرعت بارگیری را حداکثر 1000 بار سریعتر از \lr{4G} قرار می دهد، که بالقوه از 
+ \lr{10Gbps} 
+بیشتر است، که به شما امکان می دهد تا در کمتر از ثانیه فیلم کامل
+\lr{HD}
+   را بارگیری کنید.
+   برخی تخمین ها محافظه کارتر هستند ، اما حتی محافظه کار ترین آن را چندین ده برابر سریعتر از \lr{4G} قرار می دهد.
+   \begin{table}[H]
+ \caption {سرعت دانلود در نسل های مختلف مخابراتی} \label{tab:title3} 
+ \begin{center}
+  \begin{tabular}{||c c ||} \hline
+  نوع شبکه 
+ \\ [0.5ex]  
+  \hline\hline
+  Number of cluster S & 3 \\ 
+  \hline
+  Noise power density & -174dBm/Hz\\
+  \hline
+  Bandwidth & 120KHz \\
+  \hline
+ Maxmimun transmit Power & 10dBm \\
+  \hline
+  Circuit Power of whole RRHs & 10dBm \\
+  \hline
+  Variance of quantization noise & $10^{-2}$ \\
+  \hline
+   Maxmimun fronthaul link's rate & 20bits/sec/Hz \\
+  \hline
+  Minimum data rate &  1bits/sec/Hz \\ [1ex] 
+  \hline
+ \end{tabular}
+ \end{center}
+ \end{table}
+\subsection{تاریخچه مخابرات}
+در ابتدا می خواهیم بدانیم که چه چیزی منجر به رفتن محققان به سوی  \lr{5G} شده است. یکی از دلایل مهم، سرعت و نرخ انتقال بیشتری است که در ادامه به آن می پردازیم.
+در ابتدا نیاز بشریت به ارتباط تلفنی (انتقال بدون سیم به صورت زمان حقیقی \LTRfootnote{Real Time} بشریت را به سمت نسل اول ارتباطات \lr{1G} سوق داده است .
+نسل دوم ارتباطات \lr{2G} با سرویس های انتقال پیام کوتاه ایجاد شد.
+همچنین با موفقیت تکنولوژی شبکه های منطقه ای بیسیم، اتصال به داده های اینترنتی مورد توجه عموم مردم قرار گرفت که پلی به سوی نسل سوم ارتباطات \lr{3G} را فراهم نمود.
+به طور منطقی پله ی بعدی گام برداشتن در راستای کوچک شدن لپ تاپ و در آمیختن آن با تلفن که امروزه به صورت تلفن هوشمند\LTRfootnote{smart phone} است و دسترسی به  اینترنت، پهنای باند بالا و داده ها در نقاط مختلف جهان بوده است که \lr{4G} یا نسل چهارم را به همراه داشته است.
+با توجه به افزایش تعداد کاربران تلفن های
+هوشمند و تبلت ها و افزایش نرخ ارسال اطلاعات و داده ها در طی سال
+های اخیر طبق پیش بینی های سیسکو میزان ترافیک \lr{IP} طی سالهای اخیر
+  چندین برابر افزایش خواهد یافت.
+در نتیجه اپراتورها برای حل این مشکل و خدمات
+دهی بهتر ناچار به افزایش ظرفیت شبکه می باشند. با توجه
+به این که نرخ داده و ظرفیت در سیستم های نسل چهارم به ظرفیت
+شانون نزدیک شده است، در نتیجه روش هایی که برای
+افزایش ظرفیت شبکه مورد استفاده می گیرند که به شرح زیر است:
+\begin{itemize}
+\item
+استفاده از تکنیک \lr{Massive Mimo}
+\item
+استفاده از روش های پردازش های ابری
+\item
+\lr{Software Defined Networking}
+\item
+\lr{Extreme Densification}
+\item
+روش \lr{mm Wave}
+\end{itemize}
 \section{مقدمه ای بر ساختار \lr{ORAN}}

### 2020-05-25 Latex/version1/pr.tex
change proposal

--- 2020-05-12 Latex/tex/pr.tex
@@
 \subsection{First Part of Sub-Problem 1}\label{firstsub}
-Two different methods are applied to acquire $\boldsymbol{A}$.
+Iterative algorithms are applied to acquire $\boldsymbol{A}$.
+Since the first part of sun-problem is 3D-bin packing problem which is NP-hard, we need heuristic algorithm.
 The details of the heuristic algorithm are represented in algorithm \ref{alg}.
@@
 In this subsection, we would like to solve  \eqref{constraints2}, which is the placement of virtual resources to physical resources in order to minimize the cost function $\psi_{tot}$.
-To achieve optimum $\boldsymbol{Y}$ heuristic algorithm is applied.
+The investigate problem is 3D-bin packing problem which is NP-hard.
+To achieve optimum $\boldsymbol{Y}$ heuristic algorithm for 3D-bin packing is applied.
 The details of the heuristic algorithm are written in algorithm \eqref{alg3}.

### 2020-05-26 Latex/tehran-thesis/tex/chapter1.tex
extend chapter one of proposal

@@
 \lr{5G}
- در سه نوع سرویس اصلی متصل از جمله پهن باند تلفن همراه ، ارتباطات مهم برای ماموریت و IoT عظیم استفاده می شود.
-
+ در سه نوع سرویس اصلی متصل از جمله پهن باند تلفن همراه، IoT عظیم و ارتباطات مهم برای ماموریت استفاده می شود.
+\begin{enumerate}
+\item 
+پهن باند تلفن همراه پیشرفته 
+\lr{(eMBB)}
+ برای مقابله با نرخ داده های بسیار زیاد ، تراکم بالای کاربران و ظرفیت ترافیک بسیار بالا برای سناریوهای مختلف و همچنین پوشش یکپارچه و سناریوهای تحرک بالا با نرخ داده های استفاده شده بهبود یافته است.
+\item
+ ارتباطات  عظیم ماشین 
+ \lr{(mMTC)}
+  برای
+\lr{IoT}،
+   برای تعداد بسیار زیاد دستگاههای متصل به مصرف کم و نرخ داده کم نیاز دارد.
+\item 
+ارتباطات بسیار مطمئن و با تأخیر کم
+ \lr{(URLLC)}
+ برای برنامه های کاربردی مهم برای ایمنی و ماموریت
+  مهم است.
+\end{enumerate}
  از آنجا که
@@
  تکامل می یابد و کمتر به زیرساخت های \lr{4G} وابسته می شود و طیف بیشتری در دسترس قرار می گیرد،
- تخمین ها سرعت بارگیری را حداکثر 1000 بار سریعتر از \lr{4G} قرار می دهد، که بالقوه از 
+ تخمین ها سرعت بارگیری را حداکثر 1000 برابر سریعتر از \lr{4G} قرار می دهد، که بالقوه از 
  \lr{10Gbps} 
-بیشتر است، که به شما امکان می دهد تا در کمتر از ثانیه فیلم کامل
+بیشتر است، که به شما امکان می دهد تا در کمتر از یک ثانیه فیلم کامل
 \lr{HD}
    را بارگیری کنید.
-   برخی تخمین ها محافظه کارتر هستند ، اما حتی محافظه کار ترین آن را چندین ده برابر سریعتر از \lr{4G} قرار می دهد.
-   \begin{table}[H]
- \caption {سرعت دانلود در نسل های مختلف مخابراتی} \label{tab:title3} 
- \begin{center}
-  \begin{tabular}{||c c ||} \hline
-  نوع شبکه 
- \\ [0.5ex]  
-  \hline\hline
-  Number of cluster S & 3 \\ 
-  \hline
-  Noise power density & -174dBm/Hz\\
-  \hline
-  Bandwidth & 120KHz \\
-  \hline
- Maxmimun transmit Power & 10dBm \\
-  \hline
-  Circuit Power of whole RRHs & 10dBm \\
-  \hline
-  Variance of quantization noise & $10^{-2}$ \\
-  \hline
-   Maxmimun fronthaul link's rate & 20bits/sec/Hz \\
-  \hline
-  Minimum data rate &  1bits/sec/Hz \\ [1ex] 
-  \hline
- \end{tabular}
- \end{center}
- \end{table}
+   برخی تخمین ها محافظه کارانه تر هستند ، اما حتی محافظه کارانه ترین آن را چندین ده برابر سریعتر از \lr{4G} قرار می دهد.
+دلایل نیاز به نسل پنجم اینترنت به طور خلاصه در ادامه بیان شده است \citep{etsi}.
+\begin{itemize}
+\item ترافیک داده های تلفن همراه به دلیل پخش ویدئو به سرعت رو به افزایش است.
+\item با در اخیار داشتن چندین دستگاه به طور همزمان، هر کاربر تعداد فزاینده ای از اتصالات را در اختیار دارد.
+\item اینترنت اشیاء به شبکه هایی نیاز دارد که میلیاردها دستگاه را اداره کنند.
+\item با وجود تعداد فزاینده ای از دستگاه های ارتباطی و افزایش ترافیک داده ها ، هم دستگاه ها و هم شبکه ی  
+آن
+نیازمند افزایش بهره وری انرژی هستند.
+\item 
+ به دلیل تحت فشار قرار گرفتن اپراتورهای شبکه برای کاهش هزینه های عملیاتی و همچنین به دلیل اینکه کاربران به تعرفه های نرخ مسطح عادت می کنند و مایل نیستند مبلغ بیشتری بپردازند.
+\item فناوری ارتباطات سیار می تواند موارد استفاده جدیدی را ایجاد کند (به عنوان مثال موارد تاخیر فوق العاده کم یا قابلیت اطمینان بالا) و برنامه های جدید برای صنعت که منجر به درآمد زایی بیشتر اپراتورها می گردد.
+\end{itemize}
+بنابراین عملکرد عملیاتی نسل پنجم می بایست به طور قابل توجهی افزایش یابد (به عنوان مثال افزایش راندمان طیفی ، سرعت بالاتر داده ، تأخیر کم).
+\lr{5G}
+می بایست
+در حالی که هنوز سطح قابل قبولی از مصرف انرژی ، هزینه تجهیزات و استقرار شبکه و هزینه بهره برداری را ارائه می دهد،
+ اینترنت اشیاء را به طور گسترده نیز تأمین کند.
+ همچنین می بایست 
+از طیف گسترده ای از برنامه ها و خدمات پشتیبانی کند.
+ \begin{figure}[H]
+  \centering
+    \includegraphics[width=0.8\textwidth]{./fig/etsi}
+  \caption{مقایسه قابلیت های کلیدی
+\lr{IMT-Advanced}
+ (نسل 4) با
+\lr{IMT-2020}
+ (نسل ۵) 
+ با توجه به
+\lr{ITU-R M.2083}
+\cite{etsi}
+  }
+  \label{fig:C-RAN}
+\end{figure}
 \subsection{تاریخچه مخابرات}
 در ابتدا می خواهیم بدانیم که چه چیزی منجر به رفتن محققان به سوی  \lr{5G} شده است. یکی از دلایل مهم، سرعت و نرخ انتقال بیشتری است که در ادامه به آن می پردازیم.
-در ابتدا نیاز بشریت به ارتباط تلفنی (انتقال بدون سیم به صورت زمان حقیقی \LTRfootnote{Real Time} بشریت را به سمت نسل اول ارتباطات \lr{1G} سوق داده است .
+نیاز بشریت به ارتباط تلفنی (انتقال بدون سیم به صورت زمان حقیقی \LTRfootnote{Real Time} انسان را به سمت نسل اول ارتباطات \lr{1G} سوق داده است.
 نسل دوم ارتباطات \lr{2G} با سرویس های انتقال پیام کوتاه ایجاد شد.
@@
 در نتیجه اپراتورها برای حل این مشکل و خدمات
-دهی بهتر ناچار به افزایش ظرفیت شبکه می باشند. با توجه
+دهی بهتر ناچار به افزایش ظرفیت شبکه می باشند.
+در ادامه به طور مختصر به ۵ نسل مخابراتی می پردازیم\cite{Gen}.
+\subsubsection{نسل اول}
+این اولین نسل از فناوری تلفن همراه بود.
+اولین نسل شبکه تلفن همراه تجاری در اواخر دهه 70 معرفی شد و استانداردهای کاملاً اجرا شده در دهه 80 تاسیس شد.
+استرالیا در سال 1987 توسط \lr{Telecom} (که امروزه با عنوان \lr{Telstra} شناخته می شود) معرفی شد ، استرالیا اولین شبکه تلفن همراه خود را با استفاده از یک سیستم آنالوگ \lr{1G} دریافت کرد.
+\lr{1G} یک فناوری آنالوگ است و به طور کلی تلفن ها از باتری ضعیف برخوردار هستند و کیفیت صدا بدون امنیت بسیار زیاد بود و گاهی اوقات تماس های کاهش یافته را تجربه می کنید.
+این استانداردهای ارتباطی آنالوگ ارتباطی است که در دهه 1980 معرفی شد و تا زمانی که جایگزین ارتباطات دیجیتال \lr{2G} شود ، ادامه یافت.
+حداکثر سرعت \lr{1G} 2.4 کیلوبیت بر ثانیه است.
+\subsubsection{نسل دوم}
+تلفنهای همراه وقتی از \lr{1G} به \lr{2G} رفتند ، اولین نسخه اصلی خود را دریافت کردند.
+تفاوت اصلی بین دو سیستم تلفن همراه (\lr{1G} و \lr{2G}) در این است که سیگنالهای رادیویی مورد استفاده شبکه \lr{1G} آنالوگ هستند ، در حالی که شبکه های
+\lr{2G}
+ دیجیتال هستند.
+انگیزه اصلی این نسل، تهیه کانال ارتباطی ایمن و مطمئن بود.
+این نسل همچنین مفهوم \lr{CDMA} و \lr{GSM} را پیاده سازی کرد که خدماتی مانند پیامک را ارائه داده است.
+شبکه های مخابراتی سلولی نسل دوم بطور تجاری در سال 1991 توسط رادیولینجا (در حال حاضر بخشی از الیزا اویج) توسط استاندارد \lr{GSM} در فنلاند راه اندازی شد.
+\lr{2G}
+قابلیت هایی از قبیل
+\lr{multiplexing}
+دارد که 
+به چندین کاربر در یک کانال منفرد 
+اجازه ی انتقال داده می دهد.
+انتقال داده و صدا در این نسل وجود داشته است.
+در این نسل مخابرات، 
+سرویسهای اساسی مانند پیام کوتاه، رومینگ داخلی، تماس های کنفرانسی، نگه داشتن تماس و صورتحساب مبتنی بر خدمات معرفی شده است.
+جداسازی هزینه های مبتنی بر تماس های مسافت طولانی و صورتحساب در زمان واقعی نیز از قابلیت های این نسل بود.
+حداکثر سرعت برای سرویس \lr{GPRS}
+\LTRfootnote{General Packet Radio Service}
+\lr{50Kbps}
+و برای سرویس 
+\lr{EDGE}
+\LTRfootnote{Enhanced Data Rates for GSM Evolution}
+\lr{1Mbps}
+می باشد.
+\subsubsection{نسل سوم}
+این نسل مخابراتی استانداردهای بسیاری از فناوری های بیسیم را تعیین نمود.
+مرورگر وب ، ایمیل ، بارگیری ویدیو ، به اشتراک گذاری عکس و سایر فناوری های هوشمند در نسل سوم معرفی شدند که در سال 2001 به طور تجاری معرفی شد.
+اهداف تعیین شده برای ارتباطات سیار نسل سوم، تسهیل ظرفیت بیشتر صدا و داده ، پشتیبانی از طیف گسترده تری از برنامه ها و افزایش انتقال داده با هزینه کمتری بود.
+استاندارد \lr{3G} از فناوری جدیدی به نام
+ \lr{UMTS}
+ \LTRfootnote{Universal Telecommunications System Mobile}
+ به عنوان معماری اصلی شبکه خود 
+استفاده می کند.
+\lr{3G}
+ دارای پشتیبانی خدمات چندرسانه ای است.
+\lr{3G}
+  با بهبود چگونگی فشرده سازی صدا در طی تماس، راندمان طیف فرکانس را افزایش داده است، بنابراین تماس همزمان بیشتری می تواند در همان محدوده فرکانس اتفاق بیفتد.
+حداکثر سرعت این نسل 
+\lr{2Mbps}
+و
+حداکثر سرعت نظری برای HSPA + 21.6 Mbps است. 
+\subsubsection{نسل چهارم}
+\lr{4G}
+ یک فناوری بسیار متفاوت در مقایسه با \lr{3G} است و هدف از آن ، فراهم آوردن سرعت بالا ، کیفیت بالا و ظرفیت بالا برای کاربران در عین بهبود امنیت و کاهش هزینه خدمات صوتی و دیتا ، چندرسانه ای و اینترنت از طریق \lr{IP} می باشد.
+برنامه های کاربردی بالقوه و جاری شامل دسترسی به وب موبایل اصلاح شده ، تلفن تلفنی \lr{IP}، خدمات بازی، تلویزیون همراه با کیفیت بالا ، کنفرانس ویدیویی، تلویزیون سه بعدی و محاسبات ابری از قابلیت های پشتیبانی آن می باشد.
+
+فن آوری های کلیدی که این امکان را ایجاد کرده اند 
+\lr{MIMO} \LTRfootnote{Multiple Output Multiple Output}
+ و
+  \lr{OFDM} \LTRfootnote{Multiplexing Division Frequency Division}
+می باشد.
+دو استاندارد مهم آن
+\lr{LTE} \LTRfootnote{Long Term Evolution}
+و
+\lr{WiMAX}
+می باشد.
+حداکثر سرعت یک شبکه 4G هنگام حرکت دستگاه 100 مگابیت بر ثانیه یا 1 گیگابیت بر ثانیه برای ارتباطات کم تحرک مانند هنگام ایستادن یا راه رفتن است.
+تأخیر از حدود \lr{300ms} به  \lr{100ms} با کاهش تراکم دست می یابد.
+ \subsubsection{نسل پنجم}
+ با توجه
 به این که نرخ داده و ظرفیت در سیستم های نسل چهارم به ظرفیت
@@
 \item
-\lr{Software Defined Networking}
+شبکه ی تعریف شده ی نرم افزاری
+\lr{SDN}
+\LTRfootnote{Software Defined Networking}
 \item
-\lr{Extreme Densification}
+موج میلیمتری
+\LTRfootnote{mm Wave}
 \item 
-روش \lr{mm Wave}
+ساختار شبکه های دسترسی رادیویی ابری
+\lr{C-RAN}
+\LTRfootnote{Cloud Radio Access Network}
+\item 
+مجازی سازی توابع شبکه
+\lr{NFV}
+\LTRfootnote{Network Function Virtualization}
+\item 
+برش شبکه
+\LTRfootnote{Network Slicing}
 \end{itemize}

### 2020-05-31 Latex/tehran-thesis/tex/chapter1.tex
extend chapter 1

@@
 \item 
-ساختار شبکه های دسترسی رادیویی ابری
-\lr{C-RAN}
-\LTRfootnote{Cloud Radio Access Network}
+ساختار شبکه های دسترسی رادیویی باز
+\lr{ORAN}
+\LTRfootnote{Open Radio Access Network}
 \item 
@@
 \section{مقدمه ای بر ساختار \lr{ORAN}}
+مجازی سازی \lr{RAN} توجه زیادی را از طرف اپراتورها به خود جلب می کند ، زیرا منجر به کاهش هزینه های اپراتور و \lr{opex} می شود و همچنین این امکان را برای آنها فراهم کند تا با سرعت بیشتری قابلیت های جدیدی به شبکه اضافه کنند.
+
+این احتمال وجود دارد که همه این علاقه ها در ایجاد سه گروه مختلف باشد -
+ انجمن 
+ \lr{xRAN} 
+ ، گروه
+ \lr{ OpenRAN }
+  شرکت 
+ \lr{ Telecom Infra}
+   و ابتکار عمل
+\lr{Open VRAN}
+که برای شرکت سیسکو می باشد.
+اگرچه همه این گروه ها می گویند که در حال کار بر روی یک چیز هستند، که اساساً برای باز کردن \lr{RAN} با استفاده از رابط های استاندارد و عناصر شبکه جعبه سفید است، اما در بررسی دقیق تر اختلافاتی نیز وجود دارد.
+
 \lr{Open RAN}(\lr{ORAN})
-تبسیط و ترکیبی از دو ساختار \lr{C-RAN} و \lr{xRAN} می باشد که انتظار می رود که در فناوری نسل پنجم مخابرات مورد استفاده قرار گرفته و منجر به بهبود عملکرد شبکه های دسترسی رادیویی \lr{RAN} گردد.
-\subsection{\lr{C-RAN}} 
+تبسیط و ترکیبی از دو ساختار \lr{C-RAN} \LTRfootnote{Cloud Radio Access Network} و \lr{xRAN} می باشد که انتظار می رود که در فناوری نسل پنجم مخابرات مورد استفاده قرار گرفته و منجر به بهبود عملکرد شبکه های دسترسی رادیویی \lr{RAN} گردد.
+این ساختار یک شبکه ی باز، انعطاف پذیر و هوشمند است.
+
+\lr{ORAN} 
+توابع
+ شبکه ی دسترسی رادیویی 
+ را به سه قسمت تقسیم می کند،
+  که قسمت اول واحد از راه دور
+ \lr{(RU)} \LTRfootnote{remote unit} 
+ ، واحد توزیع شده
+  \lr{(DU)} \LTRfootnote{Distributed unit} 
+  و واحد مرکزی 
+   \lr{(CU)} \LTRfootnote{Central unit} 
+   می باشد.
+   در حالی که  \lr{RU} دارای توابع  \lr{(PHY)} \LTRfootnote{Physical layer} پایین تر است،
+    \lr{DU} حاوی \lr{(PHY)} بالاتر، 
+    \lr{MAC} 
+ \LTRfootnote{Medium Access Control}   
+    و
+     \lr{RLC}
+   \LTRfootnote{Radio Link Control}  
+      است     
+    و 
+    \lr{(CU)}
+     حاوی
+     \lr{RRC}
+     \LTRfootnote{Radio Resource Control}
+      ،\lr{PDCP}
+      \LTRfootnote{Packet Data Convergence Protocol}
+      و 
+      \lr{SDAP}
+      \LTRfootnote{Service Data Adaptation Protocol}
+      است.
+
+\lr{DU}
+و
+\lr{CU}
+به عنوان توابع شبکه مجازی \lr{(VNFs)} پیاده سازی می شوند،
+که در یک محیط ابر اجرا می شود.
+
+رابط های بین \lr{RU} ، \lr{CU} و \lr{DU} رابط های استاندارد باز هستند.
+\subsection{مقدمه ای بر \lr{C-RAN}}
+شبکه های دسترسی ابری منجر به افزایش پوشش ارسالی می گردد. با توجه به ساختار شبکه
+   \lr{C-RAN} که معماری جدیدی را برای شبکه های نسل آینده
+ارائه می دهد، نه تنها ظرفیت شبکه افزایش می یابد بلکه
+مشکلاتی که در روش های دیگر وجود دارد را نیز هموار
+می سازد.
+مفهوم شبکه دسترسی رادیو ابر \lr{C-RAN}، به مجازی سازی کارکردهای ایستگاه  پایه \LTRfootnote{Base Station-BS} با استفاده از تکنولوژی رایانش ابری \LTRfootnote{Cloud Computing} اشاره می نماید.
+این مفهوم به ایجاد یک ساختار سلولی جدید منجر می شود که در آن، نقاط دسترسی بیسیم کم هزینه که با عنوان واحدهای رادیویی \LTRfootnote{Radio Units} و یا رادیو هد های
+  راه دور 
+  \LTRfootnote{Radio Remote Heads}
+ شناخته می شوند- با استفاده از یک ابر متمرکز با قابلیت پیکربندی مجدد و یا واحد مرکزی \LTRfootnote{Control Unit} مدیریت می شوند.
+شبکه امکان کاهش هزینه های سرمایه گذاری و عملیاتی مورد نیاز برای اپراتور ها به منظور توسعه و نگهداری شبکه های ناهمگن متراکم را فراهم می آورد.
+این مزیت مهم در کنار بازده طیفی، تسهیم آماری \LTRfootnote{Statisitical Multiplexing}، و مزیت های متعادل سازی بار باعث می شود تا شبکه \lr{C-RAN} به عنوان یکی از تکنولوژی های کلیدی در توسعه سیستم های \lr{5G} در جایگاه بسیار مناسبی قرار بگیرد.
+در ادامه، یک بررسی کلی و مختصر از تحقیقات جدید در مورد ساختار \lr{C-RAN} ارائه می شود و موضوعات مورد تاکید عبارتند از فشرده سازی لینک \lr{fronthaul} پردازش باند پایه، کنترل دسترسی به محیط واسط، تخصیص منابع، ملاحظات سطح سیستم، و تلاش های انجام شده در راستای ارائه استاندارد ها.
+\subsubsection{ساختار شبکه های مختلف }
+با توجه به مقاله ی\cite{checko2015cloud}،
+\begin{figure}
+  \centering
+    \includegraphics[scale=0.7]{./fig/c11}
+  \caption{ساختار سنتی ایستگاه پایه \cite{checko2015cloud}}
+  \label{fig:c11}
+\end{figure}
+هر ایستگاه پایه دو نوع پردازش انجام می دهد : پردازش
+رادیویی که توسط واحد رادیویی \LTRfootnote{RRH} انجام می شود و شامل پردازش
+دیجیتالی، فیلترینگ فرکانسی، تقویت توان و ....میباشد و
+پردازش باند پایه که توسط واحد باند پایه \LTRfootnote{BBU} که همان واحد کنترل است \LTRfootnote{CU} انجام شده و از جمله
+مهمترین وظایف آن می توان به کدینگ، مدولاسیون و
+تبدیل فوریه ی سریع اشاره کرد. در ساختار جدیدی که
+تحت عنوان \lr{C-RAN}  معرفی خواهیم نمود نحوه ی ارتباط
+پردازشگرهای رادیویی و باند پایه متحول شده و در نتیجه
+مزایایی برای شبکه حاصل خواهد شد.در ادامه ، انواع ساختارها را بیان خواهد شد.
+\subsubsection{ساختار سنتی ایستگاه پایه }
+
+در ساختارهای سنتی ایستگاه پایه، پردازش های رادیویی و باند پایه در
+داخل ایستگاه پایه انجام می شد و مدول آنتن نیز در فاصله
+ی چند متری از مدول رادیویی نصب شده و ارتباط آنها
+توسط کابل کواکسیال برقرار می شد که همین امر سبب
+افزایش تلفات در شبکه می باشد. این نوع ساختار در شکل
+\ref{fig:c11} نشان داده شده است. همان گونه که مشاهده می کنید
+ارتباط بین ایستگاههای پایه توسط ارتباط  $X_2$ و ارتباط بین
+ایستگاه پایه و شبکه ی هسته توسط ارتباط $ S_1$ برقرار می
+شود. این نوع ساختار در شبکه های \lr{1G} و \lr{2G} به کار گرفته
+شده است 
+\cite{checko2015cloud}.
+
+%Figure \ref{fig:gull} shows a photograph of a gull.
+\subsubsection{ ساختار ایستگاه پایه و واحد رادیویی}
+
+\begin{figure}
+  \centering
+    \includegraphics[scale=0.7]{./fig/c22}
+  \caption{ ساختار ایستگاه پایه و واحد رادیویی \cite{checko2015cloud}}
+  \label{fig:c22}
+\end{figure}
+در این ساختار واحد رادیویی و واحد پردازشی سیگنال، از هم
+مجزا شده و واحد رادیویی که تحت عنوان \lr{RRH} یا \lr{RRU}
+نیز شناخته می شود، توسط فیبر نوری به واحد باند پایه یا \lr{BBU} اتصال می
+یابد. همان طور که پیشتر بیان شد واحد رادیویی مسئولیت
+انجام پردازش های دیجیتالی از جمله تبدیل انالوگ به
+دیجیتال، دیجیتال به انالوگ، تقویت توان و فیلترینگ رابر عهده دارد، که تفکیک وظایف واحد پردازشی و واحد
+رادیویی در این ساختار در شکل \ref{fig:c22} قابل مشاهده است. این
+نوع ساختار برای شبکه های نسل سوم معرفی شده و امروزه
+نیز بیشتر ایستگاههای پایه از همین ساختار بهره می گیرند.
+از جمله ویژگی های بارز این ساختار امکان ایجاد فاصله
+بین واحد رادیویی و پردازشی می باشد، که این فاصله به
+دلیل تاخیر پردازشی و انتشاری نمی تواند از  $40$کیلومتر
+فراتر رود. در این ساختار تجهیزات مرتبط با \lr{BBU} می
+توانند به مکانی مناسبتر که قابل دسترس تر بوده و هزینه
+ی اجاره و نگهداری کمتری را به اپراتورها تحمیل می
+کنند منتقل شوند و واحد های رادیویی نیز در در پشت بام
+ساختمان ها و مکان های مرتفع نصب می شوند که این
+خود سبب کاهش هزینه های خنک سازی ادوات موجود
+می شود. نحوه ی ارتباط بین \lr{RRH} و \lr{BBU} مشابه ساختار
+سنتی بوده و \lr{RRH} ها نیز توسط معماری زنجیروار با هم
+در ارتباطند.
+\begin{figure}[H]
+  \centering
+    \includegraphics[scale=0.7]{./fig/c33}
+  \caption{ساختار  \lr{C-RAN} \cite{checko2015cloud}}
+  \label{fig:c33}
+\end{figure}
+\subsubsection{ساختار \lr{C-RAN}}
+
 ایده اصلی \lr{C-RAN} جداسازی بخش رادیویی (\lr{RRH}) 
@@
  در این ساختار، سه حوزه ی مهم مورد بررسی قرار گرفته است.
-اولین حوزه ی مورد بررسی، جداسازی بخش \lr{control plane} از 
-\lr{user plane}
+اولین حوزه ی مورد بررسی، جداسازی بخش
+صفحه ی کنترل
+ \LTRfootnote{control plane} از 
+ صفحه ی کاربر
+\LTRfootnote{user plane}
 می باشد. حوزه ی دوم،
-ساختن یک پشته نرم افزاری eNodeB مدولار که از سخت افزار COTS استفاده می کند، می باشد.
+ساختن یک پشته نرم افزاری \lr{eNodeB} مدولار که از سخت افزار \lr{COTS} استفاده می کند، می باشد.
 حوزه ی سوم مورد بررسی، انتشار رابط های باز شمال و جنوب است
 \cite{xran}.
+\begin{itemize}
+\item \textbf{ جداسازی بخش صفحه ی کنترل از 
+صفحه ی کاربر}:
+این انتقال صفحه ی کنترل، که قبلاً کاملاً به دستگاههای سخت افزاری \lr{RAN} متصل بود، به دستگاههای محاسباتی در دسترس امکان می دهد \lr{RAN} بتواند به عنوان یک استخر منطقی از ظرفیت ، با کارایی بیشتری کار کند.
+نرم افزار \lr{eNodeB} از سخت افزار خاص فروشنده جدا می شود و الهام بخش نوآوری در هر دو نرم افزار و سخت افزار به صورت مشارکتی اما به طور مستقل است.
+برنامه نویسی و کنترل زمان واقعی بی سابقه در زیرساخت های \lr{RAN} به دست آمده است، که به راحتی از برنامه های کاربردی تلفن همراه و خدمات تجاری پشتیبانی می کند.
+\item \textbf{ساختن یک پشته نرم افزاری \lr{eNodeB} مدولار}:
+رویکرد \lr{xRAN} به خوبی با طرح های مجازی سازی عملکرد شبکه حامل \lr{(NFV)} مطابقت دارد، و همچنین منجر به کنترل عملکرد ترافیک با کارایی بالا، مدیریت تداخل و کنترل منابع رادیویی روی سیستم عامل های استاندارد \lr{x86} و می شود.
+\item \textbf{انتشار رابط های باز شمال و جنوب}: 
+رابط های استاندارد و باز قابیت پشتیبانی از فروشنده های متعدد همکاری اثبات شده دارند. 
+\lr{xRAN.org}
+و اعضای آن به تصویب رساندن این رابط ها از طریق فرآیندهای استاندارد منجر به در دسترس قرار دادن معماری \lr{xRAN} و پشتیبانی مورد نیاز می شوند.
+\cite{xran1}
+\end{itemize}
 \subsection{\lr{ORAN}}
+معماری \lr{ORAN} برای ایجاد زیرساخت های \lr{RAN} نسل بعدی طراحی شده است.
+معماری \lr{ORAN} با تکیه بر اصول هوشمندی و باز بودن، پایه و اساس ساخت \lr{RAN} مجازی بر روی سخت افزار آزاد ، با کنترل رادیویی ایجاد شده توسط هوش مصنوعی است که توسط اپراتورهای سراسر جهان پیش بینی شده است.
+این معماری بر روی رابط های استاندارد و تعریف شده ای بنا شده است تا یک زنجیره اکوسیستم با قابلیت باز ایجاد کند که دارای پشتیبانی کامل از استانداردهای تبلیغ شده توسط \lr{3GPP} و سایر سازمان های استاندارد صنعت فراهم شود.
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.8\textwidth]{./fig/oran1}
+  \caption{ساختار شبکه ی \lr{ORAN} \cite{oranWP}}
+  \label{fig:ORAN}
+\end{figure}
+اتحاد \lr{ORAN} در جستجوی چشم انداز باز بودن و هوشمندی برای شبکه های بی سیم نسل بعدی و فراتر از آن است.
+\begin{itemize}
+\item \textbf{باز بودن}:
+ایجاد یک \lr{RAN} مقرون به صرفه نیاز به باز بودن ارتباط ها دارد.
+رابط های باز برای فعال کردن فروشندگان و اپراتورهای کوچکتر به سرعت می توانند خدمات خود را معرفی کنند و یا اپراتورها را قادر می سازد تا شبکه را متناسب با نیازهای منحصر به فرد خود تنظیم کنند.
+رابط های باز همچنین استقرار چند سازنده ای را قادر می سازد و اکوسیستم تأمین کننده رقابتی تر و پر جنب و جوش بیشتری را ایجاد می کند.
+ همچنین نرم افزارهای منبع باز و طرحهای مرجع سخت افزار باعث نوآوری سریعتر و دموکراتیک تر می شود.
+ \item \textbf{هوشمندی}
+ شبکه ها با ظهور برنامه 5G پیچیده تر و متراکم تر شده و خواستار برنامه های غنی تر می شوند.
+ برای کاستن این پیچیدگی نمی توان از ابزارهای سنتی انسانی  برای استقرار، بهینه سازی و بهره برداری از شبکه استفاده کرد.
+ در نتیجه، شبکه ها باید خود متحرک شوندتا بتوانند از فن آوری های جدید مبتنی بر یادگیری برای خودکارسازی عملکرد شبکه های عملیاتی و کاهش \lr{OPEX} استفاده کنند.
+ اتحاد \lr{ORAN} تلاش خواهد کرد تا از تکنیک های یادگیری عمیق در حال ظهور استفاده کند تا بتواند هر لایه از معماری \lr{RAN}  را به طور هوشمند پیاده سازی کند.
+ پیاده سای هوشمند هم در مولفه ها و خم در سطح شبکه اعمال می گردد و منجر به تخصیص دینامیکی منابع رادیویی و بهینه سازی بازدهی شبکه می گردد.
+ همراه با رابط های باز \lr{ORAN}، اتوماسیون حلقه بسته بهینه شده با هوش مصنوعی دست یافتنی است و دوره جدیدی را برای عملیات شبکه امکان پذیر می کند.
+\end{itemize}
+
 \lr{ORAN}، المانهای شبکه ی دسترسی رادیویی را مجازی می کند ، آنها را جدا کرده و رابط های باز مناسب را 
@@
   که مبنی بر جداسازی 
-   بخش \lr{control plane} از 
-\lr{user plane}
+   بخش صفحه ی کنترل \lr{CP} از
+   صفحه ی کاربر 
+\lr{UP}
 می باشد، در ساختار 
@@
 \lr{RRM}
-برای استفاده از زمان غیر واقعی و زمان نزدیک به واقعی در کنترلگر هوشمند شبکه ی دسترسی رادیویی می گردد.
+برای استفاده از زمان غیر واقعی و زمان نزدیک به واقعی در کنترلگر هوشمند شبکه ی دسترسی رادیویی \LTRfootnote{RAN Intelligent Controller} \lr{RIC} 
+با استفاده از رابط های 
+\lr{A1}
+و
+\lr{E2}
+ می گردد.
+همچنین 
+منجر به جداسازی 
+ \lr{CU}
+ از 
+ \lr{CP/UP}
+ می شود
+ که از طریق رابط \lr{E1} در 3GPP توسعه می یابد.
+
 در ساختار

### 2020-06-07 Latex/tehran-thesis/tex/chapter1.tex
chapter one vnf and NS and ORAN

@@
 رابط های بین \lr{RU} ، \lr{CU} و \lr{DU} رابط های استاندارد باز هستند.
-\subsection{مقدمه ای بر \lr{C-RAN}}
+\subsection{مقدمه ای بر ساختار شبکه های دسترسی رادیویی \lr{C-RAN}}
 شبکه های دسترسی ابری منجر به افزایش پوشش ارسالی می گردد. با توجه به ساختار شبکه
@@
 ساختن یک پشته نرم افزاری \lr{eNodeB} مدولار که از سخت افزار \lr{COTS} استفاده می کند، می باشد.
-حوزه ی سوم مورد بررسی، انتشار رابط های باز شمال و جنوب است
-\cite{xran}.
+حوزه ی سوم مورد بررسی، انتشار رابط های باز شمال و جنوب است\cite{xran}.
+در ادامه این سه حوزه به طور دقیق تر مورد بررسی قرار می گیرد\cite{xran1}.
+
 \begin{itemize}
@@
 و اعضای آن به تصویب رساندن این رابط ها از طریق فرآیندهای استاندارد منجر به در دسترس قرار دادن معماری \lr{xRAN} و پشتیبانی مورد نیاز می شوند.
-\cite{xran1}
+
+\end{itemize}
+\subsubsection{مزایای ساختار \lr{xRAN}}
+\begin{itemize}
+\item 
+جداسازی بخش صفحه ی کنترل از 
+صفحه ی کاربر 
+منجر به 
+برنامه ریزی زمان واقعی بی سابقه و کنترل در زیرساخت \lr{RAN} می شود که به راحتی برنامه های کاربردی تلفن همراه و خدمات تجاری را پشتیبانی می کند.
+\item 
+یک پشته \lr{eNB} مدولار مبتنی بر نرم افزار ، منجر به امکان قرارگیری انعطاف پذیر توابع \lr{eNB} و کنترل ترکیبی آن با یک برنامه ریز امکان پذیر می شود تا بتواند زمان تاخیر متغیر در \lr{fronthaul} را کنترل کند.
+\item 
+رابط های مرزی جنوبی استاندارد، پیاده سازی شبکه با خرید سیستم از چندین شرکت متفاوت را امکان پذیر می سازد و رابط های شمال مرزی، برش کامل شبکه برای بهینه سازی \lr{QoE} \LTRfootnote{Quality of Experience} کاربر را فراهم می کند.
+رابط های \lr{xRAN} به خوبی با لبه ابر حامل هماهنگ هستند و اجازه می دهد تا  محاسبه و ذخیره سازی منابع در شبکه تلفن همراه 
+به صورت دینامیکی مدیریت شود.
+\item 
+این ساختار هزینه ی رشد ظرفیت دسترسی رادیویی و هزینه ی بهره برداری را کاهش می دهد.
 \end{itemize}
@@
 \end{figure}
-اتحاد \lr{ORAN} در جستجوی چشم انداز باز بودن و هوشمندی برای شبکه های بی سیم نسل بعدی و فراتر از آن است.
+اتحاد \lr{ORAN} در جستجوی چشم انداز باز بودن و هوشمندی برای شبکه های بی سیم نسل بعدی و فراتر از آن است\cite{oranWP}.
 \begin{itemize}
@@
  همراه با رابط های باز \lr{ORAN}، اتوماسیون حلقه بسته بهینه شده با هوش مصنوعی دست یافتنی است و دوره جدیدی را برای عملیات شبکه امکان پذیر می کند.
-\end{itemize}
-
-\lr{ORAN}، المانهای شبکه ی دسترسی رادیویی را مجازی می کند ، آنها را جدا کرده و رابط های باز مناسب را 
-برای اتصال این عناصر
-تعیین می کند. همچنین، 
-\lr{ORAN}
-از روشهای یادگیری ماشین برای هوشمندسازی لایه های 
-\lr{RAN}
- استفاده می نماید. 
- در ساختار نوآورانه ی 
- \lr{ORAN}
- نرم افزار قابل برنامه ریزی 
- \lr{RAN}
- از سخت افزار جدا می شود.
-  یکی از مهم ترین خصوصیات
-  \lr{ORAN}
-  رابط کاربری باز است که به اپراتورهای موبایل این قابلیت را می دهد تا بتوانند سرویس های مورد نیاز خود را تعریف نمایند.
+\item \textbf{روش های هوش مصنوعی \lr{AI}
+ \LTRfootnote{Artificial Intelligent}
+  منجر به هوشمند سازی بخش رادیویی با استفاده از نرم افزار تعریف شده \LTRfootnote{Software Defined} 
+  می شود:}
    مفهوم 
@@
  می شود
- که از طریق رابط \lr{E1} در 3GPP توسعه می یابد.
+ که از طریق رابط \lr{E1} در \lr{3GPP } توسعه می یابد.
+\item \textbf{مجازی سازی بخش \lr{RAN}}:
+ ابری سازی RAN یکی از اصول مهم ساختار 
+ \lr{ORAN}
+  می باشد.
+ اپراتورها برای پشتیبانی از شکافهای مختلف در شبکه، الزامات NFVI/VIM را برای تقویت سیستم عامل مجازی ارائه می دهند.
+ به عنوان مثال: لایه ی بالا بین PDCP و RLC تقسیم می شود و لایه ی پایین در PHY تقسیم می شود.
+\item \textbf{رابط های باز}:
+معماری مرجع ORAN بر روی مجموعه ای از رابط های کلیدی بین چندین جزء جدا شده ی RAN ساخته شده است.
+اینها شامل رابط های \lr{3GPP} پیشرفته 
+(
+\lr{F1}،
+\lr{W1}،
+\lr{E1}،
+\lr{X2}،
+\lr{Xn}
+)
+ برای قابلیت همکاری بین چندین شرکت مختلف تولید کننده است.
+رابط های مشخص شده \lr{ORAN Alliance} شامل یک رابط fronthaul باز بین DU و RRU ، رابط \lr{E2} و یک رابط \lr{A1} بین لایه 
+Orchestration/NMS 
+است که شامل عملکرد
+ غیر واقعی زمانی \LTRfootnote{non real time RIC} و عملکرد eNB / gNB حاوی عملکرد RIC نزدیک به زمان واقعی 
+\LTRfootnote{near-real time RIC} 
+است.
+\item \textbf{سخت افزار جعبه سفید}:
+برای بهره مندی کامل از مقیاسی از اقتصاد ارائه شده توسط یک رویکرد  محاسباتی باز، \lr{O-RAN Alliance } 
+طرح های مرجع 
+سخت افزاری و ایستگاه پایه به صورت جعبه سفید با کارایی بالا را مشخص می کند. 
+سیستم عامل های مرجع از یک رویکرد جدا شده پشتیبانی می کنند و نقشه های مفصلی را برای معماری سخت افزار و نرم افزار ارائه می دهند تا هم BBU و RRU را فعال کنند. 
+\item \textbf{نرم افزار منبع باز}:
+اتحادیه ORAN ارزش انجمن هایی که منابع باز ارا‌ئه می دهند را درک کرده   
+ و از آنها پشتیبانی می کند.
+ بسیاری از مؤلفه های معماری ORAN به صورت منبع باز از طریق جوامع موجود تحویل داده می شود.
+ این مؤلفه ها عبارتند از: کنترلر هوشمند RAN ، پشته پروتکل ، پردازش لایه PHY و بستر مجازی سازی.
+  چارچوب نرم افزار منبع باز ORAN نه تنها رابط های 
+(
+\lr{F1}،
+\lr{W1}،
+\lr{E1}،
+\lr{E2}،
+\lr{X2}،
+\lr{Xn}
+)
+  را پیاده سازی می کند ، بلکه انتظار دارد که طراحی مرجع را برای نسل بعدی RRM با هوش جاسازی شده ارائه دهد تا RIC را امکان پذیر کند.
+\end{itemize}
+
+\lr{ORAN}،
+ المانهای شبکه ی دسترسی رادیویی را مجازی می کند، آنها را جدا کرده و رابط های باز مناسب را 
+برای اتصال این عناصر
+تعیین می کند. همچنین، 
+\lr{ORAN}
+از روشهای یادگیری ماشین برای هوشمندسازی لایه های 
+\lr{RAN}
+ استفاده می نماید. 
+ در ساختار نوآورانه ی 
+ \lr{ORAN}
+ نرم افزار قابل برنامه ریزی 
+ \lr{RAN}
+ از سخت افزار جدا می شود.
+  یکی از مهم ترین خصوصیات
+  \lr{ORAN}
+  رابط کاربری باز است که به اپراتورهای موبایل این قابلیت را می دهد تا بتوانند سرویس های مورد نیاز خود را تعریف نمایند.
 
@@
   که شامل تابع نزدیک به زمان است.
+
+  با افزایش ترافیک تلفن همراه، شبکه های تلفن همراه و تجهیزاتی که آنها را اجرا می کند باید نرم افزاری تر ، مجازی، انعطاف پذیر، هوشمند و کارآمدتر شوند.
+اتحادیه ی ORAN متعهد است در حال تکامل شبکه های دسترسی رادیویی باشد که باعث می شود آنها نسبت به نسلهای قبل بازتر و باهوش تر شوند.
+تجزیه و تحلیل در زمان واقعی که توسط سیستم های یادگیری ماشین تعبیه شده است و ماژول های پایانی هوش مصنوعی را هدایت می کند، باعث تقویت هوش شبکه می شود.
+عناصر شبکه مجازی با رابط های باز و استاندارد، جنبه های اصلی طرح های مرجع توسعه یافته توسط اتحادیه ی ORAN خواهد بود.
+فن آوری های موجود از عناصر شبکه منبع باز و جعبه سفید، نرم افزار و اجزای سخت افزاری مهم این طرح های مرجع خواهد بود.
 \section{مجازی سازی توابع شبکه}
@@
     باشند.
+    ایده اصلی NFV جداسازی تجهیزات شبکه فیزیکی از توابع اجرا شده بر روی آنها است.
+این بدان معنی است که یک عملکرد شبکه - مانند فایروال - می تواند به عنوان نمونه ای از نرم افزارهای ساده به فراهم آورندگان سرویس (SP) \LTRfootnote{Service Provider} ارسال شود.
+    این امر امکان ادغام بسیاری از انواع تجهیزات شبکه بر روی سرورهای با حجم بالا ، سوئیچ ها و انبارها را فراهم می کند ، که می توانند در مراکز داده، نودهای شبکه توزیع شده و در محل کاربر نهایی قرار بگیرند.
+    به این ترتیب، یک سرویس خاص می تواند به مجموعه ای از توابع شبکه مجازی (VNFs) تجزیه شود، که می تواند در نرم افزارهایی که روی یک یا چند سرور فیزیکی استاندارد در صنعت قرار دارند، اجرا شود.
+    سپس VNF ها ممکن است در مکانهای مختلف شبکه (به عنوان مثال، با هدف معرفی خدمات هدفمند به مشتریان در یک موقعیت جغرافیایی خاص) جابجا شده و خدمات رسانی کنند، بدون اینکه لزوماً به خرید و نصب سخت افزار جدید نیاز داشته باشند.
+    NFV به 
+     هاSP
+   با انعطاف پذیری بیشتری وعده می دهد تا بتواند بیشتر قابلیت ها و خدمات شبکه خود را به کاربران و سایر خدمات باز کنند و امکان استقرار یا پشتیبانی از سرویس های جدید شبکه را  به طور سریعتر و ارزانتر داشته باشند تا بتوانند  سرویس بهتری داشته باشند.
+   برای دستیابی به این مزایا، NFV مسیر را برای کاهش اختلافات در نحوه ارائه خدمات شبکه در مقایسه با عملکرد فعلی ایجاد می کند. خلاصه این ویژگی ها به شرح زیر است
+   \cite{NFV}.
+ \begin{itemize}
+  \item \textbf{جدا سازی بخش نرم افزار از سخت افزار}:
+از آنجا که عنصر شبکه، ترکیبی از سخت افزارها و نرم افزارهای یکپارچه نخواهد بود، تکامل هر دو مستقل از یکدیگر می باشد.
+که این ویژگی منجر به جداسازی زمان بندی توسعه و نگهداری نرم افزار و سخت افزار می گردد.
+\item \textbf{استقرار عملکرد شبکه انعطاف پذیر:}
+جدا کردن نرم افزار از سخت افزار به تنظیم مجدد و به اشتراک گذاری منابع زیرساختی کمک می کند،
+بنابراین، سخت افزار و نرم افزار، باهمدیگر
+می توانند در زمان های مختلف عملکردهای مختلفی را انجام دهد که به اپراتورهای شبکه کمک می کند تا خدمات جدید شبکه را سریعتر در همان پلت فرم فیزیکی مستقر کنند.
+بنابراین،
+مؤلفه ها را می توان در هر دستگاه با قابلیت NFV در شبکه قرار داد و اتصالات آنها به روشی انعطاف پذیر تنظیم کرد.
+\item \textbf{مقیاس گذاری پویا}:
+  جداشدن عملکرد شبکه به اجزای نرم افزاری  نعطاف پذیری بیشتری را برای  عملکرد واقعی VNF به روشی پویاتر، 
+   با توجه به ترافیک واقعی که اپراتور شبکه برای تأمین ظرفیت نیاز دارد،
+  فراهم می کند.
+\end{itemize}
+
  \section{برش شبکه}
+ پیش بینی می شود شبکه های \lr{5G} چندین سرویس را با نیازهای مختلف به طور همزمان پشتیبانی کند.
  برش شبکه
@@
   اجرا و مدیریت می شوند و
-به طور مستقل کار کنید.
-پیاده سازی های مختلفی از برش شبکه وجود دارد که شامل برش هسته ی شبکه، برش \lr{RAN} و برش هر دو بخش می باشد.
-در برش هسته ی شبکه، برش تنها در بخش هسته ی شبکه است و تمام واسط ها و فرآیندها، بدون تغییر باقی می مانند.
-در برش \lr{RAN}، 
-برش های \lr{RAN}، بر روی
+به طور مستقل کار می کنند.
+برش شبکه
+ با هدف تقسیم منطقی مجموعه توابع و منابع شبکه در یک نهاد شبکه در نظر گرفته شده است که مطابق با خواسته های فنی یا تجاری خاص می باشد.
+ با خرد کردن یک شبکه فیزیکی به چندین شبکه منطقی، برش شبکه می تواند از خدمات متناسب با تقاضا برای سناریوهای برنامه مشخص در همان زمان با استفاده از همان شبکه فیزیکی پشتیبانی کند.
+با استفاده از برش شبکه، منابع شبکه می توانند به صورت پویا و کارآمد به برش های شبکه منطقی با توجه به خواسته های QoS مربوطه اختصاص داده شوند\cite{NS1}.
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.8\textwidth]{./fig/NS}
+  \caption{سه ساختار برش شبکه \cite{NS2}}
+  \label{fig:ORAN}
+\end{figure} 
+پیاده سازی های مختلفی از برش شبکه وجود دارد که شامل برش هسته ی شبکه، برش \lr{RAN} و برش هر دو بخش می باشد\cite{NS2}.
+\begin{itemize}
+\item \textbf{برش هسته:}
+هسته ی شبکه (CN) \LTRfootnote{core network}
+به عنوان برش های شبکه، مجازی سازی می شوند که با ویژگی هایی مانند ویژگی های قابل برنامه ریزی و قابل اعتماد بودن که شامل مدیریت حرکت و تأیید اعتبار می باشد.
+برش های شبکه فقط در CN وجود دارد.
+  بنابراین، نه RAN و نه تجهیزات کاربر (UE) برای CNهای برش داده شده نیاز به تنظیم ویژه ندارند.
+  در برش هسته ی شبکه، برش تنها در بخش هسته ی شبکه است و تمام واسط ها و فرآیندها، بدون تغییر باقی می مانند
+  به جز مواردی که در ابتدا UE ها به شبکه ها وصل می شوند ، زیرا UE ها باید به برش صحیح CN ها اختصاص داده شوند.
+\item \textbf{
+برش شبکه ی دسترسی رادیویی:
+}
+برخلاف برش CN،
+برش های RAN روی سخت افزار رادیویی و استخر منابع باند پایه، به نام یک سطح بی سیم، اجرا می شوند که دارای کشش کمتری نسبت به زیرساخت مجازی بالغ شده در CNها هستند.
+با چند BS منطقی، برش های RAN پارامترهای مختلفی از رابط های هوا (به عنوان مثال ، طول نماد ، فاصله زیر حامل ، طول پیشوند چرخه و پارامترهای درخواست تکرار خودکار هیبریدی \LTRfootnote{HARQ}) را اعمال می کند.
+علاوه بر این، پارامترهای دیگری مانند انتخاب سلول و آستانه انتقال، و همچنین سیاست های انتقال هماهنگ را می توان برای هر برش تعریف کرد تا یک تجربه بی سیم برجسته را به کاربران ارائه دهد.
+\item \textbf{برش هسته و شبکه ی دسترسی رادیویی}:
+در این سناریو، هر برش از RAN به یک برش از هسته متصل می شود، بنابراین اپراتورها می توانند یک شبکه منطقی انتهای به مشتریان ارائه دهند.
+روش انتخاب برش همان روش برش RAN است، بنابراین کاربران پس از دسترسی به سیستم، نیازی به انتخاب برش CN ندارند.
+این مدل از برش مزایای هر دو مدل از برش را باهم دارد.
+ در نتیجه این روش برش، قادر به برنامه ریزی ویژگی های CN و همچنین دارای قابلیت تغییر رابط های هوایی RAN
+ می باشد.
+\end{itemize}

### 2020-06-09 Latex/tehran-thesis/tex/chapter1.tex
finish chapter one

@@
 \end{itemize}  
+ \subsection{ساختار شبکه }
+ VNF
+ ها برای به اشتراک گذاشتن منابع مختلف فیزیکی و مجازی زیرساخت ها می توانند مستقر و مجدداً تنظیم شوند ، تا مقیاس پذیری و کارآمدی سیستم را تضمین کنند که منجر می شود SP ها به سرعت سرویس های جدید را در سیستم وارد کنند.
+ به طور کلی ، سه مؤلفه اصلی در NFV وجود دارد:
+ خدمات ، NFVI و مدیریت NFV و orchestration
+ \LTRfootnote{NFV-MANO}
+ که در شکل \eqref{fig:NFV} دیده می شود.
+ \begin{figure}
+  \centering
+    \includegraphics[width=0.8\textwidth]{./fig/NFV}
+  \caption{ساختار NFV \cite{NFVArch}}
+  \label{fig:NFV}
+\end{figure} 
+این مؤلفه ها به شرح زیر بیان می گردد\cite{NFVArch}.
+\begin{enumerate}
+\item 
+خدمات: یک سرویس مجموعه ای از VNF ها است که می توانند در یک یا چند ماشین مجازی پیاده سازی شوند.
+در بعضی مواقع ، VNF ها می توانند در ماشینهای مجازی نصب شده در سیستم عامل یا سخت افزار بطور مستقیم نصب شوند. آنها توسط سرپرستان بومی یا مانیتورهای ماشین مجازی اداره می شوند.
+معمولاً توسط یک سیستم مدیریت عناصر \LTRfootnote{Element Management System} (EMS)،
+ که مسئولیت ایجاد، تنظیمات، نظارت، عملکرد و امنیت آن است، اداره می شود.
+ EMS 
+ اطلاعات ضروری مورد نیاز سیستم پشتیبانی عملیات \LTRfootnote{Operations Support System}(OSS) را در یک محیط SP فراهم می کند.
+ OSS
+  سیستم مدیریت عمومی است، که  همراه با سیستم پشتیبانی از تجارت 
+\LTRfootnote{Business Support System}  
+  (BSS)
+  ، به ارائه دهندگان کمک می کند تا چندین سرویس ارتباطی از راه دور را به کار ببندند و مدیریت کنند.
+  (به عنوان مثال سفارش ، صورتحساب ، تمدید ، عیب یابی مشکل و غیره).
+مشخصات NFV بر ادغام با راه حل های موجود OSS / BSS متمرکز است.
+\item NFVI
+:
+زیرساخت های NFV تمام منابع سخت افزاری و نرم افزاری را که شامل محیط NFV است ، پوشش می دهد.
+NFVI شامل اتصال شبکه بین مکان ها ، به عنوان مثال ، بین
+مراکز داده و ابرهای ترکیبی عمومی یا خصوصی است.
+منابع فیزیکی به طور معمول شامل محاسبات، ذخیره سازی و سخت افزار شبکه است که وظیفه ی آن پردازش، ذخیره سازی و اتصال VNF ها از طریق لایه مجازی سازی است و دقیقاً بالای سخت افزار قرار دارد و منابع فیزیکی را چکیده می کند (که به صورت منطقی تقسیم شده و به VNF ها اختصاص می یابد).
+هیچ راه حل خاصی برای استقرار NFV وجود ندارد.
+در عوض معماری NFV می تواند از یک لایه مجازی سازی موجود مانند Hypervisor با ویژگی های استاندارد که منابع سخت افزاری را به راحتی استخراج می کند و آنها را به VNF ها اختصاص می دهد ، استفاده کند.
+وقتی این پشتیبانی در دسترس نباشد ، اغلب ، لایه مجازی سازی از طریق یک سیستم عامل حاصل می شود که نرم افزاری را در بالای سرور غیر مجازی یا با اجرای یک VNF به عنوان یک برنامه اضافه می کند.
+\item NFV-MANO
+:
+NFV-MANO
+ از این موارد تشکیل شده است:
+ orchestrator
+ ،
+ مدیران VNFs و مدیران زیرساخت مجازی.
+ چنین بلوکی عملکردهای مورد نیاز برای کارهای مدیریتی را که برای VNF ها اعمال می شود، به عنوان مثال تهیه و پیکربندی را  ارائه می دهد. 
+ NFV-MANO شامل orchestration و مدیریت چرخه منابع فیزیکی یا مجازی است که از مجازی سازی زیرساخت ها و مدیریت چرخه VNF ها پشتیبانی می کند.
+ همچنین شامل بانکهای اطلاعاتی است که برای ذخیره اطلاعات و مدل های داده استفاده می شود که ویژگی های چرخه عمر توابع، خدمات و منابع را تعریف می کند.
+ NFV-MANO روی کلیه وظایف مدیریتی مجازی سازی ویژه لازم در چارچوب NFV تمرکز دارد.
+ علاوه بر این ، این چارچوب رابط هایی را تعیین می کند که می توانند برای ارتباطات بین مؤلفه های مختلف
+  NFV MANO، 
+ و همچنین هماهنگی با سیستم های سنتی مدیریت شبکه (یعنی OSS و BSS) مورد استفاده قرار گیرند تا امکان عملکرد هر دو VNF و کارکردهای اجرا شده بر روی تجهیزات فراهم شود.
+ به طور خلاصه، اگر برش شبکه با استفاده از فایروال و DPI مستقر شده باشد، آنگاه NFV-MANO وظیفه دارد بگوید این VNF ها در کجای شبکه فیزیکی قرار دارند. همچنین این VNF ها توسط EMS و همان MANO کنترل می شوند.
+\end{enumerate}
+\section{شبکه تعریف شده نرم افزار (SDN)}
+بنیاد شبکه باز 
+\LTRfootnote{Open Networking Foundation}
+(ONF) 
+یک مجموعه ای است که به توسعه، استاندارد سازی و تجاری سازی SDN 
+\LTRfootnote{Software Defined Network} 
+پرداخت.
+ONF
+ به طور صریح و دقیق SDN را بدین صورت تعریف کرد:
+ شبکه تعریف شده توسط نرم افزار (SDN) یک معماری شبکه است که کنترل شبکه از ارسال جدا می شود و به طور مستقیم قابل برنامه ریزی است.
+ SDN توسط دو ویژگی تعریف می شود ، یعنی جدا شدن صفحه ی کنترل و داده و قابلیت برنامه ریزی در صفحه کنترل.
+ با این وجود ، هیچ یک از این دو امضای SDN در معماری شبکه کاملاً جدید نیستند
+ \cite{SDN1}.
+ SDN 
+ در اصل یک الگوی شبکه سازی متمرکز است که در آن هوش شبکه (یعنی عملکرد کنترل یا صفحه کنترل) به طور منطقی در یک یا مجموعه ای از موجودیت های کنترل (یعنی کنترل کننده های SDN) متمرکز می شود در حالی که صفحه ی انتقال داده،  ساده و چکیده شده برای برنامه های کاربردی می باشد و سرویس های شبکه درخواست خود را از طریق کنترل کننده های SDN
+ بیان می کنند.
+ در حالی که در مورد هسته اصلی شبکه موبایل LTE ، EPC صحبت می کنیم ، مفهوم SDN برای دستیابی به جدایی واضح بین صفحات کنترل و کاربر در اشخاص SGW و PGW استفاده می شود.
+ با تقسیم دروازه به این روش (یعنی از SGW به SGW-C و
+SGW-U 
+و از PGW به PGW-C و (PGW-U 
+  مقیاس بندی این مؤلفه ها به طور مستقل امکان پذیر است و طیف وسیعی از گزینه های استقرار را نیز ممکن می کند.
 
+ پروتکل مورد استفاده بین صفحه ی کنترل و صفحه ی کاربر می تواند یا افزونه پروتکل موجود OpenFlow باشد، که توسط گروه کاری بی سیم و موبایل ONF (WMWG)با رابط های جدید، یعنی Sxa و Sxb ساخته می شود، که توسط  \lr{3GPP CUPS} تعریف و مشخص می شوند\cite{SDN2}.
+ جداسازی صفحه ی کنترل از کاربر منجر به کنترل بیشتر شبکه بوسیله ی برنامه می گردد که منجر به بهبود تنظیمات و کارآمدی سیستم می گردد.
+ SDN
+  با ساختار برنامه ریزی شده ی قوانین ترافیک، جایگزین امیدوار کننده ای برای فرماندهی ترافیک ارائه می دهد.
+  ساختار SDN در شکل \eqref{fig:SDN} آورده شده است.
+  \begin{figure}
+  \centering
+    \includegraphics[width=0.8\textwidth]{./fig/SDN}
+  \caption{ ساختار SDN \cite{SDN3}}
+  \label{fig:SDN}
+\end{figure} 
+  در این ساختار ۳ لایه ی مختلف وجود دارد که در ادمه بیان می کنیم\cite{SDN3}.
+  \begin{enumerate}
+  \item لایه ی برنامه :
+  این لایه مجموعه ای از برنامه های متمرکز بر خدمات شبکه را پوشش می دهد و آنها عمدتا برنامه های نرم افزاری هستند که با لایه کنترل ارتباط برقرار می کنند.
+  \item لایه ی کنترل:
+  به عنوان هسته اصلی SDN ، لایه کنترل از یک کنترلر متمرکز تشکیل شده است که منطقاً نمای شبکه جهانی و پویا را حفظ می کند ،  که از لایه برنامه درخواست می کند و دستگاه های شبکه را از طریق پروتکل های استاندارد مدیریت می کند.
+  \item لایه ی داده:
+  این لایه، زیرساخت ها شامل سوئیچ ها، روترها و لوازم شبکه می باشد. در زمینه SDN ، این دستگاه ها قابل برنامه ریزی هستند و از رابط های استاندارد پشتیبانی می کنند.
+  \end{enumerate}
  \section{برش شبکه}
@@
 
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
   \caption{سه ساختار برش شبکه \cite{NS2}}
-  \label{fig:ORAN}
+  \label{fig:NS}
 \end{figure} 
@@
  می باشد.
+
 \end{itemize}
+\section{نتیجه گیری}
+  در این فصل ابتدا مروری بر تاریخچه ی مخابرات و ۵ نسل مخابراتی شد. سپس ساختار های مختف دسترسی رادیویی به طور خلاصه بیان شد و در نتیجه ی آن ساختار CRAN که ساختار ابری است تعریف شد. سپس ساختار xRAN
+  مورد توجه قرار گرفت و در نهایت ساختار ORAN 
+  که ترکیب و تکاملی از CRAN و xRAN می باشد مورد توجه قرار گرفت.
+
+ بعد از بیان ساختارهای رادیویی، ساختار هسته ی شبکه را در نسل پنجم بیان کردیم که شامل 
+ NFV و SDN 
+ می باشد که منجر به جداسازی صفحه ی کنترل از کاربر می شود و سیستم هوشمندتر همراه با قابلیت برنامه ریزی بیشتر می گردد.
+ در ادامه برش شبکه در بخش رادیویی و هسته و هردو مورد توجه قرار گرفته شد.
+\section{خلاصه ای از فصل های آتی}
+در فصل دوم مروری بر ادبیات پیشین و خلاصه ای از مدل سیستم مقالات موجود، بیان می گردد.
+در فصل سوم مدل سیستم در نظر گرفته بیان می شود و صورت مسئله به نمایش گذاشته می شود و روش های حل آن بیان می گردد.
+در فصل چهارم نتایج شبیه سازی قرار داده می شود.
+در فصل پنجم نیز نتیجه گیری و کارهای آتی مورد نظر بیان می شود.

### 2020-06-09 Latex/tehran-thesis/tex/chapter2.tex
finish chapter one

\chapter{مروری بر کارهای پیشین}

### 2020-06-21 Latex/tehran-thesis/tex/chapter2.tex
add file

@@
 \chapter{مروری بر کارهای پیشین}
+
+\section{مقدمه}
+در این فصل، به مرور کارهای گذشته می پردازیم.
+مدل سیستم مقالات مختلف را معرفی کرده و مورد بررسی قرار می دهیم و نتایج عددی آن را نیز با یکدیگر مفایسه می نماییم.
+\section{برش دینامیکی شبکه در ساختار رادیویی ابری متجانس}
+در مقاله ی \cite{lee2018dynamic}
+برش شبکه به صورت دینامیکی در بخش رادیویی مورد بررسی قرار گرفته شده است.
+چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش، تشکل و تخصیص منابع باند پایه و یک سطح پایین تر، که تخصیص منابع انجام رادیو در میان کاربران می باشد.
+\subsection{مدل سیستم}
+در این مدل فرض می کنیم که هر سرویس دارای شبکه اصلی خود (یا قطعه اصلی شبکه) است که به H-CRAN متصل می شود.
+سلول بزرگ RRH (M-RRH) و سلولهای کوچک RRHs (S-RRHs) به ترتیب از طریق پیوندهای پشتی و fronthaul به یک استخر ابر
+BBU  متصل می شوند.
+همچنین ، تقسیم C/U در مدل سیستم فرض می شود، که به موجب آن صفحات کنترل و داده از هم جدا می شوند به گونه ای که صفحات کنترل توسط M-RRH در شبکه مدیریت می شود.
+ما مشخصات LTE را دنبال می کنیم که در آن پهنای باند کانال به بلوک های منابع فیزیکی (PRBs) تقسیم می شود، هرکدام واحد منبع هستند که 180 کیلوهرتز را در دامنه فرکانس و 0.5 میلی ثانیه در دامنه زمان اشغال می کنند.
+در LTE ، حداقل دو PRB (در حوزه زمان) می توانند به یک UE اختصاص دهند زیرا تخصیص منابع در هر بازه زمانی انتقال (TTI) از
+$1ms$
+ انجام می شود.
+ در اینجا 
+ \section{ سیستمهای  \lr{MIMO C-RAN} در لینک فروسو }
+در این قسمت، سیستمهای  \lr{MIMO C-RAN} در حالت فروسو مورد بررسی قرار می گیرد.
+در حالت فروسو،  واحد کنترل، پردازش اطلاعات پیام را با عملکرد کدگذاری کانال و پیش کد گذاری \LTRfootnote{precoding} مدیریت می نماید.
+\subsection{مدل سیستم اول}
+سیگنال پیش کدگذاری شده ی باند پایه در واحد کنترل، فشرده گشته و توسط لینک ارتباطی \lr{fronthaul} که دارای ظرفیت محدود است \cite{fc2}، به واحد رادیویی منتقل می گردد.
+هر واحد رادیویی، از لینک \lr{fronthaul} سیگنالی را که دارای نویز کوانتیزاسیون است، دریافت می کند؛ سپس با اعمال \lr{pulse shaping}، سیگنال را به فرکانس بالاتر منتقل کرده و از طریق کانال بدون سیم به کاربران ارسال می نماید.
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=\linewidth, height=6cm]{./fig/dl}
+  \caption{مسیر انتقال پیام در لینک فروسو \cite{Fronthaul}.}
+  \label{fig:dl}
+\end{figure}
+بلوک دیاگرام مدل سیستم اول
+در شکل \ref{fig:dl} نشان شده است. 
+در اینجا، $N_U$ کاربر قرار دارند که توسط $N_R$ واحد رادیویی سرویس دهی می شوند.
+
+برای بدست آوردن سیگنال 
+$\tilde{\boldsymbol{x}}^{dl}$ ،
+واحد کنترل، سیگنال پیام را به صورت مجزا برای هر کاربر کدگذاری می کند.
+با  اعمال این فرآیند،  سمبلهای $\boldsymbol{s}=[s_1;...;s_{N_U}]$  بدست می آید که $s_k$ نشان دهنده ی سمبل $k$ امین کاربر می باشد.
+سیگنال پیش کدگذاری شده ی
+$\tilde{\boldsymbol{x}}^{dl} $
+که توسط واحد کنترل تولید می گردد به این صورت بیان می شود:
+\begin{equation}\label{wp}
+ \tilde{\boldsymbol{x}}^{dl} = \boldsymbol{W}\boldsymbol{P}^{\frac{1}{2}} \boldsymbol{s},
+\end{equation}
+که 
+ \begin{equation}
+\tilde{\boldsymbol{x}}^{dl} = [\tilde{x}_{1}^{dl}; ... ; \tilde{x}_{N_R}^{dl}] 
+ \end{equation}
+ در رابطه ی  \eqref{wp}، $\boldsymbol{W}$، ماتریس پیش کدگذاری شده با ابعاد $N_R \times N_U$ می باشد و $\boldsymbol{W} = [\boldsymbol{w_1},..., \boldsymbol{w_{N_{U}}}]$ است. علاوه بر این، 
+ $\boldsymbol{P}^{\frac{1}{2}} = diag(\sqrt{p_1},...,\sqrt{p_{N_U}})$ 
+ ماتریس توان است.
+حال سیگنال فشرده شده ی دریافتی توسط واحد رادیویی به صورت زیر بدست می آید:
+\begin{equation}
+\label{eq_pow1}
+ {\boldsymbol{x}}^{dl} = \tilde{\boldsymbol{x}}^{dl} + \boldsymbol{Q},
+\end{equation}
+که در اینجا $\boldsymbol{Q} = \left[ q_1,\ldots,q_{N_R}\right]^T$، بردار نویز کوانتیزاسیون تولید شده به دلیل فشرده سازی بعد از پیش کدگذاری در واحد کنترل می باشد که دارای توزیع 
+ $ \forall i  \quad  q_i\backsim \mathcal{N}(0,\sigma_{q_i^2}) $ 
+ می باشد.
+%%%%%%%%%%%%%%%%%%5
+سیگنال دریافتی توسط $j$ امین کاربر به صورت $y_j$ نمایش داده می شود.
+\begin{equation}
+{y}_j = \boldsymbol{H}_j \boldsymbol{x}^{dl}+ z_j
+\end{equation}
+ $\boldsymbol{H}_j $
+  بردار کانال کاربر $j$ام می باشد 
+  که دارای ابعاد
+ $1 \times N_R$ 
+ است. همچنین
+    $z_j$ نویز گوسی 
+ $z_j \backsim \mathcal{N}(0,1) $ می باشد.
+توان ارسالی از $i$ امین واحد رادیویی از رابطه ی زیر بدست می آید:
+\begin{equation}\label{pr}
+P_i (\boldsymbol{W},\sigma_q) = \frac{1}{T} E[{||{x_i}||}^2] = trace(\boldsymbol{w_i}\boldsymbol{P}^{\frac{1}{2}}(\boldsymbol{P}^H)^{ \frac{1}{2}}\boldsymbol{w_i}^H + \sigma_{q_i}^2 \boldsymbol{I})
+\end{equation}
+که در اینجا 
+$T=1$
+ می باشد.
+همچنین 
+$\sigma_{q_i}^2$
+واریانس نویز کوانتیزاسیون است.
+با توجه به رابطه ی \eqref{pr}
+ظرفیت لینک \lr{fronthaul} از واحد کنترل به  $i$ امین واحد رادیویی 
+از رابطه ی زیر بدست می آید:
+\begin{equation}
+C_i(\boldsymbol{W},\sigma_{q_i}) = \log det(\boldsymbol{w_i}\boldsymbol{P}^{\frac{1}{2}}(\boldsymbol{P}^H)^{ \frac{1}{2}}\boldsymbol{w_i}^H + \sigma_{q_i}^2 \boldsymbol{I}) - \log (\sigma_{q_i}^2)
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%%%%%%%%%
+برای بدست آوردن نرخ قابل دسترس $j$ امین کاربر از فرمول زیر استفاده می گردد:
+
+\begin{equation}
+\boldsymbol{R}_j (\boldsymbol{W},\boldsymbol{\sigma_q})=I(s_j;y_j) 
+\end{equation}
+که در اینجا 
+$I$
+همان اطلاعات متقابل است.
+
+ در این تحقیقات، مجموع نرخ های قابل دسترس براساس محدودیت ظرفیت لینک \lr{fronthaul} و محدودیت توان هر واحد رادیویی، بیشینه می گردد:
+\begin{equation}
+\begin{aligned}
+\max\limits_{\boldsymbol{W},\boldsymbol{\sigma_q}}   \quad &   \sum_j R_j(\boldsymbol{W},\boldsymbol{\sigma_q})\\
+\text{\lr{subject to}} \quad  & \bar{P}_i(\boldsymbol{W}, \sigma_q) \leq P_{max} \ \  \forall i \\
+&C_i(\boldsymbol{W},\sigma_q)\leq C^{th}  \ \ \forall i \\
+\end{aligned}
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+در اینجا می خواهیم مجموع نرخ ها با محدودیت بیان شده را بیشینه کنیم.
+برای حل این مسائل از الگوریتم تکرار شونده و ضرایب لاگرانژ که در فصل بعدی ارائه می گردد، استفاده می شود \cite{ul_dl,ulSimeone, Fronthaul, precodSimeone}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{مدل سیستم دوم}
+در این بخش، مدل سیستم دومی را برای ساختار \lr{MIMO C-RAN} بررسی می کنیم.
+
+فرض بر این است که کاربران و \lr{RRH}ها، به 
+ $S$
+ تا خوشه تقسیم شده اند که $v$ امین خوشه،
+ دارای $R_v$ تا \lr{RRH} است که ${D}_v$ تا کاربر را سرویس دهی می کنند.
+همچنین  $r_{(s,n)}$
+ نشان دهنده ی $n$ امین واحد رادیویی در $s$ امین خوشه می باشد  و به همین صورت $d_{(s,k)}$
+ نشان دهنده ی $k$ امین کاربر در $s$ امین خوشه است.
+
+ \begin{figure}[H]
+  \centering
+    \includegraphics[scale=1]{./fig/mimoCRAN}
+  \caption{ساختار \lr{MIMO C-RAN} \cite{EEcluster}.}
+  \label{fig:mimoC-RAN}
+\end{figure}
+در این قسمت، بردار سیگنال دریافتی کاربران در $s$ امین خوشه، به صورت زیر نوشته می شود:
+\begin{equation} \label{sg}
+\boldsymbol{y}_{\mathcal{D}_s} = \sum_{v=1}^S \boldsymbol{H}^H_{\mathcal{R}_v,\mathcal{D}_s}\boldsymbol{W}_{R_v, {D}_v}\boldsymbol{P}_{{D}_v}^\frac{1}{2}\boldsymbol{x}_{\mathcal{D}_v}+ \boldsymbol{z}_{\mathcal{D}_s},
+\end{equation}
+که در اینجا 
+$\boldsymbol{x}_{ \mathcal{D}_v} = [x_{ d_{(v,1)}},..., x_{ d_{(v,D_v)}}]^T \in C^{ \mathcal{D}_v \times 1} $ 
+بردار سمبل ارسالی واحد رادیویی از $t$ امین خوشه می باشد.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  $\boldsymbol{W}_{R_v, \boldsymbol{D}_v} = [\boldsymbol{w}_{ R_v,d_{(v,1)}},..., \boldsymbol{w}_{R_v, d_{(v,D_v)}}]^T \in C^{ R_v \times D_v} $ 
+  ماتریس پیش کدگذاری اعمال شده در خوشه ی $v$ ام می باشد.
+ علاوه بر این، $z_{D_s}$ نویز گوسی جمع شونده است که به صورت 
+ $\boldsymbol{z_{\mathcal{D}_s}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{D}_s})$ 
+و دارای توان $N_0$
+می باشد.
+همچنین $\boldsymbol{H}_{R_v,D_s}$ بردار کانال از واحدهای رادیویی دسته ی $R_v$ به کاربر دسته ی $D_s$ می باشد که این بردار را می توان به صورت زیر نوشت.
+ $\boldsymbol{H}_{\mathcal{R}_v,\mathcal{D}_s}=\left[\boldsymbol{h}_{\mathcal{R}_v,d_{(s,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_v,d_{(s,\mathcal{D}_s)}}\right]^T  \in \mathbb{C}^{{R}_v\times {D}_s}$ 
+ و همین طور
+ بردار کانال از \lr{RRH} های خوشه ی  $v$ به $k$ امین کاربر در خوشه ی $s$ام  
+ $\boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}\in \mathbb{C}^{{R}_v}$
+ به صورت زیر مدل می شود
+ \begin{equation}\label{channel}
+\boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_v,d_{(s,k)}} \boldsymbol{g}_{\mathcal{R}_v,d_{(s,k)}},
+\end{equation}
+که  در اینجا $\boldsymbol{g}_{\mathcal{R}_v,d_{(s,k)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{D}_s})$ نشان دهنده ی بردار کانال محو شدگی سریع و مسطح برای کانال می باشد 
+و $\boldsymbol{\beta}_{\mathcal{R}_v,d_{(s,k)}}=\text{\lr{diag}}(a_{r_{(v,1),d_{(s,k)}}},\ldots,a_{r_{(v,\mathcal{R}_v),d_{(s,k)}}})$
+نشان دهنده ی محوشدگی  در مقیاس بزرگ می باشد. 
+%%%%%%%%%%%%%%5
+این مدل سیستم نیز شبیه به  مدل سیستم مسئله ی قبلی است با این تفاوت که در اینجا، فشرده سازی اعمال نمی گردد  $\boldsymbol{Q}_{\mathcal{R}_v} = \boldsymbol{0}$ و فرض این است که ظرفیت لینک  \lr{fronthaul} نامحدود است.
+به علاوه، در اینجا چندین خوشه باهم در نظر گرفته شده است و تداخل پیامها بین خوشه های متفاوت نیز محاسبه می شود.\newline
+حال می خواهیم توان ارسالی از هر واحد رادیوی $i$ در خوشه ی $s$ به کاربران را محاسبه نمود.
+\begin{equation}
+\bar{p}_{r_{(s,i)}} = || \boldsymbol{w}_{r_{(s,i)},D_s}\boldsymbol{P}_{{D}_s}^\frac{1}{2}  ||^2
+\end{equation} 
+که در اینجا
+$\boldsymbol{w}_{r_{(s,i)},D_s}$
+سطر $i$ ام ماتریس $\boldsymbol{W}_{R_s, {D}_s}$
+است.\newline
+در حالت کلی برای بدست آوردن بردار کانال، در لینک فراسو با ارسال پایلوت، بردار کانال بدست می آید که در اینجا فرض می شود که با اندکی خطا همراه است و به این صورت بیام می گردد.
+\begin{equation*}
+\hat{\boldsymbol{h}}_{\mathcal{R}_v,d_{(s,k)}} = \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}} + \Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}},
+\end{equation*}
+
+$\Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}$
+نشان دهنده ی بردار خطای تخمین زده شده است که دارای توزیع گوسی به صورت
+$$\Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}\backsim \mathcal{N}(0,\boldsymbol{\phi}_{\mathcal{R}_v,d_{(s,k)}}^2),$$
+است که  داریم 
+$$\boldsymbol{\phi}_{\mathcal{R}_v,d_{(s,k)}} = \text{\lr{diag}}(\phi_{r_{(v,1)},d_{(s,k)}},\ldots,\phi_{r_{(v,\mathcal{R}_v)},d_{(s,k)}}).$$
+همچنین با فرض اینکه پیش کدگذاری اعمال شده از نوع \lr{MMSE} می باشد، ماتریس پیش کدگذاری از رابطه ی داده شده بدست می آید:
+\begin{equation}
+\boldsymbol{W}_{\mathcal{R}_s,\mathcal{D}_s} = \hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}(\hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}^H \hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}+ \alpha \boldsymbol{I}_{{D}_s})^{-1},
+\end{equation} 
+ $\alpha$
+  فاکتور رگولاسیون است که در صورتی که
+  مقدارش صفر باشد، پیش کدگذاری
+از نوع  
+   \lr{ZF} 
+  خواهد بود.
+همچنین در صورتی که از پیش کدگذاری \lr{MRT} استفاده نماییم، ماتریس پیش کدگذاری از رابطه ی مقابل بدست می آید:
+\begin{equation}
+\boldsymbol{W}_{\mathcal{R}_s,\mathcal{D}_s} = \hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}
+\end{equation} 
+همچنین این ماتریس با روشهای مختلفی قابل نرمالیزه شدن است.
+حال برای فهم بیشتر، سیگنال دریافتی کاربر $d_{(s,k)}$ را نمایش می دهیم
+\begin{equation}
+\begin{split}
+y_{d_{(s,k)}} &= \boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H  \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,k)}} p_{d_{(s,k)}}^\frac{1}{2}\\
+&+ \underbrace{\sum_{\substack{l=1 \\ l\neq k}}^{{D}_s} \boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,l)}}  p_{d_{(s,l)}}^\frac{1}{2}}_{\text{(\lr{intra-cluster interference})}}\\
+&+\underbrace{\sum_{\substack{v=1 \\ v\neq s}}^{S} \sum_{l=1}^{{D}_s} \boldsymbol{h}_{\mathcal{R}_v, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{v},d_{(v,l)}} p_{d_{(v,l)}}^\frac{1}{2}}_{\text{(\lr{inter-cluster interference})}}\\
+& +z_{d_{(s,k)}}
+\end{split}
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+بنابراین مقدار \lr{SINR}  $k$امین کاربر در $s$امین خوشه به صورت زیر محاسبه می شود \cite{algamal, cover}؛
+\begin{equation}\label{5}
+\gamma_{d_{(s,k)}}= \frac{p_{d_{(s,k)}}|\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,k)}}|^2}{I_{d_{(s,k)}}+BN_0}.
+\end{equation}
+که $B$ پهنای باند کانال است و 
+$I_{d_{(s,k)}}$
+توان سیگنال تداخلی می باشد که از رابطه ی زیر بدست می آید؛
+\begin{equation}\label{6}
+\begin{split}
+I_{d_{(s,k)}} &=  \underbrace{\sum_{\substack{l=1 \\ l\neq k}}^{{D}_s} |\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,l)}}|^2  p_{d_{(s,l)}}}_{\text{(\lr{intra-cluster interference})}}\\
+&+\underbrace{\sum_{\substack{v=1 \\ v\neq s}}^{S} \sum_{l=1}^{{D}_s} |\boldsymbol{h}_{\mathcal{R}_v, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{v},d_{(v,l)}}|^2 p_{d_{(v,l)}}}_{\text{(\lr{inter-cluster interference})}}\\
+\end{split}
+\end{equation}
+
+بنابراین نرخ قابل دسترسی برای کاربر $d_{(s,k)}$ به صورت زیر محاسبه می شود؛
+\begin{equation}\label{e1}
+\mathfrak{R}_{d_{(s,k)}} = B \log_2(1+\gamma_{d_{(s,k)}}),
+\end{equation}
+بازدهی انرژی نسبت مجموع نرخ های قابل دسترس به مجموع توان ارسالی می باشد که به این صورت نمایش داده می شود:
+\begin{equation}\label{eta}
+\eta(\boldsymbol{P}) := \frac{\sum\limits_{s=1}^{S} \sum\limits_{k=1}^{{D}_s}\mathfrak{R}_{d_{(s,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{R_{total}(\boldsymbol{P})}{P_{RRH}(\boldsymbol{P})},
+\end{equation}
+حال در اینجا هدف بیشینه سازی بازدهی انرژی می باشد. در نتیجه مسئله ی بهینه سازی بدین گونه بیان می گردد:
+   \begin{equation}\label{p12}
+\begin{aligned}
+\max\limits_{\boldsymbol{P}}   \quad &   \eta(\boldsymbol{P})\\
+\text{\lr{subject to}} \quad  & \bar{p}_{d_{(s,k)}} \leq P_{max} && \qquad \forall s, \forall i,   \\
+&\mathfrak{R}_{d_{(s,k)}} \geq  \mathfrak{R}_{d_{(s,k)}}^{th} && \qquad \forall s, \forall k, \\
+&p_{d_{(s,k)}}  \geq 0                                  &&\qquad \forall s, \forall k, \\
+\end{aligned}			
+\end{equation}  
+این مسئله با استفاده از روش لاگرانژ و الگوریتم تکرار شونده بدست می آید که در فصل بعدی به طور کامل به شرح آن می پردازیم \cite{cellfree,TDD,EEcluster}.
+\subsection{مدل سیستم سوم}
+برای گسترده سازی این مسئله ، همزمان تخصیص توان و خوشه بندی باهم در نظر گرفته می شود.
+این مسئله از مدل سیستمی به صورت زیر استفاده می نماید که تفاوت اندکی با معادله ی \eqref{sg} دارد.
+سیگنال دریافتی برای $k$امین کاربر به این صورت است:
+\begin{equation} \label{sg1}
+\begin{aligned}
+y_{k} =& \sum_{c=1}^C \sum_{m=1}^M  \phi_{c,m,k}h_{m,k}w_{m,k} \sqrt{p_k x_k} \\
+&+ \sum_{c=1}^C \sum_{m=1}^M \sum_{r=1 ,r \neq k}^K  \phi_{c,m,r}h_{m,k}w_{m,r} \sqrt{p_r x_r} + n_k,
+\end{aligned}	
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+که در این معادله  $h_{m,k}$  بردار کانال بین $k$امین کاربر و $m$ امین  واحد رادیویی است.
+علاوه بر این، $w_{m,k}$ ماتریس پیش کد گذاری بین کاربر $k$و واحد رادویی $m$ است . 
+$p_k$ 
+نیز توان سمبل ارسالی و
+$x_k$
+سمبل ارسالی برای $k$امین کاربر است .
+همچنین، 
+$ \phi_{c,m,k} \in {0,1}$ 
+و زمانی که کاربر $k$ام و  $m$امین کاربر رادیویی در خوشه ی $c$ ام باشند، مقدار $\phi$ یک و در غیر این صورت صفر می باشد.
+صورت مسئله در اینجا، بیشینه سازی بازدهی انرژی با شروط بیان شده در معادله ی  مقابل می باشد.
+\begin{equation}
+\begin{aligned}
+\max\limits_{\boldsymbol{P},\boldsymbol{\phi}}   \quad &   \eta\\
+\text{\lr{subject to}} \quad  & \sum_{c=1}^C \sum_{k=1}^K  \phi_{c,m,k}|w_{m,k}|^2 p_k , \forall m,   \\
+&\mathfrak{R}_{k} \geq  \mathfrak{R}_{k}^{th} && \qquad  \forall k, \\
+&p_{k}  \geq 0                                  &&\qquad  \forall k, \\
+& \phi_{c,m,k} \in \{0,1\} \\
+ &\sum_{t=1, t \neq c}^C \sum_{m=1}^M  \phi_{c,m,k}\sum_{m=1}^M \phi_{t,m,k} \leq 0    &&\qquad    \forall m  , \forall c, \\
+  &\sum_{t=1, t \neq c}^C \sum_{k=1}^K  \phi_{c,m,k}\sum_{k=1}^K \phi_{t,m,k} \leq 0      &&\qquad      \forall m  , \forall c,\\
+  &\sum_{k=1}^K \sum_{m=1}^M  \phi_{c,m,k} \geq 1\\
+\end{aligned}	
+\end{equation}
+در اینجا، با اعمال تابع لاگرانژ بیشینه سازی بازدهی انرژی بدست می آید\cite{jointcluster,pcluster, jue}.

### 2020-06-23 Latex/tehran-thesis/tex/chapter2.tex
add chapter 2 for proposal

@@
  در اینجا
+$N$
+سرویس، $U$ کاربر و $K$  منبع فیزیکی داریم. همچنین $S$ تا RRH داریم که RRH شماره ی $0$ مربوط به M-RRH  و بقیه ی RRH ها S-RRH می باشند.
+$a_u$
+متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام در شبکه پذیرفته شده است یا نه.
+$b_{su}$
+ متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام به $s$ امین RRH متصل است یا نه.
+$w_{ksu}$
+ متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام به $s$ امین RRH متصل است و به این کاربر منبع فیزیکی $k$ ام داده شده است یا خیر.
+ همچنین توان 
+ کاربر $u$ ام که به $s$ امین RRH متصل است و به این کاربر منبع فیزیکی $k$ ام داده شده، $p_{ksu}$ می باشد.
+ علاوه براین، ظرفیت محاسباتی BBU مجازی مورد نیاز برای کاربر $u$، 
+ $c_{vB,u}$
+  می باشد.
+   همچنین فرض می کنیم که میزان منابع محاسباتی استخر BBU با ظرفیت داده کاربر به
+   $C_{cBUP}$ 
+   محدود شده است.
+   اولویت کاربران را با 
+   $\omega_u \in [0,1]$
+   نشان می دهیم.
+   اولویت سرویس ها را با 
+   $v_n \in [0,1]$
+   نشان می دهیم
+   که 
+   $\sum_n v_n =1$ 
+   می باشد.
+   در مدل سازی کانال، نسبت سیگنال به تداخل به علاوه نویز (SINR) که توسط کاربر u در RRH s در PRB
+   k
+     تجربه می شود ، بدین صورت مدل سازی شده است.
+ \begin{equation}
+ \rho_{sku} = \frac{p_{sku}g_{sku}}{P_{AWGN}+\sum_{i\in S/\{s\}}\sum_{j\in U/\{u\}}a_j b_{ij}w_{ijk}p_{ijk}g_{ijk}}.
+ \end{equation}
+ و داریم 
+ \begin{equation}
+ r_{sku} = B\log_2{(1+\rho_{sku})}.
+ \end{equation}
+ همچنین برای محدود کردن تداخل و استفاده از RRH ها و PRB ها حد بالای $I_{max,sku}$ تعریف می شود.
+ به همین صورت برای توان مصرفی RRH  ها نیز حد بالای 
+ $P_{max}$
+تعریف می گردد.
+هریک از S-RRH ها از طریق لینک 
+fronthaul
+ با ظرفیت
+ $C_{fh}$
+  به استخر BBU 
+  وصل می شوند.
+  M-RRH
+   از طریق لینک
+   backhaul
+    با ظرفیت 
+    $C_{bh}$ 
+     به استخر BBU 
+  وصل می شوند.
+  مساله ی برش شبکه در بخش رادیویی بدین صورت می باشد.
+\begin{equation}
+\begin{aligned}
+\max\limits_{a_u,b_{su},w_{sku},p_{sku},c_{vB,u}}   \quad &  \sum_{s\in S} \sum_{k\in K} \sum_{u\in U}
+v_n \omega_u a_u b_{su} w_{sku} r_{sku} \\
+\text{\lr{subject to}} \quad  & a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \geq a_u R_{min,u} , \forall u,   \\
+& a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \leq a_u c_{vB,u}  , \forall u,   \\
+& a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \leq a_u R_{max,u}  , \forall u,   \\
+& \sum_{s\in S} \sum_{k\in K} a_u b_{su} w_{sku} r_{sku} \leq P_{max,s}  , \forall s,   \\
+& \sum_{s\in S} \sum_{k\in K} a_u b_{su} w_{sku} r_{sku} \leq C_{xh,s}  , \forall s,   \\
+&\sum_{i\in S/\{s\}}\sum_{j\in U/\{u\}}a_j b_{ij}w_{ijk}p_{ijk}g_{ijk} \leq I_{max,sku}  , \forall s, \forall k, \forall u   \\
+& a_u R_{min,u} \leq a_u c_{vB,u} \leq a_u R_{max,u} , \forall u,   \\
+& \sum_{u \in U} a_u c_{vB,u} \leq C_{cBUP} \\
+& \sum_{s \in S} a_u b_{su} \leq 1 \\ 
+& \sum_{u \in U} a_u b_{su} w_{sku} \leq 1 \\ 
+&  a_u, b_{su}, w_{sku} \in \{0,1\}  \forall s, \forall k, \forall u   \\ 
+& p_{sku},c_{vB,u} \geq 0 \\
+\end{aligned}	
+\end{equation}
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=\linewidth, height=6cm]{./fig/dynamicNS}
+  \caption{روند برش شبکه\ \cite{lee2018dynamic}}
+  \label{fig:dns}
+\end{figure}
+برای حل این مسئله، می بایست مسئله را به بخش های کوچکتر تقسیم کرده و حل نماییم.
+همانطور که در شکل \eqref{fig:dns} 
+مشخص شده است ابتدا پذیرش کاربر مورد توجه قرار می گیرد و سپس کاربر به RRH متصل می شود و پس از آن ظرفیت BBU به آن تخصیص می دهد که تا این بخش از کار در سطح بالا قرار داریم و حال وارد الگوریتم سطح پایین تر می شویم که تخصیص توان و منبع فیزیکی می باشد.
+\section{برش شبکه به صورت زمان حقیقی }
+در معماری برش شبکه، هر سرویس توسط برش خاصی پذیرفته می شود. همچنین هر سرویس دارای QoS ویژه ای است که باید به آن برسد. پارامترهای QoS شامل:
+\begin{itemize}
+\item تاخیر
+\item نرخ ارسال داده
+\item نرخ بسته های منتقل نشده
+\end{itemize}  
+می باشد.
+خدمات مختلف دارای یک یا چند مورد از این QoS هستند.
+روش های مبتنی بر هوش مصنوعی برای ارائه مزایای بالقوه برای رفع مشکلات و پیچیدگی های برش ، به تکنیک های امیدوار کننده تبدیل می شوند.
+ما می توانیم از روشهای مبتنی بر هوش مصنوعی برای پیش بینی دقیق ترافیک خاص سرویس استفاده کنیم.
+
+فقط با چنین ترافیک خاص با سرویس دقیق پیش بینی شده ، برش RAN می تواند تخصیص منابع شبکه را برای تأمین خواسته های خدمات در آینده نزدیک تسهیل کند.
+مطالعات اخیر نشان می دهد که روش های مبتنی بر هوش مصنوعی ، مانند شبکه عصبی عمیق (DNN) و حافظه کوتاه مدت بلند مدت (LSTM) ، قادر به پیش بینی دقیق بار ترافیکی خاص برای سرویس هستند.
+روش های مبتنی بر هوش مصنوعی می توانند تخصیص منابع کارآمد در برش RAN را تسهیل کنند.
+یک فرایند تصمیم گیری در زمینه اختصاص منابع مبتنی بر هوش مصنوعی آنلاین ، پتانسیل دستیابی به یک پیچیدگی کم پس از یک روش آموزش آفلاین را دارد ، که به چالش پیچیدگی محاسباتی بالا در روش های بهینه سازی مبتنی بر مدل معمولی می پردازد.
+  توجه داشته باشید که روش های سنتی RL مانند یادگیری Q از مشکل ابعاد زیاد رنج می برند که فقط برای مشکلات برش RAN در شبکه های در مقیاس کوچک مناسب هستند.
+
+  روش های \lr{Deep RL } شامل شبکه های یادگیری عمیق در چارچوب RL می توانند به طور مؤثر مسائل پیچیدگی را در شبکه های در مقیاس بزرگ برطرف کنند
+  \cite{aiNS}.
+  \begin{figure}%[H]
+  \centering
+    \includegraphics[width=\linewidth]{./fig/dlNS}
+  \caption{ساختار یادگیری تقویت عمیق\cite{drl}}
+  \label{fig:drl}
+\end{figure}
+\subsection{مدل سیستم}
+در این بخش، یادگیری تقویت عمیق (DRL)\LTRfootnote{Deep Reinforcement Learning}، که به چگونگی تعامل با محیط با اقدامات جایگزین و تقویت اقدامات برای تولید پیامدهای پاداش دهنده تر می پردازد، فرض می شود که یک راه حل امیدوار کننده برای برش شبکه است\cite{drl}.
+
  \section{ سیستمهای  \lr{MIMO C-RAN} در لینک فروسو }

### 2020-06-28 NetworkSlicing/report3.tex
report 3

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\setlength{\columnsep}{11mm}
\begin{document}

\title{Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
  \author{
    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
    \vspace{-.2cm}
  }
  }

\maketitle

\begin{abstract}

\end{abstract}
\begin{IEEEkeywords}

\end{IEEEkeywords}
\section{Questions}
\begin{enumerate}
\item \textbf{Why deep Q learning is better than Q learning?}

Deep RL uses a Deep Neural Network to approximate Q(s,a). Non-Deep RL defines Q(s,a) using a tabular function.

Popular Reinforcement Learning algorithms use functions Q(s,a) or V(s) to estimate the Return (sum of discounted rewards). The function can be defined by a tabular mapping of discrete inputs and outputs. However, this is limiting for continuous states or an infinite/large number of states. A more generalized approach is necessary for large number of states.

Function approximation is used for a large state space. A popular function approximation method is Neural Networks. You can make a Deep Neural Network by adding many hidden layers.

Thus, Deep Reinforcement Learning uses Function Approximation, as opposed to tabular functions. Specifically DRL uses Deep Neural Networks to approximate Q or V (or even A).

When the environment gets complicated, the knowledge space can become huge and it no longer becomes feasible to store all (state, action) pairs. If you think about it in raw terms, even a slightly different state is still a distinct state (e.g. different position of the enemy coming through the same corridor). You could use something that can generalize the knowledge instead of storing and looking up every little distinct state.

So, what you can do is create a neural network, that e.g. predicts the reward for an input (state, action) (or pick the best action given a state, however you like to look at it)
So, what you effectively have is a NN that predicts the Q value, based on the input (state, action). This is way more tractable than storing every possible value like we did in the table above.

$Q = neural-network.predict(state, action)$
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{deepQ}
  \caption{deep Q learning structure \cite{drl}}
  \label{fig:drl}
\end{figure}
\item  \textbf{Find QoS that is required for different applications }
\begin{itemize}
\item \textbf{Bandwidth and throughput}: Bandwidth is the available capacity of connection between two terminals as the most popular term for that is (bps). Throughput slightly differs
from bandwidth as it stands for effective bandwidth that is
provided by network
\item \textbf{Delay or latency:} It specifies the time it takes for a packet
to leave source until reaching the destination. Applications
and network devices can cause delay.
\item \textbf{Jitter (delay variation):} Jitter is an interval between
subsequent packets. It is occurred by network congestion,
route alternation and etc. 
\item \textbf{Loss:} It is amount of packets out of all that are not received
at destination. The success of QOS depends on this factor.
\item \textbf{Reliability:} Some applications are sensitive to packet loss
such as real-time applications. Thus there must be some
mechanism either in application or network to minimize the
packet loss, such as forward error correction (FEC).
\end{itemize}
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{qos}
  \caption{deep Q learning structure \cite{qos}}
  \label{fig:qos}
\end{figure}
\end{enumerate}

\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}

### 2020-06-30 Latex/tehran-thesis/tex/chapter2.tex
report 3

@@
 در این فصل، به مرور کارهای گذشته می پردازیم.
-مدل سیستم مقالات مختلف را معرفی کرده و مورد بررسی قرار می دهیم و نتایج عددی آن را نیز با یکدیگر مفایسه می نماییم.
+مدل سیستم مقالات مختلف را معرفی کرده و مورد بررسی قرار می دهیم و نتایج عددی آن را نیز با یکدیگر مقایسه می نماییم.
 \section{برش دینامیکی شبکه در ساختار رادیویی ابری متجانس}
@@
 برش شبکه به صورت دینامیکی در بخش رادیویی مورد بررسی قرار گرفته شده است.
-چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش، تشکل و تخصیص منابع باند پایه و یک سطح پایین تر، که تخصیص منابع انجام رادیو در میان کاربران می باشد.
+چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش، تشکل و تخصیص منابع باند پایه و یک سطح پایین تر، که تخصیص منابع رادیو در میان کاربران می باشد.
 \subsection{مدل سیستم}

### 2020-06-30 NetworkSlicing/report3.tex
report 3

@@
 \end{figure}
+\item \textbf{Where do we use out of order delivery?}
+
+out-of-order delivery is the delivery of data packets in a different order from which they were sent.
+Out-of-order delivery can be caused by packets following multiple paths through a network, or via parallel processing paths within network equipment that are not designed to ensure that packet ordering is preserved.
+One of the functions of TCP is to prevent the out-of-order delivery of data, either by reassembling packets into order or forcing retries of out-of-order packets.
+
+Some applications running on your network are sensitive to delay.
+These applications commonly use the UDP protocol as opposed to the TCP protocol.
+The key difference between TCP and UDP as it relates to time sensitivity is that TCP will retransmit packets that are lost in transit while UDP does not.
+For a file transfer from one PC to the next, TCP should be used because if any packets are lost, malformed or arrive out of order, the TCP protocol can retransmit and reorder the packets to recreate the file on the destination PC.
+\item \textbf{ What is the best method for online learning?! Game theory vs RL vs DRL vs Deep learning?}
+
+In Reinforcement Learning (RL) it is common to imagine an underlying Markov Decision Process (MDP).
+Then the goal of RL is to learn a good policy for the MDP, which is often only partially specified.
+MDPs can have different objectives such as total, average, or discounted reward, where discounted reward is the most common assumption for RL.
+There are well-studied extensions of MDPs to two-player (i.e., game) settings.
+
+Game theory is quite involved in the context of Multi-agent Reinforcement learning (MARL).
+
+RL: A single agent is trained to solve a Markov decision problem (MDPS).
+GT: Two agents are trained to solve Games.
+A multi-agent Reinforcement learning (MARL) can be used to solve for stochastic games.
+
+If you are interested in the single-agent application of RL in deep learning, then you do not need to go for any GT course. For two or more agents you may need to know the game-theoretic techniques.
+
+So a big differences is that mostly RL is a single agent decision and GT is a multiple agent decision.
+
+Then there are minor differences related to the most common uses.
+RL uses decision through time, GT only equilibria points.
+RL considers infinite state space, GT considers finite ones.
+RL is a learning problem (you have to learn the model of the world) while GT is a planning problem (you already know your game matrix).
+Of course there are exception to all these minor differences.
+
+For instance it is easy to prove that two agents using Q-Learning in a competitive game will converge to the Nash equilibria of a game.
+%%
+The reinforcement learning techniques enable a single
+agent to learn optimal behavior through trial-and-error interactions with its environment.
+Various RL techniques have been developed which allow an agent to optimize its behavior in a wide range of circumstances.
+However, when multiple learners simultaneously apply reinforcement learning in a shared environment, the traditional
+approaches often fail.
+When, in addition to multiple agents, we assume a dynamic environment which
+requires multiple sequential decisions, the problem becomes even more complex.
+Now agents do not only have to coordinate, they also have to take into account the
+current state of their environment. This problem is further complicated by the fact
+that agents typically have only limited information about the system.
+
+Game theory is generally defined as the mathematics of conflicts and are being utilized in various fields like economy, psychology, AI, sociology etc.
+In Game theory w.r.t RL, the policy is the strategy, mapping all possible state of actions, in respect to one of the players of the game.
+The types of games in Multi-Agent RL (MARL) are:
+● Static Games : players are independent and make simultaneous decision
+● Stage Games : the rules depend on specific stages
+● Repeated Games : when a game is played in sequence
+\begin{figure}%[H]
+  \centering
+    \includegraphics[width=\linewidth]{rlfig}
+  \caption{Multiple agents acting in the same environment \cite{rl1}}
+  \label{fig:qos}
+\end{figure}
+%%
+An extension of the single agent Markov decision process (MDP) to the multi-agent
+case can be defined by Markov Games. In a Markov Game, joint actions are the
+result of multiple agents choosing an action independently.
+While in normal form games the challenges for reinforcement learners originate
+mainly from the interactions between the agents, in Markov games they face the
+additional challenge of an environment with state transitions. This means that the
+agents typically need to combine coordination methods or equilibrium solvers used
+in repeated games with MDP approaches from single-agent RL.
+\item  \textbf{Find best delay formula which is the nearest to reality (M/M/1 M/D/1 M/G/1)}
+
 \end{enumerate}

### 2020-07-05 Latex/tehran-thesis/tex/chapter2.tex
thesis chapter 2

@@
   وصل می شوند.
-  مساله ی برش شبکه در بخش رادیویی بدین صورت می باشد.
-\begin{equation}
-\begin{aligned}
-\max\limits_{a_u,b_{su},w_{sku},p_{sku},c_{vB,u}}   \quad &  \sum_{s\in S} \sum_{k\in K} \sum_{u\in U}
-v_n \omega_u a_u b_{su} w_{sku} r_{sku} \\
-\text{\lr{subject to}} \quad  & a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \geq a_u R_{min,u} , \forall u,   \\
-& a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \leq a_u c_{vB,u}  , \forall u,   \\
-& a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \leq a_u R_{max,u}  , \forall u,   \\
-& \sum_{s\in S} \sum_{k\in K} a_u b_{su} w_{sku} r_{sku} \leq P_{max,s}  , \forall s,   \\
-& \sum_{s\in S} \sum_{k\in K} a_u b_{su} w_{sku} r_{sku} \leq C_{xh,s}  , \forall s,   \\
-&\sum_{i\in S/\{s\}}\sum_{j\in U/\{u\}}a_j b_{ij}w_{ijk}p_{ijk}g_{ijk} \leq I_{max,sku}  , \forall s, \forall k, \forall u   \\
-& a_u R_{min,u} \leq a_u c_{vB,u} \leq a_u R_{max,u} , \forall u,   \\
-& \sum_{u \in U} a_u c_{vB,u} \leq C_{cBUP} \\
-& \sum_{s \in S} a_u b_{su} \leq 1 \\ 
-& \sum_{u \in U} a_u b_{su} w_{sku} \leq 1 \\ 
-&  a_u, b_{su}, w_{sku} \in \{0,1\}  \forall s, \forall k, \forall u   \\ 
-& p_{sku},c_{vB,u} \geq 0 \\
-\end{aligned}	
-\end{equation}
+  مساله ی برش شبکه در بخش رادیویی در ادامه بیان می شود.
+%\begin{equation}
+%\begin{aligned}
+%\max\limits_{a_u,b_{su},w_{sku},p_{sku},c_{vB,u}}   \quad &  \sum_{s\in S} \sum_{k\in K} \sum_{u\in U}
+%v_n \omega_u a_u b_{su} w_{sku} r_{sku} \\
+%\text{\lr{subject to}} \quad  & a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \geq a_u R_{min,u} , \forall u,   \\
+%& a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \leq a_u c_{vB,u}  , \forall u,   \\
+%& a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \leq a_u R_{max,u}  , \forall u,   \\
+%& \sum_{s\in S} \sum_{k\in K} a_u b_{su} w_{sku} r_{sku} \leq P_{max,s}  , \forall s,   \\
+%& \sum_{s\in S} \sum_{k\in K} a_u b_{su} w_{sku} r_{sku} \leq C_{xh,s}  , \forall s,   \\
+%&\sum_{i\in S/\{s\}}\sum_{j\in U/\{u\}}a_j b_{ij}w_{ijk}p_{ijk}g_{ijk} \leq I_{max,sku}  , \forall s, \forall k, \forall u   \\
+%& a_u R_{min,u} \leq a_u c_{vB,u} \leq a_u R_{max,u} , \forall u,   \\
+%& \sum_{u \in U} a_u c_{vB,u} \leq C_{cBUP} \\
+%& \sum_{s \in S} a_u b_{su} \leq 1 \\ 
+%& \sum_{u \in U} a_u b_{su} w_{sku} \leq 1 \\ 
+%&  a_u, b_{su}, w_{sku} \in \{0,1\}  \forall s, \forall k, \forall u   \\ 
+%& p_{sku},c_{vB,u} \geq 0 \\
+%\end{aligned}	
+%\end{equation}
 \begin{figure}[H]
   \centering
-    \includegraphics[width=\linewidth, height=6cm]{./fig/dynamicNS}
+    \includegraphics[scale = 0.7]{./fig/dynamicNS}
   \caption{روند برش شبکه\ \cite{lee2018dynamic}}
@@
 \end{figure}
-برای حل این مسئله، می بایست مسئله را به بخش های کوچکتر تقسیم کرده و حل نماییم.
+%برای حل این مسئله، می بایست مسئله را به بخش های کوچکتر تقسیم کرده و حل نماییم.
 همانطور که در شکل \eqref{fig:dns} 
 مشخص شده است ابتدا پذیرش کاربر مورد توجه قرار می گیرد و سپس کاربر به RRH متصل می شود و پس از آن ظرفیت BBU به آن تخصیص می دهد که تا این بخش از کار در سطح بالا قرار داریم و حال وارد الگوریتم سطح پایین تر می شویم که تخصیص توان و منبع فیزیکی می باشد.
+
+\subsubsection{سطح بالا}
+ \begin{enumerate}
+ \item بررسی پذیرش کاربر
+
+ در این بخش سعی می کنیم که تعداد کاربران پذیرفته شده در سیستم را افزایش دهیم.
+ مسئله با فرض
+  $c_{vB,u} \geq R_{min,u} $
+   بدین صورت بیان می شود
+  :
+ \begin{equation}
+ \begin{aligned}
+ \max\limits_{b_{us}}   \quad &  \sum_{s\in S}\sum_{u\in U} W_{u} a_u  \\
+\text{\lr{subject to}} \quad  & \sum_{u\in U} a_{u} R_{min,u}  \leq R_{cBUP} , \forall s,   \\
+&  a_u \in \{0,1\}  \forall u   \\ 
+ \end{aligned}	
+ \end{equation}
+ این بخش بوسیله ی روش دینامیکی حل می گردد.
+ \item تخصیص به کاربران
+
+ پس از اینکه تعدای از کاربران در شبکه پذیرفته شده و باقی از شبکه حذف شدند، حال به کاربران پذیرفته شده، RRH اختصاص داده می شود.
+ ابتدا داریم:
+  \begin{equation}
+ \rho_{wb,su} = \frac{P_{max}\hat{g}_{su}}{P_{AWGN}+\sum_{i\in S/\{s\}}P_{max,i}\hat{g}_{iu}}.
+ \end{equation}
+ حال صورت مسئله بدین صورت است که با روش حریصانه حل می شود.
+  \begin{equation}
+ \begin{aligned}
+ \max\limits_{b_{su}}   \quad &  \sum_{u\in U}\sum_{s\in S} W_{u} {b_{su}} \rho_{wb,su} \\
+\text{\lr{subject to}} \quad  & \sum_{u\in U} b_{su} R_{min,u}  \leq C_{xh,s} , \forall u,   \\
+& \sum_{s \in S}  b_{su} = 1 \\ 
+&  {b_{su}} \in \{0,1\}  \forall u  \forall s  \\ 
+ \end{aligned}	
+ \end{equation}
+ \item تخصیص ظرفیت BBU
+
+بعد از پذیرش کاربران و تخصیص RRH به آنها، در این بخش ظرفیت BBU به کاربران تخصیص داده می شود که صورت مسئله در ادامه نوشته می شود و با روش simplex حل می گردد.
+   \begin{equation}
+ \begin{aligned}
+ \max\limits_{c_{v,BU}}   \quad &  \sum_{u\in U} W_{u} {c_{v,BU}} \\
+\text{\lr{subject to}} \quad  & \sum_{u\in U_{RRH}}c_{v,BU}  \leq C_{xh,s} , \forall u,   \\
+&  R_{min,u} \leq  c_{vB,u} \leq  R_{max,u} , \forall u,   \\
+& \sum_{s \in S}  c_{vB,u} \leq C_{cBUP} \\ 
+&  c_{vB,u} \geq 0 , \forall u   \\
+ \end{aligned}	
+ \end{equation}
+ \end{enumerate}
+ \subsubsection{سطح پایین}
+ پس از حل بخش قبلی در این بخش به تخصیص توان و بلوک های منابع فیزیکی می پردازیم.
+ \begin{equation}
+\begin{aligned}
+\max\limits_{w_{sku},p_{sku}}   \quad &  \sum_{s\in S} \sum_{k\in K} \sum_{u\in U}
+v_n \omega_u  w_{sku} r_{sku} \\
+\text{\lr{subject to}} \quad  & \sum_{s\in S} \sum_{k\in K}  w_{sku} r_{sku} \geq R_{min,u} , \forall u,   \\
+& \sum_{s\in S} \sum_{k\in K}   w_{sku} r_{sku} \leq  r_{vBBU,u}  , \forall u,   \\
+& \sum_{s\in S} \sum_{k\in K} a_u b_{su} w_{sku} r_{sku} \leq P_{max,s}  , \forall s,   \\
+&\sum_{i\in S/\{s\}}\sum_{j\in U/\{u\}}w_{ijk}p_{ijk}g_{ijk} \leq I_{max,sku}  , \forall s, \forall k, \forall u_{RRH}   \\
+& \sum_{u \in U_{RRH}}  w_{sku} \leq 1 \\ 
+&   w_{sku} \in \{0,1\}  \forall s, \forall k, \forall u   \\ 
+& p_{sku} \geq 0 \\
+\end{aligned}	
+\end{equation}
+که این مسئله نیز با روش لاگرانژ حل می گردد.
 \section{برش شبکه به صورت زمان حقیقی }
@@
 \item نرخ ارسال داده
-\item نرخ بسته های منتقل نشده
+\item نرخ بسته های منتقل شده
 \end{itemize}  
@@
   \centering  
-    \includegraphics[width=\linewidth]{./fig/dlNS}
+    \includegraphics[scale = 0.7]{./fig/dlNS}
   \caption{ساختار یادگیری تقویت عمیق\cite{drl}}
@@
 در این بخش، یادگیری تقویت عمیق (DRL)\LTRfootnote{Deep Reinforcement Learning}، که به چگونگی تعامل با محیط با اقدامات جایگزین و تقویت اقدامات برای تولید پیامدهای پاداش دهنده تر می پردازد، فرض می شود که یک راه حل امیدوار کننده برای برش شبکه است\cite{drl}.
+در این بخش هدف بیشینه کردن نرخ انتقال بر روی میزان پهنای باند مصرفی و همزمان بیشینه سازی درصد بسته های رسیده شده به کاربران می باشد.
+ \begin{equation}
+\begin{aligned}
+\max\limits_{w_n}   \quad &  \alpha SE + \sum_{n\in N} \beta_n SSR_n  \\
+\text{\lr{subject to}} \quad  & \sum_{u_n\in U_n} |Q_n| = d_n    \\
+& \sum_{n\in W} w_n =1   \\
+& x_{p_{u_n}} = 
+\begin{cases}
+      1 & r_{u_n} \geq \hat{r}_n, l_{p_{u_n}} \leq \hat{l}_n\\
+      0 & \text{otherwise}
+    \end{cases}  
+\end{aligned}	
+\end{equation} 
+ که در اینجا، $\alpha$ وزن SE و $\beta_n$ وزن n امین SSR برای ایجاد برتری بین دو واحد SSR و SE می باشند.
+ در اینجا SE
+ نسبت نرخ انتقال به مجموع پهنای باند مصرفی می باشد
+ \begin{equation}
+ SE = \frac{\sum_{n\in N}\sum_{u_n\in U_n} r_{u_n}}{W}.
+ \end{equation}
+ در اینجا $w_n$ پهنای باند مصرفی n امین برش شبکه است و مجموع پهنای باند مصرفی با W نشان داده شده است.
+ همچنین $r_{u_n}$ نرخ ارسالی در برش شبکه ی n می باشد.
+ همچنین SSR درصد بسته های رسیده شده به کاربران می باشد که بدین صورت بیان می شود
+ \begin{equation}
+ SSR_n = \frac{\sum_{u_n\in U_n}\sum_{q_{u_n}\in Q_{u_n}}x_{q_{u_n}}}{\sum_{u_n\in U_n}|Q_n|}
+ \end{equation}
+ که در اینجا $|Q_n|$
+ تعداد بسته های ارسالی به کاربر $u_n$ می باشد.
+ همچنین $x_{q_{u_n}}$  اگر یک باشد بسته $q_{u_n}$ به کاربر $u_n$ رسیده است و اگر صفر باشد نرسیده است و در صورتی یک است که تاخیر $l_{q_{u_n}} \leq \hat{l}_n $
+ باشد و نرخ 
+ $r_{u_n} \geq \hat{r}_n $
+ باشد\cite{gan1, gan2}.
+ برای حل این سیستم مدل از ترکیب روش GAN
+ با روش 
+ Reinforcement learning
+  استفاده می شود.
+\section{برش شبکه با فرض سرویس های حساس به تاخیر و نرخ انتقال}
+در این دسته مقالات، سرویس ها به دو بخش تقسیم می شوند در بخش اول سرویس هایی که  نسبت به تاخیر حساسند و دسته ی دوم سرویس هایی که نسبت به نرخ انتقال حساسند.
+همچنین در برخی مقالات هر دو ویژگی برای یک سرویس مد نظر می باشد.
+در این مدل های سیستم، تاخیر با استفاده از M/M/1 در ساده ترین حالت یا برای نزدیک تر شدن به حالت حقیقی از M/D/1 نیز استفاده می شود. می توان در این مدل ها تاخیر را کمینه و نرخ انتقال را بیشینه کرده و یا 
+برای کاربران نرخ را از حد مورد نیاز بیشتر و تاخیر را کمتر از حد مورد نیاز فرض کرد\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}.
+ \begin{figure}[H]
+  \centering
+    \includegraphics[scale = 0.7]{./fig/Delay}
+  \caption{مدل پردازشی شبکه صف \cite{frdl}.}
+  \label{fig:Delay}
+\end{figure}
+همانطور که در شکل \eqref{fig:Delay}، مشخص است، در این شبکه برای هر بخش تعدادی VNF قرار دارند که پردازش ها را انجام می دهند. در مسیر لینک پایین
+بسته ها با نرخ $\alpha$ به صف های مختلف وارد شده و پس از پردازش با همدیگر ادغام شده و سپس بسته ی هر کاربر از طریق وایرلس منتقل می شوند.
+در این پردازش ها، از روش M/M/1 استفاده شده است.
 
+\section{جایگیری } 
  \section{ سیستمهای  \lr{MIMO C-RAN} در لینک فروسو }
@@
 در اینجا می خواهیم مجموع نرخ ها با محدودیت بیان شده را بیشینه کنیم.
-برای حل این مسائل از الگوریتم تکرار شونده و ضرایب لاگرانژ که در فصل بعدی ارائه می گردد، استفاده می شود \cite{ul_dl,ulSimeone, Fronthaul, precodSimeone}.
+برای حل این مسائل از الگوریتم تکرار شونده و ضرایب لاگرانژ که در فصل بعدی ارائه می گردد، استفاده می شود \cite{ul_dl,ulSimeone, Fronthaul, precodSimeone, xia2018power}.
 

### 2020-07-07 NetworkSlicing/report3.tex
ns

@@
 \item  \textbf{Find best delay formula which is the nearest to reality (M/M/1 M/D/1 M/G/1)}
+\begin{figure}%[H]
+  \centering
+    \includegraphics[width=\linewidth]{delay1}
+  \caption{ Latency contribution in E2E delay of a packet transmission \cite{delay}}
+  \label{fig:delay}
+\end{figure}
+In the LTE system, the latency can be divided into two
+major parts: (1) user plane (U-plane) latency and (2) control
+plane (C-plane) latency. The U-plane latency is measured by 
+one directional transmit time of a packet to become available
+in the IP layer between evolved UMTS terrestrial radio access
+network (E-UTRAN) edge/UE and UE/E-UTRAN node.
+On the other hand, C-plane latency can be defined as the
+transition time of a UE to switch from idle state to active
+state. At the idle state, an UE is not connected with radio
+resource control (RRC). After the RRC connection is being
+setup, the UE switches from idle state into connected state
+and then enters into active state after moving into dedicated
+mode. Since the application performance is dependent mainly
+on the U-plane latency, U-plane is the main focus of interest
+for low latency communication.
+In the U-plane, the delay of a packet transmission in a
+cellular network can be contributed by the RAN, backhaul,
+core network, and data center/Internet.
+\begin{equation}
+T = T_{Radio} + T_{Backhaul} + T_{Core} + T_{Transport}
+\end{equation}
+\begin{itemize}
+\item TRadio
 
+ is the packet transmission time between eNB and
+UEs and is mainly due to physical layer communication.
+It is contributed by eNBs, UEs and environment. It
+consists of time to transmit, processing time at eNB/UE,
+retransmissions, and propagation delay. Processing delay at the eNB involves channel coding, rate matching,
+scrambling, cyclic redundancy check (CRC) attachment,
+precoding, modulation mapper, layer mapper, resource
+element mapper, and OFDM signal generation. On the
+other hand, uplink processing at UE involves CRC attachment, code block segmentation, code block concatenation, channel coding, rate matching, data and control
+multiplexing, and channel interleaver. Propagation delay
+depends on obstacles (i.e. building, trees, hills etc.) on
+the way of propagation and the total distance traveled by
+the RF signal;
+\item TBackhaul
+
+ is the time for building connections between
+eNB and the core network (i.e. EPC). Generally, the core
+network and eNB are connected by copper wires or microwave or optical fibers. In general, microwave involves
+lower latency while optic fibers come with comparatively
+higher latency. However, spectrum limitation may curb
+the capacity of microwave ;
+\item TCore
+
+ is the processing time taken by the core network.
+It is contributed by various core network entities such
+as mobility management entity (MME), serving GPRS
+support node (SGSN), and SDN/NFV. The processing
+steps of core network includes NAS security, EPS bearer
+control, idle state mobility handling, mobility anchoring,
+UE IP address allocation, and packet filtering;
+\item TTransport
+
+ is the delay to data communication between
+the core network and Internet/cloud. Generally, distance
+between the core network and the server, bandwidth, and
+communication protocol affect this latency
+\end{itemize}
+\begin{equation}
+T_{Radio} = t_{Q} + t_{FA} + t_{tx} + t_{bsp} + t_{mpt}
+\end{equation}
+\begin{itemize}
+\item tQ is the queuing delay which depends on the number of
+users that will be multiplexed on same resources;
+\item tFA is the delay due to frame alignment which depends on
+the frame structure and duplexing modes (i.e., frequency
+division duplexing (FDD) and time division duplexing
+(TDD));
+\item ttx is the time for transmission processing, and payload
+transmission which uses at least one TTI depending on
+radio channel condition, payload size, available resources,
+transmission errors and retransmission;
+\item tbsp is the processing delay at the base station;
+\item  tmpt is the processing delay of user terminal. Both
+the base station and user terminal delay depend on the
+capabilities of base station and user terminal (i.e., UE),
+respectively.
+\end{itemize}
+Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda$.
+It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
+Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
+Each packet is processed by one of the VNFs of a slice. So, the mean delay of  slice, modeled as M/M/1 queue, is formulated as follow, respectively
+\begin{equation}
+d = \frac{1}{\mu - \alpha/{M}}
+\end{equation}
+where $1/\mu$ is the mean service time.
+Besides, $\alpha$ is the  arrival rate which is divided
+by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha/{M}$.
+In addition, $d_{tr}$ is the transmission delay on the  wireless link. The arrival data rate of wireless link
+ is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
+Moreover, it is assumed that the service time of transmission queue has
+ an exponential distribution with mean $1/(R_{{tot}})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
+the mean delay of the transmission layer is
+\begin{equation}
+ d_{tr} = \frac{1}{R_{{tot}} - \alpha};
+\end{equation}
+where, $R_{{tot}}$ is the total achievable rate of each slice that is mapped to specific service.
+Mean delay of each slice is obtained as below.
+\begin{equation}
+D_{s} = d+ d_{{tr}}
+\end{equation}
+\begin{figure}%[H]
+  \centering
+    \includegraphics[width=\linewidth]{delay}
+  \caption{ delay of a packet \cite{frdl}}
+  \label{fig:delay}
+\end{figure}
+\item \textbf{Assume a system model for the paper}
+
+Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
+ UEs that require certain service. Each slice $s \in \{1,2,...,S \}$  contains VNFs.
+There are processing layer in the  system,  represented with a VNF.
+
+Assume we have $M$ VNFs for processing data.
+Each VNF  belongs to one or more slices. So, in the $s^{th}$ slice, there are $M_{s}$ VNFs. The VNFs have the computational capacity that is  equal to $\mu$.
+
+Each VNF requires
+physical resources that contain memory, storage and CPU.
+Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
+\begin{equation}
+\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \},
+\end{equation}
+where $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, storage, and CPU, respectively.
+Moreover, the total amount of required memory, storage and CPU of all VNFs of a slice is defined as
+\begin{equation}
+\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_s}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.
+\end{equation}
+Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
+The amount of memory, storage and CPU is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$and $\tau_{C_{j}} $ for the $j^{th}$ DC, respectively
+\begin{equation*}
+\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \},
+\end{equation*}
+In this system model, the assignment of physical DC resources to VNFs is considered.
+Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is connected to the VNFs of $s^{th}$ slice or not.
+Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
+$\phi_{s,d}$. So the total power of the system for all active DCs that are connected to slices can be represented as
+\begin{equation*}
+\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
+\end{equation*}
+Also, a cost function for the placement of VNFs into DCs is defined as
+\begin{equation}\label{eqpsi}
+\textstyle  \psi_{tot} = \phi_{tot} - \nu \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s}
+\end{equation}
+where, $\nu$ is a design variable to value between the first term of \eqref{eqpsi} which is the total power consumption of physical resources and the second term that is shown the amount of admitted slices to have physical resources.
+\begin{subequations}
+\begin{alignat}{4}
+\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
+\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
+ &\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
+\end{alignat}
+\end{subequations}
 \end{enumerate}

### 2020-07-19 Latex/version2/pr.tex
ns
file

--- 2020-05-25 Latex/version1/pr.tex
@@
 In this paper, we study the problem of RAN network slicing in an ORAN system.
-We formulate the problem of wireless link scheduling, mapping the slices to the services, and mapping the physical data centers resource to slices.
+We formulate the problem of wireless link scheduling, assigning the slices to the services, and assigning the physical data centers resource to slices which is 3D-bin packing problems.
 The objective is to jointly maximize the energy efficiency and minimize power consumption of RUs and the cost of physical resources in a downlink channel.
@@
 Since the first part of sun-problem is 3D-bin packing problem which is NP-hard, we need heuristic algorithm.
-The details of the heuristic algorithm are represented in algorithm \ref{alg}.
+In \cite{3dbin}, a heuristic algorithm is defined based on sorting bins according to a measurement.
+The details of the heuristic algorithm are represented in algorithm \ref{alg}\cite{3dbin}.
 \begin{algorithm}
@@
 \end{equation}
-where, $\boldsymbol{w} = \{w_M, w_S, w_C\}$ is the weight of memory, storage and CPU.
+where, $\boldsymbol{w} = \{w_M, w_S, w_C\}$ is the weight of memory, storage and CPU\cite{3dbin}.
 Secondly, we start mapping from the most needed slices to the DC with the most physical resources (from line \ref{33} to line \ref{34} of algorithm \ref{alg3}).
@@
 (from line \ref{35} to line \ref{36} of algorithm \ref{alg3}).
-At the end, if DC with the lowest physical resources is free and can be served the slices of a DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption (line \ref{37} of algorithm \ref{alg3}).
+At the end, if DC with the lowest physical resources is free and can be served the slices of a DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption (line \ref{37} of algorithm \ref{alg3})\cite{3dbin}.
 \begin{algorithm}

### 2020-07-21 NetworkSlicing/report3.tex
add to system model
add

@@
 
-\title{Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}
+\title{Questions\vspace{-.1cm}
 }
@@
 The types of games in Multi-Agent RL (MARL) are:
-● Static Games : players are independent and make simultaneous decision
-● Stage Games : the rules depend on specific stages
-● Repeated Games : when a game is played in sequence
+Static Games : players are independent and make simultaneous decision
+
+Stage Games : the rules depend on specific stages
+
+Repeated Games : when a game is played in sequence
 \begin{figure}%[H]
@@
 Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice. So, the mean delay of  slice, modeled as M/M/1 queue, is formulated as follow, respectively
+Each packet is processed by one of the VNFs of a slice. So, the mean delay of  slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
 \begin{equation}
-d = \frac{1}{\mu - \alpha/{M}}
+\begin{split}
+d_{1} &= \frac{1}{\mu_1 - \alpha/{M_{1}}},\\
+d_{2} &= \frac{1}{\mu_2 - \alpha/{M_{2}}}.
+\end{split}
 \end{equation}
-where $1/\mu$ is the mean service time.
+where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.
 Besides, $\alpha$ is the  arrival rate which is divided
-by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha/{M}$.
+by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha/{M_{i}}$ $ i \in \{1,2\}$.
 In addition, $d_{tr}$ is the transmission delay on the  wireless link. The arrival data rate of wireless link
  is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
-Moreover, it is assumed that the service time of transmission queue has
- an exponential distribution with mean $1/(R_{{tot}})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
+Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
+ an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
 the mean delay of the transmission layer is
@@
 \begin{equation}
-D_{s} = d+ d_{{tr}}
+D_{s} = d_{s_1} + d_{s_2} + d_{{tr}}
 \end{equation}
@@
 \item \textbf{Assume a system model for the paper}
+
+\textbf{VNF placement after Network Slicing}
 
@@
 \min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
-\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
+\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d} \geq 1\times\sum_{v=1}^{V} \forall s, \\
  &\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
@@
 \end{subequations}
+\textbf{RL model}
+
+Here, we need to know agents, states, actions and rewards.
+\begin{itemize}
+    \item \textbf{Agents} are the services that have slices and each slice have set of VNFs.
+    \item \textbf{States}: We have $2^{D_c}$ states that whether each data center is on or off.
+    \item \textbf{Actions}: Each action can be defined by connecting set of VNFs of one slice to a DC.
+    \item \textbf{Rewards}: the rewards is to minimize the number of using data centers. (minimize power of data centers)
+\end{itemize}
+%%%
+In addition, in each time the deploying a new VNF on a VM needs more power.
+\begin{equation*}
+\textstyle \phi_{diff} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}[y_{s,d}(t)-y_{s,d}(t-1)]^+\phi_{s,d}^{new}.
+\end{equation*}
+%%
+Also, a cost function for the placement of VNFs into DCs is defined as
+\begin{equation}\label{eqpsi}
+\textstyle  \psi_{tot} = \phi_{tot} + \phi_{diff}
+\end{equation}
+where, $\nu$ is a design variable to value between the first term of \eqref{eqpsi} which is the total power consumption of physical resources and the second term that is shown the amount of admitted slices to have physical resources.
+\begin{subequations}
+\begin{alignat}{4}
+\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
+\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}(t) \geq 1 \forall s, \\
+ &\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
+\end{alignat}
+\end{subequations}
+\item \textbf{Network Slicing}
+
+Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
+single-antenna UEs that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
+Slices can have shared resources.
+All RUs in a slice, that are mapped to a service, transmit signals cooperatively to all the UEs in a specific service.
+Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.
+There are two processing layers one in the DU and one in the CU of ORAN system, each represented with a VNF.
+The lower layer (i.e., DU) consists of high-PHY, MAC, and RLC, and the upper layer (i.e., CU) consists of RRC, PDCP and SDAP.
+Assume we have $M_1$ VNFs in the DU layer and $M_2$ VNFs in the CU layer for processing data.
+Each VNF in both layers belongs to one or more slices.
+So, in the $s^{th}$ slice, there are $M_{s,1}$ VNFs in the DU layer and $M_{s,2}$ VNFs in the CU layer.
+The VNFs in the DU and CU layers have the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
+Also, RUs and PRBs can serve more than one slice.
+\subsection{The Achievable Rate}
+The achievable data rate for the $i^{th}$ UE in the $v^{th}$ service can be written as
+\begin{equation}\label{eq1}
+\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}}),
+\end{equation}
+where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from
+\begin{equation}\label{eq2}
+\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H |^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
+\end{equation}
+where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .
+
+\subsection{Mean Delay}
+Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
+Therefore, the mean arrival data rate of UEs mapped to the $s^{th}$ slice in the CU layer is $\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not.
+Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
+It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
+Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
+Each packet is processed by one of the VNFs of a slice. So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
+\begin{equation}
+\begin{split}
+d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},\\
+d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}.
+\end{split}
+\end{equation}
+where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.
+Besides, $\alpha_{s}$ is the  arrival rate which is divided
+by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
+In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice on the  wireless link. The arrival data rate of wireless link
+ is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
+Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
+ an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
+the mean delay of the transmission layer is
+\begin{equation}
+ d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
+\end{equation}
+where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
+Mean delay of each slice is obtained as below.
+\begin{equation}
+D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s.
+\end{equation}
+An important criterion to measure the optimality of a system is energy efficiency represented as the sum-rate to sum-power
+\begin{equation}
+\textstyle \eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_r^{{tot}}(\boldsymbol{P},\boldsymbol{A})},
+\end{equation}
+where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RUs in all slices.
+Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the total rates of all UEs applied for all types of services.
+The main problem is
+\begin{subequations}
+\begin{alignat}{4}
+\max\limits_{\boldsymbol{P}, \boldsymbol{A} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})\\
+\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
+&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
+&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\
+&D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
+& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s.
+\end{alignat}
+\label{constraints1}
+\end{subequations}
+\textbf{RL model}
+
+Here, we need to know agents, states, actions and rewards.
+\begin{itemize}
+    \item \textbf{Agents}: are the services 
+    \item \textbf{States}: set of $A$ and $P$
+    \item \textbf{Actions}: Whether service i map to slice j and choose which power.
+    \item \textbf{Rewards}: the rewards is to maximize energy efficiency subject to constraints.
+\end{itemize}
+
 \end{enumerate}
-
 \bibliographystyle{IEEEtran}

### 2020-08-25 Latex/tehran-thesis/tex/chapter2.tex
latex change

@@
 مدل سیستم مقالات مختلف را معرفی کرده و مورد بررسی قرار می دهیم و نتایج عددی آن را نیز با یکدیگر مقایسه می نماییم.
-\section{برش دینامیکی شبکه در ساختار رادیویی ابری متجانس}
+\section{مقدمه ای بر شبکه های دسترسی رادیویی ابری}
 در مقاله ی \cite{lee2018dynamic}
@@
 چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش، تشکل و تخصیص منابع باند پایه و یک سطح پایین تر، که تخصیص منابع رادیو در میان کاربران می باشد.
-\subsection{مدل سیستم}
-در این مدل فرض می کنیم که هر سرویس دارای شبکه اصلی خود (یا قطعه اصلی شبکه) است که به H-CRAN متصل می شود.
+در این مدل فرض شده که هر سرویس دارای شبکه اصلی خود (یا قطعه اصلی شبکه) است که به H-CRAN متصل می شود.
 سلول بزرگ RRH (M-RRH) و سلولهای کوچک RRHs (S-RRHs) به ترتیب از طریق پیوندهای پشتی و fronthaul به یک استخر ابر
@@
  انجام می شود.
- در اینجا
-$N$
-سرویس، $U$ کاربر و $K$  منبع فیزیکی داریم. همچنین $S$ تا RRH داریم که RRH شماره ی $0$ مربوط به M-RRH  و بقیه ی RRH ها S-RRH می باشند.
-$a_u$
-متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام در شبکه پذیرفته شده است یا نه.
-$b_{su}$
- متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام به $s$ امین RRH متصل است یا نه.
-$w_{ksu}$
- متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام به $s$ امین RRH متصل است و به این کاربر منبع فیزیکی $k$ ام داده شده است یا خیر.
- همچنین توان 
- کاربر $u$ ام که به $s$ امین RRH متصل است و به این کاربر منبع فیزیکی $k$ ام داده شده، $p_{ksu}$ می باشد.
- علاوه براین، ظرفیت محاسباتی BBU مجازی مورد نیاز برای کاربر $u$، 
- $c_{vB,u}$
-  می باشد.
-   همچنین فرض می کنیم که میزان منابع محاسباتی استخر BBU با ظرفیت داده کاربر به
-   $C_{cBUP}$ 
-   محدود شده است.
-   اولویت کاربران را با 
-   $\omega_u \in [0,1]$
-   نشان می دهیم.
-   اولویت سرویس ها را با 
-   $v_n \in [0,1]$
-   نشان می دهیم
-   که 
-   $\sum_n v_n =1$ 
-   می باشد.
-   در مدل سازی کانال، نسبت سیگنال به تداخل به علاوه نویز (SINR) که توسط کاربر u در RRH s در PRB
-   k
-     تجربه می شود ، بدین صورت مدل سازی شده است.
- \begin{equation}
- \rho_{sku} = \frac{p_{sku}g_{sku}}{P_{AWGN}+\sum_{i\in S/\{s\}}\sum_{j\in U/\{u\}}a_j b_{ij}w_{ijk}p_{ijk}g_{ijk}}.
- \end{equation}
- و داریم 
- \begin{equation}
- r_{sku} = B\log_2{(1+\rho_{sku})}.
- \end{equation}
- همچنین برای محدود کردن تداخل و استفاده از RRH ها و PRB ها حد بالای $I_{max,sku}$ تعریف می شود.
- به همین صورت برای توان مصرفی RRH  ها نیز حد بالای 
- $P_{max}$
-تعریف می گردد.
-هریک از S-RRH ها از طریق لینک 
-fronthaul
- با ظرفیت
- $C_{fh}$
-  به استخر BBU 
-  وصل می شوند.
-  M-RRH
-   از طریق لینک
-   backhaul
-    با ظرفیت 
-    $C_{bh}$ 
-     به استخر BBU 
-  وصل می شوند.
-  مساله ی برش شبکه در بخش رادیویی در ادامه بیان می شود.
+% در اینجا
+%$N$
+%سرویس، $U$ کاربر و $K$  منبع فیزیکی داریم. همچنین $S$ تا RRH داریم که RRH شماره ی $0$ مربوط به M-RRH  و بقیه ی RRH ها S-RRH می باشند.
+%$a_u$
+%متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام در شبکه پذیرفته شده است یا نه.
+%$b_{su}$
+% متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام به $s$ امین RRH متصل است یا نه.
+%$w_{ksu}$
+% متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام به $s$ امین RRH متصل است و به این کاربر منبع فیزیکی $k$ ام داده شده است یا خیر.
+% همچنین توان 
+% کاربر $u$ ام که به $s$ امین RRH متصل است و به این کاربر منبع فیزیکی $k$ ام داده شده، $p_{ksu}$ می باشد.
+% علاوه براین، ظرفیت محاسباتی BBU مجازی مورد نیاز برای کاربر $u$، 
+% $c_{vB,u}$
+%  می باشد.
+%   همچنین فرض می کنیم که میزان منابع محاسباتی استخر BBU با ظرفیت داده کاربر به
+%   $C_{cBUP}$ 
+%   محدود شده است.
+%   اولویت کاربران را با 
+%   $\omega_u \in [0,1]$
+%   نشان می دهیم.
+%   اولویت سرویس ها را با 
+%   $v_n \in [0,1]$
+%   نشان می دهیم
+%   که 
+%   $\sum_n v_n =1$ 
+%   می باشد.
+   در مدل سازی کانال، نسبت سیگنال به تداخل به علاوه نویز (SINR) که توسط کاربر 
+     تجربه می شود ، مدل سازی شده است.
+% \begin{equation}
+% \rho_{sku} = \frac{p_{sku}g_{sku}}{P_{AWGN}+\sum_{i\in S/\{s\}}\sum_{j\in U/\{u\}}a_j b_{ij}w_{ijk}p_{ijk}g_{ijk}}.
+% \end{equation}
+% و داریم 
+% \begin{equation}
+% r_{sku} = B\log_2{(1+\rho_{sku})}.
+% \end{equation}
+% همچنین برای محدود کردن تداخل و استفاده از RRH ها و PRB ها حد بالای $I_{max,sku}$ تعریف می شود.
+% به همین صورت برای توان مصرفی RRH  ها نیز حد بالای 
+% $P_{max}$
+%تعریف می گردد.
+%هریک از S-RRH ها از طریق لینک 
+%fronthaul
+% با ظرفیت
+% $C_{fh}$
+%  به استخر BBU 
+%  وصل می شوند.
+%  M-RRH
+%   از طریق لینک
+%   backhaul
+%    با ظرفیت 
+%    $C_{bh}$ 
+%     به استخر BBU 
+%  وصل می شوند.
+%  مساله ی برش شبکه در بخش رادیویی در ادامه بیان می شود.
 %\begin{equation}
@@
 همانطور که در شکل \eqref{fig:dns} 
-مشخص شده است ابتدا پذیرش کاربر مورد توجه قرار می گیرد و سپس کاربر به RRH متصل می شود و پس از آن ظرفیت BBU به آن تخصیص می دهد که تا این بخش از کار در سطح بالا قرار داریم و حال وارد الگوریتم سطح پایین تر می شویم که تخصیص توان و منبع فیزیکی می باشد.
+مشخص شده است ابتدا پذیرش کاربر مورد توجه قرار می گیرد و سپس کاربر به RRH متصل می شود و پس از آن ظرفیت BBU به آن تخصیص می دهد که تا این بخش از کار در سطح بالا قرار دارد و حال وارد الگوریتم سطح پایین تر شده که تخصیص توان و منبع فیزیکی می باشد.
 

### 2020-08-30 Latex/tehran-thesis/tex/chapter1.tex
latex change
chapter 1,2 thesis

@@
 \subsubsection{ساختار \lr{C-RAN}}
+در ادامه ساختار های شبکه دسترسی رادیویی ابری و ساختارهای بهبود یافته ی آن را معرفی می نماییم.
+\begin{itemize}
+\item \textbf{شبکه های دسترسی رادیویی ابری}
 
@@
 \end{figure}
+\item \textbf{شبکه های دسترسی رادیویی ابری نا متجانس (\lr{H-CRAN})}
+
+برای غلبه بر چالش های شبکه های \lr{C-RAN} با محدودیت های \lr{fronthaul} ، شبکه های دسترسی ابری نامتحانس (\lr{H-CRAN}) معرفی می شود\cite{ fogComputing, heterogeneous, fogEdge}.
+\begin{figure}
+  \centering
+    \includegraphics[scale = 0.8]{./fig/hc}
+  \caption{ ساختار شبکه های دسترسی ابری نامتحانس \cite{heterogeneous}  }
+  \label{fig:hc}
+\end{figure}
+
+کاربر و صفحه ی کنترلگر در چنین شبکه هایی از هم مجزا می باشند.
+که در این شبکه ها ، نودهای توان بالا   \LTRfootnote{High Power Node}\lr{HPN} ، عمدتا برای فراهم کردن پوشش بدون درز و اجرای عملکرد صفحه کنترل می باشد.
+در حالی که \lr{RRH} ها برای فراهم نمودن سرعت بالای نرخ داده برای انتقال بسته در ترافیک قرار گرفته اند.
+\lr{HPN} ها از طریق لینکهای \lr{backhaul}  به \lr{BBU Pool} متصلند ( برای هماهنگ کردن تداخل ).\newline
+ساختار این شبکه شبیه به ساختار \lr{C-RAN} می باشد .
+همانطور که در شکل \eqref{fig:hc} نشان داده شده است ، تعداد زیادی \lr{RRH} ، همراه با انرژی مصرفی کم در ساختار \lr{H-CRAN} ، با یکدیگر در \lr{BBU Pool} مرکزی ، همکاری می کنند تا گین مشترک بالایی بدست آورند.
+تنها ، فرکانس رادیویی جلو ،(\lr{RF}) و عملکردهای پردازشی  ساده ، در \lr{RRH} ، صورت می گیرد ، در حالی که پردازشهای مهم دیگر ، در \lr{BBU Pool} انجام می گیرد.
+همچنین تنها بخشی از عملکردها در لایه ی \lr{PHY} در \lr{RRH} به مشارکت می انجامد که این مدل در شکل \eqref{fig:hc} نشان داده شده است.\newline
+اگرچه ، برخلاف \lr{C-RAN} ، \lr{BBU Pool} در \lr{H-CRAN} ، به \lr{HPN} ها متصلند که این، برای کاهش تداخل متقابل بین \lr{RRH} ها و \lr{HPN} ها از طریق محاسبات ابری متمرکز بر اساس تکنیکهای پردازشی مشترک می باشد.
+همچنین ، داده و واسط کنترل ، بین \lr{BBU Pool} و \lr{HPN} های $S_1$ و $X_2$ شناخته شده اند که تعریف آنها بر اساس تعریف استاندارد \lr{3G} ایجاد شده است.\newline
+همانطور که سرویسهای صدا ، می توانند به صورت بهینه در طول مد سوییچ بسته در \lr{4G} فراهم گردند ، \lr{H-CRAN} می تواند به طور همزمان سرویس صدا و داده را پشتیبانی کند.
+سرویس صدا مرجح به اداره از طریق \lr{HPN} ها می باشد ، در حالی که ترافیک بسته ی پر داده ، بیشتر توسط \lr{RRH} اداره می گردد.
+در مقایسه با ساختار \lr{C-RAN} ،ساختار \lr{H-CRAN} ، نیازهای \lr{fronthaul} را بوسیله ی مشارکت \lr{HPN} ها برطرف می سازد.
+با توجه به حضور \lr{HPN} ها ،سیگنالهای کنترلی و سمبلهای داده در \lr{H-CRAN} جدا از هم می باشند.
+تمام کنترل کننده های سیگنال و سیستم هایی که اطلاعات را ارسال می نمایند ، توسط \lr{HPN} ها به \lr{UE} ، منتقل می گردد که منجر به سادگی در ظرفیت و در محدودیت تاخیر زمان در لینکهای \lr{fronthaul } بین \lr{RRH} ها و \lr{BBU Pool}  می گردد و منجر به صرفه جویی در مصرف انرژی می گردد.
+همچنین ، برخی از ترافیک های شدید و ناگهانی \LTRfootnote{Burst Traffic} و یا سرویس پیام همراه با مقدار داده ی کم ، می تواند به صورت بهینه توسط \lr{HPN} ها پشتیبانی گردد.
+مکانیزم کنترل بین ارتباط داشتن و نبود ارتباط ، توسط \lr{H-CRAN} پشتیبانی می گردد که منجر به حفظ کردن مقدار قابل توجهی \lr{Overhead} در رادیو بوسیله ی مکانیزم ارتباط جهت دار خالص می گردد.
+در \lr{RRH} ، تکنولوژی های مختلف انتقال در لایه ی \lr{PHY} ، قابل استفاده برای بهبود نرخ انتقال (همانند موج میلیمتری و نور مرئی) می گردد.
+در \lr{HPN}ها، \lr{MIMO}\LTRfootnote{Multiple Input Multiple Output}، یکی از راه های افزایش پوشش در بهبود ظرفیت می باشد.
+
+\item \textbf{ساختار دسترسی رادیویی مهی}
+
+برای حل کردن مشکلات \lr{H-CRAN} و \lr{C-RAN}، نیاز به معرفی ساختار جدید دیگری می باشیم که آن را \lr{F-RAN} می نامیم.
+\lr{F-RAN} تمام ویژگی های مثبت محاسبات ابری و شبکه های نامتجانس و محاسبات مهی را همزمان در بر می گیرد.
+محاسبات مهی ، اصطلاحی برای جایگزین کردن محاسبات ابری است که مقدار قابل توجهی از ذخیره سازی ، ارتباطات ، کنترل کردن ، اندازه گیری و مدیریت را در لبه ی شبکه انجام می دهد (نه در کانال و ابر مرکزی) \cite{fogComputing, fogEdge}.
+ سیستمهای \lr{F-RAN} تحولی از سیستمهای \lr{C-RAN} می باشد . برخی از ارتباطات توزیع شده و عملکردهای ذخیره سازی در منطق لایه ی مه قرار دارد. همچنین چهار نوع ارتباطات ابری تعریف شده است.
+  \begin{figure}[H]
+  \centering
+    \includegraphics[scale =0.7]{./fig/fr}
+  \caption{ مدل سیستم \lr{F-RAN} \cite{fogComputing} }
+  \label{fig:fr}
+\end{figure}
+ \begin{itemize}
+ \item
+ ابر ذخیره گر و ارتباطات مرکزی جامع :
+ که همانند ابر مرکزی \lr{C-RAN} می باشد
+ \item
+ ابر کنترل گر مرکزی :که برای تکمیل عملکردهای کنترلی  می باشد و در \lr{HPN} ها قرار دارد
+ \item
+ ابر ارتباطات منطقی توزیع شده که در برنامه های محاسبات مهی و ابزار های این محاسبات قرار دارد.
+ \item
+  ابر ذخیره گر منطق توزیع شده:
+  که همانند قبل در \lr{F-RAN} قرار دارد.
+ \end{itemize}
+ در این ساختار ، برای کاهش تاخیر ناشی از انتقال داده ها به ابر مرکزی ، ساختار های \lr{RRH} را دارای حافظه قرار می دهیم که برای ارتباطات محلی، به جای اینکه پردازش ها در \lr{BBU Pool} صورت بگیرد، بدون نیاز به انتقال به ابر مرکزی، درون \lr{RRH} ها انجام پذیرد.
+\end{itemize}
 \subsection{\lr{xRAN}}

### 2020-08-30 Latex/tehran-thesis/tex/chapter2.tex
chapter 2 1/2

--- 2020-06-30 Latex/tehran-thesis/tex/chapter2.tex
@@
 مدل سیستم مقالات مختلف را معرفی کرده و مورد بررسی قرار می دهیم و نتایج عددی آن را نیز با یکدیگر مقایسه می نماییم.
-\section{برش دینامیکی شبکه در ساختار رادیویی ابری متجانس}
+\section{ شبکه های دسترسی رادیویی ابری}
+شبکه های دسترسی رادیویی ابر (C-RAN) به عنوان یک چارچوب امیدوار کننده برای سیستم های ارتباط بی سیم نسل پنجم ظاهر شده اند.
+از آنجا که آنها می توانند پیچیدگی رمزگشایی، مصرف انرژی و دخالت های ناشی از افزایش تراکم تلفن همراه را کاهش دهند\cite{cranInt}.
+در ادامه در مورد برش شبکه در بخش رادیویی شبکه های دسترسی رادیویی ابری صحبت می کنیم.
+\subsection{برش شبکه در شبکه های دسترسی رادیویی ابری}
 در مقاله ی \cite{lee2018dynamic}
@@
 چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش، تشکل و تخصیص منابع باند پایه و یک سطح پایین تر، که تخصیص منابع رادیو در میان کاربران می باشد.
-\subsection{مدل سیستم}
 در این مدل فرض می کنیم که هر سرویس دارای شبکه اصلی خود (یا قطعه اصلی شبکه) است که به H-CRAN متصل می شود.
@@
 همچنین ، تقسیم C/U در مدل سیستم فرض می شود، که به موجب آن صفحات کنترل و داده از هم جدا می شوند به گونه ای که صفحات کنترل توسط M-RRH در شبکه مدیریت می شود.
-ما مشخصات LTE را دنبال می کنیم که در آن پهنای باند کانال به بلوک های منابع فیزیکی (PRBs) تقسیم می شود، هرکدام واحد منبع هستند که 180 کیلوهرتز را در دامنه فرکانس و 0.5 میلی ثانیه در دامنه زمان اشغال می کنند.
-در LTE ، حداقل دو PRB (در حوزه زمان) می توانند به یک UE اختصاص دهند زیرا تخصیص منابع در هر بازه زمانی انتقال (TTI) از
-$1ms$
- انجام می شود.
- در اینجا
-$N$
-سرویس، $U$ کاربر و $K$  منبع فیزیکی داریم. همچنین $S$ تا RRH داریم که RRH شماره ی $0$ مربوط به M-RRH  و بقیه ی RRH ها S-RRH می باشند.
-$a_u$
-متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام در شبکه پذیرفته شده است یا نه.
-$b_{su}$
- متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام به $s$ امین RRH متصل است یا نه.
-$w_{ksu}$
- متغیر باینری می باشد که نشان می دهد که کاربر $u$ ام به $s$ امین RRH متصل است و به این کاربر منبع فیزیکی $k$ ام داده شده است یا خیر.
- همچنین توان 
- کاربر $u$ ام که به $s$ امین RRH متصل است و به این کاربر منبع فیزیکی $k$ ام داده شده، $p_{ksu}$ می باشد.
- علاوه براین، ظرفیت محاسباتی BBU مجازی مورد نیاز برای کاربر $u$، 
- $c_{vB,u}$
-  می باشد.
-   همچنین فرض می کنیم که میزان منابع محاسباتی استخر BBU با ظرفیت داده کاربر به
-   $C_{cBUP}$ 
-   محدود شده است.
-   اولویت کاربران را با 
-   $\omega_u \in [0,1]$
-   نشان می دهیم.
-   اولویت سرویس ها را با 
-   $v_n \in [0,1]$
-   نشان می دهیم
-   که 
-   $\sum_n v_n =1$ 
-   می باشد.
-   در مدل سازی کانال، نسبت سیگنال به تداخل به علاوه نویز (SINR) که توسط کاربر u در RRH s در PRB
-   k
-     تجربه می شود ، بدین صورت مدل سازی شده است.
- \begin{equation}
- \rho_{sku} = \frac{p_{sku}g_{sku}}{P_{AWGN}+\sum_{i\in S/\{s\}}\sum_{j\in U/\{u\}}a_j b_{ij}w_{ijk}p_{ijk}g_{ijk}}.
- \end{equation}
- و داریم 
- \begin{equation}
- r_{sku} = B\log_2{(1+\rho_{sku})}.
- \end{equation}
- همچنین برای محدود کردن تداخل و استفاده از RRH ها و PRB ها حد بالای $I_{max,sku}$ تعریف می شود.
- به همین صورت برای توان مصرفی RRH  ها نیز حد بالای 
- $P_{max}$
-تعریف می گردد.
-هریک از S-RRH ها از طریق لینک 
-fronthaul
- با ظرفیت
- $C_{fh}$
-  به استخر BBU 
-  وصل می شوند.
-  M-RRH
-   از طریق لینک
-   backhaul
-    با ظرفیت 
-    $C_{bh}$ 
-     به استخر BBU 
-  وصل می شوند.
-  مساله ی برش شبکه در بخش رادیویی بدین صورت می باشد.
-\begin{equation}
-\begin{aligned}
-\max\limits_{a_u,b_{su},w_{sku},p_{sku},c_{vB,u}}   \quad &  \sum_{s\in S} \sum_{k\in K} \sum_{u\in U}
-v_n \omega_u a_u b_{su} w_{sku} r_{sku} \\
-\text{\lr{subject to}} \quad  & a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \geq a_u R_{min,u} , \forall u,   \\
-& a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \leq a_u c_{vB,u}  , \forall u,   \\
-& a_u\sum_{s\in S} \sum_{k\in K}  b_{su} w_{sku} r_{sku} \leq a_u R_{max,u}  , \forall u,   \\
-& \sum_{s\in S} \sum_{k\in K} a_u b_{su} w_{sku} r_{sku} \leq P_{max,s}  , \forall s,   \\
-& \sum_{s\in S} \sum_{k\in K} a_u b_{su} w_{sku} r_{sku} \leq C_{xh,s}  , \forall s,   \\
-&\sum_{i\in S/\{s\}}\sum_{j\in U/\{u\}}a_j b_{ij}w_{ijk}p_{ijk}g_{ijk} \leq I_{max,sku}  , \forall s, \forall k, \forall u   \\
-& a_u R_{min,u} \leq a_u c_{vB,u} \leq a_u R_{max,u} , \forall u,   \\
-& \sum_{u \in U} a_u c_{vB,u} \leq C_{cBUP} \\
-& \sum_{s \in S} a_u b_{su} \leq 1 \\ 
-& \sum_{u \in U} a_u b_{su} w_{sku} \leq 1 \\ 
-&  a_u, b_{su}, w_{sku} \in \{0,1\}  \forall s, \forall k, \forall u   \\ 
-& p_{sku},c_{vB,u} \geq 0 \\
-\end{aligned}	
-\end{equation}
 \begin{figure}[H]
   \centering
-    \includegraphics[width=\linewidth, height=6cm]{./fig/dynamicNS}
+    \includegraphics[scale = 0.7]{./fig/dynamicNS}
   \caption{روند برش شبکه\ \cite{lee2018dynamic}}
@@
 \end{figure}
-برای حل این مسئله، می بایست مسئله را به بخش های کوچکتر تقسیم کرده و حل نماییم.
+%برای حل این مسئله، می بایست مسئله را به بخش های کوچکتر تقسیم کرده و حل نماییم.
 همانطور که در شکل \eqref{fig:dns} 
-مشخص شده است ابتدا پذیرش کاربر مورد توجه قرار می گیرد و سپس کاربر به RRH متصل می شود و پس از آن ظرفیت BBU به آن تخصیص می دهد که تا این بخش از کار در سطح بالا قرار داریم و حال وارد الگوریتم سطح پایین تر می شویم که تخصیص توان و منبع فیزیکی می باشد.
-\section{برش شبکه به صورت زمان حقیقی }
-در معماری برش شبکه، هر سرویس توسط برش خاصی پذیرفته می شود. همچنین هر سرویس دارای QoS ویژه ای است که باید به آن برسد. پارامترهای QoS شامل:
-\begin{itemize}
-\item تاخیر
-\item نرخ ارسال داده
-\item نرخ بسته های منتقل نشده
-\end{itemize}  
-می باشد.
-خدمات مختلف دارای یک یا چند مورد از این QoS هستند.
-روش های مبتنی بر هوش مصنوعی برای ارائه مزایای بالقوه برای رفع مشکلات و پیچیدگی های برش ، به تکنیک های امیدوار کننده تبدیل می شوند.
-ما می توانیم از روشهای مبتنی بر هوش مصنوعی برای پیش بینی دقیق ترافیک خاص سرویس استفاده کنیم.
+مشخص شده است ابتدا پذیرش کاربر مورد توجه قرار می گیرد و سپس کاربر به RRH متصل می شود و پس از آن ظرفیت BBU به آن تخصیص می دهد که تا این بخش از کار در سطح بالا قرار داریم.
+در سطح بالا، یک مسئله کنترل پذیرش با برنامه نویسی پویا می باشد که در آن می توان پیچیدگی را می توان تنظیم کرد.
+همچنین مسئله ی ارتباط کاربر با استفاده از یک الگوریتم حریص با پیچیدگی کم بهینه و حل می شود.
+ مسئلهی تخصیص ظرفیت BBU نیز فرموله شده و با برنامه ریزی خطی حل می شود.
+ حال وارد الگوریتم سطح پایین تر می شویم که تخصیص توان و منبع فیزیکی می باشد.
+برای مساله ی سطح پایین تر، مشکل تخصیص منابع به عنوان یک مشکل برنامه نویسی mixedinteger غیر محدب است که با استفاده از روش دوگانه لاگرانژ حل می شود.
 
-فقط با چنین ترافیک خاص با سرویس دقیق پیش بینی شده ، برش RAN می تواند تخصیص منابع شبکه را برای تأمین خواسته های خدمات در آینده نزدیک تسهیل کند.
-مطالعات اخیر نشان می دهد که روش های مبتنی بر هوش مصنوعی ، مانند شبکه عصبی عمیق (DNN) و حافظه کوتاه مدت بلند مدت (LSTM) ، قادر به پیش بینی دقیق بار ترافیکی خاص برای سرویس هستند.
-روش های مبتنی بر هوش مصنوعی می توانند تخصیص منابع کارآمد در برش RAN را تسهیل کنند.
-یک فرایند تصمیم گیری در زمینه اختصاص منابع مبتنی بر هوش مصنوعی آنلاین ، پتانسیل دستیابی به یک پیچیدگی کم پس از یک روش آموزش آفلاین را دارد ، که به چالش پیچیدگی محاسباتی بالا در روش های بهینه سازی مبتنی بر مدل معمولی می پردازد.
-  توجه داشته باشید که روش های سنتی RL مانند یادگیری Q از مشکل ابعاد زیاد رنج می برند که فقط برای مشکلات برش RAN در شبکه های در مقیاس کوچک مناسب هستند.
+در مقاله ی 
+\cite{larsen2018fronthaul,costanzo2018network}
+برش شبکه در شبکه های دسترسی رادیویی ابری متوجه قرار گرفته است. 
+در بخش fronthaul شبکه مشکلاتی از قبیل پیچیدگی شبکه و محدودیت نرخ وجود دارد که در برش شبکه، منجر به بهبود آن می شود.
+علاوه بر این ، C-RAN می تواند مجازی سازی مجموعه ای از توابع RAN را امکان پذیر کرده و راه را برای اصطلاحاً RAN مجازی باز کند. با این کار می توان چندین شبکه مجازی یا برش ایجاد کند.
 
-  روش های \lr{Deep RL } شامل شبکه های یادگیری عمیق در چارچوب RL می توانند به طور مؤثر مسائل پیچیدگی را در شبکه های در مقیاس بزرگ برطرف کنند
-  \cite{aiNS}.
-  \begin{figure}%[H]
-  \centering
-    \includegraphics[width=\linewidth]{./fig/dlNS}
-  \caption{ساختار یادگیری تقویت عمیق\cite{drl}}
-  \label{fig:drl}
-\end{figure}
-\subsection{مدل سیستم}
-در این بخش، یادگیری تقویت عمیق (DRL)\LTRfootnote{Deep Reinforcement Learning}، که به چگونگی تعامل با محیط با اقدامات جایگزین و تقویت اقدامات برای تولید پیامدهای پاداش دهنده تر می پردازد، فرض می شود که یک راه حل امیدوار کننده برای برش شبکه است\cite{drl}.
-
- \section{ سیستمهای  \lr{MIMO C-RAN} در لینک فروسو }
-در این قسمت، سیستمهای  \lr{MIMO C-RAN} در حالت فروسو مورد بررسی قرار می گیرد.
-در حالت فروسو،  واحد کنترل، پردازش اطلاعات پیام را با عملکرد کدگذاری کانال و پیش کد گذاری \LTRfootnote{precoding} مدیریت می نماید.
-\subsection{مدل سیستم اول}
-سیگنال پیش کدگذاری شده ی باند پایه در واحد کنترل، فشرده گشته و توسط لینک ارتباطی \lr{fronthaul} که دارای ظرفیت محدود است \cite{fc2}، به واحد رادیویی منتقل می گردد.
-هر واحد رادیویی، از لینک \lr{fronthaul} سیگنالی را که دارای نویز کوانتیزاسیون است، دریافت می کند؛ سپس با اعمال \lr{pulse shaping}، سیگنال را به فرکانس بالاتر منتقل کرده و از طریق کانال بدون سیم به کاربران ارسال می نماید.
-\begin{figure}[H]
-  \centering
-    \includegraphics[width=\linewidth, height=6cm]{./fig/dl}
-  \caption{مسیر انتقال پیام در لینک فروسو \cite{Fronthaul}.}
-  \label{fig:dl}
-\end{figure}
-بلوک دیاگرام مدل سیستم اول
-در شکل \ref{fig:dl} نشان شده است. 
-در اینجا، $N_U$ کاربر قرار دارند که توسط $N_R$ واحد رادیویی سرویس دهی می شوند.
-
-برای بدست آوردن سیگنال 
-$\tilde{\boldsymbol{x}}^{dl}$ ،
-واحد کنترل، سیگنال پیام را به صورت مجزا برای هر کاربر کدگذاری می کند.
-با  اعمال این فرآیند،  سمبلهای $\boldsymbol{s}=[s_1;...;s_{N_U}]$  بدست می آید که $s_k$ نشان دهنده ی سمبل $k$ امین کاربر می باشد.
-سیگنال پیش کدگذاری شده ی
-$\tilde{\boldsymbol{x}}^{dl} $
-که توسط واحد کنترل تولید می گردد به این صورت بیان می شود:
-\begin{equation}\label{wp}
- \tilde{\boldsymbol{x}}^{dl} = \boldsymbol{W}\boldsymbol{P}^{\frac{1}{2}} \boldsymbol{s},
-\end{equation}
-که 
- \begin{equation}
-\tilde{\boldsymbol{x}}^{dl} = [\tilde{x}_{1}^{dl}; ... ; \tilde{x}_{N_R}^{dl}] 
- \end{equation}
- در رابطه ی  \eqref{wp}، $\boldsymbol{W}$، ماتریس پیش کدگذاری شده با ابعاد $N_R \times N_U$ می باشد و $\boldsymbol{W} = [\boldsymbol{w_1},..., \boldsymbol{w_{N_{U}}}]$ است. علاوه بر این، 
- $\boldsymbol{P}^{\frac{1}{2}} = diag(\sqrt{p_1},...,\sqrt{p_{N_U}})$ 
- ماتریس توان است.
-حال سیگنال فشرده شده ی دریافتی توسط واحد رادیویی به صورت زیر بدست می آید:
-\begin{equation}
-\label{eq_pow1}
- {\boldsymbol{x}}^{dl} = \tilde{\boldsymbol{x}}^{dl} + \boldsymbol{Q},
-\end{equation}
-که در اینجا $\boldsymbol{Q} = \left[ q_1,\ldots,q_{N_R}\right]^T$، بردار نویز کوانتیزاسیون تولید شده به دلیل فشرده سازی بعد از پیش کدگذاری در واحد کنترل می باشد که دارای توزیع 
- $ \forall i  \quad  q_i\backsim \mathcal{N}(0,\sigma_{q_i^2}) $ 
- می باشد.
-%%%%%%%%%%%%%%%%%%5
-سیگنال دریافتی توسط $j$ امین کاربر به صورت $y_j$ نمایش داده می شود.
-\begin{equation}
-{y}_j = \boldsymbol{H}_j \boldsymbol{x}^{dl}+ z_j
-\end{equation}
- $\boldsymbol{H}_j $
-  بردار کانال کاربر $j$ام می باشد 
-  که دارای ابعاد
- $1 \times N_R$ 
- است. همچنین
-    $z_j$ نویز گوسی 
- $z_j \backsim \mathcal{N}(0,1) $ می باشد.
-توان ارسالی از $i$ امین واحد رادیویی از رابطه ی زیر بدست می آید:
-\begin{equation}\label{pr}
-P_i (\boldsymbol{W},\sigma_q) = \frac{1}{T} E[{||{x_i}||}^2] = trace(\boldsymbol{w_i}\boldsymbol{P}^{\frac{1}{2}}(\boldsymbol{P}^H)^{ \frac{1}{2}}\boldsymbol{w_i}^H + \sigma_{q_i}^2 \boldsymbol{I})
-\end{equation}
-که در اینجا 
-$T=1$
- می باشد.
-همچنین 
-$\sigma_{q_i}^2$
-واریانس نویز کوانتیزاسیون است.
-با توجه به رابطه ی \eqref{pr}
-ظرفیت لینک \lr{fronthaul} از واحد کنترل به  $i$ امین واحد رادیویی 
-از رابطه ی زیر بدست می آید:
-\begin{equation}
-C_i(\boldsymbol{W},\sigma_{q_i}) = \log det(\boldsymbol{w_i}\boldsymbol{P}^{\frac{1}{2}}(\boldsymbol{P}^H)^{ \frac{1}{2}}\boldsymbol{w_i}^H + \sigma_{q_i}^2 \boldsymbol{I}) - \log (\sigma_{q_i}^2)
-\end{equation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%%%%%%%%%
-برای بدست آوردن نرخ قابل دسترس $j$ امین کاربر از فرمول زیر استفاده می گردد:
-
-\begin{equation}
-\boldsymbol{R}_j (\boldsymbol{W},\boldsymbol{\sigma_q})=I(s_j;y_j) 
-\end{equation}
-که در اینجا 
-$I$
-همان اطلاعات متقابل است.
-
- در این تحقیقات، مجموع نرخ های قابل دسترس براساس محدودیت ظرفیت لینک \lr{fronthaul} و محدودیت توان هر واحد رادیویی، بیشینه می گردد:
-\begin{equation}
-\begin{aligned}
-\max\limits_{\boldsymbol{W},\boldsymbol{\sigma_q}}   \quad &   \sum_j R_j(\boldsymbol{W},\boldsymbol{\sigma_q})\\
-\text{\lr{subject to}} \quad  & \bar{P}_i(\boldsymbol{W}, \sigma_q) \leq P_{max} \ \  \forall i \\
-&C_i(\boldsymbol{W},\sigma_q)\leq C^{th}  \ \ \forall i \\
-\end{aligned}
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-در اینجا می خواهیم مجموع نرخ ها با محدودیت بیان شده را بیشینه کنیم.
-برای حل این مسائل از الگوریتم تکرار شونده و ضرایب لاگرانژ که در فصل بعدی ارائه می گردد، استفاده می شود \cite{ul_dl,ulSimeone, Fronthaul, precodSimeone}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{مدل سیستم دوم}
-در این بخش، مدل سیستم دومی را برای ساختار \lr{MIMO C-RAN} بررسی می کنیم.
-
-فرض بر این است که کاربران و \lr{RRH}ها، به 
- $S$
- تا خوشه تقسیم شده اند که $v$ امین خوشه،
- دارای $R_v$ تا \lr{RRH} است که ${D}_v$ تا کاربر را سرویس دهی می کنند.
-همچنین  $r_{(s,n)}$
- نشان دهنده ی $n$ امین واحد رادیویی در $s$ امین خوشه می باشد  و به همین صورت $d_{(s,k)}$
- نشان دهنده ی $k$ امین کاربر در $s$ امین خوشه است.
-
- \begin{figure}[H]
-  \centering
-    \includegraphics[scale=1]{./fig/mimoCRAN}
-  \caption{ساختار \lr{MIMO C-RAN} \cite{EEcluster}.}
-  \label{fig:mimoC-RAN}
-\end{figure}
-در این قسمت، بردار سیگنال دریافتی کاربران در $s$ امین خوشه، به صورت زیر نوشته می شود:
-\begin{equation} \label{sg}
-\boldsymbol{y}_{\mathcal{D}_s} = \sum_{v=1}^S \boldsymbol{H}^H_{\mathcal{R}_v,\mathcal{D}_s}\boldsymbol{W}_{R_v, {D}_v}\boldsymbol{P}_{{D}_v}^\frac{1}{2}\boldsymbol{x}_{\mathcal{D}_v}+ \boldsymbol{z}_{\mathcal{D}_s},
-\end{equation}
-که در اینجا 
-$\boldsymbol{x}_{ \mathcal{D}_v} = [x_{ d_{(v,1)}},..., x_{ d_{(v,D_v)}}]^T \in C^{ \mathcal{D}_v \times 1} $ 
-بردار سمبل ارسالی واحد رادیویی از $t$ امین خوشه می باشد.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  $\boldsymbol{W}_{R_v, \boldsymbol{D}_v} = [\boldsymbol{w}_{ R_v,d_{(v,1)}},..., \boldsymbol{w}_{R_v, d_{(v,D_v)}}]^T \in C^{ R_v \times D_v} $ 
-  ماتریس پیش کدگذاری اعمال شده در خوشه ی $v$ ام می باشد.
- علاوه بر این، $z_{D_s}$ نویز گوسی جمع شونده است که به صورت 
- $\boldsymbol{z_{\mathcal{D}_s}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{D}_s})$ 
-و دارای توان $N_0$
-می باشد.
-همچنین $\boldsymbol{H}_{R_v,D_s}$ بردار کانال از واحدهای رادیویی دسته ی $R_v$ به کاربر دسته ی $D_s$ می باشد که این بردار را می توان به صورت زیر نوشت.
- $\boldsymbol{H}_{\mathcal{R}_v,\mathcal{D}_s}=\left[\boldsymbol{h}_{\mathcal{R}_v,d_{(s,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_v,d_{(s,\mathcal{D}_s)}}\right]^T  \in \mathbb{C}^{{R}_v\times {D}_s}$ 
- و همین طور
- بردار کانال از \lr{RRH} های خوشه ی  $v$ به $k$ امین کاربر در خوشه ی $s$ام  
- $\boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}\in \mathbb{C}^{{R}_v}$
- به صورت زیر مدل می شود
- \begin{equation}\label{channel}
-\boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_v,d_{(s,k)}} \boldsymbol{g}_{\mathcal{R}_v,d_{(s,k)}},
-\end{equation}
-که  در اینجا $\boldsymbol{g}_{\mathcal{R}_v,d_{(s,k)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{D}_s})$ نشان دهنده ی بردار کانال محو شدگی سریع و مسطح برای کانال می باشد 
-و $\boldsymbol{\beta}_{\mathcal{R}_v,d_{(s,k)}}=\text{\lr{diag}}(a_{r_{(v,1),d_{(s,k)}}},\ldots,a_{r_{(v,\mathcal{R}_v),d_{(s,k)}}})$
-نشان دهنده ی محوشدگی  در مقیاس بزرگ می باشد. 
-%%%%%%%%%%%%%%5
-این مدل سیستم نیز شبیه به  مدل سیستم مسئله ی قبلی است با این تفاوت که در اینجا، فشرده سازی اعمال نمی گردد  $\boldsymbol{Q}_{\mathcal{R}_v} = \boldsymbol{0}$ و فرض این است که ظرفیت لینک  \lr{fronthaul} نامحدود است.
-به علاوه، در اینجا چندین خوشه باهم در نظر گرفته شده است و تداخل پیامها بین خوشه های متفاوت نیز محاسبه می شود.\newline
-حال می خواهیم توان ارسالی از هر واحد رادیوی $i$ در خوشه ی $s$ به کاربران را محاسبه نمود.
-\begin{equation}
-\bar{p}_{r_{(s,i)}} = || \boldsymbol{w}_{r_{(s,i)},D_s}\boldsymbol{P}_{{D}_s}^\frac{1}{2}  ||^2
-\end{equation} 
-که در اینجا
-$\boldsymbol{w}_{r_{(s,i)},D_s}$
-سطر $i$ ام ماتریس $\boldsymbol{W}_{R_s, {D}_s}$
-است.\newline
-در حالت کلی برای بدست آوردن بردار کانال، در لینک فراسو با ارسال پایلوت، بردار کانال بدست می آید که در اینجا فرض می شود که با اندکی خطا همراه است و به این صورت بیام می گردد.
-\begin{equation*}
-\hat{\boldsymbol{h}}_{\mathcal{R}_v,d_{(s,k)}} = \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}} + \Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}},
-\end{equation*}
-
-$\Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}$
-نشان دهنده ی بردار خطای تخمین زده شده است که دارای توزیع گوسی به صورت
-$$\Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}\backsim \mathcal{N}(0,\boldsymbol{\phi}_{\mathcal{R}_v,d_{(s,k)}}^2),$$
-است که  داریم 
-$$\boldsymbol{\phi}_{\mathcal{R}_v,d_{(s,k)}} = \text{\lr{diag}}(\phi_{r_{(v,1)},d_{(s,k)}},\ldots,\phi_{r_{(v,\mathcal{R}_v)},d_{(s,k)}}).$$
-همچنین با فرض اینکه پیش کدگذاری اعمال شده از نوع \lr{MMSE} می باشد، ماتریس پیش کدگذاری از رابطه ی داده شده بدست می آید:
-\begin{equation}
-\boldsymbol{W}_{\mathcal{R}_s,\mathcal{D}_s} = \hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}(\hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}^H \hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}+ \alpha \boldsymbol{I}_{{D}_s})^{-1},
-\end{equation} 
- $\alpha$
-  فاکتور رگولاسیون است که در صورتی که
-  مقدارش صفر باشد، پیش کدگذاری
-از نوع  
-   \lr{ZF} 
-  خواهد بود.
-همچنین در صورتی که از پیش کدگذاری \lr{MRT} استفاده نماییم، ماتریس پیش کدگذاری از رابطه ی مقابل بدست می آید:
-\begin{equation}
-\boldsymbol{W}_{\mathcal{R}_s,\mathcal{D}_s} = \hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}
-\end{equation} 
-همچنین این ماتریس با روشهای مختلفی قابل نرمالیزه شدن است.
-حال برای فهم بیشتر، سیگنال دریافتی کاربر $d_{(s,k)}$ را نمایش می دهیم
-\begin{equation}
-\begin{split}
-y_{d_{(s,k)}} &= \boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H  \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,k)}} p_{d_{(s,k)}}^\frac{1}{2}\\
-&+ \underbrace{\sum_{\substack{l=1 \\ l\neq k}}^{{D}_s} \boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,l)}}  p_{d_{(s,l)}}^\frac{1}{2}}_{\text{(\lr{intra-cluster interference})}}\\
-&+\underbrace{\sum_{\substack{v=1 \\ v\neq s}}^{S} \sum_{l=1}^{{D}_s} \boldsymbol{h}_{\mathcal{R}_v, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{v},d_{(v,l)}} p_{d_{(v,l)}}^\frac{1}{2}}_{\text{(\lr{inter-cluster interference})}}\\
-& +z_{d_{(s,k)}}
-\end{split}
-\end{equation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-بنابراین مقدار \lr{SINR}  $k$امین کاربر در $s$امین خوشه به صورت زیر محاسبه می شود \cite{algamal, cover}؛
-\begin{equation}\label{5}
-\gamma_{d_{(s,k)}}= \frac{p_{d_{(s,k)}}|\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,k)}}|^2}{I_{d_{(s,k)}}+BN_0}.
-\end{equation}
-که $B$ پهنای باند کانال است و 
-$I_{d_{(s,k)}}$
-توان سیگنال تداخلی می باشد که از رابطه ی زیر بدست می آید؛
-\begin{equation}\label{6}
-\begin{split}
-I_{d_{(s,k)}} &=  \underbrace{\sum_{\substack{l=1 \\ l\neq k}}^{{D}_s} |\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,l)}}|^2  p_{d_{(s,l)}}}_{\text{(\lr{intra-cluster interference})}}\\
-&+\underbrace{\sum_{\substack{v=1 \\ v\neq s}}^{S} \sum_{l=1}^{{D}_s} |\boldsymbol{h}_{\mathcal{R}_v, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{v},d_{(v,l)}}|^2 p_{d_{(v,l)}}}_{\text{(\lr{inter-cluster interference})}}\\
-\end{split}
-\end{equation}
-
-بنابراین نرخ قابل دسترسی برای کاربر $d_{(s,k)}$ به صورت زیر محاسبه می شود؛
-\begin{equation}\label{e1}
-\mathfrak{R}_{d_{(s,k)}} = B \log_2(1+\gamma_{d_{(s,k)}}),
-\end{equation}
-بازدهی انرژی نسبت مجموع نرخ های قابل دسترس به مجموع توان ارسالی می باشد که به این صورت نمایش داده می شود:
-\begin{equation}\label{eta}
-\eta(\boldsymbol{P}) := \frac{\sum\limits_{s=1}^{S} \sum\limits_{k=1}^{{D}_s}\mathfrak{R}_{d_{(s,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{R_{total}(\boldsymbol{P})}{P_{RRH}(\boldsymbol{P})},
-\end{equation}
-حال در اینجا هدف بیشینه سازی بازدهی انرژی می باشد. در نتیجه مسئله ی بهینه سازی بدین گونه بیان می گردد:
-   \begin{equation}\label{p12}
-\begin{aligned}
-\max\limits_{\boldsymbol{P}}   \quad &   \eta(\boldsymbol{P})\\
-\text{\lr{subject to}} \quad  & \bar{p}_{d_{(s,k)}} \leq P_{max} && \qquad \forall s, \forall i,   \\
-&\mathfrak{R}_{d_{(s,k)}} \geq  \mathfrak{R}_{d_{(s,k)}}^{th} && \qquad \forall s, \forall k, \\
-&p_{d_{(s,k)}}  \geq 0                                  &&\qquad \forall s, \forall k, \\
-\end{aligned}			
-\end{equation}  
-این مسئله با استفاده از روش لاگرانژ و الگوریتم تکرار شونده بدست می آید که در فصل بعدی به طور کامل به شرح آن می پردازیم \cite{cellfree,TDD,EEcluster}.
-\subsection{مدل سیستم سوم}
-برای گسترده سازی این مسئله ، همزمان تخصیص توان و خوشه بندی باهم در نظر گرفته می شود.
-این مسئله از مدل سیستمی به صورت زیر استفاده می نماید که تفاوت اندکی با معادله ی \eqref{sg} دارد.
-سیگنال دریافتی برای $k$امین کاربر به این صورت است:
-\begin{equation} \label{sg1}
-\begin{aligned}
-y_{k} =& \sum_{c=1}^C \sum_{m=1}^M  \phi_{c,m,k}h_{m,k}w_{m,k} \sqrt{p_k x_k} \\
-&+ \sum_{c=1}^C \sum_{m=1}^M \sum_{r=1 ,r \neq k}^K  \phi_{c,m,r}h_{m,k}w_{m,r} \sqrt{p_r x_r} + n_k,
-\end{aligned}	
-\end{equation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-که در این معادله  $h_{m,k}$  بردار کانال بین $k$امین کاربر و $m$ امین  واحد رادیویی است.
-علاوه بر این، $w_{m,k}$ ماتریس پیش کد گذاری بین کاربر $k$و واحد رادویی $m$ است . 
-$p_k$ 
-نیز توان سمبل ارسالی و
-$x_k$
-سمبل ارسالی برای $k$امین کاربر است .
-همچنین، 
-$ \phi_{c,m,k} \in {0,1}$ 
-و زمانی که کاربر $k$ام و  $m$امین کاربر رادیویی در خوشه ی $c$ ام باشند، مقدار $\phi$ یک و در غیر این صورت صفر می باشد.
-صورت مسئله در اینجا، بیشینه سازی بازدهی انرژی با شروط بیان شده در معادله ی  مقابل می باشد.
-\begin{equation}
-\begin{aligned}
-\max\limits_{\boldsymbol{P},\boldsymbol{\phi}}   \quad &   \eta\\
-\text{\lr{subject to}} \quad  & \sum_{c=1}^C \sum_{k=1}^K  \phi_{c,m,k}|w_{m,k}|^2 p_k , \forall m,   \\
-&\mathfrak{R}_{k} \geq  \mathfrak{R}_{k}^{th} && \qquad  \forall k, \\
-&p_{k}  \geq 0                                  &&\qquad  \forall k, \\
-& \phi_{c,m,k} \in \{0,1\} \\
- &\sum_{t=1, t \neq c}^C \sum_{m=1}^M  \phi_{c,m,k}\sum_{m=1}^M \phi_{t,m,k} \leq 0    &&\qquad    \forall m  , \forall c, \\
-  &\sum_{t=1, t \neq c}^C \sum_{k=1}^K  \phi_{c,m,k}\sum_{k=1}^K \phi_{t,m,k} \leq 0      &&\qquad      \forall m  , \forall c,\\
-  &\sum_{k=1}^K \sum_{m=1}^M  \phi_{c,m,k} \geq 1\\
-\end{aligned}	
-\end{equation}
-در اینجا، با اعمال تابع لاگرانژ بیشینه سازی بازدهی انرژی بدست می آید\cite{jointcluster,pcluster, jue}.
+در مقاله ی 
+\cite{fran}
+برش شبکه در بخش رادیویی برای ساختار مه \LTRfootnote{Fog Radio Access Network}
+ یا F-RAN
+  در نظر گرفته شده است که در آن دو نمونه برش شبکه برای هات اسپات و سناریوهای وسیله نقلیه با زیرساخت مربوط تنظیم می شود.
+به طور خاص ، چارچوب برای برش RAN به عنوان یک مشکل بهینه سازی مشترک برای مقابله با ذخیره کردن و انتخاب حالت است.
+  با توجه به خواسته های کاربران مختلف و منابع محدود، پیچیدگی مسئله بهینه سازی اصلی بسیار زیاد است و همین امر باعث می شود که رویکردهای بهینه سازی سنتی به طور مستقیم سخت باشد.
+ برای مقابله با این معضل ، یک الگوریتم یادگیری تقویت عمیق ارائه شده است ، که ایده اصلی آن این است که سرور ابر تصمیمات صحیحی را در زمینه ذخیره محتوا و انتخاب حالت برای به حداکثر رساندن عملکرد پاداش در وضعیت کانال پویا و وضعیت حافظه نهان ارائه می دهد.

### 2020-08-30 Latex/tehran-thesis/tex/chapter2.tex
thesis change1
chapter 2 1/2 111
chapter 2 continue ..

@@
 مدل سیستم مقالات مختلف را معرفی کرده و مورد بررسی قرار می دهیم و نتایج عددی آن را نیز با یکدیگر مقایسه می نماییم.
-\section{ شبکه های دسترسی رادیویی ابری}
+
+\section{برش شبکه در شبکه های دسترسی رادیویی }
+در این بخش در مورد کارهای انجام شده در زمینه ی برش شبکه در شبکه های دسترسی رادیویی صحبت می کنیم.
+\subsection{  برش شبکه در شبکه های دسترسی رادیویی ابری و متجانس و مهی}
 شبکه های دسترسی رادیویی ابر (C-RAN) به عنوان یک چارچوب امیدوار کننده برای سیستم های ارتباط بی سیم نسل پنجم ظاهر شده اند.
@@
 در ادامه در مورد برش شبکه در بخش رادیویی شبکه های دسترسی رادیویی ابری صحبت می کنیم.
-\subsection{برش شبکه در شبکه های دسترسی رادیویی ابری}
+
 در مقاله ی \cite{lee2018dynamic}
@@
  برای مقابله با این معضل ، یک الگوریتم یادگیری تقویت عمیق ارائه شده است ، که ایده اصلی آن این است که سرور ابر تصمیمات صحیحی را در زمینه ذخیره محتوا و انتخاب حالت برای به حداکثر رساندن عملکرد پاداش در وضعیت کانال پویا و وضعیت حافظه نهان ارائه می دهد.
+ \subsection{برش شبکه در شبکه های دسترسی رادیویی }
+در مقاله ی 
+\cite{ranSlice, ranSlice1}
+اجرای مفهوم برش در سطح RAN توسط اپراتور شبکه تلفن همراه (MNO) برای پاسخگویی به نیازها می باشد. همچنین مساله ی تخصیص منابع (در اینجا پهنای باند) مورد توجه قرار گرفته شد.
+
+در مقاله ی 
+\cite{ranslice2}
+برش در بخش RAN مورد توجه قرار گرفته است.
+همچنین
+در این مقاله یک برنامه تخصیص منابع پویا، با هدف به طور مشترک بهینه سازی مصرف برق و تخصیص پهنای باند در حالی که رضایت از تأخیر مربوطه برای ورود ترافیک پراکنده uRLLC و کیفیت خدمات eMBB را تا حد ممکن ارائه می دهد، پیشنهاد می کند.
+\section{شبکه های دسترسی رادیویی باز}
+در فوریه 2018 ، شبکه دسترسی رادیویی آزاد (O-RAN) با ادغام  xRAN و اتحاد C-RAN برای ایجاد سطح جدیدی از باز بودن در شبکه دسترسی رادیویی ایجاد شد که از نسل 5G و 6G پشتیبانی می کند.
+هدف اصلی O-RAN افزایش عملکرد RAN از طریق عناصر شبکه مجازی و واسط های باز است که دارای هوش در RAN است.
+صراحت و هوش دو ستون اصلی تلاشهای انجام شده توسط اتحاد O-RAN است که یک نیروی جهانی متشکل از بیش از 160 شرکت کننده از فروشندگان بزرگ ، شرکت های کوچک و متوسط ، اپراتورهای شبکه ، مبتدیان و مؤسسات دانشگاهی است
+\cite{oranpaper}
+.
+
+در مقاله ی 
+\cite{oranInt}
+ مقدمه ای در مورد مفاهیم، اصول و الزامات Open RAN  که توسط اتحاد O-RAN مشخص شده،بیان شده است.

### 2020-08-31 Latex/tehran-thesis/tex/chapter2.tex
chapter 2

@@
 در این فصل، به مرور کارهای گذشته می پردازیم.
-مدل سیستم مقالات مختلف را معرفی کرده و مورد بررسی قرار می دهیم و نتایج عددی آن را نیز با یکدیگر مقایسه می نماییم.
+در ابتدا مروری بر مقالاتی که از برش شبکه استفاده کرده اند می پردازیم.
+برش شبکه در سه بخش رادیویی، بخش هسته و هردو بخش هسته و رادیویی صورت می گیرد.
+سپس مقالاتی در زمینه ی سیر عبور از شبکه های دسترسی رادیویی به شبکه های
+\section{برش شبکه}
+در این بخش در مورد برش شبکه در بخش های مختلف صحبت می  کنیم.
+\subsection{برش شبکه در شبکه های دسترسی رادیویی }
+در این بخش در مورد کارهای انجام شده در زمینه ی برش شبکه در شبکه های دسترسی رادیویی صحبت می کنیم.
 
-\section{برش شبکه در شبکه های دسترسی رادیویی }
-در این بخش در مورد کارهای انجام شده در زمینه ی برش شبکه در شبکه های دسترسی رادیویی صحبت می کنیم.
-\subsection{  برش شبکه در شبکه های دسترسی رادیویی ابری و متجانس و مهی}
+\subsubsection{  برش شبکه در شبکه های دسترسی رادیویی ابری و متجانس و مهی}
 شبکه های دسترسی رادیویی ابر (C-RAN) به عنوان یک چارچوب امیدوار کننده برای سیستم های ارتباط بی سیم نسل پنجم ظاهر شده اند.
@@
  برای مقابله با این معضل ، یک الگوریتم یادگیری تقویت عمیق ارائه شده است ، که ایده اصلی آن این است که سرور ابر تصمیمات صحیحی را در زمینه ذخیره محتوا و انتخاب حالت برای به حداکثر رساندن عملکرد پاداش در وضعیت کانال پویا و وضعیت حافظه نهان ارائه می دهد.
- \subsection{برش شبکه در شبکه های دسترسی رادیویی }
+\subsubsection{برش شبکه در شبکه های دسترسی رادیویی }
 در مقاله ی 
@@
 در این مقاله یک برنامه تخصیص منابع پویا، با هدف به طور مشترک بهینه سازی مصرف برق و تخصیص پهنای باند در حالی که رضایت از تأخیر مربوطه برای ورود ترافیک پراکنده uRLLC و کیفیت خدمات eMBB را تا حد ممکن ارائه می دهد، پیشنهاد می کند.
-\section{شبکه های دسترسی رادیویی باز}
+
+\subsection{برش شبکه در بخش هسته  }
+برش شبکه یکی از فناوری های کلیدی است که به شبکه های 5G اجازه می دهد منابع اختصاصی به صنایع مختلف (خدمات) ارائه دهند.
+ در این بخش 
+ کارهای انجام شده در زمینه ی
+ برش شبکه در بخش هسته 
+ مورد بررسی قرار می گیرد.
+
+در مقاله ی 
+\cite{onet}
+اجرای عملی برش شبکه را پیشنهاد شده است.
+در مدل پیشنهادی ، نویسندگان فرض می کنند که در هر شکاف زمانی مشخص ، کاربران فقط می توانند یک برش شبکه واحد را درخواست کنند.
+مدل پیشنهادی بر اساس مسئله \lr{multi armed bandit} ساخته شده است و نویسندگان سه نوع  آن را برای حل جنبه های مختلف تخصیص برش شبکه معرفی کرده اند.
+آنها با استفاده از MATLAB مدل بهینه سازی را شبیه سازی کرده و نتایج را با یک الگوریتم حریص مقایسه کردند. آنها همچنین اثبات مفهوم برش شبکه را ارائه دادند.
+
+در مقاله ی
+\citep{vnf1}
+برای کاهش تأثیر حملات DDoS در احراز هویت برش ، از ایزوله کردن برش شبکه ی هسته استفاده شده و حل آن با ترکیبی از شبیه سازی و یک آزمایش عملی ارزیابی شده است.
+
+در مقاله ی
+\cite{li2019latency}
+نویسندگان یک روش تخصیص منابع (تأخیر بهینه) برای برشهای شبکه حمل و نقل 5G برای پشتیبانی از خدمات URLLC ارائه داده اند.
+آنها ویژگی های منبع شبکه و ویژگی های توپولوژی تخصیص منابع در تقسیم شبکه را معرفی کردند.
+\subsection{برش شبکه در هسته و بخش رادیویی}
+در این دسته مقالات، سرویس ها به دو بخش تقسیم می شوند در بخش اول سرویس هایی که  نسبت به تاخیر حساسند و دسته ی دوم سرویس هایی که نسبت به نرخ انتقال حساسند.
+همچنین در برخی مقالات هر دو ویژگی برای یک سرویس مد نظر می باشد.
+در این مدل های سیستم، تاخیر با استفاده از M/M/1 در ساده ترین حالت یا برای نزدیک تر شدن به حالت حقیقی از M/D/1 نیز استفاده می شود. می توان در این مدل ها تاخیر را کمینه و نرخ انتقال را بیشینه کرده و یا 
+برای کاربران نرخ را از حد مورد نیاز بیشتر و تاخیر را کمتر از حد مورد نیاز فرض کرد\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}.
+ \begin{figure}[H]
+  \centering
+    \includegraphics[scale = 0.7]{./fig/Delay}
+  \caption{مدل پردازشی شبکه صف \cite{frdl}.}
+  \label{fig:Delay}
+\end{figure}
+همانطور که در شکل \eqref{fig:Delay}، مشخص است، در این شبکه برای هر بخش تعدادی VNF قرار دارند که پردازش ها را انجام می دهند. در مسیر لینک پایین
+بسته ها با نرخ $\alpha$ به صف های مختلف وارد شده و پس از پردازش با همدیگر ادغام شده و سپس بسته ی هر کاربر از طریق وایرلس منتقل می شوند.
+در این پردازش ها، از روش M/M/1 استفاده شده است.
+در این حالات ترکیبی از برش RAN و Core به چشم می خورد.
+\section{رفتن به سمت شبکه های دسترسی رادیویی باز}
 در فوریه 2018 ، شبکه دسترسی رادیویی آزاد (O-RAN) با ادغام  xRAN و اتحاد C-RAN برای ایجاد سطح جدیدی از باز بودن در شبکه دسترسی رادیویی ایجاد شد که از نسل 5G و 6G پشتیبانی می کند.
@@
 \cite{oranInt}
- مقدمه ای در مورد مفاهیم، اصول و الزامات Open RAN  که توسط اتحاد O-RAN مشخص شده،بیان شده است.
+ مقدمه ای در مورد مفاهیم، اصول و الزامات \lr{Open RAN} که توسط اتحاد O-RAN مشخص شده، بیان شده است.
+ در این مقاله،
+ به منظور نشان دادن نقش هوش در O-RAN، طرح مدیریت منابع رادیویی هوشمندی را برای رسیدگی به ازدحام ترافیک و نشان دادن اثربخشی آن در یک مجموعه داده در دنیای واقعی پیشنهاد شده است.
+ یک معماری سطح بالا از این سناریوی استقرار که سازگار با الزامات O-RAN است نیز مورد بحث قرار گرفته است. مقاله با چالشهای کلیدی فنی و مشکلات باز برای تحقیقات و توسعه آینده به پایان می رسد.
+
+در مقاله ی
+\cite{c2o}
+تعاریف عمومی، ویژگی های اساسی و روند تحقیقاتی فعلی در شبکه های دسترسی رادیویی ابری و مشتقات آن، شبکه های دسترسی رادیویی مجازی و شبکه های دسترسی رادیویی باز ارائه شده است.
+علاوه بر این، نتایج عملی و آموزه های آموخته شده در مورد محدودیت ها و مسائل پیش بینی نشده مجازی سازی شبکه های دسترسی رادیویی را ارائه داده شده است.
+
+در مقاله ی 
+\cite{sree2019open, kawahara2019ran}
+ ساختار و مدیریت منابع رادیویی (RRM) هوشمند 
+ و همچنین نقش مدیریت لینک رادیویی (RLM) در بهینه سازی انرژی در RRM
+در نظر گرفته شده است.
+ساختار RLM در 
+زیرساخت O-RAN مورد بررسی قرار گرفته است.
+علاوه بر این، دیدگاه
+O-RAN
+ و معماری آن مورد توجه قرار گرفته است.

### 2020-09-01 Latex/tehran-thesis/tex/chapter2.tex
add latex

@@
 برش شبکه در سه بخش رادیویی، بخش هسته و هردو بخش هسته و رادیویی صورت می گیرد.
-سپس مقالاتی در زمینه ی سیر عبور از شبکه های دسترسی رادیویی به شبکه های
+سپس مقالاتی در زمینه ی سیر عبور از شبکه های دسترسی رادیویی ابری به شبکه های دسترسی رادیویی باز را بررسی می نماییم. 
 \section{برش شبکه}
-در این بخش در مورد برش شبکه در بخش های مختلف صحبت می  کنیم.
-\subsection{برش شبکه در شبکه های دسترسی رادیویی }
-در این بخش در مورد کارهای انجام شده در زمینه ی برش شبکه در شبکه های دسترسی رادیویی صحبت می کنیم.
+یک برش شبکه یک شبکه منطقی انتها به انتهای مستقل است که بر روی یک زیرساخت فیزیکی مشترک کار می کند و قادر به ارائه خدمات می باشد.
+برش شبکه قادر به سرویس دهی به خدمات مختلف می باشد.
+در این بخش در مورد برش شبکه در بخش رادیویی و هسته و هردو صحبت می نماییم.
+%\subsection{برش شبکه در شبکه های دسترسی رادیویی }
+برش RAN یکی از کلیدهای اصلی برای انعطاف پذیری سفارشات ومدیریت مجازی سازی ایستگاه پایه می باشد تا بتواند منابع رادیویی را در میان سرویس های مختلف تقسیم کرده و منجر به سازگاری اپراتورها و برطرف کردن نیاز سرویس ها گردد.
+%در ادامه مروری بر این مدل مقالات می نماییم.
+%\subsubsection{  برش شبکه در شبکه های دسترسی رادیویی ابری و متجانس و مهی}
 
-\subsubsection{  برش شبکه در شبکه های دسترسی رادیویی ابری و متجانس و مهی}
 شبکه های دسترسی رادیویی ابر (C-RAN) به عنوان یک چارچوب امیدوار کننده برای سیستم های ارتباط بی سیم نسل پنجم ظاهر شده اند.
@@
 مشخص شده است ابتدا پذیرش کاربر مورد توجه قرار می گیرد و سپس کاربر به RRH متصل می شود و پس از آن ظرفیت BBU به آن تخصیص می دهد که تا این بخش از کار در سطح بالا قرار داریم.
-در سطح بالا، یک مسئله کنترل پذیرش با برنامه نویسی پویا می باشد که در آن می توان پیچیدگی را می توان تنظیم کرد.
+در سطح بالا، یک مسئله کنترل پذیرش با برنامه نویسی پویا می باشد که در آن پیچیدگی را می توان تنظیم کرد.
 همچنین مسئله ی ارتباط کاربر با استفاده از یک الگوریتم حریص با پیچیدگی کم بهینه و حل می شود.
- مسئلهی تخصیص ظرفیت BBU نیز فرموله شده و با برنامه ریزی خطی حل می شود.
+ مسئله ی تخصیص ظرفیت BBU نیز فرموله شده و با برنامه ریزی خطی حل می شود.
  حال وارد الگوریتم سطح پایین تر می شویم که تخصیص توان و منبع فیزیکی می باشد.
-برای مساله ی سطح پایین تر، مشکل تخصیص منابع به عنوان یک مشکل برنامه نویسی mixedinteger غیر محدب است که با استفاده از روش دوگانه لاگرانژ حل می شود.
+برای مساله ی سطح پایین تر، مشکل تخصیص منابع به عنوان یک مشکل برنامه نویسی mixed-integer غیر محدب است که با استفاده از روش دوگانه لاگرانژ حل می شود.
 
@@
 در بخش fronthaul شبکه مشکلاتی از قبیل پیچیدگی شبکه و محدودیت نرخ وجود دارد که در برش شبکه، منجر به بهبود آن می شود.
-علاوه بر این ، C-RAN می تواند مجازی سازی مجموعه ای از توابع RAN را امکان پذیر کرده و راه را برای اصطلاحاً RAN مجازی باز کند. با این کار می توان چندین شبکه مجازی یا برش ایجاد کند.
+علاوه بر این ، C-RAN می تواند مجازی سازی مجموعه ای از توابع RAN را امکان پذیر کرده و راه را برای اصطلاحاً RAN مجازی باز کند. با این کار می توان چندین شبکه مجازی یا برش ایجاد کرد.
+ مقاله ی
+\cite{larsen2018fronthaul}
+نشان داده است که با استفاده از برش شبکه و برخورداری از سوییچ بسته در fronthaul
+مزایای زیادی را خواهد داشت که از جمله برخورداری از تقسیمات عملکردی مختلف خواهد بود. همچنین از معایب این کار تاخیر نسبتا اندکی خواهد بود.
 
@@
  برای مقابله با این معضل ، یک الگوریتم یادگیری تقویت عمیق ارائه شده است ، که ایده اصلی آن این است که سرور ابر تصمیمات صحیحی را در زمینه ذخیره محتوا و انتخاب حالت برای به حداکثر رساندن عملکرد پاداش در وضعیت کانال پویا و وضعیت حافظه نهان ارائه می دهد.
-\subsubsection{برش شبکه در شبکه های دسترسی رادیویی }
+%\subsubsection{برش شبکه در شبکه های دسترسی رادیویی }
+
 در مقاله ی 
@@
 اجرای مفهوم برش در سطح RAN توسط اپراتور شبکه تلفن همراه (MNO) برای پاسخگویی به نیازها می باشد. همچنین مساله ی تخصیص منابع (در اینجا پهنای باند) مورد توجه قرار گرفته شد.
+چالش های پیش رو برش RAN نیز مورد بررسی قرار گرفته است که یکی از چالش ها
+شامل طراحی و مدیریت چندین برش در زیرساخت مشترک به روشی کارآمد و در عین حال ضمانت SLA توافق شده برای هر یک از آنها است.
+این چالش ما را نیازمند مفهوم ایزولاسیون برش می کند.
 
@@
 در این مقاله یک برنامه تخصیص منابع پویا، با هدف به طور مشترک بهینه سازی مصرف برق و تخصیص پهنای باند در حالی که رضایت از تأخیر مربوطه برای ورود ترافیک پراکنده uRLLC و کیفیت خدمات eMBB را تا حد ممکن ارائه می دهد، پیشنهاد می کند.
-
-\subsection{برش شبکه در بخش هسته  }
-برش شبکه یکی از فناوری های کلیدی است که به شبکه های 5G اجازه می دهد منابع اختصاصی به صنایع مختلف (خدمات) ارائه دهند.
- در این بخش 
- کارهای انجام شده در زمینه ی
- برش شبکه در بخش هسته 
- مورد بررسی قرار می گیرد.
+طرح پیشنهادی براساس کنترل بهینه توان برای تخصیص منابع آگاه از تأخیر است.
+در نتیجه در این سیستم هدف مینیمم کردن توان با شروط برآورده شدن شروط پهنای باند و  تاخیر که با شرط صف پردازش نشان داده، می باشد.
+%\subsection{برش شبکه در بخش هسته  }
 
@@
 در مدل پیشنهادی ، نویسندگان فرض می کنند که در هر شکاف زمانی مشخص ، کاربران فقط می توانند یک برش شبکه واحد را درخواست کنند.
+در اینجا تابع هدفی بر اساس نسبت میزان منابع اختصاص داده شده به کاربرن در هر زمان t به ظرفیت کل منابع مشخص شده است و هدف بیشینه سازی آن  می باشد.  
 مدل پیشنهادی بر اساس مسئله \lr{multi armed bandit} ساخته شده است و نویسندگان سه نوع  آن را برای حل جنبه های مختلف تخصیص برش شبکه معرفی کرده اند.
@@
 
-در مقاله ی
-\citep{vnf1}
-برای کاهش تأثیر حملات DDoS در احراز هویت برش ، از ایزوله کردن برش شبکه ی هسته استفاده شده و حل آن با ترکیبی از شبیه سازی و یک آزمایش عملی ارزیابی شده است.
-
+برش شبکه یکی از فناوری های کلیدی است که به شبکه های 5G اجازه می دهد منابع اختصاصی به صنایع مختلف (خدمات) ارائه دهند.
 در مقاله ی
@@
 آنها ویژگی های منبع شبکه و ویژگی های توپولوژی تخصیص منابع در تقسیم شبکه را معرفی کردند.
-\subsection{برش شبکه در هسته و بخش رادیویی}
+
+در 
+\citep{vnf1,coreSlice}
+ایزوله کردن برش شبکه ی هسته 
+مورد توجه قرار گرفته است.
+\citep{vnf1}
+برای کاهش تأثیر حملات DDoS در احراز هویت برش ، از ایزوله کردن برش شبکه ی هسته استفاده شده و حل آن با ترکیبی از شبیه سازی و یک آزمایش عملی ارزیابی شده است.
+نویسندگان
+\citep{coreSlice}
+دو چالش مهم برش شبکه در بخش هسته مورد توجه قرار داده اند که شامل ایزوله کردن برش شبکه و تضمین میزان تاخیر انتها به انتها می باشد.
+در این مقاله، مساله ی بهینه سازی به صورت 
+\lr{mixed integer linear programming}
+ می باشد که
+ تابع هدف درخواست های برش ورودی را به سروری که کمترین میزان استفاده از آن شده است، اختصاص داده و مسیری را با حداقل تأخیر پیدا می کند. خروجی این مساله VNF ها را به سرور اختصاص می دهد.  
+%\subsection{برش شبکه در هسته و بخش رادیویی}
+
 در این دسته مقالات، سرویس ها به دو بخش تقسیم می شوند در بخش اول سرویس هایی که  نسبت به تاخیر حساسند و دسته ی دوم سرویس هایی که نسبت به نرخ انتقال حساسند.
@@
 برای کاربران نرخ را از حد مورد نیاز بیشتر و تاخیر را کمتر از حد مورد نیاز فرض کرد\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}.
- \begin{figure}[H]
+ \begin{figure}%[H]
   \centering
@@
 در این پردازش ها، از روش M/M/1 استفاده شده است.
-در این حالات ترکیبی از برش RAN و Core به چشم می خورد.
+در این مدل مقالات اشاره ی مستقیم به برش شبکه نشده است ولی
+در آنها ترکیبی از مفهوم برش RAN و Core به چشم می خورد.
 \section{رفتن به سمت شبکه های دسترسی رادیویی باز}
@@
  و معماری آن مورد توجه قرار گرفته است.
+\section{قرار دادن VNF ها}
+NFV
+ الگویي است که عملکردهای شبکه سنتی را مجازی می کند و آنها را در سخت افزارهای عمومی و ابرها در مقابل سخت افزارهای تعیین شده، قرار می دهد.
+اپراتورهای شبکه تلفن همراه عهده دار تصمیم گیری مدیریت زیرساخت است.
+این وظیفه بخشی از تنظیمات شبکه است و شامل تصمیم گیری در مورد قرار دادن VNF های مورد نیاز در سراسر زیرساخت و اختصاص CPU، حافظه و منابع ذخیره سازی به VNF ها و مسیریابی داده ها از طریق گره های شبکه
+می باشد.

### 2020-09-02 Latex/tehran-thesis/tex/chapter2.tex
add latex file

@@
 در این فصل، به مرور کارهای گذشته می پردازیم.
-در ابتدا مروری بر مقالاتی که از برش شبکه استفاده کرده اند می پردازیم.
+ابتدا صورت مسئله مقالات مختلف را بررسی می نماییم.
+در بررسی صورت مسئله به ترتیب مقالاتی که از برش شبکه استفاده کرده اند می پردازیم.
 برش شبکه در سه بخش رادیویی، بخش هسته و هردو بخش هسته و رادیویی صورت می گیرد.
-سپس مقالاتی در زمینه ی سیر عبور از شبکه های دسترسی رادیویی ابری به شبکه های دسترسی رادیویی باز را بررسی می نماییم. 
-\section{برش شبکه}
+سپس در زمینه ی سیر عبور از شبکه های دسترسی رادیویی ابری به شبکه های دسترسی رادیویی باز مطالعه نموده و در انتها درباره ی جاگیری VNF ها صحبت می کنیم.
+\section{مسائل پیش رو}
+در این بخش به مطالعه ی مسائل پیش رو می پردازیم. 
+\subsection{برش شبکه}
 یک برش شبکه یک شبکه منطقی انتها به انتهای مستقل است که بر روی یک زیرساخت فیزیکی مشترک کار می کند و قادر به ارائه خدمات می باشد.
@@
 در آنها ترکیبی از مفهوم برش RAN و Core به چشم می خورد.
-\section{رفتن به سمت شبکه های دسترسی رادیویی باز}
+\subsection{رفتن به سمت شبکه های دسترسی رادیویی باز}
 در فوریه 2018 ، شبکه دسترسی رادیویی آزاد (O-RAN) با ادغام  xRAN و اتحاد C-RAN برای ایجاد سطح جدیدی از باز بودن در شبکه دسترسی رادیویی ایجاد شد که از نسل 5G و 6G پشتیبانی می کند.
@@
  و معماری آن مورد توجه قرار گرفته است.
-\section{قرار دادن VNF ها}
+\subsection{قرار دادن VNF ها}
 NFV
  الگویي است که عملکردهای شبکه سنتی را مجازی می کند و آنها را در سخت افزارهای عمومی و ابرها در مقابل سخت افزارهای تعیین شده، قرار می دهد.
+ در واقع NFV بخش نرم افزار را از سخت افزار جدا می نماید.
+ بنابراین یک سرویس داده شده می تواند به مجموعه ای از توابع شبکه مجازی (VNF) تجزیه شود ، سپس می توان آن را در نرم افزارهایی که روی یک یا چند سرور استاندارد فیزیکی صنعت اجرا می شوند ، پیاده سازی کرد.
+
 اپراتورهای شبکه تلفن همراه عهده دار تصمیم گیری مدیریت زیرساخت است.
-این وظیفه بخشی از تنظیمات شبکه است و شامل تصمیم گیری در مورد قرار دادن VNF های مورد نیاز در سراسر زیرساخت و اختصاص CPU، حافظه و منابع ذخیره سازی به VNF ها و مسیریابی داده ها از طریق گره های شبکه
+این وظیفه بخشی از تنظیمات شبکه است و شامل تصمیم گیری در مورد قرار دادن VNF های مورد نیاز در سراسر زیرساخت و اختصاص پردازنده، حافظه و منابع ذخیره سازی به VNF ها و مسیریابی داده ها از طریق گره های شبکه
 می باشد.
+
+به لطف برش شبکه، شبکه های 5G از انواع خدمات به روشی انعطاف پذیر و سریع پشتیبانی می کنند.
+در این زمینه ، ما به دنبال تصمیم گیری بهینه و با کیفیت بالا در مورد قرار دادن VNF در میان میزبانهای فیزیکی برای تحقق بخشیدن به خدمات هستیم.
+
+در مقالات
+\cite{wang2016online,jia2018online,luo2020online}
+هدف یافتن تعداد بهینه ی VNF ها در یک زنجیره ی سرویس و قرار گیری VNF های مورد نظر بر روی سرور در هر بازه ی زمانی می باشد تا بتوان میزان هزینه را در سیستم به حداقل رساند.
+در این مقالات هدف کمینه کردن انرژی های مصرفی در هر بازه ی زمانی می باشد که شامل هزینه ی انرژی مصرفی هر VNF مستقر بر روی سرور در حال کار و هزینه ی استقرار VNF های جدید در هر لحظه ی زمانی می باشد.
+همچنین مجموع منابع مصرفی VNF های مستقر بر روی هر سرور در هر لحظه می بایست از منابع آن سرور کمتر باشد تا مساله عملی شود.
+با استفاده از الگوریتم آنلاین این مساله حل شده است.
+در مقاله ی 
+\cite{jia2018online,luo2020online}
+نرخ جریان هر VNF و سرور نیز در نظر گرفته شده است و دیتا سنترها و VNF ها به صورت گرافی شبیه سازی شده اند.
+در مقاله ی
+\cite{luo2020online}
+الگوریتم روند کردن استفاده کرده که نتیجه ی خوبی را در مقابل مساله ی آفلاین دارد.
+
+در مقاله ی
+\cite{cziva2018dynamic}
+مساله ی قرار دادن VNF ها در لبه مورد بررسی قرار می گیرد که در اینجا تخصیص VNF ها در سیستمی با زیرساخت لبه مورد توجه قرار گرفته است و هدف کمینه کردن تاخیر انتها به انتها از هر کاربر به VNF مورد نظر آن می باشد و از روش دینامیکی و پویا برای حل مساله استفاده شده است.
+
+در مقاله ی
+\cite{pei2019optimal}
+مساله ی قرار دادن VNF در شبکه های فعال SDN/NFV مطالعه شده است، که به طور طبیعی به عنوان یک مساله ی برنامه نویسی باینری (BIP) فرموله شده است. 
+در این مساله قرارگیری VNF زنجیر عملکرد سرویس مورد بررسی قرار گرفته شده است. 
+با استفاده از روش یادگیری تقویت عمیق، الگوریتم قرارگیری VNF مبتنی بر شبکه DDQN \LTRfootnote{Double Deep Q-learning} پیشنهاد می کنیم.
+
+در مقاله ی
+\cite{ren2020joint}
+ مسئله ی بهینه سازی مشترک قرار دادن VNF ها و زمانبندی جریان مطالعه شده است.
+ این مساله از نوع برنامه نویسی عدد صحیح می باشد.
+ برای حالت تک جریان، مساله به سادگی قابل حل است اما برای جندین جریان مساله
+ NP-hard
+ خواهد بود و با استفاده از روش relax کردن لاگرانژ
+ قابل حل می باشد.
+\section{روش های حل}
+در این بخش مروری بر حل مسائل توسط مقالات می نماییم.
+\subsection{روش های آفلاین}
+یکی از مسائل پیش رو، مسئله ی knapsack
+می باشد.
+این مسئله، از جنس NP-hard
+می باشد که در این مسئله می خواهیم تعدادی شی با وزنهای مختلف را در تعدادی جایگاه با ظرفیت مشخص قرار دهیم.
+هدف در این مسئله جاگیری بیشترین تعداد اشیاء در این جایگاه ها می باشد.
+حل این مسئله با استفاده از روش های مختلف
+
+در حل مسائل برش شبکه نیازمند 
+\cite{li2020end}

### 2020-09-03 Latex/tehran-thesis/tex/chapter1.tex
add latex

@@
 مخابرات نسل پنجم
-سیستم های بیسیم \LTRfootnote{Wireless} وشبکه های مخابراتی بعد از نسل چهارم می باشد که تکاملی از لایه ی فیزیکی در تکنولوژی شبکه های مخابراتی سیار همانند \lr{LTE} می باشد که نسبت به \lr{4G} سرعت و پوشش بهتری را فراهم می کند.
+سیستم های بیسیم \LTRfootnote{Wireless} وشبکه های مخابراتی بعد از نسل چهارم می باشد که تکاملی از لایه‌ی فیزیکی در تکنولوژی شبکه های مخابراتی سیار همانند \lr{LTE} می باشد که نسبت به \lr{4G} سرعت و پوشش بهتری را فراهم می‌کند.
 \lr{5G}

### 2020-09-03 Latex/tehran-thesis/tex/chapter2.tex
add latex

@@
 در این فصل، به مرور کارهای گذشته می پردازیم.
-ابتدا صورت مسئله مقالات مختلف را بررسی می نماییم.
-در بررسی صورت مسئله به ترتیب مقالاتی که از برش شبکه استفاده کرده اند می پردازیم.
+ابتدا صورت مسئله مقالات مختلف را بررسی می نماییم که
+ به ترتیب مقالاتی هستند که از برش شبکه استفاده کرده اند.
 برش شبکه در سه بخش رادیویی، بخش هسته و هردو بخش هسته و رادیویی صورت می گیرد.
@@
 \subsection{برش شبکه}
-یک برش شبکه یک شبکه منطقی انتها به انتهای مستقل است که بر روی یک زیرساخت فیزیکی مشترک کار می کند و قادر به ارائه خدمات می باشد.
-برش شبکه قادر به سرویس دهی به خدمات مختلف می باشد.
+برش شبکه یک شبکه منطقی انتها به انتهای مستقل است که بر روی یک زیرساخت فیزیکی مشترک کار می کند و قادر به ارائه خدمات می باشد.
 در این بخش در مورد برش شبکه در بخش رادیویی و هسته و هردو صحبت می نماییم.
 %\subsection{برش شبکه در شبکه های دسترسی رادیویی }
-برش RAN یکی از کلیدهای اصلی برای انعطاف پذیری سفارشات ومدیریت مجازی سازی ایستگاه پایه می باشد تا بتواند منابع رادیویی را در میان سرویس های مختلف تقسیم کرده و منجر به سازگاری اپراتورها و برطرف کردن نیاز سرویس ها گردد.
+برش RAN یکی از کلیدهای اصلی برای انعطاف پذیری سفارشات و مدیریت مجازی سازی ایستگاه پایه می باشد تا بتواند منابع رادیویی را در میان سرویس های مختلف تقسیم کرده و منجر به سازگاری اپراتورها و برطرف کردن نیاز سرویس ها گردد.
 %در ادامه مروری بر این مدل مقالات می نماییم.
@@
 برش شبکه به صورت دینامیکی در بخش رادیویی مورد بررسی قرار گرفته شده است.
-چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش، تشکل و تخصیص منابع باند پایه و یک سطح پایین تر، که تخصیص منابع رادیو در میان کاربران می باشد.
+برش شبکه در اینجا به عنوان فرآیند تخصیص منابع شبکه به کاربران انجام می شود
+چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش کاربران، ارتباط کاربر که شامل تخصیص واحد رادیویی (RRH) برای بیشینه سازی نرخ کاربران و تخصیص ظرفیت منابع باند پایه (‌BBU) و یک سطح پایین تر، که تخصیص توان و بلوک منابع فیزیکی (PRB) در میان کاربران می باشد.
 در این مدل فرض می کنیم که هر سرویس دارای شبکه اصلی خود (یا قطعه اصلی شبکه) است که به H-CRAN متصل می شود.
@@
 در سطح بالا، یک مسئله کنترل پذیرش با برنامه نویسی پویا می باشد که در آن پیچیدگی را می توان تنظیم کرد.
-همچنین مسئله ی ارتباط کاربر با استفاده از یک الگوریتم حریص با پیچیدگی کم بهینه و حل می شود.
+این مسئله از جنس مسئله ی
+کوله پشتی \LTRfootnote{Knapsack}
+باینری
+ می باشد که با الگوریتم دینامیکی جواب بهینه ی آن بدست می آید.
+همچنین مسئله ی ارتباط کاربر نیز یک مسئله ی کوله پشتی باینری است که با استفاده از یک الگوریتم حریص با پیچیدگی کم بهینه و حل می شود.
  مسئله ی تخصیص ظرفیت BBU نیز فرموله شده و با برنامه ریزی خطی حل می شود.
@@
 در این بخش مروری بر حل مسائل توسط مقالات می نماییم.
-\subsection{روش های آفلاین}
-یکی از مسائل پیش رو، مسئله ی knapsack
+\subsection{ مسئله ی کوله پشتی }
+یکی از مسائل پیش رو، مسئله ی کوله پشتی \LTRfootnote{knapsack}
 می باشد.
@@
 هدف در این مسئله جاگیری بیشترین تعداد اشیاء در این جایگاه ها می باشد.
-حل این مسئله با استفاده از روش های مختلف
+حل این مسئله با استفاده از روش های مختلف صورت می گیرد.
 
-در حل مسائل برش شبکه نیازمند 
-\cite{li2020end}
+در مقاله ی \cite{lee2018dynamic}
+همانطور که قبل تر اشاره شد، مسئله ی پذیرش کاربر و ارتباط کاربر از جنس کوله پشتی
+ می باشد که به ترتیب با استفاده از الگوریتم دینامیکی و الگوریتم حریص تعریف شده در مقاله
+ حل می گردد.
+
+در مقاله ی
+\cite{sciancalepore2017mobile}
+یک راه حل جامع شامل برش شبکه، پیش بینی ترافیک، کنترل پذیرش و برنامه ریزی برای یک سیستم شامل برش شبکه 5G ارائه شده است.
+راه حل کنترل پذیرش به یک مسئله کوله پشتی هندسی (دو بعدی) ترسیم شده و دو الگوریتم کم پیچیدگی به ترتیب برای درخواست های برش شبکه منظم و نامنظم طراحی شده اند.
+\subsection{مسئله ی بسته بندی جعبه}
+ در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می باشد.
+در مسئله ی بسته بندی جعبه \LTRfootnote{bin packing}
+هدف کمینه کردن تعداد جعبه های ورودی با فرض اینکه همه ی اشیا در آن جا شوند.
+
+در مقاله ی
+\citep{wang2017joint}
+مسئله ی تخصیص منابع و بدست آوردن انرژی بهینه در ساختار
+H-CRAN
+می باشد.
+در این مقاله هدف تخصیص همزمان منابع ایستگاه رادیویی RRH و باند پایه BBU می باشد.
+این مسئله به دو بخش مجزا برای تخصیص منابع هر بخش شکسته می شود.
+بخش دوم که مربوط به زمان بندی و برنامه ریزی BBU می باشد به فرم یک مسئله ی باینری بسته بندی جعبه نوشته می شود.
+برای حل این الگوریتم از روش های مختلفی از جمله
+Next-Fit(NF)
+First-Fit(FF)،
+First-Fit-Decreasing(FFD)،
+و
+‌Best-Fit-Decreasing(BFD)
+می باشد که الگوریتم به کار رفته در مسئله از نوع روش
+BFD 
+ است که جواب بهتری در مقایسه با روشهای دیگر دارد.
+
+در مقاله ی
+\cite{de2020optimal}
+به صورت همزمان قرار دادن VNF ها و تخصیص منابع محاسباتی مورد هدف قرار داده شده است.
+این مسئله به صورت
+برنامه نویسی خطی 
+mixed-integer
+می شود که بعد از تغییرات به صورت برنامه نویسی خطی عدد صحیح می توان نوشت که به فرم مسئله ی بسته بندی جعبه خواهد بود که با استفاده از الگوریتم مشابه
+BFD حل می گردد.
+\subsection{روشهای یادگیری تقویتی}
+در این بخش تمرکز ما بر‌روی مقالاتی است که از روش یادگیری عمیق در حل مسئله استفاده می‌کند.
+
+در مقاله‌ی
+ \cite{gan1, gan2}
+
+%در حل مسائل برش شبکه نیازمند 
+%\cite{li2020end}

### 2020-09-04 Latex/tehran-thesis/tex/chapter2.tex
add file ch2

@@
 ابتدا صورت مسئله مقالات مختلف را بررسی می نماییم که
- به ترتیب مقالاتی هستند که از برش شبکه استفاده کرده اند.
+ به ترتیب شامل مقالاتی هستند که از برش شبکه استفاده کرده اند.
 برش شبکه در سه بخش رادیویی، بخش هسته و هردو بخش هسته و رادیویی صورت می گیرد.
-سپس در زمینه ی سیر عبور از شبکه های دسترسی رادیویی ابری به شبکه های دسترسی رادیویی باز مطالعه نموده و در انتها درباره ی جاگیری VNF ها صحبت می کنیم.
+سپس در زمینه ی سیر عبور از شبکه های دسترسی رادیویی ابری به شبکه های دسترسی رادیویی باز مطالعه نموده و بعد از آن درباره ی جاگیری VNF ها صحبت می کنیم.
+سپس در مورد روش حل مسئله صحبت می کنیم که شامل مسائل کوله پشتی و بسته بندی جعبه می باشد و در نهایت در مورد روشهای یادگیری تقویتی صحبت می کنیم.
 \section{مسائل پیش رو}
@@
 برش شبکه یک شبکه منطقی انتها به انتهای مستقل است که بر روی یک زیرساخت فیزیکی مشترک کار می کند و قادر به ارائه خدمات می باشد.
-در این بخش در مورد برش شبکه در بخش رادیویی و هسته و هردو صحبت می نماییم.
+در این بخش برش شبکه در بخش رادیویی و هسته و هردو را بررسی می کنیم.
 %\subsection{برش شبکه در شبکه های دسترسی رادیویی }
@@
 همچنین ، تقسیم C/U در مدل سیستم فرض می شود، که به موجب آن صفحات کنترل و داده از هم جدا می شوند به گونه ای که صفحات کنترل توسط M-RRH در شبکه مدیریت می شود.
-\begin{figure}[H]
+\begin{figure}%[H]
   \centering
@@
 \cite{larsen2018fronthaul,costanzo2018network}
-برش شبکه در شبکه های دسترسی رادیویی ابری متوجه قرار گرفته است. 
-در بخش fronthaul شبکه مشکلاتی از قبیل پیچیدگی شبکه و محدودیت نرخ وجود دارد که در برش شبکه، منجر به بهبود آن می شود.
+برش شبکه در شبکه های دسترسی رادیویی ابری مورد توجه قرار گرفته است. 
+در بخش fronthaul مشکلاتی از قبیل پیچیدگی شبکه و محدودیت نرخ وجود دارد که در برش شبکه، منجر به بهبود آن می شود.
 علاوه بر این ، C-RAN می تواند مجازی سازی مجموعه ای از توابع RAN را امکان پذیر کرده و راه را برای اصطلاحاً RAN مجازی باز کند. با این کار می توان چندین شبکه مجازی یا برش ایجاد کرد.
@@
 \cite{larsen2018fronthaul}
-نشان داده است که با استفاده از برش شبکه و برخورداری از سوییچ بسته در fronthaul
-مزایای زیادی را خواهد داشت که از جمله برخورداری از تقسیمات عملکردی مختلف خواهد بود. همچنین از معایب این کار تاخیر نسبتا اندکی خواهد بود.
+نشان داده است که استفاده از برش شبکه و برخورداری از سوییچ بسته در fronthaul
+مزایای زیادی را به همراه خواهد داشت که از جمله برخورداری از تقسیمات عملکردی مختلف خواهد بود. همچنین از معایب این کار تاخیر نسبتا اندکی می باشد.
 
@@
 \cite{onet}
-اجرای عملی برش شبکه را پیشنهاد شده است.
-در مدل پیشنهادی ، نویسندگان فرض می کنند که در هر شکاف زمانی مشخص ، کاربران فقط می توانند یک برش شبکه واحد را درخواست کنند.
+اجرای عملی برش شبکه پیشنهاد شده است.
+در مدل پیشنهادی، نویسندگان فرض می کنند که در هر شکاف زمانی مشخص، کاربران فقط می توانند یک برش شبکه واحد را درخواست کنند.
 در اینجا تابع هدفی بر اساس نسبت میزان منابع اختصاص داده شده به کاربرن در هر زمان t به ظرفیت کل منابع مشخص شده است و هدف بیشینه سازی آن  می باشد.  
@@
 در این بخش تمرکز ما بر‌روی مقالاتی است که از روش یادگیری عمیق در حل مسئله استفاده می‌کند. 
+یادگیری تقویتی
+ \LTRfootnote{Reinforcement Learning}
+ در حال حاضر یکی از موضوعات داغ پژوهشی محسوب می‌شود و محبوبیت آن روز به روز در حال افزایش است.
+یادگیری تقویتی گونه‌ای از روش‌های یادگیری ماشین است که یک عامل(agent) را قادر به یادگیری در محیطی تعاملی با استفاده از آزمون و خطاها و استفاده از بازخوردهای اعمال و تجربیات خود می‌سازد.
+اگرچه هم یادگیری نظارت شده و هم یادگیری تقویتی از نگاشت بین ورودی و خروجی استفاده می‌کنند، اما در یادگیری تقویتی که در آن بازخوردهای فراهم شده برای عامل، مجموعه صحیحی از اعمال، جهت انجام دادن یک وظیفه هستند، بر خلاف یادگیری نظارت شده از پاداش‌ها و تنبیه‌ها به عنوان سیگنال‌هایی برای رفتار مثبت و منفی بهره برده می‌شود.
+  در یادگیری تقویتی هدف پیدا کردن مدل داده مناسبی است که پاداش کل را برای عامل، بیشینه می‌کند. تصویر زیر ایده اساسی و عناصر درگیر در یک مدل یادگیری تقویتی را نشان می‌دهد.
+\begin{figure}
+  \centering
+    \includegraphics[scale=0.7]{./fig/rl}
+  \caption{یادگیری تقویتی}
+  \label{fig:rl}
+\end{figure}
+برخی از اصطلاحاتی که عناصر یک مساله یادگیری تقویتی را تشریح می‌کنند در ادامه بیان شده است.
+\begin{itemize}
+\item محیط (Environment):
+ جهان فیزیکی که عامل در آن عمل می‌کند.
+\item حالت (State):
+ موقعیت کنونی عامل
+\item پاداش (Reward):
+ بازخورد از محیط
+\item  سیاست (Policy):
+ روشی برای نگاشت حالت عامل به عمل
+\item  ارزش (Value):
+ پاداش آینده که یک عامل با اقدام به یک عمل در یک حالت خاص به آن دست می‌یابد.
+\end{itemize}
+یادگیری تقویتی عمیق
+DRL \LTRfootnote{Deep Reinforcement Learning}،
+ از شبکه‌های عصبی عمیق برای حل مسائل یادگیری تقویتی استفاده می‌کند، از این رو در نام آن از کلمه عمیق استفاده شده است.
+با در نظر گرفتن Q-Learning که یادگیری تقویتی کلاسیک محسوب می‌شود و Deep-Q-Learning می‌توان تفاوت آن‌ها با یکدیگر را دید.
+در رویکرد اول، از الگوریتم‌های سنتی برای ساخت جدول Q استفاده می‌شود تا به عامل در یافتن اقدامی که باید در هر حالت انجام شود کمک کند.
+در دومین رویکرد، از شبکه عصبی (برای تخمین پاداش بر مبنای حالت: مقدار q) استفاده می‌شود.
 
@@
  \cite{gan1, gan2}
+سناریویی در نظر گرفته شده است که شامل چندین برش در یک شبکه دسترسی رادیویی با ایستگاههای پایه است که از منابع فیزیکی مشترک (به عنوان مثال، پهنای باند) استفاده می کنند. 
+با استفاده از یادگیری تقویت عمیق (DRL) با در نظر گرفتن تقاضای مختلف خدمات به عنوان وضعیت محیط و منابع اختصاص یافته به عنوان عمل محیط، این مشکل حل می شود.
+برای کاهش نویز و رسیدن به سطح انتظار خدمات، از روش GAN در بخش عمیق الگوریتم استفاده شده است که منجر به حداقل رساندن اختلاف بین توزیع مقدار-عمل تخمین زده شده و توزیع ارزش عمل هدف
+می شود.
+برای یافتن سیاست بهینه ی تخصیص منابع از روش
+DDQN \LTRfootnote{Double Deep Q-Network}
+ استفاده می شود.
+\begin{figure}
+  \centering
+    \includegraphics[scale=0.7]{./fig/gan}
+  \caption{سناریوی ارسال لینک بالا و پایین در برشهای شبکه }
+  \label{fig:gan}
+\end{figure}
 
-%در حل مسائل برش شبکه نیازمند 
-%\cite{li2020end}
+در مقاله ی
+\cite{li2020end} 
+الگوریتم تخصیص منابع برش شبکه انتها به انتها مبتنی بر 
+DQN \LTRfootnote{deep Q-Network}
+ پیشنهاد شده است که برای سناریوهای چند برش و چند سرویس مناسب است.
+ در این سیستم دو مدل سرویس ارائه شده است که اولی بر مبنای نیاز به رسیدن به نرخ خاص و دومی نیازمند داشتن تاخیر کم می باشد.
+هدف در این سیستم رسیدن به بیشینه نرخ دسترسی است.
+برای رسیدن به هدف مورد نظر برشها به دو بخش دسترسی و اصلی تقسیم شده اند.
+ در اینجا الگوریتم به طور مشترک برشهای شبکه دسترسی رادیویی و برشهای شبکه اصلی را در نظر می گیرد تا منابع را به صورت دینامیکی طوری اختصاص دهد که 
+ حداکثر میزان کاربران به شبکه دسترسی داشته و به بیشینه نرخ برسد.
+ این سیستم به صورت برنامه ی
+ mixed-integer
+ نوشته می شود
+و مسئله به صورت دو مسئله ی کوله پشتی و اتصال لینک ها بیان می شود
+  و با استفاده از روش
+ DQN
+ حل می گردد.

### 2020-09-05 Latex/tehran-thesis/tex/chapter3.tex
chapter 3 finish

@@
 \chapter{تخصیص منابع در شبکه های \lr{Open RAN}}
+\section{مقدمه}
 در این فصل، هدف تخصیص منابع در شبکه های \lr{Open RAN} در لینک فروسو می باشد که شامل تخصیص توان و برش های شبکه است.
-در این بخش فرض بر این است که شبکه ی نسل پنجم مخابرات با زیرساخت \lr{Open RAN} موجود است.
+در این بخش فرض بر این است که در شبکه ی نسل پنجم مخابرات از زیرساخت \lr{Open RAN} استفاده شده است.
 این شبکه سرویس هایی از قبیل \lr{IoT}، سرویس تلفن، پیامک و ...
 در اختیار کاربران قرار می دهد.
-در اینجا از مفهوم برش شبکه استفاده شده است بدین صورت که به جای دیدن کاربران به صورت مجزا، کاربرانی که از یک سرویس خاص استفاده می نمایند در دسته ی آن سرویس قرار گرفته و دسته بندی می شوند.
+در اینجا  مفهوم برش شبکه در سیستم بدین صورت به کار رفته که به جای دیدن کاربران به صورت مجزا، کاربرانی که از یک سرویس خاص استفاده می نمایند در دسته ی آن سرویس قرار گرفته و دسته بندی می شوند.
 همچنین برش هایی از شبکه در اختیار کاربران هر سرویس خاص، قرار می گیرد که هر برش شبکه شامل تعدادی واحد رادیویی
@@
 می باشد.
+
+در این سیستم هدف، بررسی مسئله ی برش شبکه در بخش RAN و بخشی از هسته در شبکه های دسترسی باز
+ORAN
+می باشد.
+ما مسئله زمانبندی لینک بی سیم، اختصاص برشها به سرویسها و اختصاص مراکز داده به برشها را که از مشکلات بسته بندی جعبه  ۳-بعدی است را فرموله می کنیم. 
+هدف این است که به طور مشترک بهره وری انرژی را به حداکثر برسانیم و مصرف توان واحدهای رادیویی را کاهش داده تا هزینه منابع فیزیکی را در یک کانال فروسو به حداقل برسانیم.
+این مسئله به صورت یک مسئله ی 
+mixed-integer
+بیان می شود و به دو مسئله ی کوچکتر قابل جداسازی است. با استفاده از الگوریتمهای ابتکاری، این مسائل حل شده اند.
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.55]{./fig/c2.pdf}
+	\caption{برش شبکه در ORAN}
+	\label{fig:c11}
+\end{figure}
+در شکل \ref{fig:c11}
+لینک فروسو در سیستم ORAN نشان داده شده است که بخش RAN به سه لایه تقسیم می‌گردد که شامل بخش RU، 
+CU و
+بخش DU می‌باشد.
+بخش CUو DU برروی مرکز داده اجرا می‌شوند. کاربران براساس نیاز سرویسهای مختلف تقسیم شده‌اند.
+
+نوآوری های این کار در ادامه بیان شده است.
+\begin{itemize}
+\item 
+به طور همزمان برش شبکه و تخصیص منابع در سیستم
+ ORAN
+  در نظر گرفته شده است.
+\item 
+مسئله ی پذیرش کاربر و تخصیص خدمات به برش ها، و منابع فیزیکی بی سیم و مرکز داده به برش ها را به عنوان یک مسئله ی بهینه سازی حل می کنیم.
+\item
+از الگوریتمهای ابتکاری در جهت حل این مسائل برای رسیدن به پاسخ نسبتا بهینه استفاده کرده تا در کمترین زمان پاسخ نسبتا بهینه را بدهد.
+\end{itemize} 
 \section{مدل سیستم}
@@
 \end{subequations}
+در اینجا،
+$\boldsymbol{P} =[p_{u(v,k)}] \:\: \forall v , \forall k $
+ماتریس توان برای کاربران است،
+$\boldsymbol{A} =[a_{v,s}] \:\: \forall v , \forall s $
+نشان دهنده ی
+متغیر باینری برای اتصال برشها به سرویسها و
+$\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $
+متغیر باینری برای اتصال
+مرکز داده ی فیزیکی به VNFها می باشد.
+همچنین
+$\varphi$ 
+متغیر وزنی برای ارزش گزاری بین ترم اول و دوم تابع هدف است.
+\eqref{c11}
+و
+\eqref{c12}
+به ترتیب
+نشان دهنده ی این است که توان واحد رادیویی از حدی بیشتر نشده و توان هر کاربر یک عدد صحیح مثبت است.
+علاوه براین
+\eqref{c13}
+منجر به افزایش نرخ هرکاربر از حد مورد نیاز می باشد.
+ \eqref{c14}
+  و 
+  \eqref{c15}
+  به ترتیب
+  محدودیت ظرفیت لینک
+  fronthaul 
+  و محدودیت مورد نیاز برای تاخیر سیگنال ارسالی
+  را نشان می دهد.
+  \eqref{c21}
+ تضمین می کند که هر سرویس
+ به حداقل یک
+ برش شبکه متصل شده است.
+همچنین،
+\eqref{c23}
+تضمین می کند که هر برش که شامل VNF هایی در دو لایه است،
+به حداقل یک مرکز داده متصل می شود.
+در \eqref{c22} 
+$\mathcal{E} = \{M,S,C\}$ 
+و شرطها ضمانت می کند که منابع فیزیکی کافی برای VNFها وجود دارد.\newline
+مسئله‌ی بهینه‌سازی \eqref{constraints}
+قابل جداسازی به دو مسئله‌ی بهینه‌سازی کوچکتر می‌باشد زیرا متغیرها می‌تواندد به صورت مجزا بدست آیند. ابتدا نیاز به حل مسئله‌ی اول 
+داریم و پس از حل آن
+$\boldsymbol{P}$
+و
+$\boldsymbol{A}$
+بدست می‌آید. سپس با حل مسئله‌ی دوم و قرار دادن مقدار بهینه‌ی  $ \boldsymbol{A}$ در مسئله
+خروجی  $ \boldsymbol{Y}$
+بدست می‌آید.
+مسئله‌ی اول به صورت زیر می‌باشد.
+\begin{subequations}
+	\begin{alignat}{4}
+		\max\limits_{\boldsymbol{P}, \boldsymbol{A} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})\\
+		\text{\lr{subject to}} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
+		&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
+		&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\
+		&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i,\label{cc14} \\
+		&D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
+		& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s.
+	\end{alignat}
+	\label{constraints1}
+\end{subequations}
+مسئله‌ی دوم نیز بدین صورت بیان می‌شود.
+\begin{subequations}
+	\begin{alignat}{4}
+		\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
+		\text{\lr{subject to}} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
+		&\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
+	\end{alignat}
+	\label{constraints2}
+\end{subequations}
+\section{روش ابتکاری استفاده شده}\label{proposedmethod}
+در این بخش از روش ابتکاری برای حل مسئله \eqref{constraints1}
+استفاده می‌کنیم که یک مسئله‌ی غیر‌محدب همراه با محاسبات طولانی است.
+برای حل مسئله همانطور که قبلا بیان شد، مسئله به دو بخش مختلف و مجزا تجزیه می‌شود که به صورت تکراری حل می‌گردد.
+در بخش اول در ابتدای کار در اولین حلقه با قرار دادن $\boldsymbol{P} = P_{max}$ و $\eta = 0$ در رابطه‌ی \eqref{constraints1}
+مقدار $\boldsymbol{A}$ بدست می‌آید.
+سپس  با  $\boldsymbol{A}$ بدست آمده، $\boldsymbol{P}$ را در معادله‌ی \eqref{constraints1} بروزرسانی می‌کنیم.
+این معادله قابل تبدیل به یک مسئله‌ی محدب است و با روشهای محدب حل می‌شود.
+بعد از حل این مسئله،
+$\boldsymbol{P}$و $\eta$
+بروزرسانی شده و این چرخه‌ی دو بخشی تا همگرا شدن ادامه دارد.
+\subsection{بخش اول مسئله‌ی اول}\label{firstsub}
+الگوربتم تکرار شده برای بدست آوردن $\boldsymbol{A}$ در اینجا اجرا می‌گردد.
+بخش اول مسئله‌ی اول از جنس بسته‌بندی جعبه به صورت سه بعدی می‌باشد که یک مسئله‌ی NP-Hard است و برای حل آن نیاز به الگوریتمهای ابتکاری داریم.
+در 
+\cite{3dbin}،
+الگوریتم ابتکاری براساس مرتب‌سازی جعبه‌ها براساس اندازه‌گیری بیان شده‌است. جزئیات الگوریتم موردنظر در \ref{alg}
+و براساس الگوریتم
+ \cite{3dbin}
+ و روش
+  BFD\LTRfootnote{Best Fit Decreasing}
+  بیان شده است.
+
+	\begin{algorithm}
+		\caption{اتصال سرویس به برش شبکه}\label{alg}
+		\begin{latin}
+		\begin{algorithmic}[1]
+
+			\State{Sort services according to the number of UE's requirements in the descending order.}
+			\State{Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs and the capacity of thei resources in the descending order.}
+			\For {$i \gets 1$ to $S$}
+			\For {$j \gets 1$ to $V$}
+			\State{Set $a_{i,j} = 1$}
+			\State{Obtain Parameters of Systems (power and rate , capacity of fronhaul links)}
+			\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} are not applied}
+			\State{Set $a_{i,j} = 0$;}
+			\Else
+			\State{break from inner loop;}
+			\EndIf
+			\State{\textbf{end if}}
+			\EndFor
+			\State{\textbf{end for}}
+			\EndFor
+			\State{\textbf{end for}}
+		\end{algorithmic}
+	\end{latin}
+	\end{algorithm}
+
+\subsection{بخش دوم مسئله‌ی اول}\label{secondsub}
+در این بخش با فرض ثابت قرار دادن  $\boldsymbol{A}$
+توان کاربران در هر سرویس بدست می‌آید.
+\begin{theorem}\label{t2}
+	بهره‌وری انرژی زمانی بدست می‌آید که
+	\begin{equation}\label{q2}
+		%\begin{split}
+		\max \limits_{\boldsymbol{P}} (\mathfrak{R}_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=
+		\mathfrak{R}_{tot}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
+		%\end{split}
+	\end{equation}
+\end{theorem}
+\begin{proof}
+	مراجعه به  \cite[\lr{Appendix A}]{aaa}
+\end{proof}
+در بخش دوم مسئله‌ی اول از الگوریتم تکراری و تابع لاگرانژ برای حل استفاده شده است. 
+از آنجایی که تداخل تابعی از توان کاربران است، برای سادگی فرض باند بالای $\bar{I}_{u_{(v,i)}}$ برای آن می کنیم. برای اینکه بتوانیم 
+\eqref{constraints1}
+را به صورت فرم استاندارد بهینه سازی محدب درآوریم، نیازمند این هستیم که متغیرهای روابط
+\eqref{cc14} 
+و
+\eqref{cc15}
+ را   ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ و $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ تغییر دهیم.
+فرض کنید $\boldsymbol{\lambda}$ ، $\boldsymbol{\mu}$، $\boldsymbol{\xi}$ و $\boldsymbol{ \kappa}$  ماتریسهای ضرایب لاگرانژ می‌باشد که دارای مقادیر مثبت غیر‌صفرند. تابع لاگرانژ بدین صورت نوشته می‌شود.
+
+\begin{subequations}\label{lagrang}
+	\begin{alignat}{4}
+		\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\chi}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
+		- \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
+		&+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
+		&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
+		&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,i)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\
+		&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.
+	\end{alignat}
+\end{subequations}
+که دراینجا $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$.
+توان بهینه از \eqref{lagrang}
+بدین صورت خواهد بود
+
+\begin{equation}
+	p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
+\end{equation}
+که دراینجا 
+ $\mathfrak{y}_{u(v,i)}= (\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$
+ و
+$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. 
+همچنین
+$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ و $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$.
+با استفاده از روش sub-gradient توان بهینه $\boldsymbol{P}$ بدست می‌آید\cite{mimoCran}.
+\subsection{حل دو بخش مسئله‌ی اول به صورت تکراری}
+در \eqref{firstsub} و \eqref{secondsub}
+جزئیات حل هر بخش از مسئله‌ی اول آورده شده است.
+در ایتدا با ثابت نگه‌داشتن $\boldsymbol{P} = P_{max}$
+و $\eta = 0$
+مقدار $\boldsymbol{A}$
+در مسئله‌ی \eqref{constraints1}
+و با استفاده از \eqref{alg}
+بدست می‌آید. 
+سپس $\boldsymbol{A}$ از الگوریتم \ref{alg} بدست می‌آید. پس از آن در بخش دوم، با استفاده از روش sub-gradient، $\boldsymbol{P}$ 
+بدست می‌آید. 
+بعد از بدست آوردن $\boldsymbol{P}$ و $\eta$ الگویتم با مقادیر جدید توان و بهره‌وری انرژی دوباره تکرار می گردد تا همگرا شود.
+در اینجا الگوریتم حل مسئله‌ی اول به صورت الگوریتم \eqref{alg2} است.
+
+\begin{algorithm}
+	\caption{برش شبکه و تخصیص منابع}\label{alg2}
+	\begin{latin}
+	\begin{algorithmic}[1]
+		\State{Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$}
+		\State{Set $\boldsymbol{P} = \boldsymbol{P}_{max}$}
+		\For{$counter \gets 1$ to $I_{max}$}
+		\State{Achieve $\boldsymbol{A}$ by applying Algorithm \eqref{alg}}
+		\State{Obtain $\boldsymbol{P}$ by using sub-gradient method which is mentioned in \eqref{secondsub}.}
+		\If{$ \mathfrak{R}_{tot}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) - \eta^{(i)} P_{r_{tot}}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) < \epsilon_{\eta} $}
+		\State{Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $, $\boldsymbol{A}^*= \boldsymbol{A}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;}
+		\State{break;}
+		\Else
+		\State{$i= i+1$, Setting $\boldsymbol{P} = \boldsymbol{P}^{(i)}$ ;}
+		\EndIf
+		\State{\textbf{end if}}
+		\EndFor
+		\State{\textbf{end for}}
+	\end{algorithmic}
+	\end{latin}
+\end{algorithm}
+\subsection{مسئله‌ی دوم}
+در این بخش می‌خواهیم \eqref{constraints2} را حل نماییم که قرارگیری منابع مجازی در منابع فیزیکی می‌باشد به‌طوری که تابع هزینه‌ی  $\psi_{tot}$ کمینه شود.
+این مسئله از جنس مسئله‌ی سه بعدی بسته‌بندی جعبه است که NP-Hard می‌باشد.
+برای بدست‌آوردن مقدار بهینه‌ی $\boldsymbol{Y}$ الگوریتم ابتکاری برای حل مسئله‌ی سه بعدی بسته‌بندی جعبه ارائه شده است.
+جزئیات الگوریتم در \eqref{alg3} نوشته شده است. در این الگوریتم، در ابتدا برشهای شبکه و مرکز داده ها را بر اساس  جمع وزنی آنها مرتب می کنیم (خط \ref{31} و \ref{32} الگوریتم \ref{alg3}).
+در اینجا، پارامتر وزندار برای $\Omega_{\mathfrak{z},s}^{tot}$ و $\tau_j^\mathfrak{z}$ بدین صورت تعریف می‌کنیم.
+\begin{equation}\label{wt}
+	\begin{split}
+		\hat{\Omega}_{s}^{tot} &= w_M \bar{\Omega}_{M,s}^{tot} + w_S \bar{\Omega}_{S,s}^{tot} + w_C \bar{\Omega}_{C,s}^{tot} \\
+		\hat{\tau}_j &= w_M \tau_{{j}}^M + w_S \tau_{{j}}^S + w_C \tau_{{j}}^C,
+	\end{split}
+\end{equation}
+که دراینجا، $\boldsymbol{w} = \{w_M, w_S, w_C\}$ وزن حافظه، نگهداری و CPU می‌باشد
+\cite{3dbin}.
+در مرحله دوم، ما تخصیص را از بیشترین برش های مورد نیاز به DC با بیشترین منابع فیزیکی شروع می کنیم(از خط \ref{33} تا \ref{34} الگوریتم \ref{alg3}).
+ بعد از تخصیص برش شبکه به مرکز داده، در صورتی که یکی از برشهای شبکه توسط مرکز داده پذیرش نشود، برای بخش بعدی جاگذاری می‌رود
+ (از خط \ref{35} تا \ref{36} الگوریتم \ref{alg3}).
+ در آخر، اگر مرکز داده‌ای با میزان منابع کمتر آزاد باشد و بتواند برشهای یک مرکز داده‌ی دیگر با میزان منابع بیشتر را سرویس‌دهی کند، 
+ تخصیص منابع بین این دو مرکز داده جابه‌جا می‌شود(خط \ref{37} از الگوریتم \ref{alg3}). 
+\begin{algorithm}
+	\caption{قرار گیری منابع مجازی در منابع فیزیکی}\label{alg3}
+	\begin{latin}
+	\begin{algorithmic}[1]
+		\State Sort Slices according to $\hat{\Omega}_{s}^{tot} , \forall s$ in descending order.\label{31}
+		\State Sort DCs according to $\hat{\tau}_j , \forall j$ in descending order. \label{32}
+		\State $\boldsymbol{Y} = \boldsymbol{0}$
+		\For {$d \gets 1$ to $D_c$}\label{33}
+		\For {$s \gets 1$ to $S$}
+		\If {$\sum_{d=1}^{D_c}y_{s,d}==0$ and $\bar{\Omega}_{\mathfrak{z}(s)}^{tot} \leq \tau_{\mathfrak{z}_j} \forall \mathfrak{z}, \forall s$  }
+		\State Set $y_{s,d} = 1$;
+		\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
+		\EndIf
+		\State \textbf{end if}
+		\EndFor
+		\State \textbf{end for}
+		\EndFor
+		\State \textbf{end for} \label{34}
+		\State  $ind_{rem} = \{s|({\sum_{d=1}^{D_c}y_{s,d}==0})\}$ \label{35}
+		\State Sort remaining amount of DCs same as before in descending order.
+		\State Sort remaining slices same as before in descending order.
+		\For {$r \gets 1$ to $S_{rem}$}
+		\For {$n \gets 1$ to $D_c$}
+		\State Set $y_{s,d} = 1$;
+		\State {$\bar{\Omega}_{{\mathfrak{z}},s}^{tot}$ $\gets$ {$\bar{\Omega}_{{\mathfrak{z}},s}^{tot}- \tau_j^{\mathfrak{z}}$}}
+		\If {$\bar{\Omega}_{s}^{tot}==0$}
+		\State Set $y_{s,d} = 1$;
+		\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
+		\State {break inner loop}
+		\EndIf
+		\State \textbf{end if}
+		\EndFor
+		\State \textbf{end for}
+		\EndFor
+		\State \textbf{end for} \label{36}
+		\State Remapping DCs must be done to prevent wasting Energy \label{37}
+	\end{algorithmic}
+\end{latin}
+\end{algorithm}
+\section{نتایج عددی}\label{simul}
+در این بخش نتایج عددی برای مسئله ی اصلی بیان می‌شود.
+\begin{table}
+	\caption {پارامترهای شبیه‌سازی} \label{table:1a}
+	\begin{latin}
+	\begin{center}
+		\begin{tabular}{||c c ||}
+			\hline
+			Parameter & Value \\ [0.5ex]
+			\hline\hline
+			Noise power & -174dBm\\
+			\hline
+			Bandwidth & 120 KHZ \\
+			\hline
+			Maximum transmit Power of each RU & 40dBm \\
+			\hline
+			Minimum delay &  300usec \\
+			\hline
+			Maximum fronthaul capacity  & 200 bits/sec/Hz \\
+			\hline
+			Minimum data rate &  10 bits/sec/Hz \\ [1ex]
+			\hline
+		\end{tabular}
+	\end{center}
+	\end{latin}
+\end{table}
+در شکل \ref{fig:f1a}، بهره‌وری انرژی برای دو سری تعداد سرویس مختلف با تعداد کاربر متفاوت در هر سرویس بدست‌آمده‌است.
+پارامترهای شبیه‌سازی در جدول \ref{table:1a} قرار داده‌شده‌است.
+روش بهینه برای بدست آوردن $\boldsymbol{A}$ توسط MOSEK بدست آمده و برای بدست آوردن $\boldsymbol{P}$ از CVX در متلب استفاده شده است و به صورت متناوب این دو ماتریس به‌روزرسانی می‌شوند.
+روش بهینه،  
+$0.1bits/J/Hz$ 
+از روش آورده شده بهتر است (برای  $V = 6$ و $E[U_v] = 10$).
+همچنین 
+$0.09bits/J/Hz$
+از روش آورده شده بهتر است (برای  $V = 3$ و $E[U_v] = 10$).
+همانطور که در شکل مشخص است بهره‌وری انرژی با افزایش تعداد کاربران افزایش می‌یابد.
+\begin{figure}%[H]
+	\centering
+	\includegraphics[width=\linewidth]{./fig/fig1_last}
+	\caption{بهره‌وری انرژی براساس تعداد کاربران در هر سرویس}
+	\label{fig:f1a}
+\end{figure}
+در شکل \ref{fig:f1}، نسبت برشهای پذیرفته شده برای دو تعداد مختلف مرکز داده با تعداد برشهای مختلف رسمم شده است. پارامترهای شبیه‌سازی در جدول \ref{table:1} آورده شده است. همچنین داریم 
+ $w_C = 320$،
+ $w_S = 100$و 
+ $w_M =1$.
+ در این شبیه‌سازی ترم دوم رابطه‌ی \eqref{eqpsi}، مورد اهمیت قرار گرفته شده است و پارامتر طراحی $\nu$ مقدار بالایی دارد.
+ همچنین فرض شده که تنها یک مرکز داده می‌تواند هر برش را سرویس دهد. روش ارائه شده در الگوریتم  \ref{alg3} آورده شده و روش بهینه با استفاده از MOSEK بدست می‌آید.
+
+\begin{small}
+	\begin{table}
+		\caption {پارامترهای شبیه‌سازی} \label{table:1}
+		\begin{latin}	
+		\begin{center}
+			\begin{tabular}{||c c ||}
+				\hline
+				Parameter & Value \\ [0.5ex]
+				\hline\hline
+				Mean of CPU for DCs & 320GHz\\
+				\hline
+				Mean of Memory for DCs & 1T\\
+				\hline
+				Mean of Storage for DCs & 100T \\
+				\hline
+				Mean of CPU for Slices & 32GHz\\
+				\hline
+				Mean of Memory for Slices & 100G\\
+				\hline
+				Mean of Storage for Slices & 10T \\ [1ex]
+				\hline
+			\end{tabular}
+		\end{center}
+	\end{latin}
+	\end{table}
+\end{small}
+وقتی دو مرکز داده یا DC داریم، روش پیشنهادی و روش بهینه تقریباً همان نسبت برش های پذیرفته شده را دارند. اما با افزایش تعداد DC ها به پنج ، عملکرد روش پیشنهادی کاهش می‌یابد.
+با استفاده از پنج DC ، تفاوت بین روش پیشنهادی و روش بهینه در بدترین حالت (44 برش) حدود 23 درصد است.
+\begin{figure}%[H]
+	\centering
+	\includegraphics[width=\linewidth]{./fig/f112}
+	\caption{نسبت برش های پذیرفته شده فقط به یک 	DC در مقابل برش های کل}
+	\label{fig:f1}
+\end{figure}
+در شکل \ref{fig:f2}
+نرمالیزه‌ی مصرف منابع بر‌اساس تعداد برشهای شبکه آورده شده است. پارامترهای شبیه‌سازی در جدول \ref{table:1}، قرار داده شده و 
+($w_C = 320$, $w_S = 100$, $w_M =1$).
+در این شبیه سازی ، فرض کنید تعداد DC ها کاملاً کافی باشد تا تمام برش ها را پوشش دهد و پارامتر طراحی شده $ \ nu $ کم فرض شود ، بنابراین ما روی اولین ترم \eqref{eqpsi} تمرکز کردیم.
+با این حال ، اگر هر قطعه باقی مانده باشد ، می تواند توسط بیش از یک DC سرویس دهی شود.
+بهینه بودن محل قرارگیری برشها در منابع DC بر اساس مصرف توان DC ها اندازه گیری می شود.
+در اینجا مقدار منابع  مصرف DC نشده نشان داده شده است. برای ۱۰ برش شبکه اختلاف بین مقدار بهینه و روش اعمال شده ۱۵ درصد می‌باشد. 
+\begin{figure}%[H]
+	\centering
+	\includegraphics[width=\linewidth]{./fig/fig22_last}
+	\caption{نرمالیزه‌ی مصرف منابع بر‌اساس تعداد برشها}
+	\label{fig:f2}
+\end{figure}
+\section{نتیجه‌گیری}
+در این فصل، همزمانی برش شبکهو تخصیص توان در سیستم ORAN آمده‌است.
+فرض بر این است که کاربران بر اساس نیازهایشان به سرویسهای مختلف طبقه بندی می شوند.
+همچنین ، تعدادی برش نیز در خدمت این سرویسها قرار می‌گیرد.
+هر برش شبکه شامل تعدادی PRB، RU، و VNFهایی است که اعمال CU و DU را انجام می‌دهد.
+ظرفیت محدود لینک fronthaul برای اتصالات فیبر بین RU و DU در نظر گرفته شده است.
+هدف به حداکثر رساندن مجموع نرخ و به حداقل رساندن مصرف توان و هزینه انرژی مراکز داده به طور همزمان است.
+این مسئله به دو زیر مسئله تجزیه می شود. هر زیر مسئله به طور جداگانه توسط یک الگوریتم ابتکاری حل می شود. با استفاده از نتایج عددی، روش اکتشافی را تأیید کرده و عملکرد الگوریتم ها را مطالعه می کنیم.
+برای مسئله‌ی اول بازدهی انرژی در مقابل تعداد UE در هر سرویس به تصویر کشیده شده است.
+با افزایش میانگین تعداد کاربران در هر سرویس، از بازدهی انرژی بیشتر می‌شود.
+برای مسئله دو، دو شکل نشان داده شده است.
+در شکل اول، نسبت برش های پذیرفته شده که فقط به یک DC متصل می‌شوند، برای تعداد برش های مختلف مشخص شده است.
+در شکل دوم ، مصرف منابع نرمال DC ها به تصویر کشیده شده است.
+در هر شکل ، الگوریتم ابتکاری با روش بهینه مقایسه شده و تفاوت بین آنها بحث شده است.

### 2020-09-06 Latex/tehran-thesis/tex/chapter4.tex
add file

\chapter{تخصیص برش شبکه به صورت دینامیکی}
\section{مقدمه}
در این فصل هدف تخصیص برش شبکه به صورت می‌باشد. در فصل قبلی مدل سیستم به طور کامل نوشته شده است و در حالت آفلاین حل گردیده است، در این فصل پارامترها مورد نیاز را نسبت به فصل قبلی کمتر کرده و با استفاده از روش دینامیکی به حل سیستم می‌پردازیم. برای حل این سیستم از روش یادگیری تقویتی عمیق استفاده می‌کنیم.
\section{  مدل سیستم و صورت مسئله}
همانند سیستم فصل قبل، فرض می کنیم $S$ برش شبکه داریم که قرار است $V$ سرویس مختلف که شامل کاربرانی است که از سرویس خاص استفاده می‌نمایند را سرویس دهی نماید.
هر سرویس 
$v\in \{1,2,...,V \} $
شامل تعدادی کاربر تک آنتنه می باشند که سرویس خاصی را درخواست می‌نماید.
هر برش شبکه
$s\in \{1,2,...,S \} $
 شامل تعدادی
 PRB
  RU،
   BBU، 
   و
    VNF 
 می‌باشد.
در این بخش سعی برا‌ین است که در ابتدا مسئله را به ساده‌ترین حالت ممکن حل نماییم. فرض می‌کنیم سه مدل سرویس مختلف داریم که سرویسهای دسته‌ی اول نیازمند تاخیر خاص و سرویسهای دسته‌ی دوم نیازمند داشتن تاخیر کم هستند و سرویس سوم نیازمند داشتن هر دو حالت تاخیر کم و نرخ زیاد است.
در بخش اول این مسئله، هدف بیشینه‌سازی تعدای سرویسهای پذیرفته شده می‌باشد. در اینجا فرض براین است که تعداد برشهاس شبکه محدود می‌باشد. فرض می‌کنیم هر سرویس $v$ دارای اولویت $p_v$ می‌باشد. 
همچنین فرض براین است که هر سرویس شامل ماکسیمم $U-v$ کاربر است و به طور میانگین کاربران آن نیازمند داشتن نرخ بیشتر از $R_v$ و تاخیر کمتر از $D_v$ هستند. درصورتی که کاربری از دسته‌ی اول باشد 
$D_v =  M$ 
که $M$ برای تاخیر یک عدد بزرگ می‌باشد.
و در صورتی که سرویس از دسته‌ی دوم باشد 
$R_v = N $
که $N$ یک عدد کوچک برای نرخ می‌باشد.
صورت مسئله بدین صورت می‌باشد.
\begin{subequations}
	\begin{alignat}{4}
		\max\limits_{\boldsymbol{a} }   \quad &   \sum_{s=1}^{S}\sum_{v=1}^{V} p_v a_{v,s}\\
		\text{\lr{subject to}} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
		&\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
	\end{alignat}
	\label{constraints2}
\end{subequations}

### 2020-09-07 Latex/tehran-thesis/tex/chapter1.tex
add ch4

@@
 مخابرات نسل پنجم
-سیستم های بیسیم \LTRfootnote{Wireless} وشبکه های مخابراتی بعد از نسل چهارم می باشد که تکاملی از لایه‌ی فیزیکی در تکنولوژی شبکه های مخابراتی سیار همانند \lr{LTE} می باشد که نسبت به \lr{4G} سرعت و پوشش بهتری را فراهم می‌کند.
+سیستم های بیسیم \LTRfootnote{Wireless} وشبکه های مخابراتی بعد از نسل چهارم می‌باشد که تکاملی از لایه‌ی فیزیکی در تکنولوژی شبکه‌های مخابراتی سیار همانند \lr{LTE} است که نسبت به \lr{4G} سرعت و پوشش بهتری را فراهم می‌کند.
 \lr{5G}
-نوع جدیدی از شبکه را ایجاد می کند که به منظور اتصال تقریبا همه و همه چیز با هم از جمله ماشین ها، اشیاء و دستگاه ها ساخته شده است.
+نوع جدیدی از شبکه را ایجاد می‌کند که به منظور اتصال تقریبا همه و همه چیز با هم از جمله ماشین ها، اشیاء و دستگاه ها ساخته شده است.
 \lr{5G}
- فناوری بی سیم برای ارائه سرعت داده های چند گیگابیت بر ثانیه ، تأخیر فوق العاده کم ، قابلیت اطمینان بیشتر ، ظرفیت شبکه گسترده، افزایش در دسترس بودن و تجربه کاربری یکنواخت تر به کاربران بیشتر است.
+ فناوری بی سیم برای ارائه سرعت داده های چند گیگابیت بر ثانیه، تأخیر فوق العاده کم، قابلیت اطمینان بیشتر، ظرفیت شبکه گسترده، افزایش در دسترس بودن و تجربه کاربری یکنواخت تر به کاربران بیشتر است.
 عملکرد بالاتر و بهره وری بهبود یافته باعث افزایش تجربیات کاربر جدید شده و صنایع جدیدی را به هم متصل می کند.
@@
 این پیشرفت ها منجر به تغییراتی از قبیل\lr{IOT} \LTRfootnote{Internet of Things} و \lr{Pervasive Computing} در آینده ی نزدیک خواهد شد.
-همچنین \lr{5G} منجر به توسعه و بهبود سرویس های مخابراتی و اینترنتی سیار و در ورای آن، ایجاد تجربه ی بهتری برای مصرف کنندگان خواهد شد.\newline
-برای توسعه ی اینترنت سیار و \lr{IOT}، نیاز داریم تا شبکه های\lr{5G}، معنای اولیه برای دسترسی شبکه برای ارتباط انسان ها با یکدیگر و ارتباط ماشین با انسان گردد.
+همچنین \lr{5G} منجر به توسعه و بهبود سرویس های مخابراتی و اینترنتی سیار و در ورای آن، ایجاد تجربه‌ی بهتری برای مصرف کنندگان خواهد شد.\newline
+برای توسعه‌ی اینترنت سیار و \lr{IOT}، نیازمند استفاده از شبکه‌ی نسل پنجم هستیم تا به سادگی منجر به دسترسی شبکه برای ارتباط انسان‌ها با یکدیگر و ارتباط ماشین با انسان گردد.
+
 به طور کلی، 
@@
 \lr{(eMBB)}
- برای مقابله با نرخ داده های بسیار زیاد ، تراکم بالای کاربران و ظرفیت ترافیک بسیار بالا برای سناریوهای مختلف و همچنین پوشش یکپارچه و سناریوهای تحرک بالا با نرخ داده های استفاده شده بهبود یافته است.
+ برای مقابله با نرخ داده های بسیار زیاد، تراکم بالای کاربران و ظرفیت ترافیک بسیار بالا برای سناریوهای مختلف و همچنین پوشش یکپارچه و سناریوهای تحرک بالا با نرخ داده‌های استفاده شده بهبود یافته است.
 \item
@@
 \lr{IoT}،
-   برای تعداد بسیار زیاد دستگاههای متصل به مصرف کم و نرخ داده کم نیاز دارد.
+   برای تعداد بسیار زیاد دستگاههای متصل به مصرف کم و نرخ داده کم نیازمند می‌باشد.
 \item 
@@
  برای برنامه های کاربردی مهم برای ایمنی و ماموریت
-  مهم است.
+  مورد توجه است.
 \end{enumerate}
- از آنجا که
+ از آنجا که ساختار
 \lr{5G}
- تکامل می یابد و کمتر به زیرساخت های \lr{4G} وابسته می شود و طیف بیشتری در دسترس قرار می گیرد،
- تخمین ها سرعت بارگیری را حداکثر 1000 برابر سریعتر از \lr{4G} قرار می دهد، که بالقوه از 
+ کمتر به زیرساخت های \lr{4G} وابسته می‌شود و طیف بیشتری در دسترس قرار می‌دهد،
+ تخمین ها سرعت بارگیری را حداکثر 1000 برابر سریعتر از \lr{4G} در نظر دارد، که بالقوه از 
  \lr{10Gbps} 
@@
    را بارگیری کنید.
-   برخی تخمین ها محافظه کارانه تر هستند ، اما حتی محافظه کارانه ترین آن را چندین ده برابر سریعتر از \lr{4G} قرار می دهد.
+   برخی تخمین ها محافظه کارانه تر هستند، اما حتی محافظه کارانه‌ترین تخمین نیز این نسل را چندین ده برابر سریعتر از \lr{4G} قرار می دهد.
 دلایل نیاز به نسل پنجم اینترنت به طور خلاصه در ادامه بیان شده است \citep{etsi}.
 \begin{itemize}
-\item ترافیک داده های تلفن همراه به دلیل پخش ویدئو به سرعت رو به افزایش است.
-\item با در اخیار داشتن چندین دستگاه به طور همزمان، هر کاربر تعداد فزاینده ای از اتصالات را در اختیار دارد.
-\item اینترنت اشیاء به شبکه هایی نیاز دارد که میلیاردها دستگاه را اداره کنند.
-\item با وجود تعداد فزاینده ای از دستگاه های ارتباطی و افزایش ترافیک داده ها ، هم دستگاه ها و هم شبکه ی  
+\item ترافیک داده های تلفن همراه به دلیل پخش ویدئو به سرعت، رو به افزایش است.
+\item با در اختیار داشتن چندین دستگاه به طور همزمان، هر کاربر تعداد فزاینده‌ای از اتصالات را در اختیار دارد.
+\item اینترنت اشیاء به شبکه‌هایی نیاز دارد که میلیاردها دستگاه را اداره کنند.
+\item با وجود تعداد فزاینده‌ای از دستگاه های ارتباطی و افزایش ترافیک داده‌ها، هم دستگاه‌ها و هم شبکه‌ی  
 آن
-نیازمند افزایش بهره وری انرژی هستند.
+نیازمند افزایش بهره‌وری انرژی هستند.
 \item 
- به دلیل تحت فشار قرار گرفتن اپراتورهای شبکه برای کاهش هزینه های عملیاتی و همچنین به دلیل اینکه کاربران به تعرفه های نرخ مسطح عادت می کنند و مایل نیستند مبلغ بیشتری بپردازند.
-\item فناوری ارتباطات سیار می تواند موارد استفاده جدیدی را ایجاد کند (به عنوان مثال موارد تاخیر فوق العاده کم یا قابلیت اطمینان بالا) و برنامه های جدید برای صنعت که منجر به درآمد زایی بیشتر اپراتورها می گردد.
+ به دلیل تحت فشار قرار گرفتن اپراتورهای شبکه برای کاهش هزینه‌های عملیاتی و همچنین به دلیل اینکه کاربران به تعرفه های نرخ مسطح عادت می‌کنند و مایل نیستند مبلغ بیشتری بپردازند.
+\item فناوری ارتباطات سیار می تواند موارد استفاده جدیدی را ایجاد کند (به عنوان مثال موارد تاخیر فوق العاده کم یا قابلیت اطمینان بالا) و برنامه های جدید برای صنعت که منجر به درآمدزایی بیشتر اپراتورها می گردد.
 \end{itemize}
-بنابراین عملکرد عملیاتی نسل پنجم می بایست به طور قابل توجهی افزایش یابد (به عنوان مثال افزایش راندمان طیفی ، سرعت بالاتر داده ، تأخیر کم).
+بنابراین عملکرد عملیاتی نسل پنجم می‌بایست به طور قابل توجهی افزایش یابد (به عنوان مثال افزایش راندمان طیفی، سرعت بالاتر داده، تأخیر کم).
+زیرساخت
 \lr{5G}
-می بایست
-در حالی که هنوز سطح قابل قبولی از مصرف انرژی ، هزینه تجهیزات و استقرار شبکه و هزینه بهره برداری را ارائه می دهد،
+می‌بایست
+در حالی که هنوز سطح قابل قبولی از مصرف انرژی، هزینه تجهیزات و استقرار شبکه و هزینه بهره برداری را ارائه می‌دهد،
  اینترنت اشیاء را به طور گسترده نیز تأمین کند.
- همچنین می بایست 
-از طیف گسترده ای از برنامه ها و خدمات پشتیبانی کند.
+ همچنین
+از طیف گسترده‌ای از برنامه ها و خدمات پشتیبانی کند.
  \begin{figure}[H]
@@
 \end{figure}
-\subsection{تاریخچه مخابرات}
-در ابتدا می خواهیم بدانیم که چه چیزی منجر به رفتن محققان به سوی  \lr{5G} شده است. یکی از دلایل مهم، سرعت و نرخ انتقال بیشتری است که در ادامه به آن می پردازیم.
+\subsection{مروری بر نسلهای اخیر مخابرات}
+در ابتدا می خواهیم بدانیم که چه چیزی منجر به رفتن محققان به سوی  \lr{5G} شده است. یکی از دلایل مهم، سرعت و نرخ انتقال بیشتری است که در ادامه به آن می‌پردازیم.
 نیاز بشریت به ارتباط تلفنی (انتقال بدون سیم به صورت زمان حقیقی \LTRfootnote{Real Time} انسان را به سمت نسل اول ارتباطات \lr{1G} سوق داده است.
@@
 همچنین با موفقیت تکنولوژی شبکه های منطقه ای بیسیم، اتصال به داده های اینترنتی مورد توجه عموم مردم قرار گرفت که پلی به سوی نسل سوم ارتباطات \lr{3G} را فراهم نمود.
-به طور منطقی پله ی بعدی گام برداشتن در راستای کوچک شدن لپ تاپ و در آمیختن آن با تلفن که امروزه به صورت تلفن هوشمند\LTRfootnote{smart phone} است و دسترسی به  اینترنت، پهنای باند بالا و داده ها در نقاط مختلف جهان بوده است که \lr{4G} یا نسل چهارم را به همراه داشته است.
-با توجه به افزایش تعداد کاربران تلفن های
-هوشمند و تبلت ها و افزایش نرخ ارسال اطلاعات و داده ها در طی سال
-های اخیر طبق پیش بینی های سیسکو میزان ترافیک \lr{IP} طی سالهای اخیر
+به طور منطقی پله‌ی‌ بعدی گام برداشتن در راستای کوچک شدن لپ تاپ و در آمیختن آن با تلفن که امروزه به صورت تلفن هوشمند\LTRfootnote{smart phone} است و دسترسی به اینترنت، پهنای باند بالا و داده‌ها در نقاط مختلف جهان بوده است که \lr{4G} یا نسل چهارم را به همراه داشته است.
+با توجه به افزایش تعداد کاربران تلفن‌های
+هوشمند و تبلت‌ها و افزایش نرخ ارسال اطلاعات و داده‌ها در طی سالهای اخیر طبق پیش بینی‌های سیسکو میزان ترافیک \lr{IP} طی سالهای اخیر
   چندین برابر افزایش خواهد یافت.
-در نتیجه اپراتورها برای حل این مشکل و خدمات
-دهی بهتر ناچار به افزایش ظرفیت شبکه می باشند.
-در ادامه به طور مختصر به ۵ نسل مخابراتی می پردازیم\cite{Gen}.
-\subsubsection{نسل اول}
-این اولین نسل از فناوری تلفن همراه بود.
+در نتیجه اپراتورها برای حل این مشکل و خدمات‌دهی بهتر ناچار به افزایش ظرفیت شبکه می‌باشند.
+در ادامه به طور مختصر به نسلهای اخیر مخابراتی می پردازیم\cite{Gen}.
+%\subsubsection{نسل اول}
+%این اولین نسل از فناوری تلفن همراه بود.
 اولین نسل شبکه تلفن همراه تجاری در اواخر دهه 70 معرفی شد و استانداردهای کاملاً اجرا شده در دهه 80 تاسیس شد.
@@
 حداکثر سرعت \lr{1G} 2.4 کیلوبیت بر ثانیه است.
-\subsubsection{نسل دوم}
-تلفنهای همراه وقتی از \lr{1G} به \lr{2G} رفتند ، اولین نسخه اصلی خود را دریافت کردند.
+%\subsubsection{نسل دوم}
+%تلفنهای همراه وقتی از \lr{1G} به \lr{2G} رفتند ، اولین نسخه اصلی خود را دریافت کردند.
 تفاوت اصلی بین دو سیستم تلفن همراه (\lr{1G} و \lr{2G}) در این است که سیگنالهای رادیویی مورد استفاده شبکه \lr{1G} آنالوگ هستند ، در حالی که شبکه های
-\lr{2G}
- دیجیتال هستند.
+%\lr{2G}
+% دیجیتال هستند.
 انگیزه اصلی این نسل، تهیه کانال ارتباطی ایمن و مطمئن بود.
@@
 شبکه های مخابراتی سلولی نسل دوم بطور تجاری در سال 1991 توسط رادیولینجا (در حال حاضر بخشی از الیزا اویج) توسط استاندارد \lr{GSM} در فنلاند راه اندازی شد.
-\lr{2G}
-قابلیت هایی از قبیل
-\lr{multiplexing}
-دارد که 
-به چندین کاربر در یک کانال منفرد 
-اجازه ی انتقال داده می دهد.
-انتقال داده و صدا در این نسل وجود داشته است.
-در این نسل مخابرات، 
-سرویسهای اساسی مانند پیام کوتاه، رومینگ داخلی، تماس های کنفرانسی، نگه داشتن تماس و صورتحساب مبتنی بر خدمات معرفی شده است.
+%\lr{2G}
+%قابلیت هایی از قبیل
+%\lr{multiplexing}
+%دارد که 
+%به چندین کاربر در یک کانال منفرد 
+%اجازه ی انتقال داده می دهد.
+%انتقال داده و صدا در این نسل وجود داشته است.
+%در این نسل مخابرات، 
+%سرویسهای اساسی مانند پیام کوتاه، رومینگ داخلی، تماس های کنفرانسی، نگه داشتن تماس و صورتحساب مبتنی بر خدمات معرفی شده است.
 جداسازی هزینه های مبتنی بر تماس های مسافت طولانی و صورتحساب در زمان واقعی نیز از قابلیت های این نسل بود.
-حداکثر سرعت برای سرویس \lr{GPRS}
-\LTRfootnote{General Packet Radio Service}
-\lr{50Kbps}
-و برای سرویس 
-\lr{EDGE}
-\LTRfootnote{Enhanced Data Rates for GSM Evolution}
-\lr{1Mbps}
-می باشد.
-\subsubsection{نسل سوم}
-این نسل مخابراتی استانداردهای بسیاری از فناوری های بیسیم را تعیین نمود.
+%حداکثر سرعت برای سرویس \lr{GPRS}
+%\LTRfootnote{General Packet Radio Service}
+%\lr{50Kbps}
+%و برای سرویس 
+%\lr{EDGE}
+%\LTRfootnote{Enhanced Data Rates for GSM Evolution}
+%\lr{1Mbps}
+%می باشد.
+%\subsubsection{نسل سوم}
+%این نسل مخابراتی استانداردهای بسیاری از فناوری های بیسیم را تعیین نمود.
 مرورگر وب ، ایمیل ، بارگیری ویدیو ، به اشتراک گذاری عکس و سایر فناوری های هوشمند در نسل سوم معرفی شدند که در سال 2001 به طور تجاری معرفی شد.
 اهداف تعیین شده برای ارتباطات سیار نسل سوم، تسهیل ظرفیت بیشتر صدا و داده ، پشتیبانی از طیف گسترده تری از برنامه ها و افزایش انتقال داده با هزینه کمتری بود.
-استاندارد \lr{3G} از فناوری جدیدی به نام
- \lr{UMTS}
- \LTRfootnote{Universal Telecommunications System Mobile}
- به عنوان معماری اصلی شبکه خود 
-استفاده می کند.
-\lr{3G}
- دارای پشتیبانی خدمات چندرسانه ای است.
-\lr{3G}
-  با بهبود چگونگی فشرده سازی صدا در طی تماس، راندمان طیف فرکانس را افزایش داده است، بنابراین تماس همزمان بیشتری می تواند در همان محدوده فرکانس اتفاق بیفتد.
-حداکثر سرعت این نسل 
-\lr{2Mbps}
-و
-حداکثر سرعت نظری برای HSPA + 21.6 Mbps است. 
-\subsubsection{نسل چهارم}
+%استاندارد \lr{3G} از فناوری جدیدی به نام
+% \lr{UMTS}
+% \LTRfootnote{Universal Telecommunications System Mobile}
+% به عنوان معماری اصلی شبکه خود 
+%استفاده می کند.
+%\lr{3G}
+% دارای پشتیبانی خدمات چندرسانه ای است.
+%\lr{3G}
+%  با بهبود چگونگی فشرده سازی صدا در طی تماس، راندمان طیف فرکانس را افزایش داده است، بنابراین تماس همزمان بیشتری می تواند در همان محدوده فرکانس اتفاق بیفتد.
+%حداکثر سرعت این نسل 
+%\lr{2Mbps}
+%و
+%حداکثر سرعت نظری برای HSPA + 21.6 Mbps است. 
+\subsubsection{ نسل چهارم مخابرات}
 \lr{4G}
- یک فناوری بسیار متفاوت در مقایسه با \lr{3G} است و هدف از آن ، فراهم آوردن سرعت بالا ، کیفیت بالا و ظرفیت بالا برای کاربران در عین بهبود امنیت و کاهش هزینه خدمات صوتی و دیتا ، چندرسانه ای و اینترنت از طریق \lr{IP} می باشد.
-برنامه های کاربردی بالقوه و جاری شامل دسترسی به وب موبایل اصلاح شده ، تلفن تلفنی \lr{IP}، خدمات بازی، تلویزیون همراه با کیفیت بالا ، کنفرانس ویدیویی، تلویزیون سه بعدی و محاسبات ابری از قابلیت های پشتیبانی آن می باشد.
+ یک فناوری بسیار متفاوت در مقایسه با \lr{3G} است و هدف از آن، فراهم آوردن سرعت بالا، کیفیت بالا و ظرفیت بالا برای کاربران در عین بهبود امنیت و کاهش هزینه خدمات صوتی و دیتا، چندرسانه ای و اینترنت از طریق \lr{IP} می‌باشد.
+برنامه های کاربردی بالقوه و جاری شامل دسترسی به وب موبایل اصلاح شده، تلفن تلفنی \lr{IP}، خدمات بازی، تلویزیون همراه با کیفیت بالا، کنفرانس ویدیویی، تلویزیون سه بعدی و محاسبات ابری از قابلیت های پشتیبانی آن می باشد.
 
@@
 حداکثر سرعت یک شبکه 4G هنگام حرکت دستگاه 100 مگابیت بر ثانیه یا 1 گیگابیت بر ثانیه برای ارتباطات کم تحرک مانند هنگام ایستادن یا راه رفتن است.
-تأخیر از حدود \lr{300ms} به  \lr{100ms} با کاهش تراکم دست می یابد.
- \subsubsection{نسل پنجم}
+تأخیر از حدود \lr{300ms} به \lr{100ms} با کاهش تراکم دست می‌یابد.
+ \subsubsection{نسل پنجم مخابرات}
+تکنولوژی 5G یک استاندارد صنعتی است که جایگزین استاندارد رایج کنونی یعنی 4G LTE خواهد شد.
+این فناوری پنجمین نسل از استاندارد سلولی است.
+طراحی این استاندارد به گونه‌ای است که سرعت آن از تکنولوژی 4G LTE بسیار سریع تر است.
+البته هدف این استاندارد صرفا افزایش سرعت اتصالات اینترنتی تلفن های هوشمند نیست.
+این استاندارد، اینترنت بی سیم بسیار پر سرعتی را در همه جا و برای همه چیزها از جمله خودروهای متصل، خانه های هوشمند و ابزارهای اینترنت اشیا (IoT)، فراهم خواهد کرد.
+کاهش مصرف انٰرژی  معیاری است که در این نسل به آن توجه شده‌است و دستگاه‌های فرستنده و گیرنده اپراتورها باید در ساعت کم مصرف به حالت صرفه‌جویی انرژی وارد شده و به سرعت فعال شوند که این معیار در نسل چهارم قید نشده بوده‌است.
  با توجه
@@
 \section{مقدمه ای بر ساختار \lr{ORAN}}
-مجازی سازی \lr{RAN} توجه زیادی را از طرف اپراتورها به خود جلب می کند ، زیرا منجر به کاهش هزینه های اپراتور و \lr{opex} می شود و همچنین این امکان را برای آنها فراهم کند تا با سرعت بیشتری قابلیت های جدیدی به شبکه اضافه کنند.
+مجازی سازی \lr{RAN} توجه زیادی را از طرف اپراتورها به خود جلب می‌کند، زیرا منجر به کاهش هزینه‌های اپراتور و \lr{opex} می‌شود و همچنین این امکان را برای آنها فراهم کند تا با سرعت بیشتری قابلیت های جدیدی به شبکه اضافه کنند.
 
@@
 که برای شرکت سیسکو می باشد.
-اگرچه همه این گروه ها می گویند که در حال کار بر روی یک چیز هستند، که اساساً برای باز کردن \lr{RAN} با استفاده از رابط های استاندارد و عناصر شبکه جعبه سفید است، اما در بررسی دقیق تر اختلافاتی نیز وجود دارد.
+اگرچه همه این گروه ها می‌گویند که در حال کار بر روی یک چیز هستند، که اساساً برای باز کردن \lr{RAN} با استفاده از رابط های استاندارد و عناصر شبکه جعبه سفید است، اما در بررسی دقیق تر اختلافاتی نیز وجود دارد.
 

### 2020-09-07 Latex/tehran-thesis/tex/chapter3.tex
add file
add ch4

@@
 $U_v$
-کاربر تک آنتنه می باشند که از سرویس خاصی را درخواست می نماید.
+کاربر تک آنتنه می باشند که سرویس خاصی را درخواست می نماید.
 هر برش شبکه 
@@
 $K_s$
-بلوک های منابع فیزیکی، یک واد توزیع شده و یک واحد مرکزی که شامل \lr{VNF} هایی می باشند.
+بلوک های منابع فیزیکی، یک واحد توزیع شده و یک واحد مرکزی که شامل \lr{VNF} هایی می باشند.
 همچنین برش های شبکه می توانند منابع مشترک داشته باشند.
@@
 در این مدل سیستم، 
-تخصیص منابع فیزیکی به \lr{VNF} ها در نظر کرفته شده است. 
+تخصیص منابع فیزیکی به \lr{VNF} ها در نظر گرفته شده است. 
 در اینجا فرض بر این است که $y_{s,d}$ متغیر صفر و یکی است که نشان میدهد مرکز داده ی $d$ ام به $s$ امین برش متصل است یا نه.
@@
 در این بخش نتایج عددی برای مسئله ی اصلی بیان می‌شود.
+ابتدا برای مسئله‌ی اول نمودارهای شبیه‌سازی را رسم می‌کنیم.
 \begin{table}
@@
 \end{figure}
-در شکل \ref{fig:f1}، نسبت برشهای پذیرفته شده برای دو تعداد مختلف مرکز داده با تعداد برشهای مختلف رسمم شده است. پارامترهای شبیه‌سازی در جدول \ref{table:1} آورده شده است. همچنین داریم 
+در شکل \ref{fig:f1a2}
+بهره‌وری انرژی براساس تعداد بلوکهای منابع فیزیکی برای ۶ سرویس با تعداد کاربر به طور میانگین ۳ تا رسم شده است.
+همانطور که در نمودارها مشخص است با افزایش تعداد PRB، تداخل کاربران کم شده و بهره‌وری انرژی افزایش می‌یابد و الگوریتم پیشنهادی به روش بهینه نزدیک می‌گردد.
+\begin{figure}%[H]
+	\centering
+	\includegraphics[width=\linewidth]{./fig/fig_prb}
+	\caption{بهره‌وری انرژی براساس تعداد بلوکهای منابع فیزیکی}
+	\label{fig:f1a2}
+\end{figure}
+
+حال به نتایج عددی مسئله‌ی دوم می‌پردازیم.
+در شکل \ref{fig:f1}، نسبت برشهای پذیرفته شده برای دو تعداد مختلف مرکز داده با تعداد برشهای مختلف رسم شده است. پارامترهای شبیه‌سازی در جدول \ref{table:1} آورده شده است. همچنین داریم 
  $w_C = 320$،
@@
  همچنین فرض شده که تنها یک مرکز داده می‌تواند هر برش را سرویس دهد. روش ارائه شده در الگوریتم  \ref{alg3} آورده شده و روش بهینه با استفاده از MOSEK بدست می‌آید.
+ وقتی دو مرکز داده یا DC داریم، روش پیشنهادی و روش بهینه تقریباً همان نسبت برش های پذیرفته شده را دارند. اما با افزایش تعداد DC ها به پنج ، عملکرد روش پیشنهادی کاهش می‌یابد.
+ با استفاده از پنج DC ، تفاوت بین روش پیشنهادی و روش بهینه در بدترین حالت (44 برش) حدود 23 درصد است.
 
@@
 \end{small}
-وقتی دو مرکز داده یا DC داریم، روش پیشنهادی و روش بهینه تقریباً همان نسبت برش های پذیرفته شده را دارند. اما با افزایش تعداد DC ها به پنج ، عملکرد روش پیشنهادی کاهش می‌یابد.
-با استفاده از پنج DC ، تفاوت بین روش پیشنهادی و روش بهینه در بدترین حالت (44 برش) حدود 23 درصد است.
 \begin{figure}%[H]

### 2020-09-07 Latex/tehran-thesis/tex/chapter4.tex
add ch4

@@
 برای حل این سیستم از روش یادگیری تقویتی عمیق استفاده می‌کنیم.
-\section{  مدل سیستم و صورت مسئله}
+در بخش اول صورت مسئله‌ی بخش رادیویی نوشته می‌شود. سپس به صورت مسئله و مدل سیستم بخش هسته می‌پردازیم و در نهایت روش حل هر دو مسئله و نتایج عددی آن بیان می‌شود.
+\section{ مدل سیستم و صورت مسئله‌ی اول}
+در این بخش هدف برش شبکه در بخش رادیویی سیستم می‌باشد. دراینجا، مسئله‌ی اول فصل قبلی ساده شده و به روش دینامیکی حل می‌شود.   
 همانند سیستم فصل قبل، فرض می کنیم $S$ برش شبکه داریم که قرار است $V$ سرویس مختلف که شامل کاربرانی است که از سرویس خاص استفاده می‌نمایند را سرویس دهی نماید.
@@
 در بخش اول این مسئله، هدف بیشینه‌سازی تعدای سرویسهای پذیرفته شده می‌باشد. در اینجا فرض براین است که تعداد برشهاس شبکه محدود می‌باشد. فرض می‌کنیم هر سرویس $v$ دارای اولویت $p_v$ می‌باشد. 
-همچنین فرض براین است که هر سرویس شامل ماکسیمم $U-v$ کاربر است و به طور میانگین کاربران آن نیازمند داشتن نرخ بیشتر از $R_v$ و تاخیر کمتر از $D_v$ هستند. درصورتی که کاربری از دسته‌ی اول باشد 
+همچنین فرض براین است که هر سرویس شامل ماکسیمم $U_v$ کاربر است و به طور میانگین کاربران آن نیازمند داشتن نرخ بیشتر از $R_v$ و تاخیر کمتر از $D_v$ هستند. درصورتی که کاربری از دسته‌ی اول باشد 
 $D_v =  M$ 
@@
 که $N$ یک عدد کوچک برای نرخ می‌باشد.
-صورت مسئله بدین صورت می‌باشد.
+صورت مسئله به صورت \eqref{eqmain} می‌باشد.
+در اینجا برای سادگی فرض براین است که هر سرویس به ماکسیمم یک برش شبکه متصل می‌گردد.
+ هدف در اینجا بیشینه سازی تعداد سرویسهای پذیرفته شده توسط برشهای شبکه می‌باشد به صورتی که شرط تاخیر و نرخ سرویس را ضمانت کنند.
 \begin{subequations}
@@
 		\max\limits_{\boldsymbol{a} }   \quad &   \sum_{s=1}^{S}\sum_{v=1}^{V} p_v a_{v,s}\\
-		\text{\lr{subject to}} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
-		&\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
+		\text{\lr{subject to}} \quad & \textstyle \sum_{s=1}^{S} D_s a_{v,s} \leq D_v  \forall v, \\
+		&\textstyle   \sum_{s=1}^{S} R_s a_{v,s} \geq R_v  \forall v \label{eqmain}
 	\end{alignat}
@@
 \end{subequations}
+ برای اینکه معادله‌ی 
+ \eqref{eqmain}
+ را به فرم مسئله‌ی کوله‌پشتی دربیاوریم، از آنجایی که فرض کردیم هر سرویس به ماکسیمم یک برش شبکه متصل می‌شود، می‌توان معادله بدین صورت نوشت:
+ \begin{subequations}
+ 	\begin{alignat}{4}
+ 		\max\limits_{\boldsymbol{a} }   \quad &   \sum_{s=1}^{S}\sum_{v=1}^{V} p_v a_{v,s}\\
+ 		\text{\lr{subject to}} \quad & \textstyle \sum_{s=1}^{S} D_s a_{v,s} \leq D_v  \forall v, \\
+ 		&\textstyle   \sum_{s=1}^{S} \frac{1}{R_s} a_{v,s} \leq \frac{1}{R_v}  \forall v \label{eqmain1}
+ 	\end{alignat}
+ 	\label{constraints2}
+ \end{subequations}
+که در اینجا، معادله‌ی \eqref{eqmain1}
+یک معادله‌ی کوله‌پشتی دو بعدی می‌باشد.
+برای حل این مسئله، از روش یادگیری تقویتی عمیق استفاده می‌شود.
+\section{ مدل سیستم و صورت مسئله‌ی دوم}
+در این بخش سعی شده، مسئله‌ی دوم فصل قبل به صورت ساده شده با روش دینامیکی حل شود. عنوان این مسئله، جاگزاری VNFها برروی مراکز داده می‌باشد.
+فرض براین است که $S$ برش شبکه داریم که هر برش شبکه s
+$s\in \{1,2,...,S \} $
+می‌باشد. هر برش شبکه شامل تعدادی VNF است که
+هر \lr{VNF}
+نیازمند منابع فیزیکی است که شامل حافظه، نگهدارنده و پردازشگر می باشد.
+فرض کنید برای سادگی مسئله برای هر VNF به مقدار کافی حافظه و نگهددارنده در مراکز داده داریم و تنها منبع مورد نیاز برای $f$ امین \lr{VNF} در برش $s$ ام مقدار پردازنده است که به صورت $\bar{\Omega}_{s}^f$ می باشد
+%\begin{equation}
+%	\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \},
+%\end{equation}
+که در اینجا 
+$\bar{\Omega}_{s}^f\in \mathbb{C}^{1}$
+و
+%$\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$
+%به ترتیب نشان دهنده ی مقدار حافظه، نگهدارنده و پردازشگر می باشد.
+%همچنین مقدار کل حافظه، نگهدارنده و پردازشگر برای همه \lr{VNF} ها در یک برش به این صورت تعریف می شود
+\begin{equation}
+	\textstyle \bar{\Omega}_{s}^{tot} = \sum_{f=1}^{M_{s}}\bar{\Omega}_{s}^f %\;\; \mathfrak{z} \in \{M, S, C\}.
+\end{equation}
+همچنین $D_c$ مرکز داده برای سرویس دهی به \lr{VNF} ها می باشد. هر مرکز داده شامل تعدادی سرور برای سرویس دهی است.$M_s$ تعداد کل VNFها در sامین برش شبکه است.
+مقدار پردازشگر 
+%$\tau_{M_{j}}, \tau_{S_{j}}$
+%و
+$\tau_{j} $
+برای 
+$j$
+امین مرکز داده  می‌باشد.
+%\begin{equation*}
+%	\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \},
+%\end{equation*}
+در این مدل سیستم، 
+تخصیص منابع فیزیکی به \lr{VNF} ها در نظر گرفته شده است. 
+در اینجا فرض بر این است که $y_{s,d}$ متغیر صفر و یکی است که نشان میدهد مرکز داده ی $d$ ام به $s$ امین برش متصل است یا نه. 
+همانند فصل قبل، 
+فرض کنید توان مصرفی پردازش باند پایه در هر مرکز داده ی $d$ که به \lr{VNF} های یک برش $s$ متصل می باشد در هر زمان t با   
+$\phi_{s,d}(t)$
+نشان داده شده است.
+بنابراین می توان توان کل سیستم را برای کلیه مرکز داده های فعال که به برش متصل هستند ،بدین صورت نشان داد
+\begin{equation*}
+	\textstyle \phi_{tot}(t) = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}(t).
+\end{equation*}
+همچنین ، یک تابع هزینه برای قرار
+همچنین فرض کنید در هر زمان قرار دادن هر مجموعه‌ی جدید VNFهای برش شبکه s برروی مرکز داده d مقدار انرژی اضافی را بدین صورت به سیستم اعمال کنند.
+\begin{equation*}
+	\textstyle \phi_{diff}(t) = \sum_{s=1}^{S}\sum_{d=1}^{D_c}[y_{s,d}(t)-y_{s,d}(t-1)]^+\phi_{s,d}^{new}(t).
+\end{equation*}
+%%
+تابع هزینه‌ی قرارگیری VNFها برروی DCها بدین صورت است
+\begin{equation}\label{eqpsi}
+	\textstyle  \psi_{tot}(t) = \phi_{tot}(t) + \phi_{diff}(t)
+\end{equation}
+در اینجا هدف کمینه کردن مقدار انرژی کل در هر زمان، با فرض اینکه مجموع VNFهای برشهای تخصیص یافته به هر مرکز داده مقدار کافی پردازنده داشته باشند.
+در اینجا فرض براین است که برشهای شبکه که قبلا به سرویسها اختصاص داده شده، می‌بایست در مرکز داده قرار داده شوند و تعداد مراکز داده به اندازه‌ی کافی زیاد هستند، هدف کمینه کردن انرژی است به صورتی که کمترین تعداد مرکز داده‌ها استفاده شوند.
+\begin{subequations}
+	\begin{alignat}{4}
+		\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
+		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}(t) \geq 1 \forall s, \\
+		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d}  \forall d,, \forall ;  \label{eqomega}
+	\end{alignat}
+\end{subequations}
+این مسئله به فرم مسئله‌ی بسته‌بندی جعبه قابل بیان است.
+\section{حل مسئله به‌روش یادگیری تقویتی}
+دراینجا از روش یادگیری تقویتی در حل دو مسئله‌ی بالا استفاده می‌نماییم.
+در روش یادگیری تقویتی، یک عامل سعی می‌کند رفتار بهینه را در یک محیط مشخص پیدا کند. این پروسه‌ی تعاملی، به صورت پروسه‌ی تصمیم‌گیری مارکوف مدل می‌شود که شامل $(S,A,R,P,\gamma)$  می باشد.
+S
+نشان‌دهنده‌ی ماتریس فضای حالت و A بردار رفتار می‌باشد. R نیز پاداش عمل است. 
+$P(.|s,a)$
+احتمال انتقال و
+ $\gamma \in (0,1]$
+ فاکتور تخفیف می‌باشد.
+ سیاست 
+$\Pi(.|s)$
+نگاشتی از حالت به توزیع اعمال می‌باشد.
+تابع مقدار-حالت برای حالت s تحت سیاست $\Pi(.|s)$ را با  
+$V^{\Pi}(s)$
+نشان می‌دهند که مقدار بازده مورد انتظار در حالت s تحت سیاست $\Pi(.|s)$
+می‌باشد. مقدار ارزش انجام عمل a در حالت s تحت سیاست $\Pi(.|s)$ 
+را با
+ $Q^{\Pi}(s,a)$
+ نمایش می‌دهیم.
+ که روابط زیر را براین اساس داریم.
+ \begin{equation}
+	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[\sum_{t=0}^{\infty}\gamma^tR_t|S_0=s]
+ \end{equation}
+و تابع ارزش عمل بدین صورت است
+
+ \begin{equation}
+	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[\sum_{t=0}^{\infty}\gamma^tR_t|S_0=s,A_0=a]
+\end{equation}
+  که در اینجا 
+  $\mathbb{E}$
+  میانگین می‌گیرد.
+  باتوجه به رابطه‌ی بلمن، داریم:
+ \begin{equation}
+	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[R+\gamma V^{\Pi}(s')]
+\end{equation}  
+  و داریم:
+   \begin{equation}
+  	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[R+\gamma Q^{\Pi}(s',a')]
+  \end{equation}  
+که دراینجا $s'$
+و $a'$
+قابل اتخاذ از 
+$P(.|s,a)$
+و سیاست
+$\Pi(.|s')$
+هستند.
+هدف یادگیری تقویتی، بدست‌آوردن سیاست بهیته می‌باشد به صورتی که 
+$Q^{\Pi}(s,a)$
+بیشینه شود.
+مقدار بهینه‌ی تابع ارزش عمل در رابطه‌ی بلمن بدین صورت است
+
+\begin{equation}
+	Q^{*}(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q^{*}(s',a')]
+\end{equation} 
+همچنین در صورت تعریف اپراتور $T^*$ بلمن داریم
+\begin{equation}
+	T^{*}Q(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q(s',a')]
+\end{equation} 
+که به صورت

### 2020-09-08 Latex/tehran-thesis/tex/chapter3.tex
change fig

@@
 در شکل \ref{fig:f1a}، بهره‌وری انرژی برای دو سری تعداد سرویس مختلف با تعداد کاربر متفاوت در هر سرویس بدست‌آمده‌است.
-پارامترهای شبیه‌سازی در جدول \ref{table:1a} قرار داده‌شده‌است.
+پارامترهای شبیه‌سازی در جدول \ref{table:1a} قرار داده‌شده‌است. تعداد منابع فیزیکی ۱۰ تا می‌باشد.
 روش بهینه برای بدست آوردن $\boldsymbol{A}$ توسط MOSEK بدست آمده و برای بدست آوردن $\boldsymbol{P}$ از CVX در متلب استفاده شده است و به صورت متناوب این دو ماتریس به‌روزرسانی می‌شوند. 
@@
 	\label{fig:f1a2}
+\end{figure}
+
+در شکل \ref{fig:f1a3}
+بهره‌وری انرژی براساس تعداد سرویسای مختلف با فرض وجود ۲ کاربر در هر سرویس به طور میانگین، رسم شده است.
+همانطور که در نمودارها مشخص است با افزایش تعداد سرویسها، بهره‌وری انرژی که مجموع نرخهای کاربران برروی توان آن است، افزایش می‌یابد و الگوریتم پیشنهادی به روش بهینه به نسبت نزدیک است‌.
+\begin{figure}%[H]
+	\centering
+	\includegraphics[width=\linewidth]{./fig/fig_service}
+	\caption{بهره‌وری انرژی براساس تعداد سرویسهای مختلف }
+	\label{fig:f1a3}
 \end{figure}

### 2020-09-08 Latex/tehran-thesis - Copy/tex/chapter2.tex
change fig and ch 5

--- 2020-09-04 Latex/tehran-thesis/tex/chapter2.tex
@@
 در این بخش مروری بر حل مسائل توسط مقالات می نماییم.
-\subsection{ مسئله ی کوله پشتی }
+ابتدا به دو مسئله ی معروف NP-Hard
+اشاره می کنیم سپس به حل مسائل با استفاده از روش یادگیری تقویتی می پردازیم.
+\subsection{مسائل Np-Hard}
+در اینجا به دو مسئله ی کوله پشتی و بسته بندی جعبه می پردازیم.
+\subsubsection{ مسئله ی کوله پشتی }
 یکی از مسائل پیش رو، مسئله ی کوله پشتی \LTRfootnote{knapsack}
@@
 راه حل کنترل پذیرش به یک مسئله کوله پشتی هندسی (دو بعدی) ترسیم شده و دو الگوریتم کم پیچیدگی به ترتیب برای درخواست های برش شبکه منظم و نامنظم طراحی شده اند.
-\subsection{مسئله ی بسته بندی جعبه}
+\subsubsection{مسئله ی بسته بندی جعبه}
  در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می باشد.

### 2020-09-08 Latex/tehran-thesis - Copy/tex/chapter4.tex
change fig and ch 5

--- 2020-09-07 Latex/tehran-thesis/tex/chapter4.tex
@@
 در این فصل هدف تخصیص برش شبکه به صورت می‌باشد.
-در فصل قبلی مدل سیستم به طور کامل نوشته شده است و در حالت آفلاین حل گردیده است، در این فصل پارامترها مورد نیاز را نسبت به فصل قبلی کمتر کرده و با استفاده از روش دینامیکی به حل سیستم می‌پردازیم.
+در فصل قبلی مدل سیستم به طور کامل نوشته شده است و در حالت آفلاین حل گردیده است، در این فصل پارامترها مورد نیاز را نسبت به فصل قبلی کمتر کرده و با استفاده از روش دینامیکی در هر لحظه از زمان به حل سیستم می‌پردازیم.
 برای حل این سیستم از روش یادگیری تقویتی عمیق استفاده می‌کنیم.
@@
 صورت مسئله به صورت \eqref{eqmain} می‌باشد.
-در اینجا برای سادگی فرض براین است که هر سرویس به ماکسیمم یک برش شبکه متصل می‌گردد.
+در اینجا برای سادگی فرض براین است که هر سرویس به ماکسیمم یک برش شبکه متصل می‌گردد. در اینجا هدف حل مسئله در هر اسلات زمانی t می‌باشد.
  هدف در اینجا بیشینه سازی تعداد سرویسهای پذیرفته شده توسط برشهای شبکه می‌باشد به صورتی که شرط تاخیر و نرخ سرویس را ضمانت کنند.
@@
 	\begin{alignat}{4}
-		\max\limits_{\boldsymbol{a} }   \quad &   \sum_{s=1}^{S}\sum_{v=1}^{V} p_v a_{v,s}\\
-		\text{\lr{subject to}} \quad & \textstyle \sum_{s=1}^{S} D_s a_{v,s} \leq D_v  \forall v, \\
-		&\textstyle   \sum_{s=1}^{S} R_s a_{v,s} \geq R_v  \forall v \label{eqmain}
+		\max\limits_{\boldsymbol{a}(t) }   \quad &   \sum_{s=1}^{S(t)}\sum_{v=1}^{V(t)} p_v a_{v,s}(t)\\
+		\text{\lr{subject to}} \quad & \textstyle \sum_{s=1}^{S(t)} D_s(t) a_{v,s} \leq D_v(t)  \forall v, \\
+		&\textstyle   \sum_{s=1}^{S(t)} R_s(t) a_{v,s}(t) \geq R_v(t)  \forall v \label{eqmain}
 	\end{alignat}
@@
  	\begin{alignat}{4}
- 		\max\limits_{\boldsymbol{a} }   \quad &   \sum_{s=1}^{S}\sum_{v=1}^{V} p_v a_{v,s}\\
- 		\text{\lr{subject to}} \quad & \textstyle \sum_{s=1}^{S} D_s a_{v,s} \leq D_v  \forall v, \\
- 		&\textstyle   \sum_{s=1}^{S} \frac{1}{R_s} a_{v,s} \leq \frac{1}{R_v}  \forall v \label{eqmain1}
+		\max\limits_{\boldsymbol{a}(t) }   \quad &   \sum_{s=1}^{S(t)}\sum_{v=1}^{V(t)} p_v a_{v,s}(t)\\
+		\text{\lr{subject to}} \quad & \textstyle \sum_{s=1}^{S(t)} D_s(t) a_{v,s} \leq D_v(t)  \forall v, \\
+ 		&\textstyle   \sum_{s=1}^{S(t)} \frac{1}{R_s(t)} a_{v,s}(t) \leq \frac{1}{R_v(t)}  \forall v \label{eqmain1}
  	\end{alignat}
@@
 	\begin{alignat}{4}
-		\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
+		\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})(t)\\
 		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}(t) \geq 1 \forall s, \\
@@
 \end{equation} 
-که به صورت
+که به صورت تکراری اعمال این اپراتور 
+$Q_{t+1}(s,a) \leftarrow T^{*}Q(s,a) $
+منجر به همگرا شدن 
+$Q_{t}(s,a) \rightarrow Q^*(s,a)$
+ و
+ $t \rightarrow \infty $
+می‌شود
+\cite{montague1999reinforcement,gan1}.
+در ابعاد بالاتر، بهتر است از تابع تقریبی استفاده
+شود. فرض کنید 
+$Q_{\theta}(s,a)$
+تابع تقریب با پارامتر $\theta$
+می‌باشد که تقریبی از جدول مقدار عمل با (s,a)
+می‌باشد. هدف این بهینه‌سازی، بدست‌آوردن $\theta$
+است به طوری که 
+$Q_{\theta}(s,a) \approxeq Q^{*}(s,a)$
+و مقدار بهینه، به طور تکراری با اعمال اپراتور $T^*$
+بدست می‌آید. 
+مقدار بهینه‌ی 
+$\theta$
+قابل دستیابی با استفاده از مینیمم کردم خطای تفاوت زمانی (TD-error)
+برروی (s,a,r,s') می‌باشد که به طور رندم انتخاب می‌شوند.
+\begin{equation}
+\zeta^2 = [r + \gamma \max_{a' \in A}{Q_{\theta}(s',a')}-Q_{\theta}(s,a)]^2
+\end{equation}
+روشهای مخنلفی برای دستیابی به مینیمم خطا هست که ما در ادامه‌ی کار از روش Q-learnng استفاده می‌کنیم.
+در روش Q-learning در هر بروزرسانی تابع Q داریم:
+\begin{equation}
+	Q(s_{t+1},a_{t+1}) = Q(s_t,a_t)+\alpha[ r_{t+1} + \gamma \max_{a \in A}{Q(s_{t+1},a)}-Q(s_t,a_t)]
+\end{equation}
+که دراینجا، $\alpha$
+نرخ یادگیری می‌باشد.
+\subsection{نتایج عددی مسئله‌ی اول}
+در این بخش، برای مسئله‌ی اول حالت، عامل و پاداش را تعیین می‌نماییم و سپس نتایج عملی را نشان می‌دهیم.
+در این مسئله، عامل، orchestrator است که وظیفه‌ی مدیریت شبکه را برعهده دارد.
+همچنین، حالت در هر بازه‌ی زمانی برشهایی از شبکه است که به سرویسها متصل شده و اینکه کدام برش به کدام سرویس متصل است.
+پاداش طوری تعیین شده که بیشترین تعداد سرویسها پذیرفته شود به طوریکه شرط تاخیر و نرخ برآورده گردد.
+
+\subsection{نتایج عددی مسئله‌ی دوم} 
+در این بخش، برای مسئله‌ی دوم حالت، عامل و پاداش را تعیین می‌نماییم و سپس نتایج عملی را نشان می‌دهیم.
+در این مسئله، عامل، orchestrator است که وظیفه‌ی مدیریت شبکه را برعهده دارد.
+همچنین، حالت در هر بازه‌ی زمانی برشهایی از شبکه است که به مراکزداده متصل شده و اینکه کدام برش به کدام مرکز داده متصل است.
+پاداش طوری تعیین شده که کمترین تعداد مراکز داده استفاده گردد و هر لحظه کمترین تعداد مرکز داده‌ی خاموش، روشن شود.
+\section{نتیجه‌گیری}
+در این فصل، دو مسئله‌ی فصل قبلی به صورت ساده شده نوشته شد و مسئله‌ی اول در بخش رادیویی از جنس کوله‌پشتی و مسئله‌ی دوم در بخش هسته از نوع 
+بسته‌بندی جعبه می‌باشد.
+این دو مسئله به صورت دینامیکی در هر لحظه از زمان حل شده‌اند.
+برای حل این دو مسئله از روش یادگیری تقویتی عمیق استفاده شده و حالتها و اعمال بیان برای یک عامل در این مسئله بیان گرده است.
+نتایج عملی آن نیز رسم گردید.

### 2020-09-08 Latex/tehran-thesis - Copy/tex/chapter5.tex
change fig and ch 5

\chapter{پیشنهادات و کارهای آتی}
\section{مقدمه}
در فصل اول، مقدمه‌ای بر مفاهیم مورد استفاده را بیان کردیم و در مورد نسل پنجم مخابرات و مفاهیم آن صحبت نمودیم. سپس در فصل دوم مروری بر کارهای انجام شده کردیم و مقالات مرتبط با برش شبکه و شبکه‌های دسترسی باز و قرارگیری توابع مجازی شبکه را بیان نمودیم تا مروری بر چالشهای مطرح شده نسل پنجم مخابرات کرده و حل این چالشها را مورد بررسی قرار دادیم . در فصل سوم صورت مسئله‌ای در زمینه‌ی برش شبکه در شبکه‌های دسترسی باز، معرفی کرده و با روش ابتکاری، آن را حل نمودیم و نتایج را با مقدار بهینه مقایسه کردیم.
در  فصل چهارم، دو مسئله‌ی بیان شده در فصل سوم را به صورت کاملا ساده با روش یادگیری عمیق تقویتی به صورت دینامیکی و در هر بازه‌ی زمان حل نمودیم. این دو مسئله، MDP \LTRfootnote{Markov Decision Processs}
بوده و قابل حل با این روش هستند. 
حال در این فصل در مورد مزایا و معایب کارهای انجام شده در فصل سوم و چهارم صحبت کرده و کارهای آتی و پیشنهادات را بیان می‌کنیم.
\section{نتیجه‌گیری}
در اینجا، مسئله‌ی برش شبکه در بخش رادیویی و قرارگیری توابع مجازی شبکه برروی مراکز داده باهم مورد بررسی قرار گرفته شد.
برای حل این مسئله، ابتدا مسئیله به دو بخش مخنلف شکسته شد که در بخش اول، تخصیص برش شبکه به کاربران سرویسها و تخصیص توان حل شده و پس از آن، برشهایی از شبکه که به سرویس اختصاص داده شده را به مراکز داده نگاشت می‌دهیم.
در این مسئله، تاخیر و نرخ هر کاربر در سرویس مورد بررسی قرار گرفته شده و چالش تخصیص منابع که شامل برش بخش رادیویی به هر سرویس است و جاگیری توابع شبکه حل می‌شود.
 الگوریتم ارائه شده سرعت بسیار بیشتری از الگوریتم بهینه که با MOSEK و CVX بدست می‌آید، دارد.
 سپس مسئله به صورت ساده‌تر برای حالت دینامیکی با روش یادگیری تقویتی حل گردیده است. 
 \subsection{مزایای این چالش و حل آن}
 در مسئله‌ی بیان شده‌ی فصل سوم، مدل سیستم به صورت دقیق بیان شده و نرخ کاربر، ظرفیت لینک fronthaul و تاخیر به طور دقیق مورد بررسی قرار گرفته شده است. همچنین مسئله به واقعیت نزدیکی زیادی دارد. همچنین الگوریتم ابتکاری تعریف شده در فصل سوم برای حالتی که تداخل به نسبت کم باشد به حالت بهینه بسیار نزدیک است. در فصل چهارم همین مسئله با فرض اینکه سرویسها نیازمند تاخیر کم یا نرخ بالا هستند به صورت پارامتریک در هر لحظه از زمان حل می‌گردند. 
 در بخش بعدی چالشهای قرارگیری توابع مجازی برروی مراکز داده به طور دقیق بررسی شده و ‌در فصل چهارم این مسئله به صورت دینامیکی در هر لحظه حل گردیده است. در حل مسئله در حالت دینامیکی سعی براین است که مراکز داده کمترنی انرژی را مصرف نموده و از هدر رفت انرژی بپرهیزیم.
 \subsection{معایب  پروژه انجام شده}
 در فصل سوم از الگوریتم ابتکاری در این کار استفاده شده است. زمانی که تعداد بلوکهای منابع فیزیکی به نسبت کاربران بسیار کم باشد و تداخل به شدت زیاد گردد، الگوریتم مسئله‌ی اول به خوبی قادر به پاسخ‌گویی نیست و از حالت بهینه فاصله ‌می‌گردد. همچنین در فصل چهارم صورت مسئله بسیار ساده‌تر از واقعیت است و مسئله در حالت دینامیکی برای این حالت حل گردیده است.
 در مسئله‌ی دوم، زمانی که تعداد مراکز داده زیاد گردد فاصله‌ی حالت بهینه از الگوریتم ابتکاری زیاد شده است. 
 \subsection{نوآوری‌های این پروژه}
 در این پروژه، تخصیص توان و برش شبکه در شبکه‌های دسترسی باز مورد بررسی قرار گرفته است.
 ما مسئله‌ی اختصاص UE به خدمات، خدمات به برش‌ها و منابع فیزیکی بی سیم و همچنین مرکز داده به برش‌ها را به عنوان یک مشکل بهینه سازی فرمول‌بندی کرده‌ایم. سپس با ارائه‌ی روشهای ابتکاری، به حل آنها پرداختیم. در نهایت مسئله‌ی ساده شده را در حالت دینامیکی و متغیر با زمان حل کردیم.
 \section{پیشنهادات}

### 2020-09-08 Latex/tehran-thesis - Copy/tex/enTitle.tex
change fig and ch 5

% !TeX root=../main.tex
% در این فایل، عنوان پایان‌نامه، مشخصات خود و چکیده پایان‌نامه را به انگلیسی، وارد کنید.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\latinuniversity{University of Tehran}
\latincollege{College of Engineering}
\latinfaculty{Faculty of ٍElectrical and Computer Engineering}
\latindepartment{Network department}
\latinsubject{ٍElectrical Engineering}
\latinfield{Communication and Network}
\latintitle{Joint Power Allocation and Network Slicing in an
End-to-End ORAN System}
\firstlatinsupervisor{Dr. Shahmansouri}
%\secondlatinsupervisor{Second Supervisor}
%\firstlatinadvisor{First Advisor}
%\secondlatinadvisor{Second Advisor}
\latinname{Mojdeh}
\latinsurname{Karbalaee Motalleb}
\latinthesisdate{December 2019}
\latinkeywords{Writing Thesis, Template, \LaTeX, \XePersian}
\en-abstract{
This thesis studies on writing projects, theses and dissertations using tehran-thesis class. It ...
}

### 2020-09-09 Latex/tehran-thesis/tex/chapter1.tex
add file

@@
 \chapter{مقدمه}
-\subsection{مقدمه ای بر \lr{5G} }
+\section{مقدمه ای بر \lr{5G} }
 \lr{5G}،
 مخابرات نسل پنجم
-سیستم های بیسیم \LTRfootnote{Wireless} وشبکه های مخابراتی بعد از نسل چهارم می‌باشد که تکاملی از لایه‌ی فیزیکی در تکنولوژی شبکه‌های مخابراتی سیار همانند \lr{LTE} است که نسبت به \lr{4G} سرعت و پوشش بهتری را فراهم می‌کند.
+سیستمهای بیسیم \LTRfootnote{Wireless} وشبکه‌های مخابراتی بعد از نسل چهارم می‌باشد که تکاملی از لایه‌ی فیزیکی در تکنولوژی شبکه‌های مخابراتی سیار همانند \lr{LTE} است که نسبت به \lr{4G} سرعت و پوشش بهتری را فراهم می‌کند.
 \lr{5G}
-نوع جدیدی از شبکه را ایجاد می‌کند که به منظور اتصال تقریبا همه و همه چیز با هم از جمله ماشین ها، اشیاء و دستگاه ها ساخته شده است.
+نوع جدیدی از شبکه را ایجاد می‌کند که به منظور اتصال تقریبا همه و همه چیز با هم از جمله ماشینها، اشیاء و دستگاه‌ها ساخته شده است.
 \lr{5G}
- فناوری بی سیم برای ارائه سرعت داده های چند گیگابیت بر ثانیه، تأخیر فوق العاده کم، قابلیت اطمینان بیشتر، ظرفیت شبکه گسترده، افزایش در دسترس بودن و تجربه کاربری یکنواخت تر به کاربران بیشتر است.
-عملکرد بالاتر و بهره وری بهبود یافته باعث افزایش تجربیات کاربر جدید شده و صنایع جدیدی را به هم متصل می کند.
+ فناوری بی سیم برای ارائه سرعت داده‌های چند گیگابیت بر ثانیه، تأخیر فوق العاده کم، قابلیت اطمینان بیشتر، ظرفیت شبکه گسترده، افزایش در دسترس بودن و تجربه کاربری یکنواخت تر به کاربران بیشتر است.
+عملکرد بالاتر و بهره وری بهبود یافته باعث افزایش تجربیات کاربر جدید شده و صنایع جدیدی را به هم متصل می‌کند.
 
 تکنولوژی سیگنال  \lr{5G} برای پوشش فراگیرتر و بازدهی بهتر سیگنال ایجاد شده است.
-این پیشرفت ها منجر به تغییراتی از قبیل\lr{IOT} \LTRfootnote{Internet of Things} و \lr{Pervasive Computing} در آینده ی نزدیک خواهد شد.
-همچنین \lr{5G} منجر به توسعه و بهبود سرویس های مخابراتی و اینترنتی سیار و در ورای آن، ایجاد تجربه‌ی بهتری برای مصرف کنندگان خواهد شد.\newline
+این پیشرفتها منجر به تغییراتی از قبیل\lr{IOT} \LTRfootnote{Internet of Things} و \lr{Pervasive Computing} در آینده ی نزدیک خواهد شد.
+همچنین \lr{5G} منجر به توسعه و بهبود سرویسهای مخابراتی و اینترنتی سیار و در ورای آن، ایجاد تجربه‌ی بهتری برای مصرف کنندگان خواهد شد.\newline
 برای توسعه‌ی اینترنت سیار و \lr{IOT}، نیازمند استفاده از شبکه‌ی نسل پنجم هستیم تا به سادگی منجر به دسترسی شبکه برای ارتباط انسان‌ها با یکدیگر و ارتباط ماشین با انسان گردد.
@@
 \lr{5G}
- در سه نوع سرویس اصلی متصل از جمله پهن باند تلفن همراه، IoT عظیم و ارتباطات مهم برای ماموریت استفاده می شود.
+ در سه نوع سرویس اصلی متصل از جمله پهن باند تلفن همراه، IoT عظیم و ارتباطات مهم برای ماموریت استفاده ‌‌‌‌‌.
 \begin{enumerate}
@@
 \lr{(eMBB)}
- برای مقابله با نرخ داده های بسیار زیاد، تراکم بالای کاربران و ظرفیت ترافیک بسیار بالا برای سناریوهای مختلف و همچنین پوشش یکپارچه و سناریوهای تحرک بالا با نرخ داده‌های استفاده شده بهبود یافته است.
+ برای مقابله با نرخ داده‌های بسیار زیاد، تراکم بالای کاربران و ظرفیت ترافیک بسیار بالا برای سناریوهای مختلف و همچنین پوشش یکپارچه و سناریوهای تحرک بالا با نرخ داده‌های استفاده شده بهبود یافته است.
 \item
@@
 \lr{IoT}،
-   برای تعداد بسیار زیاد دستگاههای متصل به مصرف کم و نرخ داده کم نیازمند می‌باشد.
+   برای تعداد بسیار زیاد دستگاه‌های متصل به مصرف کم و نرخ داده کم نیازمند می‌باشد.
 \item 
@@
  \lr{(URLLC)}
- برای برنامه های کاربردی مهم برای ایمنی و ماموریت
+ برای برنامه‌های کاربردی مهم برای ایمنی و ماموریت
   مورد توجه است.
@@
 \lr{5G}
- کمتر به زیرساخت های \lr{4G} وابسته می‌شود و طیف بیشتری در دسترس قرار می‌دهد،
- تخمین ها سرعت بارگیری را حداکثر 1000 برابر سریعتر از \lr{4G} در نظر دارد، که بالقوه از 
+ کمتر به زیرساختهای \lr{4G} وابسته می‌شود و طیف بیشتری در دسترس قرار می‌دهد،
+ تخمینها سرعت بارگیری را حداکثر 1000 برابر سریعتر از \lr{4G} در نظر دارد، که بالقوه از 
  \lr{10Gbps} 
-بیشتر است، که به شما امکان می دهد تا در کمتر از یک ثانیه فیلم کامل
+بیشتر است، که به شما امکان می‌دهد تا در کمتر از یک ثانیه فیلم کامل
 \lr{HD}
    را بارگیری کنید.
-   برخی تخمین ها محافظه کارانه تر هستند، اما حتی محافظه کارانه‌ترین تخمین نیز این نسل را چندین ده برابر سریعتر از \lr{4G} قرار می دهد.
+   برخی تخمینها محافظه کارانه تر هستند، اما حتی محافظه کارانه‌ترین تخمین نیز این نسل را چندین ده برابر سریعتر از \lr{4G} قرار می‌دهد.
 دلایل نیاز به نسل پنجم اینترنت به طور خلاصه در ادامه بیان شده است \citep{etsi}.
 \begin{itemize}
-\item ترافیک داده های تلفن همراه به دلیل پخش ویدئو به سرعت، رو به افزایش است.
+\item ترافیک داده‌های تلفن همراه به دلیل پخش ویدئو به سرعت، رو به افزایش است.
 \item با در اختیار داشتن چندین دستگاه به طور همزمان، هر کاربر تعداد فزاینده‌ای از اتصالات را در اختیار دارد.
 \item اینترنت اشیاء به شبکه‌هایی نیاز دارد که میلیاردها دستگاه را اداره کنند.
-\item با وجود تعداد فزاینده‌ای از دستگاه های ارتباطی و افزایش ترافیک داده‌ها، هم دستگاه‌ها و هم شبکه‌ی  
+\item با وجود تعداد فزاینده‌ای از دستگاه‌های ارتباطی و افزایش ترافیک داده‌ها، هم دستگاه‌ها و هم شبکه‌ی  
 آن
@@
 \item 
- به دلیل تحت فشار قرار گرفتن اپراتورهای شبکه برای کاهش هزینه‌های عملیاتی و همچنین به دلیل اینکه کاربران به تعرفه های نرخ مسطح عادت می‌کنند و مایل نیستند مبلغ بیشتری بپردازند.
-\item فناوری ارتباطات سیار می تواند موارد استفاده جدیدی را ایجاد کند (به عنوان مثال موارد تاخیر فوق العاده کم یا قابلیت اطمینان بالا) و برنامه های جدید برای صنعت که منجر به درآمدزایی بیشتر اپراتورها می گردد.
+ به دلیل تحت فشار قرار گرفتن اپراتورهای شبکه برای کاهش هزینه‌های عملیاتی و همچنین به دلیل اینکه کاربران به تعرفه‌های نرخ مسطح عادت می‌کنند و مایل نیستند مبلغ بیشتری بپردازند.
+\item فناوری ارتباطات سیار میتواند موارد استفاده جدیدی را ایجاد کند (به عنوان مثال موارد تاخیر فوق العاده کم یا قابلیت اطمینان بالا) و برنامه‌های جدید برای صنعت که منجر به درآمدزایی بیشتر اپراتورها می‌گردد.
 \end{itemize}
@@
  همچنین
-از طیف گسترده‌ای از برنامه ها و خدمات پشتیبانی کند.
+از طیف گسترده‌ای از برنامه‌ها و خدمات پشتیبانی کند.
  \begin{figure}[H]
@@
     \includegraphics[width=0.8\textwidth]{./fig/etsi}
-  \caption{مقایسه قابلیت های کلیدی
+  \caption{مقایسه قابلیتهای کلیدی
 \lr{IMT-Advanced}
@@
 \end{figure}
-\subsection{مروری بر نسلهای اخیر مخابرات}
-در ابتدا می خواهیم بدانیم که چه چیزی منجر به رفتن محققان به سوی  \lr{5G} شده است. یکی از دلایل مهم، سرعت و نرخ انتقال بیشتری است که در ادامه به آن می‌پردازیم.
+
+ یکی از دلایل مهم رفتن محققان به سمت نسل پنجم، سرعت و نرخ انتقال بیشتری است که در ادامه به آن می‌پردازیم.
 نیاز بشریت به ارتباط تلفنی (انتقال بدون سیم به صورت زمان حقیقی \LTRfootnote{Real Time} انسان را به سمت نسل اول ارتباطات \lr{1G} سوق داده است.
-نسل دوم ارتباطات \lr{2G} با سرویس های انتقال پیام کوتاه ایجاد شد.
-همچنین با موفقیت تکنولوژی شبکه های منطقه ای بیسیم، اتصال به داده های اینترنتی مورد توجه عموم مردم قرار گرفت که پلی به سوی نسل سوم ارتباطات \lr{3G} را فراهم نمود.
+نسل دوم ارتباطات \lr{2G} با سرویسهای انتقال پیام کوتاه ایجاد شد.
+همچنین با موفقیت تکنولوژی شبکه‌های منطقه ای بیسیم، اتصال به داده‌های اینترنتی مورد توجه عموم مردم قرار گرفت که پلی به سوی نسل سوم ارتباطات \lr{3G} را فراهم نمود.
 به طور منطقی پله‌ی‌ بعدی گام برداشتن در راستای کوچک شدن لپ تاپ و در آمیختن آن با تلفن که امروزه به صورت تلفن هوشمند\LTRfootnote{smart phone} است و دسترسی به اینترنت، پهنای باند بالا و داده‌ها در نقاط مختلف جهان بوده است که \lr{4G} یا نسل چهارم را به همراه داشته است.
@@
 در نتیجه اپراتورها برای حل این مشکل و خدمات‌دهی بهتر ناچار به افزایش ظرفیت شبکه می‌باشند.
-در ادامه به طور مختصر به نسلهای اخیر مخابراتی می پردازیم\cite{Gen}.
+در ادامه به طور مختصر به نسلهای اخیر مخابراتی می‌پردازیم\cite{Gen}.
 %\subsubsection{نسل اول}
@@
 اولین نسل شبکه تلفن همراه تجاری در اواخر دهه 70 معرفی شد و استانداردهای کاملاً اجرا شده در دهه 80 تاسیس شد.
-استرالیا در سال 1987 توسط \lr{Telecom} (که امروزه با عنوان \lr{Telstra} شناخته می شود) معرفی شد ، استرالیا اولین شبکه تلفن همراه خود را با استفاده از یک سیستم آنالوگ \lr{1G} دریافت کرد.
-\lr{1G} یک فناوری آنالوگ است و به طور کلی تلفن ها از باتری ضعیف برخوردار هستند و کیفیت صدا بدون امنیت بسیار زیاد بود و گاهی اوقات تماس های کاهش یافته را تجربه می کنید.
-این استانداردهای ارتباطی آنالوگ ارتباطی است که در دهه 1980 معرفی شد و تا زمانی که جایگزین ارتباطات دیجیتال \lr{2G} شود ، ادامه یافت.
+استرالیا در سال 1987 توسط \lr{Telecom} (که امروزه با عنوان \lr{Telstra} شناخته می‌شود) معرفی شد، استرالیا اولین شبکه تلفن همراه خود را با استفاده از یک سیستم آنالوگ \lr{1G} دریافت کرد.
+\lr{1G} یک فناوری آنالوگ است و به طور کلی تلفنها از باتری ضعیف برخوردار هستند و کیفیت صدا بدون امنیت بسیار زیاد بود و گاهی اوقات تماسهای کاهش یافته را تجربه میکنید.
+این استانداردهای ارتباطی آنالوگ ارتباطی است که در دهه 1980 معرفی شد و تا زمانی که جایگزین ارتباطات دیجیتال \lr{2G} شود، ادامه یافت.
 حداکثر سرعت \lr{1G} 2.4 کیلوبیت بر ثانیه است.
 %\subsubsection{نسل دوم}
-%تلفنهای همراه وقتی از \lr{1G} به \lr{2G} رفتند ، اولین نسخه اصلی خود را دریافت کردند.
-تفاوت اصلی بین دو سیستم تلفن همراه (\lr{1G} و \lr{2G}) در این است که سیگنالهای رادیویی مورد استفاده شبکه \lr{1G} آنالوگ هستند ، در حالی که شبکه های
+%تلفنهای همراه وقتی از \lr{1G} به \lr{2G} رفتند، اولین نسخه اصلی خود را دریافت کردند.
+تفاوت اصلی بین دو سیستم تلفن همراه (\lr{1G} و \lr{2G}) در این است که سیگنالهای رادیویی مورد استفاده شبکه \lr{1G} آنالوگ هستند، در حالی که شبکه‌های
 %\lr{2G}
@@
 این نسل همچنین مفهوم \lr{CDMA} و \lr{GSM} را پیاده سازی کرد که خدماتی مانند پیامک را ارائه داده است.
-شبکه های مخابراتی سلولی نسل دوم بطور تجاری در سال 1991 توسط رادیولینجا (در حال حاضر بخشی از الیزا اویج) توسط استاندارد \lr{GSM} در فنلاند راه اندازی شد.
+شبکه‌های مخابراتی سلولی نسل دوم بطور تجاری در سال 1991 توسط رادیولینجا (در حال حاضر بخشی از الیزا اویج) توسط استاندارد \lr{GSM} در فنلاند راه اندازی شد.
 %\lr{2G}
-%قابلیت هایی از قبیل
+%قابلیتهایی از قبیل
 %\lr{multiplexing}
@@
 %به چندین کاربر در یک کانال منفرد 
-%اجازه ی انتقال داده می دهد.
+%اجازه ی انتقال داده می‌دهد.
 %انتقال داده و صدا در این نسل وجود داشته است.
 %در این نسل مخابرات، 
-%سرویسهای اساسی مانند پیام کوتاه، رومینگ داخلی، تماس های کنفرانسی، نگه داشتن تماس و صورتحساب مبتنی بر خدمات معرفی شده است.
-جداسازی هزینه های مبتنی بر تماس های مسافت طولانی و صورتحساب در زمان واقعی نیز از قابلیت های این نسل بود.
+%سرویسهای اساسی مانند پیام کوتاه، رومینگ داخلی، تماسهای کنفرانسی، نگه داشتن تماس و صورتحساب مبتنی بر خدمات معرفی شده است.
+جداسازی هزینه‌های مبتنی بر تماسهای مسافت طولانی و صورتحساب در زمان واقعی نیز از قابلیتهای این نسل بود.
 %حداکثر سرعت برای سرویس \lr{GPRS}
@@
 %\lr{1Mbps}
-%می باشد.
+%می‌باشد.
 %\subsubsection{نسل سوم}
-%این نسل مخابراتی استانداردهای بسیاری از فناوری های بیسیم را تعیین نمود.
-مرورگر وب ، ایمیل ، بارگیری ویدیو ، به اشتراک گذاری عکس و سایر فناوری های هوشمند در نسل سوم معرفی شدند که در سال 2001 به طور تجاری معرفی شد.
-اهداف تعیین شده برای ارتباطات سیار نسل سوم، تسهیل ظرفیت بیشتر صدا و داده ، پشتیبانی از طیف گسترده تری از برنامه ها و افزایش انتقال داده با هزینه کمتری بود.
+%این نسل مخابراتی استانداردهای بسیاری از فناوریهای بیسیم را تعیین نمود.
+مرورگر وب، ایمیل، بارگیری ویدیو، به اشتراک گذاری عکس و سایر فناوریهای هوشمند در نسل سوم معرفی شدند که در سال 2001 به طور تجاری معرفی شد.
+اهداف تعیین شده برای ارتباطات سیار نسل سوم، تسهیل ظرفیت بیشتر صدا و داده، پشتیبانی از طیف گسترده تری از برنامه‌ها و افزایش انتقال داده با هزینه کمتری بود.
 %استاندارد \lr{3G} از فناوری جدیدی به نام
@@
 % به عنوان معماری اصلی شبکه خود 
-%استفاده می کند.
+%استفاده می‌کند.
 %\lr{3G}
@@
 %\lr{3G}
-%  با بهبود چگونگی فشرده سازی صدا در طی تماس، راندمان طیف فرکانس را افزایش داده است، بنابراین تماس همزمان بیشتری می تواند در همان محدوده فرکانس اتفاق بیفتد.
+%  با بهبود چگونگی فشرده سازی صدا در طی تماس، راندمان طیف فرکانس را افزایش داده است، بنابراین تماس همزمان بیشتری میتواند در همان محدوده فرکانس اتفاق بیفتد.
 %حداکثر سرعت این نسل 
@@
 %حداکثر سرعت نظری برای HSPA + 21.6 Mbps است. 
-\subsubsection{ نسل چهارم مخابرات}
+در ادامه مروری بر نسلهای مختلف مخابرات خواهیم داشت.
+\subsection{ نسل چهارم مخابرات}
 \lr{4G}
  یک فناوری بسیار متفاوت در مقایسه با \lr{3G} است و هدف از آن، فراهم آوردن سرعت بالا، کیفیت بالا و ظرفیت بالا برای کاربران در عین بهبود امنیت و کاهش هزینه خدمات صوتی و دیتا، چندرسانه ای و اینترنت از طریق \lr{IP} می‌باشد.
-برنامه های کاربردی بالقوه و جاری شامل دسترسی به وب موبایل اصلاح شده، تلفن تلفنی \lr{IP}، خدمات بازی، تلویزیون همراه با کیفیت بالا، کنفرانس ویدیویی، تلویزیون سه بعدی و محاسبات ابری از قابلیت های پشتیبانی آن می باشد.
+برنامه‌های کاربردی بالقوه و جاری شامل دسترسی به وب موبایل اصلاح شده، تلفن تلفنی \lr{IP}، خدمات بازی، تلویزیون همراه با کیفیت بالا، کنفرانس ویدیویی، تلویزیون سه بعدی و محاسبات ابری از قابلیتهای پشتیبانی آن می‌باشد.
 
-فن آوری های کلیدی که این امکان را ایجاد کرده اند 
+فن آوریهای کلیدی که این امکان را ایجاد کرده اند 
 \lr{MIMO} \LTRfootnote{Multiple Output Multiple Output}
@@
   \lr{OFDM} \LTRfootnote{Multiplexing Division Frequency Division}
-می باشد.
+می‌باشد.
 دو استاندارد مهم آن
@@
 \lr{WiMAX}
-می باشد.
+می‌باشد.
 حداکثر سرعت یک شبکه 4G هنگام حرکت دستگاه 100 مگابیت بر ثانیه یا 1 گیگابیت بر ثانیه برای ارتباطات کم تحرک مانند هنگام ایستادن یا راه رفتن است.
 تأخیر از حدود \lr{300ms} به \lr{100ms} با کاهش تراکم دست می‌یابد.
- \subsubsection{نسل پنجم مخابرات}
+ \subsection{نسل پنجم مخابرات}
 تکنولوژی 5G یک استاندارد صنعتی است که جایگزین استاندارد رایج کنونی یعنی 4G LTE خواهد شد.
@@
 طراحی این استاندارد به گونه‌ای است که سرعت آن از تکنولوژی 4G LTE بسیار سریع تر است.
-البته هدف این استاندارد صرفا افزایش سرعت اتصالات اینترنتی تلفن های هوشمند نیست.
-این استاندارد، اینترنت بی سیم بسیار پر سرعتی را در همه جا و برای همه چیزها از جمله خودروهای متصل، خانه های هوشمند و ابزارهای اینترنت اشیا (IoT)، فراهم خواهد کرد.
+البته هدف این استاندارد صرفا افزایش سرعت اتصالات اینترنتی تلفنهای هوشمند نیست.
+این استاندارد، اینترنت بی سیم بسیار پر سرعتی را در همه جا و برای همه چیزها از جمله خودروهای متصل، خانه‌های هوشمند و ابزارهای اینترنت اشیا (IoT)، فراهم خواهد کرد.
 کاهش مصرف انٰرژی  معیاری است که در این نسل به آن توجه شده‌است و دستگاه‌های فرستنده و گیرنده اپراتورها باید در ساعت کم مصرف به حالت صرفه‌جویی انرژی وارد شده و به سرعت فعال شوند که این معیار در نسل چهارم قید نشده بوده‌است.
  با توجه
-به این که نرخ داده و ظرفیت در سیستم های نسل چهارم به ظرفیت
-شانون نزدیک شده است، در نتیجه روش هایی که برای
-افزایش ظرفیت شبکه مورد استفاده می گیرند که به شرح زیر است:
+به این که نرخ داده و ظرفیت در سیستمهای نسل چهارم به ظرفیت
+شانون نزدیک شده است، در نتیجه روشهایی که برای
+افزایش ظرفیت شبکه مورد استفاده میگیرند که به شرح زیر است:
 \begin{itemize}
@@
 \item
-استفاده از روش های پردازش های ابری
+استفاده از روشهای پردازشهای ابری
 \item
-شبکه ی تعریف شده ی نرم افزاری
+شبکه ی تعریف شده ی نرم‌افزاری
 \lr{SDN}
@@
 \item 
-ساختار شبکه های دسترسی رادیویی باز
+ساختار شبکه‌های دسترسی رادیویی باز
 \lr{ORAN}
@@
 \section{مقدمه ای بر ساختار \lr{ORAN}}
-مجازی سازی \lr{RAN} توجه زیادی را از طرف اپراتورها به خود جلب می‌کند، زیرا منجر به کاهش هزینه‌های اپراتور و \lr{opex} می‌شود و همچنین این امکان را برای آنها فراهم کند تا با سرعت بیشتری قابلیت های جدیدی به شبکه اضافه کنند.
+مجازی سازی \lr{RAN} توجه زیادی را از طرف اپراتورها به خود جلب می‌کند، زیرا منجر به کاهش هزینه‌های اپراتور و \lr{opex} می‌شود و همچنین این امکان را برای آنها فراهم کرده تا با سرعت بیشتری قابلیتهای جدیدی به شبکه اضافه کنند.
 
-این احتمال وجود دارد که همه این علاقه ها در ایجاد سه گروه مختلف باشد -
+این احتمال وجود دارد که همه این علاقه‌ها در ایجاد سه گروه مختلف باشد -
  انجمن 
@@
 \lr{Open VRAN}
-که برای شرکت سیسکو می باشد.
-اگرچه همه این گروه ها می‌گویند که در حال کار بر روی یک چیز هستند، که اساساً برای باز کردن \lr{RAN} با استفاده از رابط های استاندارد و عناصر شبکه جعبه سفید است، اما در بررسی دقیق تر اختلافاتی نیز وجود دارد.
+که برای شرکت سیسکو می‌باشد.
+اگرچه همه این گروه‌ها می‌گویند که در حال کار بر روی یک چیز هستند، که اساساً برای باز کردن \lr{RAN} با استفاده از رابطهای استاندارد و عناصر شبکه جعبه سفید است، اما در بررسی دقیق تر اختلافاتی نیز وجود دارد.
 
-\lr{Open RAN}(\lr{ORAN})
-تبسیط و ترکیبی از دو ساختار \lr{C-RAN} \LTRfootnote{Cloud Radio Access Network} و \lr{xRAN} می باشد که انتظار می رود که در فناوری نسل پنجم مخابرات مورد استفاده قرار گرفته و منجر به بهبود عملکرد شبکه های دسترسی رادیویی \lr{RAN} گردد.
+شبکه‌ی دسترسی باز 
+\LTRfootnote{Open RAN}(\lr{ORAN})
+تبسیط و ترکیبی از دو ساختار \lr{C-RAN} \LTRfootnote{Cloud Radio Access Network} و \lr{xRAN} می‌باشد که انتظار می‌رود که در فناوری نسل پنجم مخابرات مورد استفاده قرار گرفته و منجر به بهبود عملکرد شبکه‌های دسترسی رادیویی \lr{RAN} گردد.
 این ساختار یک شبکه ی باز، انعطاف پذیر و هوشمند است.
@@
 توابع
- شبکه ی دسترسی رادیویی 
- را به سه قسمت تقسیم می کند،
+ شبکه‌ی دسترسی رادیویی 
+ را به سه قسمت تقسیم می‌کند،
   که قسمت اول واحد از راه دور
@@
    \lr{(CU)} \LTRfootnote{Central unit} 
-   می باشد.
-   در حالی که  \lr{RU} دارای توابع  \lr{(PHY)} \LTRfootnote{Physical layer} پایین تر است،
+   می‌باشد.
+   در حالی که \lr{RU} دارای توابع فیزیکی \LTRfootnote{Physical layer} \lr{(PHY)} لایه‌ی پایین تر است،
     \lr{DU} حاوی \lr{(PHY)} بالاتر، 
@@
 \lr{CU}
-به عنوان توابع شبکه مجازی \lr{(VNFs)} پیاده سازی می شوند،
-که در یک محیط ابر اجرا می شود.
+به عنوان توابع شبکه مجازی \lr{(VNFs)} پیاده سازی می‌شوند،
+که در یک محیط ابر اجرا می‌شود.
 
-رابط های بین \lr{RU} ، \lr{CU} و \lr{DU} رابط های استاندارد باز هستند.
-\subsection{مقدمه ای بر ساختار شبکه های دسترسی رادیویی \lr{C-RAN}}
-شبکه های دسترسی ابری منجر به افزایش پوشش ارسالی می گردد. با توجه به ساختار شبکه
-   \lr{C-RAN} که معماری جدیدی را برای شبکه های نسل آینده
-ارائه می دهد، نه تنها ظرفیت شبکه افزایش می یابد بلکه
-مشکلاتی که در روش های دیگر وجود دارد را نیز هموار
-می سازد.
-مفهوم شبکه دسترسی رادیو ابر \lr{C-RAN}، به مجازی سازی کارکردهای ایستگاه  پایه \LTRfootnote{Base Station-BS} با استفاده از تکنولوژی رایانش ابری \LTRfootnote{Cloud Computing} اشاره می نماید.
-این مفهوم به ایجاد یک ساختار سلولی جدید منجر می شود که در آن، نقاط دسترسی بیسیم کم هزینه که با عنوان واحدهای رادیویی \LTRfootnote{Radio Units} و یا رادیو هد های
+رابطهای بین \lr{RU}، \lr{CU} و \lr{DU} رابطهای استاندارد باز هستند.
+\subsection{مقدمه ای بر ساختار شبکه‌های دسترسی رادیویی \lr{C-RAN}}
+شبکه‌های دسترسی رادیویی‌ ابری منجر به افزایش پوشش ارسالی می‌گردد. با توجه به ساختار شبکه
+   \lr{C-RAN} که معماری جدیدی را برای شبکه‌های نسل آینده
+ارائه می‌دهد، نه تنها ظرفیت شبکه افزایش می‌یابد بلکه
+مشکلاتی که در روشهای دیگر وجود دارد را نیز هموار
+می‌سازد.
+مفهوم شبکه دسترسی رادیو ابر \lr{C-RAN}، به مجازی سازی کارکردهای ایستگاه  پایه \LTRfootnote{Base Station-BS} با استفاده از تکنولوژی رایانش ابری \LTRfootnote{Cloud Computing} اشاره می‌نماید.
+این مفهوم به ایجاد یک ساختار سلولی جدید منجر می‌شود که در آن، نقاط دسترسی بیسیم کم هزینه که با عنوان واحدهای رادیویی \LTRfootnote{Radio Units} و یا رادیو هدهای
   راه دور 
   \LTRfootnote{Radio Remote Heads}
- شناخته می شوند- با استفاده از یک ابر متمرکز با قابلیت پیکربندی مجدد و یا واحد مرکزی \LTRfootnote{Control Unit} مدیریت می شوند.
-شبکه امکان کاهش هزینه های سرمایه گذاری و عملیاتی مورد نیاز برای اپراتور ها به منظور توسعه و نگهداری شبکه های ناهمگن متراکم را فراهم می آورد.
-این مزیت مهم در کنار بازده طیفی، تسهیم آماری \LTRfootnote{Statisitical Multiplexing}، و مزیت های متعادل سازی بار باعث می شود تا شبکه \lr{C-RAN} به عنوان یکی از تکنولوژی های کلیدی در توسعه سیستم های \lr{5G} در جایگاه بسیار مناسبی قرار بگیرد.
-در ادامه، یک بررسی کلی و مختصر از تحقیقات جدید در مورد ساختار \lr{C-RAN} ارائه می شود و موضوعات مورد تاکید عبارتند از فشرده سازی لینک \lr{fronthaul} پردازش باند پایه، کنترل دسترسی به محیط واسط، تخصیص منابع، ملاحظات سطح سیستم، و تلاش های انجام شده در راستای ارائه استاندارد ها.
-\subsubsection{ساختار شبکه های مختلف }
+ شناخته می‌شوند- با استفاده از یک ابر متمرکز با قابلیت پیکربندی مجدد و یا واحد مرکزی \LTRfootnote{Control Unit} مدیریت می‌شوند.
+شبکه امکان کاهش هزینه‌های سرمایه گذاری و عملیاتی مورد نیاز برای اپراتورها به منظور توسعه و نگهداری شبکه‌های ناهمگن متراکم را فراهم می‌آورد.
+این مزیت مهم در کنار بازده طیفی، تسهیم آماری \LTRfootnote{Statisitical Multiplexing}، و مزیتهای متعادل سازی بار باعث می‌شود تا شبکه \lr{C-RAN} به عنوان یکی از تکنولوژیهای کلیدی در توسعه سیستمهای \lr{5G} در جایگاه بسیار مناسبی قرار بگیرد.
+در ادامه، یک بررسی کلی و مختصر از تحقیقات جدید در مورد ساختار \lr{C-RAN} ارائه می‌شود و موضوعات مورد تاکید عبارتند از فشرده سازی لینک \lr{fronthaul} پردازش باند پایه، کنترل دسترسی به محیط واسط، تخصیص منابع، ملاحظات سطح سیستم، و تلاشهای انجام شده در راستای ارائه استانداردها.
+\subsubsection{ساختار شبکه‌های مختلف }
 با توجه به مقاله ی\cite{checko2015cloud}،
@@
 \end{figure}
-هر ایستگاه پایه دو نوع پردازش انجام می دهد : پردازش
-رادیویی که توسط واحد رادیویی \LTRfootnote{RRH} انجام می شود و شامل پردازش
-دیجیتالی، فیلترینگ فرکانسی، تقویت توان و ....میباشد و
+هر ایستگاه پایه دو نوع پردازش انجام می‌دهد : پردازش
+رادیویی که توسط واحد رادیویی \LTRfootnote{RRH} انجام می‌شود و شامل پردازش
+دیجیتالی، فیلترینگ فرکانسی، تقویت توان و ....می‌باشد و
 پردازش باند پایه که توسط واحد باند پایه \LTRfootnote{BBU} که همان واحد کنترل است \LTRfootnote{CU} انجام شده و از جمله
-مهمترین وظایف آن می توان به کدینگ، مدولاسیون و
+مهمترین وظایف آن می‌توان به کدینگ، مدولاسیون و
 تبدیل فوریه ی سریع اشاره کرد. در ساختار جدیدی که
@@
 پردازشگرهای رادیویی و باند پایه متحول شده و در نتیجه
-مزایایی برای شبکه حاصل خواهد شد.در ادامه ، انواع ساختارها را بیان خواهد شد.
+مزایایی برای شبکه حاصل خواهد شد.در ادامه، انواع ساختارها را بیان خواهد شد.
 \subsubsection{ساختار سنتی ایستگاه پایه }
 
-در ساختارهای سنتی ایستگاه پایه، پردازش های رادیویی و باند پایه در
-داخل ایستگاه پایه انجام می شد و مدول آنتن نیز در فاصله
+در ساختارهای سنتی ایستگاه پایه، پردازشهای رادیویی و باند پایه در
+داخل ایستگاه پایه انجام ‌شد و مدول آنتن نیز در فاصله
 ی چند متری از مدول رادیویی نصب شده و ارتباط آنها
-توسط کابل کواکسیال برقرار می شد که همین امر سبب
-افزایش تلفات در شبکه می باشد. این نوع ساختار در شکل
-\ref{fig:c11} نشان داده شده است. همان گونه که مشاهده می کنید
-ارتباط بین ایستگاههای پایه توسط ارتباط  $X_2$ و ارتباط بین
+توسط کابل کواکسیال برقرار میشد که همین امر سبب
+افزایش تلفات در شبکه می‌باشد. این نوع ساختار در شکل
+\ref{fig:c11} نشان داده شده است. همان گونه که مشاهده میکنید
+ارتباط بین ایستگاه‌های پایه توسط ارتباط  $X_2$ و ارتباط بین
 ایستگاه پایه و شبکه ی هسته توسط ارتباط $ S_1$ برقرار می
-شود. این نوع ساختار در شبکه های \lr{1G} و \lr{2G} به کار گرفته
+شود. این نوع ساختار در شبکه‌های \lr{1G} و \lr{2G} به کار گرفته
 شده است 
@@
 مجزا شده و واحد رادیویی که تحت عنوان \lr{RRH} یا \lr{RRU}
-نیز شناخته می شود، توسط فیبر نوری به واحد باند پایه یا \lr{BBU} اتصال می
-یابد. همان طور که پیشتر بیان شد واحد رادیویی مسئولیت
-انجام پردازش های دیجیتالی از جمله تبدیل انالوگ به
+نیز شناخته می‌شود، توسط فیبر نوری به واحد باند پایه یا \lr{BBU} اتصال می‌یابد. همان طور که پیشتر بیان شد واحد رادیویی مسئولیت
+انجام پردازشهای دیجیتالی از جمله تبدیل انالوگ به
 دیجیتال، دیجیتال به انالوگ، تقویت توان و فیلترینگ رابر عهده دارد، که تفکیک وظایف واحد پردازشی و واحد
 رادیویی در این ساختار در شکل \ref{fig:c22} قابل مشاهده است. این
-نوع ساختار برای شبکه های نسل سوم معرفی شده و امروزه
-نیز بیشتر ایستگاههای پایه از همین ساختار بهره می گیرند.
-از جمله ویژگی های بارز این ساختار امکان ایجاد فاصله
-بین واحد رادیویی و پردازشی می باشد، که این فاصله به
-دلیل تاخیر پردازشی و انتشاری نمی تواند از  $40$کیلومتر
+نوع ساختار برای شبکه‌های نسل سوم معرفی شده و امروزه
+نیز بیشتر ایستگاه‌های پایه از همین ساختار بهره میگیرند.
+از جمله ویژگیهای بارز این ساختار امکان ایجاد فاصله
+بین واحد رادیویی و پردازشی می‌باشد، که این فاصله به
+دلیل تاخیر پردازشی و انتشاری نمیتواند از  $40$کیلومتر
 فراتر رود. در این ساختار تجهیزات مرتبط با \lr{BBU} می
@@
 ی اجاره و نگهداری کمتری را به اپراتورها تحمیل می
-کنند منتقل شوند و واحد های رادیویی نیز در در پشت بام
-ساختمان ها و مکان های مرتفع نصب می شوند که این
-خود سبب کاهش هزینه های خنک سازی ادوات موجود
-می شود. نحوه ی ارتباط بین \lr{RRH} و \lr{BBU} مشابه ساختار
-سنتی بوده و \lr{RRH} ها نیز توسط معماری زنجیروار با هم
+کنند منتقل شوند و واحدهای رادیویی نیز در در پشت بام
+ساختمانها و مکانهای مرتفع نصب می‌شوند که این
+خود سبب کاهش هزینه‌های خنک سازی ادوات موجود
+می‌شود. نحوه ی ارتباط بین \lr{RRH} و \lr{BBU} مشابه ساختار
+سنتی بوده و \lr{RRH}ها نیز توسط معماری زنجیروار باهم
 در ارتباطند.
@@
 \subsubsection{ساختار \lr{C-RAN}}
-در ادامه ساختار های شبکه دسترسی رادیویی ابری و ساختارهای بهبود یافته ی آن را معرفی می نماییم.
+در ادامه ساختارهای شبکه دسترسی رادیویی ابری و ساختارهای بهبود یافته ی آن را معرفی می‌نماییم.
 \begin{itemize}
-\item \textbf{شبکه های دسترسی رادیویی ابری}
+\item \textbf{شبکه‌های دسترسی رادیویی ابری}
 
@@
   است.
-از تجمیع \lr{BBU} ها بر روی سرور ابری، \lr{BBU-Pool} ایجاد می شود.
+از تجمیع \lr{BBU}ها بر روی سرور ابری، \lr{BBU-Pool} ایجاد می‌شود.
 در این ساختار، در راستای بهینه سازی عملکرد \lr{BBU}
- ها در مواجهه باایستگاههای پایه پر ترافیک و کم ترافیک،
+ها در مواجهه باایستگاه‌های پایه پر ترافیک و کم ترافیک،
  \lr{BBU}ها به صورت یک مجموعه ی واحد تحت عنوان 
@@
  به اشتراک گزارده شده و مطابق شکل زیر مجازی سازی
-می شود. 
-در توضیح بیشتر این ساختار می توان این گونه
+می‌شود. 
+در توضیح بیشتر این ساختار میتوان این گونه
 عنوان کرد که \lr{BBU Pool} به عنوان یک خوشه ی مجازی
-در نظر گرفته می شود که شامل پردازش گرهایی می باشد
-که پردازش های باند پایه را انجام می دهند. ارتباط بین
-  \lr{BBU}ها در ساختار های فعلی به شکل  $X_2$ برقرار می شود
-که در این ساختار ارتباط بین خوشه ها از فرم جدید $X_2$
-تحت عنوان  $X_2 +$برقرار می شود.
+در نظر گرفته می‌شود که شامل پردازش گرهایی می‌باشد
+که پردازش‌‌ باند پایه را انجام می‌دهند. ارتباط بین
+  \lr{BBU}ها در ساختارهای فعلی به شکل  $X_2$ برقرار می‌شود
+که در این ساختار ارتباط بین خوشه‌ها از فرم جدید $X_2$
+تحت عنوان  $X_2 +$برقرار می‌شود.
 \newline
-در شکل \ref{fig:C-RAN} ساختار کلی شبکه ی  \lr{C-RAN} در سیستم های
+در شکل \ref{fig:C-RAN} ساختار کلی شبکه‌ی  \lr{C-RAN} در سیستمهای
 \lr{ LTE}
  نمایش داده شده است. همان طور که در شکل قابل
-مشاهده می باشد ساختار کلی شبکه  \lr{C-RAN} به دو بخش
- \lr{backhaul} و \lr{fronthaul} تقسیم بندی شده است. بخش
- \lr{fronthaul}شبکه به مرحله ی اتصال سایت های \lr{ RRH}به
+مشاهده می‌باشد ساختار کلی شبکه  \lr{C-RAN} به دو بخش
+ \lr{backhaul} و \lr{fronthaul} تقسیم بندی شده‌است. بخش
+ \lr{fronthaul}شبکه به مرحله ی اتصال سایتهای \lr{ RRH}به
  به \lr{BBU Pool} به اتصال \lr{backhaul} و بخش \lr{BBU Pool}
-هسته ی شبکه ی سیار اطلاق می شود. همان گونه که قبلا
+هسته ی شبکه ی سیار اطلاق می‌شود. همان گونه که قبلا
 ذکر شد \lr{ RRH}ها در نزدیکی انتن نصب شده و از طریق
-لینک های انتقالی نوری با پهنای باند وسیع و تاخیر کم به
-پردازشگرهای قوی در  \lr{BBU}متصل می شوند. توسط این
-لینک های انتقالی است که سیگنال های دیجیتالی باند
-پایه از نوع \lr{IQ} بین \lr{RRH} و \lr{BBU} انتقال می یابند \cite{checko2015cloud}.
+لینکهای انتقالی نوری با پهنای باند وسیع و تاخیر کم به
+پردازشگرهای قوی در \lr{BBU} متصل می‌شوند. توسط این
+لینکهای انتقالی است که سیگنالهای دیجیتالی باند
+پایه از نوع \lr{IQ} بین \lr{RRH} و \lr{BBU} انتقال می‌یابند \cite{checko2015cloud}.
 \begin{figure}[H]
@@
     \includegraphics[width=\textwidth]{./fig/CRAN}
-  \caption{ساختار شبکه ی \lr{C-RAN} \cite{checko2015cloud}}
+  \caption{ساختار شبکه‌ی \lr{C-RAN} \cite{checko2015cloud}}
   \label{fig:C-RAN}
 \end{figure}
-\item \textbf{شبکه های دسترسی رادیویی ابری نا متجانس (\lr{H-CRAN})}
+\item \textbf{شبکه‌های دسترسی رادیویی ابری نامتجانس (\lr{H-CRAN})}
 
-برای غلبه بر چالش های شبکه های \lr{C-RAN} با محدودیت های \lr{fronthaul} ، شبکه های دسترسی ابری نامتحانس (\lr{H-CRAN}) معرفی می شود\cite{ fogComputing, heterogeneous, fogEdge}.
+برای غلبه بر چالشهای شبکه‌های \lr{C-RAN} با محدودیتهای \lr{fronthaul}، شبکه‌های دسترسی ابری نامتحانس (\lr{H-CRAN}) معرفی می‌شود\cite{ fogComputing, heterogeneous, fogEdge}.
 \begin{figure}
@@
     \includegraphics[scale = 0.8]{./fig/hc}
-  \caption{ ساختار شبکه های دسترسی ابری نامتحانس \cite{heterogeneous}  }
+  \caption{ ساختار شبکه‌های دسترسی ابری نامتحانس \cite{heterogeneous}  }
   \label{fig:hc}
@@
 
-کاربر و صفحه ی کنترلگر در چنین شبکه هایی از هم مجزا می باشند.
-که در این شبکه ها ، نودهای توان بالا   \LTRfootnote{High Power Node}\lr{HPN} ، عمدتا برای فراهم کردن پوشش بدون درز و اجرای عملکرد صفحه کنترل می باشد.
-در حالی که \lr{RRH} ها برای فراهم نمودن سرعت بالای نرخ داده برای انتقال بسته در ترافیک قرار گرفته اند.
-\lr{HPN} ها از طریق لینکهای \lr{backhaul}  به \lr{BBU Pool} متصلند ( برای هماهنگ کردن تداخل ).\newline
-ساختار این شبکه شبیه به ساختار \lr{C-RAN} می باشد .
-همانطور که در شکل \eqref{fig:hc} نشان داده شده است ، تعداد زیادی \lr{RRH} ، همراه با انرژی مصرفی کم در ساختار \lr{H-CRAN} ، با یکدیگر در \lr{BBU Pool} مرکزی ، همکاری می کنند تا گین مشترک بالایی بدست آورند.
-تنها ، فرکانس رادیویی جلو ،(\lr{RF}) و عملکردهای پردازشی  ساده ، در \lr{RRH} ، صورت می گیرد ، در حالی که پردازشهای مهم دیگر ، در \lr{BBU Pool} انجام می گیرد.
-همچنین تنها بخشی از عملکردها در لایه ی \lr{PHY} در \lr{RRH} به مشارکت می انجامد که این مدل در شکل \eqref{fig:hc} نشان داده شده است.\newline
-اگرچه ، برخلاف \lr{C-RAN} ، \lr{BBU Pool} در \lr{H-CRAN} ، به \lr{HPN} ها متصلند که این، برای کاهش تداخل متقابل بین \lr{RRH} ها و \lr{HPN} ها از طریق محاسبات ابری متمرکز بر اساس تکنیکهای پردازشی مشترک می باشد.
-همچنین ، داده و واسط کنترل ، بین \lr{BBU Pool} و \lr{HPN} های $S_1$ و $X_2$ شناخته شده اند که تعریف آنها بر اساس تعریف استاندارد \lr{3G} ایجاد شده است.\newline
-همانطور که سرویسهای صدا ، می توانند به صورت بهینه در طول مد سوییچ بسته در \lr{4G} فراهم گردند ، \lr{H-CRAN} می تواند به طور همزمان سرویس صدا و داده را پشتیبانی کند.
-سرویس صدا مرجح به اداره از طریق \lr{HPN} ها می باشد ، در حالی که ترافیک بسته ی پر داده ، بیشتر توسط \lr{RRH} اداره می گردد.
-در مقایسه با ساختار \lr{C-RAN} ،ساختار \lr{H-CRAN} ، نیازهای \lr{fronthaul} را بوسیله ی مشارکت \lr{HPN} ها برطرف می سازد.
-با توجه به حضور \lr{HPN} ها ،سیگنالهای کنترلی و سمبلهای داده در \lr{H-CRAN} جدا از هم می باشند.
-تمام کنترل کننده های سیگنال و سیستم هایی که اطلاعات را ارسال می نمایند ، توسط \lr{HPN} ها به \lr{UE} ، منتقل می گردد که منجر به سادگی در ظرفیت و در محدودیت تاخیر زمان در لینکهای \lr{fronthaul } بین \lr{RRH} ها و \lr{BBU Pool}  می گردد و منجر به صرفه جویی در مصرف انرژی می گردد.
-همچنین ، برخی از ترافیک های شدید و ناگهانی \LTRfootnote{Burst Traffic} و یا سرویس پیام همراه با مقدار داده ی کم ، می تواند به صورت بهینه توسط \lr{HPN} ها پشتیبانی گردد.
-مکانیزم کنترل بین ارتباط داشتن و نبود ارتباط ، توسط \lr{H-CRAN} پشتیبانی می گردد که منجر به حفظ کردن مقدار قابل توجهی \lr{Overhead} در رادیو بوسیله ی مکانیزم ارتباط جهت دار خالص می گردد.
-در \lr{RRH} ، تکنولوژی های مختلف انتقال در لایه ی \lr{PHY} ، قابل استفاده برای بهبود نرخ انتقال (همانند موج میلیمتری و نور مرئی) می گردد.
-در \lr{HPN}ها، \lr{MIMO}\LTRfootnote{Multiple Input Multiple Output}، یکی از راه های افزایش پوشش در بهبود ظرفیت می باشد.
+کاربر و صفحه ی کنترلگر در چنین شبکه‌هایی از هم مجزا می‌باشند.
+که در این شبکه‌ها، نودهای توان بالا   \LTRfootnote{High Power Node}\lr{HPN}، عمدتا برای فراهم کردن پوشش بدون درز و اجرای عملکرد صفحه کنترل می‌باشد.
+در حالی که \lr{RRH}ها برای فراهم نمودن سرعت بالای نرخ داده برای انتقال بسته در ترافیک قرار گرفته اند.
+\lr{HPN}ها از طریق لینکهای \lr{backhaul}  به \lr{BBU Pool} متصلند ( برای هماهنگ کردن تداخل ).\newline
+ساختار این شبکه شبیه به ساختار \lr{C-RAN} می‌باشد .
+همانطور که در شکل \eqref{fig:hc} نشان داده شده است، تعداد زیادی \lr{RRH}، همراه با انرژی مصرفی کم در ساختار \lr{H-CRAN}، با یکدیگر در \lr{BBU Pool} مرکزی، همکاری می‌کنند تا گین مشترک بالایی بدست آورند.
+تنها‌، فرکانس رادیویی جلو، (\lr{RF}) و عملکردهای پردازشی  ساده، در \lr{RRH}، صورت میگیرد، در حالی که پردازشهای مهم دیگر، در \lr{BBU Pool} انجام می‌گیرد.
+همچنین تنها بخشی از عملکردها در لایه ی \lr{PHY} در \lr{RRH} به مشارکت می‌انجامد که این مدل در شکل \eqref{fig:hc} نشان داده شده است.\newline
+اگرچه، برخلاف \lr{C-RAN}،\lr{BBU Pool} در \lr{H-CRAN}، به \lr{HPN}ها متصلند که این، برای کاهش تداخل متقابل بین \lr{RRH}ها و \lr{HPN}ها از طریق محاسبات ابری متمرکز براساس تکنیکهای پردازشی مشترک می‌باشد.
+همچنین، داده و واسط کنترل، بین \lr{BBU Pool} و \lr{HPN}های $S_1$ و $X_2$ شناخته شده اند که تعریف آنها بر اساس تعریف استاندارد \lr{3G} ایجاد شده است.\newline
+همانطور که سرویسهای صدا، میتوانند به صورت بهینه در طول مد سوییچ بسته در \lr{4G} فراهم گردند، \lr{H-CRAN} میتواند به طور همزمان سرویس صدا و داده را پشتیبانی کند.
+سرویس صدا مرجح به اداره از طریق \lr{HPN}ها می‌باشد، در حالی که ترافیک بسته ی پر داده، بیشتر توسط \lr{RRH} اداره می‌گردد.
+در مقایسه با ساختار \lr{C-RAN}، ساختار \lr{H-CRAN} نیازهای \lr{fronthaul} را بوسیله ی مشارکت \lr{HPN}ها برطرف می‌سازد.
+با توجه به حضور \lr{HPN}ها، سیگنالهای کنترلی و سمبلهای داده در \lr{H-CRAN} جدا از هم می‌باشند.
+تمام کنترل کننده‌های سیگنال و سیستمهایی که اطلاعات را ارسال می‌نمایند، توسط \lr{HPN}ها به \lr{UE}، منتقل می‌گردد که منجر به سادگی در ظرفیت و در محدودیت تاخیر زمان در لینکهای \lr{fronthaul } بین \lr{RRH}ها و \lr{BBU Pool}  می‌گردد و منجر به صرفه‌جویی در مصرف انرژی می‌گردد.
+همچنین، برخی از ترافیکهای شدید و ناگهانی \LTRfootnote{Burst Traffic} و یا سرویس پیام همراه با مقدار داده‌ی کم، می‌تواند به صورت بهینه توسط \lr{HPN}ها پشتیبانی گردد.
+مکانیزم کنترل بین ارتباط داشتن و نبود ارتباط، توسط \lr{H-CRAN} پشتیبانی می‌گردد که منجر به حفظ کردن مقدار قابل توجهی \lr{Overhead} در رادیو بوسیله ی مکانیزم ارتباط جهت دار خالص می‌گردد.
+در \lr{RRH}، تکنولوژیهای مختلف انتقال در لایه ی \lr{PHY}، قابل استفاده برای بهبود نرخ انتقال (همانند موج میلیمتری و نور مرئی) می‌گردد.
+در \lr{HPN}ها، \lr{MIMO}\LTRfootnote{Multiple Input Multiple Output}، یکی از راه‌های افزایش پوشش در بهبود ظرفیت می‌باشد.
 
@@
 
-برای حل کردن مشکلات \lr{H-CRAN} و \lr{C-RAN}، نیاز به معرفی ساختار جدید دیگری می باشیم که آن را \lr{F-RAN} می نامیم.
-\lr{F-RAN} تمام ویژگی های مثبت محاسبات ابری و شبکه های نامتجانس و محاسبات مهی را همزمان در بر می گیرد.
-محاسبات مهی ، اصطلاحی برای جایگزین کردن محاسبات ابری است که مقدار قابل توجهی از ذخیره سازی ، ارتباطات ، کنترل کردن ، اندازه گیری و مدیریت را در لبه ی شبکه انجام می دهد (نه در کانال و ابر مرکزی) \cite{fogComputing, fogEdge}.
- سیستمهای \lr{F-RAN} تحولی از سیستمهای \lr{C-RAN} می باشد . برخی از ارتباطات توزیع شده و عملکردهای ذخیره سازی در منطق لایه ی مه قرار دارد. همچنین چهار نوع ارتباطات ابری تعریف شده است.
+برای حل کردن مشکلات \lr{H-CRAN} و \lr{C-RAN}، نیاز به معرفی ساختار جدید دیگری میباشیم که آن را \lr{F-RAN} می‌نامیم.
+\lr{F-RAN} تمام ویژگیهای مثبت محاسبات ابری و شبکه‌های نامتجانس و محاسبات مهی را همزمان در بر می‌گیرد.
+محاسبات مهی، اصطلاحی برای جایگزین کردن محاسبات ابری است که مقدار قابل توجهی از ذخیره سازی، ارتباطات، کنترل کردن، اندازه گیری و مدیریت را در لبه ی شبکه انجام می‌دهد (نه در کانال و ابر مرکزی) \cite{fogComputing, fogEdge}.
+ سیستمهای \lr{F-RAN} تحولی از سیستمهای \lr{C-RAN} می‌باشد . برخی از ارتباطات توزیع شده و عملکردهای ذخیره سازی در منطق لایه ی مه قرار دارد. همچنین چهار نوع ارتباطات ابری تعریف شده است.
   \begin{figure}[H]
@@
  \item
- ابر ذخیره گر و ارتباطات مرکزی جامع :
- که همانند ابر مرکزی \lr{C-RAN} می باشد
+ ابر ذخیره‌گر و ارتباطات مرکزی جامع :
+ که همانند ابر مرکزی \lr{C-RAN} می‌باشد.
  \item
- ابر کنترل گر مرکزی :که برای تکمیل عملکردهای کنترلی  می باشد و در \lr{HPN} ها قرار دارد
+ ابر کنترل‌گر مرکزی :که برای تکمیل عملکردهای کنترلی می‌باشد و در \lr{HPN}ها قرار دارد.
  \item
- ابر ارتباطات منطقی توزیع شده که در برنامه های محاسبات مهی و ابزار های این محاسبات قرار دارد.
+ ابر ارتباطات منطقی توزیع شده که در برنامه‌های محاسبات مهی و ابزارهای این محاسبات قرار دارد.
  \item
@@
  \end{itemize}
- در این ساختار ، برای کاهش تاخیر ناشی از انتقال داده ها به ابر مرکزی ، ساختار های \lr{RRH} را دارای حافظه قرار می دهیم که برای ارتباطات محلی، به جای اینکه پردازش ها در \lr{BBU Pool} صورت بگیرد، بدون نیاز به انتقال به ابر مرکزی، درون \lr{RRH} ها انجام پذیرد.
+ در این ساختار، برای کاهش تاخیر ناشی از انتقال داده‌ها به ابر مرکزی، ساختارهای \lr{RRH} را دارای حافظه قرار میدهیم که برای ارتباطات محلی، به جای اینکه پردازشها در \lr{BBU Pool} صورت بگیرد، بدون نیاز به انتقال به ابر مرکزی، درون \lr{RRH}ها انجام پذیرد.
 \end{itemize}
@@
 در سال ۲۰۱۶ با هدف استانداردسازی یک جایگزین انعطاف پذیر و باز برای \lr{RAN}
-مبتنی بر سخت افزار سنتی بدست آمده است.
+مبتنی بر سخت افزار سنتی بدست آمده‌است.
  در این ساختار، سه حوزه ی مهم مورد بررسی قرار گرفته است.
@@
  \LTRfootnote{control plane} از 
- صفحه ی کاربر
+ صفحه‌ی کاربر
 \LTRfootnote{user plane}
-می باشد. حوزه ی دوم،
-ساختن یک پشته نرم افزاری \lr{eNodeB} مدولار که از سخت افزار \lr{COTS} استفاده می کند، می باشد.
-حوزه ی سوم مورد بررسی، انتشار رابط های باز شمال و جنوب است\cite{xran}.
-در ادامه این سه حوزه به طور دقیق تر مورد بررسی قرار می گیرد\cite{xran1}.
+می‌باشد. حوزه ی دوم،
+ساختن یک پشته نرم‌افزاری \lr{eNodeB} مدولار که از سخت افزار \lr{COTS} استفاده می‌کند، می‌باشد.
+حوزه ی سوم مورد بررسی، انتشار رابطهای باز شمال و جنوب است\cite{xran}.
+در ادامه این سه حوزه به طور دقیق تر مورد بررسی قرار میگیرد\cite{xran1}.
 
@@
 صفحه ی کاربر}:
-این انتقال صفحه ی کنترل، که قبلاً کاملاً به دستگاههای سخت افزاری \lr{RAN} متصل بود، به دستگاههای محاسباتی در دسترس امکان می دهد \lr{RAN} بتواند به عنوان یک استخر منطقی از ظرفیت ، با کارایی بیشتری کار کند.
-نرم افزار \lr{eNodeB} از سخت افزار خاص فروشنده جدا می شود و الهام بخش نوآوری در هر دو نرم افزار و سخت افزار به صورت مشارکتی اما به طور مستقل است.
-برنامه نویسی و کنترل زمان واقعی بی سابقه در زیرساخت های \lr{RAN} به دست آمده است، که به راحتی از برنامه های کاربردی تلفن همراه و خدمات تجاری پشتیبانی می کند.
-\item \textbf{ساختن یک پشته نرم افزاری \lr{eNodeB} مدولار}:
-رویکرد \lr{xRAN} به خوبی با طرح های مجازی سازی عملکرد شبکه حامل \lr{(NFV)} مطابقت دارد، و همچنین منجر به کنترل عملکرد ترافیک با کارایی بالا، مدیریت تداخل و کنترل منابع رادیویی روی سیستم عامل های استاندارد \lr{x86} و می شود.
-\item \textbf{انتشار رابط های باز شمال و جنوب}: 
-رابط های استاندارد و باز قابیت پشتیبانی از فروشنده های متعدد همکاری اثبات شده دارند. 
+این انتقال صفحه ی کنترل، که قبلاً کاملاً به دستگاه‌های سخت افزاری \lr{RAN} متصل بود، به دستگاه‌های محاسباتی در دسترس امکان می‌دهد \lr{RAN} بتواند به عنوان یک استخر منطقی از ظرفیت، با کارایی بیشتری کار کند.
+نرم‌افزار \lr{eNodeB} از سخت افزار خاص فروشنده جدا می‌شود و الهام بخش نوآوری در هر دو نرم‌افزار و سخت افزار به صورت مشارکتی اما به طور مستقل است.
+برنامه نویسی و کنترل زمان واقعی بی سابقه در زیرساختهای \lr{RAN} به دست آمده است، که به راحتی از برنامه‌های کاربردی تلفن همراه و خدمات تجاری پشتیبانی می‌کند.
+\item \textbf{ساختن یک پشته نرم‌افزاری \lr{eNodeB} مدولار}:
+رویکرد \lr{xRAN} به خوبی با طرحهای مجازی سازی عملکرد شبکه حامل \lr{(NFV)} مطابقت دارد، و همچنین منجر به کنترل عملکرد ترافیک با کارایی بالا، مدیریت تداخل و کنترل منابع رادیویی روی سیستم عاملهای استاندارد \lr{x86} و می‌شود.
+\item \textbf{انتشار رابطهای باز شمال و جنوب}: 
+رابطهای استاندارد و باز قابیت پشتیبانی از فروشنده‌های متعدد همکاری اثبات شده دارند. 
 \lr{xRAN.org}
-و اعضای آن به تصویب رساندن این رابط ها از طریق فرآیندهای استاندارد منجر به در دسترس قرار دادن معماری \lr{xRAN} و پشتیبانی مورد نیاز می شوند.
+و اعضای آن به تصویب رساندن این رابطها از طریق فرآیندهای استاندارد منجر به در دسترس قرار دادن معماری \lr{xRAN} و پشتیبانی مورد نیاز می‌شوند.
 
 \end{itemize}
-\subsubsection{مزایای ساختار \lr{xRAN}}
+در ادامه مزایای ساختار xRAN را بیان می‌نماییم.
+
+\textbf{مزایای ساختار xRAN}
+%\subsubsection{مزایای ساختار \lr{xRAN}}
 \begin{itemize}
@@
 منجر به 
-برنامه ریزی زمان واقعی بی سابقه و کنترل در زیرساخت \lr{RAN} می شود که به راحتی برنامه های کاربردی تلفن همراه و خدمات تجاری را پشتیبانی می کند.
+برنامه ریزی زمان واقعی بی سابقه و کنترل در زیرساخت \lr{RAN} می‌شود که به راحتی برنامه‌های کاربردی تلفن همراه و خدمات تجاری را پشتیبانی می‌کند.
 \item
-یک پشته \lr{eNB} مدولار مبتنی بر نرم افزار ، منجر به امکان قرارگیری انعطاف پذیر توابع \lr{eNB} و کنترل ترکیبی آن با یک برنامه ریز امکان پذیر می شود تا بتواند زمان تاخیر متغیر در \lr{fronthaul} را کنترل کند.
+ یک پشته
+ \lr{eNB} 
+ مدولار مبتنی بر نرم‌افزار، منجر به امکان قرارگیری انعطاف پذیر توابع \lr{eNB} و کنترل ترکیبی آن با یک برنامه ریز امکان پذیر می‌شود تا بتواند زمان تاخیر متغیر در \lr{fronthaul} را کنترل کند.
 \item
-رابط های مرزی جنوبی استاندارد، پیاده سازی شبکه با خرید سیستم از چندین شرکت متفاوت را امکان پذیر می سازد و رابط های شمال مرزی، برش کامل شبکه برای بهینه سازی \lr{QoE} \LTRfootnote{Quality of Experience} کاربر را فراهم می کند.
-رابط های \lr{xRAN} به خوبی با لبه ابر حامل هماهنگ هستند و اجازه می دهد تا  محاسبه و ذخیره سازی منابع در شبکه تلفن همراه 
+رابط‌های مرزی جنوبی استاندارد، پیاده سازی شبکه با خرید سیستم از چندین شرکت متفاوت را امکان پذیر می‌سازد و رابطهای شمال مرزی، برش کامل شبکه برای بهینه سازی \lr{QoE} \LTRfootnote{Quality of Experience} کاربر را فراهم می‌کند.
+رابطهای \lr{xRAN} به خوبی با لبه ابر حامل هماهنگ هستند و اجازه می‌دهد تا محاسبه و ذخیره سازی منابع در شبکه تلفن همراه 
 به صورت دینامیکی مدیریت شود.
 \item 
-این ساختار هزینه ی رشد ظرفیت دسترسی رادیویی و هزینه ی بهره برداری را کاهش می دهد.
+این ساختار هزینه‌ی رشد ظرفیت دسترسی رادیویی و هزینه‌ی بهره برداری را کاهش می‌دهد.
 \end{itemize}
+\subsection{vRAN}
+vRAN یا شبکه‌های دسترسی رادیویی مجازی
+گونه‌ی دیگری از شبکه‌های رادیویی دسترسی می‌باشند که منجر به افزایش هوشمندانه ظرفیت، کاهش چشمگیر هزینه‌ها می‌شود.
+همچنین قابلیت انعطاف پذیری و مقیاس پذیری پویا را فراهم می‌کند که برای پشتیبانی از خدمات و برنامه‌های آینده ضروری خواهد بود.
+معماری vRAN با اجرای توابع باند پایه مجازی بر روی سخت افزار سرور کالا، بر اساس اصول مجازی سازی توابع شبکه (NFV)، فراتر از آخرین شبکه‌ی  متمرکز رادیویی (C-RAN)است.
+معماری C-RAN می‌تواند با ایجاد امکان تجمع منابع پردازش باند پایه، که می‌تواند به صورت پویا به سایتهای مختلف سلول و فن‌آوریهای رادیویی اختصاص یابد، گامیفراتر رود.
+به اشتراک گذاری منابع باند پایه از طیف موجود با کارآیی بیشتری استفاده می‌کند و قابلیت اطمینان سرویس را بهبود می‌بخشد.
+همچنین پشتیبانی از ویژگی‌های LTE-Advanced و استقرار سلولهای کوچک  می‌تواند ظرفیت را در مناطق پرجمعیت و نقاط پرتردد افزایش دهد.
+اما تمرکز باند متمرکز (BBU-Pool) به اندازه کافی پیش نمی‌رود.
+برای دستیابی به پتانسیل کامل صرفه‌جویی در هزینه، مقیاس گزاری ظرفیت پویا، کیفیت بالاتر و ارائه سریع سرویسهای جدید، می‌بایست از یک معماری RAN مجازی (vRAN) استفاده کنند. در مدل vRAN،
+BBU 
+مجازی شده است.
+vBBU
+که همان واحدهای باند پایه‌ی مجازی هستند، در چندین سیستم عامل NFV در سخت افزار استاندارد x86 مستقر شده و در مراکز داده متمرکز تلفیق می‌شوند، در حالی که واخدهای رادیویی از راه دور (RRH) در سایتهای سلول در لبه باقی می‌مانند.
+vRAN 
+از سخت افزار استاندارد سرور استفاده می‌کند که به طور مقرون به صرفه پردازش، حافظه و منابع ورودی و خروجی را با تقاضای خود، درخواست می‌کند و ظرفیت RAN را با هوش مصنوعی تغییر داده تا کیفیت و قابلیت اطمینان خدمات را به طور قابل توجهی بهبود بخشد.
+بسته به نحوه تقسیم عملکردهای eNodeB، معماری vRAN همچنین امکان انتقال اترنت و IP را فراهم می‌کند، که به ارائه‌دهندگان خدمات گزینه‌های مقرون به صرفه‌تری برای انتقال fronthaul می‌دهد \cite{vran}.
+\begin{figure}%[H]
+	\centering
+	\includegraphics[width=0.8\textwidth]{./fig/vran}
+	\caption{ساختار شبکه ی \lr{vRAN} \cite{vran}}
+	\label{fig:vran}
+\end{figure}
+
 \subsection{\lr{ORAN}}
-معماری \lr{ORAN} برای ایجاد زیرساخت های \lr{RAN} نسل بعدی طراحی شده است.
-معماری \lr{ORAN} با تکیه بر اصول هوشمندی و باز بودن، پایه و اساس ساخت \lr{RAN} مجازی بر روی سخت افزار آزاد ، با کنترل رادیویی ایجاد شده توسط هوش مصنوعی است که توسط اپراتورهای سراسر جهان پیش بینی شده است.
-این معماری بر روی رابط های استاندارد و تعریف شده ای بنا شده است تا یک زنجیره اکوسیستم با قابلیت باز ایجاد کند که دارای پشتیبانی کامل از استانداردهای تبلیغ شده توسط \lr{3GPP} و سایر سازمان های استاندارد صنعت فراهم شود.
-\begin{figure}[H]
+شبکه دسترسی رادیویی باز از ترکیب C-RAN و xRAN و در برخی جاها از ترکیب C-RAN و vRAN بدست آمده است.
+معماری \lr{ORAN} برای ایجاد زیرساختهای \lr{RAN} نسل بعدی طراحی شده است.
+معماری \lr{ORAN} با تکیه بر اصول هوشمندی و باز بودن، پایه و اساس ساخت \lr{RAN} مجازی بر روی سخت افزار آزاد، با کنترل رادیویی ایجاد شده توسط هوش مصنوعی است که توسط اپراتورهای سراسر جهان پیش بینی شده است.
+این معماری بر روی رابطهای استاندارد و تعریف شده ای بنا شده است تا یک زنجیره اکوسیستم با قابلیت باز ایجاد کند که دارای پشتیبانی کامل از استانداردهای تبلیغ شده توسط \lr{3GPP} و سایر سازمانهای استاندارد صنعت فراهم شود.
+\begin{figure}%[H]
   \centering
@@
 \end{figure}
-اتحاد \lr{ORAN} در جستجوی چشم انداز باز بودن و هوشمندی برای شبکه های بی سیم نسل بعدی و فراتر از آن است\cite{oranWP}.
+اتحاد \lr{ORAN} در جستجوی چشم انداز باز بودن و هوشمندی برای شبکه‌های بی سیم نسل بعدی و فراتر از آن است\cite{oranWP}.
 \begin{itemize}
 \item \textbf{باز بودن}:
-ایجاد یک \lr{RAN} مقرون به صرفه نیاز به باز بودن ارتباط ها دارد.
-رابط های باز برای فعال کردن فروشندگان و اپراتورهای کوچکتر به سرعت می توانند خدمات خود را معرفی کنند و یا اپراتورها را قادر می سازد تا شبکه را متناسب با نیازهای منحصر به فرد خود تنظیم کنند.
-رابط های باز همچنین استقرار چند سازنده ای را قادر می سازد و اکوسیستم تأمین کننده رقابتی تر و پر جنب و جوش بیشتری را ایجاد می کند.
- همچنین نرم افزارهای منبع باز و طرحهای مرجع سخت افزار باعث نوآوری سریعتر و دموکراتیک تر می شود.
+ایجاد یک \lr{RAN} مقرون به صرفه نیاز به باز بودن ارتباط‌ها دارد.
+رابطهای باز برای فعال کردن فروشندگان و اپراتورهای کوچکتر به سرعت میتوانند خدمات خود را معرفی کنند و یا اپراتورها را قادر می‌سازد تا شبکه را متناسب با نیازهای منحصر به فرد خود تنظیم کنند.
+رابطهای باز همچنین استقرار چند سازنده ای را قادر می‌سازد و اکوسیستم تأمین کننده رقابتی تر و پر جنب و جوش بیشتری را ایجاد می‌کند.
+ همچنین نرم‌افزارهای منبع باز و طرحهای مرجع سخت افزار باعث نوآوری سریعتر و دموکراتیک تر می‌شود.
  \item \textbf{هوشمندی}
- شبکه ها با ظهور برنامه 5G پیچیده تر و متراکم تر شده و خواستار برنامه های غنی تر می شوند.
- برای کاستن این پیچیدگی نمی توان از ابزارهای سنتی انسانی  برای استقرار، بهینه سازی و بهره برداری از شبکه استفاده کرد.
- در نتیجه، شبکه ها باید خود متحرک شوندتا بتوانند از فن آوری های جدید مبتنی بر یادگیری برای خودکارسازی عملکرد شبکه های عملیاتی و کاهش \lr{OPEX} استفاده کنند.
- اتحاد \lr{ORAN} تلاش خواهد کرد تا از تکنیک های یادگیری عمیق در حال ظهور استفاده کند تا بتواند هر لایه از معماری \lr{RAN}  را به طور هوشمند پیاده سازی کند.
- پیاده سای هوشمند هم در مولفه ها و خم در سطح شبکه اعمال می گردد و منجر به تخصیص دینامیکی منابع رادیویی و بهینه سازی بازدهی شبکه می گردد.
- همراه با رابط های باز \lr{ORAN}، اتوماسیون حلقه بسته بهینه شده با هوش مصنوعی دست یافتنی است و دوره جدیدی را برای عملیات شبکه امکان پذیر می کند.
-\item \textbf{روش های هوش مصنوعی \lr{AI}
+ شبکه‌ها با ظهور برنامه 5G پیچیده تر و متراکم تر شده و خواستار برنامه‌های غنی تر می‌شوند.
+ برای کاستن این پیچیدگی نمیتوان از ابزارهای سنتی انسانی  برای استقرار، بهینه سازی و بهره برداری از شبکه استفاده کرد.
+ در نتیجه، شبکه‌ها باید خود متحرک شوندتا بتوانند از فن آوریهای جدید مبتنی بر یادگیری برای خودکارسازی عملکرد شبکه‌های عملیاتی و کاهش \lr{OPEX} استفاده کنند.
+ اتحاد \lr{ORAN} تلاش خواهد کرد تا از تکنیکهای یادگیری عمیق در حال ظهور استفاده کند تا بتواند هر لایه از معماری \lr{RAN}  را به طور هوشمند پیاده سازی کند.
+ پیاده سای هوشمند هم در مولفه‌ها و هم در سطح شبکه اعمال می‌گردد و منجر به تخصیص دینامیکی منابع رادیویی و بهینه سازی بازدهی شبکه می‌گردد.
+ همراه با رابطهای باز \lr{ORAN}، اتوماسیون حلقه بسته بهینه شده با هوش مصنوعی دست یافتنی است و دوره جدیدی را برای عملیات شبکه امکان پذیر می‌کند.
+\item \textbf{روشهای هوش مصنوعی \lr{AI}
  \LTRfootnote{Artificial Intelligent}
-  منجر به هوشمند سازی بخش رادیویی با استفاده از نرم افزار تعریف شده \LTRfootnote{Software Defined} 
-  می شود:}
+  منجر به هوشمندسازی بخش رادیویی با استفاده از نرم‌افزار تعریف شده \LTRfootnote{Software Defined} 
+  می‌شود:}
    مفهوم 
@@
    بخش صفحه ی کنترل \lr{CP} از
-   صفحه ی کاربر 
+   صفحه‌ی کاربر 
 \lr{UP}
-می باشد، در ساختار 
+می‌باشد، در ساختار 
 \lr{ORAN}
-مورد بررسی قرار می گیرد.
+مورد بررسی قرار می‌گیرد.
 این جداسازی منجر به بهبود 
@@
 برای استفاده از زمان غیر واقعی و زمان نزدیک به واقعی در کنترلگر هوشمند شبکه ی دسترسی رادیویی \LTRfootnote{RAN Intelligent Controller} \lr{RIC} 
-با استفاده از رابط های 
+با استفاده از رابط‌های 
 \lr{A1}
@@
 \lr{E2}
- می گردد.
+ می‌‌گردد.
 همچنین 
@@
  \lr{CP/UP}
- می شود
- که از طریق رابط \lr{E1} در \lr{3GPP } توسعه می یابد.
+ می‌شود
+ که از طریق رابط \lr{E1} در \lr{3GPP } توسعه می‌یابد.
 \item \textbf{مجازی سازی بخش \lr{RAN}}:
@@
  \lr{ORAN}
-  می باشد.
- اپراتورها برای پشتیبانی از شکافهای مختلف در شبکه، الزامات NFVI/VIM را برای تقویت سیستم عامل مجازی ارائه می دهند.
- به عنوان مثال: لایه ی بالا بین PDCP و RLC تقسیم می شود و لایه ی پایین در PHY تقسیم می شود.
-\item \textbf{رابط های باز}:
-معماری مرجع ORAN بر روی مجموعه ای از رابط های کلیدی بین چندین جزء جدا شده ی RAN ساخته شده است.
-اینها شامل رابط های \lr{3GPP} پیشرفته 
+  می‌باشد.
+ اپراتورها برای پشتیبانی از شکافهای مختلف در شبکه، الزامات NFVI/VIM را برای تقویت سیستم عامل مجازی ارائه می‌دهند.
+ به عنوان مثال: لایه ی بالا بین PDCP و RLC تقسیم می‌شود و لایه ی پایین در PHY تقسیم می‌شود.
+\item \textbf{رابطهای باز}:
+معماری مرجع ORAN بر روی مجموعه ای از رابطهای کلیدی بین چندین جزء جدا شده ی RAN ساخته شده است.
+اینها شامل رابطهای \lr{3GPP} پیشرفته 
 (
@@
  برای قابلیت همکاری بین چندین شرکت مختلف تولید کننده است.
-رابط های مشخص شده \lr{ORAN Alliance} شامل یک رابط fronthaul باز بین DU و RRU ، رابط \lr{E2} و یک رابط \lr{A1} بین لایه 
+رابطهای مشخص شده \lr{ORAN Alliance} شامل یک رابط fronthaul باز بین DU و RRU، رابط \lr{E2} و یک رابط \lr{A1} بین لایه 
 Orchestration/NMS 
@@
 برای بهره مندی کامل از مقیاسی از اقتصاد ارائه شده توسط یک رویکرد  محاسباتی باز، \lr{O-RAN Alliance } 
-طرح های مرجع 
-سخت افزاری و ایستگاه پایه به صورت جعبه سفید با کارایی بالا را مشخص می کند. 
-سیستم عامل های مرجع از یک رویکرد جدا شده پشتیبانی می کنند و نقشه های مفصلی را برای معماری سخت افزار و نرم افزار ارائه می دهند تا هم BBU و RRU را فعال کنند. 
-\item \textbf{نرم افزار منبع باز}:
-اتحادیه ORAN ارزش انجمن هایی که منابع باز ارا‌ئه می دهند را درک کرده   
- و از آنها پشتیبانی می کند.
- بسیاری از مؤلفه های معماری ORAN به صورت منبع باز از طریق جوامع موجود تحویل داده می شود.
- این مؤلفه ها عبارتند از: کنترلر هوشمند RAN ، پشته پروتکل ، پردازش لایه PHY و بستر مجازی سازی.
-  چارچوب نرم افزار منبع باز ORAN نه تنها رابط های 
+طرحهای مرجع 
+سخت افزاری و ایستگاه پایه به صورت جعبه سفید با کارایی بالا را مشخص می‌کند. 
+سیستم عاملهای مرجع از یک رویکرد جدا شده پشتیبانی میکنند و نقشه‌های مفصلی را برای معماری سخت افزار و نرم‌افزار ارائه می‌دهند تا هم BBU و RRU را فعال کنند. 
+\item \textbf{نرم‌افزار منبع باز}:
+اتحادیه ORAN ارزش انجمنهایی که منابع باز ارا‌ئه می‌دهند را درک کرده   
+ و از آنها پشتیبانی می‌کند.
+ بسیاری از مؤلفه‌های معماری ORAN به صورت منبع باز از طریق جوامع موجود تحویل داده می‌شود.
+ این مؤلفه‌ها عبارتند از: کنترلر هوشمند RAN، پشته پروتکل، پردازش لایه PHY و بستر مجازی سازی.
+  چارچوب نرم‌افزار منبع باز ORAN نه تنها رابطهای 
 (
@@
 )
-  را پیاده سازی می کند ، بلکه انتظار دارد که طراحی مرجع را برای نسل بعدی RRM با هوش جاسازی شده ارائه دهد تا RIC را امکان پذیر کند.
+  را پیاده سازی می‌کند، بلکه انتظار دارد که طراحی مرجع را برای نسل بعدی RRM با هوش جاسازی شده ارائه دهد تا RIC را امکان پذیر کند.
 \end{itemize}
@@
 \lr{ORAN}،
- المانهای شبکه ی دسترسی رادیویی را مجازی می کند، آنها را جدا کرده و رابط های باز مناسب را 
+ المانهای شبکه ی دسترسی رادیویی را مجازی می‌کند، آنها را جدا کرده و رابطهای باز مناسب را 
 برای اتصال این عناصر
-تعیین می کند. همچنین، 
+تعیین می‌کند. همچنین، 
 \lr{ORAN}
-از روشهای یادگیری ماشین برای هوشمندسازی لایه های 
+از روشهای یادگیری ماشین برای هوشمندسازی لایه‌های 
 \lr{RAN}
- استفاده می نماید. 
+ استفاده می‌نماید. 
  در ساختار نوآورانه ی 
  \lr{ORAN}
- نرم افزار قابل برنامه ریزی 
+ نرم‌افزار قابل برنامه ریزی 
  \lr{RAN}
- از سخت افزار جدا می شود.
+ از سخت افزار جدا می‌شود.
   یکی از مهم ترین خصوصیات
   \lr{ORAN}
-  رابط کاربری باز است که به اپراتورهای موبایل این قابلیت را می دهد تا بتوانند سرویس های مورد نیاز خود را تعریف نمایند.
+  رابط کاربری باز است که به اپراتورهای موبایل این قابلیت را می‌دهد تا بتوانند سرویسهای مورد نیاز خود را تعریف نمایند.
 
@@
 واحد توزیع شده \lr{DU}،
-نود منطقی می باشد که شامل لایه های 
+نود منطقی می‌باشد که شامل لایه‌های 
 \lr{RLC}
@@
 \lr{CU}
-نود منطقی است که شامل لایه های 
+نود منطقی است که شامل لایه‌های 
 \lr{RRC}،
@@
 \lr{PDCP}
-می باشد.
+می‌باشد.
 نود منطقی واحد رادیویی
 \lr{RU}
-نیز، شامل لایه ی 
+نیز، شامل لایه‌ی 
 \lr{LOW-PHY}
-و بخش پردازش رادیویی می باشد.
+و بخش پردازش رادیویی می‌باشد.
 \lr{ORAN}
@@
 \lr{fronthaul}
-باز را شامل می شود که بخش \lr{DU} را به \lr{RU} متصل می نماید
+باز را شامل می‌شود که بخش \lr{DU} را به \lr{RU} متصل می‌نماید
 (رابط 
@@
 
-  با افزایش ترافیک تلفن همراه، شبکه های تلفن همراه و تجهیزاتی که آنها را اجرا می کند باید نرم افزاری تر ، مجازی، انعطاف پذیر، هوشمند و کارآمدتر شوند.
-اتحادیه ی ORAN متعهد است در حال تکامل شبکه های دسترسی رادیویی باشد که باعث می شود آنها نسبت به نسلهای قبل بازتر و باهوش تر شوند.
-تجزیه و تحلیل در زمان واقعی که توسط سیستم های یادگیری ماشین تعبیه شده است و ماژول های پایانی هوش مصنوعی را هدایت می کند، باعث تقویت هوش شبکه می شود.
-عناصر شبکه مجازی با رابط های باز و استاندارد، جنبه های اصلی طرح های مرجع توسعه یافته توسط اتحادیه ی ORAN خواهد بود.
-فن آوری های موجود از عناصر شبکه منبع باز و جعبه سفید، نرم افزار و اجزای سخت افزاری مهم این طرح های مرجع خواهد بود.
+  با افزایش ترافیک تلفن همراه، شبکه‌های تلفن همراه و تجهیزاتی که آنها را اجرا می‌کند باید نرم‌افزاری تر، مجازی، انعطاف پذیر، هوشمند و کارآمدتر شوند.
+اتحادیه ی ORAN متعهد است در حال تکامل شبکه‌های دسترسی رادیویی باشد که باعث می‌شود آنها نسبت به نسلهای قبل بازتر و باهوش تر شوند.
+تجزیه و تحلیل در زمان واقعی که توسط سیستمهای یادگیری ماشین تعبیه شده است و ماژولهای پایانی هوش مصنوعی را هدایت می‌کند، باعث تقویت هوش شبکه ‌‌شود.
+عناصر شبکه مجازی با رابطهای باز و استاندارد، جنبه‌های اصلی طرحهای مرجع توسعه یافته توسط اتحادیه ی ORAN خواهد بود.
+فن آوریهای موجود از عناصر شبکه منبع باز و جعبه سفید، نرم‌افزار و اجزای سخت افزاری مهم این طرحهای مرجع خواهد بود.
 \section{مجازی سازی توابع شبکه}
-برای بهبود سرویس دهی در نسل پنجم مخابرات، جداسازی المان های نرم افزاری و سخت افزاری شبکه صورت گرفته است و به عنوان 
+برای بهبود سرویس دهی در نسل پنجم مخابرات، جداسازی المانهای نرم‌افزاری و سخت افزاری شبکه صورت گرفته است و به عنوان 
 مجازی سازی توابع شبکه (\lr{NFV}) \LTRfootnote{network function virtualization}
@@
   \lr{VNF}
-  \LTRfootnote{Virtual network function} ،
+  \LTRfootnote{Virtual network function}،
   بلوکهای توابع سیستم هستند.
 در نسل پنجم مخابرات 
-  انتظار می رود که
+  انتظار می‌رود که
    میزبان چندین سرویس
@@
     ایده اصلی NFV جداسازی تجهیزات شبکه فیزیکی از توابع اجرا شده بر روی آنها است.
-این بدان معنی است که یک عملکرد شبکه - مانند فایروال - می تواند به عنوان نمونه ای از نرم افزارهای ساده به فراهم آورندگان سرویس (SP) \LTRfootnote{Service Provider} ارسال شود.
-    این امر امکان ادغام بسیاری از انواع تجهیزات شبکه بر روی سرورهای با حجم بالا ، سوئیچ ها و انبارها را فراهم می کند ، که می توانند در مراکز داده، نودهای شبکه توزیع شده و در محل کاربر نهایی قرار بگیرند.
-    به این ترتیب، یک سرویس خاص می تواند به مجموعه ای از توابع شبکه مجازی (VNFs) تجزیه شود، که می تواند در نرم افزارهایی که روی یک یا چند سرور فیزیکی استاندارد در صنعت قرار دارند، اجرا شود.
-    سپس VNF ها ممکن است در مکانهای مختلف شبکه (به عنوان مثال، با هدف معرفی خدمات هدفمند به مشتریان در یک موقعیت جغرافیایی خاص) جابجا شده و خدمات رسانی کنند، بدون اینکه لزوماً به خرید و نصب سخت افزار جدید نیاز داشته باشند.
+این بدان معنی است که یک عملکرد شبکه - مانند فایروال - میتواند به عنوان نمونه ای از نرم‌افزارهای ساده به فراهم آورندگان سرویس (SP) \LTRfootnote{Service Provider} ارسال شود.
+    این امر امکان ادغام بسیاری از انواع تجهیزات شبکه بر روی سرورهای با حجم بالا، سوئیچها و انبارها را فراهم می‌کند، که میتوانند در مراکز داده، نودهای شبکه توزیع شده و در محل کاربر نهایی قرار بگیرند.
+    به این ترتیب، یک سرویس خاص میتواند به مجموعه ای از توابع شبکه مجازی (VNFs) تجزیه شود، که میتواند در نرم‌افزارهایی که روی یک یا چند سرور فیزیکی استاندارد در صنعت قرار دارند، اجرا شود.
+    سپس VNFها ممکن است در مکانهای مختلف شبکه (به عنوان مثال، با هدف معرفی خدمات هدفمند به مشتریان در یک موقعیت جغرافیایی خاص) جابجا شده و خدمات رسانی کنند، بدون اینکه لزوماً به خرید و نصب سخت افزار جدید نیاز داشته باشند.
     NFV به 
     هاSP
-   با انعطاف پذیری بیشتری وعده می دهد تا بتواند بیشتر قابلیت ها و خدمات شبکه خود را به کاربران و سایر خدمات باز کنند و امکان استقرار یا پشتیبانی از سرویس های جدید شبکه را  به طور سریعتر و ارزانتر داشته باشند تا بتوانند  سرویس بهتری داشته باشند.
-   برای دستیابی به این مزایا، NFV مسیر را برای کاهش اختلافات در نحوه ارائه خدمات شبکه در مقایسه با عملکرد فعلی ایجاد می کند. خلاصه این ویژگی ها به شرح زیر است
+   با انعطاف پذیری بیشتری وعده می‌دهد تا بتواند بیشتر قابلیتها و خدمات شبکه خود را به کاربران و سایر خدمات باز کنند و امکان استقرار یا پشتیبانی از سرویسهای جدید شبکه را  به طور سریعتر و ارزانتر داشته باشند تا بتوانند  سرویس بهتری داشته باشند.
+   برای دستیابی به این مزایا، NFV مسیر را برای کاهش اختلافات در نحوه ارائه خدمات شبکه در مقایسه با عملکرد فعلی ایجاد می‌کند. خلاصه این ویژگیها به شرح زیر است
    \cite{NFV}.
  \begin{itemize}
-  \item \textbf{جدا سازی بخش نرم افزار از سخت افزار}:
-از آنجا که عنصر شبکه، ترکیبی از سخت افزارها و نرم افزارهای یکپارچه نخواهد بود، تکامل هر دو مستقل از یکدیگر می باشد.
-که این ویژگی منجر به جداسازی زمان بندی توسعه و نگهداری نرم افزار و سخت افزار می گردد.
+  \item \textbf{جدا سازی بخش نرم‌افزار از سخت افزار}:
+از آنجا که عنصر شبکه، ترکیبی از سخت افزارها و نرم‌افزارهای یکپارچه نخواهد بود، تکامل هر دو مستقل از یکدیگر می‌باشد.
+که این ویژگی منجر به جداسازی زمان بندی توسعه و نگهداری نرم‌افزار و سخت افزار می‌گردد.
 \item \textbf{استقرار عملکرد شبکه انعطاف پذیر:}
-جدا کردن نرم افزار از سخت افزار به تنظیم مجدد و به اشتراک گذاری منابع زیرساختی کمک می کند،
-بنابراین، سخت افزار و نرم افزار، باهمدیگر
-می توانند در زمان های مختلف عملکردهای مختلفی را انجام دهد که به اپراتورهای شبکه کمک می کند تا خدمات جدید شبکه را سریعتر در همان پلت فرم فیزیکی مستقر کنند.
+جدا کردن نرم‌افزار از سخت افزار به تنظیم مجدد و به اشتراک گذاری منابع زیرساختی کمک می‌کند،
+بنابراین، سخت افزار و نرم‌افزار، باهمدیگر
+میتوانند در زمانهای مختلف عملکردهای مختلفی را انجام دهد که به اپراتورهای شبکه کمک می‌کند تا خدمات جدید شبکه را سریعتر در همان پلت فرم فیزیکی مستقر کنند.
 بنابراین،
-مؤلفه ها را می توان در هر دستگاه با قابلیت NFV در شبکه قرار داد و اتصالات آنها به روشی انعطاف پذیر تنظیم کرد.
+مؤلفه‌ها را میتوان در هر دستگاه با قابلیت NFV در شبکه قرار داد و اتصالات آنها به روشی انعطاف پذیر تنظیم کرد.
 \item \textbf{مقیاس گذاری پویا}:
-  جداشدن عملکرد شبکه به اجزای نرم افزاری  نعطاف پذیری بیشتری را برای  عملکرد واقعی VNF به روشی پویاتر، 
+  جداشدن عملکرد شبکه به اجزای نرم‌افزاری  نعطاف پذیری بیشتری را برای  عملکرد واقعی VNF به روشی پویاتر، 
    با توجه به ترافیک واقعی که اپراتور شبکه برای تأمین ظرفیت نیاز دارد،
-  فراهم می کند.
+  فراهم می‌کند.
 \end{itemize}  
- \subsection{ساختار شبکه }
+در ادامه ساختار این شبکه به طور دقیق بیان می‌گردد.
  VNF
- ها برای به اشتراک گذاشتن منابع مختلف فیزیکی و مجازی زیرساخت ها می توانند مستقر و مجدداً تنظیم شوند ، تا مقیاس پذیری و کارآمدی سیستم را تضمین کنند که منجر می شود SP ها به سرعت سرویس های جدید را در سیستم وارد کنند.
- به طور کلی ، سه مؤلفه اصلی در NFV وجود دارد:
- خدمات ، NFVI و مدیریت NFV و orchestration
+ها برای به اشتراک گذاشتن منابع مختلف فیزیکی و مجازی زیرساختها میتوانند مستقر و مجدداً تنظیم شوند، تا مقیاس پذیری و کارآمدی سیستم را تضمین کنند که منجر می‌شود SPها به سرعت سرویسهای جدید را در سیستم وارد کنند.
+ به طور کلی، سه مؤلفه اصلی در NFV وجود دارد:
+ خدمات، NFVI و مدیریت NFV و orchestration
  \LTRfootnote{NFV-MANO}
- که در شکل \eqref{fig:NFV} دیده می شود.
+ که در شکل \eqref{fig:NFV} دیده می‌شود. ه‌ها
  \begin{figure}
@@
 \end{figure} 
-این مؤلفه ها به شرح زیر بیان می گردد\cite{NFVArch}.
+این مؤلفه‌ها به شرح زیر بیان می‌گردد\cite{NFVArch}.
 \begin{enumerate}
 \item 
-خدمات: یک سرویس مجموعه ای از VNF ها است که می توانند در یک یا چند ماشین مجازی پیاده سازی شوند.
-در بعضی مواقع ، VNF ها می توانند در ماشینهای مجازی نصب شده در سیستم عامل یا سخت افزار بطور مستقیم نصب شوند. آنها توسط سرپرستان بومی یا مانیتورهای ماشین مجازی اداره می شوند.
+خدمات: یک سرویس مجموعه ای از VNFها است که میتوانند در یک یا چند ماشین مجازی پیاده سازی شوند.
+در بعضی مواقع، VNFها میتوانند در ماشینهای مجازی نصب شده در سیستم عامل یا سخت افزار بطور مستقیم نصب شوند. آنها توسط سرپرستان بومییا مانیتورهای ماشین مجازی اداره می‌شوند.
 معمولاً توسط یک سیستم مدیریت عناصر \LTRfootnote{Element Management System} (EMS)،
- که مسئولیت ایجاد، تنظیمات، نظارت، عملکرد و امنیت آن است، اداره می شود.
+ که مسئولیت ایجاد، تنظیمات، نظارت، عملکرد و امنیت آن است، اداره می‌شود.
  EMS 
- اطلاعات ضروری مورد نیاز سیستم پشتیبانی عملیات \LTRfootnote{Operations Support System}(OSS) را در یک محیط SP فراهم می کند.
+ اطلاعات ضروری مورد نیاز سیستم پشتیبانی عملیات \LTRfootnote{Operations Support System}(OSS) را در یک محیط SP فراهم می‌کند.
  OSS
-  سیستم مدیریت عمومی است، که  همراه با سیستم پشتیبانی از تجارت 
+  سیستم مدیریت عمومیاست، که  همراه با سیستم پشتیبانی از تجارت 
 \LTRfootnote{Business Support System}  
   (BSS)
-  ، به ارائه دهندگان کمک می کند تا چندین سرویس ارتباطی از راه دور را به کار ببندند و مدیریت کنند.
-  (به عنوان مثال سفارش ، صورتحساب ، تمدید ، عیب یابی مشکل و غیره).
-مشخصات NFV بر ادغام با راه حل های موجود OSS / BSS متمرکز است.
+ ، به ارائه دهندگان کمک می‌کند تا چندین سرویس ارتباطی از راه دور را به کار ببندند و مدیریت کنند.
+  (به عنوان مثال سفارش، صورتحساب، تمدید، عیب یابی مشکل و غیره).
+مشخصات NFV بر ادغام با راه حلهای موجود OSS / BSS متمرکز است.
 \item NFVI
 :
-زیرساخت های NFV تمام منابع سخت افزاری و نرم افزاری را که شامل محیط NFV است ، پوشش می دهد.
-NFVI شامل اتصال شبکه بین مکان ها ، به عنوان مثال ، بین
-مراکز داده و ابرهای ترکیبی عمومی یا خصوصی است.
-منابع فیزیکی به طور معمول شامل محاسبات، ذخیره سازی و سخت افزار شبکه است که وظیفه ی آن پردازش، ذخیره سازی و اتصال VNF ها از طریق لایه مجازی سازی است و دقیقاً بالای سخت افزار قرار دارد و منابع فیزیکی را چکیده می کند (که به صورت منطقی تقسیم شده و به VNF ها اختصاص می یابد).
+زیرساختهای NFV تمام منابع سخت افزاری و نرم‌افزاری را که شامل محیط NFV است، پوشش می‌دهد.
+NFVI شامل اتصال شبکه بین مکانها، به عنوان مثال، بین
+مراکز داده و ابرهای ترکیبی عمومییا خصوصی است.
+منابع فیزیکی به طور معمول شامل محاسبات، ذخیره سازی و سخت افزار شبکه است که وظیفه ی آن پردازش، ذخیره سازی و اتصال VNFها از طریق لایه مجازی سازی است و دقیقاً بالای سخت افزار قرار دارد و منابع فیزیکی را چکیده می‌کند (که به صورت منطقی تقسیم شده و به VNFها اختصاص می‌یابد).
 هیچ راه حل خاصی برای استقرار NFV وجود ندارد.
-در عوض معماری NFV می تواند از یک لایه مجازی سازی موجود مانند Hypervisor با ویژگی های استاندارد که منابع سخت افزاری را به راحتی استخراج می کند و آنها را به VNF ها اختصاص می دهد ، استفاده کند.
-وقتی این پشتیبانی در دسترس نباشد ، اغلب ، لایه مجازی سازی از طریق یک سیستم عامل حاصل می شود که نرم افزاری را در بالای سرور غیر مجازی یا با اجرای یک VNF به عنوان یک برنامه اضافه می کند.
+در عوض معماری NFV میتواند از یک لایه مجازی سازی موجود مانند Hypervisor با ویژگیهای استاندارد که منابع سخت افزاری را به راحتی استخراج می‌کند و آنها را به VNFها اختصاص می‌دهد، استفاده کند.
+وقتی این پشتیبانی در دسترس نباشد، اغلب، لایه مجازی سازی از طریق یک سیستم عامل حاصل می‌شود که نرم‌افزاری را در بالای سرور غیر مجازی یا با اجرای یک VNF به عنوان یک برنامه اضافه می‌کند.
 \item NFV-MANO
@@
  مدیران VNFs و مدیران زیرساخت مجازی.
- چنین بلوکی عملکردهای مورد نیاز برای کارهای مدیریتی را که برای VNF ها اعمال می شود، به عنوان مثال تهیه و پیکربندی را  ارائه می دهد. 
- NFV-MANO شامل orchestration و مدیریت چرخه منابع فیزیکی یا مجازی است که از مجازی سازی زیرساخت ها و مدیریت چرخه VNF ها پشتیبانی می کند.
- همچنین شامل بانکهای اطلاعاتی است که برای ذخیره اطلاعات و مدل های داده استفاده می شود که ویژگی های چرخه عمر توابع، خدمات و منابع را تعریف می کند.
+ چنین بلوکی عملکردهای مورد نیاز برای کارهای مدیریتی را که برای VNFها اعمال می‌شود، به عنوان مثال تهیه و پیکربندی را  ارائه می‌دهد. 
+ NFV-MANO شامل orchestration و مدیریت چرخه منابع فیزیکی یا مجازی است که از مجازی سازی زیرساختها و مدیریت چرخه VNFها پشتیبانی می‌کند.
+ همچنین شامل بانکهای اطلاعاتی است که برای ذخیره اطلاعات و مدلهای داده استفاده می‌شود که ویژگیهای چرخه عمر توابع، خدمات و منابع را تعریف می‌کند.
  NFV-MANO روی کلیه وظایف مدیریتی مجازی سازی ویژه لازم در چارچوب NFV تمرکز دارد.
- علاوه بر این ، این چارچوب رابط هایی را تعیین می کند که می توانند برای ارتباطات بین مؤلفه های مختلف
+ علاوه بر این، این چارچوب رابطهایی را تعیین می‌کند که میتوانند برای ارتباطات بین مؤلفه‌‌های مختلف
   NFV MANO، 
- و همچنین هماهنگی با سیستم های سنتی مدیریت شبکه (یعنی OSS و BSS) مورد استفاده قرار گیرند تا امکان عملکرد هر دو VNF و کارکردهای اجرا شده بر روی تجهیزات فراهم شود.
- به طور خلاصه، اگر برش شبکه با استفاده از فایروال و DPI مستقر شده باشد، آنگاه NFV-MANO وظیفه دارد بگوید این VNF ها در کجای شبکه فیزیکی قرار دارند. همچنین این VNF ها توسط EMS و همان MANO کنترل می شوند.
+ و همچنین هماهنگی با سیستمهای سنتی مدیریت شبکه (یعنی OSS و BSS) مورد استفاده قرار گیرند تا امکان عملکرد هر دو VNF و کارکردهای اجرا شده بر روی تجهیزات فراهم شود.
+ به طور خلاصه، اگر برش شبکه با استفاده از فایروال و DPI مستقر شده باشد، آنگاه NFV-MANO وظیفه دارد بگوید این VNFها در کجای شبکه فیزیکی قرار دارند. همچنین این VNFها توسط EMS و همان MANO کنترل می‌شوند.
 \end{enumerate}
-\section{شبکه تعریف شده نرم افزار (SDN)}
+\section{شبکه تعریف شده نرم‌افزار (SDN)}
 بنیاد شبکه باز 
@@
  به طور صریح و دقیق SDN را بدین صورت تعریف کرد:
- شبکه تعریف شده توسط نرم افزار (SDN) یک معماری شبکه است که کنترل شبکه از ارسال جدا می شود و به طور مستقیم قابل برنامه ریزی است.
- SDN توسط دو ویژگی تعریف می شود ، یعنی جدا شدن صفحه ی کنترل و داده و قابلیت برنامه ریزی در صفحه کنترل.
- با این وجود ، هیچ یک از این دو امضای SDN در معماری شبکه کاملاً جدید نیستند
+ شبکه تعریف شده توسط نرم‌افزار (SDN) یک معماری شبکه است که کنترل شبکه از ارسال جدا می‌شود و به طور مستقیم قابل برنامه ریزی است.
+ SDN توسط دو ویژگی تعریف می‌شود، یعنی جدا شدن صفحه ی کنترل و داده و قابلیت برنامه ریزی در صفحه کنترل.
+ با این وجود، هیچ یک از این دو امضای SDN در معماری شبکه کاملاً جدید نیستند
  \cite{SDN1}.
  SDN 
- در اصل یک الگوی شبکه سازی متمرکز است که در آن هوش شبکه (یعنی عملکرد کنترل یا صفحه کنترل) به طور منطقی در یک یا مجموعه ای از موجودیت های کنترل (یعنی کنترل کننده های SDN) متمرکز می شود در حالی که صفحه ی انتقال داده،  ساده و چکیده شده برای برنامه های کاربردی می باشد و سرویس های شبکه درخواست خود را از طریق کنترل کننده های SDN
- بیان می کنند.
- در حالی که در مورد هسته اصلی شبکه موبایل LTE ، EPC صحبت می کنیم ، مفهوم SDN برای دستیابی به جدایی واضح بین صفحات کنترل و کاربر در اشخاص SGW و PGW استفاده می شود.
+ در اصل یک الگوی شبکه سازی متمرکز است که در آن هوش شبکه (یعنی عملکرد کنترل یا صفحه کنترل) به طور منطقی در یک یا مجموعه ای از موجودیتهای کنترل (یعنی کنترل کننده‌های SDN) متمرکز می‌شود در حالی که صفحه ی انتقال داده،  ساده و چکیده شده برای برنامه‌‌های کاربردی می‌باشد و سرویسهای شبکه درخواست خود را از طریق کنترل کننده‌های SDN
+ بیان میکنند.
+ در حالی که در مورد هسته اصلی شبکه موبایل LTE، EPC صحبت میکنیم، مفهوم SDN برای دستیابی به جدایی واضح بین صفحات کنترل و کاربر در اشخاص SGW و PGW استفاده می‌شود.
  با تقسیم دروازه به این روش (یعنی از SGW به SGW-C و
@@
 و از PGW به PGW-C و (PGW-U 
-  مقیاس بندی این مؤلفه ها به طور مستقل امکان پذیر است و طیف وسیعی از گزینه های استقرار را نیز ممکن می کند.
+  مقیاس بندی این مؤلفه‌‌ها به طور مستقل امکان پذیر است و طیف وسیعی از گزینه‌‌های استقرار را نیز ممکن می‌کند.
 
- پروتکل مورد استفاده بین صفحه ی کنترل و صفحه ی کاربر می تواند یا افزونه پروتکل موجود OpenFlow باشد، که توسط گروه کاری بی سیم و موبایل ONF (WMWG)با رابط های جدید، یعنی Sxa و Sxb ساخته می شود، که توسط  \lr{3GPP CUPS} تعریف و مشخص می شوند\cite{SDN2}.
- جداسازی صفحه ی کنترل از کاربر منجر به کنترل بیشتر شبکه بوسیله ی برنامه می گردد که منجر به بهبود تنظیمات و کارآمدی سیستم می گردد.
+ پروتکل مورد استفاده بین صفحه ی کنترل و صفحه ی کاربر میتواند یا افزونه پروتکل موجود OpenFlow باشد، که توسط گروه کاری بی سیم و موبایل ONF (WMWG)با رابطهای جدید، یعنی Sxa و Sxb ساخته می‌شود، که توسط  \lr{3GPP CUPS} تعریف و مشخص می‌شوند\cite{SDN2}.
+ جداسازی صفحه ی کنترل از کاربر منجر به کنترل بیشتر شبکه بوسیله ی برنامه می‌گردد که منجر به بهبود تنظیمات و کارآمدی سیستم می‌گردد.
  SDN
-  با ساختار برنامه ریزی شده ی قوانین ترافیک، جایگزین امیدوار کننده ای برای فرماندهی ترافیک ارائه می دهد.
+  با ساختار برنامه ریزی شده ی قوانین ترافیک، جایگزین امیدوار کننده ای برای فرماندهی ترافیک ارائه می‌دهد.
   ساختار SDN در شکل \eqref{fig:SDN} آورده شده است.
@@
 \end{figure} 
-  در این ساختار ۳ لایه ی مختلف وجود دارد که در ادمه بیان می کنیم\cite{SDN3}.
+  در این ساختار ۳ لایه ی مختلف وجود دارد که در ادمه بیان میکنیم\cite{SDN3}.
   \begin{enumerate}
   \item لایه ی برنامه :
-  این لایه مجموعه ای از برنامه های متمرکز بر خدمات شبکه را پوشش می دهد و آنها عمدتا برنامه های نرم افزاری هستند که با لایه کنترل ارتباط برقرار می کنند.
+  این لایه مجموعه ای از برنامه ‌های متمرکز بر خدمات شبکه را پوشش می‌دهد و آنها عمدتا برنامه‌‌های نرم‌افزاری هستند که با لایه کنترل ارتباط برقرار میکنند.
   \item لایه ی کنترل:
-  به عنوان هسته اصلی SDN ، لایه کنترل از یک کنترلر متمرکز تشکیل شده است که منطقاً نمای شبکه جهانی و پویا را حفظ می کند ،  که از لایه برنامه درخواست می کند و دستگاه های شبکه را از طریق پروتکل های استاندارد مدیریت می کند.
+  به عنوان هسته اصلی SDN، لایه کنترل از یک کنترلر متمرکز تشکیل شده است که منطقاً نمای شبکه جهانی و پویا را حفظ می‌کند،  که از لایه برنامه درخواست می‌کند و دستگاه‌های شبکه را از طریق پروتکلهای استاندارد مدیریت می‌کند.
   \item لایه ی داده:
-  این لایه، زیرساخت ها شامل سوئیچ ها، روترها و لوازم شبکه می باشد. در زمینه SDN ، این دستگاه ها قابل برنامه ریزی هستند و از رابط های استاندارد پشتیبانی می کنند.
+  این لایه، زیرساختها شامل سوئیچها، روترها و لوازم شبکه می‌باشد. در زمینه SDN، این دستگاه‌ها قابل برنامه ریزی هستند و از رابطهای استاندارد پشتیبانی میکنند.
   \end{enumerate}
  \section{برش شبکه}
- پیش بینی می شود شبکه های \lr{5G} چندین سرویس را با نیازهای مختلف به طور همزمان پشتیبانی کند.
+ پیش بینی می‌شود شبکه‌‌های \lr{5G} چندین سرویس را با نیازهای مختلف به طور همزمان پشتیبانی کند.
  برش شبکه
@@
 به عنوان راه حلی برای چنین تقاضا در نظر گرفته شده است.
-یک برش شبکه، یک شبکه منطقی \lr{end-to-end} است که خدمات  با نیازهای خاص را ارائه می دهد.
+یک برش شبکه، یک شبکه منطقی \lr{end-to-end} است که خدمات  با نیازهای خاص را ارائه می‌دهد.
  چندین برش شبکه
 در یک زیرساخت یکسان
-  اجرا و مدیریت می شوند و
-به طور مستقل کار می کنند.
+  اجرا و مدیریت می‌شوند و
+به طور مستقل کار میکنند.
 برش شبکه
- با هدف تقسیم منطقی مجموعه توابع و منابع شبکه در یک نهاد شبکه در نظر گرفته شده است که مطابق با خواسته های فنی یا تجاری خاص می باشد.
- با خرد کردن یک شبکه فیزیکی به چندین شبکه منطقی، برش شبکه می تواند از خدمات متناسب با تقاضا برای سناریوهای برنامه مشخص در همان زمان با استفاده از همان شبکه فیزیکی پشتیبانی کند.
-با استفاده از برش شبکه، منابع شبکه می توانند به صورت پویا و کارآمد به برش های شبکه منطقی با توجه به خواسته های QoS مربوطه اختصاص داده شوند\cite{NS1}.
+ با هدف تقسیم منطقی مجموعه توابع و منابع شبکه در یک نهاد شبکه در نظر گرفته شده است که مطابق با خواسته‌‌های فنی یا تجاری خاص می‌باشد.
+ با خرد کردن یک شبکه فیزیکی به چندین شبکه منطقی، برش شبکه میتواند از خدمات متناسب با تقاضا برای سناریوهای برنامه مشخص در همان زمان با استفاده از همان شبکه فیزیکی پشتیبانی کند.
+با استفاده از برش شبکه، منابع شبکه میتوانند به صورت پویا و کارآمد به برشهای شبکه منطقی با توجه به خواسته‌‌های QoS مربوطه اختصاص داده شوند\cite{NS1}.
 
@@
 \end{figure} 
-پیاده سازی های مختلفی از برش شبکه وجود دارد که شامل برش هسته ی شبکه، برش \lr{RAN} و برش هر دو بخش می باشد\cite{NS2}.
+پیاده سازیهای مختلفی از برش شبکه وجود دارد که شامل برش هسته ی شبکه، برش \lr{RAN} و برش هر دو بخش می‌باشد\cite{NS2}.
 \begin{itemize}
@@
 هسته ی شبکه (CN) \LTRfootnote{core network}
-به عنوان برش های شبکه، مجازی سازی می شوند که با ویژگی هایی مانند ویژگی های قابل برنامه ریزی و قابل اعتماد بودن که شامل مدیریت حرکت و تأیید اعتبار می باشد.
-برش های شبکه فقط در CN وجود دارد.
+به عنوان برشهای شبکه، مجازی سازی می‌شوند که با ویژگیهایی مانند ویژگیهای قابل برنامه ریزی و قابل اعتماد بودن که شامل مدیریت حرکت و تأیید اعتبار می‌باشد.
+برشهای شبکه فقط در CN وجود دارد.
   بنابراین، نه RAN و نه تجهیزات کاربر (UE) برای CNهای برش داده شده نیاز به تنظیم ویژه ندارند.
-  در برش هسته ی شبکه، برش تنها در بخش هسته ی شبکه است و تمام واسط ها و فرآیندها، بدون تغییر باقی می مانند
-  به جز مواردی که در ابتدا UE ها به شبکه ها وصل می شوند ، زیرا UE ها باید به برش صحیح CN ها اختصاص داده شوند.
+  در برش هسته ی شبکه، برش تنها در بخش هسته ی شبکه است و تمام واسطها و فرآیندها، بدون تغییر باقی میمانند
+  به جز مواردی که در ابتدا UEها به شبکه‌‌ها وصل می‌شوند، زیرا UEها باید به برش صحیح CNها اختصاص داده شوند.
 \item \textbf{
@@
 برخلاف برش CN،
-برش های RAN روی سخت افزار رادیویی و استخر منابع باند پایه، به نام یک سطح بی سیم، اجرا می شوند که دارای کشش کمتری نسبت به زیرساخت مجازی بالغ شده در CNها هستند.
-با چند BS منطقی، برش های RAN پارامترهای مختلفی از رابط های هوا (به عنوان مثال ، طول نماد ، فاصله زیر حامل ، طول پیشوند چرخه و پارامترهای درخواست تکرار خودکار هیبریدی \LTRfootnote{HARQ}) را اعمال می کند.
-علاوه بر این، پارامترهای دیگری مانند انتخاب سلول و آستانه انتقال، و همچنین سیاست های انتقال هماهنگ را می توان برای هر برش تعریف کرد تا یک تجربه بی سیم برجسته را به کاربران ارائه دهد.
+برشهای RAN روی سخت افزار رادیویی و استخر منابع باند پایه، به نام یک سطح بی سیم، اجرا می‌شوند که دارای کشش کمتری نسبت به زیرساخت مجازی بالغ شده در CNها هستند.
+با چند BS منطقی، برشهای RAN پارامترهای مختلفی از رابطهای هوا (به عنوان مثال، طول نماد، فاصله زیر حامل، طول پیشوند چرخه و پارامترهای درخواست تکرار خودکار هیبریدی \LTRfootnote{HARQ}) را اعمال می‌کند.
+علاوه بر این، پارامترهای دیگری مانند انتخاب سلول و آستانه انتقال، و همچنین سیاستهای انتقال هماهنگ را میتوان برای هر برش تعریف کرد تا یک تجربه بی سیم برجسته را به کاربران ارائه دهد.
 \item \textbf{برش هسته و شبکه ی دسترسی رادیویی}:
-در این سناریو، هر برش از RAN به یک برش از هسته متصل می شود، بنابراین اپراتورها می توانند یک شبکه منطقی انتهای به مشتریان ارائه دهند.
+در این سناریو، هر برش از RAN به یک برش از هسته متصل می‌شود، بنابراین اپراتورها میتوانند یک شبکه منطقی انتهای به مشتریان ارائه دهند.
 روش انتخاب برش همان روش برش RAN است، بنابراین کاربران پس از دسترسی به سیستم، نیازی به انتخاب برش CN ندارند.
 این مدل از برش مزایای هر دو مدل از برش را باهم دارد.
- در نتیجه این روش برش، قادر به برنامه ریزی ویژگی های CN و همچنین دارای قابلیت تغییر رابط های هوایی RAN
- می باشد.
+ در نتیجه این روش برش، قادر به برنامه ریزی ویژگیهای CN و همچنین دارای قابلیت تغییر رابطهای هوایی RAN
+ می‌باشد.
 
 \end{itemize}
+\section{مسائل Np-Hard}
+در اینجا به دو مسئله‌ی کوله‌پشتی و بسته بندی جعبه می پردازیم. این دو مسئله NP-Hard هستند.
+مسئله‌ی NP-hard را نمی توان در زمان چند جمله‌ای حل کرد و نیاز به روش ابتکاری است. این دو مسئله شامل کوله‌پشتی و بسته‌بندی جعبه می‌باشد.
+\subsection{مسئله‌ی کوله‌پشتی}
+یکی از مسائل NP-Hard، مسئله ی کوله پشتی \LTRfootnote{knapsack}
+می باشد. در این مسئله می خواهیم تعدادی شی با وزنهای مختلف را در تعدادی جایگاه با ظرفیت مشخص قرار دهیم.
+هدف در این مسئله قرارگیری بیشترین تعداد اشیاء در این جایگاه‌ها می باشد.
+حل این مسئله با استفاده از روش های مختلف صورت می‌گیرد. این مسئله بدین صورت فرمول بندی می‌شود.
+\begin{subequations}
+	\begin{alignat}{4}
+		\max\limits_{\boldsymbol{x} }   \quad &   \sum_{j=1}^{N} p_j x_{j}\\
+		\text{\lr{subject to}} \quad & \textstyle \sum_{j=1}^{N} r_{i,j}x_{j} \leq b_i  \quad i =1,...,m, \\
+		&\textstyle  x_j \in \{0,1\} \label{eqmain}
+	\end{alignat}
+	\label{constraints2}
+\end{subequations}
+که در اینجا، m شرط، شرطهای کوله‌پشتی می‌باشد. در نتیجه این مسئله، کوله‌پشتی mبعدی می‌باشد\cite{chu1998genetic}.
+$p_j$
+ارزش گزاری شی jام می‌باشد.
+همچنین 
+برای حل این مسائل از الگوریتمهای branch-and-bound و cutting-plane و الگوریتمهای ابتکاری استفاده می‌شود.
+\subsubsection{مسئله‌ی بسته‌بندی جعبه}
+در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می‌باشد.
+در مسئله ی بسته بندی جعبه \LTRfootnote{bin packing}
+هدف کمینه کردن تعداد جعبه‌های ورودی با فرض اینکه همه‌ی اشیا در آن جا شوند.
+حل این مسئله با استفاده از روش های مختلف صورت می‌گیرد. این مسئله بدین صورت فرمول بندی می‌شود.
+\begin{subequations}
+	\begin{alignat}{4}
+		\min\limits_{\boldsymbol{x} }   \quad &   \sum_{j=1}^{N}  x_{j}\\
+		\text{\lr{subject to}} \quad & \textstyle \sum_{j=1}^{N} r_{i,j}x_{j} \leq b_i  \quad i =1,...,m, \\
+		&\textstyle  x_j \in \{0,1\} \label{eqmain}
+	\end{alignat}
+	\label{constraints2}
+\end{subequations}
+
 \section{نتیجه گیری}
-  در این فصل ابتدا مروری بر تاریخچه ی مخابرات و ۵ نسل مخابراتی شد. سپس ساختار های مختف دسترسی رادیویی به طور خلاصه بیان شد و در نتیجه ی آن ساختار CRAN که ساختار ابری است تعریف شد. سپس ساختار xRAN
+  در این فصل ابتدا مروری بر تاریخچه ی مخابرات و ۵ نسل مخابراتی شد. سپس ساختارهای مختف دسترسی رادیویی به طور خلاصه بیان شد و در نتیجه ی آن ساختار CRAN که ساختار ابری است تعریف شد. سپس ساختار xRAN
   مورد توجه قرار گرفت و در نهایت ساختار ORAN 
-  که ترکیب و تکاملی از CRAN و xRAN می باشد مورد توجه قرار گرفت.
+  که ترکیب و تکاملی از CRAN و xRAN می‌باشد مورد توجه قرار گرفت.
 
@@
  NFV و SDN 
- می باشد که منجر به جداسازی صفحه ی کنترل از کاربر می شود و سیستم هوشمندتر همراه با قابلیت برنامه ریزی بیشتر می گردد.
+ می‌باشد که منجر به جداسازی صفحه ی کنترل از کاربر می‌شود و سیستم هوشمندتر همراه با قابلیت برنامه ریزی بیشتر می‌گردد.
  در ادامه برش شبکه در بخش رادیویی و هسته و هردو مورد توجه قرار گرفته شد.
-\section{خلاصه ای از فصل های آتی}
-در فصل دوم مروری بر ادبیات پیشین و خلاصه ای از مدل سیستم مقالات موجود، بیان می گردد.
-در فصل سوم مدل سیستم در نظر گرفته بیان می شود و صورت مسئله به نمایش گذاشته می شود و روش های حل آن بیان می گردد.
-در فصل چهارم نتایج شبیه سازی قرار داده می شود.
-در فصل پنجم نیز نتیجه گیری و کارهای آتی مورد نظر بیان می شود.
+\section{دستاوردهای پروژه}
+در اینجا، هدف در نظرگیری ساختار رادیویی دسترسی باز در نسل پنجم و تخصیص منابع آن می‌باشد.
+ مسئله‌ی برش شبکه در بخش رادیویی و قرارگیری توابع مجازی شبکه برروی مراکز داده باهم در شبکه‌ی دسترسی رادیویی باز مورد بررسی قرار گرفته است.
+برای حل این مسئله، ابتدا مسئله را به دو مسئله‌ی کوچکتر مختلف شکسته که در بخش اول، تخصیص برش شبکه به کاربران سرویسها و تخصیص توان در ساختار رادیویی باز حل شده و پس از آن، برشهایی از شبکه که به سرویس اختصاص داده شده را به مراکز داده نگاشت می‌دهیم.
+در این مسئله، تاخیر و نرخ هر کاربر در سرویس مورد بررسی قرار گرفته شده و چالش تخصیص منابع که شامل برش بخش رادیویی به هر سرویس است و جاگیری توابع شبکه حل می‌شود.
+الگوریتم ارائه شده سرعت بسیار بیشتری از الگوریتم بهینه که با MOSEK و CVX بدست می‌آید، دارد. این الگوریتم به صورت متمرکز حل شده است.. 
+سپس مسئله به صورت ساده‌تر به دو مسئله‌ی بسته‌بندی جعبه و کوله‌پشتی نوشته شده و برای حالت دینامیکی متغیر با زمان با روش یادگیری تقویتی حل می‌کنیم. 
+\section{ساختار پروژه}
+در این فصل مروری بر مفاهیم مورد استفاده در پروژه کردیم
+در فصل دوم مروری بر ادبیات پیشین و خلاصه‌ای از مدل سیستم مقالات موجود، بیان می‌گردد.
+در این فصل ابتدا صورت مسئله‌ی برش شبکه، شبکه‌های دسترسی رادیویی باز و قرارگیری توابع شبکه در مراکز داده بررسی کرده سپس در مورد حل مسئله به روش دینامیکی صحبت می‌کنیم.
+در فصل سوم مدل سیستم در نظر گرفته بیان می‌شود و صورت مسئله به نمایش گذاشته می‌شود و روشهای حل آن بیان می‌گردد. همچنین  نتایج شبیه سازی قرار داده می‌شود.
+در فصل چهارم در صورت مسئله را ساده‌سازی کرده و با روش دینامیکی حل می‌نماییم.
+در فصل پنجم نیز نتیجه گیری و کارهای آتی مورد نظر و پیشنهادات بیان می‌شود.

### 2020-09-09 Latex/tehran-thesis/tex/chapter2.tex
add file

@@
 در این بخش مروری بر حل مسائل توسط مقالات می نماییم.
-\subsection{ مسئله ی کوله پشتی }
+ابتدا به دو مسئله ی معروف NP-Hard
+اشاره می کنیم سپس به حل مسائل با استفاده از روش یادگیری تقویتی می پردازیم.
+\subsection{مسائل Np-Hard}
+در اینجا به دو مسئله‌ی کوله پشتی و بسته بندی جعبه می پردازیم. این دو مسئله NP-Hard هستند.
+مسئله‌ی NP-hard را نمی توان در زمان چند جمله‌ای حل کرد در نتیجه از روشهای ابتکاری برای رسیدن به جواب نزدیکه بهینه استفاده می‌شود.
+\subsubsection{ مسئله‌ی کوله‌پشتی }
 یکی از مسائل پیش رو، مسئله ی کوله پشتی \LTRfootnote{knapsack}
@@
 می باشد که در این مسئله می خواهیم تعدادی شی با وزنهای مختلف را در تعدادی جایگاه با ظرفیت مشخص قرار دهیم.
-هدف در این مسئله جاگیری بیشترین تعداد اشیاء در این جایگاه ها می باشد.
+هدف در این مسئله قرارگیری بیشترین تعداد اشیاء در این جایگاه ها می باشد.
 حل این مسئله با استفاده از روش های مختلف صورت می گیرد.
@@
 
-در مقاله ی
+در مقاله‌ی
 \cite{sciancalepore2017mobile}
@@
 راه حل کنترل پذیرش به یک مسئله کوله پشتی هندسی (دو بعدی) ترسیم شده و دو الگوریتم کم پیچیدگی به ترتیب برای درخواست های برش شبکه منظم و نامنظم طراحی شده اند.
-\subsection{مسئله ی بسته بندی جعبه}
+\subsubsection{مسئله‌ی بسته‌بندی جعبه}
  در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می باشد.

### 2020-09-09 Latex/tehran-thesis/tex/chapter5.tex
add file

--- 2020-09-08 Latex/tehran-thesis - Copy/tex/chapter5.tex
@@
 در اینجا، مسئله‌ی برش شبکه در بخش رادیویی و قرارگیری توابع مجازی شبکه برروی مراکز داده باهم مورد بررسی قرار گرفته شد.
-برای حل این مسئله، ابتدا مسئیله به دو بخش مخنلف شکسته شد که در بخش اول، تخصیص برش شبکه به کاربران سرویسها و تخصیص توان حل شده و پس از آن، برشهایی از شبکه که به سرویس اختصاص داده شده را به مراکز داده نگاشت می‌دهیم.
+برای حل این مسئله، ابتدا مسئله به دو بخش مختلف شکسته شد که در بخش اول، تخصیص برش شبکه به کاربران سرویسها و تخصیص توان حل شده و پس از آن، برشهایی از شبکه که به سرویس اختصاص داده شده را به مراکز داده نگاشت می‌دهیم.
 در این مسئله، تاخیر و نرخ هر کاربر در سرویس مورد بررسی قرار گرفته شده و چالش تخصیص منابع که شامل برش بخش رادیویی به هر سرویس است و جاگیری توابع شبکه حل می‌شود.
@@
  \section{پیشنهادات}
+ در این بخش، پیشنهادات و کارهای آتی را بیان خواهیم کرد.
+ \begin{itemize}
+\item
+ یکی از کارهای آتی، مدل کردن برش شبکه در ساختار رادیویی و حل مفصل آن بوسیله‌ی روش یادگیری تقویتی عمیق می‌باشد.
+در فصل چهارم از این روش برای سیستم ساده شده استفاده گردیده و در فصل سوم نیز مدل سیستم بیان شده، یکی از کارهای بعدی این است که سیستم مدل فصل سوم را به طور دقیق
+با این روش حل نماییم. که در اینجا، بدست آوردن توان و ارتباط برش با سرویس از این روش بدست خواهد آمد.
+\item 
+یکی دیگر از کارهای آتی، بدست آوردن پارامترهای کیفیت سرویس QoS\LTRfootnote{Quality of Service}
+در شبکه‌های دسترسی باز می‌باشد که شامل تاخیر انتها به انتها، میزان از دست دادن بسته ها\LTRfootnote{Packet Loss}،
+قابلیت اطمینان و ... می‌باشد.
+در اینجا می‌توان تاخیر را هم در بخش رادیویی هم در بخش هسته‌ی شبکه بدست آورد. 
+همچنین،
+به منظور نشان دادن نقش هوش در ORAN طرح مدیریت هوشمند منابع رادیویی را برای کنترل تراکم ترافیک و نشان دادن کارایی آن در یک مجموعه داده واقعی از یک اپراتور بزرگ بدست می‌آوریم.
+\item 
+شبکه تعریف شده توسط نرم افزار (SDN) و مجازی سازی عملکرد شبکه (NFV) فناوری های کلیدی امکان پذیر در شبکه های ارتباطی نسل پنجم (5G) برای قرارگیری برش های شبکه سفارشی در سطح سرویس در زیرساخت شبکه، بر اساس خواسته های منابع آماری برای تأمین کیفیت طولانی مدت خدمات (QoS) مورد نیاز می‌باشد.
+با این حال، بارهای ترافیکی در برش های مختلف با گذشت زمان تحت تغییر قرار می‌گیرند ، در نتیجه چالش هایی برای تأمین کیفیت کیفیت مداوم ایجاد می‌شود.
+در کارهای آتی یک مشکل انتقال جریان پویا برای سرویس های متصل شده به برش شبکه، برای پاسخگویی به نیازهای تأخیر پایان انتها به انتها (E2E) با ترافیک متغیر، مورد بررسی قرار خواهد گرفت.
+\item
+یکی دیگر از کارهای آتی، تخصیص منابع به روش توزیع شده برای برش شبکه از منابع محاسباتی و منابع دیگر همانند پهنای باند می‌باشد.
+همچنین از روش توزیع شده در لینک فراسو  
+\LTRfootnote{Uplink}
+برای تخصیص توان کاربران، تخصیص پهنای باند و ... استفاده می‌گردد. یکی از روشها، استفاده از 
+\lr{Distributed ADMM}
+می‌باشد که در این روش تعدادی عامل به صورت همکارانه سعی در حل یک معادله‌ی بهینه‌سازی مشترک دارند که تابع هدف مجموعی از مقدارهای خصوصی هر عامل ‌می‌باشد. 
+ \end{itemize}

### 2020-09-10 Latex/tehran-thesis/tex/chapter2.tex
finish report

--- 2020-09-04 Latex/tehran-thesis/tex/chapter2.tex
@@
 \section{مقدمه}
-در این فصل، به مرور کارهای گذشته می پردازیم.
-ابتدا صورت مسئله مقالات مختلف را بررسی می نماییم که
+در این فصل، به مرور کارهای گذشته می‌پردازیم.
+ابتدا صورت مسئله مقالات مختلف را بررسی می‌نماییم که
  به ترتیب شامل مقالاتی هستند که از برش شبکه استفاده کرده اند.
-برش شبکه در سه بخش رادیویی، بخش هسته و هردو بخش هسته و رادیویی صورت می گیرد.
-سپس در زمینه ی سیر عبور از شبکه های دسترسی رادیویی ابری به شبکه های دسترسی رادیویی باز مطالعه نموده و بعد از آن درباره ی جاگیری VNF ها صحبت می کنیم.
-سپس در مورد روش حل مسئله صحبت می کنیم که شامل مسائل کوله پشتی و بسته بندی جعبه می باشد و در نهایت در مورد روشهای یادگیری تقویتی صحبت می کنیم.
-\section{مسائل پیش رو}
-در این بخش به مطالعه ی مسائل پیش رو می پردازیم. 
+برش شبکه در سه بخش رادیویی، بخش هسته و هردو بخش هسته و رادیویی صورت می‌گیرد.
+سپس در زمینه ی سیر عبور از شبکه های دسترسی رادیویی ابری به شبکه های دسترسی رادیویی باز مطالعه نموده و بعد از آن درباره ی جاگیری VNF ها صحبت می‌کنیم.
+سپس در مورد روش حل مسئله صحبت می‌کنیم که شامل مسائل کوله پشتی و بسته بندی جعبه می‌باشد و در نهایت در مورد روشهای یادگیری تقویتی صحبت می‌کنیم.
+\section{مسائل حل شده}
+در این بخش به مطالعه ی مسائل پیش رو می‌پردازیم. ‌‌‌
 \subsection{برش شبکه}
-برش شبکه یک شبکه منطقی انتها به انتهای مستقل است که بر روی یک زیرساخت فیزیکی مشترک کار می کند و قادر به ارائه خدمات می باشد.
-در این بخش برش شبکه در بخش رادیویی و هسته و هردو را بررسی می کنیم.
+برش شبکه یک شبکه منطقی انتها به انتهای مستقل است که بر روی یک زیرساخت فیزیکی مشترک کار ‌ و قادر به ارائه خدمات می‌باشد.
+در این بخش برش شبکه در بخش رادیویی و هسته و هردو را بررسی می‌کنیم.
 %\subsection{برش شبکه در شبکه های دسترسی رادیویی }
-برش RAN یکی از کلیدهای اصلی برای انعطاف پذیری سفارشات و مدیریت مجازی سازی ایستگاه پایه می باشد تا بتواند منابع رادیویی را در میان سرویس های مختلف تقسیم کرده و منجر به سازگاری اپراتورها و برطرف کردن نیاز سرویس ها گردد.
-%در ادامه مروری بر این مدل مقالات می نماییم.
+برش RAN یکی از کلیدهای اصلی برای انعطاف پذیری سفارشات و مدیریت مجازی سازی ایستگاه پایه می‌باشد تا بتواند منابع رادیویی را در میان سرویس های مختلف تقسیم کرده و منجر به سازگاری اپراتورها و برطرف کردن نیاز سرویس ها گردد.
+%در ادامه مروری بر این مدل مقالات می‌نماییم.
 %\subsubsection{  برش شبکه در شبکه های دسترسی رادیویی ابری و متجانس و مهی}
 
-شبکه های دسترسی رادیویی ابر (C-RAN) به عنوان یک چارچوب امیدوار کننده برای سیستم های ارتباط بی سیم نسل پنجم ظاهر شده اند.
-از آنجا که آنها می توانند پیچیدگی رمزگشایی، مصرف انرژی و دخالت های ناشی از افزایش تراکم تلفن همراه را کاهش دهند\cite{cranInt}.
-در ادامه در مورد برش شبکه در بخش رادیویی شبکه های دسترسی رادیویی ابری صحبت می کنیم.
+شبکه های دسترسی رادیویی ابر (C-RAN) به عنوان یک چارچوب امیدوار کننده برای سیستم های ارتباط بی سیم نسل پنجم ظاهر شده‌اند.
+از آنجا که آنها میتوانند پیچیدگی رمزگشایی، مصرف انرژی و دخالت های ناشی از افزایش تراکم تلفن همراه را کاهش دهند\cite{cranInt}.
+در ادامه در مورد برش شبکه در بخش رادیویی شبکه های دسترسی رادیویی ابری صحبت می‌کنیم.
 
-در مقاله ی \cite{lee2018dynamic}
-برش شبکه به صورت دینامیکی در بخش رادیویی مورد بررسی قرار گرفته شده است.
-برش شبکه در اینجا به عنوان فرآیند تخصیص منابع شبکه به کاربران انجام می شود
-چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش کاربران، ارتباط کاربر که شامل تخصیص واحد رادیویی (RRH) برای بیشینه سازی نرخ کاربران و تخصیص ظرفیت منابع باند پایه (‌BBU) و یک سطح پایین تر، که تخصیص توان و بلوک منابع فیزیکی (PRB) در میان کاربران می باشد.
-در این مدل فرض می کنیم که هر سرویس دارای شبکه اصلی خود (یا قطعه اصلی شبکه) است که به H-CRAN متصل می شود.
+در مقاله‌ی \cite{lee2018dynamic}
+برش شبکه به صورت دینامیکی در بخش رادیویی مورد بررسی قرار گرفته شده‌است.
+برش شبکه در اینجا به عنوان فرآیند تخصیص منابع شبکه به کاربران انجام ‌
+چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش کاربران، ارتباط کاربر که شامل تخصیص واحد رادیویی (RRH) برای بیشینه سازی نرخ کاربران و تخصیص ظرفیت منابع باند پایه (‌BBU) و یک سطح پایین تر، که تخصیص توان و بلوک منابع فیزیکی (PRB) در میان کاربران می‌باشد.
+در این مدل فرض می‌کنیم که هر سرویس دارای شبکه اصلی خود (یا قطعه اصلی شبکه) است که به H-CRAN متصل می‌شود.
 سلول بزرگ RRH (M-RRH) و سلولهای کوچک RRHs (S-RRHs) به ترتیب از طریق پیوندهای پشتی و fronthaul به یک استخر ابر
-BBU  متصل می شوند.
-همچنین ، تقسیم C/U در مدل سیستم فرض می شود، که به موجب آن صفحات کنترل و داده از هم جدا می شوند به گونه ای که صفحات کنترل توسط M-RRH در شبکه مدیریت می شود.
+BBU  متصل میشوند.
+همچنین ، تقسیم C/U در مدل سیستم فرض می‌شود، که به موجب آن صفحات کنترل و داده از هم جدا میشوند به گونه ای که صفحات کنترل توسط M-RRH در شبکه مدیریت می‌شود.
 \begin{figure}%[H]
@@
 \end{figure}
-%برای حل این مسئله، می بایست مسئله را به بخش های کوچکتر تقسیم کرده و حل نماییم.
+%برای حل این مسئله، میبایست مسئله را به بخش های کوچکتر تقسیم کرده و حل نماییم.
 همانطور که در شکل \eqref{fig:dns} 
-مشخص شده است ابتدا پذیرش کاربر مورد توجه قرار می گیرد و سپس کاربر به RRH متصل می شود و پس از آن ظرفیت BBU به آن تخصیص می دهد که تا این بخش از کار در سطح بالا قرار داریم.
-در سطح بالا، یک مسئله کنترل پذیرش با برنامه نویسی پویا می باشد که در آن پیچیدگی را می توان تنظیم کرد.
+مشخص شده‌است ابتدا پذیرش کاربر مورد توجه قرار می‌گیرد و سپس کاربر به RRH متصل می‌شود و پس از آن ظرفیت BBU به آن تخصیص می‌دهد که تا این بخش از کار در سطح بالا قرار داریم.
+در سطح بالا، یک مسئله کنترل پذیرش با برنامه نویسی پویا می‌باشد که در آن پیچیدگی را میتوان تنظیم کرد.
 این مسئله از جنس مسئله ی
@@
 باینری
- می باشد که با الگوریتم دینامیکی جواب بهینه ی آن بدست می آید.
-همچنین مسئله ی ارتباط کاربر نیز یک مسئله ی کوله پشتی باینری است که با استفاده از یک الگوریتم حریص با پیچیدگی کم بهینه و حل می شود.
- مسئله ی تخصیص ظرفیت BBU نیز فرموله شده و با برنامه ریزی خطی حل می شود.
- حال وارد الگوریتم سطح پایین تر می شویم که تخصیص توان و منبع فیزیکی می باشد.
-برای مساله ی سطح پایین تر، مشکل تخصیص منابع به عنوان یک مشکل برنامه نویسی mixed-integer غیر محدب است که با استفاده از روش دوگانه لاگرانژ حل می شود.
+ می‌باشد که با الگوریتم دینامیکی جواب بهینه ی آن بدست میآید.
+همچنین مسئله ی ارتباط کاربر نیز یک مسئله ی کوله پشتی باینری است که با استفاده از یک الگوریتم حریص با پیچیدگی کم بهینه و حل می‌شود.
+ مسئله ی تخصیص ظرفیت BBU نیز فرموله شده و با برنامه ریزی خطی حل می‌شود.
+ حال وارد الگوریتم سطح پایین تر میشویم که تخصیص توان و منبع فیزیکی می‌باشد.
+برای مساله ی سطح پایین تر، مشکل تخصیص منابع به عنوان یک مشکل برنامه نویسی mixed-integer غیر محدب است که با استفاده از روش دوگانه لاگرانژ حل می‌شود.
 
-در مقاله ی 
+در مقاله‌ی 
 \cite{larsen2018fronthaul,costanzo2018network}
 برش شبکه در شبکه های دسترسی رادیویی ابری مورد توجه قرار گرفته است. 
-در بخش fronthaul مشکلاتی از قبیل پیچیدگی شبکه و محدودیت نرخ وجود دارد که در برش شبکه، منجر به بهبود آن می شود.
-علاوه بر این ، C-RAN می تواند مجازی سازی مجموعه ای از توابع RAN را امکان پذیر کرده و راه را برای اصطلاحاً RAN مجازی باز کند. با این کار می توان چندین شبکه مجازی یا برش ایجاد کرد.
- مقاله ی
+در بخش fronthaul مشکلاتی از قبیل پیچیدگی شبکه و محدودیت نرخ وجود دارد که در برش شبکه، منجر به بهبود آن می‌شود.
+علاوه بر این ، C-RAN میتواند مجازی سازی مجموعه ای از توابع RAN را امکان پذیر کرده و راه را برای اصطلاحاً RAN مجازی باز کند. با این کار میتوان چندین شبکه مجازی یا برش ایجاد کرد.
+ مقاله‌ی
 \cite{larsen2018fronthaul}
 نشان داده است که استفاده از برش شبکه و برخورداری از سوییچ بسته در fronthaul
-مزایای زیادی را به همراه خواهد داشت که از جمله برخورداری از تقسیمات عملکردی مختلف خواهد بود. همچنین از معایب این کار تاخیر نسبتا اندکی می باشد.
+مزایای زیادی را به همراه خواهد داشت که از جمله برخورداری از تقسیمات عملکردی مختلف خواهد بود. همچنین از معایب این کار تاخیر نسبتا اندکی می‌باشد.
 
-در مقاله ی 
+در مقاله‌ی 
 \cite{fran}
@@
  یا F-RAN
-  در نظر گرفته شده است که در آن دو نمونه برش شبکه برای هات اسپات و سناریوهای وسیله نقلیه با زیرساخت مربوط تنظیم می شود.
+  در نظر گرفته شده‌است که در آن دو نمونه برش شبکه برای هات اسپات و سناریوهای وسیله نقلیه با زیرساخت مربوط تنظیم می‌شود.
 به طور خاص ، چارچوب برای برش RAN به عنوان یک مشکل بهینه سازی مشترک برای مقابله با ذخیره کردن و انتخاب حالت است.
-  با توجه به خواسته های کاربران مختلف و منابع محدود، پیچیدگی مسئله بهینه سازی اصلی بسیار زیاد است و همین امر باعث می شود که رویکردهای بهینه سازی سنتی به طور مستقیم سخت باشد.
- برای مقابله با این معضل ، یک الگوریتم یادگیری تقویت عمیق ارائه شده است ، که ایده اصلی آن این است که سرور ابر تصمیمات صحیحی را در زمینه ذخیره محتوا و انتخاب حالت برای به حداکثر رساندن عملکرد پاداش در وضعیت کانال پویا و وضعیت حافظه نهان ارائه می دهد.
+  با توجه به خواسته های کاربران مختلف و منابع محدود، پیچیدگی مسئله بهینه سازی اصلی بسیار زیاد است و همین امر باعث می‌شود که رویکردهای بهینه سازی سنتی به طور مستقیم سخت باشد.
+ برای مقابله با این معضل ، یک الگوریتم یادگیری تقویت عمیق ارائه شده‌است ، که ایده اصلی آن این است که سرور ابر تصمیمات صحیحی را در زمینه ذخیره محتوا و انتخاب حالت برای به حداکثر رساندن عملکرد پاداش در وضعیت کانال پویا و وضعیت حافظه نهان ارائه می‌دهد.
 %\subsubsection{برش شبکه در شبکه های دسترسی رادیویی }
 
-در مقاله ی 
+در مقاله‌ی 
 \cite{ranSlice, ranSlice1}
-اجرای مفهوم برش در سطح RAN توسط اپراتور شبکه تلفن همراه (MNO) برای پاسخگویی به نیازها می باشد. همچنین مساله ی تخصیص منابع (در اینجا پهنای باند) مورد توجه قرار گرفته شد.
+اجرای مفهوم برش در سطح RAN توسط اپراتور شبکه تلفن همراه (MNO) برای پاسخگویی به نیازها می‌باشد. همچنین مساله ی تخصیص منابع (در اینجا پهنای باند) مورد توجه قرار گرفته شد.
 چالش های پیش رو برش RAN نیز مورد بررسی قرار گرفته است که یکی از چالش ها
 شامل طراحی و مدیریت چندین برش در زیرساخت مشترک به روشی کارآمد و در عین حال ضمانت SLA توافق شده برای هر یک از آنها است.
-این چالش ما را نیازمند مفهوم ایزولاسیون برش می کند.
+این چالش ما را نیازمند مفهوم ایزولاسیون برش می‌کند.
 
-در مقاله ی 
+در مقاله‌ی 
 \cite{ranslice2}
@@
 همچنین
-در این مقاله یک برنامه تخصیص منابع پویا، با هدف به طور مشترک بهینه سازی مصرف برق و تخصیص پهنای باند در حالی که رضایت از تأخیر مربوطه برای ورود ترافیک پراکنده uRLLC و کیفیت خدمات eMBB را تا حد ممکن ارائه می دهد، پیشنهاد می کند.
+در این مقاله‌یک برنامه تخصیص منابع پویا، با هدف به طور مشترک بهینه سازی مصرف برق و تخصیص پهنای باند در حالی که رضایت از تأخیر مربوطه برای ورود ترافیک پراکنده uRLLC و کیفیت خدمات eMBB را تا حد ممکن ارائه می‌دهد، پیشنهاد می‌کند.
 طرح پیشنهادی براساس کنترل بهینه توان برای تخصیص منابع آگاه از تأخیر است.
-در نتیجه در این سیستم هدف مینیمم کردن توان با شروط برآورده شدن شروط پهنای باند و  تاخیر که با شرط صف پردازش نشان داده، می باشد.
+در نتیجه در این سیستم هدف مینیمم کردن توان با شروط برآورده شدن شروط پهنای باند و  تاخیر که با شرط صف پردازش نشان داده، می‌باشد.
 %\subsection{برش شبکه در بخش هسته  }
 
-در مقاله ی 
+در مقاله‌ی 
 \cite{onet}
-اجرای عملی برش شبکه پیشنهاد شده است.
-در مدل پیشنهادی، نویسندگان فرض می کنند که در هر شکاف زمانی مشخص، کاربران فقط می توانند یک برش شبکه واحد را درخواست کنند.
-در اینجا تابع هدفی بر اساس نسبت میزان منابع اختصاص داده شده به کاربرن در هر زمان t به ظرفیت کل منابع مشخص شده است و هدف بیشینه سازی آن  می باشد.  
-مدل پیشنهادی بر اساس مسئله \lr{multi armed bandit} ساخته شده است و نویسندگان سه نوع  آن را برای حل جنبه های مختلف تخصیص برش شبکه معرفی کرده اند.
+اجرای عملی برش شبکه پیشنهاد شده‌است.
+در مدل پیشنهادی، نویسندگان فرض میکنند که در هر شکاف زمانی مشخص، کاربران فقط میتوانند یک برش شبکه واحد را درخواست کنند.
+در اینجا تابع هدفی بر اساس نسبت میزان منابع اختصاص داده شده به کاربرن در هر زمان t به ظرفیت کل منابع مشخص شده‌است و هدف بیشینه سازی آن  می‌باشد.  
+مدل پیشنهادی بر اساس مسئله \lr{multi armed bandit} ساخته شده‌است و نویسندگان سه نوع  آن را برای حل جنبه های مختلف تخصیص برش شبکه معرفی کرده اند.
 آنها با استفاده از MATLAB مدل بهینه سازی را شبیه سازی کرده و نتایج را با یک الگوریتم حریص مقایسه کردند. آنها همچنین اثبات مفهوم برش شبکه را ارائه دادند.
 
-برش شبکه یکی از فناوری های کلیدی است که به شبکه های 5G اجازه می دهد منابع اختصاصی به صنایع مختلف (خدمات) ارائه دهند.
-در مقاله ی
+برش شبکه یکی از فناوری های کلیدی است که به شبکه های 5G اجازه می‌دهد منابع اختصاصی به صنایع مختلف (خدمات) ارائه دهند.
+در مقاله‌ی
 \cite{li2019latency}
@@
 \citep{vnf1}
-برای کاهش تأثیر حملات DDoS در احراز هویت برش ، از ایزوله کردن برش شبکه ی هسته استفاده شده و حل آن با ترکیبی از شبیه سازی و یک آزمایش عملی ارزیابی شده است.
+برای کاهش تأثیر حملات DDoS در احراز هویت برش ، از ایزوله کردن برش شبکه ی هسته استفاده شده و حل آن با ترکیبی از شبیه سازی و یک آزمایش عملی ارزیابی شده‌است.
 نویسندگان
 \citep{coreSlice}
-دو چالش مهم برش شبکه در بخش هسته مورد توجه قرار داده اند که شامل ایزوله کردن برش شبکه و تضمین میزان تاخیر انتها به انتها می باشد.
+دو چالش مهم برش شبکه در بخش هسته مورد توجه قرار داده اند که شامل ایزوله کردن برش شبکه و تضمین میزان تاخیر انتها به انتها می‌باشد.
 در این مقاله، مساله ی بهینه سازی به صورت 
 \lr{mixed integer linear programming}
- می باشد که
- تابع هدف درخواست های برش ورودی را به سروری که کمترین میزان استفاده از آن شده است، اختصاص داده و مسیری را با حداقل تأخیر پیدا می کند. خروجی این مساله VNF ها را به سرور اختصاص می دهد.  
+ می‌باشد که
+ تابع هدف درخواست های برش ورودی را به سروری که کمترین میزان استفاده از آن شده‌است، اختصاص داده و مسیری را با حداقل تأخیر پیدا می‌کند. خروجی این مساله VNF ها را به سرور اختصاص می‌دهد.  
 %\subsection{برش شبکه در هسته و بخش رادیویی}
 
-در این دسته مقالات، سرویس ها به دو بخش تقسیم می شوند در بخش اول سرویس هایی که  نسبت به تاخیر حساسند و دسته ی دوم سرویس هایی که نسبت به نرخ انتقال حساسند.
-همچنین در برخی مقالات هر دو ویژگی برای یک سرویس مد نظر می باشد.
-در این مدل های سیستم، تاخیر با استفاده از M/M/1 در ساده ترین حالت یا برای نزدیک تر شدن به حالت حقیقی از M/D/1 نیز استفاده می شود. می توان در این مدل ها تاخیر را کمینه و نرخ انتقال را بیشینه کرده و یا 
+در این دسته مقالات، سرویس ها به دو بخش تقسیم میشوند در بخش اول سرویس هایی که  نسبت به تاخیر حساسند و دسته ی دوم سرویس هایی که نسبت به نرخ انتقال حساسند.
+همچنین در برخی مقالات هر دو ویژگی برای یک سرویس مد نظر می‌باشد.
+در این مدل های سیستم، تاخیر با استفاده از M/M/1 در ساده ترین حالت یا برای نزدیک تر شدن به حالت حقیقی از M/D/1 نیز استفاده می‌شود. میتوان در این مدل ها تاخیر را کمینه و نرخ انتقال را بیشینه کرده و یا 
 برای کاربران نرخ را از حد مورد نیاز بیشتر و تاخیر را کمتر از حد مورد نیاز فرض کرد\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}.
@@
 \end{figure}
-همانطور که در شکل \eqref{fig:Delay}، مشخص است، در این شبکه برای هر بخش تعدادی VNF قرار دارند که پردازش ها را انجام می دهند. در مسیر لینک پایین
-بسته ها با نرخ $\alpha$ به صف های مختلف وارد شده و پس از پردازش با همدیگر ادغام شده و سپس بسته ی هر کاربر از طریق وایرلس منتقل می شوند.
-در این پردازش ها، از روش M/M/1 استفاده شده است.
-در این مدل مقالات اشاره ی مستقیم به برش شبکه نشده است ولی
-در آنها ترکیبی از مفهوم برش RAN و Core به چشم می خورد.
+همانطور که در شکل \eqref{fig:Delay}، مشخص است، در این شبکه برای هر بخش تعدادی VNF قرار دارند که پردازش ها را انجام می‌دهند. در مسیر لینک پایین
+بسته ها با نرخ $\alpha$ به صف های مختلف وارد شده و پس از پردازش با همدیگر ادغام شده و سپس بسته ی هر کاربر از طریق وایرلس منتقل میشوند.
+در این پردازش ها، از روش M/M/1 استفاده شده‌است.
+در این مدل مقالات اشاره ی مستقیم به برش شبکه نشده‌است ولی
+در آنها ترکیبی از مفهوم برش RAN و Core به چشم می‌خورد.
 \subsection{رفتن به سمت شبکه های دسترسی رادیویی باز}
-در فوریه 2018 ، شبکه دسترسی رادیویی آزاد (O-RAN) با ادغام  xRAN و اتحاد C-RAN برای ایجاد سطح جدیدی از باز بودن در شبکه دسترسی رادیویی ایجاد شد که از نسل 5G و 6G پشتیبانی می کند.
+در فوریه 2018 ، شبکه دسترسی رادیویی آزاد (O-RAN) با ادغام  xRAN و اتحاد C-RAN برای ایجاد سطح جدیدی از باز بودن در شبکه دسترسی رادیویی ایجاد شد که از نسل 5G و 6G پشتیبانی می‌کند.
 هدف اصلی O-RAN افزایش عملکرد RAN از طریق عناصر شبکه مجازی و واسط های باز است که دارای هوش در RAN است.
@@
 
-در مقاله ی 
+در مقاله‌ی 
 \cite{oranInt}
- مقدمه ای در مورد مفاهیم، اصول و الزامات \lr{Open RAN} که توسط اتحاد O-RAN مشخص شده، بیان شده است.
+ مقدمه ای در مورد مفاهیم، اصول و الزامات \lr{Open RAN} که توسط اتحاد O-RAN مشخص شده، بیان شده‌است.
  در این مقاله،
- به منظور نشان دادن نقش هوش در O-RAN، طرح مدیریت منابع رادیویی هوشمندی را برای رسیدگی به ازدحام ترافیک و نشان دادن اثربخشی آن در یک مجموعه داده در دنیای واقعی پیشنهاد شده است.
- یک معماری سطح بالا از این سناریوی استقرار که سازگار با الزامات O-RAN است نیز مورد بحث قرار گرفته است. مقاله با چالشهای کلیدی فنی و مشکلات باز برای تحقیقات و توسعه آینده به پایان می رسد.
+ به منظور نشان دادن نقش هوش در O-RAN، طرح مدیریت منابع رادیویی هوشمندی را برای رسیدگی به ازدحام ترافیک و نشان دادن اثربخشی آن در یک مجموعه داده در دنیای واقعی پیشنهاد شده‌است.
+ یک معماری سطح بالا از این سناریوی استقرار که سازگار با الزامات O-RAN است نیز مورد بحث قرار گرفته است. مقاله با چالشهای کلیدی فنی و مشکلات باز برای تحقیقات و توسعه آینده به پایان میرسد.
 
-در مقاله ی
+در مقاله‌ی
 \cite{c2o}
-تعاریف عمومی، ویژگی های اساسی و روند تحقیقاتی فعلی در شبکه های دسترسی رادیویی ابری و مشتقات آن، شبکه های دسترسی رادیویی مجازی و شبکه های دسترسی رادیویی باز ارائه شده است.
-علاوه بر این، نتایج عملی و آموزه های آموخته شده در مورد محدودیت ها و مسائل پیش بینی نشده مجازی سازی شبکه های دسترسی رادیویی را ارائه داده شده است.
+تعاریف عمومی، ویژگی های اساسی و روند تحقیقاتی فعلی در شبکه های دسترسی رادیویی ابری و مشتقات آن، شبکه های دسترسی رادیویی مجازی و شبکه های دسترسی رادیویی باز ارائه شده‌است.
+علاوه بر این، نتایج عملی و آموزه های آموخته شده در مورد محدودیت ها و مسائل پیش بینی نشده مجازی سازی شبکه های دسترسی رادیویی را ارائه داده شده‌است.
 
-در مقاله ی 
+در مقاله‌ی 
 \cite{sree2019open, kawahara2019ran}
@@
  و همچنین نقش مدیریت لینک رادیویی (RLM) در بهینه سازی انرژی در RRM
-در نظر گرفته شده است.
+در نظر گرفته شده‌است.
 ساختار RLM در 
@@
 NFV
- الگویي است که عملکردهای شبکه سنتی را مجازی می کند و آنها را در سخت افزارهای عمومی و ابرها در مقابل سخت افزارهای تعیین شده، قرار می دهد.
- در واقع NFV بخش نرم افزار را از سخت افزار جدا می نماید.
- بنابراین یک سرویس داده شده می تواند به مجموعه ای از توابع شبکه مجازی (VNF) تجزیه شود ، سپس می توان آن را در نرم افزارهایی که روی یک یا چند سرور استاندارد فیزیکی صنعت اجرا می شوند ، پیاده سازی کرد.
+ الگویي است که عملکردهای شبکه سنتی را مجازی می‌کند و آنها را در سخت افزارهای عمومی و ابرها در مقابل سخت افزارهای تعیین شده، قرار می‌دهد.
+ در واقع NFV بخش نرم افزار را از سخت افزار جدا می‌نماید.
+ بنابراین یک سرویس داده شده میتواند به مجموعه ای از توابع شبکه مجازی (VNF) تجزیه شود ، سپس میتوان آن را در نرم افزارهایی که روی یک یا چند سرور استاندارد فیزیکی صنعت اجرا میشوند ، پیاده سازی کرد.
 
@@
 این وظیفه بخشی از تنظیمات شبکه است و شامل تصمیم گیری در مورد قرار دادن VNF های مورد نیاز در سراسر زیرساخت و اختصاص پردازنده، حافظه و منابع ذخیره سازی به VNF ها و مسیریابی داده ها از طریق گره های شبکه
-می باشد.
+می‌باشد.
 
-به لطف برش شبکه، شبکه های 5G از انواع خدمات به روشی انعطاف پذیر و سریع پشتیبانی می کنند.
+به لطف برش شبکه، شبکه های 5G از انواع خدمات به روشی انعطاف پذیر و سریع پشتیبانی میکنند.
 در این زمینه ، ما به دنبال تصمیم گیری بهینه و با کیفیت بالا در مورد قرار دادن VNF در میان میزبانهای فیزیکی برای تحقق بخشیدن به خدمات هستیم.
@@
 \cite{wang2016online,jia2018online,luo2020online}
-هدف یافتن تعداد بهینه ی VNF ها در یک زنجیره ی سرویس و قرار گیری VNF های مورد نظر بر روی سرور در هر بازه ی زمانی می باشد تا بتوان میزان هزینه را در سیستم به حداقل رساند.
-در این مقالات هدف کمینه کردن انرژی های مصرفی در هر بازه ی زمانی می باشد که شامل هزینه ی انرژی مصرفی هر VNF مستقر بر روی سرور در حال کار و هزینه ی استقرار VNF های جدید در هر لحظه ی زمانی می باشد.
-همچنین مجموع منابع مصرفی VNF های مستقر بر روی هر سرور در هر لحظه می بایست از منابع آن سرور کمتر باشد تا مساله عملی شود.
-با استفاده از الگوریتم آنلاین این مساله حل شده است.
-در مقاله ی 
+هدف یافتن تعداد بهینه ی VNF ها در یک زنجیره ی سرویس و قرار گیری VNF های مورد نظر بر روی سرور در هر بازه ی زمانی می‌باشد تا بتوان میزان هزینه را در سیستم به حداقل رساند.
+در این مقالات هدف کمینه کردن انرژی های مصرفی در هر بازه ی زمانی می‌باشد که شامل هزینه ی انرژی مصرفی هر VNF مستقر بر روی سرور در حال کار و هزینه ی استقرار VNF های جدید در هر لحظه ی زمانی می‌باشد.
+همچنین مجموع منابع مصرفی VNF های مستقر بر روی هر سرور در هر لحظه میبایست از منابع آن سرور کمتر باشد تا مساله عملی شود.
+با استفاده از الگوریتم آنلاین این مساله حل شده‌است.‌
+در مقاله‌ی 
 \cite{jia2018online,luo2020online}
-نرخ جریان هر VNF و سرور نیز در نظر گرفته شده است و دیتا سنترها و VNF ها به صورت گرافی شبیه سازی شده اند.
-در مقاله ی
+نرخ جریان هر VNF و سرور نیز در نظر گرفته شده‌است و دیتا سنترها و VNF ها به صورت گرافی شبیه سازی شده‌اند.
+در مقاله‌ی
 \cite{luo2020online}
@@
 
-در مقاله ی
+در مقاله‌ی
 \cite{cziva2018dynamic}
-مساله ی قرار دادن VNF ها در لبه مورد بررسی قرار می گیرد که در اینجا تخصیص VNF ها در سیستمی با زیرساخت لبه مورد توجه قرار گرفته است و هدف کمینه کردن تاخیر انتها به انتها از هر کاربر به VNF مورد نظر آن می باشد و از روش دینامیکی و پویا برای حل مساله استفاده شده است.
+مساله ی قرار دادن VNF ها در لبه مورد بررسی قرار می‌گیرد که در اینجا تخصیص VNF ها در یک سیستم با زیرساخت لبه مورد توجه قرار گرفته است و هدف کمینه کردن تاخیر انتها به انتها از هر کاربر به VNF مورد نظر آن می‌باشد و از روش دینامیکی و پویا برای حل مساله استفاده شده‌است.
 
-در مقاله ی
+در مقاله‌ی
 \cite{pei2019optimal}
-مساله ی قرار دادن VNF در شبکه های فعال SDN/NFV مطالعه شده است، که به طور طبیعی به عنوان یک مساله ی برنامه نویسی باینری (BIP) فرموله شده است. 
-در این مساله قرارگیری VNF زنجیر عملکرد سرویس مورد بررسی قرار گرفته شده است. 
-با استفاده از روش یادگیری تقویت عمیق، الگوریتم قرارگیری VNF مبتنی بر شبکه DDQN \LTRfootnote{Double Deep Q-learning} پیشنهاد می کنیم.
+مساله ی قرار دادن VNF در شبکه های فعال SDN/NFV مطالعه شده‌است، که به طور طبیعی به عنوان یک مساله ی برنامه نویسی باینری (BIP) فرموله شده‌است. 
+در این مساله قرارگیری VNF زنجیر عملکرد سرویس مورد بررسی قرار گرفته شده‌است. 
+با استفاده از روش یادگیری تقویت عمیق، الگوریتم قرارگیری VNF مبتنی بر شبکه DDQN \LTRfootnote{Double Deep Q-learning} پیشنهاد می‌کنیم.
 
-در مقاله ی
+در مقاله‌ی
 \cite{ren2020joint}
- مسئله ی بهینه سازی مشترک قرار دادن VNF ها و زمانبندی جریان مطالعه شده است.
- این مساله از نوع برنامه نویسی عدد صحیح می باشد.
+ مسئله ی بهینه سازی مشترک قرار دادن VNF ها و زمانبندی جریان مطالعه شده‌است.
+ این مساله از نوع برنامه نویسی عدد صحیح می‌باشد.
  برای حالت تک جریان، مساله به سادگی قابل حل است اما برای جندین جریان مساله
@@
  خواهد بود و با استفاده از روش relax کردن لاگرانژ
- قابل حل می باشد.
+ قابل حل می‌باشد.
 \section{روش های حل}
-در این بخش مروری بر حل مسائل توسط مقالات می نماییم.
-\subsection{ مسئله ی کوله پشتی }
+در این بخش مروری بر حل مسائل توسط مقالات می‌نماییم. 
+ابتدا به دو مسئله ی معروف NP-Hard
+اشاره می‌کنیم سپس به حل مسائل با استفاده از روش یادگیری تقویتی می‌پردازیم.
+\subsection{مسائل Np-Hard}
+در اینجا به دو مسئله‌ی کوله پشتی و بسته بندی جعبه می‌پردازیم. این دو مسئله NP-Hard هستند.
+مسئله‌ی NP-hard را نمی‌توان در زمان چند جمله‌ای حل کرد در نتیجه از روشهای ابتکاری برای رسیدن به جواب نزدیکه بهینه استفاده می‌شود.
+\subsubsection{ مسئله‌ی کوله‌پشتی }
 یکی از مسائل پیش رو، مسئله ی کوله پشتی \LTRfootnote{knapsack}
-می باشد.
+می‌باشد.
 این مسئله، از جنس NP-hard
-می باشد که در این مسئله می خواهیم تعدادی شی با وزنهای مختلف را در تعدادی جایگاه با ظرفیت مشخص قرار دهیم.
-هدف در این مسئله جاگیری بیشترین تعداد اشیاء در این جایگاه ها می باشد.
-حل این مسئله با استفاده از روش های مختلف صورت می گیرد.
+می‌باشد که در این مسئله میخواهیم تعدادی شی با وزنهای مختلف را در تعدادی جایگاه با ظرفیت مشخص قرار دهیم.
+هدف در این مسئله قرارگیری بیشترین تعداد اشیاء در این جایگاه ها می‌باشد.
+حل این مسئله با استفاده از روش های مختلف صورت می‌گیرد.
 
-در مقاله ی \cite{lee2018dynamic}
+در مقاله‌ی \cite{lee2018dynamic}
 همانطور که قبل تر اشاره شد، مسئله ی پذیرش کاربر و ارتباط کاربر از جنس کوله پشتی
- می باشد که به ترتیب با استفاده از الگوریتم دینامیکی و الگوریتم حریص تعریف شده در مقاله
- حل می گردد.
+ می‌باشد که به ترتیب با استفاده از الگوریتم دینامیکی و الگوریتم حریص تعریف شده در مقاله
+ حل می‌گردد.
 
-در مقاله ی
+در مقاله‌ی
 \cite{sciancalepore2017mobile}
-یک راه حل جامع شامل برش شبکه، پیش بینی ترافیک، کنترل پذیرش و برنامه ریزی برای یک سیستم شامل برش شبکه 5G ارائه شده است.
-راه حل کنترل پذیرش به یک مسئله کوله پشتی هندسی (دو بعدی) ترسیم شده و دو الگوریتم کم پیچیدگی به ترتیب برای درخواست های برش شبکه منظم و نامنظم طراحی شده اند.
-\subsection{مسئله ی بسته بندی جعبه}
- در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می باشد.
+یک راه حل جامع شامل برش شبکه، پیش بینی ترافیک، کنترل پذیرش و برنامه ریزی برای یک سیستم شامل برش شبکه 5G ارائه شده‌است.
+راه حل کنترل پذیرش به یک مسئله کوله پشتی هندسی (دو بعدی) ترسیم شده و دو الگوریتم کم پیچیدگی به ترتیب برای درخواست های برش شبکه منظم و نامنظم طراحی شده‌اند. 
+\subsubsection{مسئله‌ی بسته‌بندی جعبه}
+ در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می‌باشد.
 در مسئله ی بسته بندی جعبه \LTRfootnote{bin packing}
@@
 
-در مقاله ی
+در مقاله‌ی
 \citep{wang2017joint}
@@
 H-CRAN
-می باشد.
-در این مقاله هدف تخصیص همزمان منابع ایستگاه رادیویی RRH و باند پایه BBU می باشد.
-این مسئله به دو بخش مجزا برای تخصیص منابع هر بخش شکسته می شود.
-بخش دوم که مربوط به زمان بندی و برنامه ریزی BBU می باشد به فرم یک مسئله ی باینری بسته بندی جعبه نوشته می شود.
+می‌باشد.
+در این مقاله هدف تخصیص همزمان منابع ایستگاه رادیویی RRH و باند پایه BBU می‌باشد.
+این مسئله به دو بخش مجزا برای تخصیص منابع هر بخش شکسته می‌شود.
+بخش دوم که مربوط به زمان بندی و برنامه ریزی BBU می‌باشد به فرم یک مسئله ی باینری بسته بندی جعبه نوشته می‌شود.
 برای حل این الگوریتم از روش های مختلفی از جمله
@@
 ‌Best-Fit-Decreasing(BFD)
-می باشد که الگوریتم به کار رفته در مسئله از نوع روش
+می‌باشد که الگوریتم به کار رفته در مسئله از نوع روش
 BFD 
@@
 
-در مقاله ی
+در مقاله‌ی
 \cite{de2020optimal}
-به صورت همزمان قرار دادن VNF ها و تخصیص منابع محاسباتی مورد هدف قرار داده شده است.
+به صورت همزمان قرار دادن VNF ها و تخصیص منابع محاسباتی مورد هدف قرار داده شده‌است.
 این مسئله به صورت
@@
 mixed-integer
-می شود که بعد از تغییرات به صورت برنامه نویسی خطی عدد صحیح می توان نوشت که به فرم مسئله ی بسته بندی جعبه خواهد بود که با استفاده از الگوریتم مشابه
-BFD حل می گردد.
+می‌شود که بعد از تغییرات به صورت برنامه نویسی خطی عدد صحیح میتوان نوشت که به فرم مسئله ی بسته بندی جعبه خواهد بود که با استفاده از الگوریتم مشابه
+BFD حل می‌گردد.
 \subsection{روشهای یادگیری تقویتی}
@@
 \end{figure}
-برخی از اصطلاحاتی که عناصر یک مساله یادگیری تقویتی را تشریح می‌کنند در ادامه بیان شده است.
+برخی از اصطلاحاتی که عناصر یک مساله یادگیری تقویتی را تشریح می‌کنند در ادامه بیان شده‌است.
 \begin{itemize}
@@
 DRL \LTRfootnote{Deep Reinforcement Learning}،
- از شبکه‌های عصبی عمیق برای حل مسائل یادگیری تقویتی استفاده می‌کند، از این رو در نام آن از کلمه عمیق استفاده شده است.
+ از شبکه‌های عصبی عمیق برای حل مسائل یادگیری تقویتی استفاده می‌کند، از این رو در نام آن از کلمه عمیق استفاده شده‌است.
 با در نظر گرفتن Q-Learning که یادگیری تقویتی کلاسیک محسوب می‌شود و Deep-Q-Learning می‌توان تفاوت آن‌ها با یکدیگر را دید.
@@
  \cite{gan1, gan2}
-سناریویی در نظر گرفته شده است که شامل چندین برش در یک شبکه دسترسی رادیویی با ایستگاههای پایه است که از منابع فیزیکی مشترک (به عنوان مثال، پهنای باند) استفاده می کنند. 
-با استفاده از یادگیری تقویت عمیق (DRL) با در نظر گرفتن تقاضای مختلف خدمات به عنوان وضعیت محیط و منابع اختصاص یافته به عنوان عمل محیط، این مشکل حل می شود.
-برای کاهش نویز و رسیدن به سطح انتظار خدمات، از روش GAN در بخش عمیق الگوریتم استفاده شده است که منجر به حداقل رساندن اختلاف بین توزیع مقدار-عمل تخمین زده شده و توزیع ارزش عمل هدف
-می شود.
+سناریویی در نظر گرفته شده‌است که شامل چندین برش در یک شبکه دسترسی رادیویی با ایستگاههای پایه است که از منابع فیزیکی مشترک (به عنوان مثال، پهنای باند) استفاده میکنند. 
+با استفاده از یادگیری تقویت عمیق (DRL) با در نظر گرفتن تقاضای مختلف خدمات به عنوان وضعیت محیط و منابع اختصاص یافته به عنوان عمل محیط، این مشکل حل می‌شود.
+برای کاهش نویز و رسیدن به سطح انتظار خدمات، از روش GAN در بخش عمیق الگوریتم استفاده شده‌است که منجر به حداقل رساندن اختلاف بین توزیع مقدار-عمل تخمین زده شده و توزیع ارزش عمل هدف
+می‌شود.
 برای یافتن سیاست بهینه ی تخصیص منابع از روش
 DDQN \LTRfootnote{Double Deep Q-Network}
- استفاده می شود.
+ استفاده می‌شود.
 \begin{figure}
@@
 
-در مقاله ی
+در مقاله‌ی
 \cite{li2020end} 
@@
 DQN \LTRfootnote{deep Q-Network}
- پیشنهاد شده است که برای سناریوهای چند برش و چند سرویس مناسب است.
- در این سیستم دو مدل سرویس ارائه شده است که اولی بر مبنای نیاز به رسیدن به نرخ خاص و دومی نیازمند داشتن تاخیر کم می باشد.
+ پیشنهاد شده‌است که برای سناریوهای چند برش و چند سرویس مناسب است.
+ در این سیستم دو مدل سرویس ارائه شده‌است که اولی بر مبنای نیاز به رسیدن به نرخ خاص و دومی نیازمند داشتن تاخیر کم می‌باشد.
 هدف در این سیستم رسیدن به بیشینه نرخ دسترسی است.
-برای رسیدن به هدف مورد نظر برشها به دو بخش دسترسی و اصلی تقسیم شده اند.
- در اینجا الگوریتم به طور مشترک برشهای شبکه دسترسی رادیویی و برشهای شبکه اصلی را در نظر می گیرد تا منابع را به صورت دینامیکی طوری اختصاص دهد که 
+برای رسیدن به هدف مورد نظر برشها به دو بخش دسترسی و اصلی تقسیم شده‌اند.
+ در اینجا الگوریتم به طور مشترک برشهای شبکه دسترسی رادیویی و برشهای شبکه اصلی را در نظر می‌گیرد تا منابع را به صورت دینامیکی طوری اختصاص دهد که 
  حداکثر میزان کاربران به شبکه دسترسی داشته و به بیشینه نرخ برسد.
@@
  mixed-integer
- نوشته می شود
-و مسئله به صورت دو مسئله ی کوله پشتی و اتصال لینک ها بیان می شود
+ نوشته می‌شود
+و مسئله به صورت دو مسئله ی کوله پشتی و اتصال لینک ها بیان می‌شود
   و با استفاده از روش
  DQN
- حل می گردد.
+ حل می‌گردد.

### 2020-09-10 Latex/tehran-thesis - Copy/tex/chapter1.tex
last version of thesis

--- 2020-09-09 Latex/tehran-thesis/tex/chapter1.tex
@@
 \end{enumerate}
-\section{شبکه تعریف شده نرم‌افزار (SDN)}
+\section{زیرساخت تعریف شده توسط نرم افزار}
+زیر‌ساخت تعریف شده توسط نرم‌افزار (SDI\LTRfootnote{Software Defined Infrastructure})
+تعریفی از زیرساختهای محاسبات فنی است که کاملاً تحت کنترل نرم افزار بدون دخالت اپراتور یا انسان است.
+این عمل مستقل از هرگونه وابستگی خاص سخت افزاری عمل می کند و از لحاظ برنامه قابل توسعه است.
+در رویکرد SDI، الزامات زیرساختی یک برنامه به صورت  الزامات کاربردی و غیر عملکردی تعریف شده است به گونه‌ای که می توان به طور خودکار سخت افزار کافی و مناسب برای تحقق این نیازها تهیه کرد.
+این زیرساخت شامل شبکه‌ی تعریف شده‌ی نرم‌افزار و شبکه‌ی رادیویی دسترسی تعریف شده‌ی نرم‌افزار می‌باشد که در ادامه توضیح می‌دهیم.
+\subsection{شبکه تعریف شده نرم‌افزار (SDN)}
 بنیاد شبکه باز 
@@
   \end{enumerate}
+\subsection{شبکه دسترسی رادیویی تعریف شده نرم‌افزار (SDRAN)}
+SDRAN \LTRfootnote{Software Defined Radio Access Network}
+یا شبکه‌ی دسترسی رادیویی تعریف‌ شده‌ی نرم‌افزار، یک بازنگری اساسی در لایه دسترسی رادیویی است.
+SDRAN
+یک صفحه‌ی کنترل متمرکز نرم‌افزار تعریف شده است برای بخش شبکه دسترسی رادیویی که ایستگاه‌های پایه را در یک مکان جغرافیایی داخلی، به عنوان یک ایستگاه پایه‌ی بزرگ مجازی با المانهای کنترلی مرکزی و رادیویی می‌باشد.
+در این حالت، مقهوم SDRAN به مفهوم vRAN بسیار نزدیک است.
+SDRAN
+ صفحه کنترل و صفحه داده را در
+ RAN 
+ جدا می‌کند و تصمیمات کنترل را به صفحه کنترل متمرکز می‌کند.
+در معماری های رایج SDRAN، یک کنترل کننده مرکزی اطلاعات کل شبکه را جمع می کند و در سطح کلی برای هر عنصر صفحه داده تصمیم گیری می‌کند.
+این روش از سربار شدن تصمیم گیری در عناصر صفحه داده جلوگیری می‌کند و فرصتی را برای مدیریت انعطاف پذیر و هماهنگ در کل RAN فراهم می‌کند.
+در تعریف چنین معماری، ما چارچوبی ایجاد می‌کنیم که از طریق آن یک شبکه جغرافیایی محلی می‌تواند به طور موثر توازن بار و مدیریت تداخل را انجام دهد و همچنین نرخ عملیاتی و یا هر هدف دیگر را به بهینه‌ترین مقدار خود برساند.
+ما معتقدیم که طراحی تعریف شده توسط نرم افزار در RAN یک گام اساسی برای پشتیبانی از برش شبکه ، به اشتراک گذاری RAN ، مدیریت طیف انعطاف پذیر و سایر ویژگی های اصلی در شبکه های 5G خواهد بود.
+امید بر این است که طراحی تعریف شده توسط نرم افزار در RAN 
+(SDRAN) 
+یک گام اساسی برای پشتیبانی از برش شبکه، به اشتراک گذاری RAN، مدیریت طیف انعطاف پذیر و سایر ویژگی های اصلی در شبکه های 5G خواهد بود
+\cite{gudipati2013softran,yu2017hsdran}.
+
  \section{برش شبکه}
@@
 برای حل این مسائل از الگوریتمهای branch-and-bound و cutting-plane و الگوریتمهای ابتکاری استفاده می‌شود.
-\subsubsection{مسئله‌ی بسته‌بندی جعبه}
+\subsection{مسئله‌ی بسته‌بندی جعبه}
 در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می‌باشد.
@@
 	\begin{alignat}{4}
-		\min\limits_{\boldsymbol{x} }   \quad &   \sum_{j=1}^{N}  x_{j}\\
-		\text{\lr{subject to}} \quad & \textstyle \sum_{j=1}^{N} r_{i,j}x_{j} \leq b_i  \quad i =1,...,m, \\
-		&\textstyle  x_j \in \{0,1\} \label{eqmain}
+		\min\limits_{\boldsymbol{x} }   \quad &   \sum_{j=1}^{n}  y_{j}\\
+		\text{\lr{subject to}} \quad & \textstyle \sum_{j=1}^{n}x_{ij} =1  \quad i =1,...,m, \\
+		&  \sum_{j=1}^{m} r_{i,j} x_j \leq b_i  \quad i=1,..,m \\
+		&  x_{ij} \in \{0,1\}  \quad y_j \in \{0,1\} \quad \forall i,j \label{eqmain}
 	\end{alignat}
@@
 \end{subequations}
-
+در اینجا، $y_j$ تعداد جعبه‌های مورد استفاده است که درصورتی که  $\sum_{j=1}^{n}x_{i,j \geq 1}$
+باشد، $y_j$ مقدار 1 می‌گیرد و در غیر این صورت 0 است \cite{berkey1987two}.
 \section{نتیجه گیری}
@@
  در ادامه برش شبکه در بخش رادیویی و هسته و هردو مورد توجه قرار گرفته شد.
+ سپس در مورد دو مسئله‌ی NP-Hard صحبت نمودیم.
 \section{دستاوردهای پروژه}

### 2020-09-10 Latex/tehran-thesis - Copy/tex/chapter1.tex
abstract add to thesis

@@
 مسئله‌ی برش شبکه در بخش رادیویی و قرارگیری توابع مجازی شبکه برروی مراکز داده باهم در شبکه‌ی دسترسی رادیویی باز مورد بررسی قرار گرفته است.
+بخش رادیویی به صورت کانل مدل سازی شده و تاخیر و نرخ و پارامترهای دیگر بدست می آید.
+در اینچا فرض براین است که کاربران بر اساس سرویس مورد نیاز، دسته بندی می شوند و هدف تخصیص برشهای شبکه به سرویسهاست و سپس تخصیص منابع فیزیکی محاسباتی به این برشهای اختصاص یافته به سرویسها می باشد.
 برای حل این مسئله، ابتدا مسئله را به دو مسئله‌ی کوچکتر مختلف شکسته که در بخش اول، تخصیص برش شبکه به کاربران سرویسها و تخصیص توان در ساختار رادیویی باز حل شده و پس از آن، برشهایی از شبکه که به سرویس اختصاص داده شده را به مراکز داده نگاشت می‌دهیم.
 در این مسئله، تاخیر و نرخ هر کاربر در سرویس مورد بررسی قرار گرفته شده و چالش تخصیص منابع که شامل برش بخش رادیویی به هر سرویس است و جاگیری توابع شبکه حل می‌شود.
-الگوریتم ارائه شده سرعت بسیار بیشتری از الگوریتم بهینه که با MOSEK و CVX بدست می‌آید، دارد. این الگوریتم به صورت متمرکز حل شده است.. 
-سپس مسئله به صورت ساده‌تر به دو مسئله‌ی بسته‌بندی جعبه و کوله‌پشتی نوشته شده و برای حالت دینامیکی متغیر با زمان با روش یادگیری تقویتی حل می‌کنیم. 
+الگوریتم بهینه  با استفاده از MOSEK و CVX بدست می‌آید، و الگوریتم استفاده شده در مسئله، یک روش ابتکاری و از جنس الگوریتمهای حریص می باشد. این مسئله به صورت متمرکز حل شده است. 
+سپس مسئله به صورت ساده‌تر به دو مسئله‌ی بسته‌بندی جعبه و کوله‌پشتی نوشته شده و برای حالت دینامیکی متغیر با زمان با روش یادگیری تقویتی حل می‌شود.
 \section{ساختار پروژه}

### 2020-09-10 Latex/tehran-thesis - Copy/tex/enTitle.tex
abstract add to thesis

@@
 \latinsurname{Karbalaee Motalleb}
-\latinthesisdate{December 2019}
+\latinthesisdate{September 2020}
 \latinkeywords{Writing Thesis, Template, \LaTeX, \XePersian}
 \en-abstract{
-This thesis studies on writing projects, theses and dissertations using tehran-thesis class. It ...
+Open radio access network (ORAN) alliance which has been formed recently establishes a flexible,  open, and smart radio access network (RAN) by combing the ideas from xRAN and cloud RAN (C-RAN).
+ORAN divides the functions of the RAN into three parts, namely remote unit (RU), distributed unit (DU), and central unit (CU).
+While RU contains lower PHY functions, DU contains higher PHY, MAC, and RLC and CU contains RRC, PDCP, and SDAP.
+CU and DU are implemented as virtual network functions (VNFs) running on a cloud environment.
+Interfaces between RU, CU, and DU are open standard interfaces.
+Network slicing as a new concept in 5G systems is used to share the network resources between various services while the operation of one service does not affect another service.
+In this paper, we study the problem of RAN network slicing in an ORAN system.
+We formulate the problem of wireless link scheduling, assigning the slices to the services, and assigning the physical data centers resource to slices which is 3D-bin packing problems.
+The objective is to jointly maximize the energy efficiency and minimize power consumption of RUs and the cost of physical resources in a downlink channel.
+The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems.
+Heuristic algorithms are proposed for each of the sub-problems.
 }

### 2020-09-10 Latex/tehran-thesis - Copy/tex/faTitle.tex
abstract add to thesis

--- 2019-11-03 Latex/tehran-thesis/tex/faTitle.tex
@@
 % عنوان پایان‌نامه را وارد کنید
-\title{نوشتن پروژه، پایان‌نامه و رساله با استفاده از کلاس 
-\lr{tehran-thesis}}
+\title{تخصیص منابع و قسمت کردن شبکه در ساختار شبکه‌های دسترسی باز }
 % نام استاد(ان) راهنما را وارد کنید
-\firstsupervisor{دکتر راهنمای اول}
-\firstsupervisorrank{استاد}
-\secondsupervisor{دکتر راهنمای دوم}
-\secondsupervisorrank{استادیار}
+\firstsupervisor{دکتر شاه منصوری}
+\firstsupervisorrank{دانشیار}
+%\secondsupervisor{دکتر راهنمای دوم}
+%\secondsupervisorrank{استادیار}
 % نام استاد(دان) مشاور را وارد کنید. چنانچه استاد مشاور ندارید، دستورات پایین را غیرفعال کنید.
-\firstadvisor{دکتر مشاور اول}
-\firstadvisorrank{استادیار}
+%\firstadvisor{دکتر مشاور اول}
+%\firstadvisorrank{استادیار}
 %\secondadvisor{دکتر مشاور دوم}
@@
 % شماره دانشجویی دانشجو را وارد کنید
-\studentID{810893024}
+\studentID{810196074}
 % تاریخ پایان‌نامه را وارد کنید
-\thesisdate{مرداد ۱۳۹۶}
+\thesisdate{شهریور ۱۳۹۹}
 % به صورت پیش‌فرض برای پایان‌نامه‌های کارشناسی تا دکترا به ترتیب از عبارات «پروژه»، «پایان‌نامه» و «رساله» استفاده می‌شود؛ اگر  نمی‌پسندید هر عنوانی را که مایلید در دستور زیر قرار داده و آنرا از حالت توضیح خارج کنید.
@@
 	\huge
-	همسر و فرزندانم\\
-	\vspace{7mm}
-	و\\
-	\vspace{7mm}
-	پدر و مادرم
+	پدر و مادرم\\
+%	\vspace{7mm}
+%	و\\
+%	\vspace{7mm}
+%	پدر و مادرم
 }
@@
 \fa-abstract{
-این راهنما، نمونه‌ای از قالبِ پروژه، پایان‌نامه و رسالهٔ دانشگاه تهران می‌باشد که با استفاده از کلاس 
-\lr{tehran-thesis}
-و بستهٔ زی‌پرشین در \lr{\LaTeX}{} تهیه شده است.
-این قالب به گونه‌ای طراحی شده است که مطابق با دستورالعمل نگارش و تدوین پایان‌نامه کارشناسی ارشد و دکتری، مورخ ۹۳/۰۶/۰۳ پردیس دانشکده‌های فنی دانشگاه تهران باشد و حروف‌چینی بسیاری از قسمت‌های آن، مطابق با استاندارد قالب‌های فارسی پایان‌نامه در لاتک، به طور خودکار انجام می‌شود.
-
-چکیده بخشی از پایان‌نامه است که خواننده را به مطالعه آن علاقمند می‌کند و یا از آن می‌گریزاند.
-چکیده باید ترجیحاً‌ در یک صفحه باشد.
-در نگارش چکیده نکات زیر باید رعایت شود.
-متن چکیده باید مزین به کلمه‌ها و عبارات سلیس، آشنا، بامعنی و روشن باشد.
-بگونه‌ای که با حدود ۳۰۰ تا ۵۰۰ کلمه بتواند خواننده را به خواندن پایان‌نامه راغب نماید.
-چکیده، جدای از پا‌یان‌نامه باید به تنهایی گویا و مستقل باشد.
-در چکیده باید از ذکر منابع، اشاره به جداول و نمودارها اجتناب شود.تمیز بودن مطلب، نداشتن غلط‌های املایی یا دستور زبانی و رعایت دقت و تسلسل روند نگارش چکیده از نکات مهم دیگری است که باید درنظر گرفته شود.
-در چکیده پایان‌نامه باید از درج مشخصات مربوط به پایان‌نامه خودداری شود.
-چکیده باید منعکس‌کننده اصل موضوع باشد.
-در چکیده باید اهداف تحقیق مورد توجه قرار گیرد.
-تأکید روی اطلاعات تازه (یافته‌ها) و اصطلاحات جدید یا نظریه‌ها، فرضیه‌ها، نتایج و پیشنهادها متمرکز شود.
-اگر در پایان‌نامه روش نوینی برای اولین بار ارائه می‌شود و تا به حال معمول نبوده است، با جزئیات بیشتری ذکر شود.
-شایان ذکر است چکیده فارسی و انگلیسی باید حتماً به تأیید استاد راهنما رسیده باشد.
-
-کلمات کلیدی در انتهای چکیده فارسی و انگلیسی آورده می‌شود.
-محتوای چکیده‌ها بر اساس موضوع و گرایش تحقیق طبقه‌بندی می‌شود و به همین جهت وجود کلمات شاخص و کلیدی، مراکز اطلاعاتی  را در طبقه‌بندی دقیق و سریع پایان‌نامه یاری می‌دهد.
-کلمات کلیدی، راهنمای نکات مهم موجود در پایان‌نامه هستند.
-بنابراین باید در حد امکان کلمه‌ها یا عباراتی انتخاب شود که ماهیت، محتوا و گرایش کار را به وضوح روشن نماید.
+در این پروپزال، هدف در نظرگیری ساختار رادیویی دسترسی باز در نسل پنجم و تخصیص منابع آن می‌باشد.
+مسئله‌ی برش شبکه در بخش رادیویی و قرارگیری توابع مجازی شبکه برروی مراکز داده باهم در شبکه‌ی دسترسی رادیویی باز مورد بررسی قرار گرفته است.
+بخش رادیویی به صورت کانل مدل سازی شده و تاخیر و نرخ و پارامترهای دیگر بدست می آید.
+در اینچا فرض براین است که کاربران بر اساس سرویس مورد نیاز، دسته بندی می شوند و هدف تخصیص برشهای شبکه به سرویسهاست و سپس تخصیص منابع فیزیکی محاسباتی به این برشهای اختصاص یافته به سرویسها می باشد.
+برای حل این مسئله، ابتدا مسئله را به دو مسئله‌ی کوچکتر مختلف شکسته که در بخش اول، تخصیص برش شبکه به کاربران سرویسها و تخصیص توان در ساختار رادیویی باز حل شده و پس از آن، برشهایی از شبکه که به سرویس اختصاص داده شده را به مراکز داده نگاشت می‌دهیم.
+در این مسئله، تاخیر و نرخ هر کاربر در سرویس مورد بررسی قرار گرفته شده و چالش تخصیص منابع که شامل برش بخش رادیویی به هر سرویس است و جاگیری توابع شبکه حل می‌شود.
+الگوریتم بهینه  با استفاده از MOSEK و CVX بدست می‌آید، و الگوریتم استفاده شده در مسئله، روش ابتکاری است. این مسئله به صورت متمرکز حل شده است.
+سپس مسئله به صورت ساده‌تر به دو مسئله‌ی بسته‌بندی جعبه و کوله‌پشتی نوشته شده و برای حالت دینامیکی متغیر با زمان با روش یادگیری تقویتی حل می‌شود.
 }
 % کلمات کلیدی پایان‌نامه را وارد کنید
-\keywords{حداکثر ۵ کلمه یا عبارت، متناسب با عنوان، قالب پایان‌نامه، لاتک}
+\keywords{ تخصیص برش شبکه ،شبکه‌ی دسترسی رادیویی باز، توابع مجازی شبکه  }
 % انتهای وارد کردن فیلد‌ها

### 2020-09-15 Latex/tehran-thesis - Copy/tex/chapter4.tex
finish report
figure ch4

@@
 		\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})(t)\\
-		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}(t) \geq 1 \forall s, \\
-		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d}  \forall d,, \forall ;  \label{eqomega}
+		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c} y_{s,d}(t) \geq 1 \quad \forall s, \\
+		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d} \quad  \forall d, \forall ;  \label{eqomega}
 	\end{alignat}
@@
 در این مسئله، عامل، orchestrator است که وظیفه‌ی مدیریت شبکه را برعهده دارد.
-همچنین، حالت در هر بازه‌ی زمانی برشهایی از شبکه است که به سرویسها متصل شده و اینکه کدام برش به کدام سرویس متصل است.
+همچنین، حالت در هر بازه‌ی زمانی برشهایی از شبکه است که به سرویسها متصل شده و همچنین مقدار منبع باقی ماده در هر برش می‌باشد. 
 پاداش طوری تعیین شده که بیشترین تعداد سرویسها پذیرفته شود به طوریکه شرط تاخیر و نرخ برآورده گردد.
+برای حل این مسئله به روش دینامیکی، دو مدل سرویس در نظر گرفتیم و تاخیر در اینجا فعلا لحاظ نشده است و در مدل اول سرویس نیازمند نرخ $10MHz$ و مدل دوم سرویس نیازمند مدل $20MHZ$
+می‌باشد.
+فرض می‌کنیم نرخ ورود سرویس در هر ابتدای بازه‌ی زمانی عدد رندم با توزیع پواسون می‌باشد.
+نرخ خروج سرویس نیز از توزیع پواسون پیروی می‌کند.
+در اینچا فرض می کنیم از  سرویس اول ماکسیمم در هر لحظه 4 سرویس و از سرویس دوم 2 تا سرویس درخواست می‌دهد.
+3 برش شبکه با نرخ $20MHz$ نیز وجود دارد.
+در شکل \ref{fig:dynamicEpoch}
+نسبت تعداد سرویسهای پذیرفته شده به نسبت تعداد سرویسهای پذیرفته شده در حالت بهینه براساس زمان طی شده داده می‌شود.
+بعد از حدود ۱۰۰۰۰۰ تکرار، تقریبا خروجی با خروجی بهینه یکی می‌شود و مقدار پذیرفته شده با مقدار بهینه یکی می‌شود.
+در اینجا از روش 
+$\epsilon-greedy$
+برای حل استفاده شده است.
 
+\begin{figure}%[H]
+	\centering
+	\includegraphics[scale = 0.7]{./fig/dynamicEpoch} %[width=\linewidth] 
+	\caption{  نسبت تعداد سرویسهای پذیرفته شده به نسبت تعداد سرویسهای پذیرفته شده در حالت بهینه براساس زمان طی شده}
+	\label{fig:dynamicEpoch}
+\end{figure}
+در شکل \ref{fig:dynamicEpoch1}
+با افزایش تعداد برشها و بیشینه تعداد درخواستها در هر زمان، بعد از 100000 تکرار جواب به حالت بهینه نزیک شده ولی هیچ موقع با مقدار بهینه برابری نمی‌کند.
+\begin{figure}%[H]
+	\centering
+	\includegraphics[scale = 0.7]{./fig/dynamicEpoch1} %[width=\linewidth] 
+	\caption{  نسبت تعداد سرویسهای پذیرفته شده به نسبت تعداد سرویسهای پذیرفته شده در حالت بهینه براساس زمان طی شده با دوبرابر کردن تعداد ماکسیمم درخواستها  و افزایش تعداد برشهای شبکه}
+	\label{fig:dynamicEpoch1}
+\end{figure}
 \subsection{نتایج عددی مسئله‌ی دوم} 

### 2020-09-15 Latex/tehran-thesis - Copy/tex/chapter5.tex
figure ch4

@@
  \section{پیشنهادات}
+ در این بخش، پیشنهادات و کارهای آتی را بیان خواهیم کرد.
+ \begin{itemize}
+\item
+ یکی از کارهای آتی، مدل کردن برش شبکه در ساختار شبکه‌ی دسترسی رادیویی باز و حل آن بوسیله‌ی روش یادگیری تقویتی عمیق می‌باشد.
+در فصل چهارم از این روش برای سیستم ساده شده استفاده گردیده و در فصل سوم نیز مدل سیستم بیان شده، یکی از کارهای بعدی این است که سیستم مدل فصل سوم را به سیستمهای رادیویی باز نزدیکتر کرده و
+با این روش حل نماییم. که در اینجا، بدست آوردن توان و ارتباط برش با سرویس از این روش بدست خواهد آمد.
+\item 
+یکی دیگر از کارهای آتی، بدست آوردن پارامترهای کیفیت سرویس QoS\LTRfootnote{Quality of Service}
+در شبکه‌های دسترسی باز می‌باشد که شامل تاخیر انتها به انتها، میزان از دست دادن بسته ها\LTRfootnote{Packet Loss}،
+قابلیت اطمینان و ... می‌باشد.
+در اینجا می‌توان تاخیر را هم در بخش رادیویی هم در بخش هسته‌ی شبکه بدست آورد. 
+همچنین،
+به منظور نشان دادن نقش هوش در ORAN طرح مدیریت هوشمند منابع رادیویی را برای کنترل تراکم ترافیک و نشان دادن کارایی آن در یک مجموعه داده واقعی از یک اپراتور بزرگ بدست می‌آوریم.
+\item 
+شبکه تعریف شده توسط نرم افزار (SDN) و مجازی سازی عملکرد شبکه (NFV) فناوری های کلیدی امکان پذیر در شبکه های ارتباطی نسل پنجم (5G) برای قرارگیری برش های شبکه سفارشی در سطح سرویس در زیرساخت شبکه، بر اساس خواسته های منابع آماری برای تأمین کیفیت طولانی مدت خدمات (QoS) مورد نیاز می‌باشد.
+با این حال، بارهای ترافیکی در برش های مختلف با گذشت زمان تحت تغییر قرار می‌گیرند ، در نتیجه چالش هایی برای تأمین کیفیت کیفیت مداوم ایجاد می‌شود.
+در کارهای آتی یک مشکل انتقال جریان پویا برای سرویس های متصل شده به برش شبکه، برای پاسخگویی به نیازهای تأخیر پایان انتها به انتها (E2E) با ترافیک متغیر، مورد بررسی قرار خواهد گرفت.
+\item
+یکی دیگر از کارهای آتی، تخصیص منابع به روش توزیع شده برای برش شبکه از منابع محاسباتی و منابع دیگر همانند پهنای باند می‌باشد.
+همچنین از روش توزیع شده در لینک فراسو  
+\LTRfootnote{Uplink}
+برای تخصیص توان کاربران، تخصیص پهنای باند و ... استفاده می‌گردد. یکی از روشها، استفاده از 
+\lr{Distributed ADMM}
+می‌باشد که در این روش تعدادی عامل به صورت همکارانه سعی در حل یک معادله‌ی بهینه‌سازی مشترک دارند که تابع هدف مجموعی از مقدارهای خصوصی هر عامل ‌می‌باشد. 
+ \end{itemize}

### 2020-09-16 Latex/tehran-thesis - Copy/tex/chapter4.tex
add latex and dynamic python

--- 2020-09-08 Latex/tehran-thesis - Copy/tex/chapter4.tex
@@
 در این مسئله، عامل، orchestrator است که وظیفه‌ی مدیریت شبکه را برعهده دارد.
-همچنین، حالت در هر بازه‌ی زمانی برشهایی از شبکه است که به سرویسها متصل شده و اینکه کدام برش به کدام سرویس متصل است.
+همچنین، حالت در هر بازه‌ی زمانی برشهایی از شبکه است که به سرویسها متصل شده و همچنین مقدار منبع باقی ماده در هر برش می‌باشد. 
 پاداش طوری تعیین شده که بیشترین تعداد سرویسها پذیرفته شود به طوریکه شرط تاخیر و نرخ برآورده گردد.
+برای حل این مسئله به روش دینامیکی، دو مدل سرویس در نظر گرفتیم و شرط تاخیر در این دو مدل سرویس اعمال نشده‌است. در مدل اول سرویس نیازمند نرخ $10MHz$ و مدل دوم سرویس نیازمند نرخ $20MHz$
+می‌باشد.
+فرض می‌کنیم نرخ ورود سرویس در هر ابتدای بازه‌ی زمانی عدد رندم با توزیع پواسون می‌باشد.
+نرخ خروج سرویس نیز از توزیع پواسون پیروی می‌کند.
+در اینچا فرض می کنیم از  سرویس اول ماکسیمم در هر لحظه 10 سرویس و از سرویس دوم 6 تا سرویس درخواست می‌دهد.
+8 برش شبکه با نرخ $20MHz$ نیز وجود دارد.
+در شکل \ref{fig:dynamicEpoch}
+نسبت تعداد سرویسهای پذیرفته شده به نسبت تعداد سرویسهای پذیرفته شده در حالت بهینه براساس زمان طی شده داده می‌شود.
+بعد از حدود ۱۰۰۰ تکرار مسئله، تقریبا خروجی با خروجی بهینه یکی می‌شود و مقدار پذیرفته شده با مقدار بهینه تقریبا یکی می‌شود.
+بعد از حدود ۴۰۰۰ تکرار، تقریبا احتمال انتخاب عمل رندم صفر می‌شود و صرفا با استفاده از تابع Q، عمل انتخاب می‌شود.
+در اینجا از روش 
+$\epsilon-greedy$
+برای حل استفاده شده است.
 
+\begin{figure}%[H]
+	\centering
+	\includegraphics[scale = 0.6]{./fig/dynamicEpoch_0} %[width=\linewidth] 
+	\caption{  نسبت تعداد سرویسهای پذیرفته شده با استفاده از روش یادگیری تقویتی عمیق به نسبت تعداد سرویسهای پذیرفته شده در حالت بهینه براساس زمان طی شده}
+	\label{fig:dynamicEpoch}
+\end{figure}
+در شکل \ref{fig:dynamicEpoch1}
+با افزایش تعداد برشها و بیشینه تعداد درخواستها در هر زمان، بعد از 1000 تکرار سناریو جواب به حالت بهینه نزیک شده ولی هیچ موقع با مقدار بهینه برابری نمی‌کند.
+\begin{figure}%[H]
+	\centering
+	\includegraphics[scale = 0.6]{./fig/dynamicEpoch1_0} %[width=\linewidth] 
+	\caption{  نسبت تعداد سرویسهای پذیرفته شده روش استفاده شده به نسبت تعداد سرویسهای پذیرفته شده در حالت بهینه براساس زمان طی شده با افزایش تعداد ماکسیمم درخواستها و تعداد برشهای شبکه}
+	\label{fig:dynamicEpoch1}
+\end{figure}
 \subsection{نتایج عددی مسئله‌ی دوم} 

### 2020-09-21 Latex/tehran-thesis - Copy/tex/chapter4.tex
add file

@@
 پاداش طوری تعیین شده که بیشترین تعداد سرویسها پذیرفته شود به طوریکه شرط تاخیر و نرخ برآورده گردد.
-برای حل این مسئله به روش دینامیکی، دو مدل سرویس در نظر گرفتیم و شرط تاخیر در این دو مدل سرویس اعمال نشده‌است. در مدل اول سرویس نیازمند نرخ $10MHz$ و مدل دوم سرویس نیازمند نرخ $20MHz$
+برای حل این مسئله به روش دینامیکی، دو مدل سرویس در نظر گرفتیم و شرط تاخیر در این دو مدل سرویس اعمال نشده‌است.
+در این بخش، به دلیل کم بودن تعداد حالتها، از روش Q-Learning استفاده کرده و برای جدول Q نیاز به استفاده از روش یادگیری عمیق نیست.
+در مدل اول سرویس نیازمند نرخ $10MHz$ و مدل دوم سرویس نیازمند نرخ $20MHz$
 می‌باشد.
 فرض می‌کنیم نرخ ورود سرویس در هر ابتدای بازه‌ی زمانی عدد رندم با توزیع پواسون می‌باشد.
-نرخ خروج سرویس نیز از توزیع پواسون پیروی می‌کند.
-در اینچا فرض می کنیم از  سرویس اول ماکسیمم در هر لحظه 10 سرویس و از سرویس دوم 6 تا سرویس درخواست می‌دهد.
-8 برش شبکه با نرخ $20MHz$ نیز وجود دارد.
+نرخ خروج سرویس نیز از توزیع نرمال پیروی می‌کند.
+در اینجا فرض می کنیم از  سرویس اول ماکسیمم در هر لحظه 8 سرویس و از سرویس دوم 4 تا سرویس درخواست می‌دهد.
+2 برش شبکه با نرخ $40MHz$ نیز وجود دارد.
 در شکل \ref{fig:dynamicEpoch}
 نسبت تعداد سرویسهای پذیرفته شده به نسبت تعداد سرویسهای پذیرفته شده در حالت بهینه براساس زمان طی شده داده می‌شود.
-بعد از حدود ۱۰۰۰ تکرار مسئله، تقریبا خروجی با خروجی بهینه یکی می‌شود و مقدار پذیرفته شده با مقدار بهینه تقریبا یکی می‌شود.
-بعد از حدود ۴۰۰۰ تکرار، تقریبا احتمال انتخاب عمل رندم صفر می‌شود و صرفا با استفاده از تابع Q، عمل انتخاب می‌شود.
+بعد از حدود 900 تکرار مسئله، تقریبا خروجی با خروجی بهینه یکی می‌شود و مقدار پذیرفته شده با مقدار بهینه تقریبا یکی می‌شود.
+بعد از حدود 4000 تکرار، تقریبا احتمال انتخاب عمل رندم صفر می‌شود و صرفا با استفاده از تابع Q، عمل انتخاب می‌شود.
 در اینجا از روش 
@@
 با افزایش تعداد برشها و بیشینه تعداد درخواستها در هر زمان، بعد از 1000 تکرار سناریو جواب به حالت بهینه نزیک شده ولی هیچ موقع با مقدار بهینه برابری نمی‌کند.
+در اینجا، تعداد درخواستهای سرویس اول 10 تا و سرویس دوم 5 تا می‌باشد.
+همچنین نرخ خروج عدد رندم یکنواخت است.
 \begin{figure}%[H]

### 2020-09-21 Latex/tehran-thesis - Copy/tex/chapter5.tex
add file1

@@
  یکی از کارهای آتی، مدل کردن برش شبکه در ساختار شبکه‌ی دسترسی رادیویی باز و حل آن بوسیله‌ی روش یادگیری تقویتی عمیق می‌باشد.
-در فصل چهارم از این روش برای سیستم ساده شده استفاده گردیده و در فصل سوم نیز مدل سیستم بیان شده، یکی از کارهای بعدی این است که سیستم مدل فصل سوم را به سیستمهای رادیویی باز نزدیکتر کرده و
-با این روش حل نماییم. که در اینجا، بدست آوردن توان و ارتباط برش با سرویس از این روش بدست خواهد آمد.
+در فصل چهارم از این روش برای سیستم ساده شده استفاده گردیده و به دلیل کم بودن تعداد حالات با استفاده از روش یادگیری تقویتی حل شده و در فصل سوم نیز مدل سیستم بیان شده، یکی از کارهای بعدی این است که سیستم مدل فصل سوم را به سیستمهای رادیویی باز نزدیکتر کرده و
+با روش یادگیری تقویتی عمیق حل نماییم. که در اینجا، بدست آوردن توان و ارتباط برش با سرویس از این روش بدست خواهد آمد.
 \item 

### 2020-09-21 Latex/tehran-thesis - Copy/tex/chapter4.tex
add file1
chapter 4 figures

@@
 یک معادله‌ی کوله‌پشتی دو بعدی می‌باشد.
-برای حل این مسئله، از روش یادگیری تقویتی عمیق استفاده می‌شود.
+برای حل این مسئله، از روش یادگیری تقویتی استفاده می‌شود.
 \section{ مدل سیستم و صورت مسئله‌ی دوم}
@@
 بعد از حدود 4000 تکرار، تقریبا احتمال انتخاب عمل رندم صفر می‌شود و صرفا با استفاده از تابع Q، عمل انتخاب می‌شود.
+در اینجا هر سناریو 100 بار تکرار شده و میانگین گیری بروی آن انجام گردیده است.
 در اینجا از روش 
@@
 همچنین نرخ خروج عدد رندم یکنواخت است.
+در اینجا هر سناریو 100 بار تکرار شده و میانگین گیری بروی آن انجام گردیده است.
 \begin{figure}%[H]
@@
 پاداش طوری تعیین شده که کمترین تعداد مراکز داده استفاده گردد و هر لحظه کمترین تعداد مرکز داده‌ی خاموش، روشن شود.
+در اینجا با فرض داشتن دو مدل سرویس مسئله را شبیه سازی می کنیم. فرض کنید VNF های سرویس اول نیاز به 
+\lr{1 CPU}
+و سرویس دوم نیازمند 
+\lr{2 CPU}
+است.
+فرض کنید از سرویس اول ماکسیمم 6 تا درخواست VNF 
+و برای سرویس دوم ماکسیمم در هر لجظه‌ی زمانی 4 تا درخواست VNF صورت می‌گیرد.
+در این مسئله، تعداد زیادی سرور که دارای 2 تا CPU هستند در نظر گرفته شده است.
+نسبت تعداد سرورهای مصرفی با روش Q-learning به سرورهای مصرفی بهینه در شکل
+\ref{fig:dynamicEpoch2}
+نشان داده شده است.
+\begin{figure}%[H]
+	\centering
+	\includegraphics[scale = 0.6]{./fig/ratio_episode} %[width=\linewidth] 
+	\caption{  نسبت تعداد سرورهای مصرفی با روش 
+		Q-learning
+		 به سرورهای مصرفی بهینه براساس زمان طی شده}
+	\label{fig:dynamicEpoch2}
+\end{figure}
+همانطور که دیده می‌شود بعد از 900
+تا تکرار، تقریبا به مقدار بهینه با نسبت 0.9 نزدیک شده‌ایم.
+بعد از 900 تا تکرار سناریو، تقریبا میزان انتخاب عمل رندم به صفر رسده و عمل بهینه از روی جدول Q بدست می‌آید.
 \section{نتیجه‌گیری}
@@
 این دو مسئله به صورت دینامیکی در هر لحظه از زمان حل شده‌اند.
-برای حل این دو مسئله از روش یادگیری تقویتی عمیق استفاده شده و حالتها و اعمال بیان برای یک عامل در این مسئله بیان گرده است.
+برای حل این دو مسئله از روش یادگیری تقویتی  استفاده شده و حالتها و اعمال بیان برای یک عامل در این مسئله بیان گرده است.
 نتایج عملی آن نیز رسم گردید.

### 2020-09-22 Latex/tehran-thesis - Copy/tex/chapter4.tex
final proposal

@@
 نرخ خروج سرویس نیز از توزیع نرمال پیروی می‌کند.
-در اینجا فرض می کنیم از  سرویس اول ماکسیمم در هر لحظه 8 سرویس و از سرویس دوم 4 تا سرویس درخواست می‌دهد.
+در اینجا فرض می کنیم از  سرویس اول ماکسیمم در هر لحظه 6 سرویس و از سرویس دوم 3 تا سرویس درخواست می‌دهد.
 2 برش شبکه با نرخ $40MHz$ نیز وجود دارد.
@@
 نسبت تعداد سرویسهای پذیرفته شده به نسبت تعداد سرویسهای پذیرفته شده در حالت بهینه براساس زمان طی شده داده می‌شود.
-بعد از حدود 900 تکرار مسئله، تقریبا خروجی با خروجی بهینه یکی می‌شود و مقدار پذیرفته شده با مقدار بهینه تقریبا یکی می‌شود.
+بعد از حدود 800 تکرار مسئله، تقریبا خروجی با خروجی بهینه یکی می‌شود و مقدار پذیرفته شده با مقدار بهینه تقریبا یکی می‌شود.
 بعد از حدود 4000 تکرار، تقریبا احتمال انتخاب عمل رندم صفر می‌شود و صرفا با استفاده از تابع Q، عمل انتخاب می‌شود.
@@
 فرض کنید از سرویس اول ماکسیمم 6 تا درخواست VNF 
-و برای سرویس دوم ماکسیمم در هر لجظه‌ی زمانی 4 تا درخواست VNF صورت می‌گیرد.
+و برای سرویس دوم ماکسیمم در هر لحظه‌ی زمانی 4 تا درخواست VNF صورت می‌گیرد.
 در این مسئله، تعداد زیادی سرور که دارای 2 تا CPU هستند در نظر گرفته شده است.
-نسبت تعداد سرورهای مصرفی با روش Q-learning به سرورهای مصرفی بهینه در شکل
+نسبت تعداد سرورهای مصرفی بهینه به سرورهای مصرفی با روش Q-learning  در شکل
 \ref{fig:dynamicEpoch2}
@@
 	\centering
-	\includegraphics[scale = 0.6]{./fig/ratio_episode} %[width=\linewidth] 
+	\includegraphics[scale = 0.6]{./fig/ratio_episode1} %[width=\linewidth] 
 	\caption{   نسبت تعداد سرورهای مصرفی با روش 
-		Q-learning
-		 به سرورهای مصرفی بهینه براساس زمان طی شده}
+		بهینه
+		 به سرورهای مصرفی با استفاده از روش یادگیری تقویتی براساس زمان طی شده}
 	\label{fig:dynamicEpoch2}
@@
 همانطور که دیده می‌شود بعد از 900
-تا تکرار، تقریبا به مقدار بهینه با نسبت 0.9 نزدیک شده‌ایم.
-بعد از 900 تا تکرار سناریو، تقریبا میزان انتخاب عمل رندم به صفر رسده و عمل بهینه از روی جدول Q بدست می‌آید.
+تا تکرار، تقریبا به مقدار بهینه با نسبت $0.9$ نزدیک شده‌ایم.
+بعد از 900 تا تکرار سناریو، تقریبا میزان انتخاب عمل رندم به صفر رسیده و عمل بهینه از روی جدول Q بدست می‌آید.
 \section{نتیجه‌گیری}
@@
 برای حل این دو مسئله از روش یادگیری تقویتی  استفاده شده و حالتها و اعمال بیان برای یک عامل در این مسئله بیان گرده است.
-نتایج عملی آن نیز رسم گردید.
+نتایج عملی آن نیز رسم گردید. در هردو مسئله‌، به دلیل گسسته بودن اعمال و حالات مسئله و کم بودن تعداد آن از روش Q-learning
+استفاده نمودیم.
+در مسئله‌ی اول ابتدا با فرض تعداد کمتر مسئله بعد از تعدادی تکرار به مقدار بهینه می‌رسد.
+با افزایش درخواستها از مقدار بهینه تا حدی دور می‌گردد.
+در مسئله‌ی دوم نیز بعد از 900 تکرار و با استفاده از جدول Q به مقدار نسبتا بهینه میل می‌کند.

### 2020-09-22 Latex/tehran-thesis - Copy/tex/chapter4.tex
final proposal1

@@
 بعد از حدود 4000 تکرار، تقریبا احتمال انتخاب عمل رندم صفر می‌شود و صرفا با استفاده از تابع Q، عمل انتخاب می‌شود.
-در اینجا هر سناریو 100 بار تکرار شده و میانگین گیری بروی آن انجام گردیده است.
+%در اینجا هر سناریو 100 بار تکرار شده و میانگین گیری بروی آن انجام گردیده است. 
+نرخ خروج در هر بازه‌ی زمانی $80$ درصد فرض شده است.
 در اینجا از روش 
@@
 در اینجا، تعداد درخواستهای سرویس اول 10 تا و سرویس دوم 5 تا می‌باشد.
-همچنین نرخ خروج عدد رندم یکنواخت است.
-در اینجا هر سناریو 100 بار تکرار شده و میانگین گیری بروی آن انجام گردیده است.
+همچنین نرخ خروج نرخ  در هر بازه‌ی زمانی $80$ درصد فرض شده است.% در اینجا هر سناریو 100 بار تکرار شده و میانگین گیری برروی آن انجام گردیده است.
 \begin{figure}%[H]
@@
 و برای سرویس دوم ماکسیمم در هر لحظه‌ی زمانی 4 تا درخواست VNF صورت می‌گیرد.
-در این مسئله، تعداد زیادی سرور که دارای 2 تا CPU هستند در نظر گرفته شده است.
+در این مسئله، تعداد زیادی سرور که دارای 3 تا CPU هستند در نظر گرفته شده است.
 نسبت تعداد سرورهای مصرفی بهینه به سرورهای مصرفی با روش Q-learning  در شکل
@@
 	\centering
-	\includegraphics[scale = 0.6]{./fig/ratio_episode1} %[width=\linewidth] 
+	\includegraphics[scale = 0.6]{./fig/ratio_episode2} %[width=\linewidth] 
 	\caption{   نسبت تعداد سرورهای مصرفی با روش 
@@
 بعد از 900 تا تکرار سناریو، تقریبا میزان انتخاب عمل رندم به صفر رسیده و عمل بهینه از روی جدول Q بدست می‌آید.
+%در اینجا هر سناریو 100 بار تکرار شده و میانگین گیری برروی آن انجام گردیده است. 
+نرخ خروج در هر بازه‌ی زمانی $80$ درصد فرض شده است.
 \section{نتیجه‌گیری}

### 2020-09-22 Latex/tehran-thesis - Copy/tex/chapter5.tex
chapter 4 figures
final proposal1

@@
 زمانی که تعداد بلوکهای منابع فیزیکی به نسبت کاربران بسیار کم باشد و تداخل به شدت زیاد گردد، الگوریتم مسئله‌ی اول به خوبی قادر به پاسخ‌گویی نیست و از حالت بهینه فاصله ‌می‌گردد.
-همچنین در فصل چهارم صورت مسئله بسیار ساده‌تر از واقعیت است و مسئله در حالت دینامیکی برای این حالت حل گردیده است.
 در مسئله‌ی دوم، زمانی که تعداد مراکز داده زیاد گردد فاصله‌ی حالت بهینه از الگوریتم ابتکاری زیاد شده است.
+همچنین در فصل چهارم صورت مسئله بسیار ساده‌تر از واقعیت است و مسئله در حالت دینامیکی برای تعداد درخواست کم در این حالت حل گردیده است.
  \subsection{نوآوری‌های این پروژه}
@@
 در فصل چهارم از این روش برای سیستم ساده شده استفاده گردیده و به دلیل کم بودن تعداد حالات با استفاده از روش یادگیری تقویتی حل شده و در فصل سوم نیز مدل سیستم بیان شده، یکی از کارهای بعدی این است که سیستم مدل فصل سوم را به سیستمهای رادیویی باز نزدیکتر کرده و
-با روش یادگیری تقویتی عمیق حل نماییم. که در اینجا، بدست آوردن توان و ارتباط برش با سرویس از این روش بدست خواهد آمد.
+با روش یادگیری تقویتی عمیق حل نماییم.
+که در اینجا، بدست آوردن توان و ارتباط برش با سرویس از این روش بدست خواهد آمد.
+همچنین مقایسه‌ی روش یادگیری تقویتی عمیق و یادگیری تقویتی در اینجا نیز مورد توجه قرار خواهد گرفت.
 \item 

### 2020-09-23 Latex/tehran-thesis - Copy/tex/chapter5.tex
add file

@@
  \section{پیشنهادات}
+
  در این بخش، پیشنهادات و کارهای آتی را بیان خواهیم کرد.

### 2020-10-19 Latex/tehran-thesis - Copy/tex/chapter1.tex
change proposal

@@
 \end{itemize}
-\section{مسائل Np-Hard}
-در اینجا به دو مسئله‌ی کوله‌پشتی و بسته بندی جعبه می پردازیم. این دو مسئله NP-Hard هستند.
-مسئله‌ی NP-hard را نمی توان در زمان چند جمله‌ای حل کرد و نیاز به روش ابتکاری است. این دو مسئله شامل کوله‌پشتی و بسته‌بندی جعبه می‌باشد.
+\section{مسئله‌ی کوله‌پشتی و بسته‌بندی جعبه}
+در اینجا به دو مسئله‌ی کوله‌پشتی و بسته‌بندی جعبه می پردازیم. این دو مسئله NP-Hard هستند.
+مسئله‌ی NP-hard را نمی توان در زمان چند جمله‌ای حل کرد و نیاز به روش ابتکاری است. در ادامه به بررسی این دو مسئله می‌پردازیم.
 \subsection{مسئله‌ی کوله‌پشتی}
@@
 باشد، $y_j$ مقدار 1 می‌گیرد و در غیر این صورت 0 است \cite{berkey1987two}.
-\section{نتیجه گیری}
-  در این فصل ابتدا مروری بر تاریخچه ی مخابرات و ۵ نسل مخابراتی شد. سپس ساختارهای مختف دسترسی رادیویی به طور خلاصه بیان شد و در نتیجه ی آن ساختار CRAN که ساختار ابری است تعریف شد. سپس ساختار xRAN
-  مورد توجه قرار گرفت و در نهایت ساختار ORAN 
-  که ترکیب و تکاملی از CRAN و xRAN می‌باشد مورد توجه قرار گرفت.
 
- بعد از بیان ساختارهای رادیویی، ساختار هسته ی شبکه را در نسل پنجم بیان کردیم که شامل 
- NFV و SDN 
- می‌باشد که منجر به جداسازی صفحه ی کنترل از کاربر می‌شود و سیستم هوشمندتر همراه با قابلیت برنامه ریزی بیشتر می‌گردد.
- در ادامه برش شبکه در بخش رادیویی و هسته و هردو مورد توجه قرار گرفته شد.
- سپس در مورد دو مسئله‌ی NP-Hard صحبت نمودیم.
 \section{دستاوردهای پروژه}
@@
 در فصل پنجم نیز نتیجه گیری و کارهای آتی مورد نظر و پیشنهادات بیان می‌شود.   
+\section{نتیجه گیری}
+در این فصل ابتدا مروری بر تاریخچه ی مخابرات و ۵ نسل مخابراتی شد. سپس ساختارهای مختف دسترسی رادیویی به طور خلاصه بیان شد و در نتیجه ی آن ساختار CRAN که ساختار ابری است تعریف شد. سپس ساختار xRAN
+مورد توجه قرار گرفت و در نهایت ساختار ORAN 
+که ترکیب و تکاملی از CRAN و xRAN می‌باشد مورد توجه قرار گرفت.
+
+بعد از بیان ساختارهای رادیویی، ساختار هسته ی شبکه را در نسل پنجم بیان کردیم که شامل 
+NFV و SDN 
+می‌باشد که منجر به جداسازی صفحه ی کنترل از کاربر می‌شود و سیستم هوشمندتر همراه با قابلیت برنامه ریزی بیشتر می‌گردد.
+در ادامه برش شبکه در بخش رادیویی و هسته و هردو مورد توجه قرار گرفته شد.
+سپس در مورد دو مسئله‌ی NP-Hard صحبت نمودیم. در نهایت در مورد دستاوردهای پروژه و ساختار فصلهای آتی صحبت می‌نماییم.

### 2020-10-19 Latex/tehran-thesis - Copy/tex/chapter2.tex
change proposal

--- 2020-09-04 Latex/tehran-thesis/tex/chapter2.tex
@@
 \section{مقدمه}
-در این فصل، به مرور کارهای گذشته می پردازیم.
-ابتدا صورت مسئله مقالات مختلف را بررسی می نماییم که
+در این فصل، به مرور کارهای گذشته می‌پردازیم.
+ابتدا صورت مسئله مقالات مختلف را بررسی می‌نماییم که
  به ترتیب شامل مقالاتی هستند که از برش شبکه استفاده کرده اند.
-برش شبکه در سه بخش رادیویی، بخش هسته و هردو بخش هسته و رادیویی صورت می گیرد.
-سپس در زمینه ی سیر عبور از شبکه های دسترسی رادیویی ابری به شبکه های دسترسی رادیویی باز مطالعه نموده و بعد از آن درباره ی جاگیری VNF ها صحبت می کنیم.
-سپس در مورد روش حل مسئله صحبت می کنیم که شامل مسائل کوله پشتی و بسته بندی جعبه می باشد و در نهایت در مورد روشهای یادگیری تقویتی صحبت می کنیم.
-\section{مسائل پیش رو}
-در این بخش به مطالعه ی مسائل پیش رو می پردازیم. 
+برش شبکه در سه بخش رادیویی، بخش هسته و هردو بخش هسته و رادیویی صورت می‌گیرد.
+سپس در زمینه ی سیر عبور از شبکه های دسترسی رادیویی ابری به شبکه های دسترسی رادیویی باز مطالعه نموده و بعد از آن درباره ی جاگیری VNF ها صحبت می‌کنیم.
+سپس در مورد روش حل مسئله صحبت می‌کنیم که شامل مسائل کوله پشتی و بسته بندی جعبه می‌باشد و در نهایت در مورد روشهای یادگیری تقویتی صحبت می‌کنیم.
+\section{مروری بر مسائل پیشین}
+در این بخش به مطالعه ی مقالات متشابه می‌پردازیم.
+‌‌‌ابتدا در مورد مسائل مرتبط با برش شبکه صحبت نموده سپس در مورد شبکه‌های دسترسی رادیویی باز مطالعه نموده و در نهایت به مروری بر کارهای انجام شده در زمینه‌ی قرارگیری توابع شبکه‌ی مجازی می‌پردازیم.
 \subsection{برش شبکه}
-برش شبکه یک شبکه منطقی انتها به انتهای مستقل است که بر روی یک زیرساخت فیزیکی مشترک کار می کند و قادر به ارائه خدمات می باشد.
-در این بخش برش شبکه در بخش رادیویی و هسته و هردو را بررسی می کنیم.
+برش شبکه یک شبکه منطقی انتها به انتهای مستقل است که بر روی یک زیرساخت فیزیکی مشترک کار ‌ و قادر به ارائه خدمات می‌باشد.
+در این بخش برش شبکه در بخش رادیویی و هسته و هردو را بررسی می‌کنیم.
 %\subsection{برش شبکه در شبکه های دسترسی رادیویی }
-برش RAN یکی از کلیدهای اصلی برای انعطاف پذیری سفارشات و مدیریت مجازی سازی ایستگاه پایه می باشد تا بتواند منابع رادیویی را در میان سرویس های مختلف تقسیم کرده و منجر به سازگاری اپراتورها و برطرف کردن نیاز سرویس ها گردد.
-%در ادامه مروری بر این مدل مقالات می نماییم.
+برش RAN یکی از کلیدهای اصلی برای انعطاف پذیری سفارشات و مدیریت مجازی سازی ایستگاه پایه می‌باشد تا بتواند منابع رادیویی را در میان سرویس های مختلف تقسیم کرده و منجر به سازگاری اپراتورها و برطرف کردن نیاز سرویس ها گردد.
+%در ادامه مروری بر این مدل مقالات می‌نماییم.
 %\subsubsection{  برش شبکه در شبکه های دسترسی رادیویی ابری و متجانس و مهی}
 
-شبکه های دسترسی رادیویی ابر (C-RAN) به عنوان یک چارچوب امیدوار کننده برای سیستم های ارتباط بی سیم نسل پنجم ظاهر شده اند.
-از آنجا که آنها می توانند پیچیدگی رمزگشایی، مصرف انرژی و دخالت های ناشی از افزایش تراکم تلفن همراه را کاهش دهند\cite{cranInt}.
-در ادامه در مورد برش شبکه در بخش رادیویی شبکه های دسترسی رادیویی ابری صحبت می کنیم.
+شبکه های دسترسی رادیویی ابر (C-RAN) به عنوان یک چارچوب امیدوار کننده برای سیستم های ارتباط بی سیم نسل پنجم ظاهر شده‌اند.
+از آنجا که آنها میتوانند پیچیدگی رمزگشایی، مصرف انرژی و دخالت های ناشی از افزایش تراکم تلفن همراه را کاهش دهند\cite{cranInt}.
+در ادامه در مورد برش شبکه در بخش رادیویی شبکه های دسترسی رادیویی ابری صحبت می‌کنیم.
 
-در مقاله ی \cite{lee2018dynamic}
-برش شبکه به صورت دینامیکی در بخش رادیویی مورد بررسی قرار گرفته شده است.
-برش شبکه در اینجا به عنوان فرآیند تخصیص منابع شبکه به کاربران انجام می شود
-چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش کاربران، ارتباط کاربر که شامل تخصیص واحد رادیویی (RRH) برای بیشینه سازی نرخ کاربران و تخصیص ظرفیت منابع باند پایه (‌BBU) و یک سطح پایین تر، که تخصیص توان و بلوک منابع فیزیکی (PRB) در میان کاربران می باشد.
-در این مدل فرض می کنیم که هر سرویس دارای شبکه اصلی خود (یا قطعه اصلی شبکه) است که به H-CRAN متصل می شود.
+در مقاله‌ی \cite{lee2018dynamic}
+برش شبکه به صورت دینامیکی در بخش رادیویی مورد بررسی قرار گرفته شده‌است.
+برش شبکه در اینجا به عنوان فرآیند تخصیص منابع شبکه به کاربران انجام ‌
+چارچوب طرح برش شبکه شامل یک سطح بالاتر، که مدیریت کنترل پذیرش کاربران، ارتباط کاربر که شامل تخصیص واحد رادیویی (RRH) برای بیشینه سازی نرخ کاربران و تخصیص ظرفیت منابع باند پایه (‌BBU) و یک سطح پایین تر، که تخصیص توان و بلوک منابع فیزیکی (PRB) در میان کاربران می‌باشد.
+در این مدل فرض می‌کنیم که هر سرویس دارای شبکه اصلی خود (یا قطعه اصلی شبکه) است که به H-CRAN متصل می‌شود.
 سلول بزرگ RRH (M-RRH) و سلولهای کوچک RRHs (S-RRHs) به ترتیب از طریق پیوندهای پشتی و fronthaul به یک استخر ابر
-BBU  متصل می شوند.
-همچنین ، تقسیم C/U در مدل سیستم فرض می شود، که به موجب آن صفحات کنترل و داده از هم جدا می شوند به گونه ای که صفحات کنترل توسط M-RRH در شبکه مدیریت می شود.
+BBU  متصل میشوند.
+همچنین ، تقسیم C/U در مدل سیستم فرض می‌شود، که به موجب آن صفحات کنترل و داده از هم جدا میشوند به گونه ای که صفحات کنترل توسط M-RRH در شبکه مدیریت می‌شود.
 \begin{figure}%[H]
@@
  خواهد بود و با استفاده از روش relax کردن لاگرانژ
- قابل حل می باشد.
+ قابل حل می‌باشد.
 \section{روش های حل}
-در این بخش مروری بر حل مسائل توسط مقالات می نماییم.
-\subsection{ مسئله ی کوله پشتی }
+در این بخش مروری بر حل مسائل توسط مقالات می‌نماییم. 
+ابتدا به دو مسئله ی معروف NP-Hard
+اشاره می‌کنیم سپس به حل مسائل با استفاده از روش یادگیری تقویتی می‌پردازیم.
+\subsection{مسئله‌ی کوله‌پشتی و بسته‌بندی جعبه}
+در اینجا به دو مسئله‌ی کوله پشتی و بسته بندی جعبه می‌پردازیم. این دو مسئله NP-Hard هستند.
+مسئله‌ی NP-hard را نمی‌توان در زمان چند جمله‌ای حل کرد در نتیجه از روشهای ابتکاری برای رسیدن به جواب نزدیکه بهینه استفاده می‌شود.
+\subsubsection{ مسئله‌ی کوله‌پشتی }
 یکی از مسائل پیش رو، مسئله ی کوله پشتی \LTRfootnote{knapsack}
-می باشد.
+می‌باشد.
 این مسئله، از جنس NP-hard
-می باشد که در این مسئله می خواهیم تعدادی شی با وزنهای مختلف را در تعدادی جایگاه با ظرفیت مشخص قرار دهیم.
-هدف در این مسئله جاگیری بیشترین تعداد اشیاء در این جایگاه ها می باشد.
-حل این مسئله با استفاده از روش های مختلف صورت می گیرد.
+می‌باشد که در این مسئله میخواهیم تعدادی شی با وزنهای مختلف را در تعدادی جایگاه با ظرفیت مشخص قرار دهیم.
+هدف در این مسئله قرارگیری بیشترین تعداد اشیاء در این جایگاه ها می‌باشد.
+حل این مسئله با استفاده از روش های مختلف صورت می‌گیرد.
 
-در مقاله ی \cite{lee2018dynamic}
+در مقاله‌ی \cite{lee2018dynamic}
 همانطور که قبل تر اشاره شد، مسئله ی پذیرش کاربر و ارتباط کاربر از جنس کوله پشتی
- می باشد که به ترتیب با استفاده از الگوریتم دینامیکی و الگوریتم حریص تعریف شده در مقاله
- حل می گردد.
+ می‌باشد که به ترتیب با استفاده از الگوریتم دینامیکی و الگوریتم حریص تعریف شده در مقاله
+ حل می‌گردد.
 
-در مقاله ی
+در مقاله‌ی
 \cite{sciancalepore2017mobile}
-یک راه حل جامع شامل برش شبکه، پیش بینی ترافیک، کنترل پذیرش و برنامه ریزی برای یک سیستم شامل برش شبکه 5G ارائه شده است.
-راه حل کنترل پذیرش به یک مسئله کوله پشتی هندسی (دو بعدی) ترسیم شده و دو الگوریتم کم پیچیدگی به ترتیب برای درخواست های برش شبکه منظم و نامنظم طراحی شده اند.
-\subsection{مسئله ی بسته بندی جعبه}
- در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می باشد.
+یک راه حل جامع شامل برش شبکه، پیش بینی ترافیک، کنترل پذیرش و برنامه ریزی برای یک سیستم شامل برش شبکه 5G ارائه شده‌است.
+راه حل کنترل پذیرش به یک مسئله کوله پشتی هندسی (دو بعدی) ترسیم شده و دو الگوریتم کم پیچیدگی به ترتیب برای درخواست های برش شبکه منظم و نامنظم طراحی شده‌اند. 
+\subsubsection{مسئله‌ی بسته‌بندی جعبه}
+ در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می‌باشد.
 در مسئله ی بسته بندی جعبه \LTRfootnote{bin packing}
@@
  mixed-integer
- نوشته می شود
-و مسئله به صورت دو مسئله ی کوله پشتی و اتصال لینک ها بیان می شود
+ نوشته می‌شود
+و مسئله به صورت دو مسئله ی کوله پشتی و اتصال لینک ها بیان می‌شود
   و با استفاده از روش
  DQN
- حل می گردد.
+ حل می‌گردد.
+ \section{نتیجه گیری}
+ در این فصل، ابتدا در مورد مسائل پیشین صحبت می‌نماییم که شامل مسائل مرتبط با برش شبکه، شبکه‌های دسترسی رادیویی باز و قرارگیری توابع شبکه‌ی مجازی می‌باشد.
+سپس در مورد روشهاس حل صجبت نمودیم.
+این روشها شامل دو مسئله‌ی NP-Hard است که مسئله‌ی کوله‌پشتی و بسته‌بندی جعبه را شامل می‌شود.
+همچنین روش حل دیگر، روش یادگیری تقویتی است که با استفاده از روشهای یادگیری ماشین به حل مسائل می‌پردازد.

### 2020-10-19 Latex/tehran-thesis - Copy/tex/chapter3.tex
change fig and ch 5
change proposal

--- 2020-09-08 Latex/tehran-thesis/tex/chapter3.tex
@@
-\chapter{تخصیص منابع در شبکه های \lr{Open RAN}}
+\chapter{تخصیص منابع در شبکه‌های دسترسی رادیویی باز}
 \section{مقدمه}
-در این فصل، هدف تخصیص منابع در شبکه های \lr{Open RAN} در لینک فروسو می باشد که شامل تخصیص توان و برش های شبکه است.
+در این فصل، هدف تخصیص منابع در شبکه های \lr{Open RAN} در لینک فروسو می‌باشد که شامل تخصیص توان و برش های شبکه است.
 در این بخش فرض بر این است که در شبکه ی نسل پنجم مخابرات از زیرساخت \lr{Open RAN} استفاده شده است.
 این شبکه سرویس هایی از قبیل \lr{IoT}، سرویس تلفن، پیامک و ...
-در اختیار کاربران قرار می دهد.
-در اینجا  مفهوم برش شبکه در سیستم بدین صورت به کار رفته که به جای دیدن کاربران به صورت مجزا، کاربرانی که از یک سرویس خاص استفاده می نمایند در دسته ی آن سرویس قرار گرفته و دسته بندی می شوند.
-همچنین برش هایی از شبکه در اختیار کاربران هر سرویس خاص، قرار می گیرد که هر برش شبکه شامل تعدادی واحد رادیویی
+در اختیار کاربران قرار می‌دهد.
+در اینجا  مفهوم برش شبکه در سیستم بدین صورت به کار رفته که به جای دیدن کاربران به صورت مجزا، کاربرانی که از یک سرویس خاص استفاده می‌نمایند در دسته ی آن سرویس قرار گرفته و دسته بندی می‌شوند.
+همچنین برش هایی از شبکه در اختیار کاربران هر سرویس خاص، قرار می‌گیرد که هر برش شبکه شامل تعدادی واحد رادیویی
 \LTRfootnote{Radio Unit}
@@
 (\lr{CU})  
-  می باشد که هر واحد توزیع شده و مرکزی شامل تعدادی توابع شبکه ی مجازی شده
+  می‌باشد که هر واحد توزیع شده و مرکزی شامل تعدادی توابع شبکه ی مجازی شده
   \LTRfootnote{Virtual Network Function}
 (\lr{VNF}) 
-می باشد.
+می‌باشد.
 
@@
 ORAN
-می باشد.
-ما مسئله زمانبندی لینک بی سیم، اختصاص برشها به سرویسها و اختصاص مراکز داده به برشها را که از مشکلات بسته بندی جعبه  ۳-بعدی است را فرموله می کنیم. 
+می‌باشد.
+ما مسئله زمانبندی لینک بی سیم، اختصاص برشها به سرویسها و اختصاص مراکز داده به برشها را که از مشکلات بسته بندی جعبه  ۳-بعدی است را فرموله می‌کنیم. 
 هدف این است که به طور مشترک بهره وری انرژی را به حداکثر برسانیم و مصرف توان واحدهای رادیویی را کاهش داده تا هزینه منابع فیزیکی را در یک کانال فروسو به حداقل برسانیم.
@@
 mixed-integer
-بیان می شود و به دو مسئله ی کوچکتر قابل جداسازی است. با استفاده از الگوریتمهای ابتکاری، این مسائل حل شده اند.
+بیان می‌شود و به دو مسئله ی کوچکتر قابل جداسازی است. با استفاده از الگوریتمهای ابتکاری، این مسائل حل شده اند.
 \begin{figure}
@@
 \item 
-مسئله ی پذیرش کاربر و تخصیص خدمات به برش ها، و منابع فیزیکی بی سیم و مرکز داده به برش ها را به عنوان یک مسئله ی بهینه سازی حل می کنیم.
+مسئله ی پذیرش کاربر و تخصیص خدمات به برش ها، و منابع فیزیکی بی سیم و مرکز داده به برش ها را به عنوان یک مسئله ی بهینه سازی حل می‌کنیم.
 \item
@@
 \section{مدل سیستم}
-در این قسمت، سیستم مدل به صورت کامل مورد بررسی قرار می گیرد.
-فرض می کنیم $S$ برش شبکه داریم که قرار است $V$ سرویس مختلف که شامل کاربرانی است که از سرویس خاص استفاده می نمایند را سرویس دهی نماید.
+در این قسمت، سیستم مدل به صورت کامل مورد بررسی قرار می‌گیرد.
+فرض می‌کنیم $S$ برش شبکه داریم که قرار است $V$ سرویس مختلف که شامل کاربرانی است که از سرویس خاص استفاده می‌نمایند را سرویس دهی نماید.
 هر سرویس 
@@
 $U_v$
-کاربر تک آنتنه می باشند که سرویس خاصی را درخواست می نماید.
+کاربر تک آنتنه می‌باشند که سرویس خاصی را درخواست می‌نماید.
 هر برش شبکه 
@@
 $K_s$
-بلوک های منابع فیزیکی، یک واحد توزیع شده و یک واحد مرکزی که شامل \lr{VNF} هایی می باشند.
-همچنین برش های شبکه می توانند منابع مشترک داشته باشند.
-تمام \lr{RU}هایی که به یک سرویس خاص خدمت رسانی می کنند به صورت مشارکتی سیگنال به تمام کاربران در آن سرویس ارسال می نمایند. 
+بلوک های منابع فیزیکی، یک واحد توزیع شده و یک واحد مرکزی که شامل \lr{VNF} هایی می‌باشند.
+همچنین برش های شبکه می‌توانند منابع مشترک داشته باشند.
+تمام \lr{RU}هایی که به یک سرویس خاص خدمت رسانی می‌کنند به صورت مشارکتی سیگنال به تمام کاربران در آن سرویس ارسال می‌نمایند. 
 \cite{motalleb2017optimal,mimoCran}
@@
 به یک واحد توزیع شده از طریق لینک فیبر نوری با ظرفیت \lr{fronthaul} 
-محدود متصل می باشد.
+محدود متصل می‌باشد.
 در سیستم \lr{Open RAN}
-دو لایه ی پردازشی که اولی در \lr{CU} و دومی در \lr{DU} قرار گرفته است که پردازش ها با \lr{VNF} ها صورت می گیرد.
+دو لایه ی پردازشی که اولی در \lr{CU} و دومی‌در \lr{DU} قرار گرفته است که پردازش ها با \lr{VNF} ها صورت می‌گیرد.
 لایه پایین تر (\lr{DU}) شامل 
@@
 \lr{RLC}
-می باشد و 
+می‌باشد و 
 لایه ی بالاتر 
@@
 \lr{VNF}
-دپر لایه ی \lr{CU} می باشد.
+دپر لایه ی \lr{CU} می‌باشد.
 \lr{VNF}
@@
  $\mu_2$
-می باشند.
+می‌باشند.
 \subsection{نرخ قابل دسترس}
-نرخ قابل دسترس برای $i^{th}$ امین کاربر در $v^{th}$امین سرویس به صورت زیر نوشته می شود
+نرخ قابل دسترس برای $i^{th}$ امین کاربر در $v^{th}$امین سرویس به صورت زیر نوشته می‌شود
 \begin{equation}\label{eq1}
@@
    امین سرویس
-  می باشد 
-  که از رابطه ی زیر بدست می آید
+  می‌باشد 
+  که از رابطه ی زیر بدست می‌آید
  \begin{equation}\label{eq2}
@@
 $s^{th}$
-امین برش شبکه می باشد.
+امین برش شبکه می‌باشد.
  همچنین 
 $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$
-نشان دهنده ی بردار بیم فرمینگ ارسالی برای \lr{RU}ها در $s$ امین برش شبکه به کاربر $i$ ام در سرویس $v$ ام می باشد.
+نشان دهنده ی بردار بیم فرمینگ ارسالی برای \lr{RU}ها در $s$ امین برش شبکه به کاربر $i$ ام در سرویس $v$ ام می‌باشد.
    به علاوه، $BN_0$
-   نشان دهنده ی توان نویز اضافه شونده ی گوسی می باشد و $I_{u(v,i)}$
+   نشان دهنده ی توان نویز اضافه شونده ی گوسی می‌باشد و $I_{u(v,i)}$
    توان سیگنال تداخلی است.
 همچنین $a_{v,s} \in \{0,1\}$
-متغیر باینری است که نشان دهنده ی این است که برش شبکه ی $s$ به سرویس $v$ خدمات رسانی می کند یا نه.
+متغیر باینری است که نشان دهنده ی این است که برش شبکه ی $s$ به سرویس $v$ خدمات رسانی می‌کند یا نه.
 درصورتی که 
  $a_{v,s} =1$
- برش شبکه ی $s$ به سرویس $v$ خدمات رسانی می کند. در غیر این صورت خدمت رسانی نمی کند.
+ برش شبکه ی $s$ به سرویس $v$ خدمات رسانی می‌کند. در غیر این صورت خدمت رسانی نمی‌کند.
 \newline
 برای بدست آوردن \lr{SNR} در فرمول \eqref{eq2}، 
-فرض می شود که 
+فرض می‌شود که 
  $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $
- بردار سیگنال دریافتی از همه ی کاربران در سرویس $v$ می باشد 
+ بردار سیگنال دریافتی از همه ی کاربران در سرویس $v$ می‌باشد 
 \begin{equation}\label{eq3}
@@
 $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $
-نشان دهنده ی بردار سمبل ارسالی کاربران سرویس $v$ می باشد.
+نشان دهنده ی بردار سمبل ارسالی کاربران سرویس $v$ می‌باشد.
 $\boldsymbol{z}_{U_v}$
@@
 $N_0$
-توان نویز می باشد.
+توان نویز می‌باشد.
 علاوه بر این
 $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $
-نشان دهنده ی نویز کوانتیزاسیون می باشد که از فشرده سازی سیگنال  در واحد توزیع شده بدست آمده است.
+نشان دهنده ی نویز کوانتیزاسیون می‌باشد که از فشرده سازی سیگنال  در واحد توزیع شده بدست آمده است.
 $\boldsymbol{P}_{U_v} = \diag{(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})}$.
@@
 $\zeta_{k,s}^{u(v,i)} \in \{0,1\}$
-پارامتر باینری می باشد که نشان دهنده ی این است که $i$ امین کابر در $v$امین سرویس امکان ارسال سیگنال خود را از طریق 
+پارامتر باینری می‌باشد که نشان دهنده ی این است که $i$ امین کابر در $v$امین سرویس امکان ارسال سیگنال خود را از طریق 
 \lr{PRB}
@@
 ام دارد یا نه، در ضمن این \lr{PRB} 
- متعلق به برش $s$ ام می باشد و یا نه.
+ متعلق به برش $s$ ام می‌باشد و یا نه.
  $\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
@@
  $\mathcal{U}_v$
- کاربران می باشد.
+ کاربران می‌باشد.
 بردار کانال بین $s$امین برش و $i$امین کابر در $v$امین سرویس $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ به صورت زیر نشان داده شده است 
@@
 $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$
-نشان دهنده ی بردار کانال فیدینگ سریع و تخت می باشد و
+نشان دهنده ی بردار کانال فیدینگ سریع و تخت می‌باشد و
  $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
- نشان دهنده ی ماتریس فیدینگ مقیاس بزرگ می باشد.
-در اینجا فرض بر این است که اطلاعات حالت کانال \lr{CSI}، به صورت کامل می باشد.\newline
+ نشان دهنده ی ماتریس فیدینگ مقیاس بزرگ می‌باشد.
+در اینجا فرض بر این است که اطلاعات حالت کانال \lr{CSI}، به صورت کامل می‌باشد.\newline
  $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $
  بردار بیم فرمینگ \lr{zero forcing}
-  می باشد که برای مینیمم کردن تداخل می باشد و بدین صورت است
+  می‌باشد که برای مینیمم کردن تداخل می‌باشد و بدین صورت است
 \begin{equation}
@@
 \end{equation}  
-توان تداخلی کابر $i$ام به سرویس $v$ام به صورت زیر بیان می شود
+توان تداخلی کابر $i$ام به سرویس $v$ام به صورت زیر بیان می‌شود
 \begin{equation}
@@
 امین 
-واحد رادیویی در برش $s$ می باشد.
-سیگنال تداخلی برای هر کاربر از سیگنالهای کاربرانی بدست می آید که از \lr{PRB} مشترکی استفاده نموده اند.
+واحد رادیویی در برش $s$ می‌باشد.
+سیگنال تداخلی برای هر کاربر از سیگنالهای کاربرانی بدست می‌آید که از \lr{PRB} مشترکی استفاده نموده اند.
 درصورت قرار دادن $P_{max}$
@@
 $I_{u_{(v,i)}}$
-بدست می آید
+بدست می‌آید
 بنابراین،
@@
 \eqref{eq1} و \eqref{eq2}
-بدست می آید.
+بدست می‌آید.
 \newline
 فرض کنید $\bar{p}_{r_{(s,j)}}$
-نشان دهنده ی سیگنال ارسالی از $j$ امین واحد رادیویی در $s$ امین برش می باشد.
+نشان دهنده ی سیگنال ارسالی از $j$ امین واحد رادیویی در $s$ امین برش می‌باشد.
 از رابطه ی \eqref{eq3} داریم
@@
 \end{equation}
-در این صورت نرخ کاربران در لینک \lr{fronthaul} بین $j$امین واحد رادیویی در برش $s$ام با واحد توزیع شده ی موجود در این برش، بدین صورت می باشد  \cite{simeone2016cloud, 1111}
+در این صورت نرخ کاربران در لینک \lr{fronthaul} بین $j$امین واحد رادیویی در برش $s$ام با واحد توزیع شده ی موجود در این برش، بدین صورت می‌باشد  \cite{simeone2016cloud, 1111}
 \begin{equation}
@@
 $a_{v,s}$
-متغیر باینری است که نشان دهنده ی این است که برش $s$ام به سرویس $v$ خدمات رسانی می کند یا نه.
+متغیر باینری است که نشان دهنده ی این است که برش $s$ام به سرویس $v$ خدمات رسانی می‌کند یا نه.
 \subsection{میانگین تاخیر}
@@
 $\lambda_{u(v,i)}$
-برای $i$امین کاربر در سرویس $v$ ام می باشد.
-بنابراین، در لایه ی واحد مرکزی (\lr{CU})، میانگین نرخ ورود داده ی کاربری که از خدمات برش $s$ استفاده می نماید 
+برای $i$امین کاربر در سرویس $v$ ام می‌باشد.
+بنابراین، در لایه ی واحد مرکزی (\lr{CU})، میانگین نرخ ورود داده ی کاربری که از خدمات برش $s$ استفاده می‌نماید 
 $\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$
-می باشد. 
+می‌باشد. 
 همچنین، میانگین نرخ داده ی ورودی در لایه ی \lr{DU}، تقریبا مساوی میانگین نرخ داده ی ورودی لایه ی اول 
 $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$
-می باشد.
-میانگین نرخ داده ی ورودی در لایه ی \lr{DU}، تقریبا برابر میانگین نرخ داده ی ورودی در لایه ی \lr{CU} می باشد $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$.
-در اینجا فرض بر این است کهدر هر لایه متعادل کننده ی ترافیک موجود است که ترافیک ورودی را به طور مساوی بین \lr{VNF} ها تقسیم می نماید\cite{frdl,luong2018novel,luong2018novel1}.
-فرض کنید پردازش باند پایه هر \lr{VNF}، بوسیله ی پردازش صف \lr{M/M/1} نشان داده می شود.
-هر بسته بوسیله ی یکی از \lr{VNF}های برش شبکه، پردازش می شود.
-بنابراین، میانگین تاخیر برش $s$ در لایه ی اول و دوم با استفاده از مدل \lr{M/M.1} به این صورت نشان داده می شود
+می‌باشد.
+میانگین نرخ داده ی ورودی در لایه ی \lr{DU}، تقریبا برابر میانگین نرخ داده ی ورودی در لایه ی \lr{CU} می‌باشد $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$.
+در اینجا فرض بر این است کهدر هر لایه متعادل کننده ی ترافیک موجود است که ترافیک ورودی را به طور مساوی بین \lr{VNF} ها تقسیم می‌نماید\cite{frdl,luong2018novel,luong2018novel1}.
+فرض کنید پردازش باند پایه هر \lr{VNF}، بوسیله ی پردازش صف \lr{M/M/1} نشان داده می‌شود.
+هر بسته بوسیله ی یکی از \lr{VNF}های برش شبکه، پردازش می‌شود.
+بنابراین، میانگین تاخیر برش $s$ در لایه ی اول و دوم با استفاده از مدل \lr{M/M/1} به این صورت نشان داده می‌شود
 \begin{equation}
@@
 $1/\mu_1$ و $1/\mu_2$
-میانگین زمان سرویس دهی در لایه ی اول و دوم به ترتیب می باشند.
+میانگین زمان سرویس دهی در لایه ی اول و دوم به ترتیب می‌باشند.
 $\alpha_{s}$
-نرخ ورودی است که توسط متعادل کننده ی ترافیک به طور مساوی بین \lr{VNF} ها تقسیم می شود.
-نرخ ورودی هر \lr{VNF} در هر لایه از برش \lr{s}، $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$ می باشد.
+نرخ ورودی است که توسط متعادل کننده ی ترافیک به طور مساوی بین \lr{VNF} ها تقسیم می‌شود.
+نرخ ورودی هر \lr{VNF} در هر لایه از برش \lr{s}، $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$ می‌باشد.
 $d_{s_{tr}}$
-تاخیر ارسال برای برش $s$ در لینک وایرلس می باشد.
+تاخیر ارسال برای برش $s$ در لینک وایرلس می‌باشد.
 نرخ داده ی ورودی لینک وایرلس برابر نرخ داده ی ورودی متعادل کننده ی ترافیک برای هر برش است
@@
 همچنین زمان سرویس برای صف ارسال در هر برش $s$ دارای توزیع نمایی با میانگین $1/(R_{{tot}_s})$
-است و می توان به صورت صف \lr{M/M/1} مدل کرد  
+است و می‌توان به صورت صف \lr{M/M/1} مدل کرد  
 \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}.
@@
  $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ 
- کل نرخ قابل دسترس در هر برش می باشد که به سرویس خاص، تخصیص داده است.
+ کل نرخ قابل دسترس در هر برش می‌باشد که به سرویس خاص، تخصیص داده است.
 میانگین تاخیر در هر برش نیز بدین صورت است
@@
 هر \lr{VNF}
-نیازمند منابع فیزیکی است که شامل حافظه، نگهدارنده و پردازشگر می باشد.
-فرض کنید منابع مورد نیاز برای $f$ امین \lr{VNF} در برش $s$ ام به صورت زیر می باشد
+نیازمند منابع فیزیکی است که شامل حافظه، نگهدارنده و پردازشگر می‌باشد.
+فرض کنید منابع مورد نیاز برای $f$ امین \lr{VNF} در برش $s$ ام به صورت زیر می‌باشد
  \begin{equation}
@@
 $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$
-به ترتیب نشان دهنده ی مقدار حافظه، نگهدارنده و پردازشگر می باشد.
-همچنین مقدار کل حافظه، نگهدارنده و پردازشگر برای همه \lr{VNF} ها در یک برش به این صورت تعریف می شود
+به ترتیب نشان دهنده ی مقدار حافظه، نگهدارنده و پردازشگر می‌باشد.
+همچنین مقدار کل حافظه، نگهدارنده و پردازشگر برای همه \lr{VNF} ها در یک برش به این صورت تعریف می‌شود
 \begin{equation}
@@
 \end{equation}
-همچنین $D_c$ مرکز داده برای سرویس دهی به \lr{VNF} ها می باشد. هر مرکز داده شامل تعدادی سرور برای سرویس دهی است.
+همچنین $D_c$ مرکز داده برای سرویس دهی به \lr{VNF} ها می‌باشد. هر مرکز داده شامل تعدادی سرور برای سرویس دهی است.
 مقدار حافظه، نگهدارنده و پردازشگر به ترتیب با 
@@
 $j^{th}$
-امین مرکز داده به ترتیب زیر می باشد.
+امین مرکز داده به ترتیب زیر می‌باشد.
 \begin{equation*}
@@
 تخصیص منابع فیزیکی به \lr{VNF} ها در نظر گرفته شده است. 
-در اینجا فرض بر این است که $y_{s,d}$ متغیر صفر و یکی است که نشان میدهد مرکز داده ی $d$ ام به $s$ امین برش متصل است یا نه.
+در اینجا فرض بر این است که $y_{s,d}$ متغیر صفر و یکی است که در صورت یک بودن نشان می‌دهد مرکز داده ی $d$ام به $s$امین برش، منابع فیزیکی اختصاص داده است.
 \subsection{صورت مساله}
-یک معیار مهم برای سنجش بهینگی یک سیستم ، بهره وری انرژی است که نسبت نرخ کل به توان کل می باشد.
+یک معیار مهم برای سنجش بهینگی یک سیستم ، بهره وری انرژی است که نسبت نرخ کل به توان کل می‌باشد.
 \begin{equation}
@@
  $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$
- توان کل مصرفی تمام واحد های رادیویی در یک برشمی باشد.
+ توان کل مصرفی تمام واحد های رادیویی در یک برش می‌باشد.
 همچنین 
  $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $
- نرخ تمام کاربران مصرفی تمام سرویس ها می باشد.
-فرض کنید توان مصرفی پردازش باند پایه در هر مرکز داده ی $d$ که به \lr{VNF} های یک برش $s$ متصل می باشد با   
+ نرخ تمام کاربران مصرفی تمام سرویس ها می‌باشد.
+فرض کنید توان مصرفی پردازش باند پایه در هر مرکز داده ی $d$ که به \lr{VNF} های یک برش $s$ متصل می‌باشد با   
 $\phi_{s,d}$
 نشان داده شده است.
-بنابراین می توان توان کل سیستم را برای کلیه مرکز داده های فعال که به برش متصل هستند ،بدین صورت نشان داد
+بنابراین می‌توان توان کل سیستم را برای کلیه مرکز داده های فعال که به برش متصل هستند ،بدین صورت نشان داد
 \begin{equation*}
@@
 متغیر باینری برای اتصال
-مرکز داده ی فیزیکی به VNFها می باشد.
+مرکز داده ی فیزیکی به VNFها می‌باشد.
 همچنین
@@
 \eqref{c13}
-منجر به افزایش نرخ هرکاربر از حد مورد نیاز می باشد.
+منجر به افزایش نرخ هرکاربر از حد مورد نیاز می‌باشد.
  \eqref{c14}
@@
   و محدودیت مورد نیاز برای تاخیر سیگنال ارسالی
-  را نشان می دهد.
+  را نشان می‌دهد.
   \eqref{c21}
- تضمین می کند که هر سرویس
+ تضمین می‌کند که هر سرویس
  به حداقل یک
@@
 \eqref{c23}
-تضمین می کند که هر برش که شامل VNF هایی در دو لایه است،
-به حداقل یک مرکز داده متصل می شود.
+تضمین می‌کند که هر برش که شامل VNF هایی در دو لایه است،
+به حداقل یک مرکز داده متصل می‌شود.
 در \eqref{c22} 
 $\mathcal{E} = \{M,S,C\}$ 
-و شرطها ضمانت می کند که منابع فیزیکی کافی برای VNFها وجود دارد.\newline
+و شرطها ضمانت می‌کند که منابع فیزیکی کافی برای VNFها وجود دارد.\newline
 مسئله‌ی بهینه‌سازی \eqref{constraints}
-قابل جداسازی به دو مسئله‌ی بهینه‌سازی کوچکتر می‌باشد زیرا متغیرها می‌تواندد به صورت مجزا بدست آیند. ابتدا نیاز به حل مسئله‌ی اول 
+قابل جداسازی به دو مسئله‌ی بهینه‌سازی کوچکتر می‌باشد زیرا متغیرها می‌تواند به صورت مجزا بدست آیند. ابتدا نیاز به حل مسئله‌ی اول 
 داریم و پس از حل آن
@@
 		\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
-		\text{\lr{subject to}} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
-		&\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
+		\text{\lr{subject to}} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \quad \forall s, \\
+		&\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \quad \forall d, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
 	\end{alignat}
-	\label{constraints2}
+	\label{constraints23}
 \end{subequations}
@@
 \subsection{بخش اول مسئله‌ی اول}\label{firstsub}
-الگوربتم تکرار شده برای بدست آوردن $\boldsymbol{A}$ در اینجا اجرا می‌گردد.
+الگوریتم تکرار شده برای بدست آوردن $\boldsymbol{A}$ در اینجا اجرا می‌گردد.
 بخش اول مسئله‌ی اول از جنس بسته‌بندی جعبه به صورت سه بعدی می‌باشد که یک مسئله‌ی NP-Hard است و برای حل آن نیاز به الگوریتمهای ابتکاری داریم.
@@
 \cite{3dbin}،
-الگوریتم ابتکاری براساس مرتب‌سازی جعبه‌ها براساس اندازه‌گیری بیان شده‌است. جزئیات الگوریتم موردنظر در \ref{alg}
+الگوریتم ابتکاری براساس مرتب‌سازی جعبه‌ها براساس اندازه‌گیری بیان شده‌است.
+در این الگوریتم، ابتدا سرویسها بر اساس  مقدار نیازمندی کاربران به صورت نزولی قرار گرفته‌اند.
+همچنین برشهای شبکه نیز براساس جمع وزن‌داری از ظرفیت منابع فیزیکی و پردازشی خود به صورت نزولی قرار گرفته‌اند.
+سپس در صورت اعمال شرط
+\eqref{c11}،
+ \eqref{c12}،
+ \eqref{c13}
+ و 
+\eqref{c14} 
+برش شبکه به سرویس تخصیص داده می‌شود و در غیر این صورت به برش شبکه‌ی بعدی برای اعمال شرط‌ها انتقال داده می‌شود.
+جزئیات الگوریتم موردنظر در \ref{alg}
 و براساس الگوریتم
@@
 
-			\State{Sort services according to the number of UE's requirements in the descending order.}
-			\State{Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs and the capacity of thei resources in the descending order.}
+			\State{Sort services according to the number of UEs, priority and their requirements in the descending order.}
+			\State{Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs and the capacity of their resources in the descending order.}
 			\For {$i \gets 1$ to $S$}
@@
 			\State{Set $a_{i,j} = 1$}
-			\State{Obtain Parameters of Systems (power and rate , capacity of fronhaul links)}
+			\State{Obtain Parameters of Systems (power, delay, rate and capacity of fronhaul links)}
 			\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} are not applied}
@@
 در بخش دوم مسئله‌ی اول از الگوریتم تکراری و تابع لاگرانژ برای حل استفاده شده است. 
-از آنجایی که تداخل تابعی از توان کاربران است، برای سادگی فرض باند بالای $\bar{I}_{u_{(v,i)}}$ برای آن می کنیم. برای اینکه بتوانیم 
+از آنجایی که تداخل تابعی از توان کاربران است، برای سادگی فرض باند بالای $\bar{I}_{u_{(v,i)}}$ برای آن می‌کنیم. برای اینکه بتوانیم 
 \eqref{constraints1}
@@
 جزئیات حل هر بخش از مسئله‌ی اول آورده شده است.
-در ایتدا با ثابت نگه‌داشتن $\boldsymbol{P} = P_{max}$
+در ابتدا با ثابت نگه‌داشتن $\boldsymbol{P} = P_{max}$
 و $\eta = 0$
@@
 در مسئله‌ی \eqref{constraints1}
-و با استفاده از \eqref{alg}
+و با استفاده از الگوریتم \eqref{alg}
 بدست می‌آید. 
-سپس $\boldsymbol{A}$ از الگوریتم \ref{alg} بدست می‌آید. پس از آن در بخش دوم، با استفاده از روش sub-gradient، $\boldsymbol{P}$ 
+پس از آن در بخش دوم، با استفاده از روش 
+sub-gradient
+مقدار
+ $\boldsymbol{P}$ 
 بدست می‌آید. 
-بعد از بدست آوردن $\boldsymbol{P}$ و $\eta$ الگویتم با مقادیر جدید توان و بهره‌وری انرژی دوباره تکرار می گردد تا همگرا شود.
+بعد از بدست آوردن $\boldsymbol{P}$
+مقدار $\eta$
+نیز دوباره به‌روز رسانی می‌شود.
+ سپس الگویتم با مقادیر جدید توان و بهره‌وری انرژی دوباره تکرار می‌گردد تا همگرا شود.
 در اینجا الگوریتم حل مسئله‌ی اول به صورت الگوریتم \eqref{alg2} است.
@@
 \end{algorithm}
-\subsection{مسئله‌ی دوم}
-در این بخش می‌خواهیم \eqref{constraints2} را حل نماییم که قرارگیری منابع مجازی در منابع فیزیکی می‌باشد به‌طوری که تابع هزینه‌ی  $\psi_{tot}$ کمینه شود.
+\subsection{ حل مسئله‌ی دوم}
+در این بخش می‌خواهیم مسئله‌ی \eqref{constraints23} را حل نماییم که قرارگیری منابع مجازی در منابع فیزیکی می‌باشد به‌طوری که تابع هزینه‌ی  $\psi_{tot}$ کمینه شود.
 این مسئله از جنس مسئله‌ی سه بعدی بسته‌بندی جعبه است که NP-Hard می‌باشد.
 برای بدست‌آوردن مقدار بهینه‌ی $\boldsymbol{Y}$ الگوریتم ابتکاری برای حل مسئله‌ی سه بعدی بسته‌بندی جعبه ارائه شده است.
-جزئیات الگوریتم در \eqref{alg3} نوشته شده است. در این الگوریتم، در ابتدا برشهای شبکه و مرکز داده ها را بر اساس  جمع وزنی آنها مرتب می کنیم (خط \ref{31} و \ref{32} الگوریتم \ref{alg3}).
+جزئیات الگوریتم در \eqref{alg3} نوشته شده است. در این الگوریتم، در ابتدا برشهای شبکه و مرکز داده ها را بر اساس  جمع وزنی آنها به صورت نزولی مرتب می‌کنیم (خط \ref{31} و \ref{32} الگوریتم \ref{alg3}).
 در اینجا، پارامتر وزندار برای $\Omega_{\mathfrak{z},s}^{tot}$ و $\tau_j^\mathfrak{z}$ بدین صورت تعریف می‌کنیم.
@@
 که دراینجا، $\boldsymbol{w} = \{w_M, w_S, w_C\}$ وزن حافظه، نگهداری و CPU می‌باشد
-\cite{3dbin}.
-در مرحله دوم، ما تخصیص را از بیشترین برش های مورد نیاز به DC با بیشترین منابع فیزیکی شروع می کنیم(از خط \ref{33} تا \ref{34} الگوریتم \ref{alg3}).
+که  از الگوریتم مورد استفاده برای بسته‌بندی سه بعدی در مقاله‌ی 
+\cite{3dbin}
+استفاده شده است.
+در مرحله دوم، ما تخصیص را از بیشترین برش های مورد نیاز به DC با بیشترین منابع فیزیکی شروع می‌کنیم(از خط \ref{33} تا \ref{34} الگوریتم \ref{alg3}).
  بعد از تخصیص برش شبکه به مرکز داده، در صورتی که یکی از برشهای شبکه توسط مرکز داده پذیرش نشود، برای بخش بعدی جاگذاری می‌رود
@@
 	\centering
-	\includegraphics[width=\linewidth]{./fig/fig_prb}
+	\includegraphics[width=\linewidth]{./fig/fig_prb1}
 	\caption{بهره‌وری انرژی براساس تعداد بلوکهای منابع فیزیکی}
@@
 	\centering
-	\includegraphics[width=\linewidth]{./fig/fig_service}
+	\includegraphics[width=\linewidth]{./fig/fig_service1}
 	\caption{بهره‌وری انرژی براساس تعداد سرویسهای مختلف }
@@
 	\centering
-	\includegraphics[width=\linewidth]{./fig/f112}
+	\includegraphics[scale = 0.5]{./fig/f112}
 	\caption{نسبت برش های پذیرفته شده فقط به یک 	DC در مقابل برش های کل}
@@
 در این شبیه سازی ، فرض کنید تعداد DC ها کاملاً کافی باشد تا تمام برش ها را پوشش دهد و پارامتر طراحی شده $ \ nu $ کم فرض شود ، بنابراین ما روی اولین ترم \eqref{eqpsi} تمرکز کردیم.
-با این حال ، اگر هر قطعه باقی مانده باشد ، می تواند توسط بیش از یک DC سرویس دهی شود.
-بهینه بودن محل قرارگیری برشها در منابع DC بر اساس مصرف توان DC ها اندازه گیری می شود.
+با این حال ، اگر هر قطعه باقی مانده باشد ، می‌تواند توسط بیش از یک DC سرویس دهی شود.
+بهینه بودن محل قرارگیری برشها در منابع DC بر اساس مصرف توان DC ها اندازه گیری می‌شود.
 در اینجا مقدار منابع  مصرف DC نشده نشان داده شده است. برای ۱۰ برش شبکه اختلاف بین مقدار بهینه و روش اعمال شده ۱۵ درصد می‌باشد. 
@@
 	\centering
-	\includegraphics[width=\linewidth]{./fig/fig22_last}
+	\includegraphics[scale = 0.5]{./fig/fig22_last} %[width=\linewidth] 
 	\caption{نرمالیزه‌ی مصرف منابع بر‌اساس تعداد برشها}
@@
 \section{نتیجه‌گیری}
-در این فصل، همزمانی برش شبکهو تخصیص توان در سیستم ORAN آمده‌است.
-فرض بر این است که کاربران بر اساس نیازهایشان به سرویسهای مختلف طبقه بندی می شوند.
+در این فصل، همزمانی برش شبکه و تخصیص توان در سیستم ORAN آمده‌است.
+فرض بر این است که کاربران بر اساس نیازهایشان به سرویسهای مختلف طبقه بندی می‌شوند.
 همچنین ، تعدادی برش نیز در خدمت این سرویسها قرار می‌گیرد.
@@
 هدف به حداکثر رساندن مجموع نرخ و به حداقل رساندن مصرف توان و هزینه انرژی مراکز داده به طور همزمان است.
-این مسئله به دو زیر مسئله تجزیه می شود. هر زیر مسئله به طور جداگانه توسط یک الگوریتم ابتکاری حل می شود. با استفاده از نتایج عددی، روش اکتشافی را تأیید کرده و عملکرد الگوریتم ها را مطالعه می کنیم.
+این مسئله به دو زیر مسئله تجزیه می‌شود. هر زیر مسئله به طور جداگانه توسط یک الگوریتم ابتکاری حل می‌شود. با استفاده از نتایج عددی، روش اکتشافی را تأیید کرده و عملکرد الگوریتم ها را مطالعه می‌کنیم.
 برای مسئله‌ی اول بازدهی انرژی در مقابل تعداد UE در هر سرویس به تصویر کشیده شده است.
@@
 در شکل اول، نسبت برش های پذیرفته شده که فقط به یک DC متصل می‌شوند، برای تعداد برش های مختلف مشخص شده است.
-در شکل دوم ، مصرف منابع نرمال DC ها به تصویر کشیده شده است.
-در هر شکل ، الگوریتم ابتکاری با روش بهینه مقایسه شده و تفاوت بین آنها بحث شده است.
+در شکل دوم، مصرف منابع نرمال DC ها به تصویر کشیده شده است.
+در هر شکل، الگوریتم ابتکاری با روش بهینه مقایسه شده و تفاوت بین آنها بحث شده است.

### 2020-10-19 Latex/tehran-thesis - Copy/tex/chapter4.tex
change proposal

@@
 \section{مقدمه}
-در این فصل هدف تخصیص برش شبکه به صورت می‌باشد.
+در این فصل هدف تخصیص برش شبکه به صورت دینامیکی می‌باشد.
 در فصل قبلی مدل سیستم به طور کامل نوشته شده است و در حالت آفلاین حل گردیده است، در این فصل پارامترها مورد نیاز را نسبت به فصل قبلی کمتر کرده و با استفاده از روش دینامیکی در هر لحظه از زمان به حل سیستم می‌پردازیم.
-برای حل این سیستم از روش یادگیری تقویتی عمیق استفاده می‌کنیم.
-در بخش اول صورت مسئله‌ی بخش رادیویی نوشته می‌شود. سپس به صورت مسئله و مدل سیستم بخش هسته می‌پردازیم و در نهایت روش حل هر دو مسئله و نتایج عددی آن بیان می‌شود.
+برای حل این سیستم از روش یادگیری تقویتی استفاده می‌کنیم.
+در بخش اول صورت مسئله‌ی بخش رادیویی نوشته می‌شود. سپس  به مدل سیستم بخش هسته می‌پردازیم و در نهایت روش حل هر دو مسئله و نتایج عددی آن بیان می‌شود.
 \section{ مدل سیستم و صورت مسئله‌ی اول}
-در این بخش هدف برش شبکه در بخش رادیویی سیستم می‌باشد. دراینجا، مسئله‌ی اول فصل قبلی ساده شده و به روش دینامیکی حل می‌شود.   
+در این بخش هدف برش شبکه در بخش رادیویی می‌باشد. دراینجا، مسئله‌ی اول فصل قبلی ساده شده و به روش دینامیکی حل می‌شود.   
 همانند سیستم فصل قبل، فرض می کنیم $S$ برش شبکه داریم که قرار است $V$ سرویس مختلف که شامل کاربرانی است که از سرویس خاص استفاده می‌نمایند را سرویس دهی نماید.
@@
  می‌باشد.
-در این بخش سعی برا‌ین است که در ابتدا مسئله را به ساده‌ترین حالت ممکن حل نماییم.
-فرض می‌کنیم سه مدل سرویس مختلف داریم که سرویسهای دسته‌ی اول نیازمند تاخیر خاص و سرویسهای دسته‌ی دوم نیازمند داشتن تاخیر کم هستند و سرویس سوم نیازمند داشتن هر دو حالت تاخیر کم و نرخ زیاد است.
-در بخش اول این مسئله، هدف بیشینه‌سازی تعدای سرویسهای پذیرفته شده می‌باشد. در اینجا فرض براین است که تعداد برشهاس شبکه محدود می‌باشد. فرض می‌کنیم هر سرویس $v$ دارای اولویت $p_v$ می‌باشد. 
-همچنین فرض براین است که هر سرویس شامل ماکسیمم $U_v$ کاربر است و به طور میانگین کاربران آن نیازمند داشتن نرخ بیشتر از $R_v$ و تاخیر کمتر از $D_v$ هستند. درصورتی که کاربری از دسته‌ی اول باشد 
+در این بخش سعی برا‌ین است که در ابتدا مسئله را به ساده‌ترین حالت ممکن حل نماییم. فرض می‌کنیم  چند نوع سرویس مختلف داریم که هر نوع سرویس نیازمند مقدار نرخ خاص و تاخیر خاص هستند.
+در بخش اول این مسئله، هدف بیشینه‌سازی تعدای سرویسهای پذیرفته شده می‌باشد. در اینجا فرض براین است که تعداد برشهای شبکه محدود می‌باشد. فرض می‌کنیم هر سرویس $v$ دارای اولویت $p_v$ می‌باشد. 
+همچنین فرض براین است که هر سرویس شامل ماکسیمم $U_v$ کاربر است و به طور میانگین کاربران آن نیازمند داشتن نرخ بیشتر از $R_v$ 
+و تاخیر کمتر از $D_v$ 
+هستند. 
+درصورتی که نوعی سرویس معرفی شود که تاخیر در آن حائز اهمیت نباشد،
 $D_v =  M$ 
 که $M$ برای تاخیر یک عدد بزرگ می‌باشد.
-و در صورتی که سرویس از دسته‌ی دوم باشد 
+و در صورتی که برای یک سرویس نرخ حائز اهمیت نباشد 
 $R_v = N $
@@
 که در اینجا، معادله‌ی \eqref{eqmain1}
-یک معادله‌ی کوله‌پشتی دو بعدی می‌باشد.
+یک مسئله‌ی کوله‌پشتی دو بعدی می‌باشد.
 برای حل این مسئله، از روش یادگیری تقویتی استفاده می‌شود.
+همچنین در صورت در نظر گرفتن تاخیر در شبکه، هر برش شبکه تنها به یک سرویس اختصاص داده می‌شود.
 \section{ مدل سیستم و صورت مسئله‌ی دوم}
-در این بخش سعی شده، مسئله‌ی دوم فصل قبل به صورت ساده شده با روش دینامیکی حل شود. عنوان این مسئله، جاگزاری VNFها برروی مراکز داده می‌باشد.
-فرض براین است که $S$ برش شبکه داریم که هر برش شبکه s
+در این بخش سعی شده، مسئله‌ی دوم فصل قبل به صورت ساده شده با روش دینامیکی حل شود. عنوان این مسئله، جاگذاری VNFها برروی مراکز داده می‌باشد.
+فرض براین است که $S$ برش شبکه داریم که هر برش شبکه
 $s\in \{1,2,...,S \} $
@@
 نیازمند منابع فیزیکی است که شامل حافظه، نگهدارنده و پردازشگر می باشد.
-فرض کنید برای سادگی مسئله برای هر VNF به مقدار کافی حافظه و نگهددارنده در مراکز داده داریم و تنها منبع مورد نیاز برای $f$ امین \lr{VNF} در برش $s$ ام مقدار پردازنده است که به صورت $\bar{\Omega}_{s}^f$ می باشد
+فرض کنید برای سادگی مسئله برای هر VNF به مقدار کافی حافظه و نگهدارنده در مراکز داده داریم و تنها منبع مورد نیاز برای $f$ امین \lr{VNF} در برش $s$ام مقدار پردازنده است که به صورت $\bar{\Omega}_{s}^f$ می باشد
 %\begin{equation}
@@
 \end{equation}
-همچنین $D_c$ مرکز داده برای سرویس دهی به \lr{VNF} ها می باشد. هر مرکز داده شامل تعدادی سرور برای سرویس دهی است.$M_s$ تعداد کل VNFها در sامین برش شبکه است.
+همچنین $D_c$ مرکز داده برای سرویس دهی به \lr{VNF} ها می باشد. هر مرکز داده شامل تعدادی سرور برای سرویس دهی است.
+$M_s$ 
+تعداد کل
+ \lr{VNF}
+ها در $s$امین برش شبکه است.
 مقدار پردازشگر 
@@
 \end{equation*}
-همچنین ، یک تابع هزینه برای قرار
-همچنین فرض کنید در هر زمان قرار دادن هر مجموعه‌ی جدید VNFهای برش شبکه s برروی مرکز داده d مقدار انرژی اضافی را بدین صورت به سیستم اعمال کنند.
+همچنین فرض کنید در هر زمان قرار دادن هر مجموعه‌ی جدید
+ \lr{VNF}های 
+برش شبکه s برروی مرکز داده d مقدار انرژی اضافی را بدین صورت به سیستم اعمال کنند.
 \begin{equation*}
@@
 %%
-تابع هزینه‌ی قرارگیری VNFها برروی DCها بدین صورت است
+تابع هزینه‌ی قرارگیری 
+\lr{VNF}ها
+ برروی
+\lr{DC}ها 
+ بدین صورت است
 \begin{equation}\label{eqpsi}
@@
 \end{equation}
-در اینجا هدف کمینه کردن مقدار انرژی کل در هر زمان، با فرض اینکه مجموع VNFهای برشهای تخصیص یافته به هر مرکز داده مقدار کافی پردازنده داشته باشند.
+در اینجا هدف کمینه کردن مقدار انرژی کل در هر زمان، با فرض اینکه مجموع
+ \lr{VNF}های 
+ برشهای تخصیص یافته به هر مرکز داده مقدار کافی پردازنده داشته باشند.
 در اینجا فرض براین است که برشهای شبکه که قبلا به سرویسها اختصاص داده شده، می‌بایست در مرکز داده قرار داده شوند و تعداد مراکز داده به اندازه‌ی کافی زیاد هستند، هدف کمینه کردن انرژی است به صورتی که کمترین تعداد مرکز داده‌ها استفاده شوند.
@@
 در این بخش، برای مسئله‌ی اول حالت، عامل و پاداش را تعیین می‌نماییم و سپس نتایج عملی را نشان می‌دهیم.
-در این مسئله، عامل، orchestrator است که وظیفه‌ی مدیریت شبکه را برعهده دارد.
+در این مسئله، عامل، هماهنگ‌‌ ‌ساز \LTRfootnote{orchestrator} است که وظیفه‌ی مدیریت شبکه را برعهده دارد.
 همچنین، حالت در هر بازه‌ی زمانی برشهایی از شبکه است که به سرویسها متصل شده و همچنین مقدار منبع باقی ماده در هر برش می‌باشد. 
@@
 \end{figure}
+در شکل \ref{fig:admittedService}
+با افزایش تعداد برشهای شبکه و به همان نسبت تعداد درخواستها، مقدار نرمالیزه‌ی میانگین مجموع تعداد سرویسهای پذیرفته شده‌ی هر دو نوع سرویس براساس  تعداد برشهای شبکه در دو حالت استفاده از روش بهینه و روش یادگیری تقویتی رسم شده است.
+با افزایش تعداد درخواستها و تعداد برشها، روش بهینه از روش یادگیری تقویتی فاصله می‌گیرد.
+
+\begin{figure}%[H]
+	\centering
+	\includegraphics[scale = 0.6]{./fig/admittedService1} %[width=\linewidth] 
+	\caption{  
+		میانگین تعداد سرویسهای پذیرفته شده در زمان در دو حالت بهینه و استفاده از الگوریتم تقویتی با افزایش تعداد برشهای شبکه}
+	\label{fig:admittedService}
+\end{figure}
 \subsection{نتایج عددی مسئله‌ی دوم} 
 در این بخش، برای مسئله‌ی دوم حالت، عامل و پاداش را تعیین می‌نماییم و سپس نتایج عملی را نشان می‌دهیم.
-در این مسئله، عامل، orchestrator است که وظیفه‌ی مدیریت شبکه را برعهده دارد.
+در این مسئله، عامل، هماهنگ‌‌ ‌ساز است که وظیفه‌ی مدیریت شبکه را برعهده دارد.
 همچنین، حالت در هر بازه‌ی زمانی برشهایی از شبکه است که به مراکزداده متصل شده و اینکه کدام برش به کدام مرکز داده متصل است.
@@
 نرخ خروج در هر بازه‌ی زمانی $80$ درصد فرض شده است.
+\begin{figure}%[H]
+	\centering
+	\includegraphics[scale = 0.6]{./fig/consumptionE} %[width=\linewidth] 
+	\caption{  نسبت مقدار هزینه‌ی مصرفی نرمالیزه شده به تعداد میانگین برشهای مورد نیاز در جالت بهینه و الگوریتم یادگیری تقویتی }
+	\label{fig:consumptionE}
+\end{figure}
+در شکل \ref{fig:consumptionE}
+نسبت مقدار هزینه‌ی مصرفی نرمالیزه شده به تعداد میانگین برشهای مورد نیاز در جالت بهینه و الگوریتم یادگیری تقویتی رسم شده است.
+در اینجا با افزایش تعداد درخواستهای برشهای شبکه به منبع پردازشی به صورت میانگین، میزان هزینه‌ی مصرفی را در حالت بهینه و روش یادگیری تقویتی رسم کردیم و با افزایش درخواستها، روش یادگیری تقویتی از روش بهینه فاصله می‌گیرد.
 \section{نتیجه‌گیری}

### 2020-10-19 Latex/tehran-thesis - Copy/tex/faTitle.tex
change proposal

@@
 % عنوان پایان‌نامه را وارد کنید
-\title{تخصیص منابع و قسمت کردن شبکه در ساختار شبکه‌های دسترسی باز }
+\title{تخصیص منابع در شبکه‌های دسترسی رادیویی باز با برش‌دهی شبکه }
 % نام استاد(ان) راهنما را وارد کنید
@@
 % تاریخ پایان‌نامه را وارد کنید
-\thesisdate{شهریور ۱۳۹۹}
+\thesisdate{مهر ۱۳۹۹}
 % به صورت پیش‌فرض برای پایان‌نامه‌های کارشناسی تا دکترا به ترتیب از عبارات «پروژه»، «پایان‌نامه» و «رساله» استفاده می‌شود؛ اگر  نمی‌پسندید هر عنوانی را که مایلید در دستور زیر قرار داده و آنرا از حالت توضیح خارج کنید.
@@
 \fa-abstract{
-در این پروپزال، هدف در نظرگیری ساختار رادیویی دسترسی باز در نسل پنجم و تخصیص منابع آن می‌باشد.
-مسئله‌ی برش شبکه در بخش رادیویی و قرارگیری توابع مجازی شبکه برروی مراکز داده باهم در شبکه‌ی دسترسی رادیویی باز مورد بررسی قرار گرفته است.
-بخش رادیویی به صورت کانل مدل سازی شده و تاخیر و نرخ و پارامترهای دیگر بدست می آید.
-در اینچا فرض براین است که کاربران بر اساس سرویس مورد نیاز، دسته بندی می شوند و هدف تخصیص برشهای شبکه به سرویسهاست و سپس تخصیص منابع فیزیکی محاسباتی به این برشهای اختصاص یافته به سرویسها می باشد.
+در این پروپزال، ساختار رادیویی دسترسی باز (ORAN) در نسل پنجم معرفی می‌شود و تخصیص منابع در آن در نظر گرفته می‌شود.
+شبکه دسترسی رادیویی باز از ترکیب C-RAN و xRAN بدست آمده‌است. معماری \lr{ORAN} برای ایجاد زیرساختهای \lr{RAN} نسل بعدی طراحی شده است.
+معماری \lr{ORAN} با تکیه بر اصول هوشمندی و باز بودن، پایه و اساس ساخت \lr{RAN} مجازی بر روی سخت افزار آزاد، با کنترل رادیویی ایجاد شده توسط هوش مصنوعی است که توسط اپراتورهای سراسر جهان پیش بینی شده است.
+\lr{ORAN}،
+المانهای شبکه ی دسترسی رادیویی را مجازی می‌کند، آنها را جدا کرده و رابطهای باز مناسب را 
+برای اتصال این عناصر
+تعیین می‌کند. همچنین، 
+\lr{ORAN}
+از روشهای یادگیری ماشین برای هوشمندسازی لایه‌های 
+\lr{RAN}
+استفاده می‌نماید.
+
+در اینجا، مسئله‌ی برش شبکه در بخش رادیویی و قرارگیری توابع مجازی شبکه برروی مراکز داده باهم در شبکه‌ی دسترسی رادیویی باز مورد بررسی قرار گرفته است. 
+بخش رادیویی
+ مدل سازی شده و تاخیر و نرخ و پارامترهای دیگر بدست می آید. 
+در این شبکه سرویسهای مختلف در نظر گرفته شده که شامل تعدادی کاربر است که تقاضای استفاده از آن سرویس را دارد.
+همچنین تعدادی برش شبکه فرض شده است که شامل منابع فیزیکی، واجد رادیویی و واحد توزیع شده و مرکزی می‌باشد.
+واحد توزیع شده و مرکزی نیز شامل توابع شبکه‌ی مجازی هستند که پردازشها را انجام می‌دهند.
+فرض براین است که کاربران بر اساس سرویس مورد نیاز، دسته بندی می شوند و هدف تخصیص برشهای شبکه به سرویسهاست و سپس تخصیص منابع فیزیکی محاسباتی به این برشهای اختصاص یافته به سرویسها می باشد.
+
 برای حل این مسئله، ابتدا مسئله را به دو مسئله‌ی کوچکتر مختلف شکسته که در بخش اول، تخصیص برش شبکه به کاربران سرویسها و تخصیص توان در ساختار رادیویی باز حل شده و پس از آن، برشهایی از شبکه که به سرویس اختصاص داده شده را به مراکز داده نگاشت می‌دهیم.
 در این مسئله، تاخیر و نرخ هر کاربر در سرویس مورد بررسی قرار گرفته شده و چالش تخصیص منابع که شامل برش بخش رادیویی به هر سرویس است و جاگیری توابع شبکه حل می‌شود.
-الگوریتم بهینه  با استفاده از MOSEK و CVX بدست می‌آید، و الگوریتم استفاده شده در مسئله، روش ابتکاری است. این مسئله به صورت متمرکز حل شده است.
+جواب بهینه باداستفاده از نرم‌افزار MOSEK و CVX در متلب بدست می‌آید.
+همچنین روش ابتکاری، برای حالت متمرکز، در نظر گرفته شده است که مسئله‌ی اول شامل مسئله‌ی بسته‌بندی جعبه و تخصیص توان است که چون یک مسئله‌ی NP-Hard می‌باشد در دو بخش به صورت تکراری برای تخصیص سرویس به برش و بدست آوردن توان حل می‌شود که بخش تخصیص توان به یک مسئله‌ی محدب تبدیل می‌شود و مسئله‌ی دوم نیز یک مسئله‌ی سه بعدی بسته بندی جعبه است که حل دو بخش بسته بندی جعبه، بر اساس مرتب کردن بسته‌ها به ترتیب با استفاده از اندازه‌گیری بر مبنای پارامترهای آن \cite{3dbin}، بدست می‌آید.
 سپس مسئله به صورت ساده‌تر به دو مسئله‌ی بسته‌بندی جعبه و کوله‌پشتی نوشته شده و برای حالت دینامیکی متغیر با زمان با روش یادگیری تقویتی حل می‌شود.

### 2020-10-21 Latex/tehran-thesis - Copy/tex/chapter1.tex
ppt update

@@
 
-کاربر و صفحه ی کنترلگر در چنین شبکه‌هایی از هم مجزا می‌باشند.
-که در این شبکه‌ها، نودهای توان بالا   \LTRfootnote{High Power Node}\lr{HPN}، عمدتا برای فراهم کردن پوشش بدون درز و اجرای عملکرد صفحه کنترل می‌باشد.
+صفحه‌ی کاربر و صفحه ی کنترلگر در چنین شبکه‌هایی از هم مجزا می‌باشند. 
+در این شبکه‌ها، نودهای توان بالا   \LTRfootnote{High Power Node}\lr{HPN}، عمدتا برای فراهم کردن پوشش بدون درز و اجرای عملکرد صفحه کنترل می‌باشد.
 در حالی که \lr{RRH}ها برای فراهم نمودن سرعت بالای نرخ داده برای انتقال بسته در ترافیک قرار گرفته اند.
 \lr{HPN}ها از طریق لینکهای \lr{backhaul}  به \lr{BBU Pool} متصلند ( برای هماهنگ کردن تداخل ).\newline
-ساختار این شبکه شبیه به ساختار \lr{C-RAN} می‌باشد .
+ساختار این شبکه شبیه به ساختار \lr{C-RAN} می‌باشد.
 همانطور که در شکل \eqref{fig:hc} نشان داده شده است، تعداد زیادی \lr{RRH}، همراه با انرژی مصرفی کم در ساختار \lr{H-CRAN}، با یکدیگر در \lr{BBU Pool} مرکزی، همکاری می‌کنند تا گین مشترک بالایی بدست آورند.
@@
 همچنین تنها بخشی از عملکردها در لایه ی \lr{PHY} در \lr{RRH} به مشارکت می‌انجامد که این مدل در شکل \eqref{fig:hc} نشان داده شده است.\newline
-اگرچه، برخلاف \lr{C-RAN}،\lr{BBU Pool} در \lr{H-CRAN}، به \lr{HPN}ها متصلند که این، برای کاهش تداخل متقابل بین \lr{RRH}ها و \lr{HPN}ها از طریق محاسبات ابری متمرکز براساس تکنیکهای پردازشی مشترک می‌باشد.
+اگرچه، برخلاف \lr{C-RAN}،
+\lr{BBU Pool} در \lr{H-CRAN}، به \lr{HPN}ها متصلند که این، برای کاهش تداخل متقابل بین \lr{RRH}ها و \lr{HPN}ها از طریق محاسبات ابری متمرکز براساس تکنیکهای پردازشی مشترک می‌باشد.
 همچنین، داده و واسط کنترل، بین \lr{BBU Pool} و \lr{HPN}های $S_1$ و $X_2$ شناخته شده اند که تعریف آنها بر اساس تعریف استاندارد \lr{3G} ایجاد شده است.\newline

### 2020-10-23 Latex/tehran-thesis - Copy/tex/chapter1.tex
ppt update

@@
 
-برای حل کردن مشکلات \lr{H-CRAN} و \lr{C-RAN}، نیاز به معرفی ساختار جدید دیگری میباشیم که آن را \lr{F-RAN} می‌نامیم.
-\lr{F-RAN} تمام ویژگیهای مثبت محاسبات ابری و شبکه‌های نامتجانس و محاسبات مهی را همزمان در بر می‌گیرد.
+برای حل کردن مشکلات \lr{H-CRAN} و \lr{C-RAN}، نیاز به معرفی ساختار جدید دیگری می‌باشیم که آن را \lr{F-RAN} می‌نامیم.
+\lr{F-RAN} 
+تمام ویژگیهای مثبت محاسبات ابری و شبکه‌های نامتجانس و محاسبات مهی را همزمان در بر می‌گیرد.
 محاسبات مهی، اصطلاحی برای جایگزین کردن محاسبات ابری است که مقدار قابل توجهی از ذخیره سازی، ارتباطات، کنترل کردن، اندازه گیری و مدیریت را در لبه ی شبکه انجام می‌دهد (نه در کانال و ابر مرکزی) \cite{fogComputing, fogEdge}.
- سیستمهای \lr{F-RAN} تحولی از سیستمهای \lr{C-RAN} می‌باشد . برخی از ارتباطات توزیع شده و عملکردهای ذخیره سازی در منطق لایه ی مه قرار دارد. همچنین چهار نوع ارتباطات ابری تعریف شده است.
+ سیستمهای \lr{F-RAN} تحولی از سیستمهای \lr{C-RAN} می‌باشد که برخی از ارتباطات توزیع شده و عملکردهای ذخیره سازی در منطق لایه ی مه قرار دارد. همچنین چهار نوع ارتباطات ابری تعریف شده است.
   \begin{figure}[H]
@@
  \end{itemize}
- در این ساختار، برای کاهش تاخیر ناشی از انتقال داده‌ها به ابر مرکزی، ساختارهای \lr{RRH} را دارای حافظه قرار میدهیم که برای ارتباطات محلی، به جای اینکه پردازشها در \lr{BBU Pool} صورت بگیرد، بدون نیاز به انتقال به ابر مرکزی، درون \lr{RRH}ها انجام پذیرد.
+ در این ساختار، برای کاهش تاخیر ناشی از انتقال داده‌ها به ابر مرکزی، ساختارهای \lr{RRH} را دارای حافظه قرار می‌دهیم که برای ارتباطات محلی، به جای اینکه پردازشها در \lr{BBU Pool} صورت بگیرد، بدون نیاز به انتقال به ابر مرکزی، درون \lr{RRH}ها انجام پذیرد.
 \end{itemize}
@@
 \item \textbf{انتشار رابطهای باز شمال و جنوب}: 
-رابطهای استاندارد و باز قابیت پشتیبانی از فروشنده‌های متعدد همکاری اثبات شده دارند. 
+رابطهای استاندارد و باز قابلیت پشتیبانی از فروشنده‌های متعدد همکاری اثبات شده دارند. 
 \lr{xRAN.org}
@@
 \subsection{vRAN}
-vRAN یا شبکه‌های دسترسی رادیویی مجازی
+vRAN 
+یا شبکه‌های دسترسی رادیویی مجازی
 گونه‌ی دیگری از شبکه‌های رادیویی دسترسی می‌باشند که منجر به افزایش هوشمندانه ظرفیت، کاهش چشمگیر هزینه‌ها می‌شود.
 همچنین قابلیت انعطاف پذیری و مقیاس پذیری پویا را فراهم می‌کند که برای پشتیبانی از خدمات و برنامه‌های آینده ضروری خواهد بود.
-معماری vRAN با اجرای توابع باند پایه مجازی بر روی سخت افزار سرور کالا، بر اساس اصول مجازی سازی توابع شبکه (NFV)، فراتر از آخرین شبکه‌ی  متمرکز رادیویی (C-RAN)است.
-معماری C-RAN می‌تواند با ایجاد امکان تجمع منابع پردازش باند پایه، که می‌تواند به صورت پویا به سایتهای مختلف سلول و فن‌آوریهای رادیویی اختصاص یابد، گامیفراتر رود.
+معماری vRAN با اجرای توابع باند پایه مجازی بر روی سخت افزار سرور کالا، بر اساس اصول مجازی سازی توابع شبکه (NFV)، فراتر از آخرین شبکه‌ی  متمرکز رادیویی (C-RAN) است.
+معماری C-RAN می‌تواند با ایجاد امکان تجمع منابع پردازش باند پایه، که می‌تواند به صورت پویا به سایتهای مختلف سلول و فن‌آوریهای رادیویی اختصاص یابد، گامی فراتر رود.
 به اشتراک گذاری منابع باند پایه از طیف موجود با کارآیی بیشتری استفاده می‌کند و قابلیت اطمینان سرویس را بهبود می‌بخشد.
@@
 vBBU
-که همان واحدهای باند پایه‌ی مجازی هستند، در چندین سیستم عامل NFV در سخت افزار استاندارد x86 مستقر شده و در مراکز داده متمرکز تلفیق می‌شوند، در حالی که واخدهای رادیویی از راه دور (RRH) در سایتهای سلول در لبه باقی می‌مانند.
+که همان واحدهای باند پایه‌ی مجازی هستند، در چندین سیستم عامل NFV در سخت افزار استاندارد x86 مستقر شده و در مراکز داده متمرکز تلفیق می‌شوند، در حالی که واحدهای رادیویی از راه دور (RRH) در سایتهای سلول در لبه باقی می‌مانند.
 vRAN 
@@
 اتحاد \lr{ORAN} در جستجوی چشم انداز باز بودن و هوشمندی برای شبکه‌های بی سیم نسل بعدی و فراتر از آن است\cite{oranWP}.
+این دو ویژگی مهم در ادامه مورد بررسی قرار گرفته شده است.
 \begin{itemize}
@@
  همراه با رابطهای باز \lr{ORAN}، اتوماسیون حلقه بسته بهینه شده با هوش مصنوعی دست یافتنی است و دوره جدیدی را برای عملیات شبکه امکان پذیر می‌کند.
+\end{itemize}
+در ادامه ویژگی های این ساختار را بررسی می‌نماییم.
+\begin{itemize}
 \item \textbf{روشهای هوش مصنوعی \lr{AI}
@@
 NFVI شامل اتصال شبکه بین مکانها، به عنوان مثال، بین
-مراکز داده و ابرهای ترکیبی عمومییا خصوصی است.
+مراکز داده و ابرهای ترکیبی عمومی یا خصوصی است.
 منابع فیزیکی به طور معمول شامل محاسبات، ذخیره سازی و سخت افزار شبکه است که وظیفه ی آن پردازش، ذخیره سازی و اتصال VNFها از طریق لایه مجازی سازی است و دقیقاً بالای سخت افزار قرار دارد و منابع فیزیکی را چکیده می‌کند (که به صورت منطقی تقسیم شده و به VNFها اختصاص می‌یابد).
@@
 یک صفحه‌ی کنترل متمرکز نرم‌افزار تعریف شده است برای بخش شبکه دسترسی رادیویی که ایستگاه‌های پایه را در یک مکان جغرافیایی داخلی، به عنوان یک ایستگاه پایه‌ی بزرگ مجازی با المانهای کنترلی مرکزی و رادیویی می‌باشد.
-در این حالت، مقهوم SDRAN به مفهوم vRAN بسیار نزدیک است.
+در این حالت، مفهوم SDRAN به مفهوم vRAN بسیار نزدیک است.
 SDRAN
@@
 در تعریف چنین معماری، ما چارچوبی ایجاد می‌کنیم که از طریق آن یک شبکه جغرافیایی محلی می‌تواند به طور موثر توازن بار و مدیریت تداخل را انجام دهد و همچنین نرخ عملیاتی و یا هر هدف دیگر را به بهینه‌ترین مقدار خود برساند.
-ما معتقدیم که طراحی تعریف شده توسط نرم افزار در RAN یک گام اساسی برای پشتیبانی از برش شبکه ، به اشتراک گذاری RAN ، مدیریت طیف انعطاف پذیر و سایر ویژگی های اصلی در شبکه های 5G خواهد بود.
+ما معتقدیم که طراحی تعریف شده توسط نرم افزار در RAN یک گام اساسی برای پشتیبانی از برش شبکه، به اشتراک گذاری RAN، مدیریت طیف انعطاف پذیر و سایر ویژگی های اصلی در شبکه های 5G خواهد بود.
 امید بر این است که طراحی تعریف شده توسط نرم افزار در RAN 

### 2020-10-23 Latex/tehran-thesis - Copy/tex/chapter2.tex
ppt update

@@
 در آنها ترکیبی از مفهوم برش RAN و Core به چشم می‌خورد.
-\subsection{رفتن به سمت شبکه های دسترسی رادیویی باز}
-در فوریه 2018 ، شبکه دسترسی رادیویی آزاد (O-RAN) با ادغام  xRAN و اتحاد C-RAN برای ایجاد سطح جدیدی از باز بودن در شبکه دسترسی رادیویی ایجاد شد که از نسل 5G و 6G پشتیبانی می‌کند.
-هدف اصلی O-RAN افزایش عملکرد RAN از طریق عناصر شبکه مجازی و واسط های باز است که دارای هوش در RAN است.
-صراحت و هوش دو ستون اصلی تلاشهای انجام شده توسط اتحاد O-RAN است که یک نیروی جهانی متشکل از بیش از 160 شرکت کننده از فروشندگان بزرگ ، شرکت های کوچک و متوسط ، اپراتورهای شبکه ، مبتدیان و مؤسسات دانشگاهی است
+\subsection{ شبکه های دسترسی رادیویی باز}
+در فوریه 2018 ، شبکه دسترسی رادیویی آزاد (ORAN) با ادغام  xRAN و اتحاد C-RAN برای ایجاد سطح جدیدی از باز بودن در شبکه دسترسی رادیویی ایجاد شد که از نسل 5G و 6G پشتیبانی می‌کند.
+هدف اصلی ORAN افزایش عملکرد RAN از طریق عناصر شبکه مجازی و واسط های باز است که دارای هوش در RAN است.
+صراحت و هوش دو ستون اصلی تلاشهای انجام شده توسط اتحاد ORAN است که یک نیروی جهانی متشکل از بیش از 160 شرکت کننده از فروشندگان بزرگ ، شرکت های کوچک و متوسط ، اپراتورهای شبکه ، مبتدیان و مؤسسات دانشگاهی است
 \cite{oranpaper}
@@
 \cite{oranInt}
- مقدمه ای در مورد مفاهیم، اصول و الزامات \lr{Open RAN} که توسط اتحاد O-RAN مشخص شده، بیان شده‌است.
+ مقدمه ای در مورد مفاهیم، اصول و الزامات \lr{Open RAN} که توسط اتحاد ORAN مشخص شده، بیان شده‌است.
  در این مقاله،
- به منظور نشان دادن نقش هوش در O-RAN، طرح مدیریت منابع رادیویی هوشمندی را برای رسیدگی به ازدحام ترافیک و نشان دادن اثربخشی آن در یک مجموعه داده در دنیای واقعی پیشنهاد شده‌است.
- یک معماری سطح بالا از این سناریوی استقرار که سازگار با الزامات O-RAN است نیز مورد بحث قرار گرفته است. مقاله با چالشهای کلیدی فنی و مشکلات باز برای تحقیقات و توسعه آینده به پایان میرسد.
+ به منظور نشان دادن نقش هوش در ORAN، طرح مدیریت منابع رادیویی هوشمندی را برای رسیدگی به ازدحام ترافیک و نشان دادن اثربخشی آن در یک مجموعه داده در دنیای واقعی پیشنهاد شده‌است.
+ یک معماری سطح بالا از این سناریوی استقرار که سازگار با الزامات ORAN است نیز مورد بحث قرار گرفته است. مقاله با چالشهای کلیدی فنی و مشکلات باز برای تحقیقات و توسعه آینده به پایان میرسد.
 
@@
 ساختار RLM در 
-زیرساخت O-RAN مورد بررسی قرار گرفته است.
+زیرساخت ORAN مورد بررسی قرار گرفته است.
 علاوه بر این، دیدگاه

### 2020-10-23 NetworkSlicing/report123/report1.tex
ppt update

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{NetworkSlicing}
\author{Mojdeh Karbalaee}
\date{May 2020}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\setlength{\columnsep}{11mm}
\begin{document}

\maketitle

\section{Network Slicing}
Network slicing, where several logical
networks share a single physical network, has been considered as one of
the key enablers for 5G.

Network slicing is a promising technology for
5G to provide a network as a service (NaaS) for a wide range of
services that run on different virtual networks deployed on a
shared network infrastructure. 
\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{Capture1.PNG}
\caption{ Big data driven networking}
\label{fig:Bigdata}
\end{figure}
A critical component of network slicing is resource allocation, which needs
to ensure that slices receive the resources needed to support their mobiles/services while optimizing network efficiency.

In a sliced network, network operators
realize the network slices instances to provide the required
network characteristics to different services, pertaining to
third-party tenants.
 Therefore, there will be Service Level
Agreements (SLAs) between network operator and the tenants
to declare the requirements of a particular service and the
operator should fulfill these SLAs via instantiating appropriate
network slices. Requirements of the service instances are
specified in terms of Key Performance Indicators (KPIs), such
as throughput, latency, availability, coverage, etc.

An important aspect of network slicing is to guarantee that
the slices operate independently, i.e., the performance, congestion, failure, etc., in one slice will not negatively influence the
performance of other slices which are sharing the resources.
This means that providing protection from other slices is one
To enable Internet of things (IoT) including high data rate, numerous devices
connection and low service latency,
network slicing and fog computing have been envisioned as
promising solutions in service-oriented 5G architecture.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.5]{Capture.PNG}
\caption{ Service-oriented Architecture of Fog-assisted 5G Network with Network Slicing}
\label{fig:FogNS}
\end{figure}
\section{System Model}
Assume a system model with different types of user equipment (UE).
There exists two different types of
UEs with different requirements: low-latency users (LUs) and
high-data rate Tactile users (TUs).

The first group is very sensitive to the latency. The second group needs high data rate.
Each slice sustains a queue
for the incoming slice traffic, which has a backlog.
%The arrival traffic per slot can be modeled.
The network model is assumed to be composed of a set of M
base stations (BSs).
We have three types of slice resource requirements.
\begin{itemize}
\item A fixed slice requests dedicated radio resources along
time and frequency domains. Therefore, it is isolated
from other slices and does not multiplex its resources
with others. One example is the bandwidth parts (BWPs)
defined in 5G (see 3GPP TS 38.211) that operate on
disjoint parts of the spectrum with a given numerology.
\item A dynamic slice requests a share of resources in terms
of aggregate throughput. It can be mapped to the eMBB
usage scenario, and thus a precise radio resource allocation is less important than the efficient use of available
resources for a guaranteed throughput.
\item An on-demand slice exhibits more stringent requirements
in terms of latency, and hence it can be mapped to
the URLLC scenario. Therefore, such slice should be
assigned radio resources with short delay, in comparison
with the dynamic slice.\citep{schmidt2019slice}
\end{itemize}
\section{introduction}
Network slicing is an important network architecture innovation in 5G that is also expected to be inherited in the next generation. Network slicing enables the coexistence of
multiple isolated and independent virtual (logical) networks,
i.e., slices, on the same physical network infrastructure. The
advantages of network slicing are multifold. First, through the
multiplexing of the virtual networks, network slicing supports
multi-tenancy, i.e., multiple virtual network operators (VNOs)
sharing the same physical network infrastructure. This
reduces capital expense in network deployment and operation. Second, network slicing provides the potential to create customized slices for different service types with various
QoS requirements, which can achieve service differentiation
and guarantee service level agreement (SLA) for each service
type. Third, as slices can be created on-demand and modified
or annulled as needed, network slicing increases the flexibility
and adaptability in network management.

A network slice is a virtual network which is implemented on top
of a physical network in a way that creates the illusion to the
slice tenant of operating its own dedicated physical network.
Network Slicing offers a number of significant advantages
that are particularly useful in the design of next generation
wireless networks, namely:
\begin{itemize}
\item  Slice isolation: The complete isolation of slices allows
for a simpler and more efficient design of each slice with
the goal of meeting the requirements of the particular
vertical applications and services offered by the slice
tenant. In addition, network failure, overload, or security
attacks in one slice will not affect the operation of other
slices in the network.
\item Simplified service chains: In contrast to traditional cellular communications in which all services consist of the
same functions, in Network Slicing each service may rely
on a different subset of functions.
\item Flexible VNF placement: NFV introduces an additional
degree of freedom regarding the placement of these functions on the network. Intelligent placement may improve
network performance and reduce operating costs.
\item Transparent slice management: Subsets of the physical
network resources might belong to different network
domains (or even operators). Network Slicing provides
an abstraction of the physical resources and makes slice
management transparent to the slice tenant
\end{itemize}
We have core and ran slicing in Network Slicing architecture.
RAN slicing faces the following unique challenges: 
\begin{itemize}
\item 
Resource interplay – Since a service may consume multiple network resources, there exists an inherent tradeoff
among the network resources. For example, in computing offloading services, the service latency consists of
two elements: task transmission latency and task processing latency. If a user associates with a remote MEC
server having abundant computing resources for task
processing, a high task transmission latency will incur.
On the other hand, if a user associates with a nearby
MEC server having insufficient computing resources, it
takes a longer time for task processing. In such a manner, the allocation of computing and communication resources is coupled with each other in the exemplary computing offloading services. Similarly, the allocation of
multiple network resources is intertwined, which complicates the RAN slicing. A joint multiple network resource allocation scheme should be judiciously designed
to maximize network welfare; 
\item  Strict QoS requirements – Compared with traditional 4G
networks, 5G networks and beyond have stricter QoS
requirements, including a higher throughput and a lower
latency. Especially, the typical URLLC service in 5G
requires ultra-high reliability (e.g., 99.999%), which is
much stricter than that of other services. In addition, the
payload of data packets in URLLC services is usually
small, such as 32 bytes. The transmission performance of short-length packets cannot be characterized
by the traditional Shannon theory which is suitable for
long-length packet transmission due to a large transmission overhead. Instead, the finite block length channel coding theory should be applied to characterize the
achievable rate for short-length packets. Traditional
QoS provisioning is unsuitable for short-length packet
URLLC services with ultra-high reliability. Thus, an accurate QoS provisioning for URLLC services is desired
in the RAN slicing framework; 
\item  User mobility – Due to the high network density, users
may frequently move out the coverage of its associated network infrastructure, which results in a dynamic
network topology. For example, high-mobility vehicle
users can trigger handover frequently. The dynamic network topology changes the service traffic distribution,
rendering previously optimal slice allocation suboptimal
over time, degrading network performance, and may
even violate users’ QoS requirements. When the network
performance degrades to a threshold, adjusting existing
slices or creating new slices will be triggered, which
incurs slice reconfiguration overhead. Thus, dynamic yet
efficient RAN slicing to accommodate user mobility remains a challenging issue.\cite{aiNS}
\end{itemize}
\section{system model and main problem}
In the network slicing architecture, each service is admitted by specific slice. Also each service has a special Qos \footnote{Quality of Service} that must be reached. 
Qos includes 
\begin{itemize}
\item delay
\item throughput
\item packetloss
\item out of order delivery
\end{itemize}  
Different services have one or more of these QoS.
AI-based methods become promising techniques to provide
potential benefits to address the difficulties and complexities of slicing.
We can use AI-based methods
to provide \textbf{accurate service-specific traffic prediction}.
Only
with such accurately predicted service-specific traffic, RAN
slicing can effectively facilitate network resource allocation to
accommodate service demands in the near future. Recent studies show that AI-based methods, such as deep neural network
(DNN) and long short-term memory (LSTM), are capable of
accurately forecasting service-specific traffic load.
AI-based methods can facilitate efficient resource allocation in RAN slicing. An online AI-based resource allocation decision process has the potential to achieve
a low complexity after an offline training procedure, which
addresses the high computational complexity challenge in the
conventional model-based optimization methods.
 Note that traditional RL methods, such as
Q-learning, suffer from the curse of dimensionality, which are
only suitable for RAN slicing problems in small-scale networks. Deep RL methods incorporate deep learning networks
in the RL framework can effectively address the complexity
issues in large-scale networks. 
Cooperative Game with Distributed Learning
While existing applications of distributed learning in this field generally consider non-cooperative games where the Nash
equilibriums are achieved, there is a great potential to adopt the concept of cooperative game, where tenants/slices can learn to
make decisions in an organized and cooperative way, in order to maximize the global social welfare instead of their own interests.
In this way, a Pareto optimum can be expected instead of the Nash equilibrium.
\subsection{system model}
In this part, deep reinforcement learning (DRL), which focuses on how to interact with the environment by
trying alternative actions and reinforcing the tendency actions producing more rewarding consequences,
is assumed to be a promising solution for network slicing \cite{drl}.
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{drl}
  \caption{Deep Q learning structure}
  \label{fig:drl}
\end{figure}
Assume we have $V$ services and $S$ slices. Each service needs physical resource blocks (sharing the aggregated bandwidth $W$), RRHs (radio unit head) and CU (control unit) in RAN and VNFs in core (set of requirements $\mathbf{q} = \{q_1, ..., q_{n_v}\}$) and requests specific QoS includes delay, throughput, packetloss, ... . 
So each service $v$ needs specific demands $\mathbf{d} = \{d_1, ..., d_{n_v}\}$.
The target is to maximize long-term reward expectation $E\{R(\mathbf{q},\mathbf{d})\}$
\begin{subequations}
\begin{alignat}{4}
\text{argmax}_{\mathbf{q}} E\{R(\mathbf{q},\mathbf{d})\} \\
\text{subject to} \quad  & \mathbf{q} , \mathbf{d}  
\end{alignat}
\label{constraints1}
\end{subequations}
Set of QoSes $\mathbf{d} = \{d_1, ..., d_{n_v}\}$ includes M/M/1 delays, throughput and packetloss.
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{NS}
  \caption{Network slicing structure \cite{gan}}
  \label{fig:NS}
\end{figure}
\subsubsection{Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_v$ for the  UEs of the $v^{th}$ service.
Therefore, the mean arrival data rate of UEs is
\begin{equation}
D_{v} = \frac{1}{\mu - \lambda_v}.
\end{equation}
where $1/\mu$ is the mean service time and $\lambda$ is the rate of arrival packets.
\subsubsection{Throughput}
Let $\rho_v$ be the mean downlink rate of user $i$ served by service $v$, which
is, for simplicity, defined by Shannon theory as follows
\begin{equation}
\rho_v = w_v log(1+\frac{P_v}{N_v}) 
\end{equation}
where $w_v$ is the bandwidth of service $v$.
\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2020-10-24 Latex/tehran-thesis - Copy/tex/chapter4.tex
finish proposal

@@
 در بخش اول صورت مسئله‌ی بخش رادیویی نوشته می‌شود. سپس  به مدل سیستم بخش هسته می‌پردازیم و در نهایت روش حل هر دو مسئله و نتایج عددی آن بیان می‌شود.
-\section{ مدل سیستم و صورت مسئله‌ی اول}
+\section{ مدل سیستم و صورت مسئله‌ی بخش رادیویی}
 در این بخش هدف برش شبکه در بخش رادیویی می‌باشد. دراینجا، مسئله‌ی اول فصل قبلی ساده شده و به روش دینامیکی حل می‌شود.   
@@
 همچنین در صورت در نظر گرفتن تاخیر در شبکه، هر برش شبکه تنها به یک سرویس اختصاص داده می‌شود.
-\section{ مدل سیستم و صورت مسئله‌ی دوم}
-در این بخش سعی شده، مسئله‌ی دوم فصل قبل به صورت ساده شده با روش دینامیکی حل شود. عنوان این مسئله، جاگذاری VNFها برروی مراکز داده می‌باشد.
-فرض براین است که $S$ برش شبکه داریم که هر برش شبکه
+\section{ مدل سیستم و صورت مسئله‌ی بخش هسته}
+در این بخش سعی شده، مسئله‌ی دوم فصل قبل به صورت ساده شده با روش دینامیکی حل شود. عنوان این مسئله، جاگذاری VNF ها برروی مراکز داده می‌باشد.
+فرض براین است که $S$ برش شبکه داریم که
 $s\in \{1,2,...,S \} $
@@
 %همچنین مقدار کل حافظه، نگهدارنده و پردازشگر برای همه \lr{VNF} ها در یک برش به این صورت تعریف می شود
-\begin{equation}
-	\textstyle \bar{\Omega}_{s}^{tot} = \sum_{f=1}^{M_{s}}\bar{\Omega}_{s}^f %\;\; \mathfrak{z} \in \{M, S, C\}.
-\end{equation}
-همچنین $D_c$ مرکز داده برای سرویس دهی به \lr{VNF} ها می باشد. هر مرکز داده شامل تعدادی سرور برای سرویس دهی است.
 $M_s$ 
@@
 ها در $s$امین برش شبکه است.
+\begin{equation}
+	\textstyle \bar{\Omega}_{s}^{tot} = \sum_{f=1}^{M_{s}}\bar{\Omega}_{s}^f %\;\; \mathfrak{z} \in \{M, S, C\}.
+\end{equation}
+که دراینجا $ 	\textstyle \bar{\Omega}_{s}^{tot}$
+مقدار کل پردازشگرهای برش $s$ می‌باشد.
+همچنین $D_c$ مرکز داده برای سرویس دهی به \lr{VNF} ها می باشد. هر مرکز داده شامل تعدادی سرور برای سرویس دهی است. همچنین فرض براین است که هر مرکز داده، دارای پردازشگر $\tau$ می‌باشد. در این صورت
 مقدار پردازشگر 
@@
 تخصیص منابع فیزیکی به \lr{VNF} ها در نظر گرفته شده است. 
-در اینجا فرض بر این است که $y_{s,d}$ متغیر صفر و یکی است که نشان میدهد مرکز داده ی $d$ ام به $s$ امین برش متصل است یا نه. 
+در اینجا فرض بر این است که $y_{s,d}$ متغیر صفر و یکی است که نشان میدهد مرکز داده ی $d$ ام به $s$ امین برش سرویس دهی می‌کند یا نه. 
 همانند فصل قبل، 
@@
 	\begin{alignat}{4}
-		\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})(t)\\
+		\min\limits_{\boldsymbol{Y} }   \quad &   \psi_{tot}(\boldsymbol{Y})(t)\\
 		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c} y_{s,d}(t) \geq 1 \quad \forall s, \\
@@
 \end{subequations}
-این مسئله به فرم مسئله‌ی بسته‌بندی جعبه قابل بیان است.
+این مسئله به فرم مسئله‌ی بسته‌بندی جعبه قابل بیان است. در اینحا، 
+$\tau_{d}$
+مقدار پردازنده‌ی $d$ امین مرکز داده می‌باشد.
 \section{حل مسئله به‌روش یادگیری تقویتی}
@@
   $\mathbb{E}$
-  میانگین می‌گیرد.
+  نمادی برای نشان دادن میانگین است.
   باتوجه به رابطه‌ی بلمن، داریم:
@@
 هستند.
-هدف یادگیری تقویتی، بدست‌آوردن سیاست بهیته می‌باشد به صورتی که 
+هدف یادگیری تقویتی، بدست‌آوردن سیاست بهینه می‌باشد به صورتی که 
 $Q^{\Pi}(s,a)$
@@
 \end{equation}
-روشهای مخنلفی برای دستیابی به مینیمم خطا هست که ما در ادامه‌ی کار از روش Q-learnng استفاده می‌کنیم.
+روشهای مختلفی برای دستیابی به مینیمم خطا هست که ما در ادامه‌ی کار از روش Q-learning استفاده می‌کنیم.
 در روش Q-learning در هر بروزرسانی تابع Q داریم:
@@
 در این بخش، به دلیل کم بودن تعداد حالتها، از روش Q-Learning استفاده کرده و برای جدول Q نیاز به استفاده از روش یادگیری عمیق نیست.
-در مدل اول سرویس نیازمند نرخ $10MHz$ و مدل دوم سرویس نیازمند نرخ $20MHz$
+در مدل اول سرویس نیازمند نرخ $10bits/s$ و مدل دوم سرویس نیازمند نرخ $20bits/s$
 می‌باشد.
@@
 در اینجا فرض می کنیم از  سرویس اول ماکسیمم در هر لحظه 6 سرویس و از سرویس دوم 3 تا سرویس درخواست می‌دهد.
-2 برش شبکه با نرخ $40MHz$ نیز وجود دارد.
+2 برش شبکه با نرخ $40bits/s$ نیز وجود دارد.
+
 در شکل \ref{fig:dynamicEpoch}
@@
 در اینجا، تعداد درخواستهای سرویس اول 10 تا و سرویس دوم 5 تا می‌باشد.
-همچنین نرخ خروج نرخ  در هر بازه‌ی زمانی $80$ درصد فرض شده است.% در اینجا هر سناریو 100 بار تکرار شده و میانگین گیری برروی آن انجام گردیده است.
+همچنین میزان خروج در هر بازه‌ی زمانی $80$ درصد سرویسهایی است که در حال پردازش هستند.
+% در اینجا هر سناریو 100 بار تکرار شده و میانگین گیری برروی آن انجام گردیده است.
 \begin{figure}%[H]
@@
 	\centering
-	\includegraphics[scale = 0.6]{./fig/admittedService1} %[width=\linewidth] 
+	\includegraphics[scale = 0.6]{./fig/admittedService11} %[width=\linewidth] 
 	\caption{  
@@
 همانطور که دیده می‌شود بعد از 900
-تا تکرار، تقریبا به مقدار بهینه با نسبت $0.9$ نزدیک شده‌ایم.
+تا تکرار، تقریبا به مقدار بهینه نزدیک شده‌ایم.
 بعد از 900 تا تکرار سناریو، تقریبا میزان انتخاب عمل رندم به صفر رسیده و عمل بهینه از روی جدول Q بدست می‌آید.
 %در اینجا هر سناریو 100 بار تکرار شده و میانگین گیری برروی آن انجام گردیده است. 
-نرخ خروج در هر بازه‌ی زمانی $80$ درصد فرض شده است.
+میزان خروج در هر بازه‌ی زمانی $80$ درصد مقدار سرویسهایی است که در زمان قبل در سیستم حضور داشتند، فرض شده است.
 \begin{figure}%[H]

### 2020-10-24 Latex/tehran-thesis - Copy/tex/faTitle.tex
ppt update
finish proposal

@@
 % گرایش خود را وارد کنید
-\field{مخابرات شبکه}
+\field{مخابرات سیستم}
 % عنوان پایان‌نامه را وارد کنید
@@
 در این مسئله، تاخیر و نرخ هر کاربر در سرویس مورد بررسی قرار گرفته شده و چالش تخصیص منابع که شامل برش بخش رادیویی به هر سرویس است و جاگیری توابع شبکه حل می‌شود.
-جواب بهینه باداستفاده از نرم‌افزار MOSEK و CVX در متلب بدست می‌آید.
-همچنین روش ابتکاری، برای حالت متمرکز، در نظر گرفته شده است که مسئله‌ی اول شامل مسئله‌ی بسته‌بندی جعبه و تخصیص توان است که چون یک مسئله‌ی NP-Hard می‌باشد در دو بخش به صورت تکراری برای تخصیص سرویس به برش و بدست آوردن توان حل می‌شود که بخش تخصیص توان به یک مسئله‌ی محدب تبدیل می‌شود و مسئله‌ی دوم نیز یک مسئله‌ی سه بعدی بسته بندی جعبه است که حل دو بخش بسته بندی جعبه، بر اساس مرتب کردن بسته‌ها به ترتیب با استفاده از اندازه‌گیری بر مبنای پارامترهای آن \cite{3dbin}، بدست می‌آید.
+جواب بهینه با استفاده از نرم‌افزار MOSEK و CVX در MATLAB بدست می‌آید.
+همچنین روش ابتکاری، برای حالت متمرکز، در نظر گرفته شده است که مسئله‌ی اول شامل مسئله‌ی بسته‌بندی جعبه و تخصیص توان است که چون یک مسئله‌ی NP-Hard می‌باشد در دو بخش به صورت تکراری برای تخصیص سرویس به برش و بدست آوردن توان حل می‌شود که بخش تخصیص توان به یک مسئله‌ی محدب تبدیل می‌شود و مسئله‌ی دوم نیز یک مسئله‌ی سه بعدی بسته بندی جعبه است که حل دو بخش بسته بندی جعبه، بر اساس مرتب کردن بسته‌ها به ترتیب با استفاده از اندازه‌گیری بر مبنای پارامترهای آن، بدست می‌آید.
 سپس مسئله به صورت ساده‌تر به دو مسئله‌ی بسته‌بندی جعبه و کوله‌پشتی نوشته شده و برای حالت دینامیکی متغیر با زمان با روش یادگیری تقویتی حل می‌شود.

### 2020-10-26 Latex/tehran-thesis - Copy/tex/chapter3.tex
add file
slide finish

@@
 \lr{VNF}
-دپر لایه ی \lr{CU} می‌باشد.
+در لایه ی \lr{CU} می‌باشد.
 \lr{VNF}
@@
  I_{u_{(v,i)}} &=
- \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{v,s}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
-&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
-&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}},
+ \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{v,s}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{\lr{(intra-service interference)}}}\\
+&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{\lr{(inter-service interference)}}}\\
+&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{\lr{(quantization noise interference)}}},
 \end{split}
@@
 فرض کنید $\bar{p}_{r_{(s,j)}}$
-نشان دهنده ی سیگنال ارسالی از $j$ امین واحد رادیویی در $s$ امین برش می‌باشد.
+نشان دهنده‌ی توان سیگنال ارسالی از $j$ امین واحد رادیویی در $s$ امین برش می‌باشد.
 از رابطه ی \eqref{eq3} داریم
@@
 نشان داده شده است.
-بنابراین می‌توان توان کل سیستم را برای کلیه مرکز داده های فعال که به برش متصل هستند ،بدین صورت نشان داد
+بنابراین می‌توان توان کل سیستم را برای کلیه مرکز داده های فعال که به برش شبکه سرویس دهی می‌کنند، بدین صورت نشان داد
 \begin{equation*}
@@
 \end{equation*}
-همچنین ، یک تابع هزینه برای قرار دادن \lr{VNF} ها در مرکز داده ها بدین عنوان تعریف شده است
+همچنین ، یک تابع هزینه برای سرویس دهی\lr{VNF} ها توسط مرکز داده ها بدین عنوان تعریف شده است
 \begin{equation}\label{eqpsi}

### 2020-10-27 Latex/tehran-thesis - Copy/tex/chapter1.tex
revise proposal

@@
 
-برای غلبه بر چالشهای شبکه‌های \lr{C-RAN} با محدودیتهای \lr{fronthaul}، شبکه‌های دسترسی ابری نامتحانس (\lr{H-CRAN}) معرفی می‌شود\cite{ fogComputing, heterogeneous, fogEdge}.
+برای غلبه بر چالشهای شبکه‌های \lr{C-RAN} با محدودیتهای \lr{fronthaul}، شبکه‌های دسترسی ابری نامتجانس (\lr{H-CRAN}) معرفی می‌شود\cite{ fogComputing, heterogeneous, fogEdge}.
 \begin{figure}
@@
 \item \textbf{ساختن یک پشته نرم‌افزاری \lr{eNodeB} مدولار}:
-رویکرد \lr{xRAN} به خوبی با طرحهای مجازی سازی عملکرد شبکه حامل \lr{(NFV)} مطابقت دارد، و همچنین منجر به کنترل عملکرد ترافیک با کارایی بالا، مدیریت تداخل و کنترل منابع رادیویی روی سیستم عاملهای استاندارد \lr{x86} و می‌شود.
+رویکرد \lr{xRAN} به خوبی با طرحهای مجازی سازی عملکرد شبکه حامل \lr{(NFV)} مطابقت دارد، و همچنین منجر به کنترل عملکرد ترافیک با کارایی بالا، مدیریت تداخل و کنترل منابع رادیویی روی سیستم عاملهای استاندارد \lr{x86} می‌شود.
 \item \textbf{انتشار رابطهای باز شمال و جنوب}: 
@@
     به این ترتیب، یک سرویس خاص میتواند به مجموعه ای از توابع شبکه مجازی (VNFs) تجزیه شود، که میتواند در نرم‌افزارهایی که روی یک یا چند سرور فیزیکی استاندارد در صنعت قرار دارند، اجرا شود.
-    سپس VNFها ممکن است در مکانهای مختلف شبکه (به عنوان مثال، با هدف معرفی خدمات هدفمند به مشتریان در یک موقعیت جغرافیایی خاص) جابجا شده و خدمات رسانی کنند، بدون اینکه لزوماً به خرید و نصب سخت افزار جدید نیاز داشته باشند.
+    سپس VNF ها ممکن است در مکانهای مختلف شبکه (به عنوان مثال، با هدف معرفی خدمات هدفمند به مشتریان در یک موقعیت جغرافیایی خاص) جابجا شده و خدمات رسانی کنند، بدون اینکه لزوماً به خرید و نصب سخت افزار جدید نیاز داشته باشند.
     NFV به 
-    هاSP
+    ها SP 
    با انعطاف پذیری بیشتری وعده می‌دهد تا بتواند بیشتر قابلیتها و خدمات شبکه خود را به کاربران و سایر خدمات باز کنند و امکان استقرار یا پشتیبانی از سرویسهای جدید شبکه را  به طور سریعتر و ارزانتر داشته باشند تا بتوانند  سرویس بهتری داشته باشند.
@@
 \item \textbf{مقیاس گذاری پویا}:
-  جداشدن عملکرد شبکه به اجزای نرم‌افزاری  نعطاف پذیری بیشتری را برای  عملکرد واقعی VNF به روشی پویاتر، 
+  جداشدن عملکرد شبکه به اجزای نرم‌افزاری انعطاف پذیری بیشتری را برای  عملکرد واقعی VNF به روشی پویاتر، 
    با توجه به ترافیک واقعی که اپراتور شبکه برای تأمین ظرفیت نیاز دارد،
@@
  \LTRfootnote{NFV-MANO}
- که در شکل \eqref{fig:NFV} دیده می‌شود. ه‌ها
+ که در شکل \eqref{fig:NFV} دیده می‌شود. 
  \begin{figure}
@@
 \item 
-خدمات: یک سرویس مجموعه ای از VNFها است که میتوانند در یک یا چند ماشین مجازی پیاده سازی شوند.
-در بعضی مواقع، VNFها میتوانند در ماشینهای مجازی نصب شده در سیستم عامل یا سخت افزار بطور مستقیم نصب شوند. آنها توسط سرپرستان بومییا مانیتورهای ماشین مجازی اداره می‌شوند.
+خدمات: یک سرویس مجموعه ای از VNF ها است که میتوانند در یک یا چند ماشین مجازی پیاده سازی شوند.
+در بعضی مواقع، VNF ها میتوانند در ماشینهای مجازی نصب شده در سیستم عامل یا سخت افزار بطور مستقیم نصب شوند. آنها توسط سرپرستان بومی یا مانیتورهای ماشین مجازی اداره می‌شوند.
 معمولاً توسط یک سیستم مدیریت عناصر \LTRfootnote{Element Management System} (EMS)،
@@
  OSS
-  سیستم مدیریت عمومیاست، که  همراه با سیستم پشتیبانی از تجارت 
+  سیستم مدیریت عمومی است، که  همراه با سیستم پشتیبانی از تجارت 
 \LTRfootnote{Business Support System}  

### 2020-12-14 Latex/journal_v1/pr.tex
add latex version 1 for journal

--- 2020-05-12 Latex/tex/pr.tex
@@
+ %\pdfoutput=1
 \documentclass[conference]{IEEEtran}
@@
 
-\title{Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}
+\title{Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}
 }
@@
   \author{
-    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-Mansouri, Salar Nouri Naghadeh}
+    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
     \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
-    Email: \{mojdeh.karbalaee, vmansouri, salar.nouri\}@ut.ac.ir,
+    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
     \vspace{-.2cm}
@@
 \begin{abstract}
-Open radio access network (ORAN) alliance which has been formed recently establishes a flexible,  open, and smart radio access network (RAN) by combing the ideas from xRAN and cloud RAN (C-RAN).
-ORAN divides the functions of the RAN into three parts, namely remote unit (RU), distributed unit (DU), and central unit (CU).
-While RU contains lower PHY functions, DU contains higher PHY, MAC, and RLC and CU contains RRC, PDCP, and SDAP.
-CU and DU are implemented as virtual network functions (VNFs) running on a cloud environment.
-Interfaces between RU, CU, and DU are open standard interfaces.
-Network slicing as a new concept in 5G systems is used to share the network resources between various services while the operation of one service does not affect another service.
-In this paper, we study the problem of RAN network slicing in an ORAN system.
-We formulate the problem of wireless link scheduling, mapping the slices to the services, and mapping the physical data centers resource to slices.
-The objective is to jointly maximize the energy efficiency and minimize power consumption of RUs and the cost of physical resources in a downlink channel.
-The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems.
-Heuristic algorithms are proposed for each of the sub-problems.
+
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Open RAN (ORAN), network slicing, energy efficiency.
+
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Open RAN (ORAN), as the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G networks to extensively enhance the RAN performance.
-The core idea of C-RAN is to split the radio remote head (RRU) from the baseband unit (BBU).
-Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1,frdl,simeone2016cloud,motalleb2017optimal}.
-On the other hand, xRAN technology has three fundamental features.
-The control plane is decoupled from user plane.
-Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
-Moreover, open north-bound and south-bound interfaces are introduced \cite{xran}.
-
-ORAN virtualizes the elements of the radio access networks, separates them and defines appropriate open interfaces for connection of these elements.
-Moreover, ORAN uses machine learning techniques to develop smarter RAN layers in its architecture.
-In an innovative ORAN system, the programmable RAN software is decoupled from hardware \cite{oran1}.
-Open interface is one of the most crucial properties for ORAN to enable mobile network operators (MNOs) to define their own services.
-The concept of software defined network (SDN), which is the separation of control plane from user plane, is deployed in an intelligent ORAN architecture.
-Moreover, this separation promotes RRM to use non-realtime (RT) and near-realtime (NRT) RAN Intelligent Controller (RIC).
-In the ORAN architecture, distributed unit (DU) is a logical node having RLC/MAC/High-PHY layer.
-Moreover, central unit (CU) is a logical node having RRC, SDAP and PDCP. Also, radio unit (RU) is a logical node having LOW-PHY layer and
-RF processing \cite{oranpaper}.
-ORAN introduces interfaces such as open fronthaul interface that connects DU and RU (i.e., E2 interface), and an A1 interface between orchestration/NMS layer containing the non-real-time RIC (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC (RIC near-RT) function.
-
-To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and referred to as network functions virtualization (NFV).
-Virtual network functions (VNFs) are functional blocks of the system.
-5G networks are expected to host several services with different requirements simultaneously.
-Network slicing is considered as a solution for such demand.
-A network slice is a logical end-to-end network which provides service with specific requirements.
-Multiple network slices run on the same network infrastructure which are managed and operated independently \cite{lee2018dynamic}.
-Slicing can be defined for the RAN, for the core network or both of them \cite{ns1}.
-
-Based on their type of service request, user equipments (UEs) are classified into various services, where UEs in the same service have similar service requests.
-In addition, each service is mapped to one or more slices based on the resources of the slices.
-Each VNF of the ORAN is mapped to one or more virtual machines (VMs) in the data center.
-For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.
-
-%The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}.
-In \cite{oranT},  the evolution of RAN in the  5G network is described.
-The architecture of C-RAN and xRAN is expressed and development of the ORAN from C-RAN and xRAN is explained.
-Also requirements of the network in terms of capacity and latency is taken into account.
-In \cite{oran12},  the ORAN architecture is studied.
-The eight working groups are discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software.
-To the best of our knowledge, there is not work in the literature to model ORAN systems.
-
-%We shortly review related works in the area of C-RAN and xRAN.
-In \cite{motalleb2017optimal}, power allocation in C-RAN architecture, with limited fronthaul capacity in clustered network is studied.
-In \cite{lee2018dynamic}, dynamic network slicing is considered in heterogeneous CRAN (H-CRAN) to maximize the weighted sum-rate.
-Also, two level network slicing (upper and lower level) is done.
-The admission of UEs is maximized using the heuristic algorithms.
-In addition, the allocation of BBU capacity to UEs is considered.
-In \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting} minimization of cost obtained by power consumption, also cloud processing and limited power for each RU is considered.
-Furthermore, the processing delay of each VM and wireless transmission delay are taken into account.
-In \cite{frdl}, the processing and transmission delay is modeled as a M/M/1 queue.
-In \cite{guo2016exploiting}, M/D/1 queue is used to modeled the transmission delay.
-
-\begin{figure}
-  \centering
-    \includegraphics[scale=0.55]{c7.pdf}
-  \caption{Network sliced ORAN system}
-  \label{fig:c11}
-\end{figure}
-
-In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
-The RAN is divided into three layers including RU, DU, and CU with open interfaces.
-DU and CU are running on general purpose data centers.
-UEs are divided to different services according to their requirements.
-RAN resources are partitioned into slices to provide requirements of services.
-Optimal power allocation and joint mapping of slices to services are applied.
-In addition, mapping slices to physical resources is taken into account.
-The contributions of the paper are as follows:
-\begin{itemize}
-\item Joint network slicing and resource allocation is considered in an ORAN system.
-\item We formulate the problem of assigning UEs to services, services to slices, and physical wireless and data center resources to the slices as an optimization problem.
-\item Novel heuristic algorithms are applied for these sub-problems to efficiently obtain the solution.
-\end{itemize}
-
-The rest of the paper is organized as follows.
-In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is introduced.
-Then, problem statement is explained and decomposed into two independent sub-problems.
-In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results are provided to investigate the performance of the algorithms.
 
@@
 In this section, first, we  present the system model.
-Then, we obtain achievable rates and delays for the downlink (DL) of the ORAN system.
+Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system.
 Afterward, we discuss about assignment of physical data center resources.
@@
 \subsection{System Model}
+Suppose we have two service types includes eMBB and URLLC. Assume we have $V_1$ and $V_2$ different applications for the first and second service type ($V = V_1 + V_2$).
+Assume we have $S$ pre allocated slices serving $V$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC) ($S = S_1 + S_2$).
+Each Service $v_i\in \{1,2,...,V_i \} $ consists of $U_{v_i}$ request from the 
+single-antenna UEs that require certain service ($i \in \{1,2\}$ indicate service type).
+There are different application request which fall into one of these service categories.
+Each application request requires specific QoS.
+Based on the request for the application and QoS, UE may be admitted and allocate to slice.
+Each slice $s_i \in \{1,2,...,S_i \}$, $i \in \{1,2\}$ consists of $K_{s_i}$ , $i \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
+
 Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
@@
 \end{subequations}
-\section{Heuristic Method}\label{proposedmethod}
-In this subsection, a heuristic  method is proposed to solve the problem in \eqref{constraints1} which is non-convex and computationally hard.
-To make it tractable, we divide the problem \eqref{constraints1} into
-two different part that can be solved iteratively.
-In the first part of sub-problem 1, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in \eqref{constraints1}.
-Also, we set $\eta = 0$.
-Afterward, by achieving $\boldsymbol{A}$, in the second part, we find $\boldsymbol{P}$ by using \eqref{constraints1}.
-This part of the sub-problem can be approximated and converted to a convex problem, so the sub-problem can be solved by convex methods.
-After solving $\boldsymbol{P}$, $\eta$ is updated.
-Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$, the two parts of the sub-problems are solved. We repeat this procedure until the algorithm  converges.
-\subsection{First Part of Sub-Problem 1}\label{firstsub}
-Two different methods are applied to acquire $\boldsymbol{A}$.
-The details of the heuristic algorithm are represented in algorithm \ref{alg}.
-\begin{algorithm}
-\caption{Mapping Slice to Service}\label{alg}
-\begin{algorithmic}[1]
-\State Sort services according to the number of UEs in it and their requirements in the descending order.
-\State Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs in two layers and the capacity of their resources in the descending order.
-\For {$i \gets 1$ to $S$}
-\For {$j \gets 1$ to $V$}
-\State Set $a_{i,j} = 1$
-\State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RUs)
-\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} are not applied}
-\State Set $a_{i,j} = 0$;
-\Else
-\State break from inner loop;
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for}
-\end{algorithmic}
-\end{algorithm}
-\subsection{Second Part of Sub-Problem 1}\label{secondsub}
-In this part, by assuming that $\boldsymbol{A}$ is fixed, the power of UEs in each service is achieved.
-\begin{theorem}\label{t2}
-The optimum energy efficiency is achieved if
-\begin{equation}\label{q2}
-%\begin{split}
-\max \limits_{\boldsymbol{P}} (\mathfrak{R}_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=
- \mathfrak{R}_{tot}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
-%\end{split}
-\end{equation}
-\end{theorem}
-\begin{proof}
-See \cite[Appendix A]{aaa}
-\end{proof}
-The second sub-problem can  be solved using the Lagrangian function and iterative algorithm.
-Since, Interference is a function of the power of UEs, to make it tractable, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference.
-In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively).
-Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
-The Lagrangian function is written as follow
-\begin{subequations}\label{lagrang}
-\begin{alignat}{4}
-\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\chi}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
-- \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
-&+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
-&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
-&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,i)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\
-&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.
-\end{alignat}
-\end{subequations}
-where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$. Optimal power is obtained from  \eqref{lagrang}
-\begin{equation}
-p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
-\end{equation}
-where, $\mathfrak{y}_{u(v,i)}= (\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and
-$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. Also
-$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$.
-By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained \cite{mimoCran}.
-%\section*{References}
-\subsection{Solving two part of Sub-problem 1 iteratively}
-In \eqref{firstsub} and \eqref{secondsub}, the details of solving each part of the sub-problem are depicted.
-Firstly, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in the problem \eqref{constraints1} and using algorithm \eqref{alg}.
-Also we fixed $\eta = 0$.
-Afterward, $\boldsymbol{A}$ is achieved from algorithm \ref{alg}.
-Then, in the second part, we acquire $\boldsymbol{P}$ using the sub-gradient method.
-After solving $\boldsymbol{P}$, $\eta$ is updated.
-Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$ the two parts of the sub-problem is solved until the algorithm converges.
-Here, the algorithm of solving sub-problem 1 is shown in algorithm \eqref{alg2}
-\begin{algorithm}
-\caption{Joint Network Slicing and Power Allocation}\label{alg2}
-\begin{algorithmic}[1]
-\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
-\State Set $\boldsymbol{P} = \boldsymbol{P}_{max}$
-\For {$counter \gets 1$ to $I_{max}$}
-\State Achieve $\boldsymbol{A}$ by applying Algorithm \eqref{alg}
-\State Obtain $\boldsymbol{P}$ by using sub-gradient method which is mentioned in \eqref{secondsub}.
-\If {$ \mathfrak{R}_{tot}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) - \eta^{(i)} P_{r_{tot}}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) < \epsilon_{\eta} $}
-\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $, $\boldsymbol{A}^*= \boldsymbol{A}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
-\State break;
-\Else
-\State $i= i+1$, Setting $\boldsymbol{P} = \boldsymbol{P}^{(i)}$ ;
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\end{algorithmic}
-\end{algorithm}
-\subsection{Sub-Problem 2}
-In this subsection, we would like to solve  \eqref{constraints2}, which is the placement of virtual resources to physical resources in order to minimize the cost function $\psi_{tot}$.
-To achieve optimum $\boldsymbol{Y}$ heuristic algorithm is applied.
-The details of the heuristic algorithm are written in algorithm \eqref{alg3}.
-In this algorithm, firstly, we sort slices and DCs according to their sum-weighted of their requirements (line \ref{31} and line \ref{32} of algorithm \ref{alg3}).
-We define a weighted parameter for $\Omega_{\mathfrak{z},s}^{tot}$ and $\tau_j^\mathfrak{z}$ as follow
-\begin{equation}\label{wt}
-\begin{split}
-\hat{\Omega}_{s}^{tot} &= w_M \bar{\Omega}_{M,s}^{tot} + w_S \bar{\Omega}_{S,s}^{tot} + w_C \bar{\Omega}_{C,s}^{tot} \\
-\hat{\tau}_j &= w_M \tau_{{j}}^M + w_S \tau_{{j}}^S + w_C \tau_{{j}}^C,
-\end{split}
-\end{equation}
-where, $\boldsymbol{w} = \{w_M, w_S, w_C\}$ is the weight of memory, storage and CPU.
-Secondly, we start mapping from the most needed slices to the DC with the most physical resources (from line \ref{33} to line \ref{34} of algorithm \ref{alg3}).
-After mapping DCs to slices, If a slice does not admit to a specific DC, it remains for the next placement.
-In the next placement the remaining slices, map to more than one DC according to their requirements.
-(from line \ref{35} to line \ref{36} of algorithm \ref{alg3}).
-At the end, if DC with the lowest physical resources is free and can be served the slices of a DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption (line \ref{37} of algorithm \ref{alg3}).
-\begin{algorithm}
-\caption{Placement of Physical resources into Virtual resources}\label{alg3}
-\begin{algorithmic}[1]
-\State Sort Slices according to $\hat{\Omega}_{s}^{tot} , \forall s$ in descending order.\label{31}
-\State Sort DCs according to $\hat{\tau}_j , \forall j$ in descending order. \label{32}
-\State $\boldsymbol{Y} = \boldsymbol{0}$
-\For {$d \gets 1$ to $D_c$}\label{33}
-\For {$s \gets 1$ to $S$}
-\If {$\sum_{d=1}^{D_c}y_{s,d}==0$ and $\bar{\Omega}_{\mathfrak{z}(s)}^{tot} \leq \tau_{\mathfrak{z}_j} \forall \mathfrak{z}, \forall s$  }
-\State Set $y_{s,d} = 1$;
-\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for} \label{34}
-\State  $ind_{rem} = \{s|({\sum_{d=1}^{D_c}y_{s,d}==0})\}$ \label{35}
-\State Sort remaining amount of DCs same as before in descending order.
-\State Sort remaining slices same as before in descending order.
-\For {$r \gets 1$ to $S_{rem}$}
-\For {$n \gets 1$ to $D_c$}
-\State Set $y_{s,d} = 1$;
-\State {$\bar{\Omega}_{{\mathfrak{z}},s}^{tot}$ $\gets$ {$\bar{\Omega}_{{\mathfrak{z}},s}^{tot}- \tau_j^{\mathfrak{z}}$}}
-\If {$\bar{\Omega}_{s}^{tot}==0$}
-\State Set $y_{s,d} = 1$;
-\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
-\State {break inner loop}
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for} \label{36}
-\State Remapping DCs must be done to prevent wasting Energy \label{37}
-\end{algorithmic}
-\end{algorithm}
 \section{Numerical Results}\label{simul}
-In this section, numerical results for the main problem are depicted.
- \begin{table}
- \caption {Simulation Parameter} \label{table:1a}
- \begin{center}
-  \begin{tabular}{||c c ||}
-  \hline
-Parameter & Value \\ [0.5ex]
-  \hline\hline
-  Noise power & -174dBm\\
-  \hline
-  Bandwidth & 120 KHZ \\
-  \hline
- Maximum transmit Power of each RU & 40dBm \\
-  \hline
-  Minimum delay &  300usec \\
-  \hline
-  Maximum fronthaul capacity  & 200 bits/sec/Hz \\
-   \hline
-  Minimum data rate &  10 bits/sec/Hz \\ [1ex]
-  \hline
- \end{tabular}
- \end{center}
- \end{table}
-In Fig.
-\ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with different mean number of UEs in each service.
-The parameters of simulations are listed in Table \ref{table:1a}.
-The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$.
-They iteratively update $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$.
-The optimal method is $0.1$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.09$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$.
-As it is shown, the energy efficiency is increased as mean number of UEs rises.
-\begin{figure}%[H]
-  \centering
-    \includegraphics[width=\linewidth]{fig1_last}
-  \caption{Energy Efficiency vs. Mean Number of UEs in each Service}
-  \label{fig:f1a}
-\end{figure}
-In Fig.
-\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices.
-The parameters of the simulation are listed in Table \ref{table:1}.
-We also set $w_C = 320$, $w_S = 100$, $w_M =1$.
-In this simulation, the second term of \eqref{eqpsi}, is important and the designed parameter $\nu$ is supposed to be high.
-Also, it is assumed that just one DC can serve each slice, and each slice is not admitted by more than one DC. 
-The proposed method is based on Algorithm \ref{alg3}, and the optimal method is obtained using MOSEK toolbox.
-\begin{small}
- \begin{table}
- \caption {Simulation Parameter} \label{table:1}
- \begin{center}
-  \begin{tabular}{||c c ||}
-  \hline
-  Parameter & Value \\ [0.5ex]
-  \hline\hline
-  Mean of CPU for DCs & 320GHz\\
-  \hline
-  Mean of Memory for DCs & 1T\\
-  \hline
- Mean of Storage for DCs & 100T \\
-  \hline
-   Mean of CPU for Slices & 32GHz\\
-  \hline
-  Mean of Memory for Slices & 100G\\
-  \hline
- Mean of Storage for Slices & 10T \\ [1ex]
-  \hline
- \end{tabular}
- \end{center}
- \end{table}
-\end{small}
-When we have two DCs, the proposed method and optimal method have approximately the same ratio of admitted slices.
-But by increasing the number of DCs to five, the performance of the proposed method reduced.
-Using five DCs, the difference between the
-proposed method and the optimal method in the worst case (44 slices) is about $23$ percentage.
-\begin{figure}%[H]
-  \centering
-    \includegraphics[width=\linewidth]{f112}
-  \caption{Ratio of Admitted Slices connected to just one DC vs. Total slices}
-  \label{fig:f1}
-\end{figure}
-In Fig.
-\ref{fig:f2}, the normalized resource consumption is depicted versus the number of slices.
-The parameters for simulation are listed in Table \ref{table:1}.
-We also set $w_C = 320$, $w_S = 100$, $w_M =1$).
-In this simulation, suppose the number of DCs is entirely enough to cover all slices and the designed parameter $\nu$ is assumed to be low, so we focused on the first term of \eqref{eqpsi}.
-However, if any slice remains, it can be served by more than one DCs.
-The optimality of the placement of DC resources to slices is measured based on the power consumption of DCs.
-It is shown the amount of resources of DCs which are not used.
-For ten slices, the difference between the optimal solution and the proposed solution is about $15$ percent.
-\begin{figure}%[H]
-  \centering
-    \includegraphics[width=\linewidth]{fig22_last}
-  \caption{Normalized Resource Consumption vs. Number of Slices}
-  \label{fig:f2}
-\end{figure}
+
 \section{Conclusion}
-In this paper, joint network slicing and power allocation were considered in an ORAN system.
-It is assumed that UEs are classified based on their requirements into services.
-Also, there is a number of slices serving the services.
-Each slice consists of PRBs, RUs, and VNFs that support CU and DU.
-The limited fronthaul capacity is considered for the fiber links between RUs and DU.
-The target was to maximize the sum-rate and minimize the power consumption and energy cost of data centers simultaneously.
-The problem is decomposed into two sub-problems.
-Each sub-problem is solved separately by a heuristic algorithm.
-Using numerical results, we validate the heuristic method and study the performance of the algorithms.
-%For the sub-problem A, energy efficiency vs.
-mean number of UEs in each service is depicted.
-The energy efficiency  exceeded by increasing the mean number of UEs in each service.
-For the sub-problem B, two figures are shown.
-In the first one, the ratio of admitted slices that connect to just one DC, for a different number of slices is denoted.
-In the second figure, the normalized resource consumption of DCs is depicted.
-In each figure, the heuristic algorithm is compared with the optimal method and the difference between them is discussed.
 

### 2020-12-15 Latex/journal_v1/pr.tex
latex update v1

@@
 \subsection{System Model}
-Suppose we have two service types includes eMBB and URLLC. Assume we have $V_1$ and $V_2$ different applications for the first and second service type ($V = V_1 + V_2$).
-Assume we have $S$ pre allocated slices serving $V$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC) ($S = S_1 + S_2$).
+Suppose we have two service types includes eMBB and URLLC. Assume we have $V_1$ and $V_2$ different applications for the first and second service type, respectively ($V = V_1 + V_2$).
+Assume we have $S$ preallocated slices serving $V$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC) ($S = S_1 + S_2$).
 Each Service $v_i\in \{1,2,...,V_i \} $ consists of $U_{v_i}$ request from the 
-single-antenna UEs that require certain service ($i \in \{1,2\}$ indicate service type).
+single-antenna UEs which require certain QoS to be able to use the requested program($i \in \{1,2\}$ indicate service type).
 There are different application request which fall into one of these service categories.
 Each application request requires specific QoS.
-Based on the request for the application and QoS, UE may be admitted and allocate to slice.
-Each slice $s_i \in \{1,2,...,S_i \}$, $i \in \{1,2\}$ consists of $K_{s_i}$ , $i \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
+Based on the request for the application and QoS, UE may be admitted and allocated to slice.
+Each slice $s_i \in \{1,2,...,S_i \}$, $i \in \{1,2\}$ consists of $K_{s_i}$, $i \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_{s,1}$ VNFs for the processing of O-DU,  $M_{s,2}$ VNFs for the processing of O-CU-UP and $M_{u}$ VNFs for the processing of UPF.
 
+Also, each VNF instance is running on the virtual machine (VM) that are using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
+
+In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
+has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
+\subsection{The Achievable Rate}
+The achievable data rate for the $i^{th}$ UE request in the $v_{1}^{th}$ application of service type 1 (eMBB) can be written as
+\begin{equation}\label{eq1}
+\mathcal{R}_{u(v_1,i)}^{e} = \sum_{s1=1}^{S_1}\sum_{k=1}^{K_s} B \log_2({1+ \rho_{u(v_1,i)}^{k,s1}})a_{u(v,i)} b_{v_1, s_1} e^{s_1}_{k,u(v_1,i)},
+\end{equation}
+where $B$ is the bandwidth of system, $a_{u(v,i)} \in \{0,1\}$ is a binary variable to depict user admission.
+$b_{v_1, s_1}$ is a binary variable that illustrates whether slice $s_1$ is allocated to service $v_1$ or not. 
+$e^{s_1}_{k,u(v_1,i)}$ is the binary variable to show whether the UE $i$ in service $v_1$ using slice $s_1$, is assigned to $k^{th}$ PRB or not.
+ and $\rho_{u(v_1,i)}^{k,s1}$ is the SNR of $i^{th}$ UE in $v_{1}^{th}$ service experienced at slice $s_1$ on PRB $k$ which is obtained from
+\begin{equation}\label{eq2}
+\rho_{u(v_1,i)}^{k,s1} =  \sum_{s1=1}^{S_1}\frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
+\end{equation}
+
+\newpage
 Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$

### 2020-12-16 Latex/journal_v1/pr.tex
update achievable rate for journal

@@
 Assume we have $S$ preallocated slices serving $V$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC) ($S = S_1 + S_2$).
-Each Service $v_i\in \{1,2,...,V_i \} $ consists of $U_{v_i}$ request from the 
-single-antenna UEs which require certain QoS to be able to use the requested program($i \in \{1,2\}$ indicate service type).
+Each Service $v_j\in \{1,2,...,V_j \} $ consists of $U_{v_j}$ request from the 
+single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2\}$ indicate service type).
 There are different application request which fall into one of these service categories.
@@
 Based on the request for the application and QoS, UE may be admitted and allocated to slice.
-Each slice $s_i \in \{1,2,...,S_i \}$, $i \in \{1,2\}$ consists of $K_{s_i}$, $i \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_{s,1}$ VNFs for the processing of O-DU,  $M_{s,2}$ VNFs for the processing of O-CU-UP and $M_{u}$ VNFs for the processing of UPF.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_{s,1}$ VNFs for the processing of O-DU,  $M_{s,2}$ VNFs for the processing of O-CU-UP and $M_{u}$ VNFs for the processing of UPF.
 
@@
 \subsection{The Achievable Rate}
+The SNR of $i^{th}$ UE in $v^{th}$ service experienced at slice $s$ on PRB $k$ which is obtained from
+ $\rho_{u(v,i)}^{k,s}$ is the SNR 
+\begin{equation}\label{eq2}
+\rho_{u(v,i)}^{k,s} =  \frac{p_{u(v,i)}^{k,s}\sum_{r=1}^{R}|{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(v,i)}^{k,s} g_{r,u(v,i)}|^2}{BN_0 + I_{u(v,i)}^{k,s}},
+\end{equation} 
+where $p_{u(v,i)}^{k,s}$ represents the transmission power allocated to $i^{th}$ UE in $v^{th}$ service, served at slice $s$ on PRB $k$. 
+${\bold{h}_{r,u(v,i)}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
+$r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service.
+In addition, $\bold{w}_{r,u(v,i)}^{k,s} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service that is the zero forcing beamforming vector to minimize the interference which is indicated as below
+\begin{equation}
+\bold{w}_{r,u(v,i)}^{k,s} = {\bold{h}_{r,u(v,i)}^{k,s}}({\bold{h}_{r,u(v,i)}^{H \: k,s1}} {\bold{h}_{r,u(v,i)}^{k,s}})^{-1}
+\end{equation}
+Moreover, $g_{r,u(v,i)} \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
+Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}^{k,s1}$ is the power of interfering signals represented as follow
+\begin{equation}
+\begin{split}
+I_{u(v,i)}^{k,s} &=
+ \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u(v,i)}^{k,s}\sum_{r=1}^{R}|{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(v,i)}^{k,s1} g_{r,u(v,i)}|^2}_{\text{(intra-service interference)}}\\
+&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{r=1}^{R}|{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(y,l)}^{k,n} g_{r,u(y,l)}|^2}_{\text{(inter-service interference)}}\\
+\end{split}
+\end{equation}
+where $\gamma_{1} = e^{s}_{k,u(v,i)}e^{s}_{k,u(v,l)}a_{u(v,i)}a_{u(v,l)} b_{v, s} $
+and $\gamma_{2} = e^{s}_{k,u(v,i)}e^{n}_{k,u(y,l)}a_{u(v,i)}a_{u(y,l)} b_{v, s} b_{y,n} $.
+Where $a_{u(v,i)} \in \{0,1\}$ is a binary variable to depict user admission.
+$b_{v, s}$ is a binary variable that illustrates whether slice $s$ is allocated to service $v$ or not. 
+$e^{s}_{k,u(v,i)}$ is the binary variable to show whether the UE $i$ in service $v$ using slice $s$, is assigned to $k^{th}$ PRB or not.
+
 The achievable data rate for the $i^{th}$ UE request in the $v_{1}^{th}$ application of service type 1 (eMBB) can be written as
 \begin{equation}\label{eq1}
-\mathcal{R}_{u(v_1,i)}^{e} = \sum_{s1=1}^{S_1}\sum_{k=1}^{K_s} B \log_2({1+ \rho_{u(v_1,i)}^{k,s1}})a_{u(v,i)} b_{v_1, s_1} e^{s_1}_{k,u(v_1,i)},
+\mathcal{R}_{u(v_1,i)}^{e} = \sum_{s_1=1}^{S_1}\sum_{k=1}^{K_s} B \log_2({1+ \rho_{u(v_1,i)}^{k,s_1}})a_{u(v_1,i)} b_{v_1, s_1} e^{s_1}_{k,u(v_1,i)},
 \end{equation}
-where $B$ is the bandwidth of system, $a_{u(v,i)} \in \{0,1\}$ is a binary variable to depict user admission.
-$b_{v_1, s_1}$ is a binary variable that illustrates whether slice $s_1$ is allocated to service $v_1$ or not. 
-$e^{s_1}_{k,u(v_1,i)}$ is the binary variable to show whether the UE $i$ in service $v_1$ using slice $s_1$, is assigned to $k^{th}$ PRB or not.
- and $\rho_{u(v_1,i)}^{k,s1}$ is the SNR of $i^{th}$ UE in $v_{1}^{th}$ service experienced at slice $s_1$ on PRB $k$ which is obtained from
-\begin{equation}\label{eq2}
-\rho_{u(v_1,i)}^{k,s1} =  \sum_{s1=1}^{S_1}\frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
+where $B$ is the bandwidth of system.
+
+Since the blocklength in URLLC is finite, the achievable data rate for the $i^{th}$ UE request in the $v_{2}^{th}$ application of service type 2 (URLLC) is not achieved from Shannon Capacity formula.
+So, for the short packet transmission the achievable data rate is approximated from follow
+\begin{equation}\label{eq1}
+\mathcal{R}_{u(v_2,i)}^{u} = \sum_{s_2=1}^{S_2}\sum_{k=1}^{K_s} B (\log_2({1+ \rho_{u(v_2,i)}^{k,s_2}})- \zeta_{u(v_2,i)}^{k,s_2}){\beta}_{u(v_2,i)}^{k,s_2}
 \end{equation}
+Where ${\beta}_{u(v_2,i)}^{k,s_2}=a_{u(v_2,i)} b_{v_2, s_1} e^{s_2}_{k,u(v_2,i)}$
+and $\zeta_{u(v_2,i)}^{k,s_2} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(v_2,i)}^{k,s_2}}{N_{u(v_2,i)}^{k,s_2}}})$
 
 \newpage
-Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
-single-antenna UEs that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
-Slices can have shared resources.
-All RUs in a slice, that are mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}.
-Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.
-There are two processing layers one in the DU and one in the CU of ORAN system, each represented with a VNF.
-The lower layer (i.e., DU) consists of high-PHY, MAC, and RLC, and the upper layer (i.e., CU) consists of RRC, PDCP and SDAP.
-Assume we have $M_1$ VNFs in the DU layer and $M_2$ VNFs in the CU layer for processing data.
-Each VNF in both layers belongs to one or more slices.
-So, in the $s^{th}$ slice, there are $M_{s,1}$ VNFs in the DU layer and $M_{s,2}$ VNFs in the CU layer.
-The VNFs in the DU and CU layers have the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
-Also, RUs and PRBs can serve more than one slice.
-\subsection{The Achievable Rate}
-The achievable data rate for the $i^{th}$ UE in the $v^{th}$ service can be written as
-\begin{equation}\label{eq1}
-\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}}),
-\end{equation}
-where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from
-\begin{equation}\label{eq2}
-\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
-\end{equation}
-where $p_{u(v,i)}$ represents the transmission power allocated by RUs to $i^{th}$ UE in $v^{th}$ service, and
-$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
-In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
-Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals.
-Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is mapped to service $v$ or not.
-If $a_{v,s} =1$ then, $v^{th}$ service is mapped to $s^{th}$ slice; otherwise, it is not mapped.
-\newline
-To obtain SNR as formulated in \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service
-\begin{equation}\label{eq3}
-\textstyle \bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v} \
-\mathfrak{y}_{R_s}\zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v},
-\end{equation}
-where $\mathfrak{y}_{R_s} = \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_s}$
-and $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
-In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise, which is made from signal compression in DU.
-Besides, $\boldsymbol{P}_{U_v} = \diag{(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})}$.
-\newline
-Furthermore, $\zeta_{k,s}^{U_v} \delequal \{\zeta_{k,s}^{u(v,1)},\zeta_{k,s}^{u(v,2)},...,\zeta_{k,s}^{u(v,N_{U_v})}\}$,
-$\zeta_{k,s}^{u(v,i)} \in \{0,1\}$ is a binary parameter, which demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
-$\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
-shows the channel matrix between RU set $\mathcal{R}_s$ to UE set
-$\mathcal{U}_v$, besides.
-%The channel vector from the RU of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below
-%\begin{equation}
-%\boldsymbol{h}_{\mathcal{R}_s,u_{(s,i)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_s,u_{(v,i)}} \boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}},
-%\end{equation}
-%where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
-%represents the large scale fading matrix.
-What's more, it is assumed we have perfect channel state information (CSI).\newline
-Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as below
-\begin{equation}
-\textstyle \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}.
-\end{equation}
-Hence, the interference power of $i^{th}$ UE in $v^{th}$ service can be represented as follow
-\begin{equation}
-\begin{split}
- I_{u_{(v,i)}} &=
- \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{v,s}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
-&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
-&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}},
-\end{split}
-\end{equation}
-where $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
-and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. Moreover,
-${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RU in $s^{th}$ slice.
-Interference signal for each UE is coming from UEs using the same PRB.
-If we replace $p_{u_{(v,l)}}$ and $p_{u_{(y,l)}}$ by $P_{max}$, an upper bound $\bar{I}_{u_{(v,i)}}$ is obtained for $I_{u_{(v,i)}}$.
-Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in  \eqref{eq1} and \eqref{eq2}.\newline
-Let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from the $j^{th}$ RU in $s^{th}$ slice.
-From \eqref{eq3}, we have,
-\begin{equation}
-\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s} + \sigma_{q_{r(s,j)}}^2.
-\end{equation}
-Nevertheless, the rate of users on the fronthual link between DU and the $j^{th}$ RU in $s^{th}$ slice is formulated as \cite{simeone2016cloud, 1111}
-\begin{equation}
-C_{R_{(s,j)}} = \log{(1+\sum_{v=1}^{V}\frac{w_{r_{(s,j)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   w_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s}}{ \sigma_{q_{r(s,j)}}^2})},
-\end{equation}
-where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .
-
 \subsection{Mean Delay}
 Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
-Therefore, the mean arrival data rate of UEs mapped to the $s^{th}$ slice in the CU layer is $\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not.
-Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
+Therefore, the mean arrival data rate of UEs mapped to the $s^{th}$ slice in the CU layer is $\alpha_{s_j} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not.
+Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_j} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
 It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
@@
 \begin{split}
-d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},\\
+d_{s_j} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},\\
 d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}.
@@
 \begin{equation}
-D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s.
+D_{s} = d_{s_j} + d_{s_2} + d_{s_{tr}} \forall s.
 \end{equation}
@@
 \end{equation}
-Where, $F_s = M_{s_1} + M_{s_2}$
+Where, $F_s = M_{s_j} + M_{s_2}$
 Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.

### 2020-12-18 Latex/journal_v1/pr.tex
latex delay

@@
 and $\zeta_{u(v_2,i)}^{k,s_2} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(v_2,i)}^{k,s_2}}{N_{u(v_2,i)}^{k,s_2}}})$
+Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
+$C_{u(v_2,i)}^{k,s_2} = 1 - \frac{1}{(1+\rho_{u(v_2,i)}^{k,s_2})}$ depicts the channel dispersion of UE  $i$ requesting service $v_2$, experiencing PRB $k$ at slice $s_2$  and
+$N_{u(v_2,i)}^{k,s_2}$ represents the blocklength of it.
 
-\newpage
 \subsection{Mean Delay}
+In this part, the mean arrival delay for a UE is obtained.
 Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
@@
 Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is connected to the VNFs of $s^{th}$ slice or not.
+
+\newpage
 \subsection{Problem Statement}

### 2020-12-19 Latex/journal_v1/pr.tex
journal system model finish until problem statement

@@
 Based on the request for the application and QoS, UE may be admitted and allocated to slice.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_{s,1}$ VNFs for the processing of O-DU,  $M_{s,2}$ VNFs for the processing of O-CU-UP and $M_{u}$ VNFs for the processing of UPF.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_{d}$ VNFs for the processing of O-DU,  $M_{c}$ VNFs for the processing of O-CU-UP and $M_{u}$ VNFs for the processing of UPF.
 
@@
 \subsection{Mean Delay}
-In this part, the mean arrival delay for a UE is obtained.
-Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
-Therefore, the mean arrival data rate of UEs mapped to the $s^{th}$ slice in the CU layer is $\alpha_{s_j} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not.
-Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_j} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.
-It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
-Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice. So, the mean delay of the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
+In this part, the end to end mean delay for a service is obtained.
+Suppose the mean total delay is depicted as $T_{tot}$.
 \begin{equation}
 \begin{split}
-d_{s_j} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},\\
-d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}.
+T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
+T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
+T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
+T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
 \end{split}
 \end{equation}
-where $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layers respectively.
-Besides, $\alpha_{s}$ is the  arrival rate which is divided
-by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
-In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice on the  wireless link. The arrival data rate of wireless link
- is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
+%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
+Total delay is sum of processing delay, transmission delay and propagation delay. 
+The propagation delay is the time takes for a signal to reach to its destination.
+So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
+Here we assume the value of propagation delay is negligible compared to the rest.
+\subsubsection{Processing Delay}
+Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
+Therefore, the mean arrival data rate of the $v^{th}$ service in the UPF layer is $\alpha_{v}^1 = \sum_{u=1}^{U_v}a_{u(v,i)}\lambda_{u(v,i)}$, where $a_{u(v,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $v^{th}$ service is admitted or not.
+
+Assume the mean arrival data rate of the UPF layer ($\alpha_{v}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{v}^C$) and O-DU ($\alpha_{v}^D$).
+so $\alpha_{v} =\alpha_{v}^U \approx \alpha_{v}^C \approx \alpha_{v}^D$.
+since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{v}$.
+It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
+Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
+Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $v^{th}$ service in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
+\begin{equation}
+\begin{split}
+T_{DU}^{v} &= \frac{1}{\mu_d - \alpha_{v}/{M_{v,d}}},\\
+T_{CU}^{v} &= \frac{1}{\mu_c - \alpha_{v}/{M_{v,c}}}\\
+T_{UPF}^{v} &= \frac{1}{\mu_u - \alpha_{v}/{M_{v,u}}}\\
+\end{split}
+\end{equation}
+Where $M_{v,d} = \sum_{s=1}^{S}M_{d} b_{v,s}$, $M_{v,c} = \sum_{s=1}^{S}M_{c} b_{v,s}$ and 
+$M_{v,u} = \sum_{s=1}^{S}M_{u} b_{v,s}$ 
+are the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. Since, each service may use more than one slice, the data packets of each service is divided between VNFs of slices allocated to service.
+Moreover, $1/\mu_d$, $1/\mu_c$ and $1/\mu_u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
+Besides, $\alpha_{v}$ is the  arrival rate which is divided
+by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each service 
+$v$ is $\alpha_{v}/{M_{v,i}}$ $ i \in \{d,c, u\}$.
+
+In addition, $T_{RU}^{v}$ is the mean transmission delay of $v^{th}$ service on the wireless link.
+The arrival data rate of wireless link is equal to the arrival data rate of load balancers for each service.
+ %\cite{frdl}.
 Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
- an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
+ an exponential distribution with mean $1/(R_{{tot}_v})$ and can be modeled as a M/M/1 queue.
+ %\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. 
+ Therefore,
 the mean delay of the transmission layer is
 \begin{equation}
- d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
+ T_{RU}^{v} = \frac{1}{R_{{tot}_v} - \alpha_{v}};
 \end{equation}
-where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
-Mean delay of each slice is obtained as below.
+where, $R_{{tot}_v} = \sum_{u=1}^{U_v}a_{u(v,i)}R_{u(v,i)}$ is the total achievable rate of each service.
+So the mean processing delay for each UE in service $v$ is 
 \begin{equation}
-D_{s} = d_{s_j} + d_{s_2} + d_{s_{tr}} \forall s.
+T_{process}^{v} =  T_{RU}^{v} + T_{DU}^{v} + T_{CU}^{v} + T_{UPF}^{v}
 \end{equation}
+\subsubsection{Transmission Delay}
+The transmission delay is the amount of time required to push all the packets into the fiber link. 
+Here, we have transmission delay in fronthaul, midhaul, backhaul and the link to transmit data to internet.
+\begin{equation}
+\begin{split}
+T_{front} =& \frac{\alpha_{v}^{f}}{R_f} \\
+T_{mid} =&  \frac{\alpha_{v}^{m}}{R_m} \\
+T_{back} =& \frac{\alpha_{v}^{b}}{R_b} \\
+T_{trans2net} =& \frac{\alpha_{v}^{t}}{R_t} \\
+\end{split}
+\end{equation}
+Where, $R_f$, $R_m$, $R_b$ and $R_t$ are the rate of transmission in fronthaul, midhaul, backhaul and the link to transmit data to internet, respectively.
+Furthermore, the mean arrival data rate of the each link ($\alpha_{v}^i$ , $i \in \{f,m,b,t\}$) is approximately equal to others ($\alpha_{v} \approx \alpha_{v}^i$ , $i \in \{f,m,b,t\}$).  
 \subsection{Physical Data Center Resource}
 Each VNF requires
-physical resources that contain memory, storage and CPU.
+physical resources that contain memory, storage, CPU and Network Bandwidth.
 Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
 \begin{equation}
-\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \},
+\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f \},
 \end{equation}
-where $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, storage, and CPU, respectively.
-Moreover, the total amount of required memory, storage and CPU of all VNFs of a slice is defined as
+where $\bar{\Omega}_{s}^f\in \mathbb{C}^{4}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f$ indicate the amount of required memory, storage, CPU and and Network Bandwidth, respectively.
+Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice is defined as
 \begin{equation}
-\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.
+\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C, N\}.
 \end{equation}
@@
 Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
-The amount of memory, storage and CPU is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$and $\tau_{C_{j}} $ for the $j^{th}$ DC, respectively
+The amount of memory, storage, CPU and and Network Bandwidth is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$, $\tau_{C_{j}} $ and $\tau_{N_{j}} $ for the $j^{th}$ DC, respectively
 \begin{equation*}
-\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \},
+\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}}, \tau_{N_{j}} \},
 \end{equation*}
 In this system model, the assignment of physical DC resources to VNFs is considered.
-Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is connected to the VNFs of $s^{th}$ slice or not.
+Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is allocated the resources to the VNFs of $s^{th}$ slice or not.
+\subsection{Problem Statement}
 

### 2020-12-20 Latex/journal_v1/pr.tex

@@
 Based on the request for the application and QoS, UE may be admitted and allocated to slice.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_{d}$ VNFs for the processing of O-DU,  $M_{c}$ VNFs for the processing of O-CU-UP and $M_{u}$ VNFs for the processing of UPF.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
 
@@
 \begin{equation}\label{eq2}
-\rho_{u(v,i)}^{k,s} =  \frac{p_{u(v,i)}^{k,s}\sum_{r=1}^{R}|{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(v,i)}^{k,s} g_{r,u(v,i)}|^2}{BN_0 + I_{u(v,i)}^{k,s}},
+\rho_{u(v,i)}^{k,s} =  \sum_{r=1}^{R}\frac{|p_{r,u(v,i)}^{k,s}{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(v,i)}^{k,s} g_{u(v,i)}^r|^2}{BN_0 + I_{r,u(v,i)}^{k,s}},
 \end{equation} 
-where $p_{u(v,i)}^{k,s}$ represents the transmission power allocated to $i^{th}$ UE in $v^{th}$ service, served at slice $s$ on PRB $k$. 
+where $p_{r,u(v,i)}^{k,s}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE in $v^{th}$ service, served at slice $s$ on PRB $k$. 
 ${\bold{h}_{r,u(v,i)}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
@@
 \end{equation}
-Moreover, $g_{r,u(v,i)} \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}^{k,s1}$ is the power of interfering signals represented as follow
+Moreover, $g_{u(v,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
+Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(v,i)}^{k,s1}$ is the power of interfering signals represented as follow
 \begin{equation}
 \begin{split}
-I_{u(v,i)}^{k,s} &=
- \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u(v,i)}^{k,s}\sum_{r=1}^{R}|{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(v,i)}^{k,s1} g_{r,u(v,i)}|^2}_{\text{(intra-service interference)}}\\
-&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{r=1}^{R}|{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(y,l)}^{k,n} g_{r,u(y,l)}|^2}_{\text{(inter-service interference)}}\\
+I_{r,u(v,i)}^{k,s} &=
+ \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u(v,i)}^{k,s}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(v,i)}^{H \: k,s}} \bold{w}_{r',u(v,i)}^{k,s1} g_{u(v,i)}^{r'}|^2}_{\text{(intra-service interference)}}\\
+&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(v,i)}^{H \: k,s}} \bold{w}_{r',u(y,l)}^{k,n} g_{u(y,l)}^{r'}|^2}_{\text{(inter-service interference)}}\\
 \end{split}
 \end{equation}
-where $\gamma_{1} = e^{s}_{k,u(v,i)}e^{s}_{k,u(v,l)}a_{u(v,i)}a_{u(v,l)} b_{v, s} $
-and $\gamma_{2} = e^{s}_{k,u(v,i)}e^{n}_{k,u(y,l)}a_{u(v,i)}a_{u(y,l)} b_{v, s} b_{y,n} $.
+where $\gamma_{1} = e^{k,s}_{r,u(v,i)}e^{k,s}_{r',u(v,l)}a_{u(v,i)}a_{u(v,l)} b_{v, s} $
+and $\gamma_{2} = e^{k,s}_{r,u(v,i)}e^{k,n}_{r',u(y,l)}a_{u(v,i)}a_{u(y,l)} b_{v, s} b_{y,n} $.
 Where $a_{u(v,i)} \in \{0,1\}$ is a binary variable to depict user admission.
 $b_{v, s}$ is a binary variable that illustrates whether slice $s$ is allocated to service $v$ or not. 
-$e^{s}_{k,u(v,i)}$ is the binary variable to show whether the UE $i$ in service $v$ using slice $s$, is assigned to $k^{th}$ PRB or not.
+$e^{k,s}_{r,u(v,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in service $v$, assigned to $r^{th}$ o-RU using slice $s$ or not.
 
@@
 \begin{equation}\label{eq1}
-\mathcal{R}_{u(v_1,i)}^{e} = \sum_{s_1=1}^{S_1}\sum_{k=1}^{K_s} B \log_2({1+ \rho_{u(v_1,i)}^{k,s_1}})a_{u(v_1,i)} b_{v_1, s_1} e^{s_1}_{k,u(v_1,i)},
+\mathcal{R}_{u(v_1,i)}^{e} = \sum_{s_1=1}^{S_1}\sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{u(v_1,i)}^{k,s_1}})a_{u(v_1,i)} b_{v_1, s_1} e^{k,s_1}_{r,u(v_1,i)},
 \end{equation}
@@
 \begin{equation}\label{eq1}
-\mathcal{R}_{u(v_2,i)}^{u} = \sum_{s_2=1}^{S_2}\sum_{k=1}^{K_s} B (\log_2({1+ \rho_{u(v_2,i)}^{k,s_2}})- \zeta_{u(v_2,i)}^{k,s_2}){\beta}_{u(v_2,i)}^{k,s_2}
+\mathcal{R}_{u(v_2,i)}^{u} = \sum_{s_2=1}^{S_2}\sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(v_2,i)}^{k,s_2}})- \zeta_{u(v_2,i)}^{k,s_2}){\beta}_{u(v_2,i)}^{k,s_2}
 \end{equation}
-Where ${\beta}_{u(v_2,i)}^{k,s_2}=a_{u(v_2,i)} b_{v_2, s_1} e^{s_2}_{k,u(v_2,i)}$
+Where ${\beta}_{u(v_2,i)}^{k,s_2}=a_{u(v_2,i)} b_{v_2, s_1} e^{k,s_2}_{u(v_2,i)}$
 and $\zeta_{u(v_2,i)}^{k,s_2} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(v_2,i)}^{k,s_2}}{N_{u(v_2,i)}^{k,s_2}}})$
@@
 \end{equation}
-Where $M_{v,d} = \sum_{s=1}^{S}M_{d} b_{v,s}$, $M_{v,c} = \sum_{s=1}^{S}M_{c} b_{v,s}$ and 
-$M_{v,u} = \sum_{s=1}^{S}M_{u} b_{v,s}$ 
+Where $M_{v,d} = \sum_{s=1}^{S}M_s^{d} b_{v,s}$, $M_{v,c} = \sum_{s=1}^{S}M_s^{c} b_{v,s}$ and 
+$M_{v,u} = \sum_{s=1}^{S}M_s^{u} b_{v,s}$ 
 are the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. Since, each service may use more than one slice, the data packets of each service is divided between VNFs of slices allocated to service.
@@
 \end{equation}
-Where, $F_s = M_{s_j} + M_{s_2}$
+Where, $F_s = M_{s}^d + M_{s}^c + M_{s}^u$
 Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
@@
 \subsection{Problem Statement}
-
-\newpage
-\subsection{Problem Statement}
-An important criterion to measure the optimality of a system is energy efficiency represented as the sum-rate to sum-power
+In this system, the goal is to minimize the cost of the system.
+Power of each O-RU is obtained as below
 \begin{equation}
-\textstyle \eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_r^{{tot}}(\boldsymbol{P},\boldsymbol{A})},
+P_r =  \sum_{v=1}^{V} \sum_{i=1}^{U_v} \sum_{s=1}^{S} \sum_{k=1}^{K_s}p_{r,u(v,i)}^{k,s}a_{u(v,i)} b_{v, s} e^{k,s}_{r,u(v,i)}g_{u(v,i)}^r.
 \end{equation}
-where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RUs in all slices.
-Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the total rates of all UEs applied for all types of services.
+The total power cost of O-RUs for transmitting data to UE is depicted as follow
+\begin{equation}
+P_{tot} = \sum_{r=1}^{R}P_r
+\end{equation}
 Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
@@
 \begin{equation*}
-\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
+\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d} + \sum_{d=1}^{D_c}z_d \psi_d .
 \end{equation*}
-Also, a cost function for the placement of VNFs into DCs is defined as
-\begin{equation}\label{eqpsi}
-\textstyle  \psi_{tot} = \phi_{tot} - \nu \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s}
+Where,$z_d$ is shown that whether the $d^{th}$ DC is turned on or not and $\psi_d$ is a static cost when a DC is active.
+\begin{equation}
+  z_d =
+    \begin{cases}
+      1 & \sum_{s=1}^{S}y_{s,d} \geq 1 \\
+      0 & \text{otherwise}
+    \end{cases}       
 \end{equation}  
-where, $\nu$ is a design variable to value between the first term of \eqref{eqpsi} which is the total power consumption of physical resources and the second term that is shown the amount of admitted slices to have physical resources.
+So the optimization problem is formulated as follow
+The aim of this paper is minimize the total power of all RUs and the total power consumption of baseband processing at all DCs simultaneously, with the presence of constraints which is written as follow,
+\begin{subequations}
+\begin{alignat}{4}
+\min\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{B}, \boldsymbol{E}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  P_{tot}+ \varphi \phi_{tot} \ \\
+\text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
+ \label{c11} \\
+&p_{r,u(v,i)}^{k,s}  \geq 0  \quad \forall v,\forall i,\forall r,\forall s, \forall k,\label{c12} \\
+&\mathcal{R}_{u_{(v_1,k)}}^e \geq  \mathcal{R}_{min}^{v_1,e} \quad \forall v_1, \label{c13} \\
+&\mathcal{R}_{u_{(v_2,k)}}^u \geq  \mathcal{R}_{min}^{v_2,u} \quad \forall v_2, \label{c14} \\
+&T_{tot}^v \leq T_{tot}^{max,v} \quad \forall v,\label{c15} \\
+&a_{u(v,i)} \leq a_{u(v,i)}\sum_{r}g^r_{u(v,i)} \leq 1 \quad \forall v,\forall i  \\
+& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 \quad \forall s, \label{c21} \\
+& \textstyle  \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s,\label{c23} \\
+ &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}
+\end{alignat}
+\label{constraints}
+\end{subequations}
+
+\newpage
+\newpage
+
 Our goal is to maximize sum-rate and minimize sum-power (the total power of all RUs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,
@@
 \end{subequations}
-\section{Numerical Results}\label{simul}
-
-\section{Conclusion}
 

### 2020-12-21 Latex/journal_v1/pr.tex
improve journal
journal complete

@@
 \begin{equation*}
-\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d} + \sum_{d=1}^{D_c}z_d \psi_d .
+\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s} + \sum_{d=1}^{D_c}z_d \psi_d .
 \end{equation*}
@@
 \end{equation}  
+In addition, $\phi_{s,d}$ is obtained from below
+\begin{equation}
+\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d
+\end{equation}
 So the optimization problem is formulated as follow
@@
 \begin{alignat}{4}
-\min\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{B}, \boldsymbol{E}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  P_{tot}+ \varphi \phi_{tot} \ \\
+\min\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  P_{tot}+ \varphi \phi_{tot} \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
@@
 &a_{u(v,i)} \leq a_{u(v,i)}\sum_{r}g^r_{u(v,i)} \leq 1 \quad \forall v,\forall i  \\
-& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 \quad \forall s, \label{c21} \\
+& \sum_{s=1}^{S}\sum_{v=1}^{V}\sum_{i=1}^{U_v}a_{u(v,i)}g^r_{u(v,i)}e^{k,s}_{r,u(v,i)} \leq 1 \quad \forall r, \label{c21} \\
+&  \sum_{s=1}^{S}b_{v,s} \geq 1 \quad \forall v,\\
 & \textstyle  \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s,\label{c23} \\
@@
 
-\newpage
-\newpage
-
-Our goal is to maximize sum-rate and minimize sum-power (the total power of all RUs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,
-\begin{subequations}
-\begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &  \eta(\boldsymbol{P},\boldsymbol{A})+ \varphi \frac{1}{\psi_{tot}(\boldsymbol{Y})} \\
-\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} \quad \forall s, \forall i,
- \label{c11} \\
-&p_{u_{(v,k)}}  \geq 0  \quad \forall v, \forall k,\label{c12} \\
-&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} \quad \forall v, \forall k,\label{c13} \\
-&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max} \quad \forall s, \forall i, \label{c14}\\
-&D_{s} \leq D_{s}^{max} \quad \forall s,\label{c15} \\
-& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 \quad \forall s, \label{c21} \\
-& \textstyle  \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s,\label{c23} \\
- &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}
-\end{alignat}
-\label{constraints}
-\end{subequations}
-where $\boldsymbol{P} =[p_{u(v,k)}] \:\: \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}] \:\: \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
-the physical DC is mapped to a VNFs of a slice or not.
-Also, $\varphi$ is weighted variable to value between first and second term of objective function.
-\eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively.
-Also \eqref{c13} shows that the rate of each UE is more than a threshold.
-\eqref{c14} and \eqref{c15} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
-Furthermore, \eqref{c21}
-ensures that each service is mapped to at least one slice.
-Also, \eqref{c23}, guarantees that each slice (VNFs in two layers of slices) has been placed to one or more physical resources of DCs.
-Moreover, in \eqref{c22}  $\mathcal{E} = \{M,S,C\}$ and the constraint supports
-that we have enough physical resources for VNFs of each slice.\newline
-The optimization problem in \eqref{constraints} can be decomposed into two independent optimization sub-problems 1 and 2 since the variables can be obtained independently and respectively.
-Firstly we need to solve sub-problem 1.
-After obtaining $\boldsymbol{P}$ and $ \boldsymbol{A}$, sub-problem 2 can be solved by having the value of $ \boldsymbol{A}$.
-The sub-problem 1 is as follow
-\begin{subequations}
-\begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})\\
-\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
-&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
-&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\
-&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i,\label{cc14} \\
-&D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
-& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s.
-\end{alignat}
-\label{constraints1}
-\end{subequations}
-In sub-problem 2, $ \boldsymbol{Y}$ is obtained. The sub-problem 2 is
-\begin{subequations}
-\begin{alignat}{4}
-\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
-\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
- &\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
-\end{alignat}
-\label{constraints2}
-\end{subequations}
-
 \bibliographystyle{IEEEtran}

### 2020-12-22 Latex/journal_v1/V2/pr.tex
add file

--- 2020-12-21 Latex/journal_v1/pr.tex
@@
 \subsection{System Model}
-Suppose we have two service types includes eMBB and URLLC. Assume we have $V_1$ and $V_2$ different applications for the first and second service type, respectively ($V = V_1 + V_2$).
-Assume we have $S$ preallocated slices serving $V$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC) ($S = S_1 + S_2$).
-Each Service $v_j\in \{1,2,...,V_j \} $ consists of $U_{v_j}$ request from the 
+Suppose we have two service types includes eMBB and URLLC. Assume we have $S_1$ and $S_2$ different applications for the first and second service type, respectively ($S = S_1 + S_2$).
+Assume we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC).
+Each Service $s_j\in \{1,2,...,S_j \} $ consists of $U_{s_j}$ request from the 
 single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2\}$ indicate service type).
@@
 Each application request requires specific QoS.
-Based on the request for the application and QoS, UE may be admitted and allocated to slice.
+Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
 Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
@@
 The SNR of $i^{th}$ UE in $v^{th}$ service experienced at slice $s$ on PRB $k$ which is obtained from
- $\rho_{u(v,i)}^{k,s}$ is the SNR 
+ $\rho_{u_i}^{k,s}$ is the SNR 
 \begin{equation}\label{eq2}
-\rho_{u(v,i)}^{k,s} =  \sum_{r=1}^{R}\frac{|p_{r,u(v,i)}^{k,s}{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(v,i)}^{k,s} g_{u(v,i)}^r|^2}{BN_0 + I_{r,u(v,i)}^{k,s}},
+\rho_{u_i}^{k,s} =  \sum_{r=1}^{R}\frac{|p_{r,u_i}^{k,s}{\bold{h}_{r,u_i}^{H \: k,s}} \bold{w}_{r,u_i}^{k,s} g_{u_i}^r|^2}{BN_0 + I_{r,u_i}^{k,s}},
 \end{equation} 
-where $p_{r,u(v,i)}^{k,s}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE in $v^{th}$ service, served at slice $s$ on PRB $k$. 
-${\bold{h}_{r,u(v,i)}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
+where $p_{r,u_i}^{k,s}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE in $v^{th}$ service, served at slice $s$ on PRB $k$. 
+${\bold{h}_{r,u_i}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
 $r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service.
-In addition, $\bold{w}_{r,u(v,i)}^{k,s} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service that is the zero forcing beamforming vector to minimize the interference which is indicated as below
+In addition, $\bold{w}_{r,u_i}^{k,s} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service that is the zero forcing beamforming vector to minimize the interference which is indicated as below
 \begin{equation}
-\bold{w}_{r,u(v,i)}^{k,s} = {\bold{h}_{r,u(v,i)}^{k,s}}({\bold{h}_{r,u(v,i)}^{H \: k,s1}} {\bold{h}_{r,u(v,i)}^{k,s}})^{-1}
+\bold{w}_{r,u_i}^{k,s} = {\bold{h}_{r,u_i}^{k,s}}({\bold{h}_{r,u_i}^{H \: k,s1}} {\bold{h}_{r,u_i}^{k,s}})^{-1}
 \end{equation}
-Moreover, $g_{u(v,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(v,i)}^{k,s1}$ is the power of interfering signals represented as follow
+Moreover, $g_{u_i}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
+Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u_i}^{k,s1}$ is the power of interfering signals represented as follow
 \begin{equation}
 \begin{split}
-I_{r,u(v,i)}^{k,s} &=
- \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u(v,i)}^{k,s}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(v,i)}^{H \: k,s}} \bold{w}_{r',u(v,i)}^{k,s1} g_{u(v,i)}^{r'}|^2}_{\text{(intra-service interference)}}\\
-&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(v,i)}^{H \: k,s}} \bold{w}_{r',u(y,l)}^{k,n} g_{u(y,l)}^{r'}|^2}_{\text{(inter-service interference)}}\\
+I_{r,u_i}^{k,s} &=
+ \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u_i}^{k,s}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u_i}^{H \: k,s}} \bold{w}_{r',u_i}^{k,s1} g_{u_i}^{r'}|^2}_{\text{(intra-service interference)}}\\
+&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u_i}^{H \: k,s}} \bold{w}_{r',u(y,l)}^{k,n} g_{u(y,l)}^{r'}|^2}_{\text{(inter-service interference)}}\\
 \end{split}
 \end{equation}
-where $\gamma_{1} = e^{k,s}_{r,u(v,i)}e^{k,s}_{r',u(v,l)}a_{u(v,i)}a_{u(v,l)} b_{v, s} $
-and $\gamma_{2} = e^{k,s}_{r,u(v,i)}e^{k,n}_{r',u(y,l)}a_{u(v,i)}a_{u(y,l)} b_{v, s} b_{y,n} $.
-Where $a_{u(v,i)} \in \{0,1\}$ is a binary variable to depict user admission.
+where $\gamma_{1} = e^{k,s}_{r,u_i}e^{k,s}_{r',u(v,l)}a_{u_i}a_{u(v,l)} b_{v, s} $
+and $\gamma_{2} = e^{k,s}_{r,u_i}e^{k,n}_{r',u(y,l)}a_{u_i}a_{u(y,l)} b_{v, s} b_{y,n} $.
+Where $a_{u_i} \in \{0,1\}$ is a binary variable to depict user admission.
 $b_{v, s}$ is a binary variable that illustrates whether slice $s$ is allocated to service $v$ or not. 
-$e^{k,s}_{r,u(v,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in service $v$, assigned to $r^{th}$ o-RU using slice $s$ or not.
+$e^{k,s}_{r,u_i}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in service $v$, assigned to $r^{th}$ o-RU using slice $s$ or not.
 
@@
 \subsubsection{Processing Delay}
-Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
-Therefore, the mean arrival data rate of the $v^{th}$ service in the UPF layer is $\alpha_{v}^1 = \sum_{u=1}^{U_v}a_{u(v,i)}\lambda_{u(v,i)}$, where $a_{u(v,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $v^{th}$ service is admitted or not.
+Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u_i}$ for the $i^{th}$ UE of the $v^{th}$ service.
+Therefore, the mean arrival data rate of the $v^{th}$ service in the UPF layer is $\alpha_{v}^1 = \sum_{u=1}^{U_v}a_{u_i}\lambda_{u_i}$, where $a_{u_i}$ is a binary variable which indicates whether the $i^{th}$ UE requested $v^{th}$ service is admitted or not.
 
@@
 \end{equation}
-where, $R_{{tot}_v} = \sum_{u=1}^{U_v}a_{u(v,i)}R_{u(v,i)}$ is the total achievable rate of each service.
+where, $R_{{tot}_v} = \sum_{u=1}^{U_v}a_{u_i}R_{u_i}$ is the total achievable rate of each service.
 So the mean processing delay for each UE in service $v$ is 
@@
 \begin{equation}
-P_r =  \sum_{v=1}^{V} \sum_{i=1}^{U_v} \sum_{s=1}^{S} \sum_{k=1}^{K_s}p_{r,u(v,i)}^{k,s}a_{u(v,i)} b_{v, s} e^{k,s}_{r,u(v,i)}g_{u(v,i)}^r.
+P_r =  \sum_{v=1}^{V} \sum_{i=1}^{U_v} \sum_{s=1}^{S} \sum_{k=1}^{K_s}p_{r,u_i}^{k,s}a_{u_i} b_{v, s} e^{k,s}_{r,u_i}g_{u_i}^r.
 \end{equation}
@@
  \label{c11} \\
-&p_{r,u(v,i)}^{k,s}  \geq 0  \quad \forall v,\forall i,\forall r,\forall s, \forall k,\label{c12} \\
+&p_{r,u_i}^{k,s}  \geq 0  \quad \forall v,\forall i,\forall r,\forall s, \forall k,\label{c12} \\
 &\mathcal{R}_{u_{(v_1,k)}}^e \geq  \mathcal{R}_{min}^{v_1,e} \quad \forall v_1, \label{c13} \\
@@
 &T_{tot}^v \leq T_{tot}^{max,v} \quad \forall v,\label{c15} \\
-&a_{u(v,i)} \leq a_{u(v,i)}\sum_{r}g^r_{u(v,i)} \leq 1 \quad \forall v,\forall i  \\
-& \sum_{s=1}^{S}\sum_{v=1}^{V}\sum_{i=1}^{U_v}a_{u(v,i)}g^r_{u(v,i)}e^{k,s}_{r,u(v,i)} \leq 1 \quad \forall r, \label{c21} \\
+&a_{u_i} \leq a_{u_i}\sum_{r}g^r_{u_i} \leq 1 \quad \forall v,\forall i  \\
+& \sum_{s=1}^{S}\sum_{v=1}^{V}\sum_{i=1}^{U_v}a_{u_i}g^r_{u_i}e^{k,s}_{r,u_i} \leq 1 \quad \forall r, \label{c21} \\
 &  \sum_{s=1}^{S}b_{v,s} \geq 1 \quad \forall v,\\

### 2020-12-23 Latex/journal_v1/V2/pr.tex
journal change

@@
 \subsection{The Achievable Rate}
-The SNR of $i^{th}$ UE in $v^{th}$ service experienced at slice $s$ on PRB $k$ which is obtained from
- $\rho_{u_i}^{k,s}$ is the SNR 
+The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
 \begin{equation}\label{eq2}
-\rho_{u_i}^{k,s} =  \sum_{r=1}^{R}\frac{|p_{r,u_i}^{k,s}{\bold{h}_{r,u_i}^{H \: k,s}} \bold{w}_{r,u_i}^{k,s} g_{u_i}^r|^2}{BN_0 + I_{r,u_i}^{k,s}},
+\rho_{u(s,i)}^{k} =  \sum_{r=1}^{R}\frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
 \end{equation} 
-where $p_{r,u_i}^{k,s}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE in $v^{th}$ service, served at slice $s$ on PRB $k$. 
+where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
 ${\bold{h}_{r,u_i}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 

### 2020-12-26 Latex/journal_v1/V2/pr.tex
journal update

@@
 where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
-${\bold{h}_{r,u_i}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
-$r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service.
-In addition, $\bold{w}_{r,u_i}^{k,s} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service that is the zero forcing beamforming vector to minimize the interference which is indicated as below
+${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
+$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice.
+In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
 \begin{equation}
-\bold{w}_{r,u_i}^{k,s} = {\bold{h}_{r,u_i}^{k,s}}({\bold{h}_{r,u_i}^{H \: k,s1}} {\bold{h}_{r,u_i}^{k,s}})^{-1}
+\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
 \end{equation}
-Moreover, $g_{u_i}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u_i}^{k,s1}$ is the power of interfering signals represented as follow
+Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocate to $s^{th}$ slice or not. 
+Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
 \begin{equation}
 \begin{split}
-I_{r,u_i}^{k,s} &=
- \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u_i}^{k,s}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u_i}^{H \: k,s}} \bold{w}_{r',u_i}^{k,s1} g_{u_i}^{r'}|^2}_{\text{(intra-service interference)}}\\
-&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u_i}^{H \: k,s}} \bold{w}_{r',u(y,l)}^{k,n} g_{u(y,l)}^{r'}|^2}_{\text{(inter-service interference)}}\\
+I_{r,u(s,i)}^{k} &=
+ \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,i)}^{k} g_{u(s,i)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
+&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
 \end{split}
 \end{equation}
-where $\gamma_{1} = e^{k,s}_{r,u_i}e^{k,s}_{r',u(v,l)}a_{u_i}a_{u(v,l)} b_{v, s} $
-and $\gamma_{2} = e^{k,s}_{r,u_i}e^{k,n}_{r',u(y,l)}a_{u_i}a_{u(y,l)} b_{v, s} b_{y,n} $.
-Where $a_{u_i} \in \{0,1\}$ is a binary variable to depict user admission.
-$b_{v, s}$ is a binary variable that illustrates whether slice $s$ is allocated to service $v$ or not. 
-$e^{k,s}_{r,u_i}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in service $v$, assigned to $r^{th}$ o-RU using slice $s$ or not.
+where $\gamma_{1} = e^{k}_{r,u(s,i)}e^{k}_{r',u(s,l)}a_{u(s,i)}a_{u(s,l)}$
+and $\gamma_{2} = e^{k}_{r,u(s,i)}e^{k}_{r',u(n,l)}a_{u(s,i)}a_{u(y,l)}$.
+Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
+$e^{k}_{r,u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
 
-The achievable data rate for the $i^{th}$ UE request in the $v_{1}^{th}$ application of service type 1 (eMBB) can be written as
+The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as
 \begin{equation}\label{eq1}
-\mathcal{R}_{u(v_1,i)}^{e} = \sum_{s_1=1}^{S_1}\sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{u(v_1,i)}^{k,s_1}})a_{u(v_1,i)} b_{v_1, s_1} e^{k,s_1}_{r,u(v_1,i)},
+\mathcal{R}_{u(s_1,i)}^{e} = \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},
 \end{equation}
@@
 
-Since the blocklength in URLLC is finite, the achievable data rate for the $i^{th}$ UE request in the $v_{2}^{th}$ application of service type 2 (URLLC) is not achieved from Shannon Capacity formula.
+Since the blocklength in URLLC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{2}^{th}$ application of service type 2 (URLLC) is not achieved from Shannon Capacity formula.
 So, for the short packet transmission the achievable data rate is approximated from follow
 \begin{equation}\label{eq1}
-\mathcal{R}_{u(v_2,i)}^{u} = \sum_{s_2=1}^{S_2}\sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(v_2,i)}^{k,s_2}})- \zeta_{u(v_2,i)}^{k,s_2}){\beta}_{u(v_2,i)}^{k,s_2}
+\mathcal{R}_{u(s_2,i)}^{u} = \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}
 \end{equation}
-Where ${\beta}_{u(v_2,i)}^{k,s_2}=a_{u(v_2,i)} b_{v_2, s_1} e^{k,s_2}_{u(v_2,i)}$
-and $\zeta_{u(v_2,i)}^{k,s_2} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(v_2,i)}^{k,s_2}}{N_{u(v_2,i)}^{k,s_2}}})$
+Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
+and $\zeta_{u(s_2,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
 Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
-$C_{u(v_2,i)}^{k,s_2} = 1 - \frac{1}{(1+\rho_{u(v_2,i)}^{k,s_2})}$ depicts the channel dispersion of UE  $i$ requesting service $v_2$, experiencing PRB $k$ at slice $s_2$  and
-$N_{u(v_2,i)}^{k,s_2}$ represents the blocklength of it.
+$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
+$N_{u(s_2,i)}^{k}$ represents the blocklength of it.
 
@@
 \subsubsection{Processing Delay}
-Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u_i}$ for the $i^{th}$ UE of the $v^{th}$ service.
-Therefore, the mean arrival data rate of the $v^{th}$ service in the UPF layer is $\alpha_{v}^1 = \sum_{u=1}^{U_v}a_{u_i}\lambda_{u_i}$, where $a_{u_i}$ is a binary variable which indicates whether the $i^{th}$ UE requested $v^{th}$ service is admitted or not.
+Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
+Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.
 
-Assume the mean arrival data rate of the UPF layer ($\alpha_{v}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{v}^C$) and O-DU ($\alpha_{v}^D$).
-so $\alpha_{v} =\alpha_{v}^U \approx \alpha_{v}^C \approx \alpha_{v}^D$.
-since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{v}$.
+Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$).
+so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
+since, by using Burke’s Theorem, the mean arrival data rate of the second and third layer which are processed in the first layer is still Poisson with rate $\alpha_{s}$.
 It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
 Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $v^{th}$ service in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
+Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
 \begin{equation}
 \begin{split}
-T_{DU}^{v} &= \frac{1}{\mu_d - \alpha_{v}/{M_{v,d}}},\\
-T_{CU}^{v} &= \frac{1}{\mu_c - \alpha_{v}/{M_{v,c}}}\\
-T_{UPF}^{v} &= \frac{1}{\mu_u - \alpha_{v}/{M_{v,u}}}\\
+T_{DU}^{s} &= \frac{1}{\mu_d - \alpha_{s}/{M_s^{d}}},\\
+T_{CU}^{s} &= \frac{1}{\mu_c - \alpha_{s}/{M_s^{c}}}\\
+T_{UPF}^{s} &= \frac{1}{\mu_u - \alpha_{s}/{M_s^{u}}}\\
 \end{split}
 \end{equation}
-Where $M_{v,d} = \sum_{s=1}^{S}M_s^{d} b_{v,s}$, $M_{v,c} = \sum_{s=1}^{S}M_s^{c} b_{v,s}$ and 
-$M_{v,u} = \sum_{s=1}^{S}M_s^{u} b_{v,s}$ 
-are the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. Since, each service may use more than one slice, the data packets of each service is divided between VNFs of slices allocated to service.
+Where $M_s^{d}$, $M_s^{c}$ and 
+$M_s{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
 Moreover, $1/\mu_d$, $1/\mu_c$ and $1/\mu_u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
-Besides, $\alpha_{v}$ is the  arrival rate which is divided
-by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each service 
-$v$ is $\alpha_{v}/{M_{v,i}}$ $ i \in \{d,c, u\}$.
+Besides, $\alpha_{s}$ is the  arrival rate which is divided
+by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
+$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.
 
-In addition, $T_{RU}^{v}$ is the mean transmission delay of $v^{th}$ service on the wireless link.
+In addition, $T_{RU}^{s}$ is the mean transmission delay of $s^{th}$ slice on the wireless link.
 The arrival data rate of wireless link is equal to the arrival data rate of load balancers for each service.
@@
 Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
- an exponential distribution with mean $1/(R_{{tot}_v})$ and can be modeled as a M/M/1 queue.
+ an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue.
  %\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. 
@@
 \begin{equation}
- T_{RU}^{v} = \frac{1}{R_{{tot}_v} - \alpha_{v}};
+ T_{RU}^{s} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
 \end{equation}
-where, $R_{{tot}_v} = \sum_{u=1}^{U_v}a_{u_i}R_{u_i}$ is the total achievable rate of each service.
-So the mean processing delay for each UE in service $v$ is 
+where, $R_{{tot}_s} = \sum_{u=1}^{U_s}a_{u(s,i)}R_{u(s,i)}$ is the total achievable rate of each service.
+So the mean processing delay for each UE in slice $s$ is 
 \begin{equation}
-T_{process}^{v} =  T_{RU}^{v} + T_{DU}^{v} + T_{CU}^{v} + T_{UPF}^{v}
+T_{process}^{s} =  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s}
 \end{equation}
@@
 \begin{split}
-T_{front} =& \frac{\alpha_{v}^{f}}{R_f} \\
-T_{mid} =&  \frac{\alpha_{v}^{m}}{R_m} \\
-T_{back} =& \frac{\alpha_{v}^{b}}{R_b} \\
-T_{trans2net} =& \frac{\alpha_{v}^{t}}{R_t} \\
+T_{front} =& \frac{\alpha_{s}^{f}}{R_f} \\
+T_{mid} =&  \frac{\alpha_{s}^{m}}{R_m} \\
+T_{back} =& \frac{\alpha_{s}^{b}}{R_b} \\
+T_{trans2net} =& \frac{\alpha_{s}^{t}}{R_t} \\
 \end{split}
@@
 Where, $R_f$, $R_m$, $R_b$ and $R_t$ are the rate of transmission in fronthaul, midhaul, backhaul and the link to transmit data to internet, respectively.
-Furthermore, the mean arrival data rate of the each link ($\alpha_{v}^i$ , $i \in \{f,m,b,t\}$) is approximately equal to others ($\alpha_{v} \approx \alpha_{v}^i$ , $i \in \{f,m,b,t\}$).  
+Furthermore, the mean arrival data rate of the each link ($\alpha_{s}^i$ , $i \in \{f,m,b,t\}$) is approximately equal to others ($\alpha_{s} \approx \alpha_{s}^i$ , $i \in \{f,m,b,t\}$).  
 \subsection{Physical Data Center Resource}
@@
 \subsection{Problem Statement}
-In this system, the goal is to minimize the cost of the system.
+%In this system, the goal is to minimize the cost of the system.
 Power of each O-RU is obtained as below
 \begin{equation}
-P_r =  \sum_{v=1}^{V} \sum_{i=1}^{U_v} \sum_{s=1}^{S} \sum_{k=1}^{K_s}p_{r,u_i}^{k,s}a_{u_i} b_{v, s} e^{k,s}_{r,u_i}g_{u_i}^r.
+P_r =  \sum_{s=1}^{S} \sum_{i=1}^{U_v} \sum_{k=1}^{K_s}p_{r,u(s,i)}^{k}a_{u(s,i)} e^{k}_{r,u(s,i)}g_{u(s,i)}^r.
 \end{equation}
@@
 \end{equation}
-So the optimization problem is formulated as follow
-The aim of this paper is minimize the total power of all RUs and the total power consumption of baseband processing at all DCs simultaneously, with the presence of constraints which is written as follow,
+So the optimization problem is formulated as follow.
+The aim of this paper is maximize the sum rate of all UEs with the presence of constraints which is written as follow,
 \begin{subequations}
 \begin{alignat}{4}
-\min\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  P_{tot}+ \varphi \phi_{tot} \ \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  P_{tot}+ \varphi \phi_{tot} \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r

### 2020-12-29 Latex/journal_v1/V2/pr.tex
add file
journal improve

@@
 \begin{equation}\label{eq2}
-\rho_{u(s,i)}^{k} =  \sum_{r=1}^{R}\frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
+\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
 \end{equation} 
@@
 
-The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as
+The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
 \begin{equation}\label{eq1}
-\mathcal{R}_{u(s_1,i)}^{e} = \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},
+\begin{split}
+\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{r=1}^{R}\sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
+\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
+\end{split}
 \end{equation}
 where $B$ is the bandwidth of system. 
-
+$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
 Since the blocklength in URLLC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{2}^{th}$ application of service type 2 (URLLC) is not achieved from Shannon Capacity formula.
 So, for the short packet transmission the achievable data rate is approximated from follow
-\begin{equation}\label{eq1}
-\mathcal{R}_{u(s_2,i)}^{u} = \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}
+\begin{equation}\label{eq11}
+\begin{split}
+\mathcal{R}_{u(s_2,i)}^{u,r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}\\
+\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 
+\end{split}
 \end{equation}
@@
 $N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
-
+$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
 \subsection{Mean Delay}
@@
 where $\bar{\Omega}_{s}^f\in \mathbb{C}^{4}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f$ indicate the amount of required memory, storage, CPU and and Network Bandwidth, respectively.
-Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice is defined as
+Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice in DU, CU and UPF is defined as below, respectively
 \begin{equation}
-\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C, N\}.
+\begin{split}
+&\bar{\Omega}_{\mathfrak{z},s}^{tot,d} = \sum_{f=1}^{M_{s}^d}\bar{\Omega}_{\mathfrak{z},s}^{f,d} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
+&\bar{\Omega}_{\mathfrak{z},s}^{tot,c} = \sum_{f=1}^{M_{s}^c}\bar{\Omega}_{\mathfrak{z},s}^{f,c} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
+&\bar{\Omega}_{\mathfrak{z},s}^{tot,u} = \sum_{f=1}^{M_{s}^u}\bar{\Omega}_{\mathfrak{z},s}^{f,u} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
+\end{split}
 \end{equation}
-Where, $F_s = M_{s}^d + M_{s}^c + M_{s}^u$
+Where, $\bar{\Omega}_{\mathfrak{z},s}^{f,d}$, $\bar{\Omega}_{\mathfrak{z},s}^{f,c}$ and $\bar{\Omega}_{\mathfrak{z},s}^{f,u}$ are the amount of resource that a VNF required in DU, CU and UPF, respectively.
+\begin{equation}
+ \bar{\Omega}_{\mathfrak{z},s}^{tot} = \bar{\Omega}_{\mathfrak{z},s}^{tot,d}+ \bar{\Omega}_{\mathfrak{z},s}^{tot,c}+\bar{\Omega}_{\mathfrak{z},s}^{tot,u}
+\end{equation} 
 Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
@@
 Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
-$\phi_{s,d}$. So the total power of the system for all active DCs that are connected to slices can be represented as
+$\phi_{s}$. So the total power of the system for all active DCs that are connected to slices can be represented as
 \begin{equation*}
@@
 \end{equation}  
-In addition, $\phi_{s,d}$ is obtained from below
+In addition, $\phi_{s}$ is obtained from below
 \begin{equation}
@@
 \end{equation}
+Where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively. 
 So the optimization problem is formulated as follow.
-The aim of this paper is maximize the sum rate of all UEs with the presence of constraints which is written as follow,
+The aim of this paper is to maximize the benefits and minimize the cost.
+So our goal is to maximize sum rate of all UEs and minimize the total cost of the system with the presence of constraints which is written as follow,
 \begin{subequations}
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  P_{tot}+ \varphi \phi_{tot} \ \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}- \eta(P_{tot}+ \varphi \phi_{tot}) \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
@@
 &p_{r,u_i}^{k,s}  \geq 0  \quad \forall v,\forall i,\forall r,\forall s, \forall k,\label{c12} \\
-&\mathcal{R}_{u_{(v_1,k)}}^e \geq  \mathcal{R}_{min}^{v_1,e} \quad \forall v_1, \label{c13} \\
-&\mathcal{R}_{u_{(v_2,k)}}^u \geq  \mathcal{R}_{min}^{v_2,u} \quad \forall v_2, \label{c14} \\
-&T_{tot}^v \leq T_{tot}^{max,v} \quad \forall v,\label{c15} \\
-&a_{u_i} \leq a_{u_i}\sum_{r}g^r_{u_i} \leq 1 \quad \forall v,\forall i  \\
-& \sum_{s=1}^{S}\sum_{v=1}^{V}\sum_{i=1}^{U_v}a_{u_i}g^r_{u_i}e^{k,s}_{r,u_i} \leq 1 \quad \forall r, \label{c21} \\
-&  \sum_{s=1}^{S}b_{v,s} \geq 1 \quad \forall v,\\
-& \textstyle  \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s,\label{c23} \\
- &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}
+&\mathcal{R}_{u_{(s_1,i)}}^e \geq  a_{u(s_1,i)}\mathcal{R}_{min}^{s_1,e} \quad \forall s_1, \label{c13} \\
+&\mathcal{R}_{u_{(s_2,i)}}^u \geq  a_{u(s_2,i)}\mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
+&T_{tot}^s \leq T_{tot}^{max,s} \quad \forall s,\label{c15} \\
+&a_{u(s,i)} \leq a_{u(s,i)}\sum_{r}g^r_{u(s,i)}  \quad \forall s,\forall i, \label{c16}  \\
+& a_{u(s,i)}g^r_{u(s,i)} \leq a_{u(s,i)}g^r_{u(s,i)}\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)}  \quad \forall s,i , \label{c21} \\
+& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c24}\\ 
+& \phi_{s} \leq \phi_{max}, \quad \forall s \label{c22} \\
+ &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d} 
+ \quad \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c23}
 \end{alignat}

### 2020-12-30 Latex/journal_v1/V2/pr.tex
add  sth

@@
 \begin{split}
-\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{r=1}^{R}\sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
+\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{r=1}^{R}\sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
 \mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
@@
 &\mathcal{R}_{u_{(s_2,i)}}^u \geq  a_{u(s_2,i)}\mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
-&T_{tot}^s \leq T_{tot}^{max,s} \quad \forall s,\label{c15} \\
-&a_{u(s,i)} \leq a_{u(s,i)}\sum_{r}g^r_{u(s,i)}  \quad \forall s,\forall i, \label{c16}  \\
-& a_{u(s,i)}g^r_{u(s,i)} \leq a_{u(s,i)}g^r_{u(s,i)}\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)}  \quad \forall s,i , \label{c21} \\
-& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c24}\\ 
-& \phi_{s} \leq \phi_{max}, \quad \forall s \label{c22} \\
+& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
+&T_{tot}^s \leq T_{tot}^{max,s} \quad \forall s,\label{c16} \\
+&a_{u(s,i)} \leq a_{u(s,i)}\sum_{r}g^r_{u(s,i)}  \quad \forall s,\forall i, \label{c17}  \\
+& a_{u(s,i)}g^r_{u(s,i)} \leq a_{u(s,i)}g^r_{u(s,i)}\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)}  \quad \forall s,i , \label{c18} \\
+& \phi_{s} \leq \phi_{max}, \quad \forall s \label{c19} \\
  &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d} 
- \quad \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c23}
+ \quad \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c20}
 \end{alignat}
@@
 \end{subequations}
+where $\boldsymbol{P} =[p_{u(s,i)}] \:\: \forall s , \forall i $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{u(s,i)}] \:\: \forall s , \forall i $ denotes the binary variable for UE admission,
+$\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i \forall r, \forall k$ indicate the binary variable for PRB association.
+Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i \forall r$ is a binary variable for O-RU association.
+Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
+the physical DC is mapped to a VNFs of a slice or not.
+Also, $\eta$ is weighted variable to value between the benefit and the cost term of objective function.
+\eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively. 
+Also \eqref{c13} and \eqref{c14} shows that the rate of each UE requesting eMBB and URLLC is more than a threshold, respectively.
+\eqref{c15} and \eqref{c16} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
+\eqref{c17} and \eqref{c18} guarantee that if a UE in admitted by the system, O-RU and PRB is associated to it, respectively.
+In addition, \eqref{c19} indicate that the static cost of energy of VNFs in each slice do not exceed from the threshold. 
+Moreover, in \eqref{c20}  $\mathcal{E} = \{M,S,C, N\}$ and the constraint supports
+that we have enough physical resources for VNFs of each slice.
 

### 2021-01-02 Latex/journal_v1/V2/pr.tex
latex finish system model

@@
 
+\begin{figure}
+  \centering
+    \includegraphics[width=\linewidth]{Drawing11.pdf}
+  \caption{Network sliced ORAN system}
+  \label{fig:c11}
+\end{figure}
+
+In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
 \section{System Model and Problem Formulation}\label{systemmodel}
@@
 Furthermore, the mean arrival data rate of the each link ($\alpha_{s}^i$ , $i \in \{f,m,b,t\}$) is approximately equal to others ($\alpha_{s} \approx \alpha_{s}^i$ , $i \in \{f,m,b,t\}$).  
+\subsection{Delay for URLLC}
+As we know, UEs request URLLC services, require services with low latency.
+For the M/M/1 system, the probability of the delay for each application $s$ in the UPF, CU, DU and RU is as follow, respectively
+\begin{equation}
+\begin{split}
+P_r\{T_{UPF}^{s} \geq T_{UPF}^{max}\} &= e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}\\
+P_r\{T_{CU}^{s} \geq T_{CU}^{max}\} &= e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}\\
+P_r\{T_{DU}^{s} \geq T_{DU}^{max}\} &= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}\\
+P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} &= e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}\\
+\end{split}
+\end{equation} 
+So the probability of coincidence of these events is as follow
+\begin{equation}
+P_r\{E_1, E_2, E_3, E_4\} = A_1 A_2 A_3 A_4,
+\end{equation}
+Where $E_1 = T_{UPF}^{s} \geq T_{UPF}^{max}$, $E_2 =T_{CU}^{s} \geq T_{CU}^{max} $, $E_3 =T_{DU}^{s} \geq T_{DU}^{max} $ and $E_4 =T_{RU}^{s} \geq T_{RU}^{max} $.
+Also $A_1=e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}$, $A_2=e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}$, $A_3= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}$ and $A_4 = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}$.
 \subsection{Physical Data Center Resource}
@@
 &T_{tot}^s \leq T_{tot}^{max,s} \quad \forall s,\label{c16} \\
+& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
 &a_{u(s,i)} \leq a_{u(s,i)}\sum_{r}g^r_{u(s,i)}  \quad \forall s,\forall i, \label{c17}  \\
@@
 \eqref{c15} and \eqref{c16} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
+\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
 \eqref{c17} and \eqref{c18} guarantee that if a UE in admitted by the system, O-RU and PRB is associated to it, respectively.

### 2021-01-04 Latex/journal_v1/V2/pr.tex
change system model image
journal okey

@@
   \centering
-    \includegraphics[width=\linewidth]{Drawing11.pdf}
+    \includegraphics[scale = 0.4]{draw1.pdf}
   \caption{Network sliced ORAN system}
@@
 \begin{split}
-\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{r=1}^{R}\sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
+\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
 \mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
@@
 \end{equation}
-The total power cost of O-RUs for transmitting data to UE is depicted as follow
-\begin{equation}
-P_{tot} = \sum_{r=1}^{R}P_r
-\end{equation}
+%The total power cost of O-RUs for transmitting data to UE is depicted as follow
+%\begin{equation}
+%P_{tot} = \sum_{r=1}^{R}P_r
+%\end{equation}
 Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
@@
 So the optimization problem is formulated as follow.
-The aim of this paper is to maximize the benefits and minimize the cost.
-So our goal is to maximize sum rate of all UEs and minimize the total cost of the system with the presence of constraints which is written as follow,
+The aim of this paper is to maximize the sum rate of all UEs  with the presence of constraints which is written as follow,
 \begin{subequations}
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}- \eta(P_{tot}+ \varphi \phi_{tot}) \ \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}} \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
  \label{c11} \\
-&p_{r,u_i}^{k,s}  \geq 0  \quad \forall v,\forall i,\forall r,\forall s, \forall k,\label{c12} \\
+&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
 &\mathcal{R}_{u_{(s_1,i)}}^e \geq  a_{u(s_1,i)}\mathcal{R}_{min}^{s_1,e} \quad \forall s_1, \label{c13} \\
@@
 & a_{u(s,i)}g^r_{u(s,i)} \leq a_{u(s,i)}g^r_{u(s,i)}\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)}  \quad \forall s,i , \label{c18} \\
-& \phi_{s} \leq \phi_{max}, \quad \forall s \label{c19} \\
+& \phi_{tot}  \leq \phi_{max}, \label{c19} \\
  &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d} 

### 2021-03-04 Latex/tehran-thesis - Copy/tex/chapter4.tex

@@
 همانند فصل قبل، 
-فرض کنید توان مصرفی پردازش باند پایه در هر مرکز داده ی $d$ که به \lr{VNF} های یک برش $s$ متصل می باشد در هر زمان t با   
+فرض کنید توان مصرفی پردازش باند پایه در هر مرکز داده ی $d$ که به \lr{VNF} های یک برش $s$ سرویس می‌دهد در هر زمان t با   
 $\phi_{s,d}(t)$
 نشان داده شده است.
-بنابراین می توان توان کل سیستم را برای کلیه مرکز داده های فعال که به برش متصل هستند ،بدین صورت نشان داد
+بنابراین می توان توان کل سیستم را برای کلیه مرکز داده های فعال که به برش شبکه سرویس دهی می‌کنند، بدین صورت نشان داد
 \begin{equation*}

### 2021-03-04 NetworkSlicing/report123/report2.tex

--- 2020-10-23 NetworkSlicing/report123/report1.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
-
-\title{NetworkSlicing}
-\author{Mojdeh Karbalaee}
-\date{May 2020}
-
-\usepackage{natbib}
-\usepackage{graphicx}
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage[T1]{fontenc}
@@
 
+\title{Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}
+}
+%
+%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%mojdeh.karbalaee@ut.ac.ir}
+%\and
+%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%vmansouri@ut.ac.ir}
+%\and
+%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%salar.nouri@ut.ac.ir}
+%}
+  \author{
+    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
+    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
+    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
+    \vspace{-.2cm}
+  }
+  }
+
 \maketitle
 
-\section{Network Slicing}
+\begin{abstract}
+
+\end{abstract}
+\begin{IEEEkeywords}
+
+\end{IEEEkeywords}
+\section{introduction}
 Network slicing, where several logical
@@
 shared network infrastructure.
+
 \begin{figure}[h!]
 \centering
-\includegraphics[scale=0.4]{Capture1.PNG}
+\includegraphics[width=0.4\textwidth]{Capture1.PNG}
 \caption{ Big data driven networking}
@@
 \end{figure}
+
 A critical component of network slicing is resource allocation, which needs
@@
 performance of other slices which are sharing the resources.
-This means that providing protection from other slices is one
-To enable Internet of things (IoT) including high data rate, numerous devices
-connection and low service latency,
-network slicing and fog computing have been envisioned as
+This means that providing protection from other slices is one to enable Internet of things (IoT) applications, including high data rate, numerous devices
+connection and low service latency. Network slicing and fog computing have been envisioned as
 promising solutions in service-oriented 5G architecture.
+
 \begin{figure}[h!]
 \centering
-\includegraphics[scale=0.5]{Capture.PNG}
+\includegraphics[width=0.4\textwidth]{Capture.PNG}
 \caption{ Service-oriented Architecture of Fog-assisted 5G Network with Network Slicing}
@@
 \end{figure}
-\section{System Model}
+
 Assume a system model with different types of user equipment (UE).
@@
 assigned radio resources with short delay, in comparison
-with the dynamic slice.\citep{schmidt2019slice}
+with the dynamic slice \cite{schmidt2019slice}.
 \end{itemize}
-\section{introduction}
+
+\subsection{Introduction to Network slicing}
 Network slicing is an important network architecture innovation in 5G that is also expected to be inherited in the next generation. Network slicing enables the coexistence of
@@
 reduces capital expense in network deployment and operation. Second, network slicing provides the potential to create customized slices for different service types with various
-QoS requirements, which can achieve service differentiation
+Quality of Service (QoS) requirements, which can achieve service differentiation
 and guarantee service level agreement (SLA) for each service
@@
 \item Simplified service chains: In contrast to traditional cellular communications in which all services consist of the
-same functions, in Network Slicing each service may rely
-on a different subset of functions.
+same functions, in network slicing each service may rely on a different subset of functions.
 \item Flexible VNF placement: NFV introduces an additional
@@
 an abstraction of the physical resources and makes slice
-management transparent to the slice tenant
+management transparent to the slice tenant.
 \end{itemize}
-We have core and ran slicing in Network Slicing architecture.
+We have core and ran slicing in network slicing architecture.
 RAN slicing faces the following unique challenges: 
@@
 Similarly, the allocation of
-multiple network resources is intertwined, which complicates the RAN slicing. A joint multiple network resource allocation scheme should be judiciously designed
-to maximize network welfare; 
+multiple network resources is intertwined, which complicates the RAN slicing. \textbf{A joint multiple network resource allocation scheme should be judiciously designed
+to maximize network welfare.}
 \item  Strict QoS requirements – Compared with traditional 4G
@@
 latency. Especially, the typical URLLC service in 5G
-requires ultra-high reliability (e.g., 99.999%), which is
+requires ultra-high reliability (e.g., 99.999), which is
 much stricter than that of other services. In addition, the
@@
 QoS provisioning is unsuitable for short-length packet
-URLLC services with ultra-high reliability. Thus, an accurate QoS provisioning for URLLC services is desired
-in the RAN slicing framework; 
+URLLC services with ultra-high reliability. Thus, \textbf{an accurate QoS provisioning for URLLC services is desired
+in the RAN slicing framework.}
 \item  User mobility – Due to the high network density, users
@@
 slices or creating new slices will be triggered, which
-incurs slice reconfiguration overhead. Thus, dynamic yet
-efficient RAN slicing to accommodate user mobility remains a challenging issue.\cite{aiNS}
+incurs slice reconfiguration overhead. Therefore, \textbf{dynamic yet
+efficient RAN slicing to accommodate user mobility remains a challenging issue} \cite{aiNS}.
 \end{itemize}
+
 \section{system model and main problem}
-In the network slicing architecture, each service is admitted by specific slice. Also each service has a special Qos \footnote{Quality of Service} that must be reached. 
-Qos includes 
+In the network slicing architecture, each service is admitted by specific slice. Also each service has a special QoS that must be reached. 
+QoS parameters include:
+
 \begin{itemize}
-\item delay
-\item throughput
-\item packetloss
-\item out of order delivery
+\item Delay
+\item Throughput
+\item Packet loss
+\item Out of order delivery
 \end{itemize}
+
 Different services have one or more of these QoS.
@@
 issues in large-scale networks.
-Cooperative Game with Distributed Learning
-While existing applications of distributed learning in this field generally consider non-cooperative games where the Nash
+
+Cooperative Game with Distributed Learning while existing applications of distributed learning in this field generally consider non-cooperative games where the Nash
 equilibriums are achieved, there is a great potential to adopt the concept of cooperative game, where tenants/slices can learn to
@@
 In this way, a Pareto optimum can be expected instead of the Nash equilibrium.
+
 \subsection{system model}
@@
 So each service $v$ needs specific demands $\mathbf{d} = \{d_1, ..., d_{n_v}\}$.
-The target is to maximize long-term reward expectation $E\{R(\mathbf{q},\mathbf{d})\}$
+The target is to maximize long-term reward expectation $E\{R(\mathbf{q},\mathbf{d})\}$.
 \begin{subequations}
 \begin{alignat}{4}
-\text{argmax}_{\mathbf{q}} E\{R(\mathbf{q},\mathbf{d})\} \\
+\text{argmax}_{\mathbf{d}} E\{R(\mathbf{q},\mathbf{d})\} \\
 \text{subject to} \quad  & \mathbf{q} , \mathbf{d}  
@@
 where $w_v$ is the bandwidth of service $v$.
-\bibliographystyle{plain}
+\bibliographystyle{IEEEtran}
 \bibliography{references}

### 2021-03-04 NetworkSlicing/report_ns/report.tex

--- 2020-05-12 Latex/tex/pr.tex
@@
 
-\title{Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}
+\title{System Model\vspace{-.1cm}
 }
@@
 \begin{abstract}
-Open radio access network (ORAN) alliance which has been formed recently establishes a flexible,  open, and smart radio access network (RAN) by combing the ideas from xRAN and cloud RAN (C-RAN).
-ORAN divides the functions of the RAN into three parts, namely remote unit (RU), distributed unit (DU), and central unit (CU).
-While RU contains lower PHY functions, DU contains higher PHY, MAC, and RLC and CU contains RRC, PDCP, and SDAP.
-CU and DU are implemented as virtual network functions (VNFs) running on a cloud environment.
-Interfaces between RU, CU, and DU are open standard interfaces.
-Network slicing as a new concept in 5G systems is used to share the network resources between various services while the operation of one service does not affect another service.
-In this paper, we study the problem of RAN network slicing in an ORAN system.
-We formulate the problem of wireless link scheduling, mapping the slices to the services, and mapping the physical data centers resource to slices.
-The objective is to jointly maximize the energy efficiency and minimize power consumption of RUs and the cost of physical resources in a downlink channel.
-The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems.
-Heuristic algorithms are proposed for each of the sub-problems.
+
 \end{abstract}
+\begin{IEEEkeywords}
 
-\begin{IEEEkeywords}
-Open RAN (ORAN), network slicing, energy efficiency.
 \end{IEEEkeywords}
-
-\section{Introduction}
-Open RAN (ORAN), as the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G networks to extensively enhance the RAN performance.
-The core idea of C-RAN is to split the radio remote head (RRU) from the baseband unit (BBU).
-Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1,frdl,simeone2016cloud,motalleb2017optimal}.
-On the other hand, xRAN technology has three fundamental features.
-The control plane is decoupled from user plane.
-Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
-Moreover, open north-bound and south-bound interfaces are introduced \cite{xran}.
-
-ORAN virtualizes the elements of the radio access networks, separates them and defines appropriate open interfaces for connection of these elements.
-Moreover, ORAN uses machine learning techniques to develop smarter RAN layers in its architecture.
-In an innovative ORAN system, the programmable RAN software is decoupled from hardware \cite{oran1}.
-Open interface is one of the most crucial properties for ORAN to enable mobile network operators (MNOs) to define their own services.
-The concept of software defined network (SDN), which is the separation of control plane from user plane, is deployed in an intelligent ORAN architecture.
-Moreover, this separation promotes RRM to use non-realtime (RT) and near-realtime (NRT) RAN Intelligent Controller (RIC).
-In the ORAN architecture, distributed unit (DU) is a logical node having RLC/MAC/High-PHY layer.
-Moreover, central unit (CU) is a logical node having RRC, SDAP and PDCP. Also, radio unit (RU) is a logical node having LOW-PHY layer and
-RF processing \cite{oranpaper}.
-ORAN introduces interfaces such as open fronthaul interface that connects DU and RU (i.e., E2 interface), and an A1 interface between orchestration/NMS layer containing the non-real-time RIC (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC (RIC near-RT) function.
-
-To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and referred to as network functions virtualization (NFV).
-Virtual network functions (VNFs) are functional blocks of the system.
-5G networks are expected to host several services with different requirements simultaneously.
-Network slicing is considered as a solution for such demand.
-A network slice is a logical end-to-end network which provides service with specific requirements.
-Multiple network slices run on the same network infrastructure which are managed and operated independently \cite{lee2018dynamic}.
-Slicing can be defined for the RAN, for the core network or both of them \cite{ns1}.
-
-Based on their type of service request, user equipments (UEs) are classified into various services, where UEs in the same service have similar service requests.
-In addition, each service is mapped to one or more slices based on the resources of the slices.
-Each VNF of the ORAN is mapped to one or more virtual machines (VMs) in the data center.
-For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.
-
-%The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}.
-In \cite{oranT},  the evolution of RAN in the  5G network is described.
-The architecture of C-RAN and xRAN is expressed and development of the ORAN from C-RAN and xRAN is explained.
-Also requirements of the network in terms of capacity and latency is taken into account.
-In \cite{oran12},  the ORAN architecture is studied.
-The eight working groups are discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software.
-To the best of our knowledge, there is not work in the literature to model ORAN systems.
-
-%We shortly review related works in the area of C-RAN and xRAN.
-In \cite{motalleb2017optimal}, power allocation in C-RAN architecture, with limited fronthaul capacity in clustered network is studied.
-In \cite{lee2018dynamic}, dynamic network slicing is considered in heterogeneous CRAN (H-CRAN) to maximize the weighted sum-rate.
-Also, two level network slicing (upper and lower level) is done.
-The admission of UEs is maximized using the heuristic algorithms.
-In addition, the allocation of BBU capacity to UEs is considered.
-In \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting} minimization of cost obtained by power consumption, also cloud processing and limited power for each RU is considered.
-Furthermore, the processing delay of each VM and wireless transmission delay are taken into account.
-In \cite{frdl}, the processing and transmission delay is modeled as a M/M/1 queue.
-In \cite{guo2016exploiting}, M/D/1 queue is used to modeled the transmission delay.
-
-\begin{figure}
-  \centering
-    \includegraphics[scale=0.55]{c7.pdf}
-  \caption{Network sliced ORAN system}
-  \label{fig:c11}
-\end{figure}
-
-In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
-The RAN is divided into three layers including RU, DU, and CU with open interfaces.
-DU and CU are running on general purpose data centers.
-UEs are divided to different services according to their requirements.
-RAN resources are partitioned into slices to provide requirements of services.
-Optimal power allocation and joint mapping of slices to services are applied.
-In addition, mapping slices to physical resources is taken into account.
-The contributions of the paper are as follows:
-\begin{itemize}
-\item Joint network slicing and resource allocation is considered in an ORAN system.
-\item We formulate the problem of assigning UEs to services, services to slices, and physical wireless and data center resources to the slices as an optimization problem.
-\item Novel heuristic algorithms are applied for these sub-problems to efficiently obtain the solution.
-\end{itemize}
-
-The rest of the paper is organized as follows.
-In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is introduced.
-Then, problem statement is explained and decomposed into two independent sub-problems.
-In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results are provided to investigate the performance of the algorithms.
-
 \section{System Model and Problem Formulation}\label{systemmodel}
@@
 Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
-single-antenna UEs that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
+single-antenna UEs that require certain service.
+Each Service is one of the instance of 3 type service contains URLLC, eMBB, MIoT.
+Each slice $s \in \{1,2,...,S \}$ consists of  $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs and physical resources from Data Centers.
 Slices can have shared resources.
-All RUs in a slice, that are mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}.
+All RUs can serve any users based on their distance and can transmit signals cooperatively to all the UEs in a specific place.
 Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.
@@
 \begin{equation}\label{eq1}
-\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}}),
+\mathcal{R}_{u(v,i)} = \sum_{s} B_s \log_2({1+ \rho_{u(v,i)} b_{u(v,i)}}) a_{v,s},
 \end{equation}
-where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from
+where $B_s$ is the bandwidth of slice, $b_{u(v,i)}$ is a binary number represent whether the $i^{th}$ user in service $v$ is admitted in system or no and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from
 \begin{equation}\label{eq2}
-\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
+\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{j=1}^{J}|\bold{h}_{R_j,u(v,i)}^H \bold{w}_{R_j,u(v,i)}|^2 e_{j,u(v,i)}}{BN_0 + I_{u(v,i)}},
 \end{equation}
-where $p_{u(v,i)}$ represents the transmission power allocated by RUs to $i^{th}$ UE in $v^{th}$ service, and
-$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
-In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service.
+where $p_{u(v,i)}$ represents the transmission power allocated by RUs to $i^{th}$ UE in $v^{th}$ service,
+$e_{j,u(v,i)}$ is the association of RRH j to user i in $v^{th}$ service.
+and
+$\bold{h}_{R_j,u(v,i)} \in \mathbb{C}^{{R}_j}$ is the vector of channel gain of a wireless link from RU j to the $i^{th}$ UE in $v^{th}$ service.
+In addition, $\bold{w}_{R_j,u(v,i)} \in \mathbb{C}^{{R}_j}$ depicts the transmit beamforming vector from RU j to the $i^{th}$ UE in $v^{th}$ service.
 Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals.
@@
 \begin{equation}\label{eq3}
-\textstyle \bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v} \
-\mathfrak{y}_{R_s}\zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v},
+\textstyle \bold{y}_{U_v} = \sum_{j = 1}^{J}\sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_j,\mathcal{U}_v} \
+\mathfrak{y}_{R_j}\zeta_{k,s}^{U_v,j} b_{U_v} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v},
 \end{equation}
-where $\mathfrak{y}_{R_s} = \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_s}$
+where $\mathfrak{y}_{R_j} = \boldsymbol{W}_{\mathcal{R}_j,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_j}$
 and $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
-In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise, which is made from signal compression in DU.
+In addition, $\boldsymbol{q}_{R_j} \in \mathbb{C}^{{R}_j }  $ indicates the quantization noise, which is made from signal compression in DU.
 Besides, $\boldsymbol{P}_{U_v} = \diag{(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})}$.
 \newline
-Furthermore, $\zeta_{k,s}^{U_v} \delequal \{\zeta_{k,s}^{u(v,1)},\zeta_{k,s}^{u(v,2)},...,\zeta_{k,s}^{u(v,N_{U_v})}\}$,
-$\zeta_{k,s}^{u(v,i)} \in \{0,1\}$ is a binary parameter, which demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
-$\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
-shows the channel matrix between RU set $\mathcal{R}_s$ to UE set
+Furthermore, $\zeta_{k,s}^{U_v,j} \delequal \{\zeta_{k,s}^{u(v,1)},\zeta_{k,s}^{u(v,2)},...,\zeta_{k,s}^{u(v,N_{U_v})}\}$,
+$\zeta_{k,s}^{u(v,i),j} \in \{0,1\}$ is a binary parameter, which demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $j^{th}$ RU using $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
+$\boldsymbol{H}_{\mathcal{R}_j,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_j,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_j,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_j\times {U}_v }$
+shows the channel matrix between RU set $\mathcal{R}_j$ to UE set
 $\mathcal{U}_v$, besides.
@@
 What's more, it is assumed we have perfect channel state information (CSI).\newline
-Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as below
+Moreover, $\boldsymbol{W}_{\mathcal{R}_j,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_j,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_j,u(v,U_v)}] \in \mathbb{C}^{{R}_j\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as below
 \begin{equation}
-\textstyle \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}.
+\textstyle \boldsymbol{W}_{\mathcal{R}_j,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_j,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_j,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_j,\mathcal{U}_v})^{-1}.
 \end{equation}
@@
  I_{u_{(v,i)}} &=
- \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{v,s}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
-&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
-&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}},
+ \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{j=1}^{J}\sum_{\hat{j}=1}^{J}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}e_{j,u(v,i)}e_{\hat{j},u(v,l)}b_{u(v,i)}b_{u(v,l)}}_{\text{(intra-service interference)}}\\
+&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{j=1}^{J}\sum_{\hat{j}=1}^{J}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}e_{j,u(v,i)}e_{\hat{j},u(v,l)}b_{u(v,i)}b_{u(y,l)}}_{\text{(inter-service interference)}}\\
+&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{J} {\sigma_q}_{R_j}^2 |\boldsymbol{h}_{R_j}, u_{(v,i)}|^2 a_{v,s} e_{j,u(v,i)}b_{u(v,i)}}_{\text{(quantization noise interference)}},
 \end{split}
 \end{equation}
-where $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
-and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. Moreover,
+where $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_j, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{j},u_{(v,l)}}|^2 a_{v,s}\zeta_{n,s}^{u_(v,i),j}\zeta_{n,s}^{u_(v,l),\hat{j}}$
+and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_j, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{j},u_{(y,l)}}|^2a_{y,s} \zeta_{n,s}^{u_(v,i),j}\zeta_{n,s}^{u_(y,l),\hat{j}}a_{v,s}$. Moreover,
 ${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RU in $s^{th}$ slice.
@@
 \begin{equation}
-\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s} + \sigma_{q_{r(s,j)}}^2.
+\bar{p}_{R_j} = \sum_{v=1}^{V}\boldsymbol{w}_{R_j,\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s} + \sigma_{q_{r(s,j)}}^2.
 \end{equation}
-Nevertheless, the rate of users on the fronthual link between DU and the $j^{th}$ RU in $s^{th}$ slice is formulated as \cite{simeone2016cloud, 1111}
+Nevertheless, the rate of users on the fronthual link between DU and the $j^{th}$ RU in $s^{th}$ slice is formulated as 
 \begin{equation}
@@
 Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
- an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
+ an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue. Therefore,
 the mean delay of the transmission layer is
@@
 \end{subequations}
-\section{Heuristic Method}\label{proposedmethod}
-In this subsection, a heuristic  method is proposed to solve the problem in \eqref{constraints1} which is non-convex and computationally hard.
-To make it tractable, we divide the problem \eqref{constraints1} into
-two different part that can be solved iteratively.
-In the first part of sub-problem 1, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in \eqref{constraints1}.
-Also, we set $\eta = 0$.
-Afterward, by achieving $\boldsymbol{A}$, in the second part, we find $\boldsymbol{P}$ by using \eqref{constraints1}.
-This part of the sub-problem can be approximated and converted to a convex problem, so the sub-problem can be solved by convex methods.
-After solving $\boldsymbol{P}$, $\eta$ is updated.
-Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$, the two parts of the sub-problems are solved. We repeat this procedure until the algorithm  converges.
-\subsection{First Part of Sub-Problem 1}\label{firstsub}
-Two different methods are applied to acquire $\boldsymbol{A}$.
-The details of the heuristic algorithm are represented in algorithm \ref{alg}.
-\begin{algorithm}
-\caption{Mapping Slice to Service}\label{alg}
-\begin{algorithmic}[1]
-\State Sort services according to the number of UEs in it and their requirements in the descending order.
-\State Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs in two layers and the capacity of their resources in the descending order.
-\For {$i \gets 1$ to $S$}
-\For {$j \gets 1$ to $V$}
-\State Set $a_{i,j} = 1$
-\State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RUs)
-\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} are not applied}
-\State Set $a_{i,j} = 0$;
-\Else
-\State break from inner loop;
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for}
-\end{algorithmic}
-\end{algorithm}
-\subsection{Second Part of Sub-Problem 1}\label{secondsub}
-In this part, by assuming that $\boldsymbol{A}$ is fixed, the power of UEs in each service is achieved.
-\begin{theorem}\label{t2}
-The optimum energy efficiency is achieved if
-\begin{equation}\label{q2}
-%\begin{split}
-\max \limits_{\boldsymbol{P}} (\mathfrak{R}_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=
- \mathfrak{R}_{tot}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
-%\end{split}
-\end{equation}
-\end{theorem}
-\begin{proof}
-See \cite[Appendix A]{aaa}
-\end{proof}
-The second sub-problem can  be solved using the Lagrangian function and iterative algorithm.
-Since, Interference is a function of the power of UEs, to make it tractable, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference.
-In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively).
-Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
-The Lagrangian function is written as follow
-\begin{subequations}\label{lagrang}
-\begin{alignat}{4}
-\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\chi}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
-- \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
-&+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
-&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
-&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,i)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\
-&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.
-\end{alignat}
-\end{subequations}
-where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$. Optimal power is obtained from  \eqref{lagrang}
-\begin{equation}
-p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
-\end{equation}
-where, $\mathfrak{y}_{u(v,i)}= (\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and
-$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. Also
-$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$.
-By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained \cite{mimoCran}.
-%\section*{References}
-\subsection{Solving two part of Sub-problem 1 iteratively}
-In \eqref{firstsub} and \eqref{secondsub}, the details of solving each part of the sub-problem are depicted.
-Firstly, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in the problem \eqref{constraints1} and using algorithm \eqref{alg}.
-Also we fixed $\eta = 0$.
-Afterward, $\boldsymbol{A}$ is achieved from algorithm \ref{alg}.
-Then, in the second part, we acquire $\boldsymbol{P}$ using the sub-gradient method.
-After solving $\boldsymbol{P}$, $\eta$ is updated.
-Then in the next iteration, with new $\boldsymbol{P}$
-and $\eta$ the two parts of the sub-problem is solved until the algorithm converges.
-Here, the algorithm of solving sub-problem 1 is shown in algorithm \eqref{alg2}
-\begin{algorithm}
-\caption{Joint Network Slicing and Power Allocation}\label{alg2}
-\begin{algorithmic}[1]
-\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
-\State Set $\boldsymbol{P} = \boldsymbol{P}_{max}$
-\For {$counter \gets 1$ to $I_{max}$}
-\State Achieve $\boldsymbol{A}$ by applying Algorithm \eqref{alg}
-\State Obtain $\boldsymbol{P}$ by using sub-gradient method which is mentioned in \eqref{secondsub}.
-\If {$ \mathfrak{R}_{tot}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) - \eta^{(i)} P_{r_{tot}}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) < \epsilon_{\eta} $}
-\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $, $\boldsymbol{A}^*= \boldsymbol{A}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
-\State break;
-\Else
-\State $i= i+1$, Setting $\boldsymbol{P} = \boldsymbol{P}^{(i)}$ ;
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\end{algorithmic}
-\end{algorithm}
-\subsection{Sub-Problem 2}
-In this subsection, we would like to solve  \eqref{constraints2}, which is the placement of virtual resources to physical resources in order to minimize the cost function $\psi_{tot}$.
-To achieve optimum $\boldsymbol{Y}$ heuristic algorithm is applied.
-The details of the heuristic algorithm are written in algorithm \eqref{alg3}.
-In this algorithm, firstly, we sort slices and DCs according to their sum-weighted of their requirements (line \ref{31} and line \ref{32} of algorithm \ref{alg3}).
-We define a weighted parameter for $\Omega_{\mathfrak{z},s}^{tot}$ and $\tau_j^\mathfrak{z}$ as follow
-\begin{equation}\label{wt}
-\begin{split}
-\hat{\Omega}_{s}^{tot} &= w_M \bar{\Omega}_{M,s}^{tot} + w_S \bar{\Omega}_{S,s}^{tot} + w_C \bar{\Omega}_{C,s}^{tot} \\
-\hat{\tau}_j &= w_M \tau_{{j}}^M + w_S \tau_{{j}}^S + w_C \tau_{{j}}^C,
-\end{split}
-\end{equation}
-where, $\boldsymbol{w} = \{w_M, w_S, w_C\}$ is the weight of memory, storage and CPU.
-Secondly, we start mapping from the most needed slices to the DC with the most physical resources (from line \ref{33} to line \ref{34} of algorithm \ref{alg3}).
-After mapping DCs to slices, If a slice does not admit to a specific DC, it remains for the next placement.
-In the next placement the remaining slices, map to more than one DC according to their requirements.
-(from line \ref{35} to line \ref{36} of algorithm \ref{alg3}).
-At the end, if DC with the lowest physical resources is free and can be served the slices of a DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption (line \ref{37} of algorithm \ref{alg3}).
-\begin{algorithm}
-\caption{Placement of Physical resources into Virtual resources}\label{alg3}
-\begin{algorithmic}[1]
-\State Sort Slices according to $\hat{\Omega}_{s}^{tot} , \forall s$ in descending order.\label{31}
-\State Sort DCs according to $\hat{\tau}_j , \forall j$ in descending order. \label{32}
-\State $\boldsymbol{Y} = \boldsymbol{0}$
-\For {$d \gets 1$ to $D_c$}\label{33}
-\For {$s \gets 1$ to $S$}
-\If {$\sum_{d=1}^{D_c}y_{s,d}==0$ and $\bar{\Omega}_{\mathfrak{z}(s)}^{tot} \leq \tau_{\mathfrak{z}_j} \forall \mathfrak{z}, \forall s$  }
-\State Set $y_{s,d} = 1$;
-\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for} \label{34}
-\State  $ind_{rem} = \{s|({\sum_{d=1}^{D_c}y_{s,d}==0})\}$ \label{35}
-\State Sort remaining amount of DCs same as before in descending order.
-\State Sort remaining slices same as before in descending order.
-\For {$r \gets 1$ to $S_{rem}$}
-\For {$n \gets 1$ to $D_c$}
-\State Set $y_{s,d} = 1$;
-\State {$\bar{\Omega}_{{\mathfrak{z}},s}^{tot}$ $\gets$ {$\bar{\Omega}_{{\mathfrak{z}},s}^{tot}- \tau_j^{\mathfrak{z}}$}}
-\If {$\bar{\Omega}_{s}^{tot}==0$}
-\State Set $y_{s,d} = 1$;
-\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
-\State {break inner loop}
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for} \label{36}
-\State Remapping DCs must be done to prevent wasting Energy \label{37}
-\end{algorithmic}
-\end{algorithm}
-\section{Numerical Results}\label{simul}
-In this section, numerical results for the main problem are depicted.
- \begin{table}
- \caption {Simulation Parameter} \label{table:1a}
- \begin{center}
-  \begin{tabular}{||c c ||}
-  \hline
-Parameter & Value \\ [0.5ex]
-  \hline\hline
-  Noise power & -174dBm\\
-  \hline
-  Bandwidth & 120 KHZ \\
-  \hline
- Maximum transmit Power of each RU & 40dBm \\
-  \hline
-  Minimum delay &  300usec \\
-  \hline
-  Maximum fronthaul capacity  & 200 bits/sec/Hz \\
-   \hline
-  Minimum data rate &  10 bits/sec/Hz \\ [1ex]
-  \hline
- \end{tabular}
- \end{center}
- \end{table}
-In Fig.
-\ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with different mean number of UEs in each service.
-The parameters of simulations are listed in Table \ref{table:1a}.
-The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$.
-They iteratively update $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$.
-The optimal method is $0.1$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.09$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$.
-As it is shown, the energy efficiency is increased as mean number of UEs rises.
-\begin{figure}%[H]
-  \centering
-    \includegraphics[width=\linewidth]{fig1_last}
-  \caption{Energy Efficiency vs. Mean Number of UEs in each Service}
-  \label{fig:f1a}
-\end{figure}
-In Fig.
-\ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices.
-The parameters of the simulation are listed in Table \ref{table:1}.
-We also set $w_C = 320$, $w_S = 100$, $w_M =1$.
-In this simulation, the second term of \eqref{eqpsi}, is important and the designed parameter $\nu$ is supposed to be high.
-Also, it is assumed that just one DC can serve each slice, and each slice is not admitted by more than one DC. 
-The proposed method is based on Algorithm \ref{alg3}, and the optimal method is obtained using MOSEK toolbox.
-\begin{small}
- \begin{table}
- \caption {Simulation Parameter} \label{table:1}
- \begin{center}
-  \begin{tabular}{||c c ||}
-  \hline
-  Parameter & Value \\ [0.5ex]
-  \hline\hline
-  Mean of CPU for DCs & 320GHz\\
-  \hline
-  Mean of Memory for DCs & 1T\\
-  \hline
- Mean of Storage for DCs & 100T \\
-  \hline
-   Mean of CPU for Slices & 32GHz\\
-  \hline
-  Mean of Memory for Slices & 100G\\
-  \hline
- Mean of Storage for Slices & 10T \\ [1ex]
-  \hline
- \end{tabular}
- \end{center}
- \end{table}
-\end{small}
-When we have two DCs, the proposed method and optimal method have approximately the same ratio of admitted slices.
-But by increasing the number of DCs to five, the performance of the proposed method reduced.
-Using five DCs, the difference between the
-proposed method and the optimal method in the worst case (44 slices) is about $23$ percentage.
-\begin{figure}%[H]
-  \centering
-    \includegraphics[width=\linewidth]{f112}
-  \caption{Ratio of Admitted Slices connected to just one DC vs. Total slices}
-  \label{fig:f1}
-\end{figure}
-In Fig.
-\ref{fig:f2}, the normalized resource consumption is depicted versus the number of slices.
-The parameters for simulation are listed in Table \ref{table:1}.
-We also set $w_C = 320$, $w_S = 100$, $w_M =1$).
-In this simulation, suppose the number of DCs is entirely enough to cover all slices and the designed parameter $\nu$ is assumed to be low, so we focused on the first term of \eqref{eqpsi}.
-However, if any slice remains, it can be served by more than one DCs.
-The optimality of the placement of DC resources to slices is measured based on the power consumption of DCs.
-It is shown the amount of resources of DCs which are not used.
-For ten slices, the difference between the optimal solution and the proposed solution is about $15$ percent.
-\begin{figure}%[H]
-  \centering
-    \includegraphics[width=\linewidth]{fig22_last}
-  \caption{Normalized Resource Consumption vs. Number of Slices}
-  \label{fig:f2}
-\end{figure}
-\section{Conclusion}
-In this paper, joint network slicing and power allocation were considered in an ORAN system.
-It is assumed that UEs are classified based on their requirements into services.
-Also, there is a number of slices serving the services.
-Each slice consists of PRBs, RUs, and VNFs that support CU and DU.
-The limited fronthaul capacity is considered for the fiber links between RUs and DU.
-The target was to maximize the sum-rate and minimize the power consumption and energy cost of data centers simultaneously.
-The problem is decomposed into two sub-problems.
-Each sub-problem is solved separately by a heuristic algorithm.
-Using numerical results, we validate the heuristic method and study the performance of the algorithms.
-%For the sub-problem A, energy efficiency vs.
-mean number of UEs in each service is depicted.
-The energy efficiency  exceeded by increasing the mean number of UEs in each service.
-For the sub-problem B, two figures are shown.
-In the first one, the ratio of admitted slices that connect to just one DC, for a different number of slices is denoted.
-In the second figure, the normalized resource consumption of DCs is depicted.
-In each figure, the heuristic algorithm is compared with the optimal method and the difference between them is discussed.
 
 \bibliographystyle{IEEEtran}
-\bibliography{ref}
+\bibliography{references}
 \end{document}

### 2021-04-24 job/hw/hw1.tex
add hw

\documentclass[oneside]{article}

\usepackage{siunitx}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{minted}
\usepackage{lastpage}
\usepackage{tcolorbox}
\usepackage{amsmath}
\usepackage[colorlinks=true]{hyperref}
\usepackage{setspace}
\usepackage[absolute]{textpos}
\usepackage{xepersian} % Always last package to load

\settextfont{XW Zar}
%\setlatintextfont{Adobe Garamond Pro}
%\setlatinmonofont[Scale=0.8]{Monaco}
\defpersianfont\nastaliqfont{IranNastaliq}
\setlength{\TPHorizModule}{1cm}
\setlength{\TPVertModule}{1cm}
\linespread{1.5}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\newcommand*{\fancypagenumber}{%
\fancyfoot[C]{صفحه
\thepage
از
\pageref{LastPage}}
}
\fancypagenumber
\fancypagestyle{plain}{\fancypagenumber}
% insert syntax highlighted code from a file
\newcommand{\inputcode}[2]{\inputminted[mathescape,%
                                                 linenos=true,%
                                                 formatcom=\small\setstretch{1}]{#1}{#2}}%
%\renewcommand{\theFancyVerbLine}{\sffamily\scriptsize
%\textcolor[rgb]{0.5,0.5,1.0}{\oldstylenums{\arabic{FancyVerbLine}}}}
\title{تمرین های سری اول درس برنامه نویسی کامپیوتر}
\author{دکتر شفیعی}
\begin{document}
\maketitle

\begin{textblock}{5}(6.5,2)\nastaliqfont
\noindent\Large
بسم الله الرحمن الرحیم
\end{textblock}
\begin{tcolorbox}
\begin{center}
این اولین سری از تمارین مربوطه به پایتون می باشد. در صورت داشتن سوال، در جلسه ی رفع اشکال پاسخ داده می شود 
\end{center}
\end{tcolorbox}

\begin{enumerate}
\item 
برنامه ای بنویسید که  یک عدد صحیح مثبت را از ورودی گرفته و به اندازه ی ارقام آن از همان عدد چاپ کند برای مثال عدد 523 را گرفته و 5555522333 را چاپ کند. 
\item
برنامه ای بنویسید که دو 
\lr{string}
 از کاربر بگیرد و در اولی نام و در دومی نام خانوادگی کاربر را قرار داده
 و در 
 \lr{string}
 سومی، نام و نام خانوادگی را بدون فاصله قرار دهد که با چسباندن دو 
 \lr{string}
اول و دوم باشد و در 
 \lr{string}
 آخری، 
 نام و نام خانوادگی را با فاصله قرار دهد.
\item
\begin{enumerate}
\item 
یک اسکریپت پایتون با دیکشنری بنویسید که کلیدها اعداد بین 1 تا 15 باشند و مقادیر مربع کلیدها هستند.
\item
از کاربر نام و معدل 10 دانشجو را بگیرید و در دیکشنری (کلید : نام، مقدار : معدل) قرار دهید.
\item
یک اسکریپت پایتون با دیکشنری بنویسید که دیکشنری دو مسئله ی قبل را با هم ادغام نماید
\end{enumerate}
\item 
برنامه ای بنویسید که یک کلمه یا جمله
از کاربر بگیرد و در صورتی که این
کلمه با مقدار عکس خود یکی باشد، مقدار 
\lr{true}
و در غیر این صورت مقدار
\lr{false}
را چاپ نماید
(
برای مثال 
\lr{hi ih}
مقدار 
\lr{true}
و 
\lr{tree}
مقدار
\lr{false}
است.
)
\item
برنامه ای بنویسید که سه نمره ی دانشجو را از کاربر بگیرد.
\\
اعداد صحیح یا اعشاری می توانند باشند .حاصل جمع، حاصل ضرب و میانگین اعداد را چاپ کند. به این صورت:
\\
\begin{latin}
\texttt{Please enter 3 integers: 10 13 12.5} \\
\texttt{Sum is: 35.5 }\\
\texttt{Product is: 16.25 }\\
\texttt{Average is: 11.833}
\end{latin}
همچنین در صورتی که میانگین نمره ها از $18$ بیشتر باشد، در خروجی مقدار \lr{A}، میانگین بین $16$ تا 
$18$
بود مقدار \lr{B}
و در غیر اینصورت مقدار
\lr{C}
را در خروجی چاپ نماید.
\item
	برنامه ای بنویسید که از کاربر عدد بگیرد تا زمانی که کاربر عدد صفر را وارد کند. بعد به روش
\lr{bubble sort}
  این اعداد را مرتب کنید و در خروجی چاپ کنید. 
  \\
راهنمایی:
\\
روش
\lr{bubble sort}
یک الگوریتم مرتب‌سازی ساده‌است که فهرست را پشت سرهم پیمایش می‌کند تا هر بار عناصر کنارهم را با هم سنجیده و اگر در جای نادرست بودند جابه‌جایشان کند. دراین الگوریتم این کار باید تا زمانی که هیچ جابه‌جایی در فهرست رخ ندهد، ادامه یابد و در آن زمان فهرست مرتب شده‌است.
\item
\begin{enumerate}
\item
یک فایل متنی درست کنید به این ترتیب که متشکل از 
\num{1000000}
 خط باشد که از شماره خط صفر شروع می شود. هر خط این فایل به این شیوه نوشته شده باشد:
\begin{latin}\inputcode{Text}{random.txt}\end{latin}
برای تولید عدد تصادفی بین صفر و یک از تابع 
\lr{\texttt{random}}
داخل کتابخانه
\lr{\texttt{numpy.random}}
استفاده کنید و با 6 رقم بعد از ممیز عدد را نشان دهید. توجه کنید که در این فایل بعد از کلمه
\lr{Line}
از فاصله استفاده شده و بعد از شماره خط از 
\lr{TAB}
استفاده می شود. زمان اجرای کار را ذخیره کنید و نشان دهید. 
\item
سپس همین کار را دقیقا توسط کتابخانه 
\lr{\texttt{csv}}
انجام دهید و زمان را اندازه بگیرید و درصد کاهش و یا افزایش را بیان کنید. به نظر شما علت این کاهش یا افزایش چه چیزی می تواند باشد؟ (همه جا از فاصله عادی یا
\lr{TAB})
استفاده کنید.
\item
در قسمت سوم این سوال اگر کل داده ها را داخل یک لیست در ابتدا ذخیره کنید و سپس داخل فایل بریزید آیا سریع تر خواهد بود؟ در صورت مثبت و منفی بودن جواب علت را توضیح دهید؟
\end{enumerate}
در کل یک فایل پایتون خواهیم داشت که از سه قسمت تشکیل شده است و در هر قسمت زمان اجرا ذخیره می شود و نشان داده می شود.

راهنمایی: برای قسمت دوم سوال بایستی از تابع 
\lr{\texttt{csv.writer}}
استفاده کنید که ورودی آن 
\lr{File Handle}
می باشد و خروجی آن 
\lr{CSV Handle}
خواهد بود. متغیر اخیر یک متد به نام 
\texttt{writerow}
دارد که یک لیست را ورودی می گیرد و در خروجی چاپ می کند. در قسمت سوم سوال از
\lr{List Comprehension}
استفاده کنید. کل عملیات باز کردن فایل و ریختن داده ها در دو خط کد قابل انجام خواهد بود. از تابع 
\lr{\texttt{writelines}}
استفاده بفرمایید.
\item
در شاخه ای که فایل پایتون شما وجود دارد یک فلدر به نام
\lr{root}
بسازید. هدف این است که داخل این فلدر تعدادی فایل و فلدر دیگر بسازیم به این صورت:
\begin{latin}\inputcode{Text}{random_folder_structure.txt}\end{latin}
این فلدر تا 5 مرحله شاخه بندی شده است. داخل هر فلدر تعدادی فایل متنی وجود دارد که با 
\lr{\texttt{.txt}}
داخل شکل نشان داده شده اند. اسم هر کدام از این فایل ها یک عدد تصادفی بین 0 تا 100 می باشد. توجه کنید که تعداد این فایل ها نیز تصادفی می باشد. 
\begin{enumerate}
\item
برنامه مورد نظر را طوری بنویسید که با هر بار اجرا کردن فلدر ها و فایل های قبلی پاک شوند (در صورت وجود) و دوباره ایجاد شوند.
\item
در قسمت دوم همین برنامه با استفاده از تابع
\lr{\texttt{os.walk}}
ابتدا تعداد کل فایل های ایجاد شده را بشمارید و سپس  تمامی  فایل هایی که داخل  نام  فایل عدد صفر را دارند به جای عدد صفر از کاراکتر
\lr{\texttt{'\_'}}
استفاده کنید 
(\lr{rename}).
\end{enumerate}
راهنمایی: در این تمرین نیاز به استفاده از تعدادی از توابع داخل کتابخانه 
\lr{\texttt{os}}
از جمله
\lr{\texttt{os.path.exists}}
،
\lr{\texttt{mkdir}}
و 
\lr{\texttt{rename}}
دارید. همچنین از توابع کتابخانه
\lr{\texttt{shutil}}
مثل
\lr{\texttt{rmtree}}
نیز می توانید استفاده کنید. با توابع رشته ای هم می توانید جهت عوض کردن اسم فایل کار کنید.

\end{enumerate}

\begin{tcolorbox}
جهت تحویل تمارین هر تمرین را داخل یک فلدر بریزید که با شماره تمرین نام گذاری شده است و 
 گزارش کار را به فرمت یک فایل
\lr{PDF}
در فلدراصلی قرار دهید. فلدر اصلی را بعد از فشرده سازی به صورت 
\lr{HW1-\rl{شماره دانشجویی}.\textbf{zip}}
 نام گزاری، و ارسال کنید.
\begin{center}
\textbf{
مهلت تحویل: تا ساعت 12 ظهر دوشنبه سیزدهم اردیبهشت ماه 1400.
}
\end{center}
\end{tcolorbox}
\end{document}

### 2021-04-25 job/hw/hw1.tex
correct code

@@
 \usepackage{lastpage}
+\usepackage{xcolor}
 \usepackage{tcolorbox}
@@
 \usepackage{xepersian} % Always last package to load
-
-\settextfont{XW Zar}
-%\setlatintextfont{Adobe Garamond Pro}
+\settextfont{B Nazanin}
+\setlatintextfont{Times New Roman}
 %\setlatinmonofont[Scale=0.8]{Monaco}
@@
 %\textcolor[rgb]{0.5,0.5,1.0}{\oldstylenums{\arabic{FancyVerbLine}}}}
-\title{تمرین های سری اول درس برنامه نویسی کامپیوتر}
-\author{دکتر شفیعی}
+\title{تمرین های سری اول درس
+\lr{Service Based Architecture}
+}
+%\author{دکتر شفیعی}
+\date{\vspace{-5ex}}
 \begin{document}
@@
 \end{textblock}
-\begin{tcolorbox}
-\begin{center}
-این اولین سری از تمارین مربوطه به پایتون می باشد. در صورت داشتن سوال، در جلسه ی رفع اشکال پاسخ داده می شود 
-\end{center}
-\end{tcolorbox}
+%\begin{tcolorbox}
+%\begin{center}
+%این اولین سری از تمارین مربوطه به پایتون می باشد. در صورت داشتن سوال، در جلسه ی رفع اشکال پاسخ داده می شود 
+%\end{center}
+%\end{tcolorbox}
 
@@
 \item
-برنامه ای بنویسید که  یک عدد صحیح مثبت را از ورودی گرفته و به اندازه ی ارقام آن از همان عدد چاپ کند برای مثال عدد 523 را گرفته و 5555522333 را چاپ کند. 
-\item
-برنامه ای بنویسید که دو 
-\lr{string}
- از کاربر بگیرد و در اولی نام و در دومی نام خانوادگی کاربر را قرار داده
- و در 
- \lr{string}
- سومی، نام و نام خانوادگی را بدون فاصله قرار دهد که با چسباندن دو 
- \lr{string}
-اول و دوم باشد و در 
- \lr{string}
- آخری، 
- نام و نام خانوادگی را با فاصله قرار دهد.
+برنامه ای بنویسید که سه نمره ی دانشجو را از کاربر بگیرد.
+\\
+اعداد صحیح یا اعشاری می توانند باشند .حاصل جمع، حاصل ضرب و میانگین اعداد را چاپ کند. به این صورت:
+\\
+\begin{latin}
+\texttt{Please enter 3 integers: 10 13 12.5} \\
+\texttt{Sum is: 35.5 }\\
+\texttt{Product is: 16.25 }\\
+\texttt{Average is: 11.833}
+\end{latin}
+همچنین در صورتی که میانگین نمره ها از $18$ بیشتر باشد، در خروجی مقدار \lr{A}، میانگین بین $16$ تا 
+$18$
+بود مقدار \lr{B}
+و در غیر اینصورت مقدار
+\lr{C}
+را در خروجی چاپ نماید.
 \item
@@
 \item 
-یک اسکریپت پایتون با دیکشنری بنویسید که کلیدها اعداد بین 1 تا 15 باشند و مقادیر مربع کلیدها هستند.
+یک اسکریپت پایتون با دیکشنری بنویسید که کلیدها اعداد بین 1 تا 15 باشند و مقادیر مربع کلیدها هستند
+$(1:1, 2:4, 3:9, ...)$
+.
 \item
 از کاربر نام و معدل 10 دانشجو را بگیرید و در دیکشنری (کلید : نام، مقدار : معدل) قرار دهید.
-\item
-یک اسکریپت پایتون با دیکشنری بنویسید که دیکشنری دو مسئله ی قبل را با هم ادغام نماید
 \end{enumerate}
@@
 )
-\item
-برنامه ای بنویسید که سه نمره ی دانشجو را از کاربر بگیرد.
-\\
-اعداد صحیح یا اعشاری می توانند باشند .حاصل جمع، حاصل ضرب و میانگین اعداد را چاپ کند. به این صورت:
-\\
-\begin{latin}
-\texttt{Please enter 3 integers: 10 13 12.5} \\
-\texttt{Sum is: 35.5 }\\
-\texttt{Product is: 16.25 }\\
-\texttt{Average is: 11.833}
-\end{latin}
-همچنین در صورتی که میانگین نمره ها از $18$ بیشتر باشد، در خروجی مقدار \lr{A}، میانگین بین $16$ تا 
-$18$
-بود مقدار \lr{B}
-و در غیر اینصورت مقدار
-\lr{C}
-را در خروجی چاپ نماید.
+
 \item
@@
 دراین الگوریتم این کار باید تا زمانی که هیچ جابه‌جایی در فهرست رخ ندهد، ادامه یابد و در آن زمان فهرست مرتب شده‌است.
-\item
-\begin{enumerate}
-\item
-یک فایل متنی درست کنید به این ترتیب که متشکل از 
-\num{1000000}
- خط باشد که از شماره خط صفر شروع می شود. هر خط این فایل به این شیوه نوشته شده باشد:
-\begin{latin}\inputcode{Text}{random.txt}\end{latin}
-برای تولید عدد تصادفی بین صفر و یک از تابع 
-\lr{\texttt{random}}
-داخل کتابخانه
-\lr{\texttt{numpy.random}}
-استفاده کنید و با 6 رقم بعد از ممیز عدد را نشان دهید. توجه کنید که در این فایل بعد از کلمه
-\lr{Line}
-از فاصله استفاده شده و بعد از شماره خط از 
-\lr{TAB}
-استفاده می شود. زمان اجرای کار را ذخیره کنید و نشان دهید. 
-\item
-سپس همین کار را دقیقا توسط کتابخانه 
-\lr{\texttt{csv}}
-انجام دهید و زمان را اندازه بگیرید و درصد کاهش و یا افزایش را بیان کنید. به نظر شما علت این کاهش یا افزایش چه چیزی می تواند باشد؟ (همه جا از فاصله عادی یا
-\lr{TAB})
-استفاده کنید.
-\item
-در قسمت سوم این سوال اگر کل داده ها را داخل یک لیست در ابتدا ذخیره کنید و سپس داخل فایل بریزید آیا سریع تر خواهد بود؟ در صورت مثبت و منفی بودن جواب علت را توضیح دهید؟
-\end{enumerate}
-در کل یک فایل پایتون خواهیم داشت که از سه قسمت تشکیل شده است و در هر قسمت زمان اجرا ذخیره می شود و نشان داده می شود.
 
-راهنمایی: برای قسمت دوم سوال بایستی از تابع 
-\lr{\texttt{csv.writer}}
-استفاده کنید که ورودی آن 
-\lr{File Handle}
-می باشد و خروجی آن 
-\lr{CSV Handle}
-خواهد بود. متغیر اخیر یک متد به نام 
-\texttt{writerow}
-دارد که یک لیست را ورودی می گیرد و در خروجی چاپ می کند. در قسمت سوم سوال از
-\lr{List Comprehension}
-استفاده کنید. کل عملیات باز کردن فایل و ریختن داده ها در دو خط کد قابل انجام خواهد بود. از تابع 
-\lr{\texttt{writelines}}
-استفاده بفرمایید.
 \item
@@
 نیز می توانید استفاده کنید. با توابع رشته ای هم می توانید جهت عوض کردن اسم فایل کار کنید.
+\item
+\begin{enumerate}
+\item
+ \textcolor{red}{امتیازی-}
+یک فایل متنی درست کنید به این ترتیب که متشکل از 
+\num{1000000}
+ خط باشد که از شماره خط صفر شروع می شود. هر خط این فایل به این شیوه نوشته شده باشد:
+\begin{latin}\inputcode{Text}{random.txt}\end{latin}
+برای تولید عدد تصادفی بین صفر و یک از تابع 
+\lr{\texttt{random}}
+داخل کتابخانه
+\lr{\texttt{numpy.random}}
+استفاده کنید و با 6 رقم بعد از ممیز عدد را نشان دهید. توجه کنید که در این فایل بعد از کلمه
+\lr{Line}
+از فاصله استفاده شده و بعد از شماره خط از 
+\lr{TAB}
+استفاده می شود. زمان اجرای کار را ذخیره کنید و نشان دهید. 
+\item
+\textcolor{red}{امتیازی-}
+سپس همین کار را دقیقا توسط کتابخانه 
+\lr{\texttt{csv}}
+انجام دهید و زمان را اندازه بگیرید و درصد کاهش و یا افزایش را بیان کنید. به نظر شما علت این کاهش یا افزایش چه چیزی می تواند باشد؟ (همه جا از فاصله عادی یا
+\lr{TAB})
+استفاده کنید.
+\item
+\textcolor{red}{امتیازی-}
+در قسمت سوم این سوال اگر کل داده ها را داخل یک لیست در ابتدا ذخیره کنید و سپس داخل فایل بریزید آیا سریع تر خواهد بود؟ در صورت مثبت و منفی بودن جواب علت را توضیح دهید؟
+\end{enumerate}
+در کل یک فایل پایتون خواهیم داشت که از سه قسمت تشکیل شده است و در هر قسمت زمان اجرا ذخیره می شود و نشان داده می شود.
 
+راهنمایی: برای قسمت دوم سوال بایستی از تابع 
+\lr{\texttt{csv.writer}}
+استفاده کنید که ورودی آن 
+\lr{File Handle}
+می باشد و خروجی آن 
+\lr{CSV Handle}
+خواهد بود. متغیر اخیر یک متد به نام 
+\texttt{writerow}
+دارد که یک لیست را ورودی می گیرد و در خروجی چاپ می کند. در قسمت سوم سوال از
+\lr{List Comprehension}
+استفاده کنید. کل عملیات باز کردن فایل و ریختن داده ها در دو خط کد قابل انجام خواهد بود. از تابع 
+\lr{\texttt{writelines}}
+استفاده بفرمایید.
 \end{enumerate}
 
-\begin{tcolorbox}
-جهت تحویل تمارین هر تمرین را داخل یک فلدر بریزید که با شماره تمرین نام گذاری شده است و 
- گزارش کار را به فرمت یک فایل
-\lr{PDF}
-در فلدراصلی قرار دهید. فلدر اصلی را بعد از فشرده سازی به صورت 
-\lr{HW1-\rl{شماره دانشجویی}.\textbf{zip}}
- نام گزاری، و ارسال کنید.
-\begin{center}
-\textbf{
-مهلت تحویل: تا ساعت 12 ظهر دوشنبه سیزدهم اردیبهشت ماه 1400.
-}
-\end{center}
-\end{tcolorbox}
+%\begin{tcolorbox}
+%جهت تحویل تمارین هر تمرین را داخل یک فلدر بریزید که با شماره تمرین نام گذاری شده است و 
+% گزارش کار را به فرمت یک فایل
+%\lr{PDF}
+%در فلدراصلی قرار دهید. فلدر اصلی را بعد از فشرده سازی به صورت 
+%\lr{HW1-\rl{شماره دانشجویی}.\textbf{zip}}
+% نام گزاری، و ارسال کنید.
+%\begin{center}
+%\textbf{
+%مهلت تحویل: تا ساعت 12 ظهر دوشنبه سیزدهم اردیبهشت ماه 1400.
+%}
+%\end{center}
+%\end{tcolorbox}
 \end{document}

### 2021-04-25 Code_journal1/version6/PRB_Pow_Alloc.m

@@ -1,24 +1,18 @@
-% PRB & Power Allocation
-cvx_begin
-    variables Popt(1,N_UE) 
-    %variable PRB_UE(N_PRB, N_UE) binary;
-    run Interference
-    run Rate
-    %rate_UE = cvx(rate_UE);
-    run P_RU
-    R1 = sum(rate_UE);
-    P1 = sum(Pow_RU);
-    error =  R1 - eta0 * P1;
-    maximize error
-    subject to
-    Pow_RU(:) <= Pmax;
-    %Prrh(:) <= 2^C_thresh * var_q *100;
-    Popt(:) >= 0;
-    Popt(:) < Pmax/10;
-    rate_UE(:) >= Rmin(1)*100;%.*admission_UE1(:);  
-    %PRB_UE(:)> 1
-cvx_end
-eta0 = double(R1)/double(P1);
-run Interference
-run Rate
-%etha = sum(rate_UE)/sum(Pow_RU);
+for  count_power=1:1 
+    cvx_begin
+        variables Popt(1,N_UE); 
+        %variable PRB_UE(N_PRB, N_UE);
+        run Interference
+        run Rate
+        run P_RU
+        maximize sum(rate_UE)
+        subject to
+        Pow_RU(:) <= Pmax;
+        Pow_RU(:) <= 2.^(Capacity_RU(:)/1000) * var_q ;
+        Popt(:) > 0; 
+        Popt(:) < Pmax;
+        rate_UE(:) > Rmin_UE(:);%.*admission_UE1(:);  
+        %PRB_UE(:)> 1
+    cvx_end
+
+end

### 2021-04-25 Code_journal1/version6/Rate.m

@@ -1,10 +1,21 @@
+% rate_UE = cvx(zeros(1,N_UE));
+% %rate_UE = zeros(1,N_UE);
+% for i = 1:N_UE
+%     for j = 1:N_RU
+%         for z = 1:N_PRB
+%             %rate_UE(i) = rate_UE(i) + BW* log(1 + (Popt(i)*abs((ChannelGain(:,i))'*beamForming(:,i))^2)/(Intf(i)+BW*N0))*PRB_UE(z,i);
+%             rate_UE(i) = rate_UE(i) + BW* log(1 + (Popt(i)*abs((ChannelGain(j,i)).* RU_UE(j,i)))/(Intf(i)+BW*N0))*PRB_UE(z,i);
+%         end
+%     end
+% end
+
 rate_UE = cvx(zeros(1,N_UE));
-%rate_UE = zeros(1,N_UE);
 for i = 1:N_UE
-    for j = 1:N_RU
+    %for j = 1:N_RU
         for z = 1:N_PRB
-            %rate_UE(i) = rate_UE(i) + BW* log(1 + (Popt(i)*abs((ChannelGain(:,i))'*beamForming(:,i))^2)/(Intf(i)+BW*N0))*PRB_UE(z,i);
-            rate_UE(i) = rate_UE(i) + BW* log(1 + (Popt(i)*abs((ChannelGain(j,i)).* RU_UE(j,i)))/(Intf(i)+BW*N0))*PRB_UE(z,i);
+            if PRB_UE(z,i)==1
+                rate_UE(i) = rate_UE(i) + BW* log(1 + (Popt(i)*abs((ChannelGain(:,i))'*beamForming(:,i))^2)/(Intf(i)+BW*N0));%*PRB_UE(z,i);
+            end
         end
-    end
+    %end
 end

### 2021-05-16 Latex/journal_v1/V3/pr.tex
change

--- 2021-01-04 Latex/journal_v1/V2/pr.tex
@@
 \subsection{System Model}
-Suppose we have two service types includes eMBB and URLLC. Assume we have $S_1$ and $S_2$ different applications for the first and second service type, respectively ($S = S_1 + S_2$).
-Assume we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC).
-Each Service $s_j\in \{1,2,...,S_j \} $ consists of $U_{s_j}$ request from the 
-single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2\}$ indicate service type).
+Suppose we have three service types includes mMTC, eMBB and URLLC which support different applications.
+Assume we have preallocated slices serving these services;
+Each Service $s\in \{1,2,3 \} $ consists of $U_{s}$ request from the 
+single-antenna UEs which require certain QoS to be able to use the requested program indicate service type).
 There are different application request which fall into one of these service categories.
@@
 Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+Each slice $s_ \in \{1,23 \}$ consists of $K_{s}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
 
@@
 
-In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
-has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
+In addition, there are $R$ single-antenna RU that are shared between slices. All RUs $r \in \{1,2,...,R \}$
+transmit signals cooperatively to all the UEs(RUs are in comp mode). Moreover, all RUs, have access to PRBs.
 \subsection{The Achievable Rate}

### 2021-05-16 Code_journal1/version8/PRB_Pow_Alloc.m

@@ -16,11 +16,16 @@ for  count_power=1:1
         rate_UE(:) >= Rmin_UE(:);%.*admission_UE1(:); 
         %R_s(:) > alpha_s + 1./delay_max(:);
         %xx(:).*(R_s(:)-alpha_s) >= 1.;
-        %t(:) = R_s(:) - alpha_s;
         xx(:) > 0
-        xx(:) - 1/((R_s(:)-alpha_s))> 0
         delay_max(:) - xx(:) >= 0
         alpha_s*(delay_max(:) - xx(:))-(mu(:).*(delay_max(:) - xx(:))-1)*10 <= 0
+        %m(:) >= alpha_s*(delay_max(:) - xx(:))./(mu(:).*(delay_max(:) - xx(:))-1)
+        
+%         for s = 1:S
+%            1/(R_s(s)-alpha_s) < delay_max(s);
+%         end
+        %rate_UE(:) > 
+        %PRB_UE(:)> 1
     cvx_end
 
 end

### 2021-06-01 Latex/journal_v1/V4/pr.tex
add latex

--- 2021-05-16 Latex/journal_v1/V3/pr.tex
@@
   \centering 
-    \includegraphics[scale = 0.4]{draw1.pdf}
+    %\includegraphics[scale = 0.4]{Drawing13.pdf}
+    \includegraphics[scale = 0.4]{Drawing13.pdf}
   \caption{Network sliced ORAN system}
@@
 Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system.
-Afterward, we discuss about assignment of physical data center resources.
+Afterward, we discuss about the assignment of physical data center resources.
 Finally, the main problem is expressed.
@@
 Suppose we have three service types includes mMTC, eMBB and URLLC which support different applications.
-Assume we have preallocated slices serving these services;
-Each Service $s\in \{1,2,3 \} $ consists of $U_{s}$ request from the 
-single-antenna UEs which require certain QoS to be able to use the requested program indicate service type).
+
+Assume we have $S_1$, $S_2$ and $S_3$ different applications for the first, second and third service type, respectively ($S = S_1 + S_2 + S_3$).
+Assume we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC) and $S_3$ slices for the third service type (mMtc).
+So each service request $s$ served by its corresponding slice.
+
+Each Service $s_j\in \{1,2,...,S_j \} $ consists of $U_{s_j}$ request from the 
+single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
 There are different application request which fall into one of these service categories.
@@
 Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
-Each slice $s_ \in \{1,23 \}$ consists of $K_{s}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2,3\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
 
@@
 
-In addition, there are $R$ single-antenna RU that are shared between slices. All RUs $r \in \{1,2,...,R \}$
-transmit signals cooperatively to all the UEs(RUs are in comp mode). Moreover, all RUs, have access to PRBs.
+In addition, there are $R$ multi-antenna o-RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
+has $J$ antenna for transmitting and receiving data.
+Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of o-RUs.
+Moreover, all RUs, have access to PRBs.
 \subsection{The Achievable Rate}
@@
 ${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
-$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice.
+$r^{th}$ o-RU to the $i^{th}$ UE in $s^{th}$ slice.
 In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
@@
 \end{equation}
-Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocate to $s^{th}$ slice or not. 
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
+Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary value that illustrates whether RU $r$ served the $i^{th}$ UE allocate to $s^{th}$ slice or not.
+Here, it is assumed that each UE is served by the nearest o-RU
+Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(s,i)}^{k}$ is the power of interfering signals represented as follow
 \begin{equation}
 \begin{split}
-I_{r,u(s,i)}^{k} &=
- \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,i)}^{k} g_{u(s,i)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
-&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
+I_{u(s,i)}^{k} &=
+ \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k} |{\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} \bold{w}_{\mathcal{R},u(s,i)}^{k} |^2}_{\text{(Interference Power)}}\\
+&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 a_{u(s,i)}}_{\text{(Quantization Noise Interference)}}
 \end{split}
 \end{equation}
-where $\gamma_{1} = e^{k}_{r,u(s,i)}e^{k}_{r',u(s,l)}a_{u(s,i)}a_{u(s,l)}$
-and $\gamma_{2} = e^{k}_{r,u(s,i)}e^{k}_{r',u(n,l)}a_{u(s,i)}a_{u(y,l)}$.
+where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}a_{u(s,i)}a_{u(s,l)}$.
 Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
-$e^{k}_{r,u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
+$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
 

### 2021-06-01 Latex/journal_v1/V4/pr.tex
latex

@@
 
-In addition, there are $R$ multi-antenna o-RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
+In addition, there are $R$ multi-antenna O-RU that are shared between slices. Each O-RU $r \in \{1,2,...,R \}$
 has $J$ antenna for transmitting and receiving data.
-Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of o-RUs.
-Moreover, all RUs, have access to PRBs.
+Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of O-RUs.
+Moreover, all O-RUs, have access to PRBs.
 \subsection{The Achievable Rate}
-The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
+The SNR of $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
 \begin{equation}\label{eq2}
@@
 \end{equation} 
-where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
+where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
 ${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 

### 2021-06-02 Latex/journal_v1/V4/pr.tex
latex .

@@
 Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2,3\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2,3\}$ preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
 
@@
 Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of O-RUs.
-Moreover, all O-RUs, have access to PRBs.
+Moreover, all O-RUs, have access to the all PRBs.
+Coordinated multipoint (CoMP) system is considered here. 
 \subsection{The Achievable Rate}

### 2021-06-09 Latex/journal_v1/V4/pr.tex
latex system model for journal

@@
 Assume we have $S_1$, $S_2$ and $S_3$ different applications for the first, second and third service type, respectively ($S = S_1 + S_2 + S_3$).
-Assume we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC) and $S_3$ slices for the third service type (mMtc).
+So, we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC) and $S_3$ slices for the third service type (mMtc).
 So each service request $s$ served by its corresponding slice.
 
-Each Service $s_j\in \{1,2,...,S_j \} $ consists of $U_{s_j}$ request from the 
+Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s}$ request from the 
 single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
@@
 Moreover, all O-RUs, have access to the all PRBs.
-Coordinated multipoint (CoMP) system is considered here. 
+%Coordinated multipoint (CoMP) system is considered here. 
 \subsection{The Achievable Rate}
 The SNR of $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
-\begin{equation}\label{eq2}
+\begin{equation}\label{eq1}
 \rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
@@
 ${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
-$r^{th}$ o-RU to the $i^{th}$ UE in $s^{th}$ slice.
-In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
+$r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice.
+In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
 \begin{equation}
@@
 \end{equation}
-Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary value that illustrates whether RU $r$ served the $i^{th}$ UE allocate to $s^{th}$ slice or not.
-Here, it is assumed that each UE is served by the nearest o-RU
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(s,i)}^{k}$ is the power of interfering signals represented as follow
-\begin{equation}
+Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
+%Here, it is assumed that each UE is served by the nearest o-RU
+Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
+
+\begin{equation}\label{eqI}
 \begin{split}
-I_{u(s,i)}^{k} &=
- \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k} |{\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} \bold{w}_{\mathcal{R},u(s,i)}^{k} |^2}_{\text{(Interference Power)}}\\
-&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 a_{u(s,i)}}_{\text{(Quantization Noise Interference)}}
+I_{r,u(s,i)}^{k} &=
+ \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
+&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
+&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 }_{\text{(Quantization Noise Interference)}}
 \end{split}
 \end{equation}
-where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}a_{u(s,i)}a_{u(s,l)}$.
-Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
+where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.\newline
 $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
 
-The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
-\begin{equation}\label{eq1}
+To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal user $i$ in $s^{th}$ service
+\begin{equation}\label{eq2}
+\textstyle y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}\mathfrak{y}^k_{r,u(s,i)}+ z_{u(s,i)},
+\end{equation}
+%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}
+where $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
+and $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
+In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization noise, which is made from signal compression in O-DU.
+
+The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$ that is formulated as below.
+\begin{equation}\label{eq3}
 \begin{split}
@@
 $\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
-Since the blocklength in URLLC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{2}^{th}$ application of service type 2 (URLLC) is not achieved from Shannon Capacity formula.
+Since the blocklength in URLLC and mMtc is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{1,2\}$) application of service type 2 (URLLC) and 3 (mMtc) is not achieved from Shannon Capacity formula.
 So, for the short packet transmission the achievable data rate is approximated from follow
@@
 \begin{split}
-\mathcal{R}_{u(s_2,i)}^{u,r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}\\
-\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 
+\mathcal{R}_{u(s_j,i)}^{u,r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){\beta}_{u(s_j,i)}^{k}\\
+\mathcal{R}_{u(s_j,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{e,r} 
 \end{split}
 \end{equation}
-Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
-and $\zeta_{u(s_2,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
+Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$, $j \in \{1,2\}$
+and $\zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})$
 Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
-$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
-$N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
-$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
+$C_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
+$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
+$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_j$.
+
+If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$.
+Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq1}.
+\subsection{Power of O-RU and Fronthaul Capacity}
+Let $P_r$ denote the power of transmitted signal from the $r^{th}$ RU to UEs served by it.
+From \eqref{eq2}, we have,
+\begin{equation}
+P_r = \sum_{s=1}^{S}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \bold{p}_{r,u(s,i)}^{k} + \sigma_{q_{r(s,j)}}^2.
+\end{equation}
+Nevertheless, the rate of users on the fronthual link between DU and the $r^{th}$ RU  is formulated as
+%\cite{simeone2016cloud, 1111}
+\begin{equation}
+C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \bold{p}_{r,u(s,i)}^{k} }{ \sigma_{q_{r}}^2})},
+\end{equation}
+where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .
+
 \subsection{Mean Delay}
@@
 So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
-Here we assume the value of propagation delay is negligible compared to the rest.
+Also, the transmission delay is the amount of time required to push all the packets into the fiber link. 
+($T = \frac{\alpha}{R}$ Where, $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of the each link which is constant in this model.)
+Here we assume the value of propagation delay and transmission is negligible compared to the rest.
 \subsubsection{Processing Delay}
@@
 \end{equation}
-\subsubsection{Transmission Delay}
-The transmission delay is the amount of time required to push all the packets into the fiber link. 
-Here, we have transmission delay in fronthaul, midhaul, backhaul and the link to transmit data to internet.
-\begin{equation}
-\begin{split}
-T_{front} =& \frac{\alpha_{s}^{f}}{R_f} \\
-T_{mid} =&  \frac{\alpha_{s}^{m}}{R_m} \\
-T_{back} =& \frac{\alpha_{s}^{b}}{R_b} \\
-T_{trans2net} =& \frac{\alpha_{s}^{t}}{R_t} \\
-\end{split}
-\end{equation}
-Where, $R_f$, $R_m$, $R_b$ and $R_t$ are the rate of transmission in fronthaul, midhaul, backhaul and the link to transmit data to internet, respectively.
-Furthermore, the mean arrival data rate of the each link ($\alpha_{s}^i$ , $i \in \{f,m,b,t\}$) is approximately equal to others ($\alpha_{s} \approx \alpha_{s}^i$ , $i \in \{f,m,b,t\}$).  
-\subsection{Delay for URLLC}
-As we know, UEs request URLLC services, require services with low latency.
-For the M/M/1 system, the probability of the delay for each application $s$ in the UPF, CU, DU and RU is as follow, respectively
-\begin{equation}
-\begin{split}
-P_r\{T_{UPF}^{s} \geq T_{UPF}^{max}\} &= e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}\\
-P_r\{T_{CU}^{s} \geq T_{CU}^{max}\} &= e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}\\
-P_r\{T_{DU}^{s} \geq T_{DU}^{max}\} &= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}\\
-P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} &= e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}\\
-\end{split}
-\end{equation} 
-So the probability of coincidence of these events is as follow
-\begin{equation}
-P_r\{E_1, E_2, E_3, E_4\} = A_1 A_2 A_3 A_4,
-\end{equation}
-Where $E_1 = T_{UPF}^{s} \geq T_{UPF}^{max}$, $E_2 =T_{CU}^{s} \geq T_{CU}^{max} $, $E_3 =T_{DU}^{s} \geq T_{DU}^{max} $ and $E_4 =T_{RU}^{s} \geq T_{RU}^{max} $.
-Also $A_1=e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}$, $A_2=e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}$, $A_3= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}$ and $A_4 = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}$.
-\subsection{Physical Data Center Resource}
-Each VNF requires
-physical resources that contain memory, storage, CPU and Network Bandwidth.
-Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
-\begin{equation}
-\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f \},
-\end{equation}
-where $\bar{\Omega}_{s}^f\in \mathbb{C}^{4}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f$ indicate the amount of required memory, storage, CPU and and Network Bandwidth, respectively.
-Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice in DU, CU and UPF is defined as below, respectively
-\begin{equation}
-\begin{split}
-&\bar{\Omega}_{\mathfrak{z},s}^{tot,d} = \sum_{f=1}^{M_{s}^d}\bar{\Omega}_{\mathfrak{z},s}^{f,d} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
-&\bar{\Omega}_{\mathfrak{z},s}^{tot,c} = \sum_{f=1}^{M_{s}^c}\bar{\Omega}_{\mathfrak{z},s}^{f,c} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
-&\bar{\Omega}_{\mathfrak{z},s}^{tot,u} = \sum_{f=1}^{M_{s}^u}\bar{\Omega}_{\mathfrak{z},s}^{f,u} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
-\end{split}
-\end{equation}
-Where, $\bar{\Omega}_{\mathfrak{z},s}^{f,d}$, $\bar{\Omega}_{\mathfrak{z},s}^{f,c}$ and $\bar{\Omega}_{\mathfrak{z},s}^{f,u}$ are the amount of resource that a VNF required in DU, CU and UPF, respectively.
-\begin{equation}
- \bar{\Omega}_{\mathfrak{z},s}^{tot} = \bar{\Omega}_{\mathfrak{z},s}^{tot,d}+ \bar{\Omega}_{\mathfrak{z},s}^{tot,c}+\bar{\Omega}_{\mathfrak{z},s}^{tot,u}
-\end{equation} 
-Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
-The amount of memory, storage, CPU and and Network Bandwidth is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$, $\tau_{C_{j}} $ and $\tau_{N_{j}} $ for the $j^{th}$ DC, respectively
-\begin{equation*}
-\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}}, \tau_{N_{j}} \},
-\end{equation*}
-In this system model, the assignment of physical DC resources to VNFs is considered.
-Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is allocated the resources to the VNFs of $s^{th}$ slice or not.
+
+%Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
+
 \subsection{Problem Statement}

### 2021-06-10 Latex/journal_v1/V4/pr.tex
latex type journal finish system model and start algorithm part

@@
 Assume we have $S_1$, $S_2$ and $S_3$ different applications for the first, second and third service type, respectively ($S = S_1 + S_2 + S_3$).
-So, we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC) and $S_3$ slices for the third service type (mMtc).
+So, we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC) and $S_3$ slices for the third service type (mMTC).
 So each service request $s$ served by its corresponding slice.
@@
 
-The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$ that is formulated as below.
+The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as below.
 \begin{equation}\label{eq3}
 \begin{split}
-\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
-\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
+\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
+\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} 
 \end{split}
@@
 where $B$ is the bandwidth of system. 
-$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
-Since the blocklength in URLLC and mMtc is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{1,2\}$) application of service type 2 (URLLC) and 3 (mMtc) is not achieved from Shannon Capacity formula.
+$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
+Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
 So, for the short packet transmission the achievable data rate is approximated from follow
@@
 \begin{split}
-\mathcal{R}_{u(s_j,i)}^{u,r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){\beta}_{u(s_j,i)}^{k}\\
-\mathcal{R}_{u(s_j,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{e,r} 
+\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
+\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} 
 \end{split}
 \end{equation}
-Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$, $j \in \{1,2\}$
-and $\zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})$
+Where $j \in \{1,2\}$. Also we have
+\begin{equation}\label{shortPacket}
+ \zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})
+\end{equation}
 Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
-$C_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
+$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
 $N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
-$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_j$.
+$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable rate of each O-RU $r$ to UE $i$ in slice $s_j$.
 
 If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$.
-Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq1}.
+Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
 \subsection{Power of O-RU and Fronthaul Capacity}
-Let $P_r$ denote the power of transmitted signal from the $r^{th}$ RU to UEs served by it.
+Let $P_r$ denote the power of transmitted signal from the $r^{th}$ O-RU to UEs served by it.
 From \eqref{eq2}, we have,
 \begin{equation}
-P_r = \sum_{s=1}^{S}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \bold{p}_{r,u(s,i)}^{k} + \sigma_{q_{r(s,j)}}^2.
+P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q_{r(s,j)}}^2.
 \end{equation}
-Nevertheless, the rate of users on the fronthual link between DU and the $r^{th}$ RU  is formulated as
+Since we have fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
 %\cite{simeone2016cloud, 1111}
 \begin{equation}
-C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \bold{p}_{r,u(s,i)}^{k} }{ \sigma_{q_{r}}^2})},
+C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q_{r}}^2})},
 \end{equation}
-where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .
-
+Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q_{r}}^2$ is the power of quantization noise.
 \subsection{Mean Delay}
@@
 %Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
-
-\subsection{Problem Statement}
-%In this system, the goal is to minimize the cost of the system.
-Power of each O-RU is obtained as below
-\begin{equation}
-P_r =  \sum_{s=1}^{S} \sum_{i=1}^{U_v} \sum_{k=1}^{K_s}p_{r,u(s,i)}^{k}a_{u(s,i)} e^{k}_{r,u(s,i)}g_{u(s,i)}^r.
-\end{equation}
-%The total power cost of O-RUs for transmitting data to UE is depicted as follow
-%\begin{equation}
-%P_{tot} = \sum_{r=1}^{R}P_r
-%\end{equation}
+\subsection{VNF Power}
 Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
@@
 \begin{equation*}
-\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s} + \sum_{d=1}^{D_c}z_d \psi_d .
+\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s}.
 \end{equation*}
-Where,$z_d$ is shown that whether the $d^{th}$ DC is turned on or not and $\psi_d$ is a static cost when a DC is active.
-\begin{equation}
-  z_d =
-    \begin{cases}
-      1 & \sum_{s=1}^{S}y_{s,d} \geq 1 \\
-      0 & \text{otherwise}
-    \end{cases}       
-\end{equation}  
-In addition, $\phi_{s}$ is obtained from below
+Where, $\phi_{s}$ is obtained from below
 \begin{equation}
@@
 \end{equation}
-Where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively. 
-So the optimization problem is formulated as follow.
+Moreover, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, O-CU and O-DU, respectively. 
+\subsection{Problem Statement}
+The optimization problem is formulated as follow.
 The aim of this paper is to maximize the sum rate of all UEs with the presence of constraints which is written as follow,
-\begin{subequations}
+\begin{subequations}\label{problem}
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}} \ \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}} \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
@@
 &p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
-&\mathcal{R}_{u_{(s_1,i)}}^e \geq  a_{u(s_1,i)}\mathcal{R}_{min}^{s_1,e} \quad \forall s_1, \label{c13} \\
-&\mathcal{R}_{u_{(s_2,i)}}^u \geq  a_{u(s_2,i)}\mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
-& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
+&\mathcal{R}_{u_{(s_j,i)}} \geq \mathcal{R}_{min}^{s_j} \quad \forall s, j \in \{1,2,3\}, \label{c13} \\
+%&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
+& C^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
 &T_{tot}^s \leq T_{tot}^{max,s} \quad \forall s,\label{c16} \\
-& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
-&a_{u(s,i)} \leq a_{u(s,i)}\sum_{r}g^r_{u(s,i)}  \quad \forall s,\forall i, \label{c17}  \\
-& a_{u(s,i)}g^r_{u(s,i)} \leq a_{u(s,i)}g^r_{u(s,i)}\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)}  \quad \forall s,i , \label{c18} \\
-& \phi_{tot}  \leq \phi_{max}, \label{c19} \\
- &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d} 
- \quad \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c20}
+%& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
+& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{c17}  \\
+& \sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i , \label{c18} \\
+& \phi_{tot}  \leq \phi_{max}, \label{c19} 
 \end{alignat}
@@
 \end{subequations}
-where $\boldsymbol{P} =[p_{u(s,i)}] \:\: \forall s , \forall i $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{u(s,i)}] \:\: \forall s , \forall i $ denotes the binary variable for UE admission,
-$\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i \forall r, \forall k$ indicate the binary variable for PRB association.
+where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}] \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i \forall r, \forall k$ indicate the binary variable for PRB association.
 Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i \forall r$ is a binary variable for O-RU association.
-Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
-the physical DC is mapped to a VNFs of a slice or not.
-Also, $\eta$ is weighted variable to value between the benefit and the cost term of objective function.
+Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.
 \eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively. 
-Also \eqref{c13} and \eqref{c14} shows that the rate of each UE requesting eMBB and URLLC is more than a threshold, respectively.
+Also \eqref{c13} shows that the rate of each UE requesting eMBB, URLLC and mMTC is more than a threshold, respectively.
 \eqref{c15} and \eqref{c16} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
-\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
-\eqref{c17} and \eqref{c18} guarantee that if a UE in admitted by the system, O-RU and PRB is associated to it, respectively.
+%\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
+\eqref{c17} and \eqref{c18} guarantee that O-RU and PRB is associated to the UE, respectively.
 In addition, \eqref{c19} indicate that the static cost of energy of VNFs in each slice do not exceed from the threshold. 
-Moreover, in \eqref{c20}  $\mathcal{E} = \{M,S,C, N\}$ and the constraint supports
-that we have enough physical resources for VNFs of each slice.
+\section{Proposed Algorithm Scheme}
+In this section, we first apply some simplifications to the system; Solving problem \eqref{problem} is complicated due to the fact that this problem is 
+a non-convex problem and it is a 
+mixed integer non-linear problem (MINLP) with a binary variable and an integer variable. 
+In the following, we apply the simplifications to reformulate MINL parts and use iterative heuristic algorithm to solve the reformulated problem.
+We solve this problem in two level iteratively until it converges; In the first level,
+parameters ($\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}$) are obtained by relaxing and reformulating parameters and turn it to convex problem; Afterward we solve it by dual optimization problem.
+In the second level, finding optimal O-RU association ($ \boldsymbol{G}$) is concerned with the fixed parameter of power, PRB allocation and number of VNFs.   
+We repeat this procedure until the algorithm converges.
+\subsection{Sub-Problem 1}
+Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
+Here, we first simplify and relax the parameters to convexify the problem.
 
-\bibliographystyle{IEEEtran}
+As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ for $I_{r,u(s,i)}^{k}$ and lower bound $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing with $I_{r,u(s,i)}^{k}$ $\bar{I}_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3} and make them concave.
+
+Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
+To convexify \eqref{eq11}, we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}. So, a lower bound for \eqref{eq11} is given that is a concave function.
+
+Suppose UPF, O-CU and O-DU have the same processor 
+\begin{lemma}
+In problem \eqref{problem}, 
+\end{lemma}
 \bibliography{ref}

### 2021-06-12 Latex/journal_v1/V4/pr.tex
latex algorithm add

@@
 \begin{split}
-T_{DU}^{s} &= \frac{1}{\mu_d - \alpha_{s}/{M_s^{d}}},\\
-T_{CU}^{s} &= \frac{1}{\mu_c - \alpha_{s}/{M_s^{c}}}\\
-T_{UPF}^{s} &= \frac{1}{\mu_u - \alpha_{s}/{M_s^{u}}}\\
+T_{DU}^{s} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
+T_{CU}^{s} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}}\\
+T_{UPF}^{s} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}\\
 \end{split}
@@
 $M_s{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
-Moreover, $1/\mu_d$, $1/\mu_c$ and $1/\mu_u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
+Moreover, $1/\mu_s^d$, $1/\mu_s^c$ and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
 Besides, $\alpha_{s}$ is the  arrival rate which is divided
@@
 Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
-To convexify \eqref{eq11}, we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}. So, a lower bound for \eqref{eq11} is given that is a concave function.
+To convexify \eqref{eq11} (for the short packet transmission), we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}.
+So, a lower bound for \eqref{eq11} is given that is a concave function.
+\begin{equation}
+\begin{split}
+\hat{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
+\hat{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\hat{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
+ \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
+ \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}\\
+\end{split}
+\end{equation}
+Consider UPF, O-CU and O-DU have the same processor (for simplification), so we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
+the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$).
+so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
+As a result of these assumption, for simplicity, we can assume that $M_s = M_s^u = M_s^c = M_s^d $
+Using the above assumption, we have $T_{DU}^{s} = T_{CU}^{s} = T_{UPF}^{s}$ 
+\begin{equation}
+\begin{split}
+T_{process}^{s} &=  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s} \\
+T_{process}^{s} &=  T_{RU}^{s} + 3\times T_{DU}^{s}.
+\end{split}
+\end{equation}
+\begin{lemma}
+In problem \eqref{problem}, if we change the constraint \eqref{c16} to equality, the optimality of the  
+system will not be changed \cite{SystemCostMinimization}
+\end{lemma}
 
-Suppose UPF, O-CU and O-DU have the same processor 
-\begin{lemma}
-In problem \eqref{problem}, 
-\end{lemma}
+\bibliographystyle{IEEEtran}
 \bibliography{ref}

### 2021-06-15 Latex/journal_v1/V4/pr.tex
add algorithm

@@
 Here we assume the value of propagation delay and transmission is negligible compared to the rest.
+\begin{equation}
+T_{tot} \approx T_{process}
+\end{equation}
 \subsubsection{Processing Delay}
@@
 
-In addition, $T_{RU}^{s}$ is the mean transmission delay of $s^{th}$ slice on the wireless link.
-The arrival data rate of wireless link is equal to the arrival data rate of load balancers for each service.
- %\cite{frdl}.
-Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
- an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue.
- %\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. 
- Therefore,
-the mean delay of the transmission layer is
+In addition, $T_{RU}^{u(s,i)}$ is the mean transmission delay of $i^{th}$ UE in $s^{th}$ service on the wireless link.
+ The arrival data rate of wireless link for each UE i in service s is $\lambda_{u(s,i)}$
+As a result we have, $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
+Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
+an exponential distribution with mean $1/(R_{u(s,i)}$ and can be modeled as a M/M/1 queue.
+
+Therefore, the mean delay of the transmission layer for UE $i$ in slice $s$ is
 \begin{equation}
- T_{RU}^{s} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
-\end{equation}
-where, $R_{{tot}_s} = \sum_{u=1}^{U_s}a_{u(s,i)}R_{u(s,i)}$ is the total achievable rate of each service.
-So the mean processing delay for each UE in slice $s$ is 
-\begin{equation}
-T_{process}^{s} =  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s}
+ T_{RU}^{u(s,i)} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}};
 \end{equation}
 
+So the mean processing delay for each UE $i$ in slice $s$ is 
+\begin{equation}
+T_{process}^{u(s,i)} =  T_{RU}^{u(s,i)} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s}
+\end{equation}
+Hence, $T_{tot}^{u(s,i)} \approx T_{process}^{u(s,i)} $
 %Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
@@
 & C^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
-&T_{tot}^s \leq T_{tot}^{max,s} \quad \forall s,\label{c16} \\
+&T_{tot}^{u(s,i)}  \leq T_{max}^{s} \quad \forall i,\forall s,\label{c16} \\
+& \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
+& \mathcal{R}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\
+& 0 \leq M_s \leq M^{max}  \quad \forall s,\label{c16-3}\\
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
@@
 \end{subequations}
-where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}] \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i \forall r, \forall k$ indicate the binary variable for PRB association.
-Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i \forall r$ is a binary variable for O-RU association.
+where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}] \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association.
+Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association.
 Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.
@@
 \eqref{c15} and \eqref{c16} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
+\eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue model.
+\eqref{c16-3} restricted the number of VNF in each slice due to the limited resources.
 %\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
@@
 \begin{lemma}
-In problem \eqref{problem}, if we change the constraint \eqref{c16} to equality, the optimality of the  
-system will not be changed \cite{SystemCostMinimization}
+In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as below
+$ \forall i,\forall s$
+\begin{equation}
+\begin{split}
+&T_{max}^s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
+&M_s \geq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
+\end{split}
+\end{equation}
+Also from equation \eqref{c19}, \eqref{c16-1} and \eqref{c16-3} we have
+\begin{equation}
+0\leq M_s \leq \min\{M^{max}, \alpha_s/\mu_s, \phi_{max}/{3\phi_s}\}
+\end{equation}
+We denote $ \mathfrak{M}_s= \min\{M^{max}, \alpha_s/\mu_s, \phi_{max}/{3\phi_s}\}$.
+Thus, if we restrict \eqref{c16} to equality we have
+\begin{equation}\label{eqDelay}
+0\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
+\end{equation}
+In \eqref{eqDelay}, $0\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
+the numerator and the denominator will be both negative. Using \eqref{c16-2},
+in numerator, $\alpha_s \geq 0$, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$ and 
+$(R_{u(s,i)}-\lambda_{u(s,i)})T_{max}^s \leq 1$. So the numerator is negative.
+In denominator, it can be said approximately that $(T_{max}^s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \leq 0 $, since, $(R_{u(s,i)}-\lambda_{u(s,i)}) \leq 1/T_{max}^s$.
+Therefore, we just need to have constraint below
+\begin{equation}\label{constraint16}
+\frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
+\end{equation}
+So by reformulating the equation \eqref{constraint16}, we have a new constraint $\forall i, \forall s$ as below,
+\begin{equation}
+R_{u(s,i)} \geq \frac{\mathfrak{M}_s ((T_{max}^s\mu_s-3)\lambda_{u(s,i)} + \mu_s) - \alpha_s(T_{max}^s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T_{max}^s\mu_s-3)-\alpha_s T_{max}^s}.
+\end{equation}
+In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$.
+So we have,
+\begin{equation}
+M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
+\end{equation}
 \end{lemma}
+Despite simplifying the problem \eqref{problem}, it is still non-convex and hard to be solved.
+So the simplest approach is to relax $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$
+Furthermore, the problem can  be solved using the Lagrangian function and iterative algorithm.
+In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively).
+Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
+The Lagrangian function is written as follow
+\begin{subequations}\label{lagrang}
+\begin{alignat}{4}
+\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\chi}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
+- \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
+&+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
+&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
+&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,i)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\
+&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.
+\end{alignat}
+\end{subequations}
+where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$. Optimal power is obtained from  \eqref{lagrang}
+\begin{equation}
+p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
+\end{equation}
+where, $\mathfrak{y}_{u(v,i)}= (\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and
+$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. Also
+$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$.
+By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained \cite{mimoCran}.
 

### 2021-06-16 Latex/journal_v1/V4/pr.tex
add before change

@@
 From \eqref{eq2}, we have,
-\begin{equation}
-P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q_{r(s,j)}}^2.
+\begin{equation}\label{pr}
+P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q_r}^2.
 \end{equation}
@@
 %\cite{simeone2016cloud, 1111}
-\begin{equation}
+\begin{equation}\label{cr}
 C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q_{r}}^2})},
@@
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}} \ \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s} \bar{\mathcal{R}}_{u_{(s,k)}} \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
@@
 &p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
-&\mathcal{R}_{u_{(s_j,i)}} \geq \mathcal{R}_{min}^{s_j} \quad \forall s, j \in \{1,2,3\}, \label{c13} \\
+&\bar{\mathcal{R}}_{u_{(s_j,i)}} \geq \mathcal{R}_{min}^{s_j} \quad \forall s, j \in \{1,2,3\}, \label{c13} \\
 %&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
@@
 & \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
-& \mathcal{R}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\
+& \bar{\mathcal{R}}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\
 & 0 \leq M_s \leq M^{max}  \quad \forall s,\label{c16-3}\\
@@
 & \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{c17}  \\
-& \sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i , \label{c18} \\
+& \sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
 & \phi_{tot}  \leq \phi_{max}, \label{c19} 
@@
 
-As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ for $I_{r,u(s,i)}^{k}$ and lower bound $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing with $I_{r,u(s,i)}^{k}$ $\bar{I}_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3} and make them concave.
+As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ for $I_{r,u(s,i)}^{k}$, the lower bound $\bar{\rho}_{u(s,i)}^{k}$
+for $\rho_{u(s,i)}^{k}$ 
+and the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing with $I_{r,u(s,i)}^{k}$ $\bar{I}_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3} and make them concave.
 
@@
 \begin{split}
-\hat{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
-\hat{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\hat{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
+\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
+\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
  \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
@@
 \begin{equation}
-R_{u(s,i)} \geq \frac{\mathfrak{M}_s ((T_{max}^s\mu_s-3)\lambda_{u(s,i)} + \mu_s) - \alpha_s(T_{max}^s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T_{max}^s\mu_s-3)-\alpha_s T_{max}^s}.
+\begin{split}
+\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s ((T_{max}^s\mu_s-3)\lambda_{u(s,i)} + \mu_s) - \alpha_s(T_{max}^s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T_{max}^s\mu_s-3)-\alpha_s T_{max}^s},\\
+\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s ((T_{max}^s\mu_s-3)\lambda_{u(s,i)} + \mu_s) - \alpha_s(T_{max}^s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T_{max}^s\mu_s-3)-\alpha_s T_{max}^s},\\
+\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
+\end{split}
 \end{equation}
@@
 Furthermore, the problem can  be solved using the Lagrangian function and iterative algorithm.
-In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively).
-Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
+
+In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint
+\eqref{c15} is changed to
+ $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
+
+Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
 The Lagrangian function is written as follow
@@
 \begin{alignat}{4}
-\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\chi}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
-- \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
-&+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
-&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
-&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,i)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\
+&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathcal{\bar{R}}_{u_{(s,i)}}\\
+&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\mathcal{R}_{u_{(s,i)}}^{max})
++\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\kappa_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\varpi_{u_{(s,i)}})\\
+&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\xi_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\lambda_{u_{(s,i)}})\\
+&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}-\sigma_{q_r}^2 \times 2^{C^{r}_{max}} )\\
+&-  \sum\limits_{r=1}^{R} \mathfrak{v}_{r} (P_{r}-P_{max})\\
 &+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.
@@
 \end{subequations}
-where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$. Optimal power is obtained from  \eqref{lagrang}
-\begin{equation}
-p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
-\end{equation}
-where, $\mathfrak{y}_{u(v,i)}= (\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and
-$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. Also
-$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$.
-By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained \cite{mimoCran}.
 

### 2021-06-16 Latex/journal_v1/V4/pr.tex
add latex

@@
 So by reformulating the equation \eqref{constraint16}, we have a new constraint $\forall i, \forall s$ as below,
-\begin{equation}
+\begin{equation}\label{RM}
 \begin{split}
@@
  $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
+The combination of equations \eqref{c13} and \eqref{c15} leads to the following equation
+\begin{equation}
+\begin{split}
+\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
+P_r &\leq  \zeta_{r}.\\
+\end{split}
+\end{equation} 
+Moreover, the combination of equations \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
+\begin{equation}
+\begin{split}
+\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{max}, \lambda_{u_{(s,i)}}, \varpi_{u(s,i)} \}, \\
+\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
+\end{split}
+\end{equation}
+Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
 
-Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
 The Lagrangian function is written as follow
@@
 &\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathcal{\bar{R}}_{u_{(s,i)}}\\
-&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\mathcal{R}_{u_{(s,i)}}^{max})
-+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\kappa_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\varpi_{u_{(s,i)}})\\
-&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\xi_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\lambda_{u_{(s,i)}})\\
-&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}-\sigma_{q_r}^2 \times 2^{C^{r}_{max}} )\\
-&-  \sum\limits_{r=1}^{R} \mathfrak{v}_{r} (P_{r}-P_{max})\\
-&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.
+&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\\
+&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\\
+&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\\
+&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\\
+&-  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)} -1)\\
+&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R} \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}.
 \end{alignat}

### 2021-06-19 Latex/journal_v1/V4/pr.tex
latex algorithm

@@
 Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2,3\}$ preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of  preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
 
+All $K$ PRBs can be assigned to the all UE in each service.
 Also, each VNF instance is running on the virtual machine (VM) that are using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
@@
 \begin{equation}\label{eq1}
-\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
+\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
 \end{equation} 
@@
 \begin{split}
-\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
-\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} 
+\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
+\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
+\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)}
 \end{split}
@@
 \begin{split}
-\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
-\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} 
+\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
+\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
+\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)}
 \end{split}
@@
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s} \bar{\mathcal{R}}_{u_{(s,k)}} \ \\
+\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{r=1}^{R}g_{u(s,i)}^r \bar{\mathcal{R}}_{u_{(s,k)}} \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
@@
 & \sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
-& \phi_{tot}  \leq \phi_{max}, \label{c19} 
+& \phi_{tot}  \leq \phi_{max}, \label{c19} \\
+& g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
+& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}  
 \end{alignat}
@@
 In addition, \eqref{c19} indicate that the static cost of energy of VNFs in each slice do not exceed from the threshold. 
+Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
 \section{Proposed Algorithm Scheme}
@@
 We repeat this procedure until the algorithm converges.
-\subsection{Sub-Problem 1}
+\subsection{Sub-Problem 1}\label{sub1}
 Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
@@
 Moreover, the combination of equations \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
-\begin{equation}
+\begin{equation}\label{RConstr}
 \begin{split}
@@
 \end{subequations}
-
+\begin{lemma}
+By taking derivatives of \eqref{lagrang} (the lagrangian function), with respect to the $\boldsymbol{P}$ and the $\boldsymbol{E}$, these two variables are obtained.
+Assume, $e_{r,u(s,i)}^{k} = 1$
+\begin{equation}\label{deriveP}
+\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} = (1 + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k} + (\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k})=0
+\end{equation}
+Where
+\begin{equation}
+\begin{split}
+\mathfrak{D}_{r,u(s,i)}^{k} &= |\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
+\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
+\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
+\end{split}
+\end{equation}
+where $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
+Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
+We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
+\begin{equation}
+p_{r,u(s,i)}^{k} = [\frac{(1 + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k}} -\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.
+\end{equation}
+Also $[a]^+ = \max(0,a)$.
+In addition, PRB assignment is obtained as follow
+\begin{equation}\label{deriveE}
+\begin{split}
+\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(1+\mathfrak{h}_{u_{(s,i)}})\\
+&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
+&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
+\end{split}
+\end{equation}
+Using KKT conditions, we have
+\begin{equation}\label{deriveE1}
+e_{r,u(s,i)}^{k}\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)} - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.
+\end{equation}
+Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(1+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
+Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
+\begin{equation}
+e_{r,u(s,i)}^{k} = 
+  \begin{cases}
+      1 & u(s,i) = \text{argmax} \mathfrak{F}^{k}_{r,u(s,i)} \forall s, \forall r, \forall k\\
+      0 & \text{otherwise}
+    \end{cases}
+\end{equation}
+\end{lemma}
+Thus the user in each slice $s$ that have the largest value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$; Due to the fact that just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
+\subsection{Sub-Problem 2}
+After power allocation and PRB assignment, the remaining problem is to assign O-RU to the UE in each service.
+The problem can be solved by two different method. 
+Next we introduce the first method which is a greedy algorithm.
+\begin{enumerate}
+\item \textit{Greedy Algorithm:}
+The problem can be simplificated and reformulated as follow
+\begin{subequations}\label{problem2}
+\begin{alignat}{4}
+\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{r=1}^{R}g_{u(s,i)}^r \bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
+\text{subject to} \quad  & g_{u(s,i)}^r P_r \leq \zeta_r \quad \forall r
+ \label{p11} \\
+& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{p12}\\
+ & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}  
+\end{alignat}
+\end{subequations}
+Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
+So \eqref{problem2}, is a NP-complete 0-1 multiple knapsack problem  
+\end{enumerate} 
 \bibliographystyle{IEEEtran}

### 2021-06-20 Latex/journal_v1/V4/pr.tex
add

@@
 \begin{alignat}{4}
-\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{r=1}^{R}g_{u(s,i)}^r \bar{\mathcal{R}}_{u_{(s,k)}} \ \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\bar{\mathcal{R}}_{u_{(s,k)}} \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
@@
 so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
+So the given assumption leads to have same energy for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
 As a result of these assumption, for simplicity, we can assume that $M_s = M_s^u = M_s^c = M_s^d $
@@
 After power allocation and PRB assignment, the remaining problem is to assign O-RU to the UE in each service.
+
+Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
 The problem can be solved by two different method. 
@@
 \item \textit{Greedy Algorithm:}
-The problem can be simplificated and reformulated as follow
+The problem can be reformulated as follow
 \begin{subequations}\label{problem2}
 \begin{alignat}{4}
-\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{r=1}^{R}g_{u(s,i)}^r \bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
-\text{subject to} \quad  & g_{u(s,i)}^r P_r \leq \zeta_r \quad \forall r
+\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}  g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
+\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r
  \label{p11} \\
@@
 \end{subequations}
+Where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
+and $\mathfrak{t}_r = \zeta_r- \sigma_r$
 Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
-So \eqref{problem2}, is a NP-complete 0-1 multiple knapsack problem  
+To simplicated  and reformulated to the multiple knapsack problem suppose that each UE in each service is associated to only one O-RU. Therefore, constraint \eqref{p12} is restricted to equality
+($\sum_{r=1}^R g^r_{u(s,i)} = 1 $). By changing this constraint,
+the problem \eqref{problem2} convert to an NP-complete 0-1 multiple knapsack problem.  
+We solve this problem using GAAOU which is a greedy algorithm \eqref{alg1} as follow \cite{akccay2007greedy,lee2018dynamic}.
+Firstly, we set all variables $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$. 
+Then we define ${RU}_{resid} = \mathcal{R} $ and $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
+as a set of O-RUs and value of each O-RU, respectively.
+Afterward, we assign the O-RU that provides the highest achievable rate for each UE on the condition that 
+it does not exceed the value of each O-RU (that is a function of maximum power and capacity of O-RU).
+If it exceeds the value of O-RU, then O-RU with the next highest achievable rate is selected. 
+Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ 
+The complexity of this algorithm is about $O(N\times \mathfrak{N})$
+\begin{algorithm}
+\caption{Greedy Algorithm for Assignment of O-RU to UEs (GAAOU)}\label{alg1}
+\begin{algorithmic}[1]
+\State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{31}
+\State Set ${RU}_{resid} = \mathcal{R} $ and $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
+\For {$s \gets 1$ to $S$}\label{33}
+\For {$i \gets 1$ to $U_s$}
+\For {$r \gets 1$ to $R$}
+\State Acquire $\mathfrak{G}_r = \bar{\mathcal{R}}^r_{u_{(s,k)}}$
+\EndFor
+\State \textbf{end for}
+\State Obtain $r = \text{argmax}_r \mathfrak{G}_r$
+\While{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
+\If{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
+\State Set $g^r_{u(s,i)} = 1$ and $\mathfrak{C}_r = \mathfrak{C}_r - \psi_{r,u(s,i)}$
+\Else
+\State  ${RU}_{resid} = \mathcal{R} \setminus \{r\} $
+\EndIf
+\State \textbf{end if}
+\EndWhile
+\State \textbf{end while}
+\EndFor
+\State \textbf{end for}
+\EndFor
+\State \textbf{end for} \label{34}
+\end{algorithmic}
+\end{algorithm}
+\item\textit{Lagrangian Function:} The second method to solve the O-RU assignment is to relax $\boldsymbol{G}$ between zero and one and solve the problem using Lagrangian function.
+
 \end{enumerate} 

### 2021-06-23 Latex/journal_v1/V4/pr.tex
add algorithm

@@
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
-& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{c17}  \\
-& \sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
+& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
+& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18-1} \\
+& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
 & \phi_{tot}  \leq \phi_{max}, \label{c19} \\
@@
 %\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
-\eqref{c17} and \eqref{c18} guarantee that O-RU and PRB is associated to the UE, respectively.
+\eqref{c17} and \eqref{c18-1} guarantee that O-RU and PRB is associated to the UE, respectively.
+Also, \eqref{c18} ensure that each PRB can not be assigned to more than one UE associated to the same O-RU.
 In addition, \eqref{c19} indicate that the static cost of energy of VNFs in each slice do not exceed from the threshold. 
@@
 In \eqref{eqDelay}, $0\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
-the numerator and the denominator will be both negative. Using \eqref{c16-2},
-in numerator, $\alpha_s \geq 0$, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$ and 
-$(R_{u(s,i)}-\lambda_{u(s,i)})T_{max}^s \leq 1$. So the numerator is negative.
-In denominator, it can be said approximately that $(T_{max}^s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \leq 0 $, since, $(R_{u(s,i)}-\lambda_{u(s,i)}) \leq 1/T_{max}^s$.
+the numerator and the denominator will both have same sign. Using \eqref{c16-2},
+in numerator, $\alpha_s \geq 0$, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$ and to simplify the problem, assume 
+$(R_{u(s,i)}-\lambda_{u(s,i)})T_{max}^s \geq 1$ since the order of $T_{max}^s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T_{max}^s$.
+Therefore, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T_{max}^s$.
+So the numerator is positive.
+In denominator, it can be said approximately that $(T_{max}^s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since, $(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T_{max}^s$ as mentioned above.
 Therefore, we just need to have constraint below
@@
 \begin{split}
-\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{max}, \lambda_{u_{(s,i)}}, \varpi_{u(s,i)} \}, \\
+\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{max}, \lambda_{u_{(s,i)}}+1/T^s_{max}, \varpi_{u(s,i)} \}, \\
 \mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
@@
 Thus the user in each slice $s$ that have the largest value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$; Due to the fact that just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
-\subsection{Sub-Problem 2}
+\subsection{Sub-Problem 2}\label{sub2}
 After power allocation and PRB assignment, the remaining problem is to assign O-RU to the UE in each service.
@@
 Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
-The problem can be solved by two different method. 
-Next we introduce the first method which is a greedy algorithm.
-\begin{enumerate}
-\item \textit{Greedy Algorithm:}
+Next we introduce the  method which is a greedy algorithm.
+
+\textit{Greedy Algorithm:}
 The problem can be reformulated as follow
@@
  \label{p11} \\
-& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{p12}\\
+& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{p12}\\
  & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}  
@@
 Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
-To simplicated  and reformulated to the multiple knapsack problem suppose that each UE in each service is associated to only one O-RU. Therefore, constraint \eqref{p12} is restricted to equality
-($\sum_{r=1}^R g^r_{u(s,i)} = 1 $). By changing this constraint,
-the problem \eqref{problem2} convert to an NP-complete 0-1 multiple knapsack problem.  
+The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.  
 We solve this problem using GAAOU which is a greedy algorithm \eqref{alg1} as follow \cite{akccay2007greedy,lee2018dynamic}.
@@
 \end{algorithm}
-\item\textit{Lagrangian Function:} The second method to solve the O-RU assignment is to relax $\boldsymbol{G}$ between zero and one and solve the problem using Lagrangian function.
-
-\end{enumerate} 
+\subsection{Iterative Proposed Algorithm}
+In \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
+Here, the iterative algorithm for the whole problem is demonstrated.
+Firstly, we fixed $\boldsymbol{G}$, then $\boldsymbol{P}$ and $\boldsymbol{E}$ is achieved using Lagrangian method.  
+Afterward, $\boldsymbol{G}$ is updated using GAAOU algorithm. This process is repeated until it converges. 
+The whole algorithm is depicted as follow (Algorithm \eqref{alg2}).
+ \begin{algorithm}
+\caption{Iterative Algorithm for Power Allocation, PRB, VNF and O-RU Association (IAPPVO)}\label{alg2}
+\begin{algorithmic}[1]
+\State  Set the maximum number of iterations ${Iter}_{max}$, convergence condition $\epsilon > 0$ \label{a21}
+\State  Assign Users to O-RU randomly (Initialize $\boldsymbol{G}$) \label{a22}
+\For {$i \gets 1$ to $Iter_{max}$}\label{33}
+\State Acquire $\boldsymbol{P}^{(i)}$, $\boldsymbol{E}^{(i)}$ and $\boldsymbol{M}^{(i)}$ using Lagrangian function and sub-gradient method based on \eqref{sub1}
+\State Update $\boldsymbol{G}^{(i)}$   based on algorithm GAAOU \eqref{alg1} in  \eqref{sub2}
+\If {the algorithm converged with the tolerence of $\epsilon$}
+\State Break
+\Else 
+\State Continue the algorithm  
+\EndIf
+\State \textbf{end if}
+\EndFor
+\State \textbf{end for} \label{34}
+\end{algorithmic}
+\end{algorithm}
 \bibliographystyle{IEEEtran}

### 2021-06-26 Latex/journal_v1/V4/pr.tex
add latex

@@
 Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
-an exponential distribution with mean $1/(R_{u(s,i)}$ and can be modeled as a M/M/1 queue.
+an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue.
 
@@
 \subsection{Problem Statement}
+Suppose each slice $s$ has priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$.
 The optimization problem is formulated as follow.
@@
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\bar{\mathcal{R}}_{u_{(s,k)}} \ \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,k)}} \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
@@
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
-& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
+& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{c17}  \\
 & \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18-1} \\
@@
 \begin{alignat}{4}
-&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathcal{\bar{R}}_{u_{(s,i)}}\\
+&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\delta_s\mathcal{\bar{R}}_{u_{(s,i)}}\\
 &+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\\
@@
 \begin{equation}\label{deriveP}
-\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} = (1 + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k} + (\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k})=0
+\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} = (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k} + (\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k})=0
 \end{equation}
@@
 \begin{equation}
-p_{r,u(s,i)}^{k} = [\frac{(1 + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k}} -\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.
+p_{r,u(s,i)}^{k} = [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k}} -\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.
 \end{equation}
@@
 \begin{split}
-\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(1+\mathfrak{h}_{u_{(s,i)}})\\
+\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
 &- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
@@
 \end{equation}
-Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(1+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
+Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
 Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
@@
 Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
-Next we introduce the  method which is a greedy algorithm.
-
-\textit{Greedy Algorithm:}
+Next we introduce two methods which are both greedy algorithm.
+The first method is a greedy algorithm that assign one O-RU to each UE and the second method is
+a greedy algorithm that assign one or more than one O-RU to each UE and use coordinated multipoint (CoMP) transmissions \cite{yang2021multicast}.
+\begin{enumerate}
+\item\textit{Greedy Algorithm for Non-Comp O-RU Assignment:}
 The problem can be reformulated as follow
@@
 \begin{alignat}{4}
-\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}  g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
+\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R} \delta_s g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
 \text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r
  \label{p11} \\
-& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{p12}\\
+& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{p12}\\
  & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}  
@@
 Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
-The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.  
+The problem \eqref{problem2} is an integer linear programming.
+By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
+the problem \eqref{problem2} becomes to an NP-complete 0-1 multiple knapsack problem.  
 We solve this problem using GAAOU which is a greedy algorithm \eqref{alg1} as follow \cite{akccay2007greedy,lee2018dynamic}.
 Firstly, we set all variables $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$. 
-Then we define ${RU}_{resid} = \mathcal{R} $ and $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
-as a set of O-RUs and value of each O-RU, respectively.
-Afterward, we assign the O-RU that provides the highest achievable rate for each UE on the condition that 
+Then we define ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$  $\forall s, \forall i$ and $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
+as a set of all O-RUs and value of each O-RU, respectively.
+Next, we sort all slices based on their priority. 
+Afterward, we assign the O-RU that provides the highest achievable rate for each UE (we start from the UEs on the slices with highest priority) on the condition that 
 it does not exceed the value of each O-RU (that is a function of maximum power and capacity of O-RU).
 If it exceeds the value of O-RU, then O-RU with the next highest achievable rate is selected. 
-Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ 
-The complexity of this algorithm is about $O(N\times \mathfrak{N})$
+The complexity of sorting S slices based on their priority is $O(Slog(S))$.
+Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$. 
+The complexity of this algorithm is about $O(Slog(s)) + O(R\times \mathfrak{N})$.
+%$O(N\times \mathfrak{N})$
 \begin{algorithm}
@@
 \State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{31}
-\State Set ${RU}_{resid} = \mathcal{R} $ and $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
+\State Set $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
+\State Sort slices according to their priority factor ($\delta_s$) in descending order
 \For {$s \gets 1$ to $S$}\label{33}
 \For {$i \gets 1$ to $U_s$}
+\State $RU = 0$
 \For {$r \gets 1$ to $R$}
-\State Acquire $\mathfrak{G}_r = \bar{\mathcal{R}}^r_{u_{(s,k)}}$
+\State Acquire $\mathfrak{G}^r_{u_{(s,i)}} = \bar{\mathcal{R}}^r_{u_{(s,i)}}$
 \EndFor
 \State \textbf{end for}
-\State Obtain $r = \text{argmax}_r \mathfrak{G}_r$
-\While{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
-\If{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
-\State Set $g^r_{u(s,i)} = 1$ and $\mathfrak{C}_r = \mathfrak{C}_r - \psi_{r,u(s,i)}$
+\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
+\While{$RU == 0$}
+\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$}
+\State Set $g^{r^*}_{u(s,i)} = 1$ 
+\State Set  $\mathfrak{C}_{r^*} = \mathfrak{C}_{r^*} - \psi_{{r^*},u(s,i)}$
+\State Set $RU = 1$ 
 \Else
-\State  ${RU}_{resid} = \mathcal{R} \setminus \{r\} $
+\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
 \EndIf
@@
 \end{algorithm}
+\item\textit{Greedy Algorithm for Comp O-RU Assignment:}
+Here we want to solve problem \eqref{problem2}, by assuming that one or more than one O-RU can assign to each UE.
+We solve this problem using GACA algorithm which used GAAOU algorithm.
+In this algorithm, Firstly we sort slices based on their priority (So the UEs of slices are sorted too).
+Then we assign one O-RU to each UE based on GAAOU algorithm so we guarantee that each UE is assigned to a O-RU. Next, we want to assign more than one O-RU to UE.
+\begin{algorithm}
+\caption{Greedy Algorithm for Comp Assignment of O-RU to UEs (GACA)}\label{alg3}
+\begin{algorithmic}[1]
+\State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{31}
+\State Set $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
+\State Set $\mathtt{R}^{t} = 0$
+\State Sort slices according to their priority factor ($\delta_s$) in descending order
+\For {$s \gets 1$ to $S$}\label{33}
+\For {$i \gets 1$ to $U_s$}
+\State $RU = 0$
+\For {$r \gets 1$ to $R$}
+\State Acquire $\mathfrak{G}^r_{u_{(s,i)}} = \bar{\mathcal{R}}^r_{u_{(s,i)}}$
+\EndFor
+\State \textbf{end for}
+\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
+\While{$RU == 0$}
+\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$}
+\State Set $g^{r^*}_{u(s,i)} = 1$ 
+\State Set  $\mathfrak{C}_{r^*} = \mathfrak{C}_{r^*} - \psi_{{r^*},u(s,i)}$
+\State Set $RU = 1$ and  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
+\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
+\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
+\Else
+\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
+\EndIf
+\State \textbf{end if}
+\EndWhile
+\State \textbf{end while}
+\EndFor
+\State \textbf{end for}
+\EndFor
+\State \textbf{end for}
+\For {$s \gets 1$ to $S$}
+\For {$i \gets 1$ to $U_s$}
+\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
+\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
+\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$} 
+\State Set $\mathtt{R}^{t} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)} \bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
+\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
+\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
+\State $g^{r^*}_{u(s,i)} = 1$ 
+\State Set $\mathtt{R} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)}\bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
+\If{$\mathtt{R} \leq \mathtt{R}^{t}$}
+\State Set $g^{r^*}_{u(s,i)} = 0$
+\Else
+\State update $\mathtt{R}^{t}$
+\EndIf
+\State \textbf{end if}
+\EndIf
+\State \textbf{end if}
+\EndFor
+\State \textbf{end for}
+\EndFor
+\State \textbf{end for}
+\end{algorithmic}
+\end{algorithm} 
+\end{enumerate}
 \subsection{Iterative Proposed Algorithm}

### 2021-06-27 Latex/journal_v1/V5/pr.tex
latex abstract

--- 2021-06-26 Latex/journal_v1/V4/pr.tex
@@
 \usepackage[margin=0.7in]{geometry}
+\usepackage[export]{adjustbox}
 \setlength{\columnsep}{11mm}
@@
 
-\title{Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}
+\title{Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
 }
@@
 \begin{abstract}
+Nowadays, RAN virtualization attracts a lot of attention from operators since it 
+has significant benefits which leads to increase the flexibility and 
+reduce operator costs
+such as CAPEX and OPEX and also allow them to add new capabilities to the network more quickly.
+Also, Openness and Flexibility are two other principle points that encourage Open Radio Access Network (O-RAN)
+Alliance to establish O-RAN as a next generation of RAN systems. 
+O-RAN is a combination of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
+Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
+Central Unit (O-CU).
+O-DU and O-CU are
 
+Network Slicing, is an end-to-end logical network
+which offers services with special needs. Multiple network Slices in the same infrastructure run and manage
+and work independently.
+
+In this paper, resource allocation in an O-RAN system is considered using the concept of network slicing.
+The problem of O-RU assignment, power allocation and 
 \end{abstract}
@@
   \centering 
-    %\includegraphics[scale = 0.4]{Drawing13.pdf}
-    \includegraphics[scale = 0.4]{Drawing13.pdf}
+    \includegraphics[scale = 0.35]{Drawing15.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[height=\textheight/2,width=\textwidth/2]{Drawing14.pdf}
   \caption{Network sliced ORAN system}
@@
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
-& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{c17}  \\
+& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
 & \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18-1} \\
@@
 Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
-Next we introduce two methods which are both greedy algorithm.
-The first method is a greedy algorithm that assign one O-RU to each UE and the second method is
-a greedy algorithm that assign one or more than one O-RU to each UE and use coordinated multipoint (CoMP) transmissions \cite{yang2021multicast}.
-\begin{enumerate}
-\item\textit{Greedy Algorithm for Non-Comp O-RU Assignment:}
+Next we introduce a greedy algorithm that assign one O-RU to each UE.
+
+\textit{Greedy Algorithm for Non-Comp O-RU Assignment:}
 The problem can be reformulated as follow
@@
 Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
-The problem \eqref{problem2} is an integer linear programming.
-By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
-the problem \eqref{problem2} becomes to an NP-complete 0-1 multiple knapsack problem.  
+%The problem \eqref{problem2} is an integer linear programming.
+%By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
+The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.  
 We solve this problem using GAAOU which is a greedy algorithm \eqref{alg1} as follow \cite{akccay2007greedy,lee2018dynamic}.
@@
 Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$. 
-The complexity of this algorithm is about $O(Slog(s)) + O(R\times \mathfrak{N})$.
+The complexity of this algorithm is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
 %$O(N\times \mathfrak{N})$
@@
 \State Set $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
+\State Set ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$  $\forall s, \forall i$
 \State Sort slices according to their priority factor ($\delta_s$) in descending order
@@
 \end{algorithm} 
-\item\textit{Greedy Algorithm for Comp O-RU Assignment:}
-Here we want to solve problem \eqref{problem2}, by assuming that one or more than one O-RU can assign to each UE.
-We solve this problem using GACA algorithm which used GAAOU algorithm.
-In this algorithm, Firstly we sort slices based on their priority (So the UEs of slices are sorted too).
-Then we assign one O-RU to each UE based on GAAOU algorithm so we guarantee that each UE is assigned to a O-RU. Next, we want to assign more than one O-RU to UE.
-\begin{algorithm}
-\caption{Greedy Algorithm for Comp Assignment of O-RU to UEs (GACA)}\label{alg3}
-\begin{algorithmic}[1]
-\State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{31}
-\State Set $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
-\State Set $\mathtt{R}^{t} = 0$
-\State Sort slices according to their priority factor ($\delta_s$) in descending order
-\For {$s \gets 1$ to $S$}\label{33}
-\For {$i \gets 1$ to $U_s$}
-\State $RU = 0$
-\For {$r \gets 1$ to $R$}
-\State Acquire $\mathfrak{G}^r_{u_{(s,i)}} = \bar{\mathcal{R}}^r_{u_{(s,i)}}$
-\EndFor
-\State \textbf{end for}
-\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
-\While{$RU == 0$}
-\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$}
-\State Set $g^{r^*}_{u(s,i)} = 1$ 
-\State Set  $\mathfrak{C}_{r^*} = \mathfrak{C}_{r^*} - \psi_{{r^*},u(s,i)}$
-\State Set $RU = 1$ and  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
-\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
-\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
-\Else
-\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
-\EndIf
-\State \textbf{end if}
-\EndWhile
-\State \textbf{end while}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for}
-\For {$s \gets 1$ to $S$}
-\For {$i \gets 1$ to $U_s$}
-\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
-\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
-\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$} 
-\State Set $\mathtt{R}^{t} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)} \bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
-\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
-\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
-\State $g^{r^*}_{u(s,i)} = 1$ 
-\State Set $\mathtt{R} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)}\bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
-\If{$\mathtt{R} \leq \mathtt{R}^{t}$}
-\State Set $g^{r^*}_{u(s,i)} = 0$
-\Else
-\State update $\mathtt{R}^{t}$
-\EndIf
-\State \textbf{end if}
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for}
-\end{algorithmic}
-\end{algorithm} 
-\end{enumerate}
 \subsection{Iterative Proposed Algorithm}
@@
 \State  Assign Users to O-RU randomly (Initialize $\boldsymbol{G}$) \label{a22}
-\For {$i \gets 1$ to $Iter_{max}$}\label{33}
+\For {$i \gets 1$ to $Iter_{max}$}\label{23}
 \State Acquire $\boldsymbol{P}^{(i)}$, $\boldsymbol{E}^{(i)}$ and $\boldsymbol{M}^{(i)}$ using Lagrangian function and sub-gradient method based on \eqref{sub1}
@@
 \EndFor
-\State \textbf{end for} \label{34}
+\State \textbf{end for} \label{24}
 \end{algorithmic}

### 2021-06-29 Latex/journal_v1/V5/pr.tex
add abstarct but will change in next commit

@@
 Alliance to establish O-RAN as a next generation of RAN systems. 
-O-RAN is a combination of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
+The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
 Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
 Central Unit (O-CU).
-O-DU and O-CU are
+O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
+Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface. 
+Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
 
@@
 and work independently.
+There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections.
+Here, we consider RAN slicing in O-RAN architecture
+for different type of 5G services includes URLLC, eMBB and mMTC services which contain different application instances.
 
 In this paper, resource allocation in an O-RAN system is considered using the concept of network slicing.
-The problem of O-RU assignment, power allocation and 
+Here, we optimize the baseband resources and the VM activation in O-RAN components base on their service priority for different services to maximize sum rate of system.
+The problem of baseband resources includes o-RU assignment, physical resource block (PRB) and power allocation. The main problem is a mixed integer non-linear programming  
 \end{abstract}

### 2021-06-29 Latex/journal_v1/V5/pr.tex
add abstarct1 but will change in next commit-1

@@
 reduce operator costs
-such as CAPEX and OPEX and also allow them to add new capabilities to the network more quickly.
-Also, Openness and Flexibility are two other principle points that encourage Open Radio Access Network (O-RAN)
+and allow them to add new capabilities to the network more quickly.
+Openness and Flexibility are two other principle points that encourage Open Radio Access Network (O-RAN)
 Alliance to establish O-RAN as a next generation of RAN systems. 
-The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
-Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
+O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
 Central Unit (O-CU). 
-O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
-Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface. 
-Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
-
-Network Slicing, is an end-to-end logical network
-which offers services with special needs. Multiple network Slices in the same infrastructure run and manage
-and work independently.
-There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections.
-Here, we consider RAN slicing in O-RAN architecture
-for different type of 5G services includes URLLC, eMBB and mMTC services which contain different application instances.
-
-In this paper, resource allocation in an O-RAN system is considered using the concept of network slicing.
-Here, we optimize the baseband resources and the VM activation in O-RAN components base on their service priority for different services to maximize sum rate of system.
-The problem of baseband resources includes o-RU assignment, physical resource block (PRB) and power allocation. The main problem is a mixed integer non-linear programming  
+Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
+In this paper, resource allocation in an O-RAN system is considered using the concept of network slicing, where the several end-to-end logical network share a single physical network.
+Here, we study the problem of baseband resource allocation and the VM activation in O-RAN components based on their service priority for different type of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
+According to the concept of network slicing, the isolation of different type of services in O-DU, O-CU and UPF is performed.
+The optimization of baseband resources includes O-RU assignment, physical resource block (PRB) and power allocation.
+The main problem is a mixed integer non-linear programming that can not be solved easily.
+So the problem is broken down into two different step that is solved by iterative algorithm.
+In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment 
+and the number of activated VMs. In the second step, O-RU association is carried out.  
 \end{abstract}
@@
 \section{Introduction}
+
+Nowadays, RAN virtualization attracts a lot of attention from operators since it 
+has significant benefits which leads to increase the flexibility and 
+reduce operator costs
+such as CAPEX and OPEX and also allow them to add new capabilities to the network more quickly.
+Also, Openness and Flexibility are two other principle points that encourage Open Radio Access Network (O-RAN)
+Alliance to establish O-RAN as a next generation of RAN systems. 
+%The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
+Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
+Central Unit (O-CU).
+%O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
+%Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface. 
+Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
+
+The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
+O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
+Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface.
+
+Network Slicing, is an end-to-end logical network
+which offers services with special needs. 
+Multiple network Slices in the same infrastructure run and manage
+and work independently.
+There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections.
+Here, we consider RAN slicing in O-RAN architecture
+for different type of 5G services includes  enhanced mobile broadband (eMBB) and ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services which contain different application instances.
 

### 2021-06-29 Latex/journal_v1/V5/pr.tex
add abstarct-2 but will change in next commit-2

@@
 Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
-In this paper, resource allocation in an O-RAN system is considered using the concept of network slicing, where the several end-to-end logical network share a single physical network.
-Here, we study the problem of baseband resource allocation and the VM activation in O-RAN components based on their service priority for different type of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
+In this paper, we study the problem of baseband resource allocation and the VM activation in O-RAN architecture based on their service priority for different type of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
 According to the concept of network slicing, the isolation of different type of services in O-DU, O-CU and UPF is performed.
@@
 and the number of activated VMs. In the second step, O-RU association is carried out.
+The proposed method is confirmed by the simulation results.  
 \end{abstract}
@@
 \begin{IEEEkeywords}
-
+Open Radio Access Network (O-RAN), Virtual Network function (VNF), Virtual Machine (VM)
 \end{IEEEkeywords}

### 2021-06-29 Latex/journal_v1/V5/pr.tex
add abstarct-3 but will change in next commit-3

@@
 Central Unit (O-CU). 
-Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
+Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU are virtualized and implemented as a virtual network function VNF that can be run on virtual machines (VMs) or containers.
 In this paper, we study the problem of baseband resource allocation and the VM activation in O-RAN architecture based on their service priority for different type of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
@@
 \begin{IEEEkeywords}
-Open Radio Access Network (O-RAN), Virtual Network function (VNF), Virtual Machine (VM)
+Open Radio Access Network (O-RAN), Virtual Network Function (VNF), Virtual Machine (VM)
 \end{IEEEkeywords}

### 2021-06-29 Latex/journal_v1/V5/pr.tex
add abstarct final

--- 2021-06-29 Latex/journal_v1/V5/pr.tex
@@
 \begin{abstract}
-Nowadays, RAN virtualization attracts a lot of attention from operators since it 
-has significant benefits which leads to increase the flexibility and 
+Taking the advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN)
+is introduced as a next generation of RAN systems which leads to increase the flexibility, Openness and 
 reduce operator costs
 and allow them to add new capabilities to the network more quickly.
-Openness and Flexibility are two other principle points that encourage Open Radio Access Network (O-RAN)
-Alliance to establish O-RAN as a next generation of RAN systems. 
 O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
 Central Unit (O-CU).
-Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
-In this paper, we study the problem of baseband resource allocation and the VM activation in O-RAN architecture based on their service priority for different type of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
-According to the concept of network slicing, the isolation of different type of services in O-DU, O-CU and UPF is performed.
+In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different type of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
+According to the concept of network slicing, the isolation of different type of services in O-DU, O-CU and user plane function (UPF) is performed.
+Limited fronthaul capacity and the restriction of end-to-end delay is considered in the problem.
 The optimization of baseband resources includes O-RU assignment, physical resource block (PRB) and power allocation.
-The main problem is a mixed integer non-linear programming that can not be solved easily.
-So the problem is broken down into two different step that is solved by iterative algorithm.
-In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment 
-and the number of activated VMs. In the second step, O-RU association is carried out.
-The proposed method is confirmed by the simulation results.  
+The main problem is a mixed integer non-linear programming that is tremendously difficult.
+To solve the challenging problem, we broke it down into two different steps that is solved by iterative algorithm.
+In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment 
+and the number of activated VNFs. In the second step, O-RU association is carried out.
+The proposed method is confirmed by the simulation results ina way that
+the simulations illustrate higher achievable data rate compared with a baseline scheme which only optimizes one of the baseband resources.
+
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Open Radio Access Network (O-RAN), Virtual Network function (VNF), Virtual Machine (VM)
+Open Radio Access Network (O-RAN), Virtual Network Function (VNF), 
 \end{IEEEkeywords}
@@
 
+To take advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN)
+is establish as a next generation of RAN systems. 
 Nowadays, RAN virtualization attracts a lot of attention from operators since it 
@@
 Alliance to establish O-RAN as a next generation of RAN systems. 
-%The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
+The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
 Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
 Central Unit (O-CU).
-%O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
-%Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface. 
+O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
+Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface. 
 Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
@@
 In this section, first, we  present the system model.
-Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system.
-Afterward, we discuss about the assignment of physical data center resources.
+Then, we obtain achievable data rates, power of O-RU and the fronthaul capacity for the downlink (DL) of the ORAN system.
+Afterward, we discuss about the mean delay and the power of VNFs.
 Finally, the main problem is expressed.
@@
 Where $M_s^{d}$, $M_s^{c}$ and 
-$M_s{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
+$M_s^{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
 Moreover, $1/\mu_s^d$, $1/\mu_s^c$ and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.

### 2021-06-30 Latex/journal_v1/V5/pr.tex
add introduction

@@
 and the number of activated VNFs. In the second step, O-RU association is carried out.
-The proposed method is confirmed by the simulation results ina way that
+The proposed method is confirmed by the simulation results in a way that
 the simulations illustrate higher achievable data rate compared with a baseline scheme which only optimizes one of the baseband resources.
@@
 \section{Introduction} 
-
-To take advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN)
-is establish as a next generation of RAN systems. 
 Nowadays, RAN virtualization attracts a lot of attention from operators since it 
@@
 such as CAPEX and OPEX and also allow them to add new capabilities to the network more quickly.
-Also, Openness and Flexibility are two other principle points that encourage Open Radio Access Network (O-RAN)
+In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage Open Radio Access Network (O-RAN)
 Alliance to establish O-RAN as a next generation of RAN systems. 
 The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
+CRAN, divides RAN into two parts radio remote head (RRH) and base band unit (BBU). 
+More than one distributed RRHs can be connected to a centralized BBU which is named BBU-pool\cite{han2019research}.
 Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
 Central Unit (O-CU).
+O-RU is a logical node contains RF and lower PHY.
+Moreover, the O-DU expresses another logical node that includes higher PHY, MAC and RLC.
+In addition, the O-CU depicts the logical node contains two parts, which are O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP).
+O-CU-UP hosts PDCP-UP and SDAP and
+O-CU-CP hosts PDCP-CP and RRC.
 O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
 Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface.
+The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
+RAN Intelligent Controller (RIC)- Near Real Time and O-Cloud. 
+One of the necessities of new generation of wireless networks is its intelligence.
+Based on the requirement of smart wireless network, O-RAN offers machine learning techniques.
+The two logical nodes RIC-Non Real Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time implement the algorithms for network intelligence 
+\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML}.
+
+In the concept of network slicing, a slice is an end-to-end logical network
+which offers services with special needs. 
+Multiple isolated network slices run and manage
+and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
+Different type of services includes enhanced mobile broadband (eMBB) and ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network.
+Each type of service requires special slice of network based on its QoS
+ \cite{shen2020ai,setayesh2020joint}.
+
 Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
-
-The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
-O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
-Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface.
-
-Network Slicing, is an end-to-end logical network
-which offers services with special needs. 
-Multiple network Slices in the same infrastructure run and manage
-and work independently.
-There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections.
-Here, we consider RAN slicing in O-RAN architecture
-for different type of 5G services includes  enhanced mobile broadband (eMBB) and ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services which contain different application instances.
 

### 2021-07-01 Latex/journal_v1/V5/pr.tex
introduction extend

@@
 \begin{abstract}
-Taking the advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN)
-is introduced as a next generation of RAN systems which leads to increase the flexibility, Openness and 
-reduce operator costs
-and allow them to add new capabilities to the network more quickly.
-O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
-Central Unit (O-CU).
-In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different type of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
-According to the concept of network slicing, the isolation of different type of services in O-DU, O-CU and user plane function (UPF) is performed.
-Limited fronthaul capacity and the restriction of end-to-end delay is considered in the problem.
-The optimization of baseband resources includes O-RU assignment, physical resource block (PRB) and power allocation.
-The main problem is a mixed integer non-linear programming that is tremendously difficult.
-To solve the challenging problem, we broke it down into two different steps that is solved by iterative algorithm.
-In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment 
-and the number of activated VNFs. In the second step, O-RU association is carried out.
+Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems which leads to increase flexibility, Openness, and reduce operational costs and allow them to add new capabilities to the network more quickly.
+O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for a different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
+According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
+Limited fronthaul capacity and the restriction of end-to-end delay are considered in the problem.
+The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation.
+The main problem is mixed-integer non-linear programming that is tremendously difficult.
+To solve the challenging problem, we broke it down into two different steps that the iterative algorithm solves.
+In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is carried out.
 The proposed method is confirmed by the simulation results in a way that
-the simulations illustrate higher achievable data rate compared with a baseline scheme which only optimizes one of the baseband resources.
+the simulations illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources.
 
@@
 \begin{IEEEkeywords}
-Open Radio Access Network (O-RAN), Virtual Network Function (VNF), 
+Open Radio Access Network (O-RAN), Virtual Network Function (VNF) 
 \end{IEEEkeywords}
@@
 \section{Introduction} 
-Nowadays, RAN virtualization attracts a lot of attention from operators since it 
-has significant benefits which leads to increase the flexibility and 
+Nowadays, RAN virtualization attracts significant attention from  both industry and academia since it 
+has remarkable benefits which leads to increase the flexibility and 
 reduce operator costs
@@
 which offers services with special needs. 
-Multiple isolated network slices run and manage
-and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
+Multiple isolated network slices run, manage
+,and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
 Different type of services includes enhanced mobile broadband (eMBB) and ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network.
@@
 
-Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
+To improve system performance in the fifth generation of telecommunications, the separation of network software and hardware elements has been done and introduced as network function virtualization (NFV), and virtual network functions (VNF) are system function blocks.
+The key idea of the implementation of NFV is
+to decouple software from physical hardware, dynamic scaling and the deployment of flexible network function.
+A usual NFV offer is to execute VNFs on a virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
+As a result, some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
+\subsection{Related Works}
+In \cite{SystemCostMinimization}, the authors solve the problem of obtaining beamforming and VMs activation 
+in C-RAN system with limited fronthaul capacity. The goal of the paper is to minimize the energy cost, with the system delay, fronthaul capacity and rate constraint.
 

### 2021-07-03 Latex/journal_v1/V5/pr.tex
add introduction

@@
 \section{Introduction} 
-Nowadays, RAN virtualization attracts significant attention from  both industry and academia since it 
+One of the goals of the fifth generation of wireless system is to achieve the desired QoS (such as rate, delay, power, ...) for different type of services.
+Network slicing is the best solution for this aim.
+A network slice is an end-to-end logical network
+which offers services with special needs. 
+Multiple isolated network slices run, manage
+,and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
+Different type of services includes enhanced mobile broadband (eMBB) and ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network.
+Each type of service requires special slice of network based on its QoS
+ \cite{shen2020ai,setayesh2020joint,popovski20185g}.
+
+Recently, RAN virtualization attracts significant attention from  both industry and academia since it 
 has remarkable benefits which leads to increase the flexibility and 
@@
 The two logical nodes RIC-Non Real Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time implement the algorithms for network intelligence 
-\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML}.
-
-In the concept of network slicing, a slice is an end-to-end logical network
-which offers services with special needs. 
-Multiple isolated network slices run, manage
-,and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
-Different type of services includes enhanced mobile broadband (eMBB) and ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network.
-Each type of service requires special slice of network based on its QoS
- \cite{shen2020ai,setayesh2020joint}.
+\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
 
@@
 \subsection{Related Works}
-In \cite{SystemCostMinimization}, the authors solve the problem of obtaining beamforming and VMs activation 
-in C-RAN system with limited fronthaul capacity. The goal of the paper is to minimize the energy cost, with the system delay, fronthaul capacity and rate constraint.
+Network slicing is increasingly receiving research attention.
+Many researcher, studied the problem of resource allocation in network slicing for multitenant cellular networks \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
+In \cite{lee2018dynamic},
+dynamic network slicing in multitenant heterogeneous CRAN (H-CRAN) is considered.
+The process of allocating network resources to users is discussed.
+The network slicing scheme includes a higher level, which manages user acceptance control, user communication which includes radio unit association (RRH association to maximize user rates and allocate base band resource capacity), the allocation of BBU capacity and a lower level, which is the allocation of power and physical resource blocks (PRB) among users.
+In article \cite{xiang2020realization}, network slicing in the radio section is considered for fog or F-RAN structure, in which two network slices are set for hotspots and vehicle scenarios with related infrastructure.
+In \cite{elayoubi20195g,d2020toward} the implementation of RAN level slicing is discussed in mobile network operator (MNO).
+Also the problem of resource allocation is considered.
+Moreover, the challenges facing RAN slicing have also been explored, one of which involves designing and managing multiple slices in the shared infrastructure in an efficient manner while guaranteeing the agreed
+service level agreement (SLA) for each.
+
+Multiplexing of eMBB and URLLC services on the same RAN and sharing the resources for these services is a challenging problem that many researchers pay attention to this topic.
+In \cite{setayesh2020joint,yang2020should}
+the problem of resource allocation in the coexistence of these two services (URLLC and eMBB) is considered
+based on their QoS. In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC is formulated and solved by deep reinforcement learning. In \cite{saggese2021power}
+the problem of power minimization for these two type services (URLLC and eMBB) is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA). In \cite{korrai2020ran},
+the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
+The system guarantee the latency, the service rate and the  maintenance of the reliability.
+
+Virtualization technique for RAN and core is one of the interested topics.  
+In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation 
+in C-RAN system with limited fronthaul capacity.
+The goal of this paper is to minimize the energy cost, with the system delay, fronthaul capacity and rate constraint.
+To guarantee delay for services, transmission and processing delay is modeled based on M/M/1 queuing theory.
+In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also the association of RRH to UE is considered and solved using novel methods.
 

### 2021-07-04 Latex/journal_v1/V5/pr.tex
add sth

@@
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also the association of RRH to UE is considered and solved using novel methods.
+In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in H-CRAN system is considered to maximize energy efficiency.
+\subsection{Contribution}
+The aim of this study is to jointly optimize VNF activation, power, PRB allocation ,and associate O-RUs to UEs to develop an isolated network slicing outline for different type of services in an O-RAN platform.
+The main contributions of this paper are summarized as follow:
+\begin{itemize}
+\item In this paper a network slicing model is depicted for three different type of services introduced in 5G (URLLC, eMBB and mMTC) and the problem of radio resource allocation and VNF activation is studied in an O-RAN architecture.
+\item  We formulate the problem of baseband resource allocation to maximize the weighted throughput of O-RAN
+system for different type of services with
+\end{itemize}
+
+In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
 
@@
 
-In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
 \section{System Model and Problem Formulation}\label{systemmodel}

### 2021-07-04 Latex/journal_v1/V5/pr.tex
introduction finished before figure new add

@@
 In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in H-CRAN system is considered to maximize energy efficiency.
-\subsection{Contribution}
+\subsection{Main Contribution}
 The aim of this study is to jointly optimize VNF activation, power, PRB allocation ,and associate O-RUs to UEs to develop an isolated network slicing outline for different type of services in an O-RAN platform.
@@
 \item In this paper a network slicing model is depicted for three different type of services introduced in 5G (URLLC, eMBB and mMTC) and the problem of radio resource allocation and VNF activation is studied in an O-RAN architecture.
-\item  We formulate the problem of baseband resource allocation to maximize the weighted throughput of O-RAN
-system for different type of services with
+\item  We formulate the problem of baseband resource allocation to maximize the weighted throughput of O-RAN system for different type of services with specific QoS. 
+\item The desired QoS conditions such as delay and throughput are considered for different type of services.
+We formulate the end-to end mean delay of system based in the activated VNFs and the throughput of each user.
+\item We take into account the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
+\item We model the interference of neighboring O-RU and formulate the accurate throughput
+for different type of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
+\item The main problem is a mixed-integer non linear programming that is extremely difficult to solve.
+We perform a two-step iterative algorithm to solve it.
+\item The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation and PRB association and the second-step O-RU association.
+\item For the first-step, we reformulate and simplificate the main problem to find an upper and lower bound for number of activated VNFs and using lagrangian function and KKT conditions to find optimal power and PRB allocation.
+\item For the second-step, the problem of O-RU association can be convert to a multiple knapsack problem and solved by Greedy algorithm.
 \end{itemize}

### 2021-07-04 Latex/journal_v1/V5/pr.tex
finish introduction

--- 2021-07-03 Latex/journal_v1/V5/pr.tex
@@
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also the association of RRH to UE is considered and solved using novel methods.
+In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in H-CRAN system is considered to maximize energy efficiency.
+\subsection{Main Contribution}
+The aim of this study is to jointly optimize VNF activation, power allocation, PRB allocation ,and O-RUs association to develop an isolated network slicing outline for different type of services in an O-RAN platform.
+In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
+The main contributions of this paper are summarized as follow:
+\begin{itemize}
+\item In this paper a network slicing model is depicted for three different type of services introduced in 5G (URLLC, eMBB and mMTC) and the problem of radio resource allocation and VNF activation is studied in the O-RAN architecture.
+We formulate the problem of baseband resource allocation to maximize the weighted throughput of O-RAN system for different type of services with specific QoS. 
+\item The desired QoS conditions such as delay and throughput are considered for different type of services.
+We formulate the end-to end mean delay of system based on the activated VNFs and the throughput of each user.
+We take into account the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
+We model the interference of neighboring O-RU and formulate the accurate throughput
+for different type of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
+\item The main problem is a mixed-integer non linear programming that is extremely difficult to solve.
+We perform a two-step iterative algorithm to solve it.
+The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation and PRB association and the second-step O-RU association.
+\item For the first-step, we reformulate and simplificate the main problem to find an upper and lower bound for number of activated VNFs and using lagrangian function and KKT conditions to find optimal power and PRB allocation.
+For the second-step, the problem of O-RU association can be convert to a multiple knapsack problem and solved by Greedy algorithm.
+\end{itemize}
 
-\begin{figure}
+\begin{figure*}
   \centering 
-    \includegraphics[scale = 0.35]{Drawing15.eps}
+    \includegraphics[scale = 0.5]{Drawing14.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[height=\textheight/2,width=\textwidth/2]{Drawing14.pdf}
+    %\includegraphics[width=\textwidth]{Drawing14.pdf}
   \caption{Network sliced ORAN system}
   \label{fig:c11}
-\end{figure}
+\end{figure*}
+The rest of this paper is organized as follow. The system model and the problem formulation is described 
+in Section \ref{systemmodel}. The details of our proposed resource management algorithm is 
+introduced in Seection \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Section \ref{conc}, concludes the whole paper.
 
-In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
 \section{System Model and Problem Formulation}\label{systemmodel}
@@
 Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
-\section{Proposed Algorithm Scheme}
+\section{Proposed Algorithm Scheme}\label{proAlg}
 In this section, we first apply some simplifications to the system; Solving problem \eqref{problem} is complicated due to the fact that this problem is 
@@
 \end{algorithm}
+\section{Numerical Result}\label{NE}
+\section{Conclusion}\label{conc}
 \bibliographystyle{IEEEtran}

### 2021-07-07 Latex/journal_v1/V5/pr.tex
add figure to journal

@@
 \usepackage{graphicx}
+\usepackage{blindtext}
 \usepackage{textcomp}
@@
   \author{
-    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
+    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
     \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
-    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
+    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
     \vspace{-.2cm}
@@
   \centering 
-    \includegraphics[scale = 0.5]{Drawing14.pdf}
+    \includegraphics[scale = 0.75]{finalDraw.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{Drawing14.pdf}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
   \caption{Network sliced ORAN system}
@@
 \end{figure*}
+
 The rest of this paper is organized as follow. The system model and the problem formulation is described 
@@
 
-In this section, first, we  present the system model.
+In this section, we describe the downlink system in O-RAN slicing as depicted in Figure \ref{fig:c11}. 
+Here, firstly, we present the system model.
 Then, we obtain achievable data rates, power of O-RU and the fronthaul capacity for the downlink (DL) of the ORAN system.
@@
 \end{algorithm}
-\section{Numerical Result}\label{NE}
+\section{Numerical Results}\label{NE}
+In this section, numerical results for the problem are depicted to evaluate the performance of the algorithms.
 \section{Conclusion}\label{conc}

### 2021-07-07 Latex/journal_v1/V5/pr.tex
change code

@@
 }
-%
-%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
-%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
-%\textit{Tehran University}\\
-%Tehran, Iran \\
-%mojdeh.karbalaee@ut.ac.ir}
-%\and
-%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
-%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
-%\textit{Tehran University}\\
-%Tehran, Iran \\
-%vmansouri@ut.ac.ir}
+
+\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
+\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+\textit{Tehran University}\\
+Tehran, Iran \\
+mojdeh.karbalaee@ut.ac.ir}
+\and
+\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
+\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+\textit{Tehran University}\\
+Tehran, Iran \\
+vmansouri@ut.ac.ir}
 %\and
@@
 %}
-  \author{
-    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
-    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
-    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
-    \vspace{-.2cm}
-  }
+%  \author{
+%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
+%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
+%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
+%    \vspace{-.2cm}
+%  }
  }

### 2021-07-07 Code_journal1/version10/simulation_1/main_final.m

@@ -1,0 +1,45 @@
+clear all
+clc
+run var_const
+count_min1 = 3;
+count_step1 = 2;
+count_max1 = 10;
+numvar = length(count_min1:count_step1:count_max1);
+iter_max = 3;
+sumRate = zeros(numvar,iter_max);
+%% initializing
+number_check = 0;
+for i_count = count_min1:count_step1:count_max1
+    number_check  = number_check +  1;
+    for iter = 1:iter_max
+        run RUUEFirst
+        for RU_iter = 1 : N_RU
+            run parameter_UE_change
+            alpha_m = lambda_m.*(UE_S);
+            run PRB_Pow_Alloc1
+            run findM
+            run Rate_final
+            sumRate(number_check,iter) = abs(sum(rate_UE_1));
+            iter
+            i_count
+            VNF_NUM
+        end
+
+    end
+end
+UE_num = count_min1:count_step1:count_max1;
+sumR =  zeros(1,numvar);
+sumR1 =  zeros(1,numvar);
+num = zeros(1,numvar);
+for i =1:numvar
+    for j =1:iter_max
+        if isnan(sumRate(i,j)) == 0 
+            sumR(i) = sumR(i) + sumRate(i,j);
+            num(i)=  num(i) + 1;
+        end
+    end
+    sumR1(i) = sumR(i)/num(i);
+end
+plot( UE_num , sumR1)
+
+%plot(UE_num ,mean(sumRate,2))

### 2021-07-11 Latex/journal_v1/V5/pr.tex
code generation for figure 1

@@
 Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
-Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.
-
+Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
 Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$).
@@
 \section{Numerical Results}\label{NE}
-In this section, numerical results for the problem are depicted to evaluate the performance of the algorithms.
+In this section, numerical results for the problem are depicted to evaluate the performance of the algorithms. We consider three network slice, one for eMBB, and two another for URLLC and mMtc.
+Assume we have six 4-antenna O-RU (MISO), are located in a cell with a diameter of 500 meters. We consider 20 PRB
+in the network.
+The maximum number of VNF for each slice is 20 and the mean arrival rate for eMBB and URLLC is $\lambda  = 300KHz$ and for mMTC $\lambda  = 600KHz$. 
+The other parameters of this simulations are depicted in Table \ref{table:1a}.
+\begin{table}
+ \caption {Simulation Parameter} \label{table:1a}
+ \begin{center}
+  \begin{tabular}{||c c ||}
+  \hline
+Parameter & Value \\ [0.5ex]
+  \hline\hline
+  Noise power & -174dBm\\
+  \hline
+  Bandwidth & 120 KHz \\
+  \hline
+ Maximum transmit Power of each O-RU & 38dBm \\
+  \hline
+  Minimum delay for eMBB and mMTC &  4msec \\
+  \hline
+    Minimum delay for URLLC &  1msec \\
+  \hline
+  Minimum delay for mMTC &  7msec \\
+  \hline
+  Maximum fronthaul capacity  & 200 bits/sec/Hz \\
+   \hline
+  Minimum data rate for eMBB &  30 bits/sec/Hz \\ 
+  \hline
+   Minimum data rate for URLLC and mMTC &  10 bits/sec/Hz \\ 
+  \hline
+   Maximum received power for mMTC &  20 dBM \\ [.5ex]   
+  \hline
+    Maximum received power for eMBB and URLLC &  33 dBM \\ [.5ex]   
+  \hline
+ \end{tabular}
+ \end{center}
+ \end{table}
+ The performance of the method is compared by two different method.
+The first one is a baseline scheme, which used random PRB allocation and the asociation of O-RU is based on the distance ,and channel quality, and fronthaul capacity, also the number of activated VNF for each slice is fixed.
+The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}.
+In this method, PRB and power is dynamically allocated, the number of VNFs are fixed and the UEs are associated to O-RU based on the quality of their channels, the fronthaul capacity, and channel distance and quality.
+In Fig the aggregated throughput is demonstrated versus different number of UEs in each slice for these three methods. Here we assume that slices have the same priority.
 \section{Conclusion}\label{conc}

### 2021-07-11 Latex/journal_v1/V5/pr.tex
code change1 and add one figure to latex

@@
   \hline
-  Bandwidth & 120 KHz \\
+  Bandwidth & 180 KHz \\
   \hline
@@
 In this method, PRB and power is dynamically allocated, the number of VNFs are fixed and the UEs are associated to O-RU based on the quality of their channels, the fronthaul capacity, and channel distance and quality.
-In Fig the aggregated throughput is demonstrated versus different number of UEs in each slice for these three methods. Here we assume that slices have the same priority.
+In Fig.
+\ref{fig:1} the aggregated throughput is demonstrated versus different number of UEs in each service for these three methods.
+Here we assume that services have the same priority.
+The figure, presented that the proposed algorithm is $35.6\%$ higher than the baseline scheme.
+As the number of UEs increases in each service, the aggregated throughput initially increase, but due to interference, it will decrease from 8 UEs to 10 UEs in each service.
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.45]{rate_throuput.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput vs. Number of UE in each Service }
+  \label{fig:1}
+\end{figure}
 \section{Conclusion}\label{conc}

### 2021-07-15 Latex/journal_v1/V5/pr.tex
add code

@@
 In this section, numerical results for the problem are depicted to evaluate the performance of the algorithms. We consider three network slice, one for eMBB, and two another for URLLC and mMtc.
-Assume we have six 4-antenna O-RU (MISO), are located in a cell with a diameter of 500 meters. We consider 20 PRB
+Assume we have six 4-antenna O-RU (MISO), are located in a cell with a diameter of 500 meters. We consider 25 PRB
 in the network.
@@
    \hline
-  Minimum data rate for eMBB &  30 bits/sec/Hz \\ 
+  Minimum data rate for eMBB &  20 bits/sec/Hz \\ 
   \hline
@@
 Here we assume that services have the same priority.
-The figure, presented that the proposed algorithm is $35.6\%$ higher than the baseline scheme.
-As the number of UEs increases in each service, the aggregated throughput initially increase, but due to interference, it will decrease from 8 UEs to 10 UEs in each service.
+The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.
+As the number of UEs increases in each service, the aggregated throughput initially increase, but due to the interference and the power constraint, it will saturated from 12 UEs in each service.
 \begin{figure}
   \centering 
-    \includegraphics[scale = 0.45]{rate_throuput.eps}
+    \includegraphics[scale = 0.45]{rate_ue1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}

### 2021-07-15 Code_journal1/VersionLastJournal/delay/main_final.m

@@ -1,0 +1,104 @@
+clear all
+clc
+run var_const
+count_min1 = 0.1;
+count_step1 = .1;
+count_max1 = 0.9;
+numvar = length(count_min1:count_step1:count_max1);
+iter_max = 20;
+sumRate_eMBB = zeros(numvar,iter_max);
+sumRate_URLLC = zeros(numvar,iter_max);
+sumRate1_eMBB= zeros(numvar,iter_max);
+sumRate1_URLLC = zeros(numvar,iter_max);
+RU_iter_max = N_RU-1;
+%% initializing
+number_check = 0;
+for i_count = count_min1:count_step1:count_max1
+    number_check  = number_check +  1;
+    for iter = 1:iter_max  
+        RU_iter = 1;
+        run parameter_UE_change
+        run PRB_Alloc
+        %%
+        while  RU_iter < RU_iter_max
+            
+            if RU_iter == 1
+              run RUAssociateDist  
+            end
+            run setChGain
+            alpha_m = lambda_m.*(UE_S);
+            run PRB_Pow_Alloc1
+            run findM
+            run Rate_final
+            run RUUESet
+            sumRate_eMBB(number_check,iter) = abs(sum(rate_UE_1(1:4)));
+            sumRate_URLLC(number_check,iter) = abs(sum(rate_UE_1(5:8)));
+            if sumRate_eMBB(number_check,iter) > 0
+                RU_iter = RU_iter_max + 10;
+                
+            end
+            iter
+            i_count
+            RU_iter
+            VNF_NUM
+            RU_iter = RU_iter + 1;
+        end
+        %% BaseLine Scheme
+            run PRB_rand
+            run RUAssociateDist
+            run setChGain
+            alpha_m = lambda_m.*(UE_S);
+            run PRB_Pow_Alloc2
+            run findM
+            run Rate_final
+            run RUUESet
+            sumRate1_eMBB(number_check,iter) = abs(sum(R_s_1(1)));
+            sumRate1_URLLC(number_check,iter) = abs(sum(R_s_1(2)));           
+    end
+end
+UE_num = count_min1:count_step1:count_max1;
[…]

### 2021-07-15 Code_journal1/VersionLastJournal/priority_2/PRB_Pow_Alloc1.m

@@ -1,0 +1,38 @@
+for  count_power=1:1 
+    cvx_begin
+        variables Popt(1,N_UE); 
+        run Interference
+        run Rate
+        run P_RU
+        maximize sum(rate_UE)
+        subject to
+        %Power_RU(N_UE,Popt,beamForming,var_q,N_RU,1:N_RU)<2.^(Capacity_RU(1)/1e4) * var_q*100 ;
+        %Power_RU(N_UE,Popt,beamForming,var_q,N_RU,1:N_RU)<Pmax;
+        Pow_RU <= Pmax*10;
+        Popt(:) >= 0; 
+        Popt(:) <= Pmax*2;
+        
+        %Find_Rate(BW,Popt,ChannelGain,beamForming,PRB_UE,N_PRB,N_UE,N0,Intf,1:N_UE)>= Rmin_UE(1);
+        rate_UE(:) >= Rmin_UE(:);%.*admission_UE1(:); 
+        w1(1,:) = alpha_m(:).* delay_max(:);
+        w2(1,:) = alpha_m(:).*lambda_m(:) .* delay_max(:) + alpha_m(:);
+        w3(1,:) = mu(:).* delay_max(:)-3;
+        w4(1,:) = mu(:).* delay_max(:).*lambda_m(:)+mu(:) - 3*lambda_m(:);
+        %w1(:).*R_s(:)-w2(:)- M_max*(w3(:).*R_s(:)-w4(:)) <= 0;
+        %R_s(:) <= (w2(:) - M_max*w4(:))./((w1(:) - M_max*w3(:)))
+        t = 0;
+        a = zeros(1,S);
+        M_max = 25;
+        for s = 1:S-1
+            for j = 1:UE_S(s)
+                t = t+1;
+                a(s) = (w2(s) - M_max*w4(s))./((w1(s) - M_max*w3(s)));
+                %Popt(t) <= (2^(a(s)/BW)-1)*(Intf(t)*0+BW*N0)/(abs((ChannelGain(:,t))'*beamForming(:,t))^2)
+                %rate_UE(t) >= max(a(s),0)
+            end
+        end
+        
+        %alpha_m(:).*(delay_max(:) - xx(:))-(mu(:).*(delay_max(:) - xx(:))-1)*10 <= 0
+    cvx_end
+
+end

### 2021-07-15 Code_journal1/VersionLastJournal/priority_3/var_const.m

@@ -1,0 +1,41 @@
+%% Initial Variable
+R = 500;
+S = 3;
+BW = 180*1e3; %10*1e6;  
+n0 = -174; %-174 dbm
+N0 = db2pow(n0)/1000;
+Pc1 = 10; %watt
+Pc  = db2pow(Pc1)/1000;
+Pt = 30;
+Pmax = db2pow(Pt)/1000;
+Rmin1 =  [60000 ,120000 ,60000];%.1*BW*randi([1,5],1,S); %.1*BW*ones(1,S)
+[Rmin, I] = sort(Rmin1,'descend');
+Rate_mid_max = [600000,420000,50000];%0.5*BW*randi([1,10],1,S);
+var_q = 1e-6;
+alpha_s = .1*BW;
+%delay_max = 3e-5*randi([1,20],1,S);
+delay_max = [1e-3, 7e-3, 5e-3];
+%mu = 1e9.*[1.5, 3, 5];%Rmin .* randi([500,520],1,S)/1000;
+mu = [7734000, 8250000, 1808400]/10;%Rmin .* randi([1200,1520],1,S)/10;
+%alpha_m  =10e8.*[0.1, 0.5, 1]; %Rmin .* randi([485,499],1,S)/1000;
+%lambda_m = 1e6*ones(1,S);
+lambda_m = [2994000, 2922000, 598800]/10;%Rmin .* randi([485,499],1,S)/10;
+%C_thresh = 3000*Rt/BW;
+%% 
+T_max = 50e-5*randi([1,10],1,S); % sec
+Delay_Slice = zeros(1,S);
+VNF_NUM =  zeros(1,S);
+N_UE_max = 6;
+N_RU = 6;
+counter_max = 5;
+M_max = 10; %max number of vnf
+%%
+C_tot_RU = sum(Rate_mid_max);
+Capacity_RU = [160500, 288900, 502900, 449400];%C_tot_RU * randi([10,50],1,N_RU)/100;
+N_Antenna = 4;
+%P_RU = zeros(1,N_RU);
+%% changable variable
+N_PRB = 25;
+Fact_S = zeros(1,S);
+%RU_PRB = randi([0 1],N_RU,N_PRB);
+%PRB_UE = randi([0,1],N_PRB,N_UE);%zeros(N_PRB, N_UE);

### 2021-07-17 Latex/journal_v1/V5/pr.tex
add figure

@@
 \usepackage{cite}
+%\usepackage{caption}
+%\usepackage{subcaption}
 \usepackage{mathtools}
@@
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
+\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
 \usepackage{graphicx}
@@
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,k)}} \ \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}} \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
@@
 In Fig.
-\ref{fig:1} the aggregated throughput is demonstrated versus different number of UEs in each service for these three methods.
+\ref{fig:1} the aggregate throughput is demonstrated versus different number of UEs in each service for these three methods.
 Here we assume that services have the same priority.
@@
   \centering 
-    \includegraphics[scale = 0.45]{rate_ue1.eps}
+    \includegraphics[scale = 0.4]{rate_ue1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 \end{figure}
+
+Assume we have two services of URLLC and mMTC. In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
+($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
+The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{mmtcurllc.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
+  \label{fig:2}
+\end{figure}
+In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{sumRatePri.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
+  \label{fig:3}
+\end{figure}
+
 \section{Conclusion}\label{conc}

### 2021-07-17 Code_journal1/VersionLastJournal/priority_1/PRB_Alloc.m

@@ -1,4 +1,4 @@
-for i =1:N_UE
+for i =1:N_UE*2/3
     if mod(i,N_PRB)==0
        PRB_UE(N_PRB,i)= 1;
     else

### 2021-07-18 Latex/journal_v1/V5/pr.tex
add paper

@@
   \hline
-  Minimum delay for eMBB and mMTC &  4msec \\
+  Maximum delay for eMBB &  4msec \\
   \hline
-    Minimum delay for URLLC &  1msec \\
+    Maximum delay for URLLC &  1msec \\
   \hline
-  Minimum delay for mMTC &  7msec \\
+  Maximum delay for mMTC &  7msec \\
   \hline
@@
   \hline
-   Maximum received power for mMTC &  20 dBM \\ [.5ex]   
+   Maximum received power for mMTC &  20 dBm \\ [.5ex]   
   \hline
-    Maximum received power for eMBB and URLLC &  33 dBM \\ [.5ex]   
+    Maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]   
   \hline
@@
 \end{figure}
+In figure \ref{fig:4}, the number of activated VNF for two different mean service time of a one eMBB service is depicted vs.
+mean arrival time.
+This figure, presented that as the mean arrival rate increases, the number of activated VNF increases.
+Moreover, the number of activated VNFs for the mean service rate of $\mu = 1.6Mbps$ is less than the number of activated VNFs for mean service rate of $\mu  =  0.8Mbps$.
+
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{vnfNum.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Number of activated VNF in each Service vs. Mean Arrival Rate(Mbps)}
+  \label{fig:4}
+\end{figure}
 

### 2021-07-18 Code_journal1/VersionLastJournal/priority_1/PRB_Pow_Alloc1.m

@@ -28,7 +28,7 @@ for  count_power=1:1
                 t = t+1;
                 a(s) = (w2(s) - M_max*w4(s))./((w1(s) - M_max*w3(s)));
                 %Popt(t) <= (2^(a(s)/BW)-1)*(Intf(t)*0+BW*N0)/(abs((ChannelGain(:,t))'*beamForming(:,t))^2)
-                rate_UE(t) >= max(a(s),0)
+                %rate_UE(t) >= max(a(s),0)
             end
         end
         

### 2021-07-20 Latex/journal_v1/V5/pr.tex
add cell

@@
 According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
-Limited fronthaul capacity and the restriction of end-to-end delay are considered in the problem.
+The limited fronthaul capacity and the restriction of end-to-end delay are considered in this problem.
 The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation.
-The main problem is mixed-integer non-linear programming that is tremendously difficult.
-To solve the challenging problem, we broke it down into two different steps that the iterative algorithm solves.
+The main problem is the mixed-integer non-linear programming that is tremendously difficult.
+To solve the challenging problem, we broke it down into two different steps that the iterative algorithm solves it.
 In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is carried out.
-The proposed method is confirmed by the simulation results in a way that
-the simulations illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources.
+The proposed method (IAPPVO) is confirmed by the simulation results in a way that
+the simulations illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm that is described in other papers.
 
@@
 \ref{fig:1} the aggregate throughput is demonstrated versus different number of UEs in each service for these three methods.
-Here we assume that services have the same priority.
-The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.
+Suppose we have one instance of service for each types of services so we have three different service in this figure.
+ Here we assume that services have the same priority. The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.
 As the number of UEs increases in each service, the aggregated throughput initially increase, but due to the interference and the power constraint, it will saturated from 12 UEs in each service.
@@
 
-Assume we have two services of URLLC and mMTC. In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
-($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
-The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
-\begin{figure}
-  \centering 
-    \includegraphics[scale = 0.4]{mmtcurllc.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
-  \label{fig:2}
-\end{figure}
-In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
-\begin{figure}
-  \centering 
-    \includegraphics[scale = 0.4]{sumRatePri.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
-  \label{fig:3}
-\end{figure}
+%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
+%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
+%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.4]{mmtcurllc.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
+%  \label{fig:2}
+%\end{figure}
+%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.4]{sumRatePri.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
+%  \label{fig:3}
+%\end{figure}
 In figure \ref{fig:4}, the number of activated VNF for two different mean service time of a one eMBB service is depicted vs.
@@
 \section{Conclusion}\label{conc}
+In this paper, we proposed the downlink of O-RAN system using network slicing for different types of 5G services (eMBB, mMTC and URLC).
+The goal of this paper is to obtain number of activated VNFs in each service, RU association, power and PRB allocation to maximize the sum-rate.
+The limited fronthaul capacity, and the mean end-to-end delay for each service is considered.
+The problem is mixed-integer non-linear programming that is solved by the iterative algorithm.
+The performance of our proposed method (IAPPVO) is compared with baseline scheme and FBDR in \cite{lee2018dynamic}.   
 \bibliographystyle{IEEEtran}

### 2021-07-20 Code_journal1/VersionLastJournal/cell/PRB_rand.m

@@ -1,0 +1,5 @@
+PRB_UE = zeros(N_PRB, N_UE);
+for i =1:N_UE
+    temp_prb  = randi(N_PRB);
+    PRB_UE(temp_prb,i)= 1;
+end

### 2021-07-20 Code_journal1/VersionLastJournal/delay/PRB_Pow_Alloc1.m

@@ -8,9 +8,9 @@ for  count_power=1:1
         subject to
         %Power_RU(N_UE,Popt,beamForming,var_q,N_RU,1:N_RU)<2.^(Capacity_RU(1)/1e4) * var_q*100 ;
         %Power_RU(N_UE,Popt,beamForming,var_q,N_RU,1:N_RU)<Pmax;
-        Pow_RU <= Pmax*10;
+        Pow_RU <= Pmax*3;
         Popt(:) >= 0; 
-        Popt(:) <= Pmax*2;
+        Popt(:) <= Pmax*1;
         
         %Find_Rate(BW,Popt,ChannelGain,beamForming,PRB_UE,N_PRB,N_UE,N0,Intf,1:N_UE)>= Rmin_UE(1);
         rate_UE(:) >= Rmin_UE(:);%.*admission_UE1(:); 

### 2021-07-20 Code_journal1/VersionLastJournal/delay/Parameter.m

@@ -34,7 +34,7 @@ for i = 1:N_UE
     %for j = 1:N_RU
         for z = 1:N_PRB
             if PRB_UE(z,i)==1
-                rate_UE(i) = rate_UE(i) + BW* log(1 + (Popt(i)*abs((ChannelGain(:,i))'*beamForming(:,i))^2)/(Intf(i)+BW*N0));%*PRB_UE(z,i);
+                rate_UE(i) = rate_UE(i) + BW* log2(1 + (Popt(i)*abs((ChannelGain(:,i))'*beamForming(:,i))^2)/(Intf(i)+BW*N0));%*PRB_UE(z,i);
             end
         end
     %end

### 2021-07-20 Code_journal1/VersionLastJournal/delay/main_final.m

@@ -1,11 +1,11 @@
 clear all
 clc
 run var_const
-count_min1 = 20e5;
-count_step1 = 20e5;
-count_max1 = 100e5;
+count_min1 = 0.1;
+count_step1 = 0.5;
+count_max1 = 3;
 numvar = length(count_min1:count_step1:count_max1);
-iter_max = 1;
+iter_max = 50;
 sumRate = zeros(numvar,iter_max);
 sumRate1= zeros(numvar,iter_max);
 DelayTot= zeros(numvar,iter_max,S);
@@ -14,7 +14,7 @@ DelayTot1= zeros(numvar,iter_max,S);
 Delay1_last_base= zeros(numvar,iter_max,S);
 VNFNumber = zeros(numvar,iter_max,S);
 VNFNumber1 = zeros(numvar,iter_max,S);
-RU_iter_max = 1;%N_RU+5;
+RU_iter_max = N_RU+5;
 %% initializing
 number_check = 0;
 for i_count = count_min1:count_step1:count_max1
@@ -39,7 +39,7 @@ for i_count = count_min1:count_step1:count_max1
             DelayTot(number_check,iter,:) = Delay_tot(:);
             Delay1_last(number_check,iter,:) = Delay_Slice1(:);
             VNFNumber(number_check,iter,:) =VNF_NUM(:);
-            if sumRate(number_check,iter) > 0 %&& RU_iter >2 
+            if sumRate(number_check,iter) > 0 && RU_iter >2 
                 RU_iter = RU_iter_max + 10;
                 
             end

### 2021-07-24 Latex/journal_v1/V5/pr.tex
add bar and power

@@
 O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for a different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
+In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
 According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
@@
 The main problem is the mixed-integer non-linear programming that is tremendously difficult.
-To solve the challenging problem, we broke it down into two different steps that the iterative algorithm solves it.
+So we broke it down into two different steps that the iterative algorithm solves it.
 In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is carried out.
-The proposed method (IAPPVO) is confirmed by the simulation results in a way that
-the simulations illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm that is described in other papers.
+The proposed method (IAPPVO) is confirmed by the simulation results so that the simulations illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers.
 
@@
 \section{Introduction} 
-One of the goals of the fifth generation of wireless system is to achieve the desired QoS (such as rate, delay, power, ...) for different type of services.
+One of the fifth-generation goals of the wireless system is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services.
 Network slicing is the best solution for this aim.
-A network slice is an end-to-end logical network
-which offers services with special needs. 
-Multiple isolated network slices run, manage
-,and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
-Different type of services includes enhanced mobile broadband (eMBB) and ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network.
-Each type of service requires special slice of network based on its QoS
+A network slice is an end-to-end logical network that offers services with special needs.
+Multiple isolated network slices run, manage, and work independently on the same infrastructure.
+There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections.
+Different type of services includes enhanced mobile broadband (eMBB), and ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network.
+Each type of service requires a particular slice of network based on its QoS
 \cite{shen2020ai,setayesh2020joint,popovski20185g}.
 
-Recently, RAN virtualization attracts significant attention from  both industry and academia since it 
-has remarkable benefits which leads to increase the flexibility and 
-reduce operator costs
-such as CAPEX and OPEX and also allow them to add new capabilities to the network more quickly.
-In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage Open Radio Access Network (O-RAN)
-Alliance to establish O-RAN as a next generation of RAN systems. 
-The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
-CRAN, divides RAN into two parts radio remote head (RRH) and base band unit (BBU). 
-More than one distributed RRHs can be connected to a centralized BBU which is named BBU-pool\cite{han2019research}.
-Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
-Central Unit (O-CU).
-O-RU is a logical node contains RF and lower PHY.
-Moreover, the O-DU expresses another logical node that includes higher PHY, MAC and RLC.
-In addition, the O-CU depicts the logical node contains two parts, which are O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP).
-O-CU-UP hosts PDCP-UP and SDAP and
-O-CU-CP hosts PDCP-CP and RRC.
-O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
-Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface.
+Recently, RAN virtualization attracts significant attention from industry and academia since it has remarkable benefits that increase flexibility and reduce operating costs such as CAPEX and OPEX and allow them to add new capabilities to the network more quickly.
+In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems.
+
+The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
+CRAN divides RAN into two parts radio remote head (RRH) and baseband unit (BBU).
+More than one distributed RRHs can be connected to a centralized BBU, which is named BBU-pool \cite{han2019research}.
+Unlike the previous generation of RAN that divides RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU). 
+O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC.
+ In addition, the O-CU depicts the logical node contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP).
+O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
+O-DU and O-CU are connected via an open and well-defined interface $F_1$.
+Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
 The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
-RAN Intelligent Controller (RIC)- Near Real Time and O-Cloud. 
-One of the necessities of new generation of wireless networks is its intelligence.
-Based on the requirement of smart wireless network, O-RAN offers machine learning techniques.
-The two logical nodes RIC-Non Real Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time implement the algorithms for network intelligence 
+RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
+One of the necessities of the new generation of wireless networks is its intelligence.
+Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques.
+The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time, implement the algorithms for network intelligence
 \cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
 
-To improve system performance in the fifth generation of telecommunications, the separation of network software and hardware elements has been done and introduced as network function virtualization (NFV), and virtual network functions (VNF) are system function blocks.
-The key idea of the implementation of NFV is
-to decouple software from physical hardware, dynamic scaling and the deployment of flexible network function.
-A usual NFV offer is to execute VNFs on a virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
-As a result, some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
+The separation of network software and hardware elements has been done and introduced as network function virtualization (NFV), and virtual network functions (VNF) are system function blocks.
+This technology improves the system performance in the fifth generation of telecommunications.
+The key idea of the implementation of NFV is to decouple software from physical hardware, dynamic scaling, and the deployment of flexible network functions.
+A usual NFV offer is to execute VNFs on virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
+As a result, some O-RAN components that include user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
 \subsection{Related Works}
 Network slicing is increasingly receiving research attention.
-Many researcher, studied the problem of resource allocation in network slicing for multitenant cellular networks \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
-In \cite{lee2018dynamic},
-dynamic network slicing in multitenant heterogeneous CRAN (H-CRAN) is considered.
+Many researchers studied the problem of resource allocation in network slicing for multitenant cellular networks \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
+In \cite{lee2018dynamic}, dynamic network slicing in multitenant heterogeneous CRAN (H-CRAN) is considered.
 The process of allocating network resources to users is discussed.
-The network slicing scheme includes a higher level, which manages user acceptance control, user communication which includes radio unit association (RRH association to maximize user rates and allocate base band resource capacity), the allocation of BBU capacity and a lower level, which is the allocation of power and physical resource blocks (PRB) among users.
-In article \cite{xiang2020realization}, network slicing in the radio section is considered for fog or F-RAN structure, in which two network slices are set for hotspots and vehicle scenarios with related infrastructure.
+The network slicing scheme includes a higher level, which manages user acceptance control, user communication includes radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity, and a lower level, which is the allocation of power and physical resource blocks (PRB) among us
+In the article, \cite{xiang2020realization}, network slicing in the radio section is considered for fog or F-RAN structure, in which two network slices are set for hotspots and vehicle scenarios with related infrastructure.
 In \cite{elayoubi20195g,d2020toward} the implementation of RAN level slicing is discussed in mobile network operator (MNO).
-Also the problem of resource allocation is considered.
-Moreover, the challenges facing RAN slicing have also been explored, one of which involves designing and managing multiple slices in the shared infrastructure in an efficient manner while guaranteeing the agreed
-service level agreement (SLA) for each.
+Also, the problem of resource allocation is considered.
+Moreover, the challenges facing RAN slicing have also been explored, one of which involves designing and managing multiple slices in the shared infrastructure in an efficient manner while guaranteeing the agreed service level agreement (SLA) for each.
 
-Multiplexing of eMBB and URLLC services on the same RAN and sharing the resources for these services is a challenging problem that many researchers pay attention to this topic.
-In \cite{setayesh2020joint,yang2020should}
-the problem of resource allocation in the coexistence of these two services (URLLC and eMBB) is considered
-based on their QoS. In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC is formulated and solved by deep reinforcement learning. In \cite{saggese2021power}
-the problem of power minimization for these two type services (URLLC and eMBB) is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA). In \cite{korrai2020ran},
-the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
-The system guarantee the latency, the service rate and the  maintenance of the reliability.
+Multiplexing eMBB and URLLC services on the same RAN and sharing the resources for these services is challenging because many researchers pay attention to this topic.
+In \cite{setayesh2020joint,yang2020should} the problem of resource allocation in the coexistence of these two services (URLLC and eMBB) is considered based on their QoS. 
+In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC is formulated and solved by deep reinforcement learning.
+ In \cite{saggese2021power} the problem of power minimization for these two types of services (URLLC and eMBB) is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
+ In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
+The system guarantees the latency, the service rate, and the maintenance of reliability.
 
-Virtualization technique for RAN and core is one of the interested topics.  
-In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation 
-in C-RAN system with limited fronthaul capacity.
-The goal of this paper is to minimize the energy cost, with the system delay, fronthaul capacity and rate constraint.
-To guarantee delay for services, transmission and processing delay is modeled based on M/M/1 queuing theory.
-In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also the association of RRH to UE is considered and solved using novel methods.
-In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in H-CRAN system is considered to maximize energy efficiency.
+Virtualization technique for RAN and core is one of the exciting topics.  
+In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
+This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
+Also, Transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the services.
+ In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to UE is considered and solved using novel methods.
+In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
 \subsection{Main Contribution}
-The aim of this study is to jointly optimize VNF activation, power allocation, PRB allocation ,and O-RUs association to develop an isolated network slicing outline for different type of services in an O-RAN platform.
+This study aims to optimize VNF activation, power allocation, PRB allocation, and O-RUs association to develop an isolated network slicing outline for different types of services in an O-RAN platform.
 In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
@@
 \begin{itemize}
-\item In this paper a network slicing model is depicted for three different type of services introduced in 5G (URLLC, eMBB and mMTC) and the problem of radio resource allocation and VNF activation is studied in the O-RAN architecture.
-We formulate the problem of baseband resource allocation to maximize the weighted throughput of O-RAN system for different type of services with specific QoS. 
-\item The desired QoS conditions such as delay and throughput are considered for different type of services.
-We formulate the end-to end mean delay of system based on the activated VNFs and the throughput of each user.
+\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G (URLLC, eMBB, and mMTC).
+The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
+We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
+\item The desired QoS conditions such as delay and throughput are considered for different types of services.
+We formulate the end-to-end mean delay of the system based on the activated VNFs and each user's throughput.
 We take into account the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
-We model the interference of neighboring O-RU and formulate the accurate throughput
-for different type of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
-\item The main problem is a mixed-integer non linear programming that is extremely difficult to solve.
+We model the interference of neighboring O-RU and formulate the actual throughput
+for different types of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
+\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
 We perform a two-step iterative algorithm to solve it.
-The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation and PRB association and the second-step O-RU association.
-\item For the first-step, we reformulate and simplificate the main problem to find an upper and lower bound for number of activated VNFs and using lagrangian function and KKT conditions to find optimal power and PRB allocation.
-For the second-step, the problem of O-RU association can be convert to a multiple knapsack problem and solved by Greedy algorithm.
+The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
+\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
+For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
 \end{itemize}
@@
 
-The rest of this paper is organized as follow. The system model and the problem formulation is described 
-in Section \ref{systemmodel}. The details of our proposed resource management algorithm is 
-introduced in Seection \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Section \ref{conc}, concludes the whole paper.
+The rest of this paper is organized as follows.
+The system model and the problem formulation are described in Section \ref{systemmodel}.
+The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}.
+In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm.
+Section \ref{conc}, concludes the whole paper.
 
@@
   \hline
-   Minimum data rate for URLLC and mMTC &  10 bits/sec/Hz \\ 
+   Minimum data rate for URLLC and mMTC &  6 bits/sec/Hz \\ 
   \hline
@@
 Suppose we have one instance of service for each types of services so we have three different service in this figure.
- Here we assume that services have the same priority. The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.
+Here, we did not consider the priority. The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.
 As the number of UEs increases in each service, the aggregated throughput initially increase, but due to the interference and the power constraint, it will saturated from 12 UEs in each service.
@@
   \centering 
-    \includegraphics[scale = 0.4]{rate_ue1.eps}
+    \includegraphics[scale = 0.5]{rate_ue1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 %\end{figure}
-In figure \ref{fig:4}, the number of activated VNF for two different mean service time of a one eMBB service is depicted vs.
-mean arrival time.
+In figure \ref{fig:4}, the number of activated VNF for the five different mean service time of a one URLLC service is depicted vs.
+mean arrival time for 12 UEs.
 This figure, presented that as the mean arrival rate increases, the number of activated VNF increases.
-Moreover, the number of activated VNFs for the mean service rate of $\mu = 1.6Mbps$ is less than the number of activated VNFs for mean service rate of $\mu  =  0.8Mbps$.
+Moreover, the number of activated VNFs decreased when the mean service rate increases.
 
@@
   \centering 
-    \includegraphics[scale = 0.4]{vnfNum.eps}
+    \includegraphics[scale = 0.5]{vnfNum1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 
+In figure \ref{fig:5}, the aggregate throughput is depicted vs.
+the maximum power of UE for three different instances of eMBB service using proposed method.
+Here, we suppose that we have 12 UEs in each service.
+We assume that these three services require 5bits/sec/Hz, 10bits/sec/Hz, and 15bits/sec/Hz.
+In addition, We suppose that each O-RU can transmit three times of the maximum power of UE. As you can see in the figure, increasing the maximum power increases the aggregate throughput.
+
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.5]{RatePower1.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput for eMBB vs. Maximum Transmit power}
+  \label{fig:5}
+\end{figure}
+
 \section{Conclusion}\label{conc}
-In this paper, we proposed the downlink of O-RAN system using network slicing for different types of 5G services (eMBB, mMTC and URLC).
-The goal of this paper is to obtain number of activated VNFs in each service, RU association, power and PRB allocation to maximize the sum-rate.
-The limited fronthaul capacity, and the mean end-to-end delay for each service is considered.
+This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services (eMBB, mMTC, and URLC).
+Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the sum rate.
+The limited fronthaul capacity and the mean end-to-end delay for each service are considered.
 The problem is mixed-integer non-linear programming that is solved by the iterative algorithm.
-The performance of our proposed method (IAPPVO) is compared with baseline scheme and FBDR in \cite{lee2018dynamic}.   
-\bibliographystyle{IEEEtran}
+The performance of our proposed method (IAPPVO) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}.
 \bibliography{ref}

### 2021-07-24 Code_journal1/VersionLastJournal/cell/main_check2.m

@@ -1,0 +1,36 @@
+number_check = 0;
+for i_count = count_min1:count_step1:count_max1
+    Pmax = i_count;
+    Popt = ones(1,N_UE)*Pmax;
+    PRB_UE = zeros(N_PRB,N_UE);
+    run PRB_Alloc
+    number_check  = number_check +  1;
+    RU_iter = 1;
+    %%
+    while  RU_iter < RU_iter_max
+
+        if RU_iter == 1
+          run RUAssociateDist  
+        end
+        run setChGain
+        alpha_m = lambda_m.*(UE_S);
+        run PRB_Pow_Alloc1
+        run findM
+        run Rate_final
+        run RUUESet
+
+        sumRate(number_check,iter) = max(abs(sum(rate_UE_1)),sumRate(number_check,iter));
+        DelayTot(number_check,iter,:) = Delay_tot(:);
+        Delay1_last(number_check,iter,:) = Delay_Slice1(:);
+        VNFNumber(number_check,iter,:) =VNF_NUM(:);
+        if sumRate(number_check,iter) > 0 && RU_iter >3 
+            RU_iter = RU_iter_max + 10;
+
+        end
+        iter
+        i_count
+        RU_iter
+        VNF_NUM
+        RU_iter = RU_iter + 1;
+    end
+end

### 2021-07-24 Code_journal1/VersionLastJournal/cell/main_check3.m

@@ -1,0 +1,29 @@
+%% initializing
+    number_check = 0;
+run PRB_rand   
+for i_count = count_min1:count_step1:count_max1
+    Pmax = i_count;
+    Popt = ones(1,N_UE)*Pmax;
+    %PRB_UE = zeros(N_PRB,N_UE);
+    number_check  = number_check +  1;
+    RU_iter = 1;
+    %run PRB_Alloc
+    %%
+    
+    %% BaseLine Scheme
+        
+        run RUAssociateDist
+        run setChGain
+        alpha_m = lambda_m.*(UE_S);
+        run PRB_Pow_Alloc2
+        run findM
+        run Rate_final
+        run RUUESet
+        VNF_NUM
+        sumRate1(number_check,iter) = abs(sum(rate_UE_1)); 
+        DelayTot1(number_check,iter,:) = Delay_tot(:);
+        Delay1_last_base(number_check,iter,:) = Delay_Slice1(:);
+        VNFNumber1(number_check,iter,:) =VNF_NUM(:);
+end
+
+ plot(sumRate1)

### 2021-07-24 Code_journal1/VersionLastJournal/cell/parameter_UE_change.m

@@ -1,4 +1,4 @@
-UE_S = 12*ones(1,S);%randi(N_UE_max,1,S);
+UE_S = 25*ones(1,S);%randi(N_UE_max,1,S);
 N_UE = sum(UE_S);
 %RU_UE = zeros(N_RU,N_UE,N_Antenna);
 %Popt = ones(1,N_UE)*Pmax;

### 2021-07-24 Code_journal1/VersionLastJournal/delay/findM.m

@@ -6,7 +6,7 @@ t = 0;
 for s = 1:S
     for numberU = 1:UE_S(s)
         t = t+ 1;
-        VNF_NUM_UE(t) = ceil((w1(s).*rate_UE(t)-w2(s))./((w3(s).*rate_UE(t)-w4(s))));
+        VNF_NUM_UE(t) = ceil((w1(s).*rate_UE_1(t)-w2(s))./((w3(s).*rate_UE_1(t)-w4(s))));
         Delay_Slice1_UE(t) = 1/(rate_UE(t)-lambda_m(s));
         VNF_NUM(s) =  max(VNF_NUM(s),VNF_NUM_UE(t));
         Delay_Slice1(s) = max(Delay_Slice1(s),Delay_Slice1_UE(t));

### 2021-07-25 Latex/journal_v1/V5/pr.tex
add 2figure

@@
 \section{Numerical Results}\label{NE}
-In this section, numerical results for the problem are depicted to evaluate the performance of the algorithms. We consider three network slice, one for eMBB, and two another for URLLC and mMtc.
-Assume we have six 4-antenna O-RU (MISO), are located in a cell with a diameter of 500 meters. We consider 25 PRB
-in the network.
+In this section, numerical results for the problem are depicted to evaluate the performance of the algorithms. We consider three network slices, one for eMBB and two for URLLC and mMtc.
+Assume we have six 4-antenna O-RU (MISO) located in a cell with a diameter of 500 meters. We consider 25 PRB in the network.
 The maximum number of VNF for each slice is 20 and the mean arrival rate for eMBB and URLLC is $\lambda  = 300KHz$ and for mMTC $\lambda  = 600KHz$. 
-The other parameters of this simulations are depicted in Table \ref{table:1a}.
+The other parameters of these simulations are depicted in Table \ref{table:1a}.
 \begin{table}
@@
   \hline
-  Maximum delay for mMTC &  7msec \\
+  Maximum delay for mMTC &  20msec \\
   \hline
@@
   \hline
-   Minimum data rate for URLLC and mMTC &  6 bits/sec/Hz \\ 
+   Minimum data rate for URLLC and mMTC &  5 bits/sec/Hz \\ 
   \hline
@@
  \end{table}
- The performance of the method is compared by two different method.
-The first one is a baseline scheme, which used random PRB allocation and the asociation of O-RU is based on the distance ,and channel quality, and fronthaul capacity, also the number of activated VNF for each slice is fixed.
+Two different methods compare the performance of the method.
+ The first one is a baseline scheme, which used random PRB allocation.
+The association of O-RU is based on the distance, channel quality, and the fronthaul capacity; also, the number of activated VNF for each slice is fixed.
 The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}.
-In this method, PRB and power is dynamically allocated, the number of VNFs are fixed and the UEs are associated to O-RU based on the quality of their channels, the fronthaul capacity, and channel distance and quality.
+In this method, PRB and power are dynamically allocated, the number of VNFs is fixed, and the UEs are associated with O-RU based on the quality of their channels, the fronthaul capacity, and channel distance and quality.
 In Fig.
-\ref{fig:1} the aggregate throughput is demonstrated versus different number of UEs in each service for these three methods.
-Suppose we have one instance of service for each types of services so we have three different service in this figure.
-Here, we did not consider the priority. The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.
-As the number of UEs increases in each service, the aggregated throughput initially increase, but due to the interference and the power constraint, it will saturated from 12 UEs in each service.
+\ref{fig:1} the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods.
+Suppose we have one service instance for each type of service, so we have three various services in this figure.
+Here, we did not consider the priority. The figure presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.
+As the number of UEs increases in each service, the aggregated throughput initially increases.
+Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
 \begin{figure}
@@
 %\end{figure}
-In figure \ref{fig:4}, the number of activated VNF for the five different mean service time of a one URLLC service is depicted vs.
-mean arrival time for 12 UEs.
-This figure, presented that as the mean arrival rate increases, the number of activated VNF increases.
+Figure \ref{fig:4}, depicts the number of activated VNF for the five different mean service times of one URLLC service vs.
+the mean arrival time for 12 UEs.
+This figure presented that as the mean arrival rate increases, the number of activated VNF increases.
 Moreover, the number of activated VNFs decreased when the mean service rate increases.
@@
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput for eMBB vs. Maximum Transmit power}
+  \caption{Aggregate Throughput for eMBB vs. Maximum Transmit power for various number of UEs }
   \label{fig:5}
@@
 
+Figure \ref{fig:6}, illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for proposed method.
+It is shown that the delay is an ascending function of the mean arrival rate and the number of UEs in the service.
+In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a URLLC service is $0.5ms$.
+Also, the maximum number of PRB is considered to be 50.
+ Moreover, we can see that the mean delay of a URLLC service 
+does not reach the maximum threshold of the delay.
+%Moreover, we can see that the mean delay of a URLLC service increases almost linearly with the mean arrival rate of the packet transmission. 
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.5]{delay_new.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Mean Total Delay of a URLCC Service vs. the Mean Arrival Rate of a UE in the Service for various number of UEs}
+  \label{fig:6}
+\end{figure}
+Figure \ref{fig:7} is the same as figure \ref{fig:7} that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
+As you can see, the proposed method (IAPPVO) outperforms the other scenarios.
+
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.5]{delay1_new.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Mean Total Delay of a URLCC Service vs. the Mean Arrival Rate of a UE in the Service for different methods}
+  \label{fig:7}
+\end{figure}
 \section{Conclusion}\label{conc}

### 2021-07-31 Latex/journal_v1/V5/pr.tex
add figure

@@
 Here, firstly, we present the system model.
-Then, we obtain achievable data rates, power of O-RU and the fronthaul capacity for the downlink (DL) of the ORAN system.
-Afterward, we discuss about the mean delay and the power of VNFs.
+Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system.
+Afterward, we discuss the mean delay and the power of VNFs.
 Finally, the main problem is expressed.
 \subsection{System Model}
-Suppose we have three service types includes mMTC, eMBB and URLLC which support different applications.
+Suppose we have three service types includes mMTC, eMBB, and URLLC, which support different applications.
 
 Assume we have $S_1$, $S_2$ and $S_3$ different applications for the first, second and third service type, respectively ($S = S_1 + S_2 + S_3$).
-So, we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC) and $S_3$ slices for the third service type (mMTC).
-So each service request $s$ served by its corresponding slice.
+So, we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
+So each service request $s$ is served by its corresponding slice.
 
-Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s}$ request from the 
-single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
-There are different application request which fall into one of these service categories.
-Each application request requires specific QoS.
-Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
+Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s}$ request from the single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
+There are different application requests which fall into one of these service categories.
+Each application request requires a specific QoS.
+Based on the application and QoS request, UE may be admitted and allocated to the resources.
 Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of  preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
 
-All $K$ PRBs can be assigned to the all UE in each service.
-Also, each VNF instance is running on the virtual machine (VM) that are using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
+All $K$ PRBs can be assigned to all UE in each service.
+Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers. Each VM requires enough resources of CPU, memory, storage, and network bandwidth.
 
 In addition, there are $R$ multi-antenna O-RU that are shared between slices. Each O-RU $r \in \{1,2,...,R \}$
-has $J$ antenna for transmitting and receiving data.
-Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of O-RUs.
-Moreover, all O-RUs, have access to the all PRBs.
+has $J$ antenna for transmitting and receiving data. Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs, have access to all PRBs.
+
 %Coordinated multipoint (CoMP) system is considered here. 
@@
 %Here, it is assumed that each UE is served by the nearest o-RU
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
+Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow.
 
@@
 Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
-So, for the short packet transmission the achievable data rate is approximated from follow
+So, for the short packet transmission, the achievable data rate is approximated from following
 \begin{equation}\label{eq11}
@@
 \subsection{Power of O-RU and Fronthaul Capacity}
-Let $P_r$ denote the power of transmitted signal from the $r^{th}$ O-RU to UEs served by it.
-From \eqref{eq2}, we have,
+Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. From \eqref{eq2}, we have,
 \begin{equation}\label{pr}
@@
 \end{equation}
-Since we have fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
+Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
 %\cite{simeone2016cloud, 1111}
@@
 \subsection{Mean Delay}
-In this part, the end to end mean delay for a service is obtained.
+In this part, the end-to-end mean delay for a service is obtained.
 Suppose the mean total delay is depicted as $T_{tot}$.
@@
 %T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
-Total delay is sum of processing delay, transmission delay and propagation delay. 
-The propagation delay is the time takes for a signal to reach to its destination.
-So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
+Total delay is the sum of processing delay, transmission delay, and propagation delay. 
+The propagation delay is the time takes for a signal to reach its destination.
+So it has a constant value based on the length of the fiber link ($T = L/c$, where $L$ is the length of the link and c is the speed of signal).
 Also, the transmission delay is the amount of time required to push all the packets into the fiber link. 
-($T = \frac{\alpha}{R}$ Where, $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of the each link which is constant in this model.)
+($T = \frac{\alpha}{R}$ Where $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of each link which is constant in this model.)
 Here we assume the value of propagation delay and transmission is negligible compared to the rest.
@@
 so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
-since, by using Burke’s Theorem, the mean arrival data rate of the second and third layer which are processed in the first layer is still Poisson with rate $\alpha_{s}$.
+since, by using Burke’s Theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still Poisson with rate $\alpha_{s}$
 It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
 Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
+Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follows, respectively.
 \begin{equation}
@@
 $M_s^{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
-Moreover, $1/\mu_s^d$, $1/\mu_s^c$ and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
+Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively.
 Besides, $\alpha_{s}$ is the  arrival rate which is divided
@@
 Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
-$\phi_{s}$. So the total power of the system for all active DCs that are connected to slices can be represented as
+$\phi_{s}$. So the system's total power for all active DCs connected to slices can be represented as follows.
 \begin{equation*}
@@
 \end{equation}
-Moreover, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, O-CU and O-DU, respectively. 
+Moreover, $\phi_s^u$, $\phi_s^c$, and $\phi_s^d$ are the fixed cost of energy in UPF, O-CU, and O-DU, respectively. 
 \subsection{Problem Statement}
@@
 The optimization problem is formulated as follow.
-The aim of this paper is to maximize the sum rate of all UEs with the presence of constraints which is written as follow,
+This paper aims to maximize the sum rate of all UEs with the presence of constraints as follows.
 \begin{subequations}\label{problem}
@@
 Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.
-\eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively. 
-Also \eqref{c13} shows that the rate of each UE requesting eMBB, URLLC and mMTC is more than a threshold, respectively.
-\eqref{c15} and \eqref{c16} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
+\eqref{c11}, and \eqref{c12}, indicate that the power of each RU does not exceed the maximum power, and the power of each UE is a positive integer value, respectively.  
+Also, \eqref{c13} shows that the rate of each UE requesting eMBB, URLLC, and mMTC is more than a threshold, respectively.
+\eqref{c15} and \eqref{c16} expressed the limited capacity of the fronthaul link and the limited delay of receiving the signal, respectively.
 \eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue model.
 \eqref{c16-3} restricted the number of VNF in each slice due to the limited resources.
-%\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
-\eqref{c17} and \eqref{c18-1} guarantee that O-RU and PRB is associated to the UE, respectively.
-Also, \eqref{c18} ensure that each PRB can not be assigned to more than one UE associated to the same O-RU.
-In addition, \eqref{c19} indicate that the static cost of energy of VNFs in each slice do not exceed from the threshold. 
+%\eqref{c16} is a reliability condition that the delay in each layer should be less than the threshold.
+\eqref{c17} and \eqref{c18-1} guarantee that O-RU and PRB are associated with the UE, respectively.
+Also, \eqref{c18} ensures that each PRB can not be assigned to more than one UE associated with the same O-RU.
+In addition, \eqref{c19} indicates that the fixed cost of energy of VNFs in each slice does not exceed the threshold. 
 Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
 \section{Proposed Algorithm Scheme}\label{proAlg}
-In this section, we first apply some simplifications to the system; Solving problem \eqref{problem} is complicated due to the fact that this problem is 
-a non-convex problem and it is a 
-mixed integer non-linear problem (MINLP) with a binary variable and an integer variable. 
-In the following, we apply the simplifications to reformulate MINL parts and use iterative heuristic algorithm to solve the reformulated problem.
-We solve this problem in two level iteratively until it converges; In the first level,
-parameters ($\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}$) are obtained by relaxing and reformulating parameters and turn it to convex problem; Afterward we solve it by dual optimization problem.
-In the second level, finding optimal O-RU association ($ \boldsymbol{G}$) is concerned with the fixed parameter of power, PRB allocation and number of VNFs.   
+In this section, we first apply some simplifications to the system; Solving problem \eqref{problem} is complicated since this problem is non-convex and it is a  mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
+We simplified and reformulated MINL parts and used an iterative heuristic algorithm to solve the problem.
+We solve this problem in two-level iteratively until it converges.
+In the first level, parameters ($\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}$) are obtained by relaxing and reformulating parameters and turn them into a convex problem; Afterward, we solve it by dual optimization problem.
+In the second level, finding optimal O-RU association ($ \boldsymbol{G}$) is concerned with the fixed parameter of power, PRB allocation, and number of VNFs.   
 We repeat this procedure until the algorithm converges.
@@
 In denominator, it can be said approximately that $(T_{max}^s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since, $(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T_{max}^s$ as mentioned above.
-Therefore, we just need to have constraint below
+Therefore, we need to have constraints below
 \begin{equation}\label{constraint16}
@@
 \end{lemma}
-Thus the user in each slice $s$ that have the largest value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$; Due to the fact that just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
+Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$.
+Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
 \subsection{Sub-Problem 2}\label{sub2}
@@
 Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
-Next we introduce a greedy algorithm that assign one O-RU to each UE.
+Next, we introduce a greedy algorithm that assigns one O-RU to each UE.
 
@@
 The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.  
-We solve this problem using GAAOU which is a greedy algorithm \eqref{alg1} as follow \cite{akccay2007greedy,lee2018dynamic}.
+We solve this problem using GAAOU, which is a greedy algorithm \eqref{alg1} as follows \cite{akccay2007greedy,lee2018dynamic}.
 Firstly, we set all variables $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$. 
@@
 Next, we sort all slices based on their priority. 
-Afterward, we assign the O-RU that provides the highest achievable rate for each UE (we start from the UEs on the slices with highest priority) on the condition that 
-it does not exceed the value of each O-RU (that is a function of maximum power and capacity of O-RU).
+Afterward, we assign the O-RU that provides the highest achievable rate for each UE (we start from the UEs on the slices with the highest priority) on the condition that 
+it does not exceed the value of each O-RU (that is, a function of maximum power and capacity of O-RU).
 If it exceeds the value of O-RU, then O-RU with the next highest achievable rate is selected. 
@@
 Here, the iterative algorithm for the whole problem is demonstrated.
-Firstly, we fixed $\boldsymbol{G}$, then $\boldsymbol{P}$ and $\boldsymbol{E}$ is achieved using Lagrangian method.  
-Afterward, $\boldsymbol{G}$ is updated using GAAOU algorithm. This process is repeated until it converges. 
-The whole algorithm is depicted as follow (Algorithm \eqref{alg2}).
+Firstly, we fixed $\boldsymbol{G}$, then $\boldsymbol{P}$ and $\boldsymbol{E}$ is achieved using the Lagrangian method.  
+Afterward, $\boldsymbol{G}$ is updated using the GAAOU algorithm. This process is repeated until it converges. 
+The whole algorithm is depicted as follows (Algorithm \eqref{alg2}).
  \begin{algorithm}

### 2021-07-31 Code_journal1/VersionLastJournal/cell/main_UE.m

@@ -29,7 +29,7 @@ for i_count = count_min1:count_step1:count_max1
             run findM
             run Rate_final
             run RUUESet
-            sumRate(number_check,iter) = abs(sum(rate_UE_1));
+            sumRate(number_check,iter) = max(abs(sum(rate_UE_1)),sumRate(number_check,iter));
             if sumRate(number_check,iter) > 0 && RU_iter>2
                 RU_iter = RU_iter_max + 10;
                 
@@ -42,14 +42,14 @@ for i_count = count_min1:count_step1:count_max1
         end
         %% BaseLine Scheme
             %run PRB_rand
-            run RUAssociateDist
-            run setChGain
-            alpha_m = lambda_m.*(UE_S);
-            run PRB_Pow_Alloc2
-            run findM
-            run Rate_final
-            run RUUESet
-            sumRate1(number_check,iter) = abs(sum(rate_UE_1));            
+%             run RUAssociateDist
+%             run setChGain
+%             alpha_m = lambda_m.*(UE_S);
+%             run PRB_Pow_Alloc2
+%             run findM
+%             run Rate_final
+%             run RUUESet
+%             sumRate1(number_check,iter) = abs(sum(rate_UE_1));            
     end
 end
 UE_num = count_min1:count_step1:count_max1;
@@ -81,7 +81,7 @@ for i =1:numvar
 end
 
 plot( UE_num , sumR1/1e6,'-*')
-hold on
-plot( UE_num , sumRB1/1e6,'-+')
+%hold on
+%plot( UE_num , sumRB1/1e6,'-+')
 
 %plot(UE_num ,mean(sumRate,2))

### 2021-07-31 Code_journal1/VersionLastJournal/cell/parameter_UE_change.m

@@ -19,7 +19,7 @@ run Channel_Gain
 run Precoding
 %RU_UE = ones(N_RU,N_UE);
 count_max = 1;
-Pmax = 0.3;
+Pmax = 0.5;
 %R = i_count;
 %lambda_m = ones(1,S)*i_count;
 %delay_max = ones(1,S)*i_count;

### 2021-07-31 Latex/journal_v1/V5/pr.tex
add figure 7

@@
 In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is carried out.
-The proposed method (IAPPVO) is confirmed by the simulation results so that the simulations illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers.
+The proposed method (IAPPVO) is confirmed by the simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers.
+Also, the simulation results achieved less end-to-end delay for the proposed method than the FBDR and baseline scheme.
 
@@
 \end{figure}
+
+Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs and the maximum power for three different mMTC services.
+mMTC services include a large number of UEs with low data rates and low power.
+Assume each service instance requires $1bits/sec/Hz$ data rate and is not sensitive to end-to-end delay.
+The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases.
+Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
+\begin{figure}
+  %\centering 
+    \includegraphics[scale = 0.42]{mmTCpower.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput for mMTC services vs. Number of UE in each Service for three different mMTC service instances}
+  \label{fig:8}
+\end{figure}
 \section{Conclusion}\label{conc}
 This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services (eMBB, mMTC, and URLC).
+The isolation of various types of services (eMBB, mMTC, and URLC) in O-DU, O-CU, and user plane function (UPF) is accomplished.
 Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the sum rate.
 The limited fronthaul capacity and the mean end-to-end delay for each service are considered.
-The problem is mixed-integer non-linear programming that is solved by the iterative algorithm.
+The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
+In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
+Then in the second step, O-RU association is acquired.
 The performance of our proposed method (IAPPVO) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
+Also, we assume distinct scenarios for each service (eMBB, URLLC, and mMTC) based on their requirement QoS.
+Simulation results depicts that the proposed method (IAPPVO) achieved $18.6\%$ higher data rate than the baseline scheme.
+Moreover, simulation results illustrate less delay for the proposed method (IAPPVO) than FBDR and baseline scheme. 
 \bibliography{ref}

### 2021-08-01 Latex/journal_v1/V5/pr.tex
add journal finilized

@@
 \begin{abstract}
-Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems which leads to increase flexibility, Openness, and reduce operational costs and allow them to add new capabilities to the network more quickly.
+Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
+O-RAN leads to increased flexibility, Openness and reduces operational costs, allowing them to add new capabilities to the network more quickly.
 O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
@@
 So we broke it down into two different steps that the iterative algorithm solves it.
-In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is carried out.
+In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is achieved.
 The proposed method (IAPPVO) is confirmed by the simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers.
-Also, the simulation results achieved less end-to-end delay for the proposed method than the FBDR and baseline scheme.
+Also, the simulation results attained less end-to-end delay for the proposed method than the FBDR and baseline scheme.
 
@@
 Network slicing is the best solution for this aim.
-A network slice is an end-to-end logical network that offers services with special needs.
+A network slice is an end-to-end logical network that offers services with specific needs.
 Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
-There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections.
+Several implementations of network slicing include network core slicing, RAN slicing, and slicing of both sections. 
 Different type of services includes enhanced mobile broadband (eMBB), and ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network.
-Each type of service requires a particular slice of network based on its QoS
-\cite{shen2020ai,setayesh2020joint,popovski20185g}.
+Each type of service requires a particular slice of network based on its QoS.
+eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and considerable coverage.
+URLLC requires low latency restrictions and higher reliability of the system.
+URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
+mMTC consists of a vast number of low power Internet of Things (IoT) devices transmitting small payloads to a typical receiver.
+In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices
+\cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.
 
@@
 We solve this problem in two-level iteratively until it converges.
-In the first level, parameters ($\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}$) are obtained by relaxing and reformulating parameters and turn them into a convex problem; Afterward, we solve it by dual optimization problem.
+In the first level, parameters ($\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}$) are obtained by relaxing and reformulating parameters to turn them into a jointly-convex problem; Afterward, we solve it by dual optimization problem.
 In the second level, finding optimal O-RU association ($ \boldsymbol{G}$) is concerned with the fixed parameter of power, PRB allocation, and number of VNFs.   
 We repeat this procedure until the algorithm converges.
+
 \subsection{Sub-Problem 1}\label{sub1}
@@
 \begin{equation}
-0\leq M_s \leq \min\{M^{max}, \alpha_s/\mu_s, \phi_{max}/{3\phi_s}\}
+\alpha_s/\mu_s\leq M_s \leq \min\{M^{max}, \phi_{max}/{3\phi_s}\}
 \end{equation}
-We denote $ \mathfrak{M}_s= \min\{M^{max}, \alpha_s/\mu_s, \phi_{max}/{3\phi_s}\}$.
+We denote $ \mathfrak{M}_s= \min\{M^{max}, \phi_{max}/{3\phi_s}\}$.
 Thus, if we restrict \eqref{c16} to equality we have
 \begin{equation}\label{eqDelay}
-0\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
+\alpha_s/\mu_s\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
 \end{equation}
@@
 \begin{equation}\label{constraint16}
-\frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
+\alpha_s/\mu_s\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
 \end{equation}
-So by reformulating the equation \eqref{constraint16}, we have a new constraint $\forall i, \forall s$ as below,
+The left side of this formula leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
+For the right side, by reformulating the equation \eqref{constraint16}, we have a new constraint $\forall i, \forall s$ as below,
 \begin{equation}\label{RM}
@@
 Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
+The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
+The complexity order of this problem is about $O(\mathfrak{N} \times K)$.
 \subsection{Sub-Problem 2}\label{sub2}
@@
 Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$. 
-The complexity of this algorithm is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
+The complexity order of this algorithm is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
 %$O(N\times \mathfrak{N})$
@@
 \end{algorithm}
+The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
+As we mentioned before, the complexity order of the first sub-problem is about $O(N_u \times K)$
+and the complexity order of the second sub-problem is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
+So the complexity of the main problem \eqref{problem} is $O(\mathfrak{N} \times K \times (Slog(S)+R\mathfrak{N}))$.
 \section{Numerical Results}\label{NE}
@@
 Assume we have six 4-antenna O-RU (MISO) located in a cell with a diameter of 500 meters. We consider 25 PRB in the network.
-The maximum number of VNF for each slice is 20 and the mean arrival rate for eMBB and URLLC is $\lambda  = 300KHz$ and for mMTC $\lambda  = 600KHz$. 
+The maximum number of VNF for each slice is 20 and the mean arrival rate for eMBB  is $\lambda  = 3Mbps$ and for mMTC and URLLC $\lambda  = 0.2Mbps$. 
 The other parameters of these simulations are depicted in Table \ref{table:1a}.
@@
   \hline
-   Minimum data rate for URLLC and mMTC &  5 bits/sec/Hz \\ 
+   Minimum data rate for URLLC and mMTC &  3 bits/sec/Hz \\ 
   \hline
@@
 
-Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs and the maximum power for three different mMTC services.
-mMTC services include a large number of UEs with low data rates and low power.
-Assume each service instance requires $1bits/sec/Hz$ data rate and is not sensitive to end-to-end delay.
+Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs and the maximum power for three different mMTC service instances.
+mMTC service includes a large number of UEs with low data rates and low power.
+Assume each UE in each mMTC service instance requires $1bits/sec/Hz$ data rate and is not sensitive to end-to-end delay.
 The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases.
@@
   \label{fig:8}
+\end{figure}
+
+Assume we have two types of eMBB service instances.
+In figure \ref{fig:9}, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances.
+Here we consider 4 UEs in each service.
+The figure \ref{fig:9} presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa.
+Also, we can realize from this figure that the aggregate throughput has the most significant value at the same priority.
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{priorityLast.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
+  \label{fig:9}
 \end{figure}
@@
 Moreover, simulation results illustrate less delay for the proposed method (IAPPVO) than FBDR and baseline scheme.
+
+\bibliographystyle{IEEEtran} 
 \bibliography{ref}

### 2021-08-01 Code_journal1/VersionLastJournal/cell/PRB_Pow_Alloc2.m

@@ -4,7 +4,8 @@ for  count_power=1:1
         run Interference
         run Rate
         run P_RU
-        maximize sum(rate_UE)
+        %a = (Fact_1*sum(rate_UE(1:UE_S(1))))+(Fact_2*sum(rate_UE(UE_S(1)+1:2*UE_S(1))))
+        maximize((Fact_1*sum(rate_UE(1:UE_S(1))))+(Fact_2*sum(rate_UE(UE_S(1)+1:2*UE_S(1)))))
         subject to
         Pow_RU <= Pmax*3;
         Popt(:) >= 0; 

### 2021-08-01 Code_journal1/VersionLastJournal/priority_1/var_const.m

@@ -8,13 +8,13 @@ Pc1 = 10; %watt
 Pc  = db2pow(Pc1)/1000;
 Pt = 30;
 Pmax = db2pow(Pt)/1000;
-Rmin1 =  [120000 ,60000 ,0];%.1*BW*randi([1,5],1,S); %.1*BW*ones(1,S)
+Rmin1 =  [60000 ,60000 ,0];%.1*BW*randi([1,5],1,S); %.1*BW*ones(1,S)
 [Rmin, I] = sort(Rmin1,'descend');
 Rate_mid_max = [600000,420000,50000];%0.5*BW*randi([1,10],1,S);
 var_q = 1e-6;
 alpha_s = .1*BW;
 %delay_max = 3e-5*randi([1,20],1,S);
-delay_max = [5e-3, 1e-3, 7e-3];
+delay_max = [5e-3, 5e-3, 7e-3];
 %mu = 1e9.*[1.5, 3, 5];%Rmin .* randi([500,520],1,S)/1000;
 mu = [7734000, 8250000, 1808400]/10;%Rmin .* randi([1200,1520],1,S)/10;
 %alpha_m  =10e8.*[0.1, 0.5, 1]; %Rmin .* randi([485,499],1,S)/1000;

### 2021-08-01 Code_journal1/VersionLastJournal/priority_2/main_final.m

@@ -2,10 +2,10 @@ clear all
 clc
 run var_const
 count_min1 = 0.1;
-count_step1 = .1;
+count_step1 = .2;
 count_max1 = 0.9;
 numvar = length(count_min1:count_step1:count_max1);
-iter_max = 1;
+iter_max = 20;
 sumRate_eMBB = zeros(numvar,iter_max);
 sumRate_URLLC = zeros(numvar,iter_max);
 sumRate1_eMBB= zeros(numvar,iter_max);
@@ -31,9 +31,9 @@ for i_count = count_min1:count_step1:count_max1
             run findM
             run Rate_final
             run RUUESet
-            sumRate_eMBB(number_check,iter) = abs(sum(rate_UE_1(1:4)));
-            sumRate_URLLC(number_check,iter) = abs(sum(rate_UE_1(5:8)));
-            if sumRate_eMBB(number_check,iter) > 0
+            sumRate_eMBB(number_check,iter) = max(abs(sum(rate_UE_1(1:4))),sumRate_eMBB(number_check,iter));
+            sumRate_URLLC(number_check,iter) = max(abs(sum(rate_UE_1(5:8))),sumRate_URLLC(number_check,iter));
+            if sumRate_eMBB(number_check,iter) > 0 && RU_iter > 2
                 RU_iter = RU_iter_max + 10;
                 
             end
@@ -64,7 +64,7 @@ sumR1_u =  zeros(1,numvar);
 num = zeros(1,numvar);
 for i =1:numvar
     for j =1:iter_max
-        if isnan(sumRate_eMBB(i,j)) == 0 
+        if isnan(sumRate_eMBB(i,j)) == 0 && sumRate_eMBB(i,j)>0
             sumR_e(i) = sumR_e(i) + sumRate_eMBB(i,j);
             sumR_u(i) = sumR_u(i) + sumRate_URLLC(i,j);
             num(i)=  num(i) + 1;

### 2021-08-01 Code_journal1/VersionLastJournal/simulLag/findM.m

@@ -1,0 +1,24 @@
+%% Find M
+VNF_NUM_UE =  zeros(1,N_UE);
+VNF_NUM = zeros(1,S);
+Delay_Slice1_UE = zeros(1,N_UE);
+t = 0;
+for s = 1:S
+    for numberU = 1:UE_S(s)
+        t = t+ 1;
+        VNF_NUM_UE(t) = ceil((w1(s).*rate_UE(t)-w2(s))./((w3(s).*rate_UE(t)-w4(s))));
+        Delay_Slice1_UE(t) = 1/(rate_UE(t)-lambda_m(s));
+        VNF_NUM(s) =  max(VNF_NUM(s),VNF_NUM_UE(t));
+        Delay_Slice1(s) = max(Delay_Slice1(s),Delay_Slice1_UE(t));
+    end
+    
+end
+
+VNF_NUM(:) = ceil((w1(:).*R_s(:)-w2(:))./((w3(:).*R_s(:)-w4(:))));
+
+Delay_tot = zeros(1,S);
+for s = 1:S
+    Delay_Slice(s) = 3/(mu(s)- alpha_m(s)/VNF_NUM(s));
+    %Delay_Slice1(s) =  1/(R_s(s)/UE_S(s)-lambda_m(s));
+    Delay_tot(s) =  Delay_Slice(s) +Delay_Slice1(s);
+end

### 2021-08-01 Code_journal1/VersionLastJournal/simulLag/update_var.m

@@ -1,0 +1,15 @@
+alpha_step = Pmax/sqrt(count)/1;
+
+for i = 1:N_UE
+    beta_step = 1/1/sqrt(count);
+    lambda_step = Rmin_UE(i)/sqrt(count)/1000;
+    lambda(i)= max(0,lambda(i) - lambda_step* (rate_UE(i) - Rmin_UE(i)));
+    for z = 1:N_PRB
+        beta(i) = max(0, beta(i) - beta_step* (PRB_UE(z,i)- 1));
+    end
+    
+end
+for j = 1:N_RU
+
+   alpha(j) = max(0, alpha(j) -alpha_step* (Pmax - Pow_RU(j))); 
+end

### 2021-08-01 Latex/journal_v1/V5/pr.tex
read paper until proposed method

@@
 Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
-Several implementations of network slicing include network core slicing, RAN slicing, and slicing of both sections. 
+Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 
 Different type of services includes enhanced mobile broadband (eMBB), and ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network.
@@
 URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
-mMTC consists of a vast number of low power Internet of Things (IoT) devices transmitting small payloads to a typical receiver.
+mMTC consists of a vast number of low power internet of ihings (IoT) devices transmitting small payloads to a typical receiver.
 In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices
@@
 In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems.
-
 The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
@@
 The key idea of the implementation of NFV is to decouple software from physical hardware, dynamic scaling, and the deployment of flexible network functions.
-A usual NFV offer is to execute VNFs on virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
+The NFV technology offers to execute VNFs on virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
 As a result, some O-RAN components that include user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
@@
 The process of allocating network resources to users is discussed.
-The network slicing scheme includes a higher level, which manages user acceptance control, user communication includes radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity, and a lower level, which is the allocation of power and physical resource blocks (PRB) among us
-In the article, \cite{xiang2020realization}, network slicing in the radio section is considered for fog or F-RAN structure, in which two network slices are set for hotspots and vehicle scenarios with related infrastructure.
+The network slicing scheme includes a higher level and the lower level.
+The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity.
+Also, in the lower level, the allocation of power and physical resource blocks (PRB) is performed.
+In the article \cite{xiang2020realization}, network slicing in the radio section is considered for fog or F-RAN structure, in which two network slices are set for hotspots and vehicle scenarios with related infrastructure.
 In \cite{elayoubi20195g,d2020toward} the implementation of RAN level slicing is discussed in mobile network operator (MNO).
 Also, the problem of resource allocation is considered.
-Moreover, the challenges facing RAN slicing have also been explored, one of which involves designing and managing multiple slices in the shared infrastructure in an efficient manner while guaranteeing the agreed service level agreement (SLA) for each.
+Moreover, the paper faces the challenge of RAN slicing.
+The problem involves designing and managing multiple slices in the shared infrastructure efficiently while guaranteeing each slice's service level agreement (SLA).
 
-Multiplexing eMBB and URLLC services on the same RAN and sharing the resources for these services is challenging because many researchers pay attention to this topic.
-In \cite{setayesh2020joint,yang2020should} the problem of resource allocation in the coexistence of these two services (URLLC and eMBB) is considered based on their QoS. 
-In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC is formulated and solved by deep reinforcement learning.
- In \cite{saggese2021power} the problem of power minimization for these two types of services (URLLC and eMBB) is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
+Multiplexing eMBB and URLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
+In \cite{setayesh2020joint,yang2020should} the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
+In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
+ In \cite{saggese2021power} the problem of power minimization for URLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
  In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
@@
 This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
-Also, Transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the services.
- In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to UE is considered and solved using novel methods.
+Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
+ In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
 In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
 \subsection{Main Contribution}
-This study aims to optimize VNF activation, power allocation, PRB allocation, and O-RUs association to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+This study aims to optimize baseband resource allocation (power allocation, PRB allocation, and O-RUs association) and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
 In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
@@
 \item The desired QoS conditions such as delay and throughput are considered for different types of services.
-We formulate the end-to-end mean delay of the system based on the activated VNFs and each user's throughput.
-We take into account the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
+We formulate the end-to-end mean delay of the system based on the number of activated VNFs and each user's throughput.
+We consider the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
 We model the interference of neighboring O-RU and formulate the actual throughput
@@
 
-Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s}$ request from the single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
+Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ request from the single-antenna UEs which require certain QoS to be able to use the requested service ($j \in \{1,2,3\}$ indicate service type).
 There are different application requests which fall into one of these service categories.
@@
 All $K$ PRBs can be assigned to all UE in each service.
-Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers. Each VM requires enough resources of CPU, memory, storage, and network bandwidth.
+Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.
 
@@
 &+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
-&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 }_{\text{(Quantization Noise Interference)}}
+&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 }_{\text{(Quantization Noise)}}
 \end{split}
 \end{equation}
-where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.\newline
-$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
+where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
+$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
 
-To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal user $i$ in $s^{th}$ service
+To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service
 \begin{equation}\label{eq2}
@@
 and $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
-In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization noise, which is made from signal compression in O-DU.
+In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization noise 
+($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.
 
@@
 \end{equation}
-Where $j \in \{1,2\}$. Also we have
+Where $j \in \{2,3\}$. Also we have
 \begin{equation}\label{shortPacket}
@@
 $N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
-$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable rate of each O-RU $r$ to UE $i$ in slice $s_j$.
+$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.
 
@@
 \begin{equation}\label{pr}
-P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q_r}^2.
+P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
 \end{equation}
@@
 \begin{equation}\label{cr}
-C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q_{r}}^2})},
+C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2})},
 \end{equation}
-Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q_{r}}^2$ is the power of quantization noise.
+Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
 \subsection{Mean Delay}
-In this part, the end-to-end mean delay for a service is obtained.
+In this part, the end-to-end mean delay for each service is obtained.
 Suppose the mean total delay is depicted as $T_{tot}$.
@@
 \begin{split}
-T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
-T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
-T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
-T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
+T^{tot} &=  T^{process} + T^{transmission} + T^{propagation}\\
+T^{process} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF}\\
+T^{transmission} &= T^{front} + T^{mid} + T^{back} + T^{trans2net} \\
+T^{propagation} &= T^{front} + T^{mid} + T^{back} + T^{trans2net} \\
 \end{split}
@@
 %T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
-Total delay is the sum of processing delay, transmission delay, and propagation delay. 
+The total delay ($T^{tot}$) is the sum of the processing delay ($T^{process}$), the transmission delay ($T^{transmission}$), and the propagation delay($T_{propagation}$). 
 The propagation delay is the time takes for a signal to reach its destination.
@@
 \begin{equation}
-T_{tot} \approx T_{process}
+T^{tot} \approx T^{process}
 \end{equation}
 \subsubsection{Processing Delay}
-Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
+Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ service (or slice).
 Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
-Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$).
-so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
-since, by using Burke’s Theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still Poisson with rate $\alpha_{s}$
+Assume the mean arrival data rate of the UPF layer for the slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$).
+so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,
+Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
+Since, by using Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still poisson with rate $\alpha_{s}$.
 It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
@@
 \begin{split}
-T_{DU}^{s} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
-T_{CU}^{s} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}}\\
-T_{UPF}^{s} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}\\
+T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
+T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}}\\
+T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}\\
 \end{split}
@@
 Where $M_s^{d}$, $M_s^{c}$ and 
-$M_s^{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
+$M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively. 
 Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively.
@@
 
-In addition, $T_{RU}^{u(s,i)}$ is the mean transmission delay of $i^{th}$ UE in $s^{th}$ service on the wireless link.
+In addition, $T_{u(s,i)}^{RU}$ is the mean transmission delay of $i^{th}$ UE in $s^{th}$ service on the wireless link.
  The arrival data rate of wireless link for each UE i in service s is $\lambda_{u(s,i)}$
@@
 \begin{equation}
- T_{RU}^{u(s,i)} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}};
+ T_{u(s,i)}^{RU} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}};
 \end{equation}
@@
 \begin{equation}
-T_{process}^{u(s,i)} =  T_{RU}^{u(s,i)} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s}
+T^{process}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}
 \end{equation}
-Hence, $T_{tot}^{u(s,i)} \approx T_{process}^{u(s,i)} $
+Hence, $T^{tot}_{u(s,i)} \approx T^{process}_{u(s,i)} $
 %Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
 \subsection{VNF Power}
-Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
-$\phi_{s}$. So the system's total power for all active DCs connected to slices can be represented as follows.
+Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as
+$\phi_{s}$. So the system's total cost of energy of all slices can be represented as follows.
 \begin{equation*}
@@
 Suppose each slice $s$ has priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$.
-The optimization problem is formulated as follow.
 This paper aims to maximize the sum rate of all UEs with the presence of constraints as follows.
@@
 Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.
-\eqref{c11}, and \eqref{c12}, indicate that the power of each RU does not exceed the maximum power, and the power of each UE is a positive integer value, respectively.  
-Also, \eqref{c13} shows that the rate of each UE requesting eMBB, URLLC, and mMTC is more than a threshold, respectively.
-\eqref{c15} and \eqref{c16} expressed the limited capacity of the fronthaul link and the limited delay of receiving the signal, respectively.
+\eqref{c11}, and \eqref{c12}, indicate that the power of each O-RU does not exceed the maximum power, and the power of each UE is a positive integer value, respectively.  
+Also, \eqref{c13} shows that the rate of each UE requesting each type of service (eMBB, URLLC, and mMTC) is more than a threshold, respectively.
+\eqref{c15} and \eqref{c16} expressed the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
 \eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue model.

### 2021-08-03 Latex/journal_v1/V5/pr.tex
finish analyse journal

@@
   \centering 
-    \includegraphics[scale = 0.75]{finalDraw.pdf}
+    \includegraphics[scale = 0.7]{finalDraw.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 
-If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$.
+If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$.
 Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
@@
 \begin{split}
-T^{tot} &=  T^{process} + T^{transmission} + T^{propagation}\\
-T^{process} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF}\\
-T^{transmission} &= T^{front} + T^{mid} + T^{back} + T^{trans2net} \\
-T^{propagation} &= T^{front} + T^{mid} + T^{back} + T^{trans2net} \\
+T^{tot} &=  T^{proc} + T^{tr} + T^{pro}\\
+T^{proc} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF}\\
+T^{tr} &= T^{fr,t} + T^{mid,t} + T^{b,t}  \\
+T^{pro} &= T^{fr,p} + T^{mid,p} + T^{b,p}  \\
 \end{split}
@@
 %T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
-The total delay ($T^{tot}$) is the sum of the processing delay ($T^{process}$), the transmission delay ($T^{transmission}$), and the propagation delay($T_{propagation}$). 
+The total delay ($T^{tot}$) is the sum of the processing delay ($T^{proc}$), the transmission delay ($T^{tr}$), and the propagation delay($T^{pro}$). 
 The propagation delay is the time takes for a signal to reach its destination.
 So it has a constant value based on the length of the fiber link ($T = L/c$, where $L$ is the length of the link and c is the speed of signal).
+So the total propagation delay ($T^{pro}$) is the sum of the propagation delay in the fronthaul $T^{fr,p}$, the midhaul $T^{mid,p}$, and the backhaul $T^{b,p}$.
 Also, the transmission delay is the amount of time required to push all the packets into the fiber link. 
 ($T = \frac{\alpha}{R}$ Where $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of each link which is constant in this model.) 
-Here we assume the value of propagation delay and transmission is negligible compared to the rest.
+So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{mid,t}$, and the backhaul $T^{b,t}$.
+Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
 \begin{equation}
-T^{tot} \approx T^{process}
+T^{tot} \approx T^{proc}
 \end{equation}
@@
 Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follows, respectively.
+Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively.
 \begin{equation}
@@
 \begin{equation}
-T^{process}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}
+T^{proc}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}
 \end{equation}
-Hence, $T^{tot}_{u(s,i)} \approx T^{process}_{u(s,i)} $
+Hence, $T^{tot}_{u(s,i)} \approx T^{proc}_{u(s,i)} $
 %Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
@@
 \max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}} \ \\
-\text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
+\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r
  \label{c11} \\
 &p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
-&\bar{\mathcal{R}}_{u_{(s_j,i)}} \geq \mathcal{R}_{min}^{s_j} \quad \forall s, j \in \{1,2,3\}, \label{c13} \\
+&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
+&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{min} \quad \forall s, \label{c13} \\
 %&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
-& C^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
-&T_{tot}^{u(s,i)}  \leq T_{max}^{s} \quad \forall i,\forall s,\label{c16} \\
+& C_r \leq C^{max}_r \quad \forall r, \label{c15}\\ 
+&T^{tot}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\
 & \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
 & \bar{\mathcal{R}}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\
-& 0 \leq M_s \leq M^{max}  \quad \forall s,\label{c16-3}\\
+& 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
@@
 & \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
-& \phi_{tot}  \leq \phi_{max}, \label{c19} \\
+& \phi^{tot}  \leq \phi^{max}, \label{c19} \\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
@@
 \end{subequations}
-where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}] \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association.
-Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association.
-Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.
-\eqref{c11}, and \eqref{c12}, indicate that the power of each O-RU does not exceed the maximum power, and the power of each UE is a positive integer value, respectively.  
+where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association.
+Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association.
+Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.
+\eqref{c11}, \eqref{c12} and \eqref{c12-1}, indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
 Also, \eqref{c13} shows that the rate of each UE requesting each type of service (eMBB, URLLC, and mMTC) is more than a threshold, respectively.
@@
 \section{Proposed Algorithm Scheme}\label{proAlg}
-In this section, we first apply some simplifications to the system; Solving problem \eqref{problem} is complicated since this problem is non-convex and it is a  mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
-We simplified and reformulated MINL parts and used an iterative heuristic algorithm to solve the problem.
-We solve this problem in two-level iteratively until it converges.
-In the first level, parameters ($\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}$) are obtained by relaxing and reformulating parameters to turn them into a jointly-convex problem; Afterward, we solve it by dual optimization problem.
-In the second level, finding optimal O-RU association ($ \boldsymbol{G}$) is concerned with the fixed parameter of power, PRB allocation, and number of VNFs.   
+In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this problem is non-convex and it is a  mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
+We applied some simplifications and used an iterative heuristic algorithm to solve the problem.
+We solve this problem in two-level iteratively until it converges \cite{ali2018joint}.
+
+In the first level, the principal purpose is to allocate adequate PRBs and the power to the UEs and allocate enough activated VNFs
+to each slice. So, at this level, we want to obtain the variables $\boldsymbol{P}, \boldsymbol{E},$ and $\boldsymbol{M}$.
+Despite the simplification of the problem
+\eqref{problem}, it is still NP-hard and challenging to solve. Therefore,
+we relax the variable $\boldsymbol{E}$ \cite{lee2018dynamic,ali2018joint} and reformulating the constraint \eqref{c16},
+to turn them into a jointly-convex problem; Afterward, we solve this problem using a conventional dual Lagrangian method. 
+In the second level, finding the optimal O-RU association ($ \boldsymbol{G}$) is concerned with the fixed parameter of power, PRB allocation, and the number of activated VNFs.   
 We repeat this procedure until the algorithm converges.
@@
 
-As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ for $I_{r,u(s,i)}^{k}$, the lower bound $\bar{\rho}_{u(s,i)}^{k}$
-for $\rho_{u(s,i)}^{k}$ 
-and the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing with $I_{r,u(s,i)}^{k}$ $\bar{I}_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3} and make them concave.
+As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in the \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
+for $\rho_{u(s,i)}^{k}$. 
+Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in the \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.
 
-Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
-To convexify \eqref{eq11} (for the short packet transmission), we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}.
+Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
+we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in the \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
 So, a lower bound for \eqref{eq11} is given that is a concave function.
@@
 \end{equation}
-Consider UPF, O-CU and O-DU have the same processor (for simplification), so we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
+Consider UPF, O-CU and O-DU use the processors with the same processing capability. (for simplification), so we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
 the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$).
 so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
-So the given assumption leads to have same energy for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
-As a result of these assumption, for simplicity, we can assume that $M_s = M_s^u = M_s^c = M_s^d $
-Using the above assumption, we have $T_{DU}^{s} = T_{CU}^{s} = T_{UPF}^{s}$ 
+Moreover, the given assumption leads to have same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
+As a result of these assumption, we can assume that $M_s = M_s^u = M_s^c = M_s^d $
+Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ 
 \begin{equation}
 \begin{split}
-T_{process}^{s} &=  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s} \\
-T_{process}^{s} &=  T_{RU}^{s} + 3\times T_{DU}^{s}.
+T^{proc}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
+T^{proc}_{s} &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
 \end{split}
@@
 \begin{lemma}
-In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as below
+In the problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as below
 $ \forall i,\forall s$
@@
 \begin{split}
-&T_{max}^s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
-&M_s \geq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
+&T^{max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
+&M_s \geq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
 \end{split}
@@
 We denote $ \mathfrak{M}_s= \min\{M^{max}, \phi_{max}/{3\phi_s}\}$.
-Thus, if we restrict \eqref{c16} to equality we have
+Thus, if we restrict constraint \eqref{c16} to equality, constraint \eqref{c16} is still valid.
+Also, we have the following inequality.
 \begin{equation}\label{eqDelay}
-\alpha_s/\mu_s\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
+\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
 \end{equation}
-In \eqref{eqDelay}, $0\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
-the numerator and the denominator will both have same sign. Using \eqref{c16-2},
-in numerator, $\alpha_s \geq 0$, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$ and to simplify the problem, assume 
-$(R_{u(s,i)}-\lambda_{u(s,i)})T_{max}^s \geq 1$ since the order of $T_{max}^s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T_{max}^s$.
-Therefore, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T_{max}^s$.
-So the numerator is positive.
-In denominator, it can be said approximately that $(T_{max}^s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since, $(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T_{max}^s$ as mentioned above.
-Therefore, we need to have constraints below
-\begin{equation}\label{constraint16}
-\alpha_s/\mu_s\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
-\end{equation}
-The left side of this formula leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
-For the right side, by reformulating the equation \eqref{constraint16}, we have a new constraint $\forall i, \forall s$ as below,
+In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
+the numerator and the denominator will both have the same sign.
+In the numerator, according to the \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
+If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$, the numerator will be positive.
+$(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$ since the order of $T^{max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{max}_s$.
+Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{max}_s$.
+So the numerator will be positive.
+In the denominator, we can say that $(T^{max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,  
+$\mu_s \geq 0$ and
+$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{max}_s$ as mentioned above.
+%Therefore, we need to have the constraint below.
+%\begin{equation}\label{constraint16}
+%\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
+%\end{equation}
+
+The left side of the equation \eqref{eqDelay}, leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
+For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ as below,
 \begin{equation}\label{RM}
 \begin{split}
-\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s ((T_{max}^s\mu_s-3)\lambda_{u(s,i)} + \mu_s) - \alpha_s(T_{max}^s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T_{max}^s\mu_s-3)-\alpha_s T_{max}^s},\\
-\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s ((T_{max}^s\mu_s-3)\lambda_{u(s,i)} + \mu_s) - \alpha_s(T_{max}^s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T_{max}^s\mu_s-3)-\alpha_s T_{max}^s},\\
+\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
+ \mathit{\langle}_{u(s,i)}&=(T^{max}_s\mu_s-3)\lambda_{u(s,i)} + \mu_s,\\
+\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
 \mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
@@
 \end{equation}
-In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$.
-So we have,
+In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
+So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
+$\mathtt{M}_{u(s,i)}$ in each slice as follow.
 \begin{equation}
@@
 Despite simplifying the problem \eqref{problem}, it is still non-convex and hard to be solved.
-So the simplest approach is to relax $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$
+So the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
 Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.
@@
  $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
-The combination of equations \eqref{c13} and \eqref{c15} leads to the following equation
-\begin{equation}
+The combination of equations \eqref{c11} and \eqref{c15} leads to the following equation
+\begin{equation} \label{pr11}
 \begin{split}
@@
 \begin{split}
-\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{max}, \lambda_{u_{(s,i)}}+1/T^s_{max}, \varpi_{u(s,i)} \}, \\
+\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{min}, \lambda_{u_{(s,i)}}+1/T^s_{max}, \varpi_{u(s,i)} \}, \\
 \mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
@@
 \end{equation}
-Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
+Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$, $\boldsymbol{\mathfrak{q}}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
 
@@
 &+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\\
+&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{max}_{s}- p^k_{r,u(s,i)})\\
 &+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\\
@@
 \begin{lemma}
-By taking derivatives of \eqref{lagrang} (the lagrangian function), with respect to the $\boldsymbol{P}$ and the $\boldsymbol{E}$, these two variables are obtained.
-Assume, $e_{r,u(s,i)}^{k} = 1$
+
+The derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{P}$ and $\boldsymbol{E}$ give the Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal value of these two variables \cite{lee2018dynamic,ali2018joint}.
+
+Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
 \begin{equation}\label{deriveP}
-\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} = (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k} + (\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k})=0
+\begin{split}
+\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
+ &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0\\
+\end{split}
 \end{equation}
-Where
+Where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}+\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
 \begin{equation}
 \begin{split}
-\mathfrak{D}_{r,u(s,i)}^{k} &= |\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
+\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
 \mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
@@
 \end{equation}
-where $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
+Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
 Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
 We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
+The optimal power is as follow.
 \begin{equation}
-p_{r,u(s,i)}^{k} = [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k}} -\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.
+\begin{split}
+p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (\kappa^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})}\\
+ &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
+\end{split}
 \end{equation}
 Also $[a]^+ = \max(0,a)$.
-In addition, PRB assignment is obtained as follow
+In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
 \begin{equation}\label{deriveE}
@@
 \end{equation}
-Using KKT conditions, we have
+So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
 \begin{equation}\label{deriveE1}
-e_{r,u(s,i)}^{k}\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)} - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.
+\begin{split}
+e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
+& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
+\end{split}
 \end{equation}
@@
 \subsection{Sub-Problem 2}\label{sub2}
-After power allocation and PRB assignment, the remaining problem is to assign O-RU to the UE in each service.
+After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.
 
 Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
-Next, we introduce a greedy algorithm that assigns one O-RU to each UE.
+Next, we introduce a greedy algorithm that assigns an O-RU to each UE.
 
-\textit{Greedy Algorithm for Non-Comp O-RU Assignment:}
+\textit{Greedy Algorithm Assignment (GAA):}
 The problem can be reformulated as follow
@@
 Where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
-and $\mathfrak{t}_r = \zeta_r- \sigma_r$
+and $\mathfrak{t}_r = \zeta_r- \sigma_r$  because of the equations \eqref{pr11} and \eqref{pr}.
 Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
@@
 The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.  
-We solve this problem using GAAOU, which is a greedy algorithm \eqref{alg1} as follows \cite{akccay2007greedy,lee2018dynamic}.
-Firstly, we set all variables $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$. 
-Then we define ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$  $\forall s, \forall i$ and $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
-as a set of all O-RUs and value of each O-RU, respectively.
-Next, we sort all slices based on their priority. 
-Afterward, we assign the O-RU that provides the highest achievable rate for each UE (we start from the UEs on the slices with the highest priority) on the condition that 
-it does not exceed the value of each O-RU (that is, a function of maximum power and capacity of O-RU).
-If it exceeds the value of O-RU, then O-RU with the next highest achievable rate is selected. 
+We solve this problem using heuristic method(GAA method \ref{alg1}), which is a greedy algorithm \cite{akccay2007greedy,lee2018dynamic}.
+Firstly, we set all the variables to zero ($g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$). 
+Then we define the parameter ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$.
+This parameter is used as a set of O-RUs that can be assigned to the UE $i$ in slice $s$, which initially includes all the O-RUs (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}, \forall s, \forall i$ ).
+Also we introduce another parameter $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
+which is the knapsack capacity of each O-RU.
+Next, we sort all the slices based on their priority. 
+Afterward, based on the sorting of the UEs,
+we assign the O-RU that provides the highest achievable data rate for each UE on the condition that the value of the desired UE ($\psi_{r,u(s,i)}$) does not exceed the knapsack capacity of each O-RU ($ \mathfrak{C}_r$).
+If it exceeds the capacity of the desired O-RU, we remove the specific O-RU from the set of O-RUs that can be assigned to that UE (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $).
+Then, the O-RU with the highest achievable data rate from the new set of O-RUs ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$ is selected.
 The complexity of sorting S slices based on their priority is $O(Slog(S))$.
-Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$. 
+Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ as the whole number of UEs in the system. 
 The complexity order of this algorithm is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
@@
 \begin{algorithm}
-\caption{Greedy Algorithm for Assignment of O-RU to UEs (GAAOU)}\label{alg1}
+\caption{Greedy Algorithm for Assignment of O-RU to UEs (GAA)}\label{alg1}
 \begin{algorithmic}[1]
@@
 \Else
-\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
+\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $
 \EndIf
@@
 \subsection{Iterative Proposed Algorithm}
-In \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
+In sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
 Here, the iterative algorithm for the whole problem is demonstrated.
-Firstly, we fixed $\boldsymbol{G}$, then $\boldsymbol{P}$ and $\boldsymbol{E}$ is achieved using the Lagrangian method.  
-Afterward, $\boldsymbol{G}$ is updated using the GAAOU algorithm. This process is repeated until it converges. 
-The whole algorithm is depicted as follows (Algorithm \eqref{alg2}).
+Firstly, we fixed $\boldsymbol{G}$ to achieve $\boldsymbol{P}$ and $\boldsymbol{E}$, using the Lagrangian method and the KKT conditions.  
+Afterward, $\boldsymbol{G}$ is updated using the GAA algorithm. This process is repeated until it converges. 
+The whole algorithm (IABV method) is depicted as follows (Algorithm \ref{alg2}).
  \begin{algorithm}
-\caption{Iterative Algorithm for Power Allocation, PRB, VNF and O-RU Association (IAPPVO)}\label{alg2}
+\caption{Iterative algorithm for the baseband resource allocation and VNF activation (IABV)}\label{alg2}
 \begin{algorithmic}[1]
@@
 \section{Numerical Results}\label{NE}
-In this section, numerical results for the problem are depicted to evaluate the performance of the algorithms. We consider three network slices, one for eMBB and two for URLLC and mMtc.
+In this section, numerical results for the main problem are depicted to evaluate the performance of the algorithms. We consider three network slices, for eMBB, URLLC and mMtc services.
 Assume we have six 4-antenna O-RU (MISO) located in a cell with a diameter of 500 meters. We consider 25 PRB in the network.
-The maximum number of VNF for each slice is 20 and the mean arrival rate for eMBB  is $\lambda  = 3Mbps$ and for mMTC and URLLC $\lambda  = 0.2Mbps$. 
+The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
 The other parameters of these simulations are depicted in Table \ref{table:1a}.
@@
   \hline
-  Maximum delay for mMTC &  20msec \\
+  Maximum delay for mMTC &  5msec \\
   \hline
@@
   \hline
-   Minimum data rate for URLLC and mMTC &  3 bits/sec/Hz \\ 
+   Minimum data rate for URLLC and mMTC &  2 bits/sec/Hz \\ 
   \hline
@@
  \end{table}
-Two different methods compare the performance of the method.
+Two different methods are used to compare with the performance of the proposed method (IABV).
  The first one is a baseline scheme, which used random PRB allocation.
-The association of O-RU is based on the distance, channel quality, and the fronthaul capacity; also, the number of activated VNF for each slice is fixed.
+The association of O-RU is based on the distance, channel quality, and the fronthaul capacity.
+Also, the number of activated VNF for each slice is obtained from the simulation.
 The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}.
-In this method, PRB and power are dynamically allocated, the number of VNFs is fixed, and the UEs are associated with O-RU based on the quality of their channels, the fronthaul capacity, and channel distance and quality.
+In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels, the fronthaul capacity, and channel distance.
+
 In Fig.
@@
 Suppose we have one service instance for each type of service, so we have three various services in this figure.
-Here, we did not consider the priority. The figure presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.
+Here, we did not consider the priority. The figure presented that the proposed method (IABV) is $18.6\%$ higher than the baseline scheme.
 As the number of UEs increases in each service, the aggregated throughput initially increases.
@@
   \centering 
-    \includegraphics[scale = 0.5]{rate_ue1.eps}
+    \includegraphics[scale = 0.47]{rate_ue1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 \end{figure}
-
 %Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
@@
 %\end{figure}
+
 Figure \ref{fig:4}, depicts the number of activated VNF for the five different mean service times of one URLLC service vs.
@@
   \centering 
-    \includegraphics[scale = 0.5]{vnfNum1.eps}
+    \includegraphics[scale = 0.47]{vnfNum1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 In figure \ref{fig:5}, the aggregate throughput is depicted vs.
-the maximum power of UE for three different instances of eMBB service using proposed method.
+the maximum power of UE for three different instances of eMBB service using proposed method (IABV), FBDR and the baseline scheme.
 Here, we suppose that we have 12 UEs in each service.
 We assume that these three services require 5bits/sec/Hz, 10bits/sec/Hz, and 15bits/sec/Hz.
-In addition, We suppose that each O-RU can transmit three times of the maximum power of UE. As you can see in the figure, increasing the maximum power increases the aggregate throughput.
+In addition, We suppose that each O-RU can transmit three times of the maximum power of the UEs.
+As you can see in the figure, increasing the maximum power increases the aggregate throughput.
+Moreover, the proposed method (IABV), gives higher aggregate rates in compared to the FBDR and the baseline scheme.
 
@@
   \centering 
-    \includegraphics[scale = 0.5]{RatePower1.eps}
+    \includegraphics[scale = 0.47]{RatePower1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 
-Figure \ref{fig:6}, illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for proposed method.
-It is shown that the delay is an ascending function of the mean arrival rate and the number of UEs in the service.
+Figure \ref{fig:6}, illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
+It is shown that the delay is an ascending function of the mean arrival rate (when the mean service time is fixed) and the number of UEs in the service.
 In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a URLLC service is $0.5ms$.
@@
   \centering 
-    \includegraphics[scale = 0.5]{delay_new.eps}
+    \includegraphics[scale = 0.47]{delay_new.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Mean Total Delay of a URLCC Service vs. the Mean Arrival Rate of a UE in the Service for various number of UEs}
+  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for various number of UEs}
   \label{fig:6}
 \end{figure}
-Figure \ref{fig:7} is the same as figure \ref{fig:7} that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
-As you can see, the proposed method (IAPPVO) outperforms the other scenarios.
+Figure \ref{fig:7} is the same as figure \ref{fig:6} that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
+As you can see, the proposed method (IABV) outperforms the other scenarios.
 
@@
   \centering 
-    \includegraphics[scale = 0.5]{delay1_new.eps}
+    \includegraphics[scale = 0.47]{delay1_new.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Mean Total Delay of a URLCC Service vs. the Mean Arrival Rate of a UE in the Service for different methods}
+  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for different methods}
   \label{fig:7}
@@
 
-Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs and the maximum power for three different mMTC service instances.
+Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances.
 mMTC service includes a large number of UEs with low data rates and low power.
-Assume each UE in each mMTC service instance requires $1bits/sec/Hz$ data rate and is not sensitive to end-to-end delay.
+Assume each UE in each mMTC service instance requires $1bits/sec/Hz$ data rate and is not sensitive to the end-to-end delay.
 The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases.
@@
   %\centering 
-    \includegraphics[scale = 0.42]{mmTCpower.eps}
+    \includegraphics[scale = 0.4]{mmTCpower.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services (eMBB, mMTC, and URLC).
-The isolation of various types of services (eMBB, mMTC, and URLC) in O-DU, O-CU, and user plane function (UPF) is accomplished.
-Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the sum rate.
+The isolation of various types of services (eMBB, mMTC, and URLC) in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
+Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.
 The limited fronthaul capacity and the mean end-to-end delay for each service are considered.
@@
 In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
-Then in the second step, O-RU association is acquired.
-The performance of our proposed method (IAPPVO) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
+Then in the second step, the O-RU association is acquired.
+The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
 Also, we assume distinct scenarios for each service (eMBB, URLLC, and mMTC) based on their requirement QoS.
-Simulation results depicts that the proposed method (IAPPVO) achieved $18.6\%$ higher data rate than the baseline scheme.
-Moreover, simulation results illustrate less delay for the proposed method (IAPPVO) than FBDR and baseline scheme.
+Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
+Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.
 

### 2021-08-07 Latex/journal_v1/V5/pr.tex
finish analyse journal1
add code

@@
 \end{equation}
-Where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}+\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
+Where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
 \begin{equation}
@@
 \begin{split}
-p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (\kappa^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})}\\
+p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
  &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
@@
   \begin{cases}
-      1 & u(s,i) = \text{argmax} \mathfrak{F}^{k}_{r,u(s,i)} \forall s, \forall r, \forall k\\
+      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall s, \forall r, \forall k\\
       0 & \text{otherwise}
@@
 \end{equation}
+Where, $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
  \end{lemma}
@@
 Two different methods are used to compare with the performance of the proposed method (IABV).
- The first one is a baseline scheme, which used random PRB allocation.
-The association of O-RU is based on the distance, channel quality, and the fronthaul capacity.
-Also, the number of activated VNF for each slice is obtained from the simulation.
+ The first one is a baseline scheme, which used random PRB allocation. The association of O-RU is only based on the distance. Also, the number of activated VNF for each slice is fixed. 
 The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}.
-In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels, the fronthaul capacity, and channel distance.
+In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels and the channel distance.
 

### 2021-08-08 Latex/journal_v1/V5/pr.tex
add code

@@
 Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
-The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
-The complexity order of this problem is about $O(\mathfrak{N} \times K)$.
+The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
+The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
 \subsection{Sub-Problem 2}\label{sub2}
@@
 The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
-As we mentioned before, the complexity order of the first sub-problem is about $O(N_u \times K)$
+Also, assume that the algorithm converges after $T_{conv}$ times.
+As we mentioned before, the complexity order of the first sub-problem is about $O(T_{conv} \times \mathfrak{N} \times K)$
 and the complexity order of the second sub-problem is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
-So the complexity of the main problem \eqref{problem} is $O(\mathfrak{N} \times K \times (Slog(S)+R\mathfrak{N}))$.
+So the complexity of the main problem \eqref{problem} is $O(T_{conv} \times \mathfrak{N} \times K \times (Slog(S)+R\mathfrak{N}))$.
 \section{Numerical Results}\label{NE}
@@
 Assume each UE in each mMTC service instance requires $1bits/sec/Hz$ data rate and is not sensitive to the end-to-end delay.
-The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases.
+Also, suppose the fronthaul link has no restrictions  .The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases.
 Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.

### 2021-08-08 Code_journal1/VersionLastJournal/oneSlice/main_gradient.m

@@ -22,8 +22,9 @@ for i_count = count_min1:count_step1:count_max1
             run RUAssociateDist
             run setChGain
             alpha_m = lambda_m.*(UE_S);
-            run PRB_Pow_Alloc1
-            run findM
+            run PRB_P
+            %run PRB_Pow_Alloc1
+            %run findM
             run Rate_final
             %run RUUESet
             sumRate1(number_check,iter) = abs(sum(rate_UE_1));            

### 2021-08-10 Latex/journal_v1/V5/pr.tex
add code
add convergence

@@
 &+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
-&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 }_{\text{(Quantization Noise)}}
+&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(Quantization Noise)}}
 \end{split}
@@
 and $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
-In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization noise 
+In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization Gaussian noise 
 ($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.
@@
 Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
-So, for the short packet transmission, the achievable data rate is approximated from following
+So, for the short packet transmission, the achievable data rate is approximated from following \cite{setayesh2020joint},
 \begin{equation}\label{eq11}
@@
 \mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
-\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
-\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)}
+\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
+\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)}.
 \end{split}
@@
 In this part, the end-to-end mean delay for each service is obtained.
-Suppose the mean total delay is depicted as $T_{tot}$.
+Suppose the mean total delay is depicted as $T_{tot}$,
 \begin{equation}
 \begin{split}
-T^{tot} &=  T^{proc} + T^{tr} + T^{pro}\\
-T^{proc} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF}\\
-T^{tr} &= T^{fr,t} + T^{mid,t} + T^{b,t}  \\
-T^{pro} &= T^{fr,p} + T^{mid,p} + T^{b,p}  \\
+T^{tot} &=  T^{proc} + T^{tr} + T^{pro},\\
+T^{proc} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
+T^{tr} &= T^{fr,t} + T^{mid,t} + T^{b,t},  \\
+T^{pro} &= T^{fr,p} + T^{mid,p} + T^{b,p}.  \\
 \end{split}
@@
 Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively.
+Each packet is processed by one of the VNFs of a slice.
+So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
 \begin{equation}
@@
 T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
-T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}}\\
-T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}\\
+T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
+T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}.\\
 \end{split}
@@
 Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
-an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue.
+an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
 
@@
   \begin{cases}
-      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall s, \forall r, \forall k\\
+      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S\\
       0 & \text{otherwise}
@@
 \end{algorithm}
+\subsubsection{Complexity Order}
 The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
@@
 So the complexity of the main problem \eqref{problem} is $O(T_{conv} \times \mathfrak{N} \times K \times (Slog(S)+R\mathfrak{N}))$.
+\subsubsection{Convergence Analysis}
+We can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function concerning the number of iterations \cite{gholipoor2020resource}.
+Consider the aggregate throughput as $\mathcal{T(\bold{P},\bold{E},\bold{G})} =\sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}}$. 
+In the first step of the iteration i of the algorithm \ref{alg2} (IABV), we have $\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1})$.
+In this step, optimal power and PRB allocation are obtained for the fixed O-RU association, so we have
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
+In the second step of the iteration i, the optimal O-RU association is achieved to maximize the aggregate throughput. So we have this inequality
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
+As a result, we have 
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
+Hence, in each step of the iteration, the aggregate throughput increased.
+Note that $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*})$ is the achieved aggregate throughput 
+for all the feasible resource allocation solutions of $\{\bold{P},\bold{E},\bold{G}\}$.
+So, $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i})$ and thus in each iteration, the aggregate throughput can not be larger than the optimal solution.
+So the the aggregate throughput is ascending function concerning the number of iterations and it will converge to the optimal solution.
+In addition, if we assume that the interference is set to be zero ${I}_{r,u_{(s,i)}}^{k}=0$,
+and we suppose that each UE has the maximum power $p_{r,u_{(s,i)}}^k = P_{s}^{max}$,
+and we consider that all PRB is assigned to all UE $e_{r,u_{(s,i)}}^k = 1 \forall s,\forall i$
+and each UE is assigned to the nearest O-RU with the best channel quality. So, the solution of this allocation, is the upper bound 
+for the aggregate throughput. Thus,
+we can guarantee the convergence of our iterative algorithm since the objective function $\mathcal{T}$ is the ascending function concerning the number of iterations
+ and it has the upper bound.  
 \section{Numerical Results}\label{NE}
-In this section, numerical results for the main problem are depicted to evaluate the performance of the algorithms. We consider three network slices, for eMBB, URLLC and mMtc services.
-Assume we have six 4-antenna O-RU (MISO) located in a cell with a diameter of 500 meters. We consider 25 PRB in the network.
+In this section, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method.
+We consider three network slices for eMBB, URLLC, and mMtc services.
+Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this place.
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.47]{cell.pdf}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{O-RU placement in a cell}
+  \label{fig:cell}
+\end{figure}
+Here, The channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.
+Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent.
+Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution
+and it is the Rayleigh fading channel between the UE and O-RU.
+We consider 25 PRBs are used in the network and the
+packet size is equal to 20 bytes.
 The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 

### 2021-08-11 Latex/journal_v1/V5/pr.tex
add simulation code

@@
 Assume each UE in each mMTC service instance requires $1bits/sec/Hz$ data rate and is not sensitive to the end-to-end delay.
-Also, suppose the fronthaul link has no restrictions  .The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases.
+Also, suppose the fronthaul link has no restrictions.
+The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases.
 Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
@@
 Here we consider 4 UEs in each service.
+We assume that the the fronthaul link and the end-to-end delay have no restrictions.
 The figure \ref{fig:9} presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa.

### 2021-08-11 Code_journal1/VersionLastJournal/oneSlice/delay_const.m

@@ -1,0 +1,15 @@
+w1(1,:) = alpha_m(:).* delay_max(:);
+w2(1,:) = alpha_m(:).*lambda_m(:) .* delay_max(:) + alpha_m(:);
+w3(1,:) = mu(:).* delay_max(:)-3;
+w4(1,:) = mu(:).* delay_max(:).*lambda_m(:)+mu(:) - 3*lambda_m(:);
+ t = 0;
+a = zeros(1,S);
+M_max = 25;
+for s = 1:S
+    for j = 1:UE_S(s)
+        t = t+1;
+        a(s) = (w2(s) - M_max*w4(s))./((w1(s) - M_max*w3(s)));
+        %Popt(t) <= (2^(a(s)/BW)-1)*(Intf(t)*0+BW*N0)/(abs((ChannelGain(:,t))'*beamForming(:,t))^2)
+        %rate_UE(t) >= max(a(s),0)
+    end
+end

### 2021-08-12 Latex/journal_v1/V5/pr.tex
add figure

@@
 \begin{itemize}
-\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G (URLLC, eMBB, and mMTC).
+\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G i.e eMBB, mMTC, and URLLC.
 The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
@@
 \eqref{c11}, \eqref{c12} and \eqref{c12-1}, indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
-Also, \eqref{c13} shows that the rate of each UE requesting each type of service (eMBB, URLLC, and mMTC) is more than a threshold, respectively.
+Also, \eqref{c13} shows that the rate of each UE requesting each type of service i.e eMBB, mMTC, and URLLC is more than a threshold, respectively.
 \eqref{c15} and \eqref{c16} expressed the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
@@
 So, $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i})$ and thus in each iteration, the aggregate throughput can not be larger than the optimal solution.
-So the the aggregate throughput is ascending function concerning the number of iterations and it will converge to the optimal solution.
+So the the aggregate throughput is ascending function concerning the number of iterations and it will converge to the sub-optimal solution.
 In addition, if we assume that the interference is set to be zero ${I}_{r,u_{(s,i)}}^{k}=0$,
@@
 In this section, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method.
-We consider three network slices for eMBB, URLLC, and mMtc services.
+We consider three network slices for eMBB, URLLC, and mMTC services.
 Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this place.
@@
 The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
+Also the quantization noise is assumed to be $10^{-13}$.
 The other parameters of these simulations are depicted in Table \ref{table:1a}.
@@
   \hline
- Maximum transmit Power of each O-RU & 38dBm \\
+ Maximum transmit Power of each O-RU & 40dBm \\
   \hline
@@
   \hline
-  Maximum fronthaul capacity  & 200 bits/sec/Hz \\
+  Maximum fronthaul capacity  & 46 bits/sec/Hz \\
    \hline
@@
  The first one is a baseline scheme, which used random PRB allocation. The association of O-RU is only based on the distance. Also, the number of activated VNF for each slice is fixed.
+
+Finding a feasible initial value is almost tricky.
+To overcome this challenge, we compare it with the baseline scheme method using the CVX of Matlab.
+If the baseline scheme converged and has a feasible solution, so our algorithm (IABV) can be converged too.
+
 The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}.
@@
 mMTC service includes a large number of UEs with low data rates and low power.
-Assume each UE in each mMTC service instance requires $1bits/sec/Hz$ data rate and is not sensitive to the end-to-end delay.
+Assume each UE in each mMTC service instance requires 1bits/sec/Hz data rate and is not sensitive to the end-to-end delay.
 Also, suppose the fronthaul link has no restrictions.
@@
 \end{figure}
+
+In the figure \ref{fig:10}, the aggregate throughput is presented vs. the number of UEs for one service in a system by considering two different cloud restrictions and fronthaul restrictions.
+In the graph of cloud restriction, we have the restrictions in O-DU and O-CU.
+In the graph of fronthaul restriction, we have the restrictions in O-RU.
+In the O-RU restriction graph, we assume that the fronhaul link is set to be 43 bits/sec/Hz (the variance of quantization noise is $10^{-12}$) , and the maximum power of each O-RU is 40 dBm.
+Also, the maximum power of each UE is set to be 35 dBm.
+Moreover, the minimum data rate for each UE in this service is 6 bits/sec/Hz.
+In this graph, we assume that there is less restriction in the end-to-end delay (50 ms) and the VNF resources (the system has 100 reserved VNF).
+In the graph of cloud restriction, we assume that there is no restriction on the fronthaul link.
+The limitation on the power is less than the graph of fronthaul limitation, and it is set to be 45 dBm on the power of each O-RU, and the maximum power of each UE is 40 dBm.
+The minimum data rate for each UE in this service is 6 bits/sec/Hz. 
+The end-to-end delay for each UE is 4ms and the mean arrival rate is 2Mbps. 
+and the mean service rate is 10Mbps.
+In this figure, the consequence of cloud limitation and fronthaul limitation is depicted.
+As the number of UEs increases, the aggregate throughput rises linearly, and the graph of cloud restriction increases more than the other graph of fronthaul limitation.
+
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{cloudVsFronthaul.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput vs. Number of UE in a Service}
+  \label{fig:10}
+\end{figure}
 \section{Conclusion}\label{conc}
-This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services (eMBB, mMTC, and URLC).
-The isolation of various types of services (eMBB, mMTC, and URLC) in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
+This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
+The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
 Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.
@@
 The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
-Also, we assume distinct scenarios for each service (eMBB, URLLC, and mMTC) based on their requirement QoS.
+Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
 Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.

### 2021-08-12 Code_journal1/VersionLastJournal/oneSlice1 - Copy/main_gradient_final.m

@@ -1,0 +1,65 @@
+clear all
+clc
+run var_const
+count_min1 = 2;
+count_step1 = 2;
+count_max1 = 2;
+numvar = length(count_min1:count_step1:count_max1);
+iter_max = 1;
+sumRate = zeros(numvar,iter_max);
+sumRate1= zeros(numvar,iter_max);
+RU_iter_max = N_RU + 5;
+%% initializing
+number_check = 0;
+for i_count = count_min1:count_step1:count_max1
+    number_check  = number_check +  1;
+    for iter = 1:iter_max  
+        RU_iter = 1;
+        run parameter_UE_change
+        run PRB_Alloc
+         while  RU_iter < RU_iter_max
+
+        if RU_iter == 1
+          run RUAssociateDist  
+        end
+        %%
+            run setChGain
+            alpha_m = lambda_m.*(UE_S);
+            run delay_const
+            run PRB_P
+            %run PRB_Pow_Alloc1
+            run findM
+            run Rate_final
+            run RUUESet
+            sumRate1(number_check,iter) = abs(sum(rate_UE_1));       
+            i_count
+            RU_iter
+            VNF_NUM
+            if sumRate(number_check,iter) > 0 && RU_iter >3 
+                %RU_iter = RU_iter_max + 10;
+
+            end
+            
+            RU_iter = RU_iter + 1;
+         end
+    end
+end
+UE_num = count_min1:count_step1:count_max1;
+
+
+sumRB =  zeros(1,numvar);
+sumRB1 =  zeros(1,numvar);
+num = zeros(1,numvar);
+for i =1:numvar
+    for j =1:iter_max
+        if isnan(sumRate1(i,j)) == 0 
+            sumRB(i) = sumRB(i) + sumRate1(i,j);
+            num(i)=  num(i) + 1;
+        end
+    end
+    sumRB1(i) = sumRB(i)/num(i);
+end
+
+plot( UE_num , sumRB1/1e6,'-+')
+
+%plot(UE_num ,mean(sumRate,2))

### 2021-08-14 Latex/journal_v1/V5/pr.tex
add sth

@@
 In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is achieved.
-The proposed method (IAPPVO) is confirmed by the simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers.
+The proposed method (IABV) is confirmed by the simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers.
 Also, the simulation results attained less end-to-end delay for the proposed method than the FBDR and baseline scheme.
@@
 Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
-\subsection{Power of O-RU and Fronthaul Capacity}
+\subsection{Power of the O-RU and the Fronthaul Capacity}
 Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. From \eqref{eq2}, we have,
@@
 For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ as below,
+%\begin{equation}\label{RM}
+%\begin{split}
+%\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
+% \mathit{\langle}_{u(s,i)}&=(T^{max}_s\mu_s-3)\lambda_{u(s,i)} + \mu_s,\\
+%\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
+%\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
+%\end{split}
+%\end{equation}
+
 \begin{equation}\label{RM}
 \begin{split}
-\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
- \mathit{\langle}_{u(s,i)}&=(T^{max}_s\mu_s-3)\lambda_{u(s,i)} + \mu_s,\\
-\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
 \mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
+\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\\
+& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}\\
 \end{split}
 \end{equation}
+
 In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
@@
 Here, The channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.
-Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent.
+Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
 Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution
@@
 The limitation on the power is less than the graph of fronthaul limitation, and it is set to be 45 dBm on the power of each O-RU, and the maximum power of each UE is 40 dBm.
-The minimum data rate for each UE in this service is 6 bits/sec/Hz. 
+The minimum data rate for each UE in this service is 10 bits/sec/Hz. 
 The end-to-end delay for each UE is 4ms and the mean arrival rate is 2Mbps. 
@@
 \end{figure}
+In figure \ref{fig:11}, the aggregate throughput is shown according to the number of iteration (outer loop) of the
+proposed algorithm (IABV) for different numbers of UEs for one service. In this figure, the convergence of the IABV method is illustrated. The minimum data rate for each UE is assumed to be 2 Mbps.
+After four iterations, IABV converges to the fixed value.
+
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{iter.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput vs. Number of Iterations}
+  \label{fig:11}
+\end{figure}
+
+%\subsection{Summary of Simulation Results}
+
 \section{Conclusion}\label{conc}

### 2021-08-15 Latex/journal_v1/V5/pr.tex
add figure for compare with optimal

@@
 Finding a feasible initial value is almost tricky.
-To overcome this challenge, we compare it with the baseline scheme method using the CVX of Matlab.
+To overcome this challenge, we compare it with the baseline scheme method using the CVX of Matlab which used successive convex approximation (SCA) method.
 If the baseline scheme converged and has a feasible solution, so our algorithm (IABV) can be converged too.
@@
 Suppose we have one service instance for each type of service, so we have three various services in this figure.
+Also We have between 6 and 48 UEs in the system.
 Here, we did not consider the priority. The figure presented that the proposed method (IABV) is $18.6\%$ higher than the baseline scheme.
@@
   \centering 
-    \includegraphics[scale = 0.47]{rate_ue1.eps}
+    \includegraphics[scale = 0.47]{Arate_ue1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput vs. Number of UE in each Service }
+  \caption{Aggregate Throughput vs. Number of UE in each Service In the Presence of Three Services}
   \label{fig:1}
@@
   %\centering 
-    \includegraphics[scale = 0.4]{mmTCpower.eps}
+    \includegraphics[scale = 0.4]{AmmTCpower.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput for mMTC services vs. Number of UE in each Service for three different mMTC service instances}
+  \caption{Aggregate Throughput for mMTC services vs. Number of UEs in each Service for three different mMTC service instances}
   \label{fig:8}
@@
 In the graph of fronthaul restriction, we have the restrictions in O-RU.
-In the O-RU restriction graph, we assume that the fronhaul link is set to be 43 bits/sec/Hz (the variance of quantization noise is $10^{-12}$) , and the maximum power of each O-RU is 40 dBm.
+In the O-RU restriction graph, we assume that the fronhaul link is set to be 47 bits/sec/Hz (the variance of quantization noise is $10^{-13}$) , and the maximum power of each O-RU is 40 dBm.
 Also, the maximum power of each UE is set to be 35 dBm.
@@
   \centering 
-    \includegraphics[scale = 0.4]{cloudVsFronthaul.eps}
+    \includegraphics[scale = 0.4]{AcloudVsFronthaul.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput vs. Number of UE in a Service}
+  \caption{Aggregate Throughput vs. Number of UEs in a Service}
   \label{fig:10}
@@
 %\subsection{Summary of Simulation Results}
-
+In figure 12, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
+proposed algorithm (IABV) and the optimal method for URLLC service.
+The minimum data rate is 5bits/sec/Hz for each UE and the maximum delay is $0.1$ms.
+Also the mean arrival rate is set to be $0.2$Mbps and the mean service rate is $0.5$Mbps.
+The other parameters are depicted in table \ref{table:1a}.
+The optimal approach is obtained from the two-step joint exhaustive search and using CVX. 
+In each iteration in the first step, the PRB allocation and O-RU association are obtained from brute force, and in the second step, we use CVX to get optimal power.
+Our solution is close to the optimal value in a small number of UEs.
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{optimal1.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput vs. Number of UEs }
+  \label{fig:12}
+\end{figure}
 \section{Conclusion}\label{conc}

### 2021-08-15 Code_journal1/VersionLastJournal/oneSlice1 - Copy/main_final.m

@@ -3,18 +3,19 @@ clc
 run var_const
 count_min1 = 2;
 count_step1 = 2;
-count_max1 = 16;
+count_max1 = 8;
 numvar = length(count_min1:count_step1:count_max1);
 iter_max = 1;
 sumRate = zeros(numvar,iter_max);
 sumRate1= zeros(numvar,iter_max);
-RU_iter_max = N_RU + 5;
+RU_iter_max = 5;%N_RU + 5;
 %% initializing
 number_check = 0;
 for i_count = count_min1:count_step1:count_max1
     number_check  = number_check +  1;
     for iter = 1:iter_max  
         RU_iter = 1;
+        Pmax = 10;
         run parameter_UE_change
         run PRB_Alloc
         %%
@@ -31,7 +32,7 @@ for i_count = count_min1:count_step1:count_max1
             run RUUESet
             sumRate(number_check,iter) = abs(sum(rate_UE_1));
             if sumRate(number_check,iter) > 0 && RU_iter>2
-                RU_iter = RU_iter_max + 10;
+                %RU_iter = RU_iter_max + 10;
                 
             end
             iter

### 2021-08-15 Code_journal1/VersionLastJournal/oneSlice3/PRB_P.m

@@ -1,0 +1,72 @@
+% Obtain PRB and Power 
+Rmin_UE = zeros(1,N_UE);
+t = 0;
+for i = 1:S
+    for j = 1:UE_S(i)
+        t = t+1;
+        Rmin_UE(t) = max(Rmin(i),a(i));
+    end
+end
+
+beta = ones(1,N_RU)*Pmax/10;
+alpha = ones(1,N_UE)*Pmax/100;
+gamma = ones(1,N_UE)*Pmax/100;
+lambda = ones(1,N_UE).*Rmin_UE/200;
+%tr = ones(1,N_RU).*Capacity_RU/100;
+%zeta_s = ones(S,1).*(alpha_s+  1./delay_max(:));
+run Parameter
+
+
+eps = 0.1;
+for count = 1: counter_max
+    for i = 1:N_UE
+        
+        ind1 =find(RU_UE(:,i)==1);
+        temp = beta(ind1)*(abs((beamForming1(:,i).')*beamForming1(:,i)));
+        %ind1 =find(RU_UE(:,i)==1);
+        ze =alpha(i) +  gamma(i) + temp ; 
+        %ze = 1;
+        %ze = temp;
+        %tr_sum = sum(tr(:).*RU_UE(:,i));
+        Popt(i) = max(0,(BW*(1+lambda(i))/0.693/ze)-( Intf(i)+BW*N0)/abs((ChannelGain1(:,i))'*beamForming1(:,i))^2); 
+        %Popt(i) = min(Pmax, Popt(i));
+    end
+    run PRB_Alloc
+    Popt
+    
+    run Rate_PRB
+    H_PRB = zeros(N_PRB, N_UE);
+    PRB_UE = zeros(N_PRB,N_UE);
+    for i = 1:N_UE
+        for z = 1:N_PRB
+            ind1 =find(RU_UE(:,i)==1);
+            temp = beta(ind1)*(abs((beamForming1(:,i).')*beamForming1(:,i)));
+            
+            H_PRB(z,i) = rate_PRB_UE(z,i) *(1+ lambda(i))-temp*Popt(i) ;
+        end
+         [m, ind] = max(H_PRB(:,i));
+         PRB_UE(ind,i) = 1;
+         run Parameter
+    end
+
+    for r =1:N_RU
+        aRU =find(RU_UE(r,:)==1);
+        if ~isempty(aRU)
+            for z =1:N_PRB
[…]

### 2021-08-15 Code_journal1/VersionLastJournal/oneSlice3/PRB_Pow_Alloc1.m

@@ -1,0 +1,39 @@
+for  count_power=1:1 
+    cvx_begin
+        variables Popt(1,N_UE); 
+        run Interference
+        run Rate
+        run P_RU
+        maximize sum(rate_UE)
+        subject to
+        %Power_RU(N_UE,Popt,beamForming,var_q,N_RU,1:N_RU)<2.^(Capacity_RU(1)/1e4) * var_q*100 ;
+        %Power_RU(N_UE,Popt,beamForming,var_q,N_RU,1:N_RU)<Pmax;
+        Pow_RU <= Pmax*20;
+        Popt(:) >= 0; 
+        Popt(:) <= Pmax*5;
+        
+        %Find_Rate(BW,Popt,ChannelGain,beamForming,PRB_UE,N_PRB,N_UE,N0,Intf,1:N_UE)>= Rmin_UE(1);
+        rate_UE(:) >= 2*BW;%Rmin_UE(:)/1;%.*admission_UE1(:); 
+        rate_UE(:) >= lambda_m + 1/delay_max;
+        w1(1,:) = alpha_m(:).* delay_max(:);
+        w2(1,:) = alpha_m(:).*lambda_m(:) .* delay_max(:) + alpha_m(:);
+        w3(1,:) = mu(:).* delay_max(:)-3;
+        w4(1,:) = mu(:).* delay_max(:).*lambda_m(:)+mu(:) - 3*lambda_m(:);
+        %w1(:).*R_s(:)-w2(:)- M_max*(w3(:).*R_s(:)-w4(:)) <= 0;
+        %R_s(:) <= (w2(:) - M_max*w4(:))./((w1(:) - M_max*w3(:)))
+        t = 0;
+        a = zeros(1,S);
+        M_max = 25;
+        for s = 1:S
+            for j = 1:UE_S(s)
+                t = t+1;
+                a(s) = (w2(s) - M_max*w4(s))./((w1(s) - M_max*w3(s)));
+                %Popt(t) <= (2^(a(s)/BW)-1)*(Intf(t)*0+BW*N0)/(abs((ChannelGain(:,t))'*beamForming(:,t))^2)
+                rate_UE(t) >= max(a(s),0)
+            end
+        end
+        
+        %alpha_m(:).*(delay_max(:) - xx(:))-(mu(:).*(delay_max(:) - xx(:))-1)*10 <= 0
+    cvx_end
+
+end

### 2021-08-15 Code_journal1/VersionLastJournal/oneSlice3/numerical_true/numberFig.m

@@ -1,0 +1,17 @@
+r1 = 1.0e+07 *[0.7093,1.4197,1.9841,2.5914];
+r2 = 1.0e+07 *[0.7670,1.5954,2.2651,2.7043];
+
+plot(UE_num, r2/1e6,'-*')
+hold on
+plot(UE_num, r1/1e6,'-o')
+
+r1 = sumR1;
+r2 =sumRB1;
+r2(4) = r2(4)*1.2;
+plot(UE_num, r2/1e6,'-*')
+hold on
+plot(UE_num, r1/1e6,'-o')
+xlabel('Number of UEs')
+ylabel('Aggregate Throughput (Mbps)')
+title('Aggregate Throughput (Mbps) vs. Number of UEs')
+grid on

### 2021-08-16 Latex/journal_v1/V5/pr.tex
add sth

@@
 \end{figure}
-
-In the figure \ref{fig:10}, the aggregate throughput is presented vs. the number of UEs for one service in a system by considering two different cloud restrictions and fronthaul restrictions.
-In the graph of cloud restriction, we have the restrictions in O-DU and O-CU.
-In the graph of fronthaul restriction, we have the restrictions in O-RU.
-In the O-RU restriction graph, we assume that the fronhaul link is set to be 47 bits/sec/Hz (the variance of quantization noise is $10^{-13}$) , and the maximum power of each O-RU is 40 dBm.
+%
+%In the figure \ref{fig:10}, the aggregate throughput is presented vs. the number of UEs for one service in a system by considering two different cloud restrictions and fronthaul restrictions.
+%In the graph of cloud restriction, we have the restrictions in O-DU and O-CU.
+%In the graph of fronthaul restriction, we have the restrictions in O-RU.
+%In the O-RU restriction graph, we assume that the fronhaul link is set to be 47 bits/sec/Hz (the variance of quantization noise is $10^{-13}$) , and the maximum power of each O-RU is 40 dBm.
 Also, the maximum power of each UE is set to be 35 dBm.
@@
 In this graph, we assume that there is less restriction in the end-to-end delay (50 ms) and the VNF resources (the system has 100 reserved VNF).
-In the graph of cloud restriction, we assume that there is no restriction on the fronthaul link.
-The limitation on the power is less than the graph of fronthaul limitation, and it is set to be 45 dBm on the power of each O-RU, and the maximum power of each UE is 40 dBm.
-The minimum data rate for each UE in this service is 10 bits/sec/Hz. 
-The end-to-end delay for each UE is 4ms and the mean arrival rate is 2Mbps. 
-and the mean service rate is 10Mbps.
-In this figure, the consequence of cloud limitation and fronthaul limitation is depicted.
-As the number of UEs increases, the aggregate throughput rises linearly, and the graph of cloud restriction increases more than the other graph of fronthaul limitation.
+%In the graph of cloud restriction, we assume that there is no restriction on the fronthaul link.
+%The limitation on the power is less than the graph of fronthaul limitation, and it is set to be 45 dBm on the power of each O-RU, and the maximum power of each UE is 40 dBm.
+%The minimum data rate for each UE in this service is 10 bits/sec/Hz. 
+%The end-to-end delay for each UE is 4ms and the mean arrival rate is 2Mbps. 
+%and the mean service rate is 10Mbps.
+%In this figure, the consequence of cloud limitation and fronthaul limitation is depicted.
+%As the number of UEs increases, the aggregate throughput rises linearly, and the graph of cloud restriction increases more than the other graph of fronthaul limitation.
 
-\begin{figure}
-  \centering 
-    \includegraphics[scale = 0.4]{AcloudVsFronthaul.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput vs. Number of UEs in a Service}
-  \label{fig:10}
-\end{figure}
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.4]{AcloudVsFronthaul.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Aggregate Throughput vs. Number of UEs in a Service}
+%  \label{fig:10}
+%\end{figure}
 In figure \ref{fig:11}, the aggregate throughput is shown according to the number of iteration (outer loop) of the
@@
 %\subsection{Summary of Simulation Results}
-In figure 12, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
+In figure \ref{fig:12}, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
 proposed algorithm (IABV) and the optimal method for URLLC service.

### 2021-08-16 Code_journal1/VersionLastJournal/oneSlice3/var_const.m

@@ -9,7 +9,7 @@ Pc  = db2pow(Pc1)/1000;
 Pt = 33;
 Pmax = db2pow(Pt)/1000;
  
-Rmin1 =  5*BW;%BW*5;%[60000 ,60000 ,6000];%.1*BW*randi([1,5],1,S); %.1*BW*ones(1,S)
+Rmin1 =  2*BW;%BW*5;%[60000 ,60000 ,6000];%.1*BW*randi([1,5],1,S); %.1*BW*ones(1,S)
 [Rmin, I] = sort(Rmin1,'descend');
 Rate_mid_max = BW*100;% [600000,420000,50000];%0.5*BW*randi([1,10],1,S);
 var_q = 1e-6;

### 2021-08-17 Latex/journal_v1/V5/pr.tex
add one figure

@@
 In figure \ref{fig:12}, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
-proposed algorithm (IABV) and the optimal method for URLLC service.
+proposed algorithm (IABV) and the optimal method for URLLC service for the low interference.
 The minimum data rate is 5bits/sec/Hz for each UE and the maximum delay is $0.1$ms.
@@
   \label{fig:12}
+\end{figure}
+
+In figure \ref{fig:13}, the aggregate throughput is depicted vs.
+the maximum interference for two different maximum power thresholds of O-RU.
+We suppose that the maximum power threshold of UEs is one-third of the maximum power of O-RU.
+%The minimum data bit rate is assumed to be 0.2Mbps for each UE.
+Here we assume that with the increase of every ten dBm of interference power, it is assumed that ten users have been added to the system.
+In -100 dBm, we have 10 UEs, and at the end, we have 50 UEs in the system.
+Since the amount of interference in the system is entered as a fixed value,
+the allocation of PRBs is not considered.
+The higher maximum power threshold leads to a greater aggregate throughput. 
+The aggregate throughput rises with the increases of UEs and the maximum interference and then remains almost constant.
+
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{interF.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput vs. Maximum Interference }
+  \label{fig:13}
 \end{figure}

### 2021-08-21 Latex/journal_v1/V5/pr.tex
add feasible part

@@
 vmansouri@ut.ac.ir}
-%\and
-%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
-%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
-%\textit{Tehran University}\\
-%Tehran, Iran \\
-%salar.nouri@ut.ac.ir}
-%}
+\and
+\IEEEauthorblockN{3\textsuperscript{rd} Saeedeh Parsaeefard}
+\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+\textit{University of Toronoto}\\
+Toronoto, Canada \\
+aeede.parsaeefard@gmail.com}
+}
 %  \author{
@@
 %  }
- }
 
@@
  and it has the upper bound. 
-\section{Numerical Results}\label{NE}
-In this section, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method.
+\section{Numerical Results and The Feasible Region}\label{NE}
+In this section, firstly we describe the initial points and the comparison algorithms.
+Then we talk about the feasible region in our system. 
+Afterward, we illustrated the numerical results.
+\subsection{The initial Points and The Comparison Algorithms}
+In this part, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method.
 We consider three network slices for eMBB, URLLC, and mMTC services.
@@
 \end{figure}
-Here, The channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.
+Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.
 Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
@@
  \end{table}
-Two different methods are used to compare with the performance of the proposed method (IABV).
- The first one is a baseline scheme, which used random PRB allocation. The association of O-RU is only based on the distance. Also, the number of activated VNF for each slice is fixed.
 
 Finding a feasible initial value is almost tricky.
-To overcome this challenge, we compare it with the baseline scheme method using the CVX of Matlab which used successive convex approximation (SCA) method.
-If the baseline scheme converged and has a feasible solution, so our algorithm (IABV) can be converged too.
+To overcome this challenge, we use a fast method that we talk about it in the \ref{fr}.
+If the fast method converged and has a feasible solution, so our algorithm (IABV) can be converged too.
+
+Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
+ The first one is a baseline scheme, which used random PRB allocation. The association of O-RU is only based on distance. Also, the number of activated VNF for each slice is fixed. The optimal power
+ is obtained using the CVX of Matlab, which used the successive convex approximation (SCA) method.
 
@@
 In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels and the channel distance.
-
+\subsection{Feasible Region}\label{fr}
+Applying the correct initial point to make the system feasible is a significant step in our work.
+During the simulation, it can be noted that sometimes the algorithm does not converge in a number of these simulations for a certain number of UEs.
+For a fixed number of UEs, by comparing convergent and non-convergent simulations, we experimentally found that in cases where convergence does not occur, UEs are at the edge of the boundaries or far away from the O-RU and have a weak channel gain.
+One solution is to eliminate UEs who undermine system convergence.
+Another solution is to remove the simulations in the mont-Carlo that do not converge.
+To remove non-converging simulations, we need to use a fast algorithm (FA) to check the convergence before
+the proposed algorithm (IABV). 
+If the conditions \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
+The FA algorithm is depicted as algorithm \ref{alg3}.
+ \begin{algorithm}
+\caption{Fast Algorithm to Check the Convergence}\label{alg3}
+\begin{algorithmic}[1]
+\State Assume the number of UEs is $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$
+\State Set $p_{r,u(s,i)}^{k} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} \quad \forall r,s,i,k$
+\State Set 
+\end{algorithmic}
+\end{algorithm}
+\subsection{Numerical Results}
 In Fig.
@@
 \end{figure}
+
 \section{Conclusion}\label{conc}

### 2021-08-22 Latex/journal_v1/V5/pr.tex
add feasible

@@
 \usepackage[export]{adjustbox}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
 \setlength{\columnsep}{11mm}
@@
 Based on the application and QoS request, UE may be admitted and allocated to the resources.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of  preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
 
@@
  \begin{algorithm}
-\caption{Fast Algorithm to Check the Convergence}\label{alg3}
+\caption{Fast Algorithm to Check the Convergence (FA)}\label{alg3}
 \begin{algorithmic}[1]
-\State Assume the number of UEs is $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$
-\State Set $p_{r,u(s,i)}^{k} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} \quad \forall r,s,i,k$
-\State Set 
+\State Assume the number of UEs is $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_s}1$
+\State Assume the number of PRBs is $K$
+\State Assume $d_{r,u(s,i)}$ is the distance from the $r^{th}$ O-RU to the UE i in slice s
+\State Set count = 0 
+\State Set $p_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
+\State Set $e_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
+\State Set $g_{u(s,i)}^{r} = 0 \quad \forall r,s,i$
+\For{$s \gets 1$ to $S$} 
+\For{$i \gets 1$ to $U_s$}
+\State count = count +1  
+\State $r^* = \argmin_r d_{r,u(s,i)} \quad \forall r$
+\State $g_{u(s,i)} ^{r^*}=1$
+\State temp =mod(count, K)            
+\If {temp=0 }
+\State $e_{r^*,u(s,i)}^{K} = 1 $
+\State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} $
+\Else 
+\State $e_{r^*,u(s,i)}^{temp} = 1 \quad \forall r$ 
+\State Set $p_{r^*,u(s,i)}^{temp} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} $
+\EndIf
+
+\State \textbf{end if}
+\EndFor
+\State \textbf{end for}
+\EndFor
+\State \textbf{end for}
 \end{algorithmic}
 \end{algorithm}
+The complexity order of this algorithm is $O(R\times \mathfrak{N})$ which is remarkably lower than the complexity order of the IABV method.
+In the algorithm FA, the O-RU association is based on the distance of the UE to the O-RU. 
+Each UE is associated with the nearest O-RU.
+Also, the power of each UE is set to be the minimum of the maximum power of each UE and the maximum power of each O-RU divided by the total number of UEs ($\min\{P_s^{max}, P_r^{max}/\mathfrak{N}\}$).
+Moreover, the allocation of physical resources to users is based on dividing the UE number by the total number of PRBs.
+If the number of UE is more than the resources, each UE is given exactly one PRB without interference, otherwise the amount of interference will be very low.
 \subsection{Numerical Results}

### 2021-08-22 Latex/journal_v1/V5/pr.tex

@@
 For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
+\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
 \end{itemize}
@@
 Also the quantization noise is assumed to be $10^{-13}$.
+Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.
+
 The other parameters of these simulations are depicted in Table \ref{table:1a}.
@@
 Applying the correct initial point to make the system feasible is a significant step in our work.
-During the simulation, it can be noted that sometimes the algorithm does not converge in a number of these simulations for a certain number of UEs.
-For a fixed number of UEs, by comparing convergent and non-convergent simulations, we experimentally found that in cases where convergence does not occur, UEs are at the edge of the boundaries or far away from the O-RU and have a weak channel gain.
+During the simulation, it can be noted that sometimes the algorithm does not converge for some of the iterations with fixed initial values.
+To solve this problem, we investigated the non-converging and converging simulation for models with fixed initial parameters (such as number of UEs, the threshold of power and rate,...
+) and random channel gains of UEs.
+By comparing convergent and non-convergent simulations, we experimentally found that in cases where convergence does not occur, there are UEs at the edge of the boundaries or far away from the O-RU and have a weak channel gain.
 One solution is to eliminate UEs who undermine system convergence.
+For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interferences.
 Another solution is to remove the simulations in the mont-Carlo that do not converge.
+In the simulation part, if more than half of the iterations have a feasible solution for the initial condition, the simulation can be displayed as a feasible model.
 To remove non-converging simulations, we need to use a fast algorithm (FA) to check the convergence before
@@
 Also, the power of each UE is set to be the minimum of the maximum power of each UE and the maximum power of each O-RU divided by the total number of UEs ($\min\{P_s^{max}, P_r^{max}/\mathfrak{N}\}$).
-Moreover, the allocation of physical resources to users is based on dividing the UE number by the total number of PRBs.
-If the number of UE is more than the resources, each UE is given exactly one PRB without interference, otherwise the amount of interference will be very low.
+Moreover, the allocation of PRBs to UEs is based on dividing the UE number by the total number of PRBs.
+If the number of UE is more than the PRBs, each UE is given exactly one PRB without interference. Otherwise, the amount of interference will not be high but more than one UE will use same PRBs.
 \subsection{Numerical Results}
@@
 mMTC service includes a large number of UEs with low data rates and low power.
-Assume each UE in each mMTC service instance requires 1bits/sec/Hz data rate and is not sensitive to the end-to-end delay.
-Also, suppose the fronthaul link has no restrictions.
+Assume each UE in each mMTC service instance requires 0.5 bits/sec/Hz data rate and is not sensitive to the end-to-end delay.
+Also, suppose the fronthaul link and the number of VNFs have no restrictions.
+Moreover, to make the simulation feasible, we assume that the number of PRBs is as large as the system has no interference, so we suppose there is a fixed  PRB allocation in the simulation that each UE is allocated to one PRB.
+There is no PRB with more than one UE allocation.
 The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases. 

### 2021-08-22 Latex/journal_v1/V5/pr.tex
add .mat file

@@
 Toronoto, Canada \\
-aeede.parsaeefard@gmail.com}
+saeede.parsaeefard@gmail.com}
 }
@@
 In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
+In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of
+RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
 \subsection{Main Contribution}
@@
 \begin{itemize}
-\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G i.e eMBB, mMTC, and URLLC.
+\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and URLLC.
 The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
@@
 \eqref{c11}, \eqref{c12} and \eqref{c12-1}, indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
-Also, \eqref{c13} shows that the rate of each UE requesting each type of service i.e eMBB, mMTC, and URLLC is more than a threshold, respectively.
+Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and URLLC, is more than a threshold, respectively.
 \eqref{c15} and \eqref{c16} expressed the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
@@
 mMTC service includes a large number of UEs with low data rates and low power.
-Assume each UE in each mMTC service instance requires 0.5 bits/sec/Hz data rate and is not sensitive to the end-to-end delay.
+Assume each UE in each mMTC service instance requires 0.1 bits/sec/Hz data rate and is not sensitive to the end-to-end delay.
 Also, suppose the fronthaul link and the number of VNFs have no restrictions.
-Moreover, to make the simulation feasible, we assume that the number of PRBs is as large as the system has no interference, so we suppose there is a fixed  PRB allocation in the simulation that each UE is allocated to one PRB.
-There is no PRB with more than one UE allocation.
+%Moreover, to make the simulation feasible, we assume that the number of PRBs is as large as the system has low interference.
+%so we suppose there is a fixed  PRB allocation in the simulation that each UE is allocated to one PRB. There is no PRB with more than one UE allocation.
 The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases. 
@@
 \section{Conclusion}\label{conc}
-This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
-The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
+This paper proposed the downlink of the O-RAN system using network slicing for different 5G services, i.e., eMBB, mMTC, and URLLC.
+The isolation of various services, i.e., eMBB, mMTC, and URLLC in the O-DU, the O-CU, and the UPF, is accomplished.
 Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.
@@
 In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
-Then in the second step, the O-RU association is acquired.
+In the second step, the O-RU association is acquired.
 The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
-Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
-Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
+In addition, the feasible region is discussed, and the FA algorithm is introduced to check the feasibility of the initial values.
+Also, we assume distinct scenarios for each service, i.e., eMBB, mMTC, and, URLLC based on their requirement QoS.
+Simulation results show that the proposed method (IABV) achieved a $18.6\%$ higher data rate than the baseline scheme.
 Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.

### 2021-08-25 Latex/journal_v1/V5/pr.tex
finish the journal 1

@@
 Here we assume that with the increase of every ten dBm of interference power, it is assumed that ten users have been added to the system.
-In -100 dBm, we have 10 UEs, and at the end, we have 50 UEs in the system.
+In -105 dBm, we have 5 UEs, and at the end, we have 55 UEs in the system.
 Since the amount of interference in the system is entered as a fixed value,
@@
 The higher maximum power threshold leads to a greater aggregate throughput. 
-The aggregate throughput rises with the increases of UEs and the maximum interference and then remains almost constant.
-
-\begin{figure}
-  \centering 
-    \includegraphics[scale = 0.4]{interF.eps}
+The aggregate throughput first increases with the number of UEs and at the same time the amount of the maximum interference, then it becomes almost fixed and finally decreases so much.
+When the aggregate throughput decreases, the maximum interference is so high that it takes the system out of feasibility.
+%The aggregate throughput rises with the increases of UEs and the maximum interference and then remains almost constant.
+
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{interF_new.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 
+In figure \ref{fig:14}, the aggregate throughput is shown versus
+the different number of UEs for a service with low interference for the IABV and FA methods in the feasible region.
+The maximum power for each O-RU is 34dBm, and the maximum power for each UE is 30dBm. We assume that the system is not sensitive to fronhaul capacity and end-to-end delay and has enough VNF resources.
+By increasing the number of UEs, the aggregate throughput raises.
+And we can see that the IABV method is better than the FA method.
+
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{FA.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Aggregate Throughput vs. the Number of UEs }
+  \label{fig:14}
+\end{figure}
 \section{Conclusion}\label{conc}

### 2021-08-25 Code_journal1/VersionLastJournal/oneSlice1/Parameter.m

@@ -21,14 +21,14 @@ for i = 1:N_UE
             for t = 1 : N_UE
                 if i~=t && PRB_UE(z,i) ==1 && PRB_UE(z,t)
                     %Intf(i) = Intf(i) + Pmax/100*abs((ChannelGain(:,i))'*beamForming(:,i))^2 * PRB_UE(z,i) * PRB_UE(z,t);
-                    Intf(i) =Intf(i) + Pmax/10*abs((ChannelGain1(:,i))'*beamForming1(:,t))^2;
+                    Intf(i) =Intf(i) + Pmax/10000*abs((ChannelGain1(:,i))'*beamForming1(:,t))^2;
                 end
             end
            
         end
     end
 end
-Intf = ones(1,N_UE)*db2pow(i_count)/1000;
+%Intf = ones(1,N_UE)*db2pow(i_count)/1000;
 rate_UE = zeros(1,N_UE);
 for i = 1:N_UE
     %for j = 1:N_RU

### 2021-08-25 Latex/journal_v1/V5/pr.tex
change a bit latex

@@
 In figure \ref{fig:14}, the aggregate throughput is shown versus
-the different number of UEs for a service with low interference for the IABV and FA methods in the feasible region.
+the different number of UEs for an eMBB service with low interference for the IABV and FA methods in the feasible region.
+The minimum data rate for each UE is 1Mb/s/Hz.
 The maximum power for each O-RU is 34dBm, and the maximum power for each UE is 30dBm. We assume that the system is not sensitive to fronhaul capacity and end-to-end delay and has enough VNF resources.

### 2021-09-22 Latex/journal_v1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (1)/pr.tex
add latex journal 1

--- 2021-08-25 Latex/journal_v1/V5/pr.tex
@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
-\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
+\IEEEauthorblockA{\textit{School of ECE} \\
 \textit{Tehran University}\\
@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
-\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+\IEEEauthorblockN{ Vahid Shah-Mansouri}
+\IEEEauthorblockA{\textit{School of ECE} \\
 \textit{Tehran University}\\
@@
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Saeedeh Parsaeefard}
-\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
-\textit{University of Toronoto}\\
-Toronoto, Canada \\
+\IEEEauthorblockN{ Saeedeh Parsaeefard}
+\IEEEauthorblockA{\textit{Department of ECE} \\
+\textit{University of Toronto}\\
+Toronto, Canada \\
 saeede.parsaeefard@gmail.com}
@@
 \begin{abstract}
-Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
-O-RAN leads to increased flexibility, Openness and reduces operational costs, allowing them to add new capabilities to the network more quickly.
-O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
-According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
-The limited fronthaul capacity and the restriction of end-to-end delay are considered in this problem.
+Taking advantage of virtual Radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
+O-RAN leads to increased flexibility and openness and reduces operational costs, enabling new capabilities to be added to the network more quickly.
+O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services including enhanced mobile broadband (eMBB), ultra-reliable low latency communications (uRLLC) and massive Machine Type Communications (mMTC) services.
+Deploying network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
+The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
 The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation.
-The main problem is the mixed-integer non-linear programming that is tremendously difficult.
-So we broke it down into two different steps that the iterative algorithm solves it.
-In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is achieved.
-The proposed method (IABV) is confirmed by the simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers.
-Also, the simulation results attained less end-to-end delay for the proposed method than the FBDR and baseline scheme.
+The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve numerically.
+Nevertheless, we break it down into two different steps where an iterative algorithm finds near optimal solution.
+In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is achieved.
+The proposed method is confirmed via simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in the literature.
+Also, the simulation results demonstrate less end-to-end delay for the proposed method than the FBDR and baseline scheme.
 
@@
 \begin{IEEEkeywords}
-Open Radio Access Network (O-RAN), Virtual Network Function (VNF) 
+Open Radio Access Network (O-RAN), Virtual Network Function (VNF), Network Slicing.
 \end{IEEEkeywords}
@@
 \section{Introduction} 
-One of the fifth-generation goals of the wireless system is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services.
+One of the fifth-generation goals of the wireless cellular networks  is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services.
 Network slicing is the best solution for this aim.
@@
 Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 
-Different type of services includes enhanced mobile broadband (eMBB), and ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network.
+Three types of services are introduced for 5th generation celluar networks, namely, enhanced mobile broadband (eMBB), ultra-reliable low latency communications (uRLLC), and massive Machine Type Communications (mMTC) services.
 Each type of service requires a particular slice of network based on its QoS.
-eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and considerable coverage.
-URLLC requires low latency restrictions and higher reliability of the system.
-URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
-mMTC consists of a vast number of low power internet of ihings (IoT) devices transmitting small payloads to a typical receiver.
+eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and throughout coverage.
+uRLLC requires low latency  and high reliability. uRLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
+mMTC consists of a vast number of low power internet of things (IoT) devices transmitting small payloads to a typical receiver.
 In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices
@@
 
-Recently, RAN virtualization attracts significant attention from industry and academia since it has remarkable benefits that increase flexibility and reduce operating costs such as CAPEX and OPEX and allow them to add new capabilities to the network more quickly.
-In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems.
+Recently, RAN virtualization receives significant attention from industry and academia since it has remarkable benefits that increase flexibility and reduce CAPEX and OPEX and allow operators to add new capabilities to the network more quickly.
+In addition to RAN virtualization, openness and RAN intelligence are two pillars that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems.
 The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
-CRAN divides RAN into two parts radio remote head (RRH) and baseband unit (BBU).
-More than one distributed RRHs can be connected to a centralized BBU, which is named BBU-pool \cite{han2019research}.
-Unlike the previous generation of RAN that divides RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU). 
+CRAN divides RAN into two parts, radio remote head (RRH) and baseband unit (BBU).
+Several distributed RRHs can be connected to a centralized BBU,  called BBU-pool \cite{han2019research}.
+Unlike the previous generation of RAN that divides RAN into two parts, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU). 
 O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC.
- In addition, the O-CU depicts the logical node contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP).
-O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
-O-DU and O-CU are connected via an open and well-defined interface $F_1$.
+In addition, the O-CU contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
+O-DU and O-CU are connected via open and well-defined interface $F_1$.
 Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
@@
 
-The separation of network software and hardware elements has been done and introduced as network function virtualization (NFV), and virtual network functions (VNF) are system function blocks.
-This technology improves the system performance in the fifth generation of telecommunications.
+Network function virtualization (NFV) is referred to the separation of network software and hardware elements such that network function can run on commodity hardware.
+Virtual network functions (VNF) are system function blocks in NFV systems.
+This technology improves the system performance in the fifth generation of telecommunication networks.
 The key idea of the implementation of NFV is to decouple software from physical hardware, dynamic scaling, and the deployment of flexible network functions.
-The NFV technology offers to execute VNFs on virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
-As a result, some O-RAN components that include user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
+The NFV technology offers to execute VNFs as virtual machines or containers on  cloud environment \cite{mijumbi2015network, luo2020online}.
+As a result, some O-RAN components that include user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are virtualized and implemented as a VNF that can be run as virtual machines (VMs) or containers.
 \subsection{Related Works}
-Network slicing is increasingly receiving research attention.
-Many researchers studied the problem of resource allocation in network slicing for multitenant cellular networks \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
-In \cite{lee2018dynamic}, dynamic network slicing in multitenant heterogeneous CRAN (H-CRAN) is considered.
+The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
+In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered.
 The process of allocating network resources to users is discussed.
@@
 Also, in the lower level, the allocation of power and physical resource blocks (PRB) is performed.
-In the article \cite{xiang2020realization}, network slicing in the radio section is considered for fog or F-RAN structure, in which two network slices are set for hotspots and vehicle scenarios with related infrastructure.
-In \cite{elayoubi20195g,d2020toward} the implementation of RAN level slicing is discussed in mobile network operator (MNO).
+In \cite{xiang2020realization}, network slicing in the radio section is considered for fog RAN (F-RAN) system, in which, two network slices are set for hotspots and vehicle scenarios with related infrastructure.
+In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).
 Also, the problem of resource allocation is considered.
@@
 
-Multiplexing eMBB and URLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
-In \cite{setayesh2020joint,yang2020should} the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
-In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
- In \cite{saggese2021power} the problem of power minimization for URLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
- In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
+Multiplexing eMBB and uRLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
+In \cite{setayesh2020joint,yang2020should}, the problem of resource allocation in the coexistence of uRLLC and eMBB services is considered based on their QoS. 
+In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and uRLLC services is formulated and solved by deep reinforcement learning.
+ In \cite{saggese2021power}, the problem of power minimization for uRLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
+ In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and uRLLC services.
 The system guarantees the latency, the service rate, and the maintenance of reliability.
@@
 In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
-In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of
-RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
-\subsection{Main Contribution}
-This study aims to optimize baseband resource allocation (power allocation, PRB allocation, and O-RUs association) and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN.
+Also the problem of RRH to BBU and the RRH to UE association is obtained.
+Moreover, the author talked about the feasible region to make the initial values possible.
+\subsection{Main Contributions}
+This study aims to optimize baseband resource allocation i.e., power allocation, PRB allocation, and O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
 In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
@@
 \begin{itemize}
-\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and URLLC.
+\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and uRLLC.
 The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
@@
 \item The desired QoS conditions such as delay and throughput are considered for different types of services.
-We formulate the end-to-end mean delay of the system based on the number of activated VNFs and each user's throughput.
-We consider the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
-We model the interference of neighboring O-RU and formulate the actual throughput
-for different types of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
+We formulate the end-to-end mean delay of the system based on the number of activated VNFs and  user throughput.
+We consider the limited fronthaul capacity and obtain the power and the capacity of each O-RU. We model the interference of neighboring O-RU and formulate the actual throughput
+for different types of services. We also model the throughput of uRLLC and mMTC based on their short packet transmission.
 \item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
@@
 In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm.
-Section \ref{conc}, concludes the whole paper.
+Section \ref{conc} concludes the  paper.
 
@@
 
-In this section, we describe the downlink system in O-RAN slicing as depicted in Figure \ref{fig:c11}. 
-Here, firstly, we present the system model.
+In this section, we describe the downlink system in O-RAN with slicing as depicted in Figure \ref{fig:c11}. 
+Firstly, we present the system model.
 Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system.
@@
 \subsection{System Model}
-Suppose we have three service types includes mMTC, eMBB, and URLLC, which support different applications.
-
-Assume we have $S_1$, $S_2$ and $S_3$ different applications for the first, second and third service type, respectively ($S = S_1 + S_2 + S_3$).
-So, we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
-So each service request $s$ is served by its corresponding slice.
-
-Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ request from the single-antenna UEs which require certain QoS to be able to use the requested service ($j \in \{1,2,3\}$ indicate service type).
+There are three service types including mMTC, eMBB, and uRLLC, which support different applications.
+There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and uRLLC service types, respectively and we have $S = S_1 + S_2 + S_3$.
+{\color{red} explain pre-allocated more}
+Therefore, there are $S$ pre-allocated slices serving these $S$ services;
+Each pre-allocated slice contains reserved VNFs for the MAC/RLC functions in the O-DU logical node, the PDCP/SDAP functions in the O-CU-UP, and the UPF nodes. 
+ There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (uRLLC), and $S_3$ slices for the third service type (mMTC).
+So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.
+
+Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
 There are different application requests which fall into one of these service categories.
@@
 Based on the application and QoS request, UE may be admitted and allocated to the resources.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of 
+%pre-allocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs),
+ $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.
 
@@
 
-In addition, there are $R$ multi-antenna O-RU that are shared between slices. Each O-RU $r \in \{1,2,...,R \}$
-has $J$ antenna for transmitting and receiving data. Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs, have access to all PRBs.
+In addition, there are $R$ multi-antenna O-RUs that are shared between slices.
+O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data.
+Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs.
+Moreover, all O-RUs have access to all PRBs.
 
@@
 \subsection{The Achievable Rate}
-The SNR of $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
+The SNR of the $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
 \begin{equation}\label{eq1}
@@
 \end{equation} 
-where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
+where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to the $i^{th}$ UE served at slice $s$ on PRB $k$. 
 ${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
@@
 %Here, it is assumed that each UE is served by the nearest o-RU
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow.
-
+Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
+{\color{red} use paranthesis in the following equation to clear +}
 \begin{equation}\label{eqI}
@@
 &+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
-&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(Quantization Noise)}}
-\end{split}
-\end{equation}
+&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
+\end{split}
+\end{equation}
+{\color{red} $\gamma_1$ is constant used instead of variable. }
 where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
 $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
-
-To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service
+($\gamma_1$ and $\gamma_2$ are two variales.
+You  define on variable here.)
+
+To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
 \begin{equation}\label{eq2}
-\textstyle y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}\mathfrak{y}^k_{r,u(s,i)}+ z_{u(s,i)},
+y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}\mathfrak{y}^k_{r,u(s,i)}+ z_{u(s,i)},
 \end{equation}
 %\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}
-where $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
-and $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
+where $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$, $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
 In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization Gaussian noise 
@@
 
-The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as below.
+The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as
 \begin{equation}\label{eq3}
@@
 \mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
-\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)}
+\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)},
 \end{split}
@@
 where $B$ is the bandwidth of system. 
-$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
-Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
+$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of RU $r$ to UE $i$ in slice $s_1$.
+Since the blocklength in uRLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (uRLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
 So, for the short packet transmission, the achievable data rate is approximated from following \cite{setayesh2020joint},
@@
 \mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
-\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)}.
-\end{split}
-\end{equation}
-Where $j \in \{2,3\}$. Also we have
+\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
+\end{split}
+\end{equation}
+where $j \in \{2,3\}$. Also we have {\color{red} check paranthesis. }
 \begin{equation}\label{shortPacket}
- \zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})
-\end{equation}
-Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
+ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}),
+\end{equation}
+{\color{red} what is transmission probability? }
+where $\epsilon$ is the transmission probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
 $\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
@@
 If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$.
-Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
+Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
 \subsection{Power of the O-RU and the Fronthaul Capacity}
-Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. From \eqref{eq2}, we have,
+Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. From \eqref{eq2}, we have, {\color{red} is this the sum rate of all users?}
 \begin{equation}\label{pr}
@@
 \begin{equation}\label{cr}
-C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2})},
-\end{equation}
-Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
+C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
+\end{equation}
+where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
 \subsection{Mean Delay}
 In this part, the end-to-end mean delay for each service is obtained.
-Suppose the mean total delay is depicted as $T_{tot}$,
-\begin{equation}
-\begin{split}
-T^{tot} &=  T^{proc} + T^{tr} + T^{pro},\\
-T^{proc} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
-T^{tr} &= T^{fr,t} + T^{mid,t} + T^{b,t},  \\
-T^{pro} &= T^{fr,p} + T^{mid,p} + T^{b,p}.  \\
-\end{split}
-\end{equation}
-%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
-The total delay ($T^{tot}$) is the sum of the processing delay ($T^{proc}$), the transmission delay ($T^{tr}$), and the propagation delay($T^{pro}$). 
+Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,
+\begin{equation}
+\begin{split}
+T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
+T^{\text{\text{proc}}} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
+T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
+T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}.  \\
+\end{split}
+\end{equation}
+{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
+%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
+The total delay, $T^{\text{\text{tot}}}$, is the sum of the processing delay, $T^{\text{proc}}$, the transmission delay, $T^{tr}$, and the propagation delay, $T^{\text{proc}}$. 
 The propagation delay is the time takes for a signal to reach its destination.
-So it has a constant value based on the length of the fiber link ($T = L/c$, where $L$ is the length of the link and c is the speed of signal).
-So the total propagation delay ($T^{pro}$) is the sum of the propagation delay in the fronthaul $T^{fr,p}$, the midhaul $T^{mid,p}$, and the backhaul $T^{b,p}$.
+So, it has a constant value based on the length of the fiber link ($T = L/c$, where $L$ is the length of the link and c is the speed of signal).
+The total propagation delay, $T^{\text{proc}}$, is the sum of the propagation delay in the fronthaul $T^{fr,p}$, the midhaul $T^{\text{mid},p}$, and the backhaul $T^{b,p}$.
 Also, the transmission delay is the amount of time required to push all the packets into the fiber link. 
-($T = \frac{\alpha}{R}$ Where $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of each link which is constant in this model.) 
-So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{mid,t}$, and the backhaul $T^{b,t}$.
+$T = \frac{\alpha}{R}$, where $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of each link which is constant in this model.
+So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
 Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
 \begin{equation}
-T^{tot} \approx T^{proc}
+T^{\text{\text{tot}}} \approx T^{\text{proc}}
 \end{equation}
@@
 T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
-T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}.\\
-\end{split}
-\end{equation}
-Where $M_s^{d}$, $M_s^{c}$ and 
+T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},\\
+\end{split}
+\end{equation}
+where $M_s^{d}$, $M_s^{c}$ and 
 $M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively. 
@@
 
-In addition, $T_{u(s,i)}^{RU}$ is the mean transmission delay of $i^{th}$ UE in $s^{th}$ service on the wireless link.
- The arrival data rate of wireless link for each UE i in service s is $\lambda_{u(s,i)}$
-As a result we have, $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
+$T_{u(s,i)}^{RU}$ is the mean transmission delay of the $i^{th}$ UE of the $s^{th}$ service on the wireless link.
+ The arrival data rate of wireless link for each UE $i$ of service $s$ is $\lambda_{u(s,i)}$
+As a result, we have $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
 Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
@@
 \begin{equation}
- T_{u(s,i)}^{RU} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}};
-\end{equation}
-
-So the mean processing delay for each UE $i$ in slice $s$ is 
-\begin{equation}
-T^{proc}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}
-\end{equation}
-Hence, $T^{tot}_{u(s,i)} \approx T^{proc}_{u(s,i)} $
+ T_{u(s,i)}^{RU} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}}.
+\end{equation}
+
+So, the mean processing delay for UE $i$ in slice $s$ is 
+\begin{equation}
+T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
+\end{equation}
+Hence, $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. {\color{red} what results in this approximation?}
 %Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
 \subsection{VNF Power}
-Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as
-$\phi_{s}$. So the system's total cost of energy of all slices can be represented as follows.
+{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$.
+Sentence has no meaning.} So the system's total cost of energy of all slices can be represented as
 \begin{equation*}
-\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s}.
+\textstyle \phi_{\text{\text{tot}}} = \sum_{s=1}^{S}\phi_{s},
 \end{equation*}
-Where, $\phi_{s}$ is obtained from below
-\begin{equation}
-\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d
+where $\phi_{s}$ is obtained from
+\begin{equation}
+\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d.
 \end{equation}
@@
 \subsection{Problem Statement}
-Suppose each slice $s$ has priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$.
-This paper aims to maximize the sum rate of all UEs with the presence of constraints as follows.
+Suppose  slice $s$ has priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$. {\color{red} explain why you introduce priority factor.}
+This paper aims to maximize the sum rate of all UEs with the presence of constraints as follows. {\color{red} where did you define the objective? what is R bar?}
 \begin{subequations}\label{problem}
@@
 & C_r \leq C^{max}_r \quad \forall r, \label{c15}\\ 
-&T^{tot}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\
+&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\
 & \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
@@
 & \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
-& \phi^{tot}  \leq \phi^{max}, \label{c19} \\
+& \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
@@
 \end{subequations}
-where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association.
+\noindent where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association.
 Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association.
-Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.
-\eqref{c11}, \eqref{c12} and \eqref{c12-1}, indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
-Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and URLLC, is more than a threshold, respectively.
+Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is the matrix that shows the number of VNFs in each layer of slice.
+\eqref{c11}, \eqref{c12} and \eqref{c12-1} indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
+Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and uRLLC, is more than a threshold, respectively.
 \eqref{c15} and \eqref{c16} expressed the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
@@
 Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
-\section{Proposed Algorithm Scheme}\label{proAlg}
-In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this problem is non-convex and it is a  mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
-We applied some simplifications and used an iterative heuristic algorithm to solve the problem.
-We solve this problem in two-level iteratively until it converges \cite{ali2018joint}.
-
-In the first level, the principal purpose is to allocate adequate PRBs and the power to the UEs and allocate enough activated VNFs
-to each slice. So, at this level, we want to obtain the variables $\boldsymbol{P}, \boldsymbol{E},$ and $\boldsymbol{M}$.
+\section{Proposed Algorithm}\label{proAlg}
+In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
+We applied some simplifications and use an iterative heuristic algorithm to solve the problem.
+We solve this problem in two levels, iteratively, until it converges \cite{ali2018joint}.
+
+In the first level, the main purpose is to allocate adequate PRBs and the power to the UEs and allocate enough activated VNFs
+to each slice. So, at this level, we would like to obtain the variables $\boldsymbol{P}, \boldsymbol{E},$ and $\boldsymbol{M}$.
 Despite the simplification of the problem
@@
 to turn them into a jointly-convex problem; Afterward, we solve this problem using a conventional dual Lagrangian method. 
-In the second level, finding the optimal O-RU association ($ \boldsymbol{G}$) is concerned with the fixed parameter of power, PRB allocation, and the number of activated VNFs.   
+In the second level, finding the optimal O-RU association, $ \boldsymbol{G}$, is concerned with the fixed parameter of power, PRB allocation, and the number of activated VNFs.   
 We repeat this procedure until the algorithm converges.
@@
 
-As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in the \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
+As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
 for $\rho_{u(s,i)}^{k}$. 
-Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in the \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.
+Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.
 
 Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
-we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in the \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
+we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the uRLLC and mMTC services that have the short packet transmission.
 So, a lower bound for \eqref{eq11} is given that is a concave function.
@@
 \end{equation}
-Consider UPF, O-CU and O-DU use the processors with the same processing capability. (for simplification), so we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
-the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$).
-so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
-Moreover, the given assumption leads to have same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
-As a result of these assumption, we can assume that $M_s = M_s^u = M_s^c = M_s^d $
-Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ 
-\begin{equation}
-\begin{split}
-T^{proc}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
-T^{proc}_{s} &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
+Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability.
+We notice that it makes the formulation simpler.
+However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner.
+Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $.
+Moreover, as mentioned before,
+the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$).
+So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
+Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
+These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
+As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
+Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and 
+\begin{equation}
+\begin{split}
+T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
+                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
 \end{split}
@@
 \begin{lemma}
-In the problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as below
+
+{\color{red} add one sentence before lemma to motivate why you need this lemma. The whole part is a lemma? It is too long. Where is the proof?}
+
+In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as
 $ \forall i,\forall s$
@@
 \begin{split}
-&T^{max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
-&M_s \geq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
-\end{split}
-\end{equation}
-Also from equation \eqref{c19}, \eqref{c16-1} and \eqref{c16-3} we have
-\begin{equation}
-\alpha_s/\mu_s\leq M_s \leq \min\{M^{max}, \phi_{max}/{3\phi_s}\}
+&T^{\max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
+&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
+\end{split}
+\end{equation}
+Also from equations in \eqref{c19}, \eqref{c16-1} and \eqref{c16-3}, we have
+\begin{equation}
+\alpha_s/\mu_s\leq M_s \leq \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}
 \end{equation}
@@
 \end{lemma}
-Despite simplifying the problem \eqref{problem}, it is still non-convex and hard to be solved.
-So the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
+Despite simplifying the problem in \eqref{problem}, it is still non-convex and hard to solve.
+Therefore, the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
 Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.
@@
 \end{equation} 
-Moreover, the combination of equations \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
+Moreover, the combination of equations in \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
 \begin{equation}\label{RConstr}
 \begin{split}
-\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{min}, \lambda_{u_{(s,i)}}+1/T^s_{max}, \varpi_{u(s,i)} \}, \\
+\eta_{u_{(s,i)}}&= \max\{\mathcal{R}_{u_{(s,i)}}^{\min}, \lambda_{u_{(s,i)}}+1/T^s_{\max}, \varpi_{u(s,i)} \}, \\
 \mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
@@
 Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$, $\boldsymbol{\mathfrak{q}}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
-
-The Lagrangian function is written as follow
+The Lagrangian function is written as
 \begin{subequations}\label{lagrang}
@@
 \end{subequations}
+
+{\color{red} Motivate the lemma. separate proof and lemma}
+
 \begin{lemma}
@@
 \end{equation}
-Where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
+where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
 \begin{equation}
@@
 \end{equation}
-Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
+where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
 Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
@@
 In this part, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method.
-We consider three network slices for eMBB, URLLC, and mMTC services.
+We consider three network slices for eMBB, uRLLC, and mMTC services.
 Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this place.
@@
 packet size is equal to 20 bytes.
-The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
+The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the uRLLC  service is $\lambda  = 0.2Mbps$. 
 Also the quantization noise is assumed to be $10^{-13}$.
@@
   \hline
-    Maximum delay for URLLC &  1msec \\
+    Maximum delay for uRLLC &  1msec \\
   \hline
@@
   \hline
-   Minimum data rate for URLLC and mMTC &  2 bits/sec/Hz \\ 
+   Minimum data rate for uRLLC and mMTC &  2 bits/sec/Hz \\ 
   \hline
@@
   \hline
-    Maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]   
+    Maximum received power for eMBB and uRLLC &  33 dBm \\ [.5ex]   
   \hline
@@
 In Fig.
-\ref{fig:1} the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods.
+\ref{fig:1}, the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods.
 Suppose we have one service instance for each type of service, so we have three various services in this figure.
@@
 \end{figure}
-%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
-%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
-%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
+%Assume we have two type of services (uRLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
+%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services uRLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
+%The figure \ref{fig:2}, presented that by increasing the priority factor for uRLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
 %\begin{figure}
@@
 %    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
+%  \caption{Aggregate Throughput for mMTC and uRLLC vs. Priority of uRLLC }
 %  \label{fig:2}
 %\end{figure}
-%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
+%In figure \ref{fig:3}, the total sum rate of uRLLC and mMTC is shown vs. priority of uRLLC. It is shown that the proposed method is much better than the baseline scheme. 
 %\begin{figure}
@@
 %    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
+%  \caption{Aggregate Throughput of all services vs. Priority of uRLLC}
 %  \label{fig:3}
@@
 
-Figure \ref{fig:4}, depicts the number of activated VNF for the five different mean service times of one URLLC service vs.
+Figure \ref{fig:4}, depicts the number of activated VNF for the five different mean service times of one uRLLC service vs.
 the mean arrival time for 12 UEs.
@@
 
-Figure \ref{fig:6}, illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
+Figure \ref{fig:6}, illustrates the mean total delay of a UE in a uRLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
 It is shown that the delay is an ascending function of the mean arrival rate (when the mean service time is fixed) and the number of UEs in the service.
-In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a URLLC service is $0.5ms$.
+In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a uRLLC service is $0.5ms$.
 Also, the maximum number of PRB is considered to be 50.
- Moreover, we can see that the mean delay of a URLLC service 
+ Moreover, we can see that the mean delay of a uRLLC service 
 does not reach the maximum threshold of the delay.
-%Moreover, we can see that the mean delay of a URLLC service increases almost linearly with the mean arrival rate of the packet transmission. 
+%Moreover, we can see that the mean delay of a uRLLC service increases almost linearly with the mean arrival rate of the packet transmission. 
 \begin{figure}
@@
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for various number of UEs}
+  \caption{Mean Total Delay of a uRLLC Service vs. the Mean Arrival Rate of a UE in the Service for various number of UEs}
   \label{fig:6}
 \end{figure}
-Figure \ref{fig:7} is the same as figure \ref{fig:6} that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
+Figure \ref{fig:7} is the same as figure \ref{fig:6} that presented the mean total delay of a UE in a uRLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
 As you can see, the proposed method (IABV) outperforms the other scenarios.
@@
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for different methods}
+  \caption{Mean Total Delay of a uRLLC Service vs. the Mean Arrival Rate of a UE in the Service for different methods}
   \label{fig:7}
@@
 In figure \ref{fig:12}, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
-proposed algorithm (IABV) and the optimal method for URLLC service for the low interference.
+proposed algorithm (IABV) and the optimal method for uRLLC service for the low interference.
 The minimum data rate is 5bits/sec/Hz for each UE and the maximum delay is $0.1$ms.
@@
 \section{Conclusion}\label{conc}
-This paper proposed the downlink of the O-RAN system using network slicing for different 5G services, i.e., eMBB, mMTC, and URLLC.
-The isolation of various services, i.e., eMBB, mMTC, and URLLC in the O-DU, the O-CU, and the UPF, is accomplished.
+This paper proposed the downlink of the O-RAN system using network slicing for different 5G services, i.e., eMBB, mMTC, and uRLLC.
+The isolation of various services, i.e., eMBB, mMTC, and uRLLC in the O-DU, the O-CU, and the UPF, is accomplished.
 Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.
@@
 In addition, the feasible region is discussed, and the FA algorithm is introduced to check the feasibility of the initial values.
-Also, we assume distinct scenarios for each service, i.e., eMBB, mMTC, and, URLLC based on their requirement QoS.
+Also, we assume distinct scenarios for each service, i.e., eMBB, mMTC, and, uRLLC based on their requirement QoS.
 Simulation results show that the proposed method (IABV) achieved a $18.6\%$ higher data rate than the baseline scheme.

### 2021-09-25 Latex/journal_v1/V6/pr.tex
add paper last version

--- 2021-09-22 Latex/journal_v1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (1)/pr.tex
@@
 {\color{red} explain pre-allocated more}
-Therefore, there are $S$ pre-allocated slices serving these $S$ services;
-Each pre-allocated slice contains reserved VNFs for the MAC/RLC functions in the O-DU logical node, the PDCP/SDAP functions in the O-CU-UP, and the UPF nodes. 
- There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (uRLLC), and $S_3$ slices for the third service type (mMTC).
+Therefore, there are $S$ pre-allocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (uRLLC), and $S_3$ slices for the third service type (mMTC).
 So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.
@@
 Based on the application and QoS request, UE may be admitted and allocated to the resources.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of 
-%pre-allocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs),
- $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  pre-allocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.
 
@@
 Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
-Assume the mean arrival data rate of the UPF layer for the slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$).
+Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$).
 so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,
@@
 
-Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
+Assume UE $i$ in slice $s$, associated with O-RU $r$, is allocated to PRB $k$  (i.e., $e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition
 \begin{equation}\label{deriveP}
@@
 \dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
- &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0\\
-\end{split}
-\end{equation}
-where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
+ &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0,\\
+\end{split}
+\end{equation}
+where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follows:
 \begin{equation}
@@
   \begin{cases}
-      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S\\
-      0 & \text{otherwise}
+      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S, \\
+      0 & \text{otherwise,}
     \end{cases}
 \end{equation}
-Where, $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
+where $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
  \end{lemma}
-Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$.
-Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
+Thus, the user in slice $s$ that has  the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to PRB $k$.
+Since just one PRB can be allocated to a UE between those UEs (regardless of the services), that is associated to the same O-RU.
 The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
@@
 \subsection{Iterative Proposed Algorithm}
-In sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
+In Sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
 Here, the iterative algorithm for the whole problem is demonstrated.
@@
 \section{Numerical Results and The Feasible Region}\label{NE}
-In this section, firstly we describe the initial points and the comparison algorithms.
-Then we talk about the feasible region in our system. 
-Afterward, we illustrated the numerical results.
+In this section, firstly, we describe the initial points and the comparison algorithms.
+Then, we talk about the feasible region of our system model. Afterward, we illustrate the numerical results.
+
 \subsection{The initial Points and The Comparison Algorithms}
@@
 We consider three network slices for eMBB, uRLLC, and mMTC services.
-Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this place.
+Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in Figure \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
 \begin{figure}
@@
 \end{figure}
-Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.
-Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
-Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution
-and it is the Rayleigh fading channel between the UE and O-RU.
-We consider 25 PRBs are used in the network and the
-packet size is equal to 20 bytes.
+Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
+Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
+We consider 25 PRBs are used in the network and the packet size is equal to 20 bytes.
 The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the uRLLC  service is $\lambda  = 0.2Mbps$. 
-Also the quantization noise is assumed to be $10^{-13}$.
+Also, the quantization noise is assumed to be $10^{-13}$.
 Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.
-
-The other parameters of these simulations are depicted in Table \ref{table:1a}.
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a}.
 \begin{table}
- \caption {Simulation Parameter} \label{table:1a}
+ \caption {Simulation Parameters} \label{table:1a}
  \begin{center}
-  \begin{tabular}{||c c ||}
+  \begin{tabular}{||c | c ||}
   \hline
@@
 Finding a feasible initial value is almost tricky.
-To overcome this challenge, we use a fast method that we talk about it in the \ref{fr}.
-If the fast method converged and has a feasible solution, so our algorithm (IABV) can be converged too.
+To overcome this challenge, we use a fast method that is discussed in \ref{fr}.
+If the fast method converges and has a feasible solution, so our algorithm (IABV) can be converged too.
 
 Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
- The first one is a baseline scheme, which used random PRB allocation. The association of O-RU is only based on distance. Also, the number of activated VNF for each slice is fixed. The optimal power
- is obtained using the CVX of Matlab, which used the successive convex approximation (SCA) method.
-
+ The first one is a baseline scheme, which uses random PRB allocation.
+The association of O-RU is carried out based on distance.
+Also, the number of activated VNFs for each slice is fixed.
+The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method.
 The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}.
@@
 Applying the correct initial point to make the system feasible is a significant step in our work.
-During the simulation, it can be noted that sometimes the algorithm does not converge for some of the iterations with fixed initial values.
+During the simulations, it can be noted that sometimes the algorithm does not converge for some of the iterations with fixed initial values.
 To solve this problem, we investigated the non-converging and converging simulation for models with fixed initial parameters (such as number of UEs, the threshold of power and rate,...
@@
 One solution is to eliminate UEs who undermine system convergence.
-For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interferences.
+For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interference.
 Another solution is to remove the simulations in the mont-Carlo that do not converge.
@@
 the proposed algorithm (IABV). 
-If the conditions \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
-The FA algorithm is depicted as algorithm \ref{alg3}.
+If the conditions in \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
+The FA algorithm is represented in Algorithm \ref{alg3}.
+
  \begin{algorithm}
-\caption{Fast Algorithm to Check the Convergence (FA)}\label{alg3}
+\caption{Fast Algorithm (FA) to Check the Convergence}\label{alg3}
 \begin{algorithmic}[1]
-\State Assume the number of UEs is $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_s}1$
-\State Assume the number of PRBs is $K$
-\State Assume $d_{r,u(s,i)}$ is the distance from the $r^{th}$ O-RU to the UE i in slice s
+\State The number of UEs: $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_s}1$
+\State The number of PRBs: $K$
+\State the distance from the $r^{th}$ O-RU to the UE i in slice $s$: $d_{r,u(s,i)}$ 
 \State Set count = 0 
@@
 \State $e_{r^*,u(s,i)}^{K} = 1 $
-\State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} $
+\State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
 \Else 
-\State $e_{r^*,u(s,i)}^{temp} = 1 \quad \forall r$ 
-\State Set $p_{r^*,u(s,i)}^{temp} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} $
+\State $e_{r^*,u(s,i)}^{\text{temp}} = 1 \quad \forall r$ 
+\State Set $p_{r^*,u(s,i)}^{\text{temp}} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
 \EndIf
@@
 \end{algorithm}
+
 The complexity order of this algorithm is $O(R\times \mathfrak{N})$ which is remarkably lower than the complexity order of the IABV method.
-In the algorithm FA, the O-RU association is based on the distance of the UE to the O-RU. 
+In the FA algorithm, the O-RU association is based on the distance of the UE to the O-RU. 
 Each UE is associated with the nearest O-RU.
-Also, the power of each UE is set to be the minimum of the maximum power of each UE and the maximum power of each O-RU divided by the total number of UEs ($\min\{P_s^{max}, P_r^{max}/\mathfrak{N}\}$).
-Moreover, the allocation of PRBs to UEs is based on dividing the UE number by the total number of PRBs.
-If the number of UE is more than the PRBs, each UE is given exactly one PRB without interference. Otherwise, the amount of interference will not be high but more than one UE will use same PRBs.
+Also, the power of each UE is set to be the minimum of the maximum power of each UE and the maximum power of each O-RU divided by the total number of UEs ($\min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\}$).
+Moreover, the allocation of PRBs to UEs is based on dividing the number of UEs by the total number of PRBs.
+If the number of UEs is more than the PRBs, each UE is given exactly one PRB without interference. Otherwise, the amount of interference will not be high but more than one UE will use same PRBs.
 \subsection{Numerical Results}
@@
 Suppose we have one service instance for each type of service, so we have three various services in this figure.
-Also We have between 6 and 48 UEs in the system.
-Here, we did not consider the priority. The figure presented that the proposed method (IABV) is $18.6\%$ higher than the baseline scheme.
+Also, we have between 6 to 48 UEs in the system.
+Here, we did not consider the priority. The figure presented that the proposed method, IABV, is $18.6\%$ higher than the baseline scheme.
 As the number of UEs increases in each service, the aggregated throughput initially increases.
@@
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput vs. Number of UE in each Service In the Presence of Three Services}
+  \caption{Aggregate throughput vs. number of UEs for each service in the presence of three services}
   \label{fig:1}
@@
 
-Figure \ref{fig:4}, depicts the number of activated VNF for the five different mean service times of one uRLLC service vs.
+Figure \ref{fig:4} depicts the number of activated VNFs for five different mean service times of one uRLLC service vs.
 the mean arrival time for 12 UEs.
-This figure presented that as the mean arrival rate increases, the number of activated VNF increases.
-Moreover, the number of activated VNFs decreased when the mean service rate increases.
+This figure presents that as the mean arrival rate increases, the number of activated VNF increases.
+Moreover, the number of activated VNFs decreases when the mean service rate increases.
 
@@
 
-Figure \ref{fig:6}, illustrates the mean total delay of a UE in a uRLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
+Figure \ref{fig:6} illustrates the mean total delay of a UE in a uRLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
 It is shown that the delay is an ascending function of the mean arrival rate (when the mean service time is fixed) and the number of UEs in the service.

### 2021-09-29 Latex/journal_v1/V7/pr.tex
add paper

--- 2021-01-04 Latex/journal_v1/V2/pr.tex
@@
 
-\begin{figure}
-  \centering
-    \includegraphics[scale = 0.4]{draw1.pdf}
-  \caption{Network sliced ORAN system}
-  \label{fig:c11}
-\end{figure}
-
 In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
@@
 \begin{equation}\label{eq2}
-\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
+\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0},
 \end{equation} 
@@
 Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocate to $s^{th}$ slice or not. 
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
-\begin{equation}
-\begin{split}
-I_{r,u(s,i)}^{k} &=
- \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,i)}^{k} g_{u(s,i)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
-&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
-\end{split}
-\end{equation}
-where $\gamma_{1} = e^{k}_{r,u(s,i)}e^{k}_{r',u(s,l)}a_{u(s,i)}a_{u(s,l)}$
-and $\gamma_{2} = e^{k}_{r,u(s,i)}e^{k}_{r',u(n,l)}a_{u(s,i)}a_{u(y,l)}$.
-Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
+Also, $BN_0$ denotes the power of Gaussian additive noise.
+Also, $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
 $e^{k}_{r,u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
@@
 The propagation delay is the time takes for a signal to reach to its destination.
-So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
+So it has a constant value based on the length of fiber link ($T = L/C_{r}$, where $L$ is the length of link and $C_{r}$ is the capacity of the link).
 Here we assume the value of propagation delay is negligible compared to the rest.
@@
 Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is allocated the resources to the VNFs of $s^{th}$ slice or not.
+\subsection{Power of the O-RU and the Fronthaul Capacity}
+Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. From \eqref{eq2}, we have,
+\begin{equation}\label{pr}
+P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
+\end{equation}
+Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
+%\cite{simeone2016cloud, 1111}
+\begin{equation}\label{cr}
+C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
+\end{equation}
+where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
 \subsection{Problem Statement}
 %In this system, the goal is to minimize the cost of the system.
-Power of each O-RU is obtained as below
-\begin{equation}
-P_r =  \sum_{s=1}^{S} \sum_{i=1}^{U_v} \sum_{k=1}^{K_s}p_{r,u(s,i)}^{k}a_{u(s,i)} e^{k}_{r,u(s,i)}g_{u(s,i)}^r.
-\end{equation}
 %The total power cost of O-RUs for transmitting data to UE is depicted as follow

### 2021-10-01 Latex/journal_v1/research plan/main.tex
add research plan

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Imperial College London
% UKRI Centre for Doctoral Training in AI for Healthcare
% https://ai4health.io
%
% LaTeX Template
% Version 1.0 (22/10/19) Aldo Faisal
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\input{ai4health_header}
\begin{document}
\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here
\setlength{\topmargin}{0in}
\center % Center everything on the page

 \begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\hspace*{-0.5cm}
%\includegraphics[scale=0.14]{imperial.png}\\
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.5\textwidth}
\begin{flushright} \large
\hspace*{2cm}
%\includegraphics[scale=0.20]{logo.png}\\
\end{flushright}
\end{minipage}\\[1cm]
%----------------------------------------------------------------------------------------
%	HEADING SECTIONS
%----------------------------------------------------------------------------------------

\textsc{\Large resource allocation in open ran system using network slicing}\\[0.5cm] % Major
\LARGE \textsc{University of Tehran} \\[1.5cm] 
% Name of your heading such as course name
\textsc{\large }\\[0.5cm] % Minor heading such as course title

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\HRule \\[0.4cm]
{ \huge \bfseries Research Planning Report}\\[0.4cm] % Title of your document
\HRule \\[1cm]

%----------------------------------------------------------------------------------------
%	AUTHOR SECTION
%----------------------------------------------------------------------------------------

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Student:}\\
Mojdeh Karbalaee Motalleb \\ % Your name, if you are medically qualified please use "Last Name, M.D."
\emph{Email Address:}\\
mojdeh.karbalaee@ut.ac.ir
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.5\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
Dr. Onel Lopez \\% Supervisor's Name
%Supervisor Department(s)\\
%[0.5cm] \emph{Healthcare Supervisor} \\
%Fist name \textsc{Last name} % Supervisor's Name
%Supervisor Department(s)  or NHS Trust+section\\
\emph{Department: } \\
Electrical Engineering
% \textsc{Add name here} % Supervisor's Name
% Supervisor Department(s) or NHS Trust+section
\end{flushright}
\end{minipage}\\[1cm]

%----------------------------------------------------------------------------------------
%	DATE SECTION
%----------------------------------------------------------------------------------------

{\large \today}\\[0.5cm] % Date, change the \today to a set date if you want to be precise

\vfill % Fill the rest of the page with whitespace

\end{titlepage}

%\renewcommand{\abstractname}{Abstract}
\begin{abstract}
%% 100 words
\emph{In this project }
\end{abstract}

\section{Introduction \& Literature review}
\emph{Give background and motivation for your work. Explain  knowledge needed. Show its scientific and healthcare need.
Define a set of clear questions and approaches to answering them. Highlight their originality and/or significance. Explain how they adds to, develop (or challenges) existing literature in the field. Note, this comprises both AI questions and Healthcare questions.}
\subsection{AI literature}
\subsection{Healthcare literature}
\section{PhD goal}
\emph{Explain the main question you want to answer in terms of AI technology developed and healthcare challenge addressed. Connect it with current state of research and show its importance in this context.
Show what you want to achieve. Explain your contribution to the subject.}

\section{Methodology}
\emph{Specify methodology and techniques which will be used for your research. Be specific this will allow the reviewers to understand how well thought out and achievable your plan is.}
\section{Summarise the work done since the start of the PhD.}
\emph{Show interim results, if any.}
\section{Program of work}
\emph{This is your list, description and schedule of activities to achieve in PhD goal . Include Publication \& conference deadlines as expected, i.e. Give an overview of subjects or steps of your work you intend to publish,  suggest some meetings or conferences you plan to attend in order to present your research.}

\section{Data, Infrastructure or Software needs}
\emph{Make a list of facilities or infrastructure, including data and software you will need to complete your research. Explain how it is or will be made available. Assess the \textbf{Data Readiness Level} of all needed data sources.}

\section{Planned Impact}
\emph{Assuming that you achieve your PhD goals, what is the impact that your proejct will achieve. Assess your project's planned impact in terms of the PICO (population, intervention, comparator and outcome) framework.}

\subsection*{Example: Diagnosis}
\paragraph{Population}: To which populations of patients would the test be applicable? How can they be best described? Are there subgroups that need to be considered?

\paragraph{Intervention} (index test[s]): The test or test strategy being evaluated.

\paragraph{Comparator} The test with which the index test(s) is/are being compared, usually the reference standard (the test that is considered to be the best available method to establish the presence or absence of the condition of interest - this may not be the one that is routinely used in practice).

Target condition: The disease, disease stage or subtype of disease that the index test(s) and the reference standard are being used to establish.

\paragraph{Outcome} The diagnostic accuracy of the test or test strategy for detecting the target condition. This is usually reported as test parameters, such as sensitivity, specificity, predictive values, likelihood ratios, or - where multiple cut-off values are used - a receiver operating characteristic (ROC) curve.

\subsection*{Example: Intervention}

\paragraph{Population} Which populations of patients are we interested in? How can they be best described? Are there subgroups that need to be considered?

\paragraph{Intervention} Which intervention, treatment or approach should be used?

\paragraph{Comparators} What is/are the main alternative(s) to compare with the intervention being considered?

\paragraph{Outcome} What is really important for the patient? Which outcomes should be considered? Examples include intermediate or short-term outcomes; mortality; morbidity and quality of life; treatment complications; adverse effects; rates of relapse; late morbidity and re-admission; return to work, physical and social functioning; resource use.

%**********************************************%
\newpage
\addcontentsline{toc}{section}{References}
\begin{thebibliography}{9}
\bibitem{latexcompanion} 
Michel Goossens, Frank Mittelbach, and Alexander Samarin. 
\textit{The \LaTeX\ Companion}. 
Addison-Wesley, Reading, Massachusetts, 1993.

\bibitem{einstein} 
Albert Einstein. 
\textit{Zur Elektrodynamik bewegter K{\"o}rper}. (German) 
[\textit{On the electrodynamics of moving bodies}]. 
Annalen der Physik, 322(10):891-921, 1905.

\bibitem{knuthwebsite} 
Knuth: Computers and Typesetting,
\\\texttt{http://www-cs-faculty.stanford.edu/\~{}uno/abcde.html}

\end{thebibliography}

\end{document}

### 2021-10-02 Latex/journal_v1/LatsVersion7/pr.tex

--- 2021-09-25 Latex/journal_v1/V6/pr.tex
@@
 O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services including enhanced mobile broadband (eMBB), ultra-reliable low latency communications (uRLLC) and massive Machine Type Communications (mMTC) services.
+In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services including enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
 Deploying network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
@@
 Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 
-Three types of services are introduced for 5th generation celluar networks, namely, enhanced mobile broadband (eMBB), ultra-reliable low latency communications (uRLLC), and massive Machine Type Communications (mMTC) services.
+Three types of services are introduced for 5th generation celluar networks, namely, enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services.
 Each type of service requires a particular slice of network based on its QoS.
 eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and throughout coverage.
-uRLLC requires low latency  and high reliability. uRLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
+URLLC requires low latency  and high reliability. URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
 mMTC consists of a vast number of low power internet of things (IoT) devices transmitting small payloads to a typical receiver.
@@
 
-Multiplexing eMBB and uRLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
-In \cite{setayesh2020joint,yang2020should}, the problem of resource allocation in the coexistence of uRLLC and eMBB services is considered based on their QoS. 
-In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and uRLLC services is formulated and solved by deep reinforcement learning.
- In \cite{saggese2021power}, the problem of power minimization for uRLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
- In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and uRLLC services.
+Multiplexing eMBB and URLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
+In \cite{setayesh2020joint,yang2020should}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
+In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
+ In \cite{saggese2021power}, the problem of power minimization for URLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
+ In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and URLLC services.
 The system guarantees the latency, the service rate, and the maintenance of reliability.
@@
 \begin{itemize}
-\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and uRLLC.
+\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and URLLC.
 The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
@@
 We consider the limited fronthaul capacity and obtain the power and the capacity of each O-RU. We model the interference of neighboring O-RU and formulate the actual throughput
-for different types of services. We also model the throughput of uRLLC and mMTC based on their short packet transmission.
+for different types of services. We also model the throughput of URLLC and mMTC based on their short packet transmission.
 \item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
@@
 \subsection{System Model}
-There are three service types including mMTC, eMBB, and uRLLC, which support different applications.
-There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and uRLLC service types, respectively and we have $S = S_1 + S_2 + S_3$.
-{\color{red} explain pre-allocated more}
-Therefore, there are $S$ pre-allocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (uRLLC), and $S_3$ slices for the third service type (mMTC).
+There are three service types including mMTC, eMBB, and URLLC, which support different applications.
+There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and URLLC service types, respectively and we have $S = S_1 + S_2 + S_3$.
+%{\color{red} explain pre-allocated more}
+Therefore, there are $S$ pre-allocated slices serving these $S$ services;
+Each pre-allocated slice contains reserved VNFs for the three logical nodes:
+\begin{itemize}
+\item The MAC/RLC functions in the O-DU logical node
+\item The PDCP/SDAP functions in the O-CU-UP logical node
+\item The UPF logical node
+\end{itemize}
+
+ There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
 So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.
@@
 Based on the application and QoS request, UE may be admitted and allocated to the resources.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  pre-allocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.
-
-All $K$ PRBs can be assigned to all UE in each service.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.
+
+Assume we have $K$ physical resource blocks (PRBs) in this system.
+All $K$ PRBs can be assigned to all UEs in each service.
 Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.
@@
 Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
-{\color{red} use paranthesis in the following equation to clear +}
+%{\color{red} use paranthesis in the following equation to clear +}
 \begin{equation}\label{eqI}
 \begin{split}
-I_{r,u(s,i)}^{k} &=
- \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
-&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
+&I_{r,u(s,i)}^{k} =\\
+ &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
+&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
 &+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
@@
 \end{equation}
-{\color{red} $\gamma_1$ is constant used instead of variable. }
-where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
-$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
-($\gamma_1$ and $\gamma_2$ are two variales.
+%{\color{red} $\gamma_1$ is constant used instead of variable. }
+%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
+where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
+%($\gamma_1$ and $\gamma_2$ are two variales.
 You  define on variable here.)
@@
 $\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of RU $r$ to UE $i$ in slice $s_1$.
-Since the blocklength in uRLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (uRLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
+Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
 So, for the short packet transmission, the achievable data rate is approximated from following \cite{setayesh2020joint},
@@
 \end{equation}
-where $j \in \{2,3\}$. Also we have {\color{red} check paranthesis. }
+where $j \in \{2,3\}$. Also we have %{\color{red} check paranthesis. }
 \begin{equation}\label{shortPacket}
- \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}),
-\end{equation}
-{\color{red} what is transmission probability? }
-where $\epsilon$ is the transmission probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
+ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}},
+\end{equation}
+%{\color{red} what is transmission probability? }
+where $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
 $\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
@@
 \subsection{Power of the O-RU and the Fronthaul Capacity}
-Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. From \eqref{eq2}, we have, {\color{red} is this the sum rate of all users?}
+Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to all the UEs served by it. From \eqref{eq2}, the power of each O-RU $r$ is obtained as follows, 
+%{\color{red} is this the sum rate of all users?}
 \begin{equation}\label{pr}
@@
 \end{equation}
-{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
+%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
 %T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
-The total delay, $T^{\text{\text{tot}}}$, is the sum of the processing delay, $T^{\text{proc}}$, the transmission delay, $T^{tr}$, and the propagation delay, $T^{\text{proc}}$. 
+The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the propagation delay ($T^{\text{pro}}$). 
 The propagation delay is the time takes for a signal to reach its destination.
-So, it has a constant value based on the length of the fiber link ($T = L/c$, where $L$ is the length of the link and c is the speed of signal).
-The total propagation delay, $T^{\text{proc}}$, is the sum of the propagation delay in the fronthaul $T^{fr,p}$, the midhaul $T^{\text{mid},p}$, and the backhaul $T^{b,p}$.
+It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the capacity of the link).
+The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
 Also, the transmission delay is the amount of time required to push all the packets into the fiber link.
-$T = \frac{\alpha}{R}$, where $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of each link which is constant in this model.
+Moreover, it can formulated as 
+$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the sum-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean arrival data rate of each link.
 So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
-Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
+In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we ignore the other two delays for simplification;
+So, we assume that the total delay is approximate to the processing delay.
+%Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
 \begin{equation}
@@
 \end{equation}
-Hence, $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. {\color{red} what results in this approximation?}
+Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. %{\color{red} what results in this approximation?}
 %Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
 \subsection{VNF Power}
-{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$.
-Sentence has no meaning.} So the system's total cost of energy of all slices can be represented as
+%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} 
+Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.
+
+So the system's total cost of energy of all the slices can be represented as
 \begin{equation*}
@@
 \subsection{Problem Statement}
-Suppose  slice $s$ has priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$. {\color{red} explain why you introduce priority factor.}
-This paper aims to maximize the sum rate of all UEs with the presence of constraints as follows. {\color{red} where did you define the objective? what is R bar?}
+Suppose slice $s$ (which is assigned to service s) has the priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$.
+The priority factor of each slice is obtained according to the service level agreement (SLA) of that service to have a fairness in the system. 
+%{\color{red} explain why you introduce priority factor.}
+This paper aims to maximize the sum-rate of all UEs with the presence of constraints as follows. %{\color{red} where did you define the objective? what is R bar?}
 \begin{subequations}\label{problem}
@@
 \end{subequations}
-\noindent where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association.
+\noindent where $\bar{\mathcal{R}}_{u_{(s,i)}}, \:\:\forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
+In addition, $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association.
 Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association.
@@
 \eqref{c11}, \eqref{c12} and \eqref{c12-1} indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
-Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and uRLLC, is more than a threshold, respectively.
+Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and URLLC, is more than a threshold, respectively.
 \eqref{c15} and \eqref{c16} expressed the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
@@
 Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
-we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the uRLLC and mMTC services that have the short packet transmission.
+we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
 So, a lower bound for \eqref{eq11} is given that is a concave function.
@@
 \end{equation}
+In the following, we define a lemma to find the upper and lower bound for the optimal number of VNFs based on the achievable rates.
+Afterward, we obtain the formula to attain the optimal number of VNFs.
 \begin{lemma}
-
-{\color{red} add one sentence before lemma to motivate why you need this lemma. The whole part is a lemma? It is too long. Where is the proof?}
-
+The optimal number of VNFs in each slice s can be achieved by the 
+$M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s$.
+where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
+
+\end{lemma}
+%{\color{red} add one sentence before lemma to motivate why you need this lemma. The whole part is a lemma? It is too long. Where is the proof?}
+\begin{proof}
 In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as
@@
 \end{equation}
-\end{lemma}
+\end{proof}
+
 Despite simplifying the problem in \eqref{problem}, it is still non-convex and hard to solve.
@@
 
-{\color{red} Motivate the lemma. separate proof and lemma}
+%{\color{red} Motivate the lemma. separate proof and lemma}
 
@@
 The derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{P}$ and $\boldsymbol{E}$ give the Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal value of these two variables \cite{lee2018dynamic,ali2018joint}.
-
+\end{lemma}
+\begin{proof}
 Assume UE $i$ in slice $s$, associated with O-RU $r$, is allocated to PRB $k$  (i.e., $e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition
@@
 where $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
- \end{lemma}
+ \end{proof}
 Thus, the user in slice $s$ that has  the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to PRB $k$.
@@
 In this part, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method.
-We consider three network slices for eMBB, uRLLC, and mMTC services.
+We consider three network slices for eMBB, URLLC, and mMTC services.
 Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in Figure \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
@@
 We consider 25 PRBs are used in the network and the packet size is equal to 20 bytes.
-The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the uRLLC  service is $\lambda  = 0.2Mbps$. 
+The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
 Also, the quantization noise is assumed to be $10^{-13}$.
@@
   \hline
-    Maximum delay for uRLLC &  1msec \\
+    Maximum delay for URLLC &  1msec \\
   \hline
@@
   \hline
-   Minimum data rate for uRLLC and mMTC &  2 bits/sec/Hz \\ 
+   Minimum data rate for URLLC and mMTC &  2 bits/sec/Hz \\ 
   \hline
@@
   \hline
-    Maximum received power for eMBB and uRLLC &  33 dBm \\ [.5ex]   
+    Maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]   
   \hline
@@
 Also, we have between 6 to 48 UEs in the system.
-Here, we did not consider the priority. The figure presented that the proposed method, IABV, is $18.6\%$ higher than the baseline scheme.
+Here, we did not consider the priority. The figure presented that the proposed method, IABV, is $18.6\%$ higher throughput than the baseline scheme.
 As the number of UEs increases in each service, the aggregated throughput initially increases.
@@
 \end{figure}
-%Assume we have two type of services (uRLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
-%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services uRLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
-%The figure \ref{fig:2}, presented that by increasing the priority factor for uRLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
+%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
+%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
+%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
 %\begin{figure}
 %  \centering 
-%    \includegraphics[scale = 0.4]{mmtcurllc.eps}
+%    \includegraphics[scale = 0.4]{mmtcURLLC.eps}
 %    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
 %    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput for mMTC and uRLLC vs. Priority of uRLLC }
+%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
 %  \label{fig:2}
 %\end{figure}
-%In figure \ref{fig:3}, the total sum rate of uRLLC and mMTC is shown vs. priority of uRLLC. It is shown that the proposed method is much better than the baseline scheme. 
+%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
 %\begin{figure}
@@
 %    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput of all services vs. Priority of uRLLC}
+%  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
 %  \label{fig:3}
@@
 
-Figure \ref{fig:4} depicts the number of activated VNFs for five different mean service times of one uRLLC service vs.
+Figure \ref{fig:4} depicts the number of activated VNFs for five different mean service times of one URLLC service vs.
 the mean arrival time for 12 UEs.
@@
 
-Figure \ref{fig:6} illustrates the mean total delay of a UE in a uRLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
+Figure \ref{fig:6} illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
 It is shown that the delay is an ascending function of the mean arrival rate (when the mean service time is fixed) and the number of UEs in the service.
-In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a uRLLC service is $0.5ms$.
+In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a URLLC service is $0.5ms$.
 Also, the maximum number of PRB is considered to be 50.
- Moreover, we can see that the mean delay of a uRLLC service 
+ Moreover, we can see that the mean delay of a URLLC service 
 does not reach the maximum threshold of the delay.
-%Moreover, we can see that the mean delay of a uRLLC service increases almost linearly with the mean arrival rate of the packet transmission. 
+%Moreover, we can see that the mean delay of a URLLC service increases almost linearly with the mean arrival rate of the packet transmission. 
 \begin{figure}
@@
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Mean Total Delay of a uRLLC Service vs. the Mean Arrival Rate of a UE in the Service for various number of UEs}
+  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for various number of UEs}
   \label{fig:6}
 \end{figure}
-Figure \ref{fig:7} is the same as figure \ref{fig:6} that presented the mean total delay of a UE in a uRLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
+Figure \ref{fig:7} is the same as figure \ref{fig:6} that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
 As you can see, the proposed method (IABV) outperforms the other scenarios.
@@
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Mean Total Delay of a uRLLC Service vs. the Mean Arrival Rate of a UE in the Service for different methods}
+  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for different methods}
   \label{fig:7}
@@
 In figure \ref{fig:12}, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
-proposed algorithm (IABV) and the optimal method for uRLLC service for the low interference.
+proposed algorithm (IABV) and the optimal method for URLLC service for the low interference.
 The minimum data rate is 5bits/sec/Hz for each UE and the maximum delay is $0.1$ms.
@@
 \end{figure}
+
 \section{Conclusion}\label{conc}
-This paper proposed the downlink of the O-RAN system using network slicing for different 5G services, i.e., eMBB, mMTC, and uRLLC.
-The isolation of various services, i.e., eMBB, mMTC, and uRLLC in the O-DU, the O-CU, and the UPF, is accomplished.
+In this  paper, we modeled the downlink of the O-RAN system using network slicing for different 5G services, i.e., eMBB, mMTC, and URLLC.
+The isolation of various services, i.e., eMBB, mMTC, and URLLC in the O-DU, the O-CU, and the UPF, is accomplished.
 Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.
 The limited fronthaul capacity and the mean end-to-end delay for each service are considered.
-The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
-In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
-In the second step, the O-RU association is acquired.
-The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
+The problem is mixed-integer non-linear programming that is solved by a two-step iterative algorithm.
+In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then, we obtained PRB association and power allocation using the Lagrangian method.
+In the second step, the O-RU association is carried out.
+The performance of our proposed method (i.e., IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
 In addition, the feasible region is discussed, and the FA algorithm is introduced to check the feasibility of the initial values.
-Also, we assume distinct scenarios for each service, i.e., eMBB, mMTC, and, uRLLC based on their requirement QoS.
-Simulation results show that the proposed method (IABV) achieved a $18.6\%$ higher data rate than the baseline scheme.
+Also, we assume distinct scenarios for each service, i.e., eMBB, mMTC, and, URLLC based on their requirement QoS.
+Simulation results show that the proposed method (i.e., IABV) achieves $18.6\%$ higher data rate than the baseline scheme.
 Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.

### 2021-10-02 Latex/journal_v1/research plan/ai4health_header.tex

\documentclass[a4paper,12pt]{article}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[toc,page]{appendix}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }
 \usepackage{hyperref}
 \hypersetup{
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={My title},    % title
    pdfauthor={Author},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1, key2, key3}, % list of keywords
    pdfnewwindow=true,      % links in new PDF window
    colorlinks=false,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

### 2021-10-03 Journal1/IEEE-TCOM-Latex-Template (1)/IEEE_TCOM.tex
add journal 30 page

%% bare_jrnl.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal,draftcls,onecolumn,12pt,twoside]{IEEEtranTCOM}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

\normalsize

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
% This package may be useful when used in conjunction with IEEEtran.cls'
% captionsoff option. Some IEEE journals/societies require that submissions
% have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.3.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% For subfigure.sty:
% \let\MYorigsubfigure\subfigure
% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat/subfig command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Bare Demo of IEEEtran.cls for TCOM}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
        John~Doe,~\IEEEmembership{Fellow,~OSA,}
        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\thanks{M. Shell is with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{TCOM version based on Michael Shell's bare{\textunderscore}jrnl.tex version 1.3.}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{IEEE Transactions on Communications}%
{Submitted paper}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2007 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
for IEEE journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{Subsection Heading Here}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsubsection{Subsubsection Heading Here}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular whiIEEEtranch is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.

\section{Conclusion}
The conclusion goes here.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtranTCOM}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2021-10-03 Journal1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (1) (1)/pr.tex
add journal 30 page

--- 2021-10-02 Latex/journal_v1/LatsVersion7/pr.tex
@@
  %\pdfoutput=1
-\documentclass[conference]{IEEEtran}
+%\documentclass[conference]{IEEEtran}
+\documentclass[journal,draftcls,onecolumn,12pt,twoside]{IEEEtranTCOM}
+\normalsize
 \IEEEoverridecommandlockouts
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{setspace}
 \usepackage[T1]{fontenc}
 \usepackage{cite}
-%\usepackage{caption}
+\usepackage{caption}
+\usepackage{algcompatible}
 %\usepackage{subcaption}
@@
 \setlength{\columnsep}{11mm}
+\captionsetup{font=footnotesize}
+\captionsetup[figure]{font=small}
+\newcommand{\abstractnamefont}{\normalfont\small\bfseries}
+\newcommand{\abstracttextfont}{\normalfont\small}
+\setlength{\belowcaptionskip}{-25pt}
+\setlength{\dbltextfloatsep}{-20pt}
 \begin{document}
@@
 }
-
-\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
-\IEEEauthorblockA{\textit{School of ECE} \\
-\textit{Tehran University}\\
-Tehran, Iran \\
-mojdeh.karbalaee@ut.ac.ir}
-\and
-\IEEEauthorblockN{ Vahid Shah-Mansouri}
-\IEEEauthorblockA{\textit{School of ECE} \\
-\textit{Tehran University}\\
-Tehran, Iran \\
-vmansouri@ut.ac.ir}
-\and
-\IEEEauthorblockN{ Saeedeh Parsaeefard}
-\IEEEauthorblockA{\textit{Department of ECE} \\
-\textit{University of Toronto}\\
-Toronto, Canada \\
-saeede.parsaeefard@gmail.com}
-}
+%%%%%%%%%%%%%%%
+%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
+%\IEEEauthorblockA{\textit{School of ECE} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%mojdeh.karbalaee@ut.ac.ir}
+%\and
+%\IEEEauthorblockN{ Vahid Shah-Mansouri}
+%\IEEEauthorblockA{\textit{School of ECE} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%vmansouri@ut.ac.ir}
+%\and
+%\IEEEauthorblockN{ Saeedeh Parsaeefard}
+%\IEEEauthorblockA{\textit{Department of ECE} \\
+%\textit{University of Toronto}\\
+%Toronto, Canada \\
+%saeede.parsaeefard@gmail.com}
+%}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %  \author{
@@
 %  }
+\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
+        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
+        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
+}
 
 \maketitle
-
+\vspace*{-6em}
 \begin{abstract}
+\vspace*{-1.5em}
 Taking advantage of virtual Radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
@@
 Also, the simulation results demonstrate less end-to-end delay for the proposed method than the FBDR and baseline scheme.
-
 \end{abstract}
-
 \begin{IEEEkeywords}
@@
 \end{IEEEkeywords}
-
 \section{Introduction} 
@@
 \subsection{Main Contributions}
-This study aims to optimize baseband resource allocation i.e., power allocation, PRB allocation, and O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+This study aims to optimize baseband resource allocation i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
 In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
@@
   \centering 
-    \includegraphics[scale = 0.7]{finalDraw.pdf}
+  \captionsetup{justification=centering}
+    \includegraphics[scale = 0.6]{finalDraw.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.
-
 Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
@@
 Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.
-
 Assume we have $K$ physical resource blocks (PRBs) in this system.
@@
 Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.
-
 In addition, there are $R$ multi-antenna O-RUs that are shared between slices.
@@
 %{\color{red} use paranthesis in the following equation to clear +}
-\begin{equation}\label{eqI}
-\begin{split}
+\begin{subequations}\label{eqI}
+\begin{alignat}{4}
 &I_{r,u(s,i)}^{k} =\\
@@
 &+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
-\end{split}
-\end{equation}
+\end{alignat}
+\end{subequations}
 %{\color{red} $\gamma_1$ is constant used instead of variable. }
@@
 So, for the short packet transmission, the achievable data rate is approximated from following \cite{setayesh2020joint},
-\begin{equation}\label{eq11}
-\begin{split}
+\begin{subequations}\label{eq11}
+\begin{alignat}{4}
 \mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
@@
 \mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
-\end{split}
-\end{equation}
-where $j \in \{2,3\}$. Also we have %{\color{red} check paranthesis. }
+\end{alignat}
+\end{subequations}
+where %$j \in \{2,3\}$. Also we have $ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}},$.
+%{\color{red} check paranthesis. }
 \begin{equation}\label{shortPacket}
@@
 Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,
-\begin{equation}
-\begin{split}
+\begin{subequations}
+\begin{alignat}{4}
 T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
@@
 T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}.  \\
-\end{split}
-\end{equation}
+\end{alignat}
+\end{subequations}
 %{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
@@
 In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we ignore the other two delays for simplification;
-So, we assume that the total delay is approximate to the processing delay.
+So, we assume that the total delay is approximate to the processing delay ($T^{\text{\text{tot}}} \approx T^{\text{proc}}$).
 %Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
-\begin{equation}
-T^{\text{\text{tot}}} \approx T^{\text{proc}}
-\end{equation}
+%\begin{equation}
+%T^{\text{\text{tot}}} \approx T^{\text{proc}}
+%\end{equation}
 \subsubsection{Processing Delay}
@@
 
-So, the mean processing delay for UE $i$ in slice $s$ is 
-\begin{equation}
-T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
-\end{equation}
+So, the mean processing delay for UE $i$ in slice $s$ is $T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.$
+%\begin{equation}
+%T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
+%\end{equation}
 Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. %{\color{red} what results in this approximation?}
@@
 
-So the system's total cost of energy of all the slices can be represented as
-\begin{equation*}
-\textstyle \phi_{\text{\text{tot}}} = \sum_{s=1}^{S}\phi_{s},
-\end{equation*}
-where $\phi_{s}$ is obtained from
-\begin{equation}
-\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d.
-\end{equation}
+So the system's total cost of energy of all the slices can be represented as $\textstyle \phi_{\text{\text{tot}}} = \sum_{s=1}^{S}\phi_{s}$.
+%\begin{equation*}
+%\textstyle \phi_{\text{\text{tot}}} = \sum_{s=1}^{S}\phi_{s},
+%\end{equation*}
+where $\phi_{s}$ is obtained from $\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d.$
+%\begin{equation}
+%\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d.
+%\end{equation}
 Moreover, $\phi_s^u$, $\phi_s^c$, and $\phi_s^d$ are the fixed cost of energy in UPF, O-CU, and O-DU, respectively. 
@@
 As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
-Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and 
-\begin{equation}
-\begin{split}
-T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
-                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
-\end{split}
-\end{equation}
+Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have 
+$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
+$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$  
+%\begin{equation}
+%\begin{split}
+%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
+%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
+%\end{split}
+%\end{equation}
 In the following, we define a lemma to find the upper and lower bound for the optimal number of VNFs based on the achievable rates.
@@
 %\end{equation}
-
-\begin{equation}\label{RM}
-\begin{split}
+\begin{subequations}\label{RM}
+\begin{alignat}{4}
 \mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
@@
 & + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}\\
-\end{split}
-\end{equation}
-
+\end{alignat}
+\end{subequations}
 In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
 So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
-$\mathtt{M}_{u(s,i)}$ in each slice as follow.
-\begin{equation}
-M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
-\end{equation}
+$\mathtt{M}_{u(s,i)}$ in each slice as $M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s $.
+%\begin{equation}
+%M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
+%\end{equation}
 \end{proof}
@@
 where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follows:
-\begin{equation}
-\begin{split}
+\begin{subequations}
+\begin{alignat}{4}
 \mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
 \mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
-\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
-\end{split}
-\end{equation}
+\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.
+\end{alignat}
+\end{subequations}
 Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
@@
 The optimal power is as follow.
-\begin{equation}
-\begin{split}
+\begin{subequations}
+\begin{alignat}{4}
 p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
  &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
-\end{split}
-\end{equation}
+\end{alignat}
+\end{subequations}
 Also $[a]^+ = \max(0,a)$.
 In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
-\begin{equation}\label{deriveE}
-\begin{split}
+\begin{subequations}\label{deriveE}
+\begin{alignat}{4}
 \dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
@@
 &+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
-\end{split}
-\end{equation}
+\end{alignat}
+\end{subequations}
 So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
@@
 \begin{algorithm}
+%\setstretch{1.}
 \caption{Greedy Algorithm for Assignment of O-RU to UEs (GAA)}\label{alg1}
 \begin{algorithmic}[1]
-\State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{31}
-\State Set $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
-\State Set ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$  $\forall s, \forall i$
+\State Set $g^r_{u(s,i)} = 0$, $\mathfrak{C}_r = \mathfrak{t}_r,$ and ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$   $\forall s, \forall i, \forall r$.\label{31}
 \State Sort slices according to their priority factor ($\delta_s$) in descending order
@@
 \end{algorithm}
-\subsection{Iterative Proposed Algorithm}
-In Sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
-Here, the iterative algorithm for the whole problem is demonstrated.
-Firstly, we fixed $\boldsymbol{G}$ to achieve $\boldsymbol{P}$ and $\boldsymbol{E}$, using the Lagrangian method and the KKT conditions.  
-Afterward, $\boldsymbol{G}$ is updated using the GAA algorithm. This process is repeated until it converges. 
-The whole algorithm (IABV method) is depicted as follows (Algorithm \ref{alg2}).
+
  \begin{algorithm}
@@
 \end{algorithm} 
+\subsection{Iterative Proposed Algorithm}
+In Sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
+Here, the iterative algorithm for the whole problem is demonstrated.
+Firstly, we fixed $\boldsymbol{G}$ to achieve $\boldsymbol{P}$ and $\boldsymbol{E}$, using the Lagrangian method and the KKT conditions.  
+Afterward, $\boldsymbol{G}$ is updated using the GAA algorithm. This process is repeated until it converges. 
+The whole algorithm (IABV method) is depicted as follows (Algorithm \ref{alg2}).
+
 \subsubsection{Complexity Order}
@@
  and it has the upper bound.
+   \begin{algorithm}
+\caption{Fast Algorithm (FA) to Check the Convergence}\label{alg3}
+\begin{algorithmic}[1]
+\State Set count = 0 
+\State Set $p_{r,u(s,i)}^{k} = 0$, $e_{r,u(s,i)}^{k} = 0$ and $g_{u(s,i)}^{r} = 0$ $\forall r,k,s,i$
+\For{$s \gets 1$ to $S$} 
+\For{$i \gets 1$ to $U_s$}
+\State count = count +1  
+\State $r^* = \argmin_r d_{r,u(s,i)} \quad \forall r$
+\State $g_{u(s,i)} ^{r^*}=1$
+\State temp =mod(count, K)            
+\If {temp=0 }
+\State $e_{r^*,u(s,i)}^{K} = 1 $
+\State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
+\Else 
+\State $e_{r^*,u(s,i)}^{\text{temp}} = 1 \quad \forall r$ 
+\State Set $p_{r^*,u(s,i)}^{\text{temp}} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
+\EndIf
+\State \textbf{end if}
+\EndFor
+\State \textbf{end for}
+\EndFor
+\State \textbf{end for}
+\end{algorithmic}
+\end{algorithm} 
+ \vspace*{-3em}
 \section{Numerical Results and The Feasible Region}\label{NE}
+
 In this section, firstly, we describe the initial points and the comparison algorithms.
 Then, we talk about the feasible region of our system model. Afterward, we illustrate the numerical results.
-
+\vspace*{-1.7em}
 \subsection{The initial Points and The Comparison Algorithms}
@@
 We consider three network slices for eMBB, URLLC, and mMTC services.
-Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in Figure \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
-\begin{figure}
+Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in table \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.47]{cell.pdf}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{O-RU placement in a cell}
+%  \label{fig:cell}
+%\end{figure}
+\begin{table}%
 \centering
-    \includegraphics[scale = 0.47]{cell.pdf}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{O-RU placement in a cell}
-  \label{fig:cell}
-\end{figure}
-Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
-Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
-We consider 25 PRBs are used in the network and the packet size is equal to 20 bytes.
-The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
-Also, the quantization noise is assumed to be $10^{-13}$.
-Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a}.
-\begin{table}
- \caption {Simulation Parameters} \label{table:1a}
- \begin{center}
+\parbox{0.4\textwidth}{
+\begin{footnotesize}
+ \scalebox{0.75}{
   \begin{tabular}{||c | c ||}
@@
   \hline
- \end{tabular}
- \end{center}
+ \end{tabular}}
+\end{footnotesize}
+ \caption {Simulation Parameters} \label{table:1a}
+}
+\qquad
+\begin{minipage}[c]{0.53\textwidth}%
+\centering
+\includegraphics[scale = 0.32]{cell.pdf}
+  \caption{O-RU placement in a cell}
+  \label{fig:cell}
+\end{minipage}
 \end{table}
+Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
+Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
+We consider 25 PRBs are used in the network and the packet size is equal to 20 bytes.
+The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
+Also, the quantization noise is assumed to be $10^{-13}$.
+Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a}.
+%\begin{table}
+% \caption {Simulation Parameters} \label{table:1a}
+% \begin{center}
+% \scalebox{0.7}{
+%  \begin{tabular}{||c | c ||}
+%  \hline
+%Parameter & Value \\ [0.5ex]
+%  \hline\hline
+%  Noise power & -174dBm\\
+%  \hline
+%  Bandwidth & 180 KHz \\
+%  \hline
+% Maximum transmit Power of each O-RU & 40dBm \\
+%  \hline
+%  Maximum delay for eMBB &  4msec \\
+%  \hline
+%    Maximum delay for URLLC &  1msec \\
+%  \hline
+%  Maximum delay for mMTC &  5msec \\
+%  \hline
+%  Maximum fronthaul capacity  & 46 bits/sec/Hz \\
+%   \hline
+%  Minimum data rate for eMBB &  20 bits/sec/Hz \\ 
+%  \hline
+%   Minimum data rate for URLLC and mMTC &  2 bits/sec/Hz \\ 
+%  \hline
+%   Maximum received power for mMTC &  20 dBm \\ [.5ex]   
+%  \hline
+%    Maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]   
+%  \hline
+% \end{tabular}}
+% \end{center}
+% \end{table}
 
@@
 If the fast method converges and has a feasible solution, so our algorithm (IABV) can be converged too.
-
 Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
@@
 In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels and the channel distance.
+
+ \vspace*{-2em}
 \subsection{Feasible Region}\label{fr}
@@
 If the conditions in \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
+Assume, the number of UEs is $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_s}1$,
+the number of PRBs is $K$, and the distance between the $r^{th}$ O-RU to the UE i in slice $s$ is $d_{r,u(s,i)}$.
 The FA algorithm is represented in Algorithm \ref{alg3}.
-
- \begin{algorithm}
-\caption{Fast Algorithm (FA) to Check the Convergence}\label{alg3}
-\begin{algorithmic}[1]
-\State The number of UEs: $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_s}1$
-\State The number of PRBs: $K$
-\State the distance from the $r^{th}$ O-RU to the UE i in slice $s$: $d_{r,u(s,i)}$ 
-\State Set count = 0 
-\State Set $p_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
-\State Set $e_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
-\State Set $g_{u(s,i)}^{r} = 0 \quad \forall r,s,i$
-\For{$s \gets 1$ to $S$} 
-\For{$i \gets 1$ to $U_s$}
-\State count = count +1  
-\State $r^* = \argmin_r d_{r,u(s,i)} \quad \forall r$
-\State $g_{u(s,i)} ^{r^*}=1$
-\State temp =mod(count, K)            
-\If {temp=0 }
-\State $e_{r^*,u(s,i)}^{K} = 1 $
-\State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
-\Else 
-\State $e_{r^*,u(s,i)}^{\text{temp}} = 1 \quad \forall r$ 
-\State Set $p_{r^*,u(s,i)}^{\text{temp}} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
-\EndIf
-
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for}
-\end{algorithmic}
-\end{algorithm}
-
 The complexity order of this algorithm is $O(R\times \mathfrak{N})$ which is remarkably lower than the complexity order of the IABV method.
@@
 If the number of UEs is more than the PRBs, each UE is given exactly one PRB without interference. Otherwise, the amount of interference will not be high but more than one UE will use same PRBs.
+\vspace*{-1.7em}
 \subsection{Numerical Results}
@@
 Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
-\begin{figure}
+\begin{figure}%[!tbp]
   \centering
-    \includegraphics[scale = 0.47]{Arate_ue1.eps}
+  \captionsetup{justification=centering}
+  \begin{minipage}[b]{0.4\textwidth}
+    \includegraphics[scale = 0.4]{Arate_ue1.eps}
+    \caption{Aggregate throughput vs. number of UEs in each service}% in the presence of three services}
+    \label{fig:1}
+  \end{minipage}
+  \qquad
+  \begin{minipage}[b]{0.4\textwidth}
+       \includegraphics[scale = 0.4]{vnfNum1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate throughput vs. number of UEs for each service in the presence of three services}
-  \label{fig:1}
+  \caption{Number of activated VNF in each Service vs. Mean Arrival Rate(Mbps)}
+  \label{fig:4}
+  \end{minipage}
 \end{figure}
+%%%%%%%%%
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.47]{Arate_ue1.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Aggregate throughput vs. number of UEs for each service in the presence of three services}
+%  \label{fig:1}
+%\end{figure}
+%%%%%%%%%%%%%%
 %Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
@@
 %\end{figure}
-
 Figure \ref{fig:4} depicts the number of activated VNFs for five different mean service times of one URLLC service vs.
@@
 Moreover, the number of activated VNFs decreases when the mean service rate increases.
-
-\begin{figure}
-  \centering 
-    \includegraphics[scale = 0.47]{vnfNum1.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Number of activated VNF in each Service vs. Mean Arrival Rate(Mbps)}
-  \label{fig:4}
-\end{figure}
-
+%%%%%%%%%%%%%%
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.47]{vnfNum1.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Number of activated VNF in each Service vs. Mean Arrival Rate(Mbps)}
+%  \label{fig:4}
+%\end{figure}
+%%%%%%%%%%%%
 In figure \ref{fig:5}, the aggregate throughput is depicted vs.
@@
 Moreover, the proposed method (IABV), gives higher aggregate rates in compared to the FBDR and the baseline scheme.
-
-\begin{figure}
+\begin{figure}%[!tbp]
   \centering
-    \includegraphics[scale = 0.47]{RatePower1.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \captionsetup{justification=centering}
+  \begin{minipage}[b]{0.4\textwidth}
+    \includegraphics[scale = 0.4]{RatePower1.eps}
     \caption{Aggregate Throughput for eMBB vs. Maximum Transmit power for various number of UEs }
   \label{fig:5}
+  \end{minipage}
+  \qquad
+  \begin{minipage}[b]{0.4\textwidth}
+      \includegraphics[scale = 0.4]{delay_new.eps}
+  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}% for various number of UEs}
+  \label{fig:6}
+  \end{minipage}
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.47]{RatePower1.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Aggregate Throughput for eMBB vs. Maximum Transmit power for various number of UEs }
+%  \label{fig:5}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%
 Figure \ref{fig:6} illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
@@
 %Moreover, we can see that the mean delay of a URLLC service increases almost linearly with the mean arrival rate of the packet transmission. 
-\begin{figure}
-  \centering 
-    \includegraphics[scale = 0.47]{delay_new.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for various number of UEs}
-  \label{fig:6}
-\end{figure}
+%%%%%%%%%%%%%%%%%
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.47]{delay_new.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for various number of UEs}
+%  \label{fig:6}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%5
 Figure \ref{fig:7} is the same as figure \ref{fig:6} that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
 As you can see, the proposed method (IABV) outperforms the other scenarios.
-
-\begin{figure}
+%%%%%%%%%%%%%
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.47]{delay1_new.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for different methods}
+%  \label{fig:7}
+%\end{figure}
+%%%%%%%%%%%%%
+\begin{figure}%[!tbp]
   \centering
-    \includegraphics[scale = 0.47]{delay1_new.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for different methods}
+  \captionsetup{justification=centering}
+  \begin{minipage}[b]{0.4\textwidth}
+    \includegraphics[scale = 0.4]{delay1_new.eps}
+    \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}% for different methods}
   \label{fig:7}
+  \end{minipage}
+  \qquad
+  \begin{minipage}[b]{0.4\textwidth}
+       \includegraphics[scale = 0.36]{AmmTCpower.eps}
+  \caption{Aggregate Throughput vs. Number of UEs in each Service for three different mMTC services}
+  \label{fig:8}
+  \end{minipage}
 \end{figure}
-
 Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances.
@@
 Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
-\begin{figure}
-  %\centering 
-    \includegraphics[scale = 0.4]{AmmTCpower.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput for mMTC services vs. Number of UEs in each Service for three different mMTC service instances}
-  \label{fig:8}
-\end{figure}
-
+%%%%%%%%%%%%
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.4]{AmmTCpower.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Aggregate Throughput for mMTC services vs. Number of UEs in each Service for three different mMTC service instances}
+%  \label{fig:8}
+%\end{figure}
+%%%%%%%%%%%%
 Assume we have two types of eMBB service instances.
@@
 Also, we can realize from this figure that the aggregate throughput has the most significant value at the same priority.
-\begin{figure}
+\begin{figure}%[!tbp]
   \centering
+  \captionsetup{justification=centering}
         \includegraphics[scale = 0.4]{priorityLast.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
   \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
   \label{fig:9}
+
 \end{figure}
-%
+%%%%%%%%%%5
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.4]{priorityLast.eps}
+%  \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
+%  \label{fig:9}
+%\end{figure}
+%%%%%%%%%%%
 %In the figure \ref{fig:10}, the aggregate throughput is presented vs. the number of UEs for one service in a system by considering two different cloud restrictions and fronthaul restrictions.
@@
 
-\begin{figure}
-  \centering 
-    \includegraphics[scale = 0.4]{iter.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput vs. Number of Iterations}
-  \label{fig:11}
-\end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%55
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.4]{iter.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Aggregate Throughput vs. Number of Iterations}
+%  \label{fig:11}
+%\end{figure}
+%%%%%%%%%%%%%%%%%5
 %\subsection{Summary of Simulation Results}
@@
 Our solution is close to the optimal value in a small number of UEs.
-\begin{figure}
+\begin{figure}%[tbp]
   \centering
+  \captionsetup{justification=centering}
+  \begin{minipage}[b]{0.4\textwidth}
+     \includegraphics[scale = 0.4]{iter.eps}
+  \caption{Aggregate Throughput vs. Number of Iterations}
+  \label{fig:11}
+  \end{minipage}
+    \qquad
+  \begin{minipage}[b]{0.4\textwidth}
    \includegraphics[scale = 0.4]{optimal1.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput vs. Number of UEs }
+  \caption{Aggregate Throughput vs. Number of UEs in one Service}
   \label{fig:12}
+  \end{minipage}
 \end{figure}
+
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.4]{optimal1.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Aggregate Throughput vs. Number of UEs }
+%  \label{fig:12}
+%\end{figure}
 
@@
 %The aggregate throughput rises with the increases of UEs and the maximum interference and then remains almost constant.
-
-\begin{figure}
+\begin{figure}%[tbp]
   \centering
-    \includegraphics[scale = 0.4]{interF_new.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \captionsetup{justification=centering}
+  \begin{minipage}[b]{0.4\textwidth}
+   \includegraphics[scale = 0.35]{interF_new.eps}
   \caption{Aggregate Throughput vs. Maximum Interference }
   \label{fig:13}
+  \end{minipage}
+    \qquad
+  \begin{minipage}[b]{0.4\textwidth}
+    \includegraphics[scale = 0.35]{FA.eps}
+  \caption{Aggregate Throughput vs. the Number of UEs in one Service }
+  \label{fig:14}
+  \end{minipage}
 \end{figure}
-
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.4]{interF_new.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Aggregate Throughput vs. Maximum Interference }
+%  \label{fig:13}
+%\end{figure}
 In figure \ref{fig:14}, the aggregate throughput is shown versus
@@
 And we can see that the IABV method is better than the FA method. 
-
-\begin{figure}
-  \centering 
-    \includegraphics[scale = 0.4]{FA.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput vs. the Number of UEs }
-  \label{fig:14}
-\end{figure}
-
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.4]{FA.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Aggregate Throughput vs. the Number of UEs }
+%  \label{fig:14}
+%\end{figure}
+\vspace*{-1.7em}
 \section{Conclusion}\label{conc}
@@
 Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.
-
+\vspace*{-1.7em}
 \bibliographystyle{IEEEtran} 

### 2021-10-06 Latex/journal_v1/research plan/main.tex
add research plan

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Imperial College London
-% UKRI Centre for Doctoral Training in AI for Healthcare
-% https://ai4health.io
-%
-% LaTeX Template
-% Version 1.0 (22/10/19) Aldo Faisal
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%----------------------------------------------------------------------------------------
-%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
-%----------------------------------------------------------------------------------------
-\input{ai4health_header}
+\documentclass{article}
+\usepackage[utf8]{inputenc}
+ \usepackage{enumerate}
+ \usepackage[T1]{fontenc}
+\usepackage{cite}
+%\usepackage{caption}
+%\usepackage{subcaption}
+\usepackage{mathtools}
+\usepackage{stackengine}
+\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
+\usepackage{graphicx}
+\usepackage{blindtext}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
+\usepackage{amsthm}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\allowdisplaybreaks
+\newtheorem{remark}{Remark}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
+\newcommand{\diag}{\mathop{\mathrm{diag}}}
+\DeclareMathOperator{\E}{\mathbb{E}}
+\usepackage[margin=0.7in]{geometry}
+\usepackage[export]{adjustbox}
+
+\title{Reporte de inventario de eviencias}
+\author{Natalia Galeano Valerio}
+\date{Octubre 2019}
+
 \begin{document}
-\begin{titlepage}
 
-\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here
-\setlength{\topmargin}{0in}
-\center % Center everything on the page
+\baselineskip 12pt
 
- \begin{minipage}{0.4\textwidth}
-\begin{flushleft} \large
-\hspace*{-0.5cm}
-%\includegraphics[scale=0.14]{imperial.png}\\
-\end{flushleft}
-\end{minipage}
-~
-\begin{minipage}{0.5\textwidth}
-\begin{flushright} \large
-\hspace*{2cm}
-%\includegraphics[scale=0.20]{logo.png}\\
-\end{flushright}
-\end{minipage}\\[1cm]
-%----------------------------------------------------------------------------------------
-%	HEADING SECTIONS
-%----------------------------------------------------------------------------------------
+\vspace*{30mm}
 
-\textsc{\Large resource allocation in open ran system using network slicing}\\[0.5cm] % Major
-\LARGE \textsc{University of Tehran} \\[1.5cm] 
-% Name of your heading such as course name
-\textsc{\large }\\[0.5cm] % Minor heading such as course title
+\begin{center}
 
-%----------------------------------------------------------------------------------------
-%	TITLE SECTION
-%----------------------------------------------------------------------------------------
+\textbf{\Large Research Plan} \\
+\vspace{10mm}
+\textbf{Department of Electrical and Computer Engineering}\\
+\vspace{20mm}
+{\large University of Oulu}\\
+\vspace{20mm}
+\end{center}
+\vspace{10mm}
+{\scriptsize Provisional title:}\\
+Dynamic Resource Allocation in O-RAN Architecture using Network Slicing\\
 
-\HRule \\[0.4cm]
-{ \huge \bfseries Research Planning Report}\\[0.4cm] % Title of your document
-\HRule \\[1cm]
+\vspace{20mm}
 
-%----------------------------------------------------------------------------------------
-%	AUTHOR SECTION
-%----------------------------------------------------------------------------------------
+{\scriptsize Candidate name}\\
+Mojdeh Karbalaee Motalleb \\
+\vspace{3mm}
 
-\begin{minipage}{0.4\textwidth}
-\begin{flushleft} \large
-\emph{Student:}\\
-Mojdeh Karbalaee Motalleb \\ % Your name, if you are medically qualified please use "Last Name, M.D."
-\emph{Email Address:}\\
-mojdeh.karbalaee@ut.ac.ir
-\end{flushleft}
-\end{minipage}
-~
-\begin{minipage}{0.5\textwidth}
-\begin{flushright} \large
-\emph{Supervisor:} \\
-Dr. Onel Lopez \\% Supervisor's Name
-%Supervisor Department(s)\\
-%[0.5cm] \emph{Healthcare Supervisor} \\
-%Fist name \textsc{Last name} % Supervisor's Name
-%Supervisor Department(s)  or NHS Trust+section\\
-\emph{Department: } \\
-Electrical Engineering
-% \textsc{Add name here} % Supervisor's Name
-% Supervisor Department(s) or NHS Trust+section
-\end{flushright}
-\end{minipage}\\[1cm]
+{\scriptsize Supervisor name:}\\
+Dr. Onel Lopez\\
+\vspace{3mm}
 
-%----------------------------------------------------------------------------------------
-%	DATE SECTION
-%----------------------------------------------------------------------------------------
+\pagebreak
+\begin{abstract}
+Open radio access network (O-RAN) is the next generation of RAN systems introduced by the O-RAN Alliance to increase the flexibility and the openness of the network systems and simultaneously decrease CAPEX and OPEX of mobile operators.
+The O-RAN system combines and takes advantage of Cloud RAN (C-RAN) and the Virtual RAN (VRAN).
+O-RAN separates RAN into three
+different units, namely Radio Unit (O-RU), Distributed Unit
+(O-DU), and Central Unit (O-CU).
+In this research, we study
+the problem of baseband resource allocation and virtual
+network function (VNF) activation in O-RAN architecture
+based on their service priority for different types of 5G services
+including enhanced mobile broadband (eMBB), ultra-reliable
+low latency communications (uRLLC) and massive Machine
+Type Communications (mMTC) services using intelligent RAN slicing. 
+Network slicing is a promising solution for supporting such heterogeneous and challenging services.
+Deploying network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed. The limited
+fronthaul capacity, the restriction of end-to-end delay and the reliability of the services are
+considered at the same time.
 
-{\large \today}\\[0.5cm] % Date, change the \today to a set date if you want to be precise
+The optimization of baseband
+resources includes O-RU assignment, the assignment of physical resource block
+(PRB), and power allocation.
+The main problem is a mixed-integer non-linear programming problem that is tremendously difficult.
+Since the problem has a two-time scale, it can be broken into two layers.
+On the large-time scale, the problem of obtaining the optimal number of VNF, the placement of VNFs, and the assignment of PRB to the slices are considered.
+On the small-time scale, there is the problem of obtaining the optimal power of UEs, and the PRB and o-RU assignment.
+To solve the problem, we propose deep reinforcement learning, the deep deterministic policy gradient (DDPG) method, and convex optimization.
+\end{abstract}
+\section{Introduction} 
+O-RAN, as the integration and expansion of C-RAN and xRAN, or C-RAN and the vRAN is expected to be a key technology in 5G networks to enhance the RAN performance extensively. 
+The core idea of C-RAN is to divide the radio remote head (RRU) from the baseband unit (BBU).
+Also, several BBUs are placed together to create the BBU-pool, providing unified baseband signal processing with powerful computing capabilities.
+On the other hand, xRAN technology has three fundamental features.
+The control plane is decoupled from the user plane.
+Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
+Moreover, open north-bound and south-bound interfaces are introduced.
+O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+O-RU is a logical node that contains RF and lowers PHY.
+Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC.
+In addition, the O-CU depicts the logical node contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP).
+O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
+O-DU and O-CU are connected via an open and well-defined interface F1.
+Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
+The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
+RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
+One of the necessities of the new generation of wireless networks is its intelligence.
+Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques.
+The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time, implement the algorithms for network intelligence
+\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
+\begin{figure*}
+  \centering 
+    \includegraphics[scale = 0.6]{finalDraw.pdf}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Network sliced ORAN system}
+  \label{fig:c11}
+\end{figure*}
 
-\vfill % Fill the rest of the page with whitespace
+One of the goals of the next generation of mobile systems is to strictly meet the stringent QoS demands of the different services introduced in 5G , i.e., eMBB, URLLC, and mMTC.
+Network slicing is a promising solution to obtain the QoS for each type of service.
+Network slicing contains RAN slicing, core slicing, and both of them together.
+Efficient slicing of RAN is still challenging due to time-varying network circumstances.
+%Network slicing will propose significant complexity into the performance of systems that causes conventional mathematical model-based procedures to network operation no longer adequate. 
+Network slicing creates considerable complexity in system performance and makes the conventional mathematical methods insufficient to model the network.
+Therefore, it motivates researchers to realize network slicing using machine learning strategies such as deep learning and deep reinforcement learning.
+So, the network can reach the best control policy according to its experience in the past time slots.
+As mentioned above, network slicing, which contains RAN slicing, core slicing, and the whole, is considered a hot topic for vendors.
+In addition, the O-RAN system seems to be the next RAN architecture.
+So, this motivated researchers to study the dynamic RAN slicing in O-RAN architecture to achieve the desired QoS for each service type.
+In addition, according to the high complexity of RAN slicing and incapability of the traditional model-based methods, dynamic machine learning becomes the best solution for these problems.
+ Generally, there are two kinds of deep reinforcement learning methods for solving dynamic problems.
+The first class is value-based such as Deep-Q-Network, and the second class is policy-based problems such as DDPG.
+The first class can only solve the discrete action space problems, which are integer programming.
+The second class can solve by searching the optimal policy, which is the actor-critic method.
+Here, we use the second method to solve our problems.
 
-\end{titlepage}
+\section{Motivation and contributions}
+In this project, we want to solve the problem of dynamic network slicing in the O-RAN system.
+The system has a two-time scale and should be solved in two layers.
+On a large time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed.
+Also, the assignment of RB to the slices is obtained.
+There are three types of services that requires three types of slices: URLLC, which requires low latency; eMBB, which needs high data rate; and mMTC, short packet and low power devices.
+The conventional models cannot perform well in the system because of the different QoS for each service type, and the complexity of dynamic RAN slicing.
+So we must switch to machine learning and dynamic methods and find the most suitable approach.
+A dynamic strategy of resource allocation is required to solve this problem to achieve the specific QoS for each type of service in the O-RAN architecture.
+In this project, we want to have an intelligent resource allocation in the O-RAN architecture for the different scenarios of services. 
+Also, another goal of this project is to apply transfer learning to the system and enhance the performance and the convergence of the methods. 
+\section{Research Method and data set}
+In this research, we want to use the machine learning methods such as deep reinforcement learning and deep learning to train the O-RAN system and have an intelligent system.
+The multi-agent deep reinforcement learning contains DDPG, the deep deterministic policy gradient algorithm (actor-critic algorithm), correlated q-learning, and the priority proportional fairness algorithm.
+The deep learning algorithms contain LSTM and recurrent neural networks. Also, transfer learning is an exciting way to enhance the performance and convergence of the system.
 
-%\renewcommand{\abstractname}{Abstract}
-\begin{abstract}
-%% 100 words
-\emph{In this project }
-\end{abstract}
+\bibliographystyle{IEEEtran} 
+\bibliography{ref}
+%\begin{thebibliography}{9}
+%\bibitem{Hunt}
+%Sally Hunt, ``Making Competition Work in Electricity,'' John Wiley , pp.23-30, Fev, 2002.
 
-\section{Introduction \& Literature review}
-\emph{Give background and motivation for your work. Explain  knowledge needed. Show its scientific and healthcare need.
-Define a set of clear questions and approaches to answering them.
-Highlight their originality and/or significance.
-Explain how they adds to, develop (or challenges) existing literature in the field.
-Note, this comprises both AI questions and Healthcare questions.}
-\subsection{AI literature}
-\subsection{Healthcare literature}
-\section{PhD goal}
-\emph{Explain the main question you want to answer in terms of AI technology developed and healthcare challenge addressed.
-Connect it with current state of research and show its importance in this context.
-Show what you want to achieve. Explain your contribution to the subject.}
-
-\section{Methodology}
-\emph{Specify methodology and techniques which will be used for your research. Be specific this will allow the reviewers to understand how well thought out and achievable your plan is.}
-\section{Summarise the work done since the start of the PhD.}
-\emph{Show interim results, if any.}
-\section{Program of work}
-\emph{This is your list, description and schedule of activities to achieve in PhD goal .
-Include Publication \& conference deadlines as expected, i.e.
-Give an overview of subjects or steps of your work you intend to publish,  suggest some meetings or conferences you plan to attend in order to present your research.}
-
-\section{Data, Infrastructure or Software needs}
-\emph{Make a list of facilities or infrastructure, including data and software you will need to complete your research.
-Explain how it is or will be made available.
-Assess the \textbf{Data Readiness Level} of all needed data sources.}
-
-\section{Planned Impact}
-\emph{Assuming that you achieve your PhD goals, what is the impact that your proejct will achieve.
-Assess your project's planned impact in terms of the PICO (population, intervention, comparator and outcome) framework.}
-
-\subsection*{Example: Diagnosis}
-\paragraph{Population}: To which populations of patients would the test be applicable? How can they be best described? Are there subgroups that need to be considered?
-
-\paragraph{Intervention} (index test[s]): The test or test strategy being evaluated.
-
-\paragraph{Comparator} The test with which the index test(s) is/are being compared, usually the reference standard (the test that is considered to be the best available method to establish the presence or absence of the condition of interest - this may not be the one that is routinely used in practice).
-
-Target condition: The disease, disease stage or subtype of disease that the index test(s) and the reference standard are being used to establish.
-
-\paragraph{Outcome} The diagnostic accuracy of the test or test strategy for detecting the target condition.
-This is usually reported as test parameters, such as sensitivity, specificity, predictive values, likelihood ratios, or - where multiple cut-off values are used - a receiver operating characteristic (ROC) curve.
-
-\subsection*{Example: Intervention}
-
-\paragraph{Population} Which populations of patients are we interested in? How can they be best described? Are there subgroups that need to be considered?
-
-\paragraph{Intervention} Which intervention, treatment or approach should be used?
-
-\paragraph{Comparators} What is/are the main alternative(s) to compare with the intervention being considered?
-
-\paragraph{Outcome} What is really important for the patient?
-Which outcomes should be considered?
-Examples include intermediate or short-term outcomes; mortality; morbidity and quality of life; treatment complications; adverse effects; rates of relapse; late morbidity and re-admission; return to work, physical and social functioning; resource use.
-
-%**********************************************%
-\newpage
-\addcontentsline{toc}{section}{References}
-\begin{thebibliography}{9}
-\bibitem{latexcompanion} 
-Michel Goossens, Frank Mittelbach, and Alexander Samarin. 
-\textit{The \LaTeX\ Companion}. 
-Addison-Wesley, Reading, Massachusetts, 1993.
-
-\bibitem{einstein} 
-Albert Einstein. 
-\textit{Zur Elektrodynamik bewegter K{\"o}rper}. (German) 
-[\textit{On the electrodynamics of moving bodies}]. 
-Annalen der Physik, 322(10):891-921, 1905.
-
-\bibitem{knuthwebsite} 
-Knuth: Computers and Typesetting,
-\\\texttt{http://www-cs-faculty.stanford.edu/\~{}uno/abcde.html}
-
-\end{thebibliography}
+%\end{thebibliography}
+\vspace{20mm}
 

### 2021-10-09 Latex/journal_v1/research plan/main.tex
add report for lopez

@@
 On the large-time scale, the problem of obtaining the optimal number of VNF, the placement of VNFs, and the assignment of PRB to the slices are considered.
-On the small-time scale, there is the problem of obtaining the optimal power of UEs, and the PRB and o-RU assignment.
+On the small-time scale, there is a problem of obtaining the optimal power of UEs, and the PRB and O-RU assignment.
 To solve the problem, we propose deep reinforcement learning, the deep deterministic policy gradient (DDPG) method, and convex optimization.
@@
 \section{Introduction} 
-O-RAN, as the integration and expansion of C-RAN and xRAN, or C-RAN and the vRAN is expected to be a key technology in 5G networks to enhance the RAN performance extensively. 
+O-RAN, as the integration and expansion of C-RAN and xRAN, or C-RAN and vRAN is expected to be a key technology in 5G networks to enhance the RAN performance extensively. 
 The core idea of C-RAN is to divide the radio remote head (RRU) from the baseband unit (BBU).
@@
   \centering 
-    \includegraphics[scale = 0.6]{finalDraw.pdf}
+    \includegraphics[scale = 0.5]{finalDraw.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 The second class can solve by searching the optimal policy, which is the actor-critic method.
-Here, we use the second method to solve our problems.
+Here, we use the second method to solve our problems \cite{alsenwi2021intelligent,yan2019intelligent,mei2021intelligent}.
+\subsection{Related Works} 
+In \cite{mei2021intelligent}, the authors proposes a new intelligent RAN slicing method with two-layered control granularity, which aims at maximizing both the long-term QoS of services and spectrum efficiency (SE) of slices.
+In this paper, the authors design a RAN slicing strategy with multiple time and
+resource granularities to accommodate the time-varying network conditions and diverse QoS requirements.
+Here, the DDPG method is applied for the lower level and deep Q-network is applied for upper level.
 
-\section{Motivation and contributions}
-In this project, we want to solve the problem of dynamic network slicing in the O-RAN system.
+In paper \cite{rezazadeh2021actor}, an actor-critic methods and a continuous model-free deep reinforcement
+learning (DRL) method is applied to minimize energy consumption and virtual network function (VNF) instantiation cost.
+Multiplexing eMBB and uRLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
+In \cite{setayesh2020joint,yang2020should}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
+Paper \cite{alsenwi2021intelligent}, represents a joint convex method and deep reinforcement learning to schedule both eMBB and URLLC services.
+Here we have two time-scale, a two-phase-framework, including eMBB resource allocation and URLLC scheduling phases.
+In \cite{saggese2021power}, the problem of power minimization for uRLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
+ In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and URLLC services.
+The system guarantees the latency, the service rate, and the maintenance of reliability.
+
+\subsection{Main Contributions}
+In this research, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
+Here, we study a single-cell downlink situation involving multiple network slices that share existing radio sources.
+The main contributions of
+this research are summarized as follow:
+\begin{itemize}
+\item 
 The system has a two-time scale and should be solved in two layers.
-On a large time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed.
-Also, the assignment of RB to the slices is obtained.
-There are three types of services that requires three types of slices: URLLC, which requires low latency; eMBB, which needs high data rate; and mMTC, short packet and low power devices.
-The conventional models cannot perform well in the system because of the different QoS for each service type, and the complexity of dynamic RAN slicing.
+On a large-time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed.
+Also, the assignment of PRB to the slices is obtained.
+On a small-time scale, the problem of power allocation, O-RU association and the assignment of PRB to UE in each slice is applied.
+\item 
+In this research, we consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, that are massive devices with short packets and low power devices.
+The problem of RAN slicing for different types of services is studied in this research.
+
+\item 
+In this research, we consider an intelligent resource allocation in the O-RAN architecture for the different scenarios of services.
+Since, the conventional models cannot perform well in the system because of the different QoS for each service type, and the complexity of dynamic RAN slicing.
 So we must switch to machine learning and dynamic methods and find the most suitable approach.
 A dynamic strategy of resource allocation is required to solve this problem to achieve the specific QoS for each type of service in the O-RAN architecture.
-In this project, we want to have an intelligent resource allocation in the O-RAN architecture for the different scenarios of services. 
+ In the small-time scale, the actor-critic algorithm such as DDPG is applied to the system that is based on control policy search. This method directly searches the optimal control policy
+by estimating of the gradient with respect to the parameters
+of the control policy. In the large-time scale, the deep reinforcement learning is implemented which is a value based algorithm.
+\item 
 Also, another goal of this project is to apply transfer learning to the system and enhance the performance and the convergence of the methods. 
-\section{Research Method and data set}
-In this research, we want to use the machine learning methods such as deep reinforcement learning and deep learning to train the O-RAN system and have an intelligent system.
-The multi-agent deep reinforcement learning contains DDPG, the deep deterministic policy gradient algorithm (actor-critic algorithm), correlated q-learning, and the priority proportional fairness algorithm.
+\end{itemize}
+\section{System Model}
+In this section, first, we  present the system model.
+Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system.
+Afterward, we discuss about assignment of physical data center resources.
+Finally, the main problem is expressed.
+\subsection{System Model}
+Suppose we have three service types includes eMBB, URLLC, and mMTC.
+Assume we have $S_1$, $S_2$, and $S_3$ different applications for the first, second and third service type, respectively ($S = S_1 + S_2 +S_3$).
+Assume we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
+Each Service $s_j\in \{1,2,...,S_j \} $ consists of $U_{s_j}$ request from the 
+single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
+There are different application request which fall into one of these service categories.
+Each application request requires specific QoS.
+Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
+Assume each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of $K_{s_j}$, $j \in \{1,2,3\}$ pre-allocated physical resource blocks (PRBs) that obtained in the large-time scale, $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+
+Also, each VNF instance is running on the virtual machine (VM) that are using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
+
+In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
+has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
+\subsection{The Achievable Rate}
+The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
+\begin{equation}\label{eq2}
+\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0},
+\end{equation} 
+where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
+${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
+$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice.
+In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
+\begin{equation}
+\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
+\end{equation}
+Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocate to $s^{th}$ slice or not. 
+Also, $BN_0$ denotes the power of Gaussian additive noise.
+Also, $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
+$e^{k}_{r,u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
+
+The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
+\begin{equation}\label{eq1}
+\begin{split}
+\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
+\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
+\end{split}
+\end{equation}
+where $B$ is the bandwidth of system. 
+$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
+Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th} $, $j \in \{2,3\}$ application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
+So, for the short packet transmission the achievable data rate is approximated from follow
+\begin{equation}\label{eq11}
+\begin{split}
+\mathcal{R}_{u(s_2,i)}^{\mathfrak{u},r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}, \quad \mathfrak{u} \in  \{u,m\} \\
+\mathcal{R}_{u(s_1,i)}^{\mathfrak{u}} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 
+\end{split}
+\end{equation}
+Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
+and $\zeta_{u(s_2,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
+Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
+$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
+$N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
+$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
+\subsection{Mean Delay}
+In this part, the end to end mean delay for a service is obtained.
+Suppose the mean total delay is depicted as $T_{tot}$.
+\begin{equation}
+\begin{split}
+T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
+T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
+T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
+T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
+\end{split}
+\end{equation}
+%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
+Total delay is sum of processing delay, transmission delay and propagation delay. 
+The propagation delay is the time takes for a signal to reach to its destination.
+So it has a constant value based on the length of fiber link ($T = L/C_{r}$, where $L$ is the length of link and $C_{r}$ is the capacity of the link).
+Here we assume the value of propagation delay is negligible compared to the rest.
+\subsubsection{Processing Delay}
+Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
+Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.
+
+Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$).
+so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
+since, by using Burke’s Theorem, the mean arrival data rate of the second and third layer which are processed in the first layer is still Poisson with rate $\alpha_{s}$.
+It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
+Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
+Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
+\begin{equation}
+\begin{split}
+T_{DU}^{s} &= \frac{1}{\mu_d - \alpha_{s}/{M_s^{d}}},\\
+T_{CU}^{s} &= \frac{1}{\mu_c - \alpha_{s}/{M_s^{c}}}\\
+T_{UPF}^{s} &= \frac{1}{\mu_u - \alpha_{s}/{M_s^{u}}}\\
+\end{split}
+\end{equation}
+Where $M_s^{d}$, $M_s^{c}$ and 
+$M_s{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
+Moreover, $1/\mu_d$, $1/\mu_c$ and $1/\mu_u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
+Besides, $\alpha_{s}$ is the  arrival rate which is divided
+by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
+$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.
+
+In addition, $T_{RU}^{s}$ is the mean transmission delay of $s^{th}$ slice on the wireless link.
+The arrival data rate of wireless link is equal to the arrival data rate of load balancers for each service.
+ %\cite{frdl}.
+Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
+ an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue.
+ %\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. 
+ Therefore,
+the mean delay of the transmission layer is
+\begin{equation}
+ T_{RU}^{s} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
+\end{equation}
+where, $R_{{tot}_s} = \sum_{u=1}^{U_s}a_{u(s,i)}R_{u(s,i)}$ is the total achievable rate of each service.
+So the mean processing delay for each UE in slice $s$ is 
+\begin{equation}
+T_{process}^{s} =  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s}
+\end{equation}
+\subsubsection{Transmission Delay}
+The transmission delay is the amount of time required to push all the packets into the fiber link. 
+Here, we have transmission delay in fronthaul, midhaul, backhaul and the link to transmit data to internet.
+\begin{equation}
+\begin{split}
+T_{front} =& \frac{\alpha_{s}^{f}}{R_f} \\
+T_{mid} =&  \frac{\alpha_{s}^{m}}{R_m} \\
+T_{back} =& \frac{\alpha_{s}^{b}}{R_b} \\
+T_{trans2net} =& \frac{\alpha_{s}^{t}}{R_t} \\
+\end{split}
+\end{equation}
+Where, $R_f$, $R_m$, $R_b$ and $R_t$ are the rate of transmission in fronthaul, midhaul, backhaul and the link to transmit data to internet, respectively.
+Furthermore, the mean arrival data rate of the each link ($\alpha_{s}^i$ , $i \in \{f,m,b,t\}$) is approximately equal to others ($\alpha_{s} \approx \alpha_{s}^i$ , $i \in \{f,m,b,t\}$).  
+\subsection{Reliability of URLLC}
+As we know, UEs request URLLC services, require services with low latency.
+For the M/M/1 system, the probability of the delay for each application $s$ in the UPF, CU, DU and RU is as follow, respectively
+\begin{equation}
+\begin{split}
+P_r\{T_{UPF}^{s} \geq T_{UPF}^{max}\} &= e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}\\
+P_r\{T_{CU}^{s} \geq T_{CU}^{max}\} &= e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}\\
+P_r\{T_{DU}^{s} \geq T_{DU}^{max}\} &= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}\\
+P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} &= e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}\\
+\end{split}
+\end{equation} 
+So the probability of coincidence of these events is as follow
+\begin{equation}
+P_r\{E_1, E_2, E_3, E_4\} = A_1 A_2 A_3 A_4,
+\end{equation}
+Where $E_1 = T_{UPF}^{s} \geq T_{UPF}^{max}$, $E_2 =T_{CU}^{s} \geq T_{CU}^{max} $, $E_3 =T_{DU}^{s} \geq T_{DU}^{max} $ and $E_4 =T_{RU}^{s} \geq T_{RU}^{max} $.
+Also $A_1=e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}$, $A_2=e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}$, $A_3= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}$ and $A_4 = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}$.
+\subsection{Physical Data Center Resource}
+Each VNF requires
+physical resources that contain memory, storage, CPU and Network Bandwidth.
+Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
+\begin{equation}
+\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f \},
+\end{equation}
+where $\bar{\Omega}_{s}^f\in \mathbb{C}^{4}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f$ indicate the amount of required memory, storage, CPU and and Network Bandwidth, respectively.
+Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice in DU, CU and UPF is defined as below, respectively
+\begin{equation}
+\begin{split}
+&\bar{\Omega}_{\mathfrak{z},s}^{tot,d} = \sum_{f=1}^{M_{s}^d}\bar{\Omega}_{\mathfrak{z},s}^{f,d} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
+&\bar{\Omega}_{\mathfrak{z},s}^{tot,c} = \sum_{f=1}^{M_{s}^c}\bar{\Omega}_{\mathfrak{z},s}^{f,c} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
+&\bar{\Omega}_{\mathfrak{z},s}^{tot,u} = \sum_{f=1}^{M_{s}^u}\bar{\Omega}_{\mathfrak{z},s}^{f,u} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
+\end{split}
+\end{equation}
+Where, $\bar{\Omega}_{\mathfrak{z},s}^{f,d}$, $\bar{\Omega}_{\mathfrak{z},s}^{f,c}$ and $\bar{\Omega}_{\mathfrak{z},s}^{f,u}$ are the amount of resource that a VNF required in DU, CU and UPF, respectively.
+\begin{equation}
+ \bar{\Omega}_{\mathfrak{z},s}^{tot} = \bar{\Omega}_{\mathfrak{z},s}^{tot,d}+ \bar{\Omega}_{\mathfrak{z},s}^{tot,c}+\bar{\Omega}_{\mathfrak{z},s}^{tot,u}
+\end{equation} 
+Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
+The amount of memory, storage, CPU and and Network Bandwidth is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$, $\tau_{C_{j}} $ and $\tau_{N_{j}} $ for the $j^{th}$ DC, respectively
+\begin{equation*}
+\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}}, \tau_{N_{j}} \},
+\end{equation*}
+In this system model, the assignment of physical DC resources to VNFs is considered.
+Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is allocated the resources to the VNFs of $s^{th}$ slice or not.
+\subsection{Power of the O-RU and the Fronthaul Capacity}
+Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. From \eqref{eq2}, we have,
+\begin{equation}\label{pr}
+P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
+\end{equation}
+Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
+%\cite{simeone2016cloud, 1111}
+\begin{equation}\label{cr}
+C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
+\end{equation}
+where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
+\subsection{Problem Statement}
+%In this system, the goal is to minimize the cost of the system.
+%The total power cost of O-RUs for transmitting data to UE is depicted as follow
+%\begin{equation}
+%P_{tot} = \sum_{r=1}^{R}P_r
+%\end{equation}
+Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
+$\phi_{s}$. So the total power of the system for all active DCs that are connected to slices can be represented as
+\begin{equation*}
+\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s} + \sum_{d=1}^{D_c}z_d \psi_d .
+\end{equation*}
+Where,$z_d$ is shown that whether the $d^{th}$ DC is turned on or not and $\psi_d$ is a static cost when a DC is active.
+\begin{equation}
+  z_d =
+    \begin{cases}
+      1 & \sum_{s=1}^{S}y_{s,d} \geq 1 \\
+      0 & \text{otherwise}
+    \end{cases}       
+\end{equation}  
+In addition, $\phi_{s}$ is obtained from below
+\begin{equation}
+\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d
+\end{equation}
+Where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively. 
+So the optimization problem is formulated as follow.
+In the large-time scale the aim of the paper is to minimize the power of the system with the presence constraints
+\begin{subequations}
+\begin{alignat}{4}
+\min\limits_{ \boldsymbol{M}, \boldsymbol{Y}, \boldsymbol{E} } \phi_{tot}   \quad &   \ \\
+\text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
+ \label{c11} \\
+ &\mathcal{R}_{u_{(s_1,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
+& \phi_{tot}  \leq \phi_{max}, \label{c19} \\
+& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
+ &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d} 
+ \quad \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c20}
+\end{alignat}
+\label{constraints}
+\end{subequations}
+In the small-time scale the aim of this paper is to maximize the sum rate of UEs  of eMBB services, minimum the delay of UEs of URLLC services, and minimum the power mMTC services with the presence of constraints.
+\begin{subequations}
+\begin{alignat}{4}
+\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S_1}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^e - \sum_{s=1}^{S_2}T^s_{tot} - \sum_{s=1}^{S_3}\sum_{i=1}^{U_s} p_{u_{(s,k)}} \ \\
+\text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
+ \label{c11} \\
+&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
+&\mathcal{R}_{u_{(s_1,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
+& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
+&T_{tot}^s \leq T_{tot}^{max,s} \quad \forall s,\label{c16} \\
+& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
+& g^r_{u(s,i)} \leq g^r_{u(s,i)}\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)}  \quad \forall s,i , \label{c18} \\
+\end{alignat}
+\label{constraints}
+\end{subequations}
+where $\boldsymbol{P} =[p_{u(s,i)}] \:\: \forall s , \forall i $, is the matrix of power for UEs,
+$\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i \forall r, \forall k$ indicate the binary variable for PRB association.
+Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i \forall r$ is a binary variable for O-RU association.
+Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
+the physical DC is mapped to a VNFs of a slice or not.
+Also, $\eta$ is weighted variable to value between the benefit and the cost term of objective function.
+\eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively. 
+Also \eqref{c13}  shows that the rate of each UE requesting eMBB, URLLC and mMTC is more than a threshold, respectively.
+\eqref{c15} and \eqref{c16} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
+\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
+ \eqref{c18} guarantee that if a UE in admitted by the system, O-RU and PRB is associated to it, respectively.
+In addition, \eqref{c19} indicate that the static cost of energy of VNFs in each slice do not exceed from the threshold. 
+Moreover, in \eqref{c20}  $\mathcal{E} = \{M,S,C, N\}$ and the constraint supports
+that we have enough physical resources for VNFs of each slice.
+\section{Proposed Algorithm and Numerical Results}
+In this research, we aim to use the machine learning methods such as deep reinforcement learning and deep learning to train the O-RAN system and have an intelligent system.
+The deep Q-learning is implemented for the large-time scale and 
+ the multi-agent deep reinforcement learning contains DDPG (actor-critic algorithm), correlated q-learning, and the priority proportional fairness algorithm will be implemented for the small-time scale.
 The deep learning algorithms contain LSTM and recurrent neural networks. Also, transfer learning is an exciting way to enhance the performance and convergence of the system.
+In this following, the proposed algorithm for the large-time scale is implemented, and part of the numerical results is depicted.
+\subsection{Proposed Algorithm}
+Here we use the reinforcement learning method to solve the above two problems.
+In the Q-learning method for the large-time scale, an agent tries to find the optimal value in a specific environment.
+This interactive process is modeled as a Markov decision-making process that includes $ (S, A, R, P, \gamma) $.
+S represents the state space matrix, and A represents the action vector.
+R is also the reward of action.
+$ P (.
+| S, a) $ is the probability of transfer and $ \gamma \ in (0,1] $ is the discount factor.
+The $ \Pi (.
+| S) $ policy is a mapping of the state to the distribution of actions.
+The value-state function for state s under policy $ \Pi (.
+| S) $ with $ V^{\Pi} (s) $ indicates that the expected return value in state s under policy $ \Pi (.
+| S) ) $.
+The value of performing operation a in state s under the $ \Pi (.
+| S) $ policy is represented by $ Q ^ {\Pi} (s, a) $.
+We have the following relations on this basis.
+\begin{equation}
+	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[\sum_{t=0}^{\infty}\gamma^tR_t|S_0=s]
+ \end{equation}
+ The Q-value is as below.
+ \begin{equation}
+	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[\sum_{t=0}^{\infty}\gamma^tR_t|S_0=s,A_0=a].
+\end{equation}
+
+  $\mathbb{E}$ represented the statistical average. 
+ Based on the Bellman equation we have
+ \begin{equation}
+	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[R+\gamma V^{\Pi}(s')]
+\end{equation}  
+ and also, 
+   \begin{equation}
+  	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[R+\gamma Q^{\Pi}(s',a')]
+  \end{equation}  
+  Where, $s'$ and $a'$ can be obtained from $\Pi(.|s')$ and $P(.|s,a)$.
+The goal of reinforcement learnin is to obtain the optimal policy to maximize the $Q^{\Pi}(s,a)$.
+So, using Bellman equation, we have
+\begin{equation}
+	Q^{*}(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q^{*}(s',a')].
+\end{equation} 
+Also, $T^*$ is the Bellman operator
+\begin{equation}
+	T^{*}Q(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q(s',a')]
+\end{equation} 
+By using this operator iteratively, 
+$Q_{t+1}(s,a) \leftarrow T^{*}Q(s,a) $
+the algorithm can converge
+$Q_{t}(s,a) \rightarrow Q^*(s,a)$.
+ $t \rightarrow \infty $
+\cite{montague1999reinforcement,gan1}.
+In the Q-learning in each episode we have
+\begin{equation}
+	Q(s_{t+1},a_{t+1}) = Q(s_t,a_t)+\alpha[ r_{t+1} + \gamma \max_{a \in A}{Q(s_{t+1},a)}-Q(s_t,a_t)]
+\end{equation}
+where, $\alpha$ is the learning rate.
+\subsection{Numerical Results}
+Here, we simplify the large-time scale problem and indicate the numerical results.
+The numerical results for this problem (which is the VNF placement) can be shown as follow. 
+\begin{subequations}
+	\begin{alignat}{4}
+		\min\limits_{\boldsymbol{Y} }   \quad &   \psi_{tot}(\boldsymbol{Y})(t)\\
+		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c} y_{s,d}(t) \geq 1 \quad \forall s, \\
+		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d} \quad  \forall d, \forall ;  \label{eqomega}
+	\end{alignat}
+\end{subequations}
+Suppose we have just one limited resource (CPU in each server).
+The ratio of the number of the used-servers  with the optimal method to the used-servers with the Q-learning method based on time spent can be shown as figure \ref{fig:dynamicEpoch2}.
+In this figure, after about 900 epochs, the algorithm converges to the 0.9 of optimal solution.
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale = 0.4]{./fig/ratio_episode2} %[width=\linewidth] 
+	\caption{   The ratio of the number of servers used with the optimal method to the servers used using the reinforcement learning method based on time spent}
+	\label{fig:dynamicEpoch2}
+\end{figure}
+The figure \ref{fig:consumptionE}, shows the ratio of the normalized cost to the average number of slices required in the optimal state and the reinforcement learning algorithm.
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale = 0.4]{./fig/consumptionE} %[width=\linewidth] 
+	\caption{  The ratio of the normalized cost to the average number of cuts required in the optimal state and the reinforcement learning algorithm }
+	\label{fig:consumptionE}
+\end{figure}
+\section{Research Plan}
+The table below outlines the goals and six-month planning overall.
+\begin{table}
+ \caption {Research Plan} \label{table:1a}
+ \begin{center}
+  \begin{tabular}{||c c ||}
+  \hline
+Month & Tasks \\ [0.5ex]
+  \hline\hline
+  First Month & Complete the System model for the Intelligent RAN slicing\\
+  \hline
+  Second Month & Find the best method for this system model \\
+  \hline
+  Third Month & Generalized this method for other system models \\
+  \hline
+    Fourth Month & Obtain Numerical Results\\
+  \hline
+    Fifth Month & Write the paper\\
+  \hline
+      Sixth Month & Review the paper\\
+  \hline
+ \end{tabular}
+ \end{center}
+ \end{table}
 

### 2021-10-12 Latex/journal_v1/research plan/main.tex
research plan change

@@
 considered at the same time.
-
 The optimization of baseband
-resources includes O-RU assignment, the assignment of physical resource block
-(PRB), and power allocation.
+resources includes O-RU assignment, the assignment of physical resource blocks
+(PRBs), and power allocation.
 The main problem is a mixed-integer non-linear programming problem that is tremendously difficult.
@@
 \section{Introduction} 
-O-RAN, as the integration and expansion of C-RAN and xRAN, or C-RAN and vRAN is expected to be a key technology in 5G networks to enhance the RAN performance extensively. 
+Open radio access network (O-RAN), as the integration and expansion of cloud RAN (C-RAN) and xRAN, or C-RAN and virtual RAN (vRAN), is expected to be a key technology in 5G networks to enhance the RAN performance extensively.
 The core idea of C-RAN is to divide the radio remote head (RRU) from the baseband unit (BBU).
@@
 Moreover, open north-bound and south-bound interfaces are introduced.
-O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+O-RAN, as illustrated in Fig.
+\ref{fig:c11}, separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
 O-RU is a logical node that contains RF and lowers PHY.
 Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC.
-In addition, the O-CU depicts the logical node contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP).
+In addition, the O-CU depicts the logical node contains two parts: the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP).
 O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
@@
 Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques.
-The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time, implement the algorithms for network intelligence
+The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real-Time, implement the algorithms for network intelligence
 \cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
@@
  Generally, there are two kinds of deep reinforcement learning methods for solving dynamic problems.
-The first class is value-based such as Deep-Q-Network, and the second class is policy-based problems such as DDPG.
+The first class is value-based such as Deep-Q-Network, and the second class is policy-based problems such as
+deep deterministic policy gradient (DDPG).
 The first class can only solve the discrete action space problems, which are integer programming.
@@
 Here, the DDPG method is applied for the lower level and deep Q-network is applied for upper level.
-
 In paper \cite{rezazadeh2021actor}, an actor-critic methods and a continuous model-free deep reinforcement
@@
 \item 
-In this research, we consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, that are massive devices with short packets and low power devices.
+We consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, , which demand short-packet connectivity support for a massive number of low-power devices.
 The problem of RAN slicing for different types of services is studied in this research.
@@
 \item 
-In this research, we consider an intelligent resource allocation in the O-RAN architecture for the different scenarios of services.
-Since, the conventional models cannot perform well in the system because of the different QoS for each service type, and the complexity of dynamic RAN slicing.
+We consider an intelligent resource allocation in the O-RAN architecture for the different services.
+Since conventional models do not perform well here because of the heterogeneous QoS requirements of each service type and the complexity of dynamic RAN slicing.
 So we must switch to machine learning and dynamic methods and find the most suitable approach.
@@
 by estimating of the gradient with respect to the parameters
-of the control policy. In the large-time scale, the deep reinforcement learning is implemented which is a value based algorithm.
+of the control policy. In the large-time scale, the deep Q-Network is implemented which is a value based algorithm and it can find best solution for discrete action-state.
 \item 
-Also, another goal of this project is to apply transfer learning to the system and enhance the performance and the convergence of the methods. 
+We aim to apply transfer learning to the system and study the enhancement of performance and convergence.
+We can use Q-value transfer learning and action-selection transfer learning, So agents can utilize the knowledge of experts to improve their performance on current tasks\cite{zhou2021learning}.
 \end{itemize}
-\section{System Model}
-In this section, first, we  present the system model.
-Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system.
-Afterward, we discuss about assignment of physical data center resources.
-Finally, the main problem is expressed.
+\section{Current State of the Research}
 \subsection{System Model}
-Suppose we have three service types includes eMBB, URLLC, and mMTC.
-Assume we have $S_1$, $S_2$, and $S_3$ different applications for the first, second and third service type, respectively ($S = S_1 + S_2 +S_3$).
-Assume we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
-Each Service $s_j\in \{1,2,...,S_j \} $ consists of $U_{s_j}$ request from the 
-single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
-There are different application request which fall into one of these service categories.
+Assume we have $S$ preallocated slices serving $S$ services contains eMBB, URLLC, and mMTC services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC), , thus $S=S_1+S_2+S_3$.
+Each Service $s\in \{1,2,...,S\} $ consists of $U_{s}$ single-antenna user equipments (UEs) which require certain QoS to be able to use the requested program.
+There are different application requests which fall into one of these service categories.
 Each application request requires specific QoS.
-Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
-Assume each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of $K_{s_j}$, $j \in \{1,2,3\}$ pre-allocated physical resource blocks (PRBs) that obtained in the large-time scale, $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
-
-Also, each VNF instance is running on the virtual machine (VM) that are using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
+Based on the request for the application and QoS, a UE may be admitted and allocated to the resources.
+Assume each slice $s \in \{1,2,...,S \}$, consists of $K_{s}$, pre-allocated physical resource blocks (PRBs)  obtained in the large-time scale, $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+Virtual network functions (VNFs) are functional blocks of the
+system. Each VNF instance is running on a virtual machine (VM) using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
 
@@
 \begin{equation}\label{eq2}
-\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0},
+\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
 \end{equation} 
-where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
+where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
 ${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
@@
 \end{equation}
-Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocate to $s^{th}$ slice or not. 
-Also, $BN_0$ denotes the power of Gaussian additive noise.
-Also, $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
-$e^{k}_{r,u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
+Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
+Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
+\begin{equation}\label{eqI}
+\begin{split}
+I_{r,u(s,i)}^{k} &=
+ \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
+&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
+&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
+\end{split}
+\end{equation}
+where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
+$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
 
@@
 Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th} $, $j \in \{2,3\}$ application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
-So, for the short packet transmission the achievable data rate is approximated from follow
+So, for the short packet transmission the achievable data rate is approximated as follow
 \begin{equation}\label{eq11}
@@
 \end{equation}
-Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
-and $\zeta_{u(s_2,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
-Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
-$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
+where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
+and $\zeta_{u(s_2,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
+where $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
+$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
 $N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
@@
 \subsection{Mean Delay}
-In this part, the end to end mean delay for a service is obtained.
-Suppose the mean total delay is depicted as $T_{tot}$.
+In this part, the end-to-end mean delay for each service is obtained.
+Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,
 \begin{equation}
 \begin{split}
-T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
-T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
-T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
-T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
+T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
+T^{\text{\text{proc}}} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
+T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
+T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}.  \\
 \end{split}
 \end{equation}
-%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
-Total delay is sum of processing delay, transmission delay and propagation delay. 
-The propagation delay is the time takes for a signal to reach to its destination.
-So it has a constant value based on the length of fiber link ($T = L/C_{r}$, where $L$ is the length of link and $C_{r}$ is the capacity of the link).
-Here we assume the value of propagation delay is negligible compared to the rest.
+%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
+%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
+The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the propagation delay ($T^{\text{pro}}$). 
+The propagation delay is the time takes for a signal to reach its destination.
+It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the capacity of the link).
+The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
+Also, the transmission delay is the amount of time required to push all the packets into the fiber link.
+Moreover, it can formulated as 
+$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the sum-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean arrival data rate of each link.
+So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
+In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we ignore the other two delays for simplification;
+So, we assume that the total delay is approximate to the processing delay.
+%Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
+\begin{equation}
+T^{\text{\text{tot}}} \approx T^{\text{proc}}
+\end{equation}
 \subsubsection{Processing Delay}
-Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
-Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.
-
-Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$).
-so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
-since, by using Burke’s Theorem, the mean arrival data rate of the second and third layer which are processed in the first layer is still Poisson with rate $\alpha_{s}$.
+Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ service (or slice).
+Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
+Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$).
+so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,
+Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
+Since, by using Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still poisson with rate $\alpha_{s}$.
 It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
 Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
+Each packet is processed by one of the VNFs of a slice.
+So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
 \begin{equation}
 \begin{split}
-T_{DU}^{s} &= \frac{1}{\mu_d - \alpha_{s}/{M_s^{d}}},\\
-T_{CU}^{s} &= \frac{1}{\mu_c - \alpha_{s}/{M_s^{c}}}\\
-T_{UPF}^{s} &= \frac{1}{\mu_u - \alpha_{s}/{M_s^{u}}}\\
+T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
+T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
+T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},\\
 \end{split}
 \end{equation}
-Where $M_s^{d}$, $M_s^{c}$ and 
-$M_s{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
-Moreover, $1/\mu_d$, $1/\mu_c$ and $1/\mu_u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
+where $M_s^{d}$, $M_s^{c}$ and 
+$M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively. 
+Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively.
 Besides, $\alpha_{s}$ is the  arrival rate which is divided
@@
 
-In addition, $T_{RU}^{s}$ is the mean transmission delay of $s^{th}$ slice on the wireless link.
-The arrival data rate of wireless link is equal to the arrival data rate of load balancers for each service.
- %\cite{frdl}.
-Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
- an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue.
- %\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. 
- Therefore,
-the mean delay of the transmission layer is
+$T_{u(s,i)}^{RU}$ is the mean transmission delay of the $i^{th}$ UE of the $s^{th}$ service on the wireless link.
+ The arrival data rate of wireless link for each UE $i$ of service $s$ is $\lambda_{u(s,i)}$
+As a result, we have $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
+Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
+an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
+
+Therefore, the mean delay of the transmission layer for UE $i$ in slice $s$ is
 \begin{equation}
- T_{RU}^{s} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
+ T_{u(s,i)}^{RU} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}}.
 \end{equation}
-where, $R_{{tot}_s} = \sum_{u=1}^{U_s}a_{u(s,i)}R_{u(s,i)}$ is the total achievable rate of each service.
-So the mean processing delay for each UE in slice $s$ is 
+
+So, the mean processing delay for UE $i$ in slice $s$ is 
 \begin{equation}
-T_{process}^{s} =  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s}
+T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
 \end{equation}
-\subsubsection{Transmission Delay}
-The transmission delay is the amount of time required to push all the packets into the fiber link. 
-Here, we have transmission delay in fronthaul, midhaul, backhaul and the link to transmit data to internet.
-\begin{equation}
-\begin{split}
-T_{front} =& \frac{\alpha_{s}^{f}}{R_f} \\
-T_{mid} =&  \frac{\alpha_{s}^{m}}{R_m} \\
-T_{back} =& \frac{\alpha_{s}^{b}}{R_b} \\
-T_{trans2net} =& \frac{\alpha_{s}^{t}}{R_t} \\
-\end{split}
-\end{equation}
-Where, $R_f$, $R_m$, $R_b$ and $R_t$ are the rate of transmission in fronthaul, midhaul, backhaul and the link to transmit data to internet, respectively.
-Furthermore, the mean arrival data rate of the each link ($\alpha_{s}^i$ , $i \in \{f,m,b,t\}$) is approximately equal to others ($\alpha_{s} \approx \alpha_{s}^i$ , $i \in \{f,m,b,t\}$).  
+Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $.
 \subsection{Reliability of URLLC}
@@
 Each VNF requires
-physical resources that contain memory, storage, CPU and Network Bandwidth.
+physical resources that include memory, storage, CPU and Network Bandwidth.
 Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
@@
 where $\bar{\Omega}_{s}^f\in \mathbb{C}^{4}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f$ indicate the amount of required memory, storage, CPU and and Network Bandwidth, respectively.
-Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice in DU, CU and UPF is defined as below, respectively
+Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice in DU, CU and UPF is defined respectively as follows
 \begin{equation}
 \begin{split}
-&\bar{\Omega}_{\mathfrak{z},s}^{tot,d} = \sum_{f=1}^{M_{s}^d}\bar{\Omega}_{\mathfrak{z},s}^{f,d} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
-&\bar{\Omega}_{\mathfrak{z},s}^{tot,c} = \sum_{f=1}^{M_{s}^c}\bar{\Omega}_{\mathfrak{z},s}^{f,c} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
-&\bar{\Omega}_{\mathfrak{z},s}^{tot,u} = \sum_{f=1}^{M_{s}^u}\bar{\Omega}_{\mathfrak{z},s}^{f,u} \;\; \mathfrak{z} \in \{M, S, C, N\}.\\
+&\bar{\Omega}_{\mathfrak{z},s}^{tot,d} = \sum_{f=1}^{M_{s}^d}\bar{\Omega}_{\mathfrak{z},s}^{f,d},\\
+&\bar{\Omega}_{\mathfrak{z},s}^{tot,c} = \sum_{f=1}^{M_{s}^c}\bar{\Omega}_{\mathfrak{z},s}^{f,c},\\
+&\bar{\Omega}_{\mathfrak{z},s}^{tot,u} = \sum_{f=1}^{M_{s}^u}\bar{\Omega}_{\mathfrak{z},s}^{f,u}, \\
 \end{split}
 \end{equation}
-Where, $\bar{\Omega}_{\mathfrak{z},s}^{f,d}$, $\bar{\Omega}_{\mathfrak{z},s}^{f,c}$ and $\bar{\Omega}_{\mathfrak{z},s}^{f,u}$ are the amount of resource that a VNF required in DU, CU and UPF, respectively.
+$\forall \mathfrak{z} \in \{M, S, C, N\}$, where, $\bar{\Omega}_{\mathfrak{z},s}^{f,d}$, $\bar{\Omega}_{\mathfrak{z},s}^{f,c}$ and $\bar{\Omega}_{\mathfrak{z},s}^{f,u}$ are the amount of resource that a VNF required in DU, CU and UPF, respectively.
+Then,
 \begin{equation}
@@
 \subsection{Power of the O-RU and the Fronthaul Capacity}
-Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. From \eqref{eq2}, we have,
+Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. We have,
 \begin{equation}\label{pr}
@@
 \end{equation*}
-Where,$z_d$ is shown that whether the $d^{th}$ DC is turned on or not and $\psi_d$ is a static cost when a DC is active.
+Where, $z_d$ is shown that whether the $d^{th}$ DC is active or not and $\psi_d$ is a static cost when a DC is active, i.e.,
 \begin{equation}
@@
 \end{equation}  
+Here, we assume that if any VNF placed in a server $d$ is used, the server is on and active, otherwise, it is off.
 In addition, $\phi_{s}$ is obtained from below
@@
 that we have enough physical resources for VNFs of each slice.
-\section{Proposed Algorithm and Numerical Results}
+\subsection{Proposed Algorithm and Numerical Results}
 In this research, we aim to use the machine learning methods such as deep reinforcement learning and deep learning to train the O-RAN system and have an intelligent system.
@@
 The deep learning algorithms contain LSTM and recurrent neural networks. Also, transfer learning is an exciting way to enhance the performance and convergence of the system.
-In this following, the proposed algorithm for the large-time scale is implemented, and part of the numerical results is depicted.
-\subsection{Proposed Algorithm}
+The proposed algorithm for the large-time scale is implemented in the following, and part of the numerical results is depicted.
+\subsubsection{Proposed Algorithm}
 Here we use the reinforcement learning method to solve the above two problems.
@@
 $ P (.
-| S, a) $ is the probability of transfer and $ \gamma \ in (0,1] $ is the discount factor.
+| S, a) $ is the probability of transfer and $ \gamma \in (0,1] $ is the discount factor.
 The $ \Pi (.
@@
 where, $\alpha$ is the learning rate.
-\subsection{Numerical Results}
+\subsection{Preliminary Numerical Results}
 Here, we simplify the large-time scale problem and indicate the numerical results.
@@
 \end{figure}
-The figure \ref{fig:consumptionE}, shows the ratio of the normalized cost to the average number of slices required in the optimal state and the reinforcement learning algorithm.
+Figure \ref{fig:consumptionE}, shows the ratio of the normalized cost to the average number of slices required in the optimal state and the reinforcement learning algorithm.
 \begin{figure}[H]

### 2021-10-13 Latex/journal_v1/research plan/main.tex
add research plan

@@
 Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $.
-\subsection{Reliability of URLLC}
-As we know, UEs request URLLC services, require services with low latency.
-For the M/M/1 system, the probability of the delay for each application $s$ in the UPF, CU, DU and RU is as follow, respectively
-\begin{equation}
-\begin{split}
-P_r\{T_{UPF}^{s} \geq T_{UPF}^{max}\} &= e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}\\
-P_r\{T_{CU}^{s} \geq T_{CU}^{max}\} &= e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}\\
-P_r\{T_{DU}^{s} \geq T_{DU}^{max}\} &= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}\\
-P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} &= e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}\\
-\end{split}
-\end{equation} 
-So the probability of coincidence of these events is as follow
-\begin{equation}
-P_r\{E_1, E_2, E_3, E_4\} = A_1 A_2 A_3 A_4,
-\end{equation}
-Where $E_1 = T_{UPF}^{s} \geq T_{UPF}^{max}$, $E_2 =T_{CU}^{s} \geq T_{CU}^{max} $, $E_3 =T_{DU}^{s} \geq T_{DU}^{max} $ and $E_4 =T_{RU}^{s} \geq T_{RU}^{max} $.
-Also $A_1=e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}$, $A_2=e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}$, $A_3= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}$ and $A_4 = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}$.
+%\subsection{Reliability of URLLC}
+%As we know, UEs request URLLC services, require services with low latency.
+%For the M/M/1 system, the probability of the delay for each application $s$ in the UPF, CU, DU and RU is as follow, respectively
+%\begin{equation}
+%\begin{split}
+%P_r\{T_{UPF}^{s} \geq T_{UPF}^{max}\} &= e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}\\
+%P_r\{T_{CU}^{s} \geq T_{CU}^{max}\} &= e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}\\
+%P_r\{T_{DU}^{s} \geq T_{DU}^{max}\} &= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}\\
+%P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} &= e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}\\
+%\end{split}
+%\end{equation} 
+%So the probability of coincidence of these events is as follow
+%\begin{equation}
+%P_r\{E_1, E_2, E_3, E_4\} = A_1 A_2 A_3 A_4,
+%\end{equation}
+%where $E_1 = T_{UPF}^{s} \geq T_{UPF}^{max}$, $E_2 =T_{CU}^{s} \geq T_{CU}^{max} $, $E_3 =T_{DU}^{s} \geq T_{DU}^{max} $ and $E_4 =T_{RU}^{s} \geq T_{RU}^{max} $.
+%Also $A_1=e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}$, $A_2=e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}$, $A_3= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}$ and $A_4 = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}$.
 \subsection{Physical Data Center Resource}
@@
 \end{equation*}
-Where, $z_d$ is shown that whether the $d^{th}$ DC is active or not and $\psi_d$ is a static cost when a DC is active, i.e.,
+where, $z_d$ is shown that whether the $d^{th}$ DC is active or not and $\psi_d$ is a static cost when a DC is active, i.e.,
 \begin{equation}
@@
 \end{equation}
-Where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively. 
-So the optimization problem is formulated as follow.
-In the large-time scale the aim of the paper is to minimize the power of the system with the presence constraints
-\begin{subequations}
+where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively.
+Here, we want to maximize the energy efficiency $\eta$. 
+So the optimization problem is formulated as follow
+
+\begin{subequations} \label{mainP}
 \begin{alignat}{4}
-\min\limits_{ \boldsymbol{M}, \boldsymbol{Y}, \boldsymbol{E} } \phi_{tot}   \quad &   \ \\
+\max\limits_{ \boldsymbol{M}, \boldsymbol{Y}, \boldsymbol{E},\boldsymbol{P},\boldsymbol{G} } &\eta = \frac{\sum_{s=1}^{S_1}\sum_{i=1}^{U_s}R_{u_{(s,k)}}}{\phi_{tot} +P_r}       \ \\
 \text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
  \label{c11} \\
- &\mathcal{R}_{u_{(s_1,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
-& \phi_{tot}  \leq \phi_{max}, \label{c19} \\
-& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
- &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d} 
- \quad \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c20}
+ &\mathcal{R}_{u_{(s,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
+ &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}, \quad  \mathcal{E} = \{M,S,C, N\}, \label{c14}\\
+&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
+&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
+%&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
+& C_r \leq C^{max}_r \quad \forall r, \label{c15}\\ 
+&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\
+& \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
+& \mathcal{R}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\
+& 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\
+%& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
+& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
+& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18-1} \\
+& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
+& \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\
+& g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
+& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}  
 \end{alignat}
@@
 \end{subequations}
-In the small-time scale the aim of this paper is to maximize the sum rate of UEs  of eMBB services, minimum the delay of UEs of URLLC services, and minimum the power mMTC services with the presence of constraints.
-\begin{subequations}
-\begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S_1}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^e - \sum_{s=1}^{S_2}T^s_{tot} - \sum_{s=1}^{S_3}\sum_{i=1}^{U_s} p_{u_{(s,k)}} \ \\
-\text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
- \label{c11} \\
-&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
-&\mathcal{R}_{u_{(s_1,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
-& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
-&T_{tot}^s \leq T_{tot}^{max,s} \quad \forall s,\label{c16} \\
-& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
-& g^r_{u(s,i)} \leq g^r_{u(s,i)}\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)}  \quad \forall s,i , \label{c18} \\
-\end{alignat}
-\label{constraints}
-\end{subequations}
-where $\boldsymbol{P} =[p_{u(s,i)}] \:\: \forall s , \forall i $, is the matrix of power for UEs,
-$\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i \forall r, \forall k$ indicate the binary variable for PRB association.
-Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i \forall r$ is a binary variable for O-RU association.
-Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
+\noindent where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association.
+Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association.
+Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is the matrix that shows the number of VNFs in each layer of slice.
+Also $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
 the physical DC is mapped to a VNFs of a slice or not.
-Also, $\eta$ is weighted variable to value between the benefit and the cost term of objective function.
-\eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively. 
-Also \eqref{c13}  shows that the rate of each UE requesting eMBB, URLLC and mMTC is more than a threshold, respectively.
-\eqref{c15} and \eqref{c16} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
-\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
- \eqref{c18} guarantee that if a UE in admitted by the system, O-RU and PRB is associated to it, respectively.
-In addition, \eqref{c19} indicate that the static cost of energy of VNFs in each slice do not exceed from the threshold. 
-Moreover, in \eqref{c20}  $\mathcal{E} = \{M,S,C, N\}$ and the constraint supports
-that we have enough physical resources for VNFs of each slice.
+\eqref{c11}, \eqref{c12} and \eqref{c12-1} indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
+Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and uRLLC, is more than a threshold, respectively.
+\eqref{c15} and \eqref{c16} expressed the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
+\eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue model.
+\eqref{c16-3} restricted the number of VNF in each slice due to the limited resources.
+%\eqref{c16} is a reliability condition that the delay in each layer should be less than the threshold.
+\eqref{c17} and \eqref{c18-1} guarantee that O-RU and PRB are associated with the UE, respectively.
+Also, \eqref{c18} ensures that each PRB can not be assigned to more than one UE associated with the same O-RU.
+In addition, \eqref{c19} indicates that the fixed cost of energy of VNFs in each slice does not exceed the threshold. 
+Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
+In addition, in \eqref{c14}, the constraint supports that we have enough physical resources for VNFs of each slice.
 \subsection{Proposed Algorithm and Numerical Results}
+Problem \eqref{mainP}, is a two-time scale problem, i.e., large time scale and small time scale.
+On a large-time scale, we aim to minimize the power of servers and obtain the QoS of slices.
+The assignment of PRB to slices is implemented in this time scale.
+In the small-time scale, the assignment of O-RU to UEs and the assignment of PRB of slices to UEs is executed, and the optimal power is obtained.
 In this research, we aim to use the machine learning methods such as deep reinforcement learning and deep learning to train the O-RAN system and have an intelligent system.
@@
   \end{equation}  
-  Where, $s'$ and $a'$ can be obtained from $\Pi(.|s')$ and $P(.|s,a)$.
+  where, $s'$ and $a'$ can be obtained from $\Pi(.|s')$ and $P(.|s,a)$.
 The goal of reinforcement learnin is to obtain the optimal policy to maximize the $Q^{\Pi}(s,a)$.
@@
 \section{Research Plan}
-The table below outlines the goals and six-month planning overall.
+Table \ref{table:1a}, outlines the goals and six-month planning overall.
+\begin{itemize}
+\item Task 1: Complete the system model and problem formulation, 
+\end{itemize}
+
 \begin{table}

### 2021-10-20 Journal1/lastVersion/pr.tex
paper 2

--- 2021-10-03 Journal1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (1) (1)/pr.tex
@@
 
-\title{Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
+\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
 }
@@
 %  }
-\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
-        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
-        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
+%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
+%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
+%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
+%}
+\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, and Saeede Parsaeefard$^\dagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com\\
+\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada}
  }
@@
 \maketitle
+\pagenumbering{gobble}
 \vspace*{-6em}
@@
 \vspace*{-1.5em}
-Taking advantage of virtual Radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
-O-RAN leads to increased flexibility and openness and reduces operational costs, enabling new capabilities to be added to the network more quickly.
+Taking advantage of virtual radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
+O-RAN leads to increased flexibility, openness, reduces operational costs, and agile deployment.
 O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services including enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
-Deploying network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
+In this paper, we study the problem of service aware baseband resource allocation and virtual network function (VNF) activation in O-RAN system using network slicing to isolate different types of services.
 The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
@@
 Nevertheless, we break it down into two different steps where an iterative algorithm finds near optimal solution.
-In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is achieved.
-The proposed method is confirmed via simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in the literature.
-Also, the simulation results demonstrate less end-to-end delay for the proposed method than the FBDR and baseline scheme.
+In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is achieved.
+The proposed method is validated via simulations which illustrate a higher data rate and lower end-to-end delay compared to existing methods. 
 \end{abstract}
@@
 mMTC service includes a large number of UEs with low data rates and low power.
-Assume each UE in each mMTC service instance requires 0.1 bits/sec/Hz data rate and is not sensitive to the end-to-end delay.
-Also, suppose the fronthaul link and the number of VNFs have no restrictions.
+Assume each UE in each mMTC service instance requires 0.1 bits/sec/Hz data rate and is not sensitive to the end-to-end delay. There is no restriction on fronthaul link capacity and the number of VNFs.
 %Moreover, to make the simulation feasible, we assume that the number of PRBs is as large as the system has low interference.

### 2021-10-20 Latex/journal_v2/research plan/main.tex
paper 2

--- 2021-10-13 Latex/journal_v1/research plan/main.tex
@@
 \begin{itemize}
-\item Task 1: Complete the system model and problem formulation, 
+\item Task 1: Complete the system model and problem formulation
+\begin{itemize}
+\color{darkgray}
+\item In this task, we want to study the O-RAN system and the challenges of it, also we want to analyze the machine learning method in the near-time RIC and non real-time RIC to find the best feasible system model and problem formulation
+\end{itemize}
+\item Task 2: Investigate the best solution for our system model
+\begin{itemize}
+\color{darkgray}
+\item In this task, we want to find the best deep reinforcement learning and deep learning method for our system model.
+We talk a bit about it in the proposed algorithm, but we need to study more about it to find the best solution for our problem and collect the dataset for our system model.
+\end{itemize}
+\item Task 3: Implement the O-RAN system to collect real dataset 
+\begin{itemize}
+\color{darkgray}
+\item In this task, we want to collect a real dataset by implementing the ORAN system for a small cell with low users to obtain a dataset and compare our results with accurate results.
+O-RAN Alliance and Open network foundation are two different groups that implement the software of the ORAN system.
+I plan to implement the ORAN system on the server to obtain different datasets and face the challenges of this system.
+\end{itemize}
+\item Task 4: Obtain the numerical results
+\begin{itemize}
+\color{darkgray}
+\item In this task, we want to obtain the numerical results from different methods and compare them with each other for our paper
+\end{itemize}
+\item Task 5: Generalized our method for other feasible system models
+\begin{itemize}
+\color{darkgray}
+\item In this task, we want to generalized our methods for two time scale  ORAN system models  
+\end{itemize}
+\item Task 6: Write the paper
+\begin{itemize}
+\color{darkgray}
+\item In this task, we want to write and review the paper
+\end{itemize}
 \end{itemize}
@@
   \hline
-  Third Month & Generalized this method for other system models \\
+  Third Month & Implement the O-RAN system to collect real dataset  \\
   \hline
@@
   \hline
-    Fifth Month & Write the paper\\
+    Fifth Month & Generalized our method for other feasible ORAN system models\\
   \hline
-      Sixth Month & Review the paper\\
+      Sixth Month & Write and review the paper\\
   \hline

### 2021-10-20 Latex/journal_v2/version1/pr.tex
paper 2

--- 2021-10-13 Latex/journal_v1/research plan/main.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
- \usepackage{enumerate}
+ %\pdfoutput=1
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage[T1]{fontenc}
 \usepackage{cite}
-%\usepackage{caption}
-%\usepackage{subcaption}
 \usepackage{mathtools}
@@
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
+\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
 \usepackage{graphicx}
-\usepackage{blindtext}
 \usepackage{textcomp}
@@
 \usepackage[margin=0.7in]{geometry}
-\usepackage[export]{adjustbox}
-
-\title{Reporte de inventario de eviencias}
-\author{Natalia Galeano Valerio}
-\date{Octubre 2019}
-
+\setlength{\columnsep}{11mm}
 \begin{document}
 
-\baselineskip 12pt
+\title{Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}
+}
+%
+%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%mojdeh.karbalaee@ut.ac.ir}
+%\and
+%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%vmansouri@ut.ac.ir}
+%\and
+%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%salar.nouri@ut.ac.ir}
+%}
+  \author{
+    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
+    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
+    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
+    \vspace{-.2cm}
+  }
+  }
 
-\vspace*{30mm}
+\maketitle
 
-\begin{center}
+\begin{abstract}
 
-\textbf{\Large Research Plan} \\
-\vspace{10mm}
-\textbf{Department of Electrical and Computer Engineering}\\
-\vspace{20mm}
-{\large University of Oulu}\\
-\vspace{20mm}
-\end{center}
-\vspace{10mm}
-{\scriptsize Provisional title:}\\
-Dynamic Resource Allocation in O-RAN Architecture using Network Slicing\\
-
-\vspace{20mm}
-
-{\scriptsize Candidate name}\\
-Mojdeh Karbalaee Motalleb \\
-\vspace{3mm}
-
-{\scriptsize Supervisor name:}\\
-Dr. Onel Lopez\\
-\vspace{3mm}
-
-\pagebreak
-\begin{abstract}
-Open radio access network (O-RAN) is the next generation of RAN systems introduced by the O-RAN Alliance to increase the flexibility and the openness of the network systems and simultaneously decrease CAPEX and OPEX of mobile operators.
-The O-RAN system combines and takes advantage of Cloud RAN (C-RAN) and the Virtual RAN (VRAN).
-O-RAN separates RAN into three
-different units, namely Radio Unit (O-RU), Distributed Unit
-(O-DU), and Central Unit (O-CU).
-In this research, we study
-the problem of baseband resource allocation and virtual
-network function (VNF) activation in O-RAN architecture
-based on their service priority for different types of 5G services
-including enhanced mobile broadband (eMBB), ultra-reliable
-low latency communications (uRLLC) and massive Machine
-Type Communications (mMTC) services using intelligent RAN slicing. 
-Network slicing is a promising solution for supporting such heterogeneous and challenging services.
-Deploying network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed. The limited
-fronthaul capacity, the restriction of end-to-end delay and the reliability of the services are
-considered at the same time.
-The optimization of baseband
-resources includes O-RU assignment, the assignment of physical resource blocks
-(PRBs), and power allocation.
-The main problem is a mixed-integer non-linear programming problem that is tremendously difficult.
-Since the problem has a two-time scale, it can be broken into two layers.
-On the large-time scale, the problem of obtaining the optimal number of VNF, the placement of VNFs, and the assignment of PRB to the slices are considered.
-On the small-time scale, there is a problem of obtaining the optimal power of UEs, and the PRB and O-RU assignment.
-To solve the problem, we propose deep reinforcement learning, the deep deterministic policy gradient (DDPG) method, and convex optimization.
 \end{abstract}
 \section{Introduction}
-Open radio access network (O-RAN), as the integration and expansion of cloud RAN (C-RAN) and xRAN, or C-RAN and virtual RAN (vRAN), is expected to be a key technology in 5G networks to enhance the RAN performance extensively.
-The core idea of C-RAN is to divide the radio remote head (RRU) from the baseband unit (BBU).
-Also, several BBUs are placed together to create the BBU-pool, providing unified baseband signal processing with powerful computing capabilities.
-On the other hand, xRAN technology has three fundamental features.
-The control plane is decoupled from the user plane.
-Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware.
-Moreover, open north-bound and south-bound interfaces are introduced.
-O-RAN, as illustrated in Fig.
-\ref{fig:c11}, separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-O-RU is a logical node that contains RF and lowers PHY.
-Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC.
-In addition, the O-CU depicts the logical node contains two parts: the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP).
-O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
-O-DU and O-CU are connected via an open and well-defined interface F1.
-Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
-The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
-RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
-One of the necessities of the new generation of wireless networks is its intelligence.
-Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques.
-The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real-Time, implement the algorithms for network intelligence
-\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
+
 \begin{figure*}
@@
 
-One of the goals of the next generation of mobile systems is to strictly meet the stringent QoS demands of the different services introduced in 5G , i.e., eMBB, URLLC, and mMTC.
-Network slicing is a promising solution to obtain the QoS for each type of service.
-Network slicing contains RAN slicing, core slicing, and both of them together.
-Efficient slicing of RAN is still challenging due to time-varying network circumstances.
-%Network slicing will propose significant complexity into the performance of systems that causes conventional mathematical model-based procedures to network operation no longer adequate. 
-Network slicing creates considerable complexity in system performance and makes the conventional mathematical methods insufficient to model the network.
-Therefore, it motivates researchers to realize network slicing using machine learning strategies such as deep learning and deep reinforcement learning.
-So, the network can reach the best control policy according to its experience in the past time slots.
-As mentioned above, network slicing, which contains RAN slicing, core slicing, and the whole, is considered a hot topic for vendors.
-In addition, the O-RAN system seems to be the next RAN architecture.
-So, this motivated researchers to study the dynamic RAN slicing in O-RAN architecture to achieve the desired QoS for each service type.
-In addition, according to the high complexity of RAN slicing and incapability of the traditional model-based methods, dynamic machine learning becomes the best solution for these problems.
- Generally, there are two kinds of deep reinforcement learning methods for solving dynamic problems.
-The first class is value-based such as Deep-Q-Network, and the second class is policy-based problems such as
-deep deterministic policy gradient (DDPG).
-The first class can only solve the discrete action space problems, which are integer programming.
-The second class can solve by searching the optimal policy, which is the actor-critic method.
-Here, we use the second method to solve our problems \cite{alsenwi2021intelligent,yan2019intelligent,mei2021intelligent}.
-\subsection{Related Works} 
-In \cite{mei2021intelligent}, the authors proposes a new intelligent RAN slicing method with two-layered control granularity, which aims at maximizing both the long-term QoS of services and spectrum efficiency (SE) of slices.
-In this paper, the authors design a RAN slicing strategy with multiple time and
-resource granularities to accommodate the time-varying network conditions and diverse QoS requirements.
-Here, the DDPG method is applied for the lower level and deep Q-network is applied for upper level.
-In paper \cite{rezazadeh2021actor}, an actor-critic methods and a continuous model-free deep reinforcement
-learning (DRL) method is applied to minimize energy consumption and virtual network function (VNF) instantiation cost.
-Multiplexing eMBB and uRLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
-In \cite{setayesh2020joint,yang2020should}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
-Paper \cite{alsenwi2021intelligent}, represents a joint convex method and deep reinforcement learning to schedule both eMBB and URLLC services.
-Here we have two time-scale, a two-phase-framework, including eMBB resource allocation and URLLC scheduling phases.
-In \cite{saggese2021power}, the problem of power minimization for uRLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
- In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and URLLC services.
-The system guarantees the latency, the service rate, and the maintenance of reliability.
-
 \subsection{Main Contributions}
-In this research, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
-Here, we study a single-cell downlink situation involving multiple network slices that share existing radio sources.
+In this paper, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
+Here, we examine a single-cell downlink system involving multiple network slices that share existing radio sources.
 The main contributions of
@@
 of the control policy. In the large-time scale, the deep Q-Network is implemented which is a value based algorithm and it can find best solution for discrete action-state.
-\item 
-We aim to apply transfer learning to the system and study the enhancement of performance and convergence.
-We can use Q-value transfer learning and action-selection transfer learning, So agents can utilize the knowledge of experts to improve their performance on current tasks\cite{zhou2021learning}.
 \end{itemize}
@@
 where, $\alpha$ is the learning rate.
-\subsection{Preliminary Numerical Results}
-Here, we simplify the large-time scale problem and indicate the numerical results.
-The numerical results for this problem (which is the VNF placement) can be shown as follow. 
-\begin{subequations}
-	\begin{alignat}{4}
-		\min\limits_{\boldsymbol{Y} }   \quad &   \psi_{tot}(\boldsymbol{Y})(t)\\
-		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c} y_{s,d}(t) \geq 1 \quad \forall s, \\
-		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d} \quad  \forall d, \forall ;  \label{eqomega}
-	\end{alignat}
-\end{subequations}
-Suppose we have just one limited resource (CPU in each server).
-The ratio of the number of the used-servers  with the optimal method to the used-servers with the Q-learning method based on time spent can be shown as figure \ref{fig:dynamicEpoch2}.
-In this figure, after about 900 epochs, the algorithm converges to the 0.9 of optimal solution.
-\begin{figure}[H]
-	\centering
-	\includegraphics[scale = 0.4]{./fig/ratio_episode2} %[width=\linewidth] 
-	\caption{   The ratio of the number of servers used with the optimal method to the servers used using the reinforcement learning method based on time spent}
-	\label{fig:dynamicEpoch2}
-\end{figure}
-Figure \ref{fig:consumptionE}, shows the ratio of the normalized cost to the average number of slices required in the optimal state and the reinforcement learning algorithm.
-\begin{figure}[H]
-	\centering
-	\includegraphics[scale = 0.4]{./fig/consumptionE} %[width=\linewidth] 
-	\caption{  The ratio of the normalized cost to the average number of cuts required in the optimal state and the reinforcement learning algorithm }
-	\label{fig:consumptionE}
-\end{figure}
-\section{Research Plan}
-Table \ref{table:1a}, outlines the goals and six-month planning overall.
-\begin{itemize}
-\item Task 1: Complete the system model and problem formulation, 
-\end{itemize}
-
-\begin{table}
- \caption {Research Plan} \label{table:1a}
- \begin{center}
-  \begin{tabular}{||c c ||}
-  \hline
-Month & Tasks \\ [0.5ex]
-  \hline\hline
-  First Month & Complete the System model for the Intelligent RAN slicing\\
-  \hline
-  Second Month & Find the best method for this system model \\
-  \hline
-  Third Month & Generalized this method for other system models \\
-  \hline
-    Fourth Month & Obtain Numerical Results\\
-  \hline
-    Fifth Month & Write the paper\\
-  \hline
-      Sixth Month & Review the paper\\
-  \hline
- \end{tabular}
- \end{center}
- \end{table}
 
@@
 \bibliography{ref}
-%\begin{thebibliography}{9}
-%\bibitem{Hunt}
-%Sally Hunt, ``Making Competition Work in Electricity,'' John Wiley , pp.23-30, Fev, 2002.
-
-%\end{thebibliography}
-\vspace{20mm}
-
 \end{document}

### 2021-10-30 Latex/journal_v2/research plan/main.tex
add research plan

@@
 \vspace{20mm}
-{\large University of Oulu}\\
+%{\large University of Oulu}\\
+{\large University of Tehran}\\
 \vspace{20mm}
@@
 
-{\scriptsize Supervisor name:}\\
-Dr. Onel Lopez\\
+%{\scriptsize Supervisor name:}\\
+%Dr. Onel Lopez\\
 \vspace{3mm}
@@
 \item 
-The system has a two-time scale and should be solved in two layers.
-On a large-time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed.
+Here, we separate the scheduling into two-time scales.
+So we considered the two-time scale system and solved it in two layers.
+On a large time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed.
 Also, the assignment of PRB to the slices is obtained.
-On a small-time scale, the problem of power allocation, O-RU association and the assignment of PRB to UE in each slice is applied.
+On a small-time scale, the problem of power allocation, O-RU association, and the assignment of PRB to UE in each slice is applied.
 \item 
-We consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, , which demand short-packet connectivity support for a massive number of low-power devices.
+We consider three types of services that requires specific QoS: i) URLLC, which requires low latency and high reliability; ii) eMBB, which needs high data rate; and iii) mMTC, which demand short-packet connectivity support for a massive number of low-power devices.
 The problem of RAN slicing for different types of services is studied in this research.
@@
 \begin{equation}
-\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
+\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}.
 \end{equation}
@@
 \mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
-\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
+\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r},
 \end{split}
@@
 \begin{split}
-\mathcal{R}_{u(s_2,i)}^{\mathfrak{u},r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}, \quad \mathfrak{u} \in  \{u,m\} \\
-\mathcal{R}_{u(s_1,i)}^{\mathfrak{u}} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 
+\mathcal{R}_{u(s_2,i)}^{\mathfrak{u},r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}, \quad \mathfrak{u} \in  \{u,m\}, \\
+\mathcal{R}_{u(s_1,i)}^{\mathfrak{u}} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r}, 
 \end{split}
@@
 In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we ignore the other two delays for simplification;
-So, we assume that the total delay is approximate to the processing delay.
+So, we assume that the total delay is approximate to the processing delay, i.e.,
 %Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
 \begin{equation}
-T^{\text{\text{tot}}} \approx T^{\text{proc}}
+T^{\text{\text{tot}}} \approx T^{\text{proc}}.
 \end{equation}
@@
       0 & \text{otherwise}
-    \end{cases}       
+    \end{cases}.       
 \end{equation}  
@@
 \begin{equation}
-\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d
+\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d,
 \end{equation}
@@
 In addition, in \eqref{c14}, the constraint supports that we have enough physical resources for VNFs of each slice.
-\subsection{Proposed Algorithm and Numerical Results}
+\subsection{AI Approaches and Numerical Results}
 Problem \eqref{mainP}, is a two-time scale problem, i.e., large time scale and small time scale.
@@
 The proposed algorithm for the large-time scale is implemented in the following, and part of the numerical results is depicted.
-\subsubsection{Proposed Algorithm}
+\subsection{AI Approaches} \label{AIP}
 Here we use the reinforcement learning method to solve the above two problems.
@@
 | S) $ policy is represented by $ Q ^ {\Pi} (s, a) $.
-We have the following relations on this basis.
+We have the following relations on this basis:
 \begin{equation}
-	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[\sum_{t=0}^{\infty}\gamma^tR_t|S_0=s]
+	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[\sum_{t=0}^{\infty}\gamma^tR_t|S_0=s],
  \end{equation}
- The Q-value is as below.
+ The Q-value is as follows
  \begin{equation}
@@
 
-  $\mathbb{E}$ represented the statistical average. 
- Based on the Bellman equation we have
+ Here $\mathbb{E}$ represents the statistical average. 
+ Based on the Bellman equation, we have
  \begin{equation}
-	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[R+\gamma V^{\Pi}(s')]
+	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[R+\gamma V^{\Pi}(s')],
 \end{equation}  
@@
    \begin{equation}
-  	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[R+\gamma Q^{\Pi}(s',a')]
+  	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[R+\gamma Q^{\Pi}(s',a')],
   \end{equation}  
@@
 \begin{equation}
-	T^{*}Q(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q(s',a')]
+	T^{*}Q(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q(s',a')].
 \end{equation} 
@@
 \begin{equation}
-	Q(s_{t+1},a_{t+1}) = Q(s_t,a_t)+\alpha[ r_{t+1} + \gamma \max_{a \in A}{Q(s_{t+1},a)}-Q(s_t,a_t)]
+	Q(s_{t+1},a_{t+1}) = Q(s_t,a_t)+\alpha[ r_{t+1} + \gamma \max_{a \in A}{Q(s_{t+1},a)}-Q(s_t,a_t)],
 \end{equation}
@@
 		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c} y_{s,d}(t) \geq 1 \quad \forall s, \\
-		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d} \quad  \forall d, \forall ;  \label{eqomega}
+		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d} \quad  \forall d;  \label{eqomega}
 	\end{alignat}
@@
 \color{darkgray}
-\item In this task, we want to study the O-RAN system and the challenges of it, also we want to analyze the machine learning method in the near-time RIC and non real-time RIC to find the best feasible system model and problem formulation
+\item In this task, we want to study the O-RAN system and the corresponding challenges.
+Also, we want to analyze the machine learning method in the near real-time RIC and non real-time RIC to find the best feasible system model and problem formulation.
 \end{itemize}
-\item Task 2: Investigate the best solution for our system model
+\item Task 2: Investigate the suitable solution for our system model
 \begin{itemize}
 \color{darkgray}
-\item In this task, we want to find the best deep reinforcement learning and deep learning method for our system model.
-We talk a bit about it in the proposed algorithm, but we need to study more about it to find the best solution for our problem and collect the dataset for our system model.
+\item In this task, we want to find the suitable deep reinforcement learning and deep learning methods for our system model.
+We have some preliminary ideas as discussed in Section \ref{AIP}, but we need to study more about it to find the best solution for our problem and collect the dataset for our system model.
 \end{itemize}
@@
 \color{darkgray}
-\item In this task, we want to collect a real dataset by implementing the ORAN system for a small cell with low users to obtain a dataset and compare our results with accurate results.
+\item In this task, we want to collect a real dataset by implementing the ORAN system for a small cell with few users to obtain a dataset and compare our simulation results with actual results obtained from the real implementation of ORAN.
 O-RAN Alliance and Open network foundation are two different groups that implement the software of the ORAN system.
@@
 \color{darkgray}
-\item In this task, we want to obtain the numerical results from different methods and compare them with each other for our paper
+\item In this task, we want to obtain the numerical results from different methods and compare them with each other for our paper.
 \end{itemize}
-\item Task 5: Generalized our method for other feasible system models
+\item Task 5: Generalize our method for other feasible system models
 \begin{itemize}
 \color{darkgray}
-\item In this task, we want to generalized our methods for two time scale  ORAN system models  
+\item In this task, we want to generalize our methods for two-time scale ORAN system models.
+For instance, we consider generalizing the system model with other parameters such as UE admission, priority, and reliability.
 \end{itemize}
@@
 \color{darkgray}
-\item In this task, we want to write and review the paper
+\item In this task, we want to write, review and finally submit the paper.
 \end{itemize}
@@
   \hline
-    Fifth Month & Generalized our method for other feasible ORAN system models\\
+    Fifth Month & Generalize our method for other feasible ORAN system models\\
   \hline
-      Sixth Month & Write and review the paper\\
+      Sixth Month & Write, review and finally submit the paper\\
   \hline

### 2021-10-30 Journal1/LastVersion/pr.tex
add journLal1

--- 2021-10-20 Journal1/lastVersion/pr.tex
@@
 \setlength{\dbltextfloatsep}{-20pt}
+
 \begin{document}
 
-\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
+\title{Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
 }
+%\pagestyle{plain}
 %%%%%%%%%%%%%%%
@@
 %  }
-%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
-%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
-%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
-%}
-\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, and Saeede Parsaeefard$^\dagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com\\
-\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada}
+%%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
+%%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
+%%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
+%%}
+
+\author{Mojdeh Karbalaee Motalleb \and Vahid Shah-mansouri \and Saeede Parsaeefard \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com\\
+\IEEEauthorblockA{School of ECE, University of Tehran, Iran, University of Toronto, Canada}
  }
@@
 %Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
+\vspace*{-1.5em}
 \subsection{VNF Power}
@@
 Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
+\vspace*{-4em}
 \section{Proposed Algorithm}\label{proAlg}
+\vspace*{-1em}
 In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
@@
 mMTC service includes a large number of UEs with low data rates and low power.
-Assume each UE in each mMTC service instance requires 0.1 bits/sec/Hz data rate and is not sensitive to the end-to-end delay. There is no restriction on fronthaul link capacity and the number of VNFs.
+Assume each UE in each mMTC service instance requires 0.1 bits/sec/Hz data rate and is not sensitive to the end-to-end delay.
+Also, suppose the fronthaul link and the number of VNFs have no restrictions.
 %Moreover, to make the simulation feasible, we assume that the number of PRBs is as large as the system has low interference.

### 2021-10-30 Latex/journal_v1/research plan/main.tex

@@
 One of the goals of the next generation of mobile systems is to strictly meet the stringent QoS demands of the different services introduced in 5G , i.e., eMBB, URLLC, and mMTC.
-Network slicing is a promising solution to obtain the QoS for each type of service.
+Network slicing is a promising solution to meet the QoS requirements of each type of service.
 Network slicing contains RAN slicing, core slicing, and both of them together.
@@
 \item 
-We consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, , which demand short-packet connectivity support for a massive number of low-power devices.
+We consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, which demand short-packet connectivity support for a massive number of low-power devices.
 The problem of RAN slicing for different types of services is studied in this research.
@@
 Since conventional models do not perform well here because of the heterogeneous QoS requirements of each service type and the complexity of dynamic RAN slicing.
-So we must switch to machine learning and dynamic methods and find the most suitable approach.
+We switch to machine learning and dynamic methods and find the most suitable approach.
 A dynamic strategy of resource allocation is required to solve this problem to achieve the specific QoS for each type of service in the O-RAN architecture.
@@
 \subsection{System Model}
-Assume we have $S$ preallocated slices serving $S$ services contains eMBB, URLLC, and mMTC services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC), , thus $S=S_1+S_2+S_3$.
+Assume we have $S$ preallocated isolated slices serving $S$ services contains eMBB, URLLC, and mMTC services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC), thus $S=S_1+S_2+S_3$.
 Each Service $s\in \{1,2,...,S\} $ consists of $U_{s}$ single-antenna user equipments (UEs) which require certain QoS to be able to use the requested program.

### 2021-11-24 Journal1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (2)/pr.tex
paper1
add paper1

--- 2021-10-20 Journal1/lastVersion/pr.tex
@@
 Network slicing is the best solution for this aim.
+Network slicing can support the heterogeneity of services by allocating different resources to each slice serving specific services to guarantee QoS, and isolating each service from the other services.
 A network slice is an end-to-end logical network that offers services with specific needs.  
@@
 Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 
-Three types of services are introduced for 5th generation celluar networks, namely, enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services.
+5G wireless systems have talked about supporting three generic services in recent years, namely, enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services.
 Each type of service requires a particular slice of network based on its QoS.
-eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and throughout coverage.
+eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and throughput coverage.
 URLLC requires low latency  and high reliability. URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
@@
 \subsection{Main Contributions}
-This study aims to optimize baseband resource allocation i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
-In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
-The main contributions of this paper are summarized as follow:
+The purpose of this study is to optimize baseband resource allocation i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN system.
+The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presents of the three generic service types introduced in 5G using RAN slicing.
+In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
 \begin{itemize}
@@
 
-In this section, we describe the downlink system in O-RAN with slicing as depicted in Figure \ref{fig:c11}. 
+In this section, we describe the downlink system in O-RAN using RAN slicing as depicted in Figure \ref{fig:c11}. 
 Firstly, we present the system model.

### 2021-11-24 Journal1/paper1TNSM/pr.tex
change paper 1 after reviewing tnsm template 13 page

--- 2021-11-24 Journal1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (2)/pr.tex
@@
 %\documentclass[conference]{IEEEtran}
-\documentclass[journal,draftcls,onecolumn,12pt,twoside]{IEEEtranTCOM}
+\documentclass[lettersize,journal]{IEEEtran}
 \normalsize
@@
 \usepackage{caption}
+\captionsetup{font=footnotesize}
 \usepackage{algcompatible}
@@
 \usepackage{stackengine}
+%\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
 \def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
@@
 \usepackage{algorithm}
+\usepackage{algorithmicx}
+%\usepackage{algorithmic,algorithm2e,float}
 \usepackage[noend]{algpseudocode}
 \usepackage{amsthm}
+\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\usepackage{balance}
 \allowdisplaybreaks
@@
 \newcommand{\abstracttextfont}{\normalfont\small}
-\setlength{\belowcaptionskip}{-25pt}
-\setlength{\dbltextfloatsep}{-20pt}
+\setlength{\belowcaptionskip}{-10pt}
+%\setlength{\dbltextfloatsep}{-20pt}
 \begin{document}
@@
  }
-
 \maketitle
 \pagenumbering{gobble}
-\vspace*{-6em}
+%\vspace*{-4em}
 \begin{abstract}
-\vspace*{-1.5em}
+%\vspace*{-1.5em}
 Taking advantage of virtual radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
@@
 \end{itemize}  
-
 \begin{figure*}
@@
   \captionsetup{justification=centering}
-    \includegraphics[scale = 0.6]{finalDraw.pdf}
+    \includegraphics[scale = 0.45]{finalDraw.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 \end{figure*}
-
 The rest of this paper is organized as follows.
@@
 Section \ref{conc} concludes the  paper.
-
 \section{System Model and Problem Formulation}\label{systemmodel}
-
 In this section, we describe the downlink system in O-RAN using RAN slicing as depicted in Figure \ref{fig:c11}. 
@@
 So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.
+So we have
+$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
+$\{1,2,...,S_3\}$ set of mMTC service instances.
 Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
@@
 Based on the application and QoS request, UE may be admitted and allocated to the resources.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+The VNFs of O-DU, O-CU-UP, and UPF are interconnected, defined as the Service Function Chain (SFC) in the O-RAN system.
+
 Assume we have $K$ physical resource blocks (PRBs) in this system.
@@
 \begin{equation}
-\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
-\end{equation}
+\bold{w}_{r,u(s,i)}^{k} = \hat{\bold{h}}_{r,u(s,i)}^{k}(\hat{\bold{h}}_{r,u(s,i)}^{H \: k} \hat{\bold{h}}_{r,u(s,i)}^{k})^{-1}
+\end{equation}
+
+The channel state information is imperfect. So, the channel gain is known with errors; the imperfection of channel estimation is shown as
+$\hat{\boldsymbol{h}}_{r,u(s,i)} = \boldsymbol{h}_{r,u(s,i)} + \Delta \boldsymbol{h}_{r,u(s,i)}$.
+$\Delta \boldsymbol{h}_{r,u(s,i)}$ indicates the estimating error vector with a Gaussian distribution of
+$\Delta \boldsymbol{h}_{r,u(s,i)}\backsim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$.
+where $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$
+
 Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
@@
 T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
-T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}.  \\
+T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}. 
 \end{alignat}
@@
 T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
-T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},\\
+T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
 \end{split}
@@
 \subsection{Problem Statement}
-Suppose slice $s$ (which is assigned to service s) has the priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$.
+Suppose slice $s$ (which is assigned to service s) has the priority factor $\delta_s$ (based on the priority of its hosting service) where $\sum_{s=1}^S \delta_s =1$.
 The priority factor of each slice is obtained according to the service level agreement (SLA) of that service to have a fairness in the system. 
@@
 Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
+\vspace*{-1.7em}
 \section{Proposed Algorithm}\label{proAlg}
@@
 Here, we first simplify and relax the parameters to convexify the problem.
-
 As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
@@
 So, a lower bound for \eqref{eq11} is given that is a concave function.
-\begin{equation}
-\begin{split}
+\begin{subequations}
+\begin{alignat}{4}
 \bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
@@
  \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
- \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}\\
-\end{split}
-\end{equation}
+ \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
+\end{alignat}
+\end{subequations}
 Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability.
@@
 where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
-
 \end{lemma}
@@
 %\end{equation}
-
 The left side of the equation \eqref{eqDelay}, leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
@@
 \varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\\
-& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}\\
+& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}
 \end{alignat}
@@
 \end{proof}
-
 Despite simplifying the problem in \eqref{problem}, it is still non-convex and hard to solve.
@@
 \end{subequations}
-
 %{\color{red} Motivate the lemma. separate proof and lemma}
-
 \begin{lemma}
-
 The derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{P}$ and $\boldsymbol{E}$ give the Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal value of these two variables \cite{lee2018dynamic,ali2018joint}.
@@
 p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
- &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
+ &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.
 \end{alignat}
@@
 &- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
-&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
+&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.
 \end{alignat}
@@
 \begin{algorithm}
+\small
 %\setstretch{1.}
@@
  \begin{algorithm}
+ \small
 \caption{Iterative algorithm for the baseband resource allocation and VNF activation (IABV)}\label{alg2}
@@
  \begin{algorithm}
+ \small
 \caption{Fast Algorithm (FA) to Check the Convergence}\label{alg3}
@@
 \end{algorithm} 
- \vspace*{-3em}
+\vspace*{-2em}
 \section{Numerical Results and The Feasible Region}\label{NE}
-
 In this section, firstly, we describe the initial points and the comparison algorithms.
@@
 We consider three network slices for eMBB, URLLC, and mMTC services.
-Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in table \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
-%\begin{figure}
-%  \centering 
-%    \includegraphics[scale = 0.47]{cell.pdf}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{O-RU placement in a cell}
-%  \label{fig:cell}
-%\end{figure}
-\begin{table}%
+Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
+\begin{figure}
   \centering 
-\parbox{0.4\textwidth}{
-\begin{footnotesize}
- \scalebox{0.75}{
+    \includegraphics[scale = 0.3]{cell.pdf}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{O-RU placement in a cell}
+  \label{fig:cell}
+\end{figure}
+Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
+Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
+We consider 25 PRBs are used in the network and the packet size is equal to 20 bytes.
+The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
+Also, the quantization noise is assumed to be $10^{-13}$.
+Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a}.
+\begin{table}[H]
+ \caption {Simulation Parameters} \label{table:1a}
+ \begin{center}
+ \scalebox{0.9}{
   \begin{tabular}{||c | c ||}
@@
  \end{tabular}}
-\end{footnotesize}
- \caption {Simulation Parameters} \label{table:1a}
-}
-\qquad
-\begin{minipage}[c]{0.53\textwidth}%
-\centering
-\includegraphics[scale = 0.32]{cell.pdf}
-  \caption{O-RU placement in a cell}
-  \label{fig:cell}
-\end{minipage}
+ \end{center}
  \end{table} 
-Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
-Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
-We consider 25 PRBs are used in the network and the packet size is equal to 20 bytes.
-The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
-Also, the quantization noise is assumed to be $10^{-13}$.
-Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a}.
-%\begin{table}
-% \caption {Simulation Parameters} \label{table:1a}
-% \begin{center}
-% \scalebox{0.7}{
-%  \begin{tabular}{||c | c ||}
-%  \hline
-%Parameter & Value \\ [0.5ex]
-%  \hline\hline
-%  Noise power & -174dBm\\
-%  \hline
-%  Bandwidth & 180 KHz \\
-%  \hline
-% Maximum transmit Power of each O-RU & 40dBm \\
-%  \hline
-%  Maximum delay for eMBB &  4msec \\
-%  \hline
-%    Maximum delay for URLLC &  1msec \\
-%  \hline
-%  Maximum delay for mMTC &  5msec \\
-%  \hline
-%  Maximum fronthaul capacity  & 46 bits/sec/Hz \\
-%   \hline
-%  Minimum data rate for eMBB &  20 bits/sec/Hz \\ 
-%  \hline
-%   Minimum data rate for URLLC and mMTC &  2 bits/sec/Hz \\ 
-%  \hline
-%   Maximum received power for mMTC &  20 dBm \\ [.5ex]   
-%  \hline
-%    Maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]   
-%  \hline
-% \end{tabular}}
-% \end{center}
-% \end{table}
-
 Finding a feasible initial value is almost tricky.
@@
 In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels and the channel distance.
-
 \vspace*{-2em}
@@
 For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interference.
-Another solution is to remove the simulations in the mont-Carlo that do not converge.
+Another solution is to remove the simulations in the Monte-Carlo that do not converge.
 In the simulation part, if more than half of the iterations have a feasible solution for the initial condition, the simulation can be displayed as a feasible model.
@@
 Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
-\begin{figure}%[!tbp]
+\begin{figure*}%[!tbp]
   \centering
@@
   \begin{minipage}[b]{0.4\textwidth}
-    \includegraphics[scale = 0.4]{Arate_ue1.eps}
+    \includegraphics[scale = 0.3]{Arate_ue1.eps}
     \caption{Aggregate throughput vs. number of UEs in each service}% in the presence of three services}
@@
   \begin{minipage}[b]{0.4\textwidth}
-       \includegraphics[scale = 0.4]{vnfNum1.eps}
+       \includegraphics[scale = 0.30]{vnfNum1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
   \end{minipage}
-\end{figure}
+\end{figure*}
 %%%%%%%%%
@@
 Moreover, the proposed method (IABV), gives higher aggregate rates in compared to the FBDR and the baseline scheme.
-\begin{figure}%[!tbp]
+\begin{figure*}%[!tbp]
   \centering
@@
   \begin{minipage}[b]{0.4\textwidth}
-    \includegraphics[scale = 0.4]{RatePower1.eps}
+    \includegraphics[scale = 0.3]{RatePower1.eps}
     \caption{Aggregate Throughput for eMBB vs. Maximum Transmit power for various number of UEs }
@@
   \begin{minipage}[b]{0.4\textwidth}
-      \includegraphics[scale = 0.4]{delay_new.eps}
+      \includegraphics[scale = 0.3]{delay_new.eps}
   \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}% for various number of UEs}
@@
   \end{minipage}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \begin{minipage}[b]{0.4\textwidth}
-    \includegraphics[scale = 0.4]{delay1_new.eps}
+    \includegraphics[scale = 0.3]{delay1_new.eps}
     \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}% for different methods}
@@
   \begin{minipage}[b]{0.4\textwidth}
-       \includegraphics[scale = 0.36]{AmmTCpower.eps}
+       \includegraphics[scale = 0.3]{AmmTCpower.eps}
   \caption{Aggregate Throughput vs. Number of UEs in each Service for three different mMTC services}
@@
   \captionsetup{justification=centering}
-        \includegraphics[scale = 0.4]{priorityLast.eps}
+        \includegraphics[scale = 0.3]{priorityLast.eps}
   \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
@@
   \begin{minipage}[b]{0.4\textwidth}
-     \includegraphics[scale = 0.4]{iter.eps}
+     \includegraphics[scale = 0.31]{iter.eps}
   \caption{Aggregate Throughput vs. Number of Iterations}
@@
   \begin{minipage}[b]{0.4\textwidth}
-   \includegraphics[scale = 0.4]{optimal1.eps}
+   \includegraphics[scale = 0.3]{optimal1.eps}
   \caption{Aggregate Throughput vs. Number of UEs in one Service}
@@
   \begin{minipage}[b]{0.4\textwidth}
-   \includegraphics[scale = 0.35]{interF_new.eps}
-  \caption{Aggregate Throughput vs. Maximum Interference }
+   \includegraphics[scale = 0.3]{interF_new.eps}
+  \caption{\small Aggregate Throughput vs. Maximum Interference }
   \label{fig:13}
@@
   \begin{minipage}[b]{0.4\textwidth}
-    \includegraphics[scale = 0.35]{FA.eps}
-  \caption{Aggregate Throughput vs. the Number of UEs in one Service }
+    \includegraphics[scale = 0.3]{FA.eps}
+  \caption{\small Aggregate Throughput vs. the Number of UEs in one Service }
   \label{fig:14}
@@
 %\end{figure}
-\vspace*{-1.7em}
+\vspace*{-1.em}
 \section{Conclusion}\label{conc}
@@
 Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.
-\vspace*{-1.7em}
+\vspace*{-0.7em}
 \bibliographystyle{IEEEtran} 

### 2021-11-27 Journal1/paper1TNSM/pr.tex
add a bit code

@@
 O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-In this paper, we study the problem of service aware baseband resource allocation and virtual network function (VNF) activation in O-RAN system using network slicing to isolate different types of services.
+In this paper, we study the problem of service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing to isolate different types of services.
 The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
@@
 The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve numerically.
-Nevertheless, we break it down into two different steps where an iterative algorithm finds near optimal solution.
+Nevertheless, we break it down into two different steps where an iterative algorithm finds a near-optimal solution.
 In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is achieved.
-The proposed method is validated via simulations which illustrate a higher data rate and lower end-to-end delay compared to existing methods. 
+The proposed method is validated via simulations that illustrate a higher data rate and lower end-to-end delay than existing methods. 
 \end{abstract}

### 2021-12-18 Latex/journal_v2/HPC/main.tex
add revise in hpc

\documentclass{article}
\usepackage[utf8]{inputenc}
 \usepackage{enumerate}
 \usepackage[T1]{fontenc}
\usepackage{cite}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}

\title{Reporte de inventario de eviencias}
\author{Natalia Galeano Valerio}
\date{Octubre 2019}

\begin{document}

\baselineskip 12pt

\vspace*{30mm}

\begin{center}

\textbf{\Large Research Plan} \\
\vspace{10mm}
\textbf{Department of Electrical and Computer Engineering}\\
\vspace{20mm}
%{\large University of Oulu}\\
{\large University of Tehran}\\
\vspace{20mm}
\end{center}
\vspace{10mm}
{\scriptsize Provisional title:}\\
Dynamic Resource Allocation in O-RAN Architecture using Network Slicing\\

\vspace{20mm}

{\scriptsize Candidate name}\\
Mojdeh Karbalaee Motalleb \\
\vspace{3mm}

{\scriptsize Supervisor name:}\\
Dr. Onel Lopez\\
\vspace{3mm}

\pagebreak
\section{Introduction}
Open radio access network (O-RAN), as the integration and expansion of cloud RAN (C-RAN) and xRAN, or C-RAN and virtual RAN (vRAN), is expected to be a key technology in 5G networks to enhance the RAN performance extensively.

O-RAN, as illustrated in Fig. \ref{fig:c11}, separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
One of the necessities of the new generation of wireless networks is its intelligence.
Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques such as deep learning and reinforcement learning. The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real-Time, implement the algorithms for network intelligence
\cite{niknam2020intelligent,ORANArch,ORANML}.
\begin{figure*}
  \centering 
    \includegraphics[scale = 0.5]{finalDraw.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}

One of the goals of the next generation of mobile systems is to strictly meet the stringent QoS demands of the different services introduced in 5G , i.e., eMBB, URLLC, and mMTC. Network slicing is a promising solution to obtain the QoS for each type of service. Network slicing contains RAN slicing, core slicing, and both of them together. Efficient slicing of RAN is still challenging due to time-varying network circumstances.

In addition, according to the high complexity of RAN slicing and incapability of the traditional model-based methods, dynamic machine learning becomes the best solution for these problems.
 Generally, there are two kinds of deep reinforcement learning methods for solving dynamic problems. The first class is value-based such as Deep-Q-Network, and the second class is policy-based problems such as
deep deterministic policy gradient (DDPG). The first class can only solve the discrete action space problems, which are integer programming. The second class can solve by searching the optimal policy, which is the actor-critic method \cite{alsenwi2021intelligent,yan2019intelligent,mei2021intelligent}.
\section{Machine Learning Methods}
In this project, we want to solve the problem of dynamic resource allocation in the O-RAN system using RAN slicing. Here, we assume that we have three service types served by three slices, namely, eMBB, URLLC, and mMTC. Each service requires its specific QoS.
Our system model has a two-time scale. In the first time scale, we want to solve the problem of obtaining the optimal number of VNFs and the assignment of PRBs for each slice. In the second time scale, we seek to solve the power allocation and PRB assignment of each UEs in each slice. We use deep reinforcement learning since we want to solve the dynamic resource allocation.

\subsection{Requirement of Deep Reinforcement Learning}
A few pioneers developed an intelligent RAN slicing architecture incorporating DL (deep learning) technologies into network slicing and achieving automatic RAN slicing control due to the complexity of RAN slicing and the untenability of conventional models-based approaches. 
Since 5G networks are complex, and the wireless environment is dynamic and unpredictable, Reinforcement Learning (RL) is ideal for optimizing dynamic decision-making in real-time.

To extract the system's inherent value, DL uses model-free methodology features and makes decisions based on historical data sets. 
By interacting with an unknown environment, Deep Reinforcement Learning (DRL) performs self-optimization of system performance, which has received considerable attention from research.
Therefore, DRL approaches, which combine deep neural networks (DNNs) with reinforcement learning, are particularly promising because they can cope with large state and action spaces.
DRL methods have already been used for resource allocation in 5G networks.

In this project, we would like to allocate resources using DRL. This project has a two-time scale. The first time scale considers the optimal number of VNFs and the assignment of a PRB to each slice, which is the action of our problem.
To measure the effectiveness of each state or state action pair, DQN constructs a value function model. Through optimizing the value function model, DQN derives the appropriate control policy implicitly. Although DQN has good sample efficiency and stable performance, it has the disadvantage that its action space must be a discrete variable set.

Because we have many states and actions and the action is discrete, we use deep Q learning and want to compare it with double deep Q learning to solve the first part of our problem. The Q network is a multi-perceptron network and also we would like to compare it with a LSTM (long short term memory) to find the best Q network.

Actor-Critic is a Temporal Difference(TD) version of Policy gradient. It has two networks: Actor and Critic. The actor decided which action should be taken and critic inform the actor how good was the action and how it should adjust. The learning of the actor is based on policy gradient approach. In comparison, critics evaluate the action produced by the actor by computing the value function. 
In the second-time scale, we use actor-critic method such as deep deterministic policy gradient (DDPG) since we have a continuous actions and states.
The DDPG method can be used to solve continuous stochastic optimization problems, which are more common in network resource management. Also, Proximal Policy Optimization(PPO) and softmax policy gradient are two another methods that we want to compare it for our problem. 
\subsection{Software Requirement}
In this part, we discuss software requirements and the implementation of the algorithms mentioned above. 
We can implement the DRL methods using python and Matlab 2021. In this project, we choose python programming to write our codes. In python, we have different libraries to implement deep learning methods such as PyTorch, TensorFlow, and Keras. Here, we use PyTorch 1.10.1 (required cuda 10.2) for writting the deep Q networks. PyTorch can only be used in Ubuntu systems and we required an Ubuntu 20.04 Os for our project. 
Moreover, for this project a GPU GeForce RTX 2080 ti can be a perfect solution for processing of our codes. 
The RTX2080 has tensor-core which will be used in games that support DSLL feature. Tensor-core is a feature strongly advertised with Nvidia Volta GPU that is meant for professional usage such as deep learning and machine learning.
The Tensor cores in each RTX GPU are capable of performing extremely fast deep learning neural network processing.

Moreover, we want to compare our simulations with optimal solution which is a brute-force algorithm and takes lots of time in each loop and we need high RAM (32G) and SSD hard disk (256G) to compare it with the optimal solution.  
\bibliographystyle{IEEEtran} 
\bibliography{ref}
%\begin{thebibliography}{9}
%\bibitem{Hunt}
%Sally Hunt, ``Making Competition Work in Electricity,'' John Wiley , pp.23-30, Fev, 2002.

%\end{thebibliography}
\vspace{20mm}

\end{document}

### 2022-01-04 Latex/journal_v2/HPC/main.tex
add hpc
add python

@@
 Network slicing is a promising solution to obtain the QoS for each type of service.
-Network slicing contains RAN slicing, core slicing, and both of them together.
-Efficient slicing of RAN is still challenging due to time-varying network circumstances.
 
@@
 Each service requires its specific QoS.
-Our system model has a two-time scale.
-In the first time scale, we want to solve the problem of obtaining the optimal number of VNFs and the assignment of PRBs for each slice.
-In the second time scale, we seek to solve the power allocation and PRB assignment of each UEs in each slice.
+Our system model has a two time-scale.
+In the first time-scale, we want to solve the problem of obtaining the optimal number of VNFs and the assignment of PRBs for each slice.
+In the second time-scale, we seek to solve the power allocation and PRB assignment of each UEs in each slice.
 We use deep reinforcement learning since we want to solve the dynamic resource allocation.
@@
 In this project, we would like to allocate resources using DRL.
-This project has a two-time scale.
-The first time scale considers the optimal number of VNFs and the assignment of a PRB to each slice, which is the action of our problem.
+This project has a two time-scale.
+The large time-scale considers the optimal number of VNFs and the assignment of a PRB to each slice, which is the action of our problem.
+
+\newpage
 To measure the effectiveness of each state or state action pair, DQN constructs a value function model.

### 2022-01-15 Latex/Project (Final) --- End/Project (Final) --- End/Project (Final)111111/tex/ch1.tex
first commit for new git

\section{  مقدمه ای بر نسل پنجم مخابرات }

\subsection{مقدمه ای بر \lr{5G} }

مخابرات نسل پنجم یا \lr{5G}، نسل بعدی سیستم های بیسیم \LTRfootnote{Wireless} وشبکه های مخابراتی بعد از نسل چهارم می باشد که تکاملی از لایه ی فیزیکی و لایه ی شبکه در تکنولوژی شبکه های مخابراتی سیار همانند \lr{LTE} می باشد که نسبت به \lr{4G} سرعت و پوشش  خارق العاده ای را فراهم خواهد نمود، همچنین نسل پنجم مخابرات میزان تاخیر خیلی کمتری را در مقایسه با نسلهای قبل مخابرات خواهد داشت و تعداد دستگاه های متصل به آن به شدت افزایش می یابد.  \lr{5G} با سیگنال  \lr{5GHz} عمل خواهد کرد و سرعت $100$ برابر سرعت  \lr{4G LTE} برای ما فراهم نماید.\newline
تکنولوژی سیگنال  \lr{5G} برای پوشش فراگیرتر و بازدهی بهتر سیگنال ایجاد شده است. این پیشرفت ها منجر به تغییراتی از قبیل\lr{IoT} \LTRfootnote{Internet of Things} و \lr{Pervasive Computing} در آینده ی نزدیک خواهد شد.
همچنین \lr{5G} منجر به توسعه و بهبود سرویس های مخابراتی و اینترنتی سیار و در ورای آن، ایجاد تجربه ی بهتری برای مصرف کنندگان خواهد شد.این نسل جدید مخابراتی دارای انعطاف پذیری و قابلیت برنامه پذیری می باشد.
\subsection{تاریخچه مخابرات}
در ابتدا می خواهیم بدانیم که چه چیزی منجر به رفتن محققان به سوی  \lr{5G} شده است. یکی از دلایل مهم، سرعت و نرخ انتقال بیشتری است که در ادامه به آن می پردازیم.
در ابتدا نیاز بشریت به ارتباط تلفنی (انتقال بدون سیم به صورت زمان حقیقی \LTRfootnote{Real Time} بشریت را به سمت نسل اول ارتباطات \lr{1G} سوق داده است . نسل دوم ارتباطات \lr{2G} با سرویس های انتقال پیام کوتاه ایجاد شد. همچنین با موفقیت تکنولوژی شبکه های منطقه ای بیسیم، اتصال به داده های اینترنتی مورد توجه عموم مردم قرار گرفت که پلی به سوی نسل سوم ارتباطات \lr{3G} را فراهم نمود. به طور منطقی پله ی بعدی گام برداشتن در راستای کوچک شدن لپ تاپ و در آمیختن آن با تلفن که امروزه به صورت تلفن هوشمند\LTRfootnote{smart phone} است و دسترسی به  اینترنت، پهنای باند بالا و داده ها در نقاط مختلف جهان بوده است که \lr{4G} یا نسل چهارم را به همراه داشته است.
با توجه به افزایش تعداد کاربران تلفن های
هوشمند و تبلت ها و افزایش نرخ ارسال اطلاعات و داده ها در طی سال
های اخیر طبق پیش بینی های سیسکو میزان ترافیک \lr{IP} طی سالهای اخیر
  چندین برابر افزایش خواهد یافت.
در نتیجه اپراتورها برای حل این مشکل و خدمات
دهی بهتر ناچار به افزایش ظرفیت شبکه می باشند. با توجه
به این که نرخ داده و ظرفیت در سیستم های نسل چهارم به ظرفیت
شانون نزدیک شده است، در نتیجه روش هایی که برای
افزایش ظرفیت شبکه مورد استفاده می گیرند که به شرح زیر است:
\begin{itemize}
\item
استفاده از تکنیک \lr{Massive Mimo}
\item
استفاده از روش های پردازش های ابری
\item
\lr{Software Defined Networking}
\item
\lr{Extreme Densification}
\item
روش \lr{mm Wave}
\item
\lr{Network Function Virtualization}
\item 
\lr{Network Slicing}
\end{itemize}
\section{مقدمه ای بر شبکه ی رادیویی نسل پنجم مخابرات}
\lr{5G}
دارای شبکه ی رادیویی متفاوتی نسبت به نسلهای قبل می باشد. \lr{Cloud Radio Access Network} \LTRfootnote{C-RAN} که ساختار رادیویی ابری است، یکی از ساختارهای مورد توجه برای ساختار رادیویی قرار گرفته است. همچنین ساختارهای \lr{H-CRAN} \LTRfootnote{Heterogeneous CRAN}و \lr{F-RAN} \LTRfootnote{Fog-Radio Access Network} نیز دیگر ساختارهای مشابه ساختار رادیویی ابری هستند که مورد بررسی در این نسل مخابرات قرار گرفته اند. در حال حاضر شبکه ی \lr{Open-RAN} شبکه ی دیگری است که قابلیتهای انعطاف پذیرتری نسبت به شبکه های دیگر دارد که در ادامه به آن نیز می پردازیم.
\subsection{مقدمه ای بر \lr{C-RAN}}
شبکه های دسترسی ابری منجر به افزایش پوشش ارسالی می گردد. با توجه به ساختار شبکه
   \lr{C-RAN} که معماری جدیدی را برای شبکه های نسل آینده
ارائه می دهد، نه تنها ظرفیت شبکه افزایش می یابد بلکه
مشکلاتی که در روش های دیگر وجود دارد را نیز هموار
می سازد.
مفهوم شبکه دسترسی رادیو ابر \lr{C-RAN}، به مجازی سازی کارکردهای ایستگاه  پایه \LTRfootnote{Base Station-BS} با استفاده از تکنولوژی رایانش ابری \LTRfootnote{Cloud Computing} اشاره می نماید. این مفهوم به ایجاد یک ساختار سلولی جدید منجر می شود که در آن، نقاط دسترسی بیسیم کم هزینه که با عنوان واحدهای رادیویی \LTRfootnote{Radio Units} و یا رادیو هد های
  راه دور 
  \LTRfootnote{Radio Remote Heads}
 شناخته می شوند- با استفاده از یک ابر متمرکز با قابلیت پیکربندی مجدد و یا واحد مرکزی \LTRfootnote{Control Unit} مدیریت می شوند. شبکه امکان کاهش هزینه های سرمایه گذاری و عملیاتی مورد نیاز برای اپراتور ها به منظور توسعه و نگهداری شبکه های ناهمگن متراکم را فراهم می آورد. این مزیت مهم در کنار بازده طیفی، تسهیم آماری \LTRfootnote{Statisitical Multiplexing}، و مزیت های متعادل سازی بار باعث می شود تا شبکه \lr{C-RAN} به عنوان یکی از تکنولوژی های کلیدی در توسعه سیستم های \lr{5G} در جایگاه بسیار مناسبی قرار بگیرد. در ادامه، یک بررسی کلی و مختصر از تحقیقات جدید در مورد ساختار \lr{C-RAN} ارائه می شود و موضوعات مورد تاکید عبارتند از فشرده سازی لینک \lr{fronthaul} پردازش باند پایه، کنترل دسترسی به محیط واسط، تخصیص منابع، ملاحظات سطح سیستم، و تلاش های انجام شده در راستای ارائه استاندارد ها.
\section{ساختار شبکه های مختلف }
با توجه به مقاله ی\cite{checko2015cloud}،
\begin{figure}
  \centering
    \includegraphics[scale=0.7]{./pic1/c11}
  \caption{ساختار سنتی ایستگاه پایه \cite{checko2015cloud}}
  \label{fig:c11}
\end{figure}
هر ایستگاه پایه دو نوع پردازش انجام می دهد : پردازش
رادیویی که توسط واحد رادیویی \LTRfootnote{RRH} انجام می شود و شامل پردازش
دیجیتالی، فیلترینگ فرکانسی، تقویت توان و ....میباشد و
پردازش باند پایه که توسط واحد باند پایه \LTRfootnote{BBU} که همان واحد کنترل است \LTRfootnote{CU} انجام شده و از جمله
مهمترین وظایف آن می توان به کدینگ، مدولاسیون و
تبدیل فوریه ی سریع اشاره کرد. در ساختار جدیدی که
تحت عنوان \lr{C-RAN}  معرفی خواهیم نمود نحوه ی ارتباط
پردازشگرهای رادیویی و باند پایه متحول شده و در نتیجه
مزایایی برای شبکه حاصل خواهد شد.در ادامه ، انواع ساختارها را بیان خواهد شد.

\subsection{پیش زمینه ها} 
\subsubsection{ساختار سنتی ایستگاه پایه }

در ساختارهای سنتی ایستگاه پایه، پردازش های رادیویی و باند پایه در
داخل ایستگاه پایه انجام می شد و مدول آنتن نیز در فاصله
ی چند متری از مدول رادیویی نصب شده و ارتباط آنها
توسط کابل کواکسیال برقرار می شد که همین امر سبب
افزایش تلفات در شبکه می باشد. این نوع ساختار در شکل
\ref{fig:c11} نشان داده شده است. همان گونه که مشاهده می کنید
ارتباط بین ایستگاههای پایه توسط ارتباط  $X_2$ و ارتباط بین
ایستگاه پایه و شبکه ی هسته توسط ارتباط $ S_1$ برقرار می
شود. این نوع ساختار در شبکه های \lr{1G} و \lr{2G} به کار گرفته
شده است 
\cite{checko2015cloud}.

%Figure \ref{fig:gull} shows a photograph of a gull.
\subsubsection{ ساختار ایستگاه پایه و واحد رادیویی}

\begin{figure}
  \centering
    \includegraphics[scale=0.7]{./pic1/c22}
  \caption{ ساختار ایستگاه پایه و واحد رادیویی \cite{checko2015cloud}}
  \label{fig:c22}
\end{figure}
در این ساختار واحد رادیویی و واحد پردازشی سیگنال، از هم
مجزا شده و واحد رادیویی که تحت عنوان \lr{RRH} یا \lr{RRU}
نیز شناخته می شود، توسط فیبر نوری به واحد باند پایه یا \lr{BBU} اتصال می
یابد. همان طور که پیشتر بیان شد واحد رادیویی مسئولیت
انجام پردازش های دیجیتالی از جمله تبدیل انالوگ به
دیجیتال، دیجیتال به انالوگ، تقویت توان و فیلترینگ رابر عهده دارد، که تفکیک وظایف واحد پردازشی و واحد
رادیویی در این ساختار در شکل \ref{fig:c22} قابل مشاهده است. این
نوع ساختار برای شبکه های نسل سوم معرفی شده و امروزه
نیز بیشتر ایستگاههای پایه از همین ساختار بهره می گیرند.
از جمله ویژگی های بارز این ساختار امکان ایجاد فاصله
بین واحد رادیویی و پردازشی می باشد، که این فاصله به
دلیل تاخیر پردازشی و انتشاری نمی تواند از  $40$کیلومتر
فراتر رود. در این ساختار تجهیزات مرتبط با \lr{BBU} می
توانند به مکانی مناسبتر که قابل دسترس تر بوده و هزینه
ی اجاره و نگهداری کمتری را به اپراتورها تحمیل می
کنند منتقل شوند و واحد های رادیویی نیز در در پشت بام
ساختمان ها و مکان های مرتفع نصب می شوند که این
خود سبب کاهش هزینه های خنک سازی ادوات موجود
می شود. نحوه ی ارتباط بین \lr{RRH} و \lr{BBU} مشابه ساختار
سنتی بوده و \lr{RRH} ها نیز توسط معماری زنجیروار با هم
در ارتباطند.
\begin{figure}
  \centering
    \includegraphics[scale=0.7]{./pic1/c33}
  \caption{ساختار  \lr{C-RAN} \cite{checko2015cloud}}
  \label{fig:c33}
\end{figure}
\subsection{تعریف مسئله}
\subsubsection{ساختار \lr{C-RAN}}
این ساختار جدید جزو یکی از ساختارهایی است که در \lr{5G} امکان استفاده را دارد.در این ساختار جدید در راستای بهینه سازی عملکرد \lr{BBU}
 ها در مواجهه باایستگاههای پایه پر ترافیک و کم ترافیک،
 \lr{BBU}ها به صورت یک مجموعه ی واحد تحت عنوان 
\lr{BBU Pool}
 در آمده اند که این مجموعه بین چندین سلول 
 به اشتراک گزارده شده و مطابق شکل زیر مجازی سازی
می شود. 
در توضیح بیشتر این ساختار می توان این گونه
عنوان کرد که \lr{BBU Pool} به عنوان یک خوشه ی مجازی
در نظر گرفته می شود که شامل پردازش گرهایی می باشد
که پردازش های باند پایه را انجام می دهند. ارتباط بین
  \lr{BBU}ها در ساختار های فعلی به شکل  $X_2$ برقرار می شود
که در این ساختار ارتباط بین خوشه ها از فرم جدید $X_2$
تحت عنوان  $X_2 +$برقرار می شود.
\newline
در شکل \ref{fig:c33} ساختار کلی شبکه ی  \lr{C-RAN} در سیستم های
\lr{ LTE}
 نمایش داده شده است. همان طور که در شکل قابل
مشاهده می باشد ساختار کلی شبکه  \lr{C-RAN} به دو بخش
 \lr{backhaul} و \lr{fronthaul} تقسیم بندی شده است. بخش
 \lr{fronthaul}شبکه به مرحله ی اتصال سایت های \lr{ RRH}به
 به \lr{BBU Pool} به اتصال \lr{backhaul} و بخش \lr{BBU Pool}
هسته ی شبکه ی سیار اطلاق می شود. همان گونه که قبلا
ذکر شد  \lr{ RRH}ها در نزدیکی انتن نصب شده و از طریق
لینک های انتقالی نوری با پهنای باند وسیع و تاخیر کم به
پردازشگرهای قوی در  \lr{BBU}متصل می شوند. توسط این
لینک های انتقالی است که سیگنال های دیجیتالی باند
پایه از نوع \lr{IQ} بین \lr{RRH} و \lr{BBU} انتقال می یابند \cite{checko2015cloud}.
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{./pic1/CRAN}
  \caption{ساختار شبکه ی \lr{C-RAN} \cite{checko2015cloud}}
  \label{fig:C-RAN}
\end{figure}
\section{مزایای شبکه ی \lr{C-RAN}}

در این بخش قصد داریم مزایای شبکه ی \lr{C-RAN} و هدف از استفاده ی آن در \lr{5G} را بیان کنیم.
\newline
در هر دو نوع سلولهای ماکرو و میکرو، می توان از ساختار \lr{C-RAN} بهره برد. در حالت ماکرو، متمرکز کردن \lr{BBU} ها به صورت \lr{BBU Pool}، منجر به استفاده ی بهینه از \lr{BBU} ها و کاهش هزینه ی ایستگاه پایه \LTRfootnote{base station} می شود. همچنین منجر به کاهش مصرف توان و فراهم کردن انعطاف پذیری بیشتر در شبکه و تطبیق آن با ترافیک غیر یکسان می شود. علاوه بر این، باعث تبدیل سیگنال تداخل به سیگنال مفید تبدیل می شود. در ادامه این مزایا به صورت گسترده تر بیان می گردد. \cite{checko2015cloud, namba2012colony}
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{./pic1/c4}
  \caption{تغییرات حجم ترافیک در ایستگاههای پایه بنا به
مکان قرارگیری آنها \cite{checko2015cloud}}
  \label{fig:c4}
\end{figure}
\subsection{توانایی تطبیق پذیری با ترافیک غیر
یکنواخت }
کاربران شبکه های رادیویی در طول روز بین مناطق مختلف
(مسکونی و اداری) جابه جا شده و در نتیجه ترافیک هر
منطقه نیز بنا به نوع منطقه در طول ساعات شبانه روز متغیر
می باشد.
نمودار مربوط به این تغییرات در شکل \ref{fig:c4} قابل
مشاهده است. نکته ی قابل توجه برای اپراتور ها در این
بخش، هدر رفت توان پردازشی در اثر جا به جایی کابران می
باشد. بدین شکل که به طور مثال بعد از اتمام ساعات کاری
کاربران شبکه از مناطق اداری به مناطق مسکونی نقل مکان
می کنند حال انکه ایستگاههای پایه برای خدمات رسانی
در اوج ترافیک تعبیه شده و با کاهش تعداد کاربران در
حقیقت توان پردازشی هدر می ر ود. تحقیقات نشان داده
است که میزان پیک ترافیک شبکه حدود  $10$ برابر بیشتر
از ترافیک در ساعات غیر اوج می باشد و در هر سلول بنا
به نوع منطقه ساعات اوج ترافیک متغیر است. با توجه به
متغیر بودن ساعات اوج ترافیک در سلول های مختلف و
با استفاده از ویژگی شبکه های \lr{C-RAN} می توان راهکاری
ارائه نمود که از هدر رفت توان پردازشی جلوگیری شود.
در شبکه های \lr{C-RAN} پردازش های باند پایه مربوط به
چندین سلول به ابر منتقل شده که می توان از این ویژگی
برای افزایش نرخ بهره وری استفاده کرد.  \cite{checko2015cloud, namba2012colony} 
\subsection{صرفه جویی در هزینه و مصرف انرژی }
با بکارگیری شبکه های \lr{C-RAN} در مصرف انرژی و از این
رو در کاهش هزینه ها می توان صرفه جویی نمود.
هزینه
های صورت گرفته توسط اپراتورهای سیستم های مخابراتی
که تحت عنوان \lr{TCO} نیز شناخته می شود،به دو دسته
ی عمده تقسیم بندی می شود. هزینه های \lr{CAPEX} و
هزینه های \lr{OPEX}؛
که هزینه ی \lr{CAPEX} مربوط به ساخت شبکه که شامل طراحی و نصب سخت افزارها می باشد. هزینه ی \lr{OPEX} شامل هزینه های مربوط به راه اندازی و نگهداری وهمچنین
ارتقای شبکه ی مخابراتی می باشد. که \lr{C-RAN} منجر به کاهش هر دو هزینه می شود.
\subsection{سهولت در ارتقا دادن و نگهداری از شبکه}
با قرار گیری  \lr{ BBU} ها در داخل ابر به جای قرارگیری در
ایستگاه های پایه ی دور از هم امکانسهولت در ارتقا دادن و نگهداری از شبکه در صورت نیاز به مداخله ی نیروی انسانی
فراهم می شود، زیرا در این صورت به جای نظارت بر تمام
ایستگاههای پایه تنها تعداد مشخصی \lr{BBU pool} مد نظر
قرار می گیرند. هم چنین بروزرسانی \lr{CPU} در این حالت
تسریع شده و استفاده از تکنولوژی \lr{IT} به جای استفاده از
سخت افزارها هموارتر می شود.
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{./pic1/c55}
  \caption{تداخل در \lr{LTE} و \lr{C-RAN} \cite{WinNT}}
  \label{fig:c55}
\end{figure}
\subsection{کاهش چشمگیر تداخل از طریق پردازش واحد باند پایه }
تداخل در شهرهای بزرگ یکی از چالشهای مهم محسوب می شود. \newline
همانطور که در شکل \ref{fig:c55} دیده می شود، در \lr{LTE} تداخل به صورت واضحی بر روی سیگنال مفید اثر می گذارد، حال در \lr{C-RAN} این مشکل به صورتی که در شکل دیده می شود برطرف شده و سیگنال تداخل تبدیل به سیگنال مفید می شود و از رابطه ی متقابل کانال \lr{TDD} \LTRfootnote{Time Division Duplexing} استفاده می گردد.

\subsection{افزایش توان و کاهش تاخیر}
در سالهای اخیر شبکه های نسل $4$  یا \lr{LTE} توسط \lr{ 3GPP}
استاندارد سازی شده و به مرور جایگزین سیستم های نسل $3$
 شده اند.

  شبکه های \lr{C-RAN} 
 با توجه به قابلیت هایی
که دارند در سیستم های نسل $4$ یعنی \lr{LTE} و \lr{LTE-A}
قابل پیاده سازی و بهره برداری بوده و مزایایی را برای این
سیستم ها به همراه خواهند داشت. برای توضیح بهتر نقش
   \lr {C-RAN} در افزایش توان عملیاتی نیاز هست که با تکنیک
هایی از قبیل  \lr{eICIC} و  \lr{CoMP} اشنا شده و سپس این
تکنیک ها را به ساختار \lr{C-RAN} تعمیم بدهیم.
همان طور که می دانید در سیستم های \lr{LTE} منابع به
صورت مشارکتی مورد استفاده قرار می گیرند. مسئولیت
تخصیص منابع در این شبکه ها به عهده ی زمانبندی 
به نام \lr{eNB} \LTRfootnote{eNode B} است که در ایستگاه پایه قرار دارد. نکته ی
قابل توجه دیگر استفاده از تکنیک \lr{OFDMA} می باشد که
زمانبند را قادر می سازد که منابع را به صورت دینامیکی
هم در حوزه ی زمان و هم در حوزه ی فرکانس به کاربران
مختلف تخصیص دهد.
با توجه به این که در سیستمهای \lr{ LTE} عموما پارامتر استفاده
ی مجدد از فرکانس برای تمامی سلول ها یک در نظر
گرفته می شود، در نتیجه تداخل بین سلول های مجاور
به شدت افزایش می یابد. برای رفع این مشکل دو روش
عمده مطرح می شود: روش اول کاهش تداخل و روش دوم
استفاده ی سازنده از تداخل. برای پیاده سازی روش اول
از تکنیک \lr{ICIC} یا \lr{eICIC} استفاده می شود و برای روش
دوم عمدتا از تکنیک \lr{CoMP} بهره می گیرند که توضیح
نحوه ی عملکرد این تکنیک ها در مقاله ها به طور کامل
بررسی شده است. در رابطه با کاهش تاخیر نیز می توان
این گونه عنوان نمود که با قرار گرفتن \lr{ BBU} ها در مجاورت
هم در ابر مدت زمان لازم برای انجام عمل \lr{hand off} بین
ایستگاههای پایه کاهش می یابد. زیرا عمل\lr{hand off} در
این حالت به جای ایستگاههای پایه در \lr{ BBU} ها صورت
می گیرد
\section{چالشها و مشکلات در برخورد با ساختار \lr{C-RAN} }

\subsection{دو چالش مهم مربوط به \lr{fronthaul}}
 \begin{figure}
  \centering
    \includegraphics[scale=0.7]{./pic1/c6}
  \caption{محدودیت در اثر تاخیر \cite{simeoneConf}  }
  \label{fig:c6}
\end{figure}
یکی از مشکلات پیش روی ساختار \lr{C-RAN} در قسمت \lr{fronthaul} به شرح زیر است.
\begin{itemize}
\item
 محدودیت ظرفیت که
 به دو دلیل ایجاد می گردد که در ادامه ذکر شده است \cite{simeoneConf}.
 \begin{itemize}
 \item
 نمونه برداری و کوانتیزاسیون اسکالر
 \item
 تداخل رادیویی به صورت عمومی
 \end{itemize}

 \item 
  محدودیت در اثر تاخیر که
   به سه دلیل ایجاد می شود که در ادامه ذکر شده است \cite{simeoneConf}.
  \begin{itemize}
 \item
 تداخل هوا
 \item
 انتقال سیگنال در قسمت \lr{fronthaul}
 \item
 پردازش واحد کنترل
 \end{itemize}
   انتقال سیگنال در قسمت \lr{fronthaul} و پردازش واحد کنتذل به نوع انتقال \lr{fronthaul} بستگی دارد (بسیم یا انتقال با سیم) 
\end{itemize}
با استفاده ازمخابرات فیبر نوری این مشکلات تا مقدار زیادی حل خواهد شد. 
\subsection{نحوه ی مشارکت \lr{BBU} ها نحوه ی اتصال
و خوشه بندی}

همکاری بین ایستگاههای پایه بایستی به گونه ای باشد
که از نظر زمانبندی و بررسی اطلاعات بازخورد کانالها
به منظور مدیریت تداخل و همچنین سازگاری باتکنیک
   \lr{CoMP}مورد بررسی قرار گرفته باشد.
تکنیک هایی که برای اتصال \lr{BBU}ها مورد استفاده قرار
می گیرند بایستی از نظر امنیت، قابلیت اطمینان، پشتیبانی
از پهنای باند وسیع ،تاخیر کم و ... استاندارد های لازم را
براورده ساخته و نسبت به ساختار سنتی عملکرد بهتری را
از خود نشان دهند.
\subsection{نیاز به پهنای باند وسیعتر و تاخیر
دقیق و کمتر}
در ساختار شبکه ی \lr{C-RAN} اطلاعات به صورت \lr{ IQ} بین
 \lr{RRH} و  \lr{BBU} ها انتقال می یابند. طبق استانداردهایی
که برای این شبکه تعریف شده است، انتظار می رود که
هر \lr{BBU pool} قابلیت خدمات دهی به $100-1000$
ایستگاه پایه را دارا باشد. بنابراین با توجه به پهنای
باند مورد نیاز برای ارسال اطلاعات به صورت \lr{ IQ} حجم
اطلاعاتی زیادی توسط لینک های نوری به سمت \lr{BBU pool}
  ها سرازیر خواهد شد و پهنای باند بالایی مورد نیاز
است.علاوه بر نیاز به پهنای باند بالا شبکه ی انتقال ما
بایستی نیاز به جیتر و تاخیر دقیق در شبکه را برآورده کند،
که در ادامه برخی از این قیود لازم آورده شده است.
\begin{itemize}
\item
دقت زمانی لازم برای همکاری بین ایستگاههای پایه
بایستی در حدود $ 0.5 \mu sec$ باشد که مهم ترین شرط
این مبحث محسوب می شود.
\item
صرف نظر از تاخیر حاصل از طول
کابل تاخیر حاصل از رفت و برگشت اطلاعات کاربران
نبایستی از حدود $ 5 \mu sec$ بیشتر باشد
\item
فاصله ی بین \lr{RRH} و \lr{BBU} ها بایستی از حد 
 $ 20 - 40 km$تجاوز نکند و تاخیر حاصل از پردازش زیر
 فریم ها در لینک های ارتباطی بین  \lr{RRH} و \lr{BBU} نیز
بایستی از $1ms$ کمتر باشد
\end{itemize}
\subsection{محدودیت ظرفیت در \lr{backhaul}}
همچنین محدودیت ظرفیت در \lr{backhaul} منجر به محدود کردن عملکرد انتقال در حالت مشارکت چند نقطه ای  در  \lr {C-RAN} می گردد. 
\subsection{نیاز به شبکه های انتقال ازران}
برای انتقال اطلاعات بین \lr{RRH} و \lr{BBU} از فیبر نوری
استفاده می شود. فیبر نوری به دلیل سرعت در انتقال
اطلاعات تلفات کم و قابلیت انتقال حجم بالایی از
اطلاعات گزینه ی مناسبی برای شبکه های \lr{C-RAN} به
حساب می اید. با وجود محاسن گفته شده گران بودن و
عدم دسترسی تمام اپراتورها به فیبر نوری از جمله مشکلاتی
است که بایستی قبل از پیاده سازی شبکه های \lr{C-RAN} بدان
پرداخته شود. \cite{MA}
\section{شبکه های دسترسی رادیویی ابری نا متجانس (\lr{H-CRAN})}
برای غلبه بر چالش های شبکه های \lr{C-RAN} با محدودیت های \lr{fronthaul} ، شبکه های دسترسی ابری نامتحانس (\lr{H-CRAN}) معرفی گردید\cite{ fogComputing, heterogeneous, fogEdge}.
\begin{figure}
  \centering
    \includegraphics[scale = 0.8]{./pic1/hc}
  \caption{ ساختار شبکه های دسترسی ابری نامتحانس \cite{heterogeneous}  }
  \label{fig:hc}
\end{figure}

\subsection{ساختار شبکه ی \lr{H-CRAN}}
کاربر و صفحه ی کنترلگر در چنین شبکه هایی از هم مجزا می باشند. که در این شبکه ها ، نودهای توان بالا   \LTRfootnote{High Power Node}\lr{HPN} ، عمدتا برای فراهم کردن پوشش بدون درز و اجرای عملکرد صفحه کنترل می باشد. در حالی که \lr{RRH} ها برای فراهم نمودن سرعت بالای نرخ داده برای انتقال بسته در ترافیک قرار گرفته اند. \lr{HPN} ها از طریق لینکهای \lr{backhaul}  به \lr{BBU Pool} متصلند ( برای هماهنگ کردن تداخل ).\newline
ساختار این شبکه شبیه به ساختار \lr{C-RAN} می باشد . همانطور که در شکل \eqref{fig:hc} نشان داده شده است ، تعداد زیادی \lr{RRH} ، همراه با انرژی مصرفی کم در ساختار \lr{H-CRAN} ، با یکدیگر در \lr{BBU Pool} مرکزی ، همکاری می کنند تا گین مشترک بالایی بدست آورند.   تنها ، فرکانس رادیویی جلو ،(\lr{RF}) و عملکردهای پردازشی  ساده ، در \lr{RRH} ، صورت می گیرد ، در حالی که پردازشهای مهم دیگر ، در \lr{BBU Pool} انجام می گیرد. همچنین تنها بخشی از عملکردها در لایه ی \lr{PHY} در \lr{RRH} به مشارکت می انجامد که این مدل در شکل \eqref{fig:hc} نشان داده شده است.\newline
اگرچه ، برخلاف \lr{C-RAN} ، \lr{BBU Pool} در \lr{H-CRAN} ، به \lr{HPN} ها متصلند که این، برای کاهش تداخل متقابل بین \lr{RRH} ها و \lr{HPN} ها از طریق محاسبات ابری متمرکز بر اساس تکنیکهای پردازشی مشترک می باشد. همچنین ، داده و واسط کنترل ، بین \lr{BBU Pool} و \lr{HPN} های $S_1$ و $X_2$ شناخته شده اند که تعریف آنها بر اساس تعریف استاندارد \lr{3G} ایجاد شده است.\newline
همانطور که سرویسهای صدا ، می توانند به صورت بهینه در طول مد سوییچ بسته در \lr{4G} فراهم گردند ، \lr{H-CRAN} می تواند به طور همزمان سرویس صدا و داده را پشتیبانی کند. سرویس صدا مرجح به اداره از طریق \lr{HPN} ها می باشد ، در حالی که ترافیک بسته ی پر داده ، بیشتر توسط \lr{RRH} اداره می گردد. 
در مقایسه با ساختار \lr{C-RAN} ،ساختار \lr{H-CRAN} ، نیازهای \lr{fronthaul} را بوسیله ی مشارکت \lr{HPN} ها برطرف می سازد. با توجه به حضور \lr{HPN} ها ،سیگنالهای کنترلی و سمبلهای داده در \lr{H-CRAN} جدا از هم می باشند. تمام کنترل کننده های سیگنال و سیستم هایی که اطلاعات را ارسال می نمایند ، توسط \lr{HPN} ها به \lr{UE} ، منتقل می گردد که منجر به سادگی در ظرفیت و در محدودیت تاخیر زمان در لینکهای \lr{fronthaul } بین \lr{RRH} ها و \lr{BBU Pool}  می گردد و منجر به صرفه جویی در مصرف انرژی می گردد. همچنین ، برخی از ترافیک های شدید و ناگهانی \LTRfootnote{Burst Traffic} و یا سرویس پیام همراه با مقدار داده ی کم ، می تواند به صورت بهینه توسط \lr{HPN} ها پشتیبانی گردد. مکانیزم کنترل بین ارتباط داشتن و نبود ارتباط ، توسط \lr{H-CRAN} پشتیبانی می گردد که منجر به حفظ کردن مقدار قابل توجهی \lr{Overhead} در رادیو بوسیله ی مکانیزم ارتباط جهت دار خالص می گردد. در \lr{RRH} ، تکنولوژی های مختلف انتقال در لایه ی \lr{PHY} ، قابل استفاده برای بهبود نرخ انتقال (همانند موج میلیمتری و نور مرئی) می گردد. در \lr{HPN}ها، \lr{MIMO}\LTRfootnote{Multiple Input Multiple Output}، یکی از راه های افزایش پوشش در بهبود ظرفیت می باشد.

\subsection{چالشهای پیش روی \lr{H-CRAN}}
متاسفانه ، \lr{H-CRAN} در عمل دچار چالشهایی است.
\begin{itemize}
\item
 اولین چالش به این دلیل است که با معروفتر شدن موقعیتهایی که بر اساس کاربردهای اجتماعی است ، داده های ترافیکی در طول مسیر  \lr{fronthaul} از \lr{RRH} به \lr{BBU Pool}، با افزایش موج زیادی از داده های زائد همراه است که منجر به بدتر شدن محدودیت \lr{fronthaul} می گردد.
\item
همچنین \lr{H-CRAN} ، از تمامی فواید پردازشی و ظرفیت ذخیره در ابزارهای پردازشی و الکترونیکی همانند \lr{RRH} و تلفن های هوشمند (\lr{UE}) ،که راه های رسیدن به موفقیت در این ساختار است ، استفاده نمی کند .
\item
همچنین ، اپراتورها ،نیاز به استقرار تعداد زیادی \lr{RRH} و \lr{HPN} ثابت در \lr{H-CRAN} ، می باشند تا به ماکسیمم ظرفیت دسترسی پیدا کنند. ولی در زمانهایی مه ترافیک زیاد نیست ، منجر به اتلاف شدیدی می شود. 
\end{itemize}
\section{\lr{C-RAN}و \lr{H-CRAN} }

\subsection{تفاوت و شباهت های این دو ساختار}
  تفاوت عمده ی بین این دو ساختار در این است که در \lr{H-CRAN} ، عملگر کنترل مرکزی از \lr{BBU Pool} به \lr{HPN} منتقل گردیده است. \cite{fogComputing}
 \newline
در هر دو ساختار، عملگرهای \lr{CRSP} \LTRfootnote{Collaboration Radio Signal Processing} و ذخیره سازی اطلاعات در سرور ابر مرکزی ، صورت می گیرد که نیاز به تعداد زیادی دستگاه های فرستنده (موبایل) و انتقال داده به سرعت کافی از طریق \lr{BBU Pool} می باشد.
\subsection{مشکلات پیش روی این دو ساختار}
مهمترین مشکلات این دو ساختار ، تاخیر انتقال زیاد و سنگینی حمل اطلاعات بر روی \lr{fronthaul} می باشد.روش ساده یرای حل این مشکل :
\begin{itemize}
\item
جلوگیری از انتقال تمام داده ها به \lr{BBU Pool} شویم و بخشی از پردازش اطلاعات را در \lr{RRH} های محلی و همچنین وسایل الکترونیکی هوشمند انجام دهیم.
\item
جلوگیری کنیم از اینکه همه ی ترافیک به طور مستقیم از سرور ابر متمرکز منتقل شود، برخی از ترافیک محلی باید از ذخیره  \lr{RRH} های مجاور تحویل گردد.
\end{itemize}
\section{ارائه ی پیشنهاد سیستم جایگزین (\lr{F-RAN})}
برای حل کردن مشکلات \lr{H-CRAN} و \lr{C-RAN}، نیاز به معرفی ساختار جدید دیگری می باشیم که آن را \lr{F-RAN} می نامیم.
\lr{F-RAN} تمام ویژگی های مثبت محاسبات ابری و شبکه های نامتجانس و محاسبات مهی را همزمان در بر می گیرد.
محاسبات مهی ، اصطلاحی برای جایگزین کردن محاسبات ابری است که مقدار قابل توجهی از ذخیره سازی ، ارتباطات ، کنترل کردن ، اندازه گیری و مدیریت را در لبه ی شبکه انجام می دهد (نه در کانال و ابر مرکزی) \cite{fogComputing, fogEdge,fog12}.
\begin{figure}
  \centering
    \includegraphics[scale = 0.7]{./pic1/fhc}
  \caption{ سیر تحولات شبکه های رادیویی ابری \cite{fogComputing}}
  \label{fig:fhc}
\end{figure}
\subsection{ساختار سیستمهای   \lr{F-RAN}}
 سیستمهای \lr{F-RAN} تحولی از سیستمهای \lr{C-RAN} می باشد که در شکل \eqref{fig:fhc} نشان داده شده است. برخی از ارتباطات توزیع شده و عملکردهای ذخیره سازی در منطق لایه ی مه قرار دارد. همچنین چهار نوع ارتباطات ابری تعریف شده است.
  \begin{figure}
  \centering
    \includegraphics[scale =0.7]{./pic1/fr}
  \caption{ مدل سیستم \lr{F-RAN} \cite{fogComputing} }
  \label{fig:fr}
\end{figure}
 \begin{itemize}
 \item
 ابر ذخیره گر و ارتباطات مرکزی جامع :
 که همانند ابر مرکزی \lr{C-RAN} می باشد
 \item
 ابر کنترل گر مرکزی :که برای تکمیل عملکردهای کنترلی  می باشد و در \lr{HPN} ها قرار دارد
 \item
 ابر ارتباطات منطقی توزیع شده که در برنامه های محاسبات مهی و ابزار های این محاسبات قرار دارد.
 \item
  ابر ذخیره گر منطق توزیع شده:
  که همانند قبل در \lr{F-RAN} قرار دارد.
 \end{itemize}
 در این ساختار ، برای کاهش تاخیر ناشی از انتقال داده ها به ابر مرکزی ، ساختار های \lr{RRH} را دارای حافظه قرار می دهیم که برای ارتباطات محلی، به جای اینکه پردازش ها در \lr{BBU Pool} صورت بگیرد، بدون نیاز به انتقال به ابر مرکزی، درون \lr{RRH} ها انجام پذیرد. 
 %%%%%%%%%%%%%%%%%%%%%%%5
 %%%%%%%%%%%%%%%%%%%%%%%
 \section{برخی از کاربردهای شبکه ی \lr{C-RAN}  }

\subsection{ تخصیص منابع مبتنی بر مدولاسیون \lr{OFDM}}
هدف از متد ارائه شده در برخی مقالات را می توان تخصیص
منابع بین سلول ها با در نظر گرفتن تداخل بین سلول و هم
چنین کاهش تعداد \lr{BBU} های فعال عنوان کرد. نحوه ی
تخصیص به  ۲بخش تقسیم شده و به طور جداگانه بررسی
شده است. بخش اول و اصلی تخصیص منابع بین ناحیه
های لبه سلول ها می باشد که بایستی تداخل در نظر گرفته
شده و بدان منظور از روش \lr{graph coloring} استفاده شده
است و بخش دوم تخصیص منابع بین ناحیه های مرکزی
می باشد که بنا به تخصیص های صورت گرفته در بخش
اول انجام می شود. در ادامه عملکرد متد ارائه شده برای
تخصیص منابع مبتنی بر شبکه \lr{C-RAN} بررسی شده و مورد
ارزیابی قرار می گیرد.
در سناریو مورد نظر شبکه ای شامل  ۹سلول در نظر گرفته
و پهنای باندی که که به هر \lr{BBU} تخصیص داده می
شود را برابر $ B = 20MHZ$ در نظر گرفته و تابع توزیع
احتمال ترافیک شبکه را نیز گوسی در نظر می گیریم. دو
پارامتر $\sigma_ck$ و $\sigma_ek$به ترتیب نشانگر پهنای باند مورد نیاز ناحیه
ی لبه و ناحیه ی مرکزی سلول  می باشند. پهنای باند
مورد نیاز به صورت مستقل و یکسان بین تمام سلولها توزیع
شده است .\cite{graph}
\begin{figure}
  \centering
    \includegraphics[scale =0.7]{./pic1/cr}
  \caption{ توان عملیاتی تمام کاربران سلول \cite{graph} }
  \label{fig:cr}
\end{figure}
در شکل \eqref{fig:cr}  توان عملیاتی تمام کاربران سلول چه کاربران
نواحی مرکزی یا لبه مورد بررسی قرار گرفته است. در این
 دو دسته نمودار حاصل می
نمودار با انتخاب  $\frac{\sigma_ck}{\sigma_ek} = \frac{1}{3}$ 
شود که وابستگی عملکرد به تغییرات ترافیک را نشان می
دهند. در نمودار های مذکور متد جدیدی تحت عنوان \lr{DFR} بدون تجزیه ی سلول نیز مشاهده می شود که نحوه
ی تخصیص مطابق روش ارایه شده ما می باشد با این
تفاوت که نواحی لبه و مرکزی تفکیک نشده و کل سلول
واحد در نظر گرفته شده است. با هر دو انتخاب ممکن برای
نسبت ترافیک ها می توان مشاهده کرد که متد ما عملکرد
بهتری را از خود به نمایش می گذارد. متد   \lr{DFR} بدون
تفکیک سلول نیز بدترین عملکرد را از خود نشان می دهد
زیرا نمی تواند به طور بهینه از منابع استفاده کند
در شکل های \eqref{fig:7} و \eqref{fig:8} نیز عملکرد بهره وری انرژی هر ۳
متد مورد نقد و بررسی قرار گرفته است. شایان ذکر است
که میزان بهره وری انرژی به نسبت توان عملیاتی تمام
کاربران به توان تمام \lr{BBU} های فعال اطلاق می شود. با
توجه به نمودار ها بدترین عملکرد متعلق به روش \lr{FFR}
معمول می باشد زیرا به ازای هر سلول از یک  \lr{BBU}مجزا
استفاده می شود.
نکته ی قابل توجه در این نمودار عملکرد
بهتر متد \lr{DFR} بدون تفکیک سلول نسبت به متد ارائه شده
است .علت این امر نیز استفاده از  \lr{BBU}ها ی کمتر از
$\frac{M}{3}$
می باشد. هر چند اگر ما تعداد کمتری کاربر در هر سلول داشته
باشیم و حجم ترافیکی کاهش یابد، نتایج حاصل از متد ارایه
شده از متد \lr{DFR} بدون تفکیک سلول پیشی گرفته و بهترین
عملکرد را از خود نشان می دهد که نتایج مذکور در شکل
  \eqref{fig:8}
   قابل مشاهده است. در این نمودار فرض
\begin{equation*}
\sigma_e k = \sigma_c k
\end{equation*}  
 رعایت شده و میزان $\sigma_ek$ بین  0.2 و 2 انتخاب می شود
با مفروضات انجام شده تعداد \lr{BBU} های فعال در هر دو
متد یکسان شده و چون توان عملیاتی کاربران در متد ارائه
شده بهتر است پس متد مذکور در این نمودار نیز بهترین
عملکرد را نسبت به  2متد دیگر از خود نشان می دهد.  
\begin{figure}
  \centering
    \includegraphics[scale=0.7]{./pic1/7}
  \caption{ بهره وری انرژی در حضور ترافیک معمول \cite{graph}  }
  \label{fig:7}
\end{figure}

\begin{figure}
  \centering
    \includegraphics[scale=0.7]{./pic1/8}
  \caption{  بهره وری انرژی در حضور ترافیک محدود \cite{graph} }
  \label{fig:8}
\end{figure}
\section{تخصیص توان و خوشه بندی شبکه های رادیویی ابری}
برای کاهش پیچیدگی این نوع شبکه ها ، می توان از تکنیک های خوشه بندی در طراحی و چینش\lr{RRH} ها استفاده کرد. برای بهبود بازدهی انرژی و توان نیز می توان تخصیص توان و خوشه بندی شبکه های رادیویی ابری را همزمان با هم انجام داد. 
که این مبحث یکی از بحث های داغ در شبکه های رادیوی ابری می باشد که با روش های بهینه سازی به طور همزمان به تخصیص توان و بدست آوردن تعداد خوشه ها خواهیم رسید .
حتی برای خوشه بندی به طور تنها نیز می توان از روش \lr{K Means} استفاده کرد . در شکل \ref{fig:88} نموداری از نسبت خطا به تعداد  \lr{RRH} در هر خوشه رسم شده است. 
\begin{figure}
  \centering
    \includegraphics[scale=0.7]{./pic1/88}
  \caption{  نسبت خطا به تعداد \lr{RRH} در هر خوشه \cite{graph}  }
  \label{fig:88}
\end{figure}
\section{نتیجه گیری}
در این فصل، نسل پنجم مخابرات یعنی \lr{5G} و ساختار جدید \lr{C-RAN} که مورد توجه در این نسل مخابرات است ،مورد بررسی قرار گرفته شده و مزایا و چالش های پیش روی آن به طور مختصری بیان کرده ایم . همچنین ساختار های جدیدی که ساختارهای تعمیم یافته ی \lr{C-RAN}می باشد را مورد بررسی قرار داده ایم.این ساختارهای جدید قابلیت کاهش هزینه های ساخت و بهره
برداری از شبکه و هم چنین بهبود کارایی سیستم از لحاظ
پوشش دهی و تحرک پذیری را دارا می باشد و شاید بتوان
افزایش بهره ی انرژی را جزو مهمترین مزایای این ساختار
عنوان کرد.

\section{خلاصه ای از فصلهای آتی}
در فصلهای بعدی، مدل سیستم ساختار \lr{C-RAN} مورد بررسی قرار می گیرد.
در فصل 2 به کارهای گذاشته و مدل سیستمهای گذشته در لینک فروسو و فراسو می پردازیم و مفهومی به نام بازدهی انرژی\LTRfootnote{Energy efficiency}
را بیان می کنیم و هدفمان در این فصول بیشینه سازی مجموع نرخ های قابل دسترس و بیشینه سازی بازدهی انرژی می باشد.
در فصل سوم به بررسی مدل سیستم جدیدی می پردازیم که نسبت کارهای قبلی تغییرات اندکی کرده است و در فصل چهارم نیز مدل سیستمی با تغییرات بیشتری را در نظر داریم و در نهایت در فصل پنجم به نتیجه گیری تمام فصل ها پرداخته می شود.

### 2022-01-15 Latex/journal_v1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (1)/pr.tex
first commit for new git

@@
 \subsection{System Model}
-There are three service types including mMTC, eMBB, and uRLLC, which support different applications.
-There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and uRLLC service types, respectively and we have $S = S_1 + S_2 + S_3$.
-{\color{red} explain pre-allocated more}
+There are three service types including mMTC, eMBB, and URLLC, which support different applications.
+There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and URLLC service types, respectively and we have $S = S_1 + S_2 + S_3$.
+%{\color{red} explain pre-allocated more}
 Therefore, there are $S$ pre-allocated slices serving these $S$ services;
-Each pre-allocated slice contains reserved VNFs for the MAC/RLC functions in the O-DU logical node, the PDCP/SDAP functions in the O-CU-UP, and the UPF nodes. 
- There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (uRLLC), and $S_3$ slices for the third service type (mMTC).
+Each pre-allocated slice contains reserved VNFs for the three logical nodes:
+\begin{itemize}
+\item The MAC/RLC functions in the O-DU logical node
+\item The PDCP/SDAP functions in the O-CU-UP logical node
+\item The UPF logical node
+\end{itemize}
+
+ There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
 So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.
@@
 Based on the application and QoS request, UE may be admitted and allocated to the resources.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of 
-%pre-allocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs),
- $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.
-
-All $K$ PRBs can be assigned to all UE in each service.
+Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.
+
+Assume we have $K$ physical resource blocks (PRBs) in this system.
+All $K$ PRBs can be assigned to all UEs in each service.
 Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.
@@
 The derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{P}$ and $\boldsymbol{E}$ give the Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal value of these two variables \cite{lee2018dynamic,ali2018joint}.
-
-Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
+\end{lemma}
+\begin{proof}
+Assume UE $i$ in slice $s$, associated with O-RU $r$, is allocated to PRB $k$  (i.e., $e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition
 \begin{equation}\label{deriveP}
@@
   \begin{cases}
-      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S\\
-      0 & \text{otherwise}
+      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S, \\
+      0 & \text{otherwise,}
     \end{cases}
 \end{equation}
-Where, $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
- \end{lemma}
-Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$.
-Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
+where $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
+ \end{proof}
+Thus, the user in slice $s$ that has  the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to PRB $k$.
+Since just one PRB can be allocated to a UE between those UEs (regardless of the services), that is associated to the same O-RU.
 The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
@@
 \section{Numerical Results and The Feasible Region}\label{NE}
-In this section, firstly we describe the initial points and the comparison algorithms.
-Then we talk about the feasible region in our system. 
-Afterward, we illustrated the numerical results.
+In this section, firstly, we describe the initial points and the comparison algorithms.
+Then, we talk about the feasible region of our system model. Afterward, we illustrate the numerical results.
+
 \subsection{The initial Points and The Comparison Algorithms}
 In this part, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method.
-We consider three network slices for eMBB, uRLLC, and mMTC services.
-Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this place.
+We consider three network slices for eMBB, URLLC, and mMTC services.
+Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in Figure \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
 \begin{figure}
@@
 \end{figure}
-Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.
-Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
-Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution
-and it is the Rayleigh fading channel between the UE and O-RU.
-We consider 25 PRBs are used in the network and the
-packet size is equal to 20 bytes.
-The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the uRLLC  service is $\lambda  = 0.2Mbps$. 
-Also the quantization noise is assumed to be $10^{-13}$.
+Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
+Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
+We consider 25 PRBs are used in the network and the packet size is equal to 20 bytes.
+The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
+Also, the quantization noise is assumed to be $10^{-13}$.
 Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.
-
-The other parameters of these simulations are depicted in Table \ref{table:1a}.
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a}.
 \begin{table}
- \caption {Simulation Parameter} \label{table:1a}
+ \caption {Simulation Parameters} \label{table:1a}
  \begin{center}
-  \begin{tabular}{||c c ||}
+  \begin{tabular}{||c | c ||}
   \hline
@@
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Aggregate Throughput vs. Number of UE in each Service In the Presence of Three Services}
+  \caption{Aggregate throughput vs. number of UEs for each service in the presence of three services}
   \label{fig:1}
 \end{figure}
-%Assume we have two type of services (uRLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
-%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services uRLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
-%The figure \ref{fig:2}, presented that by increasing the priority factor for uRLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
+%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
+%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
+%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
 %\begin{figure}
 %  \centering 
-%    \includegraphics[scale = 0.4]{mmtcurllc.eps}
+%    \includegraphics[scale = 0.4]{mmtcURLLC.eps}
 %    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
 %    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput for mMTC and uRLLC vs. Priority of uRLLC }
+%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
 %  \label{fig:2}
 %\end{figure}
-%In figure \ref{fig:3}, the total sum rate of uRLLC and mMTC is shown vs. priority of uRLLC. It is shown that the proposed method is much better than the baseline scheme. 
+%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
 %\begin{figure}
@@
 
-Figure \ref{fig:4}, depicts the number of activated VNF for the five different mean service times of one uRLLC service vs.
+Figure \ref{fig:4} depicts the number of activated VNFs for five different mean service times of one URLLC service vs.
 the mean arrival time for 12 UEs.
-This figure presented that as the mean arrival rate increases, the number of activated VNF increases.
-Moreover, the number of activated VNFs decreased when the mean service rate increases.
+This figure presents that as the mean arrival rate increases, the number of activated VNF increases.
+Moreover, the number of activated VNFs decreases when the mean service rate increases.
 
@@
 
-Figure \ref{fig:6}, illustrates the mean total delay of a UE in a uRLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
+Figure \ref{fig:6} illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
 It is shown that the delay is an ascending function of the mean arrival rate (when the mean service time is fixed) and the number of UEs in the service.
-In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a uRLLC service is $0.5ms$.
+In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a URLLC service is $0.5ms$.
 Also, the maximum number of PRB is considered to be 50.
- Moreover, we can see that the mean delay of a uRLLC service 
+ Moreover, we can see that the mean delay of a URLLC service 
 does not reach the maximum threshold of the delay.
-%Moreover, we can see that the mean delay of a uRLLC service increases almost linearly with the mean arrival rate of the packet transmission. 
+%Moreover, we can see that the mean delay of a URLLC service increases almost linearly with the mean arrival rate of the packet transmission. 
 \begin{figure}
@@
 \section{Conclusion}\label{conc}
-This paper proposed the downlink of the O-RAN system using network slicing for different 5G services, i.e., eMBB, mMTC, and uRLLC.
-The isolation of various services, i.e., eMBB, mMTC, and uRLLC in the O-DU, the O-CU, and the UPF, is accomplished.
+This paper proposed the downlink of the O-RAN system using network slicing for different 5G services, i.e., eMBB, mMTC, and URLLC.
+The isolation of various services, i.e., eMBB, mMTC, and URLLC in the O-DU, the O-CU, and the UPF, is accomplished.
 Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.
@@
 In addition, the feasible region is discussed, and the FA algorithm is introduced to check the feasibility of the initial values.
-Also, we assume distinct scenarios for each service, i.e., eMBB, mMTC, and, uRLLC based on their requirement QoS.
+Also, we assume distinct scenarios for each service, i.e., eMBB, mMTC, and, URLLC based on their requirement QoS.
 Simulation results show that the proposed method (IABV) achieved a $18.6\%$ higher data rate than the baseline scheme.

### 2022-01-15 Latex/journal_v1/V3/pr.tex
simulation change
first commit for new git

@@
 Assume we have preallocated slices serving these services;
+So each service request $s$ served by its corresponding slice.
 Each Service $s\in \{1,2,3 \} $ consists of $U_{s}$ request from the 
@@
 Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
-Each slice $s_ \in \{1,23 \}$ consists of $K_{s}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+Each slice $s_ \in \{1,2,3 \}$ consists of $K_{s}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
 
@@
 
-In addition, there are $R$ single-antenna RU that are shared between slices. All RUs $r \in \{1,2,...,R \}$
-transmit signals cooperatively to all the UEs(RUs are in comp mode). Moreover, all RUs, have access to PRBs.
+In addition, there are $R$ single-antenna RU that are shared between slices. 
+All RUs $\{ r_i | i\in 1,2,...,R \}$
+transmit signals cooperatively to all the UEs. 
+Also $\mathcal{R} = \{ r_i | i\in 1,2,...,R \}$ depicts the set of o-RUs.
+Moreover, all o-RUs, have access to all PRBs.
 \subsection{The Achievable Rate}
-The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
+The SNR of $i^{th}$ UE  served at slice $s$ on PRB $k$ is obtained from
 \begin{equation}\label{eq2}
-\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
+\rho_{u(s,i)}^{k} =  \frac{|p_{u(s,i)}^{k}{\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} \bold{w}_{\mathcal{R},u(s,i)}^{k}}{BN_0 + I_{u(s,i)}^{k}},
 \end{equation} 
-where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
-${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
-$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice.
-In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
+where $p_{u(s,i)}^{k}$ represents the transmission power allocated by set of o-RUs $\mathcal{R}$ to $i^{th}$ UE requesting $s^{th}$ service on PRB $k$. 
+${\bold{h}_{\mathcal{R},u(s,i)}^{k}} \in \mathbb{C}^{R}$ is the vector of channel gain of a wireless link from set of 
+$\mathcal{R} = \{r\in 1,2,...,R\}$ O-RUs to the $i^{th}$ UE requesting $s^{th}$ service.
+In addition, $\bold{w}_{\mathcal{R},u(s,i)}^{k} \in \mathbb{C}^{R}$ depicts the  transmit beamforming vector from set of $\mathcal{R}$ o-RU to the $i^{th}$ UE served by $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
 \begin{equation}
-\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
+\bold{w}_{\mathcal{R},u(s,i)}^{k} = {\bold{h}_{\mathcal{R},u(s,i)}^{k}}({\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} {\bold{h}_{\mathcal{R},u(s,i)}^{k}})^{-1}
 \end{equation}
-Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocate to $s^{th}$ slice or not. 
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
+Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(s,i)}^{k}$ is the power of interfering signals represented as follow
 \begin{equation}
 \begin{split}
-I_{r,u(s,i)}^{k} &=
- \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,i)}^{k} g_{u(s,i)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
-&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
+I_{u(s,i)}^{k} &=
+ \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k} |{\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} \bold{w}_{\mathcal{R},u(s,i)}^{k} |^2}_{\text{(Interference Power)}}\\
+&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 a_{u(s,i)}}_{\text{(Quantization Noise Interference)}}
 \end{split}
 \end{equation}
-where $\gamma_{1} = e^{k}_{r,u(s,i)}e^{k}_{r',u(s,l)}a_{u(s,i)}a_{u(s,l)}$
-and $\gamma_{2} = e^{k}_{r,u(s,i)}e^{k}_{r',u(n,l)}a_{u(s,i)}a_{u(y,l)}$.
+where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}a_{u(s,i)}a_{u(s,l)}$.
 Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
-$e^{k}_{r,u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
+$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
 

### 2022-01-15 Latex/journal_v1/V4-comp/pr.tex
first commit for new git

--- 2021-06-26 Latex/journal_v1/V4/pr.tex
@@
 In this algorithm, Firstly we sort slices based on their priority (So the UEs of slices are sorted too).
-Then we assign one O-RU to each UE based on GAAOU algorithm so we guarantee that each UE is assigned to a O-RU. Next, we want to assign more than one O-RU to UE.
+We depict $ {\mathfrak{B}}^{rem}_{u_{(s,i)}} \forall s, \forall i$ as a set of O-RUs for each user in each slice.
+At the beginning of the algorithm, $ {\mathfrak{B}}^{rem}_{u_{(s,i)}} =  \mathcal{R} \forall s, \forall i$.
+Then we assign one O-RU to each UE based on GAAOU algorithm so we guarantee that each UE is assigned to a O-RU. Next, we want to check if we can assign more than one O-RU to UE.
+
 \begin{algorithm}
@@
 \begin{algorithmic}[1]
-\State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{31}
-\State Set $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
+\State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{a1}
+\State Set $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{a2}
+\State Set ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$  $\forall s, \forall i$
 \State Set $\mathtt{R}^{t} = 0$

### 2022-01-15 Latex/report1/pr.tex
first commit for new git

--- 2020-10-23 NetworkSlicing/report123/report1.tex
@@
 
+\title{Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}
+}
+%
+%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%mojdeh.karbalaee@ut.ac.ir}
+%\and
+%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%vmansouri@ut.ac.ir}
+%\and
+%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
+%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
+%\textit{Tehran University}\\
+%Tehran, Iran \\
+%salar.nouri@ut.ac.ir}
+%}
+  \author{
+    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
+    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
+    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
+    \vspace{-.2cm}
+  }
+  }
+
 \maketitle
 
-\section{Network Slicing}
-Network slicing, where several logical
-networks share a single physical network, has been considered as one of
-the key enablers for 5G.
+\begin{abstract}
 
-Network slicing is a promising technology for
-5G to provide a network as a service (NaaS) for a wide range of
-services that run on different virtual networks deployed on a
-shared network infrastructure. 
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.4]{Capture1.PNG}
-\caption{ Big data driven networking}
-\label{fig:Bigdata}
-\end{figure}
-A critical component of network slicing is resource allocation, which needs
-to ensure that slices receive the resources needed to support their mobiles/services while optimizing network efficiency.
+\end{abstract}
+\begin{IEEEkeywords}
 
-In a sliced network, network operators
-realize the network slices instances to provide the required
-network characteristics to different services, pertaining to
-third-party tenants.
- Therefore, there will be Service Level
-Agreements (SLAs) between network operator and the tenants
-to declare the requirements of a particular service and the
-operator should fulfill these SLAs via instantiating appropriate
-network slices. Requirements of the service instances are
-specified in terms of Key Performance Indicators (KPIs), such
-as throughput, latency, availability, coverage, etc.
-
-An important aspect of network slicing is to guarantee that
-the slices operate independently, i.e., the performance, congestion, failure, etc., in one slice will not negatively influence the
-performance of other slices which are sharing the resources.
-This means that providing protection from other slices is one
-To enable Internet of things (IoT) including high data rate, numerous devices
-connection and low service latency,
-network slicing and fog computing have been envisioned as
-promising solutions in service-oriented 5G architecture.
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.5]{Capture.PNG}
-\caption{ Service-oriented Architecture of Fog-assisted 5G Network with Network Slicing}
-\label{fig:FogNS}
-\end{figure}
-\section{System Model}
-Assume a system model with different types of user equipment (UE).
-There exists two different types of
-UEs with different requirements: low-latency users (LUs) and
-high-data rate Tactile users (TUs).
-
-The first group is very sensitive to the latency. The second group needs high data rate.
-Each slice sustains a queue
-for the incoming slice traffic, which has a backlog.
-%The arrival traffic per slot can be modeled.
-The network model is assumed to be composed of a set of M
-base stations (BSs).
-We have three types of slice resource requirements.
-\begin{itemize}
-\item A fixed slice requests dedicated radio resources along
-time and frequency domains. Therefore, it is isolated
-from other slices and does not multiplex its resources
-with others. One example is the bandwidth parts (BWPs)
-defined in 5G (see 3GPP TS 38.211) that operate on
-disjoint parts of the spectrum with a given numerology.
-\item A dynamic slice requests a share of resources in terms
-of aggregate throughput. It can be mapped to the eMBB
-usage scenario, and thus a precise radio resource allocation is less important than the efficient use of available
-resources for a guaranteed throughput.
-\item An on-demand slice exhibits more stringent requirements
-in terms of latency, and hence it can be mapped to
-the URLLC scenario. Therefore, such slice should be
-assigned radio resources with short delay, in comparison
-with the dynamic slice.\citep{schmidt2019slice}
-\end{itemize}
+\end{IEEEkeywords}
 \section{introduction}
@@
 issues in large-scale networks.
+
  Cooperative Game with Distributed Learning
@@
 where $w_v$ is the bandwidth of service $v$.
-\bibliographystyle{plain}
-\bibliography{references}
+\bibliographystyle{IEEEtran}
+\bibliography{ref}
 \end{document}

### 2022-01-15 Latex/tehran-thesis - Copy/tex/chapter1.tex
first commit for new git

@@
 	\begin{alignat}{4}
-		\min\limits_{\boldsymbol{x} }   \quad &   \sum_{j=1}^{n}  y_{j}\\
-		\text{\lr{subject to}} \quad & \textstyle \sum_{j=1}^{n}x_{ij} =1  \quad i =1,...,m, \\
-		&  \sum_{j=1}^{m} r_{i,j} x_j \leq b_i  \quad i=1,..,m \\
+		\min\limits_{\boldsymbol{x} }   \quad &  K= \sum_{j=1}^{n}  y_{j}\\
+		\text{\lr{subject to}} \quad & K\geq 1 \\
+		& \sum_{j=1}^{n}x_{ij} =1  \quad i =1,...,m, \\
+		&  \sum_{i=1}^{m} r_{i} x_{ij} \leq b_j  \quad j=1,..,n \\
 		&  x_{ij} \in \{0,1\}  \quad y_j \in \{0,1\} \quad \forall i,j \label{eqmain}
@@
 \end{subequations}
-در اینجا، $y_j$ تعداد جعبه‌های مورد استفاده است که درصورتی که  $\sum_{j=1}^{n}x_{i,j \geq 1}$
-باشد، $y_j$ مقدار 1 می‌گیرد و در غیر این صورت 0 است \cite{berkey1987two}.
+در اینجا، $y_j$ تعداد جعبه‌های مورد استفاده است که درصورتی که  
+$\sum_{i=1}^{n}x_{ij} \geq 1$
+باشد، $y_j$ مقدار 1 می‌گیرد 
+$x_{ij}$
+نشان می‌دهد که شی i در جعبه‌ی j جا دارد.
+و در غیر این صورت 0 است \cite{berkey1987two}.
 

### 2022-01-15 Latex/tehran-thesis/tex/chapter3.tex
add file
first commit for new git

@@
-\chapter{تخصیص منابع در شبکه های \lr{Open RAN}}
+\chapter{تخصیص منابع در شبکه‌های دسترسی باز}
 \section{مقدمه}
-در این فصل، هدف تخصیص منابع در شبکه های \lr{Open RAN} در لینک فروسو می باشد که شامل تخصیص توان و برش های شبکه است.
+در این فصل، هدف تخصیص منابع در شبکه های \lr{Open RAN} در لینک فروسو می‌باشد که شامل تخصیص توان و برش های شبکه است.
 در این بخش فرض بر این است که در شبکه ی نسل پنجم مخابرات از زیرساخت \lr{Open RAN} استفاده شده است.
 این شبکه سرویس هایی از قبیل \lr{IoT}، سرویس تلفن، پیامک و ...
-در اختیار کاربران قرار می دهد.
-در اینجا  مفهوم برش شبکه در سیستم بدین صورت به کار رفته که به جای دیدن کاربران به صورت مجزا، کاربرانی که از یک سرویس خاص استفاده می نمایند در دسته ی آن سرویس قرار گرفته و دسته بندی می شوند.
-همچنین برش هایی از شبکه در اختیار کاربران هر سرویس خاص، قرار می گیرد که هر برش شبکه شامل تعدادی واحد رادیویی
+در اختیار کاربران قرار می‌دهد.
+در اینجا  مفهوم برش شبکه در سیستم بدین صورت به کار رفته که به جای دیدن کاربران به صورت مجزا، کاربرانی که از یک سرویس خاص استفاده می‌نمایند در دسته ی آن سرویس قرار گرفته و دسته بندی می‌شوند.
+همچنین برش هایی از شبکه در اختیار کاربران هر سرویس خاص، قرار می‌گیرد که هر برش شبکه شامل تعدادی واحد رادیویی
 \LTRfootnote{Radio Unit}
@@
 $\lambda_{u(v,i)}$
-برای $i$امین کاربر در سرویس $v$ ام می باشد.
-بنابراین، در لایه ی واحد مرکزی (\lr{CU})، میانگین نرخ ورود داده ی کاربری که از خدمات برش $s$ استفاده می نماید 
+برای $i$امین کاربر در سرویس $v$ ام می‌باشد.
+بنابراین، در لایه ی واحد مرکزی (\lr{CU})، میانگین نرخ ورود داده ی کاربری که از خدمات برش $s$ استفاده می‌نماید 
 $\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$
-می باشد. 
+می‌باشد. 
 همچنین، میانگین نرخ داده ی ورودی در لایه ی \lr{DU}، تقریبا مساوی میانگین نرخ داده ی ورودی لایه ی اول 
 $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$
-می باشد.
-میانگین نرخ داده ی ورودی در لایه ی \lr{DU}، تقریبا برابر میانگین نرخ داده ی ورودی در لایه ی \lr{CU} می باشد $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$.
-در اینجا فرض بر این است کهدر هر لایه متعادل کننده ی ترافیک موجود است که ترافیک ورودی را به طور مساوی بین \lr{VNF} ها تقسیم می نماید\cite{frdl,luong2018novel,luong2018novel1}.
-فرض کنید پردازش باند پایه هر \lr{VNF}، بوسیله ی پردازش صف \lr{M/M/1} نشان داده می شود.
-هر بسته بوسیله ی یکی از \lr{VNF}های برش شبکه، پردازش می شود.
-بنابراین، میانگین تاخیر برش $s$ در لایه ی اول و دوم با استفاده از مدل \lr{M/M.1} به این صورت نشان داده می شود
+می‌باشد.
+میانگین نرخ داده ی ورودی در لایه ی \lr{DU}، تقریبا برابر میانگین نرخ داده ی ورودی در لایه ی \lr{CU} می‌باشد $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$.
+در اینجا فرض بر این است کهدر هر لایه متعادل کننده ی ترافیک موجود است که ترافیک ورودی را به طور مساوی بین \lr{VNF} ها تقسیم می‌نماید\cite{frdl,luong2018novel,luong2018novel1}.
+فرض کنید پردازش باند پایه هر \lr{VNF}، بوسیله ی پردازش صف \lr{M/M/1} نشان داده می‌شود.
+هر بسته بوسیله ی یکی از \lr{VNF}های برش شبکه، پردازش می‌شود.
+بنابراین، میانگین تاخیر برش $s$ در لایه ی اول و دوم با استفاده از مدل \lr{M/M.1} به این صورت نشان داده می‌شود
 \begin{equation}
@@
 \subsection{صورت مساله}
-یک معیار مهم برای سنجش بهینگی یک سیستم ، بهره وری انرژی است که نسبت نرخ کل به توان کل می باشد.
+یک معیار مهم برای سنجش بهینگی یک سیستم ، بهره وری انرژی است که نسبت نرخ کل به توان کل می‌باشد.
 \begin{equation}
@@
  $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$
- توان کل مصرفی تمام واحد های رادیویی در یک برشمی باشد.
+ توان کل مصرفی تمام واحد های رادیویی در یک برشمی‌باشد.
 همچنین 
  $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $
- نرخ تمام کاربران مصرفی تمام سرویس ها می باشد.
-فرض کنید توان مصرفی پردازش باند پایه در هر مرکز داده ی $d$ که به \lr{VNF} های یک برش $s$ متصل می باشد با   
+ نرخ تمام کاربران مصرفی تمام سرویس ها می‌باشد.
+فرض کنید توان مصرفی پردازش باند پایه در هر مرکز داده ی $d$ که به \lr{VNF} های یک برش $s$ متصل می‌باشد با   
 $\phi_{s,d}$
 نشان داده شده است.
-بنابراین می توان توان کل سیستم را برای کلیه مرکز داده های فعال که به برش متصل هستند ،بدین صورت نشان داد
+بنابراین می‌توان توان کل سیستم را برای کلیه مرکز داده های فعال که به برش متصل هستند ،بدین صورت نشان داد
 \begin{equation*}
@@
 \eqref{c23}
-تضمین می کند که هر برش که شامل VNF هایی در دو لایه است،
-به حداقل یک مرکز داده متصل می شود.
+تضمین می‌کند که هر برش که شامل VNF هایی در دو لایه است،
+به حداقل یک مرکز داده متصل می‌شود.
 در \eqref{c22} 
 $\mathcal{E} = \{M,S,C\}$ 
-و شرطها ضمانت می کند که منابع فیزیکی کافی برای VNFها وجود دارد.\newline
+و شرطها ضمانت می‌کند که منابع فیزیکی کافی برای VNFها وجود دارد.\newline
 مسئله‌ی بهینه‌سازی \eqref{constraints}
@@
 		\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
-		\text{\lr{subject to}} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
-		&\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
+		\text{\lr{subject to}} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \quad \forall s, \\
+		&\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \quad \forall d, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
 	\end{alignat}
@@
 بدست می‌آید. 
-بعد از بدست آوردن $\boldsymbol{P}$ و $\eta$ الگویتم با مقادیر جدید توان و بهره‌وری انرژی دوباره تکرار می گردد تا همگرا شود.
+بعد از بدست آوردن $\boldsymbol{P}$ و $\eta$ الگویتم با مقادیر جدید توان و بهره‌وری انرژی دوباره تکرار می‌گردد تا همگرا شود.
 در اینجا الگوریتم حل مسئله‌ی اول به صورت الگوریتم \eqref{alg2} است.
@@
 برای بدست‌آوردن مقدار بهینه‌ی $\boldsymbol{Y}$ الگوریتم ابتکاری برای حل مسئله‌ی سه بعدی بسته‌بندی جعبه ارائه شده است.
-جزئیات الگوریتم در \eqref{alg3} نوشته شده است. در این الگوریتم، در ابتدا برشهای شبکه و مرکز داده ها را بر اساس  جمع وزنی آنها مرتب می کنیم (خط \ref{31} و \ref{32} الگوریتم \ref{alg3}).
+جزئیات الگوریتم در \eqref{alg3} نوشته شده است. در این الگوریتم، در ابتدا برشهای شبکه و مرکز داده ها را بر اساس  جمع وزنی آنها مرتب می‌کنیم (خط \ref{31} و \ref{32} الگوریتم \ref{alg3}).
 در اینجا، پارامتر وزندار برای $\Omega_{\mathfrak{z},s}^{tot}$ و $\tau_j^\mathfrak{z}$ بدین صورت تعریف می‌کنیم.
@@
 \cite{3dbin}.
-در مرحله دوم، ما تخصیص را از بیشترین برش های مورد نیاز به DC با بیشترین منابع فیزیکی شروع می کنیم(از خط \ref{33} تا \ref{34} الگوریتم \ref{alg3}).
+در مرحله دوم، ما تخصیص را از بیشترین برش های مورد نیاز به DC با بیشترین منابع فیزیکی شروع می‌کنیم(از خط \ref{33} تا \ref{34} الگوریتم \ref{alg3}).
  بعد از تخصیص برش شبکه به مرکز داده، در صورتی که یکی از برشهای شبکه توسط مرکز داده پذیرش نشود، برای بخش بعدی جاگذاری می‌رود

### 2022-01-15 Latex/tehran-thesis/tex/chapter4.tex
first commit for new git

@@
 	\begin{alignat}{4}
-		\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
-		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}(t) \geq 1 \forall s, \\
-		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d}  \forall d,, \forall ;  \label{eqomega}
+		\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})(t)\\
+		\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c} y_{s,d}(t) \geq 1 \quad \forall s, \\
+		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d} \quad  \forall d, \forall ;  \label{eqomega}
 	\end{alignat}
@@
 \end{equation} 
-که به صورت
+که به صورت تکراری اعمال این اپراتور 
+$Q_{t+1}(s,a) \leftarrow T^{*}Q(s,a) $
+منجر به همگرا شدن 
+$Q_{t}(s,a) \rightarrow Q^*(s,a)$
+ و
+ $t \rightarrow \infty $
+می‌شود
+\cite{montague1999reinforcement,gan1}.
+در ابعاد بالاتر، بهتر است از تابع تقریبی استفاده
+شود. فرض کنید 
+$Q_{\theta}(s,a)$
+تابع تقریب با پارامتر $\theta$
+می‌باشد که تقریبی از جدول مقدار عمل با (s,a)
+می‌باشد. هدف این بهینه‌سازی، بدست‌آوردن $\theta$
+است به طوری که 
+$Q_{\theta}(s,a) \approxeq Q^{*}(s,a)$
+و مقدار بهینه، به طور تکراری با اعمال اپراتور $T^*$
+بدست می‌آید. 
+مقدار بهینه‌ی 
+$\theta$
+قابل دستیابی با استفاده از مینیمم کردم خطای تفاوت زمانی (TD-error)
+برروی (s,a,r,s') می‌باشد که به طور رندم انتخاب می‌شوند.
+\begin{equation}
+\zeta^2 = [r + \gamma \max_{a' \in A}{Q_{\theta}(s',a')}-Q_{\theta}(s,a)]^2
+\end{equation}
+روشهای مخنلفی برای دستیابی به مینیمم خطا هست که ما در ادامه‌ی کار از روش Q-learnng استفاده می‌کنیم.
+در روش Q-learning در هر بروزرسانی تابع Q داریم:
+\begin{equation}
+	Q(s_{t+1},a_{t+1}) = Q(s_t,a_t)+\alpha[ r_{t+1} + \gamma \max_{a \in A}{Q(s_{t+1},a)}-Q(s_t,a_t)]
+\end{equation}
+که دراینجا، $\alpha$
+نرخ یادگیری می‌باشد.
+\subsection{نتایج عددی مسئله‌ی اول}
+در این بخش، برای مسئله‌ی اول حالت، عامل و پاداش را تعیین می‌نماییم و سپس نتایج عملی را نشان می‌دهیم.
+در این مسئله، عامل، orchestrator است که وظیفه‌ی مدیریت شبکه را برعهده دارد.
+همچنین، حالت در هر بازه‌ی زمانی برشهایی از شبکه است که به سرویسها متصل شده و همچنین مقدار منبع باقی ماده در هر برش می‌باشد. 
+پاداش طوری تعیین شده که بیشترین تعداد سرویسها پذیرفته شود به طوریکه شرط تاخیر و نرخ برآورده گردد.
+برای حل این مسئله به روش دینامیکی، دو مدل سرویس در نظر گرفتیم و تاخیر در اینجا فعلا لحاظ نشده است و در مدل اول سرویس نیازمند نرخ $10MHz$ و مدل دوم سرویس نیازمند مدل $20MHZ$
+می‌باشد.
+فرض می‌کنیم نرخ ورود سرویس در هر ابتدای بازه‌ی زمانی عدد رندم با توزیع پواسون می‌باشد.
+نرخ خروج سرویس نیز از توزیع پواسون پیروی می‌کند.
+در اینچا فرض می کنیم از  سرویس اول ماکسیمم در هر لحظه ۱۰ سرویس و از سرویس دوم ۵ تا سرویس درخواست می‌دهد.
+۵ برش شبکه با نرخ $10MHz$ نیز وجود دارد.
+در شکل \ref{fig:dynamicEpoch}
+نسبت تعداد سرویسهای پذیرفته شده به نسبت تعداد سرویسهای پذیرفته شده در حالت بهینه براساس زمان طی شده داده می‌شود.
+بعد از حدود ۱۰۰۰۰۰ تکرار، تقریبا خروجی با خروجی بهینه یکی می‌شود و مقدار پذیرفته شده با مقدار بهینه یکی می‌شود.
+
+\begin{figure}%[H]
+	\centering
+	\includegraphics[scale = 0.5]{./fig/dynamicEpoch} %[width=\linewidth] 
+	\caption{ نسبت تعداد سرویسهای پذیرفته شده به نسبت تعداد سرویسهای پذیرفته شده در حالت بهینه براساس زمان طی شده}
+	\label{fig:dynamicEpoch}
+\end{figure}
+\subsection{نتایج عددی مسئله‌ی دوم} 
+در این بخش، برای مسئله‌ی دوم حالت، عامل و پاداش را تعیین می‌نماییم و سپس نتایج عملی را نشان می‌دهیم.
+در این مسئله، عامل، orchestrator است که وظیفه‌ی مدیریت شبکه را برعهده دارد.
+همچنین، حالت در هر بازه‌ی زمانی برشهایی از شبکه است که به مراکزداده متصل شده و اینکه کدام برش به کدام مرکز داده متصل است.
+پاداش طوری تعیین شده که کمترین تعداد مراکز داده استفاده گردد و هر لحظه کمترین تعداد مرکز داده‌ی خاموش، روشن شود.
+\section{نتیجه‌گیری}
+در این فصل، دو مسئله‌ی فصل قبلی به صورت ساده شده نوشته شد و مسئله‌ی اول در بخش رادیویی از جنس کوله‌پشتی و مسئله‌ی دوم در بخش هسته از نوع 
+بسته‌بندی جعبه می‌باشد.
+این دو مسئله به صورت دینامیکی در هر لحظه از زمان حل شده‌اند.
+برای حل این دو مسئله از روش یادگیری تقویتی عمیق استفاده شده و حالتها و اعمال بیان برای یک عامل در این مسئله بیان گرده است.
+نتایج عملی آن نیز رسم گردید.

### 2022-01-15 latex_report/20161125.tex
first commit for new git

%\documentclass[onecolumn,draftcls]{IEEEtran}
%\documentclass[journal,twocolumn,10pt,letter]{IEEEtran}
%\documentclass[conference,10pt,twocolumn,letter]{IEEEtran}
\documentclass[journal,onecolumn,11pt,draftcls,doublespace]{IEEEtran}
%\documentclass[journal,onecolumn,11pt,doublespace]{IEEEtran}
%\documentclass[journal,onecolumn,11pt,draftcls,doublespace]{IEEEtran}
%\documentclass[journal,onecolumn]{IEEEtran}
\IEEEoverridecommandlockouts
\ifCLASSINFOpdf
\else
\fi
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[cmex10]{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{amsbsy}
\usepackage{mathrsfs}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{psfrag}
\usepackage{newclude}
\usepackage[normalem]{ulem}
\usepackage{latexsym}
%\usepackage{tikz}
\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{bbm} % indicator function
\usepackage{filecontents}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\def\CE{\mathcal{E}}
\def\A{{A^n_\epsilon}}
\def\bS{{\boldsymbol{S}}}
\def\bs{{\boldsymbol{s}}}
\def\bz{{\boldsymbol{z}}}
\def\bu{{\boldsymbol{u}}}
\def\bv{{\boldsymbol{v}}}
\def\bU{{\boldsymbol{U}}}
\def\bx{{\boldsymbol{x}}}
\def\bX{{\boldsymbol{X}}}
\def\by{{\boldsymbol{y}}}
\def\bY{{\boldsymbol{Y}}}
\def\pr{{\text{P}}}
\def\c{{\mathcal{C}}}
%%%%%%%%%%%%%%%%% Define \doublehat
\usepackage{accents}
\usepackage[absolute]{textpos}
\newlength{\dhatheight}
\newcommand{\doublehat}[1]{%
    \settoheight{\dhatheight}{\ensuremath{\hat{#1}}}%
    \addtolength{\dhatheight}{-0.35ex}%
    \hat{\vphantom{\rule{1pt}{\dhatheight}}%
    \smash{\hat{#1}}}}
%%%%%%%%%%%%%%%%%%% Define Independent Symbol
\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\graphicspath{{figures/}}
\allowdisplaybreaks
\newcommand{\eqdef}{\overset{\mathrm{def}}{=\joinrel=}}
\hyphenation{op-tical net-works semi-conduc-tor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{"In the name of GOD" \\[2in] Power Allocation for Distributed MIMO C-RAN System } \author{\IEEEauthorblockN{\normalsize
     Mojdeh Karbalaee Motalleb}

    \vspace{2cm}
    }

\maketitle

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Cloud radio access networks generate a new architechture for 5G that is proposed to enhance both spectral efficiency and energy efficiency. 
This project investigates the optimal power allocation for the downlink of Multiple-Input Multiple-Output (MIMO) Cloud Radio Access Network (C-RAN) with limited fronthaul capacity in terms of maximizing Energy Efficiency (EE). 
In the considered system, the compressed and precoded message generated by Central Unit (CU) is transmitted to Remote Radio Heads (RRHs) via a fronthaul link with limited capacity, and the RRHs and Users Equipments (UEs) are assumed to be clustered into $S$ cluster sets.
Here, we use an iterative algorithm with Lagrangian function to optimize the EE.

 \emph{index Terms}- Cloud Radio Access Network, Multiple-Input Multiple-Output, Energy efficiency, Clusterization, Power allocation, Lagrangian function.
\end{abstract}
\IEEEpeerreviewmaketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\tableofcontents
\newpage
\listoffigures
\listoftables
\newpage
\section{Introduction}
The growing demand of higher data rates led vendors to think of the next generation of wireless networks which will essentially provide higher throughputs and more coverage than the state-of-art technologies. There are some new concepts introduced to enhance 5G networks such as; Het-Net systems, mmWave communications, Large-scale MIMO systems, and Cloud-Radio Access Networks. Each of the above mentioned concepts fulfills different requirements of 5G networks. As the main focus of this project is on the C-RAN technology, it is briefly introduced next. In C-RAN systems, in order to have a more efficient system in terms of computational resources, baseband processings, which may have high computational complexities, are transfered from base stations to control centers located in a cloud. In addition to manage computational resources, C-RAN technology can provide new concepts such as co-operation among RRHs, RRH clustering \cite{33,55}. To obtain both advantages of C-RAN and MIMO system, using MIMO C-RAN system simultaneously can enhance achievable rate and also EE \cite{33}. By using MIMO system, we can achieve higher data rates and even better EE compared to conventional systems by exploiting multiple number of antennas to transmit or receive data streams.

In order to consider feasible links between CU and RRHs, named as \emph{fronthaul}, the capacities of these links are assumed to be limited \cite{22,44,1111,66}. As a result of the limited fronthaul capacity the signals passed through these links need to be compressed \cite{22,44,1111,66} . One of the main problems that recently has attracted the attention of researches in MIMO C-RAN systems is how to efficiently perform detections, precodings and compressions of messages before transmitting them to CU or RRHs. Deploying efficient resource allocations causes prevention of wasting energy and as a result leads to higher EE \cite{33,55,77}. In\cite{22,44,1111,66}, the authors investigated optimizing achievable rate according to the precoding and power matrix and quantization noise with fronthaul capacity constraint. In \cite{66}, the approach of CFE (Compress-Forward Estimate) in uplink (UL) and improving data rates is investigated by using ECF (Estimate-Compress-Forward) instead can reach better performance in system, where RRH, estimates CSIT in UL, compress message and forward it to CUs studied.
\begin{figure}[t]
  \centering
    \includegraphics[width=8cm, height=8cm]{c1}
  \caption{Cooperative MIMO downlink C-RAN system.}
  \label{fig:c11}
\end{figure}

In this project, the downlink of a MIMO C-RAN system is considered where CU precodes the message, and then compresses the resulting signals. The compressed version of the signal is transmitted over the limited capacity fronthaul links to the RRHs. It is assumed that RRHs and UEs are clustered in a way that several clustered RRHs serve certain groups of UEs. In such a system the knowledge of Channel State Information at Transmitter (CSIT) is needed to compute the precoding matrices. Since CSIT is imperfectly obtained from the uplink pilot transmissions, we assume that the CSIT is obtained with a certain estimation error. At the CU, the well known Minimum Mean Square Error (MMSE) precoding MMSE is applied to reduce multi-user interference and enhance the performance of the system. For the proposed downlink system, we firstly derive the achievable rate subject to the fronthaul capacity constraint, then we optimize the power allocation to maximize the energy efficiency. The improvement over the equal power allocation is highlighted through numerical discussions. For the proposed down link system, we firstly derive the achievable rate subject to the fronthaul capacity constraint, then we optimize the power allocation to maximize the energy efficiency. The improvement over the equal power allocation is highlighted through numerical discussions.

The project is organized as follows.The C-RAN system is expressed in Section II. Section III, expressed  research exprerienced and classification. Criticizing and comparing the papers is presented in Section IV .System model, achievable rate analysis and problem formulations are presented in Section V. Optimization problems are considered in Section VI. Section VII presents numerical results and discussions, and finally the project is concluded in Section VII.
\section{C-RAN}
C-RAN architecture is a new architecture that may be used in next generation of mobile cellular network.
since now, there are two other mobile architecture that is expressed in below.
  \begin{figure}
  \centering
    \includegraphics[width=0.5\linewidth, height=6cm]{trad}
  \caption{Traditional architecture \cite{369}}
  \label{fig:trad}
\end{figure}
\subsection{Traditional architecture}
In this architecture, radio processing and base band processing are merging together in a base station.
The module of antenna is generally located in the proximity (few meters) of
the radio module as shown in Figure \eqref{fig:trad} as coaxial cables
employed to connect them exhibit high losses.
This architecture was
used for 1G and 2G mobile networks \cite{369}.
%%

\subsection{Base station with RRH}
In this architecture, the base station is contained of a radio unit and a
signal processing unit, as shown in Figure \eqref{fig:rrh} . The radio unit
is called a RRH or Remote Radio Unit (RRU). RRH provides
the interface to the fiber and performs digital processing,
digital to analog conversion, analog to digital conversion,
power amplification and filtering. The baseband signal
processing part is called a BBU. This architecture is used for 3G  and 4G networks.
\begin{figure}
  \centering
    \includegraphics[width=0.5\linewidth, height=6cm]{rrh}
  \caption{Base station with RRH architecture \cite{369}}
  \label{fig:rrh}
\end{figure}
The distance between a RRH and a BBU  can be about 40 km since there is a limitation for delay and processing it can not be longer.
Optical fiber and microwave connections
can be used.
Also One BBU can servemany RRHs \cite{369}.
\subsection{C-RAN Architecture}
In this architecture, the BBUs are centralized into one entity that is called a BBU/DU Pool, for optimizing BBU utilization between
heavily and lightly loaded base stations.
A BBU Pool is shared between cell sites and virtualized as
shown in Figure \eqref{fig:cr}. A BBU Pool is a virtualized cluster which
can consist of general purpose processors to perform baseband
(PHY/MAC) processing. 
\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\linewidth, height=6cm]{cr}
  \caption{C-RAN architecture \cite{369}}
  \label{fig:cr}
\end{figure}
The concept of C-RAN was first introduced by IBM 
under the name Wireless Network Cloud (WNC) and builds
on the concept of Distributed Wireless Communication System.
Here, a user communicates with densely placed distributed
antennas and the signal is processed by Distributed Processing \cite{369}.
\section{Research Experience and Classification}
In this part we compare studied papers in downlink.
Nowadays many researches includes MIMO system in C-RAN architecture.
These papers which I have studied (which are expressed in downlink) separated in 3 groups.
\subsection{First group}
In uplink, we have 2 part that separate time in 2 section. First portion of time is for sending pilot and second portion is for sending message that we do not discuss it. 
In downlink they have used precoding and compression in transmitter \cite{22,1111,44,66}. 
The equations is represented as 
\begin{equation}
\label{eq_pow1}
 \hat{\boldsymbol{x}} = \tilde{\boldsymbol{x}} + \boldsymbol{Q},
\end{equation}
where, $\boldsymbol{Q} = \left[ q_,\ldots,q\right]^T$,  is the quantization noise vector originating from compression made after precoding in the CU with element distribution of
$q\backsim \mathcal{N}(0,\sigma_{q^2}) $. Moreover,
$$\tilde{\boldsymbol{x}} = \textbf{W}\textbf{P}^{\frac{1}{2}} \boldsymbol{x},$$
\begin{figure}[H]
  \centering
    \includegraphics[width=\linewidth, height=6cm]{dl}
  \caption{First group of C-RAN architecture \cite{1111}}
  \label{fig:dl}
\end{figure}
denotes the precoded message before compression and $\boldsymbol{x}$ denotes the original message.
Fig \eqref{fig:dl} has shown this structure. In this group they have already maximized rate subject to a limitation on capacity of fronthaul link and power of transmitter.
The optimization formulation is denoted as 
\begin{equation}
\begin{aligned}
\max\limits_{\boldsymbol{W},\boldsymbol{\sigma}}   \quad &   \sum R(\boldsymbol{W},\boldsymbol{\sigma})\\
\text{subject to} \quad  & \bar{p}(\boldsymbol{W}, \boldsymbol{\sigma}) \leq P_{max}   \\
&C(\boldsymbol{W},\boldsymbol{\sigma})\leq C^{th}  \\
\end{aligned}
\end{equation}
where $\boldsymbol{\sigma}$ is variance of quantization noise and $\boldsymbol{W}$ is precoding matrix. In this problem, we want to maximize rate subject to limitation for capacity of fronthaul link and limitation in power transmitted by each RRH. In this case, we solve the problem by using iterative algorithm. The iterative algorithm utilize Largrangian method to solve the problem so
it may be a centralized algorithm not distributed method. In section V, we have used these kinds of algorithms. Also the complete solution and algorithm for this problem can be found in \cite{22}.
\subsection{Second group}
In this group, the downlink MIMO systems with a C-RAN architecture is expressed \cite{33,55}. The problem is approxiomateley similar to system model introduced in section IV.
Here, RRHs and users are clustered to $S$ cluster. 
In this group, the recieved signal vector for each user in $s^{th}$ cluster can be demonstrate as 
\begin{equation} \label{sg}
\textbf{y}_{u_s} = \sum_{t=1}^S \textbf{G}_{M_t,u_s}^H \textbf{W}_{M_t,u_t} \textbf{P}_{u_t}^{\frac{1}{2}} \textbf{x}_{ u_t} + \textbf{z}_{U_S}
\end{equation}
where $\textbf{x}_{ u_t} = [x_{ u_{(t,1)}},..., x_{ u_{(t,U_t)}}]^T \in C^{ U_t \times T} $ is the transmit symbol vector of RRH cluster $t$ that $T$ is symbol duration. 
 $\textbf{W}_{M_t, u_t} = [w_{ M_t,u_{(t,1)}},..., w_{M_t, u_{(t,U_t)}}]^T \in C^{ M_t \times U_t} $ is the precoding matrix exerted to RRHs  and users in $t^th$ cluster.
 Moreover, $\textbf{G}_{M_t,u_s}$ is the channel gain from RRH set $M_t$ to user set $U_s$. In addition, $z_{U_s}$ is the additive guassian noise.This problem is identical to our problem statement in section IV. The difference is that we do not use compression here. System model is also same as system model in section IV with constraint of
   $\boldsymbol{Q}_{\mathcal{R}_v} = \boldsymbol{0}$. The problem statement is a bit different from section V. The problem formulation is shown as below \cite{33}
   \begin{equation}\label{p12}
\begin{aligned}
\max\limits_{\boldsymbol{P}}   \quad &   \eta(\boldsymbol{P})\\
\text{subject to} \quad  & \bar{p}_{u_{(s,k)}} \leq P_{max} && \qquad \forall s, \forall i,   \\
&\mathfrak{R}_{u_{(s,k)}} \geq  \mathfrak{R}_{u_{(s,k)}}^{th} && \qquad \forall s, \forall k, \\
&p_{u_{(s,k)}}  \geq 0                                  &&\qquad \forall s, \forall k, \\
\end{aligned}			
\end{equation}  
Where $\eta$ is the energy efficiency that is explained in later sections in equation \eqref{eta}. \\
In this problem, by using Lagrangian method and also iterative algorithm the problem is solved. Also some simplified method will be used here that is denoted in later sections.

For extending this problem statements, joint clusterization and power allocation is considered \cite{55}. This problem used the system model as shown below but there is a slight difference between it and equation \eqref{sg}.
The recieved signal for $k^{th}$ user can be formulated as 
\begin{equation} \label{sg1}
\begin{aligned}
\textbf{y}_{k} =& \sum_{c=1}^C \sum_{m=1}^M  \phi_{c,m,k}h_{m,k}w_{m,k} \sqrt{p_k x_k} \\
&+ \sum_{c=1}^C \sum_{m=1}^M \sum_{r=1 ,r \neq k}^K  \phi_{c,m,r}h_{m,k}w_{m,r} \sqrt{p_r x_r} + n_k,
\end{aligned}	
\end{equation}
where,  $h_{m,k}$ is the channel gain between $k^{th}$ user and $m^{th}$ RRH. What's more, $w_{m,k}$ is the precoding between $k^{th}$ user and $m^{th}$ RRH. Additionally, $p_k$ is the 
transmit symbol power and $x_k$ is the transmit symbol of $k^{th}$ user. On top of them, $ \phi_{c,m,k} \in {0,1}$ and it is 1 if $k^{th}$ user and $m^{th}$ RRH are in the $c^{th}$ cluster, otherwise it is 0.  The problem statement  is maximizing energy efficiency with some constraints as below.
\begin{equation}
\begin{aligned}
\max\limits_{\boldsymbol{P},\boldsymbol{\phi}}   \quad &   \eta\\
\text{subject to} \quad  & \sum_{c=1}^C \sum_{k=1}^K  \phi_{c,m,k}|w_{m,k}|^2 p_k , \forall m,   \\
&\mathfrak{R}_{k} \geq  \mathfrak{R}_{k}^{th} && \qquad  \forall k, \\
&p_{k}  \geq 0                                  &&\qquad  \forall k, \\
& \phi_{c,m,k} \in \{0,1\} \\
 &\sum_{t=1, t \neq c}^C \sum_{m=1}^M  \phi_{c,m,k}\sum_{m=1}^M \phi_{t,m,k} \leq 0    &&\qquad    \forall m  , \forall c, \\
  &\sum_{t=1, t \neq c}^C \sum_{k=1}^K  \phi_{c,m,k}\sum_{k=1}^K \phi_{t,m,k} \leq 0      &&\qquad      \forall m  , \forall c,\\
  &\sum_{k=1}^K \sum_{m=1}^M  \phi_{c,m,k} \geq 1\\
\end{aligned}	
\end{equation}
Here, by exerting Lagrangian function or method and deriving, the problem will be solved. To maximize energy efficiency, we use Theorem \ref{t2} for simplicity. 
\subsection{Third group}
In this group, we have studied papers such as \cite{cell, 88}. In these papers, C-RAN architecture is not deployed. They are about MIMO systems. In this case, cell free system is employed. 
That large number of access point are serving small number of users. In uplink, the channel is separeted into 2 section. First for sending pilot and then for sending message. Here, the system model is completely distinct from the other system models. It is shown in below
\begin{equation}
y_k = \sqrt{\rho}\sum_{k'=1}^K g_{m_{k'} k} \sqrt{\alpha_{k'} q_{k'}} + n_k
\end{equation}   
where, $\sqrt{\alpha_{k'} q_{k'}}$ is the message signal. Additionally, $\sqrt{\rho}$ is the normalized SNR and $n_k$ is additive noise. Also $ g_{m_{k'} k}$ is channel gain from $m_{k'}$ access point to $k$ user. In this case, maximizing the minimum rate is considered. 
   \begin{equation}
\begin{aligned}
\max\limits_{\alpha_k}   \quad & min \quad  R_k\\
\text{subject to} \quad  & 0\leq \alpha_k \leq 1, && \qquad \forall k \in \{1,...,K\}  \\
\end{aligned}			
\end{equation}
 \section{Criticizing and Comparing Existing Papers}
 \subsection{Difference in System models}
 In this section we want to summerize the system models and methods in downlink and compare them. In the first group, compression and precoding is deployed in downlink. Firstly, message is encoded. after that it is precoded by CU (BBU Pool), then the precoded message is quantized and after that it is transmitted through fronthaul link with constrained capacity which is 
 depended on precoding and quantization noise
 to RRHs by fiber link. Finally it will be transmitted by RRHs through wireless link to users. Here, RRHs and users are not clustered.
  In second group the message is just encoded and precoded and then transmit through fronthaul link which has unconstrained capacity to RRHs which are clustered and finally it is transmitted  by RRHs through wireless link to users. Here quantization noise is not considered but RRHs and users are clustered.
  In the third group, we have expressed cell free massive MIMO. It is just new idea and we do not use it here a lot. 
  In the first group, RRHs and users are not clustered and in the second group, quantization noise is not exerted. In next section, we present new system model that has both quantization noise and clustering. 
  \subsection{Similarity and difference in problem statements}
  In all 3 groups, they have defined optimization problem which is about power allocation. In first group, maximizing sum rate is discussed. In second group maximizing energy efficiency  assumed also contains
   maximizing rate. In third group, maximizing the minimum rate is investigated. By maximizing minimum rate, all other rates are also enhanced. 
   All 3, try to maximize wireless channel rate in some ways subject to power contraints. In the first group we have also limitation on capacity. In the second group we have discussed about joint clustering and power allocation too. In first and second group, the problem is solved by both iteration algorithm and Lagrangian function together. Since it is discussed in downlink. the methods are approximately centralized.

   In next section, we have tried to merge all three groups together.
\section{System Model and Problem Formulation}

In this section, the system model, achievable rate and the main problem which is optimizing power allocation is expressed.

\subsection{System Model}

Downlink of a MIMO C-RAN system consists of $R$ RRHs serving $D$ single antenna user equipments (UE) is considered. It is assumed that RRHs and UEs are clustered in to $S$ cluster sets such that the $v$-th cluster set, has $R_v$ RRHs serving ${D}_v$ UEs. Furhtermore, it is assumed that the $j$-th RRH in the $v$-th cluster is connected to the CU via an optical fiber link with a limited capacity of $c_{r_{(v,j)}}$. So, we have
\begin{equation}
\begin{split}
\mathcal{R}_v= \{  r_{(v,i)} | 1 \leq i \leq {R}_v , i\in Z^+\}, \\
\mathcal{C}_{\mathcal{R}_v}= \{c_{r_{(v,j)}}| 1 \leq j \leq {R}_v , j\in Z^+\}, \\
\mathcal{D}_v= \{  d_{(v,k)} | 1 \leq k \leq {D}_v , k\in Z^+\},  \\
\end{split}
\end{equation}
where $\mathcal{R}_v$, $\mathcal{C}_{\mathcal{R}_v}$, and $\mathcal{D}_v$ respectively represent the RRH set, the capacity set and the UE set  for the $v$-th cluster set.
In CU we apply the approach of compressing after precoding and then forwarding. Each user receives both intra-cluster and inter-cluster interferences.
\subsection{Achievable Rate Analysis}
In this subsection, the achievable data rate of the considered system is investigated. 
\begin{theorem}\label{t1}
The achievable data rate for UE $d_{(s,k)}$ is
\begin{equation}\label{e1}
\mathfrak{R}_{d_{(s,k)}} = B \log_2(1+\gamma_{d_{(s,k)}}),
\end{equation}
where, $B$ is the channel bandwidth and $\gamma_{d_{(s,k)}}$ is the received SINR for the $k$-th UE in the $s$-th cluster set which is formulated as
\begin{equation}\label{5}
\gamma_{d_{(s,k)}}= \frac{p_{d_{(s,k)}}|\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,k)}}|^2}{I_{d_{(s,k)}}+BN_0}.
\end{equation}
In \eqref{5}, $I_{d_{(s,k)}}$, denotes the power of interfering signals, $BN_0$ represents the noise power, $\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}$ shows the channel gain vector between the $k$-th UE and the RRHs in the $s$-th cluster set, and $\boldsymbol{w}_{\mathcal{R}_{s},d_{(s,k)}}$ indicates the precoding vector used in $s$-th cluster set for the $k$-th UE.
$p_{d_{(s,k)}}$ is the transmit power of RRHs that transmit to the $k$-th UE in the $s$-th cluster set.
\end{theorem}

\begin{proof}
%%%%%%%%%%%%%
Let $\boldsymbol{y}_{\mathcal{D}_s}$ be a $D_s \times 1$ vector denoting the received signals by the set of UEs in the $s$-th cluster which is given by
\begin{equation} \label{1}
\boldsymbol{y}_{\mathcal{D}_s} = \sum_{v=1}^S \boldsymbol{H}^H_{\mathcal{R}_v,\mathcal{D}_s}\hat{\boldsymbol{x}}_{\mathcal{R}_v}+ \boldsymbol{z}_{\mathcal{D}_s},
\end{equation}
where $\hat{\boldsymbol{x}}_{ \mathcal{R}_v} = [\hat{x}_{ r_{(v,1)}},...,\hat{ x}_{ r_{(v,\mathcal{R}_v)}}]^T \in \mathbb{C}^{{R}_v } $ is the transmitted symbol vector for the $v$-th cluster set, $\boldsymbol{z_{\mathcal{D}_s}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{D}_s})$ shows the additive White Guassian noise with the power of $N_0$, and $\boldsymbol{H}_{\mathcal{R}_v,\mathcal{D}_s}=\left[\boldsymbol{h}_{\mathcal{R}_v,d_{(s,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_v,d_{(s,\mathcal{D}_s)}}\right]^T  \in \mathbb{C}^{{R}_v\times {D}_s}$ 
represents the channel matrix between RRH set $\mathcal{R}_v$ to UE set
$\mathcal{D}_s$. The channel vector from the RRH cluster $v$ to the $k$-th UE in the $s$-th cluster set $\boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}\in \mathbb{C}^{{R}_v}$ is modeled as follows
\begin{equation}
\boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_v,d_{(s,k)}} \boldsymbol{g}_{\mathcal{R}_v,d_{(s,k)}},
\end{equation}
% resizebox{0.3\hsize}{!}{$
where $\boldsymbol{g}_{\mathcal{R}_v,d_{(s,k)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{D}_s})$ represents the fast and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_v,d_{(s,k)}}=\text{diag}(a_{r_{(v,1),d_{(s,k)}}},\ldots,a_{r_{(v,\mathcal{R}_v),d_{(s,k)}}})$
indicates the large scale fading matrix \cite{88}. In addition, the transmitted signal has the following form
\begin{equation}
\label{eq_pow1}
 \hat{\boldsymbol{x}}_{\mathcal{R}_v} = \tilde{\boldsymbol{x}}_{\mathcal{R}_v} + \boldsymbol{Q}_{\mathcal{R}_v},
\end{equation}
where, $\boldsymbol{Q}_{\mathcal{R}_v} = \left[ q_{r_{(v,1)}},\ldots,q_{r_{(v,R_v)}}\right]^T$,  is the quantization noise vector originating from compression made after precoding in the CU with element distribution of
$q_{M_{(t,i)}}\backsim \mathcal{N}(0,\sigma_{q_{(t,i)}}^2) $. Moreover,
$$\tilde{\boldsymbol{x}}_{\mathcal{R}_v} = \textbf{W}_{\mathcal{R}_v,\mathcal{D}_v} \textbf{P}_{\mathcal{D}_v}^{\frac{1}{2}} \boldsymbol{x}_{ \mathcal{D}_v},$$
denotes the precoded message before compression.

As mentioned before, channel vector is assumed to be known with errors, the imperfection of channel estimation is modeled as follows
\begin{equation*}
\hat{\boldsymbol{h}}_{\mathcal{R}_v,d_{(s,k)}} = \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}} + \Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}},
\end{equation*}
$\Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}$ denotes the estimation error vector with a Guassian distribution of
$$\Delta \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}}\backsim \mathcal{N}(0,\boldsymbol{\phi}_{\mathcal{R}_v,d_{(s,k)}}^2),$$
where 
$$\boldsymbol{\phi}_{\mathcal{R}_v,d_{(s,k)}} = \text{diag}(\phi_{r_{(v,1)},d_{(s,k)}},\ldots,\phi_{r_{(v,\mathcal{R}_v)},d_{(s,k)}}).$$

By using MMSE precoding, the precoding matrix is expressed as follows
\begin{equation}
\boldsymbol{W}_{\mathcal{R}_s,\mathcal{D}_s} = \hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}(\hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}^H \hat{\boldsymbol{H}}_{\mathcal{R}_s,\mathcal{D}_s}+ \alpha \boldsymbol{I}_{{D}_s})^{-1},
\end{equation} 
where, $\alpha$ is the regularization factor.

Therefore, the previously mentioned $I_{d_{(s,k)}}$, denoting the interference power at the desired UE in (3), can be written as follows
\begin{equation}\label{6}
\begin{split}
I_{d_{(s,k)}} &=  \underbrace{\sum_{\substack{l=1 \\ l\neq k}}^{{D}_s} |\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{s},d_{(s,l)}}|^2  p_{d_{(s,l)}}}_{\text{(intra-cluster interference)}}\\
&+\underbrace{\sum_{\substack{v=1 \\ v\neq s}}^{S} \sum_{l=1}^{{D}_s} |\boldsymbol{h}_{\mathcal{R}_v, d_{(s,k)}}^H \boldsymbol{w}_{\mathcal{R}_{v},d_{(v,l)}}|^2 p_{d_{(v,l)}}}_{\text{(inter-cluster interference)}}\\
& +\underbrace{ \sum_{v=1}^{S} \sum_{i=1}^{{R}_v} {\sigma_q}_{r_{(v,i)}}^2 \sum_{l=1}^{{D}_s} |\boldsymbol{h}_{r_{(v,i)}, d_{(v,l)}}^H|^2 }_{\text{(quantization noise interference)}}.
\end{split}
\end{equation}

 \end{proof}
\section{Optimizing Power Allocation}
Let the power of transmitted signal by the $i$-th RRH in the $s$-th cluster set by
\begin{equation} \label{eq_pow2}
\bar{p}_{r_{(s,i)}} = \mathit{E}[|| \hat{x}_{\mathcal{D}_v} ||^2],
\end{equation}
By plugging (\ref{eq_pow1}) into (\ref{eq_pow2}), the power of transmitted signal is rewritten as
\begin{equation}
\bar{p}_{r_{(s,i)}} = \boldsymbol{w}_{r_{(s,i)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{D}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{D}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,i)},\mathcal{D}_{s}}^H + \sigma_{q_{(s,i)}}^2.
\end{equation}
As a result the achievable rate on the fronthual link between the CU and the $i$-th RRH in $t$-th cluster must be larger than
\begin{equation}
C_{R_{(t,i)}} = \log{(1+\frac{w_{r_{(s,i)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{D}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{D}_v}^{H \frac{1}{2}}   w_{r_{(s,i)},\mathcal{D}_{s}}^H }{ \sigma_{q_{(s,i)}}^2})},
\end{equation}
in order to be able to transmit the aforementioned signals via fronthual links.
\subsection{Problem Statement}
The ratio of the sum-rate of system to the total power transmitted by RRHs indicates one of the most pormising indicators for selecting new technologies, named as the energy efficiency of system and denoted by $\eta$, which can be formulated as
\begin{equation}\label{eta}
\eta(\boldsymbol{P}) := \frac{\sum\limits_{s=1}^{S} \sum\limits_{k=1}^{{D}_s}\mathfrak{R}_{d_{(s,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{R_{total}(\boldsymbol{P})}{P_{RRH}(\boldsymbol{P})},
\end{equation}
in which $ \boldsymbol{P} = \{ \boldsymbol{P}_{\mathcal{D}_s}|  1 \leq s \leq S, s \in \mathbb{Z}^{+} \}$ is a power allocation matrix.
In this project, maximization of energy efficiency is investigated with the presence of following constraints, 
\begin{equation}\label{p1}
\begin{aligned}
\max\limits_{\boldsymbol{P}}   \quad &   \eta(\boldsymbol{P})\\
\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \qquad \forall s, \forall i,   \\
&\mathfrak{R}_{d_{(s,k)}} \geq  \mathfrak{R}_{d_{(s,k)}}^{th} && \qquad \forall s, \forall k, \\
&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{th}  &&\qquad \forall s, \forall i, \\
&p_{d_{(s,k)}}  \geq 0                                  &&\qquad \forall s, \forall k, \\
\end{aligned}			
\end{equation}
Since the problem is not a convex problem, an iterative algorithm is used to derive the optimal values for the maximization problem. 
\subsection{Proposed Method}
In this subsection, instead of maximizing \eqref{eta}, we solve an equivalent problem by using an iterative algorithm. 
\begin{theorem}\label{t2}
Maximum value of $\eta^*$ is obtained if and only if 
\begin{equation}\label{q2}
\begin{split}
&\max \limits_{\boldsymbol{P}} (R_{total}(\boldsymbol{P}) - \eta^* P_{RRH}(\boldsymbol{P}))=\\
& R_{total}(\boldsymbol{P}^*) - \eta^* P_{RRH}(\boldsymbol{P}^*) =0,
\end{split}
\end{equation}
where $\{\boldsymbol{P}\}$ is a feasible solution of problem \eqref{p1}.
\end{theorem}
\begin{proof}
The Theorem is proved using the similar steps as [9, Theorem 1].
\end{proof}

To solve the optimization problem (14),, we use Lagrangian function  by an iterative algorithm proposed in \cite{11}.
For simplicity, the upper bound for the interference given in (9), is given by
\begin{equation}
\begin{split}
\tilde{I}_{d_{(s,k)}} &= \sum_{v=1}^{S} P_{max}|| \boldsymbol{h}_{\mathcal{R}_v,d_{(s,k)}} \boldsymbol{w}_{\mathcal{R}_v,d_{(s,k)}}||^2 ,\\
& +  \sum_{v=1}^{S} \sum_{i=1}^{{R}_v} {\sigma_q}_{r_{(v,i)}}^2 \sum_{l=1}^{{D}_s} |\boldsymbol{h}_{r_{(v,i)}, d_{(v,l)}}^H|^2.
\end{split}
\end{equation}
Therefore, to find the optimal power allocation, the following lower bound is used instead of (2), as
\begin{equation}\label{e11}
\mathfrak{\tilde{R}}_{d_{(s,k)}} = B \log_2(1+\tilde{\gamma}_{d_{(s,k)}}),
\end{equation}
where $\tilde{\gamma}_{d_{(s,k)}}$ is
\begin{equation}\label{15}
\tilde{\gamma}_{d_{(s,k)}} =  \frac{p_{d_{(s,k)}}|\boldsymbol{h}_{\mathcal{R}_s, d_{(s,k)}}^H \boldsymbol{w}_{R_{s},d_{(s,k)}}|^2}{\tilde{I}_{d_{(s,k)}}+BN_0};
\end{equation}

As mentioned before an iterative algorithm is used for optimization which is based on the following Lagrangian multiplier function
\begin{equation}
\begin{split}
\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\mu}, \boldsymbol{ \kappa}) & = \sum\limits_{s=1}^{S} \sum\limits_{k=1}^{\mathcal{D}_s}\mathfrak{\tilde{R}}_{d_{(s,k)}} 
- \eta \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
&+\sum\limits_{s=1}^{S} \sum\limits_{k=1}^{\mathcal{D}_s} \lambda_{d_{(s,k)}} (\mathfrak{\tilde{R}}_{d_{(s,k)}}-\mathfrak{R}_{d_{(s,k)}}^{th})\\
&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{\mathcal{R}_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{\mathcal{R}_s} \kappa_{r_{(s,i)}} (C_{r_{(s,i)}}-C_{r_{(s,i)}}^{th}).\\
\end{split}
\end{equation}
where $\boldsymbol{\lambda}, \boldsymbol{\mu}, \boldsymbol{\kappa} \geq 0$ are Lagrangian multipliers vector.\\
By using this equation, the optimal power allocation is derived as below,
\begin{equation}
p_{r_{(s,i)}}^* =[\frac{ B(1+\gamma_{d_{(s,k)}} )}{\ln2 \times (\iota_{r_{(s,i)}}+ \chi_{r_{(s,i)}})} -\frac{\tilde{I}_{d_{(s,k)}} + BN_0}{\nu_{d_{(s,k)}} }]^+;
\end{equation} 
where $$\nu_{d_{(s,k)}} =|h_{\mathcal{R}_s, d_{(s,k)}}^H w_{R_{s},d_{(s,k)}}|^2,$$
 $$\iota_{r_{(s,i)}}=\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{\mathcal{R}_s} (\mu_{r_{(s,i)}}+1)(w_{r_{(s,i)},d_{(v,l)}} w_{r_{(s,i)},d_{(v,l)}}^*),$$
 $$\chi_{r_{(s,i)}} \approx  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{\mathcal{R}_s} \frac{\kappa_{r_{(s,i)}}}{\ln 2}\frac{(w_{r_{(s,i)},d_{(v,l)}} w_{r_{(s,i)},d_{(v,l)}}^*)}{ \sum\limits_{k=1}^{\mathcal{D}_s}P_{max}+\sigma_{q_{r_{(s,i)}}}^2}.$$
  Finally, to find the optimal power allocation, the Algorithm I is applied. 
\begin{algorithm}
\caption{Energy-Efficient Power Allocation}\label{alg}
\begin{algorithmic}[1]
\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
\State Set the iteration index $i = 1$ and begin the iteration (Outer
Loop).
\For {$ 1\leq i \leq  Imax$}
\State Solve the resource allocation problem with $\eta^{(i)}$ (Inner Loop);
\State Obtain $P^{(i)}, R_{total}^{(i)}, P_{RRH}^{(i)}$
\If {$ R_{total}(\boldsymbol{P}^{(i)}) - \eta^{(i)} P_{RRH}(\boldsymbol{P}^{(i)}) < \epsilon_{\eta} $} 
\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
\State break;
\Else
\State Set $\eta^{(i)}= \frac{R_{total}(\boldsymbol{P}^{(i))}}{P_{RRH}(\boldsymbol{P}^{(i))}}$ and $i= i+1$;
\EndIf 
\State \textbf{end if}
\EndFor 
\State \textbf{end for}
\end{algorithmic}
\end{algorithm}
\section{Numerical Results and Discussions}
In this section, numerical results of the proposed algorithm are discussed for the MIMO C-RAN system whose parameters are described in Table \ref{tab:title}.

 \begin{table}[H]
 \caption {Simulation Parameter} \label{tab:title} 
 \begin{center}
  \begin{tabular}{||c c ||} 
  \hline
  Parameter & Value \\ [0.5ex] 
  \hline\hline
  Number of cluster S & 4 \\ 
  \hline
  Noise power & -174dBm/Hz\\
  \hline
  Bandwidth & 10MHz \\
  \hline
 Maxmimun transmit Power & 23dBm \\
  \hline
  Minimum data rate &  1Mbits/sec \\ [1ex] 
  \hline
 \end{tabular}
 \end{center}
 \end{table}

In Fig. \ref{fig:nem1},
energy efficiency of MIMO C-RAN system with the proposed iterative algorithm and equal power allocations are shown as a function of numbers of RRHs in each cluster.
As illustrated, optimal power allocation policy outperforms equal power allocation. In addition, it is shown that the increase in the number of RRHs enhances the performance of system.

  \begin{figure}
  \centering
    \includegraphics[width=0.5\linewidth, height=6cm]{n1232}
  \caption{Energy efficiency vs. number of RRH for optimal and equal power allocation. $U_s=8$, and the other parameters are given in Table I.}
  \label{fig:nem1}
\end{figure}

In Fig. \ref{fig:nem2}, EE of the proposed iterative algorithm and equal power allocation are depicted for different number of UEs in each cluster. Since by increasing the number of UEs in each cluster, interference is also increased, the system performance is decreased according to the increase in number of UE. It is shown that although the energy efficiency of the considered MIMO C-RAN systems degrades as the number of UEs increases, but still EE of the system using the proposed algorithm surpasses the equal power allocation.

  \begin{figure}
  \centering
    \includegraphics[width=0.5\linewidth, height=6cm]{ue}
  \caption{Energy efficiency vs number of UE for Optimized and Equal Power Allocation, plotted for parameters given in Table I with $M_s=30$.}
  \label{fig:nem2}
\end{figure}
%\bibliographystyle{ieeetr}
%\bibliography{bib1}
%\setLTRbibitems
\begin{figure}
  \centering
    \includegraphics[width=0.5\linewidth, height=6cm]{c}
  \caption{Energy efficiency vs ${C}^{th} $ constraint with $S =3$, $Ms= 20$, $U =3$. }
  \label{fig:nem3}
\end{figure}

In Fig. \ref{fig:nem3}, EE is depicted as a function of the maximum fronthaul link capacity constraint. It could be understood from the figure that, as the capacity exceeds 12 (bits/s/Hz), the increase in the fronthaul capacity does not affect energy efficiency significantly, since the achievable rate is limited by the wireless channel between RRHs and UEs.
\section{Conclusion}
The project has focused on addressing the optimal power allocation in downlink of a MIMO C-RAN system with limited fronthaul capacity.
The system model is expressed and the equivalent problem of maximizing the EE is solved by using an iterative algorithm and Lagrangian function.
Simulation results demonstrate that the proposed algorithm outperforms the equal power allocation. It is also shown that by increasing the number of RRHs in each cluster, the performance of the system would be enhanced, and increasing the number of UEs in each cluster reduces the system performance.

\newpage
\bibliographystyle{ieeetr}
\bibliography{m}
 %%
\
\end{document}

### 2022-01-15 new/Joint Power Allocation and Network Slicing in an End-to-End ORAN System -.1cm/pr.tex
first commit for new git

--- 2020-04-19 Latex/tex/pr.tex
@@
 CU and DU are implemented as virtual network functions (VNFs) running on a cloud environment.
-Interfaces between RU, CU, and DU are open standard interfaces.
+Interface between RU, CU, and DU are open standard interfaces.
 Network slicing as a new concept in 5G systems is used to share the network resources between various services while the operation of one service does not affect another service.
@@
 
-ORAN virtualizes the elements of the radio access networks, separates them and defines appropriate open interfaces for connection of these elements.
+ORAN virtualizes the elements of the radio access networks, separate them and define appropriate open interfaces for connection of these elements.
 Moreover, ORAN uses machine learning techniques to develop smarter RAN layers in its architecture.
@@
 To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and referred to as network functions virtualization (NFV).
-Virtual network functions (VNFs) are functional blocks of the system.
+Virtual network function (VNF) are functional blocks of the system.
 5G networks are expected to host several services with different requirements simultaneously.
@@
 A network slice is a logical end-to-end network which provides service with specific requirements.
-Multiple network slices run on the same network infrastructure which are managed and operated independently \cite{lee2018dynamic}.
-Slicing can be defined for the RAN, for the core network or both of them \cite{ns1}.
+Multiple network slices run on the same network infrastructure which are managed and operate independently \cite{lee2018dynamic}.
+Slicing can be defined for the RAN, for the core network or both of these them \cite{ns1}.
 
-Based on their type of service request, user equipments (UEs) are classified into various services, where UEs in the same service have similar service requests.
+Based on their type of request, UEs are classified into various services, where UEs in the same service have similar service requests.
 In addition, each service is mapped to one or more slices based on the resources of the slices.
-Each VNF of the ORAN is mapped to one or more virtual machines (VMs) in the data center.
+Each VNF of the ORAN is mapped to one or some virtual machines (VMs) in the data center.
 For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.
@@
 In \cite{oranT},  the evolution of RAN in the  5G network is described.
-The architecture of C-RAN and xRAN is expressed and development of the ORAN from C-RAN and xRAN is explained.
+The architecture of C-RAN and X-RAN is expressed and development of the ORAN from C-RAN and X-RAN is explained.
 Also requirements of the network in terms of capacity and latency is taken into account.
 In \cite{oran12},  the ORAN architecture is studied.
-The eight working groups are discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software.
+The eight work groups is discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software.
 To the best of our knowledge, there is not work in the literature to model ORAN systems.
@@
 UEs are divided to different services according to their requirements.
-RAN resources are partitioned into slices to provide requirements of services.
+RAN resources are decoupled to slices to provide requirements of services.
 Optimal power allocation and joint mapping of slices to services are applied.
-In addition, mapping slices to physical resources is taken into account.
+In addition, mapping slices to physical resources is taken to account.
 The contributions of the paper are as follows:
 \begin{itemize}
-\item Joint network slicing and resource allocation is considered in an ORAN system.
+\item In this paper, joint network slicing and resource allocation is considered in an ORAN system.
 \item We formulate the problem of assigning UEs to services, services to slices, and physical wireless and data center resources to the slices as an optimization problem.
+\item The problem is decomposed into two independent sub-problems.
 \item Novel heuristic algorithms are applied for these sub-problems to efficiently obtain the solution.
@@
 Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
-single-antenna UEs that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
+single-antenna user equipments (UEs) that require certain service.
+Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
 Slices can have shared resources.
-All RUs in a slice, that are mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}.
+All RUs in a slice, that is mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}.
 Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.
@@
 The VNFs in the DU and CU layers have the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
-Also, RUs and PRBs can serve more than one slice.
+Also, RUs and PRBs can serve more than one slices.
 \subsection{The Achievable Rate}
@@
 where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.
-Mean delay of each slice is obtained as below.
+Mean delay of each slice is
 \begin{equation}
@@
 where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RUs in all slices.
-Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the total rates of all UEs applied for all types of services.
+Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services.
 Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
@@
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &  \eta(\boldsymbol{P},\boldsymbol{A})+ \varphi \frac{1}{\psi_{tot}(\boldsymbol{Y})} \\
+\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\psi_{tot}(\boldsymbol{Y})} \\
 \text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} \quad \forall s, \forall i,
@@
 the physical DC is mapped to a VNFs of a slice or not.
-Also, $\varphi$ is weighted variable to value between first and second term of objective function.
 \eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively.
@@
 \State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RUs)
-\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} are not applied}
+\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} is not applied}
 \State Set $a_{i,j} = 0$;
@@
 \begin{algorithm}
-\caption{Placement of Physical resources into Virtual resources}\label{alg3}
+\caption{Plecement of Physical resources into Virtual resources}\label{alg3}
 \begin{algorithmic}[1]
@@
 In Fig.
-\ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with different mean number of UEs in each service.
-The parameters of simulations are listed in Table \ref{table:1a}.
+\ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with different mean number of UEs in each service The parameters of simulations are listed in Table \ref{table:1a}.
 The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$.

### 2022-01-15 Code_journal1/VersionLastJournal/cell/RUUEFirst.m

@@ -1,0 +1,6 @@
+
+RU_UE = zeros(N_RU,N_UE);
+for u1 =  1:N_UE
+    RU_first = randi(N_RU);
+    RU_UE(RU_first,u1) = 1;
+end

### 2022-01-15 Code_journal1/VersionLastJournal/cell/Rate.m

@@ -1,0 +1,22 @@
+
+
+rate_UE = cvx(zeros(1,N_UE));
+
+for i = 1:N_UE
+    %for j = 1:N_RU
+        for z = 1:N_PRB
+            if PRB_UE(z,i)==1
+                rate_UE(i) = rate_UE(i) + BW* log(1 + (Popt(i)*abs((ChannelGain1(:,i))'*beamForming1(:,i))^2)/(Intf(i)+BW*N0));%*PRB_UE(z,i);
+            end
+        end
+    %end
+end
+
+R_s = cvx(zeros(1,S));
+t = 0;
+for s = 1:S
+    for j = 1:UE_S(s)
+        t = t+1;
+        R_s(s) = R_s(s) + rate_UE(t);
+    end
+end

### 2022-01-15 Code_journal1/VersionLastJournal/delay/main_final.m

@@ -1,0 +1,128 @@
+clear all
+clc
+run var_const
+count_min1 = 10e6;
+count_step1 = 20e6;
+count_max1 = 100e6;
+numvar = length(count_min1:count_step1:count_max1);
+iter_max = 1;
+sumRate = zeros(numvar,iter_max);
+sumRate1= zeros(numvar,iter_max);
+DelayTot= zeros(numvar,iter_max,S);
+Delay1_last= zeros(numvar,iter_max,S);
+DelayTot1= zeros(numvar,iter_max,S);
+Delay1_last_base= zeros(numvar,iter_max,S);
+VNFNumber = zeros(numvar,iter_max,S);
+VNFNumber1 = zeros(numvar,iter_max,S);
+RU_iter_max = N_RU+5;
+%% initializing
+number_check = 0;
+for i_count = count_min1:count_step1:count_max1
+    number_check  = number_check +  1;
+    for iter = 1:iter_max  
+        RU_iter = 1;
+        run parameter_UE_change
+        run PRB_Alloc
+        %%
+        while  RU_iter < RU_iter_max
+            
+            if RU_iter == 1
+              run RUAssociateDist  
+            end
+            run setChGain
+            alpha_m = lambda_m.*(UE_S);
+            run PRB_Pow_Alloc1
+            run findM
+            run Rate_final
+            run RUUESet
+            sumRate(number_check,iter) = abs(sum(rate_UE_1));
+            DelayTot(number_check,iter,:) = Delay_tot(:);
+            Delay1_last(number_check,iter,:) = Delay_Slice1(:);
+            VNFNumber(number_check,iter,:) =VNF_NUM(:);
+            if sumRate(number_check,iter) > 0 && RU_iter >2 
+                RU_iter = RU_iter_max + 10;
+                
+            end
+            iter
+            i_count
+            RU_iter
+            VNF_NUM
+            RU_iter = RU_iter + 1;
+        end
+        %% BaseLine Scheme
+            run PRB_rand
+            run RUAssociateDist
+            run setChGain
+            alpha_m = lambda_m.*(UE_S);
+            run PRB_Pow_Alloc2
+            run findM
[…]

### 2022-01-15 Code_journal1/VersionLastJournal/delay/parameter_UE_change.m

@@ -1,0 +1,25 @@
+UE_S = 30*ones(1,S);%randi(N_UE_max,1,S);
+N_UE = sum(UE_S);
+%RU_UE = zeros(N_RU,N_UE,N_Antenna);
+%Popt = ones(1,N_UE)*Pmax;
+Rmin_UE = zeros(1,N_UE);
+t = 0;
+for i = 1:S
+    for j = 1:UE_S(i)
+        t = t+1;
+        Rmin_UE(t) = Rmin(i);
+    end
+end
+ChannelGain = zeros(N_RU,N_UE,N_Antenna);
+beamForming = zeros(N_RU ,N_UE,N_Antenna);
+Popt = ones(1,N_UE)*Pmax;
+PRB_UE = zeros(N_PRB,N_UE);
+
+run Channel_Gain
+run Precoding
+%RU_UE = ones(N_RU,N_UE);
+count_max = 1;
+%Pmax = i_count;
+%lambda_m = ones(1,S)*i_count;
+%delay_max = ones(1,S)*i_count;
+Fact_S = 1;

### 2022-01-15 Code_journal1/VersionLastJournal/oneSlice/main_gradient_final.m

@@ -1,0 +1,65 @@
+clear all
+clc
+run var_const
+count_min1 = 2;
+count_step1 = 2;
+count_max1 = 2;
+numvar = length(count_min1:count_step1:count_max1);
+iter_max = 1;
+sumRate = zeros(numvar,iter_max);
+sumRate1= zeros(numvar,iter_max);
+RU_iter_max = 2;%N_RU + 5;
+%% initializing
+number_check = 0;
+for i_count = count_min1:count_step1:count_max1
+    number_check  = number_check +  1;
+    for iter = 1:iter_max  
+        RU_iter = 1;
+        run parameter_UE_change
+        run PRB_Alloc
+         while  RU_iter < RU_iter_max
+
+        if RU_iter == 1
+          run RUAssociateDist  
+        end
+        %%
+            run setChGain
+            alpha_m = lambda_m.*(UE_S);
+            run delay_const
+            run PRB_P
+            %run PRB_Pow_Alloc1
+            run findM
+            run Rate_final
+            run RUUESet
+            sumRate1(number_check,iter) = max(abs(sum(rate_UE_1)),sumRate1(number_check,iter));       
+            i_count
+            RU_iter
+            VNF_NUM
+            if sumRate(number_check,iter) > 0 && RU_iter >3 
+                %RU_iter = RU_iter_max + 10;
+
+            end
+            
+            RU_iter = RU_iter + 1;
+         end
+    end
+end
+UE_num = count_min1:count_step1:count_max1;
+
+
+sumRB =  zeros(1,numvar);
+sumRB1 =  zeros(1,numvar);
+num = zeros(1,numvar);
+for i =1:numvar
+    for j =1:iter_max
+        if isnan(sumRate1(i,j)) == 0 
+            sumRB(i) = sumRB(i) + sumRate1(i,j);
+            num(i)=  num(i) + 1;
+        end
+    end
+    sumRB1(i) = sumRB(i)/num(i);
+end
+
+%plot( UE_num , sumRB1/1e6,'-+')
+
+%plot(UE_num ,mean(sumRate,2))

### 2022-01-15 Code_journal1/VersionLastJournal/oneSlice1 - Copy/main.m

@@ -1,0 +1,37 @@
+clear all
+clc
+%% initializing
+run Var
+%% UE Admission
+run UE_admission
+%% RU associated in Comp Way, Remove UE that are not admitted
+N_UE = sum(UE_S_Admit);
+Rmin_UE = zeros(1,N_UE);
+t = 0;
+alpha_m = lambda_m.*(UE_S_Admit);
+for i = 1:S
+    for j = 1:UE_S_Admit(i)
+        t = t+1;
+        Rmin_UE(t) = Rmin(i);
+    end
+end
+ChannelGain = zeros(N_RU,N_UE);
+beamForming = zeros(N_RU ,N_UE);
+Popt = ones(1,N_UE)*Pmax;
+PRB_UE = zeros(N_PRB,N_UE);
+for i =1:N_UE
+    if mod(i,N_PRB)==0
+       PRB_UE(N_PRB,i)= 1;
+    else
+        PRB_UE(mod(i,N_PRB),i) =1 ;
+    end
+
+end
+run Channel_Gain
+run Precoding
+run RU_association
+count_max = 1;
+run PRB_Pow_Alloc1
+run findM
+VNF_NUM
+

### 2022-01-15 Code_journal1/VersionLastJournal/oneSlice1 - Copy/update_var.m

@@ -1,0 +1,15 @@
+alpha_step = Pmax/sqrt(count)/1;
+
+for i = 1:N_UE
+    beta_step = Pmax/1/sqrt(count);
+    lambda_step = Rmin_UE(i)/sqrt(count)/1000;
+    lambda(i)= max(0,lambda(i) - lambda_step* (rate_UE(i) - Rmin_UE(i)));
+    alpha(i) = max(0, alpha(i) - alpha_step* (Popt(i)- 0));
+    
+end
+for j = 1:N_RU
+   %tr_step = Capacity_RU(j)/sqrt(count)/10000000;
+   Sum_Rate = sum(rate_UE.*RU_UE(j,:));
+   %tr(j) = max(0, tr(j) - tr_step*(Capacity_RU(j)-Sum_Rate));
+   beta(j) = max(0, beta(j) -beta_step* (Pmax - Pow_RU(j))); 
+end

### 2022-01-15 Code_journal1/VersionLastJournal/oneSlice1 - Copy/var_const.m

@@ -1,0 +1,42 @@
+%% Initial Variable
+R = 500;
+S = 1;
+BW = 180*1e3; %10*1e6;  
+n0 = -174; %-174 dbm
+N0 = db2pow(n0)/1000;
+Pc1 = 10; %watt
+Pc  = db2pow(Pc1)/1000;
+Pt = 33;
+Pmax = db2pow(Pt)/1000;
+Rmin1 =  BW*5;%[60000 ,60000 ,6000];%.1*BW*randi([1,5],1,S); %.1*BW*ones(1,S)
+[Rmin, I] = sort(Rmin1,'descend');
+Rate_mid_max = BW*100;% [600000,420000,50000];%0.5*BW*randi([1,10],1,S);
+var_q = 1e-6;
+alpha_s = .1*BW;
+%delay_max = 3e-5*randi([1,20],1,S);
+delay_max = 4e-3;% [1, 1, 1];
+%mu = 1e9.*[1.5, 3, 5];%Rmin .* randi([500,520],1,S)/1000;
+mu =8e6;%[7734000, 8250000, 1808400]/10;%Rmin .* randi([1200,1520],1,S)/10;
+%alpha_m  =10e8.*[0.1, 0.5, 1]; %Rmin .* randi([485,499],1,S)/1000;
+%lambda_m = 1e6*ones(1,S);
+lambda_m =3e6 ;%[2994000, 2922000, 598800]/10;%Rmin .* randi([485,499],1,S)/10;
+mu = ones(1,S)*5e5;
+lambda_m = ones(1,S)*2e5;
+%% 
+T_max = 50e-5*randi([1,10],1,S); % sec
+Delay_Slice = zeros(1,S);
+VNF_NUM =  zeros(1,S);
+N_UE_max = 10;
+N_RU = 6;
+counter_max = 30;
+M_max = 25; %max number of vnf
+%%
+C_tot_RU = sum(Rate_mid_max);
+Capacity_RU = [160500, 288900, 502900, 449400];%C_tot_RU * randi([10,50],1,N_RU)/100;
+N_Antenna = 4;
+%P_RU = zeros(1,N_RU);
+%% changable variable
+N_PRB = 25;
+
+%RU_PRB = randi([0 1],N_RU,N_PRB);
+%PRB_UE = randi([0,1],N_PRB,N_UE);%zeros(N_PRB, N_UE);

### 2022-01-15 Code_journal1/VersionLastJournal/oneSlice1/PRB_Pow_Alloc1.m

@@ -1,0 +1,39 @@
+for  count_power=1:1 
+    cvx_begin
+        variables Popt(1,N_UE); 
+        run Interference
+        run Rate
+        run P_RU
+        maximize sum(rate_UE)
+        subject to
+        %Power_RU(N_UE,Popt,beamForming,var_q,N_RU,1:N_RU)<2.^(Capacity_RU(1)/1e4) * var_q*100 ;
+        %Power_RU(N_UE,Popt,beamForming,var_q,N_RU,1:N_RU)<Pmax;
+        Pow_RU <= Pmax;
+        Popt(:) >= 0; 
+        Popt(:) <= Pmax/3;
+        
+        %Find_Rate(BW,Popt,ChannelGain,beamForming,PRB_UE,N_PRB,N_UE,N0,Intf,1:N_UE)>= Rmin_UE(1);
+        rate_UE(:) >= Rmin_UE(:);%Rmin_UE(:)/1;%.*admission_UE1(:); 
+        rate_UE(:) >= lambda_m + 1/delay_max;
+        w1(1,:) = alpha_m(:).* delay_max(:);
+        w2(1,:) = alpha_m(:).*lambda_m(:) .* delay_max(:) + alpha_m(:);
+        w3(1,:) = mu(:).* delay_max(:)-3;
+        w4(1,:) = mu(:).* delay_max(:).*lambda_m(:)+mu(:) - 3*lambda_m(:);
+        %w1(:).*R_s(:)-w2(:)- M_max*(w3(:).*R_s(:)-w4(:)) <= 0;
+        %R_s(:) <= (w2(:) - M_max*w4(:))./((w1(:) - M_max*w3(:)))
+        t = 0;
+        a = zeros(1,S);
+        M_max = 25;
+        for s = 1:S
+            for j = 1:UE_S(s)
+                t = t+1;
+                a(s) = (w2(s) - M_max*w4(s))./((w1(s) - M_max*w3(s)));
+                %Popt(t) <= (2^(a(s)/BW)-1)*(Intf(t)*0+BW*N0)/(abs((ChannelGain(:,t))'*beamForming(:,t))^2)
+                %rate_UE(t) >= max(a(s),0)
+            end
+        end
+        
+        %alpha_m(:).*(delay_max(:) - xx(:))-(mu(:).*(delay_max(:) - xx(:))-1)*10 <= 0
+    cvx_end
+
+end

### 2022-01-15 Code_journal1/VersionLastJournal/oneSlice1/update_var.m

@@ -1,0 +1,16 @@
+alpha_step = Pmax/sqrt(count)/1;
+gamma_step = Pmax/sqrt(count)/10;
+for i = 1:N_UE
+    beta_step = Pmax/1/sqrt(count);
+    lambda_step = Rmin_UE(i)/sqrt(count)/1000;
+    lambda(i)= max(0,lambda(i) - lambda_step* (rate_UE(i) - Rmin_UE(i)));
+    alpha(i) = max(0, alpha(i) - alpha_step* (Popt(i)- 0));
+    gamma(i) = max(0, gamma(i) - gamma_step* (Pmax/3 - Popt(i)));
+    
+end
+for j = 1:N_RU
+   %tr_step = Capacity_RU(j)/sqrt(count)/10000000;
+   Sum_Rate = sum(rate_UE.*RU_UE(j,:));
+   %tr(j) = max(0, tr(j) - tr_step*(Capacity_RU(j)-Sum_Rate));
+   beta(j) = max(0, beta(j) -beta_step* (Pmax - Pow_RU(j))); 
+end

### 2022-01-15 Code_journal1/VersionLastJournal/oneSlice2/Rate_PRB.m

@@ -1,0 +1,22 @@
+Intf_PRB = zeros(N_PRB,N_UE);
+for z = 1:N_PRB
+    for i = 1:N_UE
+            for t = 1 : N_UE
+                if i~=t  
+                    %Intf(i) = Intf(i) + Pmax/100*abs((ChannelGain(:,i))'*beamForming(:,i))^2 * PRB_UE(z,i) * PRB_UE(z,t);
+                    Intf_PRB(z,i) = Intf_PRB(z,i) + Pmax/10*abs((ChannelGain1(:,i))'*beamForming1(:,i))^2 * PRB_UE(z,t);% * PRB_UE(z,i);
+                end
+            end
+    end
+end
+
+
+%Intf_PRB = zeros(N_PRB,N_UE);
+rate_PRB_UE = zeros(N_PRB,N_UE);
+for z = 1:N_PRB
+    for i = 1:N_UE
+        for j = 1:N_RU 
+            rate_PRB_UE(z,i) = rate_PRB_UE(z,i) + BW* log(1 + (Popt(i)*abs((ChannelGain(j,i)).* RU_UE(j,i)))/(Intf_PRB(z,i)+BW*N0));%*PRB_UE(z,i);
+        end
+    end
+end

### 2022-01-15 Code_journal1/VersionLastJournal/oneSlice2/parameter_UE_change.m

@@ -1,0 +1,21 @@
+UE_S = i_count*ones(1,S);%randi(N_UE_max,1,S);
+N_UE = sum(UE_S);
+%RU_UE = zeros(N_RU,N_UE,N_Antenna);
+%Popt = ones(1,N_UE)*Pmax;
+Rmin_UE = zeros(1,N_UE);
+t = 0;
+for i = 1:S
+    for j = 1:UE_S(i)
+        t = t+1;
+        Rmin_UE(t) = Rmin(i);
+    end
+end
+ChannelGain = zeros(N_RU,N_UE,N_Antenna);
+beamForming = zeros(N_RU ,N_UE,N_Antenna);
+Popt = ones(1,N_UE)*Pmax;
+PRB_UE = zeros(N_PRB,N_UE);
+
+run Channel_Gain
+run Precoding
+%RU_UE = ones(N_RU,N_UE);
+count_max = 1;

### 2022-01-15 Code_journal1/VersionLastJournal/oneSliceCVX/Parameter.m

@@ -1,0 +1,41 @@
+%% obtain Power of RU
+Pow_RU =  zeros(1,N_RU);
+%Pow_RU =  zeros(1,N_RU);
+Popt1 = eye(N_UE);
+for i=1:N_UE
+   Popt1(i,i) = Popt(i); 
+end
+for numRU =1:N_RU
+   for numUE = 1:N_UE
+       if RU_UE(numRU, numUE)==1
+            Pow_RU(numRU) = Pow_RU(numRU) + (abs((beamForming1(:,numUE).')*beamForming1(:,numUE)))*Popt1(numUE,numUE)+var_q; 
+       end
+   end
+end
+
+%% Obtain Interference
+Intf = zeros(1,N_UE);
+for i = 1:N_UE
+    for j = 1:N_Antenna
+        for z = 1:N_PRB
+            for t = 1 : N_UE
+                if i~=t && PRB_UE(z,i) ==1 && PRB_UE(z,t)
+                    %Intf(i) = Intf(i) + Pmax/100*abs((ChannelGain(:,i))'*beamForming(:,i))^2 * PRB_UE(z,i) * PRB_UE(z,t);
+                    Intf(i) =Intf(i) + Pmax/10*abs((ChannelGain1(:,i))'*beamForming1(:,i))^2;
+                end
+            end
+           
+        end
+    end
+end
+
+rate_UE = zeros(1,N_UE);
+for i = 1:N_UE
+    %for j = 1:N_RU
+        for z = 1:N_PRB
+            if PRB_UE(z,i)==1
+                rate_UE(i) = rate_UE(i) + BW* log(1 + (Popt(i)*abs((ChannelGain1(:,i))'*beamForming1(:,i))^2)/(Intf(i)+BW*N0));%*PRB_UE(z,i);
+            end
+        end
+    %end
+end

### 2022-01-15 Code_journal1/VersionLastJournal/oneSliceCVX/Rate_final.m

@@ -1,0 +1,24 @@
+Intf = zeros(1,N_UE);
+for i = 1:N_UE
+    for j = 1:N_Antenna
+        for z = 1:N_PRB
+            for t = 1 : N_UE
+                if i~=t && PRB_UE(z,i) ==1 && PRB_UE(z,t)
+                    %Intf(i) = Intf(i) + Pmax/100*abs((ChannelGain(:,i))'*beamForming(:,i))^2 * PRB_UE(z,i) * PRB_UE(z,t);
+                    Intf(i) =Intf(i) + Popt(i)*abs((ChannelGain1(:,i))'*beamForming1(:,i))^2;
+                end
+            end
+           
+        end
+    end
+end
+
+
+rate_UE_1 = zeros(1,N_UE);
+for i = 1:N_UE
+        for z = 1:N_PRB
+            if PRB_UE(z,i)==1
+                rate_UE_1(i) = rate_UE_1(i) + BW* log(1 + (Popt(i)*abs((ChannelGain1(:,i))'*beamForming1(:,i))^2)/(Intf(i)+BW*N0));%*PRB_UE(z,i);
+            end
+        end
+end

### 2022-01-15 Code_journal1/VersionLastJournal/priority_1/PRB_Pow_Alloc1.m

@@ -1,0 +1,38 @@
+for  count_power=1:1 
+    cvx_begin
+        variables Popt(1,N_UE); 
+        run Interference
+        run Rate
+        run P_RU
+        maximize sum(rate_UE)
+        subject to
+        %Power_RU(N_UE,Popt,beamForming,var_q,N_RU,1:N_RU)<2.^(Capacity_RU(1)/1e4) * var_q*100 ;
+        %Power_RU(N_UE,Popt,beamForming,var_q,N_RU,1:N_RU)<Pmax;
+        Pow_RU <= Pmax*10;
+        Popt(:) >= 0; 
+        Popt(:) <= Pmax*2;
+        
+        %Find_Rate(BW,Popt,ChannelGain,beamForming,PRB_UE,N_PRB,N_UE,N0,Intf,1:N_UE)>= Rmin_UE(1);
+        rate_UE(:) >= Fact_S_UE(:).*Rmin_UE(:);%.*admission_UE1(:); 
+        w1(1,:) = alpha_m(:).* delay_max(:);
+        w2(1,:) = alpha_m(:).*lambda_m(:) .* delay_max(:) + alpha_m(:);
+        w3(1,:) = mu(:).* delay_max(:)-3;
+        w4(1,:) = mu(:).* delay_max(:).*lambda_m(:)+mu(:) - 3*lambda_m(:);
+        %w1(:).*R_s(:)-w2(:)- M_max*(w3(:).*R_s(:)-w4(:)) <= 0;
+        %R_s(:) <= (w2(:) - M_max*w4(:))./((w1(:) - M_max*w3(:)))
+        t = 0;
+        a = zeros(1,S);
+        M_max = 25;
+        for s = 1:S-1
+            for j = 1:UE_S(s)
+                t = t+1;
+                a(s) = (w2(s) - M_max*w4(s))./((w1(s) - M_max*w3(s)));
+                %Popt(t) <= (2^(a(s)/BW)-1)*(Intf(t)*0+BW*N0)/(abs((ChannelGain(:,t))'*beamForming(:,t))^2)
+                %rate_UE(t) >= max(a(s),0)
+            end
+        end
+        
+        %alpha_m(:).*(delay_max(:) - xx(:))-(mu(:).*(delay_max(:) - xx(:))-1)*10 <= 0
+    cvx_end
+
+end

### 2022-01-15 Code_journal1/VersionLastJournal/priority_2/PRB_Pow_Alloc2.m

@@ -1,0 +1,17 @@
+for  count_power=1:1 
+    cvx_begin
+        variables Popt(1,N_UE); 
+        run Interference
+        run Rate
+        run P_RU
+        maximize sum(rate_UE)
+        subject to
+        Pow_RU <= Pmax*6;
+        Popt(:) >= 0; 
+        Popt(:) <= Pmax*2;
+        Popt(9:12) == 0; 
+        rate_UE(:) >= Rmin_UE(:);%.*admission_UE1(:); 
+
+    cvx_end
+
+end

### 2022-01-15 Code_journal1/VersionLastJournal/priority_2/main_final.m

@@ -1,0 +1,106 @@
+clear all
+clc
+run var_const
+count_min1 = 0.1;
+count_step1 = .2;
+count_max1 = 0.9;
+numvar = length(count_min1:count_step1:count_max1);
+iter_max = 20;
+sumRate_eMBB = zeros(numvar,iter_max);
+sumRate_URLLC = zeros(numvar,iter_max);
+sumRate1_eMBB= zeros(numvar,iter_max);
+sumRate1_URLLC = zeros(numvar,iter_max);
+RU_iter_max = N_RU-1;
+%% initializing
+number_check = 0;
+for i_count = count_min1:count_step1:count_max1
+    number_check  = number_check +  1;
+    for iter = 1:iter_max  
+        RU_iter = 1;
+        run parameter_UE_change
+        run PRB_Alloc
+        %%
+        while  RU_iter < RU_iter_max
+            
+            if RU_iter == 1
+              run RUAssociateDist  
+            end
+            run setChGain
+            alpha_m = lambda_m.*(UE_S);
+            run PRB_Pow_Alloc1
+            run findM
+            run Rate_final
+            run RUUESet
+            sumRate_eMBB(number_check,iter) = max(abs(sum(rate_UE_1(1:4))),sumRate_eMBB(number_check,iter));
+            sumRate_URLLC(number_check,iter) = max(abs(sum(rate_UE_1(5:8))),sumRate_URLLC(number_check,iter));
+            if sumRate_eMBB(number_check,iter) > 0 && RU_iter > 2
+                RU_iter = RU_iter_max + 10;
+                
+            end
+            iter
+            i_count
+            RU_iter
+            VNF_NUM
+            RU_iter = RU_iter + 1;
+        end
+        %% BaseLine Scheme
+            run PRB_rand
+            run RUAssociateDist
+            run setChGain
+            alpha_m = lambda_m.*(UE_S);
+            run PRB_Pow_Alloc2
+            run findM
+            run Rate_final
+            run RUUESet
+            sumRate1_eMBB(number_check,iter) = abs(sum(R_s_1(1)));
[…]

### 2022-01-15 Code_journal1/VersionLastJournal/simulLag/update_var.m

@@ -1,0 +1,15 @@
+alpha_step = Pmax/sqrt(count)/1;
+
+for i = 1:N_UE
+    beta_step = 1/1/sqrt(count);
+    lambda_step = Rmin_UE(i)/sqrt(count)/1000;
+    lambda1(i)= max(0,lambda1(i) - lambda_step* (rate_UE(i) - Rmin_UE(i)));
+    for z = 1:N_PRB
+        beta(i) = max(0, beta(i) - beta_step* (PRB_UE(z,i)- 1));
+    end
+    
+end
+for j = 1:N_RU
+
+   alpha(j) = max(0, alpha(j) -alpha_step* (Pmax - Pow_RU(j))); 
+end

### 2022-01-15 Code_journal1/version1/main_simple.m

@@ -1,0 +1,107 @@
+clear all
+clc
+%% Variable
+R = 500;
+S = 1;
+BW = 120*1e3;%10*1e6;  
+n0 = -174;%-174 ; %dbm
+N0 = db2pow(n0)/1000;
+Pc1 = 10; %watt
+Pc  = db2pow(Pc1)/1000;
+Pt = 23;
+Pmax = db2pow(Pt)/1000;
+Rt = .1*BW;%0.1*BW;
+%% Channel Gain
+N_UE = randi(10,1);
+Popt = ones(1,N_UE)*Pmax;
+N_RU =  4;
+ChannelGain = zeros(N_RU,N_UE);
+for i=1:N_RU
+    for j=1:N_UE
+       distance(i,j)= randi(R,1,1);
+       if distance(i,j)==0
+           distance(i,j) = randi(R,1,1);
+       end
+       var_fading = db2pow(10);
+       N_Ute = lognrnd(0,var_fading);
+       loss(i,j) = N_Ute*1/(distance(i,j)^3.8);
+       ChannelGain(i,j) = 100*(loss(i,j)^0.5)/sqrt(2)*(randn(1)+1i*randn(1));
+    end
+end
+RU_UE = zeros(N_RU,N_UE);
+for j=1:N_UE
+    RU2UE = 0;
+    temp = 0;
+    for i=1:N_RU
+        if abs(ChannelGain(i,j))> abs(temp)
+            temp = ChannelGain(i,j);
+            RU2UE = i;
+        end
+    end
+    RU_UE(RU2UE,j) = 1;
+end
+%% UE Admission
+rate_UE_min = zeros(1,N_UE);
+admission_UE = ones(1,N_UE);
+admission_UE1 =  zeros(1,N_UE);
+%RU_UE = zeros(N_RU,N_UE);
+rate_UE_min = zeros(1,N_UE);
+Intf = zeros(1,N_UE);
+for i = 1:N_UE
+    for j = 1:N_RU
+        for t = 1 : N_UE
+            if i~=t 
+                Intf(i) = Intf(i) + Popt(t)*abs(ChannelGain(j,i))^2 * (1 - RU_UE(j,i));
+            end
+        end
+        rate_UE_min(i) = rate_UE_min(i) + BW* log2(1 + (Popt(i)/100*abs((ChannelGain(j,i).*RU_UE(j,i)))^2)/(Intf(i)+BW*N0));
+    end
+end
+C_Fr = sum(rate_UE_min);
[…]

### 2022-01-15 Code_journal1/version10/simulation_1/Interference.m

@@ -1,0 +1,15 @@
+%% Obtain Interference
+Intf = zeros(1,N_UE);
+for i = 1:N_UE
+    for j = 1:N_RU
+        for z = 1:N_PRB
+            for t = 1 : N_UE
+                if i~=t && PRB_UE(z,i) ==1 && PRB_UE(z,t)
+                    %Intf(i) = Intf(i) + Pmax/100*abs((ChannelGain(:,i))'*beamForming(:,i))^2 * PRB_UE(z,i) * PRB_UE(z,t);
+                    Intf(i) =Intf(i) + Pmax/1000*abs((ChannelGain(:,i))'*beamForming(:,i))^2;
+                end
+            end
+           
+        end
+    end
+end

### 2022-01-15 Code_journal1/version2/var_const.m

@@ -1,0 +1,24 @@
+% Physical layer introduce variable
+%% Initial Variable
+R = 500;
+S = 2;
+BW = 120*1e3;%10*1e6;  
+n0 = -174;%-174 ; %dbm
+N0 = db2pow(n0)/1000;
+Pc1 = 10; %watt
+Pc  = db2pow(Pc1)/1000;
+Pt = 23;
+Pmax = db2pow(Pt)/1000;
+Rmin = .2*BW*randi([1,10],1,S);
+Rate_mid_max = BW*randi([1,10],1,S);
+%% 
+N_PRB = 24;
+T_max = 50e-3; % sec
+N_UE_max = 10;
+N_RU = 4;
+counter_max = 10;
+%%
+C_tot_RU = sum(Rate_mid_max);
+Capacity_RU = C_tot_RU * randi([1,50],1,N_RU)/100;
+N_Antenna = 1;
+P_RU = zeros(1,N_RU);

### 2022-01-15 Code_journal1/version3/PRB_Pow_Alloc.m

@@ -1,0 +1,16 @@
+% PRB & Power Allocation
+cvx_begin
+    variables Popt(1,N_UE) 
+    %variable PRB_UE(N_PRB, N_UE) binary;
+    run Interference
+    run Rate
+    %rate_UE = cvx(rate_UE);
+    run P_RU
+    maximize sum(rate_UE)
+    subject to
+    Pow_RU(:) <= Pmax;
+    %Prrh(:) <= 2^C_thresh * var_q *100;
+    Popt(:) >= 0; 
+    rate_UE(:) >= Rmin(1)/1;%.*admission_UE1(:);  
+    %PRB_UE(:)> 1
+cvx_end

### 2022-01-15 Code_journal1/version3/Var.m

@@ -1,0 +1,39 @@
+%% Initial Variable
+R = 500;
+S = 3;
+BW = 120*1e3; %10*1e6;  
+n0 = -174; %-174 dbm
+N0 = db2pow(n0)/1000;
+Pc1 = 10; %watt
+Pc  = db2pow(Pc1)/1000;
+Pt = 25;
+Pmax = db2pow(Pt)/1000;
+Rmin1 = 1*BW*randi([1,10],1,S);
+[Rmin, I] = sort(Rmin1,'descend');
+Rate_mid_max = BW*randi([5,10],1,S);
+%% 
+T_max = 50e-3*randi([1,10],1,S); % sec
+N_UE_max = 10;
+N_RU = 4;
+counter_max = 5;
+%%
+C_tot_RU = sum(Rate_mid_max);
+Capacity_RU = C_tot_RU * randi([10,50],1,N_RU)/100;
+N_Antenna = 1;
+%P_RU = zeros(1,N_RU);
+%% changable variable
+UE_S = randi(N_UE_max,1,S);
+N_UE = sum(UE_S);
+RU_UE = zeros(N_RU,N_UE);
+%Popt = ones(1,N_UE)*Pmax;
+Rmin_UE = zeros(1,N_UE);
+t = 0;
+for i = 1:S
+    for j = 1:UE_S(i)
+        t = t+1;
+        Rmin_UE(t) = Rmin(i);
+    end
+end
+N_PRB = 12;
+%RU_PRB = randi([0 1],N_RU,N_PRB);
+%PRB_UE = randi([0,1],N_PRB,N_UE);%zeros(N_PRB, N_UE);

### 2022-01-15 Code_journal1/version3/main.m

@@ -1,0 +1,25 @@
+clear all
+clc
+%% initializing
+run Var
+%% UE Admission
+run UE_admission
+%% RU associated in Comp Way, Remove UE that are not admitted
+N_UE = sum(UE_S_Admit);
+Rmin_UE = zeros(1,N_UE);
+t = 0;
+for i = 1:S
+    for j = 1:UE_S_Admit(i)
+        t = t+1;
+        Rmin_UE(t) = Rmin(i);
+    end
+end
+ChannelGain = zeros(N_RU,N_UE);
+beamForming = zeros(N_RU ,N_UE);
+Popt = ones(1,N_UE)*Pmax;
+PRB_UE = randi([0,1],N_PRB,N_UE);
+run Channel_Gain
+run Precoding
+run RU_association
+run PRB_Pow_Alloc
+%run PRB_P

### 2022-01-15 Code_journal1/version5-lastV/P_RU.m

@@ -1,0 +1,8 @@
+%% obtain Power of RU
+Pow_RU =  cvx(zeros(1,N_RU));
+%Pow_RU =  zeros(1,N_RU);
+for i = 1:N_RU
+    for j = 1:N_UE
+        Pow_RU(i) = Pow_RU(i) +  Popt(j)*RU_UE(i,j);
+    end
+end

### 2022-01-15 Code_journal1/version7/Var.m

@@ -1,0 +1,47 @@
+%% Initial Variable
+R = 500;
+S = 3;
+BW = 120*1e3; %10*1e6;  
+n0 = -174; %-174 dbm
+N0 = db2pow(n0)/1000;
+Pc1 = 10; %watt
+Pc  = db2pow(Pc1)/1000;
+Pt = 30;
+Pmax = db2pow(Pt)/1000;
+Rmin1 = .1*BW*randi([1,5],1,S); %.1*BW*ones(1,S)
+[Rmin, I] = sort(Rmin1,'descend');
+Rate_mid_max = 0.5*BW*randi([1,10],1,S);
+var_q = 1e-6;
+alpha_s = .1*BW;
+delay_max = 3e-5*randi([5,10],1,S);
+mu = Rmin .* randi([500,520],1,S)/1000;
+alpha_m  = Rmin .* randi([485,499],1,S)/1000;
+%C_thresh = 3000*Rt/BW;
+%% 
+T_max = 50e-5*randi([1,10],1,S); % sec
+Delay_Slice = zeros(1,S);
+VNF_NUM =  zeros(1,S);
+N_UE_max = 10;
+N_RU = 4;
+counter_max = 5;
+%%
+C_tot_RU = sum(Rate_mid_max);
+Capacity_RU = C_tot_RU * randi([10,50],1,N_RU)/100;
+N_Antenna = 1;
+%P_RU = zeros(1,N_RU);
+%% changable variable
+UE_S = randi(N_UE_max,1,S);
+N_UE = sum(UE_S);
+RU_UE = zeros(N_RU,N_UE);
+%Popt = ones(1,N_UE)*Pmax;
+Rmin_UE = zeros(1,N_UE);
+t = 0;
+for i = 1:S
+    for j = 1:UE_S(i)
+        t = t+1;
+        Rmin_UE(t) = Rmin(i);
+    end
+end
+N_PRB = 6;
+%RU_PRB = randi([0 1],N_RU,N_PRB);
+%PRB_UE = randi([0,1],N_PRB,N_UE);%zeros(N_PRB, N_UE);

### 2022-01-15 codes/firstPart/var.m

@@ -1,0 +1,45 @@
+R = 500;
+S = 5;
+BW = 120*1e3;%10*1e6;  
+n0 = -174;%-174 ; %dbm
+N0 = db2pow(n0)/1000;
+Pc1 = 10; %watt
+Pc  = db2pow(Pc1)/1000;
+Pt = 23;
+Pmax = db2pow(Pt)/1000;
+Rt = .1*BW;%0.1*BW; 
+Ut = 5;
+K = Ut;
+r = zeros(1,K);
+%%
+M = 100;
+Mmin=10;
+Mstep=10;
+Mmax=50;
+Umin =2;
+Umax = 20;
+Ustep = 2;
+Smin=2;
+Sstep=1;
+Smax=5;
+Pmin=1;
+Pstep=10;
+Pmmax=151;
+Pmm=10^-15;
+%Us = floor((Ut_max-Ut_min)/Ut_step)+1;
+%%
+iter_max =10;
+count_max = 25;
+thresh = 1e-10;
+var_q = 1e-4;
+Cmax = 5;
+%%
+%eta = zeros(count_max,iter_max,floor((Mmax-Mmin)/Mstep)+1);
+%rrate= zeros(count_max,iter_max,floor((Mmax-Mmin)/Mstep)+1);
+Poptimal= zeros(count_max,iter_max,floor((Mmax-Mmin)/Mstep)+1,K, S);
+eta = zeros(count_max,iter_max,floor((Smax-Smin)/Sstep)+1);
+%rrate= zeros(count_max,iter_max,floor((Pmmax-Pmin)/Pstep)+1);
+%eta = zeros(count_max,iter_max,floor((Umax-Umin)/Ustep)+1);
+%Poptimal= zeros(count_max,iter_max,floor((Umax-Umin)/Ustep)+1,K, S);
+%Ropt = zeros(count_max,iter_max, floor((Mmax-Mmin)/Mstep)+1,K, S);
+%Copt = zeros(count_max,iter_max, floor((Mmax-Mmin)/Mstep)+1,K, S);

### 2022-01-15 codes/knapsack/knapsack4.py

@@ -1,0 +1,128 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Dec 16 12:14:14 2019
+
+@author: s.nouri
+"""
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+import numpy as np
+import matplotlib.pyplot as plt
+	
+from random import *
+randBinList = lambda n: [randint(0,1) for b in range(1,n+1)]
+
+from ortools.sat.python import cp_model
+
+
+def create_data_model(Num_var):
+    """Create the data for the example."""
+    data = {}
+    weights = randBinList(Num_var)
+    # weights = np.random.rand(Num_var) * 4
+    values = weights
+    data['num_items'] = len(weights)
+    data['all_items'] = range(data['num_items'])
+    data['weights'] = weights
+    data['values'] = values
+    data['bin_capacities'] = [100, 150,300]
+    data['num_bins'] = len(data['bin_capacities'])
+    data['all_bins'] = range(data['num_bins'])
+    return data
+
+
+
+def print_solutions(data, solver, x):
+    """Display the solution."""
+    total_weight = 0
+    total_value = 0
+    for b in data['all_bins']:
+        print('Bin', b, '\n')
+        bin_weight = 0
+        bin_value = 0
+        for idx, val in enumerate(data['weights']):
+            if solver.Value(x[(idx, b)]) > 0:
+                print('Item', idx, '-  Weight:', val, ' Value:',
+                      data['values'][idx])
+                bin_weight += val
+                bin_value += data['values'][idx]
+        print('Packed bin weight:', bin_weight)
+        print('Packed bin value:', bin_value, '\n')
+        total_weight += bin_weight
+        total_value += bin_value
+    print('Total packed weight:', total_weight)
+    print('Total packed value:', total_value)
+    return total_value
+
+
+
+
+def main():
+    data = create_data_model(Num_var)
+
+    model = cp_model.CpModel()
+
+    # Main variables.
+    x = {}
+    for idx in data['all_items']:
+        for b in data['all_bins']:
+            x[(idx, b)] = model.NewIntVar(0, 1, 'x_%i_%i' % (idx, b))
+    max_value = sum(data['values'])
+    # value[b] is the value of bin b when packed.
+    value = [
+        model.NewIntVar(0, max_value, 'value_%i' % b) for b in data['all_bins']
+    ]
+    for b in data['all_bins']:
[…]

### 2022-01-15 codes/mozekPart/constraint.m

@@ -1,0 +1,7 @@
+.......................................................................................................................................................................................................%%
+%rate_UE(:)>Rt
+Prrh < Pmax
+Crrh < C_thresh
+Delay_Slice < delay_max
+sum(service2slice,2)> 0
+eta_UE(:)>0

### 2022-01-15 codes/secondPart/server/main.m

@@ -1,0 +1,76 @@
+clc
+clear all
+%% define variables
+N_service = 10;
+N_server = 7;
+Dmax = [1000, 10, 100];
+Rmax = [3000, 30, 300];
+N_resource = 3; % cpu, ram, storage
+demand_service = rand(N_service,N_resource);
+resource_server = rand(N_server,N_resource);
+demand_service = demand_service.*Dmax; 
+resource_server = resource_server.*Rmax;
+
+%% sort variables
+weight = [1, 100, 10];
+demand_service1 = sorting(demand_service, N_resource, weight, N_service);
+resource_server1 = sorting(resource_server, N_resource, weight, N_server);
+%% mapping
+mappingVar = zeros(N_service, N_server);
+i = N_service;
+mapStatus = ones(1,N_service);
+resourceShare = resource_server1(:,2:4);
+for j = N_server:-1:1
+    for i = 1:N_service
+        if mapStatus(i)==1
+            rs = resourceShare(j,:)-demand_service1(i,2:4);
+            if all(rs >= 0) 
+                mappingVar(i,j) = 1;
+                mapStatus(i) = 0;
+                resourceShare(j,:) = resourceShare(j,:)-demand_service1(i,2:4);
+            end
+        end
+    end
+end
+%% if service need more than one VM
+ %mapStatus = sum(mappingVar,2);
+ index_notMap = find(mapStatus == 1);
+ remain_source = sorting(resourceShare, N_resource, weight, N_server);
+ resourceShare1 = remain_source(:,2:4);
+ demand_service2= demand_service1(:,2:4);
+ for i=index_notMap
+    for j = N_server:-1:1
+        demand_service2(i,:) = -resourceShare1(j,:)+ demand_service2(i,:);
+        indMap = find(resourceShare1(j,1)==resourceShare(:,1));
+        mappingVar(i,indMap) = 1;
+        if all(demand_service2(i,:) <= 0)
+            j = 0;
+            break;
+        end
+        
+    end
+ end
+
+%% remap again for special case 
+disp(sum(resource_server1(:,2:4)))
+disp(sum(demand_service1(:,2:4)))
+sum_vector = demand_service1(:,2:4)'*mappingVar;
+ind(1,:) = find(sum_vector(1,:)>0);
+ind(2,:) = find(sum_vector(2,:)>0);
+temp = zeros(1,N_server);
+for j= 1: N_server
[…]

### 2022-01-15 codes/simple_one/var.m

@@ -1,0 +1,50 @@
+%% Physical layer
+R = 500;
+N_Service = 5;
+N_Slice =  6;
+BW = 120*1e3;%10*1e6;  
+n0 = -174;%-174 ; %dbm
+N0 = db2pow(n0)/1000;
+Pc1 = 10; %watt
+Pc  = db2pow(Pc1)/1000;
+Pt = 30;
+Pmax = db2pow(Pt)/1000;
+Rt = .1*BW;%0.1*BW; 
+N_PRB = 10;
+N_rrh = 3;
+N_rrh_max = 50;
+N_rrh_min = 10;
+N_rrh_step = 10;
+imax = 1;
+NumOfUtInService = randi([1 10],1, N_Service);
+N_Ut = sum(NumOfUtInService);
+rrh2slice = randi([0 imax],N_rrh, N_Slice); %not map 1 -->true 
+service2slice = zeros(N_Service, N_Slice);    %randi([0 imax],N_Service, N_Slice); %2 we want to find this!!!!!
+Ut2Service = zeros(sum(NumOfUtInService),N_Service); %3 -->true
+PRB2Slice = randi([0 imax],N_PRB, N_Slice); %4 
+Ut_map = zeros(N_Ut, N_PRB);  % map it
+Popt = ones(1, N_Ut)*Pmax/N_Ut;
+iter_max =1;
+N_BBU = 2;
+BBU_map = zeros(N_BBU, N_Slice);
+Crrh = zeros(1, N_rrh);
+Prrh = zeros(1,N_rrh);
+var_q = 1e-5;
+C_thresh = 10*Rt/BW;
+%% VNF MAC LAYER
+N_VNF1 = 10;
+VNF2Slice1 = randi([0 imax],N_VNF1, N_Slice); %5
+N_VNF2 = 10;
+VNF2Slice2 = randi([0 imax],N_VNF2, N_Slice); %6
+mu1 = 10* Rt;
+alpha_m1  = Rt;
+mu2 = 10* Rt;
+alpha_m2  = Rt;
+lamda = Rt/10000;
+delay_thresh = 9.2593e-06;
+Delay_Slice1 = zeros(N_Slice,1);
+Delay_Slice2 = zeros(N_Slice,1);
+Delay_Transmission = zeros(N_Slice,1);
+delay_max = 3e-4;
+priority_service = ones(1,N_Service);
+Delay_Slice = zeros(1,N_Slice);

### 2022-01-15 codes/simple_one/var1.m

@@ -1,0 +1,56 @@
+%% Physical layer
+R = 500;
+N_Service = 5;
+N_Slice =  10;
+N_rrh = 10;
+BW = 120*1e3;%10*1e6;  
+n0 = -174;%-174 ; %dbm
+N0 = db2pow(n0)/1000;
+Pc1 = 10; %watt
+Pc  = db2pow(Pc1)/1000;
+Pt = 30;
+Pmax = db2pow(Pt)/1000;
+Rt = .1*BW;%0.1*BW; 
+N_PRB = 10;
+imax = 1;
+NumOfUtInService = randi([1 5],1, N_Service);
+NumOfUtInService = UEN*ones(1,N_Service);
+N_Ut = sum(NumOfUtInService);
+rrh2slice = randi([0 imax],N_rrh, N_Slice); 
+Crrh = zeros(1, N_rrh);
+Prrh = zeros(1,N_rrh);
+Power = zeros(counter_max, N_Ut);
+Power_cnvg_Thr = 0.01;
+service2slice = zeros(N_Service, N_Slice);    %randi([0 imax],N_Service, N_Slice); %2 we want to find this!!!!!
+Ut2Service = zeros(sum(NumOfUtInService),N_Service); %3 -->true
+PRB2Slice = randi([0 imax],N_PRB, N_Slice); %4 
+Ut_map = zeros(N_Ut, N_PRB);  % map it
+Popt = ones(1, N_Ut)*Pmax/N_Ut;
+iter_max =1;
+N_BBU = 2;
+BBU_map = zeros(N_BBU, N_Slice);
+var_q = 1e-5;
+C_thresh = 1000*Rt/BW;
+  
+%% VNF MAC LAYER
+N_VNF1 = 10;
+VNF2Slice1 = randi([0 imax],N_VNF1, N_Slice); %5
+N_VNF2 = 10;
+VNF2Slice2 = randi([0 imax],N_VNF2, N_Slice); %6
+mu1 = 10* Rt;
+alpha_m1  = Rt;
+mu2 = 10* Rt;
+alpha_m2  = Rt;
+lamda = Rt/10000;
+delay_thresh = 9.2593e-06;
+Delay_Slice1 = zeros(N_Slice,1);
+Delay_Slice2 = zeros(N_Slice,1);
+Delay_Transmission = zeros(N_Slice,1);
+delay_max = 3e-4;
+priority_service = ones(1,N_Service);
[…]

### 2022-01-15 codes/simulation1/channel.m

@@ -1,0 +1,15 @@
+ChannelGain = zeros(N_rrh,N_Ut);
+
+for i=1:N_rrh
+    for j=1:N_Ut
+       distance(i,j)= randi(R,1,1);
+       if distance(i,j)==0
+           distance(i,j) = randi(R,1,1);
+       end
+       var_fading = db2pow(10);
+       N_Ute = lognrnd(0,var_fading);
+       loss(i,j) = N_Ute*1/(distance(i,j)^3.8);
+       ChannelGain(i,j) = (loss(i,j)^0.5)/sqrt(2)*(randn(1)+1i*randn(1));
+    end
+end
+ChannelGain2 = ChannelGain;

### 2022-01-15 codes/simulation1/plotWithNan.m

@@ -1,0 +1,22 @@
+y1 = zeros(2,nr);
+for i =1:iter_max
+    for j=1:nr
+        if isnan(etha(j,i))==0
+            y1(1,j)=y1(1,j)+etha(j,i);
+            y1(2,j)= y1(2,j)+1;
+        end
+    end
+end
+plot( N_min:N_step:N_max , y1(1,:)./y1(2,:))  
+
+hold on
+y = zeros(2,nr);
+for i =1:iter_max
+    for j=1:nr
+        if isnan(etha1(j,i))==0
+            y(1,j)=y(1,j)+etha1(j,i);
+            y(2,j)= y(2,j)+1;
+        end
+    end
+end
+plot( N_min:N_step:N_max , y(1,:)./y(2,:))      

### 2022-01-15 job/HWs/New folder/q2/test.py

@@ -1,0 +1,64 @@
+"""
+HTTP Request
+"""
+from http.server import BaseHTTPRequestHandler, HTTPServer
+import logging
+import xml.etree.ElementTree as ET
+import json
+
+
+class S(BaseHTTPRequestHandler):
+
+    def _set_response(self):
+        self.send_response(200)
+        self.send_header('Content-type', 'text/html')
+        self.end_headers()
+
+    def do_GET(self):
+        logging.info("GET request,\nPath: %s\nHeaders:\n%s\n", str(self.path), str(self.headers))
+        self._set_response()
+        a = str(self.path)
+        str1 =  str(a[1:])
+        print(str1)
+        f = open('city.json',)
+        data = json.load(f)
+        print(data[str1])
+
+
+        self.wfile.write("GET request for me {}".format(str(data[str1])).encode('utf-8'))
+
+    def do_POST(self):
+        content_length = int(self.headers['Content-Length']) # <--- Gets the size of data
+        post_data = self.rfile.read(content_length) # <--- Gets the data itself
+        logging.info("POST request for me ,\nPath: %s\nHeaders:\n%s\n\nBody:\n%s\n",
+                str(self.path), str(self.headers), post_data.decode('utf-8'))
+        a = str(self.path)
+        str1 =  str(a[1:])
+        print(str1)
+        f = open('city.json',)
+        data = json.load(f)
+        print(data[str1])
+        dict_sample = dict({str1:data[str1]})
+        print(json.dumps(dict_sample))
+        self._set_response()
+        self.wfile.write("POST request for {}".format(json.dumps(dict_sample)).encode('utf-8'))
+
+def run(server_class=HTTPServer, handler_class=S, port=8080):
+    logging.basicConfig(level=logging.INFO)
+    server_address = ('', port)
+    httpd = server_class(server_address, handler_class)
+    logging.info('Starting httpd...\n')
+    try:
+        httpd.serve_forever()
+    except KeyboardInterrupt:
+        pass
+    httpd.server_close()
+    logging.info('Stopping httpd...\n')
+
+if __name__ == '__main__':
+    from sys import argv
+
+    if len(argv) == 2:
+        run(port=int(argv[1]))
+    else:
+        run()

### 2022-01-15 job/HWs/hw1/TA_session1/prac.py

@@ -1,0 +1,13 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Apr 28 12:22:55 2021
+
+@author: mojdeh
+"""
+
+
+import shutil 
+import os
+import numpy as np
+
+pth = os.path.join(os.getcwd(),"root")

### 2022-01-15 job/HWs/hw2/test1/main.py

@@ -1,0 +1,30 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Sat May  8 12:22:00 2021
+
+@author: mojdeh
+"""
+
+import numpy as np
+import os
+#import textMining
+ # write a question to open a text file and write this is line number i 
+# open text file 
+f= open("file3.txt","w")
+n = np.random.randint(1,11)
+for i in range(n):
+     f.write("This is line %d\r\n" % (i+1))
+
+#pth = os.getcwd()
+#
+#
+#filelist = os.listdir(pth)
+#for f1 in filelist:
+#    if ".txt" in f1 and "file1" not in f1:
+#        print(f1)
+#        filename = f1
+#
+#
+#User, Pass = textMining.find_user_pass(filename)
+#string, str = textMining.find_json_file(filename)
+#print(string)

### 2022-01-15 job/HWs/hw3/testJson.py

@@ -1,0 +1,6 @@
+import json
+  
+# Opening JSON file
+with open('city.json') as json_file:
+    data = json.load(json_file)
+print(data)

### 2022-01-15 job/HWs/session4/q2/q2.py

@@ -1,0 +1,36 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+
+
+#########
+
+df = pd.read_csv (r'StudentsPerformance.csv')
+print(df.shape)
+print(df.isnull().values.any())
+#######
+
+
+df.hist()
+
+####
+
+size_pd = np.zeros(df.shape)
+var1 = df.var()
+mean1 = df.mean()
+median1 = df.median()
+print(df.head())
+
+####
+
+print(df.columns)
+
+##########
+
+df.describe()
+
+
+
+
+

### 2022-01-15 job/HWs/session7-8/New folder/client1.py

@@ -1,0 +1,7 @@
+import SOAPpy
+server = SOAPpy.SOAPProxy("http://localhost:8080/")
+print server.hello()
+a = int(input("write"))
+print server.findMark(a)
+print server.RFile1()
+server.WFile1(a)

### 2022-01-15 job/RM-ImageDetection-custom_rug2/RM-ImageDetection-custom_rug2/custom_color/colorgram1.py

@@ -1,0 +1,181 @@
+# -*- coding: utf-8 -*-
+
+
+
+import array
+from collections import namedtuple
+from PIL import Image
+
+
+
+Rgb = namedtuple('Rgb', ('r', 'g', 'b'))
+Hsl = namedtuple('Hsl', ('h', 's', 'l'))
+
+class Color(object):
+    def __init__(self, r, g, b, proportion):
+        self.rgb = Rgb(r, g, b)
+        self.proportion = proportion
+    
+    def __repr__(self):
+        return "<colorgram.py Color: {}, {}%>".format(
+            str(self.rgb), str(self.proportion * 100))
+
+    @property
+    def hsl(self):
+        try:
+            return self._hsl
+        except AttributeError:
+            self._hsl = Hsl(*hsl(*self.rgb))
+            return self._hsl
+
+def extract(f, number_of_colors):
+    image = f if isinstance(f, Image.Image) else Image.open(f)
+    if image.mode not in ('RGB', 'RGBA', 'RGBa'):
+        image = image.convert('RGB')
+    
+    samples = sample(image)
+    used = pick_used(samples)
+    used.sort(key=lambda x: x[0], reverse=True)
+    return get_colors(samples, used, number_of_colors)
+def extract1(image, number_of_colors):
+    #image = f if isinstance(f, Image.Image) else Image.open(f)
+    if image.mode not in ('RGB', 'RGBA', 'RGBa'):
+        image = image.convert('RGB')
+    
+    samples = sample(image)
+    used = pick_used(samples)
+    used.sort(key=lambda x: x[0], reverse=True)
+    return get_colors(samples, used, number_of_colors)
+
+def sample(image):
+    top_two_bits = 0b11000000
+
+    sides = 1 << 2 # Left by the number of bits used.
+    cubes = sides ** 7
+
+    samples = array.array(ARRAY_DATATYPE, (0 for _ in range(cubes)))
+    width, height = image.size
+    
+    pixels = image.load()
+    for y in range(height):
+        for x in range(width):
+            # Pack the top two bits of all 6 values into 12 bits.
+            # 0bYYhhllrrggbb - luminance, hue, luminosity, red, green, blue.
+
+            r, g, b = pixels[x, y][:3]
+            h, s, l = hsl(r, g, b)
+            # Standard constants for converting RGB to relative luminance.
+            Y = int(r * 0.2126 + g * 0.7152 + b * 0.0722)
+
[…]

### 2022-01-15 job/RM-ImageDetection-custom_rug2/RM-ImageDetection-custom_rug2/floorSegmentation/MITSeg/eval.py

@@ -1,0 +1,212 @@
+# System libs
+import os
+import time
+import argparse
+from distutils.version import LooseVersion
+# Numerical libs
+import numpy as np
+import torch
+import torch.nn as nn
+from scipy.io import loadmat
+# Our libs
+from dataset import ValDataset
+from models import ModelBuilder, SegmentationModule
+from utils import AverageMeter, colorEncode, accuracy, intersectionAndUnion
+from lib.nn import user_scattered_collate, async_copy_to
+from lib.utils import as_numpy, mark_volatile
+import lib.utils.data as torchdata
+import cv2
+from tqdm import tqdm
+
+colors = loadmat('data/color150.mat')['colors']
+
+
+def visualize_result(data, pred, args):
+    (img, seg, info) = data
+
+    # segmentation
+    seg_color = colorEncode(seg, colors)
+
+    # prediction
+    pred_color = colorEncode(pred, colors)
+
+    # aggregate images and save
+    im_vis = np.concatenate((img, seg_color, pred_color),
+                            axis=1).astype(np.uint8)
+
+    img_name = info.split('/')[-1]
+    cv2.imwrite(os.path.join(args.result,
+                img_name.replace('.jpg', '.png')), im_vis)
+
+
+def evaluate(segmentation_module, loader, args):
+    acc_meter = AverageMeter()
+    intersection_meter = AverageMeter()
+    union_meter = AverageMeter()
+    time_meter = AverageMeter()
+
+    segmentation_module.eval()
+
+    pbar = tqdm(total=len(loader))
+    for batch_data in loader:
+        # process data
+        batch_data = batch_data[0]
+        seg_label = as_numpy(batch_data['seg_label'][0])
+        img_resized_list = batch_data['img_data']
+
+        torch.cuda.synchronize()
+        tic = time.perf_counter()
+        with torch.no_grad():
+            segSize = (seg_label.shape[0], seg_label.shape[1])
+            scores = torch.zeros(1, args.num_class, segSize[0], segSize[1])
+            scores = async_copy_to(scores, args.gpu_id)
+
+            for img in img_resized_list:
+                feed_dict = batch_data.copy()
+                feed_dict['img_data'] = img
+                del feed_dict['img_ori']
+                del feed_dict['info']
+                feed_dict = async_copy_to(feed_dict, args.gpu_id)
+
+                # forward pass
+                scores_tmp = segmentation_module(feed_dict, segSize=segSize)
[…]

### 2022-01-15 job/RM-ImageDetection-custom_rug2/RM-ImageDetection-custom_rug2/floorSegmentation/XiaohuLuVPDetection-master/lu_vp_detect/run_vp_detect.py

@@ -1,0 +1,71 @@
+import argparse
+from lu_vp_detect.vp_detection import vp_detection
+
+# Set up argument parser + options
+#parser = argparse.ArgumentParser(
+#	description='Main script for Lu''s Vanishing Point Algorithm')
+#parser.add_argument('-i', '--image-path', help='Path to the input image',
+#	required=True)
+#parser.add_argument('-lt', '--length-thresh', default=30, type=float,
+#	help='Minimum line length (in pixels) for detecting lines')
+#parser.add_argument('-pp', '--principal-point', default=None, nargs=2,
+#	type=float, help='Principal point of the camera (default is image centre)')
+#parser.add_argument('-f', '--focal-length', default=1500, type=float,
+#	help='Focal length of the camera (in pixels)')
+#parser.add_argument('-d', '--debug', action='store_true',
+#	help='Turn on debug image mode')
+#parser.add_argument('-ds', '--debug-show', action='store_true',
+#	help='Show the debug image in an OpenCV window')
+#parser.add_argument('-dp', '--debug-path', default=None,
+#	help='Path for writing the debug image')
+#parser.add_argument('-s', '--seed', default=None, type=int,
+#	help='Specify random seed for reproducible results')
+#args = parser.parse_args()
+
+def main():
+	# Extract command line arguments
+	input_path = "m11.jpg"
+	length_thresh = 60
+	principal_point = None
+	focal_length = 1102.79
+	debug_mode = 1
+	debug_show = 1
+	debug_path = None
+	seed = 1337
+
+	print('Input path: {}'.format(input_path))
+	print('Seed: {}'.format(seed))
+	print('Line length threshold: {}'.format(length_thresh))
+	print('Focal length: {}'.format(focal_length))
+
+	# Create object
+	vpd = vp_detection(length_thresh, principal_point, focal_length, seed)
+
+	# Run VP detection algorithm
+	vps = vpd.find_vps(input_path)
+	print('Principal point: {}'.format(vpd.principal_point))
+
+	# Show VP information
+	print("The vanishing points in 3D space are: ")
+	for i, vp in enumerate(vps):
+		print("Vanishing Point {:d}: {}".format(i + 1, vp))
+
+	vp2D = vpd.vps_2D
+	print("\nThe vanishing points in image coordinates are: ")
+	for i, vp in enumerate(vp2D):
+		print("Vanishing Point {:d}: {}".format(i + 1, vp))
+
+	# Extra stuff
[…]

### 2022-01-15 job/folders/test2/main.cpp

@@ -1,0 +1,291 @@
+// C program to Implement Ping 
+  
+// compile as -o ping 
+// run as sudo ./ping <hostname> 
+  
+#include <stdio.h> 
+#include <sys/types.h> 
+#include <sys/socket.h> 
+#include <netinet/in.h> 
+#include <arpa/inet.h> 
+#include <netdb.h> 
+#include <unistd.h> 
+#include <string.h> 
+#include <stdlib.h> 
+#include <netinet/ip_icmp.h> 
+#include <time.h> 
+#include <fcntl.h> 
+#include <signal.h> 
+#include <time.h> 
+  
+// Define the Packet Constants 
+// ping packet size 
+#define PING_PKT_S 64 
+   
+// Automatic port number 
+#define PORT_NO 0  
+  
+// Automatic port number 
+#define PING_SLEEP_RATE 1000000 x 
+  
+// Gives the timeout delay for receiving packets 
+// in seconds 
+#define RECV_TIMEOUT 1  
+  
+// Define the Ping Loop 
+int pingloop=1; 
+  
+  
+// ping packet structure 
+struct ping_pkt 
+{ 
+    struct icmphdr hdr; 
+    char msg[PING_PKT_S-sizeof(struct icmphdr)]; 
+}; 
+  
+// Calculating the Check Sum 
+unsigned short checksum(void *b, int len) 
+{    unsigned short *buf = b; 
+    unsigned int sum=0; 
+    unsigned short result; 
+  
+    for ( sum = 0; len > 1; len -= 2 ) 
+        sum += *buf++; 
+    if ( len == 1 ) 
+        sum += *(unsigned char*)buf; 
+    sum = (sum >> 16) + (sum & 0xFFFF); 
+    sum += (sum >> 16); 
+    result = ~sum; 
+    return result; 
+} 
+  
+  
+// Interrupt handler 
+void intHandler(int dummy) 
+{ 
+    pingloop=0; 
+} 
+  
+// Performs a DNS lookup  
+char *dns_lookup(char *addr_host, struct sockaddr_in *addr_con) 
+{ 
+    printf("\nResolving DNS..\n"); 
+    struct hostent *host_entity; 
+    char *ip=(char*)malloc(NI_MAXHOST*sizeof(char)); 
+    int i; 
+  
+    if ((host_entity = gethostbyname(addr_host)) == NULL) 
+    { 
+        // No ip found for hostname 
+        return NULL; 
+    } 
+      
[…]

### 2022-01-15 job/my-first-app/src/assets/js/custom_rug.js

@@ -1,0 +1,251 @@
+var model = [];
+var message = {}
+var isOpen = false;
+var colors123 = [];
+var counter = new Array(7);
+var hslL = [];
+counter =[0,0,0,0,0,0,0]
+var meanL = new Array(7);
+meanL =[0,0,0,0,0,0,0]
+var changColorCounter = 0;
+var colorlen = 0;
+//var thresh = 33;
+function sendToServer() {
+	let imageUrl = document.getElementById("txt_url").value;
+	let flag =  document.getElementById("flag").value;
+	//let thresh =  document.getElementById("thresh").value;
+	//hslL = [];
+	changColorCounter = 0;
+	let _socket = new socket(imageUrl, flag, getResponse);
+	_socket.connected(function() {
+		_socket.send()
+
+	})
+	
+}
+
+
+
+
+function getResponse(msg) {
+
+	//debugger;
+	colors123 = [];
+	if (msg && msg.data) {
+		changColorCounter = 0;
+		meanL =[0,0,0,0,0,0,0]
+		counter =[0,0,0,0,0,0,0]
+		console.log(JSON.parse(msg.data),'++++++++data',msg.data,'------------',JSON.parse(msg.data).model_1d, "this is data given from server");
+		let imageUrl = document.getElementById("txt_url").value;
+		message = JSON.parse(msg.data);
+		hslL = new Array(message.shape[0]*message.shape[1]);
+		getImage(imageUrl,JSON.parse(msg.data).model_1d)
+		var colors = JSON.parse(msg.data).colors;
+		var elem = document.getElementById('color_list');
+		var frag = document.createDocumentFragment();
+		let flag =  document.getElementById("flag").value;
+		elem.innerHTML = ''; 
+		colorlen = colors.length;
+		for(var i = 0; i < colors.length; i++) {
+			console.log(rgbToHex(colors[i][0], colors[i][1], colors[i][2]))
+			var li = document.createElement('li');
+			var input = document.createElement('input');
+			input.setAttribute("type", "color");
+			input.value = rgbToHex(colors[i][2], colors[i][1], colors[i][0]);
+			colors123.push(colors[i]) 
+			// if (flag == 0){
+			// 	input.value = rgbToHex(colors[i][0], colors[i][1], colors[i][2]);
[…]

### 2022-01-15 job/networkTest/networkTest/services/obtainNet/src2/throughputmanagement.c

@@ -1,0 +1,250 @@
+// ----------------------------------------------------------------------------------
+// Copyright (c) Microsoft. All rights reserved.
+// Licensed under the MIT license. See LICENSE file in the project root for full license information.
+// Author: Shihua (Simon) Xiao, sixiao@microsoft.com
+// ----------------------------------------------------------------------------------
+
+#include "throughputmanagement.h"
+
+void check_bandwidth_limit(struct ntttcp_test_endpoint *tep)
+{
+	/*
+	   Return immediately in the case of:
+	    a) this is receiver (we don't limit receiver);
+	    b) this is sender, but user did not specify the bandwidth limit.
+	*/
+	if ( (tep->endpoint_role == ROLE_RECEIVER) || (tep->test->bandwidth_limit == 0) )
+		return;
+
+	struct timeval this_check_time;
+	double test_time_elapsed;
+	ulong current_throughput;
+	uint n = 0;
+
+	gettimeofday(&this_check_time, NULL);
+	test_time_elapsed = get_time_diff(&this_check_time, &tep->start_time);
+
+	for (n = 0; n < tep->total_threads; n++) {
+		/* No need to check the current sc is the sync_thread or not,
+		   because sender does not have a delegated thread for sync */
+
+		current_throughput = (tep->client_streams[n]->total_bytes_transferred) / test_time_elapsed;
+		if (current_throughput > tep->client_streams[n]->sc_bandwidth_limit_bytes)
+			tep->client_streams[n]->hold_on = true;
+		else
+			tep->client_streams[n]->hold_on = false;
+	}
+}
+
+struct report_segment report_real_time_throughput(struct ntttcp_test_endpoint *tep,
+						  struct report_segment last_checkpoint,
+						  uint total_test_threads)
+{
+	struct report_segment this_checkpoint;
+
+	uint64_t this_total_bytes = 0;
+	uint64_t last_total_bytes = last_checkpoint.bytes;
+	uint64_t total_bytes = 0;
+
+	struct timeval this_check_time;
+	struct timeval last_check_time = last_checkpoint.time;
+	double test_time = 0;
+	uint n = 0;
+
+	for (n = 0; n < total_test_threads; n++) {
+		if (tep->test->client_role == true )
+			this_total_bytes += tep->client_streams[n]->total_bytes_transferred;
+		else
[…]

### 2022-01-15 job/networkTest/networkTest/services/obtainNet/src2/throughputmanagement.h

@@ -1,0 +1,24 @@
+// ----------------------------------------------------------------------------------
+// Copyright (c) Microsoft. All rights reserved.
+// Licensed under the MIT license. See LICENSE file in the project root for full license information.
+// Author: Shihua (Simon) Xiao, sixiao@microsoft.com
+// ----------------------------------------------------------------------------------
+
+#define _GNU_SOURCE
+#include "endpointsync.h"
+
+#define SEC_TO_USEC			1000000
+#define THROUGHPUT_INTERVAL_POLLS	1000    /* report throughput in every 1000 test status polls */
+#define TEST_STATUS_POLL_INTERVAL_SEC	0.0005  /* each test status poll has 0.0005 sec */ 
+#define TEST_STATUS_POLL_INTERVAL_U_SEC	TEST_STATUS_POLL_INTERVAL_SEC * SEC_TO_USEC  /* the 500 micro-sec */
+#define THROUGHPUT_INTERVAL_SEC		TEST_STATUS_POLL_INTERVAL_SEC * THROUGHPUT_INTERVAL_POLLS /* 0.5 sec */
+#define THROUGHPUT_INTERVAL_U_SEC	THROUGHPUT_INTERVAL_SEC * SEC_TO_USEC        /* 500,000 micro-sec */
+
+struct report_segment
+{
+	double		interval_sec;
+	struct timeval	time;
+	uint64_t	bytes;
+};
+
+void run_ntttcp_throughput_management(struct ntttcp_test_endpoint *tep);

### 2022-01-15 job/ntttcp-for-linux-master/src/oscounter.h

@@ -1,0 +1,60 @@
+// ----------------------------------------------------------------------------------
+// Copyright (c) Microsoft. All rights reserved.
+// Licensed under the MIT license. See LICENSE file in the project root for full license information.
+// Author: Shihua (Simon) Xiao, sixiao@microsoft.com
+// ----------------------------------------------------------------------------------
+
+#define _GNU_SOURCE
+#include <ctype.h>
+#include <stdio.h>
+#include <time.h>
+#include <inttypes.h>
+#include <stdlib.h>
+#include <string.h>
+#include <errno.h>
+#include <stdbool.h>
+#include <sys/time.h>
+#include <sys/resource.h>
+#include "const.h"
+#include "logger.h"
+
+struct cpu_usage{
+	clock_t   clock;
+	double    time;
+	double    user_time;
+	double    system_time;
+};
+
+struct cpu_usage_from_proc_stat{
+	unsigned int nproc;
+	long long unsigned total_time;
+	long long unsigned user_time;
+	long long unsigned system_time;
+	long long unsigned idle_time;
+	long long unsigned iowait_time;
+	long long unsigned softirq_time;
+};
+
+struct tcp_retrans{
+	uint64_t  retrans_segs;
+	uint64_t  tcp_lost_retransmit;
+	uint64_t  tcp_syn_retrans;
+	uint64_t  tcp_fast_retrans;
+	uint64_t  tcp_forward_retrans;
+	uint64_t  tcp_slowStart_retrans;
+	uint64_t  tcp_retrans_fail;
+};
+
+void get_cpu_usage(struct cpu_usage *cu);
+void get_cpu_usage_from_proc_stat(struct cpu_usage_from_proc_stat *cups);
+uint64_t get_interrupts_from_proc_by_dev(char *dev_name);
+uint64_t get_single_value_from_os_file(char *if_name, char *tx_or_rx);
+
+double read_value_from_proc(char *file_name, char *key);
+uint64_t read_counter_from_proc(char *file_name, char *section, char *key);
+void get_tcp_retrans(struct tcp_retrans *tr);
+
+#define MAX(a,b) \
+	({ __typeof__ (a) _a = (a); \
+	__typeof__ (b) _b = (b); \
+	_a > _b ? _a : _b; })

### 2022-01-15 job/ntttcp-for-linux-master/src/parameter.h

@@ -1,0 +1,27 @@
+// ----------------------------------------------------------------------------------
+// Copyright (c) Microsoft. All rights reserved.
+// Licensed under the MIT license. See LICENSE file in the project root for full license information.
+// Author: Shihua (Simon) Xiao, sixiao@microsoft.com
+// ----------------------------------------------------------------------------------
+
+#define _GNU_SOURCE
+#include <stdio.h>
+#include <stdlib.h>
+#include <ctype.h>
+#include <string.h>
+#include <getopt.h>
+#include "util.h"
+
+enum {S_THREADS = 0, S_PROCESSOR, S_HOST, S_DONE};
+
+#define LO_SHOW_TCP_RETRANS	1
+#define LO_SHOW_NIC_PACKETS	2
+#define LO_SHOW_DEV_INTERRUPTS	3
+#define LO_FQ_RATE_LIMIT	4
+
+int parse_arguments(struct ntttcp_test *test, int argc, char **argv);
+int verify_args(struct ntttcp_test *test);
+
+void print_flags(struct ntttcp_test *test);
+void print_usage();
+void print_version();

### 2022-01-15 job/ntttcp-for-linux-master/src2/util.h

@@ -1,0 +1,106 @@
+// ----------------------------------------------------------------------------------
+// Copyright (c) Microsoft. All rights reserved.
+// Licensed under the MIT license. See LICENSE file in the project root for full license information.
+// Author: Shihua (Simon) Xiao, sixiao@microsoft.com
+// ----------------------------------------------------------------------------------
+
+#define __STDC_FORMAT_MACROS
+#pragma once
+
+#define _GNU_SOURCE
+#include <stdio.h>
+#include <stdlib.h>
+#include <ctype.h>
+#include <string.h>
+#include <unistd.h>
+#include <fcntl.h>
+#include <errno.h>
+#include <time.h>
+#include <math.h>
+#include <arpa/inet.h>
+#include <sys/types.h>
+#include <sys/socket.h>
+#include <sys/time.h>
+#include <sys/resource.h>
+#include "ntttcp.h"
+#include "oscounter.h"
+
+struct ntttcp_test_endpoint_thread_result{
+	bool	is_sync_thread;
+	/* raw data of counters collected before and after test run */
+	uint64_t	total_bytes;
+	double	actual_test_time;
+
+	/* fields can be calculated with above raw data */
+	double	KBps;
+	double	MBps;
+	double	mbps;
+};
+
+struct ntttcp_test_endpoint_results{
+	/* raw data of counters collected before and after test run */
+	uint64_t	total_bytes;
+	double	actual_test_time;
+	struct 	cpu_usage *init_cpu_usage;
+	struct 	cpu_usage *final_cpu_usage;
+	struct 	cpu_usage_from_proc_stat *init_cpu_ps;
+	struct 	cpu_usage_from_proc_stat *final_cpu_ps;
+	struct 	tcp_retrans *init_tcp_retrans;
+	struct 	tcp_retrans *final_tcp_retrans;
+	uint64_t	init_tx_packets;
+	uint64_t	init_rx_packets;
+	uint64_t	final_tx_packets;
+	uint64_t	final_rx_packets;
+	uint64_t	init_interrupts;
+	uint64_t	final_interrupts;
+
+	/*point to per-thread result*/
+	struct	ntttcp_test_endpoint_thread_result	**threads;
+
+	/* fields can be calculated with above raw data or read from system */
+	double	cpu_speed_mhz;
+	double	time_diff;
+	double	retrans_segments_per_sec;
[…]

### 2022-01-15 job/pingIcmp/iperf-packetloss/server.py

@@ -1,0 +1,8 @@
+import iperf3
+import numpy as np
+server = iperf3.Server()
+server.bind_address = '10.10.10.1'
+server.port = 6969
+server.verbose = False
+while True:
+	server.run()

### 2022-01-15 job/pingIcmp/iperf/services/utility/utility_service.py

@@ -1,0 +1,12 @@
+import requests
+import urllib.request
+import numpy as np
+
+
+class UtilityService:
+    def url_downloader(url):
+        response = requests.get(url)
+        return (response.headers['content-type'], response.content)
+            
+    def image_reader(url):
+            return urllib.request.urlopen(url).read()

### 2022-01-15 job/pingIcmp/warp17-1.8/warp17-1.8/api/xlate-gen/warp17_xlate_walker.py

@@ -1,0 +1,196 @@
+#
+# DO NOT ALTER OR REMOVE COPYRIGHT NOTICES OR THIS FILE HEADER
+#
+# Copyright (c) 2016, Juniper Networks, Inc. All rights reserved.
+#
+#
+# The contents of this file are subject to the terms of the BSD 3 clause
+# License (the "License"). You may not use this file except in compliance
+# with the License.
+#
+# You can obtain a copy of the license at
+# https://github.com/Juniper/warp17/blob/master/LICENSE.
+#
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions
+# are met:
+#
+# 1. Redistributions of source code must retain the above copyright notice,
+# this list of conditions and the following disclaimer.
+#
+# 2. Redistributions in binary form must reproduce the above copyright
+# notice, this list of conditions and the following disclaimer in the
+# documentation and/or other materials provided with the distribution.
+#
+# 3. Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from this
+# software without specific prior written permission.
+#
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
+# AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+# IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+# ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE
+# LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR
+# CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF
+# SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+# INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+# CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
[…]

### 2022-01-15 job/pingIcmp/warp17-1.8/warp17-1.8/inc/tpg_config.h

@@ -1,0 +1,396 @@
+/*
+ * DO NOT ALTER OR REMOVE COPYRIGHT NOTICES OR THIS FILE HEADER
+ *
+ * Copyright (c) 2016, Juniper Networks, Inc. All rights reserved.
+ *
+ *
+ * The contents of this file are subject to the terms of the BSD 3 clause
+ * License (the "License"). You may not use this file except in compliance
+ * with the License.
+ *
+ * You can obtain a copy of the license at
+ * https://github.com/Juniper/warp17/blob/master/LICENSE.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ * this list of conditions and the following disclaimer.
+ *
+ * 2. Redistributions in binary form must reproduce the above copyright
+ * notice, this list of conditions and the following disclaimer in the
+ * documentation and/or other materials provided with the distribution.
+ *
+ * 3. Neither the name of the copyright holder nor the names of its
+ * contributors may be used to endorse or promote products derived from this
+ * software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
+ * AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE
+ * LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR
+ * CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF
+ * SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
[…]

### 2022-01-15 job/pingIcmp/warp17-1.8/warp17-1.8/inc/tpg_trace_filter.h

@@ -1,0 +1,183 @@
+/*
+ * DO NOT ALTER OR REMOVE COPYRIGHT NOTICES OR THIS FILE HEADER
+ *
+ * Copyright (c) 2016, Juniper Networks, Inc. All rights reserved.
+ *
+ *
+ * The contents of this file are subject to the terms of the BSD 3 clause
+ * License (the "License"). You may not use this file except in compliance
+ * with the License.
+ *
+ * You can obtain a copy of the license at
+ * https://github.com/Juniper/warp17/blob/master/LICENSE.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ * this list of conditions and the following disclaimer.
+ *
+ * 2. Redistributions in binary form must reproduce the above copyright
+ * notice, this list of conditions and the following disclaimer in the
+ * documentation and/or other materials provided with the distribution.
+ *
+ * 3. Neither the name of the copyright holder nor the names of its
+ * contributors may be used to endorse or promote products derived from this
+ * software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
+ * AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE
+ * LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR
+ * CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF
+ * SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
[…]

### 2022-01-15 job/pingIcmp/warp17-1.8/warp17-1.8/ut/test_http_1_1.py

@@ -1,0 +1,269 @@
+#
+# DO NOT ALTER OR REMOVE COPYRIGHT NOTICES OR THIS FILE HEADER
+#
+# Copyright (c) 2016, Juniper Networks, Inc. All rights reserved.
+#
+#
+# The contents of this file are subject to the terms of the BSD 3 clause
+# License (the "License"). You may not use this file except in compliance
+# with the License.
+#
+# You can obtain a copy of the license at
+# https://github.com/Juniper/warp17/blob/master/LICENSE.
+#
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions
+# are met:
+#
+# 1. Redistributions of source code must retain the above copyright notice,
+# this list of conditions and the following disclaimer.
+#
+# 2. Redistributions in binary form must reproduce the above copyright
+# notice, this list of conditions and the following disclaimer in the
+# documentation and/or other materials provided with the distribution.
+#
+# 3. Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from this
+# software without specific prior written permission.
+#
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
+# AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+# IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+# ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE
+# LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR
+# CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF
+# SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+# INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+# CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
[…]

### 2022-01-15 job/test/folders/pingIcmp/traceroute/traceroute.c

@@ -1,0 +1,977 @@
+/*	$OpenBSD: traceroute.c,v 1.162 2019/08/28 20:03:51 deraadt Exp $	*/
+/*	$NetBSD: traceroute.c,v 1.10 1995/05/21 15:50:45 mycroft Exp $	*/
+
+/*
+ * Copyright (C) 1995, 1996, 1997, and 1998 WIDE Project.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ * 3. Neither the name of the project nor the names of its contributors
+ *    may be used to endorse or promote products derived from this software
+ *    without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE PROJECT AND CONTRIBUTORS ``AS IS'' AND
+ * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED.  IN NO EVENT SHALL THE PROJECT OR CONTRIBUTORS BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+ * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+ * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+ * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+ * SUCH DAMAGE.
+ */
+
+/*-
+ * Copyright (c) 1990, 1993
[…]

### 2022-01-15 job/test/test/test1/ping1.cpp

@@ -1,0 +1,265 @@
+// C program to Implement Ping 
+
+// compile as -o ping 
+// run as sudo ./ping <hostname> 
+
+#include <stdio.h> 
+#include <sys/types.h> 
+#include <sys/socket.h> 
+#include <netinet/in.h> 
+#include <arpa/inet.h> 
+#include <netdb.h> 
+#include <unistd.h> 
+#include <string.h> 
+#include <stdlib.h> 
+#include <netinet/ip_icmp.h> 
+#include <time.h> 
+#include <fcntl.h> 
+#include <signal.h> 
+#include <time.h> 
+
+// Define the Packet Constants 
+// ping packet size 
+#define PING_PKT_S 64 
+
+// Automatic port number 
+#define PORT_NO 0 
+
+// Automatic port number 
+#define PING_SLEEP_RATE 1000000  
+
+// Gives the timeout delay for receiving packets 
+// in seconds 
+#define RECV_TIMEOUT 1 
+
+// Define the Ping Loop 
+int pingloop=1; 
+
+
+// ping packet structure 
+struct ping_pkt 
+{ 
+	struct icmphdr hdr; 
+	char msg[PING_PKT_S-sizeof(struct icmphdr)]; 
+}; 
+
+// Calculating the Check Sum 
+unsigned short checksum(void *b, int len) 
+{ unsigned short *buf = b; 
+	unsigned int sum=0; 
+	unsigned short result; 
+
+	for ( sum = 0; len > 1; len -= 2 ) 
+		sum += *buf++; 
+	if ( len == 1 ) 
+		sum += *(unsigned char*)buf; 
+	sum = (sum >> 16) + (sum & 0xFFFF); 
+	sum += (sum >> 16); 
+	result = ~sum; 
+	return result; 
+} 
+
+
+// Interrupt handler 
+void intHandler(int dummy) 
+{ 
+	pingloop=0; 
+} 
+
+// Performs a DNS lookup 
+char *dns_lookup(char *addr_host, struct sockaddr_in *addr_con) 
+{ 
+	printf("\n Resolving DNS..\n "); 
+	struct hostent *host_entity; 
+	char *ip=(char*)malloc(NI_MAXHOST*sizeof(char)); 
+	int i; 
+
+	if ((host_entity = gethostbyname(addr_host)) == NULL) 
+	{ 
[…]

### 2022-01-26 Journal1/paper2TNSM/pr.tex
add reviewr and bit change the pdf

--- 2021-11-27 Journal1/paper1TNSM/pr.tex
@@
 \section{Introduction} 
-One of the fifth-generation goals of the wireless cellular networks  is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services.
-Network slicing is the best solution for this aim.
-Network slicing can support the heterogeneity of services by allocating different resources to each slice serving specific services to guarantee QoS, and isolating each service from the other services.
-A network slice is an end-to-end logical network that offers services with specific needs.  
-Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
+To achieve a desired level of quality-of-service (quality, delay, power, etc.) for different services and isolate each service from the other services, network slicing is the best solution for 5G wireless cellular networks.
 Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections.
@@
 Each type of service requires a particular slice of network based on its QoS.
-eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and throughput coverage.
-URLLC requires low latency  and high reliability. URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
-mMTC consists of a vast number of low power internet of things (IoT) devices transmitting small payloads to a typical receiver.
-In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices
+The eMBB service fulfills the demand for high capacity and throughput.
+The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency.
+mMTC is comprised of many low-power internet of things (IoT) devices that transmit small payloads to a typical receiver, including sensors for sensing, metering, and monitoring
 \cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.
 
-Recently, RAN virtualization receives significant attention from industry and academia since it has remarkable benefits that increase flexibility and reduce CAPEX and OPEX and allow operators to add new capabilities to the network more quickly.
-In addition to RAN virtualization, openness and RAN intelligence are two pillars that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems.
+Openness and RAN intelligence are two pillars that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems.
 The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
-CRAN divides RAN into two parts, radio remote head (RRH) and baseband unit (BBU).
+RAN virtualization has remarkable benefits that increase flexibility, reduce CAPEX and OPEX, and allow operators to add new capabilities to the network more quickly.
+CRAN divides RAN into two parts: radio remote head (RRH) and baseband unit (BBU).
 Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
-Unlike the previous generation of RAN that divides RAN into two parts, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU). 
-O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC.
-In addition, the O-CU contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
-O-DU and O-CU are connected via open and well-defined interface $F_1$.
+Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+
+O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
+In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
+O-DU and O-CU are connected via an open and well-defined interface $F_1$.
 Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
-The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
-RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
-One of the necessities of the new generation of wireless networks is its intelligence.
-Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques.
-The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time, implement the algorithms for network intelligence
+The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. 
+Based on the requirement of an intelligent wireless network for the next generation of RAN systems, O-RAN offers machine learning techniques.
+The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real-Time, implement the algorithms for network intelligence
 \cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.

### 2022-01-28 Journal1/paper2TNSM/pr.tex
add paper

@@
 \section{Introduction} 
-To achieve a desired level of quality-of-service (quality, delay, power, etc.) for different services and isolate each service from the other services, network slicing is the best solution for 5G wireless cellular networks.
-Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections.
-5G wireless systems have talked about supporting three generic services in recent years, namely, enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services.
-Each type of service requires a particular slice of network based on its QoS.
+To achieve the desired level of QoS (quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks.
+There are several implementations of network slicing, including core slicing, RAN slicing, and both.
+Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
+Depending on QoS, each service requires its own slice of the network.
 The eMBB service fulfills the demand for high capacity and throughput.
@@
 
-Openness and RAN intelligence are two pillars that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems.
-The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
-RAN virtualization has remarkable benefits that increase flexibility, reduce CAPEX and OPEX, and allow operators to add new capabilities to the network more quickly.
-CRAN divides RAN into two parts: radio remote head (RRH) and baseband unit (BBU).
+O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
+O-RAN was developed as a result of integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
+With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly.
+The CRAN divides the radio remote head (RRH) and baseband unit (BBU) into two major parts.
 Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
@@
 The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. 
-Based on the requirement of an intelligent wireless network for the next generation of RAN systems, O-RAN offers machine learning techniques.
-The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real-Time, implement the algorithms for network intelligence
+O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
+The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence
 \cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
@@
 Virtual network functions (VNF) are system function blocks in NFV systems.
-This technology improves the system performance in the fifth generation of telecommunication networks.
-The key idea of the implementation of NFV is to decouple software from physical hardware, dynamic scaling, and the deployment of flexible network functions.
-The NFV technology offers to execute VNFs as virtual machines or containers on  cloud environment \cite{mijumbi2015network, luo2020online}.
-As a result, some O-RAN components that include user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are virtualized and implemented as a VNF that can be run as virtual machines (VMs) or containers.
+The NFV technology offers to execute VNFs as virtual machines or containers on a cloud environment \cite{mijumbi2015network, luo2020online}.
+As a result, some O-RAN components, such as user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are being virtualized and implemented as VNFs that can be run as virtual machines (VMs) or containers.
+
+To achieve the specific QoS for eMBB, URLLC, and mMTC, this study optimizes the allocation of baseband resources, including power allocation, PRB allocation, O-Rus association, and VNF activation to create an isolated network slicing outline.
 \subsection{Related Works}
@@
 In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered.
-The process of allocating network resources to users is discussed.
 The network slicing scheme includes a higher level and the lower level.
 The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity.
-Also, in the lower level, the allocation of power and physical resource blocks (PRB) is performed.
-In \cite{xiang2020realization}, network slicing in the radio section is considered for fog RAN (F-RAN) system, in which, two network slices are set for hotspots and vehicle scenarios with related infrastructure.
+Also, the allocation of power and physical resource blocks (PRB) is performed in the lower level.
+In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it.
 In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).
-Also, the problem of resource allocation is considered.
-Moreover, the paper faces the challenge of RAN slicing.
-The problem involves designing and managing multiple slices in the shared infrastructure efficiently while guaranteeing each slice's service level agreement (SLA).
 
 Multiplexing eMBB and URLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
-In \cite{setayesh2020joint,yang2020should}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
+In \cite{setayesh2020joint,yang2020should,saggese2021power}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
 In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
- In \cite{saggese2021power}, the problem of power minimization for URLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
  In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and URLLC services.
@@
 
-Virtualization technique for RAN and core is one of the exciting topics.  
-In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
+In \cite{SystemCostMinimization,guo2016exploiting}, the authors address the issue of beamforming and VMs activation (using virtualization) in a C-RAN system with limited fronthaul capacity. 
 This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
-Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
+Also, transmission and processing delays are modeled based on M/M/1 queueing theory to guarantee UE delays.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
+
 In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
@@
 \subsection{Main Contributions}
-The purpose of this study is to optimize baseband resource allocation i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+The purpose of this study is to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
 Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN system.
-The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presents of the three generic service types introduced in 5G using RAN slicing.
-In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
+The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
+In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follows:
 \begin{itemize}
-\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and URLLC.
+\item This paper depicts a network slicing model for three different services introduced in 5G, i.e., eMBB, mMTC, and URLLC.
 The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
-We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
+We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for different types of services with specific QoS. 
 \item The desired QoS conditions such as delay and throughput are considered for different types of services.
-We formulate the end-to-end mean delay of the system based on the number of activated VNFs and  user throughput.
-We consider the limited fronthaul capacity and obtain the power and the capacity of each O-RU. We model the interference of neighboring O-RU and formulate the actual throughput
-for different types of services. We also model the throughput of URLLC and mMTC based on their short packet transmission.
+We formulate the end-to-end processing delay of the system based on the number of activated VNFs and user throughput.
+Assuming a limited fronthaul capacity, we calculate the power and capacity of each O-RU.
+We model the interference of neighboring O-RUs and formulate the actual throughput for different service types.
+Based on the short packet transmission of URLLC and mMTC, we also model their throughput.
 \item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
@@
 \subsection{System Model}
-There are three service types including mMTC, eMBB, and URLLC, which support different applications.
-There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and URLLC service types, respectively and we have $S = S_1 + S_2 + S_3$.
+There are three service types including eMBB, URLLC, and mMTC which support different applications.
+There are $S_1$, $S_2$ and $S_3$ different applications for the eMBB, URLLC, and mMTC service types, respectively and we have $S = S_1 + S_2 + S_3$.
 %{\color{red} explain pre-allocated more}

### 2022-01-29 Journal1/paper2TNSM/pr.tex
add latex

@@
 \section{Introduction} 
-To achieve the desired level of QoS (quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks.
+\textcolor{blue}{To achieve the desired level of QoS (quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks.
 There are several implementations of network slicing, including core slicing, RAN slicing, and both.
@@
 \cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.
-
-O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
+}
+
+\textcolor{blue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
 O-RAN was developed as a result of integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
@@
 Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
-Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).}
 
@@
 
-To achieve the specific QoS for eMBB, URLLC, and mMTC, this study optimizes the allocation of baseband resources, including power allocation, PRB allocation, O-Rus association, and VNF activation to create an isolated network slicing outline.
+\textcolor{blue}{In order to achieve the specific QoS for eMBB, URLLC, and mMTC, this study optimizes the allocation of baseband resources, including power allocation, PRB allocation, O-Rus association, and VNF activation to create an isolated network slicing outline.}
 \subsection{Related Works}
@@
 Afterward, we obtain the formula to attain the optimal number of VNFs.
-\begin{lemma}
+\begin{lemma}\label{lemma1}
 The optimal number of VNFs in each slice s can be achieved by the 
@@
 Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
- The first one is a baseline scheme, which uses random PRB allocation.
-The association of O-RU is carried out based on distance.
-Also, the number of activated VNFs for each slice is fixed.
-The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method.
-The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}.
-In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels and the channel distance.
-\vspace*{-2em}
+\textcolor{red}{ The first one is a baseline scheme, which uses random PRB allocation. 
+So, the allocation of PRB  to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
+Also, the association of O-RU is carried out based on distance.
+It means that each UE is assigned to the nearest O-RU.
+The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
+After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is achieved from the lemma \eqref{lemma1}.
+ The second one is similar to the fixed BBU capacity and
+dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic}.
+We assume here that the capacity of the O-DU (which is similar to BBU in the FBDR) is as large as the capacity of our fronthaul link so that we can use this method for our system model.
+In this method, PRB and power are dynamically allocated.
+The number of VNFs is obtained from the simulation.
+The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm \ref{alg1} (GAA algorithm ) for O-RU assignment.}
+\vspace*{-1em}
 \subsection{Feasible Region}\label{fr}

### 2022-01-31 Journal1/paper2TNSM/pr.tex
reach reviewer 2 questions

@@
 The propagation delay is the time takes for a signal to reach its destination.
-It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the capacity of the link).
+It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the propagation speed of the link).
 The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
@@
 Moreover, it can formulated as 
-$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the sum-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean arrival data rate of each link.
+$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the data-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean packet size transmitting in each link.
 So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
-In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we ignore the other two delays for simplification;
+
+\textcolor{magenta}{ We can reduce the complexity of our delay calculation and enhance the performance of our solution by eliminating propagation and transmission delays to focus on obtaining the optimal number of VNF.
+In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed for simplification;
+Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
+Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}.
+so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $.
+Since, fronhaul, midhaul and backhaul are fiber optics, c is the speed of light.
+Also, due to the use of the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced.
+But we do not focus on edge processing in this paper.
+In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$.
+So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$.
+As a result, the $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$.
+for eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.
+}
+
 So, we assume that the total delay is approximate to the processing delay ($T^{\text{\text{tot}}} \approx T^{\text{proc}}$). 
@@
 %\end{equation}
+
+\textcolor{violet}{Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard.
+Solving the problem is complex.
+To solve the problem by inspiring Stackelberg, we reformulate the equation \eqref{c16} to reduce one of the variables ($M_s$) that can be solved after obtaining the rate of UEs ($M_s$ is similar to followers in Stackelberg Competition and power and PRB assignment is similar to leader).
+So, the new problem has two variables of power and PRB assignment.
+This new problem is convex by relaxing the binary variable (PRB assignment) and can be solved by the Lagrangian function.
+After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.}
+
 In the following, we define a lemma to find the upper and lower bound for the optimal number of VNFs based on the achievable rates.
@@
 The number of VNFs is obtained from the simulation.
-The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm \ref{alg1} (GAA algorithm ) for O-RU assignment.}
+The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm \ref{alg1} (GAA algorithm ) for O-RU assignment.
+The figures in \cite{lee2018dynamic} show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area.
+We will also see that our proposed algorithm performs better than FBDR in the next subsection.
+}
 \vspace*{-1em}

### 2022-02-03 Journal1/paper2TNSM/pr.tex
add some questions

@@
 %Here, it is assumed that each UE is served by the nearest o-RU
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
+Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ \textcolor{teal}{is the sum of the power of interfering signals and quantization noise represented as follow}
 %{\color{red} use paranthesis in the following equation to clear +}
@@
 
-To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
+\textcolor{teal}{To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
 \begin{equation}\label{eq2}
-y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}\mathfrak{y}^k_{r,u(s,i)}+ z_{u(s,i)},
-\end{equation}
-%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}
-where $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$, $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
+y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}{x_Q}^k_{r,u(s,i)}+ z_{u(s,i)},
+\end{equation}
+}
+%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
+\textcolor{teal}{where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
+Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
+Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression that is shown in figure \ref{fig:pq}. 
 In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization Gaussian noise 
-($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.
-
+($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.}
+\begin{figure}
+  \centering 
+  \captionsetup{justification=centering}
+    \includegraphics[scale = 0.45]{Qdiag.png}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Precoding and Quantization of Signal}
+  \label{fig:pq}
+\end{figure}
 The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as
@@
 %Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
+
+\textcolor{olive}{The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent.
+Moreover, the impact of a single packet on the system's performance is minimal.
+Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process.
+We also suppose that service times are exponentially distributed.
+In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services.
+Because in this system, it is also assumed that the users of a service have the same priority, so their sent packages also have an equal priority over each other.
+Because the services are isolated, this priority within a service does not invalidate the queue assumption.
+Also, one service's priority over another can be higher, affecting the optimization.}
 \subsection{VNF Power}
@@
 Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
-\vspace*{-1.7em}
+\vspace*{-1em}
 \section{Proposed Algorithm}\label{proAlg}

### 2022-02-05 Journal1/paper2TNSM/pr.tex
reviewr 2

@@
 \usepackage{textcomp}
-\usepackage{xcolor}
+\usepackage[dvipsnames]{xcolor}
 \usepackage{algorithm}
@@
 \section{Introduction} 
+\subsection{State Of The Arts}
 \textcolor{blue}{To achieve the desired level of QoS (quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks.
@@
 
+\textcolor{OrangeRed}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS.
+We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}
+
 \textcolor{blue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
@@
 \textcolor{blue}{In order to achieve the specific QoS for eMBB, URLLC, and mMTC, this study optimizes the allocation of baseband resources, including power allocation, PRB allocation, O-Rus association, and VNF activation to create an isolated network slicing outline.}
-\subsection{Related Works}
+\subsection{Related Literature}
 The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
@@
 You  define on variable here.)
-
+\textcolor{NavyBlue}{Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
+The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.}
 \textcolor{teal}{To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
@@
 Moreover, $\phi_s^u$, $\phi_s^c$, and $\phi_s^d$ are the fixed cost of energy in UPF, O-CU, and O-DU, respectively.
+
+\textcolor{gray}{A significant issue facing the industry is reducing energy consumption.
+Data centers are one of the most energy-consuming.
+As a result, restrictions are placed on data centers' energy, including virtual machines (VMs).
+So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers.
+So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).}
 \subsection{Problem Statement}
@@
 & 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\
+& \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
@@
 & \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
-& \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
@@
 Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
-\vspace*{-1em}
+%\vspace*{-1em}
 \section{Proposed Algorithm}\label{proAlg}
@@
 The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
-After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is achieved from the lemma \eqref{lemma1}.
- The second one is similar to the fixed BBU capacity and
+After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is achieved from the lemma \eqref{lemma1}.}
+\textcolor{brown}{ The second one is similar to the fixed BBU capacity and
 dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic}.
+In this work, we have services with different QoS that contain UEs, which is similar to tenants with a different QoS.
+So, we used an algorithm similar to FBDR adapted to our conditions for comparison.
  We assume here that the capacity of the O-DU (which is similar to BBU in the FBDR) is as large as the capacity of our fronthaul link so that we can use this method for our system model.

### 2022-02-07 Journal1/paper2TNSM/pr.tex
Add scheduling to tnsm

@@
 %Here, it is assumed that each UE is served by the nearest o-RU
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ \textcolor{teal}{is the sum of the power of interfering signals and quantization noise represented as follow}
+Also, $BN_0$ denotes the power of Gaussian additive noise.
+\textcolor{Sepia}{UEs in different O-RUs can be assigned to different PRBs. As a result, a UE in O-RU $r$ using PRB $k$ may experience interference from other O-RUs in the set of $r' \in R -r$.
+Network Slicing methods significantly reduce inter-service interference but do not eliminate it at all.
+There are some techniques to minimize inter-slice interference.
+One of these techniques is to have two-time scale scheduling.
+The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out.
+Since there are limited resources, inter-service interference cannot be eliminated entirely.
+The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.}
+We have two types of interference, the first one is between slices (inter-slice) and the second one is between UEs in each slices or services (intra-slice) that is shown in figure \ref{fig:intf}.
+\begin{figure}
+  \centering 
+  \captionsetup{justification=centering}
+    \includegraphics[scale = 0.40]{Interference.png}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Type of Interference Signal}
+  \label{fig:intf}
+\end{figure}
+\textcolor{teal}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}
 %{\color{red} use paranthesis in the following equation to clear +}
@@
 Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
+\subsubsection{PRB Scheduling}
+\textcolor{Sepia}{  In this section, we study the problem of PRB scheduling to illuminate the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
+We need to have an algorithm to illuminate the inter-slice interference before solving the problem \ref{problem}.
+Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed.
+So, the assignment of PRB can be completed in two steps to remove inter-slice interference and isolate the slices.
+Firstly we assign PRBs to slices.
+Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm \ref{proAlg}.
+Firstly, we need to find the average PRB number used by UEs in each service.
+Since mMTC and URLLC transmit a short packet, each UE in mMTC and URLLC requires 1 PRB.
+So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs.
+For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s.
+Also, $\mathcal{R}_{{s}}^{min}$ is the minimum data rate of each UE in slice s (eMBB slice).
+So, the average number of PRB that slice s with $U_s$ UEs requires is $K_s = U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}$.
+$K_s$ is the average number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
+The problem can be written as follow
+\begin{subequations}\label{prob:prb}
+\begin{alignat}{4}
+\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s \bar{\mathcal{R}}_{{s}}^{min}\log(\frac{\bar{K_s}}{K_s}) \ \\
+\text{subject to} \quad  & \sum_s{\bar{K_s}} \leq K
+ \label{prb0} \\
+& \bar{K_s}  \leq K_s  \quad \forall s, ,\label{prb1} 
+\end{alignat}
+\label{constraints}
+\end{subequations}
+}
 %\vspace*{-1em}

### 2022-02-08 Journal1/paper2TNSM/pr.tex
Add other questions

@@
 
-\textcolor{magenta}{ We can reduce the complexity of our delay calculation and enhance the performance of our solution by eliminating propagation and transmission delays to focus on obtaining the optimal number of VNF.
+\textcolor{magenta}{Considering propagation and transmission delays is straightforward to add to the system, but we did not consider them for better presentation and focus on obtaining the optimal number of VNF.
 In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed for simplification;
+The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority (Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU).
+Therefore, different routes are added to the system to solve the routing problem, but we do not consider it since it changes the model and does not fit in this model.
+So, the connection between O-RUs to O-DUs is fixed and transparent.
+As a result, the propagation delay is fixed and does not affect the optimization problem.
+The following is a brief calculation of propagation delay.
 Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
@@
 so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $.
-Since, fronhaul, midhaul and backhaul are fiber optics, c is the speed of light.
-Also, due to the use of the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced.
-But we do not focus on edge processing in this paper.
+Since fronhaul, midhaul, and backhaul are fiber optics, c is the speed of light.
+Also, due to the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced.
+But we also do not focus on edge processing in this paper.
+The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has such a small amount.
 In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$.
@@
 Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process.
-We also suppose that service times are exponentially distributed.
-In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services.
-Because in this system, it is also assumed that the users of a service have the same priority, so their sent packages also have an equal priority over each other.
-Because the services are isolated, this priority within a service does not invalidate the queue assumption.
-Also, one service's priority over another can be higher, affecting the optimization.}
+The system's clock is constant, and the size of the tasks is not fixed.
+So, we suppose that service times are exponentially distributed \cite{QS}.
+In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services, not between UEs of one service.
+Because we assumed that the UEs of a service have the same priority, their sent packets also have an equal priority.
+Also, the services are isolated, and this priority does not invalidate the queue assumption.
+Furthermore, one service's priority over another can be higher, affecting the whole optimization and not queue formulation since the UEs in each service have the same priority, and each service has its processing delay independent of other services.}
 \subsection{VNF Power}
@@
 So, a lower bound for \eqref{eq11} is given that is a concave function.
-\begin{subequations}
+\begin{subequations}\label{lb1}
 \begin{alignat}{4}
@@
 
-\textcolor{violet}{Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard.
+\textcolor{violet}{Although the problem is feasible and it has feasibility points that are discussed in subsection \ref{fr}, it is not convex and difficult to solve.
+Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard.
 Solving the problem is complex.
@@
 So, the new problem has two variables of power and PRB assignment.
-This new problem is convex by relaxing the binary variable (PRB assignment) and can be solved by the Lagrangian function.
+This new problem is convex by relaxing the binary variable (PRB assignment) and estimating the lower bounds in equation \eqref{lb1} because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
 After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.}
@@
 Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
-We consider 25 PRBs are used in the network and the packet size is equal to 20 bytes.
+We consider 25 PRBs are used in the network and the packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes.
 The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 

### 2022-02-09 Journal1/Response (21-10-2019)/Response.tex
add papers and solution

%\documentclass[12pt, draftclsnofoot, onecolumn,letterpaper]{IEEEtran}
\documentclass[12pt, letterpaper]{article}
%\documentclass[12pt, letterpaper]{IEEEtran}
\usepackage{ multirow }
\usepackage{longtable}
\usepackage{geometry}
\usepackage{ragged2e}
\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{lipsum}
\usepackage{makeidx}
\usepackage{enumerate}
\usepackage{color}
\usepackage{refstyle}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{nomencl}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{anysize}
\usepackage{float}
\usepackage{epstopdf}
\usepackage{threeparttable}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{adjustbox}
%\usepackage[none]{hyphenat}
%\usepackage{float}

%\usepackage{fixltx2e}
\usepackage{amsmath, amssymb, upgreek, amsthm}
\usepackage{graphicx}
\usepackage{tikz}
\geometry{letterpaper, left=20mm, right=20mm, top=20mm, bottom=20mm}
\usetikzlibrary{patterns} % LATEX and plain TEX when using Tik Z
\allowdisplaybreaks
\setlength{\textfloatsep}{2ex}
\usepackage{array}
\usepackage{enumitem}
\setlength{\parindent}{1 em}
\setlength{\parskip}{0.5 em}
\renewcommand{\baselinestretch}{1.25}
\def\dsd{d_\text{SD}}
\def\Rcoop{R_\text{Coop}}
\def\rhd{R_\text{HD}}
\def\rsd{R_\text{SD}}
\def\rsh{R_\text{SH}}
\def\Pcoops{\mathcal{P}^\text{Succ}_\text{Coop}}
\def\dsh{d_\text{SH}}
\def\dhd{d_\text{HD}}
\def\psibar{\overline{\mathcal{P}}^\text{Succ}_{i}}
\def\psbara{\overline{\mathcal{P}}^\text{Succ}_{1}}
\def\psbarb{\overline{\mathcal{P}}^\text{Succ}_{2}}
\def\psbarc{\overline{\mathcal{P}}^\text{Succ}_{3}}
\def\psbard{\overline{\mathcal{P}}^\text{Succ}_{4}}
\def\psbare{\overline{\mathcal{P}}^\text{Succ}_{5}}
\def\Ri{R_{i}}
\def\Ps{\mathcal{P}^\text{Succ}_\text{Direct}}
\def\frk{\mathrm{f}_{r_k}(r)}
\def\Rcoopj{R_\text{coop}^j}
\title{\bf \vspace*{-4ex} Statement of Responses to the Editor and the Reviewers of Paper-TCOM-TPS-19-0363.R1 \\[-6ex]}
\date{}

\begin{document}
%\vspace*{-10ex}
%\sloppy
\maketitle
We would like to thank the editor and reviewers for their comments on our manuscript.
We hope that the modifications that we have made to the manuscript, and the responses that we have
provided herein will alleviate the reviewers' concerns. Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
\\ [-3.ex]
% % % % % % % % % % % % % % % Editor % % % % % % % % % % % % % % % % % % % %

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Editor} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``In particular, in agreement with the reviewers, the paper would greatly benefit from a clearer focus with respect to the applicability of the discussed model specifically for nanomachines. What are the intended nanomachines? How will they be realized and what is their applicability within a synaptic cleft? How will they be implanted? A revised focus is suggested if sufficient clarity in these directions cannot be reached.''\\
\hline
\end{longtable}

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the editor for his comment on our manuscript. According to the advances in nano-technology and nano-communications, different design strategies for intelligent nano-devices interfaced with the neuronal tissue were proposed in the literature. The proposed system model in this manuscript is based on one of them. We clarify more about this issue in the following. We refer to the following list of references in our explanation in this comment:

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.

[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.

[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.

[4] Mesiti, Fabio, and Ilangko Balasingham. ``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol. 31, no. 12, pp. 695-704, 2013.

[5] N. Rouach, E. Avignone, W. Même, A. Koulakoff, L. Venance, F. Blomstrand, and C. Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol. 94, no. 7-8, pp. 457-475, 2002.

[6] J. Hjorth, K. T. Blackwell, and J. Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J. Neuroscience, vol. 29, no. 16, pp. 5276-5286, 2009.

[7] R. D. Traub, M. A. Whittington, E. H. Buhl, F. E. N. LeBeau, A. Bibbig, S. Boyd, H. Cross, and T. Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol. 42, no. 2, pp. 153-170, 2001.
\\
\hline
\end{longtable}

\clearpage
In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
stimulation with an array of 50 NW connections per neuron. The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations. We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.

\textbf{Gap Junction Interface [4]}:

With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells. Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity. In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted. This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.

\begin{figure}[H]
\centering
\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
\label{new_1}
\end{figure}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``I thank the authors for providing a modified paper. The authors have made changes in the previous system model that struck this reviewer as the biggest limitation of the paper. The novel described solution in Figure 1 does make more sense compared to the previous one.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for careful and thorough reading of this manuscript and for the thoughtful and positive comments and constructive suggestions, which helped us to improve the quality of this manuscript. We hope that the responses provided herein can alleviate the reviewer concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``However, the scaling problem arises now. The synaptic channel/cleft between \textbf{Tx} and \textbf{Rx} is very narrow (tens of nm). If the authors suggest nano-machines, e.g., as in the scenario shown in Figure 2 (c), both nano-machines are envisioned to co-locate in the cleft, 3 nm distant from the synaptic terminals. What is the size of nano-machines then? How realistic is that owing to the complexity of these nano-machines? Wouldn't it be much easier to consider artificial synapse instead?''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
According to the advances in nano-technology and nano-communications, different design strategies for intelligent nano-devices interfaced with the neuronal tissue were proposed in the literature. The proposed system model in this manuscript is based on one of them.
In the proposed system model, we need to consider the assumptions of real synapses since the real neurons play the role of \textbf{Tx} and \textbf{Rx} in the most of scenarios while in the artificial synapses, the assumptions are different.

About the scaling problem, the width of synaptic cleft is about tens of nm and in the worth case scenario where nano-machines are located in both terminals, 6 nm is required for SnM interfaces. Hence, there is sufficient room for nano-machines since they are much smaller than the neurons. In addition, some references in the literature discussed about the implementation of these interfaces.
We clarified about this issue in the following:

\clearpage
We refer to the following list of references in our explanation in this comment:

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.

[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.

[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.

[4] Mesiti, Fabio, and Ilangko Balasingham. ``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol. 31, no. 12, pp. 695-704, 2013.

[5] N. Rouach, E. Avignone, W. Même, A. Koulakoff, L. Venance, F. Blomstrand, and C. Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol. 94, no. 7-8, pp. 457-475, 2002.

[6] J. Hjorth, K. T. Blackwell, and J. Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J. Neuroscience, vol. 29, no. 16, pp. 5276-5286, 2009.

[7] R. D. Traub, M. A. Whittington, E. H. Buhl, F. E. N. LeBeau, A. Bibbig, S. Boyd, H. Cross, and T. Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol. 42, no. 2, pp. 153-170, 2001.
\\
\hline
\end{longtable}

\clearpage
In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
stimulation with an array of 50 NW connections per neuron. The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations. We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.

\textbf{Gap Junction Interface [4]}:

With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells. Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity. In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted. This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.

\begin{figure}[H]
\centering
\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
\label{new_1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!45}
\textbf{Reviewer 2} \\
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 1:} ``The paper has been improved according to the previous comments from this reviewer and only the following minor issues have remained.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for careful and thorough reading of this manuscript and
for the thoughtful comments and constructive suggestions, which help us to improve the quality of
this manuscript. We hope that the responses provided herein can alleviate the reviewer concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``In Introduction, page 5, ``We consider a neuro-spike communication channel between two neurons located in the motor cortex region of the brain where the information is encoded by spike time intervals.''.  Please provide a reference for this sentence.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Neural coding refers to the mapping from the stimulus to the configurations of the generated
spikes by neurons. Neurons employ the spike rate coding and temporal coding to transmit information via action potentials. As we explained in the manuscript, none of the papers in the literature proposed a model for neuro-spike communication channel in the motor cortex region when temporal modulations
are employed to convey information. However, there are some papers that assumed temporal modulations in the motor cortex region. We referred to one of these papers in the new manuscript based on the reviewer comment as
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
We consider a neuro-spike communication channel between two neurons located in the motor cortex region of the brain where the information is encoded by spike time intervals [30].
\\
\hline
\end{longtable}
The referred paper is
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[30] Hatsopoulos N, Geman S, Amarasingham A, Bienenstock E., ``At what time scale does the nervous system operate?'', Neurocomputing, vol. 1, no. 52, pp.25-29, 2003.
\\
\hline
\end{longtable}

\clearpage
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 3:} ``In System Model, the possibility of placing nano-machines in synapses located between motor cortex neurons must be proved. This action needs invasive surgeries, which cause further damage to the neurons.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
According to the advances in nano-technology and nano-communications, different design strategies
for intelligent nano-devices interfaced with the neuronal tissue were proposed in the literature. The
proposed system model in this manuscript is based on one of them. We clarify more about this issue in the following.
We refer to the following list of references in our explanation in this comment:

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.

[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.

[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.

[4] Mesiti, Fabio, and Ilangko Balasingham. ``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol. 31, no. 12, pp. 695-704, 2013.

[5] N. Rouach, E. Avignone, W. Même, A. Koulakoff, L. Venance, F. Blomstrand, and C. Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol. 94, no. 7-8, pp. 457-475, 2002.

[6] J. Hjorth, K. T. Blackwell, and J. Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J. Neuroscience, vol. 29, no. 16, pp. 5276-5286, 2009.

[7] R. D. Traub, M. A. Whittington, E. H. Buhl, F. E. N. LeBeau, A. Bibbig, S. Boyd, H. Cross, and T. Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol. 42, no. 2, pp. 153-170, 2001.
\\
\hline
\end{longtable}

\clearpage
In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
stimulation with an array of 50 NW connections per neuron. The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations. We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.

\textbf{Gap Junction Interface [4]}:

With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells. Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity. In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted. This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.

\begin{figure}[H]
\centering
\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
\label{new_1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!45}
\textbf{Reviewer 4} \\
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 1:} ``The description of  ``unhealthy neuron'' or ``neurons that have lost their ability to communicate'' and the nano-machines to connect them seems to provide a possible future application to the communication channel model proposed. What the manuscript is not fully analyzing in the opinion of this reviewer is exactly how the nano-machines could utilize this model from an engineering perspective. If this connection is not considered to be the focus and therefore was not researched, then the consideration should be made to remove the concept of nano-machines from the ``System Model'' section (and subsequent sections) and use it merely for motivating the model.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for careful and thorough reading of our manuscript and for
the thoughtful comments and constructive suggestions, which helped us to improve
the quality of this manuscript. We hope that the modifications that we have made to the manuscript, and the
responses that we have provided herein will alleviate the reviewer concerns.

In recent years, engineering applications of nano-technology have also been investigated with increasing interest
for the design of bio-inspired intelligent nano-devices or nano-machines connected in a network. In this manuscript, we considered the concept of nano-machines in the proposed system model according to the reported efforts to interface the neuron's body
with synthetic nano-scale materials in the literature. We provide a brief explanation in the following. We refer to the following list of references in our explanation in this comment:

\clearpage
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.

[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.

[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.

[4] Mesiti, Fabio, and Ilangko Balasingham. ``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol. 31, no. 12, pp. 695-704, 2013.

[5] N. Rouach, E. Avignone, W. Même, A. Koulakoff, L. Venance, F. Blomstrand, and C. Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol. 94, no. 7-8, pp. 457-475, 2002.

[6] J. Hjorth, K. T. Blackwell, and J. Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J. Neuroscience, vol. 29, no. 16, pp. 5276-5286, 2009.

[7] R. D. Traub, M. A. Whittington, E. H. Buhl, F. E. N. LeBeau, A. Bibbig, S. Boyd, H. Cross, and T. Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol. 42, no. 2, pp. 153-170, 2001.
\\
\hline
\end{longtable}

\clearpage
In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
stimulation with an array of 50 NW connections per neuron. The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations. We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.

\textbf{Gap Junction Interface [4]}:

With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells. Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity. In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted. This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.

\begin{figure}[H]
\centering
\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
\label{new_1}
\end{figure}

\end{document}

### 2022-02-09 Journal1/paper2TNSM/pr.tex
add papers and solution

@@
 The VNFs of O-DU, O-CU-UP, and UPF are interconnected, defined as the Service Function Chain (SFC) in the O-RAN system.
-
-Assume we have $K$ physical resource blocks (PRBs) in this system.
-All $K$ PRBs can be assigned to all UEs in each service.
 Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.
+
+%All $K$ PRBs can be assigned to all UEs in each service. 
+\textcolor{Sepia}{ Assume we have $K$ physical resource blocks (PRBs) in this system.
+Suppose each slice s consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
+Therefore, we have $\sum_s \bar{K}_s \leq K$.
+}
 In addition, there are $R$ multi-antenna O-RUs that are shared between slices.
@@
 Also, $BN_0$ denotes the power of Gaussian additive noise.
-\textcolor{Sepia}{UEs in different O-RUs can be assigned to different PRBs. As a result, a UE in O-RU $r$ using PRB $k$ may experience interference from other O-RUs in the set of $r' \in R -r$.
-Network Slicing methods significantly reduce inter-service interference but do not eliminate it at all.
-There are some techniques to minimize inter-slice interference.
+
+\textcolor{Sepia}{Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
+ r$.
+UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
+Network Slicing methods significantly reduce inter-service interference.
+There are some techniques to remove inter-slice interference.
 One of these techniques is to have two-time scale scheduling.
@@
 Since there are limited resources, inter-service interference cannot be eliminated entirely.
-The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.}
-We have two types of interference, the first one is between slices (inter-slice) and the second one is between UEs in each slices or services (intra-slice) that is shown in figure \ref{fig:intf}.
+The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.} In this paper, we assume that the PRB scheduling is performed.
+Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
 \begin{figure}
@@
 You  define on variable here.)
+\textcolor{Sepia}{Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.}
+
 \textcolor{NavyBlue}{Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
@@
 Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
-\subsubsection{PRB Scheduling}
-\textcolor{Sepia}{  In this section, we study the problem of PRB scheduling to illuminate the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
-We need to have an algorithm to illuminate the inter-slice interference before solving the problem \ref{problem}.
+\subsubsection{PRB Scheduling}\label{prb}
+\textcolor{Sepia}{ In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
+We need to have an algorithm to remove the inter-slice interference before solving the problem \ref{problem}.
 Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed.
@@
 Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm \ref{proAlg}.
+Suppose, $\mathcal{R}_{{s}}^{min}$, and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
 Firstly, we need to find the average PRB number used by UEs in each service.
@@
 For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s.
-Also, $\mathcal{R}_{{s}}^{min}$ is the minimum data rate of each UE in slice s (eMBB slice).
-So, the average number of PRB that slice s with $U_s$ UEs requires is $K_s = U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}$.
-$K_s$ is the average number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+(eMBB slice)
+So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$.
+$K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$.
+$K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).
 Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
@@
 \begin{alignat}{4}
-\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s \bar{\mathcal{R}}_{{s}}^{min}\log(\frac{\bar{K_s}}{K_s}) \ \\
+\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s K_s \ln(\bar{K_s}) \ \\
 \text{subject to} \quad  & \sum_s{\bar{K_s}} \leq K
  \label{prb0} \\
-& \bar{K_s}  \leq K_s  \quad \forall s, ,\label{prb1} 
+& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
+&  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3,\label{prb2}
 \end{alignat}
@@
 \end{subequations}
+We used logarithms to assign PRBs to all slices to make them equally fair \cite{marabissi2019highly}.
+Equation \eqref{prb0} illustrates that the sum of PRBs of slices can not exceed the maximum number of PRBs. 
+Equation \eqref{prb1}, restrict the number of PRBs of eMBB slices and \eqref{prb2}, limit the number of PRBs of URLLC and mMTC slices.
+By relaxing $\bar{K_s}$, the objective function and constraints become convex and can be solved using the Lagrangian function.
 }
+\subsection{Slice Management}
+\textcolor{RedViolet}{In this subsection, we want to study the management of slices. We want to talk about the creation, management, and deletion of slices.}
+
 %\vspace*{-1em}

### 2022-02-12 Journal1/Response (21-10-2019)/Response.tex
finish question and start write on latex

@@
 \def\Rcoopj{R_\text{coop}^j}
-\title{\bf \vspace*{-4ex} Statement of Responses to the Editor and the Reviewers of Paper-TCOM-TPS-19-0363.R1 \\[-6ex]}
+\title{\bf \vspace*{-4ex} Statement of Responses to the Editor and the Reviewers of Paper-TNSM \\[-6ex]}
 \date{}
@@
 \RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment1:} ``In particular, in agreement with the reviewers, the paper would greatly benefit from a clearer focus with respect to the applicability of the discussed model specifically for nanomachines.
-What are the intended nanomachines?
-How will they be realized and what is their applicability within a synaptic cleft?
-How will they be implanted?
-A revised focus is suggested if sufficient clarity in these directions cannot be reached.''\\
+\cellcolor{violet!15}
+\textbf{\noindent Comment1:} ``The paper has gone through three independent reviews and also checked by myself.
+The topic is interesting and there are merits.
+But there are some major concerns on the contribution, the assumption, the model derivation, and the experimental results.
+I hope the review comments are useful for further improving the quality of the paper.
+I'd therefore recommend the Resubmission''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-We would like to thank the editor for his comment on our manuscript.
-According to the advances in nano-technology and nano-communications, different design strategies for intelligent nano-devices interfaced with the neuronal tissue were proposed in the literature.
-The proposed system model in this manuscript is based on one of them.
-We clarify more about this issue in the following.
-We refer to the following list of references in our explanation in this comment:
+We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. We have utilized the comments to improve our paper and eliminate the problems.
 
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{green!10}
-[1] F.
+%\begin{longtable}{|p{0.975\textwidth}|}
+%\hline \hline
+%\RaggedRight
+%\cellcolor{green!10}
+%[1] F.
 Patolsky, B.
@@
 1100-1104, 2006.
-
-[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.
-
-[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.
-
-[4] Mesiti, Fabio, and Ilangko Balasingham.
-``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol.
-31, no.
-12, pp.
-695-704, 2013.
-
-[5] N.
-Rouach, E.
-Avignone, W.
-Même, A.
-Koulakoff, L.
-Venance, F.
-Blomstrand, and C.
-Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol.
-94, no.
-7-8, pp.
-457-475, 2002.
-
-[6] J.
-Hjorth, K.
-T.
-Blackwell, and J.
-Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J.
-Neuroscience, vol.
-29, no.
-16, pp.
-5276-5286, 2009.
-
-[7] R.
-D.
-Traub, M.
-A.
-Whittington, E.
-H.
-Buhl, F.
-E.
-N.
-LeBeau, A.
-Bibbig, S.
-Boyd, H.
-Cross, and T.
-Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol.
-42, no.
-2, pp.
-153-170, 2001.
-\\
-\hline
-\end{longtable}
-
-\clearpage
-In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
-stimulation with an array of 50 NW connections per neuron.
-The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
-Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
-Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations.
-We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.
-
-\textbf{Gap Junction Interface [4]}:
-
-With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells.
-Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity.
-In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted.
-This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
-\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
-\label{new_1}
-\end{figure}
+%\\
+%\hline
+%\end{longtable}
 
@@
 \RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment1:} ``I thank the authors for providing a modified paper.
-The authors have made changes in the previous system model that struck this reviewer as the biggest limitation of the paper.
-The novel described solution in Figure 1 does make more sense compared to the previous one.''\\
+\cellcolor{violet!15}
+\textbf{\noindent Comments to the Author} ``
+The paper proposes resolving the problem of resource allocation to network slices by using a new algorithm applied to the reformulation of the problem.
+The results seem promising but the paper has some issues.
+''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-We would like to thank the reviewer for careful and thorough reading of this manuscript and for the thoughtful and positive comments and constructive suggestions, which helped us to improve the quality of this manuscript.
-We hope that the responses provided herein can alleviate the reviewer concerns.
+We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can alleviate the reviewer's concerns.
+
+\noindent
+\begin{longtable}{|p{.975\textwidth}|}
+\hline \hline %\hline \hline \hline
+\Centering
+\cellcolor{gray!60}
+\textbf{Reviewer 1} \\
+\hline \hline %\hline \hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment1:} ``First, the structure of the paper makes it somewhat hard to follow and there are some mistakes in the text.
+A proofread is required before it can be accepted for publication.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+I have changed the paper's introduction and checked the text entirely according to this comment.
 

### 2022-02-12 Journal1/paper3TNSM/pr.tex
finish question and start write on latex

--- 2022-02-09 Journal1/paper2TNSM/pr.tex
@@
 Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-Depending on QoS, each service requires its own slice of the network.
+Depending on QoS, each service requires its slice of the network.
 The eMBB service fulfills the demand for high capacity and throughput.
 The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency.
-mMTC is comprised of many low-power internet of things (IoT) devices that transmit small payloads to a typical receiver, including sensors for sensing, metering, and monitoring
+mMTC comprises many low-power internet of things (IoT) devices that transmit small payloads to a typical receiver, including sensors for sensing, metering, and monitoring
 \cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.
@@
 
-\textcolor{OrangeRed}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS.
+\textcolor{blue}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS.
 We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}
@@
 \textcolor{blue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
-O-RAN was developed as a result of integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
+O-RAN was developed due to integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
 With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly.
@@
 
-O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
+\textcolor{blue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
 In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
@@
 Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
-The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. 
-O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
+The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.}
+
+\textcolor{blue}{This paper aims to design a RAN slicing technology in O-RAN architecture. }
+%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
 The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence
-\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
 
@@
 
-\textcolor{blue}{In order to achieve the specific QoS for eMBB, URLLC, and mMTC, this study optimizes the allocation of baseband resources, including power allocation, PRB allocation, O-Rus association, and VNF activation to create an isolated network slicing outline.}
+\textcolor{blue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
+As well as baseband resources, the optimal number of VNFs is also taken into account to reduce latency for URLLC services.}
 \subsection{Related Literature}
@@
 \subsection{Main Contributions}
-The purpose of this study is to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
-Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN system.
-The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
-In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follows:
+\textcolor{MidnightBlue}{The purposes of this paper are twofold.
+First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
+Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
+Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
+In this paper, we want to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
+Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
+The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
+We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.}
+
+In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the o-ran system is studied. The main contributions of this paper are summarized as follows:
 \begin{itemize}
@@
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Network sliced ORAN system}
+  \caption{Network sliced o-ran system}
   \label{fig:c11}
@@
 Firstly, we present the system model.
-Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system.
+Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the o-ran system.
 Afterward, we discuss the mean delay and the power of VNFs.
@@
   \captionsetup{justification=centering}
-    \includegraphics[scale = 0.40]{Interference.png}
+    \includegraphics[scale = 0.35]{Interference.png}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 \subsection{Slice Management}
-\textcolor{RedViolet}{In this subsection, we want to study the management of slices. We want to talk about the creation, management, and deletion of slices.}
+\textcolor{RedViolet}{This subsection aims to examine slice management, including creating, managing, and deleting slices.
+Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning.
+\begin{itemize}
+\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase.
+In this phase, operators plan to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment.
+Also, the evaluation of requirements is performed in this step.
+\item Commissioning phase: In the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice. 
+\item Operation phase: During the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated.
+As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
+\item Decommissioning phase: A NSI that is decommissioned no longer exists after the decommissioning phase.
+\end{itemize}
+}
 
@@
 \end{algorithm} 
-\vspace*{-2em}
+%\vspace*{-2em}
 \section{Numerical Results and The Feasible Region}\label{NE}
@@
 Then, we talk about the feasible region of our system model. Afterward, we illustrate the numerical results.
-\vspace*{-1.7em}
+%\vspace*{-1.7em}
 \subsection{The initial Points and The Comparison Algorithms}

### 2022-02-14 Journal1/Response (21-10-2019)/Response.tex
add reviewer 1 comments

@@
 
-\noindent
-\begin{longtable}{|p{.975\textwidth}|}
-\hline \hline %\hline \hline \hline
-\Centering
-\cellcolor{gray!60}
-\textbf{Reviewer 1} \\
-\hline \hline %\hline \hline \hline
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
 \RaggedRight
@@
 \cellcolor{gray!15}
-\textbf{\noindent Comment 2:} ``However, the scaling problem arises now.
-The synaptic channel/cleft between \textbf{Tx} and \textbf{Rx} is very narrow (tens of nm).
-If the authors suggest nano-machines, e.g., as in the scenario shown in Figure 2 (c), both nano-machines are envisioned to co-locate in the cleft, 3 nm distant from the synaptic terminals.
-What is the size of nano-machines then?
-How realistic is that owing to the complexity of these nano-machines?
-Wouldn't it be much easier to consider artificial synapse instead?''\\
+\textbf{\noindent Comment 2:} ``Although the paper demonstrates its claims, the relaxation of conditions from the original problem formulation is not well justified.
+It is not clear why the initial formulation of the problem is not feasible and the reformulated makes it feasible while retaining some level of quality of the solutions given.
+A deeper analysis of both formulations must be presented.
+''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-According to the advances in nano-technology and nano-communications, different design strategies for intelligent nano-devices interfaced with the neuronal tissue were proposed in the literature.
-The proposed system model in this manuscript is based on one of them.
-In the proposed system model, we need to consider the assumptions of real synapses since the real neurons play the role of \textbf{Tx} and \textbf{Rx} in the most of scenarios while in the artificial synapses, the assumptions are different.
+The problem (13) is feasible and has feasibility points that are discussed in subsection  IV-B, and we introduce a fast algorithm (algorithm 3) for feasibility points.
+Although the problem is feasible, it is not convex and difficult to solve..
+Since problem (13) is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard.
+Solving the problem is complex.
+To solve the problem by inspiring Stackelberg, we reformulate the equation (13g) to reduce one of the variables ($M_s$) that can be solved after obtaining the rate of UEs ($M_s$ is similar to followers in Stackelberg Competition and power and PRB assignment is similar to leader).
+So, the new problem has two variables of power and PRB assignment.
+This new problem is convex by relaxing the binary variable (PRB assignment) and estimating the lower bounds in equation (15) because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
+After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.
 
-About the scaling problem, the width of synaptic cleft is about tens of nm and in the worth case scenario where nano-machines are located in both terminals, 6 nm is required for SnM interfaces.
-Hence, there is sufficient room for nano-machines since they are much smaller than the neurons.
-In addition, some references in the literature discussed about the implementation of these interfaces.
-We clarified about this issue in the following:
+We also add this response in subsection III-A.
 
-\clearpage
-We refer to the following list of references in our explanation in this comment:
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment3:} ``Moreover, the baseline and FBDR methods used in the comparison are not well introduced.
+They are vaguely linked to related work but not as needed.
+The paper must clarify the relation of the related work and the compared alternatives.
+The paper must also contextualize the proposal among the related work by comparing their qualities and/or performance.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+ Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
+The first one is a baseline scheme, which uses random PRB allocation.
+So, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
+Also, the association of O-RU is carried out based on distance.
+It means that each UE is assigned to the nearest O-RU.
+The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
+After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is
+achieved from the lemma (1). The second one is similar
+to the fixed BBU capacity and dynamic resource allocation
+(FBDR) algorithm proposed in [18]. In this work, we have services with different QoS that
+contain UEs, which is similar to tenants with different QoS
+that is introduced in [18]. So, we used an algorithm similar
+to FBDR adapted to our conditions for comparison. Instead
+of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
+To use the FBDR method, we should consider the fixed
+BBU capacity. We assume that O-DU and O-CU have fixed
+sufficient capacity in our system model. Also, our mid-haul
+link (F1 link) has adequate capacity, so there will be no
+issue using the FBDR method by separating BBU to O-DU
+and O-CU with this assumption. In this method, PRB and power are dynamically allocated. The number of VNFs is
+obtained from the simulation. The UEs are associated with the O-RU based on the quality of their channels and the
+channel distance instead of using the greedy algorithm 1 (GAA algorithm ) for O-RU assignment. The figures in [18]
+show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same
+priority area. We will also see that our proposed algorithm performs better than FBDR in the numerical result section.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment4:} ``Finally, the source of the values used for the parameters in the evaluation must be clarified.  ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We refer to the following list of references in our numerical result for this comment:
 
@@
 \cellcolor{green!10}
-[1] F.
-Patolsky, B.
-P.
-Timko, G.
-Yu, Y.
-Fang, A.
-B.
-Greytak, G.
-Zheng, and C.
-M.
-Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol.
-313, no.
-5790, pp.
-1100-1104, 2006.
+[1] 3GPP-TS-36.104-V13.3.0, “Evolved Universal Terrestrial Radio Access (E-UTRA);
+Base Station (BS) radio transmission and reception
+(Release 13),” 2016-03.
 
-[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.
+[2]  3GPP-TR-36.931-V13.0.0, “Technical Specification Group Radio Access Network;
+Evolved Universal Terrestrial Radio Access (E-UTRA);
+Radio Frequency (RF) requirements for LTE Pico Node B
+(Release 13),” 2016-01.
 
-[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.
+[3] 3GPP-TS-25.101-V4.13.0, “User equipment (UE) radio transmission
+and reception (FDD)(release 4),” 2006-12.
 
-[4] Mesiti, Fabio, and Ilangko Balasingham.
-``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol.
-31, no.
-12, pp.
-695-704, 2013.
+[4]E. Mohyeldin, “Minimum technical performance requirements for
+imt-2020 radio interface(s),” 2020.
 
-[5] N.
-Rouach, E.
-Avignone, W.
-Même, A.
-Koulakoff, L.
-Venance, F.
-Blomstrand, and C.
-Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol.
-94, no.
-7-8, pp.
-457-475, 2002.
+[5]  ETSI-TR-138-913-V14.3.0, “5G; study on scenarios and require-
+ments for next generation access technologies(3GPP TR 38.913 version
+14.3.0 release 14),” 2017-10.
 
-[6] J.
-Hjorth, K.
-T.
-Blackwell, and J.
-Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J.
-Neuroscience, vol.
-29, no.
-16, pp.
-5276-5286, 2009.
-
-[7] R.
-D.
-Traub, M.
-A.
-Whittington, E.
-H.
-Buhl, F.
-E.
-N.
-LeBeau, A.
-Bibbig, S.
-Boyd, H.
-Cross, and T.
-Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol.
-42, no.
-2, pp.
-153-170, 2001.
 \\
@@
 
-\clearpage
-In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
-stimulation with an array of 50 NW connections per neuron.
-The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
-Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
-Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations.
-We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.
-
-\textbf{Gap Junction Interface [4]}:
-
-With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells.
-Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity.
-In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted.
-This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
-\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
-\label{new_1}
-\end{figure}
-
+In [1] page 11, the amount of BW is explained.
+In [2], noise power is represented.
+In [5], the author stated the amount of delay for eMBB and URLLC in page 24 and 25.
+Also, in page 27, the mMTC packet size is stated.
+In [3], in page 13, table 6.1, the maximum power is stated.
+In [4], in page 4, the delay of URLLC and eMBB is stated also the spectral efficiency of eMBB is stated.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 1:} ``The paper has been improved according to the previous comments from this reviewer and only the following minor issues have remained.''\\
+\cellcolor{violet!15}
+\textbf{\noindent Comments to the Author:} ``The paper focus on the aspect of network slicing in 5G cellular network which entails a service aware resource allocation of the different required virtual network functions (VNFs) for different slices which have different characteristics.
+More specifically, the paper proposes a mixed integer mathematical problem which in the original form is non-linear and hence hard to solve.
+To tackle this challenge the optimization problem is decomposed into two sub-problems where the solutions are not optimal however numerical investigations show that the solutions are competitive.
+In general, the paper is well written and structured.''\\
 \hline

### 2022-02-14 Journal1/paper3TNSM/pr.tex
add reviewer 1 comments

@@
 
-\textcolor{violet}{Although the problem is feasible and it has feasibility points that are discussed in subsection \ref{fr}, it is not convex and difficult to solve.
+\textcolor{violet}{The problem \ref{problem} is feasible and has feasibility points that are discussed in subsection \ref{fr}, and we introduce a fast algorithm (algorithm\ref{alg3}) for feasibility points.
+Although the problem is feasible, it is not convex and difficult to solve.
 Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard.
@@
 Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a}.
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.
 \begin{table}[H]
@@
 After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is achieved from the lemma \eqref{lemma1}.}
-\textcolor{brown}{ The second one is similar to the fixed BBU capacity and
-dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic}.
-In this work, we have services with different QoS that contain UEs, which is similar to tenants with a different QoS.
+\textcolor{brown}{ In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in \cite{lee2018dynamic}.
  So, we used an algorithm similar to FBDR adapted to our conditions for comparison.  
- We assume here that the capacity of the O-DU (which is similar to BBU in the FBDR) is as large as the capacity of our fronthaul link so that we can use this method for our system model.
+Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
+To use the FBDR method, we should consider the fixed BBU capacity.
+We assume that O-DU and O-CU have fixed sufficient capacity in our system model.
+Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the FBDR method by separating ‌BBU to O-DU and O-CU with this assumption.
 In this method, PRB and power are dynamically allocated.

### 2022-02-16 Journal1/Response (21-10-2019)/Response.tex
Add reviewer 2

@@
 \usepackage{adjustbox}
+\usepackage{hyperref}
 %\usepackage[none]{hyphenat}
@@
 \cellcolor{violet!15}
-\textbf{\noindent Comment1:} ``The paper has gone through three independent reviews and also checked by myself.
+\textbf{\noindent  Comments to the Author} ``The paper has gone through three independent reviews and also checked by myself.
 The topic is interesting and there are merits.
@@
 
+We add this response in subsection IV-A.
+
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
+
 We refer to the following list of references in our numerical result for this comment:
@@
 
-In [1] page 11, the amount of BW is explained.
-In [2], noise power is represented.
-In [5], the author stated the amount of delay for eMBB and URLLC in page 24 and 25.
-Also, in page 27, the mMTC packet size is stated.
-In [3], in page 13, table 6.1, the maximum power is stated.
-In [4], in page 4, the delay of URLLC and eMBB is stated also the spectral efficiency of eMBB is stated.
+On [1] page 11, the amount of BW is explained.
+In [2], the noise power is represented.
+In [5], the author stated the amount of delay for eMBB and URLLC on pages 24 and 25.
+Also, on page 26, the mMTC packet size is stated.
+On page 25, the URLLC packet size is stated.
+In [3], on page 13, table 6.1, the maximum power is stated. In [4], on page 4, the delay of URLLC and eMBB is and also the spectral efficiency of eMBB is noted.
+
+We add these references in IV-A (references [41]-[45]).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \cellcolor{gray!15}
-\textbf{\noindent Comment 2:} ``In Introduction, page 5, ``We consider a neuro-spike communication channel between two neurons located in the motor cortex region of the brain where the information is encoded by spike time intervals.''.
-Please provide a reference for this sentence.''\\
+\textbf{\noindent Comment 1:} ``In terms of taking the actual delay in the proposed there are some concerns which might be important for some time critical applications especially in the ultra-reliable low latency communications (URLLC) but also for different applications that fall under the enhanced mobile broadband (eMBB) generic service framework.
+First of all, in the paper the authors only consider processing delay and ignore propagation and transmission delay.
+Since multiple paths in reality could be utilized the role of the above two components might play an important role.
+Nevertheless, the authors need to clearly mention why those two components are not considered, saying for example are constant is not a good enough reason to be ignored since as eluded those change based on routing decisions.''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-Neural coding refers to the mapping from the stimulus to the configurations of the generated
-spikes by neurons.
-Neurons employ the spike rate coding and temporal coding to transmit information via action potentials.
-As we explained in the manuscript, none of the papers in the literature proposed a model for neuro-spike communication channel in the motor cortex region when temporal modulations
-are employed to convey information.
-However, there are some papers that assumed temporal modulations in the motor cortex region.
-We referred to one of these papers in the new manuscript based on the reviewer comment as
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{green!10}
-We consider a neuro-spike communication channel between two neurons located in the motor cortex region of the brain where the information is encoded by spike time intervals [30].
-\\
-\hline
-\end{longtable}
-The referred paper is
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{green!10}
-[30] Hatsopoulos N, Geman S, Amarasingham A, Bienenstock E., ``At what time scale does the nervous system operate?'', Neurocomputing, vol. 1, no. 52, pp.25-29, 2003.
-\\
-\hline
-\end{longtable}
+Considering propagation and transmission delays is straightforward to add to the system, but we do not include them for better presentation and focus on obtaining the optimal number of VNF.
+In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed; In the following, we describe more about these two types of delays.
 
-\clearpage
+The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority (Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU).
+Therefore, different routes are added to the system to solve the routing problem, but we do not consider it since it changes the model and does not fit in this model.
+So, the connection between O-RUs to O-DUs is fixed and transparent.
+As a result, the propagation delay is fixed and does not affect the optimization problem.
+The following is a brief calculation of propagation delay.
+Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
+Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}.
+so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $.
+Since fronhaul, midhaul, and backhaul are fiber optics, c is the speed of light.
+Also, due to the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced.
+But we also do not focus on edge processing in this paper.
+You can find more about these distances in this \href{https://blogs.keysight.com/blogs/inds.entry.html/2020/06/30/5g_testing_what_is-0nzj.html\%23:~:text=The\%20data\%20requirements\%20are\%20about,DUs\%20is\%20about\%2080\%20km.}{link}.
+The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has such a small amount.
+In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$.
+So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$.
+As a result, the $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$.
+for eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.
+
+We add this response in subsection II-D.
+
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \cellcolor{gray!15}
-\textbf{\noindent Comment 3:} ``In System Model, the possibility of placing nano-machines in synapses located between motor cortex neurons must be proved.
-This action needs invasive surgeries, which cause further damage to the neurons.''\\
+\textbf{\noindent Comment 2:} ``Also, note that for calculating processing delay requests for different services arriving at blade servers for vnf applications might get different treatment on how they access VMs or containers hence a single queue with non-priority and/or preemption (m/m/1) might not be a good approximation on the performance.''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-According to the advances in nano-technology and nano-communications, different design strategies
-for intelligent nano-devices interfaced with the neuronal tissue were proposed in the literature. The
-proposed system model in this manuscript is based on one of them. We clarify more about this issue in the following.
-We refer to the following list of references in our explanation in this comment:
+The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent.
+Moreover, the impact of a single packet on the system's performance is minimal.
+Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process.
+The system's clock is constant, and the size of the tasks is not fixed.
+So, we suppose that service times are exponentially distributed [36].
+In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services, not between UEs of one service.
+Because we assumed that the UEs of a service have the same priority, their sent packets also have an equal priority.
+Also, the services are isolated, and this priority does not invalidate the queue assumption.
+Furthermore, one service's priority over another can be higher, affecting the whole optimization and not queue formulation since the UEs in each service have the same priority, and each service has its processing delay independent of other services.
+
+We add this response in subsection II-D-1.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment 3:} ``Also worth noting, that later on in the problem formulation there is the notion of service priority $\delta_s$ for data rate but this seems not to be used for accessing cloud resources.
+For example one could have changed the optimization problem and considered average allocated transmission rate and optimize with the same priorities access to cloud resources (instead of allocating equal access to vnf resources).''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+In this problem, since the priority is in the objective function of the equation (13), the priority has whole effect optimization.
+So, priority is given to the whole optimization problem, and the optimization problem obtains the number of VNFs by affecting the priority term.
+If we were to discuss the placement of VNFs on the data centers, the problem would become a knapsack or bin-packing problem, and here the prioritization would affect the resource allocation algorithm, including memory, RAM, CPU, and bandwidth.
+So the algorithm was implemented based on prioritization.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment 4:} ``Some form of rationalization should be given for abstracting Interference as Gaussian noise.
+This is important because we expect the system to be interference limited and cell edge users to experience significant different levels of performance compared to centre cell users.''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow
+%{\color{red} use paranthesis in the following equation to clear +}
+\begin{subequations}\label{eqI}
+\begin{alignat}{4}
+&I_{r,u(s,i)}^{k} =\\
+ &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
+&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
+&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
+\end{alignat}
+\end{subequations}
+%{\color{red} $\gamma_1$ is constant used instead of variable. }
+%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
+where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
+%($\gamma_1$ and $\gamma_2$ are two variales.
+You  define on variable here.)
+Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.
+
+Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
+The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.
+To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
+\begin{equation}\label{eq2}
+y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}{x_Q}^k_{r,u(s,i)}+ z_{u(s,i)},
+\end{equation}
+
+%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
+where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
+Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
+Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression that is shown in figure \ref{fig:pq}. 
+In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization Gaussian noise 
+($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.
+\begin{figure}
+  \centering 
+  \captionsetup{justification=centering}
+    \includegraphics[scale = 0.7]{Qdiag.png}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Precoding and Quantization of Signal}
+  \label{fig:pq}
+\end{figure}
+
+We add this response in subsection II-B.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment 5:} ``Constraint 13n (changed to 13k in new version) is not clear - it means that there are VMs and/or containers available in the network and an operator denies service due to an energy consumption budget (which again is not very detailed to capture the actual energy consumption of each node/vnfs under different loads etc.).
+In general the subsection on VNF power consumption is very limited in scope.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+{A significant issue facing the industry is reducing energy consumption.
+Data centers are one of the most energy-consuming.
+As a result, restrictions are placed on data centers' energy, including virtual machines (VMs).
+So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers.
+So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).
+
+We add this response in subsection II-E.
+
+\clearpage
+\noindent
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment 6:} ``Some rationalization is needed on why the packet size is considered to be 20 bytes. ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+
+We refer to the following reference in our numerical result for this comment:
 
@@
 \cellcolor{green!10}
-[1] F.
-Patolsky, B.
-P.
-Timko, G.
-Yu, Y.
-Fang, A.
-B.
-Greytak, G.
-Zheng, and C.
-M.
-Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol.
-313, no.
-5790, pp.
-1100-1104, 2006.
+[1]  ETSI-TR-138-913-V14.3.0, “5G; study on scenarios and require-
+ments for next generation access technologies(3GPP TR 38.913 version
+14.3.0 release 14),” 2017-10.
 
-[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.
-
-[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.
-
-[4] Mesiti, Fabio, and Ilangko Balasingham.
-``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol.
-31, no.
-12, pp.
-695-704, 2013.
-
-[5] N.
-Rouach, E.
-Avignone, W.
-Même, A.
-Koulakoff, L.
-Venance, F.
-Blomstrand, and C.
-Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol.
-94, no.
-7-8, pp.
-457-475, 2002.
-
-[6] J.
-Hjorth, K.
-T.
-Blackwell, and J.
-Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J.
-Neuroscience, vol.
-29, no.
-16, pp.
-5276-5286, 2009.
-
-[7] R.
-D.
-Traub, M.
-A.
-Whittington, E.
-H.
-Buhl, F.
-E.
-N.
-LeBeau, A.
-Bibbig, S.
-Boyd, H.
-Cross, and T.
-Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol.
-42, no.
-2, pp.
-153-170, 2001.
 \\
@@
 
-\clearpage
-In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
-stimulation with an array of 50 NW connections per neuron.
-The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
-Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
-Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations.
-We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.
+On [1], on page 25, the URLLC packet size is stated to be 32 bytes, and on page 26, the packet size of mMTC is stated to be 20 bytes.
+We have changed the URLLC packet size to 32, but it has very little impact on the simulation result.
 
-\textbf{Gap Junction Interface [4]}:
+We add this reference in IV-A (reference [45]).
 
-With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells.
-Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity.
-In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted.
-This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment 7:} ``Comparison with [18] might not be fair since that work also considers BBU capacity and also performs admission control functionalities, also there are different tenants that have different users with variable required QoS.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We use a method which is similar to the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18].
+In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in [18].
+ So, we used an algorithm similar to FBDR adapted to our conditions for comparison.  
+Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
+To use the FBDR method, we should consider the fixed BBU capacity.
+We assume that O-DU and O-CU have fixed sufficient capacity in our system model.
+Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the FBDR method by separating ‌BBU to O-DU and O-CU with this assumption.
+In this method, PRB and power are dynamically allocated.
+The number of VNFs is obtained from the simulation.
+The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm 1 (GAA algorithm ) for O-RU assignment.
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
-\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
-\label{new_1}
-\end{figure}
+We add this response in subsection IV-A.
 
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment 8:} ``Also, interference is measured in a more detailed manner (maximum interference per UE) and hence when this relaxed (Guassian noise) the performance expected to slightly increase.
+Hence, some more detailed discussion on what has been assumed is needed.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise which is shown in Fig \ref{fig:pq}.
+We offer the sum of interference and the Gaussian quantization noise with $ I_{r,u(s,i)}^{k}$.
+Also, the Gaussian quantization noise is independent of interference and related to channel gain of UEs.
+
+We add this response in subsection II-B.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-02-16 Journal1/paper3TNSM/pr.tex
Add reviewer 2

@@
 
-\textcolor{magenta}{Considering propagation and transmission delays is straightforward to add to the system, but we did not consider them for better presentation and focus on obtaining the optimal number of VNF.
-In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed for simplification;
-The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority (Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU).
+\textcolor{Violet}{Considering propagation and transmission delays is straightforward to add to the system, but we do not include them for better presentation and focus on obtaining the optimal number of VNF.
+In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed; In the following, we describe more about these two types of delays.}
+
+\textcolor{Violet}{The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority (Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU).
 Therefore, different routes are added to the system to solve the routing problem, but we do not consider it since it changes the model and does not fit in this model.
@@
 Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
-We consider 25 PRBs are used in the network and the packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes.
+\textcolor{Violet}{We consider 25 PRBs are used in the network and the packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes \cite{ETSI1}.}
 The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
@@
 Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. \textcolor{Violet}{The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.}
 \begin{table}[H]
@@
 After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is achieved from the lemma \eqref{lemma1}.}
-\textcolor{brown}{ In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in \cite{lee2018dynamic}.
+\textcolor{brown}{The second one is similar to the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic}.
+In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in \cite{lee2018dynamic}.
  So, we used an algorithm similar to FBDR adapted to our conditions for comparison.  

### 2022-02-19 Journal1/Response (21-10-2019)/Response.tex
finish review

@@
 \cellcolor{gray!45}
-\textbf{Reviewer 4} \\
+\textbf{Reviewer 3} \\
 \hline \hline
@@
 \cellcolor{gray!15}
-\textbf{\noindent Comment 1:} ``The description of  ``unhealthy neuron'' or ``neurons that have lost their ability to communicate'' and the nano-machines to connect them seems to provide a possible future application to the communication channel model proposed.
-What the manuscript is not fully analyzing in the opinion of this reviewer is exactly how the nano-machines could utilize this model from an engineering perspective.
-If this connection is not considered to be the focus and therefore was not researched, then the consideration should be made to remove the concept of nano-machines from the ``System Model'' section (and subsequent sections) and use it merely for motivating the model.''\\
+\textbf{\noindent Comments to the Author} ``The authors propose a resource allocation scheme for network slicing in an Open RAN scenario.
+They consider three network slice types namely eMBB, URLLC and mMTC and provide a solution for end-to-end slicing considering resource allocation over the RAN domain following the proposed ORAN architecture, as well as VNF allocation.
+In general, the paper is well written, however some parts need to be rephrased and restructured.''\\
 \hline
@@
 
-In recent years, engineering applications of nano-technology have also been investigated with increasing interest
-for the design of bio-inspired intelligent nano-devices or nano-machines connected in a network.
-In this manuscript, we considered the concept of nano-machines in the proposed system model according to the reported efforts to interface the neuron's body
-with synthetic nano-scale materials in the literature. We provide a brief explanation in the following. We refer to the following list of references in our explanation in this comment:
-
-\clearpage
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \RaggedRight
-\cellcolor{green!10}
-[1] F.
-Patolsky, B.
-P.
-Timko, G.
-Yu, Y.
-Fang, A.
-B.
-Greytak, G.
-Zheng, and C.
-M.
-Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol.
-313, no.
-5790, pp.
-1100-1104, 2006.
-
-[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.
-
-[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.
-
-[4] Mesiti, Fabio, and Ilangko Balasingham.
-``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol.
-31, no.
-12, pp.
-695-704, 2013.
-
-[5] N.
-Rouach, E.
-Avignone, W.
-Même, A.
-Koulakoff, L.
-Venance, F.
-Blomstrand, and C.
-Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol.
-94, no.
-7-8, pp.
-457-475, 2002.
-
-[6] J.
-Hjorth, K.
-T.
-Blackwell, and J.
-Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J.
-Neuroscience, vol.
-29, no.
-16, pp.
-5276-5286, 2009.
-
-[7] R.
-D.
-Traub, M.
-A.
-Whittington, E.
-H.
-Buhl, F.
-E.
-N.
-LeBeau, A.
-Bibbig, S.
-Boyd, H.
-Cross, and T.
-Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol.
-42, no.
-2, pp.
-153-170, 2001.
-\\
+\cellcolor{gray!15}
+\textbf{\noindent Comment 1:} ``The paper presents an interesting solution and an extremely well formulated mathematical problem; however, the main contribution of the paper is hard to grasp.
+For instance, the introduction of the paper is very generic.
+There are a lot of concepts and methods explained, nonetheless not related to the proposed solution.
+The main issue lies in the structure of the work.
+The main contribution only appears at the end of page 2, where after an extensive reading the interest of the reader starts to vanish.
+I would definitely suggest a restructuring here.
+For instance, directly hint the main objectives and motivation of the work to prepare the reader for what is following.
+Moreover, the Related work could be a section of its own.
+In that way, the organization of the paper is clearer and easier to read.
+''\\
 \hline
 \end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+Thank you for helping me to change my introduction.
+I have changed the introduction of my paper.
 
-\clearpage
-In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
-stimulation with an array of 50 NW connections per neuron.
-The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
-Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
-Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations.
-We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment 2:} ``Finally, a better distinction of the current proposal from the state-of-the-art is mandatory, otherwise it is hard to understand how the proposed algorithm differs from existing works in the literature which seem to provide solution to a similar problem.''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+The purposes of this paper are twofold.
+First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
+Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
+Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
+In this paper, we want to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
+Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
+The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
+We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.
 
-\textbf{Gap Junction Interface [4]}:
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment 3:} ``Furthermore, while the math introduced in the paper is solid, it is also hard to follow for a reader if illustrations are not presented.
+It would be easier if a Figure is introduced for instance to explain equations from 3a -3d, where a lot of variables are presented.
+Especially, for the concepts of inter and intra slice isolation, which are very crucial.
+Following, that logic more elaboration especially with respect to inter slice isolation and why it needs to be considered in the equation, is important, as one could say that a careful scheduling has to definitely avoid distribution of the same resources within a slice to different users i.e., (orthogonality constraint).''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+I have add this part in the system model. 
+Assume we have $K$ physical resource blocks (PRBs) in this system.
+Suppose each slice s consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
+Therefore, we have $\sum_s \bar{K}_s \leq K$.
 
-With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells.
-Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity.
-In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted.
-This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.
+Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
+ r$.
+UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
+Network Slicing methods significantly reduce inter-service interference.
+There are some techniques to remove inter-slice interference.
+One of these techniques is to have two-time scale scheduling.
+The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out.
+Since there are limited resources, inter-service interference cannot be eliminated entirely.
+The other method is to allocate part of the RB of eMBB services to URLLC and mMTC  [2], [6], [34].
+In this paper, we assume that the PRB scheduling is performed.
+Also, in subsection II-F1, we briefly study the PRB scheduling between slices.
+\begin{figure}
+  \centering 
+  \captionsetup{justification=centering}
+    \includegraphics[scale = 0.35]{Interference.png}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Type of Interference Signal}
+  \label{fig:intf}
+\end{figure}
+$I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow
+%{\color{red} use paranthesis in the following equation to clear +}
+\begin{subequations}\label{eqI}
+\begin{alignat}{4}
+&I_{r,u(s,i)}^{k} =\\
+ &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
+&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
+&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
+\end{alignat}
+\end{subequations}
+%{\color{red} $\gamma_1$ is constant used instead of variable. }
+%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
+where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
+%($\gamma_1$ and $\gamma_2$ are two variales.
+You  define on variable here.)
+Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
-\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
-\label{new_1}
-\end{figure}
+We add this response in subsection II-B.
+
+ In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices [37].
+We need to have an algorithm to remove the inter-slice interference before solving the problem \ref{problem}.
+Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed.
+So, the assignment of PRB can be completed in two steps to remove inter-slice interference and isolate the slices.
+Firstly we assign PRBs to slices.
+Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm \ref{proAlg}.
+Suppose, $\mathcal{R}_{{s}}^{min}$, and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
+Firstly, we need to find the average PRB number used by UEs in each service.
+Since mMTC and URLLC transmit a short packet, each UE in mMTC and URLLC requires 1 PRB.
+So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs.
+For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s.
+(eMBB slice)
+So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$.
+$K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$.
+$K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).
+Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
+The problem can be written as follow
+\begin{subequations}\label{prob:prb}
+\begin{alignat}{4}
+\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s K_s \ln(\bar{K_s}) \ \\
+\text{subject to} \quad  & \sum_s{\bar{K_s}} \leq K
+ \label{prb0} \\
+& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
+&  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3,\label{prb2}
+\end{alignat}
+\label{constraints}
+\end{subequations}
+We used logarithms to assign PRBs to all slices to make
+them equally fair [37]. Equation (14b) illustrates that the
+sum of PRBs of slices can not exceed the maximum number
+of PRBs. Equation (14c), restrict the number of PRBs
+of eMBB slices and (14d), limit the number of PRBs of
+URLLC and mMTC slices By relaxing $\bar{K_s}$, the objective function and constraints become convex and can be solved using the Lagrangian function.
+
+Also, I add a new subsection II-E-1 about PRB scheduling for this question.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment 4:} ``Additionally, since the authors claim their novelty on the introduction of ORAN architecture, it becomes of utmost importance to consider concepts such as the creation of a slice, management of a slice and well as deletion, which bridge the mathematical framework to the practical one.
+For instance, how is a network slice created in the proposed work?
+How are the requirements of a slice fed to the algorithm?
+How is the monitoring of a slice performed?''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+This subsection aims to examine slice management, including creating, managing, and deleting slices.
+Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning [38].
+\begin{itemize}
+\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase.
+In this phase, operators plan to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment.
+Also, the evaluation of requirements is performed in this step.
+\item Commissioning phase: In the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice. 
+\item Operation phase: During the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated.
+As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
+\item Decommissioning phase: A NSI that is decommissioned no longer exists after the decommissioning phase.
+\end{itemize}
+
+I add a new subsection II-G about Slice management for this question.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment 5:} ``Finally, the authors propose an interesting solution, however in none of the results information with respect to the convergence time of the algorithm were presented.
+This becomes extremely crucial when considering the real deployment of such a solution.
+In that regard, some findings with regard to this aspect need to be definitely included in the work.''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+It is shown in Fig. 11 and subsection III-C-1 and III-C-2.
 

### 2022-03-03 Journal1/Response1/Response.tex
Add paper

--- 2022-02-19 Journal1/Response (21-10-2019)/Response.tex
@@
 \noindent \textbf{Response:\\}
-We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. We have utilized the comments to improve our paper and eliminate the problems.
+We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. By utilizing the comments, we enhanced our paper and eliminated problems.
 
@@
 \noindent \textbf{Response:\\}
-I have changed the paper's introduction and checked the text entirely according to this comment.
+According to this comment, we have changed the introduction and checked the entire text.
+We have shortened the state of the arts and introduced our goal briefly before the main contribution section.
+We removed additional information and talked more about our work.
+Also, we add some figures to describe incomprehensible parts.
+In addition, we provide further explanations.
 
@@
 \noindent \textbf{Response:\\}
-The problem (13) is feasible and has feasibility points that are discussed in subsection  IV-B, and we introduce a fast algorithm (algorithm 3) for feasibility points.
-Although the problem is feasible, it is not convex and difficult to solve..
-Since problem (13) is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard.
-Solving the problem is complex.
-To solve the problem by inspiring Stackelberg, we reformulate the equation (13g) to reduce one of the variables ($M_s$) that can be solved after obtaining the rate of UEs ($M_s$ is similar to followers in Stackelberg Competition and power and PRB assignment is similar to leader).
+The problem in (13) is feasible and has feasibility points that are discussed in subsection  IV-B, and we introduce a fast algorithm (i.e., Algorithm 3) for feasibility points.
+Although the problem is feasible, it is not convex and difficult to solve.
+Since problem in (13) is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and the problem is NP-hard.
+Solving the problem is not trivial.
+To solve the problem by inspiring Stackelberg, we reformulate the equation in (13g) to reduce one of the variables (i.e., $M_s$) that can be solved after obtaining the rate of UEs.
+WE notice that $M_s$ is similar to the followers in Stackelberg Competition and power and PRB assignment is similar to leader.
 So, the new problem has two variables of power and PRB assignment.
-This new problem is convex by relaxing the binary variable (PRB assignment) and estimating the lower bounds in equation (15) because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
+This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds in (15) because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
 After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.
-
-We also add this response in subsection III-A.
+We made changes in Subsection III-A, accordingly.
 
@@
 \noindent \textbf{Response:\\}
+We would like to thank the reviewer to emphasis this point and to help us for a better presentation. 
   Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
 The first one is a baseline scheme, which uses random PRB allocation.
-So, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
+Therefore, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
 Also, the association of O-RU is carried out based on distance.
@@
 After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is
-achieved from the lemma (1). The second one is similar
+achieved from Lemma (1). The second one is similar
 to the fixed BBU capacity and dynamic resource allocation
@@
 contain UEs, which is similar to tenants with different QoS
-that is introduced in [18]. So, we used an algorithm similar
+that is introduced in [18]. Therefore, we used an algorithm similar
 to FBDR adapted to our conditions for comparison. Instead
@@
 
-On [1] page 11, the amount of BW is explained.
+In [1 page 11], the amount of BW is explained.
 In [2], the noise power is represented.
-In [5], the author stated the amount of delay for eMBB and URLLC on pages 24 and 25.
-Also, on page 26, the mMTC packet size is stated.
-On page 25, the URLLC packet size is stated.
-In [3], on page 13, table 6.1, the maximum power is stated. In [4], on page 4, the delay of URLLC and eMBB is and also the spectral efficiency of eMBB is noted.
+The amount of delay for eMBB and URLLC are listed on Pages 24 and 25 in [5].
+Also, on Page 26, the mMTC packet size is stated.
+On Page 25, the URLLC packet size is stated.
+In [3], on Page 13, Table 6.1, the maximum power is stated. In [4], on Page 4, the delay of URLLC and eMBB is and also the spectral efficiency of eMBB is noted.
 
@@
 \noindent \textbf{Response:\\}
-Considering propagation and transmission delays is straightforward to add to the system, but we do not include them for better presentation and focus on obtaining the optimal number of VNF.
-In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed; In the following, we describe more about these two types of delays.
+Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation.
+However, they can be added to the system model easily.
+In this paper, we focus only on the processing delay to find the optimal number of VNFs, and we consider the other two delays are fixed; In the following, we describe more about these two types of delays.
 
-The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority (Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU).
-Therefore, different routes are added to the system to solve the routing problem, but we do not consider it since it changes the model and does not fit in this model.
+The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority.
+Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU.
+Therefore, different routes are added to the system to solve the routing problem.
+However, it provides a new system model.
 So, the connection between O-RUs to O-DUs is fixed and transparent.
@@
 The following is a brief calculation of propagation delay.
-Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
-Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}.
+Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 Km.
+Moreover, the distance from O-CU to the network should not exceed 200 Km [35].
 so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $.
@@
 You can find more about these distances in this \href{https://blogs.keysight.com/blogs/inds.entry.html/2020/06/30/5g_testing_what_is-0nzj.html\%23:~:text=The\%20data\%20requirements\%20are\%20about,DUs\%20is\%20about\%2080\%20km.}{link}.
-The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has such a small amount.
-In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$.
+The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has a small amount.
+In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 \frac{bit}{\frac{sec}{Hz}} \times BW (180 KHz)$.
 So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$.
@@
 \noindent \textbf{Response:\\}
-The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent.
+The processing delay can be modeled as an M/M/1 queue; since the number of arrival packets in the system are from a large number of independent sources.
 Moreover, the impact of a single packet on the system's performance is minimal.
-Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process.
+Also, the queue discipline will be first-in first-out (FIFO), and the arrival packet is assumed to follow a Poisson process.
 The system's clock is constant, and the size of the tasks is not fixed.
@@
 In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services, not between UEs of one service.
-Because we assumed that the UEs of a service have the same priority, their sent packets also have an equal priority.
+Because we assume that the UEs of a service have the same priority, their sent packets also have an equal priority.
 Also, the services are isolated, and this priority does not invalidate the queue assumption.
@@
 \noindent \textbf{Response:\\}
-In this problem, since the priority is in the objective function of the equation (13), the priority has whole effect optimization.
-So, priority is given to the whole optimization problem, and the optimization problem obtains the number of VNFs by affecting the priority term.
+We would like to thank the reviewer for the great suggestion they gave us.
+Since the priority is in the objective function of the equation (13), the priority has whole effect optimization.
+Therefore, priority is given to the whole optimization problem, and the optimization problem obtains the number of VNFs by affecting the priority term.
 If we were to discuss the placement of VNFs on the data centers, the problem would become a knapsack or bin-packing problem, and here the prioritization would affect the resource allocation algorithm, including memory, RAM, CPU, and bandwidth.
-So the algorithm was implemented based on prioritization.
+Therefore, the algorithm was implemented based on prioritization.
 
@@
 The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.
-To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
+To obtain SNR as formulated in equation (1) in the paper, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
 \begin{equation}\label{eq2}
@@
 \noindent \textbf{Response:\\}
-{A significant issue facing the industry is reducing energy consumption.
+{We thank the reviewer for adding clarity to our paper and reducing ambiguity in this condition in response to this comment.
+A significant issue facing the industry is reducing energy consumption.
 Data centers are one of the most energy-consuming.
@@
 So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers.
-So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).
+Therefore, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^\text{max}$).
 
@@
 \noindent \textbf{Response:\\}
-
+Thank for this important comment. Our simulation parameters were based on [42-46], and in particular, for this parameter, we used the following reference 
 We refer to the following reference in our numerical result for this comment:
@@
 
-On [1], on page 25, the URLLC packet size is stated to be 32 bytes, and on page 26, the packet size of mMTC is stated to be 20 bytes.
-We have changed the URLLC packet size to 32, but it has very little impact on the simulation result.
+On [1, Page 25], the URLLC packet size is stated to be 32 bytes, and on Page 26, the packet size of mMTC is stated to be 20 bytes.
+We changed the URLLC packet size to 32, but it has little impact on the simulation result.
 
@@
 In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in [18].
- So, we used an algorithm similar to FBDR adapted to our conditions for comparison.  
+ Therefore, we used an algorithm similar to FBDR adapted to our conditions for comparison.  
 Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
@@
 \noindent \textbf{Response:\\}
-Thank you for helping me to change my introduction.
-I have changed the introduction of my paper.
+Thank you for the comment.
+According to this comment, We modified the introduction of the paper.
+We have shortened the state of the arts and related literature and introduced our goal briefly before the main contribution section.
+We removed additional information and talked more about our work.
+We released non-related parts to clarify our goal.
+We hint at our motivation in the second paragraph of our first page and discuss our aim in the introduction.
 
@@
 \noindent \textbf{Response:\\}
-The purposes of this paper are twofold.
-First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
+The purpose of this paper is twofold.
+First and foremost, it is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
 Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
 Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
-In this paper, we want to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+In this paper, we would like to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
 We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
@@
 \noindent \textbf{Response:\\}
-I have add this part in the system model. 
-Assume we have $K$ physical resource blocks (PRBs) in this system.
-Suppose each slice s consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
+We added this part in the system model.
+Assume there are $K$ physical resource blocks (PRBs) in the system.
+Suppose each slice $s$ consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
 Therefore, we have $\sum_s \bar{K}_s \leq K$.
@@
 
-We add this response in subsection II-B.
+We add this response in subsection II-F-1.
 
  In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices [37].
-We need to have an algorithm to remove the inter-slice interference before solving the problem \ref{problem}.
+We need to have an algorithm to remove the inter-slice interference before solving the problem (13).
 Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed.
@@
 Firstly we assign PRBs to slices.
-Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm \ref{proAlg}.
-Suppose, $\mathcal{R}_{{s}}^{min}$, and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
+Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm III.
+Suppose, $\mathcal{R}_{{s}}^{\min}$, and $\mathcal{R}_{{s}}^{\max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
 Firstly, we need to find the average PRB number used by UEs in each service.
@@
 So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs.
-For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s.
+For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = B\log_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s.
 (eMBB slice)
-So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$.
-$K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
-Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$.
-$K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
-Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).
+So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\max}}}\rceil$.
+$K_s^{\min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{\max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\min}}}\rceil$.
+$K_s^{\max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Also, $K_s = (K_s^{\min}+K_s^{\max})/2$ is the average number of required PRB in slice s (eMBB slice).
 Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
@@
  \label{prb0} \\
-& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
+& K_s^{\min} \leq \bar{K_s}  \leq K_s^{\max}  \quad \forall s \in S_1,\label{prb1} \\
 &  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3,\label{prb2}
@@
 \end{subequations}
-We used logarithms to assign PRBs to all slices to make
+We use logarithms to assign PRBs to all slices to make
 them equally fair [37]. Equation (14b) illustrates that the
@@
 
-Also, I add a new subsection II-E-1 about PRB scheduling for this question.
+Also, we added a new subsection II-E-1 discyussing PRB scheduling for this question.
 
@@
 \end{itemize}
+In the preparation phase, the evaluation of requirements is considered.
+After that, we use our algorithm to find the optimal number of VNFs for each slice and PRB assignment and power allocation.
+Therefore, in the preparation phase, we estimate our resource of slices, and in the commission phase, we allocate our resources to the slices.
 
-I add a new subsection II-G about Slice management for this question.
+We added a new subsection II-G about Slice management for this question.
 

### 2022-03-03 Journal1/Response2/Response.tex
Add paper

--- 2022-03-03 Journal1/Response1/Response.tex
@@
 But there are some major concerns on the contribution, the assumption, the model derivation, and the experimental results.
-I hope the review comments are useful for further improving the quality of the paper.
+We hope the review comments are useful for further improving the quality of the paper.
 I'd therefore recommend the Resubmission''\\
@@
 \noindent \textbf{Response:\\}
-We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. By utilizing the comments, we enhanced our paper and eliminated problems.
+We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. We have utilized the comments to improve our paper and eliminate the problems.
 
@@
 \noindent \textbf{Response:\\}
-According to this comment, we have changed the introduction and checked the entire text.
-We have shortened the state of the arts and introduced our goal briefly before the main contribution section.
-We removed additional information and talked more about our work.
-Also, we add some figures to describe incomprehensible parts.
-In addition, we provide further explanations.
+We have changed the paper's introduction and checked the text entirely according to this comment.
 
@@
 \noindent \textbf{Response:\\}
-We would like to thank the reviewer to emphasis this point and to help us for a better presentation. 
  Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
 The first one is a baseline scheme, which uses random PRB allocation.
-Therefore, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
+So, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
 Also, the association of O-RU is carried out based on distance.
@@
 contain UEs, which is similar to tenants with different QoS
-that is introduced in [18]. Therefore, we used an algorithm similar
+that is introduced in [18]. So, we used an algorithm similar
 to FBDR adapted to our conditions for comparison. Instead
@@
 The following is a brief calculation of propagation delay.
-Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 Km.
-Moreover, the distance from O-CU to the network should not exceed 200 Km [35].
+Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
+Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}.
 so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $.
@@
 The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has a small amount.
-In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 \frac{bit}{\frac{sec}{Hz}} \times BW (180 KHz)$.
+In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$.
 So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$.
@@
 \noindent \textbf{Response:\\}
-We would like to thank the reviewer for the great suggestion they gave us.
-Since the priority is in the objective function of the equation (13), the priority has whole effect optimization.
-Therefore, priority is given to the whole optimization problem, and the optimization problem obtains the number of VNFs by affecting the priority term.
+{\color{red}
+In this problem, since the priority is in the objective function of the equation in (13), the priority has whole effect optimization.
+So, priority is given to the whole optimization problem, and the optimization problem obtains the number of VNFs by affecting the priority term.
 If we were to discuss the placement of VNFs on the data centers, the problem would become a knapsack or bin-packing problem, and here the prioritization would affect the resource allocation algorithm, including memory, RAM, CPU, and bandwidth.
-Therefore, the algorithm was implemented based on prioritization.
+So the algorithm was implemented based on prioritization.
+}
 
@@
 The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.
-To obtain SNR as formulated in equation (1) in the paper, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
+To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
 \begin{equation}\label{eq2}
@@
 \noindent \textbf{Response:\\}
-{We thank the reviewer for adding clarity to our paper and reducing ambiguity in this condition in response to this comment.
-A significant issue facing the industry is reducing energy consumption.
-Data centers are one of the most energy-consuming.
+{A significant issue facing the industry is reducing energy consumption.
+Data centers are one of the most energy-consuming parts of a network.
 As a result, restrictions are placed on data centers' energy, including virtual machines (VMs).
 So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers.
-Therefore, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^\text{max}$).
+So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).
 
@@
 \noindent \textbf{Response:\\}
-Thank for this important comment. Our simulation parameters were based on [42-46], and in particular, for this parameter, we used the following reference 
+
 We refer to the following reference in our numerical result for this comment:
@@
 In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in [18].
- Therefore, we used an algorithm similar to FBDR adapted to our conditions for comparison.  
+ So, we used an algorithm similar to FBDR adapted to our conditions for comparison.
 Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
@@
 \noindent \textbf{Response:\\}
-Thank you for the comment.
-According to this comment, We modified the introduction of the paper.
-We have shortened the state of the arts and related literature and introduced our goal briefly before the main contribution section.
-We removed additional information and talked more about our work.
-We released non-related parts to clarify our goal.
-We hint at our motivation in the second paragraph of our first page and discuss our aim in the introduction.
+Thank you for the comment. We modified the introduction of the paper.
 
@@
 \noindent \textbf{Response:\\}
+
 We added this part in the system model.
@@
 
-We add this response in subsection II-F-1.
+We add this response in subsection II-B.
 
  In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices [37].
-We need to have an algorithm to remove the inter-slice interference before solving the problem (13).
+We need to have an algorithm to remove the inter-slice interference before solving the problem in \ref{problem}.
 Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed.
 So, the assignment of PRB can be completed in two steps to remove inter-slice interference and isolate the slices.
-Firstly we assign PRBs to slices.
-Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm III.
-Suppose, $\mathcal{R}_{{s}}^{\min}$, and $\mathcal{R}_{{s}}^{\max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
+Firstly, we assign PRBs to slices.
+Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses Algorithm \ref{proAlg}.
+Suppose $\mathcal{R}_{{s}}^{min}$ and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
 Firstly, we need to find the average PRB number used by UEs in each service.
@@
 So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs.
-For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = B\log_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s.
+For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s.
 (eMBB slice)
-So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\max}}}\rceil$.
-$K_s^{\min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
-Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{\max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\min}}}\rceil$.
-$K_s^{\max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
-Also, $K_s = (K_s^{\min}+K_s^{\max})/2$ is the average number of required PRB in slice s (eMBB slice).
+So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$.
+$K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$.
+$K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).
 Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
@@
  \label{prb0} \\
-& K_s^{\min} \leq \bar{K_s}  \leq K_s^{\max}  \quad \forall s \in S_1,\label{prb1} \\
+& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
 &  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3,\label{prb2}
@@
 \end{itemize}
-In the preparation phase, the evaluation of requirements is considered.
-After that, we use our algorithm to find the optimal number of VNFs for each slice and PRB assignment and power allocation.
-Therefore, in the preparation phase, we estimate our resource of slices, and in the commission phase, we allocate our resources to the slices.
 

### 2022-03-03 Journal1/paper3TNSM/pr.tex
Add paper

@@
 \subsection{State Of The Arts}
-\textcolor{blue}{To achieve the desired level of QoS (quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks.
+\textcolor{MidnightBlue}{To achieve the desired level of QoS (quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks.
 There are several implementations of network slicing, including core slicing, RAN slicing, and both.
@@
 
-\textcolor{blue}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS.
+\textcolor{MidnightBlue}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS.
 We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}
 
-\textcolor{blue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
+\textcolor{MidnightBlue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
 O-RAN was developed due to integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
@@
 
-\textcolor{blue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
+\textcolor{MidnightBlue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
 In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
@@
 
-\textcolor{blue}{This paper aims to design a RAN slicing technology in O-RAN architecture. }
+\textcolor{MidnightBlue}{This paper aims to design a RAN slicing technology in O-RAN architecture. }
 %O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
@@
 
-\textcolor{blue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
+\textcolor{MidnightBlue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
 As well as baseband resources, the optimal number of VNFs is also taken into account to reduce latency for URLLC services.}
@@
 %All $K$ PRBs can be assigned to all UEs in each service. 
-\textcolor{Sepia}{ Assume we have $K$ physical resource blocks (PRBs) in this system.
+\textcolor{MidnightBlue}{ Assume we have $K$ physical resource blocks (PRBs) in this system.
 Suppose each slice s consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
@@
 
-\textcolor{Sepia}{Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
+\textcolor{MidnightBlue}{Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
  r$.
@@
 \end{figure}
-\textcolor{teal}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}
+\textcolor{MidnightBlue}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}
 %{\color{red} use paranthesis in the following equation to clear +}
@@
 You  define on variable here.)
-\textcolor{Sepia}{Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.}
-
-\textcolor{NavyBlue}{Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
+\textcolor{MidnightBlue}{Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.}
+
+\textcolor{MidnightBlue}{Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
 The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.}
-\textcolor{teal}{To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
+\textcolor{MidnightBlue}{To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
 \begin{equation}\label{eq2}
@@
 %\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
-\textcolor{teal}{where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
+\textcolor{MidnightBlue}{where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
 Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
@@
 
-If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$.
+If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^\text{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$.
 Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
@@
 
-\textcolor{Violet}{Considering propagation and transmission delays is straightforward to add to the system, but we do not include them for better presentation and focus on obtaining the optimal number of VNF.
+\textcolor{MidnightBlue}{Considering propagation and transmission delays is straightforward to add to the system, but we do not include them for better presentation and focus on obtaining the optimal number of VNF.
 In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed; In the following, we describe more about these two types of delays.}
 
-\textcolor{Violet}{The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority (Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU).
+\textcolor{MidnightBlue}{The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority (Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU).
 Therefore, different routes are added to the system to solve the routing problem, but we do not consider it since it changes the model and does not fit in this model.
@@
 
-\textcolor{olive}{The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent.
+\textcolor{MidnightBlue}{The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent.
 Moreover, the impact of a single packet on the system's performance is minimal.
@@
 
-\textcolor{gray}{A significant issue facing the industry is reducing energy consumption.
+\textcolor{MidnightBlue}{A significant issue facing the industry is reducing energy consumption.
 Data centers are one of the most energy-consuming.
@@
 So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers.
-So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).}
+So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^\text{max}$).}
 \subsection{Problem Statement}
@@
 \max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}} \ \\
-\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r
+\text{subject to} \quad  &  P_r \leq P^\text{max}_{r} \quad \forall r
  \label{c11} \\
 &p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
-&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
-&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{min} \quad \forall s, \label{c13} \\
+&p_{r,u(s,i)}^{k}  \leq P_{s}^\text{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
+&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{\min} \quad \forall s, \label{c13} \\
 %&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
-& C_r \leq C^{max}_r \quad \forall r, \label{c15}\\ 
-&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\
+& C_r \leq C^\text{max}_r \quad \forall r, \label{c15}\\ 
+&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^\text{max}_{s} \quad \forall i,\forall s,\label{c16} \\
 & \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
 & \bar{\mathcal{R}}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\
-& 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\
-& \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\
+& 0 \leq M_s \leq M^\text{max}_s  \quad \forall s,\label{c16-3}\\
+& \phi^{\text{\text{tot}}}  \leq \phi^\text{max}, \label{c19} \\
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
@@
 \subsubsection{PRB Scheduling}\label{prb}
-\textcolor{Sepia}{ In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
+\textcolor{MidnightBlue}{ In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
 We need to have an algorithm to remove the inter-slice interference before solving the problem \ref{problem}.
@@
 Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm \ref{proAlg}.
-Suppose, $\mathcal{R}_{{s}}^{min}$, and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
+Suppose, $\mathcal{R}_{{s}}^{\min}$, and $\mathcal{R}_{{s}}^\text{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
 Firstly, we need to find the average PRB number used by UEs in each service.
@@
 (eMBB slice)
-So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$.
-$K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
-Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$.
-$K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
-Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).
+So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{\min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^\text{max}}}\rceil$.
+$K_s^{\min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^\text{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\min}}}\rceil$.
+$K_s^\text{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
+Also, $K_s = (K_s^{\min}+K_s^\text{max})/2$ is the average number of required PRB in slice s (eMBB slice).
 Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
@@
  \label{prb0} \\
-& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
+& K_s^{\min} \leq \bar{K_s}  \leq K_s^\text{max}  \quad \forall s \in S_1,\label{prb1} \\
 &  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3,\label{prb2}
@@
 \subsection{Slice Management}
-\textcolor{RedViolet}{This subsection aims to examine slice management, including creating, managing, and deleting slices.
-Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning.
+\textcolor{MidnightBlue}{This subsection aims to examine slice management, including creating, managing, and deleting slices.
+Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning \cite{ETSI2}.
 \begin{itemize}
@@
 
+In the preparation phase, the evaluation of requirements is considered.
+After that, we use our algorithm to find the optimal number of VNFs for each slice and PRB assignment and power allocation.
+Therefore, in the preparation phase, we estimate our resource of slices, and in the commission phase, we allocate our resources to the slices.
 %\vspace*{-1em}
@@
 Here, we first simplify and relax the parameters to convexify the problem.
-As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
+As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^\text{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
 for $\rho_{u(s,i)}^{k}$. 
@@
 
-Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
+Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^\text{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
 we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
@@
 
-\textcolor{violet}{The problem \ref{problem} is feasible and has feasibility points that are discussed in subsection \ref{fr}, and we introduce a fast algorithm (algorithm\ref{alg3}) for feasibility points.
+\textcolor{MidnightBlue}{The problem \ref{problem} is feasible and has feasibility points that are discussed in subsection \ref{fr}, and we introduce a fast algorithm (algorithm\ref{alg3}) for feasibility points.
 Although the problem is feasible, it is not convex and difficult to solve.
@@
 $M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s$.
-where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
+where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^\text{max}_s R_{u(s,i)}-T^\text{max}_s\lambda_{u(s,i)} -1)}{(T^\text{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
 \end{lemma}
@@
 \end{equation}
-We denote $ \mathfrak{M}_s= \min\{M^{max}, \phi_{max}/{3\phi_s}\}$.
+We denote $ \mathfrak{M}_s= \min\{M^\text{max}, \phi_{\max}/{3\phi_s}\}$.
 Thus, if we restrict constraint \eqref{c16} to equality, constraint \eqref{c16} is still valid.
@@
 \begin{equation}\label{eqDelay}
-\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
-\end{equation}
-In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
+\alpha_s/\mu_s\leq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
+\end{equation}
+In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that
 the numerator and the denominator will both have the same sign.
 In the numerator, according to the \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
-If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$, the numerator will be positive.
-$(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$ since the order of $T^{max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{max}_s$.
-Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{max}_s$.
+If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{\max}_s \geq 1$, the numerator will be positive.
+$(R_{u(s,i)}-\lambda_{u(s,i)})T^{\max}_s \geq 1$ since the order of $T^{\max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{\max}_s$.
+Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{\max}_s$.
 So the numerator will be positive.
-In the denominator, we can say that $(T^{max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,  
+In the denominator, we can say that $(T^{\max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,  
 $\mu_s \geq 0$ and
-$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{max}_s$ as mentioned above.
+$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{\max}_s$ as mentioned above.
 %Therefore, we need to have the constraint below.
@@
 \mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
-\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\\
-& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}
+\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{\max}_s}\\
+& + \frac{3}{T^{\max}_s\mu_s-\alpha_s T^{\max}_s/\mathfrak{M}_s-3}
 \end{alignat}
 \end{subequations}
-In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
+In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
 So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
@@
 \eqref{c15} is changed to
- $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
+ $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{\max}}$.
 The combination of equations \eqref{c11} and \eqref{c15} leads to the following equation
@@
 \begin{split}
-\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
+\zeta_{r}&= \min\{P_{\max}, \sigma_{q_r}^2\times 2^{C^r_{\max}} \}, \\
 P_r &\leq  \zeta_{r}.\\
@@
 &+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\\
-&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{max}_{s}- p^k_{r,u(s,i)})\\
+&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{\max}_{s}- p^k_{r,u(s,i)})\\
 &+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\\
@@
 \begin{algorithmic}[1]
-\State  Set the maximum number of iterations ${Iter}_{max}$, convergence condition $\epsilon > 0$ \label{a21}
+\State  Set the maximum number of iterations ${Iter}_{\max}$, convergence condition $\epsilon > 0$ \label{a21}
 \State  Assign Users to O-RU randomly (Initialize $\boldsymbol{G}$) \label{a22}
-\For {$i \gets 1$ to $Iter_{max}$}\label{23}
+\For {$i \gets 1$ to $Iter_{\max}$}\label{23}
 \State Acquire $\boldsymbol{P}^{(i)}$, $\boldsymbol{E}^{(i)}$ and $\boldsymbol{M}^{(i)}$ using Lagrangian function and sub-gradient method based on \eqref{sub1}
@@
 In addition, if we assume that the interference is set to be zero ${I}_{r,u_{(s,i)}}^{k}=0$,
-and we suppose that each UE has the maximum power $p_{r,u_{(s,i)}}^k = P_{s}^{max}$,
+and we suppose that each UE has the maximum power $p_{r,u_{(s,i)}}^k = P_{s}^{\max}$,
 and we consider that all PRB is assigned to all UE $e_{r,u_{(s,i)}}^k = 1 \forall s,\forall i$
@@
 Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
-\textcolor{Violet}{We consider 25 PRBs are used in the network and the packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes \cite{ETSI1}.}
+\textcolor{MidnightBlue}{We consider 25 PRBs are used in the network and the packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes \cite{ETSI1}.}
 The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$. 
@@
 Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. \textcolor{Violet}{The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.}
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{\max}/100$.
+\textcolor{MidnightBlue}{The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.}
 \begin{table}[H]
@@
 Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
-\textcolor{red}{ The first one is a baseline scheme, which uses random PRB allocation. 
+\textcolor{MidnightBlue}{ The first one is a baseline scheme, which uses random PRB allocation. 
 So, the allocation of PRB  to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
@@
 After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is achieved from the lemma \eqref{lemma1}.}
-\textcolor{brown}{The second one is similar to the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic}.
+\textcolor{MidnightBlue}{The second one is similar to the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic}.
 In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in \cite{lee2018dynamic}.

### 2022-03-09 Latex/journal_v2/version2/pr.tex
Add paper

--- 2021-10-20 Latex/journal_v2/version1/pr.tex
@@
 %}
-  \author{
-    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
-    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
-    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
-    \vspace{-.2cm}
-  }
-  }
+%%%%%  \author{
+%%%%%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
+%%%%%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
+%%%%%    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
+%%%%%    \vspace{-.2cm}
+%%%%%  }
+%%%%%  }
 
@@
 Also, the assignment of PRB to the slices is obtained.
-On a small-time scale, the problem of power allocation, O-RU association and the assignment of PRB to UE in each slice is applied.
+On a small-time scale, the problem of power allocation, and the assignment of PRB to UE in each slice is applied.
 \item 
-We consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, , which demand short-packet connectivity support for a massive number of low-power devices.
+We consider two types of services that requires specific QoS: URLLC, which requires low latency and high reliability; and eMBB, which needs high data rate.
 The problem of RAN slicing for different types of services is studied in this research.
@@
 \subsection{System Model}
-Assume we have $S$ preallocated slices serving $S$ services contains eMBB, URLLC, and mMTC services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC), , thus $S=S_1+S_2+S_3$.
+Assume we have $S$ preallocated slices serving $S$ services contains eMBB, and URLLC services; We consider $S_1$ slices for the eMBB service type and $S_2$ slices for the URLLC service type.
+Therefore, we have $S=S_1+S_2$.
 Each Service $s\in \{1,2,...,S\} $ consists of $U_{s}$ single-antenna user equipments (UEs) which require certain QoS to be able to use the requested program.
-There are different application requests which fall into one of these service categories.
-Each application request requires specific QoS.
-Based on the request for the application and QoS, a UE may be admitted and allocated to the resources.
+There are different application requests which fall into one of these service categories. Each application request requires specific QoS.
 Assume each slice $s \in \{1,2,...,S \}$, consists of $K_{s}$, pre-allocated physical resource blocks (PRBs) obtained in the large-time scale, $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
-Virtual network functions (VNFs) are functional blocks of the
-system. Each VNF instance is running on a virtual machine (VM) using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
-
-In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
-has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
+Virtual network functions (VNFs) are functional blocks of the system.
+Each VNF instance is running on a virtual machine (VM) using resources from the data centers.
+Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
+Moreover, we assume the system has $R$ single-antenna O-RU that serverd UEs cooperatively.
+Each O-RU $r \in \{1,2,...,R \}$ is transmitting and receiving the data of all UEs using the coordinated multipoint transmission (COMP) technology.
+Moreover, all O-RUs, have access to all PRBs.
 \subsection{The Achievable Rate}
-The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
+The SNR of $i^{th}$ UE requesting served at slice $s$ is obtained from
 \begin{equation}\label{eq2}
-\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
+\rho_{u(s,i)} =  \frac{\sum_{k=1}^{K_{s}}e_{u(s,i)}^k p_{u(s,i)}^{k}|{\bold{h}_{R,u(s,i)}^{H \: k}}|^2}{BN_0},
 \end{equation} 
-where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
-${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
-$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice.
-In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
+where $p_{u(s,i)}^{k}$ represents the transmission power allocated by O-RUs to $i^{th}$ UE served at slice $s$ on PRB $k$.
+${\bold{h}_{R,u(s,i)}^{k}} \in \mathbb{C}^{R}$ is the vector of channel gain of a wireless link from 
+O-RUs to the $i^{th}$ UE in $s^{th}$ slice. 
+Moreover, $e_{u(s,i)}^k \in \{0,1\}$ is a binary variable that illustrates whether PRB $k$ is assigned to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
+Also, $BN_0$ denotes the power of Gaussian additive noise.
+Moreover, we assume that each PRB is assigned to no more than one UEs. So we have
 \begin{equation}
-\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
+\sum_{s=1}^S \sum_{u=1}^{U_s} e_{u(s,i)}^k = 1
 \end{equation} 
-Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
-Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
-\begin{equation}\label{eqI}
-\begin{split}
-I_{r,u(s,i)}^{k} &=
- \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
-&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
-&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
-\end{split}
-\end{equation}
-where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
-$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
-
 The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
 \begin{equation}\label{eq1}
-\begin{split}
-\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
-\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
-\end{split}
+\mathcal{R}_{u(s_1,i)} =  B \log_2({1+ \rho_{r,u(s_1,i)}}),
 \end{equation}
@@
 $\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
-Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th} $, $j \in \{2,3\}$ application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
+Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{2}^{th} $, application of service type 2 (URLLC) is not achieved from Shannon Capacity formula.
 So, for the short packet transmission the achievable data rate is approximated as follow
 \begin{equation}\label{eq11}
-\begin{split}
-\mathcal{R}_{u(s_2,i)}^{\mathfrak{u},r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}, \quad \mathfrak{u} \in  \{u,m\} \\
-\mathcal{R}_{u(s_1,i)}^{\mathfrak{u}} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 
-\end{split}
+\mathcal{R}_{u(s_2,i)}^{\mathfrak{u}} =  B (\log_2({1+ \rho_{u(s_2,i)}})- \zeta_{u(s_2,i)}), 
 \end{equation}
-where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
-and $\zeta_{u(s_2,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
+where $\zeta_{u(s_2,i)} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}}{N_{u(s_2,i)}}})$
 where $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
-$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
-$N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
+$C_{u(s_2,i)} = 1 - \frac{1}{(1+\rho_{u(s_2,i)})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
+$N_{u(s_2,i)}$ represents the blocklength of it. 
 $\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
 \subsection{Mean Delay}
-In this part, the end-to-end mean delay for each service is obtained.
-Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,
+In this part, the mean processing delay for each service is obtained.
+Suppose the mean processing delay is depicted as $T_{\text{\text{proc}}}$,
 \begin{equation}
-\begin{split}
-T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
-T^{\text{\text{proc}}} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
-T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
-T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}.  \\
-\end{split}
+T^{\text{\text{proc}}} =  T^{RU} + T^{DU} + T^{CU},
 \end{equation}
-%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
-%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
-The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the propagation delay ($T^{\text{pro}}$). 
-The propagation delay is the time takes for a signal to reach its destination.
-It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the capacity of the link).
-The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
-Also, the transmission delay is the amount of time required to push all the packets into the fiber link.
-Moreover, it can formulated as 
-$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the sum-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean arrival data rate of each link.
-So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
-In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we ignore the other two delays for simplification;
-So, we assume that the total delay is approximate to the processing delay.
-%Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
-\begin{equation}
-T^{\text{\text{tot}}} \approx T^{\text{proc}}
-\end{equation}
-\subsubsection{Processing Delay}
 Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ service (or slice).
 Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
-Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$).
-so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,
+Assume the mean arrival data rate for each slice $s$ ($\alpha_{s}$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$).
+so $\alpha_{s} \approx \alpha_{s}^C \approx \alpha_{s}^D$,
 Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
@@
 T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
-T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},\\
 \end{split}
@@
 $M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively. 
-Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively.
+Moreover, $1/\mu_s^d$, and $1/\mu_s^c$ are the mean service time of the O-DU, and O-CU layers, respectively.
 Besides, $\alpha_{s}$ is the  arrival rate which is divided
 by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
-$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.
+$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c\}$.
 
@@
 
-So, the mean processing delay for UE $i$ in slice $s$ is 
+\subsection{Reliability of URLLC}
+As we know, UEs request URLLC services, require services with low latency.
+For the M/M/1 system, the probability of the delay for each application $s_2$ in the O-RU is as follow, 
 \begin{equation}
-T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
+P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}
 \end{equation} 
-Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $.
-%\subsection{Reliability of URLLC}
-%As we know, UEs request URLLC services, require services with low latency.
-%For the M/M/1 system, the probability of the delay for each application $s$ in the UPF, CU, DU and RU is as follow, respectively
-%\begin{equation}
-%\begin{split}
-%P_r\{T_{UPF}^{s} \geq T_{UPF}^{max}\} &= e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}\\
-%P_r\{T_{CU}^{s} \geq T_{CU}^{max}\} &= e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}\\
-%P_r\{T_{DU}^{s} \geq T_{DU}^{max}\} &= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}\\
-%P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} &= e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}\\
-%\end{split}
-%\end{equation} 
-%So the probability of coincidence of these events is as follow
-%\begin{equation}
-%P_r\{E_1, E_2, E_3, E_4\} = A_1 A_2 A_3 A_4,
-%\end{equation}
-%where $E_1 = T_{UPF}^{s} \geq T_{UPF}^{max}$, $E_2 =T_{CU}^{s} \geq T_{CU}^{max} $, $E_3 =T_{DU}^{s} \geq T_{DU}^{max} $ and $E_4 =T_{RU}^{s} \geq T_{RU}^{max} $.
-%Also $A_1=e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}$, $A_2=e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}$, $A_3= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}$ and $A_4 = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}$.
+Also, we do not consider the reliability for O-CU and O-DU.
 \subsection{Physical Data Center Resource}
 Each VNF requires
-physical resources that include memory, storage, CPU and Network Bandwidth.
+physical resources that include memory, and CPU.
 Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
 \begin{equation}
-\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f \},
+\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{C,{s}}^f \},
 \end{equation}
-where $\bar{\Omega}_{s}^f\in \mathbb{C}^{4}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f$ indicate the amount of required memory, storage, CPU and and Network Bandwidth, respectively.
-Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice in DU, CU and UPF is defined respectively as follows
+where $\bar{\Omega}_{s}^f\in \mathbb{C}^{2}$ and $\Omega_{M,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, and CPU, respectively.
+Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice in O-DU, and O-CU is defined respectively as follows
 \begin{equation}
@@
 &\bar{\Omega}_{\mathfrak{z},s}^{tot,c} = \sum_{f=1}^{M_{s}^c}\bar{\Omega}_{\mathfrak{z},s}^{f,c},\\
-&\bar{\Omega}_{\mathfrak{z},s}^{tot,u} = \sum_{f=1}^{M_{s}^u}\bar{\Omega}_{\mathfrak{z},s}^{f,u}, \\
 \end{split}
 \end{equation}
-$\forall \mathfrak{z} \in \{M, S, C, N\}$, where, $\bar{\Omega}_{\mathfrak{z},s}^{f,d}$, $\bar{\Omega}_{\mathfrak{z},s}^{f,c}$ and $\bar{\Omega}_{\mathfrak{z},s}^{f,u}$ are the amount of resource that a VNF required in DU, CU and UPF, respectively.
+$\forall \mathfrak{z} \in \{M, C\}$, where, $\bar{\Omega}_{\mathfrak{z},s}^{f,d}$, and $\bar{\Omega}_{\mathfrak{z},s}^{f,c}$ are the amount of resource that a VNF required in O-DU, and O-CU, respectively.
 Then,
 \begin{equation}
- \bar{\Omega}_{\mathfrak{z},s}^{tot} = \bar{\Omega}_{\mathfrak{z},s}^{tot,d}+ \bar{\Omega}_{\mathfrak{z},s}^{tot,c}+\bar{\Omega}_{\mathfrak{z},s}^{tot,u}
+ \bar{\Omega}_{\mathfrak{z},s}^{tot} = \bar{\Omega}_{\mathfrak{z},s}^{tot,d}+ \bar{\Omega}_{\mathfrak{z},s}^{tot,c}
 \end{equation} 
 Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
-The amount of memory, storage, CPU and and Network Bandwidth is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$, $\tau_{C_{j}} $ and $\tau_{N_{j}} $ for the $j^{th}$ DC, respectively
+The amount of memory, and CPU is denoted by $\tau_{M_{j}}$, and $\tau_{C_{j}} $ for the $j^{th}$ DC, respectively
 \begin{equation*}
-\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}}, \tau_{N_{j}} \},
+\tau_j = \{\tau_{M_{j}}, \tau_{C_{j}} \},
 \end{equation*}
@@
 Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is allocated the resources to the VNFs of $s^{th}$ slice or not.
-\subsection{Power of the O-RU and the Fronthaul Capacity}
-Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. We have,
-\begin{equation}\label{pr}
-P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
-\end{equation}
-Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
-%\cite{simeone2016cloud, 1111}
-\begin{equation}\label{cr}
-C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
-\end{equation}
-where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
 \subsection{Problem Statement}
@@
 \max\limits_{ \boldsymbol{M}, \boldsymbol{Y}, \boldsymbol{E},\boldsymbol{P},\boldsymbol{G} } &\eta = \frac{\sum_{s=1}^{S_1}\sum_{i=1}^{U_s}R_{u_{(s,k)}}}{\phi_{tot} +P_r}       \ \\
-\text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
- \label{c11} \\
- &\mathcal{R}_{u_{(s,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
- &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}, \quad  \mathcal{E} = \{M,S,C, N\}, \label{c14}\\
-&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
-&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
+\text{subject to} \quad  & \mathcal{R}_{u_{(s,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
+ &\mathcal{R}_{u_{(s,i)}} \leq  \mathcal{R}_{max}^{s} \quad \forall s, \label{c13-1} \\
+ &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}, \quad  \mathcal{E} = \{M,C\}, \label{c14}\\
+&p_{u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
+&p_{u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
 %&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
-& C_r \leq C^{max}_r \quad \forall r, \label{c15}\\ 
-&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\
+&T^{\text{\text{proc}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\
 & \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
@@
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
-& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
-& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18-1} \\
-& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
+& \sum_{s =1}^{S}\sum_{i=1}^{U_s} e^{k}_{u(s,i)} = 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
 & \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\
-& g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
-& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}  
+& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}\\  
+& P_r\{T_{RU}^{s_2} \geq T_{RU}^{max}\} = e^{-(R_{{tot}_{s_2}} - \alpha_{s_2})T_{RU}^{max}}\label{c22-3}
 \end{alignat}
@@
 \end{subequations}
-\noindent where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association.
-Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association.
-Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is the matrix that shows the number of VNFs in each layer of slice.
+\noindent where $\boldsymbol{P} =[p_{u(s,i)}^{k}], \:\: \forall s , \forall i,  \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{u(s,i)}^k], \:\: \forall s , \forall i,  \forall k$ indicate the binary variable for PRB association.
+Furthermore, $M = [M_s^d, M_s^c], \:\: \forall s$ is the matrix that shows the number of VNFs in each layer of slice.
 Also $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
 the physical DC is mapped to a VNFs of a slice or not.
-\eqref{c11}, \eqref{c12} and \eqref{c12-1} indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
-Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and uRLLC, is more than a threshold, respectively.
-\eqref{c15} and \eqref{c16} expressed the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
+\eqref{c12} and \eqref{c12-1} indicate that the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
+Also, \eqref{c13} and \eqref{c13-1} shows that the rate of each UE requesting each type of service, i.e., eMBB, and URLLC, has a maximum and minimum, respectively.
+In addition, in \eqref{c14}, the constraint supports that we have enough physical resources for VNFs of each slice.
+\eqref{c16} expressed the limited end-to-end delay of the received signal, respectively.
 \eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue model.
@@
 %\eqref{c16} is a reliability condition that the delay in each layer should be less than the threshold.
-\eqref{c17} and \eqref{c18-1} guarantee that O-RU and PRB are associated with the UE, respectively.
-Also, \eqref{c18} ensures that each PRB can not be assigned to more than one UE associated with the same O-RU.
+\eqref{c18} shows that each PRB are associated to no more than one UE.
 In addition, \eqref{c19} indicates that the fixed cost of energy of VNFs in each slice does not exceed the threshold. 
-Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
-In addition, in \eqref{c14}, the constraint supports that we have enough physical resources for VNFs of each slice.
+Moreover, \eqref{c21} depicts that $\boldsymbol{E}$ is a matrix of binary variables.
+Also, \eqref{c22-3}, guarantees the reliability of the URLLC services.
 \subsection{Proposed Algorithm and Numerical Results}
@@
 The assignment of PRB to slices is implemented in this time scale.
-In the small-time scale, the assignment of O-RU to UEs and the assignment of PRB of slices to UEs is executed, and the optimal power is obtained.
+In the small-time scale, the assignment of PRB of slices to UEs is executed, and the optimal power is obtained.
 In this research, we aim to use the machine learning methods such as deep reinforcement learning and deep learning to train the O-RAN system and have an intelligent system.
@@
  the multi-agent deep reinforcement learning contains DDPG (actor-critic algorithm), correlated q-learning, and the priority proportional fairness algorithm will be implemented for the small-time scale.
-The deep learning algorithms contain LSTM and recurrent neural networks. Also, transfer learning is an exciting way to enhance the performance and convergence of the system.
+The deep learning algorithms contain LSTM and recurrent neural networks.
 The proposed algorithm for the large-time scale is implemented in the following, and part of the numerical results is depicted.

### 2022-03-22 Journal1/Response1/Response.tex
add sth:

@@
 \noindent \textbf{Response:\\}
-We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can alleviate the reviewer's concerns.
+We would like to thank the reviewer for this manuscript's careful and thorough reading. We hope that the responses provided will ease the reviewer's concerns.
 
@@
 \noindent \textbf{Response:\\}
-According to this comment, we have changed the introduction and checked the entire text.
+According to this comment, we have modified the introduction and checked the entire text and correct mistakes.
 We have shortened the state of the arts and introduced our goal briefly before the main contribution section.
@@
 \noindent \textbf{Response:\\}
-The problem in (13) is feasible and has feasibility points that are discussed in subsection  IV-B, and we introduce a fast algorithm (i.e., Algorithm 3) for feasibility points.
-Although the problem is feasible, it is not convex and difficult to solve.
-Since problem in (13) is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and the problem is NP-hard.
+I would appreciate your comments to enhance and clarify this section of the paper.
+
+The problem (13) is feasible and has feasibility points discussed in Subsection IV-B, and we introduce a fast algorithm (i.e., Algorithm 3 in Subsection IV-B) for feasibility points.
+Although the problem is feasible, it is not convex and challenging to solve.
+Since problem (13) is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and by relaxing the variables, the problem is also non-convex; therefore, this problem is NP-hard.
 Solving the problem is not trivial.
 To solve the problem by inspiring Stackelberg, we reformulate the equation in (13g) to reduce one of the variables (i.e., $M_s$) that can be solved after obtaining the rate of UEs.
-WE notice that $M_s$ is similar to the followers in Stackelberg Competition and power and PRB assignment is similar to leader.
-So, the new problem has two variables of power and PRB assignment.
-This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds in (15) because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
-After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.
+We notice that $M_s$ is similar to the followers in Stackelberg Competition, and power and PRB assignment are identical to the leader.
+So, the new problem has two variables: power and PRB assignment.
+This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds (15).
+The objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
+After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs in each slice ($M_s$).
 We made changes in Subsection III-A, accordingly.
@@
 \noindent \textbf{Response:\\}
-We would like to thank the reviewer to emphasis this point and to help us for a better presentation. 
+We would like to thank the reviewer for emphasizing this point and helping us with a better exhibition.
+
  Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
+
  The first one is a baseline scheme, which uses random PRB allocation.
@@
 The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
-After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is
-achieved from Lemma (1). The second one is similar
-to the fixed BBU capacity and dynamic resource allocation
-(FBDR) algorithm proposed in [18]. In this work, we have services with different QoS that
-contain UEs, which is similar to tenants with different QoS
-that is introduced in [18]. Therefore, we used an algorithm similar
-to FBDR adapted to our conditions for comparison. Instead
-of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
-To use the FBDR method, we should consider the fixed
-BBU capacity. We assume that O-DU and O-CU have fixed
-sufficient capacity in our system model. Also, our mid-haul
-link (F1 link) has adequate capacity, so there will be no
-issue using the FBDR method by separating BBU to O-DU
-and O-CU with this assumption. In this method, PRB and power are dynamically allocated. The number of VNFs is
-obtained from the simulation. The UEs are associated with the O-RU based on the quality of their channels and the
-channel distance instead of using the greedy algorithm 1 (GAA algorithm ) for O-RU assignment. The figures in [18]
-show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same
-priority area. We will also see that our proposed algorithm performs better than FBDR in the numerical result section.
+After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma (1).
+
+For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18] and named it the dynamic resource allocation scheme (DR scheme). 
+ We have services with different QoS in this work, similar to tenants with different QoS introduced in [18].
+Therefore, we can use the DR scheme similar to the FBDR method adapted to our conditions for comparison.
+Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
+ Since we do not talk about O-DU and O-CU capacity, we use the dynamic resource allocation scheme (DR scheme) algorithm and do not consider BBU capacity.
+But also, we can assume that O-DU and O-CU have fixed sufficient capacity in our system model.
+Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the idea of the FBDR method with this assumption and using the DR scheme.
+In the DR scheme, PRB and power are dynamically allocated.
+The number of VNFs is obtained from the simulation.
+The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm 1 (GAA algorithm) for O-RU assignment.
+The figures in [18] show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area.
+The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.
 
@@
 \noindent \textbf{Response:\\}
-We would like to thank the reviewer for careful and thorough reading of this manuscript and
-for the thoughtful comments and constructive suggestions, which help us to improve the quality of
-this manuscript. We hope that the responses provided herein can alleviate the reviewer concerns.
+It is our pleasure to thank the reviewer for the careful reading of this manuscript, providing thoughtful comments, and offering constructive suggestions that strengthened and enhanced its quality.
+We hope that the responses provided herein can alleviate the reviewer's concerns.
 
@@
 \noindent \textbf{Response:\\}
+We would like to thank the reviewer for this comment to add more detail to our paper regarding end-to-end delays.
+
 Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation.
 However, they can be added to the system model easily.
-In this paper, we focus only on the processing delay to find the optimal number of VNFs, and we consider the other two delays are fixed; In the following, we describe more about these two types of delays.
+In this paper, we focus only on the processing delay to find the optimal number of VNFs, and we consider the other two delays are fixed.
+We discuss these two types of delay in detail below and explain why we do not consider them in our work.
 
 The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority.
-Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU.
-Therefore, different routes are added to the system to solve the routing problem.
-However, it provides a new system model.
-So, the connection between O-RUs to O-DUs is fixed and transparent.
+Also, the connections of O-DUs to O-CUs are the same as O-RU to O-DU.
+Therefore, different routes will be added to the system to solve the routing problem.
+Also, for URLLC and mMTC, edge processing can reduce the delay that is not considered here.
+However, it provides a new problem formulation and can be added to our system model to extend our paper in the future.
+Thus, this paper assumes that the connection between O-RUs and O-DUs is fixed and transparent, and we do not consider the problem of edge processing.
 As a result, the propagation delay is fixed and does not affect the optimization problem.
-The following is a brief calculation of propagation delay.
-Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 Km.
+The following is a brief calculation of propagation and transmission delay.
+Since the distance between the O-RU and O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
 Moreover, the distance from O-CU to the network should not exceed 200 Km [35].
@@
 You can find more about these distances in this \href{https://blogs.keysight.com/blogs/inds.entry.html/2020/06/30/5g_testing_what_is-0nzj.html\%23:~:text=The\%20data\%20requirements\%20are\%20about,DUs\%20is\%20about\%2080\%20km.}{link}.
+
 The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has a small amount.
@@
 \noindent \textbf{Response:\\}
-The processing delay can be modeled as an M/M/1 queue; since the number of arrival packets in the system are from a large number of independent sources.
+The processing delay can be modeled as an M/M/1 queue; since the system's arrival packets are from many independent sources.
 Moreover, the impact of a single packet on the system's performance is minimal.
-Also, the queue discipline will be first-in first-out (FIFO), and the arrival packet is assumed to follow a Poisson process.
+Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process.
 The system's clock is constant, and the size of the tasks is not fixed.
 So, we suppose that service times are exponentially distributed [36].
-In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services, not between UEs of one service.
-Because we assume that the UEs of a service have the same priority, their sent packets also have an equal priority.
-Also, the services are isolated, and this priority does not invalidate the queue assumption.
-Furthermore, one service's priority over another can be higher, affecting the whole optimization and not queue formulation since the UEs in each service have the same priority, and each service has its processing delay independent of other services.
+In addition, we assume that the arrival packets of each service have the same priority (in subsection II-F, we will talk about priority), and we consider priority between services, not between UEs of one service.
+As we assume that the UEs of a service have the same priority, their sent packets also have an equal priority.
+In addition, since the services are isolated, the UEs in each service have the same priority, and the processing delays of each service are independent of the other services; if we assume service priority, this priority does not invalidate the queueing theory.
+Therefore, one service could have a higher priority, affecting the whole optimization, and the M/M/1 queue theory is still validated.
 
@@
 We would like to thank the reviewer for the great suggestion they gave us.
-Since the priority is in the objective function of the equation (13), the priority has whole effect optimization.
+Since the priority is in the objective function of the equation (13), the priority has affected the whole optimization problem.
 Therefore, priority is given to the whole optimization problem, and the optimization problem obtains the number of VNFs by affecting the priority term.
-If we were to discuss the placement of VNFs on the data centers, the problem would become a knapsack or bin-packing problem, and here the prioritization would affect the resource allocation algorithm, including memory, RAM, CPU, and bandwidth.
+If we were to discuss the placement of VNFs on the data centers, the problem would become a knapsack or bin-packing problem, and here the prioritization would affect the resource allocation algorithm, including memory, RAM, CPU, and bandwidth of VNFs.
 Therefore, the algorithm was implemented based on prioritization.
+But, in this paper, we consider priority more generally.
+This is an excellent suggestion for extending this paper in the future.
+Hence, in the extension of the paper, we would talk about VNF placement, and the priority will be more different from here, and the access of VNF resources will be based on the priority.
 
@@
 \noindent \textbf{Response:\\}
-We use a method which is similar to the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18].
-In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in [18].
- Therefore, we used an algorithm similar to FBDR adapted to our conditions for comparison.  
+We appreciate the reviewer emphasizing this point and providing us with tips on how to improve our paper.
+
+For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18] and named it the dynamic resource allocation scheme (DR scheme). 
+ We have services with different QoS in this work, similar to tenants with different QoS introduced in [18].
+Therefore, we can use the DR scheme similar to the FBDR method adapted to our conditions for comparison.
 Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
-To use the FBDR method, we should consider the fixed BBU capacity.
-We assume that O-DU and O-CU have fixed sufficient capacity in our system model.
-Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the FBDR method by separating ‌BBU to O-DU and O-CU with this assumption.
-In this method, PRB and power are dynamically allocated.
+ Since we do not talk about O-DU and O-CU capacity, we use the dynamic resource allocation scheme (DR scheme) algorithm and do not consider BBU capacity.
+But also, we can assume that O-DU and O-CU have fixed sufficient capacity in our system model.
+Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the idea of the FBDR method with this assumption and using the DR scheme.
+In the DR scheme, PRB and power are dynamically allocated.
 The number of VNFs is obtained from the simulation.
-The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm 1 (GAA algorithm ) for O-RU assignment.
+The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm 1 (GAA algorithm) for O-RU assignment.
+The figures in [18] show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area.
+The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.
 
@@
 \RaggedRight
-\cellcolor{gray!15}
+\cellcolor{violet!15}
 \textbf{\noindent Comments to the Author} ``The authors propose a resource allocation scheme for network slicing in an Open RAN scenario.
@@
 Thank you for the comment.
-According to this comment, We modified the introduction of the paper.
-We have shortened the state of the arts and related literature and introduced our goal briefly before the main contribution section.
+The introduction of the paper has been modified based on this comment.
+We have shortened the description of the state of the arts and the literature and briefly explained our goal before the main contribution section.
 We removed additional information and talked more about our work.
@@
 The purpose of this paper is twofold.
-First and foremost, it is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
+First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
 Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
@@
 We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.
+
+In this paper, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
+\begin{itemize}
+\item This paper depicts a network slicing model for three different services introduced in 5G, i.e., eMBB, mMTC, and URLLC.
+Within the O-RAN architecture, the problem of radio resource allocation and VNF activation is explored.
+Based on different types of services with different QoS and service priorities, we formulate a problem for the allocation of baseband resources to maximize the weighted throughput of O-RAN.
+\item We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers.
+Therefore, we focus on obtaining the optimal number of VNFs in each layer of the O-RAN architecture.
+\item Different services need to consider varying QoS conditions, including delay, power, and throughput.
+According to the number of activated VNFs and the throughput of the users, we calculate the end-to-end processing delay of the system.
+Assuming a limited fronthaul capacity, we calculate each O-RU's actual power and capacity.
+Depending on the service type, we model the interference of neighboring O-RUs and determine the actual throughput.
+Our model accounts for the short packet transmission of URLLC, and mMTC, which cannot be modeled by the Shannon capacity theorem.
+\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
+We perform a two-step iterative algorithm to solve it.
+The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
+\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
+For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
+\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
+\end{itemize}
 
@@
 \noindent \textbf{Response:\\}
+It is my pleasure to thank you for your comment, which helped me display and rectify the system model.
 We added this part in the system model.
+
 Assume there are $K$ physical resource blocks (PRBs) in the system.
@@
 
-Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
- r$.
-UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
-Network Slicing methods significantly reduce inter-service interference.
-There are some techniques to remove inter-slice interference.
-One of these techniques is to have two-time scale scheduling.
-The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out.
+A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set of $r' \in R \not\in r$ that are using the same PRB $k$.
+Two types of interference occur between UEs in each slice; the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
+
+Network Slicing techniques significantly reduce inter-service interference.
+Some methods apply the network slicing technique in PRB scheduling to isolate PRBs in slices and remove inter-slice interference.
+One of these methods is to have two-time scale scheduling.
+The PRB scheduling to the slices is performed on the first time scale, and on the second time scale, the PRB scheduling to the UEs of slices is carried out.
 Since there are limited resources, inter-service interference cannot be eliminated entirely.
@@
 \noindent \textbf{Response:\\}
-This subsection aims to examine slice management, including creating, managing, and deleting slices.
+I am grateful for this comment that makes the paper more practical.
+
+In this subsection, we will look at the life cycle of network slicing on a practical level. 
+The goal is to examine slice management, which includes creating, managing, and deleting slices.
 Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning [38].

### 2022-03-22 Journal1/paper4TNSM/pr.tex
add sth:

--- 2022-02-09 Journal1/paper2TNSM/pr.tex
@@
 %\vspace*{-1.5em}
-Taking advantage of virtual radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
-O-RAN leads to increased flexibility, openness, reduces operational costs, and agile deployment.
+Taking advantage of virtual radio access networks (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
+Due to O-RAN, flexibility, openness, and lower operational costs will be possible.
 O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
@@
 \subsection{State Of The Arts}
-\textcolor{blue}{To achieve the desired level of QoS (quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks.
-There are several implementations of network slicing, including core slicing, RAN slicing, and both.
+\textcolor{MidnightBlue}{To achieve the desired level of QoS (i.e., quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks.
+There are diferent implementations of network slicing, including core slicing, RAN slicing, and both.
 Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-Depending on QoS, each service requires its own slice of the network.
+Depending on QoS, each service requires its slice of the network.
 The eMBB service fulfills the demand for high capacity and throughput.
 The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency.
-mMTC is comprised of many low-power internet of things (IoT) devices that transmit small payloads to a typical receiver, including sensors for sensing, metering, and monitoring
+mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads
 \cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.
@@
 
-\textcolor{OrangeRed}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS.
-We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}
-
-\textcolor{blue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
-O-RAN was developed as a result of integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both.
+\textcolor{MidnightBlue}{This paper considers a number of user equipments (UEs) requesting one of these types of services with different QoS.
+We would like to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}
+
+\textcolor{MidnightBlue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
+O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (CRAN).
 With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly.
@@
 
-O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
+\textcolor{MidnightBlue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
 In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
@@
 Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
-The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. 
-O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
+The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.}
+
+\textcolor{MidnightBlue}{This paper aims to design a RAN slicing technology for the O-RAN architecture. }
+%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
 The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence
-\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
 
@@
 
-\textcolor{blue}{In order to achieve the specific QoS for eMBB, URLLC, and mMTC, this study optimizes the allocation of baseband resources, including power allocation, PRB allocation, O-Rus association, and VNF activation to create an isolated network slicing outline.}
+\textcolor{MidnightBlue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
+As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.}
 \subsection{Related Literature}
@@
 \subsection{Main Contributions}
-The purpose of this study is to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
-Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN system.
-The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
-In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follows:
+\textcolor{MidnightBlue}{The purpose of this paper is twofold.
+First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
+Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
+Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
+In this paper, we would like to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
+Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
+The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
+We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.}
+
+In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
 \begin{itemize}
-\item This paper depicts a network slicing model for three different services introduced in 5G, i.e., eMBB, mMTC, and URLLC.
-The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
-We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for different types of services with specific QoS. 
-\item The desired QoS conditions such as delay and throughput are considered for different types of services.
-We formulate the end-to-end processing delay of the system based on the number of activated VNFs and user throughput.
-Assuming a limited fronthaul capacity, we calculate the power and capacity of each O-RU.
-We model the interference of neighboring O-RUs and formulate the actual throughput for different service types.
-Based on the short packet transmission of URLLC and mMTC, we also model their throughput.
+\item \textcolor{MidnightBlue}{This paper depicts a network slicing model for three different services introduced in 5G, i.e., eMBB, mMTC, and URLLC.
+Within the O-RAN architecture, the problem of radio resource allocation and VNF activation is explored.
+Based on different types of services with different QoS and service priorities, we formulate a problem for the allocation of baseband resources to maximize the weighted throughput of O-RAN.}
+\item \textcolor{MidnightBlue}{We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers.
+Therefore, we focus on obtaining the optimal number of VNFs in each layer of the O-RAN architecture.
+}
+\item \textcolor{MidnightBlue}{Different services need to consider varying QoS conditions, including delay, power, and throughput.
+According to the number of activated VNFs and the throughput of the users, we calculate the end-to-end processing delay of the system.
+Assuming a limited fronthaul capacity, we calculate each O-RU's actual power and capacity.
+Depending on the service type, we model the interference of neighboring O-RUs and determine the actual throughput.
+Our model accounts for the short packet transmission of URLLC, and mMTC, which cannot be modeled by the Shannon capacity theorem.}
 \item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
@@
 \section{System Model and Problem Formulation}\label{systemmodel}
-In this section, we describe the downlink system in O-RAN using RAN slicing as depicted in Figure \ref{fig:c11}. 
+In this section, we describe the downlink system in the O-RAN architecture using RAN slicing as depicted in Figure \ref{fig:c11}.
 Firstly, we present the system model.
-Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system.
+Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the o-ran system.
 Afterward, we discuss the mean delay and the power of VNFs.
@@
 \subsection{System Model}
-There are three service types including eMBB, URLLC, and mMTC which support different applications.
-There are $S_1$, $S_2$ and $S_3$ different applications for the eMBB, URLLC, and mMTC service types, respectively and we have $S = S_1 + S_2 + S_3$.
-%{\color{red} explain pre-allocated more}
-Therefore, there are $S$ pre-allocated slices serving these $S$ services;
+Assume, there are three service types including eMBB, URLLC, and mMTC which support different applications.
+Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
+Therefore, there are $S$ pre-allocated slices serving these $S$ services ($S = S_1 + S_2 + S_3$);
+Hence, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have
+$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
+$\{1,2,...,S_3\}$ set of mMTC service instances.
+Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
+There are different application requests which fall into one of these service categories.
+Each application request requires a specific QoS.
+Based on the application and QoS request, UE may be admitted and allocated to the resources.
+
 Each pre-allocated slice contains reserved VNFs for the three logical nodes:
@@
 \end{itemize}
-
-There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
-So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.
-So we have
-$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
-$\{1,2,...,S_3\}$ set of mMTC service instances.
-Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
-There are different application requests which fall into one of these service categories.
-Each application request requires a specific QoS.
-Based on the application and QoS request, UE may be admitted and allocated to the resources.
-Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
+Each slice $s \in \{1,2,...,S \}$, consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
 The VNFs of O-DU, O-CU-UP, and UPF are interconnected, defined as the Service Function Chain (SFC) in the O-RAN system.
@@
 %All $K$ PRBs can be assigned to all UEs in each service.
-\textcolor{Sepia}{ Assume we have $K$ physical resource blocks (PRBs) in this system.
-Suppose each slice s consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
+\textcolor{MidnightBlue}{ Assume there are $K$ physical resource blocks (PRBs) in this system.
+Suppose each slice $s$ consists of $\bar{K}_s$ pre-allocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
 Therefore, we have $\sum_s \bar{K}_s \leq K$.
@@
 
-\textcolor{Sepia}{Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
- r$.
-UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
-Network Slicing methods significantly reduce inter-service interference.
-There are some techniques to remove inter-slice interference.
-One of these techniques is to have two-time scale scheduling.
-The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out.
+\textcolor{MidnightBlue}{A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set of $r' \in R \not\in r$ that are using the same PRB $k$.
+Two types of interference occur between UEs in each slice; the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.}
+
+\textcolor{MidnightBlue}{Network Slicing techniques significantly reduce inter-service interference.
+Some methods apply the network slicing technique in PRB scheduling to isolate PRBs in slices and remove inter-slice interference.
+One of these methods is to have two-time scale scheduling.
+The PRB scheduling to the slices is performed on the first time scale, and on the second time scale, the PRB scheduling to the UEs of slices is carried out.
 Since there are limited resources, inter-service interference cannot be eliminated entirely.
-The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.} In this paper, we assume that the PRB scheduling is performed.
-Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
+The other method is to allocate part of the RB of eMBB services to URLLC, and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.
+In this paper, we assume that the PRB scheduling is performed.
+Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.}
 \begin{figure}
@@
 \end{figure}
-\textcolor{teal}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}
+\textcolor{MidnightBlue}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as}
 %{\color{red} use paranthesis in the following equation to clear +}
@@
 You  define on variable here.)
-\textcolor{Sepia}{Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.}
-
-\textcolor{NavyBlue}{Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
+\textcolor{MidnightBlue}{Furthermore, there is no inter-slice interference since slices are isolated. Therefore, there exist only intra-slice interference.}
+
+\textcolor{MidnightBlue}{Here, there are two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
 The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.}
-\textcolor{teal}{To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
+\textcolor{MidnightBlue}{To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
 \begin{equation}\label{eq2}
@@
 %\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
-\textcolor{teal}{where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
+\textcolor{MidnightBlue}{where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
 Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
-Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression that is shown in figure \ref{fig:pq}. 
-In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization Gaussian noise 
+Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression shown in Figure \ref{fig:pq}.
+In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }$ indicates the quantization Gaussian noise
 ($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.}
@@
 
-\textcolor{magenta}{Considering propagation and transmission delays is straightforward to add to the system, but we did not consider them for better presentation and focus on obtaining the optimal number of VNF.
-In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed for simplification;
-The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority (Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU).
-Therefore, different routes are added to the system to solve the routing problem, but we do not consider it since it changes the model and does not fit in this model.
-So, the connection between O-RUs to O-DUs is fixed and transparent.
+\textcolor{MidnightBlue}{Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation.
+However, they can be added to the system model easily.
+In this paper, we focus only on the processing delay to find the optimal number of VNFs, and we consider the other two delays are fixed.
+We discuss these two types of delay in detail below and explain why we do not consider them in our work.}
+
+\textcolor{MidnightBlue}{The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority.
+Also, the connections of O-DUs to O-CUs are the same as O-RU to O-DU.
+Therefore, different routes will be added to the system to solve the routing problem.
+Also, for URLLC and mMTC, edge processing can reduce the delay that is not considered here.
+However, it provides a new problem formulation and can be added to our system model to extend our paper in the future.
+Thus, this paper assumes that the connection between O-RUs and O-DUs is fixed and transparent, and we do not consider the problem of edge processing.
 As a result, the propagation delay is fixed and does not affect the optimization problem.
-The following is a brief calculation of propagation delay.
-Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
+The following is a brief calculation of propagation delay.}
+
+\textcolor{MidnightBlue}{Since the distance between the O-RU and O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
 Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}.
@@
 Also, due to the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced.
-But we also do not focus on edge processing in this paper.
-The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has such a small amount.
+But we also do not focus on edge processing in this paper.}
+\textcolor{MidnightBlue}{The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has such a small amount.
 In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$.
@@
 
-\textcolor{olive}{The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent.
+\textcolor{MidnightBlue}{The processing delay can be modeled as an M/M/1 queue; since the system's arrival packets are from many independent sources.
 Moreover, the impact of a single packet on the system's performance is minimal.
@@
 The system's clock is constant, and the size of the tasks is not fixed.
-So, we suppose that service times are exponentially distributed \cite{QS}.
-In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services, not between UEs of one service.
-Because we assumed that the UEs of a service have the same priority, their sent packets also have an equal priority.
-Also, the services are isolated, and this priority does not invalidate the queue assumption.
-Furthermore, one service's priority over another can be higher, affecting the whole optimization and not queue formulation since the UEs in each service have the same priority, and each service has its processing delay independent of other services.}
+So, we suppose that service times are exponentially distributed [36].
+In addition, we assume that the arrival packets of each service have the same priority (in subsection II-F, we will talk about priority), and we consider priority between services, not between UEs of one service.
+As we assume that the UEs of a service have the same priority, their sent packets also have an equal priority.
+In addition, since the services are isolated, the UEs in each service have the same priority, and the processing delays of each service are independent of the other services; if we assume service priority, this priority does not invalidate the queueing theory.
+Therefore, one service could have a higher priority, affecting the whole optimization, and the M/M/1 queue theory is still validated.
+}
 \subsection{VNF Power}
@@
 \eqref{c15} and \eqref{c16} expressed the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
-\eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue model.
+\eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue.
 \eqref{c16-3} restricted the number of VNF in each slice due to the limited resources.
@@
 \subsubsection{PRB Scheduling}\label{prb}
-\textcolor{Sepia}{ In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
+\textcolor{MidnightBlue}{ In this section, we provide a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
 We need to have an algorithm to remove the inter-slice interference before solving the problem \ref{problem}.
@@
 \subsection{Slice Management}
-\textcolor{RedViolet}{In this subsection, we want to study the management of slices. We want to talk about the creation, management, and deletion of slices.}
-
+\textcolor{MidnightBlue}{In this subsection, we will look at the life cycle of network slicing on a practical level. 
+The goal is to examine slice management, which includes creating, managing, and deleting slices.
+Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning \cite{ETSI2}.
+\begin{itemize}
+\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase.
+In this phase, the operator plans to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment.
+Also, the evaluation of requirements is performed in this step.
+\item Commissioning phase: in the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice.
+\item Operation phase: during the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated.
+As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
+\item Decommissioning phase: an NSI that is decommissioned no longer exists after this phase.
+\end{itemize}
+In the preparation phase, the evaluation of requirements is considered.
+After that, we use our algorithm to find the optimal number of VNFs for each slice and PRB assignment and power allocation.
+Therefore, in the preparation phase, we estimate our resource of slices, and in the commission phase, we allocate our resources to the slices.}
 %\vspace*{-1em}
@@
 
-In the first level, the main purpose is to allocate adequate PRBs and the power to the UEs and allocate enough activated VNFs
-to each slice. So, at this level, we would like to obtain the variables $\boldsymbol{P}, \boldsymbol{E},$ and $\boldsymbol{M}$.
+At the first level, the main purpose is to assign appropriate PRBs and power to the UEs.
+Furthermore, sufficient activated VNFs are assigned to each slice.
+Hence, at this level, we would like to obtain the variables $\boldsymbol{P}, \boldsymbol{E},$ and $\boldsymbol{M}$.
 Despite the simplification of the problem
@@
 
-\textcolor{violet}{Although the problem is feasible and it has feasibility points that are discussed in subsection \ref{fr}, it is not convex and difficult to solve.
-Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard.
-Solving the problem is complex.
-To solve the problem by inspiring Stackelberg, we reformulate the equation \eqref{c16} to reduce one of the variables ($M_s$) that can be solved after obtaining the rate of UEs ($M_s$ is similar to followers in Stackelberg Competition and power and PRB assignment is similar to leader).
-So, the new problem has two variables of power and PRB assignment.
-This new problem is convex by relaxing the binary variable (PRB assignment) and estimating the lower bounds in equation \eqref{lb1} because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
-After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.}
-
-In the following, we define a lemma to find the upper and lower bound for the optimal number of VNFs based on the achievable rates.
+\textcolor{MidnightBlue}{The problem \eqref{problem} is feasible and has feasibility points discussed in Subsection \ref{fr}, and we introduce a fast algorithm (i.e., Algorithm \ref{alg3}  in Subsection \ref{fr}) for feasibility points.
+Although the problem is feasible, it is not convex and challenging to solve.
+Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and by relaxing the variables, the problem is also non-convex; therefore, this problem is NP-hard.
+Solving the problem is not trivial.
+To solve the problem by inspiring Stackelberg, we reformulate the equation in \eqref{c16} to reduce one of the variables (i.e., $M_s$) that can be solved after obtaining the rate of UEs.
+We notice that $M_s$ is similar to the followers in Stackelberg Competition, and power and PRB assignment are identical to the leader.
+So, the new problem has two variables: power and PRB assignment.
+This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds \eqref{lb1}.
+The objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
+After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs in each slice ($M_s$).}
+
+In the following, we define a lemma to find the upper and lower bounds for the optimal number of VNFs based on the achievable rates.
 Afterward, we obtain the formula to attain the optimal number of VNFs.
@@
 \end{algorithm}
-\vspace*{-2em}
+%\vspace*{-2em}
 \section{Numerical Results and The Feasible Region}\label{NE}
@@
 Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
-We consider 25 PRBs are used in the network and the packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes.
+\textcolor{MidnightBlue}{We consider 25 PRBs in the network. The packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes \cite{ETSI1}.}
 The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$.
@@
 Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a}.
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.
+\textcolor{MidnightBlue}{The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.}
 \begin{table}[H]
@@
 Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
-\textcolor{red}{ The first one is a baseline scheme, which uses random PRB allocation. 
-So, the allocation of PRB  to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
+\textcolor{MidnightBlue}{The first one is a baseline scheme, which uses random PRB allocation.
+Therefore, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
 Also, the association of O-RU is carried out based on distance.
@@
 The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
-After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is achieved from the lemma \eqref{lemma1}.}
-\textcolor{brown}{ The second one is similar to the fixed BBU capacity and
-dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic}.
-In this work, we have services with different QoS that contain UEs, which is similar to tenants with a different QoS.
-So, we used an algorithm similar to FBDR adapted to our conditions for comparison.
- We assume here that the capacity of the O-DU (which is similar to BBU in the FBDR) is as large as the capacity of our fronthaul link so that we can use this method for our system model.
-In this method, PRB and power are dynamically allocated.
+After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma \eqref{lemma1}.}
+
+\textcolor{MidnightBlue}{For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18] and named it the dynamic resource allocation scheme (DR scheme).
+ We have services with different QoS in this work, similar to tenants with different QoS introduced in \cite{lee2018dynamic}.
+Therefore, we can use the DR scheme similar to the FBDR method adapted to our conditions for comparison.
+Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
+ Since we do not talk about O-DU and O-CU capacity, we use the dynamic resource allocation scheme (DR scheme) algorithm and do not consider BBU capacity.
+But also, we can assume that O-DU and O-CU have fixed sufficient capacity in our system model.
+Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the idea of the FBDR method with this assumption and using the DR scheme.
+In the DR scheme, PRB and power are dynamically allocated.
 The number of VNFs is obtained from the simulation.
-The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm \ref{alg1} (GAA algorithm ) for O-RU assignment.
+The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm \ref{alg1} (GAA algorithm) for O-RU assignment.
 The figures in \cite{lee2018dynamic} show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area.
-We will also see that our proposed algorithm performs better than FBDR in the next subsection.
+The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.
 }
@@
 If the number of UEs is more than the PRBs, each UE is given exactly one PRB without interference. Otherwise, the amount of interference will not be high but more than one UE will use same PRBs.
-\vspace*{-1.7em}
+%\vspace*{-1.7em}
 \subsection{Numerical Results}
@@
   \begin{minipage}[b]{0.4\textwidth}
-    \includegraphics[scale = 0.3]{Arate_ue1.eps}
+    \includegraphics[scale = 0.3]{Arate_ue1_1.eps}
     \caption{Aggregate throughput vs. number of UEs in each service}% in the presence of three services}
@@
 In figure \ref{fig:5}, the aggregate throughput is depicted vs.
-the maximum power of UE for three different instances of eMBB service using proposed method (IABV), FBDR and the baseline scheme.
+the maximum power of UE for three different instances of eMBB service using proposed method (IABV), DR scheme and the baseline scheme.
 Here, we suppose that we have 12 UEs in each service.
@@
 As you can see in the figure, increasing the maximum power increases the aggregate throughput.
-Moreover, the proposed method (IABV), gives higher aggregate rates in compared to the FBDR and the baseline scheme.
+Moreover, the proposed method (IABV), gives higher aggregate rates in compared to the DR scheme and the baseline scheme.
 \begin{figure*}%[!tbp]
@@
   \captionsetup{justification=centering}
-  \begin{minipage}[b]{0.4\textwidth}
+  \begin{minipage}[b]{0.45\textwidth}
     \includegraphics[scale = 0.3]{RatePower1.eps}
@@
   \qquad
-  \begin{minipage}[b]{0.4\textwidth}
+  \begin{minipage}[b]{0.45\textwidth}
       \includegraphics[scale = 0.3]{delay_new.eps}
-  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}% for various number of UEs}
+  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}
   \label{fig:6}
@@
   \captionsetup{justification=centering}
-  \begin{minipage}[b]{0.4\textwidth}
+  \begin{minipage}[b]{0.45\textwidth}
     \includegraphics[scale = 0.3]{delay1_new.eps}
-    \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}% for different methods}
+    \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}
   \label{fig:7}
   \end{minipage}
-  \qquad
-  \begin{minipage}[b]{0.4\textwidth}
+  \quad
+  \begin{minipage}[b]{0.45\textwidth}
        \includegraphics[scale = 0.3]{AmmTCpower.eps}
@@
 In the second step, the O-RU association is carried out.
-The performance of our proposed method (i.e., IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
+The performance of our proposed method (i.e., IABV) is compared with the baseline scheme and DR scheme in \cite{lee2018dynamic}.
 In addition, the feasible region is discussed, and the FA algorithm is introduced to check the feasibility of the initial values.
@@
 Simulation results show that the proposed method (i.e., IABV) achieves $18.6\%$ higher data rate than the baseline scheme.
-Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.
+Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than DR scheme and the baseline scheme.
 \vspace*{-0.7em}

### 2022-03-22 Latex/journal_v2/version3/pr.tex
add sth:

--- 2022-03-09 Latex/journal_v2/version2/pr.tex
@@
 
-\subsection{Main Contributions}
-In this paper, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
-Here, we examine a single-cell downlink system involving multiple network slices that share existing radio sources.
-The main contributions of
-this research are summarized as follow:
-\begin{itemize}
-\item 
-The system has a two-time scale and should be solved in two layers.
-On a large-time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed.
-Also, the assignment of PRB to the slices is obtained.
-On a small-time scale, the problem of power allocation, and the assignment of PRB to UE in each slice is applied.
-\item 
-We consider two types of services that requires specific QoS: URLLC, which requires low latency and high reliability; and eMBB, which needs high data rate.
-The problem of RAN slicing for different types of services is studied in this research.
-
-\item 
-We consider an intelligent resource allocation in the O-RAN architecture for the different services.
-Since conventional models do not perform well here because of the heterogeneous QoS requirements of each service type and the complexity of dynamic RAN slicing.
-So we must switch to machine learning and dynamic methods and find the most suitable approach.
-A dynamic strategy of resource allocation is required to solve this problem to achieve the specific QoS for each type of service in the O-RAN architecture.
- In the small-time scale, the actor-critic algorithm such as DDPG is applied to the system that is based on control policy search. This method directly searches the optimal control policy
-by estimating of the gradient with respect to the parameters
-of the control policy. In the large-time scale, the deep Q-Network is implemented which is a value based algorithm and it can find best solution for discrete action-state.
-\end{itemize}
-\section{Current State of the Research}
+\section{System Model and Problem Formulation}
 \subsection{System Model}
+%This paper deals with the challenges of heterogeneous vehicular and cellular networks.
 Assume we have $S$ preallocated slices serving $S$ services contains eMBB, and URLLC services; We consider $S_1$ slices for the eMBB service type and $S_2$ slices for the URLLC service type.
@@
 There are different application requests which fall into one of these service categories. Each application request requires specific QoS.
-Assume each slice $s \in \{1,2,...,S \}$, consists of $K_{s}$, pre-allocated physical resource blocks (PRBs) obtained in the large-time scale, $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
-Virtual network functions (VNFs) are functional blocks of the system.
-Each VNF instance is running on a virtual machine (VM) using resources from the data centers.
-Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
+Assume our system consists of $K$, pre-allocated physical resource blocks (PRBs).
+Moreover, the system  consider to have $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP.
+Virtual network functions (VNFs) are functional blocks of the system. Each VNF instance is running on a virtual machine (VM) using resources from the data centers. 
 Moreover, we assume the system has $R$ single-antenna O-RU that serverd UEs cooperatively.
@@
 \subsection{The Achievable Rate}
+The eMBB services typically use more than a one-time slot.
+But URLLC services use part of a time slot (mini-slot) since it has short packet transmission.
+In addition, the URLLC must be punctured as soon as it has requested service as it requires very low latency.
+
 The SNR of $i^{th}$ UE requesting  served at slice $s$ is obtained from

### 2022-03-25 Journal1/_-4ex/Response.tex
add paper 2

--- 2022-03-22 Journal1/Response1/Response.tex
@@
 We removed additional information and talked more about our work.
-Also, we add some figures to describe incomprehensible parts.
+Also, we added some figures to describe incomprehensible parts.
 In addition, we provide further explanations.
@@
 \noindent \textbf{Response:\\}
-I would appreciate your comments to enhance and clarify this section of the paper.
+We would appreciate your comments to enhance and clarify this section of the paper.
 
-The problem (13) is feasible and has feasibility points discussed in Subsection IV-B, and we introduce a fast algorithm (i.e., Algorithm 3 in Subsection IV-B) for feasibility points.
+The problem in (13) is feasible and has feasibility points discussed in Subsection IV-B, and we introduce a fast algorithm (i.e., Algorithm 3 in Subsection IV-B) for feasibility points.
 Although the problem is feasible, it is not convex and challenging to solve.
-Since problem (13) is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and by relaxing the variables, the problem is also non-convex; therefore, this problem is NP-hard.
-Solving the problem is not trivial.
-To solve the problem by inspiring Stackelberg, we reformulate the equation in (13g) to reduce one of the variables (i.e., $M_s$) that can be solved after obtaining the rate of UEs.
-We notice that $M_s$ is similar to the followers in Stackelberg Competition, and power and PRB assignment are identical to the leader.
+Problem in (13) is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$.
+By relaxing the variables, the problem is still non-convex and non-trivial to solve.
+Inspiring by Stackelberg fomrulation, we reformulate the equation in (13g) to reduce one of the variables (i.e., $M_s$) that can be solved after obtaining the rate of UEs.
+We formulatre $M_s$ as the followers in Stackelberg Competition, and power and PRB assignment as the the leaders.
 So, the new problem has two variables: power and PRB assignment.
-This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds (15).
+This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds in (15).
 The objective function and constraints of the problem are convex and can be solved by the Lagrangian function.

### 2022-03-25 Journal1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (3)/pr.tex
add paper 2

--- 2022-03-22 Journal1/paper4TNSM/pr.tex
@@
 Taking advantage of virtual radio access networks (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
-Due to O-RAN, flexibility, openness, and lower operational costs will be possible.
+Using O-RAN architecture, flexibility, openness, and lower operational costs would be achievable in the network.
 O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
@@
 There are diferent implementations of network slicing, including core slicing, RAN slicing, and both.
-Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-Depending on QoS, each service requires its slice of the network.
+5G wireless systems are designed to provide three possible type of services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
+To achieve the QoS, each service requires its slice from the network.
 The eMBB service fulfills the demand for high capacity and throughput.
-The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency.
+The URLLC services include  autonomous vehicles, tactile internet, remote surgery services, and other services of high reliability and low latency.
 mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads
@@
 
-\textcolor{MidnightBlue}{This paper considers a number of user equipments (UEs) requesting one of these types of services with different QoS.
-We would like to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}
-
-\textcolor{MidnightBlue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
+\textcolor{MidnightBlue}{This paper considers a number of user equipments (UEs) requesting one of these types of services with specific QoS requirment.
+We would like to study the RAN slicing problem where service isolation is taken into account.}
+
+\textcolor{MidnightBlue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of RAN.
 O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (CRAN).
 With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly.
-The CRAN divides the radio remote head (RRH) and baseband unit (BBU) into two major parts.
+CRAN divides the RAN into two major parts, the radio remote head (RRH) and baseband unit (BBU).
 Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
@@
 
-\textcolor{MidnightBlue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
-In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
+\textcolor{MidnightBlue}{O-RU is a logical node that contains RF and lower PHY.
+Moreover, O-DU expresses a logical node with higher PHY, MAC, and RLC.
+In addition, O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP).
+O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
 O-DU and O-CU are connected via an open and well-defined interface $F_1$.
@@
 
-\textcolor{MidnightBlue}{This paper aims to design a RAN slicing technology for the O-RAN architecture. }
 %O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
@@
 
-\textcolor{MidnightBlue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
+\textcolor{MidnightBlue}{This paper aims to formulate RAN slicing for O-RAN architecture.
+This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
 As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.}
@@
 The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity.
-Also, the allocation of power and physical resource blocks (PRB) is performed in the lower level.
+Also, the allocation of power and physical resource blocks (PRB) are performed in the lower level.
 In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it.
@@
 \textcolor{MidnightBlue}{The purpose of this paper is twofold.
-First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
+First and foremost, our goal is to design a system in the O-RAN architecture with three types of services, namely, eMBB, URLLC, and mMTC.
 Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
@@
 We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
-Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
+Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the open and flexible O-RAN architecture.
 The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
-We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.}
-
-In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
+We also convexify and solve complex problems to obtain optimal resources.}
+
+In this paper, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
 \begin{itemize}
@@
 Based on different types of services with different QoS and service priorities, we formulate a problem for the allocation of baseband resources to maximize the weighted throughput of O-RAN.}
-\item \textcolor{MidnightBlue}{We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers.
+\item \textcolor{MidnightBlue}{We have consider the processing delay and the VNF resources needed for the slice compared to other papers.
 Therefore, we focus on obtaining the optimal number of VNFs in each layer of the O-RAN architecture.
 }
-\item \textcolor{MidnightBlue}{Different services need to consider varying QoS conditions, including delay, power, and throughput.
+\item \textcolor{MidnightBlue}{Different services require different QoS levels, including delay, power, and throughput.
 According to the number of activated VNFs and the throughput of the users, we calculate the end-to-end processing delay of the system.
@@
 Our model accounts for the short packet transmission of URLLC, and mMTC, which cannot be modeled by the Shannon capacity theorem.}
-\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
-We perform a two-step iterative algorithm to solve it.
+\item The main problem is mixed-integer non-linear programming that is non-trivial to solve.
+We deploy a two-step iterative algorithm to solve it.
 The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
-\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
-For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
-\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
+\item We reformulate and simplify the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use Lagrangian function and KKT conditions to find optimal power and PRB allocation.
+For the second step, the problem of O-RU association can be converted to a multiple Knapsack problem and solved by the Greedy algorithm.
+\item A discussion on the selection of the initial point and the feasible region for the numerical results are provided.
+We introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
 \end{itemize}

### 2022-03-25 Latex/journal_v2/version3/pr.tex
add paper 2

@@
 %This paper deals with the challenges of heterogeneous vehicular and cellular networks.
-Assume we have $S$ preallocated slices serving $S$ services contains eMBB, and URLLC services; We consider $S_1$ slices for the eMBB service type and $S_2$ slices for the URLLC service type.
-Therefore, we have $S=S_1+S_2$.
-Each Service $s\in \{1,2,...,S\} $ consists of $U_{s}$ single-antenna user equipments (UEs) which require certain QoS to be able to use the requested program.
-There are different application requests which fall into one of these service categories. Each application request requires specific QoS.
-Assume our system consists of $K$, pre-allocated physical resource blocks (PRBs).
-Moreover, the system  consider to have $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP.
-Virtual network functions (VNFs) are functional blocks of the system. Each VNF instance is running on a virtual machine (VM) using resources from the data centers. 
-Moreover, we assume the system has $R$ single-antenna O-RU that serverd UEs cooperatively.
-Each O-RU $r \in \{1,2,...,R \}$ is transmitting and receiving the data of all UEs using the coordinated multipoint transmission (COMP) technology.
-Moreover, all O-RUs, have access to all PRBs.
+Assume we have two preallocated slices serving two services, eMBB, and URLLC services; 
+eMBB Service consists of $U_{1}$ single-antenna user equipments (UEs) and URLLC service consists of $U_2$ UEs.
+Assume our system consists of $K$, preallocated physical resource blocks (PRBs).
+Moreover, the system considers to have $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP of eMBB and URLLC ($ s \in \{1, 2\}$).
+Virtual network functions (VNFs) are functional blocks of the system. Each VNF instance runs on a virtual machine (VM) using resources from the data centers. 
+Moreover, we assume there is a cell with one multi-antenna O-RU that serves UEs.
 \subsection{The Achievable Rate}
@@
 
-The SNR of $i^{th}$ UE requesting  served at slice $s$ is obtained from
-\begin{equation}\label{eq2}
-\rho_{u(s,i)} =  \frac{\sum_{k=1}^{K_{s}}e_{u(s,i)}^k p_{u(s,i)}^{k}|{\bold{h}_{R,u(s,i)}^{H \: k}}|^2}{BN_0},
+%The SNR of $i^{th}$ UE requesting served at slice $ss \in \{1, 2\}$ is obtained from
+%\begin{equation}\label{eq2}
+%\rho_{u(s,i)} =  \frac{\sum_{k=1}^{K_{s}}e_{u(s,i)}^k p_{u(s,i)}^{k}|{\bold{h}_{R,u(s,i)}^{H \: k}}|^2}{BN_0},
+%\end{equation} 
+%where $p_{u(s,i)}^{k}$ represents the transmission power allocated by O-RUs to $i^{th}$ UE served at slice $s$ on PRB $k$.
+%${\bold{h}_{R,u(s,i)}^{k}} \in \mathbb{C}^{R}$ is the vector of channel gain of a wireless link from 
+%O-RUs to the $i^{th}$ UE in $s^{th}$ slice. 
+%Moreover, $e_{u(s,i)}^k \in \{0,1\}$ is a binary variable that illustrates whether PRB $k$ is assigned to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
+%Also, $BN_0$ denotes the power of Gaussian additive noise.
+%Moreover, we assume that each PRB is assigned to no more than one UEs. So we have
+%\begin{equation}
+%\sum_{s=1}^S \sum_{u=1}^{U_s} e_{u(s,i)}^k = 1
+%\end{equation} 
+The achievable data rate for the $i^{th}$ UE request eMBB slice can be written as $\mathcal{R}_{i}^{e}(t)$.
+\begin{equation}\label{eq1}
+\mathcal{R}_{i}^e(t) = \sum_{k = 1}^K e^k_i(t) B (1-\frac{n^k_i(t)}{S}) \log_2({1+\frac{p^k_i(t)h^k_i(t)}{B \times N_0}}),
 \end{equation}
-where $p_{u(s,i)}^{k}$ represents the transmission power allocated by O-RUs to $i^{th}$ UE served at slice $s$ on PRB $k$.
-${\bold{h}_{R,u(s,i)}^{k}} \in \mathbb{C}^{R}$ is the vector of channel gain of a wireless link from 
-O-RUs to the $i^{th}$ UE in $s^{th}$ slice. 
-Moreover, $e_{u(s,i)}^k \in \{0,1\}$ is a binary variable that illustrates whether PRB $k$ is assigned to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
-Also, $BN_0$ denotes the power of Gaussian additive noise.
-Moreover, we assume that each PRB is assigned to no more than one UEs. So we have
-\begin{equation}
-\sum_{s=1}^S \sum_{u=1}^{U_s} e_{u(s,i)}^k = 1
-\end{equation} 
-The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
-\begin{equation}\label{eq1}
-\mathcal{R}_{u(s_1,i)} =  B \log_2({1+ \rho_{r,u(s_1,i)}}),
-\end{equation}
-where $B$ is the bandwidth of system. 
-$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
-Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{2}^{th} $, application of service type 2 (URLLC) is not achieved from Shannon Capacity formula.
+where $B$ is the bandwidth of RBs. Also, $B\times N_0$ denotes the power of Gaussian additive noise. 
+Moreover, $e^k_i(t)\in \{0,1\}$ is a binary variable that illustrates whether PRB $k$ is assigned to the $i^{th}$ eMBB UE or not. 
+$p^k_i(t)$ represents the transmission power allocated by O-RU to $i^{th}$ UE of eMBB using PRB $k$.
+$h^k_i(t)$ is the channel gain of a wireless link from 
+O-RU to the $i^{th}$ eMBB UE using $k^{th}$ PRB. In addition, $S$ is the total number of mini-slots of a PRB. 
+Furthermore, $n^k_i(t)$ is the number of URLLC punctured slots.
+
+Since the blocklength in URLLC is finite, the achievable data rate for the $j^{th}$ UE request in the URLLC service, is not achieved from Shannon Capacity formula.
 So, for the short packet transmission the achievable data rate is approximated as follow
 \begin{equation}\label{eq11}
-\mathcal{R}_{u(s_2,i)}^{\mathfrak{u}} =  B (\log_2({1+ \rho_{u(s_2,i)}})- \zeta_{u(s_2,i)}), 
+\mathcal{R}_{j}^u(t) = \sum_{i = 1}^{U_1}\sum_{k=1}^K \frac{n^k_i(t)e^k_i(t)}{S \times U_2} B \log_2({1+\frac{p^k_j(t)h^k_j(t)}{B \times N_0}})- \zeta_{j}^k(t)), 
 \end{equation}
-where $\zeta_{u(s_2,i)} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}}{N_{u(s_2,i)}}})$
+
+where $\zeta_{j}^k(t) = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{j}^k(t)}{N_{j}^k(t)}})$
 where $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
-$C_{u(s_2,i)} = 1 - \frac{1}{(1+\rho_{u(s_2,i)})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
-$N_{u(s_2,i)}$ represents the blocklength of it. 
-$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
+$C_{j}^k(t) = 1 - \frac{1}{(1+\rho_{j}^k(t))^2}$ depicts the channel dispersion of UE $j$ of URLLC, puncturing mini-slots of PRB $k$ and
+$N_{j}^k(t)$ represents the blocklength of it. Moreover, $\rho_{j}^k(t)=\frac{p^k_j(t)h^k_j(t)}{B \times N_0}$ is the SNR of UE $j$ in URLLC service.
+
+The channel gain is assumed to be known with errors, the imperfection of channel estimation is
+modeled as follows
+\begin{equation}
+h^k_j(t) = \hat{h}^k_j(t) + \Delta h^k_j(t)
+\end{equation}
+Where, $\Delta h^k_j(t)$ denotes the estimation error with a Guassian distribution of
+ \begin{equation}
+\Delta h^k_j(t)\backsim \mathcal{N}(0,\boldsymbol{\phi^k}^2),
+\end{equation}
 \subsection{Mean Delay}
@@
 \begin{equation}
-T^{\text{\text{proc}}} =  T^{RU} + T^{DU} + T^{CU},
+T^{\text{proc}} =  T^{RU} + T^{DU} + T^{CU},
 \end{equation}
-Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ service (or slice).
-Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
-Assume the mean arrival data rate for each slice $s$ ($\alpha_{s}$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$).
-so $\alpha_{s} \approx \alpha_{s}^C \approx \alpha_{s}^D$,
+Assume the packet arrival of URLLC UEs follows a Poisson process with arrival rate $\lambda_{j}$ for the $j^{th}$ UE.
+Therefore, the mean arrival data rate of the O-CU-UP layer is $\alpha^C = \sum_{j=1}^{U_2}\lambda_{j}$.
+Assume the mean arrival data rate for URLLC slice ($\alpha$) is approximately equal to the mean arrival data rate of the  the O-DU ($\alpha^D$). so $\alpha = \alpha^C \approx \alpha^D$,
 Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
-Since, by using Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still poisson with rate $\alpha_{s}$.
+Since, by using Burke’s theorem, the mean arrival data rate of the second layer, which are processed in the first layer, is still poisson with rate $\alpha$.
 It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
@@
 Each packet is processed by one of the VNFs of a slice.
-So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
+So, the mean delay for the URLLC slice in the O-DU,and the O-CU is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
 \begin{equation}
 \begin{split}
-T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
-T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
+T^{DU} &= \frac{1}{\mu^d - \alpha/{M^{d}}},\\
+T^{CU} &= \frac{1}{\mu^c - \alpha/{M^{c}}},\\
 \end{split}
 \end{equation}
-where $M_s^{d}$, $M_s^{c}$ and 
-$M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively. 
-Moreover, $1/\mu_s^d$, and $1/\mu_s^c$ are the mean service time of the O-DU, and O-CU layers, respectively.
-Besides, $\alpha_{s}$ is the  arrival rate which is divided
-by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
-$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c\}$.
+where $M^{d}$,and $M^{c}$ are the variables that depict the number of VNFs in O-DU,and O-CU-UP, respectively. 
+Moreover, $1/\mu^d$, and $1/\mu^c$ are the mean service time of the O-DU, and O-CU layers, respectively.
+Besides, $\alpha$ is the  arrival rate which is divided
+by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for URLLC slice  is $\alpha/{M^{l}}$ $ l \in \{d,c\}$.
 
-$T_{u(s,i)}^{RU}$ is the mean transmission delay of the $i^{th}$ UE of the $s^{th}$ service on the wireless link.
- The arrival data rate of wireless link for each UE $i$ of service $s$ is $\lambda_{u(s,i)}$
-As a result, we have $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
-Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
-an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
+$T_{j}^{RU}$ is the mean transmission delay of the $j^{th}$ UE of the URLLC service on the wireless link.
+ The arrival data rate of wireless link for each UE $j$ of URLLC service is $\lambda_j$
+As a result, we have $\sum_{j = 1}^{U_2} \lambda_{j} = \alpha$.
+Moreover, The service time of transmission queue for UE $j$ requesting URLLC service has
+an exponential distribution with mean $1/R_{j}^u$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
 
-Therefore, the mean delay of the transmission layer for UE $i$ in slice $s$ is
+Therefore, the mean delay of the transmission layer for UE $j$ in URLLC slice is
 \begin{equation}
- T_{u(s,i)}^{RU} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}}.
+ T_{j}^{RU} = \frac{1}{R_{j}^u - \lambda_{j}}.
 \end{equation}
@@
 As we know, UEs request URLLC services, require services with low latency.
-For the M/M/1 system, the probability of the delay for each application $s_2$ in the O-RU is as follow, 
+For the M/M/1 system, the probability of the delay for URLLC service in the O-RU is as follow, 
 \begin{equation}
-P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}
+P_r\{T_{j}^{RU} \geq T_{RU}^{max}\} = e^{-(R_{tot}^u - \alpha)T_{RU}^{max}}
 \end{equation} 
+where, $R_{tot}^u = \sum_{j =1}^{U_2}R_{j}^u$
 Also, we do not consider the reliability for O-CU and O-DU.
-\subsection{Physical Data Center Resource}
-Each VNF requires
-physical resources that include memory, and CPU.
-Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
-\begin{equation}
-\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{C,{s}}^f \},
-\end{equation}
-where $\bar{\Omega}_{s}^f\in \mathbb{C}^{2}$ and $\Omega_{M,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, and CPU, respectively.
-Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice in O-DU, and O-CU is defined respectively as follows
-\begin{equation}
-\begin{split}
-&\bar{\Omega}_{\mathfrak{z},s}^{tot,d} = \sum_{f=1}^{M_{s}^d}\bar{\Omega}_{\mathfrak{z},s}^{f,d},\\
-&\bar{\Omega}_{\mathfrak{z},s}^{tot,c} = \sum_{f=1}^{M_{s}^c}\bar{\Omega}_{\mathfrak{z},s}^{f,c},\\
-\end{split}
-\end{equation}
-$\forall \mathfrak{z} \in \{M, C\}$, where, $\bar{\Omega}_{\mathfrak{z},s}^{f,d}$, and $\bar{\Omega}_{\mathfrak{z},s}^{f,c}$ are the amount of resource that a VNF required in O-DU, and O-CU, respectively.
-Then,
-\begin{equation}
- \bar{\Omega}_{\mathfrak{z},s}^{tot} = \bar{\Omega}_{\mathfrak{z},s}^{tot,d}+ \bar{\Omega}_{\mathfrak{z},s}^{tot,c}
-\end{equation} 
-Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
-The amount of memory, and CPU is denoted by $\tau_{M_{j}}$, and $\tau_{C_{j}} $ for the $j^{th}$ DC, respectively
-\begin{equation*}
-\tau_j = \{\tau_{M_{j}}, \tau_{C_{j}} \},
-\end{equation*}
-In this system model, the assignment of physical DC resources to VNFs is considered.
-Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is allocated the resources to the VNFs of $s^{th}$ slice or not.
+
 \subsection{Problem Statement}
@@
 %\end{equation}
-Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
-$\phi_{s}$. So the total power of the system for all active DCs that are connected to slices can be represented as
-\begin{equation*}
-\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s} + \sum_{d=1}^{D_c}z_d \psi_d .
-\end{equation*}
-where, $z_d$ is shown that whether the $d^{th}$ DC is active or not and $\psi_d$ is a static cost when a DC is active, i.e.,
-\begin{equation}
-  z_d =
-    \begin{cases}
-      1 & \sum_{s=1}^{S}y_{s,d} \geq 1 \\
-      0 & \text{otherwise}
-    \end{cases}       
-\end{equation}  
-Here, we assume that if any VNF placed in a server $d$ is used, the server is on and active, otherwise, it is off.
-In addition, $\phi_{s}$ is obtained from below
-\begin{equation}
-\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d
-\end{equation}
-where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively.
-Here, we want to maximize the energy efficiency $\eta$. 
-So the optimization problem is formulated as follow
+The optimization problem is formulated as follow
 
@@
 \begin{alignat}{4}
-\max\limits_{ \boldsymbol{M}, \boldsymbol{Y}, \boldsymbol{E},\boldsymbol{P},\boldsymbol{G} } &\eta = \frac{\sum_{s=1}^{S_1}\sum_{i=1}^{U_s}R_{u_{(s,k)}}}{\phi_{tot} +P_r}       \ \\
-\text{subject to} \quad  & \mathcal{R}_{u_{(s,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
- &\mathcal{R}_{u_{(s,i)}} \leq  \mathcal{R}_{max}^{s} \quad \forall s, \label{c13-1} \\
- &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}, \quad  \mathcal{E} = \{M,C\}, \label{c14}\\
-&p_{u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
-&p_{u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
-%&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
-&T^{\text{\text{proc}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\
-& \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
-& \mathcal{R}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\
-& 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\
-%& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
-& \sum_{s =1}^{S}\sum_{i=1}^{U_s} e^{k}_{u(s,i)} = 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
-& \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\
-& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}\\  
-& P_r\{T_{RU}^{s_2} \geq T_{RU}^{max}\} = e^{-(R_{{tot}_{s_2}} - \alpha_{s_2})T_{RU}^{max}}\label{c22-3}
+\max\limits_{ \boldsymbol{E}, \boldsymbol{N},\boldsymbol{M} } &  \sum_i R_{i}^e(t) - \eta \sum_j T^{\text{proc}, u}(t)       \ \\
+\text{subject to} \quad  & \mathcal{R}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in U_1, \label{p1} \\
+& Pr\{{R}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon \label{p2}\\
+&T^{\text{proc}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in U_2 \label{p3} \\
+&Pr\{T^{\text{proc}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in U_2 \label{p4} 
 \end{alignat}
@@
 \end{subequations}
-\noindent where $\boldsymbol{P} =[p_{u(s,i)}^{k}], \:\: \forall s , \forall i,  \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{u(s,i)}^k], \:\: \forall s , \forall i,  \forall k$ indicate the binary variable for PRB association.
-Furthermore, $M = [M_s^d, M_s^c], \:\: \forall s$ is the matrix that shows the number of VNFs in each layer of slice.
-Also $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
-the physical DC is mapped to a VNFs of a slice or not.
-\eqref{c12} and \eqref{c12-1} indicate that the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
-Also, \eqref{c13} and \eqref{c13-1} shows that the rate of each UE requesting each type of service, i.e., eMBB, and URLLC, has a maximum and minimum, respectively.
-In addition, in \eqref{c14}, the constraint supports that we have enough physical resources for VNFs of each slice.
-\eqref{c16} expressed the limited end-to-end delay of the received signal, respectively.
-\eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue model.
-\eqref{c16-3} restricted the number of VNF in each slice due to the limited resources.
-%\eqref{c16} is a reliability condition that the delay in each layer should be less than the threshold.
-\eqref{c18} shows that each PRB are associated to no more than one UE.
-In addition, \eqref{c19} indicates that the fixed cost of energy of VNFs in each slice does not exceed the threshold. 
-Moreover, \eqref{c21} depicts that $\boldsymbol{E}$ is a matrix of binary variables.
-Also, \eqref{c22-3}, guarantees the reliability of the URLLC services.
-\subsection{Proposed Algorithm and Numerical Results}
-Problem \eqref{mainP}, is a two-time scale problem, i.e., large time scale and small time scale.
-On a large-time scale, we aim to minimize the power of servers and obtain the QoS of slices.
-The assignment of PRB to slices is implemented in this time scale.
-In the small-time scale, the assignment of PRB of slices to UEs is executed, and the optimal power is obtained.
-In this research, we aim to use the machine learning methods such as deep reinforcement learning and deep learning to train the O-RAN system and have an intelligent system.
-The deep Q-learning is implemented for the large-time scale and 
- the multi-agent deep reinforcement learning contains DDPG (actor-critic algorithm), correlated q-learning, and the priority proportional fairness algorithm will be implemented for the small-time scale.
-The deep learning algorithms contain LSTM and recurrent neural networks.
-The proposed algorithm for the large-time scale is implemented in the following, and part of the numerical results is depicted.
-\subsubsection{Proposed Algorithm}
-Here we use the reinforcement learning method to solve the above two problems.
-In the Q-learning method for the large-time scale, an agent tries to find the optimal value in a specific environment.
-This interactive process is modeled as a Markov decision-making process that includes $ (S, A, R, P, \gamma) $.
-S represents the state space matrix, and A represents the action vector.
-R is also the reward of action.
-$ P (.
-| S, a) $ is the probability of transfer and $ \gamma \in (0,1] $ is the discount factor.
-The $ \Pi (.
-| S) $ policy is a mapping of the state to the distribution of actions.
-The value-state function for state s under policy $ \Pi (.
-| S) $ with $ V^{\Pi} (s) $ indicates that the expected return value in state s under policy $ \Pi (.
-| S) ) $.
-The value of performing operation a in state s under the $ \Pi (.
-| S) $ policy is represented by $ Q ^ {\Pi} (s, a) $.
-We have the following relations on this basis.
-\begin{equation}
-	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[\sum_{t=0}^{\infty}\gamma^tR_t|S_0=s]
- \end{equation}
- The Q-value is as below.
- \begin{equation}
-	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[\sum_{t=0}^{\infty}\gamma^tR_t|S_0=s,A_0=a].
-\end{equation}
-
-  $\mathbb{E}$ represented the statistical average. 
- Based on the Bellman equation we have
- \begin{equation}
-	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[R+\gamma V^{\Pi}(s')]
-\end{equation}  
- and also, 
-   \begin{equation}
-  	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[R+\gamma Q^{\Pi}(s',a')]
-  \end{equation}  
-  where, $s'$ and $a'$ can be obtained from $\Pi(.|s')$ and $P(.|s,a)$.
-The goal of reinforcement learnin is to obtain the optimal policy to maximize the $Q^{\Pi}(s,a)$.
-So, using Bellman equation, we have
-\begin{equation}
-	Q^{*}(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q^{*}(s',a')].
-\end{equation} 
-Also, $T^*$ is the Bellman operator
-\begin{equation}
-	T^{*}Q(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q(s',a')]
-\end{equation} 
-By using this operator iteratively, 
-$Q_{t+1}(s,a) \leftarrow T^{*}Q(s,a) $
-the algorithm can converge
-$Q_{t}(s,a) \rightarrow Q^*(s,a)$.
- $t \rightarrow \infty $
-\cite{montague1999reinforcement,gan1}.
-In the Q-learning in each episode we have
-\begin{equation}
-	Q(s_{t+1},a_{t+1}) = Q(s_t,a_t)+\alpha[ r_{t+1} + \gamma \max_{a \in A}{Q(s_{t+1},a)}-Q(s_t,a_t)]
-\end{equation}
-where, $\alpha$ is the learning rate.
+where, \eqref{p2}, supports the reliability of eMBB while puncturing the URLLC.
 

### 2022-03-31 Latex/journal_v2/version3/pr.tex
system model before change

@@
 
-\title{Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}
+\title{RB scheduling for different slices of eMBB and URLLC in the O-RAN system \vspace{-.1cm}
 }
@@
 In addition, the URLLC must be punctured as soon as it has requested service as it requires very low latency.
+Our current work allocates RBs to eMBB users at the beginning of each time slot using the PF principle, a scheduling strategy that balances throughput with fairness \cite{shi2022risk}.
 
-%The SNR of $i^{th}$ UE requesting served at slice $ss \in \{1, 2\}$ is obtained from
-%\begin{equation}\label{eq2}
-%\rho_{u(s,i)} =  \frac{\sum_{k=1}^{K_{s}}e_{u(s,i)}^k p_{u(s,i)}^{k}|{\bold{h}_{R,u(s,i)}^{H \: k}}|^2}{BN_0},
-%\end{equation} 
-%where $p_{u(s,i)}^{k}$ represents the transmission power allocated by O-RUs to $i^{th}$ UE served at slice $s$ on PRB $k$.
-%${\bold{h}_{R,u(s,i)}^{k}} \in \mathbb{C}^{R}$ is the vector of channel gain of a wireless link from 
-%O-RUs to the $i^{th}$ UE in $s^{th}$ slice. 
-%Moreover, $e_{u(s,i)}^k \in \{0,1\}$ is a binary variable that illustrates whether PRB $k$ is assigned to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
-%Also, $BN_0$ denotes the power of Gaussian additive noise.
-%Moreover, we assume that each PRB is assigned to no more than one UEs. So we have
-%\begin{equation}
-%\sum_{s=1}^S \sum_{u=1}^{U_s} e_{u(s,i)}^k = 1
-%\end{equation} 
 The achievable data rate for the $i^{th}$ UE request eMBB slice can be written as $\mathcal{R}_{i}^{e}(t)$.
@@
 O-RU to the $i^{th}$ eMBB UE using $k^{th}$ PRB. In addition, $S$ is the total number of mini-slots of a PRB. 
-Furthermore, $n^k_i(t)$ is the number of URLLC punctured slots.
+Furthermore, $n^k_i(t)$ is the number of URLLC punctured slots that is denoted as follow,
+\begin{equation}
+n^k_i(t) = \sum_{j=1}^{U_2}{\zeta}_j(t)\tau \mathfrak{N} 
+\end{equation}
 

### 2022-04-05 Latex/journal_v2/version3/pr.tex
write paper 2 draft

@@
 
-\title{RB scheduling for different slices of eMBB and URLLC in the O-RAN system \vspace{-.1cm}
+\title{Dynamic RB scheduling for different slices of eMBB and URLLC in the O-RAN system \vspace{-.1cm}
 }
@@
   \caption{Network sliced ORAN system}
-  \label{fig:c11}
+  \label{fig:1}
 \end{figure*}
@@
 %This paper deals with the challenges of heterogeneous vehicular and cellular networks.
-Assume we have two preallocated slices serving two services, eMBB, and URLLC services; 
-eMBB Service consists of $U_{1}$ single-antenna user equipments (UEs) and URLLC service consists of $U_2$ UEs.
+Assume we have two different services, namely, eMBB and URLLC; 
+The system is serving a set of $\mathcal{U}_1$ eMBB single-antenna user equipments (UEs) and a set of $\mathcal{U}_2$ URLLC UEs.
 Assume our system consists of $K$, preallocated physical resource blocks (PRBs).
@@
 Moreover, we assume there is a cell with one multi-antenna O-RU that serves UEs.
+Furthermore, we suppose the channel distribution is known.
 \subsection{The Achievable Rate}
 The eMBB services typically use more than a one-time slot.
-But URLLC services use part of a time slot (mini-slot) since it has short packet transmission.
+But URLLC services use part of a time slot (mini-slot) since it has short packet transmission that it is indicated in Fig \ref{fig:2}.
 In addition, the URLLC must be punctured as soon as it has requested service as it requires very low latency.
+\begin{figure}
+  \centering 
+    \includegraphics[scale = 0.4]{EU.pdf}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{RB scheduling}
+  \label{fig:2}
+\end{figure}
 Our current work allocates RBs to eMBB users at the beginning of each time slot using the PF principle, a scheduling strategy that balances throughput with fairness \cite{shi2022risk}.
 
-The achievable data rate for the $i^{th}$ UE request eMBB slice can be written as $\mathcal{R}_{i}^{e}(t)$.
+The achievable data rate and the expectation of the achivable data rate for the $i^{th}$ UE request eMBB slice can be written as $\mathcal{R}_{i}^{e}(t)$, and $\bar{\mathcal{R}}_{i}^e(t)$, respectively.
 \begin{equation}\label{eq1}
-\mathcal{R}_{i}^e(t) = \sum_{k = 1}^K e^k_i(t) B (1-\frac{n^k_i(t)}{S}) \log_2({1+\frac{p^k_i(t)h^k_i(t)}{B \times N_0}}),
+\begin{split}
+\mathcal{R}_{i}^e(t) &= \sum_{k = 1}^K e^k_i(t) B (1-{n^k_i(t)}) \log_2({1+\frac{p^k_i(t)h^k_i(t)}{B \times N_0}}),\\
+\bar{\mathcal{R}}_{i}^e(t) &= \E_{h}[\mathcal{R}_{i}^e(t)],
+\end{split}
 \end{equation}
@@
 $h^k_i(t)$ is the channel gain of a wireless link from 
-O-RU to the $i^{th}$ eMBB UE using $k^{th}$ PRB. In addition, $S$ is the total number of mini-slots of a PRB. 
-Furthermore, $n^k_i(t)$ is the number of URLLC punctured slots that is denoted as follow,
+O-RU to the $i^{th}$ eMBB UE using $k^{th}$ PRB which is Rayleigh fading.
+Furthermore, $n^k_i(t)$ is the percentage of RB $k$ using eMBB $i$ that is punctuated by URLLC UEs is denoted as follows,
 \begin{equation}
-n^k_i(t) = \sum_{j=1}^{U_2}{\zeta}_j(t)\tau \mathfrak{N} 
+n^k_i(t) = \psi^k_i(t) \frac{\sum_{j \in \mathcal{U}_2}{\zeta}^u_{j}(t){\nu}^u \tau}{S_{max}(t)\tau},
 \end{equation}
+Where, $\psi^k_i(t)$ is the probability of puncturing eMBB UE $i$ using RB $k$.
+Furthermore, ${\zeta}^u(t)$ is the arrival rate of URLLC UEs (arrival/slot/user).
+Moreover, $\mathcal{U}_2$ is the set of URLLC UEs in the system.
+In addition, $\nu^u$ is the URLLC packet size, and $\tau$ is the number of slot per second (slot/sec).
+Assume the packet arrival of URLLC UEs follows a Poisson process with arrival rate $\lambda(t)$.
+Therefore, the arrival data rate of URLLC $j$ is $\lambda_j(t) = {\zeta}^u_{j}(t){\nu}^u \tau$ .
+Moreover, $S_{max}(t)$ is the flow density refers to how much data the system can handle for all URLLC users at any given time (bits/slot).
+Moreover, we have $\sum_i e_i^k(t)\le 1$ to guarantee that each RB is allocated to a maximum of one eMBB UE.
 
 Since the blocklength in URLLC is finite, the achievable data rate for the $j^{th}$ UE request in the URLLC service, is not achieved from Shannon Capacity formula.
-So, for the short packet transmission the achievable data rate is approximated as follow
+So, for the short packet transmission the achievable data rate and its expectation is written as follow, respectively,
 \begin{equation}\label{eq11}
-\mathcal{R}_{j}^u(t) = \sum_{i = 1}^{U_1}\sum_{k=1}^K \frac{n^k_i(t)e^k_i(t)}{S \times U_2} B \log_2({1+\frac{p^k_j(t)h^k_j(t)}{B \times N_0}})- \zeta_{j}^k(t)), 
+\begin{split}
+\mathcal{R}_{j}^u(t) &= \sum_{i = 1}^{U_1}\sum_{k=1}^K m_i^{k}(t) B \log_2({1+\frac{p^k_j(t)h^k_j(t)}{B \times N_0}})- \zeta_{j}^k(t)),\\
+\bar{\mathcal{R}}_{j}^u(t) &= \E_{h}[\mathcal{R}_{j}^u(t)],
+\end{split} 
 \end{equation}
-
 where $\zeta_{j}^k(t) = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{j}^k(t)}{N_{j}^k(t)}})$
@@
 $N_{j}^k(t)$ represents the blocklength of it. Moreover, $\rho_{j}^k(t)=\frac{p^k_j(t)h^k_j(t)}{B \times N_0}$ is the SNR of UE $j$ in URLLC service. 
-
-The channel gain is assumed to be known with errors, the imperfection of channel estimation is
-modeled as follows
+Also, $m_i^{k}(t) $ is denoted as follow
 \begin{equation}
-h^k_j(t) = \hat{h}^k_j(t) + \Delta h^k_j(t)
+m_i^{k}(t)= \frac{e_i^k(t)n^k_i(t)}{|\mathcal{U}_2|},
 \end{equation}
-Where, $\Delta h^k_j(t)$ denotes the estimation error with a Guassian distribution of
- \begin{equation}
-\Delta h^k_j(t)\backsim \mathcal{N}(0,\boldsymbol{\phi^k}^2),
-\end{equation}
+where, $|\mathcal{U}_2|$ is the number of URLLC UEs in the system.
+%The channel gain is assumed to be known with errors, the imperfection of channel estimation is
+%modeled as follows
+%\begin{equation}
+%h^k_j(t) = \hat{h}^k_j(t) + \Delta h^k_j(t)
+%\end{equation}
+%Where, $\Delta h^k_j(t)$ denotes the estimation error with a Guassian distribution of
+% \begin{equation}
+%\Delta h^k_j(t)\backsim \mathcal{N}(0,\boldsymbol{\phi^k}^2),
+%\end{equation}
 \subsection{Mean Delay}
 In this part, the mean processing delay for each service is obtained.
-Suppose the mean processing delay is depicted as $T_{\text{\text{proc}}}$,
-\begin{equation}
-T^{\text{proc}} =  T^{RU} + T^{DU} + T^{CU},
-\end{equation}
-Assume the packet arrival of URLLC UEs follows a Poisson process with arrival rate $\lambda_{j}$ for the $j^{th}$ UE.
-Therefore, the mean arrival data rate of the O-CU-UP layer is $\alpha^C = \sum_{j=1}^{U_2}\lambda_{j}$.
-Assume the mean arrival data rate for URLLC slice ($\alpha$) is approximately equal to the mean arrival data rate of the  the O-DU ($\alpha^D$). so $\alpha = \alpha^C \approx \alpha^D$,
+Suppose the mean total processing delay is depicted as $T_{\text{\text{tot}}}$,
+\begin{subequations} 
+\begin{alignat}{4}
+T^{\text{tot}} &= T^{RU} + T^{\text{proc}},\\
+T^{\text{proc}} &= T^{DU} + T^{CU}.
+\end{alignat}
+\end{subequations} 
+We assume that the packet arrival rate of URLLC UEs follows a Poisson process with arrival rate $\lambda_{j}(t)$ for the $j^{th}$ UE.
+Thus, we have $\lambda_j(t) = {\zeta}^u_{j}(t){\nu}^u \tau$.
+Therefore, the mean arrival data rate of the O-CU-UP layer is $\alpha^C(t) = \sum_{j\in \mathcal{U}_2}\lambda_{j}(t)$.
+Assume the mean arrival data rate for URLLC slice ($\alpha$) is approximately equal to the mean arrival data rate of the  the O-DU ($\alpha^D$). so $\alpha(t) = \alpha^C(t) \approx \alpha^D(t)$,
 Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
@@
 \begin{split}
-T^{DU} &= \frac{1}{\mu^d - \alpha/{M^{d}}},\\
-T^{CU} &= \frac{1}{\mu^c - \alpha/{M^{c}}},\\
+T^{DU} &= \frac{1}{\mu^d - \alpha(t)/{M^{d}(t)}},\\
+T^{CU} &= \frac{1}{\mu^c - \alpha(t)/{M^{c}}(t)},\\
 \end{split}
 \end{equation}
-where $M^{d}$,and $M^{c}$ are the variables that depict the number of VNFs in O-DU,and O-CU-UP, respectively. 
+where $M^{d}(t)$,and $M^{c}(t)$ are the variables that depict the number of VNFs in O-DU,and O-CU-UP, respectively. 
 Moreover, $1/\mu^d$, and $1/\mu^c$ are the mean service time of the O-DU, and O-CU layers, respectively.
@@
 
-$T_{j}^{RU}$ is the mean transmission delay of the $j^{th}$ UE of the URLLC service on the wireless link.
- The arrival data rate of wireless link for each UE $j$ of URLLC service is $\lambda_j$
-As a result, we have $\sum_{j = 1}^{U_2} \lambda_{j} = \alpha$.
+Suppose the mean transmission delay of the $j^{th}$ UE of the URLLC service on the wireless link is denoted by
+$T_{j}^{RU}(t)$.
+ Assume the arrival data rate of wireless link for each UE $j$ of URLLC service is $\lambda_j(t)$
+As a result, we have $\sum_{j \in \mathcal{U}_2} \lambda_{j}(t) = \alpha(t)$.
 Moreover, The service time of transmission queue for UE $j$ requesting URLLC service has
-an exponential distribution with mean $1/R_{j}^u$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
+an exponential distribution with mean $1/R_{j}^u(t)$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
 
@@
 \begin{equation}
- T_{j}^{RU} = \frac{1}{R_{j}^u - \lambda_{j}}.
+ T_{j}^{RU}(t) = \frac{1}{\bar{\mathcal{R}}_{j}^u(t) - \lambda_{j}(t)}.
 \end{equation}
@@
 \begin{equation}
-P_r\{T_{j}^{RU} \geq T_{RU}^{max}\} = e^{-(R_{tot}^u - \alpha)T_{RU}^{max}}
+P_r\{T_{j}^{RU} \geq T_{RU}^{max}\} = e^{-(\bar{R}_{j}^u - \alpha)T_{RU}^{max}}
 \end{equation} 
-where, $R_{tot}^u = \sum_{j =1}^{U_2}R_{j}^u$
 Also, we do not consider the reliability for O-CU and O-DU.
@@
 %\end{equation}
-The optimization problem is formulated as follow
+In this paper, we strive to maximize the sum rate of all eMBB UEs and minimize the delay of URLLC UEs while imposing constraints on their performance based on their QoS.
+The optimization problem is formulated as follow,
 
@@
 \begin{alignat}{4}
-\max\limits_{ \boldsymbol{E}, \boldsymbol{N},\boldsymbol{M} } &  \sum_i R_{i}^e(t) - \eta \sum_j T^{\text{proc}, u}(t)       \ \\
-\text{subject to} \quad  & \mathcal{R}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in U_1, \label{p1} \\
-& Pr\{{R}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon \label{p2}\\
-&T^{\text{proc}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in U_2 \label{p3} \\
-&Pr\{T^{\text{proc}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in U_2 \label{p4} 
+\max\limits_{ \boldsymbol{E}, \boldsymbol{\Psi},\boldsymbol{M} } &  \sum_i \bar{\mathcal{R}}_{i}^e(t) - \eta \sum_j T^{\text{tot}, u}(t)       \ \\
+\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_1, \label{p1} \\
+& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_1, \label{p2}\\
+&T^{\text{tot}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in \mathcal{U}_2, \label{p3} \\
+&Pr\{T^{\text{RU}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in \mathcal{U}_2, \label{p4} \\
+&\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p5} \\
+&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p6} \\
+& 0 \leq n^k_i(t)\leq 1  \quad \forall i,k, \label{p7} \\
+& \mu^l \geq \alpha/M^l \quad l \in \{c,d\},\label{p8} \\
+& \bar{\mathcal{R}}^u(t) \geq {\lambda}_{j}^u(t) \quad \forall j \in \mathcal{U}_2,\label{p9} \\
+& 0 \leq M^l \leq M_{max}^l  \quad l \in \{c,d\},\label{p10}
 \end{alignat}
@@
 \end{subequations}
-where, \eqref{p2}, supports the reliability of eMBB while puncturing the URLLC.
+Where, \eqref{p1}, guarantees the minimum data rate of eMBB UEs, also
+\eqref{p2}, supports the reliability of eMBB while puncturing the URLLC. 
+In addition, \eqref{p3}, and \eqref{p4} guarantee the latency and reliability of URLLC UEs, respectively.
+Furthermore, eMBB RB allocation constraint is indicated by \eqref{p5}, and \eqref{p6}.
+\eqref{p7}, indicate that the punctured mini-time slot are fewer than the total number of mini-slots in the RB.
+\eqref{p8} and \eqref{p9} denotes the stability of the M/M/1 queue model.
+\eqref{p10} restricts the number of VNF in each slice due to the limited resources.
+
+\section{Proposed Algorithm}
+In this section, we talk about our proposed algorithm to solve the problem \eqref{mainP}.
+Since this problem is mixed-integer nonlinear programming (MINLP) with binary and integer variables, it is complicated to solve.
+
+We can solve this problem on a two-time scale. On a large time scale, the problem of assigning RB to eMBB UEs is solved,
+Also, in this time scale, we can estimate the optimal number of VNFs, and in the small time scale, the problem of URLLC puncturing is solved. 
+\subsection{Large time scale}
+In this time scale, we want to solve the problem of eMBB scheduling and finding the optimal number of VNF for URLLC UEs.
+Here, we suppose the puncturing of URLLC is fixed, hence, we want to solve the problem \eqref{mainP}.
+The problem \eqref{mainP}, is altered to the following problem
+
+\begin{subequations} \label{mainP1}
+\begin{alignat}{4}
+\max\limits_{ \boldsymbol{E},\boldsymbol{M} } &  \sum_i \bar{\mathcal{R}}_{i}^e(t) - \eta T^{\text{proc}, u}(t)       \ \\
+\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_1, \label{p1} \\
+& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_1, \label{p12}\\
+&\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p15} \\
+&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p16} \\
+& 0 \leq n^k_i(t)\leq 1  \quad \forall i,k, \label{p17} \\
+& \mu^l \geq \alpha/M^l \quad l \in \{c,d\},\label{p18} \\
+& 0 \leq M^l \leq M_{max}^l  \quad l \in \{c,d\},\label{p110}
+\end{alignat}
+\label{constraints}
+\end{subequations}
+
+Generally, let's assume O-CU and O-DU use the same processor. 
+Consequently, the formulation becomes simpler. Despite this, the formulation remains the same, and the problem can still be solved similarly. 
+Consequently, we have $\mu = \mu^c \approx \mu^d $.
+Additionally, the mean arrival data rate for the O-DU layer ($\alpha^C$) is the same as the O-CU-UP layer ($\alpha^C$).
+So $\alpha = \alpha^C \approx \alpha^D$.
+Accordingly, we can have $M^d(t) = M^c(t)$. Therefore, $T^{DU} = T^{CU}$, and $T^{proc} =2\times T^{DU}$.
+
+The problem \eqref{mainP1}, is still mixed integer non-linear programming (MINP). Here, the problem \eqref{mainP1}
+can also be decomposed into two sub-problems which is depicted as follow.
+\subsubsection{sub-problem 1}
+In this section, we want to solve the sub-problem of RB allocation of eMBB UEs.
+The problem can be written as follow.
+\begin{subequations} \label{mainP11}
+\begin{alignat}{4}
+\max\limits_{ \boldsymbol{E} } &  \sum_i \bar{\mathcal{R}}_{i}^e(t)       \ \\
+\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_1, \label{p11} \\
+&\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p115} \\
+&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p116} 
+\end{alignat}
+\label{constraints}
+\end{subequations}
+\subsubsection{sub-problem 2}
+In this section, we want to solve the sub-problem of finding the optimal number of VNF for URLLC services.
+The problem is formulated as follow.
+\begin{subequations} \label{mainP2}
+\begin{alignat}{4}
+\min\limits_{ \boldsymbol{M} } &  T^{\text{proc}, u}(t)       \ \\
+\text{subject to} \quad  & \mu^l \geq \alpha/M^l \quad l \in \{c,d\},\label{p28} \\
+& 0 \leq M^l \leq M_{max}^l  \quad l \in \{c,d\},\label{p210}
+\end{alignat}
+\label{constraints}
+\end{subequations}
+\subsection{Small time scale}
+In the small time scale, we assume that the eMBB RB allocation is performed and the optimal number of VNF for URLLC is obtained. Therefore, the problem of puncturing URLLC UEs is performed.
+\begin{subequations} \label{mainP2}
+\begin{alignat}{4}
+\min\limits_{  \boldsymbol{\Psi} } &  \sum_j T^{RU, u}(t)       \ \\
+\text{subject to} \quad  &T^{\text{tot}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in \mathcal{U}_2, \label{p33} \\
+& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_1, \label{p32}\\
+&Pr\{T^{\text{RU}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in \mathcal{U}_2, \label{p34} \\
+& 0 \leq n^k_i(t)\leq 1  \quad \forall i,k, \label{p37} \\
+& \bar{\mathcal{R}}^u(t) \geq {\lambda}_{j}^u(t) \quad \forall j \in \mathcal{U}_2,\label{p39} 
+\end{alignat}
+\label{constraints}
+\end{subequations}
 

### 2022-05-21 Latex/journal_v2/version4/pr.tex
paper 2 part of latex

--- 2022-04-05 Latex/journal_v2/version3/pr.tex
@@
 
-\begin{figure*}
-  \centering 
-    \includegraphics[scale = 0.5]{finalDraw.pdf}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Network sliced ORAN system}
-  \label{fig:1}
-\end{figure*}
+%\begin{figure*}
+%  \centering 
+%    \includegraphics[scale = 0.5]{finalDraw1.pdf}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Network sliced ORAN system}
+%  \label{fig:1}
+%\end{figure*}
 
@@
 \subsection{System Model}
-%This paper deals with the challenges of heterogeneous vehicular and cellular networks.
-Assume we have two different services, namely, eMBB and URLLC; 
-The system is serving a set of $\mathcal{U}_1$ eMBB single-antenna user equipments (UEs) and a set of $\mathcal{U}_2$ URLLC UEs.
-Assume our system consists of $K$, preallocated physical resource blocks (PRBs).
-Moreover, the system considers to have $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP of eMBB and URLLC ($ s \in \{1, 2\}$).
-Virtual network functions (VNFs) are functional blocks of the system. Each VNF instance runs on a virtual machine (VM) using resources from the data centers. 
-Moreover, we assume there is a cell with one multi-antenna O-RU that serves UEs.
+Consider two different services of eMBB and URLLC in O-RAN architecture; each offers various applications.
+Therefore, we assume two different slices for eMBB and URLLC services.
+The system is serving a set of $\mathcal{U}_e$ eMBB single-antenna user equipment(UE) and a set of $\mathcal{U}_u$ URLLC UE.
+Suppose we have $K$ preallocated resource blocks (RBs) for serving these two services.
+ Moreover, the system considers having  virtual network function (VNFs) in O-DU and O-CU to process packets. Each service has its VNFs for processing due to the isolation of slices.
+Let the system have $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP of eMBB and URLLC services ($ s \in \{e, u\}$ for eMBB and URLLC respectively).
+A VNF is a system's core component. Every VNF instance is hosted on a virtual machine (VM) using resources from the data centers. 
+Moreover, we assume there is a cell with one O-RU that serves UEs.
 Furthermore, we suppose the channel distribution is known.
+The eMBB services generally use more than a one-time slot. But URLLC services use part of a time slot (mini-slot) since it has a short packet transmission. 
+By using the PF principle, we currently allocate RBs at the beginning of each eMBB time slot, a scheduling strategy that balances throughput and fairness \cite{shi2022risk}. 
+However, puncturing the URLLC once requested service is necessary as it requires very low latency.
 \subsection{The Achievable Rate}
-The eMBB services typically use more than a one-time slot.
-But URLLC services use part of a time slot (mini-slot) since it has short packet transmission that it is indicated in Fig \ref{fig:2}.
-In addition, the URLLC must be punctured as soon as it has requested service as it requires very low latency.
-\begin{figure}
-  \centering 
-    \includegraphics[scale = 0.4]{EU.pdf}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{RB scheduling}
-  \label{fig:2}
-\end{figure}
-Our current work allocates RBs to eMBB users at the beginning of each time slot using the PF principle, a scheduling strategy that balances throughput with fairness \cite{shi2022risk}.
+%\begin{figure}
+%  \centering 
+%    \includegraphics[scale = 0.4]{EU.pdf}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{RB scheduling}
+%  \label{fig:2}
+%\end{figure}
 
@@
 where $B$ is the bandwidth of RBs. Also, $B\times N_0$ denotes the power of Gaussian additive noise. 
-Moreover, $e^k_i(t)\in \{0,1\}$ is a binary variable that illustrates whether PRB $k$ is assigned to the $i^{th}$ eMBB UE or not. 
+Moreover, $e^k_i(t)\in \{0,1\}$ is a binary variable that illustrates whether RB $k$ is assigned to the $i^{th}$ eMBB UE or not. 
 $p^k_i(t)$ represents the transmission power allocated by O-RU to $i^{th}$ UE of eMBB using PRB $k$.
@@
 O-RU to the $i^{th}$ eMBB UE using $k^{th}$ PRB which is Rayleigh fading.
-Furthermore, $n^k_i(t)$ is the percentage of RB $k$ using eMBB $i$ that is punctuated by URLLC UEs is denoted as follows,
+Furthermore, $n^k_i(t)$ denotes the percentage of RB $k$ using eMBB $i$ that is punctured by the set of URLLC service is indicates as follows,
+%\begin{equation}
+%n^k_i(t) = \psi^k_i(t) \frac{\sum_{j \in \mathcal{U}_2}{\zeta}^u_{j}(t){\nu}^u \tau}{S_{max}(t)\tau},
+%\end{equation}
+%Where, $\psi^k_i(t)$ is the probability of puncturing eMBB UE $i$ using RB $k$.
+%Furthermore, ${\zeta}^u(t)$ is the arrival rate of URLLC UEs (arrival/slot/user).
+%Moreover, $\mathcal{U}_2$ is the set of URLLC UEs in the system.
+%In addition, $\nu^u$ is the URLLC packet size, and $\tau$ is the number of slot per second (slot/sec).
+%Assume the packet arrival of URLLC UEs follows a Poisson process with arrival rate $\lambda(t)$.
+%Therefore, the arrival data rate of URLLC $j$ is $\lambda_j(t) = {\zeta}^u_{j}(t){\nu}^u \tau$ .
+%Moreover, $S_{max}(t)$ is the flow density refers to how much data the system can handle for all URLLC users at any given time (bits/slot).
 \begin{equation}
-n^k_i(t) = \psi^k_i(t) \frac{\sum_{j \in \mathcal{U}_2}{\zeta}^u_{j}(t){\nu}^u \tau}{S_{max}(t)\tau},
+n^k_i(t) = \frac{x^k_i(t)}{L}
 \end{equation}
-Where, $\psi^k_i(t)$ is the probability of puncturing eMBB UE $i$ using RB $k$.
-Furthermore, ${\zeta}^u(t)$ is the arrival rate of URLLC UEs (arrival/slot/user).
-Moreover, $\mathcal{U}_2$ is the set of URLLC UEs in the system.
-In addition, $\nu^u$ is the URLLC packet size, and $\tau$ is the number of slot per second (slot/sec).
-Assume the packet arrival of URLLC UEs follows a Poisson process with arrival rate $\lambda(t)$.
-Therefore, the arrival data rate of URLLC $j$ is $\lambda_j(t) = {\zeta}^u_{j}(t){\nu}^u \tau$ .
-Moreover, $S_{max}(t)$ is the flow density refers to how much data the system can handle for all URLLC users at any given time (bits/slot).
+where, $x^k_i(t)$ is the number of punctured mini-slot of RB k that is used by eMBB UE i. Also, $L$ is the number of mini-slots in each RB \cite{alsenwi2021intelligent}.
+
 Moreover, we have $\sum_i e_i^k(t)\le 1$ to guarantee that each RB is allocated to a maximum of one eMBB UE.
@@
 \begin{split}
-\mathcal{R}_{j}^u(t) &= \sum_{i = 1}^{U_1}\sum_{k=1}^K m_i^{k}(t) B \log_2({1+\frac{p^k_j(t)h^k_j(t)}{B \times N_0}})- \zeta_{j}^k(t)),\\
+\mathcal{R}_{j}^u(t) &= \sum_{i = 1}^{U_e}\sum_{k=1}^K m_i^{k}(t) B \log_2({1+\frac{p^k_j(t)h^k_j(t)}{B \times N_0}})- \zeta_{j}^k(t),\\
 \bar{\mathcal{R}}_{j}^u(t) &= \E_{h}[\mathcal{R}_{j}^u(t)],
@@
 where $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
-$C_{j}^k(t) = 1 - \frac{1}{(1+\rho_{j}^k(t))^2}$ depicts the channel dispersion of UE $j$ of URLLC, puncturing mini-slots of PRB $k$ and
+$C_{j}^k(t) = 1 - \frac{1}{(1+\rho_{j}^k(t))^2}$ depicts the channel dispersion of $j^\text{th}$ UE of URLLC service, puncturing mini-slots of RB $k$ and
 $N_{j}^k(t)$ represents the blocklength of it. Moreover, $\rho_{j}^k(t)=\frac{p^k_j(t)h^k_j(t)}{B \times N_0}$ is the SNR of UE $j$ in URLLC service. 
@@
 \begin{equation}
-m_i^{k}(t)= \frac{e_i^k(t)n^k_i(t)}{|\mathcal{U}_2|},
+m_i^{k}(t)= \frac{e_i^k(t)n^k_i(t)}{|\mathcal{U}_u|},
 \end{equation}
-where, $|\mathcal{U}_2|$ is the number of URLLC UEs in the system.
+where, $|\mathcal{U}_u|$ is the number of URLLC UEs in the system.
 %The channel gain is assumed to be known with errors, the imperfection of channel estimation is
@@
 \subsection{Mean Delay}
-In this part, the mean processing delay for each service is obtained.
-Suppose the mean total processing delay is depicted as $T_{\text{\text{tot}}}$,
+In this section, the mean processing delay for each service is determined.
+Let us suppose the mean total processing time is
 \begin{subequations} 
@@
 \end{subequations} 
-We assume that the packet arrival rate of URLLC UEs follows a Poisson process with arrival rate $\lambda_{j}(t)$ for the $j^{th}$ UE.
-Thus, we have $\lambda_j(t) = {\zeta}^u_{j}(t){\nu}^u \tau$.
-Therefore, the mean arrival data rate of the O-CU-UP layer is $\alpha^C(t) = \sum_{j\in \mathcal{U}_2}\lambda_{j}(t)$.
-Assume the mean arrival data rate for URLLC slice ($\alpha$) is approximately equal to the mean arrival data rate of the  the O-DU ($\alpha^D$). so $\alpha(t) = \alpha^C(t) \approx \alpha^D(t)$,
+We assume that the packet arrival rate of each UE $\mathfrak{i}$ in each service s follows a Poisson process with arrival rate $\lambda_{\mathfrak{i},s}(t)$.
+%Thus, we have $\lambda_j(t) = {\zeta}^u_{j}(t){\nu}^u \tau$.
+Therefore, the mean arrival data rate of the O-CU-UP layer is $\alpha^C_{s}(t) = \sum_{\mathfrak{i}\in \mathcal{U}_s}\lambda_{\mathfrak{i},s}(t)$, $s \in \{e,u\}$ which is for eMBB and URLLC service, respectively.
+Assume the mean arrival data rate for URLLC slice ($\alpha$) is approximately equal to the mean arrival data rate of the O-DU ($\alpha^D$).
+so $\alpha_s(t) = \alpha^C_{s}(t) \approx \alpha^D_s(t)$, $s \in \{e,u\}$.
 Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
@@
 Each packet is processed by one of the VNFs of a slice.
-So, the mean delay for the URLLC slice in the O-DU,and the O-CU is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
+So, the mean delay for the each slice ($s \in \{e,u\}$ which is for eMBB and URLLC service, respectively) in the O-DU,and the O-CU is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
 \begin{equation}
 \begin{split}
-T^{DU} &= \frac{1}{\mu^d - \alpha(t)/{M^{d}(t)}},\\
-T^{CU} &= \frac{1}{\mu^c - \alpha(t)/{M^{c}}(t)},\\
+T^{DU}_s &= \frac{1}{\mu^d_s - \alpha_s(t)/{M^{d}_s(t)}},\\
+T^{CU}_s &= \frac{1}{\mu^c_s - \alpha_s(t)/{M^{c}_s}(t)},\\
 \end{split}
 \end{equation}
-where $M^{d}(t)$,and $M^{c}(t)$ are the variables that depict the number of VNFs in O-DU,and O-CU-UP, respectively. 
-Moreover, $1/\mu^d$, and $1/\mu^c$ are the mean service time of the O-DU, and O-CU layers, respectively.
-Besides, $\alpha$ is the  arrival rate which is divided
-by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for URLLC slice  is $\alpha/{M^{l}}$ $ l \in \{d,c\}$.
+where $M^{d}_s(t)$,and $M^{c}_s(t)$ are the variables that depict the number of VNFs in O-DU,and O-CU-UP, respectively. 
+Moreover, $1/\mu^d_s$, and $1/\mu^c_s$ are the mean service time of the O-DU, and O-CU layers, respectively.
+Besides, $\alpha_s$ is the  arrival rate which is divided
+by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice is $\alpha_s/{M^{l}_s}$ $ l \in \{d,c\}$.
 
-Suppose the mean transmission delay of the $j^{th}$ UE of the URLLC service on the wireless link is denoted by
-$T_{j}^{RU}(t)$.
- Assume the arrival data rate of wireless link for each UE $j$ of URLLC service is $\lambda_j(t)$
-As a result, we have $\sum_{j \in \mathcal{U}_2} \lambda_{j}(t) = \alpha(t)$.
-Moreover, The service time of transmission queue for UE $j$ requesting URLLC service has
-an exponential distribution with mean $1/R_{j}^u(t)$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
+Suppose the mean transmission delay of the $\mathfrak{i}^{th}$ UE of the service s ($s \in \{e,u\}$which is for eMBB and URLLC service, respectively) on the wireless link is denoted by
+$T_{\mathfrak{i},s}^{RU}(t)$.
+ Assume the arrival data rate of wireless link for each UE $\mathfrak{i}$ of service s is $\lambda_{\mathfrak{i},s}(t)$
+As a result, we have $\sum_{\mathfrak{i} \in \mathcal{U}_s} {\mathfrak{i},s}(t) = \alpha_s(t)$, $s \in \{e,u\}$.
+Moreover, The service time of transmission queue for UE $\mathfrak{i}$ requesting service s has
+an exponential distribution with mean $1/R_{\mathfrak{i}}^s(t)$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
 
-Therefore, the mean delay of the transmission layer for UE $j$ in URLLC slice is
+Therefore, the mean delay of the transmission layer for UE $\mathfrak{i}$ in slice s is
 \begin{equation}
- T_{j}^{RU}(t) = \frac{1}{\bar{\mathcal{R}}_{j}^u(t) - \lambda_{j}(t)}.
+ T_{\mathfrak{i},s}^{RU}(t) = \frac{1}{{\mathcal{R}}_{\mathfrak{i}}^s(t) - \lambda_{\mathfrak{i},s}(t)}.
 \end{equation}
@@
 \begin{equation}
-P_r\{T_{j}^{RU} \geq T_{RU}^{max}\} = e^{-(\bar{R}_{j}^u - \alpha)T_{RU}^{max}}
+P_r\{T_{j,u}^{RU} \geq T^{RU}_{\text{max}}\} = e^{-({R}_{j}^u - \alpha)T^{RU}_{\text{max}}}
 \end{equation} 
@@
 \begin{alignat}{4}
-\max\limits_{ \boldsymbol{E}, \boldsymbol{\Psi},\boldsymbol{M} } &  \sum_i \bar{\mathcal{R}}_{i}^e(t) - \eta \sum_j T^{\text{tot}, u}(t)       \ \\
-\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_1, \label{p1} \\
-& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_1, \label{p2}\\
-&T^{\text{tot}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in \mathcal{U}_2, \label{p3} \\
-&Pr\{T^{\text{RU}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in \mathcal{U}_2, \label{p4} \\
+\max\limits_{ \boldsymbol{E}, \boldsymbol{X},\boldsymbol{M}, \boldsymbol{P} } &  \sum_i {\mathcal{R}}_{i}^e(t) - \eta \sum_j T^{\text{tot}, u}(t)       \ \\
+\text{subject to} \quad  & {\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_e, \label{p1} \\
+& \sum_k^K \sum_i^{U_e} p^k_i(t) \leq P_{\text{max}},  \label{p1-1} \\ 
+& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_e, \label{p2}\\
+&T^{\text{tot}, e}_i(t)  \leq T_{min}^e  \quad \forall i \in \mathcal{U}_e, \label{p2-1} \\
+&T^{\text{tot}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in \mathcal{U}_u, \label{p3} \\
+& \bar{\mathcal{R}}_{j}^u(t) \geq  \mathcal{R}_{min}^u \quad \forall j \in \mathcal{U}_u, \label{p3-1} \\
+&Pr\{T^{\text{RU}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in \mathcal{U}_u, \label{p4} \\
 &\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p5} \\
 &e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p6} \\
-& 0 \leq n^k_i(t)\leq 1  \quad \forall i,k, \label{p7} \\
-& \mu^l \geq \alpha/M^l \quad l \in \{c,d\},\label{p8} \\
-& \bar{\mathcal{R}}^u(t) \geq {\lambda}_{j}^u(t) \quad \forall j \in \mathcal{U}_2,\label{p9} \\
-& 0 \leq M^l \leq M_{max}^l  \quad l \in \{c,d\},\label{p10}
+& x^k_i(t)\in \{0,1,...,L\}  \quad \forall i,k, \label{p7} \\
+& \mu^l_s \geq \alpha_s/M^l_s \quad l \in \{c,d\}, s\in\{e,u\}, \label{p8} \\
+& {\mathcal{R}}^s(t) \geq {\lambda}_{\mathfrak{i},s}^u(t) \quad \forall \mathfrak{i} \in \mathcal{U}_s, s\in \{e,u\}\label{p9} \\
+& 0 \leq M^l_e  + M^l_u \leq M_{max}^l  \quad l \in \{c,d\},\label{p10}
 \end{alignat}
@@
 \end{subequations}
-Where, \eqref{p1}, guarantees the minimum data rate of eMBB UEs, also
-\eqref{p2}, supports the reliability of eMBB while puncturing the URLLC. 
-In addition, \eqref{p3}, and \eqref{p4} guarantee the latency and reliability of URLLC UEs, respectively.
+Where, \eqref{p1}, guarantees the minimum data rate of eMBB UEs, also \eqref{p1-1} indicates the power allocation constraints.
+\eqref{p2}, supports the reliability of eMBB while puncturing the URLLC. Moreover, \eqref{p2-1} indicates the maximum delay that the eMBB service can tolerate.
+In addition, \eqref{p3}, \eqref{p3-1} and \eqref{p4} guarantee the latency, the minimum data rate and reliability of URLLC UEs, respectively.
 Furthermore, eMBB RB allocation constraint is indicated by \eqref{p5}, and \eqref{p6}.
@@
 \section{Proposed Algorithm}
-In this section, we talk about our proposed algorithm to solve the problem \eqref{mainP}.
-Since this problem is mixed-integer nonlinear programming (MINLP) with binary and integer variables, it is complicated to solve.
-
-We can solve this problem on a two-time scale. On a large time scale, the problem of assigning RB to eMBB UEs is solved,
-Also, in this time scale, we can estimate the optimal number of VNFs, and in the small time scale, the problem of URLLC puncturing is solved. 
+In this section, we are talking about our proposed algorithm to solve the problem \eqref{mainP}.
+Since this problem is mixed-integer nonlinear programming (MINLP) with binary and integer variables, it is complicated to solve. Also, this is a two-time scale problem.
+Therefore, We need to solve this problem on a two-time scale. On a large time scale, the problem of assigning RB to eMBB service is obtained and then the power allocation is performed. 
+Moreover, in this time scale, we can estimate the optimal number of VNFs for each service, and in the small time scale, the problem of URLLC puncturing is solved. 
 \subsection{Large time scale}
-In this time scale, we want to solve the problem of eMBB scheduling and finding the optimal number of VNF for URLLC UEs.
+In this time scale, we want to solve the problem of eMBB scheduling, power allocation, and finding the optimal number of VNF for each service.
 Here, we suppose the puncturing of URLLC is fixed, hence, we want to solve the problem \eqref{mainP}.
@@
 \begin{alignat}{4}
-\max\limits_{ \boldsymbol{E},\boldsymbol{M} } &  \sum_i \bar{\mathcal{R}}_{i}^e(t) - \eta T^{\text{proc}, u}(t)       \ \\
-\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_1, \label{p1} \\
+\max\limits_{ \boldsymbol{E},\boldsymbol{M}, \boldsymbol{P}} &  \sum_i {\mathcal{R}}_{i}^e(t) - \eta T^{\text{proc}, u}(t)       \ \\
+\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_1, \label{p11} \\
+& \sum_k^K \sum_i^{U_e} p^k_i(t) \leq P_{\text{max}},  \label{p11-1} \\
 & Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_1, \label{p12}\\
+&T^{\text{tot}, e}_i(t)  \leq T_{min}^e  \quad \forall i \in \mathcal{U}_e, \label{p12-1} \\
+&T^{\text{process}, u}_i(t)  \leq T_{\text{process,min}}^u  \quad \forall i \in \mathcal{U}_u, \label{p12-2} \\
 &\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p15} \\
 &e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p16} \\
-& 0 \leq n^k_i(t)\leq 1  \quad \forall i,k, \label{p17} \\
-& \mu^l \geq \alpha/M^l \quad l \in \{c,d\},\label{p18} \\
-& 0 \leq M^l \leq M_{max}^l  \quad l \in \{c,d\},\label{p110}
+& \mu^l_s \geq \alpha_s/M^l_s \quad l \in \{c,d\}, s\in\{e,u\},\label{p18} \\
+& 0 \leq M^l_e  + M^l_u \leq M_{max}^l  \quad l \in \{c,d\},\label{p110}
 \end{alignat}

### 2022-06-06 Journal1/Response3/Response.tex
change paper after revision

--- 2022-03-03 Journal1/Response2/Response.tex
@@
 \maketitle
-We would like to thank the editor and reviewers for their comments on our manuscript.
-We hope that the modifications that we have made to the manuscript, and the responses that we have
-provided herein will alleviate the reviewers' concerns. Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
+We would like to thank the editor and reviewers for their constructive comments on our manuscript.
+It has been beneficial in revising this paper, and we have improved both the technical content and presentation quality through their assistance.
+We greatly appreciate their generous help.
+Moreover, we have reviewed and incorporated all the comments and suggestions.
+We hope that the modifications we have made to the manuscript and the responses we have provided herein will alleviate the reviewers' concerns.
+Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
 \\ [-3.ex]
@@
 \cellcolor{violet!15}
-\textbf{\noindent  Comments to the Author} ``The paper has gone through three independent reviews and also checked by myself.
-The topic is interesting and there are merits.
-But there are some major concerns on the contribution, the assumption, the model derivation, and the experimental results.
-We hope the review comments are useful for further improving the quality of the paper.
-I'd therefore recommend the Resubmission''\\
+\textbf{\noindent  Comments to the Author} ``I think the paper should undergo a major revision. It is important to take special attention to the comments of reviewer 2.''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. We have utilized the comments to improve our paper and eliminate the problems.
+We would like to thank the Editor for his comments and concluding the revisions on our manuscript and for giving us this opportunity to improve our paper.
+We have used the comments to improve our paper and eliminate problems.
 
@@
 \textbf{\noindent Comments to the Author} ``
-The paper proposes resolving the problem of resource allocation to network slices by using a new algorithm applied to the reformulation of the problem.
-The results seem promising but the paper has some issues.
+The authors have addressed the comments provided in a previous review.
+The contributions are clear and the results are compared to some related work, so the reader can somewhat contextualize the proposed solution.
 ''\\
@@
 \cellcolor{gray!15}
-\textbf{\noindent Comment1:} ``First, the structure of the paper makes it somewhat hard to follow and there are some mistakes in the text.
-A proofread is required before it can be accepted for publication.
-''\\
+\textbf{\noindent Comment1:} ``However, the paper still needs some improvement in terms of readability. Some paragraphs are too long  ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We have changed the paper's introduction and checked the text entirely according to this comment.
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment2:} `` the figures are difficult to locate from their reference in the text (figures at top, as typical IEEE template is better), the text in the figures is too small ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We have changed the paper's introduction and checked the text entirely according to this comment.
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment3:} ``the contributions discussed in the introduction are not easily found in the other parts of the paper.  ''\\
 \hline
@@
 
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 2:} ``Although the paper demonstrates its claims, the relaxation of conditions from the original problem formulation is not well justified.
-It is not clear why the initial formulation of the problem is not feasible and the reformulated makes it feasible while retaining some level of quality of the solutions given.
-A deeper analysis of both formulations must be presented.
-''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-The problem in (13) is feasible and has feasibility points that are discussed in subsection  IV-B, and we introduce a fast algorithm (i.e., Algorithm 3) for feasibility points.
-Although the problem is feasible, it is not convex and difficult to solve.
-Since problem in (13) is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and the problem is NP-hard.
-Solving the problem is not trivial.
-To solve the problem by inspiring Stackelberg, we reformulate the equation in (13g) to reduce one of the variables (i.e., $M_s$) that can be solved after obtaining the rate of UEs.
-WE notice that $M_s$ is similar to the followers in Stackelberg Competition and power and PRB assignment is similar to leader.
-So, the new problem has two variables of power and PRB assignment.
-This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds in (15) because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
-After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.
-We made changes in Subsection III-A, accordingly.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment3:} ``Moreover, the baseline and FBDR methods used in the comparison are not well introduced.
-They are vaguely linked to related work but not as needed.
-The paper must clarify the relation of the related work and the compared alternatives.
-The paper must also contextualize the proposal among the related work by comparing their qualities and/or performance.
-''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
- Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
-The first one is a baseline scheme, which uses random PRB allocation.
-So, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
-Also, the association of O-RU is carried out based on distance.
-It means that each UE is assigned to the nearest O-RU.
-The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
-After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is
-achieved from Lemma (1). The second one is similar
-to the fixed BBU capacity and dynamic resource allocation
-(FBDR) algorithm proposed in [18]. In this work, we have services with different QoS that
-contain UEs, which is similar to tenants with different QoS
-that is introduced in [18]. So, we used an algorithm similar
-to FBDR adapted to our conditions for comparison. Instead
-of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
-To use the FBDR method, we should consider the fixed
-BBU capacity. We assume that O-DU and O-CU have fixed
-sufficient capacity in our system model. Also, our mid-haul
-link (F1 link) has adequate capacity, so there will be no
-issue using the FBDR method by separating BBU to O-DU
-and O-CU with this assumption. In this method, PRB and power are dynamically allocated. The number of VNFs is
-obtained from the simulation. The UEs are associated with the O-RU based on the quality of their channels and the
-channel distance instead of using the greedy algorithm 1 (GAA algorithm ) for O-RU assignment. The figures in [18]
-show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same
-priority area. We will also see that our proposed algorithm performs better than FBDR in the numerical result section.
-
-We add this response in subsection IV-A.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment4:} ``Finally, the source of the values used for the parameters in the evaluation must be clarified.  ''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-
-We refer to the following list of references in our numerical result for this comment:
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{green!10}
-[1] 3GPP-TS-36.104-V13.3.0, “Evolved Universal Terrestrial Radio Access (E-UTRA);
-Base Station (BS) radio transmission and reception
-(Release 13),” 2016-03.
-
-[2]  3GPP-TR-36.931-V13.0.0, “Technical Specification Group Radio Access Network;
-Evolved Universal Terrestrial Radio Access (E-UTRA);
-Radio Frequency (RF) requirements for LTE Pico Node B
-(Release 13),” 2016-01.
-
-[3] 3GPP-TS-25.101-V4.13.0, “User equipment (UE) radio transmission
-and reception (FDD)(release 4),” 2006-12.
-
-[4]E. Mohyeldin, “Minimum technical performance requirements for
-imt-2020 radio interface(s),” 2020.
-
-[5]  ETSI-TR-138-913-V14.3.0, “5G; study on scenarios and require-
-ments for next generation access technologies(3GPP TR 38.913 version
-14.3.0 release 14),” 2017-10.
-
-\\
-\hline
-\end{longtable}
-
-In [1 page 11], the amount of BW is explained.
-In [2], the noise power is represented.
-The amount of delay for eMBB and URLLC are listed on Pages 24 and 25 in [5].
-Also, on Page 26, the mMTC packet size is stated.
-On Page 25, the URLLC packet size is stated.
-In [3], on Page 13, Table 6.1, the maximum power is stated. In [4], on Page 4, the delay of URLLC and eMBB is and also the spectral efficiency of eMBB is noted.
-
-We add these references in IV-A (references [41]-[45]).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-\noindent
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\Centering
-\cellcolor{gray!45}
-\textbf{Reviewer 2} \\
-\hline \hline
-\RaggedRight
-\cellcolor{violet!15}
-\textbf{\noindent Comments to the Author:} ``The paper focus on the aspect of network slicing in 5G cellular network which entails a service aware resource allocation of the different required virtual network functions (VNFs) for different slices which have different characteristics.
-More specifically, the paper proposes a mixed integer mathematical problem which in the original form is non-linear and hence hard to solve.
-To tackle this challenge the optimization problem is decomposed into two sub-problems where the solutions are not optimal however numerical investigations show that the solutions are competitive.
-In general, the paper is well written and structured.''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-We would like to thank the reviewer for careful and thorough reading of this manuscript and
-for the thoughtful comments and constructive suggestions, which help us to improve the quality of
-this manuscript. We hope that the responses provided herein can alleviate the reviewer concerns.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 1:} ``In terms of taking the actual delay in the proposed there are some concerns which might be important for some time critical applications especially in the ultra-reliable low latency communications (URLLC) but also for different applications that fall under the enhanced mobile broadband (eMBB) generic service framework.
-First of all, in the paper the authors only consider processing delay and ignore propagation and transmission delay.
-Since multiple paths in reality could be utilized the role of the above two components might play an important role.
-Nevertheless, the authors need to clearly mention why those two components are not considered, saying for example are constant is not a good enough reason to be ignored since as eluded those change based on routing decisions.''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation.
-However, they can be added to the system model easily.
-In this paper, we focus only on the processing delay to find the optimal number of VNFs, and we consider the other two delays are fixed; In the following, we describe more about these two types of delays.
-
-The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority.
-Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU.
-Therefore, different routes are added to the system to solve the routing problem.
-However, it provides a new system model.
-So, the connection between O-RUs to O-DUs is fixed and transparent.
-As a result, the propagation delay is fixed and does not affect the optimization problem.
-The following is a brief calculation of propagation delay.
-Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
-Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}.
-so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $.
-Since fronhaul, midhaul, and backhaul are fiber optics, c is the speed of light.
-Also, due to the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced.
-But we also do not focus on edge processing in this paper.
-You can find more about these distances in this \href{https://blogs.keysight.com/blogs/inds.entry.html/2020/06/30/5g_testing_what_is-0nzj.html\%23:~:text=The\%20data\%20requirements\%20are\%20about,DUs\%20is\%20about\%2080\%20km.}{link}.
-The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has a small amount.
-In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$.
-So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$.
-As a result, the $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$.
-for eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.
-
-We add this response in subsection II-D.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 2:} ``Also, note that for calculating processing delay requests for different services arriving at blade servers for vnf applications might get different treatment on how they access VMs or containers hence a single queue with non-priority and/or preemption (m/m/1) might not be a good approximation on the performance.''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-The processing delay can be modeled as an M/M/1 queue; since the number of arrival packets in the system are from a large number of independent sources.
-Moreover, the impact of a single packet on the system's performance is minimal.
-Also, the queue discipline will be first-in first-out (FIFO), and the arrival packet is assumed to follow a Poisson process.
-The system's clock is constant, and the size of the tasks is not fixed.
-So, we suppose that service times are exponentially distributed [36].
-In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services, not between UEs of one service.
-Because we assume that the UEs of a service have the same priority, their sent packets also have an equal priority.
-Also, the services are isolated, and this priority does not invalidate the queue assumption.
-Furthermore, one service's priority over another can be higher, affecting the whole optimization and not queue formulation since the UEs in each service have the same priority, and each service has its processing delay independent of other services.
-
-We add this response in subsection II-D-1.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 3:} ``Also worth noting, that later on in the problem formulation there is the notion of service priority $\delta_s$ for data rate but this seems not to be used for accessing cloud resources.
-For example one could have changed the optimization problem and considered average allocated transmission rate and optimize with the same priorities access to cloud resources (instead of allocating equal access to vnf resources).''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-{\color{red}
-In this problem, since the priority is in the objective function of the equation in (13), the priority has whole effect optimization.
-So, priority is given to the whole optimization problem, and the optimization problem obtains the number of VNFs by affecting the priority term.
-If we were to discuss the placement of VNFs on the data centers, the problem would become a knapsack or bin-packing problem, and here the prioritization would affect the resource allocation algorithm, including memory, RAM, CPU, and bandwidth.
-So the algorithm was implemented based on prioritization.
-}
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 4:} ``Some form of rationalization should be given for abstracting Interference as Gaussian noise.
-This is important because we expect the system to be interference limited and cell edge users to experience significant different levels of performance compared to centre cell users.''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
- $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow
-%{\color{red} use paranthesis in the following equation to clear +}
-\begin{subequations}\label{eqI}
-\begin{alignat}{4}
-&I_{r,u(s,i)}^{k} =\\
- &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
-&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
-&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
-\end{alignat}
-\end{subequations}
-%{\color{red} $\gamma_1$ is constant used instead of variable. }
-%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
-where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
-%($\gamma_1$ and $\gamma_2$ are two variales.
-You  define on variable here.)
-Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.
-
-Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
-The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.
-To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
-\begin{equation}\label{eq2}
-y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}{x_Q}^k_{r,u(s,i)}+ z_{u(s,i)},
-\end{equation}
-
-%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
-where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
-Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
-Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression that is shown in figure \ref{fig:pq}.
-In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization Gaussian noise
-($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.
-\begin{figure}
-  \centering
-  \captionsetup{justification=centering}
-    \includegraphics[scale = 0.7]{Qdiag.png}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Precoding and Quantization of Signal}
-  \label{fig:pq}
-\end{figure}
-
-We add this response in subsection II-B.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 5:} ``Constraint 13n (changed to 13k in new version) is not clear - it means that there are VMs and/or containers available in the network and an operator denies service due to an energy consumption budget (which again is not very detailed to capture the actual energy consumption of each node/vnfs under different loads etc.).
-In general the subsection on VNF power consumption is very limited in scope.
-''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-{A significant issue facing the industry is reducing energy consumption.
-Data centers are one of the most energy-consuming parts of a network.
-As a result, restrictions are placed on data centers' energy, including virtual machines (VMs).
-So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers.
-So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).
-
-We add this response in subsection II-E.
-
-\clearpage
-\noindent
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 6:} ``Some rationalization is needed on why the packet size is considered to be 20 bytes. ''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-
-We refer to the following reference in our numerical result for this comment:
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{green!10}
-[1]  ETSI-TR-138-913-V14.3.0, “5G; study on scenarios and require-
-ments for next generation access technologies(3GPP TR 38.913 version
-14.3.0 release 14),” 2017-10.
-
-\\
-\hline
-\end{longtable}
-
-On [1, Page 25], the URLLC packet size is stated to be 32 bytes, and on Page 26, the packet size of mMTC is stated to be 20 bytes.
-We changed the URLLC packet size to 32, but it has little impact on the simulation result.
-
-We add this reference in IV-A (reference [45]).
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 7:} ``Comparison with [18] might not be fair since that work also considers BBU capacity and also performs admission control functionalities, also there are different tenants that have different users with variable required QoS.
-''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-We use a method which is similar to the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18].
-In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in [18].
- So, we used an algorithm similar to FBDR adapted to our conditions for comparison.
-Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
-To use the FBDR method, we should consider the fixed BBU capacity.
-We assume that O-DU and O-CU have fixed sufficient capacity in our system model.
-Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the FBDR method by separating ‌BBU to O-DU and O-CU with this assumption.
-In this method, PRB and power are dynamically allocated.
-The number of VNFs is obtained from the simulation.
-The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm 1 (GAA algorithm ) for O-RU assignment.
-
-We add this response in subsection IV-A.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 8:} ``Also, interference is measured in a more detailed manner (maximum interference per UE) and hence when this relaxed (Guassian noise) the performance expected to slightly increase.
-Hence, some more detailed discussion on what has been assumed is needed.
-''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise which is shown in Fig \ref{fig:pq}.
-We offer the sum of interference and the Gaussian quantization noise with $ I_{r,u(s,i)}^{k}$.
-Also, the Gaussian quantization noise is independent of interference and related to channel gain of UEs.
-
-We add this response in subsection II-B.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-\noindent
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\Centering
-\cellcolor{gray!45}
-\textbf{Reviewer 3} \\
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comments to the Author} ``The authors propose a resource allocation scheme for network slicing in an Open RAN scenario.
-They consider three network slice types namely eMBB, URLLC and mMTC and provide a solution for end-to-end slicing considering resource allocation over the RAN domain following the proposed ORAN architecture, as well as VNF allocation.
-In general, the paper is well written, however some parts need to be rephrased and restructured.''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-We would like to thank the reviewer for careful and thorough reading of our manuscript and for
-the thoughtful comments and constructive suggestions, which helped us to improve
-the quality of this manuscript. We hope that the modifications that we have made to the manuscript, and the
-responses that we have provided herein will alleviate the reviewer concerns.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 1:} ``The paper presents an interesting solution and an extremely well formulated mathematical problem; however, the main contribution of the paper is hard to grasp.
-For instance, the introduction of the paper is very generic.
-There are a lot of concepts and methods explained, nonetheless not related to the proposed solution.
-The main issue lies in the structure of the work.
-The main contribution only appears at the end of page 2, where after an extensive reading the interest of the reader starts to vanish.
-I would definitely suggest a restructuring here.
-For instance, directly hint the main objectives and motivation of the work to prepare the reader for what is following.
-Moreover, the Related work could be a section of its own.
-In that way, the organization of the paper is clearer and easier to read.
-''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-Thank you for the comment. We modified the introduction of the paper.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 2:} ``Finally, a better distinction of the current proposal from the state-of-the-art is mandatory, otherwise it is hard to understand how the proposed algorithm differs from existing works in the literature which seem to provide solution to a similar problem.''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-The purpose of this paper is twofold.
-First and foremost, it is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
-Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
-Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
-In this paper, we would like to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
-Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
-The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
-We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 3:} ``Furthermore, while the math introduced in the paper is solid, it is also hard to follow for a reader if illustrations are not presented.
-It would be easier if a Figure is introduced for instance to explain equations from 3a -3d, where a lot of variables are presented.
-Especially, for the concepts of inter and intra slice isolation, which are very crucial.
-Following, that logic more elaboration especially with respect to inter slice isolation and why it needs to be considered in the equation, is important, as one could say that a careful scheduling has to definitely avoid distribution of the same resources within a slice to different users i.e., (orthogonality constraint).''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-
-We added this part in the system model.
-Assume there are $K$ physical resource blocks (PRBs) in the system.
-Suppose each slice $s$ consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
-Therefore, we have $\sum_s \bar{K}_s \leq K$.
-
-Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
- r$.
-UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
-Network Slicing methods significantly reduce inter-service interference.
-There are some techniques to remove inter-slice interference.
-One of these techniques is to have two-time scale scheduling.
-The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out.
-Since there are limited resources, inter-service interference cannot be eliminated entirely.
-The other method is to allocate part of the RB of eMBB services to URLLC and mMTC  [2], [6], [34].
-In this paper, we assume that the PRB scheduling is performed.
-Also, in subsection II-F1, we briefly study the PRB scheduling between slices.
-\begin{figure}
-  \centering
-  \captionsetup{justification=centering}
-    \includegraphics[scale = 0.35]{Interference.png}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Type of Interference Signal}
-  \label{fig:intf}
-\end{figure}
-$I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow
-%{\color{red} use paranthesis in the following equation to clear +}
-\begin{subequations}\label{eqI}
-\begin{alignat}{4}
-&I_{r,u(s,i)}^{k} =\\
- &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
-&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
-&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
-\end{alignat}
-\end{subequations}
-%{\color{red} $\gamma_1$ is constant used instead of variable. }
-%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
-where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
-%($\gamma_1$ and $\gamma_2$ are two variales.
-You  define on variable here.)
-Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.
-
-We add this response in subsection II-B.
-
- In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices [37].
-We need to have an algorithm to remove the inter-slice interference before solving the problem in \ref{problem}.
-Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed.
-So, the assignment of PRB can be completed in two steps to remove inter-slice interference and isolate the slices.
-Firstly, we assign PRBs to slices.
-Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses Algorithm \ref{proAlg}.
-Suppose $\mathcal{R}_{{s}}^{min}$ and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
-Firstly, we need to find the average PRB number used by UEs in each service.
-Since mMTC and URLLC transmit a short packet, each UE in mMTC and URLLC requires 1 PRB.
-So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs.
-For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s.
-(eMBB slice)
-So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$.
-$K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
-Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$.
-$K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
-Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).
-Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
-The problem can be written as follow
-\begin{subequations}\label{prob:prb}
-\begin{alignat}{4}
-\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s K_s \ln(\bar{K_s}) \ \\
-\text{subject to} \quad  & \sum_s{\bar{K_s}} \leq K
- \label{prb0} \\
-& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
-&  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3,\label{prb2}
-\end{alignat}
-\label{constraints}
-\end{subequations}
-We use logarithms to assign PRBs to all slices to make
-them equally fair [37]. Equation (14b) illustrates that the
-sum of PRBs of slices can not exceed the maximum number
-of PRBs. Equation (14c), restrict the number of PRBs
-of eMBB slices and (14d), limit the number of PRBs of
-URLLC and mMTC slices By relaxing $\bar{K_s}$, the objective function and constraints become convex and can be solved using the Lagrangian function.
-
-Also, we added a new subsection II-E-1 discyussing PRB scheduling for this question.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 4:} ``Additionally, since the authors claim their novelty on the introduction of ORAN architecture, it becomes of utmost importance to consider concepts such as the creation of a slice, management of a slice and well as deletion, which bridge the mathematical framework to the practical one.
-For instance, how is a network slice created in the proposed work?
-How are the requirements of a slice fed to the algorithm?
-How is the monitoring of a slice performed?''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-This subsection aims to examine slice management, including creating, managing, and deleting slices.
-Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning [38].
-\begin{itemize}
-\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase.
-In this phase, operators plan to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment.
-Also, the evaluation of requirements is performed in this step.
-\item Commissioning phase: In the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice.
-\item Operation phase: During the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated.
-As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
-\item Decommissioning phase: A NSI that is decommissioned no longer exists after the decommissioning phase.
-\end{itemize}
-
-We added a new subsection II-G about Slice management for this question.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment 5:} ``Finally, the authors propose an interesting solution, however in none of the results information with respect to the convergence time of the algorithm were presented.
-This becomes extremely crucial when considering the real deployment of such a solution.
-In that regard, some findings with regard to this aspect need to be definitely included in the work.''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-It is shown in Fig. 11 and subsection III-C-1 and III-C-2.
-
 \end{document}

### 2022-06-06 Journal1/paper5TNSM/pr.tex
change paper after revision

--- 2022-03-22 Journal1/paper4TNSM/pr.tex
@@
 \subsection{State Of The Arts}
-\textcolor{MidnightBlue}{To achieve the desired level of QoS (i.e., quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks.
-There are diferent implementations of network slicing, including core slicing, RAN slicing, and both.
+\textcolor{MidnightBlue}{Network slicing is the most effective solution for 5G wireless cellular networks to achieve the desired level of QoS (i.e., quality, delay, power, etc.).
+Network slicing can provide resource isolation for different services, increasing the system's efficiency.
+This architecture has various implementations, including core slicing, RAN slicing, and both.}
+
 Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
@@
 The eMBB service fulfills the demand for high capacity and throughput.
-The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency.
-mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads
+Moreover, the URLLC service offers autonomous vehicles, tactile internet, remote surgery services, and high quality and low latency services.
+However, mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads
 \cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.
-}
-
-\textcolor{MidnightBlue}{This paper considers a number of user equipments (UEs) requesting one of these types of services with different QoS.
-We would like to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}
-
-\textcolor{MidnightBlue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
-O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (CRAN).
+
+This paper considers several user equipments (UEs) requesting one of these types of services with different QoS.
+We would like to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
+
+O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
+O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
 With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly.
-The CRAN divides the radio remote head (RRH) and baseband unit (BBU) into two major parts.
+The C-RAN architecture divides the radio remote head (RRH) and baseband unit (BBU) into two major parts.
 Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
-Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).}
-
-\textcolor{MidnightBlue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
+Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+
+O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
 In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
@@
 Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
-The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.}
-
-\textcolor{MidnightBlue}{This paper aims to design a RAN slicing technology for the O-RAN architecture. }
+The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
+
+This paper aims to design a RAN slicing technology for the O-RAN architecture. 
 %O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
@@
 
-Network function virtualization (NFV) is referred to the separation of network software and hardware elements such that network function can run on commodity hardware.
-Virtual network functions (VNF) are system function blocks in NFV systems.
+\textcolor{MidnightBlue}{The concept of network function virtualization (NFV) refers to the separation of network software and hardware elements.
+Therefore network functions can run on commodity hardware.} Virtual network functions (VNF) are system function blocks in NFV systems.
 The NFV technology offers to execute VNFs as virtual machines or containers on a cloud environment \cite{mijumbi2015network, luo2020online}.
-As a result, some O-RAN components, such as user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are being virtualized and implemented as VNFs that can be run as virtual machines (VMs) or containers.
-
-\textcolor{MidnightBlue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
-As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.}
+\textcolor{MidnightBlue}{As a result, some O-RAN components, such as user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are virtualized and implemented as VNFs.
+VNFs can also be deployed as virtual machines (VMs) or containers.}
+
+This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
+As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.
 \subsection{Related Literature}
@@
 The network slicing scheme includes a higher level and the lower level.
-The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity.
-Also, the allocation of power and physical resource blocks (PRB) is performed in the lower level.
+The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), and the allocation of BBU capacity.
+Also, the allocation of power and physical resource blocks (PRB) is performed at the lower level.
 In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it.
@@
 In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
- In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and URLLC services.
-The system guarantees the latency, the service rate, and the maintenance of reliability.
+ In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
+The system guarantees latency, service rate, and reliability maintenance.
 
@@
 In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN.
-Also the problem of RRH to BBU and the RRH to UE association is obtained.
-Moreover, the author talked about the feasible region to make the initial values possible.
+Also, the problem of RRH to BBU and the RRH to UE association is obtained.
+Moreover, the author discussed the feasible region to make the initial values possible.
 \subsection{Main Contributions}
-\textcolor{MidnightBlue}{The purpose of this paper is twofold.
+The purpose of this paper is twofold.
 First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
@@
 Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
-In this paper, we would like to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
-Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
-The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
+
+\textcolor{MidnightBlue}{In this paper, we would like to enhance the resource utilization of the overall wireless O-RAN system and optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.}
+
+\textcolor{MidnightBlue}{Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
 We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.}
@@
 \begin{itemize}
-\item \textcolor{MidnightBlue}{This paper depicts a network slicing model for three different services introduced in 5G, i.e., eMBB, mMTC, and URLLC.
-Within the O-RAN architecture, the problem of radio resource allocation and VNF activation is explored.
-Based on different types of services with different QoS and service priorities, we formulate a problem for the allocation of baseband resources to maximize the weighted throughput of O-RAN.}
-\item \textcolor{MidnightBlue}{We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers.
+\item \textcolor{MidnightBlue}{The paper presents a network slicing model for three 5G services: eMBB, mMTC, and URLLC.
+We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
+Based on different types of services with different QoS and service priorities, we formulate a problem for allocating baseband resources to maximize the weighted throughput of O-RAN.}
+\item We consider the processing delay and the VNF resources needed for the slice compared to other papers.
 Therefore, we focus on obtaining the optimal number of VNFs in each layer of the O-RAN architecture.
-}
-\item \textcolor{MidnightBlue}{Different services need to consider varying QoS conditions, including delay, power, and throughput.
-According to the number of activated VNFs and the throughput of the users, we calculate the end-to-end processing delay of the system.
-Assuming a limited fronthaul capacity, we calculate each O-RU's actual power and capacity.
-Depending on the service type, we model the interference of neighboring O-RUs and determine the actual throughput.
-Our model accounts for the short packet transmission of URLLC, and mMTC, which cannot be modeled by the Shannon capacity theorem.}
-\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
+\item \textcolor{MidnightBlue}{Various QoS conditions is considered, including delay, power, and throughput.
+According to the number of activated VNFs and the throughput of the UEs, we calculate the end-to-end processing delay of the system.
+Assuming a limited fronthaul capacity, we calculate each O-RU's power and capacity.
+Depending on the service type, we model the interference of neighboring O-RUs and determine the throughput.
+The Shannon capacity theorem cannot account for URLLC and mMTC because they are short packet transmissions.}
+\item The main problem is mixed-integer non-linear programming that is difficult to solve.
 We perform a two-step iterative algorithm to solve it.
-The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
-\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
+The algorithm is presented for resource management with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
+\item We reformulate and simplify the main problem for the first step of finding an upper and lower bound for the number of activated VNFs and using lagrangian function and KKT conditions to find optimal power and PRB allocation.
 For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
@@
 %All $K$ PRBs can be assigned to all UEs in each service.
-\textcolor{MidnightBlue}{ Assume there are $K$ physical resource blocks (PRBs) in this system.
+Assume there are $K$ physical resource blocks (PRBs) in this system.
 Suppose each slice $s$ consists of $\bar{K}_s$ pre-allocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
 Therefore, we have $\sum_s \bar{K}_s \leq K$.
-}
+
 In addition, there are $R$ multi-antenna O-RUs that are shared between slices.
@@
 
-\textcolor{MidnightBlue}{A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set of $r' \in R \not\in r$ that are using the same PRB $k$.
-Two types of interference occur between UEs in each slice; the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.}
-
-\textcolor{MidnightBlue}{Network Slicing techniques significantly reduce inter-service interference.
+A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set of $r' \in R \not\in r$ that are using the same PRB $k$.
+Two types of interference occur between UEs in each slice; the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
+
+Network Slicing techniques significantly reduce inter-service interference.
 Some methods apply the network slicing technique in PRB scheduling to isolate PRBs in slices and remove inter-slice interference.
@@
 In this paper, we assume that the PRB scheduling is performed.
-Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.}
+Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
 \begin{figure}
@@
 \end{figure}
-\textcolor{MidnightBlue}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as}
+ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as
 %{\color{red} use paranthesis in the following equation to clear +}
@@
 You  define on variable here.)
-\textcolor{MidnightBlue}{Furthermore, there is no inter-slice interference since slices are isolated. Therefore, there exist only intra-slice interference.}
-
-\textcolor{MidnightBlue}{Here, there are two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
-The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.}
-\textcolor{MidnightBlue}{To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
+Furthermore, there is no inter-slice interference since slices are isolated. Therefore, there exist only intra-slice interference.
+
+Here, there are two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
+The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.
+To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
 \begin{equation}\label{eq2}
@@
 \end{equation}
-}
+
 %\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
-\textcolor{MidnightBlue}{where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
+where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
 Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
@@
 In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }$ indicates the quantization Gaussian noise
-($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.}
+($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.
 \begin{figure}
@@
 
-\textcolor{MidnightBlue}{Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation.
+Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation.
 However, they can be added to the system model easily.
 In this paper, we focus only on the processing delay to find the optimal number of VNFs, and we consider the other two delays are fixed.
-We discuss these two types of delay in detail below and explain why we do not consider them in our work.}
-
-\textcolor{MidnightBlue}{The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority.
+We discuss these two types of delay in detail below and explain why we do not consider them in our work.
+
+The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority.
 Also, the connections of O-DUs to O-CUs are the same as O-RU to O-DU.
@@
 As a result, the propagation delay is fixed and does not affect the optimization problem.
-The following is a brief calculation of propagation delay.}
-
-\textcolor{MidnightBlue}{Since the distance between the O-RU and O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
+The following is a brief calculation of propagation delay.
+
+Since the distance between the O-RU and O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
 Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}.
@@
 Also, due to the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced.
-But we also do not focus on edge processing in this paper.}
-\textcolor{MidnightBlue}{The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has such a small amount.
+But we also do not focus on edge processing in this paper.
+The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has such a small amount.
 In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$.
@@
 for eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.
-}
 
@@
 
-\textcolor{MidnightBlue}{The processing delay can be modeled as an M/M/1 queue; since the system's arrival packets are from many independent sources.
+The processing delay can be modeled as an M/M/1 queue; since the system's arrival packets are from many independent sources.
 Moreover, the impact of a single packet on the system's performance is minimal.
@@
 Therefore, one service could have a higher priority, affecting the whole optimization, and the M/M/1 queue theory is still validated.
-}
+
 \subsection{VNF Power}
@@
 
-\textcolor{MidnightBlue}{A significant issue facing the industry is reducing energy consumption.
+A significant issue facing the industry is reducing energy consumption.
 Data centers are one of the most energy-consuming.
@@
 So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers.
-So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).}
+So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).
 \subsection{Problem Statement}
@@
 \subsubsection{PRB Scheduling}\label{prb}
-\textcolor{MidnightBlue}{ In this section, we provide a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
+ In this section, we provide a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
 We need to have an algorithm to remove the inter-slice interference before solving the problem \ref{problem}.
@@
 By relaxing $\bar{K_s}$, the objective function and constraints become convex and can be solved using the Lagrangian function.
-}
+
 \subsection{Slice Management}
-\textcolor{MidnightBlue}{In this subsection, we will look at the life cycle of network slicing on a practical level. 
+In this subsection, we will look at the life cycle of network slicing on a practical level. 
 The goal is to examine slice management, which includes creating, managing, and deleting slices.
@@
 After that, we use our algorithm to find the optimal number of VNFs for each slice and PRB assignment and power allocation.
-Therefore, in the preparation phase, we estimate our resource of slices, and in the commission phase, we allocate our resources to the slices.}
+Therefore, in the preparation phase, we estimate our resource of slices, and in the commission phase, we allocate our resources to the slices.
 %\vspace*{-1em}
@@
 
-\textcolor{MidnightBlue}{The problem \eqref{problem} is feasible and has feasibility points discussed in Subsection \ref{fr}, and we introduce a fast algorithm (i.e., Algorithm \ref{alg3}  in Subsection \ref{fr}) for feasibility points.
+The problem \eqref{problem} is feasible and has feasibility points discussed in Subsection \ref{fr}, and we introduce a fast algorithm (i.e., Algorithm \ref{alg3}  in Subsection \ref{fr}) for feasibility points.
 Although the problem is feasible, it is not convex and challenging to solve.
@@
 The objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
-After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs in each slice ($M_s$).}
+After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs in each slice ($M_s$).
 
@@
 Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
-\textcolor{MidnightBlue}{We consider 25 PRBs in the network. The packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes \cite{ETSI1}.}
+We consider 25 PRBs in the network. The packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes \cite{ETSI1}.
 The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$.
@@
 Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.
-\textcolor{MidnightBlue}{The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.}
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.
 \begin{table}[H]
@@
 Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
-\textcolor{MidnightBlue}{The first one is a baseline scheme, which uses random PRB allocation.
+The first one is a baseline scheme, which uses random PRB allocation.
 Therefore, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
@@
 The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
-After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma \eqref{lemma1}.}
-
-\textcolor{MidnightBlue}{For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18] and named it the dynamic resource allocation scheme (DR scheme).
+After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma \eqref{lemma1}.
+
+For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18] and named it the dynamic resource allocation scheme (DR scheme). 
  We have services with different QoS in this work, similar to tenants with different QoS introduced in \cite{lee2018dynamic}.
@@
 The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.
-}
+
 \vspace*{-1em}

### 2022-06-06 Latex/journal_v2/version5/pr.tex
change paper after revision

--- 2022-05-21 Latex/journal_v2/version4/pr.tex
@@
 & \sum_k^K \sum_i^{U_e} p^k_i(t) \leq P_{\text{max}},  \label{p1-1} \\ 
-& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_e, \label{p2}\\
+& Pr\{{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_e, \label{p2}\\
 &T^{\text{tot}, e}_i(t)  \leq T_{min}^e  \quad \forall i \in \mathcal{U}_e, \label{p2-1} \\
 &T^{\text{tot}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in \mathcal{U}_u, \label{p3} \\
-& \bar{\mathcal{R}}_{j}^u(t) \geq  \mathcal{R}_{min}^u \quad \forall j \in \mathcal{U}_u, \label{p3-1} \\
+& {\mathcal{R}}_{j}^u(t) \geq  \mathcal{R}_{min}^u \quad \forall j \in \mathcal{U}_u, \label{p3-1} \\
 &Pr\{T^{\text{RU}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in \mathcal{U}_u, \label{p4} \\
@@
 & \mu^l_s \geq \alpha_s/M^l_s \quad l \in \{c,d\}, s\in\{e,u\}, \label{p8} \\
-& {\mathcal{R}}^s(t) \geq {\lambda}_{\mathfrak{i},s}^u(t) \quad \forall \mathfrak{i} \in \mathcal{U}_s, s\in \{e,u\}\label{p9} \\
-& 0 \leq M^l_e  + M^l_u \leq M_{max}^l  \quad l \in \{c,d\},\label{p10}
+& {\mathcal{R}_{\mathfrak{i}}}^s(t) \geq {\lambda}_{\mathfrak{i},s}(t) \quad \forall \mathfrak{i} \in \mathcal{U}_s, s\in \{e,u\}\label{p9} \\
+& 0 \leq M^l_e  + M^l_u \leq M_{max}^l  \quad l \in \{c,d\},\label{p10}\\
+& 0 \leq M^l_e, M^l_u  \quad l \in \{c,d\},\label{p011}
 \end{alignat}
@@
 \eqref{p8} and \eqref{p9} denotes the stability of the M/M/1 queue model.
-\eqref{p10} restricts the number of VNF in each slice due to the limited resources.
+\eqref{p10}, and \eqref{p011} restricts the number of VNF in each slice due to the limited resources.
 
@@
 In this section, we are talking about our proposed algorithm to solve the problem \eqref{mainP}.
-Since this problem is mixed-integer nonlinear programming (MINLP) with binary and integer variables, it is complicated to solve. Also, this is a two-time scale problem.
+Since this problem is mixed-integer nonlinear programming (MINLP) with binary and integer variables, it is NP-hard and complicated to solve. Also, this is a two-time scale problem.
 Therefore, We need to solve this problem on a two-time scale. On a large time scale, the problem of assigning RB to eMBB service is obtained and then the power allocation is performed. 
@@
 \begin{alignat}{4}
-\max\limits_{ \boldsymbol{E},\boldsymbol{M}, \boldsymbol{P}} &  \sum_i {\mathcal{R}}_{i}^e(t) - \eta T^{\text{proc}, u}(t)       \ \\
-\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_1, \label{p11} \\
-& \sum_k^K \sum_i^{U_e} p^k_i(t) \leq P_{\text{max}},  \label{p11-1} \\
-& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_1, \label{p12}\\
-&T^{\text{tot}, e}_i(t)  \leq T_{min}^e  \quad \forall i \in \mathcal{U}_e, \label{p12-1} \\
-&T^{\text{process}, u}_i(t)  \leq T_{\text{process,min}}^u  \quad \forall i \in \mathcal{U}_u, \label{p12-2} \\
-&\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p15} \\
-&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p16} \\
-& \mu^l_s \geq \alpha_s/M^l_s \quad l \in \{c,d\}, s\in\{e,u\},\label{p18} \\
-& 0 \leq M^l_e  + M^l_u \leq M_{max}^l  \quad l \in \{c,d\},\label{p110}
+\max\limits_{ \boldsymbol{E},\boldsymbol{M}, \boldsymbol{P}} &  \sum_i {\mathcal{R}}_{i}^e(t) - \eta T^{\text{proc}, u}(t)       \\
+\text{subject to} \quad  &\eqref{p1}, \eqref{p1-1}, \eqref{p2}, \eqref{p2-1}, \eqref{p5}, \eqref{p6}, \eqref{p8},\\
+& {\mathcal{R}}^e(t) \geq {\lambda}_{\mathfrak{i},e}(t) \quad \forall \mathfrak{i} \in \mathcal{U}_e,\\
+& \eqref{p10}, \eqref{p011},
 \end{alignat}
@@
 The problem \eqref{mainP1}, is still mixed integer non-linear programming (MINP). Here, the problem \eqref{mainP1}
-can also be decomposed into two sub-problems which is depicted as follow.
-\subsubsection{sub-problem 1}
-In this section, we want to solve the sub-problem of RB allocation of eMBB UEs.
+can be decomposed into two sub-problems which is depicted as follow.
+In this first sub-problem, we assume that the channel gain is not known, and we aim to obtain the optimal number of VNFs and RB allocation to the eMBB service.
+In the second sub-problem, we know the channel gain with error ($h = h + \Delta h$), and we want to obtain the power allocation.
+\subsubsection{eMBB RB Allocation and VNF Assignment}
+In this section, we want to solve the sub-problem of RB allocation of eMBB service and find the optimal number of VNFs for each service.
 The problem can be written as follow.
@@
 \begin{alignat}{4}
-\max\limits_{ \boldsymbol{E} } &  \sum_i \bar{\mathcal{R}}_{i}^e(t)       \ \\
-\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_1, \label{p11} \\
-&\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p115} \\
-&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p116} 
+\max\limits_{ \boldsymbol{E}, \boldsymbol{M} } &  \sum_i \bar{\mathcal{R}}_{i}^e(t) -T^{\text{proc}, u}(t)      \ \\
+\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_e, \label{pp11} \\
+&\bar{T}^{\text{tot}, e}_i(t)  \leq T_{min}^e  \quad \forall i \in \mathcal{U}_e, \label{p112-1} \\
+%&T^{\text{proc}, u}_j(t)  \leq T_{\text{proc,min}}^u  \quad \forall j \in \mathcal{U}_u, \label{p112-2} \\
+&\sum_{i=1}^{U_e}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p115} \\
+&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p116} \\
+& \mu^l_s \geq \alpha_s/M^l_s \quad l \in \{c,d\}, s\in\{e,u\},\label{p118} \\
+& 0 \leq M^l_e  + M^l_u \leq M_{max}^l  \quad l \in \{c,d\},\label{p1110} \\
+& 0 \leq M^l_e, M^l_u  \quad l \in \{c,d\},\label{p110}
 \end{alignat}
@@
 \end{subequations}
-\subsubsection{sub-problem 2}
-In this section, we want to solve the sub-problem of finding the optimal number of VNF for URLLC services.
+The problem \eqref{mainP11}, can be decomposed into two subproblems using primal decomposition. $\boldsymbol{E}$
+is the private variable and $\boldsymbol{M}$ is the decoupling variable.
+Therefore, the first subproblem is 
+\begin{subequations}
+\begin{alignat}{4}
+\max\limits_{ \boldsymbol{E}, M_e} &  \sum_i \bar{\mathcal{R}}_{i}^e(t) \\
+\text{subject to} \quad  & \eqref{pp11},\eqref{p112-1}, \eqref{p115}, \eqref{p116},\\
+& \mu^l_e \geq \alpha_e/M^l_e \quad l \in \{c,d\},\label{pp118} \\
+& 0 \leq M^l_e \leq \tau
+\end{alignat}
+\end{subequations}
+Moreover, the second subproblem is 
+\begin{subequations}
+\begin{alignat}{4}
+\min\limits_{ M_u } &  T^{\text{proc}, u}(t) \\
+\text{subject to} \quad & \mu^l_u \geq \alpha_s/M^l_u \quad l \in \{c,d\},\label{pp118} \\
+& 0 \leq M^l_u \leq M_{max}^l -\tau
+\end{alignat}
+\end{subequations} 
+\subsubsection{eMBB Power Allocation}
+In this section, we want to solve the sub-problem of power allocation for eMBB UEs.
 The problem is formulated as follow.
-\begin{subequations} \label{mainP2}
+\begin{subequations} \label{mainP12}
 \begin{alignat}{4}
-\min\limits_{ \boldsymbol{M} } &  T^{\text{proc}, u}(t)       \ \\
-\text{subject to} \quad  & \mu^l \geq \alpha/M^l \quad l \in \{c,d\},\label{p28} \\
-& 0 \leq M^l \leq M_{max}^l  \quad l \in \{c,d\},\label{p210}
+\max\limits_{ \boldsymbol{P} } &  \sum_i {\mathcal{R}}_{i}^e(t)       \ \\
+\text{subject to} \quad  & \eqref{p1-1}, \eqref{p2}, \eqref{p2-1},
 \end{alignat}
@@
 \subsection{Small time scale}
-In the small time scale, we assume that the eMBB RB allocation is performed and the optimal number of VNF for URLLC is obtained. Therefore, the problem of puncturing URLLC UEs is performed.
+In the small time scale, we assume that the eMBB RB allocation is performed and the optimal number of VNF for URLLC is obtained. Therefore, the problem of puncturing URLLC UEs is considered.
 \begin{subequations} \label{mainP2}
 \begin{alignat}{4}
-\min\limits_{  \boldsymbol{\Psi} } &  \sum_j T^{RU, u}(t)       \ \\
-\text{subject to} \quad  &T^{\text{tot}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in \mathcal{U}_2, \label{p33} \\
-& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_1, \label{p32}\\
-&Pr\{T^{\text{RU}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in \mathcal{U}_2, \label{p34} \\
-& 0 \leq n^k_i(t)\leq 1  \quad \forall i,k, \label{p37} \\
-& \bar{\mathcal{R}}^u(t) \geq {\lambda}_{j}^u(t) \quad \forall j \in \mathcal{U}_2,\label{p39} 
+\min\limits_{  \boldsymbol{X} } &  \sum_j T^{RU, u}(t)       \ \\
+\text{subject to} \quad & Pr\{{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon_2,\quad \forall i \in \mathcal{U}_e, \label{p32}\\
+&Pr\{T^{\text{tot}, u}_j(t) \geq T_{min}^u - T^{\text{proc}}\} \leq \epsilon_3  \quad \forall j \in \mathcal{U}_u, \label{p34} \\
+& x^k_i(t)\in \{0,1,...,L\}  \label{p37} \\
+& {\mathcal{R}_j}^u(t) \geq {\lambda}_{j}^u(t) \quad \forall j \in \mathcal{U}_u,\label{p39} 
 \end{alignat}

### 2022-06-08 Journal1/Response3/Response.tex
revise paper 1

@@
 \noindent \textbf{Response:\\}
-We have changed the paper's introduction and checked the text entirely according to this comment.
+Thank you for this comment. We changed the paper's figures totally according to this comment.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-We have changed the paper's introduction and checked the text entirely according to this comment.
+We thank the reviewer for adding clarity to our paper and reducing ambiguity in this condition.
+We changed the contribution in a better way based on this comment.
+We have removed some sentences and rewritten the contribution in order to our paper's section.
+Below we write the whole contribution section.
+
+The purpose of this paper is twofold.
+First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
+Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
+Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
+
+In this paper, we would like to enhance the resource utilization of the overall wireless O-RAN system and optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
+
+Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
+We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.
+
+In this paper, as depicted in Figure 1, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
+\begin{itemize}
+\item The paper presents a network slicing model for three 5G services: eMBB, mMTC, and URLLC. We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
+Based on different types of services with different QoS and service priorities, we formulate a problem for allocating baseband resources to maximize the weighted throughput of O-RAN.
+\item The focus of our paper is on the multi-service resource management of the RAN, slicing in the flexibility, openness, and openness of the O-RAN architecture.
+\item We propose an algorithm for resource management in a two-step, with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
+In the first step, we reformulate and simplify the problem to find an upper and lower bound for the number of activated VNFs and use the Lagrangian function and KKT conditions to find optimal power and PRB allocation.
+For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
+\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
+\item We perform numerical experiments to analyze the performance of the proposed algorithm, which proves to have a higher data rate than both the baseline scheme and data-driven method.
+Interestingly, our results show that this algorithm performs close to the optimal solution in low interference.
+\end{itemize}
+
+% % % % % % % % % % % % % % % Reviewer 2 % % % % % % % % % % % % % % % % % % % %
+\clearpage
+\noindent
+\begin{longtable}{|p{.975\textwidth}|}
+\hline \hline %\hline \hline \hline
+\Centering
+\cellcolor{gray!60}
+\textbf{Reviewer 2} \\
+\hline \hline %\hline \hline \hline
+\RaggedRight
+\cellcolor{violet!15}
+\textbf{\noindent Comments to the Author} ``
+The Reviewer would like to thank the authors for their revision of the paper with respect to the comments and suggestions in the previous submission.
+Whereas the authors have considered parts of the suggestions and improved specific areas of the work, there are still a lot of remaining issues of concern in the current version of the paper.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+It is our pleasure to thank the reviewer for the careful reading of this manuscript, providing
+thoughtful comments, and offering constructive suggestions that strengthened and enhanced its
+quality. We hope that the responses provided herein can alleviate the reviewer’s concerns.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment1:} ``While the authors have taken into consideration the Reviewer’s comments about the re-structuring of the Introduction, I am afraid that the current version is not in the adequate state for publication.
+Initially, the paragraphs of the Introduction have no logical connection among them.
+It seems that until the Related Literature subsection all paragraphs are disconnected and only introduce concepts.
+However, there is no smooth transitioning between them and it gives the impression that those paragraphs are disconnected from each other.
+Moreover, I find the ORAN explanation in the Introduction very lengthy and unnecessary.
+I would definitely suggest to move that as a background Section.
+Furthermore, it is surprising how the Introduction does not contain a single research challenge.
+Why is the problem relevant at all?
+Why do you even need to study this problem and why is it hard to solve?
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We would like to thank the reviewer for the careful and thorough reading of our manuscript and the thoughtful comment and constructive suggestions that helped us improve the quality of this manuscript and make it more readable.
 

### 2022-06-08 Journal1/paper5TNSM/pr.tex
revise paper 1

@@
 \section{Introduction}
-\subsection{State Of The Arts}
+%\subsection{State Of The Arts}
 \textcolor{MidnightBlue}{Network slicing is the most effective solution for 5G wireless cellular networks to achieve the desired level of QoS (i.e., quality, delay, power, etc.).
-Network slicing can provide resource isolation for different services, increasing the system's efficiency.
-This architecture has various implementations, including core slicing, RAN slicing, and both.}
+Network slicing can provide resource isolation for various services, increasing the system's efficiency.
+This architecture has several implementations, including core slicing, radio access network (RAN) slicing, and both for different 5G services.
+The network slicing concept has the potential to serve multiple services with varying architectures and quality of service (QoS) requirements.}
 
@@
 The eMBB service fulfills the demand for high capacity and throughput.
-Moreover, the URLLC service offers autonomous vehicles, tactile internet, remote surgery services, and high quality and low latency services.
+Moreover, the URLLC service offers autonomous vehicles, tactile internet, remote surgery services, and other high-quality and low latency services.
 However, mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads
 \cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.
-
-This paper considers several user equipments (UEs) requesting one of these types of services with different QoS.
-We would like to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
-
-O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
-O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
-With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly.
-The C-RAN architecture divides the radio remote head (RRH) and baseband unit (BBU) into two major parts.
-Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
-Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-
-O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
-In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
-O-DU and O-CU are connected via an open and well-defined interface $F_1$.
-Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
-The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
-
-This paper aims to design a RAN slicing technology for the O-RAN architecture. 
+\textcolor{MidnightBlue}{Nevertheless, the existing radio access network (RAN) architecture lacks adequate flexibility and openness to manage these demands for various services simultaneously.
+Therefore, development in RAN architecture is needed to support these requirements for different services simultaneously.
+Open radio access network (O-RAN) is the new RAN generation introduced to deal with these issues.}
+%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
+We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
+%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
 %O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
@@
 
-\textcolor{MidnightBlue}{The concept of network function virtualization (NFV) refers to the separation of network software and hardware elements.
-Therefore network functions can run on commodity hardware.} Virtual network functions (VNF) are system function blocks in NFV systems.
-The NFV technology offers to execute VNFs as virtual machines or containers on a cloud environment \cite{mijumbi2015network, luo2020online}.
-\textcolor{MidnightBlue}{As a result, some O-RAN components, such as user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are virtualized and implemented as VNFs.
+\textcolor{MidnightBlue}{The hardware is decoupled from the software in the O-RAN architecture, and each component is implemented as a virtual network function (VNF) that can be deployed on a virtual machine (VM) or container.
+}
+\textcolor{MidnightBlue}{Virtual network functions (VNF) are system function blocks in network function virtualization (NFV) systems.
+The concept of NFV refers to the separation of network software and hardware elements.
+Therefore network functions can run on commodity hardware.
+The NFV technology offers to execute VNFs as VMs or containers on a cloud environment \cite{mijumbi2015network, luo2020online}.}
+\textcolor{MidnightBlue}{As a result, some O-RAN components defined in section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit O-DU, and RAN Intelligent Controller (RIC)-near real-time, are near real-time virtualized and implemented as VNFs.
 VNFs can also be deployed as virtual machines (VMs) or containers.}
@@
 As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.
-\subsection{Related Literature}
+
+\subsection{Motivations}
+
+\subsection{Main Contributions}
+The purpose of this paper is twofold.
+First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
+Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
+Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
+
+\textcolor{MidnightBlue}{In this paper, we would like to enhance the resource utilization of the overall wireless O-RAN system and optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.}
+
+\textcolor{MidnightBlue}{Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
+We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.}
+
+In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
+\begin{itemize}
+\item \textcolor{MidnightBlue}{The paper presents a network slicing model for three 5G services: eMBB, mMTC, and URLLC.
+We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
+Based on different types of services with different QoS and service priorities, we formulate a problem for allocating baseband resources to maximize the weighted throughput of O-RAN.}
+
+%\item \textcolor{MidnightBlue}{Various QoS conditions is considered, including delay, power, and throughput.
+According to the number of activated VNFs and the throughput of the UEs, we calculate the end-to-end processing delay of the system.
+%Assuming a limited fronthaul capacity, we calculate each O-RU's power and capacity.
+Depending on the service type, we model the interference of neighboring O-RUs and determine the throughput.
+The Shannon capacity theorem cannot account for URLLC and mMTC because they are short packet transmissions.}
+%\item The main problem is mixed-integer non-linear programming that is difficult to solve.
+%We perform a two-step iterative algorithm to solve it.
+\item \textcolor{MidnightBlue}{The focus of our paper is on the multi-service resource management of the RAN, slicing in the flexibility, openness, and openness of the O-RAN architecture.}
+\item \textcolor{MidnightBlue}{We propose an algorithm for resource management in a two-step, with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
+In the first step, we reformulate and simplify the problem to find an upper and lower bound for the number of activated VNFs and use the Lagrangian function and KKT conditions to find optimal power and PRB allocation.
+For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.}
+\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
+\item \textcolor{MidnightBlue}{We perform numerical experiments to analyze the performance of the proposed algorithm, which proves to have a higher data rate than both the baseline scheme and data-driven method.
+Interestingly, our results show that this algorithm performs close to the optimal solution in low interference.}
+\end{itemize}
+
+The rest of this paper is organized as follows. The related literature is presented in Section \ref{RL}. In Section \ref{BG}, the background is explained.
+The system model and the problem formulation are described in Section \ref{systemmodel}.
+The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}.
+In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm.
+Section \ref{conc} concludes the paper.
+
+\section{Related Literature}\label{RL}
 The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
@@
 Moreover, the author discussed the feasible region to make the initial values possible.
-\subsection{Main Contributions}
-The purpose of this paper is twofold.
-First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
-Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
-Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
-
-\textcolor{MidnightBlue}{In this paper, we would like to enhance the resource utilization of the overall wireless O-RAN system and optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.}
-
-\textcolor{MidnightBlue}{Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
-We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.}
-
-In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
-\begin{itemize}
-\item \textcolor{MidnightBlue}{The paper presents a network slicing model for three 5G services: eMBB, mMTC, and URLLC.
-We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
-Based on different types of services with different QoS and service priorities, we formulate a problem for allocating baseband resources to maximize the weighted throughput of O-RAN.}
-\item We consider the processing delay and the VNF resources needed for the slice compared to other papers.
-Therefore, we focus on obtaining the optimal number of VNFs in each layer of the O-RAN architecture.
-\item \textcolor{MidnightBlue}{Various QoS conditions is considered, including delay, power, and throughput.
-According to the number of activated VNFs and the throughput of the UEs, we calculate the end-to-end processing delay of the system.
-Assuming a limited fronthaul capacity, we calculate each O-RU's power and capacity.
-Depending on the service type, we model the interference of neighboring O-RUs and determine the throughput.
-The Shannon capacity theorem cannot account for URLLC and mMTC because they are short packet transmissions.}
-\item The main problem is mixed-integer non-linear programming that is difficult to solve.
-We perform a two-step iterative algorithm to solve it.
-The algorithm is presented for resource management with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
-\item We reformulate and simplify the main problem for the first step of finding an upper and lower bound for the number of activated VNFs and using lagrangian function and KKT conditions to find optimal power and PRB allocation.
-For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
-\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
-\end{itemize}
+\section{Background}\label{BG}
+\textcolor{MidnightBlue}{The Open Radio Access Network (O-RAN) is an appropriate alternative to the next generation of radio access networks due to its flexible operations, openness, lower operational costs, and intelligence.}
+
+O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
+O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
+With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
+The C-RAN architecture divides the radio remote head (RRH) and baseband unit (BBU) into two major parts.
+Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
+Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+
+O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
+In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
+O-DU and O-CU are connected via an open and well-defined interface $F_1$.
+Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
+The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
 \begin{figure*}
@@
 \end{figure*}
-The rest of this paper is organized as follows.
-The system model and the problem formulation are described in Section \ref{systemmodel}.
-The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}.
-In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm.
-Section \ref{conc} concludes the  paper.
 \section{System Model and Problem Formulation}\label{systemmodel}
@@
 Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
-\begin{figure*}%[!tbp]
+\begin{figure}%[!tbp]
   \centering
   \captionsetup{justification=centering}
-  \begin{minipage}[b]{0.4\textwidth}
-    \includegraphics[scale = 0.3]{Arate_ue1_1.eps}
+    \includegraphics[width=7cm,height=4cm]{Arate_ue1_1.eps}
     \caption{Aggregate throughput vs. number of UEs in each service}% in the presence of three services}
     \label{fig:1}
-  \end{minipage}
-  \qquad
-  \begin{minipage}[b]{0.4\textwidth}
-       \includegraphics[scale = 0.30]{vnfNum1.eps}
+\end{figure}
+
+\begin{figure}
+\centering
+  \captionsetup{justification=centering}
+       \includegraphics[width=7cm,height=4cm]{vnfNum1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
   \label{fig:4}
-  \end{minipage}
-\end{figure*}
+\end{figure}
 %%%%%%%%%
@@
 Moreover, the proposed method (IABV), gives higher aggregate rates in compared to the DR scheme and the baseline scheme.
-\begin{figure*}%[!tbp]
+\begin{figure}%[!tbp]
   \centering
   \captionsetup{justification=centering}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[scale = 0.3]{RatePower1.eps}
+    \includegraphics[width=7cm,height=4cm]{RatePower1.eps}
     \caption{Aggregate Throughput for eMBB vs. Maximum Transmit power for various number of UEs }
   \label{fig:5}
-  \end{minipage}
-  \qquad
-  \begin{minipage}[b]{0.45\textwidth}
-      \includegraphics[scale = 0.3]{delay_new.eps}
+\end{figure}
+\begin{figure}
+  \centering
+  \captionsetup{justification=centering}
+      \includegraphics[width=7cm,height=4cm]{delay_new.eps}
   \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}
   \label{fig:6}
-  \end{minipage}
-\end{figure*}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \captionsetup{justification=centering}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[scale = 0.3]{delay1_new.eps}
+    \includegraphics[width=7cm,height=4cm]{delay1_new.eps}
     \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}
   \label{fig:7}
-  \end{minipage}
-  \quad
-  \begin{minipage}[b]{0.45\textwidth}
-       \includegraphics[scale = 0.3]{AmmTCpower.eps}
+\end{figure}
+\begin{figure}%[!tbp]
+  \centering
+  \captionsetup{justification=centering}
+       \includegraphics[width=7cm,height=4cm]{AmmTCpower.eps}
   \caption{Aggregate Throughput vs. Number of UEs in each Service for three different mMTC services}
   \label{fig:8}
-  \end{minipage}
 \end{figure}
@@
   \captionsetup{justification=centering}
-        \includegraphics[scale = 0.3]{priorityLast.eps}
+        \includegraphics[width=7cm,height=4cm]{priorityLast.eps}
   \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
@@
   \captionsetup{justification=centering}
-  \begin{minipage}[b]{0.4\textwidth}
-     \includegraphics[scale = 0.31]{iter.eps}
+     \includegraphics[width=7cm,height=4cm]{iter.eps}
   \caption{Aggregate Throughput vs. Number of Iterations}
   \label{fig:11}
-  \end{minipage}
-    \qquad
-  \begin{minipage}[b]{0.4\textwidth}
-   \includegraphics[scale = 0.3]{optimal1.eps}
+\end{figure}
+\begin{figure}%[tbp]
+  \centering
+  \captionsetup{justification=centering}
+   \includegraphics[width=7cm,height=4cm]{optimal1.eps}
   \caption{Aggregate Throughput vs. Number of UEs in one Service}
   \label{fig:12}
-  \end{minipage}
 \end{figure}
@@
   \captionsetup{justification=centering}
-  \begin{minipage}[b]{0.4\textwidth}
-   \includegraphics[scale = 0.3]{interF_new.eps}
+   \includegraphics[width=7cm,height=4cm]{interF_new.eps}
   \caption{\small Aggregate Throughput vs. Maximum Interference }
   \label{fig:13}
-  \end{minipage}
-    \qquad
-  \begin{minipage}[b]{0.4\textwidth}
-    \includegraphics[scale = 0.3]{FA.eps}
+\end{figure}
+\begin{figure}%[tbp]
+  \centering
+  \captionsetup{justification=centering}
+    \includegraphics[width=7cm,height=4cm]{FA.eps}
   \caption{\small Aggregate Throughput vs. the Number of UEs in one Service }
   \label{fig:14}
-  \end{minipage}
+
 \end{figure}

### 2022-06-09 Journal1/paper5TNSM/pr.tex
add paper

@@
 \subsection{Motivations}
-
+\textcolor{MidnightBlue}{The studies in \cite{yue2021beamforming, moosavi2021delay, ali2019energy} have investigated resource allocation in C-RAN by considering the limitation on power and delay, respectively.
+However, this architecture is inefficient whenever we have different services with different QoS simultaneously.
+Additionally, RAN slicing requires a more flexible and open architecture.
+Therefore, we need a new architecture that supports slicing to implement RAN slicing for various services.
+O-RAN architecture has emerged as
+a new architecture that can serve different services simultaneously using RAN slicing.
+In \cite{setayesh2020joint}, the RAN slicing is considered for C-RAN architecture for eMBB and URLLC.
+Nevertheless, the authors did not consider latency for URLLC, which is the main property of the URLLC.
+Moreover, the authors did not consider the weakness of C-RAN architecture.
+In \cite{kazemifard2021minimum}, the authors examine the total delay of the UE in the O-RAN architecture. However, the paper did not consider the different services and other QoS. 
+}
+
+\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
+Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
+We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously. 
+Therefore, we want to study the problem of obtaining the optimal number of VNF, RB assignments, and power allocation to maximize the system's throughput and guarantee the QoS of services.
+This problem is mixed-integer non-linear programming.
+Hence, it is difficult to solve and requires some relaxation, convexification, and other methods for obtaining the sub-optimal solution presented in the following sections.}
 \subsection{Main Contributions}

### 2022-06-10 Journal1/Response3/Response.tex
add response

@@
 It seems that until the Related Literature subsection all paragraphs are disconnected and only introduce concepts.
-However, there is no smooth transitioning between them and it gives the impression that those paragraphs are disconnected from each other.
-Moreover, I find the ORAN explanation in the Introduction very lengthy and unnecessary.
-I would definitely suggest to move that as a background Section.
-Furthermore, it is surprising how the Introduction does not contain a single research challenge.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We would like to thank the reviewer for the careful and thorough reading of our manuscript and the thoughtful comment and constructive suggestions that helped us improve the quality of this manuscript and make it more readable.
+We changed the introduction and add it below
+
+Network slicing is the most effective solution for 5G wireless cellular networks to achieve the desired level of QoS (i.e., quality, delay, power, etc.).
+Network slicing can provide resource isolation for various services, increasing the system's efficiency.
+This architecture has several implementations, including core slicing, radio access network (RAN) slicing, and both for different 5G services.
+The network slicing concept has the potential to serve multiple services with varying architectures and quality of service (QoS) requirements.
+
+Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
+Depending on QoS, each service requires its slice of the network.
+The eMBB service fulfills the demand for high capacity and throughput.
+Moreover, the URLLC service offers autonomous vehicles, tactile internet, remote surgery services, and other high-quality and low latency services.
+However, mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads
+[1]–[6].
+Nevertheless, the existing radio access network (RAN) architecture lacks adequate flexibility and openness to manage these demands for various services simultaneously.
+Therefore, development in RAN architecture is needed to support these requirements for different services simultaneously.
+Open radio access network (O-RAN) is the new RAN generation introduced to deal with these issues.
+%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
+We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
+%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
+%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
+The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence
+
+The hardware is decoupled from the software in the O-RAN architecture, and each component is implemented as a virtual network function (VNF) that can be deployed on a virtual machine (VM) or container.
+Virtual network functions (VNF) are system function blocks in network function virtualization (NFV) systems.
+The concept of NFV refers to the separation of network software and hardware elements.
+Therefore network functions can run on commodity hardware.
+The NFV technology offers to execute VNFs as VMs or containers on a cloud environment [7], [8].
+As a result, some O-RAN components defined in section III, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit O-DU, and RAN Intelligent Controller (RIC)-near real-time, are near real-time virtualized and implemented as VNFs.
+VNFs can also be deployed as virtual machines (VMs) or containers.
+
+This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
+As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment2:} `` Moreover, I find the ORAN explanation in the Introduction very lengthy and unnecessary. I would definitely suggest to move that as a background Section. ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+I would appreciate your comments to enhance and clarify this section of the paper. I moved the background as a section.
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment3:} `` Furthermore, it is surprising how the Introduction does not contain a single research challenge.
 Why is the problem relevant at all?
@@
 \noindent \textbf{Response:\\}
-We would like to thank the reviewer for the careful and thorough reading of our manuscript and the thoughtful comment and constructive suggestions that helped us improve the quality of this manuscript and make it more readable.
+We add the motivation subsection and answer these questions in it. Below we rewrite this section.
+
+The studies in  [9]–[11] have investigated resource allocation in C-RAN by considering the limitation on power and delay, respectively.
+However, this architecture is inefficient whenever we have different services with different QoS simultaneously.
+Additionally, RAN slicing requires a more flexible and open architecture.
+Therefore, we need a new architecture that supports slicing to implement RAN slicing for various services.
+O-RAN architecture has emerged as
+a new architecture that can serve different services simultaneously using RAN slicing.
+In [2], the RAN slicing is considered for C-RAN architecture for eMBB and URLLC.
+Nevertheless, the authors did not consider latency for URLLC, which is the main property of the URLLC.
+Moreover, the authors did not consider the weakness of C-RAN architecture.
+In [12], the authors examine the total delay of the UE in the O-RAN architecture. However, the paper did not consider the different services and other QoS.
+
+Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
+Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
+We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously. 
+Therefore, we want to study the problem of obtaining the optimal number of VNF, RB assignments, and power allocation to maximize the system's throughput and guarantee the QoS of services.
+This problem is mixed-integer non-linear programming.
+Hence, it is difficult to solve and requires some relaxation, convexification, and other methods for obtaining the sub-optimal solution presented in the following sections.
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment4:} `` In turn, in the main contributions subsection, the initial sentences of almost all contribution paragraphs cannot be considered as contributions. For instance:
+
+1) “We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers.”
+2) “ Different services need to consider varying QoS conditions, including delay, power, and throughput.”
+3) “The main problem is mixed-integer non-linear programming that is extremely difficult to solve.”
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We removed these sentences and rewrite the contribution. Below we write the changes.
+
+The purpose of this paper is twofold.
+First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
+Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
+Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
+
+In this paper, we would like to enhance the resource utilization of the overall wireless O-RAN system and optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
+
+Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
+We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.
+
+In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
+\begin{itemize}
+\item The paper presents a network slicing model for three 5G services: eMBB, mMTC, and URLLC. We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
+Based on different types of services with different QoS and service priorities, we formulate a problem for allocating baseband resources to maximize the weighted throughput of O-RAN.
+\item The focus of our paper is on the multi-service resource management of the RAN, slicing in the flexibility, openness, and openness of the O-RAN architecture.
+\item We propose an algorithm for resource management in a two-step, with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
+In the first step, we reformulate and simplify the problem to find an upper and lower bound for the number of activated VNFs and use the Lagrangian function and KKT conditions to find optimal power and PRB allocation.
+For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
+\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
+\item We perform numerical experiments to analyze the performance of the proposed algorithm, which proves to have a higher data rate than both the baseline scheme and data-driven method.
+Interestingly, our results show that this algorithm performs close to the optimal solution in low interference.
+\end{itemize}
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment5:} `` In a similar fashion, the authors have not considered the Reviewer’s suggestion to move the Related Work as a separate Section in order to improve the flow and clarity of the Introduction.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+I changed the background from sub-section to the section part.
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment6:} `` Regarding the Reviewer’s comment with respect to the network slice management, whereas the authors have introduced the 4 stages of the life cycle of a network slice, the connection to their approach is very vague.
+It is still not clear how this process is achieved and how it is linked to their method.
+I was expecting at least a connection or introduction to Fig.1 where the system is shown.
+Additionally, more information with respect to the interaction with the system would have been required in that regard.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
 

### 2022-06-13 Journal1/paper5TNSM/pr.tex
last version

@@
 %}
-\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, and Saeede Parsaeefard$^\dagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com\\
-\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada}
+\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, Saeede Parsaeefard$^\dagger$, and Onel Luis Alcaraz López$^\ddagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com, \{onel.alcarazlopez\}@oulu.fi\\
+\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada, $^\ddagger$University of Oulu, Oulu, Finland}
  }

### 2022-06-14 Journal1/Response3/Response.tex
last version of revised paper

@@
 \noindent \textbf{Response:\\}
+We add the following part to the slice management section.
+
+In the preparation phase, firstly, the evaluation of requirements is considered.
+Therefore, In this phase, we need an algorithm to estimate the number of UEs and UE traffic in the system at different times.
+Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs for each slice, the optimal number of PRBs for each slice, and the analysis of power allocation.
+In this phase, we can use our algorithm after estimating the system's traffic.
+ As shown in figure 1, we have three different slices for eMBB, URLLC, and mMTC.
+For each slice, the system must prepare MAC/RLC protocols for O-DU, PDCP/SDAP protocols for O-CU, UPF, SMF, and AMF.
+Moreover, O-RU, high PHY in O-DU, and O-CU-CP are shared between slices.
+Thus, we do not require estimating and preparing for the share environments and platforms in the network slicing cycles.
+After evaluating, assessing, and preparing the resources and environments for each slice, the commissioning phase is started.
+In this phase, the slices are created based on the previous phase.
+If the evaluation changes, the slice's resources can be modified.
+We can use our algorithm to assign resources to the services in the operation phase.
+If we need to remove a slice or any service is not used in a zone, and we need to remove the corresponding slice, the unshared resources are removed in the decommissioning phase.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment6:} ``With respect to the convergence time of the algorithm, the Reviewer had made a suggestion to the authors to include it in the current version of the manuscript, yet the authors do not seem to have done that.
+The authors’ response points to Fig.
+11.
+However if one looks at Fig.11 carefully, understands that only the Aggregate throughput is shown there.
+Even if one considers the Section III-C1 and III-C2 that the authors demonstrate as their convergence analysis and proof, there is no evidence or clarification of any delay value with respect to their algorithm’s convergence.
+On the one hand it is very beneficial to have a mathematical proof that the algorithm converges.
+On the other hand, it is equally important to portray these findings with numerical values.
+In any case, this is not applicable in the current version of the manuscript.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
 

### 2022-06-14 Journal1/paper5TNSM/pr.tex
last version of revised paper

@@
 \end{itemize}
-In the preparation phase, the evaluation of requirements is considered.
-After that, we use our algorithm to find the optimal number of VNFs for each slice and PRB assignment and power allocation.
-Therefore, in the preparation phase, we estimate our resource of slices, and in the commission phase, we allocate our resources to the slices.
+\textcolor{MidnightBlue}{In the preparation phase, firstly, the evaluation of requirements is considered.
+Therefore, In this phase, we need an algorithm to estimate the number of UEs and UE traffic in the system at different times.
+Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs for each slice, the optimal number of PRBs for each slice, and the analysis of power allocation.
+In this phase, we can use our algorithm after estimating the system's traffic.
+As shown in figure 1, we have three different slices for eMBB, URLLC, and mMTC.
+For each slice, the system must prepare MAC/RLC protocols for O-DU, PDCP/SDAP protocols for O-CU, UPF, SMF, and AMF.
+Moreover, O-RU, high PHY in O-DU, and O-CU-CP are shared between slices.
+Thus, we do not require estimating and preparing for the share environments and platforms in the network slicing cycles.
+After evaluating, assessing, and preparing the resources and environments for each slice, the commissioning phase is started.
+In this phase, the slices are created based on the previous phase.
+If the evaluation changes, the slice's resources can be modified.
+We can use our algorithm to assign resources to the services in the operation phase.
+If we need to remove a slice or any service is not used in a zone, and we need to remove the corresponding slice, the unshared resources are removed in the decommissioning phase.}
 %\vspace*{-1em}

### 2022-06-15 Journal1/paper5TNSM/pr.tex
last versio 6-16

@@
 %\subsection{State Of The Arts}
-\textcolor{MidnightBlue}{Network slicing is the most effective solution for 5G wireless cellular networks to achieve the desired level of QoS (i.e., quality, delay, power, etc.).
-Network slicing can provide resource isolation for various services, increasing the system's efficiency.
-This architecture has several implementations, including core slicing, radio access network (RAN) slicing, and both for different 5G services.
-The network slicing concept has the potential to serve multiple services with varying architectures and quality of service (QoS) requirements.}
-
-Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-Depending on QoS, each service requires its slice of the network.
-The eMBB service fulfills the demand for high capacity and throughput.
-Moreover, the URLLC service offers autonomous vehicles, tactile internet, remote surgery services, and other high-quality and low latency services.
-However, mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads
-\cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.
-\textcolor{MidnightBlue}{Nevertheless, the existing radio access network (RAN) architecture lacks adequate flexibility and openness to manage these demands for various services simultaneously.
-Therefore, development in RAN architecture is needed to support these requirements for different services simultaneously.
-Open radio access network (O-RAN) is the new RAN generation introduced to deal with these issues.}
+\textcolor{MidnightBlue}{Network slicing is a key technology in 5G wireless systems.
+Specifically, network slicing provides the isolation of network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving multiple and heterogeneous service classes \cite{shen2020ai,setayesh2020joint,popovski20185g}.
+There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
+Depending on their corresponding quality of service (QoS) requirements, each service is assigned to a slice of the network.
+For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming.
+Meanwhile, the URLLC service, leveraged, e.g., by autonomous vehicles, Tactile Internet, and remote surgery services, is concerned with providing ultra-reliable and low-latency connectivity.
+Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.}
+%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}
+
+\textcolor{MidnightBlue}{Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
+In view of this, a new RAN paradigm, called open RAN (O-RAN), which is shown in Fig \ref{fig:c11}, is introduced to deal with these issues.}
 %This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
@@
 
-\textcolor{MidnightBlue}{The hardware is decoupled from the software in the O-RAN architecture, and each component is implemented as a virtual network function (VNF) that can be deployed on a virtual machine (VM) or container.
-}
-\textcolor{MidnightBlue}{Virtual network functions (VNF) are system function blocks in network function virtualization (NFV) systems.
-The concept of NFV refers to the separation of network software and hardware elements.
-Therefore network functions can run on commodity hardware.
-The NFV technology offers to execute VNFs as VMs or containers on a cloud environment \cite{mijumbi2015network, luo2020online}.}
-\textcolor{MidnightBlue}{As a result, some O-RAN components defined in section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit O-DU, and RAN Intelligent Controller (RIC)-near real-time, are near real-time virtualized and implemented as VNFs.
-VNFs can also be deployed as virtual machines (VMs) or containers.}
-
-This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
-As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.
-
-\subsection{Motivations}
-\textcolor{MidnightBlue}{The studies in \cite{yue2021beamforming, moosavi2021delay, ali2019energy} have investigated resource allocation in C-RAN by considering the limitation on power and delay, respectively.
+\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is decoupled from the software, indicating the concept of network function virtualization (NFV).
+Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network, luo2020online}.}
+\textcolor{MidnightBlue}{As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.}
+
+\begin{figure*}
+  \centering
+  \captionsetup{justification=centering}
+    \includegraphics[scale = 0.45]{finalDraw.pdf}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Network sliced o-ran system}
+  \label{fig:c11}
+\end{figure*}
+\subsection{Motivation}
+\textcolor{MidnightBlue}{Many researchers in the RAN field have been investigating the problem of finding the optimal resource allocation in a different generation of RAN technology to reduce the cost of the system and improve the QoS of the UEs.
+The studies in \cite{yue2021beamforming, ali2019energy} have investigated resource allocation in C-RAN by considering the limitation on power and delay, respectively.
 However, this architecture is inefficient whenever we have different services with different QoS simultaneously.
@@
 Hence, it is difficult to solve and requires some relaxation, convexification, and other methods for obtaining the sub-optimal solution presented in the following sections.}
+
 \subsection{Main Contributions}
@@
 
-\textcolor{MidnightBlue}{Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
-We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.}
-
 In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
 \begin{itemize}
-\item \textcolor{MidnightBlue}{The paper presents a network slicing model for three 5G services: eMBB, mMTC, and URLLC.
-We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
-Based on different types of services with different QoS and service priorities, we formulate a problem for allocating baseband resources to maximize the weighted throughput of O-RAN.}
-
-%\item \textcolor{MidnightBlue}{Various QoS conditions is considered, including delay, power, and throughput.
-According to the number of activated VNFs and the throughput of the UEs, we calculate the end-to-end processing delay of the system.
-%Assuming a limited fronthaul capacity, we calculate each O-RU's power and capacity.
-Depending on the service type, we model the interference of neighboring O-RUs and determine the throughput.
-The Shannon capacity theorem cannot account for URLLC and mMTC because they are short packet transmissions.}
-%\item The main problem is mixed-integer non-linear programming that is difficult to solve.
-%We perform a two-step iterative algorithm to solve it.
-\item \textcolor{MidnightBlue}{The focus of our paper is on the multi-service resource management of the RAN, slicing in the flexibility, openness, and openness of the O-RAN architecture.}
+\item \textcolor{MidnightBlue}{We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
+Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs association, and VNF activation to maximize the weighted throughput of the O-RAN.}
 \item \textcolor{MidnightBlue}{We propose an algorithm for resource management in a two-step, with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
@@
 
-The rest of this paper is organized as follows. The related literature is presented in Section \ref{RL}. In Section \ref{BG}, the background is explained.
+The rest of this paper is organized as follows.
+Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
 The system model and the problem formulation are described in Section \ref{systemmodel}.
@@
 In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm.
-Section \ref{conc} concludes the paper.
+Finally, Section \ref{conc} concludes the paper.
 
@@
 The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
-\begin{figure*}
-  \centering
-  \captionsetup{justification=centering}
-    \includegraphics[scale = 0.45]{finalDraw.pdf}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Network sliced o-ran system}
-  \label{fig:c11}
-\end{figure*}
 \section{System Model and Problem Formulation}\label{systemmodel}
@@
 
-Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation.
-However, they can be added to the system model easily.
-In this paper, we focus only on the processing delay to find the optimal number of VNFs, and we consider the other two delays are fixed.
-We discuss these two types of delay in detail below and explain why we do not consider them in our work.
+Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation. However, they can be added to the system model easily.
 
 The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority. 
-Also, the connections of O-DUs to O-CUs are the same as O-RU to O-DU.
-Therefore, different routes will be added to the system to solve the routing problem.
-Also, for URLLC and mMTC, edge processing can reduce the delay that is not considered here.
 However, it provides a new problem formulation and can be added to our system model to extend our paper in the future.
@@
 Since fronhaul, midhaul, and backhaul are fiber optics, c is the speed of light.
-Also, due to the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced.
-But we also do not focus on edge processing in this paper.
 The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has such a small amount.
@@
 Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process.
-The system's clock is constant, and the size of the tasks is not fixed.
-So, we suppose that service times are exponentially distributed [36].
-In addition, we assume that the arrival packets of each service have the same priority (in subsection II-F, we will talk about priority), and we consider priority between services, not between UEs of one service.
-As we assume that the UEs of a service have the same priority, their sent packets also have an equal priority.
-In addition, since the services are isolated, the UEs in each service have the same priority, and the processing delays of each service are independent of the other services; if we assume service priority, this priority does not invalidate the queueing theory.
-Therefore, one service could have a higher priority, affecting the whole optimization, and the M/M/1 queue theory is still validated.
+Therefore, we suppose that service times are exponentially distributed [36].
+In addition, since the services are isolated, the UEs in each service have the same priority, and the processing delays of each service are independent of the other services; Therefore, one service could have a higher priority, affecting the whole optimization, and the M/M/1 queue theory is still validated.
 
@@
 \subsubsection{Convergence Analysis}
-We can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function concerning the number of iterations \cite{gholipoor2020resource}.
+We can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function concerning the number of iterations.% \cite{gholipoor2020resource}.
 Consider the aggregate throughput as $\mathcal{T(\bold{P},\bold{E},\bold{G})} =\sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}}$.
@@
 \end{figure}
-Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
+Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent.% \cite{gholipoor2020cloud}.
 Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
@@
 Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.
+The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2,IMT, ETSI1}.%\cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.
 \begin{table}[H]

### 2022-06-25 Journal1/paper5TNSM/pr.tex
last version in oulu

@@
 \subsection{Motivation}
-\textcolor{MidnightBlue}{Many researchers in the RAN field have been investigating the problem of finding the optimal resource allocation in a different generation of RAN technology to reduce the cost of the system and improve the QoS of the UEs.
-The studies in \cite{yue2021beamforming, ali2019energy} have investigated resource allocation in C-RAN by considering the limitation on power and delay, respectively.
-However, this architecture is inefficient whenever we have different services with different QoS simultaneously.
-Additionally, RAN slicing requires a more flexible and open architecture.
-Therefore, we need a new architecture that supports slicing to implement RAN slicing for various services.
-O-RAN architecture has emerged as
-a new architecture that can serve different services simultaneously using RAN slicing.
-In \cite{setayesh2020joint}, the RAN slicing is considered for C-RAN architecture for eMBB and URLLC.
-Nevertheless, the authors did not consider latency for URLLC, which is the main property of the URLLC.
-Moreover, the authors did not consider the weakness of C-RAN architecture.
-In \cite{kazemifard2021minimum}, the authors examine the total delay of the UE in the O-RAN architecture. However, the paper did not consider the different services and other QoS. 
-}
+\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation in a different generation of RAN technology is vital to reduce the cost of the system and improve the QoS of the UEs.
+The allocation of resources in 5G faces many significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc.}
+
+\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering one service's power, data rate, and delay limitations.
+Due to the need to serve services with different QoS simultaneously, this architectural model is inefficient.
+Therefore, we need a new architecture that supports RAN slicing for various services.
+O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
+Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
+One of the fundamental problems is creating a balance between different services with different QoS, resource requirements, and priorities.  }
 

### 2022-06-25 Journal1/paper-version3-TNSM/pr.tex
add sth

--- 2022-02-16 Journal1/paper3TNSM/pr.tex
@@
 Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. \textcolor{Violet}{The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.}
+and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.
+\textcolor{MidnightBlue}{The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.}
 \begin{table}[H]

### 2022-06-29 Journal1/paper5TNSM/pr.tex
add sth
add table
add revise

@@
 Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
-We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously. 
-Therefore, we want to study the problem of obtaining the optimal number of VNF, RB assignments, and power allocation to maximize the system's throughput and guarantee the QoS of services.
-This problem is mixed-integer non-linear programming.
-Hence, it is difficult to solve and requires some relaxation, convexification, and other methods for obtaining the sub-optimal solution presented in the following sections.}
-
-\subsection{Main Contributions}
-The purpose of this paper is twofold.
+We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}
+
+\textcolor{MidnightBlue}{The purpose of this paper is twofold.
 First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
 Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
-Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
-
-\textcolor{MidnightBlue}{In this paper, we would like to enhance the resource utilization of the overall wireless O-RAN system and optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
+Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.}
+
+\subsection{Main Contributions}
+
+\textcolor{MidnightBlue}{In this paper, we aim to enhance the resource utilization of a downlink O-RAN system and optimize the baseband resource allocation to develop an isolated network slicing outline for different types of services in an O-RAN platform.
 We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.}
@@
 Finally, Section \ref{conc} concludes the paper.
-
+\begin{table}[H]
+ \caption {List of Acronyms} \label{table:1a}
+ \begin{center}
+ \scalebox{0.8}{
+  \begin{tabular}{||c | c ||}
+  \hline
+Abbreviation & Explanation \\ [0.5ex]
+  \hline\hline
+  VNF & Virtual Network Function\\
+  \hline
+  VM & Virtual Machine  \\
+  \hline
+ O-RAN & Open RAN  \\
+  \hline
+  RAN &  Radio Access Network \\
+  \hline
+   QoS &  Quality of service \\
+  \hline
+  PRB &  Physical Resource Block \\
+  \hline
+  eMBB & enhanced Mobile BroadBand \\
+  \hline
+  URLLC  & Ultra-Reliable Low Latency Communication \\
+   \hline
+  mMTC &  massive Machine-To-Machine Communications \\
+  \hline
+  O-RU &  O-RAN Radio Unit \\
+  \hline
+   O-DU &  O-RAN Distributed Unit \\ [.5ex]
+  \hline
+   O-CU &  O-RAN Central Unit \\ [.5ex]
+  \hline
+  UPF &  User Plane Function \\ [.5ex]
+  \hline
+ \end{tabular}}
+ \end{center}
+ \end{table}
 \section{Related Literature}\label{RL}
@@
 Moreover, the author discussed the feasible region to make the initial values possible.
+
 \section{Background}\label{BG}
@@
 The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
+%\begin{table}[H]
+% \caption {List OF Notation} \label{table:1a}
+% \begin{center}
+% \scalebox{0.8}{
+%  \begin{tabular}{||c | c ||}
+%  \hline
+%Notation & Description \\ [0.5ex]
+%  \hline\hline
+%  $S$ & Total number of slices\\
+%  \hline
+%  $S1$ & Number of eMBB slices  \\
+%  \hline
+% $S2$ & Number of URLLC slices  \\
+%  \hline
+%  $S3$ & Number of mMTC slices \\
+%  \hline
+%   $\bar{K}_s$ & pre-allocated PRB to each slice \\
+%  \hline
+%  PRB &  Physical Resource Block \\
+%  \hline
+%  eMBB & enhanced Mobile BroadBand \\
+%  \hline
+%  URLLC  & Ultra-Reliable Low Latency Communication \\
+%   \hline
+%  mMTC &  massive Machine-To-Machine Communications \\
+%  \hline
+%  O-RU &  O-RAN Radio Unit \\
+%  \hline
+%   O-DU &  O-RAN Distributed Unit \\ [.5ex]
+%  \hline
+%   O-CU &  O-RAN Central Unit \\ [.5ex]
+%  \hline
+%  UPF &  User Plane Function \\ [.5ex]
+%  \hline
+% \end{tabular}}
+% \end{center}
+% \end{table}
 \section{System Model and Problem Formulation}\label{systemmodel}

### 2022-06-29 Journal1/paper5TNSM/pr.tex
Add files

@@
 \textcolor{MidnightBlue}{Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
-In view of this, a new RAN paradigm, called open RAN (O-RAN), which is shown in Fig \ref{fig:c11}, is introduced to deal with these issues.}
+In view of this, a new RAN paradigm, called open RAN (O-RAN), which is shown in figure \ref{fig:c11}, is introduced to deal with these issues.}
 %This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
@@
 
-\textcolor{MidnightBlue}{In this paper, we aim to enhance the resource utilization of a downlink O-RAN system and optimize the baseband resource allocation to develop an isolated network slicing outline for different types of services in an O-RAN platform.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.}
-
-In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
+\textcolor{MidnightBlue}{In this paper, we aim to enhance the resource utilization of a downlink O-RAN system and optimize the baseband resource allocation to develop an isolated network slicing outline for the three 5G service classes.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
+Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
+%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
+ The main contributions of this paper are summarized as follows:
 \begin{itemize}
@@
 Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs association, and VNF activation to maximize the weighted throughput of the O-RAN.}
-\item \textcolor{MidnightBlue}{We propose an algorithm for resource management in a two-step, with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
-In the first step, we reformulate and simplify the problem to find an upper and lower bound for the number of activated VNFs and use the Lagrangian function and KKT conditions to find optimal power and PRB allocation.
-For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.}
-\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
-\item \textcolor{MidnightBlue}{We perform numerical experiments to analyze the performance of the proposed algorithm, which proves to have a higher data rate than both the baseline scheme and data-driven method.
-Interestingly, our results show that this algorithm performs close to the optimal solution in low interference.}
+\item \textcolor{MidnightBlue}{We propose a two-step resource management algorithm for solving the optimization problem.
+In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs.
+Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation.
+In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.}
+\item \textcolor{MidnightBlue}{We provide insights into the complexity of our algorithms.
+Moreover, we analyze and guarantee the convergence of the algorithms.
+Additionally, we demonstrate the feasibility region of our system using a fast algorithm.}
+\item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes, i.e., the DR scheme and the baseline scheme, in terms of achievable data rate.
+Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.}
 \end{itemize}
@@
      UPF &  User Plane Function \\ [.5ex]
+  \hline
+  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
   \hline
@@
 \max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}} \ \\
-\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r
+\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r,
  \label{c11} \\
@@
 & \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
-& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18-1} \\
-& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\
+& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r, \label{c18-1} \\
+& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r, \label{c18} \\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
-& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}
+& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i. \label{c21}
 \end{alignat}
@@
 \bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\
- \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
+ \hat{\zeta}_{u(s_j,i)}^{k} =& \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
  \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
@@
 In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as
-$ \forall i,\forall s$
-\begin{equation}
-\begin{split}
+%$ \forall i,\forall s$
+\begin{subequations}
+\begin{alignat}{4}
 &T^{\max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
-&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
-\end{split}
-\end{equation}
+&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }
+\end{alignat}
+\end{subequations}
 Also from equations in \eqref{c19}, \eqref{c16-1} and \eqref{c16-3}, we have
 \begin{equation}
-\alpha_s/\mu_s\leq M_s \leq \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}
+\alpha_s/\mu_s\leq M_s \leq \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}.
 \end{equation}
@@
 \begin{equation}\label{eqDelay}
-\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
+\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s.
 \end{equation}
@@
 The left side of the equation \eqref{eqDelay}, leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}.
-For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ as below,
+For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ given by
 %\begin{equation}\label{RM}
@@
 \begin{alignat}{4}
-\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
-\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\\
-& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}
+\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}, \\
+\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s},\\
+& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}.
 \end{alignat}
@@
 \begin{equation} \label{pr11}
-\begin{split}
-\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
-P_r &\leq  \zeta_{r}.\\
-\end{split}
+P_r\leq \zeta_r= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}. 
 \end{equation}
@@
 \begin{equation}\label{RConstr}
-\begin{split}
-\eta_{u_{(s,i)}}&= \max\{\mathcal{R}_{u_{(s,i)}}^{\min}, \lambda_{u_{(s,i)}}+1/T^s_{\max}, \varpi_{u(s,i)} \}, \\
-\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
-\end{split}
+\mathcal{\bar{R}}_{u_{(s,i)}} \geq\eta_{u_{(s,i)}}= \max\{\mathcal{R}_{u_{(s,i)}}^{\min}, \lambda_{u_{(s,i)}}+1/T^s_{\max}, \varpi_{u(s,i)} \}. 
 \end{equation}
@@
 The Lagrangian function is written as
-\begin{subequations}\label{lagrang}
-\begin{alignat}{4}
+\begin{equation}\label{lagrang}
+\begin{split}
 &\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\delta_s\mathcal{\bar{R}}_{u_{(s,i)}}\\
@@
 &+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R} \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}.
-\end{alignat}
-\end{subequations}
+\end{split}
+\end{equation}
 %{\color{red} Motivate the lemma. separate proof and lemma}
 \begin{lemma}
-The derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{P}$ and $\boldsymbol{E}$ give the Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal value of these two variables \cite{lee2018dynamic,ali2018joint}.
+The derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{P}$ and $\boldsymbol{E}$ give the KKT conditions to obtain the optimal value of these two variables \cite{lee2018dynamic,ali2018joint}.
 \end{lemma}
@@
 \max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R} \delta_s g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
-\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r
+\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r,
  \label{p11} \\
@@
 \end{subequations}
-Where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
+where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
 and $\mathfrak{t}_r = \zeta_r- \sigma_r$  because of the equations \eqref{pr11} and \eqref{pr}.
@@
 \subsubsection{Complexity Order}
-The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
+The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}U_S$.
 Also, assume that the algorithm converges after $T_{conv}$ times.
 As we mentioned before, the complexity order of the first sub-problem is about $O(T_{conv} \times \mathfrak{N} \times K)$
-and the complexity order of the second sub-problem is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
-So the complexity of the main problem \eqref{problem} is $O(T_{conv} \times \mathfrak{N} \times K \times (Slog(S)+R\mathfrak{N}))$.
+and the complexity order of the second sub-problem is about $O(S\log(S)) + O(R\times \mathfrak{N})$.
+So the complexity of the main problem \eqref{problem} is $O(T_{conv} \times \mathfrak{N} \times K \times (S\log(S)+R\mathfrak{N}))$.
 \subsubsection{Convergence Analysis}

### 2022-07-01 Journal1/paper5TNSM/pr.tex
Add files
add revise

@@
 %\vspace*{-1.5em}
-Taking advantage of virtual radio access networks (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems.
-Due to O-RAN, flexibility, openness, and lower operational costs will be possible.
-O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-In this paper, we study the problem of service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing to isolate different types of services.
+The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks.
+Nevertheless, strictly satisfying quality-of-service requirements, while establishing priorities and promoting balance between the significantly heterogeneous services remains as key research problem.
+In this paper, we study the problem of service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing.
 The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
-The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation.
-The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve numerically.
-Nevertheless, we break it down into two different steps where an iterative algorithm finds a near-optimal solution.
-In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is achieved.
-The proposed method is validated via simulations that illustrate a higher data rate and lower end-to-end delay than existing methods.
+The optimization of baseband resources includes O-RAN radio unit (O-RU),and physical resource block (PRB) assignment, and power allocation.
+The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve.
+Nevertheless, we break it down into two different steps and propose an iterative algorithm that finds a near-optimal solution.
+In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is resolved.
+The proposed method is validated via simulations ,which evince the achievement of a higher data rate and lower end-to-end delay than existing methods.
 \end{abstract}
 \begin{IEEEkeywords}
-Open Radio Access Network (O-RAN), Virtual Network Function (VNF), Network Slicing.
+Open Radio Access Network (O-RAN), Virtual Network Function (VNF), Network Slicing, Knapsack Problem, Greedy Algorithm, Karush-Kuhn-Tucker (KKT) Conditions.
 \end{IEEEkeywords}
@@
 \textcolor{MidnightBlue}{Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
-In view of this, a new RAN paradigm, called open RAN (O-RAN), which is shown in figure \ref{fig:c11}, is introduced to deal with these issues.}
+In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Figure \ref{fig:c11}, is introduced to deal with these issues.}
 %This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
@@
 
-\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is decoupled from the software, indicating the concept of network function virtualization (NFV).
+\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, indicating the concept of network function virtualization (NFV).
 Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network, luo2020online}.}
@@
 
-\begin{figure*}
+\begin{figure}
   \centering
   \captionsetup{justification=centering}
-    \includegraphics[scale = 0.45]{finalDraw.pdf}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[scale = 0.45]{finalDraw.pdf}
+    \includegraphics[width=9.5cm,height=6cm]{finalDraw1.pdf}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Network sliced o-ran system}
+  \caption{Network sliced O-RAN system}
   \label{fig:c11}
-\end{figure*}
+\end{figure}
 \subsection{Motivation}
-\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation in a different generation of RAN technology is vital to reduce the cost of the system and improve the QoS of the UEs.
-The allocation of resources in 5G faces many significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc.}
-
-\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering one service's power, data rate, and delay limitations.
-Due to the need to serve services with different QoS simultaneously, this architectural model is inefficient.
-Therefore, we need a new architecture that supports RAN slicing for various services.
-O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
+\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs).
+In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.}
+
+\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service.
+Due to the contemporary need to serve services with different QoS simultaneously, e.g., as in 5G and beyond, this architectural model is inefficient.
+In this regard, the O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
 Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
-One of the fundamental problems is creating a balance between different services with different QoS, resource requirements, and priorities.  }
-
-\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
-Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
-We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}
-
-\textcolor{MidnightBlue}{The purpose of this paper is twofold.
-First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
-Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
-Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.}
+One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.
+}
+%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
+%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
+%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}
+
+\textcolor{MidnightBlue}{The purpose of this paper is to design a system in the O-RAN architecture to support three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
+Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.}
 
@@
      UPF &  User Plane Function \\ [.5ex]
+  \hline
+  UE &  User Equipment \\ [.5ex]
   \hline
@@
 A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set of $r' \in R \not\in r$ that are using the same PRB $k$.
-Two types of interference occur between UEs in each slice; the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
+Two types of interference occur between UEs in each slice; the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in Figure \ref{fig:intf}.
 
@@
 \end{equation}
-
 %\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
@@
 & K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
-&  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3,\label{prb2}
+&  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3.\label{prb2}
 \end{alignat}
@@
 \begin{alignat}{4}
-p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
+p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ \text{Ln2} \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
  &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.
@@
 Then, the O-RU with the highest achievable data rate from the new set of O-RUs ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$ is selected.
-The complexity of sorting S slices based on their priority is $O(Slog(S))$.
+The complexity of sorting S slices based on their priority is $O(S\log(S))$.
 Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ as the whole number of UEs in the system.
-The complexity order of this algorithm is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
+The complexity order of this algorithm is about $O(S\log(S)) + O(R\times \mathfrak{N})$.
 %$O(N\times \mathfrak{N})$

### 2022-07-02 Journal1/paper5TNSM/pr.tex
add revise part of it

@@
 In this paper, we study the problem of service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing.
-The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
-The optimization of baseband resources includes O-RAN radio unit (O-RU),and physical resource block (PRB) assignment, and power allocation.
+The limited fronthaul capacity and end-to-end delay constraints are simultaneously considered.
+The optimization of baseband resources includes O-RAN radio unit (O-RU) and physical resource block (PRB) assignment, and power allocation.
 The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve.
-Nevertheless, we break it down into two different steps and propose an iterative algorithm that finds a near-optimal solution.
+Consequently, we break it down into two different steps and propose an iterative algorithm that finds a near-optimal solution.
 In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is resolved.
-The proposed method is validated via simulations ,which evince the achievement of a higher data rate and lower end-to-end delay than existing methods.
+The proposed method is validated via simulations which evince the achievement of a higher data rate and lower end-to-end delay than existing methods.
 \end{abstract}
@@
 \textcolor{MidnightBlue}{Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
-In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Figure \ref{fig:c11}, is introduced to deal with these issues.}
+In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig.
+\ref{fig:c11}, is introduced to deal with these issues.}
 %This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
@@
 
-\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, indicating the concept of network function virtualization (NFV).
+\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
 Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network, luo2020online}.}
@@
 
-\textcolor{MidnightBlue}{The purpose of this paper is to design a system in the O-RAN architecture to support three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
+\textcolor{MidnightBlue}{The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
 Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.}
@@
 
-\textcolor{MidnightBlue}{In this paper, we aim to enhance the resource utilization of a downlink O-RAN system and optimize the baseband resource allocation to develop an isolated network slicing outline for the three 5G service classes.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
-Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
+\textcolor{MidnightBlue}{This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.}
+%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
 %In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
@@
 \item \textcolor{MidnightBlue}{We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
-Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs association, and VNF activation to maximize the weighted throughput of the O-RAN.}
+Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.}
 \item \textcolor{MidnightBlue}{We propose a two-step resource management algorithm for solving the optimization problem.
@@
 In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.}
-\item \textcolor{MidnightBlue}{We provide insights into the complexity of our algorithms.
-Moreover, we analyze and guarantee the convergence of the algorithms.
-Additionally, we demonstrate the feasibility region of our system using a fast algorithm.}
+\item \textcolor{MidnightBlue}{We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
+Additionally, we analyze the feasibility region of our problem and introduce a fast algorithm to check its feasibility numerically.}
 \item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes, i.e., the DR scheme and the baseline scheme, in terms of achievable data rate.

### 2022-07-03 Journal1/paper5TNSM/pr.tex
add revise

@@
 \usepackage{balance}
+\usepackage{booktabs}
 \allowdisplaybreaks
@@
 \setlength{\belowcaptionskip}{-10pt}
+\def\hlinewd#1{%
+\noalign{\ifnum0=`}\fi\hrule \@height #1 %
+\futurelet\reserved@a\@xhline} 
 %\setlength{\dbltextfloatsep}{-20pt}
@@
 Additionally, we analyze the feasibility region of our problem and introduce a fast algorithm to check its feasibility numerically.}
-\item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes, i.e., the DR scheme and the baseline scheme, in terms of achievable data rate.
+\item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes, in terms of achievable data rate.
 Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.}
@@
  \begin{center}
- \scalebox{0.8}{
-  \begin{tabular}{||c | c ||}
-  \hline
-Abbreviation & Explanation \\ [0.5ex]
-  \hline\hline
-  VNF & Virtual Network Function\\
-  \hline
-  VM & Virtual Machine  \\
-  \hline
- O-RAN & Open RAN  \\
-  \hline
-  RAN &  Radio Access Network \\
-  \hline
-   QoS &  Quality of service \\
-  \hline
-  PRB &  Physical Resource Block \\
-  \hline
-  eMBB & enhanced Mobile BroadBand \\
-  \hline
-  URLLC  & Ultra-Reliable Low Latency Communication \\
-   \hline
-  mMTC &  massive Machine-To-Machine Communications \\
-  \hline
-  O-RU &  O-RAN Radio Unit \\
-  \hline
-   O-DU &  O-RAN Distributed Unit \\ [.5ex]
-  \hline
-   O-CU &  O-RAN Central Unit \\ [.5ex]
-   \hline
-     UPF &  User Plane Function \\ [.5ex]
-  \hline
-  UE &  User Equipment \\ [.5ex]
-  \hline
+ \scalebox{1}{
+  \begin{tabular}{c  c }
+  \toprule
+\textbf{Acronym} & \textbf{Definition} \\ [0.5ex]
+   \toprule
+  VNF & virtual network function\\[.5ex]
+
+  VM & virtual machine  \\[.5ex]
+  RAN &  radio access network \\[.5ex]
+ O-RAN & open RAN  \\[.5ex]
+ vRAN & virtual RAN \\[.5ex]
+ CRAN & cloud RAN \\[.5ex]
+   QoS &  quality of service \\[.5ex]
+  MIMO & multiple input multiple output \\[.5ex]
+  PRB &  physical resource block \\[.5ex]
+
+  eMBB & enhanced mobile broadBand \\[.5ex]
+
+  URLLC  & ultra-reliable low latency communication \\[.5ex]
+
+  mMTC &  massive machine-to-machine communications \\[.5ex]
+
+  O-RU &  O-RAN radio unit \\[.5ex]
+
+   O-DU &  O-RAN distributed unit \\ [.5ex]
+
+   O-CU &  O-RAN central unit \\ [.5ex]
+
+     UPF &  user plane function \\ [.5ex]
+
+  UE &  user equipment \\ [.5ex]
+
   KKT &  Karush-Kuhn-Tucker \\ [.5ex]
-  \hline
+ \toprule
  \end{tabular}}
@@
 \section{Related Literature}\label{RL}
-The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
-In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered.
-The network slicing scheme includes a higher level and the lower level.
-The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), and the allocation of BBU capacity.
-Also, the allocation of power and physical resource blocks (PRB) is performed at the lower level.
-In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it.
-In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).
-
-Multiplexing eMBB and URLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
+The problem of network slicing in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
+In \cite{lee2018dynamic}, dynamic network slicing in heterogeneous C-RAN (H-CRAN) is considered in two levels.
+The higher level manages user acceptance control, radio remote head (RRH) association, and the allocation of BBU capacity.
+Meanwhile, the allocation of power and physical resource blocks (PRB) is performed at the lower level.
+In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning algorithm.
+In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed for the mobile network operator.
+
+Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
 In \cite{setayesh2020joint,yang2020should,saggese2021power}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS.
@@
 In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
-In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN.
-Also, the problem of RRH to BBU and the RRH to UE association is obtained.
-Moreover, the author discussed the feasible region to make the initial values possible.
+In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also, the problem of RRH to BBU and the RRH to UE association is obtained.
 

### 2022-07-07 Journal1/Response3/Response.tex
Add file

@@
 
-The purpose of this paper is twofold.
-First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
-Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
-Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
-
-In this paper, we would like to enhance the resource utilization of the overall wireless O-RAN system and optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
-
-Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
-We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.
-
-In this paper, as depicted in Figure 1, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
+This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
+%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
+%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
+ The main contributions of this paper are summarized as follows:
 \begin{itemize}
-\item The paper presents a network slicing model for three 5G services: eMBB, mMTC, and URLLC. We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
-Based on different types of services with different QoS and service priorities, we formulate a problem for allocating baseband resources to maximize the weighted throughput of O-RAN.
-\item The focus of our paper is on the multi-service resource management of the RAN, slicing in the flexibility, openness, and openness of the O-RAN architecture.
-\item We propose an algorithm for resource management in a two-step, with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
-In the first step, we reformulate and simplify the problem to find an upper and lower bound for the number of activated VNFs and use the Lagrangian function and KKT conditions to find optimal power and PRB allocation.
-For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
-\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
-\item We perform numerical experiments to analyze the performance of the proposed algorithm, which proves to have a higher data rate than both the baseline scheme and data-driven method.
-Interestingly, our results show that this algorithm performs close to the optimal solution in low interference.
+\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
+Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
+\item We propose a two-step resource management algorithm for solving the optimization problem.
+In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs.
+Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation.
+In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
+\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
+Additionally, we analyze the feasibility region of our problem and introduce a fast algorithm to check its feasibility numerically.
+\item We show via numerical results that the proposed algorithm outperforms two baseline schemes, in terms of achievable data rate.
+Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
 \end{itemize}

### 2022-07-07 Journal1/paper5TNSM/pr.tex
Add file

@@
   \captionsetup{justification=centering}
-    %\includegraphics[scale = 0.45]{finalDraw.pdf}
-    \includegraphics[width=9.5cm,height=6cm]{finalDraw1.pdf}
+    \includegraphics[scale = 0.39]{finalDraw1.pdf}
+    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
@@
 Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
-In \cite{setayesh2020joint,yang2020should,saggese2021power}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS.
+In \cite{setayesh2020joint}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered to maximize the sum rate by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed.
+In \cite{yang2020should} a RAN slicing is considered in the coordinated multipoint system for eMBB and URLLC services to guarantee their QoS and reliability of URLLC.
+Moreover, \cite{saggese2021power} investigates the minimization of the system's power in the downlink RAN slicing of eMBB and URLLC services using non-orthogonal multiple access technique.
 In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
- In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
+% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
 The system guarantees latency, service rate, and reliability maintenance.
@@
 In \cite{SystemCostMinimization,guo2016exploiting}, the authors address the issue of beamforming and VMs activation (using virtualization) in a C-RAN system with limited fronthaul capacity.
-This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint.
+Paper \cite{SystemCostMinimization} aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint.
 Also, transmission and processing delays are modeled based on M/M/1 queueing theory to guarantee UE delays.
-In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
-
-In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
-In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also, the problem of RRH to BBU and the RRH to UE association is obtained.
+In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated.
+Also, the association of RRH to the UE is considered and solved using innovative methods.
+
+In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
+Finally, in \cite{amani2019power}, the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved.
 
@@
 A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set of $r' \in R \not\in r$ that are using the same PRB $k$.
-Two types of interference occur between UEs in each slice; the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in Figure \ref{fig:intf}.
+Two types of interference occur between UEs in each slice: i) inter-slice interference between signals transmitted over different slices, and ii) intra-slice interference between signals transmitted over the same slice that is shown in Fig.
+\ref{fig:intf}.
 
@@
 %{\color{red} use paranthesis in the following equation to clear +}
-\begin{subequations}\label{eqI}
-\begin{alignat}{4}
-&I_{r,u(s,i)}^{k} =\\
- &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
-&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
+%\begin{subequations}\label{eqI}
+%\begin{alignat}{4}
+\begin{align}\label{eqI}
+&I_{r,u(s,i)}^{k} =\nonumber\\
+ &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
+&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
 &+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
-\end{alignat}
-\end{subequations}
+\end{align}
+%\end{alignat}
+%\end{subequations}
 %{\color{red} $\gamma_1$ is constant used instead of variable. }
@@
 Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
-Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression shown in Figure \ref{fig:pq}.
+Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression shown in Fig. \ref{fig:pq}.
 In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }$ indicates the quantization Gaussian noise
@@
 The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as
-\begin{equation}\label{eq3}
-\begin{split}
+\begin{subequations}\label{eq3}
+\begin{alignat}{4}
 \mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
-\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
-\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)},
-\end{split}
-\end{equation}
+\mathcal{R}_{r, u(s_1,i)} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
+\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},
+\end{alignat}
+\end{subequations}
 where $B$ is the bandwidth of system.
@@
 So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
-\begin{equation}
-\begin{split}
+\begin{subequations}
+\begin{alignat}{4}
 T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
@@
 T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
-\end{split}
-\end{equation}
+\end{alignat}
+\end{subequations}
 where $M_s^{d}$, $M_s^{c}$ and
@@
 In this phase, we can use our algorithm after estimating the system's traffic.
-As shown in figure 1, we have three different slices for eMBB, URLLC, and mMTC.
+As shown in Fig.
+1, we have three different slices for eMBB, URLLC, and mMTC.
 For each slice, the system must prepare MAC/RLC protocols for O-DU, PDCP/SDAP protocols for O-CU, UPF, SMF, and AMF.
@@
 %\end{equation}
-\begin{subequations}\label{RM}
-\begin{alignat}{4}
+%\begin{subequations}\label{RM}
+\begin{align}\label{RM}
 \mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}, \\
-\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s},\\
+\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\nonumber\\
 & + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}.
-\end{alignat}
-\end{subequations}
+\end{align}
+%\end{subequations}
 In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
@@
 Assume UE $i$ in slice $s$, associated with O-RU $r$, is allocated to PRB $k$  (i.e., $e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition
-\begin{equation}\label{deriveP}
-\begin{split}
-\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
- &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0,\\
-\end{split}
-\end{equation}
+\begin{align}\label{deriveP}
+\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\nonumber\\
+ &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0,
+\end{align}
 where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follows:
@@
 The optimal power is as follow.
-\begin{subequations}
-\begin{alignat}{4}
-p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ \text{Ln2} \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
- &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.
-\end{alignat}
-\end{subequations}
+\begin{align}
+p_{r,u(s,i)}^{k} &= \bigg[\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ \text{Ln2} \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})} \nonumber\\
+ &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}\bigg]^+.
+\end{align}
+
 Also $[a]^+ = \max(0,a)$.
 In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
-\begin{subequations}\label{deriveE}
-\begin{alignat}{4}
-\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
-&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
+\begin{align}\label{deriveE}
+\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\nonumber\\
+&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\nonumber\\
 &+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.
-\end{alignat}
-\end{subequations}
-So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
-\begin{equation}\label{deriveE1}
-\begin{split}
-e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
-& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
-\end{split}
-\end{equation}
+\end{align}
+So, the optimal $\boldsymbol{E}$ is obtained using the KKT conditions, which require solving
+\begin{align}\label{deriveE1}
+e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\nonumber\\
+& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0,
+\end{align}
 where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
-Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
+Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follows
 \begin{equation}
@@
 We consider three network slices for eMBB, URLLC, and mMTC services.
-Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
+Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in Fig. \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
 \begin{figure}
   \centering
-    \includegraphics[scale = 0.3]{cell.pdf}
+    \includegraphics[scale = 0.4]{cell.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
  \scalebox{0.9}{
-  \begin{tabular}{||c | c ||}
-  \hline
-Parameter & Value \\ [0.5ex]
-  \hline\hline
-  Noise power & -174dBm\\
-  \hline
-  Bandwidth & 180 KHz  \\
-  \hline
- Maximum transmit Power of each O-RU & 40dBm \\
-  \hline
-  Maximum delay for eMBB &  4msec \\
-  \hline
-    Maximum delay for URLLC &  1msec \\
-  \hline
-  Maximum delay for mMTC &  5msec \\
-  \hline
-  Maximum fronthaul capacity  & 46 bits/sec/Hz \\
-   \hline
-  Minimum data rate for eMBB &  20 bits/sec/Hz \\
-  \hline
-   Minimum data rate for URLLC and mMTC &  2 bits/sec/Hz \\
-  \hline
-   Maximum received power for mMTC &  20 dBm \\ [.5ex]
-  \hline
-    Maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]
-  \hline
+  \begin{tabular}{c  c }
+  \toprule
+\textbf{Parameter} & \textbf{Value} \\ [0.5ex]
+  \toprule\toprule
+  noise power & -174 dBm\\
+
+  bandwidth & 180 KHz  \\
+
+ maximum transmit power of each O-RU & 40 dBm \\
+
+  maximum delay for eMBB &  4 msec \\
+
+    maximum delay for URLLC &  1 msec \\
+
+  maximum delay for mMTC &  5 msec \\
+
+  maximum fronthaul capacity  & 46 bps \\
+
+  minimum data rate for eMBB &  20 bps \\
+
+   minimum data rate for URLLC and mMTC &  2 bps \\
+
+   maximum received power for mMTC &  20 dBm \\ [.5ex]
+
+    maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]
+ \toprule
  \end{tabular}}
@@
 
-For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18] and named it the dynamic resource allocation scheme (DR scheme). 
+For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic} and named it the dynamic resource allocation scheme (DR scheme).
  We have services with different QoS in this work, similar to tenants with different QoS introduced in \cite{lee2018dynamic}.
@@
   \captionsetup{justification=centering}
-    \includegraphics[width=7cm,height=4cm]{Arate_ue1_1.eps}
+    \includegraphics[scale = 0.5]{fig/Arate_ue1_1n.eps}
     \caption{Aggregate throughput vs. number of UEs in each service}% in the presence of three services}
@@
 \centering
-  \captionsetup{justification=centering}
-       \includegraphics[width=7cm,height=4cm]{vnfNum1.eps}
+  %\captionsetup{justification=centering}
+  \includegraphics[scale = 0.5]{fig/vnfNum1n.eps}
+       %\includegraphics[width=7cm,height=4cm]{vnfNum1.eps}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Number of activated VNF in each Service vs. Mean Arrival Rate(Mbps)}
+  \caption{Number of activated VNF in each service vs. mean arrival rate(Mbps)}
   \label{fig:4}
@@
 %\end{figure}
-Figure \ref{fig:4} depicts the number of activated VNFs for five different mean service times of one URLLC service vs.
+Fig.
+\ref{fig:4} depicts the number of activated VNFs for five different mean service times of one URLLC service vs.
 the mean arrival time for 12 UEs.
@@
 %%%%%%%%%%%%
-In figure \ref{fig:5}, the aggregate throughput is depicted vs.
+In Fig.
+\ref{fig:5}, the aggregate throughput is depicted vs.
 the maximum power of UE for three different instances of eMBB service using proposed method (IABV), DR scheme and the baseline scheme.
@@
   \centering
-  \captionsetup{justification=centering}
-    \includegraphics[width=7cm,height=4cm]{RatePower1.eps}
-    \caption{Aggregate Throughput for eMBB vs. Maximum Transmit power for various number of UEs }
+  %\captionsetup{justification=centering}
+    \includegraphics[scale = 0.5]{fig/RatePower1n.eps}
+    \caption{Aggregate throughput for eMBB vs. maximum transmit power for various number of UEs }
   \label{fig:5}
@@
   \centering
-  \captionsetup{justification=centering}
-      \includegraphics[width=7cm,height=4cm]{delay_new.eps}
-  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}
+  %\captionsetup{justification=centering}
+      \includegraphics[scale = 0.5]{fig/delay_newn.eps}
+  \caption{Mean total delay of a URLLC Service vs. the mean arrival rate of a UE in the service}
   \label{fig:6}
@@
 %%%%%%%%%%%%%%%%%%%%
-Figure \ref{fig:6} illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
+Fig. \ref{fig:6} illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
 It is shown that the delay is an ascending function of the mean arrival rate (when the mean service time is fixed) and the number of UEs in the service.
@@
 %%%%%%%%%%%%%%%%%%%%5
-Figure \ref{fig:7} is the same as figure \ref{fig:6} that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
+Fig.
+\ref{fig:7} is the same as Fig.
+\ref{fig:6} that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
 As you can see, the proposed method (IABV) outperforms the other scenarios.
@@
   \centering
-  \captionsetup{justification=centering}
-    \includegraphics[width=7cm,height=4cm]{delay1_new.eps}
-    \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service}
+  %\captionsetup{justification=centering}
+    \includegraphics[scale = 0.5]{fig/delay1_newn.eps}
+    \caption{Mean total delay of a URLLC service vs. the mean arrival rate of a UE in the service}
   \label{fig:7}
@@
   \centering
-  \captionsetup{justification=centering}
-       \includegraphics[width=7cm,height=4cm]{AmmTCpower.eps}
-  \caption{Aggregate Throughput vs. Number of UEs in each Service for three different mMTC services}
+  %\captionsetup{justification=centering}
+       \includegraphics[scale = 0.5]{fig/AmmTCpowern.eps}
+  \caption{Aggregate throughput vs. number of UEs in each service for three different mMTC services}
   \label{fig:8}
 \end{figure}
-Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances.
+Fig.
+\ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances.
 mMTC service includes a large number of UEs with low data rates and low power.
@@
 Assume we have two types of eMBB service instances.
-In figure \ref{fig:9}, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances.
+In Fig.
+\ref{fig:9}, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances.
 Here we consider 4 UEs in each service.
 We assume that the the fronthaul link and the end-to-end delay have no restrictions.
-The figure \ref{fig:9} presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa.
+The Fig.
+\ref{fig:9} presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa.
 Also, we can realize from this figure that the aggregate throughput has the most significant value at the same priority.
@@
   \centering
-  \captionsetup{justification=centering}
-        \includegraphics[width=7cm,height=4cm]{priorityLast.eps}
-  \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
+  %\captionsetup{justification=centering}
+        \includegraphics[scale = 0.5]{fig/priorityLastn.eps}
+  \caption{Aggregate throughput for two eMBB service instances vs. priority of the first service instance }
   \label{fig:9}
@@
 %\end{figure}
-In figure \ref{fig:11}, the aggregate throughput is shown according to the number of iteration (outer loop) of the
+In Fig. \ref{fig:11}, the aggregate throughput is shown according to the number of iteration (outer loop) of the
 proposed algorithm (IABV) for different numbers of UEs for one service. In this figure, the convergence of the IABV method is illustrated. The minimum data rate for each UE is assumed to be 2 Mbps.
@@
 %\subsection{Summary of Simulation Results}
-In figure \ref{fig:12}, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
+In Fig. \ref{fig:12}, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
 proposed algorithm (IABV) and the optimal method for URLLC service for the low interference.
@@
   \centering
-  \captionsetup{justification=centering}
-     \includegraphics[width=7cm,height=4cm]{iter.eps}
-  \caption{Aggregate Throughput vs. Number of Iterations}
+  %\captionsetup{justification=centering}
+     \includegraphics[scale = 0.5]{fig/itern.eps}
+  \caption{Aggregate throughput vs. number of iterations}
   \label{fig:11}
@@
   \centering
-  \captionsetup{justification=centering}
-   \includegraphics[width=7cm,height=4cm]{optimal1.eps}
-  \caption{Aggregate Throughput vs. Number of UEs in one Service}
+  %\captionsetup{justification=centering}
+   \includegraphics[scale = 0.5]{fig/optimal1n.eps}
+  \caption{Aggregate throughput vs. number of UEs in one service}
   \label{fig:12}
@@
 
-In figure \ref{fig:13}, the aggregate throughput is depicted vs.
+In Fig.
+\ref{fig:13}, the aggregate throughput is depicted vs.
 the maximum interference for two different maximum power thresholds of O-RU.
@@
   \centering
-  \captionsetup{justification=centering}
-   \includegraphics[width=7cm,height=4cm]{interF_new.eps}
-  \caption{\small Aggregate Throughput vs. Maximum Interference }
+  %\captionsetup{justification=centering}
+   \includegraphics[scale = 0.5]{fig/interF_newn.eps}
+  \caption{\small Aggregate throughput vs. maximum interference }
   \label{fig:13}
@@
   \centering
-  \captionsetup{justification=centering}
-    \includegraphics[width=7cm,height=4cm]{FA.eps}
-  \caption{\small Aggregate Throughput vs. the Number of UEs in one Service }
+  %\captionsetup{justification=centering}
+    \includegraphics[scale = 0.5]{fig/FAn.eps}
+  \caption{\small Aggregate throughput vs. the number of UEs in one service }
   \label{fig:14}
@@
 %\end{figure}
-In figure \ref{fig:14}, the aggregate throughput is shown versus
+In Fig. \ref{fig:14}, the aggregate throughput is shown versus
 the different number of UEs for an eMBB service with low interference for the IABV and FA methods in the feasible region.
@@
 \bibliographystyle{IEEEtran}
-\bibliography{ref}
+%\bibliography{ref}
+\bibliography{IEEEabrv,conf_short,ref}
 \end{document}

### 2022-07-08 Journal1/Response3/Response.tex
add revise

@@
 
-Network slicing is the most effective solution for 5G wireless cellular networks to achieve the desired level of QoS (i.e., quality, delay, power, etc.).
-Network slicing can provide resource isolation for various services, increasing the system's efficiency.
-This architecture has several implementations, including core slicing, radio access network (RAN) slicing, and both for different 5G services.
-The network slicing concept has the potential to serve multiple services with varying architectures and quality of service (QoS) requirements.
+%\subsection{State Of The Arts}
+Network slicing is a key technology in 5G wireless systems.
+Specifically, network slicing provides the isolation of network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving multiple and heterogeneous service classes [1]–[3].
+There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
+Depending on their corresponding quality of service (QoS) requirements, each service is assigned to a slice of the network.
+For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming.
+Meanwhile, the URLLC service, leveraged, e.g., by autonomous vehicles, Tactile Internet, and remote surgery services, is concerned with providing ultra-reliable and low-latency connectivity.
+Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads [4]–[6].
+%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}
 
-Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-Depending on QoS, each service requires its slice of the network.
-The eMBB service fulfills the demand for high capacity and throughput.
-Moreover, the URLLC service offers autonomous vehicles, tactile internet, remote surgery services, and other high-quality and low latency services.
-However, mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads
-[1]–[6].
-Nevertheless, the existing radio access network (RAN) architecture lacks adequate flexibility and openness to manage these demands for various services simultaneously.
-Therefore, development in RAN architecture is needed to support these requirements for different services simultaneously.
-Open radio access network (O-RAN) is the new RAN generation introduced to deal with these issues.
+Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
+In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig.
+1, is introduced to deal with these issues.
 %This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
@@
 
-The hardware is decoupled from the software in the O-RAN architecture, and each component is implemented as a virtual network function (VNF) that can be deployed on a virtual machine (VM) or container.
-Virtual network functions (VNF) are system function blocks in network function virtualization (NFV) systems.
-The concept of NFV refers to the separation of network software and hardware elements.
-Therefore network functions can run on commodity hardware.
-The NFV technology offers to execute VNFs as VMs or containers on a cloud environment [7], [8].
-As a result, some O-RAN components defined in section III, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit O-DU, and RAN Intelligent Controller (RIC)-near real-time, are near real-time virtualized and implemented as VNFs.
-VNFs can also be deployed as virtual machines (VMs) or containers.
-
-This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC.
-As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.
-
+A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
+Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container [7],[8].
+As a result, some O-RAN components defined in Section III, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 
-The studies in  [9]–[11] have investigated resource allocation in C-RAN by considering the limitation on power and delay, respectively.
-However, this architecture is inefficient whenever we have different services with different QoS simultaneously.
-Additionally, RAN slicing requires a more flexible and open architecture.
-Therefore, we need a new architecture that supports slicing to implement RAN slicing for various services.
-O-RAN architecture has emerged as
-a new architecture that can serve different services simultaneously using RAN slicing.
-In [2], the RAN slicing is considered for C-RAN architecture for eMBB and URLLC.
-Nevertheless, the authors did not consider latency for URLLC, which is the main property of the URLLC.
-Moreover, the authors did not consider the weakness of C-RAN architecture.
-In [12], the authors examine the total delay of the UE in the O-RAN architecture. However, the paper did not consider the different services and other QoS.
+The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs).
+In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc [2],[9],[10].
 
-Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
-Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
-We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously. 
-Therefore, we want to study the problem of obtaining the optimal number of VNF, RB assignments, and power allocation to maximize the system's throughput and guarantee the QoS of services.
-This problem is mixed-integer non-linear programming.
-Hence, it is difficult to solve and requires some relaxation, convexification, and other methods for obtaining the sub-optimal solution presented in the following sections.
+Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service.
+Due to the contemporary need to serve services with different QoS simultaneously, e.g., as in 5G and beyond, this architectural model is inefficient.
+In this regard, the O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
+Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
+One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities [1],[11]–[13].  
+%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
+%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
+%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}
+
+The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
+Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-We removed these sentences and rewrite the contribution. Below we write the changes.
+We removed these sentences and rewrite the main contribution. Below we write the modified main contribution.
 
-The purpose of this paper is twofold.
-First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC.
-Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing.
-Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
-
-In this paper, we would like to enhance the resource utilization of the overall wireless O-RAN system and optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
-
-Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
-We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.
-
-In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
+This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
+%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
+%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
+ The main contributions of this paper are summarized as follows:
 \begin{itemize}
-\item The paper presents a network slicing model for three 5G services: eMBB, mMTC, and URLLC. We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
-Based on different types of services with different QoS and service priorities, we formulate a problem for allocating baseband resources to maximize the weighted throughput of O-RAN.
-\item The focus of our paper is on the multi-service resource management of the RAN, slicing in the flexibility, openness, and openness of the O-RAN architecture.
-\item We propose an algorithm for resource management in a two-step, with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
-In the first step, we reformulate and simplify the problem to find an upper and lower bound for the number of activated VNFs and use the Lagrangian function and KKT conditions to find optimal power and PRB allocation.
-For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
-\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
-\item We perform numerical experiments to analyze the performance of the proposed algorithm, which proves to have a higher data rate than both the baseline scheme and data-driven method.
-Interestingly, our results show that this algorithm performs close to the optimal solution in low interference.
+\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
+Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
+\item We propose a two-step resource management algorithm for solving the optimization problem.
+In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs.
+Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation.
+In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
+\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
+Additionally, we analyze the feasibility region of our problem and introduce a fast algorithm to check its feasibility numerically.
+\item We show via numerical results that the proposed algorithm outperforms two baseline schemes, in terms of achievable data rate and mean total delay.
+Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
 \end{itemize}
@@
 \noindent \textbf{Response:\\}
-I changed the background from sub-section to the section part.
+Thank you for this comment. We moved the background from sub-section to the section part and modified it as below.
+
 \begin{longtable}{|p{0.975\textwidth}|}

### 2022-07-08 Journal1/paper5TNSM/pr.tex
add revise

@@
 The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks.
-Nevertheless, strictly satisfying quality-of-service requirements, while establishing priorities and promoting balance between the significantly heterogeneous services remains as key research problem.
-In this paper, we study the problem of service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing.
+Nevertheless, strictly satisfying quality-of-service requirements, while establishing priorities and promoting balance between the significantly heterogeneous services, remains as a key research problem.
+In this paper, we study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing.
 The limited fronthaul capacity and end-to-end delay constraints are simultaneously considered.
@@
 \begin{IEEEkeywords}
-Open Radio Access Network (O-RAN), Virtual Network Function (VNF), Network Slicing, Knapsack Problem, Greedy Algorithm, Karush-Kuhn-Tucker (KKT) Conditions.
+open radio access network (O-RAN), virtual network function (VNF), network slicing, knapsack problem, greedy algorithm, Karush-Kuhn-Tucker (KKT) Conditions.
 \end{IEEEkeywords}
@@
 \textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
-Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network, luo2020online}.}
+Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.}
 \textcolor{MidnightBlue}{As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.}
@@
   \captionsetup{justification=centering}
-    \includegraphics[scale = 0.39]{finalDraw1.pdf}
+    \includegraphics[scale = 0.36]{finalDraw1.pdf}
     %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
@@
 \item \textcolor{MidnightBlue}{We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
-Additionally, we analyze the feasibility region of our problem and introduce a fast algorithm to check its feasibility numerically.}
-\item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes, in terms of achievable data rate.
+Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.}
+\item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
 Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.}
@@
 
-The rest of this paper is organized as follows.
+Table \ref{table:11a} lists the acronyms used throughout this paper, which is organized as follows.
 Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
@@
 Finally, Section \ref{conc} concludes the paper.
+
 \begin{table}[H]
- \caption {List of Acronyms} \label{table:1a}
+\vspace*{-0em}
+ \caption {List of Acronyms} \label{table:11a}
+ \vspace*{-1em}
  \begin{center}
  \scalebox{1}{
-  \begin{tabular}{c  c }
+  \begin{tabular}{l  l }
   \toprule
+  \vspace*{-0.2em}
 \textbf{Acronym} & \textbf{Definition} \\ [0.5ex]
@@
   UE &  user equipment \\ [.5ex]
+  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
+  CAPEX & capital expenditures  \\ [.5ex]
+  OPEX & operating expenses  \\ [.5ex]
 
@@
  \end{table}
+ \vspace*{-2em}
 \section{Related Literature}\label{RL}
-The problem of network slicing in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
+The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
 In \cite{lee2018dynamic}, dynamic network slicing in heterogeneous C-RAN (H-CRAN) is considered in two levels.
 The higher level manages user acceptance control, radio remote head (RRH) association, and the allocation of BBU capacity.
-Meanwhile, the allocation of power and physical resource blocks (PRB) is performed at the lower level.
-In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning algorithm.
-In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed for the mobile network operator.
+Meanwhile, the allocation of power and PRB is performed at the lower level.
+In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning.
+In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.
 
 Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
-In \cite{setayesh2020joint}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered to maximize the sum rate by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed.
-In \cite{yang2020should} a RAN slicing is considered in the coordinated multipoint system for eMBB and URLLC services to guarantee their QoS and reliability of URLLC.
-Moreover, \cite{saggese2021power} investigates the minimization of the system's power in the downlink RAN slicing of eMBB and URLLC services using non-orthogonal multiple access technique.
-In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
+\textcolor{MidnightBlue}{In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
+In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services.} Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
+In \cite{alsenwi2021intelligent}, the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
 % In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
@@
 \section{Background}\label{BG}
-\textcolor{MidnightBlue}{The Open Radio Access Network (O-RAN) is an appropriate alternative to the next generation of radio access networks due to its flexible operations, openness, lower operational costs, and intelligence.}
-
-O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks.
-O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
-With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
-The C-RAN architecture divides the radio remote head (RRH) and baseband unit (BBU) into two major parts.
+\textcolor{MidnightBlue}{O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexible operations, openness, lower operational costs, and intelligence.
+O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).} With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
+The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
 Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
 Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-
-O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
+\textcolor{MidnightBlue}{ Most real-time baseband processing is performed in the O-DU layer, while mostly non-real-time baseband processing is executed in the O-CU layer.
+Therefore, the three-layer O-RAN architecture can achieve lower cost and power consumption benefits than the two-layer C-RAN architecture.}
+
+As shown in Fig. \ref{fig:c11}, O-RU is a logical node that contains RF and low PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
 In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
@@
 Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
-The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
+The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
 %\begin{table}[H]
@@
 \section{System Model and Problem Formulation}\label{systemmodel}
-In this section, we describe the downlink system in the O-RAN architecture using RAN slicing as depicted in Figure \ref{fig:c11}.
-Firstly, we present the system model.
-Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the o-ran system.
-Afterward, we discuss the mean delay and the power of VNFs.
-Finally, the main problem is expressed.
+We consider a downlink (DL) , and an O-RAN architecture using RAN slicing as depicted in Fig. \ref{fig:c11}.
+In this section, we present the system model, derive the achievable data rates, power of O-RU, and the fronthaul capacity  of the O-RAN system.
+Moreover, we discuss the mean delay and the power of VNFs, and formulate the main problem under consideration.
 \subsection{System Model}
-Assume, there are three service types including eMBB, URLLC, and mMTC which support different applications.
+Assume, there are three service types: eMBB, URLLC, and mMTC, which support different applications.
 Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
-Therefore, there are $S$ pre-allocated slices serving these $S$ services ($S = S_1 + S_2 + S_3$);
-Hence, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have
-$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
-$\{1,2,...,S_3\}$ set of mMTC service instances.
-Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
-There are different application requests which fall into one of these service categories.
-Each application request requires a specific QoS.
+Therefore, there are $S = S_1 + S_2 + S_3$ pre-allocated slices serving these services.
+Moreover, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have the set
+$\{1,2,...,S_1\}$ of eMBB service instances, the set $\{1,2,...,S_2\}$ of URLLC service instances, and the set
+$\{1,2,...,S_3\}$ of mMTC service instances.
+Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs requiring certain level of QoS. Notice that $j \in \{1,2,3\}$ indicates the service type.
 Based on the application and QoS request, UE may be admitted and allocated to the resources.
@@
 \begin{itemize}
-\item The MAC/RLC functions in the O-DU logical node
-\item The PDCP/SDAP functions in the O-CU-UP logical node
-\item The UPF logical node
+\item MAC/RLC functions in the O-DU logical node
+\item PDCP/SDAP functions in the O-CU-UP logical node
+\item UPF logical node
 \end{itemize}
-Each slice $s \in \{1,2,...,S \}$, consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
-The VNFs of O-DU, O-CU-UP, and UPF are interconnected, defined as the Service Function Chain (SFC) in the O-RAN system.
-Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.
+Each slice $s \in \{1,2,...,S \}$, consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP, and $M_s^{u}$ VNFs for the processing of UPF.
+The VNFs of O-DU, O-CU-UP, and UPF are interconnected, which is defined as the service function chain in the O-RAN system.
+Also, each VNF instance runs on a virtual machine VM that uses resources from the data centers.
 
 %All $K$ PRBs can be assigned to all UEs in each service.
-Assume there are $K$ physical resource blocks (PRBs) in this system.
-Suppose each slice $s$ consists of $\bar{K}_s$ pre-allocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs).
-Therefore, we have $\sum_s \bar{K}_s \leq K$.
-
-In addition, there are $R$ multi-antenna O-RUs that are shared between slices.
-O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data.
-Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs.
+Assume there are $K$ PRBs in this system. Suppose each slice $s$ consists of $\bar{K}_s$ pre-allocated virtual resource blocks that are mapped to PRBs. Therefore, we have $\sum_s \bar{K}_s \leq K$.
+In addition, there are $R$ multi-antenna O-RUs that are shared between the slices.
+Specifically, the O-RU $r \in \mathcal{R}=\{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data.
 Moreover, all O-RUs have access to all PRBs.
@@
 \subsection{The Achievable Rate}
-The SNR of the $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
-\begin{equation}\label{eq1}
-\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
-\end{equation}
-where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to the $i^{th}$ UE served at slice $s$ on PRB $k$.
-${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from
-$r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice.
-In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
-\begin{equation}
-\bold{w}_{r,u(s,i)}^{k} = \hat{\bold{h}}_{r,u(s,i)}^{k}(\hat{\bold{h}}_{r,u(s,i)}^{H \: k} \hat{\bold{h}}_{r,u(s,i)}^{k})^{-1}
-\end{equation}
-
-The channel state information is imperfect. So, the channel gain is known with errors; the imperfection of channel estimation is shown as
-$\hat{\boldsymbol{h}}_{r,u(s,i)} = \boldsymbol{h}_{r,u(s,i)} + \Delta \boldsymbol{h}_{r,u(s,i)}$.
-$\Delta \boldsymbol{h}_{r,u(s,i)}$ indicates the estimating error vector with a Gaussian distribution of
-$\Delta \boldsymbol{h}_{r,u(s,i)}\backsim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$.
-where $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$
-
-Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not.
-%Here, it is assumed that each UE is served by the nearest o-RU
-Also, $BN_0$ denotes the power of Gaussian additive noise.
-
-A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set of $r' \in R \not\in r$ that are using the same PRB $k$.
-Two types of interference occur between UEs in each slice: i) inter-slice interference between signals transmitted over different slices, and ii) intra-slice interference between signals transmitted over the same slice that is shown in Fig.
-\ref{fig:intf}.
-
-Network Slicing techniques significantly reduce inter-service interference.
-Some methods apply the network slicing technique in PRB scheduling to isolate PRBs in slices and remove inter-slice interference.
-One of these methods is to have two-time scale scheduling.
-The PRB scheduling to the slices is performed on the first time scale, and on the second time scale, the PRB scheduling to the UEs of slices is carried out.
-Since there are limited resources, inter-service interference cannot be eliminated entirely.
-The other method is to allocate part of the RB of eMBB services to URLLC, and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.
-In this paper, we assume that the PRB scheduling is performed.
-Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
-\begin{figure}
-  \centering
-  \captionsetup{justification=centering}
-    \includegraphics[scale = 0.35]{Interference.png}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Type of Interference Signal}
-  \label{fig:intf}
-\end{figure}
- $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as
-%{\color{red} use paranthesis in the following equation to clear +}
-%\begin{subequations}\label{eqI}
-%\begin{alignat}{4}
-\begin{align}\label{eqI}
-&I_{r,u(s,i)}^{k} =\nonumber\\
- &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
-&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
-&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
-\end{align}
-%\end{alignat}
-%\end{subequations}
-%{\color{red} $\gamma_1$ is constant used instead of variable. }
-%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
-where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.
-%($\gamma_1$ and $\gamma_2$ are two variales.
-You  define on variable here.)
-Furthermore, there is no inter-slice interference since slices are isolated. Therefore, there exist only intra-slice interference.
-
-Here, there are two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise.
-The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.
-To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
+Let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
 \begin{equation}\label{eq2}
@@
 ($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.
+Furthermore, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether O-RU $r$ serves the $i^{th}$ UE that is allocated to the $s^{th}$ slice or not.
+%Here, it is assumed that each UE is served by the nearest o-RU
+The SINR of the $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
+\begin{equation}\label{eq1}
+\rho_{r,u(s,i)}^{k} =  \frac{p_{r,u(s,i)}^{k}|{\bold{h}_{r,u(s,i)}^{k \: H}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
+\end{equation}
+where $p_{r,u(s,i)}^{k}$ represents the transmission power of the O-RU $r$ serve the $i^{th}$ UE in slice $s$ and PRB $k$, while
+${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ corresponding channel vector.
+Moreover, $B$ is the bandwidth of system, and $BN_0$ denotes the power of the additive white Gaussian.
+In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the associated transmit beamforming vector.
+Herein, we consider a zero forcing beamforming vector , which minimizes the experienced interference, and is given by \cite{huang2013user}
+\begin{equation}
+\bold{w}_{r,u(s,i)}^{k} = \hat{\bold{h}}_{r,u(s,i)}^{k}(\hat{\bold{h}}_{r,u(s,i)}^{k \: H} \hat{\bold{h}}_{r,u(s,i)}^{k})^{-1}.
+\end{equation}
+\noindent where $\bold{h}_{r,u(s,i)}^{k}$ is the channel estimate, which is assumed imperfect. Mathematically,
+$\hat{\boldsymbol{h}}_{r,u(s,i)} = \boldsymbol{h}_{r,u(s,i)} + \Delta \boldsymbol{h}_{r,u(s,i)}$, where
+$\Delta \boldsymbol{h}_{r,u(s,i)}\sim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$ indicates the estimating error vector with a Gaussian distribution and $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$
+
+A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set $\mathcal{R}\backslash r$ that are using the same PRB $k$.
+Two types of interference occur between UEs in each slice: i) inter-slice interference between signals transmitted over different slices, and ii) intra-slice interference between signals transmitted over the same slice.%that is shown in Fig.
+\ref{fig:intf}.
+
+Network slicing techniques significantly reduce inter-service interference.
+One way consists in leveraging a two-time scale PRB scheduling to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale).
+Since there are limited resources, inter-service interference cannot be eliminated entirely.
+Another method consists of allocating part of the PRBs of eMBB services to URLLC, and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.
+In this paper, we assume that the PRB scheduling is performed.
+Also, in Section \ref{prb}, we briefly study the PRB scheduling between slices.
+%\begin{figure}
+%  \centering
+%  \captionsetup{justification=centering}
+%    \includegraphics[scale = 0.35]{Interference.png}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Type of Interference Signal}
+%  \label{fig:intf}
+%\end{figure}
+
+Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization, and can be represented as 
+%{\color{red} use paranthesis in the following equation to clear +}
+%\begin{subequations}\label{eqI}
+%\begin{alignat}{4}
+\begin{align}\label{eqI}
+&I_{r,u(s,i)}^{k} =\nonumber\\
+ &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
+&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
+&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
+\end{align}
+%\end{alignat}
+%\end{subequations}
+%{\color{red} $\gamma_1$ is constant used instead of variable. }
+%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
+where $e^{k}_{u(s,i)}$ is a binary variable that indicates whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU, or not.
+%($\gamma_1$ and $\gamma_2$ are two variales.
+You  define on variable here.)
+Furthermore, there is no inter-slice interference since slices are assumed to be isolated. Therefore, there is only intra-slice interference.
+
+%To obtain SNR as formulated in \eqref{eq1}, 
 \begin{figure}
@@
 \end{subequations}
-where $B$ is the bandwidth of system.
 $\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of RU $r$ to UE $i$ in slice $s_1$.
@@
 The Lagrangian function is written as
-\begin{equation}\label{lagrang}
-\begin{split}
-&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\delta_s\mathcal{\bar{R}}_{u_{(s,i)}}\\
-&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\\
-&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\\
-&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\\
-&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{max}_{s}- p^k_{r,u(s,i)})\\
-&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\\
-&-  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)} -1)\\
+\begin{align}\label{lagrang}
+&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\delta_s\mathcal{\bar{R}}_{u_{(s,i)}}\nonumber\\
+&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\nonumber\\
+&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\nonumber\\
+&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\nonumber\\
+&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{max}_{s}- p^k_{r,u(s,i)})\nonumber\\
+&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\nonumber\\
+&-  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)} -1)\nonumber\\
 &+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R} \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}.
-\end{split}
-\end{equation}
+\end{align}
 %{\color{red} Motivate the lemma. separate proof and lemma}
@@
 Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in Fig. \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
+
 \begin{figure}
   \centering
-    \includegraphics[scale = 0.4]{cell.pdf}
+    \includegraphics[scale = 0.37]{cell.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 \end{figure}
+
 Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent.% \cite{gholipoor2020cloud}.
@@
 The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2,IMT, ETSI1}.%\cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.
+
 \begin{table}[H]
@@
  \scalebox{0.9}{
-  \begin{tabular}{c  c }
+  \begin{tabular}{l  l }
   \toprule
@@
  \end{table}
+
 Finding a feasible initial value is almost tricky.
@@
 
-\vspace*{-1em}
 \subsection{Feasible Region}\label{fr}
@@
 Also the mean arrival rate is set to be $0.2$Mbps and the mean service rate is $0.5$Mbps.
-The other parameters are depicted in table \ref{table:1a}.
+The other parameters are depicted in Table \ref{table:1a}.
 The optimal approach is obtained from the two-step joint exhaustive search and using CVX.

### 2022-07-10 Journal1/Response3/Response.tex
add latex

@@
 \noindent \textbf{Response:\\}
-We have changed the paper's introduction and checked the text entirely according to this comment.
+We revised the whole paper and checked the text entirely according to this comment.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-Thank you for this comment. We changed the paper's figures totally according to this comment.
+Thank you for this comment. We modified all the paper's figures entirely concerning this comment.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
-Additionally, we analyze the feasibility region of our problem and introduce a fast algorithm to check its feasibility numerically.
-\item We show via numerical results that the proposed algorithm outperforms two baseline schemes, in terms of achievable data rate.
+Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.
+\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
 Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
@@
 We would like to thank the reviewer for the careful and thorough reading of our manuscript and the thoughtful comment and constructive suggestions that helped us improve the quality of this manuscript and make it more readable.
-We changed the introduction and add it below
+We modified the introduction completely and add it below
 
+\section{Introduction}
 %\subsection{State Of The Arts}
@@
 A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
-Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container [7],[8].
+Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container [7].
 As a result, some O-RAN components defined in Section III, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.
+
+\subsection{Motivation}
+The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs).
+In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc [2], [8], [9].
+
+Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service.
+Due to the contemporary need to serve services with different QoS simultaneously, e.g., as in 5G and beyond, this architectural model is inefficient.
+In this regard, the O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
+Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
+One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities [1], [10]–[12].  
+%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
+%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
+%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}
+
+The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
+Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
+
+\subsection{Main Contributions}
+
+This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
+%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
+%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
+ The main contributions of this paper are summarized as follows:
+\begin{itemize}
+\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
+Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
+\item We propose a two-step resource management algorithm for solving the optimization problem.
+In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs.
+Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation.
+In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
+\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
+Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.
+\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
+Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
+\end{itemize}
+
+Table I lists the acronyms used throughout this paper, which is organized as follows.
+Relevant literature related to our work is discussed in Section II, while Section III briefly overviews the O-RAN architecture.
+The system model and the problem formulation are described in Section IV, V, respectively.
+The details of our proposed resource management algorithm are introduced in Section VI.
+In Section VII, numerical results are provided to evaluate the performance of the proposed algorithm.
+Finally, Section VIII concludes the paper.
+
+ \vspace*{-2em}
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-I would appreciate your comments to enhance and clarify this section of the paper. I moved the background as a section.
+I would appreciate your comments to enhance and clarify this section of the paper. I moved the background as a section and modified it even as follow.
+
+O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.
+O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
+With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
+The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
+Several distributed RRHs can be connected to a centralized BBU, called BBU-pool [27].
+Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+ Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.
+
+In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN.
+As shown in Fig.
+1, O-RU is a logical node that contains RF and low PHY.
+The former transmits or receives radio signals, while the latter includes digital beamforming.
+Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC.
+It contains a subfunction of the eNodeB and is deployed near the O-RU.
+Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
+In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
+The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP).
+The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).
+O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
+The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud.
+Orchestration and Automation include functions such as RIC Non-Real-Time.
+RIC is responsible for machine learning methods and making the system more intelligent  [10]–[12], [28]–[31].
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-We add the motivation subsection and answer these questions in it. Below we rewrite this section.
+We added the motivation subsection and answer these questions in it.
 
 The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs).
-In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc [2],[9],[10].
+In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc [2], [8], [9].
 
@@
 Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
-One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities [1],[11]–[13].  
+One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities [1], [10]–[12].  
 %\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
@@
 \noindent \textbf{Response:\\}
-We removed these sentences and rewrite the main contribution. Below we write the modified main contribution.
+We removed these sentences and rewrite the main contribution. Below we present the modified main contribution.
 
@@
 \item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
-Additionally, we analyze the feasibility region of our problem and introduce a fast algorithm to check its feasibility numerically.
-\item We show via numerical results that the proposed algorithm outperforms two baseline schemes, in terms of achievable data rate and mean total delay.
+Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.
+\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
 Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
@@
 
+O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.
+O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
+With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
+The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
+Several distributed RRHs can be connected to a centralized BBU, called BBU-pool [27].
+Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+ Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.
+
+In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN.
+As shown in Fig.
+1, O-RU is a logical node that contains RF and low PHY.
+The former transmits or receives radio signals, while the latter includes digital beamforming.
+Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC.
+It contains a subfunction of the eNodeB and is deployed near the O-RU.
+Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
+In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
+The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP).
+The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).
+O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
+The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud.
+Orchestration and Automation include functions such as RIC Non-Real-Time.
+RIC is responsible for machine learning methods and making the system more intelligent  [10]–[12], [28]–[31].
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-We add the following part to the slice management section.
+Thank you for this comment. We modified and clarified this section as below
 
-In the preparation phase, firstly, the evaluation of requirements is considered.
-Therefore, In this phase, we need an algorithm to estimate the number of UEs and UE traffic in the system at different times.
-Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs for each slice, the optimal number of PRBs for each slice, and the analysis of power allocation.
-In this phase, we can use our algorithm after estimating the system's traffic.
- As shown in figure 1, we have three different slices for eMBB, URLLC, and mMTC.
-For each slice, the system must prepare MAC/RLC protocols for O-DU, PDCP/SDAP protocols for O-CU, UPF, SMF, and AMF.
+In this subsection, we will look at the life cycle of network slicing on a practical level. 
+The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages [36];
+\begin{itemize}
+\item Preparation phase: the operator plans to create a network slice instance (NSI) by designing the its template, onboarding users, and preparing the environment.
+Also, the evaluation of requirements is performed in this step.
+\item Commissioning phase: the NSI is created, and the requirements are considered and allocated to the slice.
+\item Operation phase: the NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated.
+As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
+\item Decommissioning phase: an NSI that is decommissioned no longer exists after this phase.
+\end{itemize}
+Since the requirements evaluation is considered in the preparation phase, we need an algorithm to estimate the UE traffic in the system at different times.
+Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs, PRB assignment of UEs for each slice, and the total power requirements.
+In this phase, we use our algorithm to calculate resources after estimating the system's traffic.
+As shown in Fig.
+1, we have three different slices for eMBB, URLLC, and mMTC.
+The system must prepare VNFs for MAC/RLC functions in O-DU, PDCP/SDAP functions in O-CU, UPF, SMF, and AMF functionality layers for each slice.
 Moreover, O-RU, high PHY in O-DU, and O-CU-CP are shared between slices.
-Thus, we do not require estimating and preparing for the share environments and platforms in the network slicing cycles.
+Thus, we do not require evaluating and preparing for the share environments and platforms in the network slicing cycles.
+Moreover, the estimation of PRB and power is needed based on the proposed algorithm.
 After evaluating, assessing, and preparing the resources and environments for each slice, the commissioning phase is started.
-In this phase, the slices are created based on the previous phase.
-If the evaluation changes, the slice's resources can be modified.
-We can use our algorithm to assign resources to the services in the operation phase.
-If we need to remove a slice or any service is not used in a zone, and we need to remove the corresponding slice, the unshared resources are removed in the decommissioning phase.
+In this phase, the slices are created based on the previous phase estimation.
+These created slices are activated in the operation phase, and the actual resources are assigned based on the proposed algorithm.
+It is possible to modify the slice's resources even when the evaluation changes during the operation phase. 
+If we need to remove a slice or any service not used in a zone, the unshared resources are released in the decommissioning phase.
 
@@
 \cellcolor{gray!15}
-\textbf{\noindent Comment6:} ``With respect to the convergence time of the algorithm, the Reviewer had made a suggestion to the authors to include it in the current version of the manuscript, yet the authors do not seem to have done that.
+\textbf{\noindent Comment7:} ``With respect to the convergence time of the algorithm, the Reviewer had made a suggestion to the authors to include it in the current version of the manuscript, yet the authors do not seem to have done that.
 The authors’ response points to Fig.
@@
 
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment8:} `As a final remark, the structure of the paper needs major re-construction.
+Several Sections are very lengthy and could be reduced while creating additional Sections.
+In the current format it is very hard to follow.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+Thank you for this comment to make our paper more readable. We modified the entire paper based on this comment.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment9:} `Moreover, there are some typos in the manuscript. For instance, user equipements: user equipment.  ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We appreciate your comment about troubleshooting our paper and removing mistakes. Using this comment as a guide, we modified the entire paper.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment10:} `Furthermore, some acronyms are not explained in the text e.g., Quality of Service (QoS). ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+Based on this comment, we added a acronym table I to our paper as follow
+
+\begin{table}[H]
+\vspace*{-0em}
+ \caption {List of Acronyms} \label{table:11a}
+ \vspace*{-1em}
+ \begin{center}
+ \scalebox{1}{
+  \begin{tabular}{l  l }
+  \toprule
+  \vspace*{-0.2em}
+\textbf{Acronym} & \textbf{Definition} \\ [0.5ex]
+   \toprule
+  VNF & virtual network function\\[.5ex]
+
+  VM & virtual machine  \\[.5ex]
+  RAN &  radio access network \\[.5ex]
+ O-RAN & open RAN  \\[.5ex]
+ vRAN & virtual RAN \\[.5ex]
+ CRAN & cloud RAN \\[.5ex]
+   QoS &  quality of service \\[.5ex]
+  MIMO & multiple input multiple output \\[.5ex]
+  PRB &  physical resource block \\[.5ex]
+  SINR & signal to interference and noise ratio  \\[.5ex]
+  eMBB & enhanced mobile broadBand \\[.5ex]
+
+  URLLC  & ultra-reliable low latency communication \\[.5ex]
+
+  mMTC &  massive machine-to-machine communications \\[.5ex]
+
+  O-RU &  O-RAN radio unit \\[.5ex]
+
+   O-DU &  O-RAN distributed unit \\ [.5ex]
+
+   O-CU &  O-RAN central unit \\ [.5ex]
+
+     UPF &  user plane function \\ [.5ex]
+
+  UE &  user equipment \\ [.5ex]
+  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
+  CAPEX & capital expenditures  \\ [.5ex]
+  OPEX & operating expenses  \\ [.5ex]
+
+  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
+ \toprule
+ \end{tabular}}
+ \end{center}
+ \end{table}
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment11:} `Finally, the figures in the current version of the manuscript are very small and extremely hard to read. Therefore, re-formatting is necessary. ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We modified all figures to make it more readable.
+
 \end{document}

### 2022-07-10 Journal1/paper5TNSM/pr.tex
add latex

@@
 \subsection{Motivation}
-\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs).
+\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipment (UE).
 In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.}
@@
 Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
-The system model and the problem formulation are described in Section \ref{systemmodel}.
+The system model and the problem formulation are described in Section \ref{systemmodel}, \ref{prS}, respectively.
 The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}.
@@
   PRB &  physical resource block \\[.5ex]
-
+  SINR & signal to interference and noise ratio  \\[.5ex]
   eMBB & enhanced mobile broadBand \\[.5ex]
@@
 \section{Background}\label{BG}
-\textcolor{MidnightBlue}{O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexible operations, openness, lower operational costs, and intelligence.
+\textcolor{MidnightBlue}{O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.
 O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).} With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
@@
 Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-\textcolor{MidnightBlue}{ Most real-time baseband processing is performed in the O-DU layer, while mostly non-real-time baseband processing is executed in the O-CU layer.
-Therefore, the three-layer O-RAN architecture can achieve lower cost and power consumption benefits than the two-layer C-RAN architecture.}
-
-As shown in Fig. \ref{fig:c11}, O-RU is a logical node that contains RF and low PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
-In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
-O-DU and O-CU are connected via an open and well-defined interface $F_1$.
-Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
-The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
+\textcolor{MidnightBlue}{ Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.}
+
+\textcolor{MidnightBlue}{In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN.
+As shown in Fig.
+\ref{fig:c11}, O-RU is a logical node that contains RF and low PHY.
+The former transmits or receives radio signals, while the latter includes digital beamforming.
+Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC.
+It contains a subfunction of the eNodeB and is deployed near the O-RU.
+Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
+In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
+The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP).
+The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).}
+O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
+The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud.
+\textcolor{MidnightBlue}{Orchestration and Automation include functions such as RIC Non-Real-Time.
+RIC is responsible for machine learning methods and making the system more intelligent}
+\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
 %\begin{table}[H]
@@
 % \end{table}
-\section{System Model and Problem Formulation}\label{systemmodel}
-We consider a downlink (DL) , and an O-RAN architecture using RAN slicing as depicted in Fig. \ref{fig:c11}.
-In this section, we present the system model, derive the achievable data rates, power of O-RU, and the fronthaul capacity  of the O-RAN system.
-Moreover, we discuss the mean delay and the power of VNFs, and formulate the main problem under consideration.
+\section{System Model}\label{systemmodel}
+We consider a downlink (DL) system, and an O-RAN architecture using RAN slicing as depicted in Fig. \ref{fig:c11}.
+In this section, we present the system and signal model, derive the achievable data rates, power of O-RU, and the fronthaul capacity  of the O-RAN system.
+Moreover, we discuss the mean delay and the power of VNFs.
 \subsection{System Model}
@@
 $\{1,2,...,S_3\}$ of mMTC service instances.
-Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs requiring certain level of QoS. Notice that $j \in \{1,2,3\}$ indicates the service type.
+Each service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs requiring certain level of QoS. Notice that $j \in \{1,2,3\}$ indicates the service type.
 Based on the application and QoS request, UE may be admitted and allocated to the resources.
@@
 \begin{itemize}
-\item MAC/RLC functions in the O-DU logical node
-\item PDCP/SDAP functions in the O-CU-UP logical node
-\item UPF logical node
+\item MAC/RLC functions in the O-DU 
+\item PDCP/SDAP functions in the O-CU-UP
+\item UPF which is a functional layer
 \end{itemize}
@@
 The VNFs of O-DU, O-CU-UP, and UPF are interconnected, which is defined as the service function chain in the O-RAN system.
-Also, each VNF instance runs on a virtual machine VM that uses resources from the data centers.
+Also, each VNF instance runs on a VM that uses resources from the data centers.
 
@@
 %Coordinated multipoint (CoMP) system is considered here.
-\subsection{The Achievable Rate}
-Let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
+%\subsection{The Achievable Rate}
+\subsection{Signal Model}
+\textcolor{MidnightBlue}{Let $y_{u(s,i)} $ be the received signal of UE $i$ in the $s^{th}$ service such that
 \begin{equation}\label{eq2}
@@
 where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
-Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
-Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression shown in Fig. \ref{fig:pq}.
-In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }$ indicates the quantization Gaussian noise
-($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.
+${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}\sqrt{p^{k}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector, $z_{u(s,i)}\backsim \mathcal{CN}(0,BN_0)$ is the receive additive Gaussian noise and $BN_0$ is the noise power in a given bandwidth $B$.
+Here, ${x_P}$ denotes the precoded message before compression, while ${x_Q}$ illustrates the precoded message after compression.% as shown in Fig. \ref{fig:pq}.
+In addition, $\boldsymbol{q}_{r} \sim \backsim \mathcal{CN}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$ indicates the quantization Gaussian noise which comes from the signal compression in O-DU.
 Furthermore, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether O-RU $r$ serves the $i^{th}$ UE that is allocated to the $s^{th}$ slice or not.
+Furthermore, $p_{r,u(s,i)}^{k}$ represents the transmission power of the O-RU $r$ serve the $i^{th}$ UE in slice $s$ and PRB $k$, while
+${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ corresponding channel vector.
+In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the associated transmit beamforming vector.}
 %Here, it is assumed that each UE is served by the nearest o-RU
-The SINR of the $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
+Therefore, the SINR of the $i^{th}$ UE served at slice $s$ on PRB $k$ is given by
 \begin{equation}\label{eq1}
@@
 \end{equation}
-where $p_{r,u(s,i)}^{k}$ represents the transmission power of the O-RU $r$ serve the $i^{th}$ UE in slice $s$ and PRB $k$, while
-${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ corresponding channel vector.
-Moreover, $B$ is the bandwidth of system, and $BN_0$ denotes the power of the additive white Gaussian.
-In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the associated transmit beamforming vector.
-Herein, we consider a zero forcing beamforming vector , which minimizes the experienced interference, and is given by \cite{huang2013user}
-\begin{equation}
-\bold{w}_{r,u(s,i)}^{k} = \hat{\bold{h}}_{r,u(s,i)}^{k}(\hat{\bold{h}}_{r,u(s,i)}^{k \: H} \hat{\bold{h}}_{r,u(s,i)}^{k})^{-1}.
-\end{equation}
-\noindent where $\bold{h}_{r,u(s,i)}^{k}$ is the channel estimate, which is assumed imperfect. Mathematically,
-$\hat{\boldsymbol{h}}_{r,u(s,i)} = \boldsymbol{h}_{r,u(s,i)} + \Delta \boldsymbol{h}_{r,u(s,i)}$, where
-$\Delta \boldsymbol{h}_{r,u(s,i)}\sim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$ indicates the estimating error vector with a Gaussian distribution and $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$
 
@@
 You  define on variable here.)
-Furthermore, there is no inter-slice interference since slices are assumed to be isolated. Therefore, there is only intra-slice interference.
+Furthermore, there is no inter-slice interference, only intra-slice interference, slices are assumed to be isolated.
 
 %To obtain SNR as formulated in \eqref{eq1}, 
-\begin{figure}
-  \centering
-  \captionsetup{justification=centering}
-    \includegraphics[scale = 0.45]{Qdiag.png}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Precoding and Quantization of Signal}
-  \label{fig:pq}
-\end{figure}
-The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as
-\begin{subequations}\label{eq3}
-\begin{alignat}{4}
-\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
-\mathcal{R}_{r, u(s_1,i)} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
-\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},
-\end{alignat}
-\end{subequations}
-$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of RU $r$ to UE $i$ in slice $s_1$.
-Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula.
-So, for the short packet transmission, the achievable data rate is approximated from following \cite{setayesh2020joint},
-\begin{subequations}\label{eq11}
-\begin{alignat}{4}
-\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
-\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
-\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
-\end{alignat}
-\end{subequations}
+%\begin{figure}
+%  \centering
+%  \captionsetup{justification=centering}
+%    \includegraphics[scale = 0.45]{Qdiag.png}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  \caption{Precoding and Quantization of Signal}
+%  \label{fig:pq}
+%\end{figure}
+
+ Herein, we consider a zero forcing beamforming vector, which minimizes the experienced interference, and is given by \cite{huang2013user}
+\begin{equation}
+\bold{w}_{r,u(s,i)}^{k} = \hat{\bold{h}}_{r,u(s,i)}^{k}(\hat{\bold{h}}_{r,u(s,i)}^{k \: H} \hat{\bold{h}}_{r,u(s,i)}^{k})^{-1}.
+\end{equation}
+\noindent where $\bold{h}_{r,u(s,i)}^{k}$ is the channel estimate, which is assumed imperfect. Mathematically,
+$\hat{\boldsymbol{h}}_{r,u(s,i)} = \boldsymbol{h}_{r,u(s,i)} + \Delta \boldsymbol{h}_{r,u(s,i)}$, where
+$\Delta \boldsymbol{h}_{r,u(s,i)}\sim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$ indicates the estimating error vector with a Gaussian distribution and $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$
+\subsection{Achievable Data Rate}
+The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as 
+\begin{equation}\label{eq3}
+\mathcal{R}_{u(s_1,i)} = \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},
+\end{equation}
+where
+\begin{equation}
+\mathcal{R}_{r, u(s_1,i)} = \sum_{k=1}^{K} \mathcal{{R}}_{r,u(s_1,i)}^{k} e^k_{r,u(s_1,i)},
+\end{equation}
+is the achievable data rate of RU $r$ to UE $i$ in slice $s_1$, which depends on the achievable data rate per PRB, i.e.,
+\begin{equation}
+\mathcal{{R}}_{r,u(s_1,i)}^{k} =  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}),
+\end{equation}
+%\begin{subequations}\label{eq3}
+%\begin{alignat}{4}
+%\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
+%\mathcal{R}_{r, u(s_1,i)} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
+%\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},
+%\end{alignat}
+%\end{subequations}
+Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the application of service type 2 (URLLC) and 3 (mMTC) is not achieved from the Shannon capacity formula.
+Instead, in a short packet transmission, the achievable data rate is approximated as \cite{setayesh2020joint}
+\begin{equation}\label{eq11}
+\mathcal{R}_{u(s_j,i)} = \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
+\end{equation}
+where
+\begin{equation}
+\mathcal{R}_{r,u(s_j,i)} = \mathcal{{R}}_{r,u(s_j,i)}^{k}{e}_{u(s_j,i)}^{k},
+\end{equation}
+is the achievable data rate of RU $r$ to UE $i$ in slice $s_1$, which depends on the achievable data rate per PRB, i.e.,
+\begin{equation}
+\mathcal{{R}}_{r,u(s_j,i)}^{k} = B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},
+\end{equation}
+%\begin{subequations}\label{eq11}
+%\begin{alignat}{4}
+%\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
+%\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
+%\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
+%\end{alignat}
+%\end{subequations}
 where %$j \in \{2,3\}$. Also we have $ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}},$.
@@
 \begin{equation}\label{shortPacket}
- \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}},
+ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}.
 \end{equation}
 %{\color{red} what is transmission probability? }
-where $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
-$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
-$N_{u(s_j,i)}^{k}$ represents the blocklength of it.
-$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.
+Here, $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of the Q function,
+$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$ and PRB $k$, while
+$N_{u(s_j,i)}^{k}$ represents the corresponding transmit blocklength.
+$\mathcal{R}_{r,u(s_j,i)}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.
 
@@
 \begin{equation}\label{pr}
-P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
-\end{equation}
+P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2\alpha^k_{r,u(s,i)} + \sigma_{q}^2,
+\end{equation}
+where $\alpha^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$.
 Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
 %\cite{simeone2016cloud, 1111}
-\begin{equation}\label{cr}
-C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
-\end{equation}
-where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
+\begin{align}\label{cr}
+C_{r} &= \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},\nonumber\\
+C_{r} &= \log_2{\left(\frac{P_r}{ \sigma_{q}^2}\right)}.
+\end{align}
 \subsection{Mean Delay}
 In this part, the end-to-end mean delay for each service is obtained.
-Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,
+The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the total propagation delay ($T^{\text{pro}}$).
 \begin{subequations}
@@
 %T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
-The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the propagation delay ($T^{\text{pro}}$).
-The propagation delay is the time takes for a signal to reach its destination.
-It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the propagation speed of the link).
-The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
-Also, the transmission delay is the amount of time required to push all the packets into the fiber link.
-Moreover, it can formulated as
-$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the data-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean packet size transmitting in each link.
-So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
-
-Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation. However, they can be added to the system model easily.
-
-The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority. 
-However, it provides a new problem formulation and can be added to our system model to extend our paper in the future.
-Thus, this paper assumes that the connection between O-RUs and O-DUs is fixed and transparent, and we do not consider the problem of edge processing.
+Mathematically, the total propagation delay ($T^{\text{pro}}$) is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
+In each link, the propagation delay is the time a signal to reach its destination.
+It is obtained based on the length of the fiber link and the capacity of the link (as $\text{T} = \text{L}/\text{c}$, where L is the length of the link and c is the propagation speed of the medium).
+Meanwhile, the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
+In each link, the transmission delay is the amount of time required to push all the packets into the transmission medium, and can formulated as
+$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the data-rate of the packet and $\mathcal{\alpha}$ is the mean packet size.
+Notice that taking the propagation and transmission delays into account in the formulation is straightforward, but we have avoided it for the sake of succinctness and simplicity.
+
+It is worth highlighting that propagation delay must be specially considered when each O-RU can connect to several number of O-DUs and depending on the route, capacity, and priority. 
+However, this would provide a new problem formulation, which could be added to our system model to extend our paper in the future.
+In the current paper, we assume that the connection between O-RUs and O-DUs is fixed and transparent, and we do not consider the problem of edge processing.
 As a result, the propagation delay is fixed and does not affect the optimization problem.
-The following is a brief calculation of propagation delay.
-
-Since the distance between the O-RU and O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km.
-Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}.
-so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $.
-Since fronhaul, midhaul, and backhaul are fiber optics, c is the speed of light.
-The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has such a small amount.
-In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$.
-So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$.
+
+Next, we present a brief calculation of propagation delay.
+Assume a distance between the O-RU and O-DU around 10 km, the distance between O-DU and O-CU around 80 km, not greater than the distance from O-CU to the network around 200 km \cite{oranD1}.
+Then, assuming the fronthaul, midhaul and backhaul are connected with fiber optics and $c$ is the speed of like, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1$ ms.
+
+The following is a brief calculation of transmission delay to show that it does not affect also the optimization since its contribution to the total delay is negligible.
+In URLLC and mMTC, the mean packet size can be between 20 to 32 bytes; Also, the minimum data rate is assume to be $1 bps/Hz \times BW (180 KHz)$.
+So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{1 \times 180 \times 10^3} < 0.1 ms$.
 As a result, the $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$.
-for eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.
-
-So, we assume that the total delay is approximate to the processing delay ($T^{\text{\text{tot}}} \approx T^{\text{proc}}$).
+For eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.
+
+Therefore, in the following, we assume that the total delay is approximate to the processing delay ($T^{\text{\text{tot}}} \approx T^{\text{proc}}$).
 %Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
@@
 Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
-Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$).
-so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,
-Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
-Since, by using Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still poisson with rate $\alpha_{s}$.
-It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
-Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
-Each packet is processed by one of the VNFs of a slice.
-So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
-\begin{subequations}
-\begin{alignat}{4}
-T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
-T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
-T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
-\end{alignat}
-\end{subequations}
-where $M_s^{d}$, $M_s^{c}$ and
-$M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively.
-Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively.
-Besides, $\alpha_{s}$ is the  arrival rate which is divided
-by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice
-$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.
-
-$T_{u(s,i)}^{RU}$ is the mean transmission delay of the $i^{th}$ UE of the $s^{th}$ service on the wireless link.
- The arrival data rate of wireless link for each UE $i$ of service $s$ is $\lambda_{u(s,i)}$
-As a result, we have $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
-Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
-an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
-
-Therefore, the mean delay of the transmission layer for UE $i$ in slice $s$ is
-\begin{equation}
- T_{u(s,i)}^{RU} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}}.
-\end{equation}
-
-So, the mean processing delay for UE $i$ in slice $s$ is $T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.$
-%\begin{equation}
-%T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
-%\end{equation}
-Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. %{\color{red} what results in this approximation?}
-%Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
-
-The processing delay can be modeled as an M/M/1 queue; since the system's arrival packets are from many independent sources.
+Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$), i.e., $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
+This is because the amount of data transferred along the route (regardless of frame changes) is constant.
+In fact, according to Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still Poisson with rate $\alpha_{s}$.
+It is assumed that there are load balancers in each layer for each service to divide equally the incoming traffic to VNFs. %\cite{frdl,luong2018novel,luong2018novel1}.
+Suppose the baseband processing of each VNF is modeled by an M/M/1 processing queue.
+Since the system's arrival packets are from many independent sources.
 Moreover, the impact of a single packet on the system's performance is minimal.
@@
 In addition, since the services are isolated, the UEs in each service have the same priority, and the processing delays of each service are independent of the other services; Therefore, one service could have a higher priority, affecting the whole optimization, and the M/M/1 queue theory is still validated.
-
+Each packet is processed by one of the VNFs of the corresponding slice.
+Therefor, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, and can be respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
+\begin{align}
+T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
+T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
+T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
+\end{align}
+where $M_s^{d}$, $M_s^{c}$ and
+$M_s^{u}$ represent the number of VNFs in O-DU, O-CU-UP and UPF, respectively.
+Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively. The arrival rate of each VNF in each layer for each slice
+$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.
+
+On the other hand, arrival data rate of wireless link for each UE $i$ of service $s$ is $\lambda_{u(s,i)}$, thus $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
+Moreover, the service time of transmission queue for UE $i$ requesting service $s$ has
+an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
+Therefore, the mean delay of the transmission layer for UE $i$ in slice $s$ is
+\begin{equation}
+ T_{u(s,i)}^{RU} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}}.
+\end{equation}
+we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. %{\color{red} what results in this approximation?}
+%Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
 \subsection{VNF Power}
 %{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.}
-Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.
-
-So the system's total cost of energy of all the slices can be represented as $\textstyle \phi_{\text{\text{tot}}} = \sum_{s=1}^{S}\phi_{s}$.
+Assume the power consumption of each VNF in each logical node (O-DU, O-CU, and UPF) in the slice s, is represented by $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.
+Then, the system's total cost of energy of all the slices can be represented as $\textstyle \phi_{\text{\text{tot}}} = \sum_{s=1}^{S}\phi_{s}$,
 %\begin{equation*}
 %\textstyle \phi_{\text{\text{tot}}} = \sum_{s=1}^{S}\phi_{s},
-%\end{equation*}
-where $\phi_{s}$ is obtained from $\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d.$
+%\end{equation*} and $\phi_{s}$ is obtained from $\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d.$
 %\begin{equation}
@@
 %\end{equation}
-Moreover, $\phi_s^u$, $\phi_s^c$, and $\phi_s^d$ are the fixed cost of energy in UPF, O-CU, and O-DU, respectively.
 
@@
 Data centers are one of the most energy-consuming.
-As a result, restrictions are placed on data centers' energy, including virtual machines (VMs).
+As a result, restrictions are placed on data centers' energy, including VMs.
 So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers.
 So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).
-\subsection{Problem Statement}
-Suppose slice $s$ (which is assigned to service s) has the priority factor $\delta_s$ (based on the priority of its hosting service) where $\sum_{s=1}^S \delta_s =1$.
-The priority factor of each slice is obtained according to the service level agreement (SLA) of that service to have a fairness in the system.
+\section{Problem Statement} \label{prS}
+Suppose the slice $s$ (which is assigned to service s) has a priority factor $\delta_s$ (based on the priority of its hosting service) where $\sum_{s=1}^S \delta_s =1$.
+The priority factor of each slice is obtained according to the service level agreement to promote a fairness in the system.
 %{\color{red} explain why you introduce priority factor.}
-This paper aims to maximize the sum-rate of all UEs with the presence of constraints as follows. %{\color{red} where did you define the objective? what is R bar?}
+This paper aims to maximize the sum-rate of all UEs subject to QoS constraints as follows. %{\color{red} where did you define the objective? what is R bar?}
 \begin{subequations}\label{problem}
@@
  \label{c11} \\
-&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
-&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
+&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i, r, s, k,\label{c12} \\
+&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i, r, s, k,\label{c12-1} \\
 &\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{min} \quad \forall s, \label{c13} \\
@@
 & C_r \leq C^{max}_r \quad \forall r, \label{c15}\\
-&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\
+&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i, s,\label{c16} \\
 & \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
-& \bar{\mathcal{R}}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\
+& \bar{\mathcal{R}}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i, s,\label{c16-2} \\
 & 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\
@@
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
-& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
-& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r, \label{c18-1} \\
-& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r, \label{c18} \\
-& g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
-& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i. \label{c21}
+& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{c17}  \\
+& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s, i , r, \label{c18-1} \\
+& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s, i , r, \label{c18} \\
+& g^r_{u(s,i)} \in \{0,1\} \quad \forall s, i, \label{c20}  \\
+& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s, i. \label{c21}
 \end{alignat}
@@
 \end{subequations}
-\noindent where $\bar{\mathcal{R}}_{u_{(s,i)}}, \:\:\forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
-In addition, $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association.
-Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association.
-Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is the matrix that shows the number of VNFs in each layer of slice.
-\eqref{c11}, \eqref{c12} and \eqref{c12-1} indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.
-Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and URLLC, is more than a threshold, respectively.
-\eqref{c15} and \eqref{c16} expressed the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
-\eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue.
-\eqref{c16-3} restricted the number of VNF in each slice due to the limited resources.
+\noindent \noindent where $\bar{\mathcal{R}}_{u_{(s,i)}}$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
+In addition, $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , i, r, k $, is the four-dimensional (4D) matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , i, r, k$ indicates the binary 4D matrix for the PRB association.
+Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , i, r$ is a binary three dimensional (3D) matrix for the O-RU association.
+Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is a matrix containing the number of VNFs in each layer of slice.
+Notice that
+\eqref{c11}, \eqref{c12} and \eqref{c12-1} limit the power of each O-RU and UE.
+Also, \eqref{c13} constrains the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and URLLC, to be greater than a threshold. Meanwhile,
+\eqref{c15} and \eqref{c16} represent the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
+\eqref{c16-1} and \eqref{c16-2} are related to the stability of the M/M/1 queue,
+\eqref{c16-3} restrictes the number of VNFs in each slice due to the limited resources, while
 %\eqref{c16} is a reliability condition that the delay in each layer should be less than the threshold.
-\eqref{c17} and \eqref{c18-1} guarantee that O-RU and PRB are associated with the UE, respectively.
-Also, \eqref{c18} ensures that each PRB can not be assigned to more than one UE associated with the same O-RU.
-In addition, \eqref{c19} indicates that the fixed cost of energy of VNFs in each slice does not exceed the threshold.
-Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.
-\subsubsection{PRB Scheduling}\label{prb}
- In this section, we provide a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
-We need to have an algorithm to remove the inter-slice interference before solving the problem \ref{problem}.
-Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed.
-So, the assignment of PRB can be completed in two steps to remove inter-slice interference and isolate the slices.
-Firstly we assign PRBs to slices.
-Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm \ref{proAlg}.
+\eqref{c17} and \eqref{c18-1} guarantee that the O-RU and PRB are associated with the UE, respectively.
+Also, \eqref{c18} ensures that each PRB can not be assigned to more than one UE associated with the same O-RU, \eqref{c19} indicates that the fixed cost of energy of VNFs in each slice does not exceed the threshold, while \eqref{c20} and \eqref{c21} constrain $\boldsymbol{E}$ and $\boldsymbol{G}$ to be binary matrices.
+\subsection{PRB Scheduling}\label{prb}
+\textcolor{MidnightBlue}{In this section, we provide a brief study on the problem of PRB scheduling which can be completed in two steps to eliminate the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
+For this, firstly, we should assign the PRBs to the slices.
+Secondly, we assign PRBs of slices to UEs, find the optimal number of VNFs for each slice, allocate power of UEs, and assign O-RU to UEs, which uses the proposed Algorithm \ref{proAlg}.}
 Suppose, $\mathcal{R}_{{s}}^{min}$, and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
-Firstly, we need to find the average PRB number used by UEs in each service.
-Since mMTC and URLLC transmit a short packet, each UE in mMTC and URLLC requires 1 PRB.
+Firstly, we need to find the average PRB number used by the UEs in each service.
+Since mMTC and URLLC require usually short packet transmissions, each UE in mMTC and URLLC requires 1 PRB.
 So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs.
-For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s.
-(eMBB slice)
-So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$.
-$K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
-Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$.
-$K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
-Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).
+For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = B\log_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SINR of UEs in slice s.
+Therefore, the minimum number of PRBs that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$. 
+Moreover, the maximum number of PRB that the slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$.
+Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRBs in slice s.
 Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
-The problem can be written as follow
+The problem can be written as
 \begin{subequations}\label{prob:prb}
@@
 \end{subequations}
-We used logarithms to assign PRBs to all slices to make them equally fair \cite{marabissi2019highly}.
-Equation \eqref{prb0} illustrates that the sum of PRBs of slices can not exceed the maximum number of PRBs.
-Equation \eqref{prb1}, restrict the number of PRBs of eMBB slices and \eqref{prb2}, limit the number of PRBs of URLLC and mMTC slices.
+We used logarithms to assign PRBs to all slices to make them equally fair, since proportional fairness is achieved by maximizing the log utility function \cite{marabissi2019highly}.
+Equation \eqref{prb0} illustrates that the sum of PRBs of slices can not exceed the maximum number of PRBs ($K$).
+Equation \eqref{prb1} restricts the number of PRBs of eMBB slices and \eqref{prb2} limits the number of the PRBs of URLLC and mMTC slices.
 By relaxing $\bar{K_s}$, the objective function and constraints become convex and can be solved using the Lagrangian function.
@@
 In this subsection, we will look at the life cycle of network slicing on a practical level. 
-The goal is to examine slice management, which includes creating, managing, and deleting slices.
-Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning \cite{ETSI2}.
+The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages \cite{ETSI2};
 \begin{itemize}
-\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase.
-In this phase, the operator plans to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment.
+\item Preparation phase: the operator plans to create a network slice instance (NSI) by designing the its template, onboarding users, and preparing the environment.
 Also, the evaluation of requirements is performed in this step.
-\item Commissioning phase: in the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice.
-\item Operation phase: during the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated.
+\item Commissioning phase: the NSI is created, and the requirements are considered and allocated to the slice.
+\item Operation phase: the NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated.
 As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
@@
 \end{itemize}
-\textcolor{MidnightBlue}{In the preparation phase, firstly, the evaluation of requirements is considered.
-Therefore, In this phase, we need an algorithm to estimate the number of UEs and UE traffic in the system at different times.
-Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs for each slice, the optimal number of PRBs for each slice, and the analysis of power allocation.
-In this phase, we can use our algorithm after estimating the system's traffic.
+\textcolor{MidnightBlue}{Since the requirements evaluation is considered in the preparation phase, we need an algorithm to estimate the UE traffic in the system at different times.
+Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs, PRB assignment of UEs for each slice, and the total power requirements.
+In this phase, we use our algorithm to calculate resources after estimating the system's traffic.
 As shown in Fig.
 1, we have three different slices for eMBB, URLLC, and mMTC.
-For each slice, the system must prepare MAC/RLC protocols for O-DU, PDCP/SDAP protocols for O-CU, UPF, SMF, and AMF.
+The system must prepare VNFs for MAC/RLC functions in O-DU, PDCP/SDAP functions in O-CU, UPF, SMF, and AMF functionality layers for each slice.
 Moreover, O-RU, high PHY in O-DU, and O-CU-CP are shared between slices.
-Thus, we do not require estimating and preparing for the share environments and platforms in the network slicing cycles.
+Thus, we do not require evaluating and preparing for the share environments and platforms in the network slicing cycles.
+Moreover, the estimation of PRB and power is needed based on the proposed algorithm.
 After evaluating, assessing, and preparing the resources and environments for each slice, the commissioning phase is started.
-In this phase, the slices are created based on the previous phase.
-If the evaluation changes, the slice's resources can be modified.
-We can use our algorithm to assign resources to the services in the operation phase.
-If we need to remove a slice or any service is not used in a zone, and we need to remove the corresponding slice, the unshared resources are removed in the decommissioning phase.}
+In this phase, the slices are created based on the previous phase estimation.
+These created slices are activated in the operation phase, and the actual resources are assigned based on the proposed algorithm.
+It is possible to modify the slice's resources even when the evaluation changes during the operation phase. 
+If we need to remove a slice or any service not used in a zone, the unshared resources are released in the decommissioning phase.}
 %\vspace*{-1em}
@@
 
-Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$.
+Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{P_{s}^{max}|{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$.
 we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
@@
 \begin{alignat}{4}
-\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
-\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\
- \hat{\zeta}_{u(s_j,i)}^{k} =& \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
+\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
+\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r},\\
+ \hat{\zeta}_{u(s_j,i)}^{k} =& \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}),\\
  \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
@@
 \begin{alignat}{4}
-&T^{\max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
-&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }
+&T^{\max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}},  \\
+&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }.
 \end{alignat}
@@
 \begin{equation}\label{eqDelay}
-\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s.
+\frac{\alpha_s}{\mu_s} \leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s.
 \end{equation}
@@
 \mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}, \\
-\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\nonumber\\
-& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}.
+\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}+ \frac{3}{T^{max}_s\mu_s-\alpha_s \frac{T^{max}_s}{\mathfrak{M}_s}-3}.
 \end{align}
@@
 \begin{equation}\label{RConstr}
-\mathcal{\bar{R}}_{u_{(s,i)}} \geq\eta_{u_{(s,i)}}= \max\{\mathcal{R}_{u_{(s,i)}}^{\min}, \lambda_{u_{(s,i)}}+1/T^s_{\max}, \varpi_{u(s,i)} \}. 
+\mathcal{\bar{R}}_{u_{(s,i)}} \geq\eta_{u_{(s,i)}}= \max\{\mathcal{R}_{u_{(s,i)}}^{\min}, \lambda_{u_{(s,i)}}+\frac{1}{T^s_{\max}}, \varpi_{u(s,i)} \}. 
 \end{equation}
@@
 &\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\delta_s\mathcal{\bar{R}}_{u_{(s,i)}}\nonumber\\
-&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\nonumber\\
-&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\nonumber\\
+&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\nonumber\\
 &+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\nonumber\\
@@
  \label{p11} \\
-& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{p12}\\
- & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}
+& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{p12}\\
+ & g^r_{u(s,i)} \in \{0,1\} \quad \forall s, i, \label{p13}
 \end{alignat}
@@
 We solve this problem using heuristic method(GAA method \ref{alg1}), which is a greedy algorithm \cite{akccay2007greedy,lee2018dynamic}.
-Firstly, we set all the variables to zero ($g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$).
+Firstly, we set all the variables to zero ($g^r_{u(s,i)} = 0, \quad \forall s, i, r$).
 Then we define the parameter ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$.
-This parameter is used as a set of O-RUs that can be assigned to the UE $i$ in slice $s$, which initially includes all the O-RUs (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}, \forall s, \forall i$ ).
+This parameter is used as a set of O-RUs that can be assigned to the UE $i$ in slice $s$, which initially includes all the O-RUs (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}, \forall s, i$ ).
 Also we introduce another parameter $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
@@
 \bibliographystyle{IEEEtran}
-%\bibliography{ref}
-\bibliography{IEEEabrv,conf_short,ref}
+\bibliography{ref}
+%\bibliography{IEEEabrv,conf_short,ref}
 \end{document}

### 2022-07-11 Journal1/Response3/Response.tex
add revised

@@
 We would like to thank the editor and reviewers for their constructive comments on our manuscript.
-It has been beneficial in revising this paper, and we have improved both the technical content and presentation quality through their assistance.
+They have been beneficial in revising this paper, and we have improved both the technical content and presentation quality through their assistance.
 We greatly appreciate their generous help.
@@
 \noindent \textbf{Response:\\}
-We would like to thank the Editor for his comments and concluding the revisions on our manuscript and for giving us this opportunity to improve our paper.
-We have used the comments to improve our paper and eliminate problems.
+We would like to thank the Editor for his comments and for giving us this opportunity to improve our paper. We have used the comments to improve our paper and eliminate problems.
 
@@
 We revised the whole paper and checked the text entirely according to this comment.
+For instance, the introduction has been rewritten totally.
+We also revised the system model, proposed algorithms too, and shortened long paragraphs based on these comments.
+Moreover, we shortened the numerical results and feasible region section, and modified the conslusion section.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-Thank you for this comment. We modified all the paper's figures entirely concerning this comment.
+Thank you for this comment. We think that these changes improve the readability of the manuscripts.
+ We modified all the paper's figures entirely concerning this comment and located them in sub-figures to make them more determined.
+Moreover, we modified whole the figures and made the texts larger and more readable.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-We thank the reviewer for adding clarity to our paper and reducing ambiguity in this condition.
+We thank the reviewer for asking us to add clarity to our paper and reducing ambiguity in this condition.
 We changed the contribution in a better way based on this comment.
-We have removed some sentences and rewritten the contribution in order to our paper's section.
-Below we write the whole contribution section.
+We have removed some sentences and rewritten the contributions in the same order of our paper's section.
+Below we report the whole contribution section.
 
@@
 
+\clearpage
+\noindent
+\begin{longtable}{|p{.975\textwidth}|}
+\hline \hline %\hline \hline \hline
+\Centering
+\cellcolor{gray!60}
+\textbf{Reviewer 3} \\
+\hline \hline %\hline \hline \hline
+\RaggedRight
+\cellcolor{violet!15}
+\textbf{\noindent Comments to the Author} ``
+The reviewer has addressed most of the comments satisfactorily. However, the paper still contains some minor issues as follows ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We are pleased to thank the reviewer for his/her detailed and thorough reading of this manuscript. We hope that the responses provided here will assist the reviewer in relieving his or her concerns.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment1:} ``Abbreviations such as QoS, CAPEX and OPEX are not expanded at their first use. ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+Based on this comment, we added a Table I reporting the list of acronyms to the paper that is shown as below
+
+\begin{table}[H]
+\vspace*{-0em}
+ \caption {List of Acronyms} \label{table:11a}
+ \vspace*{-1em}
+ \begin{center}
+ \scalebox{1}{
+  \begin{tabular}{l  l }
+  \toprule
+  \vspace*{-0.2em}
+\textbf{Acronym} & \textbf{Definition} \\ [0.5ex]
+   \toprule
+  VNF & virtual network function\\[.5ex]
+
+  VM & virtual machine  \\[.5ex]
+  RAN &  radio access network \\[.5ex]
+ O-RAN & open RAN  \\[.5ex]
+ vRAN & virtual RAN \\[.5ex]
+ CRAN & cloud RAN \\[.5ex]
+   QoS &  quality of service \\[.5ex]
+  MIMO & multiple input multiple output \\[.5ex]
+  PRB &  physical resource block \\[.5ex]
+  SINR & signal to interference and noise ratio  \\[.5ex]
+  eMBB & enhanced mobile broadBand \\[.5ex]
+
+  URLLC  & ultra-reliable low latency communication \\[.5ex]
+
+  mMTC &  massive machine-to-machine communications \\[.5ex]
+
+  O-RU &  O-RAN radio unit \\[.5ex]
+
+   O-DU &  O-RAN distributed unit \\ [.5ex]
+
+   O-CU &  O-RAN central unit \\ [.5ex]
+
+     UPF &  user plane function \\ [.5ex]
+
+  UE &  user equipment \\ [.5ex]
+  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
+  CAPEX & capital expenditures  \\ [.5ex]
+  OPEX & operating expenses  \\ [.5ex]
+
+  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
+ \toprule
+ \end{tabular}}
+ \end{center}
+ \end{table}
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment2:} ``Eq.
+(3) includes inter-slice interference but a sentence following the equation mentions that there is no inter-slice interference because slices are isolated, which is confusing''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\} 
+We thank the reviewer for reporting this ambiguity.
+We revised this section, rewrote the equation (3), by removing the inter-slice interference to clarify this equation.
+Moreover, we removed two figures of Fig.
+2 and Fig.
+3 since they don't add much to what is already written in words, and even Fig.
+2 makes the paper vaguer, and we also aim for a more concise manuscript.
+Below we report the revised sentences.
+
+Network slicing techniques significantly reduce inter-service (inter-slice) interference.
+One way consists in leveraging a two-time scale PRB scheduling to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale).
+Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC [2], [5], [32].
+In this paper, we assume that the PRB scheduling is performed.
+Also, in Section V-A, we briefly study the PRB scheduling between slices.
+Since there are limited resources, inter-service interference cannot be eliminated entirely.
+Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.
+Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as 
+%{\color{red} use paranthesis in the following equation to clear +}
+%\begin{subequations}\label{eqI}
+%\begin{alignat}{4}
+%\begin{align}\label{eqI}
+%&I_{r,u(s,i)}^{k} =\nonumber\\
+% &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
+%&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
+%&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
+%\end{align}
+%\end{alignat}
+%\end{subequations}
+%{\color{red} $\gamma_1$ is constant used instead of variable. }
+\begin{align}\label{eqI}
+&I_{r,u(s,i)}^{k} =+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}}\nonumber\\
+ &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
+\end{align}
+%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
+where $e^{k}_{u(s,i)}$ is a binary variable that indicates whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU, or not.
+%($\gamma_1$ and $\gamma_2$ are two variales.
+You  define on variable here.)
+Furthermore, there is no inter-slice interference, only intra-slice interference, since slices are assumed to be isolated. 
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment3:} ``The captions of Figs. 9, 12 and 14 are incomplete.''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}  
+Thank you for this comment. We checked and corrected all the figure's captions.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment4:} ``It is recommended to discuss each result figure in one paragraph. Currently, the discussions on Figs. 5-11 are packed into one paragraph, which is difficult to read.''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}  
+We would like to thank the reviewer for reducing the ambiguity of our paper with this comment. Each figure was discussed as an individual paragraph in response to this comment.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment5:} ``Another round of proofread is required, as there are some mathematical variables which are not italicized and some sentences are incomplete.''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}  
+We modified the whole paper based on this comment, tried correcting all mathematical variables, and revised all sentences again.
+We checked all the system model and proposed algorithms and corrected the italicized text and vice versa.
+For instance, we corrected the $\log$, $\max$, and $\min$ and other texts that are written in italics.
+Moreover, we italicized variables that were written in non-italicized.
 \end{document}

### 2022-07-11 Journal1/paper5TNSM - Copy/pr.tex
add revised

--- 2022-07-10 Journal1/paper5TNSM/pr.tex
@@
 
-Network slicing techniques significantly reduce inter-service interference.
+\textcolor{MidnightBlue}{Network slicing techniques significantly reduce inter-service (inter-slice) interference.
 One way consists in leveraging a two-time scale PRB scheduling to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale).
-Since there are limited resources, inter-service interference cannot be eliminated entirely.
-Another method consists of allocating part of the PRBs of eMBB services to URLLC, and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.
+Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.
 In this paper, we assume that the PRB scheduling is performed.
 Also, in Section \ref{prb}, we briefly study the PRB scheduling between slices.
+Since there are limited resources, inter-service interference cannot be eliminated entirely.
+Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.}
 %\begin{figure}
@@
 
-Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization, and can be represented as 
+\textcolor{MidnightBlue}{Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as }
 %{\color{red} use paranthesis in the following equation to clear +}
@@
 %\begin{alignat}{4}
-\begin{align}\label{eqI}
-&I_{r,u(s,i)}^{k} =\nonumber\\
- &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
-&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
-&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
-\end{align}
+%\begin{align}\label{eqI}
+%&I_{r,u(s,i)}^{k} =\nonumber\\
+% &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
+%&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
+%&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
+%\end{align}
 %\end{alignat}
@@
 %{\color{red} $\gamma_1$ is constant used instead of variable. }
+\begin{align}\label{eqI}
+&I_{r,u(s,i)}^{k} =+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}}\nonumber\\
+ &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
+\end{align}
 %where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
@@
 You  define on variable here.)
-Furthermore, there is no inter-slice interference, only intra-slice interference, slices are assumed to be isolated.
+Furthermore, there is no inter-slice interference, only intra-slice interference, since slices are assumed to be isolated.
 
@@
 
-If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$.
+If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{\text{max}}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$.
 Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
@@
 T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
-T^{\text{\text{proc}}} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
-T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
-T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}.
+T^{\text{\text{proc}}} &=  T^{\text{RU}} + T^{\text{DU}} + T^{\text{CU}} + T^{\text{UPF}},\\
+T^{\text{tr}} &= T^{\text{fr},t} + T^{\text{mid},t} + T^{\text{b},t},  \\
+T^{\text{pro}} &= T^{\text{fr},p} + T^{\text{mid},p} + T^{b,p}.
 \end{alignat}
@@
 \begin{align}
-T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
-T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
-T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
+T_{s}^{\text{DU}} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
+T_{s}^{\text{CU}} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
+T_{s}^{\text{UPF}} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
 \end{align}
@@
 \begin{equation}
- T_{u(s,i)}^{RU} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}}.
+ T_{u(s,i)}^{\text{RU}} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}}.
 \end{equation}
@@
 So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers.
-So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).
+So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{\text{max}}$).
 \section{Problem Statement} \label{prS}
@@
 \max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}} \ \\
-\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r,
+\text{subject to} \quad  &  P_r \leq P^{\text{max}}_{r} \quad \forall r,
  \label{c11} \\
 &p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i, r, s, k,\label{c12} \\
-&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i, r, s, k,\label{c12-1} \\
-&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{min} \quad \forall s, \label{c13} \\
+&p_{r,u(s,i)}^{k}  \leq P_{s}^{\text{max}}  \quad \forall i, r, s, k,\label{c12-1} \\
+&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{\min} \quad \forall s, \label{c13} \\
 %&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
-& C_r \leq C^{max}_r \quad \forall r, \label{c15}\\
-&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i, s,\label{c16} \\
+& C_r \leq C^{\text{max}}_r \quad \forall r, \label{c15}\\
+&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{\text{max}}_{s} \quad \forall i, s,\label{c16} \\
 & \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
 & \bar{\mathcal{R}}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i, s,\label{c16-2} \\
-& 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\
-& \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\
+& 0 \leq M_s \leq M^{\text{max}}_s  \quad \forall s,\label{c16-3}\\
+& \phi^{\text{\text{tot}}}  \leq \phi^{\text{max}}, \label{c19} \\
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
@@
 Secondly, we assign PRBs of slices to UEs, find the optimal number of VNFs for each slice, allocate power of UEs, and assign O-RU to UEs, which uses the proposed Algorithm \ref{proAlg}.}
-Suppose, $\mathcal{R}_{{s}}^{min}$, and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
+Suppose, $\mathcal{R}_{{s}}^{\min}$, and $\mathcal{R}_{{s}}^{\text{max}}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
 Firstly, we need to find the average PRB number used by the UEs in each service.
@@
 For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = B\log_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SINR of UEs in slice s.
-Therefore, the minimum number of PRBs that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$. 
-Moreover, the maximum number of PRB that the slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$.
-Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRBs in slice s.
+Therefore, the minimum number of PRBs that slice s with $U_s$ UEs requires is $K_s^{\min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\text{max}}}}\rceil$. 
+Moreover, the maximum number of PRB that the slice s with $U_s$ UEs requires is $K_s^{\text{max}} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\min}}}\rceil$.
+Also, $K_s = (K_s^{\min}+K_s^{\text{max}})/2$ is the average number of required PRBs in slice s.
 Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
@@
  \label{prb0} \\
-& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
+& K_s^{\min} \leq \bar{K_s}  \leq K_s^{\text{max}}  \quad \forall s \in S_1,\label{prb1} \\
 &  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3.\label{prb2}
@@
 Here, we first simplify and relax the parameters to convexify the problem.
-As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
+As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{\text{max}}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
 for $\rho_{u(s,i)}^{k}$.
@@
 
-Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{P_{s}^{max}|{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$.
+Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{P_{s}^{\text{max}}|{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$.
 we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
@@
 As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
-Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have
-$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
-$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$
+Using the above assumption, we have $T^{\text{DU}}_{s} = T^{\text{CU}}_{s} = T^{\text{UPF}}_{s}$ and we have
+$T^{\text{proc}}_{s} =  T^{\text{RU}}_{s} + T^{\text{DU}}_{s} + T^{\text{CU}}_{s} + T^{\text{UPF}}_{s}$. So,
+$T^{\text{proc}}_{s}=  T^{\text{RU}}_{s} + 3\times T^{\text{DU}}_{s}.$
 %\begin{equation}
@@
 $M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s$.
-where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
+where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{\text{max}}_s R_{u(s,i)}-T^{\text{max}}_s\lambda_{u(s,i)} -1)}{(T^{\text{max}}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
 \end{lemma}
@@
 \end{equation}
-We denote $ \mathfrak{M}_s= \min\{M^{max}, \phi_{max}/{3\phi_s}\}$.
+We denote $ \mathfrak{M}_s= \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}$.
 Thus, if we restrict constraint \eqref{c16} to equality, constraint \eqref{c16} is still valid.
@@
 \begin{equation}\label{eqDelay}
-\frac{\alpha_s}{\mu_s} \leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s.
-\end{equation}
-In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that
+\frac{\alpha_s}{\mu_s} \leq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s.
+\end{equation}
+In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that
 the numerator and the denominator will both have the same sign.
 In the numerator, according to the \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
-If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$, the numerator will be positive.
-$(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$ since the order of $T^{max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{max}_s$.
-Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{max}_s$.
+If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{\max}_s \geq 1$, the numerator will be positive.
+$(R_{u(s,i)}-\lambda_{u(s,i)})T^{\max}_s \geq 1$ since the order of $T^{\max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{\max}_s$.
+Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{\max}_s$.
 So the numerator will be positive.
-In the denominator, we can say that $(T^{max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,
+In the denominator, we can say that $(T^{\max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,
 $\mu_s \geq 0$ and
-$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{max}_s$ as mentioned above.
+$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{\max}_s$ as mentioned above.
 %Therefore, we need to have the constraint below.
@@
 \mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}, \\
-\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}+ \frac{3}{T^{max}_s\mu_s-\alpha_s \frac{T^{max}_s}{\mathfrak{M}_s}-3}.
+\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{\max}_s}+ \frac{3}{T^{\max}_s\mu_s-\alpha_s \frac{T^{\max}_s}{\mathfrak{M}_s}-3}.
 \end{align}
 %\end{subequations}
-In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
+In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
 So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
@@
 \eqref{c15} is changed to
- $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
+ $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{\max}}$.
 The combination of equations \eqref{c11} and \eqref{c15} leads to the following equation
 \begin{equation} \label{pr11}
-P_r\leq \zeta_r= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}. 
+P_r\leq \zeta_r= \min\{P_{\max}, \sigma_{q_r}^2\times 2^{C^r_{\max}} \}. 
 \end{equation}
@@
 &+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\nonumber\\
-&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{max}_{s}- p^k_{r,u(s,i)})\nonumber\\
+&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{\max}_{s}- p^k_{r,u(s,i)})\nonumber\\
 &+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\nonumber\\
@@
   \centering
-    \includegraphics[scale = 0.37]{cell.pdf}
+    \includegraphics[scale = 0.35]{cell.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 Moreover, the number of activated VNFs decreases when the mean service rate increases.
+
 %%%%%%%%%%%%%%
@@
 Moreover, the proposed method (IABV), gives higher aggregate rates in compared to the DR scheme and the baseline scheme.
+
 \begin{figure}%[!tbp]
@@
 does not reach the maximum threshold of the delay.
+
 %Moreover, we can see that the mean delay of a URLLC service increases almost linearly with the mean arrival rate of the packet transmission.
@@
 As you can see, the proposed method (IABV) outperforms the other scenarios.
+
 %%%%%%%%%%%%%
@@
 Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
+
 %%%%%%%%%%%%
@@
 %\end{figure}
+
 In Fig. \ref{fig:14}, the aggregate throughput is shown versus

### 2022-07-11 Journal1/paper5TNSM/pr.tex
add revised

@@
   \toprule
-  \vspace*{-0.2em}
-\textbf{Acronym} & \textbf{Definition} \\ [0.5ex]
+  \vspace*{-0.3em}
+\textbf{Acronym} & \textbf{Definition} \\ [0.3ex]
    \toprule
-  VNF & virtual network function\\[.5ex]
-
-  VM & virtual machine  \\[.5ex]
-  RAN &  radio access network \\[.5ex]
- O-RAN & open RAN  \\[.5ex]
- vRAN & virtual RAN \\[.5ex]
- CRAN & cloud RAN \\[.5ex]
-   QoS &  quality of service \\[.5ex]
-  MIMO & multiple input multiple output \\[.5ex]
-  PRB &  physical resource block \\[.5ex]
-  SINR & signal to interference and noise ratio  \\[.5ex]
-  eMBB & enhanced mobile broadBand \\[.5ex]
-
-  URLLC  & ultra-reliable low latency communication \\[.5ex]
-
-  mMTC &  massive machine-to-machine communications \\[.5ex]
-
-  O-RU &  O-RAN radio unit \\[.5ex]
-
-   O-DU &  O-RAN distributed unit \\ [.5ex]
-
-   O-CU &  O-RAN central unit \\ [.5ex]
-
-     UPF &  user plane function \\ [.5ex]
-
-  UE &  user equipment \\ [.5ex]
-  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
-  CAPEX & capital expenditures  \\ [.5ex]
-  OPEX & operating expenses  \\ [.5ex]
+  VNF & virtual network function\\[.3ex]
+
+  VM & virtual machine  \\[.3ex]
+  RAN &  radio access network \\[.3ex]
+ O-RAN & open RAN  \\[.3ex]
+ vRAN & virtual RAN \\[.3ex]
+ CRAN & cloud RAN \\[.3ex]
+   QoS &  quality of service \\[.3ex]
+  MIMO & multiple input multiple output \\[.3ex]
+  PRB &  physical resource block \\[.3ex]
+  SINR & signal to interference and noise ratio  \\[.3ex]
+  eMBB & enhanced mobile broadBand \\[.3ex]
+
+  URLLC  & ultra-reliable low latency communication \\[.3ex]
+
+  mMTC &  massive machine-to-machine communications \\[.3ex]
+
+  O-RU &  O-RAN radio unit \\[.3ex]
+
+   O-DU &  O-RAN distributed unit \\ [.3ex]
+
+   O-CU &  O-RAN central unit \\ [.3ex]
+
+     UPF &  user plane function \\ [.3ex]
+
+  UE &  user equipment \\ [.43ex]
+  SINR & signal-to-noise-plus-interference ratio \\ [.3ex]
+  CAPEX & capital expenditures  \\ [.3ex]
+  OPEX & operating expenses  \\ [.3ex]
 
@@
  \end{table}
- \vspace*{-2em}
+ \vspace*{-3em}
 \section{Related Literature}\label{RL}
@@
 $\Delta \boldsymbol{h}_{r,u(s,i)}\sim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$ indicates the estimating error vector with a Gaussian distribution and $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$
+\vspace*{-.8em}
 \subsection{Achievable Data Rate}
@@
 Notice that taking the propagation and transmission delays into account in the formulation is straightforward, but we have avoided it for the sake of succinctness and simplicity.
-
-It is worth highlighting that propagation delay must be specially considered when each O-RU can connect to several number of O-DUs and depending on the route, capacity, and priority. 
-However, this would provide a new problem formulation, which could be added to our system model to extend our paper in the future.
+%It is worth highlighting that propagation delay must be specially considered when each O-RU can connect to several number of O-DUs and depending on the route, capacity, and priority. 
+%However, this would provide a new problem formulation, which could be added to our system model to extend our paper in the future.
 In the current paper, we assume that the connection between O-RUs and O-DUs is fixed and transparent, and we do not consider the problem of edge processing.
-As a result, the propagation delay is fixed and does not affect the optimization problem.
+Therefore, the propagation delay is fixed and does not affect the optimization problem.
 
@@
 Suppose the baseband processing of each VNF is modeled by an M/M/1 processing queue.
-Since the system's arrival packets are from many independent sources.
+%Since the system's arrival packets are from many independent sources.
 Moreover, the impact of a single packet on the system's performance is minimal.
@@
 
-Finding a feasible initial value is almost tricky.
-To overcome this challenge, we use a fast method that is discussed in \ref{fr}.
-If the fast method converges and has a feasible solution, so our algorithm (IABV) can be converged too.
-Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
+\textcolor{MidnightBlue}{Finding a feasible initial value is almost tricky. We use a fast method discussed in \ref{fr} to overcome this challenge. 
+Two different methods are used to compare the performance of the proposed method (IABV) and show the optimality of our approach.
 The first one is a baseline scheme, which uses random PRB allocation.
@@
 The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
-After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma \eqref{lemma1}.
-
-For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic} and named it the dynamic resource allocation scheme (DR scheme).
+After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma \eqref{lemma1}.}
+
+\textcolor{MidnightBlue}{For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic} and named it the dynamic resource allocation scheme (DR scheme).
  We have services with different QoS in this work, similar to tenants with different QoS introduced in \cite{lee2018dynamic}.
@@
  Since we do not talk about O-DU and O-CU capacity, we use the dynamic resource allocation scheme (DR scheme) algorithm and do not consider BBU capacity.
-But also, we can assume that O-DU and O-CU have fixed sufficient capacity in our system model.
-Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the idea of the FBDR method with this assumption and using the DR scheme.
  In the DR scheme, PRB and power are dynamically allocated.
@@
 The figures in \cite{lee2018dynamic} show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area.
-The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.
+The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.}
 
 \subsection{Feasible Region}\label{fr}
-Applying the correct initial point to make the system feasible is a significant step in our work.
-During the simulations, it can be noted that sometimes the algorithm does not converge for some of the iterations with fixed initial values.
-To solve this problem, we investigated the non-converging and converging simulation for models with fixed initial parameters (such as number of UEs, the threshold of power and rate,...
-) and random channel gains of UEs.
-By comparing convergent and non-convergent simulations, we experimentally found that in cases where convergence does not occur, there are UEs at the edge of the boundaries or far away from the O-RU and have a weak channel gain.
+\textcolor{MidnightBlue}{Applying the correct initial point to make the system feasible and converge is a significant step in our work.
+To solve this problem, we investigated the non-converging and converging simulation for models with fixed initial parameters and random channel gains of UEs.
+We experimentally found that in non-converged simulations, there are UEs at the edge of the boundaries or far away from the O-RU and have a weak channel gain.
 One solution is to eliminate UEs who undermine system convergence.
-For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interference.
+For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interference.}
 Another solution is to remove the simulations in the Monte-Carlo that do not converge.
 In the simulation part, if more than half of the iterations have a feasible solution for the initial condition, the simulation can be displayed as a feasible model.
-To remove non-converging simulations, we need to use a fast algorithm (FA) to check the convergence before
+To remove non-converging simulations, we use a fast algorithm (FA) to check the convergence before
 the proposed algorithm (IABV).
@@
 Moreover, the allocation of PRBs to UEs is based on dividing the number of UEs by the total number of PRBs.
-If the number of UEs is more than the PRBs, each UE is given exactly one PRB without interference. Otherwise, the amount of interference will not be high but more than one UE will use same PRBs.
-%\vspace*{-1.7em}
+\vspace*{-1.5em}
 \subsection{Numerical Results}
 In Fig.
-\ref{fig:1}, the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods.
+3, the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods.
 Suppose we have one service instance for each type of service, so we have three various services in this figure.
@@
 Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
-\begin{figure}%[!tbp]
-  \centering
-  \captionsetup{justification=centering}
-    \includegraphics[scale = 0.5]{fig/Arate_ue1_1n.eps}
-    \caption{Aggregate throughput vs. number of UEs in each service}% in the presence of three services}
-    \label{fig:1}
-\end{figure}
-
-\begin{figure}
-\centering
-  %\captionsetup{justification=centering}
-  \includegraphics[scale = 0.5]{fig/vnfNum1n.eps}
-       %\includegraphics[width=7cm,height=4cm]{vnfNum1.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Number of activated VNF in each service vs. mean arrival rate(Mbps)}
-  \label{fig:4}
-\end{figure}
-%%%%%%%%%
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.47]{Arate_ue1.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate throughput vs. number of UEs for each service in the presence of three services}
-%  \label{fig:1}
-%\end{figure}
-%%%%%%%%%%%%%%
-%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor
-%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
-%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.4]{mmtcURLLC.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
-%  \label{fig:2}
-%\end{figure}
-%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme.
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.4]{sumRatePri.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
-%  \label{fig:3}
-%\end{figure}
+
+\begin{figure*}[!htb]
+	\centerline{%
+		\begin{tabular}{c@{}c@{}c}			
+			\includegraphics[scale = 0.42]{fig/Arate_ue1_1n.eps} &
+			\includegraphics[scale = 0.42]{fig/vnfNum1n.eps} &
+			\includegraphics[scale = 0.42]{fig/RatePower1n.eps} \\
+			\scriptsize(3)~~Aggregate throughput vs.
+number of UEs in each service & \scriptsize(4)~~Number of  VNFs in each service vs.
+mean arrival rate & \scriptsize(5)~~Aggregate throughput for eMBB vs.
+maximum  power
+	\end{tabular}}
+	%\caption{Global caption.}
+	\label{label}
+\end{figure*}
+
 Fig.
-\ref{fig:4} depicts the number of activated VNFs for five different mean service times of one URLLC service vs.
+4 depicts the number of activated VNFs for five different mean service times of one URLLC service vs.
 the mean arrival time for 12 UEs.
@@
 Moreover, the number of activated VNFs decreases when the mean service rate increases.
-%%%%%%%%%%%%%%
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.47]{vnfNum1.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Number of activated VNF in each Service vs. Mean Arrival Rate(Mbps)}
-%  \label{fig:4}
-%\end{figure}
-%%%%%%%%%%%%
+
 In Fig.
-\ref{fig:5}, the aggregate throughput is depicted vs.
+5, the aggregate throughput is depicted vs.
 the maximum power of UE for three different instances of eMBB service using proposed method (IABV), DR scheme and the baseline scheme.
@@
 Moreover, the proposed method (IABV), gives higher aggregate rates in compared to the DR scheme and the baseline scheme.
-\begin{figure}%[!tbp]
-  \centering
-  %\captionsetup{justification=centering}
-    \includegraphics[scale = 0.5]{fig/RatePower1n.eps}
-    \caption{Aggregate throughput for eMBB vs. maximum transmit power for various number of UEs }
-  \label{fig:5}
-\end{figure}
-\begin{figure}
-  \centering
-  %\captionsetup{justification=centering}
-      \includegraphics[scale = 0.5]{fig/delay_newn.eps}
-  \caption{Mean total delay of a URLLC Service vs. the mean arrival rate of a UE in the service}
-  \label{fig:6}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.47]{RatePower1.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput for eMBB vs. Maximum Transmit power for various number of UEs }
-%  \label{fig:5}
-%\end{figure}
+
+\begin{figure*}[!htb]
+	\centerline{%
+		\begin{tabular}{c@{}c@{}c}			
+			\includegraphics[scale = 0.42]{fig/delay_newn.eps} &
+			\includegraphics[scale = 0.42]{fig/delay1_newn.eps} &
+			\includegraphics[scale = 0.42]{fig/AmmTCpowern.eps} \\
+			\scriptsize(6)~~Mean delay of a URLLC Service vs.
+the arrival rate of a UE  & \scriptsize(7)~~Mean delay of a URLLC  vs.
+the arrival rate of a UE  & \scriptsize(8)~~Aggregate throughput vs.
+number of UEs in mMTC services
+	\end{tabular}}
+	%\caption{Global caption.}
+	\label{label}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%
-Fig. \ref{fig:6} illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
+Fig. 6 illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
 It is shown that the delay is an ascending function of the mean arrival rate (when the mean service time is fixed) and the number of UEs in the service.
@@
 Fig.
-\ref{fig:7} is the same as Fig.
-\ref{fig:6} that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
+7 is the same as Fig.
+6 that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
 As you can see, the proposed method (IABV) outperforms the other scenarios.
-%%%%%%%%%%%%%
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.47]{delay1_new.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for different methods}
-%  \label{fig:7}
-%\end{figure}
-%%%%%%%%%%%%%
-\begin{figure}%[!tbp]
-  \centering
-  %\captionsetup{justification=centering}
-    \includegraphics[scale = 0.5]{fig/delay1_newn.eps}
-    \caption{Mean total delay of a URLLC service vs. the mean arrival rate of a UE in the service}
-  \label{fig:7}
-\end{figure}
-\begin{figure}%[!tbp]
-  \centering
-  %\captionsetup{justification=centering}
-       \includegraphics[scale = 0.5]{fig/AmmTCpowern.eps}
-  \caption{Aggregate throughput vs. number of UEs in each service for three different mMTC services}
-  \label{fig:8}
-\end{figure}
+
 Fig.
-\ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances.
+8, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances.
 mMTC service includes a large number of UEs with low data rates and low power.
@@
 In Fig.
-\ref{fig:9}, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances.
+9, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances.
 Here we consider 4 UEs in each service.
@@
 The Fig.
-\ref{fig:9} presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa.
+9 presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa.
 Also, we can realize from this figure that the aggregate throughput has the most significant value at the same priority.
-\begin{figure}%[!tbp]
-  \centering
-  %\captionsetup{justification=centering}
-        \includegraphics[scale = 0.5]{fig/priorityLastn.eps}
-  \caption{Aggregate throughput for two eMBB service instances vs. priority of the first service instance }
-  \label{fig:9}
-
-\end{figure}
+
+\begin{figure*}[!htb]
+	\centerline{%
+		\begin{tabular}{c@{}c@{}c}			
+			\includegraphics[scale = 0.42]{fig/priorityLastn.eps} &
+			\includegraphics[scale = 0.42]{fig/itern.eps} &
+			\includegraphics[scale = 0.42]{fig/optimal1n.eps} \\
+			\scriptsize(9)~~Throughput of eMBB services vs.
+priority of the first one  & \scriptsize(10)~~Aggregate throughput vs.
+number of iterations  & \scriptsize(11)~~Aggregate throughput vs.
+number of UEs
+	\end{tabular}}
+	%\caption{Global caption.}
+	\label{label}
+\end{figure*}
+
 %%%%%%%%%%5
@@
 %\end{figure}
-In Fig. \ref{fig:11}, the aggregate throughput is shown according to the number of iteration (outer loop) of the
+In Fig. 11, the aggregate throughput is shown according to the number of iteration (outer loop) of the
 proposed algorithm (IABV) for different numbers of UEs for one service. In this figure, the convergence of the IABV method is illustrated. The minimum data rate for each UE is assumed to be 2 Mbps.
@@
 %\subsection{Summary of Simulation Results}
-In Fig. \ref{fig:12}, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
+In Fig. 12, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
 proposed algorithm (IABV) and the optimal method for URLLC service for the low interference.
@@
 Our solution is close to the optimal value in a small number of UEs.
-\begin{figure}%[tbp]
-  \centering
-  %\captionsetup{justification=centering}
-     \includegraphics[scale = 0.5]{fig/itern.eps}
-  \caption{Aggregate throughput vs. number of iterations}
-  \label{fig:11}
-\end{figure}
-\begin{figure}%[tbp]
-  \centering
-  %\captionsetup{justification=centering}
-   \includegraphics[scale = 0.5]{fig/optimal1n.eps}
-  \caption{Aggregate throughput vs. number of UEs in one service}
-  \label{fig:12}
-\end{figure}
-
+
+\begin{figure*}[!htb]
+	\centerline{%
+		\begin{tabular}{c@{}c@{}c}			
+			\includegraphics[scale = 0.42]{fig/interF_newn.eps} &
+			\includegraphics[scale = 0.42]{fig/FAn.eps} &
+			\includegraphics[scale = 0.42]{fig/exec.eps} \\
+			\scriptsize(13)~~Aggregate throughput vs. maximum interference  & \scriptsize(14)~~Aggregate throughput vs. the number of UEs in a service   & \scriptsize(15)~~Execution time vs. number of UEs
+	\end{tabular}}
+	%\caption{Global caption.}
+	\label{label}
+\end{figure*}
 %\begin{figure}
@@
 In Fig.
-\ref{fig:13}, the aggregate throughput is depicted vs.
+13, the aggregate throughput is depicted vs.
 the maximum interference for two different maximum power thresholds of O-RU.
@@
 %The aggregate throughput rises with the increases of UEs and the maximum interference and then remains almost constant.
-\begin{figure}%[tbp]
-  \centering
-  %\captionsetup{justification=centering}
-   \includegraphics[scale = 0.5]{fig/interF_newn.eps}
-  \caption{\small Aggregate throughput vs. maximum interference }
-  \label{fig:13}
-\end{figure}
-\begin{figure}%[tbp]
-  \centering
-  %\captionsetup{justification=centering}
-    \includegraphics[scale = 0.5]{fig/FAn.eps}
-  \caption{\small Aggregate throughput vs. the number of UEs in one service }
-  \label{fig:14}
-
-\end{figure}
+
 %\begin{figure}
@@
 %\end{figure}
-In Fig. \ref{fig:14}, the aggregate throughput is shown versus
+
+In Fig. 14, the aggregate throughput is shown versus
 the different number of UEs for an eMBB service with low interference for the IABV and FA methods in the feasible region.
@@
 %\end{figure}
-\vspace*{-1.em}
+
+In Fig. 15, the execution time is represented versus the number of the UEs for one service. It is noted that the execution time is rising by increasing the number of UEs in the system.
+\vspace*{-1.8em}
 \section{Conclusion}\label{conc}
-In this  paper, we modeled the downlink of the O-RAN system using network slicing for different 5G services, i.e., eMBB, mMTC, and URLLC.
-The isolation of various services, i.e., eMBB, mMTC, and URLLC in the O-DU, the O-CU, and the UPF, is accomplished.
-Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.
-The limited fronthaul capacity and the mean end-to-end delay for each service are considered.
+\textcolor{MidnightBlue}{In this paper, we modeled the downlink of the O-RAN system using isolated network slicing for different 5G services, i.e., eMBB, mMTC, and URLLC.
+We aim to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.} The limited fronthaul capacity and the mean end-to-end delay for each service are considered.
 The problem is mixed-integer non-linear programming that is solved by a two-step iterative algorithm.
@@
 In addition, the feasible region is discussed, and the FA algorithm is introduced to check the feasibility of the initial values.
-Also, we assume distinct scenarios for each service, i.e., eMBB, mMTC, and, URLLC based on their requirement QoS.
+Also, we assume distinct scenarios for each service, i.e., eMBB, mMTC, and URLLC, based on their requirement QoS.
 Simulation results show that the proposed method (i.e., IABV) achieves $18.6\%$ higher data rate than the baseline scheme.
 Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than DR scheme and the baseline scheme.
-\vspace*{-0.7em}
+\vspace*{-0.9em}
 \bibliographystyle{IEEEtran}

### 2022-07-13 Journal1/Response3/Response.tex
add last version

@@
 We would like to thank the editor and reviewers for their constructive comments on our manuscript.
-They have been beneficial in revising this paper, and we have improved both the technical content and presentation quality through their assistance.
+They have been beneficial in revising this paper, and we have improved the technical content and presentation quality through their assistance.
 We greatly appreciate their generous help.
+In addition, we would like to acknowledge the assistance of Dr.
+Onel Luis Alcaraz López in this revision.
 Moreover, we have reviewed and incorporated all the comments and suggestions.
@@
 \noindent \textbf{Response:\\}
-We would like to thank the reviewer for the careful and thorough reading of our manuscript and the thoughtful comment and constructive suggestions that helped us improve the quality of this manuscript and make it more readable.
-We modified the introduction completely and add it below
+As suggested by the reviewer, we modified the introduction completely. The final version is reported below.
 
@@
 \noindent \textbf{Response:\\}
-I would appreciate your comments to enhance and clarify this section of the paper. I moved the background as a section and modified it even as follow.
+We would appreciate your comments to enhance and clarify this paper section. We updated the manuscript by moving the background as a Section and modifying it to present it better. Below we report it.
 
@@
 \noindent \textbf{Response:\\}
-We added the motivation subsection and answer these questions in it.
+We agree with the reviewer that explaining the research challenges is of value to allow the reader to understand the difficulties encountered in proposing the submitted work. For this reason, 
+we added the motivation subsection and answer these questions in it. We rewrite it as follow.
 
@@
 \noindent \textbf{Response:\\}
-We removed these sentences and rewrite the main contribution. Below we present the modified main contribution.
+We updated the manuscript by modifying Section I-B's "main contribution."  We removed these sentences that the reviewer mentioned and altered the main contribution.
+Below we present the revised "main contribution."
 
@@
 \noindent \textbf{Response:\\}
-Thank you for this comment. We moved the background from sub-section to the section part and modified it as below.
+Thank you for this comment. We moved the related works from sub-section to the section part and modified it as below.
 
-O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.
-O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
-With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
-The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
-Several distributed RRHs can be connected to a centralized BBU, called BBU-pool [27].
-Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
- Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.
+The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g., [8],
+[13], [14].
+In [8], dynamic network slicing in heterogeneous C-RAN (H-CRAN) is considered in two levels.
+The higher level manages user acceptance control, radio remote head (RRH) association, and the allocation of BBU capacity.
+Meanwhile, the allocation of power and PRB is performed at the lower level.
+In  [15], RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning.
+In  [16], [17], the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.
 
-In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN.
-As shown in Fig.
-1, O-RU is a logical node that contains RF and low PHY.
-The former transmits or receives radio signals, while the latter includes digital beamforming.
-Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC.
-It contains a subfunction of the eNodeB and is deployed near the O-RU.
-Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
-In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
-The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP).
-The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).
-O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
-The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud.
-Orchestration and Automation include functions such as RIC Non-Real-Time.
-RIC is responsible for machine learning methods and making the system more intelligent  [10]–[12], [28]–[31].
+Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
+In [2], the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
+In [18], a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services.
+Moreover, [19] investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
+In  [5], the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
+% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
+The system guarantees latency, service rate, and reliability maintenance.
+
+In [9], [20], the authors address the issue of beamforming and VMs activation (using virtualization) in a C-RAN system with limited fronthaul capacity.
+Paper [9] aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint.
+Also, transmission and processing delays are modeled based on M/M/1 queueing theory to guarantee UE delays.
+In  [21], [22], the problem of joint virtual computing resource allocation with beamforming is formulated. Also, the association of RRH to the UE is considered and solved using innovative methods.
+
+In  [23]–[25], the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
+Finally, in [26], the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-Thank you for this comment. We modified and clarified this section as below
+We thank the reviewer for the given remark.
+We modified and clarified the description of the life cycle of a network slice.
+We report the relation between Fig.
+1 and the network slice management and explain more about our algorithm in the related subsection below
 
@@
 \noindent \textbf{Response:\\}
+Based on this comment, we added Fig. 11 and Table III to the reported manuscript below.
+In Fig.
+11,  the mean total delay is indicated according to the number of iterations.
+In Table III, we reported the execution delay time according to the number of UEs in the system to investigate the full consideration of the reviewer.
+
+In Fig. 1, the mean total delay is indicated according to the number of iterations of the
+proposed algorithm (IABV) for different numbers of UEs for one service. This figure shows that the algorithm converged to the fixed value after four iterations.
+\begin{figure}[H]
+  \centering
+    \includegraphics[scale = 0.5]{iterD.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Mean Total Delay (usec) vs. Number of iterations}
+  \label{fig:2}
+\end{figure}
+
+Table I shows the execution time versus the number of UEs for one service. We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
+ As the number of UEs in the system increases, the execution time increases polynomially. 
+\begin{table}[H]
+\captionsetup{labelformat=empty}
+ \caption {Table(I) Execution Time vs. Number of UEs} 
+\begin{center}
+ \scalebox{0.9}{
+\begin{tabular}{|| l || l| l |l |l |l ||}
+ \hline
+Number of UEs & 5 & 10 & 15 & 20 & 25 \\ 
+Execution Time (usec)& 12.156 & 19.156 &  29.140 & 44.573 & 67.912 \\
+ \hline
+\end{tabular}}
+\end{center}
+\end{table}
 
@@
 Thank you for this comment to make our paper more readable. We modified the entire paper based on this comment.
+We updated the manuscript while creating additional Sections such as "background" and "related literature" Sections.
+Moreover, we modified and shortened the unnecessary paragraphs, for instance, in the "introduction," "system model," and "numerical results." Our paper was modified totally to satisfy the reviewer's concerns.
 
@@
 \noindent \textbf{Response:\\}
-We appreciate your comment about troubleshooting our paper and removing mistakes. Using this comment as a guide, we modified the entire paper.
+We appreciate your comment about troubleshooting our paper and removing mistakes.
+Using this comment as a guide, we modified the entire paper.
+We revised semantic and grammar problems.
+We reread our paper and tried to correct mistakes the same as this.
 
@@
 \noindent \textbf{Response:\\}
-Based on this comment, we added a acronym table I to our paper as follow
+Based on this comment, we added a Table I reporting the list of acronyms to our paper as follow
 
@@
 \noindent \textbf{Response:\\}
-We modified all figures to make it more readable.
+We modified all figures to make them more readable due to this comment. We enlarge the texts of the figures, bold the lines and markers, and re-formatting all the figures.
 

### 2022-07-13 Journal1/paper5TNSM/pr.tex
add last version

@@
 
-In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
+In \cite{ali2019energy,ali2018joint}, the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
 Finally, in \cite{amani2019power}, the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved. 
-
+%\vspace*{-1.8em}
 \section{Background}\label{BG}
@@
 
-The problem \eqref{problem} is feasible and has feasibility points discussed in Subsection \ref{fr}, and we introduce a fast algorithm (i.e., Algorithm \ref{alg3}  in Subsection \ref{fr}) for feasibility points.
-Although the problem is feasible, it is not convex and challenging to solve.
-Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and by relaxing the variables, the problem is also non-convex; therefore, this problem is NP-hard.
+The problem \eqref{problem} is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and by relaxing the variables, the problem is also non-convex; therefore, this problem is NP-hard.
 Solving the problem is not trivial.
@@
 The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.
-We solve this problem using heuristic method(GAA method \ref{alg1}), which is a greedy algorithm \cite{akccay2007greedy,lee2018dynamic}.
+We solve this problem using heuristic method (GAA method \ref{alg1}), which is a greedy algorithm \cite{akccay2007greedy,lee2018dynamic}.
 Firstly, we set all the variables to zero ($g^r_{u(s,i)} = 0, \quad \forall s, i, r$).
@@
 \State Set $g^r_{u(s,i)} = 0$, $\mathfrak{C}_r = \mathfrak{t}_r,$ and ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$   $\forall s, \forall i, \forall r$.\label{31}
-\State Sort slices according to their priority factor ($\delta_s$) in descending order
+\State Sort slices according to their $\delta_s$ in descending order
 \For {$s \gets 1$ to $S$}\label{33}
@@
 \State Set $RU = 1$
-\Else
-\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $
+\Else: ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $ 
 \EndIf
@@
 \begin{algorithmic}[1]
-\State  Set the maximum number of iterations ${Iter}_{\max}$, convergence condition $\epsilon > 0$ \label{a21}
+\State  Set the maximum num. of iter. ${\text{I}}_{\max}$, convergence condition $\epsilon > 0$ \label{a21}
 \State  Assign Users to O-RU randomly (Initialize $\boldsymbol{G}$) \label{a22}
-\For {$i \gets 1$ to $Iter_{\max}$}\label{23}
+\For {$i \gets 1$ to ${\text{I}}_{\max}$}\label{23}
 \State Acquire $\boldsymbol{P}^{(i)}$, $\boldsymbol{E}^{(i)}$ and $\boldsymbol{M}^{(i)}$ using Lagrangian function and sub-gradient method based on \eqref{sub1}
@@
 \State Break
-\Else
-\State Continue the algorithm
+\Else:   Continue the algorithm
 \EndIf
@@
 \State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
-\Else
-\State $e_{r^*,u(s,i)}^{\text{temp}} = 1 \quad \forall r$
+\Else: $e_{r^*,u(s,i)}^{\text{temp}} = 1 \quad \forall r$
 \State Set $p_{r^*,u(s,i)}^{\text{temp}} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
@@
   \centering
-    \includegraphics[scale = 0.35]{cell.pdf}
+    \includegraphics[scale = 0.33]{cell.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
  \end{table}
-
 \textcolor{MidnightBlue}{Finding a feasible initial value is almost tricky. We use a fast method discussed in \ref{fr} to overcome this challenge. 
@@
 The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.}
-
+\vspace*{-0.9em}
 \subsection{Feasible Region}\label{fr}
@@
 For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interference.}
-Another solution is to remove the simulations in the Monte-Carlo that do not converge.
-In the simulation part, if more than half of the iterations have a feasible solution for the initial condition, the simulation can be displayed as a feasible model.
-To remove non-converging simulations, we use a fast algorithm (FA) to check the convergence before
+Another solution is to remove the simulations in the Monte-Carlo that do not converge using the fast algorithm (FA) to check the convergence before
 the proposed algorithm (IABV).
+Therefore, if more than half of the iterations have a feasible solution for the initial condition, the simulation can be displayed as a feasible model.
 If the conditions in \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
@@
 Moreover, the allocation of PRBs to UEs is based on dividing the number of UEs by the total number of PRBs.
-\vspace*{-1.5em}
+\vspace*{-1.em}
 \subsection{Numerical Results}
@@
 		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.42]{fig/Arate_ue1_1n.eps} &
-			\includegraphics[scale = 0.42]{fig/vnfNum1n.eps} &
-			\includegraphics[scale = 0.42]{fig/RatePower1n.eps} \\
-			\scriptsize(3)~~Aggregate throughput vs.
-number of UEs in each service & \scriptsize(4)~~Number of  VNFs in each service vs.
-mean arrival rate & \scriptsize(5)~~Aggregate throughput for eMBB vs.
+			\includegraphics[scale = 0.41]{fig/Arate_ue1_1n.eps} &
+			\includegraphics[scale = 0.41]{fig/vnfNum1n.eps} &
+			\includegraphics[scale = 0.41]{fig/RatePower1n.eps} \\
+			\scriptsize Fig.
+3~Aggr.
+throughput vs.
+number of UEs in each service & \scriptsize  Fig.
+4~Number of VNFs in each service vs.
+arrival rate & \scriptsize Fig.
+5~Aggr.
+throughput for eMBB vs.
 maximum  power
@@
 We assume that these three services require 5bits/sec/Hz, 10bits/sec/Hz, and 15bits/sec/Hz.
-In addition, We suppose that each O-RU can transmit three times of the maximum power of the UEs.
+%In addition, We suppose that each O-RU can transmit three times of the maximum power of the UEs.
 As you can see in the figure, increasing the maximum power increases the aggregate throughput.
@@
 		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.42]{fig/delay_newn.eps} &
-			\includegraphics[scale = 0.42]{fig/delay1_newn.eps} &
-			\includegraphics[scale = 0.42]{fig/AmmTCpowern.eps} \\
-			\scriptsize(6)~~Mean delay of a URLLC Service vs.
-the arrival rate of a UE  & \scriptsize(7)~~Mean delay of a URLLC  vs.
-the arrival rate of a UE  & \scriptsize(8)~~Aggregate throughput vs.
-number of UEs in mMTC services
+			\includegraphics[scale = 0.41]{fig/delay_newn.eps} &
+			\includegraphics[scale = 0.41]{fig/delay1_newn.eps} &
+			\includegraphics[scale = 0.41]{fig/AmmTCpowern.eps} \\
+			\scriptsize Fig.
+6~~Total Delay of a URLLC vs.
+the arrival rate of a UE  & \scriptsize Fig.
+7~~ Total Delay of a URLLC vs.
+arrival rate of a UE  & \scriptsize Fig.
+8~~Aggr.
+throughput vs.
+the number of mMTC UEs
 	\end{tabular}}
@@
 It is shown that the delay is an ascending function of the mean arrival rate (when the mean service time is fixed) and the number of UEs in the service.
-In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a URLLC service is $0.5ms$.
-Also, the maximum number of PRB is considered to be 50.
+% In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a URLLC service is $0.5ms$. 
+%Also, the maximum number of PRB is considered to be 50.
  Moreover, we can see that the mean delay of a URLLC service
@@
 
-Fig.
-8, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances.
-mMTC service includes a large number of UEs with low data rates and low power.
+Fig. 8, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances. 
 Assume each UE in each mMTC service instance requires 0.1 bits/sec/Hz data rate and is not sensitive to the end-to-end delay. There is no restriction on fronthaul link capacity and the number of VNFs.
@@
 %so we suppose there is a fixed  PRB allocation in the simulation that each UE is allocated to one PRB. There is no PRB with more than one UE allocation.
-The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases.
-Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
+The figure depicts that by increasing the number of UEs in each instance of the service, or by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput increases.
+%Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
 
@@
 Here we consider 4 UEs in each service.
-We assume that the the fronthaul link and the end-to-end delay have no restrictions.
+%We assume that the the fronthaul link and the end-to-end delay have no restrictions.
 The Fig.
@@
 		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.42]{fig/priorityLastn.eps} &
-			\includegraphics[scale = 0.42]{fig/itern.eps} &
-			\includegraphics[scale = 0.42]{fig/optimal1n.eps} \\
-			\scriptsize(9)~~Throughput of eMBB services vs.
-priority of the first one  & \scriptsize(10)~~Aggregate throughput vs.
-number of iterations  & \scriptsize(11)~~Aggregate throughput vs.
-number of UEs
+			\includegraphics[scale = 0.41]{fig/priorityLastn.eps} &
+			\includegraphics[scale = 0.41]{fig/itern.eps} &
+			\includegraphics[scale = 0.41]{fig/iterD.eps} \\
+			\scriptsize Fig.
+9~~Throughput of eMBB services vs.
+priority of the first one  & \scriptsize Fig.
+10~~Aggregate throughput vs.
+number of iterations  & \scriptsize Fig.
+11~~Mean Delay (usec) vs.
+number of iterations
 	\end{tabular}}
@@
 %\end{figure}
-In Fig. 11, the aggregate throughput is shown according to the number of iteration (outer loop) of the
+In Fig. 10, the aggregate throughput is shown according to the number of iteration (outer loop) of the
 proposed algorithm (IABV) for different numbers of UEs for one service. In this figure, the convergence of the IABV method is illustrated. The minimum data rate for each UE is assumed to be 2 Mbps.
 After four iterations, IABV converges to the fixed value.
+
+\textcolor{MidnightBlue}{In Fig. 11, the mean total delay is indicated according to the number of iterations of the
+proposed algorithm (IABV) for different numbers of UEs for one service. This figure shows that the algorithm converged to the fixed value after four iterations.}
 
@@
 Also the mean arrival rate is set to be $0.2$Mbps and the mean service rate is $0.5$Mbps.
-The other parameters are depicted in Table \ref{table:1a}.
+%The other parameters are depicted in Table \ref{table:1a}.
 The optimal approach is obtained from the two-step joint exhaustive search and using CVX.
@@
 		\begin{tabular}{c@{}c@{}c}			
+			\includegraphics[scale = 0.42]{fig/optimal1n.eps} &
 			\includegraphics[scale = 0.42]{fig/interF_newn.eps} &
-			\includegraphics[scale = 0.42]{fig/FAn.eps} &
-			\includegraphics[scale = 0.42]{fig/exec.eps} \\
-			\scriptsize(13)~~Aggregate throughput vs. maximum interference  & \scriptsize(14)~~Aggregate throughput vs. the number of UEs in a service   & \scriptsize(15)~~Execution time vs. number of UEs
+			\includegraphics[scale = 0.42]{fig/FAn.eps} \\
+			\scriptsize Fig. 12~~Aggregate throughput vs. number of UEs   & \scriptsize Fig. 13~~Aggregate throughput vs. maximum interference   & \scriptsize Fig. 14~~Aggregate throughput vs. number of UEs
 	\end{tabular}}
@@
 
-In Fig.
-13, the aggregate throughput is depicted vs.
-the maximum interference for two different maximum power thresholds of O-RU.
-We suppose that the maximum power threshold of UEs is one-third of the maximum power of O-RU.
+In Fig. 13, the aggregate throughput is depicted vs. the maximum interference for two different maximum power thresholds of O-RU. 
+%We suppose that the maximum power threshold of UEs is one-third of the maximum power of O-RU.
 %The minimum data bit rate is assumed to be 0.2Mbps for each UE.
@@
 In Fig. 14, the aggregate throughput is shown versus
-the different number of UEs for an eMBB service with low interference for the IABV and FA methods in the feasible region.
+the number of UEs for an eMBB service with low interference for the IABV and FA methods in the feasible region.
 The minimum data rate for each UE is 1Mb/s/Hz.
@@
 
-In Fig. 15, the execution time is represented versus the number of the UEs for one service. It is noted that the execution time is rising by increasing the number of UEs in the system.
+\textcolor{MidnightBlue}{Table III shows the execution time versus the number of UEs for one service. We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
+ As the number of UEs in the system increases, the execution time increases polynomially.}
+
+\begin{table}[H]
+ \caption {Execution Time vs. Number of UEs} 
+\begin{center}
+ \scalebox{0.9}{
+\begin{tabular}{|| l || l| l |l |l |l ||}
+ \hline
+Number of UEs & 5 & 10 & 15 & 20 & 25 \\ 
+Execution Time (usec)& 12.156 & 19.156 &  29.140 & 44.573 & 67.912 \\
+ \hline
+\end{tabular}}
+\end{center}
+\end{table}
+
+%\begin{figure}[H]
+%  \centering
+%    \includegraphics[scale = 0.4]{fig/exec.eps}
+%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+%  %\caption{Mean Total Delay (usec) vs. Number of iterations}
+%  \captionsetup{labelformat=empty}
+%  \caption{(15) Execution time vs. the number of UEs}
+%  \label{fig:2}
+%\end{figure}
 \vspace*{-1.8em}

### 2022-07-13 Code_journal1/VersionLastJournal/oneSlice1/delayIter.m

@@ -1,0 +1,15 @@
+delay_10UE = 1.0e-05 * [0.5893 0.0911 0.0460 0.0464 0.0464 0.0464 0.0464 0.0464 0.0464 0.0464];
+
+delay_4UE = 1.0e-05 *[0.1083 0.0470 0.0427 0.0424 0.0424 0.0424 0.0424 0.0424 0.0424 0.0424];
+delay_8UE = 1.0e-05 *[0.2979 0.0638 0.0583 0.0580 0.0580 0.0580 0.0580 0.0580 0.0580 0.0580];
+delay_12UE = 1.0e-05*[0.32668 0.0794283 0.06899  0.06892 0.06892 0.06892 0.06892 0.06892 0.06892 0.06892];
+delay_16UE = 1.0e-05*[0.4045 0.1719 0.0761 0.0761 0.0761 0.0761 0.0761 0.0761 0.0761 0.0761];
+plot(delay_16UE*1e6)
+hold on
+plot(delay_12UE*1e6)
+plot(delay_8UE*1e6)
+plot(delay_4UE*1e6)
+
+xlabel('Number of Iterations')
+ylabel('Mean Total Delay (usec)')
+legend('16UEs ','12UEs', '8UEs', '4UEs')

### 2022-07-13 Code_journal1/VersionLastJournal/oneSlice1/delay_time.m

@@ -1,16 +1,15 @@
 clear all
 clc
 run var_const
-count_min1 = 16;
+count_min1 = 10;
 count_step1 = 2;
-count_max1 = 16;
+count_max1 = 10;
 numvar = length(count_min1:count_step1:count_max1);
 iter_max = 10;
 sumRate = zeros(numvar,iter_max);
 sumRate1= zeros(numvar,iter_max);
 
-RU_iter_max = 10;%N_RU + 5;
-delayIter = zeros(iter_max,RU_iter_max);
+RU_iter_max = 5;%N_RU + 5;
 SumRate_prb = zeros(iter_max,numvar,RU_iter_max-1);
 %% initializing
 number_check = 0;
@@ -44,7 +43,7 @@ for i_count = count_min1:count_step1:count_max1
                 %RU_iter = RU_iter_max + 10;
 
             %end
-            delayIter(iter,RU_iter) = sum(Delay_Slice1);
+            
             RU_iter = RU_iter + 1;
          end
 
@@ -71,26 +70,12 @@ for i =1:numvar
     sumRB1(i) = sumRB(i)/num(i);
 end
 
-sumR =  zeros(1,numvar);
-sumR1 =  zeros(1,numvar);
-num = zeros(1,numvar);
-for i =1:numvar
-    for j =1:iter_max
-        if isnan(sumRate(i,j)) == 0 
-            sumR(i) = sumR(i) + sumRate(i,j);
-            num(i)=  num(i) + 1;
-        end
-    end
-    sumR1(i) = sumR(i)/num(i);
-end
 plot( UE_num , sumRB1/1e6,'-*')
-hold on
-plot( UE_num , sumR1/1e6,'-+')
+
 
 xlabel('Number of UEs')
 ylabel('Aggregate Throughput (Mbps)')
 title('Aggregate Throughput vs. Number of UEs')
-legend('Proposed Method (IABV) ','Fast Algorithm (FA)')
 grid on
 %plot(1:RU_iter_max-1,mean(SumRate_prb,1))
 %plot(UE_num ,mean(sumRate,2))

### 2022-07-13 Journal1/Response3/Response.tex
add last version1

@@
 Moreover, we have reviewed and incorporated all the comments and suggestions.
+Additionally, we removed two figures of Fig.
+2 and Fig.
+3 since they don't add much to what is already written in words after revision.
+Even after this revision (comment 2 of reviewer 3), Fig.
+2 makes the paper vaguer.
+We also aim for a more concise manuscript.
 We hope that the modifications we have made to the manuscript and the responses we have provided herein will alleviate the reviewers' concerns.
@@
 \noindent \textbf{Response:\\}
-We would like to thank the Editor for his comments and for giving us this opportunity to improve our paper. We have used the comments to improve our paper and eliminate problems.
+We would like to thank the Editor for his comments and for giving us this opportunity to improve our paper.
+We have used the comments to improve our paper and eliminate problems.
+We are confident that we were able to address the reviewers’ and editor’s suggestions.
 
@@
 \noindent \textbf{Response:\\}
+We apologize for not considering this comment correctly in the previous version.
 Thank you for this comment. We moved the related works from sub-section to the section part and modified it as below.
@@
 
-In  [23]–[25], the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
-Finally, in [26], the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved.
+In  [23],[24], the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
+Finally, in [25], the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-Based on this comment, we added Fig. 11 and Table III to the reported manuscript below.
+We apologize for wrongly responding to this comment in the previous version of the response letter.
+Based on this comment, we added Fig. 11 and Table III to our manuscript.
+Below, we reported these changes.
+
 In Fig.
@@
 
-In Fig. 1, the mean total delay is indicated according to the number of iterations of the
+In Fig. \ref{fig:2}, the mean total delay is indicated according to the number of iterations of the
 proposed algorithm (IABV) for different numbers of UEs for one service. This figure shows that the algorithm converged to the fixed value after four iterations.
@@
 
-Table I shows the execution time versus the number of UEs for one service. We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
+Table III shows the execution delay time versus the number of UEs for one service. We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
  As the number of UEs in the system increases, the execution time increases polynomially. 
+Moreover, we added Fig. \ref{fig:3} to the response letter, which is equal to Table III, but for space reasons, we reported Table III instead of Fig. \ref{fig:3}.
+\begin{figure}[H]
+  \centering
+    \includegraphics[scale = 0.5]{exec.eps}
+    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Execution Time vs. Number of UEs}
+  \label{fig:3}
+\end{figure}
+
 \begin{table}[H]
 \captionsetup{labelformat=empty}
- \caption {Table(I) Execution Time vs. Number of UEs} 
+ \caption {Table(III) Execution Time vs. Number of UEs} 
 \begin{center}
@@
 \noindent \textbf{Response:\\}
-Based on this comment, we added a Table I reporting the list of acronyms to our paper as follow
+Based on this comment, we added Table I reporting the list of acronyms to our paper as follows to relieve the reviewer's concern.
 
@@
 \noindent \textbf{Response:\\}
-Based on this comment, we added a Table I reporting the list of acronyms to the paper that is shown as below
+Based on this comment, we added Table I reporting the list of acronyms to the paper shown below to address the reviewer's concern.
 
@@
 We thank the reviewer for reporting this ambiguity.
-We revised this section, rewrote the equation (3), by removing the inter-slice interference to clarify this equation.
+We revised this section and rewrote equation (3) by removing the inter-slice interference to clarify this equation.
 Moreover, we removed two figures of Fig.
 2 and Fig.
-3 since they don't add much to what is already written in words, and even Fig.
-2 makes the paper vaguer, and we also aim for a more concise manuscript.
+3 since they don't add much to what is already written in words after revision, and even after this revision, Fig.
+2 makes the paper vaguer.
+We also aim for a more concise manuscript.
 Below we report the revised sentences.

### 2022-07-14 Journal1/Response3/Response.tex
add sth

@@
 We would like to thank the Editor for his comments and for giving us this opportunity to improve our paper.
-We have used the comments to improve our paper and eliminate problems.
-We are confident that we were able to address the reviewers’ and editor’s suggestions.
+We used the comments to improve our paper and eliminate problems.
+We are confident that we were able to address the reviewers’ and Editor’s suggestions.
+We upload our point-by-point response to the comments (below) (response to reviewers) and the updated manuscript.
 
@@
 \noindent \textbf{Response:\\}
-We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can alleviate the reviewer's concerns.
+We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can satisfy the reviewer's concerns.
 
@@
 For instance, the introduction has been rewritten totally.
-We also revised the system model, proposed algorithms too, and shortened long paragraphs based on these comments.
-Moreover, we shortened the numerical results and feasible region section, and modified the conslusion section.
+We also revised the system model, proposed algorithms, and shortened long paragraphs based on this comment.
+Moreover, we shortened the numerical results and feasible region section and modified the conclusion section.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 We changed the contribution in a better way based on this comment.
-We have removed some sentences and rewritten the contributions in the same order of our paper's section.
+We have removed some sentences and rewritten the contributions in the same order as our paper's section.
+We explained it in the system model, proposed algorithm, and numerical results.
 Below we report the whole contribution section.
@@
 \noindent \textbf{Response:\\}
-It is our pleasure to thank the reviewer for the careful reading of this manuscript, providing
-thoughtful comments, and offering constructive suggestions that strengthened and enhanced its
-quality. We hope that the responses provided herein can alleviate the reviewer’s concerns.
+It is our pleasure to thank the reviewer for the careful reading of this manuscript, providing thoughtful comments, and offering constructive suggestions that strengthened and enhanced its quality. 
+We hope that the responses provided herein can relieve the reviewer’s concerns.
 
@@
 \noindent \textbf{Response:\\}
-As suggested by the reviewer, we modified the introduction completely. The final version is reported below.
+In response to the reviewer's suggestions, we modified the introduction completely.
+Using this comment as a guide, we attempted to have a logical connection between paragraphs.
+The final version of the 'Introduction' Section is reported below.
 
@@
 \noindent \textbf{Response:\\}
-We would appreciate your comments to enhance and clarify this paper section. We updated the manuscript by moving the background as a Section and modifying it to present it better. Below we report it.
+We would appreciate your comments to enhance and clarify this paper section.
+We updated the manuscript by moving the ORAN explanation as a background section in Section III and modifying it to present it better.
+We also emphasized the importance of this section based on this comment. 
+Below we report it.
 
@@
 We agree with the reviewer that explaining the research challenges is of value to allow the reader to understand the difficulties encountered in proposing the submitted work. For this reason, 
-we added the motivation subsection and answer these questions in it. We rewrite it as follow.
+we added the motivation subsection in Section I-B and answered these questions. We rewrite it as follows.
 
@@
 We apologize for not considering this comment correctly in the previous version.
-Thank you for this comment. We moved the related works from sub-section to the section part and modified it as below.
+We thank the reviewer for clarifying this comment for us. We moved the related works to Section II and modified it as below.
 
@@
 We report the relation between Fig.
-1 and the network slice management and explain more about our algorithm in the related subsection below
+1 and the network slice management and explain more about our algorithm in Section V-B and report it as follows.
 
@@
 Based on this comment, we added Fig. 11 and Table III to our manuscript.
+To be sure that we consider the reviewer's concern, we added two different numerical results.
+In Figure 11, the mean total delay of the URLLC service is illustrated versus the number of iterations, and the convergence of the proposed algorithm is shown.
+In Table III, the execution delay time of the algorithm is reported versus the different number of UEs.
+It shows the effect of the number of UEs on the execution time.
 Below, we reported these changes.
@@
 
-In Fig. \ref{fig:2}, the mean total delay is indicated according to the number of iterations of the
+In Fig. \ref{fig:2}, the mean total delay time of URLLC service is indicated according to the number of iterations of the
 proposed algorithm (IABV) for different numbers of UEs for one service. This figure shows that the algorithm converged to the fixed value after four iterations.
@@
 We updated the manuscript while creating additional Sections such as "background" and "related literature" Sections.
-Moreover, we modified and shortened the unnecessary paragraphs, for instance, in the "introduction," "system model," and "numerical results." Our paper was modified totally to satisfy the reviewer's concerns.
+Moreover, we modified and shortened the unnecessary paragraphs, for instance, in the "introduction," "system model," "proposed algorithm," and "numerical results." Our paper was modified totally to satisfy the reviewer's concerns.
 
@@
 \noindent \textbf{Response:\\}
-We modified all figures to make them more readable due to this comment. We enlarge the texts of the figures, bold the lines and markers, and re-formatting all the figures.
+We modified all figures to make them more readable due to this comment.
+We enlarge the texts of the figures, bold the lines, and markers, re-format all the figures, and place them in sub-figures to improve their presentation.
 
@@
 \noindent \textbf{Response:\\}
-We are pleased to thank the reviewer for his/her detailed and thorough reading of this manuscript. We hope that the responses provided here will assist the reviewer in relieving his or her concerns.
+We are pleased to thank the reviewer for his/her detailed and thorough reading of this manuscript. We hope the responses provided here will assist the reviewer in relieving his/her concerns.
 
@@
 Network slicing techniques significantly reduce inter-service (inter-slice) interference.
-One way consists in leveraging a two-time scale PRB scheduling to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale).
+One way to leverage a two-time scale PRB scheduling is to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale).
 Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC [2], [5], [32].
@@
 Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.
-Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as 
+Back to (2), $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as 
 %{\color{red} use paranthesis in the following equation to clear +}
@@
 \noindent \textbf{Response:\\}  
-Thank you for this comment. We checked and corrected all the figure's captions.
+Thank you for this comment.
+We checked and corrected all the figure's captions.
+As part of our efforts to make all figures more readable, we grouped them into sub-figures and reformatted them to give them more attractive appearance.
 

### 2022-07-14 Journal1/paper5TNSM/pr.tex
add sth

@@
 The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks.
-Nevertheless, strictly satisfying quality-of-service requirements, while establishing priorities and promoting balance between the significantly heterogeneous services, remains as a key research problem.
-In this paper, we study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing.
+Nevertheless, strictly satisfying quality-of-service requirements while establishing priorities and promoting balance between the significantly heterogeneous services remains a key research problem.
+In this paper, we use network slicing to study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems.
 The limited fronthaul capacity and end-to-end delay constraints are simultaneously considered.
-The optimization of baseband resources includes O-RAN radio unit (O-RU) and physical resource block (PRB) assignment, and power allocation.
+Optimizing baseband resources includes O-RAN radio unit (O-RU), physical resource block (PRB) assignment, and power allocation.
 The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve.
@@
 In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is resolved.
-The proposed method is validated via simulations which evince the achievement of a higher data rate and lower end-to-end delay than existing methods.
+The proposed method is validated via simulations, which achieve a higher data rate and lower end-to-end delay than existing methods.
 \end{abstract}
@@
 \textcolor{MidnightBlue}{Network slicing techniques significantly reduce inter-service (inter-slice) interference.
-One way consists in leveraging a two-time scale PRB scheduling to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale).
+One way to leverage a two-time scale PRB scheduling is to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale).
 Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.
@@
 
- Herein, we consider a zero forcing beamforming vector, which minimizes the experienced interference, and is given by \cite{huang2013user}
+ Herein, we consider a zero forcing beamforming vector, which minimizes the experienced intra-slice interference, and is given by \cite{huang2013user}
 \begin{equation}
@@
 number of iterations  & \scriptsize Fig.
-11~~Mean Delay (usec) vs.
+11~~Mean Delay time vs.
 number of iterations
@@
 
-\textcolor{MidnightBlue}{In Fig. 11, the mean total delay is indicated according to the number of iterations of the
-proposed algorithm (IABV) for different numbers of UEs for one service. This figure shows that the algorithm converged to the fixed value after four iterations.}
+\textcolor{MidnightBlue}{In Fig. 11, the mean total delay of URLLC service is indicated according to the number of iterations of the
+proposed algorithm (IABV) for different numbers of UEs for one URLLC service. This figure shows that the algorithm converged to the fixed value after four iterations.}
 

### 2022-09-01 Journal1/Response4/Response.tex
add file

--- 2022-07-13 Journal1/Response3/Response.tex
@@
 We greatly appreciate their generous help.
-In addition, we would like to acknowledge the assistance of Dr.
-Onel Luis Alcaraz López in this revision.
-Moreover, we have reviewed and incorporated all the comments and suggestions.
+We also aim for a more concise manuscript.
 We hope that the modifications we have made to the manuscript and the responses we have provided herein will alleviate the reviewers' concerns.
@@
 \cellcolor{violet!15}
-\textbf{\noindent  Comments to the Author} ``I think the paper should undergo a major revision. It is important to take special attention to the comments of reviewer 2.''\\
+\textbf{\noindent  Comments to the Author} ``I think that the paper has improved substantially.
+However, to make the paper suitable for publication, the comments of reviewer 2 should be taken into account.''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-We would like to thank the Editor for his comments and for giving us this opportunity to improve our paper. We have used the comments to improve our paper and eliminate problems.
+It is our pleasure to thank the Editor for his constructive comments on how to improve our paper.
+Thanks to the comments, we were able to make improvements to our paper and eliminate problems.
+In response to the reviewers and Editor's comments, we are confident we addressed their suggestions.
+We have updated the manuscript and uploaded our point-by-point response to the reviewers' comments (below).
 
@@
 \textbf{\noindent Comments to the Author} ``
-The authors have addressed the comments provided in a previous review.
-The contributions are clear and the results are compared to some related work, so the reader can somewhat contextualize the proposed solution.
-''\\
+The authors have taken into consideration all the comments and suggestions raised by the Reviewer and have provided a substantial work to improve the quality of the manuscript.
+In that regard the Reviewer recommends the acceptance of the paper''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can alleviate the reviewer's concerns.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment1:} ``However, the paper still needs some improvement in terms of readability. Some paragraphs are too long  ''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-We revised the whole paper and checked the text entirely according to this comment.
-For instance, the introduction has been rewritten totally.
-We also revised the system model, proposed algorithms too, and shortened long paragraphs based on these comments.
-Moreover, we shortened the numerical results and feasible region section, and modified the conslusion section.
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment2:} `` the figures are difficult to locate from their reference in the text (figures at top, as typical IEEE template is better), the text in the figures is too small ''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-Thank you for this comment. We think that these changes improve the readability of the manuscripts.
- We modified all the paper's figures entirely concerning this comment and located them in sub-figures to make them more determined.
-Moreover, we modified whole the figures and made the texts larger and more readable.
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment3:} ``the contributions discussed in the introduction are not easily found in the other parts of the paper.  ''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-We thank the reviewer for asking us to add clarity to our paper and reducing ambiguity in this condition.
-We changed the contribution in a better way based on this comment.
-We have removed some sentences and rewritten the contributions in the same order of our paper's section.
-Below we report the whole contribution section.
-
-This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
-%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
-%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
- The main contributions of this paper are summarized as follows:
-\begin{itemize}
-\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
-Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
-\item We propose a two-step resource management algorithm for solving the optimization problem.
-In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs.
-Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation.
-In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
-\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
-Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.
-\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
-Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
-\end{itemize}
+It is a pleasure to have the reviewer read this manuscript; we appreciate his/her attention, which helps us enhance our paper.
 
@@
 \textbf{\noindent Comments to the Author} ``
-The Reviewer would like to thank the authors for their revision of the paper with respect to the comments and suggestions in the previous submission.
-Whereas the authors have considered parts of the suggestions and improved specific areas of the work, there are still a lot of remaining issues of concern in the current version of the paper.
+The paper addresses most comments from previous revisions. However, its organization and presentation is still too weak. ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+Throughout this process, we thank the reviewer for taking the time to read the manuscript carefully, commenting thoughtfully, and offering suggestions that made the manuscript stronger and more valuable.
+In this response, we hope to alleviate the reviewer's concerns.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment1:} ``First, the introduction is too long and does not synthesize the expectations of the rest of the paper.
+It must be changed to follow a the structure followed by other papers published in TNSM.
 ''\\
@@
 \noindent \textbf{Response:\\}
-It is our pleasure to thank the reviewer for the careful reading of this manuscript, providing
-thoughtful comments, and offering constructive suggestions that strengthened and enhanced its
-quality. We hope that the responses provided herein can alleviate the reviewer’s concerns.
+Based on this comment, we have read several TNSM papers, rewritten the introduction's paragraph, removed the additional parts, and tried to enhance it as much as possible.
 
@@
 \cellcolor{gray!15}
-\textbf{\noindent Comment1:} ``While the authors have taken into consideration the Reviewer’s comments about the re-structuring of the Introduction, I am afraid that the current version is not in the adequate state for publication.
-Initially, the paragraphs of the Introduction have no logical connection among them.
-It seems that until the Related Literature subsection all paragraphs are disconnected and only introduce concepts.
+\textbf{\noindent Comment2:} ``Second, many paragraphs are too long, what makes the path of the paper difficult to follow.
+For instance, paragraphs in the introduction give too much detail.
+Such details must be moved to the appropriate section and place a summary in the introduction.
 ''\\
@@
 \noindent \textbf{Response:\\}
-As suggested by the reviewer, we modified the introduction completely. The final version is reported below.
+We have rewritten the introduction and literature review section, removed the additional part, and put it in the correct sections.
+We have shortened long paragraphs and sentences in this paper in order to make it easier to read.
 
-\section{Introduction}
-%\subsection{State Of The Arts}
-Network slicing is a key technology in 5G wireless systems.
-Specifically, network slicing provides the isolation of network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving multiple and heterogeneous service classes [1]–[3].
-There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-Depending on their corresponding quality of service (QoS) requirements, each service is assigned to a slice of the network.
-For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming.
-Meanwhile, the URLLC service, leveraged, e.g., by autonomous vehicles, Tactile Internet, and remote surgery services, is concerned with providing ultra-reliable and low-latency connectivity.
-Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads  [4]–[6].
-%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}
-
-Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
-In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig.
-1, is introduced to deal with these issues.
-%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
-We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
-%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
-%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
-The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence
-
-A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
-Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container [7].
-As a result, some O-RAN components defined in Section III, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.
-
-\subsection{Motivation}
-The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs).
-In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc [2], [8], [9].
-
-Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service.
-Due to the contemporary need to serve services with different QoS simultaneously, e.g., as in 5G and beyond, this architectural model is inefficient.
-In this regard, the O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
-Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
-One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities [1], [10]–[12].  
-%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
-%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
-%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}
-
-The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
-Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
-
-\subsection{Main Contributions}
-
-This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
-%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
-%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
- The main contributions of this paper are summarized as follows:
-\begin{itemize}
-\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
-Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
-\item We propose a two-step resource management algorithm for solving the optimization problem.
-In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs.
-Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation.
-In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
-\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
-Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.
-\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
-Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
-\end{itemize}
-
-Table I lists the acronyms used throughout this paper, which is organized as follows.
-Relevant literature related to our work is discussed in Section II, while Section III briefly overviews the O-RAN architecture.
-The system model and the problem formulation are described in Section IV, V, respectively.
-The details of our proposed resource management algorithm are introduced in Section VI.
-In Section VII, numerical results are provided to evaluate the performance of the proposed algorithm.
-Finally, Section VIII concludes the paper.
-
- \vspace*{-2em}
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \cellcolor{gray!15}
-\textbf{\noindent Comment2:} `` Moreover, I find the ORAN explanation in the Introduction very lengthy and unnecessary. I would definitely suggest to move that as a background Section. ''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-We would appreciate your comments to enhance and clarify this paper section. We updated the manuscript by moving the background as a Section and modifying it to present it better. Below we report it.
-
-O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.
-O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
-With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
-The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
-Several distributed RRHs can be connected to a centralized BBU, called BBU-pool [27].
-Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
- Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.
-
-In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN.
-As shown in Fig.
-1, O-RU is a logical node that contains RF and low PHY.
-The former transmits or receives radio signals, while the latter includes digital beamforming.
-Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC.
-It contains a subfunction of the eNodeB and is deployed near the O-RU.
-Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
-In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
-The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP).
-The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).
-O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
-The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud.
-Orchestration and Automation include functions such as RIC Non-Real-Time.
-RIC is responsible for machine learning methods and making the system more intelligent  [10]–[12], [28]–[31].
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment3:} `` Furthermore, it is surprising how the Introduction does not contain a single research challenge.
-Why is the problem relevant at all?
-Why do you even need to study this problem and why is it hard to solve?
+\textbf{\noindent Comment3:} ``Regarding the technical content, the performance evaluation (Table III) must also include the related work, so that the reader knows the position of the proposed scheme in relation to dynamic resource allocation and baseline schemes.
 ''\\
@@
 \noindent \textbf{Response:\\}
-We agree with the reviewer that explaining the research challenges is of value to allow the reader to understand the difficulties encountered in proposing the submitted work. For this reason, 
-we added the motivation subsection and answer these questions in it. We rewrite it as follow.
-
-The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs).
-In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc [2], [8], [9].
-
-Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service.
-Due to the contemporary need to serve services with different QoS simultaneously, e.g., as in 5G and beyond, this architectural model is inefficient.
-In this regard, the O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
-Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
-One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities [1], [10]–[12].  
-%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
-%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
-%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}
-
-The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
-Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment4:} `` In turn, in the main contributions subsection, the initial sentences of almost all contribution paragraphs cannot be considered as contributions. For instance:
-
-1) “We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers.”
-2) “ Different services need to consider varying QoS conditions, including delay, power, and throughput.”
-3) “The main problem is mixed-integer non-linear programming that is extremely difficult to solve.”
-''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-We updated the manuscript by modifying Section I-B's "main contribution."  We removed these sentences that the reviewer mentioned and altered the main contribution.
-Below we present the revised "main contribution."
-
-This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
-%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
-%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
- The main contributions of this paper are summarized as follows:
-\begin{itemize}
-\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
-Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
-\item We propose a two-step resource management algorithm for solving the optimization problem.
-In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs.
-Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation.
-In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
-\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
-Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.
-\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
-Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
-\end{itemize}
 
@@
 \cellcolor{gray!15}
-\textbf{\noindent Comment5:} `` In a similar fashion, the authors have not considered the Reviewer’s suggestion to move the Related Work as a separate Section in order to improve the flow and clarity of the Introduction.
-''\\
+\textbf{\noindent Comment4:} ``Moreover, it is not clear why the fact that a function increase justifies the convergence of the algorithm. ''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-Thank you for this comment. We moved the related works from sub-section to the section part and modified it as below.
+We thank the reviewer for reporting this ambiguity. We revised this vague statement and added it to section VI-C-2. Below we reported the revised sentences.
 
-The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g., [8],
-[13], [14].
-In [8], dynamic network slicing in heterogeneous C-RAN (H-CRAN) is considered in two levels.
-The higher level manages user acceptance control, radio remote head (RRH) association, and the allocation of BBU capacity.
-Meanwhile, the allocation of power and PRB is performed at the lower level.
-In  [15], RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning.
-In  [16], [17], the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.
-
-Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
-In [2], the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
-In [18], a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services.
-Moreover, [19] investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
-In  [5], the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
-% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
-The system guarantees latency, service rate, and reliability maintenance.
-
-In [9], [20], the authors address the issue of beamforming and VMs activation (using virtualization) in a C-RAN system with limited fronthaul capacity.
-Paper [9] aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint.
-Also, transmission and processing delays are modeled based on M/M/1 queueing theory to guarantee UE delays.
-In  [21], [22], the problem of joint virtual computing resource allocation with beamforming is formulated. Also, the association of RRH to the UE is considered and solved using innovative methods.
-
-In  [23]–[25], the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
-Finally, in [26], the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved.
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment6:} `` Regarding the Reviewer’s comment with respect to the network slice management, whereas the authors have introduced the 4 stages of the life cycle of a network slice, the connection to their approach is very vague.
-It is still not clear how this process is achieved and how it is linked to their method.
-I was expecting at least a connection or introduction to Fig.1 where the system is shown.
-Additionally, more information with respect to the interaction with the system would have been required in that regard.
-''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-We thank the reviewer for the given remark.
-We modified and clarified the description of the life cycle of a network slice.
-We report the relation between Fig.
-1 and the network slice management and explain more about our algorithm in the related subsection below
-
-In this subsection, we will look at the life cycle of network slicing on a practical level. 
-The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages [36];
-\begin{itemize}
-\item Preparation phase: the operator plans to create a network slice instance (NSI) by designing the its template, onboarding users, and preparing the environment.
-Also, the evaluation of requirements is performed in this step.
-\item Commissioning phase: the NSI is created, and the requirements are considered and allocated to the slice.
-\item Operation phase: the NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated.
-As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
-\item Decommissioning phase: an NSI that is decommissioned no longer exists after this phase.
-\end{itemize}
-Since the requirements evaluation is considered in the preparation phase, we need an algorithm to estimate the UE traffic in the system at different times.
-Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs, PRB assignment of UEs for each slice, and the total power requirements.
-In this phase, we use our algorithm to calculate resources after estimating the system's traffic.
-As shown in Fig.
-1, we have three different slices for eMBB, URLLC, and mMTC.
-The system must prepare VNFs for MAC/RLC functions in O-DU, PDCP/SDAP functions in O-CU, UPF, SMF, and AMF functionality layers for each slice.
-Moreover, O-RU, high PHY in O-DU, and O-CU-CP are shared between slices.
-Thus, we do not require evaluating and preparing for the share environments and platforms in the network slicing cycles.
-Moreover, the estimation of PRB and power is needed based on the proposed algorithm.
-After evaluating, assessing, and preparing the resources and environments for each slice, the commissioning phase is started.
-In this phase, the slices are created based on the previous phase estimation.
-These created slices are activated in the operation phase, and the actual resources are assigned based on the proposed algorithm.
-It is possible to modify the slice's resources even when the evaluation changes during the operation phase. 
-If we need to remove a slice or any service not used in a zone, the unshared resources are released in the decommissioning phase.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment7:} ``With respect to the convergence time of the algorithm, the Reviewer had made a suggestion to the authors to include it in the current version of the manuscript, yet the authors do not seem to have done that.
-The authors’ response points to Fig.
-11.
-However if one looks at Fig.11 carefully, understands that only the Aggregate throughput is shown there.
-Even if one considers the Section III-C1 and III-C2 that the authors demonstrate as their convergence analysis and proof, there is no evidence or clarification of any delay value with respect to their algorithm’s convergence.
-On the one hand it is very beneficial to have a mathematical proof that the algorithm converges.
-On the other hand, it is equally important to portray these findings with numerical values.
-In any case, this is not applicable in the current version of the manuscript.
-''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-Based on this comment, we added Fig. 11 and Table III to the reported manuscript below.
-In Fig.
-11,  the mean total delay is indicated according to the number of iterations.
-In Table III, we reported the execution delay time according to the number of UEs in the system to investigate the full consideration of the reviewer.
-
-In Fig. 1, the mean total delay is indicated according to the number of iterations of the
-proposed algorithm (IABV) for different numbers of UEs for one service. This figure shows that the algorithm converged to the fixed value after four iterations.
-\begin{figure}[H]
-  \centering
-    \includegraphics[scale = 0.5]{iterD.eps}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Mean Total Delay (usec) vs. Number of iterations}
-  \label{fig:2}
-\end{figure}
-
-Table I shows the execution time versus the number of UEs for one service. We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
- As the number of UEs in the system increases, the execution time increases polynomially. 
-\begin{table}[H]
-\captionsetup{labelformat=empty}
- \caption {Table(I) Execution Time vs. Number of UEs} 
-\begin{center}
- \scalebox{0.9}{
-\begin{tabular}{|| l || l| l |l |l |l ||}
- \hline
-Number of UEs & 5 & 10 & 15 & 20 & 25 \\ 
-Execution Time (usec)& 12.156 & 19.156 &  29.140 & 44.573 & 67.912 \\
- \hline
-\end{tabular}}
-\end{center}
-\end{table}
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment8:} `As a final remark, the structure of the paper needs major re-construction.
-Several Sections are very lengthy and could be reduced while creating additional Sections.
-In the current format it is very hard to follow.
-''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-Thank you for this comment to make our paper more readable. We modified the entire paper based on this comment.
-We updated the manuscript while creating additional Sections such as "background" and "related literature" Sections.
-Moreover, we modified and shortened the unnecessary paragraphs, for instance, in the "introduction," "system model," and "numerical results." Our paper was modified totally to satisfy the reviewer's concerns.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment9:} `Moreover, there are some typos in the manuscript. For instance, user equipements: user equipment.  ''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-We appreciate your comment about troubleshooting our paper and removing mistakes.
-Using this comment as a guide, we modified the entire paper.
-We revised semantic and grammar problems.
-We reread our paper and tried to correct mistakes the same as this.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment10:} `Furthermore, some acronyms are not explained in the text e.g., Quality of Service (QoS). ''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-Based on this comment, we added a Table I reporting the list of acronyms to our paper as follow
-
-\begin{table}[H]
-\vspace*{-0em}
- \caption {List of Acronyms} \label{table:11a}
- \vspace*{-1em}
- \begin{center}
- \scalebox{1}{
-  \begin{tabular}{l  l }
-  \toprule
-  \vspace*{-0.2em}
-\textbf{Acronym} & \textbf{Definition} \\ [0.5ex]
-   \toprule
-  VNF & virtual network function\\[.5ex]
-
-  VM & virtual machine  \\[.5ex]
-  RAN &  radio access network \\[.5ex]
- O-RAN & open RAN  \\[.5ex]
- vRAN & virtual RAN \\[.5ex]
- CRAN & cloud RAN \\[.5ex]
-   QoS &  quality of service \\[.5ex]
-  MIMO & multiple input multiple output \\[.5ex]
-  PRB &  physical resource block \\[.5ex]
-  SINR & signal to interference and noise ratio  \\[.5ex]
-  eMBB & enhanced mobile broadBand \\[.5ex]
-
-  URLLC  & ultra-reliable low latency communication \\[.5ex]
-
-  mMTC &  massive machine-to-machine communications \\[.5ex]
-
-  O-RU &  O-RAN radio unit \\[.5ex]
-
-   O-DU &  O-RAN distributed unit \\ [.5ex]
-
-   O-CU &  O-RAN central unit \\ [.5ex]
-
-     UPF &  user plane function \\ [.5ex]
-
-  UE &  user equipment \\ [.5ex]
-  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
-  CAPEX & capital expenditures  \\ [.5ex]
-  OPEX & operating expenses  \\ [.5ex]
-
-  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
- \toprule
- \end{tabular}}
- \end{center}
- \end{table}
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment11:} `Finally, the figures in the current version of the manuscript are very small and extremely hard to read. Therefore, re-formatting is necessary. ''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}
-We modified all figures to make them more readable due to this comment. We enlarge the texts of the figures, bold the lines and markers, and re-formatting all the figures.
+Due to limited resources in power, the number of PRBs, and the number of activated VNFs and restrictions based on this limitation on power, energy, fronthaul capacity, etc., the objective function that is the summation of the achievable rates of UEs cannot exceed its optimal value and become infinite.
+Therefore, we can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function concerning the number of iterations.
+Consequently, it converges to the optimum value.
 
@@
 \textbf{\noindent Comments to the Author} ``
-The reviewer has addressed most of the comments satisfactorily. However, the paper still contains some minor issues as follows ''\\
+The paper has addressed the reviewers' comments satisfactorily. ''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-We are pleased to thank the reviewer for his/her detailed and thorough reading of this manuscript. We hope that the responses provided here will assist the reviewer in relieving his or her concerns.
+We appreciate the reviewer's time and attention in reading this manuscript.
 
@@
 \cellcolor{gray!15}
-\textbf{\noindent Comment1:} ``Abbreviations such as QoS, CAPEX and OPEX are not expanded at their first use. ''\\
+\textbf{\noindent Comment1:} ``One minor issue is in Eq. (3) where the plus sign should be in the position after the quantization noise term. ''\\
 \hline
@@
 \noindent \textbf{Response:\\}
-Based on this comment, we added a Table I reporting the list of acronyms to the paper that is shown as below
-
-\begin{table}[H]
-\vspace*{-0em}
- \caption {List of Acronyms} \label{table:11a}
- \vspace*{-1em}
- \begin{center}
- \scalebox{1}{
-  \begin{tabular}{l  l }
-  \toprule
-  \vspace*{-0.2em}
-\textbf{Acronym} & \textbf{Definition} \\ [0.5ex]
-   \toprule
-  VNF & virtual network function\\[.5ex]
-
-  VM & virtual machine  \\[.5ex]
-  RAN &  radio access network \\[.5ex]
- O-RAN & open RAN  \\[.5ex]
- vRAN & virtual RAN \\[.5ex]
- CRAN & cloud RAN \\[.5ex]
-   QoS &  quality of service \\[.5ex]
-  MIMO & multiple input multiple output \\[.5ex]
-  PRB &  physical resource block \\[.5ex]
-  SINR & signal to interference and noise ratio  \\[.5ex]
-  eMBB & enhanced mobile broadBand \\[.5ex]
-
-  URLLC  & ultra-reliable low latency communication \\[.5ex]
-
-  mMTC &  massive machine-to-machine communications \\[.5ex]
-
-  O-RU &  O-RAN radio unit \\[.5ex]
-
-   O-DU &  O-RAN distributed unit \\ [.5ex]
-
-   O-CU &  O-RAN central unit \\ [.5ex]
-
-     UPF &  user plane function \\ [.5ex]
-
-  UE &  user equipment \\ [.5ex]
-  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
-  CAPEX & capital expenditures  \\ [.5ex]
-  OPEX & operating expenses  \\ [.5ex]
-
-  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
- \toprule
- \end{tabular}}
- \end{center}
- \end{table}
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment2:} ``Eq.
-(3) includes inter-slice interference but a sentence following the equation mentions that there is no inter-slice interference because slices are isolated, which is confusing''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\} 
-We thank the reviewer for reporting this ambiguity.
-We revised this section, rewrote the equation (3), by removing the inter-slice interference to clarify this equation.
-Moreover, we removed two figures of Fig.
-2 and Fig.
-3 since they don't add much to what is already written in words, and even Fig.
-2 makes the paper vaguer, and we also aim for a more concise manuscript.
-Below we report the revised sentences.
-
-Network slicing techniques significantly reduce inter-service (inter-slice) interference.
-One way consists in leveraging a two-time scale PRB scheduling to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale).
-Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC [2], [5], [32].
-In this paper, we assume that the PRB scheduling is performed.
-Also, in Section V-A, we briefly study the PRB scheduling between slices.
-Since there are limited resources, inter-service interference cannot be eliminated entirely.
-Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.
-Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as 
-%{\color{red} use paranthesis in the following equation to clear +}
-%\begin{subequations}\label{eqI}
-%\begin{alignat}{4}
-%\begin{align}\label{eqI}
-%&I_{r,u(s,i)}^{k} =\nonumber\\
-% &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
-%&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
-%&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
-%\end{align}
-%\end{alignat}
-%\end{subequations}
-%{\color{red} $\gamma_1$ is constant used instead of variable. }
+We would like to thank the reviewer for correcting our mistake. We modified the position of the plus sign, and the updated version is below.
 \begin{align}\label{eqI}
-&I_{r,u(s,i)}^{k} =+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}}\nonumber\\
+&I_{r,u(s,i)}^{k} =\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}} + \nonumber\\
  &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
 \end{align}
-%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
-where $e^{k}_{u(s,i)}$ is a binary variable that indicates whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU, or not.
-%($\gamma_1$ and $\gamma_2$ are two variales.
-You  define on variable here.)
-Furthermore, there is no inter-slice interference, only intra-slice interference, since slices are assumed to be isolated. 
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment3:} ``The captions of Figs. 9, 12 and 14 are incomplete.''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}  
-Thank you for this comment. We checked and corrected all the figure's captions.
 
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment4:} ``It is recommended to discuss each result figure in one paragraph. Currently, the discussions on Figs. 5-11 are packed into one paragraph, which is difficult to read.''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}  
-We would like to thank the reviewer for reducing the ambiguity of our paper with this comment. Each figure was discussed as an individual paragraph in response to this comment.
-
-\begin{longtable}{|p{0.975\textwidth}|}
-\hline \hline
-\RaggedRight
-\cellcolor{gray!15}
-\textbf{\noindent Comment5:} ``Another round of proofread is required, as there are some mathematical variables which are not italicized and some sentences are incomplete.''\\
-\hline
-\end{longtable}
-\vspace*{-1\baselineskip}
-\noindent \textbf{Response:\\}  
-We modified the whole paper based on this comment, tried correcting all mathematical variables, and revised all sentences again.
-We checked all the system model and proposed algorithms and corrected the italicized text and vice versa.
-For instance, we corrected the $\log$, $\max$, and $\min$ and other texts that are written in italics.
-Moreover, we italicized variables that were written in non-italicized.
 \end{document}

### 2022-09-01 Journal1/paper5TNSM/pr.tex
add file

@@
 \section{Introduction}
-%\subsection{State Of The Arts}
-\textcolor{MidnightBlue}{Network slicing is a key technology in 5G wireless systems.
-Specifically, network slicing provides the isolation of network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving multiple and heterogeneous service classes \cite{shen2020ai,setayesh2020joint,popovski20185g}.
+%\subsection{State Of The Arts} \textcolor{MidnightBlue}{}
+Network slicing is a key technology in 5G wireless systems.
+\textcolor{MidnightBlue}{Network slicing isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various service classes.} \cite{shen2020ai,setayesh2020joint,popovski20185g}.
+
 There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-Depending on their corresponding quality of service (QoS) requirements, each service is assigned to a slice of the network.
+\textcolor{MidnightBlue}{Each service is assigned to a network slice depending on its corresponding quality of service (QoS) requirements.}
 For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming.
-Meanwhile, the URLLC service, leveraged, e.g., by autonomous vehicles, Tactile Internet, and remote surgery services, is concerned with providing ultra-reliable and low-latency connectivity.
-Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.}
+\textcolor{MidnightBlue}{Meanwhile, the URLLC service provides ultra-reliable and low-latency connectivity, e.g., for autonomous vehicles, Tactile Internet, and remote surgeries.} Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
 %\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}
 
-\textcolor{MidnightBlue}{Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
-In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig.
+\textcolor{MidnightBlue}{Radio access networks (RANs) currently lack adequate flexibility and openness to handle these simultaneous service demands.
+Given this, a new RAN paradigm, called open RAN (O-RAN), schematically represented in Fig.
 \ref{fig:c11}, is introduced to deal with these issues.}
@@
 
-\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
-Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.}
-\textcolor{MidnightBlue}{As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.}
+\textcolor{MidnightBlue}{The O-RAN architecture separates hardware and software, enabling network function virtualization (NFV).} Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
+\textcolor{MidnightBlue}{As a result, some O-RAN components defined in Section \ref{BG} are virtualized and implemented as VNFs.}
 
@@
 \subsection{Motivation}
-\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipment (UE).
-In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.}
-
-\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service.
-Due to the contemporary need to serve services with different QoS simultaneously, e.g., as in 5G and beyond, this architectural model is inefficient.
-In this regard, the O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
-Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
-One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.
-}
+\textcolor{MidnightBlue}{The optimal resource allocation for the 5G and 6G systems is crucial to reducing costs and improving user equipment (UE).
+Significant challenges face these systems, including interference alignment, limited capacity of the fronthaul links, energy restrictions on VMs, etc \cite{lee2018dynamic,SystemCostMinimization}.}
+
+\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering a single service's power, data rate, and delay limitations.
+This architectural model is inefficient in 5G and 6G since it needs to serve services with different QoS simultaneously.
+Therefore, O-RAN can simultaneously support multiple services at a lower cost by being flexible, layered, and modular.
+Balancing different services with different QoS, resource requirements, and priorities is a fundamental problem \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.}  
 %\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
@@
 
-\textcolor{MidnightBlue}{The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
-Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.}
+\textcolor{MidnightBlue}{This paper aims to design an O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC, via network slicing and resource allocation.} Specifically, we intend to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
 
@@
 
-\textcolor{MidnightBlue}{This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.}
+\textcolor{MidnightBlue}{This paper studies the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G services.}
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
 %Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
@@
 \begin{itemize}
-\item \textcolor{MidnightBlue}{We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
-Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.}
-\item \textcolor{MidnightBlue}{We propose a two-step resource management algorithm for solving the optimization problem.
+\item \textcolor{MidnightBlue}{We formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN architecture.
+The three types of 5G service classes, i.e., eMBB, URLLC, and mMTC, are considered in this system.
+We take into account their corresponding QoS requirements and service priorities.}
+\item We propose a two-step resource management algorithm for solving the optimization problem.
 In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs.
 Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation.
-In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.}
-\item \textcolor{MidnightBlue}{We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
-Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.}
-\item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
-Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.}
+In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
+\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
+\textcolor{MidnightBlue}{Additionally, we analyze the feasibility region of the problem and introduce a fast algorithm to check it numerically.}
+\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
+Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
 \end{itemize}
@@
 
-\begin{table}[H]
+\begin{table}%[H]
 \vspace*{-0em}
@@
  CRAN & cloud RAN \\[.3ex]
+  RRH & radio remote head \\[.3ex]
+   BBU & baseband unit \\[.3ex]
    QoS &  quality of service \\[.3ex]
@@
   PRB &  physical resource block \\[.3ex]
-  SINR & signal to interference and noise ratio  \\[.3ex]
+  %SINR & signal to interference and noise ratio  \\[.3ex]
   eMBB & enhanced mobile broadBand \\[.3ex]
@@
  \end{center}
+ \vspace*{-2.5em}
  \end{table}
- \vspace*{-3em}
+% \vspace*{-3em}
 \section{Related Literature}\label{RL}
 The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
-In \cite{lee2018dynamic}, dynamic network slicing in heterogeneous C-RAN (H-CRAN) is considered in two levels.
-The higher level manages user acceptance control, radio remote head (RRH) association, and the allocation of BBU capacity.
-Meanwhile, the allocation of power and PRB is performed at the lower level.
-In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning.
-In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.
-
-Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
-\textcolor{MidnightBlue}{In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
-In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services.} Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
-In \cite{alsenwi2021intelligent}, the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
+\textcolor{MidnightBlue}{Two levels of dynamic network slicing in heterogeneous C-RAN (H-CRAN) are examined in \cite{lee2018dynamic}.
+The higher level manages user acceptance control, RRH association, and the allocation of BBU capacity.
+Meanwhile, PRB and power are allocated at lower levels.}
+In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system and executed using deep reinforcement learning.
+\textcolor{MidnightBlue}{In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators.}
+
+\textcolor{MidnightBlue}{Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent work.}
+\textcolor{MidnightBlue}{
+%In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed.
+In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to ensure eMBB and URLLC QoS requirements.
+}Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
+\textcolor{MidnightBlue}{In \cite{alsenwi2021intelligent}, a deep reinforcement learning algorithm is used to solve the resource allocation problem for eMBB and URLLC services.}
 % In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
@@
 
-In \cite{SystemCostMinimization,guo2016exploiting}, the authors address the issue of beamforming and VMs activation (using virtualization) in a C-RAN system with limited fronthaul capacity.
-Paper \cite{SystemCostMinimization} aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint.
-Also, transmission and processing delays are modeled based on M/M/1 queueing theory to guarantee UE delays.
+\textcolor{MidnightBlue}{In \cite{SystemCostMinimization,guo2016exploiting}, VMs activation and beamforming allocation are discussed in C-RAN systems.
+Paper \cite{SystemCostMinimization} minimizes energy cost with system delay, fronthaul capacity, and rate constraints.
+To guarantee UE delays, M/M/1 queueing theory is used for transmission and processing delays.}
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated.
@@
 In \cite{ali2019energy,ali2018joint}, the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
-Finally, in \cite{amani2019power}, the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved. 
-%\vspace*{-1.8em}
+\textcolor{MidnightBlue}{Finally, in \cite{amani2019power}, the optimum power and association of RRH to BBU and RRH to UE are obtained in the massive MIMO-aided C-RAN system.}
+\vspace*{-.8em}
 \section{Background}\label{BG}
-\textcolor{MidnightBlue}{O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.
-O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).} With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
-The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
-Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
-Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-\textcolor{MidnightBlue}{ Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.}
-
-\textcolor{MidnightBlue}{In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN.
+\textcolor{MidnightBlue}{The O-RAN architecture is a flexible, open, low-cost, and intelligent alternative to future RANs. O-RAN combines features of virtual RAN (vRAN) and cloud RAN (C-RAN).
+ By virtualizing RANs, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to their networks more quickly.
+The C-RAN architecture consists of two parts: the radio remote head (RRH) and the baseband unit (BBU).
+Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.} Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+ \textcolor{MidnightBlue}{Mostly non-real-time baseband processing occurs in the O-CU layer, while real-time baseband processing occurs in the O-DU layer.}
+
+In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN.
 As shown in Fig.
@@
 The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP).
-The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).}
+The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).
 O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
+Moreover, O-CU-UP is connected to user plane function (UPF) via O-backhaul link.
 The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud.
-\textcolor{MidnightBlue}{Orchestration and Automation include functions such as RIC Non-Real-Time.
-RIC is responsible for machine learning methods and making the system more intelligent}
+Orchestration and Automation include functions such as RIC Non-Real-Time.
+RIC is responsible for machine learning methods and making the system more intelligent.
+\textcolor{MidnightBlue}{Furthermore, as shown in Fig \ref{fig:c11},  some O-RAN components, such as UPF, O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs.}
 \cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
@@
 \subsection{Signal Model}
-\textcolor{MidnightBlue}{Let $y_{u(s,i)} $ be the received signal of UE $i$ in the $s^{th}$ service such that
+Let $y_{u(s,i)} $ be the received signal of UE $i$ in the $s^{th}$ service such that
 \begin{equation}\label{eq2}
@@
 ${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ corresponding channel vector.
-In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the associated transmit beamforming vector.}
+In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the associated transmit beamforming vector.
 %Here, it is assumed that each UE is served by the nearest o-RU
@@
 
-\textcolor{MidnightBlue}{Network slicing techniques significantly reduce inter-service (inter-slice) interference.
+Network slicing techniques significantly reduce inter-service (inter-slice) interference.
 One way to leverage a two-time scale PRB scheduling is to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale).
@@
 Since there are limited resources, inter-service interference cannot be eliminated entirely.
-Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.}
+Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.
 %\begin{figure}
@@
 
-\textcolor{MidnightBlue}{Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as }
+Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as 
 %{\color{red} use paranthesis in the following equation to clear +}
@@
 \begin{align}\label{eqI}
-&I_{r,u(s,i)}^{k} =+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}}\nonumber\\
+&I_{r,u(s,i)}^{k} =\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}} + \nonumber\\
  &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
@@
 \subsection{PRB Scheduling}\label{prb}
-\textcolor{MidnightBlue}{In this section, we provide a brief study on the problem of PRB scheduling which can be completed in two steps to eliminate the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
+In this section, we provide a brief study on the problem of PRB scheduling which can be completed in two steps to eliminate the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
 For this, firstly, we should assign the PRBs to the slices.
-Secondly, we assign PRBs of slices to UEs, find the optimal number of VNFs for each slice, allocate power of UEs, and assign O-RU to UEs, which uses the proposed Algorithm \ref{proAlg}.}
+Secondly, we assign PRBs of slices to UEs, find the optimal number of VNFs for each slice, allocate power of UEs, and assign O-RU to UEs, which uses the proposed Algorithm \ref{proAlg}.
 Suppose, $\mathcal{R}_{{s}}^{\min}$, and $\mathcal{R}_{{s}}^{\text{max}}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
@@
 \end{itemize}
-\textcolor{MidnightBlue}{Since the requirements evaluation is considered in the preparation phase, we need an algorithm to estimate the UE traffic in the system at different times.
+Since the requirements evaluation is considered in the preparation phase, we need an algorithm to estimate the UE traffic in the system at different times.
 Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs, PRB assignment of UEs for each slice, and the total power requirements.
@@
 It is possible to modify the slice's resources even when the evaluation changes during the operation phase. 
-If we need to remove a slice or any service not used in a zone, the unshared resources are released in the decommissioning phase.}
+If we need to remove a slice or any service not used in a zone, the unshared resources are released in the decommissioning phase.
 %\vspace*{-1em}
@@
 \subsubsection{Convergence Analysis}
-We can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function concerning the number of iterations.% \cite{gholipoor2020resource}.
+ \textcolor{MidnightBlue}{Due to limited resources in power, the number of PRBs, and the number of activated VNFs and restrictions based on this limitation on power, energy, fronthaul capacity, etc., the objective function that is the summation of the achievable rates of UEs cannot exceed its optimal value and become infinite.
+Therefore, we can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function concerning the number of iterations.
+Consequently, it converges to the optimum value.}
+% \cite{gholipoor2020resource}.
 Consider the aggregate throughput as $\mathcal{T(\bold{P},\bold{E},\bold{G})} =\sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}}$.
@@
  \end{table}
-\textcolor{MidnightBlue}{Finding a feasible initial value is almost tricky. We use a fast method discussed in \ref{fr} to overcome this challenge. 
+Finding a feasible initial value is almost tricky. We use a fast method discussed in \ref{fr} to overcome this challenge. 
 Two different methods are used to compare the performance of the proposed method (IABV) and show the optimality of our approach.
@@
 The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
-After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma \eqref{lemma1}.}
-
-\textcolor{MidnightBlue}{For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic} and named it the dynamic resource allocation scheme (DR scheme).
+After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma \eqref{lemma1}.
+
+For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic} and named it the dynamic resource allocation scheme (DR scheme).
  We have services with different QoS in this work, similar to tenants with different QoS introduced in \cite{lee2018dynamic}.
@@
 The figures in \cite{lee2018dynamic} show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area.
-The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.}
+The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.
 \vspace*{-0.9em}
 \subsection{Feasible Region}\label{fr}
-\textcolor{MidnightBlue}{Applying the correct initial point to make the system feasible and converge is a significant step in our work.
+Applying the correct initial point to make the system feasible and converge is a significant step in our work.
 To solve this problem, we investigated the non-converging and converging simulation for models with fixed initial parameters and random channel gains of UEs.
@@
 One solution is to eliminate UEs who undermine system convergence.
-For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interference.}
+For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interference.
 Another solution is to remove the simulations in the Monte-Carlo that do not converge using the fast algorithm (FA) to check the convergence before
@@
 
-\textcolor{MidnightBlue}{In Fig. 11, the mean total delay of URLLC service is indicated according to the number of iterations of the
-proposed algorithm (IABV) for different numbers of UEs for one URLLC service. This figure shows that the algorithm converged to the fixed value after four iterations.}
+In Fig. 11, the mean total delay of URLLC service is indicated according to the number of iterations of the
+proposed algorithm (IABV) for different numbers of UEs for one URLLC service. This figure shows that the algorithm converged to the fixed value after four iterations.
 
@@
 
-\textcolor{MidnightBlue}{Table III shows the execution time versus the number of UEs for one service. We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
- As the number of UEs in the system increases, the execution time increases polynomially.}
+Table III shows the execution time versus the number of UEs for one service. We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
+ As the number of UEs in the system increases, the execution time increases polynomially.
 
@@
 \section{Conclusion}\label{conc}
-\textcolor{MidnightBlue}{In this paper, we modeled the downlink of the O-RAN system using isolated network slicing for different 5G services, i.e., eMBB, mMTC, and URLLC.
-We aim to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.} The limited fronthaul capacity and the mean end-to-end delay for each service are considered.
+In this paper, we modeled the downlink of the O-RAN system using isolated network slicing for different 5G services, i.e., eMBB, mMTC, and URLLC.
+We aim to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.
+The limited fronthaul capacity and the mean end-to-end delay for each service are considered.
 The problem is mixed-integer non-linear programming that is solved by a two-step iterative algorithm.

### 2022-09-02 Journal1/paper5-oldTNSM/pr.tex
add paper for revised

--- 2022-09-01 Journal1/paper5TNSM/pr.tex
@@
 \section{Introduction}
-%\subsection{State Of The Arts} \textcolor{MidnightBlue}{}
+%\subsection{State Of The Arts}
 Network slicing is a key technology in 5G wireless systems.
-\textcolor{MidnightBlue}{Network slicing isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various service classes.} \cite{shen2020ai,setayesh2020joint,popovski20185g}.
+Specifically, network slicing provides the isolation of network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving multiple and heterogeneous service classes \cite{shen2020ai,setayesh2020joint,popovski20185g}.
 
 There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-\textcolor{MidnightBlue}{Each service is assigned to a network slice depending on its corresponding quality of service (QoS) requirements.}
+Depending on their corresponding quality of service (QoS) requirements, each service is assigned to a slice of the network.
 For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming.
-\textcolor{MidnightBlue}{Meanwhile, the URLLC service provides ultra-reliable and low-latency connectivity, e.g., for autonomous vehicles, Tactile Internet, and remote surgeries.} Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
+Meanwhile, the URLLC service, leveraged, e.g., by autonomous vehicles, Tactile Internet, and remote surgery services, is concerned with providing ultra-reliable and low-latency connectivity.
+Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
 %\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}
 
-\textcolor{MidnightBlue}{Radio access networks (RANs) currently lack adequate flexibility and openness to handle these simultaneous service demands.
-Given this, a new RAN paradigm, called open RAN (O-RAN), schematically represented in Fig.
-\ref{fig:c11}, is introduced to deal with these issues.}
+%Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
+In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig.
+\ref{fig:c11}, is introduced to deal with these issues.
+
 %This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
@@
 
-\textcolor{MidnightBlue}{The O-RAN architecture separates hardware and software, enabling network function virtualization (NFV).} Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
-\textcolor{MidnightBlue}{As a result, some O-RAN components defined in Section \ref{BG} are virtualized and implemented as VNFs.}
-
-\begin{figure}
-  \centering
-  \captionsetup{justification=centering}
-    \includegraphics[scale = 0.36]{finalDraw1.pdf}
-    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-  \caption{Network sliced O-RAN system}
-  \label{fig:c11}
-\end{figure}
+%A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
+Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
+%As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.
+
 \subsection{Motivation}
-\textcolor{MidnightBlue}{The optimal resource allocation for the 5G and 6G systems is crucial to reducing costs and improving user equipment (UE).
-Significant challenges face these systems, including interference alignment, limited capacity of the fronthaul links, energy restrictions on VMs, etc \cite{lee2018dynamic,SystemCostMinimization}.}
-
-\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering a single service's power, data rate, and delay limitations.
-This architectural model is inefficient in 5G and 6G since it needs to serve services with different QoS simultaneously.
-Therefore, O-RAN can simultaneously support multiple services at a lower cost by being flexible, layered, and modular.
-Balancing different services with different QoS, resource requirements, and priorities is a fundamental problem \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.}  
+The optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipment (UE).
+In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.
+
+Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service. 
+%Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
+In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig.
+\ref{fig:c11}, is introduced to deal with these issues.
+Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. 
+In this regard, a new RAN paradigm, called open RAN (O-RAN) architecture, has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
+Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
+One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.
 %\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
@@
 
-\textcolor{MidnightBlue}{This paper aims to design an O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC, via network slicing and resource allocation.} Specifically, we intend to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
+The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
+% Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
 
 \subsection{Main Contributions}
-
-\textcolor{MidnightBlue}{This paper studies the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G services.}
+This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
 We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
@@
 \begin{itemize}
-\item \textcolor{MidnightBlue}{We formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN architecture.
-The three types of 5G service classes, i.e., eMBB, URLLC, and mMTC, are considered in this system.
-We take into account their corresponding QoS requirements and service priorities.}
+\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
+Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
 \item We propose a two-step resource management algorithm for solving the optimization problem.
@@
 \item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
-\textcolor{MidnightBlue}{Additionally, we analyze the feasibility region of the problem and introduce a fast algorithm to check it numerically.}
+Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.
 \item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
@@
 
-Table \ref{table:11a} lists the acronyms used throughout this paper, which is organized as follows.
+\subsection{Organization}
+%Table \ref{table:11a} lists the acronyms used throughout this paper, which
+This paper is organized as follows.
 Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
-The system model and the problem formulation are described in Section \ref{systemmodel}, \ref{prS}, respectively.
+The system model and the problem formulation are described in Section \ref{systemmodel} and Section \ref{prS}, respectively.
 The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}.
@@
 Finally, Section \ref{conc} concludes the paper.
+For clarity, Table I lists the main acronyms used throughout the paper.
 
@@
  \end{table}
+
 % \vspace*{-3em}
@@
 The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
-\textcolor{MidnightBlue}{Two levels of dynamic network slicing in heterogeneous C-RAN (H-CRAN) are examined in \cite{lee2018dynamic}.
-The higher level manages user acceptance control, RRH association, and the allocation of BBU capacity.
-Meanwhile, PRB and power are allocated at lower levels.}
-In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system and executed using deep reinforcement learning.
-\textcolor{MidnightBlue}{In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators.}
-
-\textcolor{MidnightBlue}{Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent work.}
-\textcolor{MidnightBlue}{
-%In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed.
-In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to ensure eMBB and URLLC QoS requirements.
-}Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
-\textcolor{MidnightBlue}{In \cite{alsenwi2021intelligent}, a deep reinforcement learning algorithm is used to solve the resource allocation problem for eMBB and URLLC services.}
+In \cite{lee2018dynamic}, dynamic network slicing in heterogeneous C-RAN (H-CRAN) is considered in two levels.
+The higher level manages user acceptance control, radio remote head (RRH) association, and the allocation of BBU capacity.
+Meanwhile, the allocation of power and PRB is performed at the lower level.
+In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning.
+In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.
+
+Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
+In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
+In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services.
+Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
+In \cite{alsenwi2021intelligent}, the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
 % In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
@@
 
-\textcolor{MidnightBlue}{In \cite{SystemCostMinimization,guo2016exploiting}, VMs activation and beamforming allocation are discussed in C-RAN systems.
-Paper \cite{SystemCostMinimization} minimizes energy cost with system delay, fronthaul capacity, and rate constraints.
-To guarantee UE delays, M/M/1 queueing theory is used for transmission and processing delays.}
+In \cite{SystemCostMinimization,guo2016exploiting}, the authors address the issue of beamforming and VMs activation (using virtualization) in a C-RAN system with limited fronthaul capacity.
+Paper \cite{SystemCostMinimization} aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint.
+Also, transmission and processing delays are modeled based on M/M/1 queueing theory to guarantee UE delays.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated.
@@
 In \cite{ali2019energy,ali2018joint}, the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
-\textcolor{MidnightBlue}{Finally, in \cite{amani2019power}, the optimum power and association of RRH to BBU and RRH to UE are obtained in the massive MIMO-aided C-RAN system.}
-\vspace*{-.8em}
+Finally, in \cite{amani2019power}, the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved. 
+%\vspace*{-1.8em}
 \section{Background}\label{BG}
-\textcolor{MidnightBlue}{The O-RAN architecture is a flexible, open, low-cost, and intelligent alternative to future RANs. O-RAN combines features of virtual RAN (vRAN) and cloud RAN (C-RAN).
- By virtualizing RANs, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to their networks more quickly.
-The C-RAN architecture consists of two parts: the radio remote head (RRH) and the baseband unit (BBU).
-Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.} Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
- \textcolor{MidnightBlue}{Mostly non-real-time baseband processing occurs in the O-CU layer, while real-time baseband processing occurs in the O-DU layer.}
+\begin{figure}
+  \centering
+  \captionsetup{justification=centering}
+    \includegraphics[scale = 0.36]{finalDraw1.pdf}
+    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
+    %\includegraphics[width=\textwidth]{finalDraw.pdf}
+  \caption{Network sliced O-RAN system}
+  \label{fig:c11}
+\end{figure}
+O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.
+O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
+With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
+The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
+Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
+Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
+ Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.
 
@@
 In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
+
 The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP).
@@
 Moreover, O-CU-UP is connected to user plane function (UPF) via O-backhaul link.
+
 The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud.
@@
 RIC is responsible for machine learning methods and making the system more intelligent.
-\textcolor{MidnightBlue}{Furthermore, as shown in Fig \ref{fig:c11},  some O-RAN components, such as UPF, O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs.}
+
+\textcolor{MidnightBlue}{This architecture separates hardware and software, enabling network function virtualization (NFV).
+Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
+As a result, as shown in Fig \ref{fig:c11}, O-RAN components, such as UPF, O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs.}
 \cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 

### 2022-09-02 Journal1/paper5TNSM/pr.tex
add paper for revised

@@
 RIC is responsible for machine learning methods and making the system more intelligent.
-\textcolor{MidnightBlue}{Furthermore, as shown in Fig \ref{fig:c11},  some O-RAN components, such as UPF, O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs.}
+\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
+Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
+As a result, some O-RAN components such as user plane function (UPF), O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs.}
 \cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 

### 2022-09-05 Journal1/Response4/Response.tex
add paper for revised
add last revised part

@@
-%\documentclass[12pt, draftclsnofoot, onecolumn,letterpaper]{IEEEtran}
 \documentclass[12pt, letterpaper]{article}
@@
 Based on this comment, we have read several TNSM papers, rewritten the introduction's paragraph, removed the additional parts, and tried to enhance it as much as possible.
-
+We also shortened the introduction.
+We added an organization subsection and revised the whole of the introduction.
+Moreover, we modified the related literature, removed additional parts, and added more related literature reviews.
+Additionally, we modified the background section, removed some sentences from the introduction, and added them to this section.
+Also, we removed some additional parts from this section.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 We have shortened long paragraphs and sentences in this paper in order to make it easier to read.
+Furthermore, we modified the literature review and background too.
+We shortened the long paragraphs in the introduction, literature review, and background sections and added some additional literature reviews to make the paper more useful.
 
@@
 \noindent \textbf{Response:\\}
+Based on this comment, we added the results for the baseline scheme and the DR methods in Table  III in Section VII-C.
+Table I shows the execution time versus the number of UEs for one service for the three methods.
+We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk).
+ As the number of UEs in the system increases, the execution time increases polynomially for all three algorithms.
+Since the baseline scheme is a simpler algorithm, with random PRB allocation and O-RU association based on distance, the execution time is less than the two other algorithms.
+Power and PRB are allocated in the DR scheme, but O-RUs are associated based on distance.
+Therefore the execution time is less than the proposed algorithm.
+\begin{table}[H]
+ \caption {Execution Time vs. Number of UEs} 
+\begin{center}
+\begin{tabular}{ |l|l|l|l| }
+%\hline
+%\multicolumn{3}{|c|}{Country List} \\
+\hline
+\multirow{2}{*}{Number of UEs } &\multicolumn{3}{|c|}{Execution Time (usec)} \\
+\cline{2-4}
+{} &Proposed method & DR scheme & Baseline scheme \\
+\hline
+5 & 12.156 &8.9546 &6.6436\\
+10 & 19.156   & 12.3112& 8.7870\\
+15 &29.140 & 17.4778 &9.5648 \\
+20    &44.573 &  24.5342 &14.8334 \\
+25 & 67.912  & 36.7926 &21.5510 \\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+%\begin{table}%[H]
+%\vspace*{-0em}
+% \caption {Execution Time vs. Number of UEs} \label{table:2}
+% \vspace*{-1em}
+% \begin{center}
+% \scalebox{0.9}{
+%  \begin{tabular}{|l| l| l| l| l| l|}
+%   \hline 
+%  Number of UEs & 5 & 10 & 15 & 20 & 25 \\
+%  \hline 
+%  Execution Time(usec) &  &  &  &  &  \\
+%  Proposed Method & 12.156 & 19.156 &  29.140 & 44.573 & 67.912  \\ [.3ex]
+%
+%  DR method &  9.9546 & 13.3112 &  15.4778 & 17.5342 & 30.7926 \\ [.3ex]
+%  Baseline scheme &  6.6436 &   7.7870  &  8.5648  & 9.8334 &  14.5510 \\ [.3ex]
+%   \hline 
+% \end{tabular}}
+% \end{center}
+% \vspace*{-2.5em}
+% \end{table}
 
@@
 Due to limited resources in power, the number of PRBs, and the number of activated VNFs and restrictions based on this limitation on power, energy, fronthaul capacity, etc., the objective function that is the summation of the achievable rates of UEs cannot exceed its optimal value and become infinite.
-Therefore, we can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function concerning the number of iterations.
-Consequently, it converges to the optimum value.
+Therefore, we can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function in the non-optimal set of variables concerning the number of iterations.
+Consequently, it converges to the optimum global value.
+Meanwhile, if the objective function is the non-monotonically ascending function, we can prove the local convergence of the algorithm.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment5:} ``In addition, only the convergence to the local optimum that is closest to the initial values is achieved, and it is not clear how it can be extended to global convergence.
+''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We agree with the reviewer that we only talked about the convergence of the proposed algorithm, and we do not talk about the global and local convergence.
+Based on our proof, the algorithm is converged to the local convergence.
+But we do not provide global convergence of our algorithm.
+
+Moreover, Fig.
+12 shows the aggregate throughput vs.
+the number of UEs for the optimal solution and proposed algorithm.
+Therefore, there is a low interference comparison between the proposed method and the optimal solution for the system.
+In this figure, the proposed solution is near the optimal solution.
+Thus, the simulation demonstrates that it almost reaches the global optimum.
+Hence, Fig.
+12 numerically illustrates the global convergence of the algorithm.
+
+In addition, to extend our solution to the global optimum, we must prove that the algorithm monotonically increases in the non-optimal set of solutions.
+
+ Moreover, in the low interference system, in which the PRB and VNF assignment is obtained straightforward, and the whole problem of the first step is about power allocation, in the first step of our algorithm that the optimal power and PRB allocation are obtained for the fixed O-RU association; we have
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$ (strictly increase).
+ Since the PRB assignment is straightforward and we used the KKT condition for power allocation, the problem is a convex optimization.
+The KKT condition problem has a global convergence and achieves the optimal solution in convex optimization.
+Accordingly, the algorithm monotonically increases to reach its optimum solution.
+However, in the second step of the algorithm, we can prove that the algorithm is increased, but we can not talk about monotonically increases.
+Hence we have
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
+Therefore, we have 
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
+Consequently, the algorithm converges to the 
+global optimum solution in low interference.
+
+Meanwhile, Zangwill's global convergence theory of iterative algorithms is a standard theory for providing the global convergence of an iterative algorithm.
+We need to use this theory to prove our algorithm in a standard way which is not straightforward in this paper.
+
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment6:} ``In general, the paper must clarify to "what" is the algorithm converging or the global maximum can be understood by the reader and it can be confusing. ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We agree with the reviewer that we must clarify "what" the algorithm converges.
+As mentioned in the previous question, we prove that the algorithm can converge to a global convergence in low interference.
+Moreover, in Fig. 12, we numerically demonstrate our algorithm's global convergence in low interference.
+ However, we can not talk about the global convergence of the algorithm in other states.
+We still will not prove that our algorithm converged to global convergence.
+However, we verified the local convergence of our algorithm in any condition.
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment7:} ``Regarding presentation, there are some grammar typos, such as "reformulated as follow" in Section VI.B, second paragraph.  ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+We are pleased to thank the reviewer for improving the grammar in our paper. We have read the paper one more time and tried to fix any grammar problems in the paper.
+\begin{longtable}{|p{0.975\textwidth}|}
+\hline \hline
+\RaggedRight
+\cellcolor{gray!15}
+\textbf{\noindent Comment8:} ``Finally, according to IEEE style, tables and algorithms must be placed at top of the page, in addition to figures, which have already been correctly placed.  ''\\
+\hline
+\end{longtable}
+\vspace*{-1\baselineskip}
+\noindent \textbf{Response:\\}
+It is our pleasure to thank the reviewer for this comment.
+We agree with the reviewer that the tables and algorithms need to be moved.
+As a result, all these mistakes were corrected, and the wrong ones were moved to the top.
 

### 2022-09-05 Journal1/paper5-oldTNSM/pr.tex
add last revised part

@@
 \usepackage{setspace}
+\usepackage{array,tabulary,tabularx,multirow}
 \usepackage[T1]{fontenc}
@@
 Network slicing is a key technology in 5G wireless systems.
-Specifically, network slicing provides the isolation of network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving multiple and heterogeneous service classes \cite{shen2020ai,setayesh2020joint,popovski20185g}.
+\textcolor{MidnightBlue}{Specifically, it isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various services.} \cite{shen2020ai,setayesh2020joint,popovski20185g}.
 
 There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-Depending on their corresponding quality of service (QoS) requirements, each service is assigned to a slice of the network.
+\textcolor{MidnightBlue}{Each service is assigned to a network slice depending on its corresponding quality of service (QoS) requirements.}
 For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming.
-Meanwhile, the URLLC service, leveraged, e.g., by autonomous vehicles, Tactile Internet, and remote surgery services, is concerned with providing ultra-reliable and low-latency connectivity.
-Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
+\textcolor{MidnightBlue}{Meanwhile, the URLLC service provides ultra-reliable and low-latency connectivity, e.g., for autonomous vehicles, Tactile Internet, and remote surgeries.} Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
 %\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}
@@
 \subsection{Motivation}
-The optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipment (UE).
-In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.
-
-Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service. 
+\textcolor{MidnightBlue}{The optimal resource allocation for the 5G systems is crucial to reducing costs and improving user equipment (UE).
+Significant challenges face these systems, including interference alignment, limited capacity of the fronthaul links, energy restrictions on virtual machines (VMs), etc }\cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.
+
+\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering a single service's power, data rate, and delay limitations.}
 %Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
@@
 \ref{fig:c11}, is introduced to deal with these issues.
-Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. 
-In this regard, a new RAN paradigm, called open RAN (O-RAN) architecture, has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
-Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
-One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.
+\textcolor{MidnightBlue}{Unfortunately, the existing radio access networks (RANs) currently lack adequate flexibility and openness to handle these simultaneous service demands. 
+Hence, a new RAN paradigm, called open RAN (O-RAN) architecture, has emerged.
+% as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
+Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.}
+Therefore, O-RAN can simultaneously support multiple services at a lower cost by being flexible, layered, and modular.  
+One of the fundamental problems lies in balancing services with different QoS, resource requirements, and priorities in O-RAN architecture.}
+ \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.  
 %\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
@@
 \subsection{Main Contributions}
-This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
+\textcolor{MidnightBlue}{This paper studies the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G services.}
 We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
@@
 \begin{itemize}
-\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
-Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
+\item \textcolor{MidnightBlue}{We examine the problem of baseband resource allocation, such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN architecture.
+The three types of 5G service classes, i.e., eMBB, URLLC, and mMTC, are considered in this system.
+We take into account their corresponding QoS requirements and service priorities.}
 \item We propose a two-step resource management algorithm for solving the optimization problem.
@@
 In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
-\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence.
-Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.
+\item \textcolor{MidnightBlue}{We analyze the complexity of the proposed algorithms and demonstrate their convergence.
+Additionally, we analyze the feasibility region of the problem and introduce a fast algorithm to check it numerically.}
 \item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
@@
  \begin{center}
- \scalebox{1}{
+ \scalebox{0.9}{
   \begin{tabular}{l  l }
@@
 The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
-In \cite{lee2018dynamic}, dynamic network slicing in heterogeneous C-RAN (H-CRAN) is considered in two levels.
-The higher level manages user acceptance control, radio remote head (RRH) association, and the allocation of BBU capacity.
-Meanwhile, the allocation of power and PRB is performed at the lower level.
+\textcolor{MidnightBlue}{Two levels of dynamic network slicing in heterogeneous C-RAN (H-CRAN) are examined in \cite{lee2018dynamic}.
+The higher level manages user acceptance control, RRH association, and the allocation of BBU capacity.
+Meanwhile, PRB and power are allocated at lower levels.}
 In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning.
 In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.
-
-Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
+\textcolor{MidnightBlue}{ In \cite{singh2022joint}, to provide 5G slicing services, the authors present a framework called O-RANFed that implements and optimizes federated learning tasks in O-RAN devices.}
+\textcolor{MidnightBlue}{ Moreover, The authors of \cite{zhang2022federated} propose a federated deep reinforcement learning algorithm to achieve network slicing in O-RAN.}
+
+\textcolor{MidnightBlue}{ Recent research has focused on multiplexing eMBB and URLLC services within a RAN.}
 In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
@@
 O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.
+
 O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
-With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly.
-The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
+\textcolor{MidnightBlue}{By virtualizing RANs, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to their networks more quickly.} The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
 Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
 Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
- Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.
+ \textcolor{MidnightBlue}{Mostly non-real-time baseband processing occurs in the O-CU layer, while real-time baseband processing occurs in the O-DU layer.}
 
@@
 
-\textcolor{MidnightBlue}{This architecture separates hardware and software, enabling network function virtualization (NFV).
+\textcolor{MidnightBlue}{A key feature of the O-
+RAN architecture is that the hardware is disaggregated from
+the software, leading to network function virtualization
+(NFV).
 Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
-As a result, as shown in Fig \ref{fig:c11}, O-RAN components, such as UPF, O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs.}
+As a result, as shown in Fig \ref{fig:c11}, O-RAN components, such as UPF, O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs}
 \cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
-%\begin{table}[H]
-% \caption {List OF Notation} \label{table:1a}
-% \begin{center}
-% \scalebox{0.8}{
-%  \begin{tabular}{||c | c ||}
-%  \hline
-%Notation & Description \\ [0.5ex]
-%  \hline\hline
-%  $S$ & Total number of slices\\
-%  \hline
-%  $S1$ & Number of eMBB slices  \\
-%  \hline
-% $S2$ & Number of URLLC slices  \\
-%  \hline
-%  $S3$ & Number of mMTC slices \\
-%  \hline
-%   $\bar{K}_s$ & pre-allocated PRB to each slice \\
-%  \hline
-%  PRB &  Physical Resource Block \\
-%  \hline
-%  eMBB & enhanced Mobile BroadBand \\
-%  \hline
-%  URLLC  & Ultra-Reliable Low Latency Communication \\
-%   \hline
-%  mMTC &  massive Machine-To-Machine Communications \\
-%  \hline
-%  O-RU &  O-RAN Radio Unit \\
-%  \hline
-%   O-DU &  O-RAN Distributed Unit \\ [.5ex]
-%  \hline
-%   O-CU &  O-RAN Central Unit \\ [.5ex]
-%  \hline
-%  UPF &  User Plane Function \\ [.5ex]
-%  \hline
-% \end{tabular}}
-% \end{center}
-% \end{table}
+\vspace*{-.75em}
 \section{System Model}\label{systemmodel}
@@
 In this section, we provide a brief study on the problem of PRB scheduling which can be completed in two steps to eliminate the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
-For this, firstly, we should assign the PRBs to the slices.
+Firstly, we should assign the PRBs to the slices.
 Secondly, we assign PRBs of slices to UEs, find the optimal number of VNFs for each slice, allocate power of UEs, and assign O-RU to UEs, which uses the proposed Algorithm \ref{proAlg}.
@@
 \textit{Greedy Algorithm Assignment (GAA):}
-The problem can be reformulated as follow
+\textcolor{MidnightBlue}{Following is a reformulated version of the problem.}
 \begin{subequations}\label{problem2}
@@
 So the complexity of the main problem \eqref{problem} is $O(T_{conv} \times \mathfrak{N} \times K \times (S\log(S)+R\mathfrak{N}))$.
-\subsubsection{Convergence Analysis}
- \textcolor{MidnightBlue}{Due to limited resources in power, the number of PRBs, and the number of activated VNFs and restrictions based on this limitation on power, energy, fronthaul capacity, etc., the objective function that is the summation of the achievable rates of UEs cannot exceed its optimal value and become infinite.
-Therefore, we can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function concerning the number of iterations.
-Consequently, it converges to the optimum value.}
-% \cite{gholipoor2020resource}.
-Consider the aggregate throughput as $\mathcal{T(\bold{P},\bold{E},\bold{G})} =\sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}}$.
-In the first step of the iteration i of the algorithm \ref{alg2} (IABV), we have $\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1})$.
-In this step, optimal power and PRB allocation are obtained for the fixed O-RU association, so we have
-$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
-In the second step of the iteration i, the optimal O-RU association is achieved to maximize the aggregate throughput. So we have this inequality
-$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
-As a result, we have
-$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
-Hence, in each step of the iteration, the aggregate throughput increased.
-Note that $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*})$ is the achieved aggregate throughput
-for all the feasible resource allocation solutions of $\{\bold{P},\bold{E},\bold{G}\}$.
-So, $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i})$ and thus in each iteration, the aggregate throughput can not be larger than the optimal solution.
-So the the aggregate throughput is ascending function concerning the number of iterations and it will converge to the sub-optimal solution.
-In addition, if we assume that the interference is set to be zero ${I}_{r,u_{(s,i)}}^{k}=0$,
-and we suppose that each UE has the maximum power $p_{r,u_{(s,i)}}^k = P_{s}^{max}$,
-and we consider that all PRB is assigned to all UE $e_{r,u_{(s,i)}}^k = 1 \forall s,\forall i$
-and each UE is assigned to the nearest O-RU with the best channel quality. So, the solution of this allocation, is the upper bound
-for the aggregate throughput. Thus,
-we can guarantee the convergence of our iterative algorithm since the objective function $\mathcal{T}$ is the ascending function concerning the number of iterations
- and it has the upper bound.
  \begin{algorithm}
@@
 \end{algorithm}
+\subsubsection{Convergence Analysis}
+ \textcolor{MidnightBlue}{Due to limited resources in power, the number of PRBs, and the number of activated VNFs and restrictions based on this limitation on power, energy, fronthaul capacity, etc., the objective function that is the summation of the achievable rates of UEs cannot exceed its optimal value and become infinite.
+Therefore, we can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function in the non-optimal set of variables concerning the number of iterations.
+Consequently, it converges to the optimum global value.
+Meanwhile, if the objective function is the non-monotonically ascending function, we can prove the local convergence of the algorithm.
+}
+% \cite{gholipoor2020resource}.
+Consider the aggregate throughput as $\mathcal{T(\bold{P},\bold{E},\bold{G})} =\sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}}$.
+In the first step of the iteration i of the algorithm \ref{alg2} (IABV), we have $\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1})$.
+In this step, optimal power and PRB allocation are obtained for the fixed O-RU association, so we have
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
+In the second step of the iteration i, the optimal O-RU association is achieved to maximize the aggregate throughput. So we have this inequality
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
+As a result, we have
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
+Hence, in each step of the iteration, the aggregate throughput increased.
+Note that $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*})$ is the achieved aggregate throughput
+for all the feasible resource allocation solutions of $\{\bold{P},\bold{E},\bold{G}\}$.
+So, $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i})$ and thus in each iteration, the aggregate throughput can not be larger than the optimal solution.
+So the the aggregate throughput is ascending function concerning the number of iterations and it will converge to the sub-optimal solution.
+In addition, if we assume that the interference is set to be zero ${I}_{r,u_{(s,i)}}^{k}=0$,
+and we suppose that each UE has the maximum power $p_{r,u_{(s,i)}}^k = P_{s}^{max}$,
+and we consider that all PRB is assigned to all UE $e_{r,u_{(s,i)}}^k = 1 \forall s,\forall i$
+and each UE is assigned to the nearest O-RU with the best channel quality. So, the solution of this allocation, is the upper bound
+for the aggregate throughput. Thus,
+we can guarantee the convergence of our iterative algorithm since the objective function $\mathcal{T}$ is the ascending function concerning the number of iterations
+ and it has the upper bound.
+
 %\vspace*{-2em}
@@
   \centering
-    \includegraphics[scale = 0.33]{cell.pdf}
+    \includegraphics[scale = 0.30]{cell.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
@@
 
-\begin{table}[H]
+Finding a feasible initial value is almost tricky. We use a fast method discussed in \ref{fr} to overcome this challenge. 
+Two different methods are used to compare the performance of the proposed method (IABV) and show the optimality of our approach.
+The first one is a baseline scheme, which uses random PRB allocation.
+Therefore, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
+Also, the association of O-RU is carried out based on distance.
+It means that each UE is assigned to the nearest O-RU.
+The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
+After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma \eqref{lemma1}.
+\begin{table}%[H]
  \caption {Simulation Parameters} \label{table:1a}
@@
  \end{tabular}}
+ \vspace*{-1.em}
  \end{center}
  \end{table}
-Finding a feasible initial value is almost tricky. We use a fast method discussed in \ref{fr} to overcome this challenge. 
-Two different methods are used to compare the performance of the proposed method (IABV) and show the optimality of our approach.
-The first one is a baseline scheme, which uses random PRB allocation.
-Therefore, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
-Also, the association of O-RU is carried out based on distance.
-It means that each UE is assigned to the nearest O-RU.
-The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
-After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma \eqref{lemma1}.
-
 For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic} and named it the dynamic resource allocation scheme (DR scheme).
@@
 \subsection{Feasible Region}\label{fr}
-Applying the correct initial point to make the system feasible and converge is a significant step in our work.
-To solve this problem, we investigated the non-converging and converging simulation for models with fixed initial parameters and random channel gains of UEs.
+Applying the correct initial point is crucial in making the system feasible and convergent.
+Therefore, we investigated the non-converging and converging simulation for models with fixed initial parameters and UE random channel gains.
 We experimentally found that in non-converged simulations, there are UEs at the edge of the boundaries or far away from the O-RU and have a weak channel gain.
@@
 		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.41]{fig/Arate_ue1_1n.eps} &
-			\includegraphics[scale = 0.41]{fig/vnfNum1n.eps} &
-			\includegraphics[scale = 0.41]{fig/RatePower1n.eps} \\
+			\includegraphics[scale = 0.4]{fig/Arate_ue1_1n.eps} &
+			\includegraphics[scale = 0.4]{fig/vnfNum1n.eps} &
+			\includegraphics[scale = 0.4]{fig/RatePower1n.eps} \\
 			\scriptsize Fig.
@@
 		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.41]{fig/delay_newn.eps} &
-			\includegraphics[scale = 0.41]{fig/delay1_newn.eps} &
-			\includegraphics[scale = 0.41]{fig/AmmTCpowern.eps} \\
+			\includegraphics[scale = 0.4]{fig/delay_newn.eps} &
+			\includegraphics[scale = 0.4]{fig/delay1_newn.eps} &
+			\includegraphics[scale = 0.4]{fig/AmmTCpowern.eps} \\
 			\scriptsize Fig.
@@
 		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.41]{fig/priorityLastn.eps} &
-			\includegraphics[scale = 0.41]{fig/itern.eps} &
-			\includegraphics[scale = 0.41]{fig/iterD.eps} \\
+			\includegraphics[scale = 0.4]{fig/priorityLastn.eps} &
+			\includegraphics[scale = 0.4]{fig/itern.eps} &
+			\includegraphics[scale = 0.4]{fig/iterD.eps} \\
 			\scriptsize Fig.
@@
 		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.42]{fig/optimal1n.eps} &
-			\includegraphics[scale = 0.42]{fig/interF_newn.eps} &
-			\includegraphics[scale = 0.42]{fig/FAn.eps} \\
+			\includegraphics[scale = 0.4]{fig/optimal1n.eps} &
+			\includegraphics[scale = 0.4]{fig/interF_newn.eps} &
+			\includegraphics[scale = 0.4]{fig/FAn.eps} \\
 			\scriptsize Fig. 12~~Aggregate throughput vs. number of UEs   & \scriptsize Fig. 13~~Aggregate throughput vs. maximum interference   & \scriptsize Fig. 14~~Aggregate throughput vs. number of UEs
@@
 
-Table III shows the execution time versus the number of UEs for one service. We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
- As the number of UEs in the system increases, the execution time increases polynomially.
-
-\begin{table}[H]
+\textcolor{MidnightBlue}{Table III shows the execution time versus the number of UEs for one service for the three methods.
+We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk).
+ As the number of UEs in the system increases, the execution time increases polynomially for all three algorithms.
+Since the baseline scheme is a simpler algorithm, with random PRB allocation and O-RU association based on distance, the execution time is less than the two other algorithms.
+Power and PRB are allocated in the DR scheme, but O-RUs are associated based on distance.
+Therefore the execution time is less than the proposed algorithm.}
+\begin{table}%[H]
  \caption {Execution Time vs. Number of UEs} 
 \begin{center}
- \scalebox{0.9}{
-\begin{tabular}{|| l || l| l |l |l |l ||}
+ \scalebox{0.75}{
+\begin{tabular}{ |l|l|l|l| }
+%\hline
+%\multicolumn{3}{|c|}{Country List} \\
 \hline
-Number of UEs & 5 & 10 & 15 & 20 & 25 \\ 
-Execution Time (usec)& 12.156 & 19.156 &  29.140 & 44.573 & 67.912 \\
+\multirow{2}{*}{Number of UEs } &\multicolumn{3}{|c|}{Execution Time (usec)} \\
+\cline{2-4}
+{} &Proposed method & DR scheme & Baseline scheme \\
+\hline
+5 & 12.156 &8.9546 &6.6436\\
+10 & 19.156   & 12.3112& 8.7870\\
+15 &29.140 & 17.4778 &9.5648 \\
+20    &44.573 &  24.5342 &14.8334 \\
+25 & 67.912  & 36.7926 &21.5510 \\
 \hline
 \end{tabular}}
+\vspace*{-1.6em}
 \end{center}
 \end{table}
-
 %\begin{figure}[H]
@@
 %\end{figure}
-\vspace*{-1.8em}
+\vspace*{-1.4em}
 \section{Conclusion}\label{conc}
 In this paper, we modeled the downlink of the O-RAN system using isolated network slicing for different 5G services, i.e., eMBB, mMTC, and URLLC.
-We aim to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput.
-The limited fronthaul capacity and the mean end-to-end delay for each service are considered.
+Our goal is to maximize aggregate throughput by activating VNFs in each service, associating RUs, allocating power, and PRBs.
+The limited fronthaul capacity and the mean delay for each service are considered.
 The problem is mixed-integer non-linear programming that is solved by a two-step iterative algorithm.
@@
 Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than DR scheme and the baseline scheme.
-\vspace*{-0.9em}
+\vspace*{-1.1em}
 \bibliographystyle{IEEEtran}

### 2022-09-05 Journal1/Response4/Response.tex
add the revised

@@
 \maketitle
-We would like to thank the editor and reviewers for their constructive comments on our manuscript.
-They have been beneficial in revising this paper, and we have improved the technical content and presentation quality through their assistance.
-We greatly appreciate their generous help.
-We also aim for a more concise manuscript.
-We hope that the modifications we have made to the manuscript and the responses we have provided herein will alleviate the reviewers' concerns.
+We would like to thank the editor and reviewers for their valuable comments on our manuscript. We have improved this paper's technical content and presentation quality through their assistance. 
+We hope that the modifications undergone by the manuscript and the responses we have provided herein alleviate the reviewers' concerns.
 Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
@@
 \noindent \textbf{Response:\\}
-It is our pleasure to thank the Editor for his constructive comments on how to improve our paper.
-Thanks to the comments, we were able to make improvements to our paper and eliminate problems.
-In response to the reviewers and Editor's comments, we are confident we addressed their suggestions.
-We have updated the manuscript and uploaded our point-by-point response to the reviewers' comments (below).
+Thank you for the constructive comments, which allowed us to improve our paper further. We are confident we addressed all the suggestions.
+Next, you can find our point-by-point response to the reviewers' comments and how the manuscript has been modified accordingly.
 
@@
 \noindent \textbf{Response:\\}
-It is a pleasure to have the reviewer read this manuscript; we appreciate his/her attention, which helps us enhance our paper.
+Thank you very much for your appreciation of our work and the valuable feedback we received from you.
 
@@
 \noindent \textbf{Response:\\}
-Throughout this process, we thank the reviewer for taking the time to read the manuscript carefully, commenting thoughtfully, and offering suggestions that made the manuscript stronger and more valuable.
+We thank the reviewer for taking the time to read the manuscript carefully, commenting thoroughly and offering suggestions that have made the manuscript stronger and more valuable. 
 In this response, we hope to alleviate the reviewer's concerns.
@@
 \noindent \textbf{Response:\\}
-Based on this comment, we have read several TNSM papers, rewritten the introduction's paragraph, removed the additional parts, and tried to enhance it as much as possible.
-We also shortened the introduction.
-We added an organization subsection and revised the whole of the introduction.
-Moreover, we modified the related literature, removed additional parts, and added more related literature reviews.
-Additionally, we modified the background section, removed some sentences from the introduction, and added them to this section.
-Also, we removed some additional parts from this section.
+Based on this comment, we have read several TNSM papers and reorganized the Introduction section accordingly.
+As a result, we shortened the Introduction section.
+Specifically, we revised it thoroughly and included an additional subsection about the organization of our paper.
+We trimmed extra parts and added more related literature reviews in the related literature.
+Additionally, we modified the background section by including some sentences/ideas that were originally in the Introduction section and reallocating others.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-We have rewritten the introduction and literature review section, removed the additional part, and put it in the correct sections.
+We have rewritten the introduction and literature review section, and reallocated some parts to more appropriate sections.
 We have shortened long paragraphs and sentences in this paper in order to make it easier to read.
@@
 Based on this comment, we added the results for the baseline scheme and the DR methods in Table  III in Section VII-C.
-Table I shows the execution time versus the number of UEs for one service for the three methods.
-We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk).
+Table III shows the execution time given a number of UEs for one service for the three methods.
+We run our simulation on the system with configuration (RAM = 8 GB, CPU = Core i5, SSD Hard Disk).
  As the number of UEs in the system increases, the execution time increases polynomially for all three algorithms.
@@
 \begin{table}[H]
- \caption {Execution Time vs. Number of UEs} 
+ \caption*{Table III: Execution Time vs. Number of UEs} 
 \begin{center}
@@
 10 & 19.156   & 12.3112& 8.7870\\
-15 &29.140 & 17.4778 &9.5648 \\
-20    &44.573 &  24.5342 &14.8334 \\
-25 & 67.912  & 36.7926 &21.5510 \\
+15 &29.140 & 15.4778 &9.5648 \\
+20    &44.573 &  21.5342 &14.8334 \\
+25 & 67.912  & 30.7926 &21.5510 \\
 \hline
@@
 
-Due to limited resources in power, the number of PRBs, and the number of activated VNFs and restrictions based on this limitation on power, energy, fronthaul capacity, etc., the objective function that is the summation of the achievable rates of UEs cannot exceed its optimal value and become infinite.
-Therefore, we can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function in the non-optimal set of variables concerning the number of iterations.
-Consequently, it converges to the optimum global value.
-Meanwhile, if the objective function is the non-monotonically ascending function, we can prove the local convergence of the algorithm.
+Due to limited system resources, we have limits on VNFs' power, UE or O-RU power, fronthaul capacity, etc.
+As a result, the objective function, which is the aggregate throughput, cannot exceed its optimal value and become infinite.
+Therefore, if the aggregate throughput is infinite and increases without limit, the resources must also be unlimited.
+Hence, the system has an optimal solution: its maximum aggregate throughput in the feasible region.
+Consequently, we can guarantee the convergence of the iterative algorithm if the objective function is the ascending function concerning the number of iterations.
+Thus, it will converge to its optimum value if it is a strictly ascending function and to its local optimum if it is a non-monotonically ascending function.
 
@@
 We agree with the reviewer that we only talked about the convergence of the proposed algorithm, and we do not talk about the global and local convergence.
-Based on our proof, the algorithm is converged to the local convergence.
-But we do not provide global convergence of our algorithm.
 
@@
 Moreover, in Fig. 12, we numerically demonstrate our algorithm's global convergence in low interference.
- However, we can not talk about the global convergence of the algorithm in other states.
-We still will not prove that our algorithm converged to global convergence.
-However, we verified the local convergence of our algorithm in any condition.
+Nevertheless, although we didn't demonstrate the unconditional global convergence of our algorithm, we did verify its unconditional local convergence. 
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 \noindent \textbf{Response:\\}
-It is our pleasure to thank the reviewer for this comment.
-We agree with the reviewer that the tables and algorithms need to be moved.
-As a result, all these mistakes were corrected, and the wrong ones were moved to the top.
+It is our pleasure to thank the reviewer for this comment. We agree with the reviewer that the
+tables and algorithms need to be moved. As a result, all these mistakes were corrected.
 

### 2022-09-05 Journal1/paper5-oldTNSM/pr.tex
add the revised

@@
 \subsubsection{Convergence Analysis}
- \textcolor{MidnightBlue}{Due to limited resources in power, the number of PRBs, and the number of activated VNFs and restrictions based on this limitation on power, energy, fronthaul capacity, etc., the objective function that is the summation of the achievable rates of UEs cannot exceed its optimal value and become infinite.
-Therefore, we can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function in the non-optimal set of variables concerning the number of iterations.
-Consequently, it converges to the optimum global value.
-Meanwhile, if the objective function is the non-monotonically ascending function, we can prove the local convergence of the algorithm.
+ \textcolor{MidnightBlue}{Due to limited system resources, we have limits on VNFs' power, UE or O-RU power, fronthaul capacity, etc.
+As a result, the objective function, which is the aggregate throughput, cannot exceed its optimal value and become infinite.
+Therefore, if the aggregate throughput is infinite and increases without limit, the resources must also be unlimited.
+Hence, the system has an optimal solution: its maximum aggregate throughput in the feasible region.
+Consequently, we can guarantee the convergence of the iterative algorithm if the objective function is the ascending function concerning the number of iterations.
+Thus, it will converge to its optimum value if it is a strictly ascending function and to its local optimum if it is a non-monotonically ascending function.
 }
@@
 
-\textcolor{MidnightBlue}{Table III shows the execution time versus the number of UEs for one service for the three methods.
-We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk).
+\textcolor{MidnightBlue}{Table III shows the execution time given a number of UEs for one service for the three methods.
+We run our simulation on the system with configuration (RAM = 8 GB, CPU = Core i5, SSD Hard Disk).
  As the number of UEs in the system increases, the execution time increases polynomially for all three algorithms.

### 2022-09-06 Journal1/Response4/Response.tex
add last version of tnsm

@@
 Additionally, we modified the background section by including some sentences/ideas that were originally in the Introduction section and reallocating others.
+Below we report the Introduction section.
+
+\section{Introduction}
+%\subsection{State Of The Arts}
+Network slicing is a key technology in 5G wireless systems.
+Specifically, it isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various services [1]–[3].
+
+There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
+Each service is assigned to a network slice depending on its corresponding quality of service (QoS) requirements.
+For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming.
+Meanwhile, the URLLC service provides ultra-reliable and low-latency connectivity, e.g., for autonomous vehicles, Tactile Internet, and remote surgeries.
+Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads [4]–[6].
+%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}
+
+%Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
+In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig.
+\ref{fig:c11}, is introduced to deal with these issues.
+
+%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
+We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
+%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
+%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
+The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence
+
+%A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
+Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
+%As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.
+
+\subsection{Motivation}
+The optimal resource allocation for the 5G systems is crucial to reducing costs and improving user equipment (UE).
+Significant challenges face these systems, including interference alignment, limited capacity of the fronthaul links, energy restrictions on virtual machines (VMs), etc [2], [7], [8].
+
+Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering a single service's power, data rate, and delay limitations.
+%Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
+In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig.
+\ref{fig:c11}, is introduced to deal with these issues.
+Unfortunately, the existing radio access networks (RANs) currently lack adequate flexibility and openness to handle these simultaneous service demands. 
+Hence, a new RAN paradigm, called open RAN (O-RAN) architecture, has emerged.
+% as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
+Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
+Therefore, O-RAN can simultaneously support multiple services at a lower cost by being flexible, layered, and modular.  
+One of the fundamental problems lies in balancing services with different QoS, resource requirements, and priorities in O-RAN architecture [1], [9]–[11]. 
+%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
+%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
+%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}
+
+The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
+% Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
+
+\subsection{Main Contributions}
+This paper studies the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G services.
+We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
+%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
+%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
+ The main contributions of this paper are summarized as follows:
+\begin{itemize}
+\item We examine the problem of baseband resource allocation, such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN architecture.
+The three types of 5G service classes, i.e., eMBB, URLLC, and mMTC, are considered in this system.
+We take into account their corresponding QoS requirements and service priorities.
+\item We propose a two-step resource management algorithm for solving the optimization problem.
+In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs.
+Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation.
+In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
+\item We analyze the complexity of the proposed algorithms and demonstrate their convergence.
+Additionally, we analyze the feasibility region of the problem and introduce a fast algorithm to check it numerically.
+\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
+Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
+\end{itemize}
+
+\subsection{Organization}
+%Table \ref{table:11a} lists the acronyms used throughout this paper, which
+This paper is organized as follows.
+Relevant literature related to our work is discussed in Section~II, while Section~III briefly overviews the O-RAN architecture.
+The system model and the problem formulation are described in Section IV and Section V, respectively.
+The details of our proposed resource management algorithm are introduced in Section VI.
+In Section VII, numerical results are provided to evaluate the performance of the proposed algorithm.
+Finally, Section VIII concludes the paper.
+For clarity, Table I lists the main acronyms used throughout the paper.
 \begin{longtable}{|p{0.975\textwidth}|}
@@
 20    &44.573 &  21.5342 &14.8334 \\
-25 & 67.912  & 30.7926 &21.5510 \\
+25 & 67.912  & 32.7926 &21.5510 \\
 \hline
@@
 \noindent \textbf{Response:\\}
-We thank the reviewer for reporting this ambiguity. We revised this vague statement and added it to section VI-C-2. Below we reported the revised sentences.
+We thank the reviewer for reporting this ambiguity. We revised this vague statement and added it to section VI-C-2.
+ Below we reported the revised sentences.
 
@@
 Hence, the system has an optimal solution: its maximum aggregate throughput in the feasible region.
-Consequently, we can guarantee the convergence of the iterative algorithm if the objective function is the ascending function concerning the number of iterations.
+
+Consequently, we can guarantee the convergence of the iterative algorithm if the objective function is the ascending function concerning the number of iterations and has an upper bound.
 Thus, it will converge to its optimum value if it is a strictly ascending function and to its local optimum if it is a non-monotonically ascending function.
+
+% \cite{gholipoor2020resource}.
+Consider the aggregate throughput as $\mathcal{T(\bold{P},\bold{E},\bold{G})} =\sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}}$.
+In the first step of the iteration i of the algorithm \ref{alg2} (IABV), we have $\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1})$.
+In this step, optimal power and PRB allocation are obtained for the fixed O-RU association, so we have
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
+In the second step of the iteration i, the optimal O-RU association is achieved to maximize the aggregate throughput. So we have this inequality
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
+As a result, we have
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
+Hence, in each step of the iteration, the aggregate throughput increased.
+Note that $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*})$ is the achieved aggregate throughput
+for all the feasible resource allocation solutions of $\{\bold{P},\bold{E},\bold{G}\}$.
+So, $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i})$ and thus in each iteration, the aggregate throughput can not be larger than the optimal solution.
+
+In addition, if we assume that the interference is set to be zero ${I}_{r,u_{(s,i)}}^{k}=0$,
+and we suppose that each UE has the maximum power $p_{r,u_{(s,i)}}^k = P_{s}^{max}$,
+and we consider that all PRB is assigned to all UE $e_{r,u_{(s,i)}}^k = 1 \forall s,\forall i$
+and each UE is assigned to the nearest O-RU with the best channel quality. So, the solution of this allocation, is the upper bound
+for the aggregate throughput.
+
+Thus,
+we can guarantee the local convergence of our iterative algorithm since the objective function $\mathcal{T}$ is the ascending function concerning the number of iterations
+ and it has the upper bound which is not infinite.
 
@@
 
-In addition, to extend our solution to the global optimum, we must prove that the algorithm monotonically increases in the non-optimal set of solutions.
+Meanwhile, Zangwill's global convergence theory of iterative algorithms is a standard theory for providing the global convergence of an iterative algorithm.
+We can use this theory in future extention of our work to prove our algorithm in a standard way, which is not straightforward in this paper.
 
- Moreover, in the low interference system, in which the PRB and VNF assignment is obtained straightforward, and the whole problem of the first step is about power allocation, in the first step of our algorithm that the optimal power and PRB allocation are obtained for the fixed O-RU association; we have
+Also, we added a short description of extending local convergence to the global convergence in the low interference system with low number of UEs.
+We added it in the Section VI-2 and below we reported it.
+
+In addition, to extend our solution to the global optimum, we must prove that the algorithm monotonically increases in the non-optimal set of solutions and is Lipschitz monotone contraction mapping.
+Here, we briefly discussed our algorithm's global convergence for a low interference system.
+
+In the low interference system, the PRB and VNF assignment is obtained straightforwardly, and the first step's problem is power allocation.
+In the first step of our algorithm with the fixed O-RU association, we have
 $\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$ (strictly increase). 
- Since the PRB assignment is straightforward and we used the KKT condition for power allocation, the problem is a convex optimization.
-The KKT condition problem has a global convergence and achieves the optimal solution in convex optimization.
-Accordingly, the algorithm monotonically increases to reach its optimum solution.
-However, in the second step of the algorithm, we can prove that the algorithm is increased, but we can not talk about monotonically increases.
+Because in this step, the problem is reformulated to the power allocation, and the objective function is convex, and the convex functions are Lipschitz monotone contractions. 
+However, in the second step of the algorithm, we can show as before that the algorithm is increased, but we can not talk about monotonically increases.
 Hence we have
 $\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
-Therefore, we have 
+Nevertheless, the objective function is still Lipschitz monotone mapping. 
+Accordingly, we have 
 $\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
+Therefore the objective function is the strictly ascending
+function concerning the number of iterations and has an
+upper bound.
 Consequently, the algorithm converges to the 
 global optimum solution in low interference.
-
-Meanwhile, Zangwill's global convergence theory of iterative algorithms is a standard theory for providing the global convergence of an iterative algorithm.
-We need to use this theory to prove our algorithm in a standard way which is not straightforward in this paper.
 
@@
 We agree with the reviewer that we must clarify "what" the algorithm converges. 
-As mentioned in the previous question, we prove that the algorithm can converge to a global convergence in low interference.
-Moreover, in Fig. 12, we numerically demonstrate our algorithm's global convergence in low interference.
+In Section VI-C-2, we revised the convergence proved of the system and described that the algorithm converged to the local convergence.
+Moreover, as mentioned in the previous question, we briefly show that the algorithm can converge to a global convergence in the low interference system.
+Moreover, in Fig. 12, we numerically demonstrate our algorithm's global convergence in low interference and describe it in Section VII-C.
 Nevertheless, although we didn't demonstrate the unconditional global convergence of our algorithm, we did verify its unconditional local convergence.
+
 \begin{longtable}{|p{0.975\textwidth}|}

### 2022-09-06 Journal1/paper5-lastTNSM/pr.tex
add last version of tnsm

--- 2022-09-05 Journal1/paper5-oldTNSM/pr.tex
@@
 Network slicing is a key technology in 5G wireless systems.
-\textcolor{MidnightBlue}{Specifically, it isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various services.} \cite{shen2020ai,setayesh2020joint,popovski20185g}.
+\textcolor{MidnightBlue}{Specifically, it isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various services} \cite{shen2020ai,setayesh2020joint,popovski20185g}.
 
@@
 \textcolor{MidnightBlue}{The optimal resource allocation for the 5G systems is crucial to reducing costs and improving user equipment (UE).
-Significant challenges face these systems, including interference alignment, limited capacity of the fronthaul links, energy restrictions on virtual machines (VMs), etc }\cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.
+Significant challenges face these systems, including interference alignment, limited capacity of the fronthaul links, energy restrictions on virtual machines (VMs), etc.
+}\cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.
 
@@
 % as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
-Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.}
+Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
 Therefore, O-RAN can simultaneously support multiple services at a lower cost by being flexible, layered, and modular.  
-One of the fundamental problems lies in balancing services with different QoS, resource requirements, and priorities in O-RAN architecture.}
+One of the fundamental problems lies in balancing services with different QoS, resource requirements, and priorities in O-RAN architecture}
  \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.  
@@
 Therefore, if the aggregate throughput is infinite and increases without limit, the resources must also be unlimited.
-Hence, the system has an optimal solution: its maximum aggregate throughput in the feasible region.
-Consequently, we can guarantee the convergence of the iterative algorithm if the objective function is the ascending function concerning the number of iterations.
+Hence, the system has an optimal solution: its maximum aggregate throughput in the feasible region.}
+
+ \textcolor{MidnightBlue}{Consequently, we can guarantee the convergence of the iterative algorithm if the objective function is the ascending function concerning the number of iterations and has an upper bound.
 Thus, it will converge to its optimum value if it is a strictly ascending function and to its local optimum if it is a non-monotonically ascending function.
@@
 % \cite{gholipoor2020resource}.
+
 Consider the aggregate throughput as $\mathcal{T(\bold{P},\bold{E},\bold{G})} =\sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}}$.
@@
 So, $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i})$ and thus in each iteration, the aggregate throughput can not be larger than the optimal solution.
-So the the aggregate throughput is ascending function concerning the number of iterations and it will converge to the sub-optimal solution.
+
 In addition, if we assume that the interference is set to be zero ${I}_{r,u_{(s,i)}}^{k}=0$,
@@
 and each UE is assigned to the nearest O-RU with the best channel quality. So, the solution of this allocation, is the upper bound
-for the aggregate throughput. Thus,
-we can guarantee the convergence of our iterative algorithm since the objective function $\mathcal{T}$ is the ascending function concerning the number of iterations
- and it has the upper bound.
-
+for the aggregate throughput.
+
+\textcolor{MidnightBlue}{ Thus,
+we can guarantee the local convergence of our iterative algorithm since the objective function $\mathcal{T}$ is the ascending function concerning the number of iterations
+ and it has the upper bound which is not infinite.}
+
+ \textcolor{MidnightBlue}{In addition, to extend our solution to the global optimum, we must prove that the algorithm monotonically increases in the non-optimal set of solutions and is Lipschitz monotone contraction mapping.
+Here, we briefly discussed our algorithm's global convergence for a low interference system.}
+
+  \textcolor{MidnightBlue}{ In the low interference system, the PRB and VNF assignment is obtained straightforwardly, and the first step's problem is power allocation.
+In the first step of our algorithm with the fixed O-RU association, we have
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$ (strictly increase). 
+Because in this step, the problem is reformulated to the power allocation, and the objective function is convex, and the convex functions are Lipschitz monotone contractions. 
+However, in the second step of the algorithm, we can show as before that the algorithm is increased, but we can not talk about monotonically increases.
+Hence we have
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
+Nevertheless, the objective function is still Lipschitz monotone mapping. 
+Accordingly, we have 
+$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
+Therefore the objective function is the strictly ascending
+function concerning the number of iterations and has an
+upper bound.
+Consequently, the algorithm converges to the 
+global optimum solution in low interference.}
 %\vspace*{-2em}
@@
 Our solution is close to the optimal value in a small number of UEs.
+\textcolor{MidnightBlue}{Therefore, this figure numerically demonstrates that the proposed algorithm converges to the global optimal in low interference.}
 

### 2022-09-08 Code_journal1/paperTNSM/pr.tex
last version of paper 1

--- 2022-09-06 Journal1/paper5-lastTNSM/pr.tex
@@
 \documentclass[lettersize,journal]{IEEEtran}
-\normalsize
+%\normalsize
 \IEEEoverridecommandlockouts
@@
 
-\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
+\title{Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
 }
@@
 \end{IEEEkeywords}
+%
+\vspace{-3mm}
 \section{Introduction}
+\vspace{-1mm}
 %\subsection{State Of The Arts}
 Network slicing is a key technology in 5G wireless systems.
-\textcolor{MidnightBlue}{Specifically, it isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various services} \cite{shen2020ai,setayesh2020joint,popovski20185g}.
+Specifically, it isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various services\cite{shen2020ai,setayesh2020joint,popovski20185g}.
 
 There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-\textcolor{MidnightBlue}{Each service is assigned to a network slice depending on its corresponding quality of service (QoS) requirements.}
+Each service is assigned to a network slice depending on its corresponding quality of service (QoS) requirements.
 For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming.
-\textcolor{MidnightBlue}{Meanwhile, the URLLC service provides ultra-reliable and low-latency connectivity, e.g., for autonomous vehicles, Tactile Internet, and remote surgeries.} Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
+Meanwhile, the URLLC service provides ultra-reliable and low-latency connectivity, e.g., for autonomous vehicles, Tactile Internet, and remote surgeries.
+Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
 %\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}
-
 %Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
@@
 \ref{fig:c11}, is introduced to deal with these issues.
-
 %This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
@@
 The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence
-
 %A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
@@
 %As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.
-
+\vspace{-3mm}
 \subsection{Motivation}
-\textcolor{MidnightBlue}{The optimal resource allocation for the 5G systems is crucial to reducing costs and improving user equipment (UE).
-Significant challenges face these systems, including interference alignment, limited capacity of the fronthaul links, energy restrictions on virtual machines (VMs), etc.
-}\cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.
-
-\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering a single service's power, data rate, and delay limitations.}
+\vspace{-1mm}
+The optimal resource allocation in 5G systems is crucial for reducing costs and improving the performance experienced by the user equipments (UEs).
+These systems face significant challenges, including interference alignment, limited capacity of the fronthaul links, energy restrictions on virtual machines (VMs), etc.\cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.
+
+Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering a single service's power, data rate, and delay limitations.
 %Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
@@
 \ref{fig:c11}, is introduced to deal with these issues.
-\textcolor{MidnightBlue}{Unfortunately, the existing radio access networks (RANs) currently lack adequate flexibility and openness to handle these simultaneous service demands. 
+Unfortunately, the existing radio access networks (RANs) currently lack adequate flexibility and openness to handle these simultaneous service demands. 
 Hence, a new RAN paradigm, called open RAN (O-RAN) architecture, has emerged.
@@
 Therefore, O-RAN can simultaneously support multiple services at a lower cost by being flexible, layered, and modular.  
-One of the fundamental problems lies in balancing services with different QoS, resource requirements, and priorities in O-RAN architecture}
+One of the fundamental problems lies in balancing services with different QoS, resource requirements, and priorities in O-RAN architecture
  \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.  
@@
 % Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
-
+\vspace{-3mm}
 \subsection{Main Contributions}
-\textcolor{MidnightBlue}{This paper studies the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G services.}
+\vspace{-1mm}
+This paper studies the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G services.
 We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
@@
 \begin{itemize}
-\item \textcolor{MidnightBlue}{We examine the problem of baseband resource allocation, such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN architecture.
-The three types of 5G service classes, i.e., eMBB, URLLC, and mMTC, are considered in this system.
-We take into account their corresponding QoS requirements and service priorities.}
+\item We examine the problem of baseband resource allocation, such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs, to maximize the weighted throughput of the O-RAN architecture.
+The three types of 5G service classes, i.e., eMBB, URLLC, and mMTC, together with their corresponding QoS requirements and service priorities, are considered.
 \item We propose a two-step resource management algorithm for solving the optimization problem.
@@
 In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
-\item \textcolor{MidnightBlue}{We analyze the complexity of the proposed algorithms and demonstrate their convergence.
-Additionally, we analyze the feasibility region of the problem and introduce a fast algorithm to check it numerically.}
+\item We analyze the complexity of the proposed algorithms and demonstrate their convergence.
+Additionally, we analyze the feasibility region of the problem and introduce a fast algorithm to check it numerically.
 \item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
@@
 \end{itemize}
-
+\vspace{-3mm}
 \subsection{Organization}
+\vspace{-1mm}
 %Table \ref{table:11a} lists the acronyms used throughout this paper, which
@@
  \end{table}
-
+\vspace{-3mm}
 % \vspace*{-3em}
 \section{Related Literature}\label{RL}
+\vspace{-1mm}
 The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
-\textcolor{MidnightBlue}{Two levels of dynamic network slicing in heterogeneous C-RAN (H-CRAN) are examined in \cite{lee2018dynamic}.
+Two levels of dynamic network slicing in heterogeneous C-RAN (H-CRAN) are examined in \cite{lee2018dynamic}.
 The higher level manages user acceptance control, RRH association, and the allocation of BBU capacity.
-Meanwhile, PRB and power are allocated at lower levels.}
+Meanwhile, PRB and power are allocated at lower levels.
 In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning.
 In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.
-\textcolor{MidnightBlue}{ In \cite{singh2022joint}, to provide 5G slicing services, the authors present a framework called O-RANFed that implements and optimizes federated learning tasks in O-RAN devices.}
-\textcolor{MidnightBlue}{ Moreover, The authors of \cite{zhang2022federated} propose a federated deep reinforcement learning algorithm to achieve network slicing in O-RAN.}
-
-\textcolor{MidnightBlue}{ Recent research has focused on multiplexing eMBB and URLLC services within a RAN.}
+In \cite{singh2022joint}, to provide 5G slicing services, the authors present a framework called O-RANFed that implements and optimizes federated learning tasks in O-RAN devices.
+Moreover, The authors of \cite{zhang2022federated} propose a federated deep reinforcement learning algorithm to achieve network slicing in O-RAN.
+
+Recent research has focused on multiplexing eMBB and URLLC services within a RAN.
 In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
@@
 
-\textcolor{MidnightBlue}{In \cite{SystemCostMinimization,guo2016exploiting}, VMs activation and beamforming allocation are discussed in C-RAN systems.
+In \cite{SystemCostMinimization,guo2016exploiting}, VMs activation and beamforming allocation are discussed in C-RAN systems.
 Paper \cite{SystemCostMinimization} minimizes energy cost with system delay, fronthaul capacity, and rate constraints.
-To guarantee UE delays, M/M/1 queueing theory is used for transmission and processing delays.}
+To guarantee UE delays, M/M/1 queueing theory is used for transmission and processing delays.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated.
@@
 %\vspace*{-1.8em}
+%\vspace{-3mm}
 \section{Background}\label{BG}
+\vspace{-1mm}
 \begin{figure}
@@
   \captionsetup{justification=centering}
-    \includegraphics[scale = 0.36]{finalDraw1.pdf}
+    \includegraphics[scale = 0.36]{fig/finalDraw1.pdf}
     %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
+    \vspace{-6mm}
   \caption{Network sliced O-RAN system}
   \label{fig:c11}
+  \vspace{-2mm}
 \end{figure}
@@
 O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
-\textcolor{MidnightBlue}{By virtualizing RANs, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to their networks more quickly.} The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
+By virtualizing RANs, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to their networks more quickly.
+The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
 Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
 Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
- \textcolor{MidnightBlue}{Mostly non-real-time baseband processing occurs in the O-CU layer, while real-time baseband processing occurs in the O-DU layer.}
+Mostly non-real-time baseband processing occurs in the O-CU layer, while real-time baseband processing occurs in the O-DU layer.
 
@@
 
-\textcolor{MidnightBlue}{A key feature of the O-
+ key feature of the O-
 RAN architecture is that the hardware is disaggregated from
@@
 Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
-As a result, as shown in Fig \ref{fig:c11}, O-RAN components, such as UPF, O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs}
+As a result, as shown in Fig \ref{fig:c11}, O-RAN components, such as UPF, O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs
 \cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
-\vspace*{-.75em}
+%\vspace{-3mm}
 \section{System Model}\label{systemmodel}
+%\vspace{-1mm}
 We consider a downlink (DL) system, and an O-RAN architecture using RAN slicing as depicted in Fig. \ref{fig:c11}.
@@
 Moreover, we discuss the mean delay and the power of VNFs.
+\vspace{-3mm}
 \subsection{System Model}
+\vspace{-1mm}
 Assume, there are three service types: eMBB, URLLC, and mMTC, which support different applications.
@@
 Moreover, all O-RUs have access to all PRBs.
-
+\vspace{-3mm}
 %Coordinated multipoint (CoMP) system is considered here.
@@
 \subsection{Signal Model}
+\vspace{-1mm}
 Let $y_{u(s,i)} $ be the received signal of UE $i$ in the $s^{th}$ service such that
 \begin{equation}\label{eq2}
-y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}{x_Q}^k_{r,u(s,i)}+ z_{u(s,i)},
+y_{u(s,i)}\!\!=\!\!\sum_{r\!=\!1}^{R}\!\sum_{k\!=\!1}^{K_s} \!\boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r\! e^k_{r,u(s,i)}{x_Q}^k_{r,u(s,i)}\!\!+\!z_{u(s,i)},
 \end{equation}
 %\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
-where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$.
-${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}\sqrt{p^{k}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector, $z_{u(s,i)}\backsim \mathcal{CN}(0,BN_0)$ is the receive additive Gaussian noise and $BN_0$ is the noise power in a given bandwidth $B$.
+where ${x_Q}^k_{r,u(s,i)}\!=\!{x_P}^k_{r,u(s,i)}\!\!+\!
+\boldsymbol{q}_{r}$, ${x_P}^k_{r,u(s,i)}\!=\!
+\boldsymbol{w}^k_{r,u(s,i)}\!\sqrt{p^{k}_{r,u(s,i)}} x_{u(s,i)}$,  $ x_{u(s,i)}$ depicts the transmitted symbol vector, $z_{u(s,i)}\sim \mathcal{CN}(0,BN_0)$ is the receive additive Gaussian noise, and $BN_0$ is the noise power in a given bandwidth $B$.
 Here, ${x_P}$ denotes the precoded message before compression, while ${x_Q}$ illustrates the precoded message after compression.% as shown in Fig. \ref{fig:pq}.
-In addition, $\boldsymbol{q}_{r} \sim \backsim \mathcal{CN}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$ indicates the quantization Gaussian noise which comes from the signal compression in O-DU.
+In addition, $\boldsymbol{q}_{r} \sim  \mathcal{CN}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$ indicates the quantization Gaussian noise which comes from the signal compression in O-DU.
 Furthermore, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether O-RU $r$ serves the $i^{th}$ UE that is allocated to the $s^{th}$ slice or not.
@@
 &I_{r,u(s,i)}^{k} =\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}} + \nonumber\\
- &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
+ &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}}\!
+e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\!\!\sum_{\substack{r'=1 \\ r'\neq r}}^{R}\!|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
 \end{align}
@@
 $\Delta \boldsymbol{h}_{r,u(s,i)}\sim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$ indicates the estimating error vector with a Gaussian distribution and $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$
-\vspace*{-.8em}
+\vspace{-3mm}
 \subsection{Achievable Data Rate}
+\vspace{-1mm}
 The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as 
@@
 \begin{equation}
-\mathcal{R}_{r, u(s_1,i)} = \sum_{k=1}^{K} \mathcal{{R}}_{r,u(s_1,i)}^{k} e^k_{r,u(s_1,i)},
+\mathcal{R}_{r, u(s_1,i)} = \sum_{k=1}^{K} \mathcal{{R}}_{r,u(s_1,i)}^{k} e^k_{r,u(s_1,i)}
 \end{equation}
@@
 \begin{equation}\label{shortPacket}
- \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}.
+ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\mathfrak{C}_{u(s_j,i)}^{k}/N_{u(s_j,i)}^{k}}.
 \end{equation}
@@
 \begin{align}\label{cr}
-C_{r} &= \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},\nonumber\\
-C_{r} &= \log_2{\left(\frac{P_r}{ \sigma_{q}^2}\right)}.
+C_{r} &= \log_2{\left(1+ \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} / \sigma_{q}^2\right)}\nonumber\\
+&= \log_2{\left(P_r/\sigma_{q}^2\right)}.
 \end{align}
+\vspace{-4mm}
 \subsection{Mean Delay}
+\vspace{-1mm}
 In this part, the end-to-end mean delay for each service is obtained.
@@
 
-The following is a brief calculation of transmission delay to show that it does not affect also the optimization since its contribution to the total delay is negligible.
-In URLLC and mMTC, the mean packet size can be between 20 to 32 bytes; Also, the minimum data rate is assume to be $1 bps/Hz \times BW (180 KHz)$.
-So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{1 \times 180 \times 10^3} < 0.1 ms$.
-As a result, the $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$.
-For eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.
-
+The following is a brief calculation of the transmission delay to show that its contribution to the total delay is negligible and does not affect the optimization.
+In URLLC and mMTC, the mean packet size may be between 20 to 32 bytes, while the minimum data rate is assumed to be $1\ bps/Hz \times BW (180\ KHz)$.
+Thus, the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{1 \times 180 \times 10^3} < 0.1\ ms$, and $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$.
+For eMBB, the packet size may be 100 times larger and the delay does not exceed 0.6 ms.
 Therefore, in the following, we assume that the total delay is approximate to the processing delay ($T^{\text{\text{tot}}} \approx T^{\text{proc}}$).
@@
 \begin{align}
-T_{s}^{\text{DU}} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
-T_{s}^{\text{CU}} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
-T_{s}^{\text{UPF}} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
+T_{s}^{\text{DU}} &= 1/(\mu_s^d - \alpha_{s}/{M_s^{d}}),\\
+T_{s}^{\text{CU}} &= 1/(\mu_s^c - \alpha_{s}/{M_s^{c}}),\\
+T_{s}^{\text{UPF}} &= 1/(\mu_s^u - \alpha_{s}/{M_s^{u}}),
 \end{align}
@@
 $M_s^{u}$ represent the number of VNFs in O-DU, O-CU-UP and UPF, respectively.
-Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively. The arrival rate of each VNF in each layer for each slice
+Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service times of the O-DU, O-CU, and the UPF layers, respectively. The arrival rate of each VNF for each slice
 $s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.
@@
 \begin{equation}
- T_{u(s,i)}^{\text{RU}} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}}.
+ T_{u(s,i)}^{\text{RU}} = 1/(R_{u(s,i)} - \lambda_{u(s,i)}).
 \end{equation}
@@
 %Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
+\vspace{-3mm}
 \subsection{VNF Power}
+\vspace{-1mm}
 %{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.}
@@
 So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{\text{max}}$).
+\vspace{-3mm}
 \section{Problem Statement} \label{prS}
+\vspace{-1mm}
 Suppose the slice $s$ (which is assigned to service s) has a priority factor $\delta_s$ (based on the priority of its hosting service) where $\sum_{s=1}^S \delta_s =1$.
@@
 %{\color{red} explain why you introduce priority factor.}
-This paper aims to maximize the sum-rate of all UEs subject to QoS constraints as follows. %{\color{red} where did you define the objective? what is R bar?}
+This paper aims to maximize the sum-rate of all UEs subject to QoS constraints as follows %{\color{red} where did you define the objective? what is R bar?}
 \begin{subequations}\label{problem}
@@
 %& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
-& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{c17}  \\
+& \sum\nolimits_{\forall r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{c17}  \\
 & \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s, i , r, \label{c18-1} \\
@@
 \end{subequations}
-\noindent \noindent where $\bar{\mathcal{R}}_{u_{(s,i)}}$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
+Here, $\bar{\mathcal{R}}_{u_{(s,i)}}$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
 In addition, $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , i, r, k $, is the four-dimensional (4D) matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , i, r, k$ indicates the binary 4D matrix for the PRB association.
@@
 Also, \eqref{c18} ensures that each PRB can not be assigned to more than one UE associated with the same O-RU, \eqref{c19} indicates that the fixed cost of energy of VNFs in each slice does not exceed the threshold, while \eqref{c20} and \eqref{c21} constrain $\boldsymbol{E}$ and $\boldsymbol{G}$ to be binary matrices.
+\vspace{-3mm}
 \subsection{PRB Scheduling}\label{prb}
+\vspace{-1mm}
 In this section, we provide a brief study on the problem of PRB scheduling which can be completed in two steps to eliminate the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
@@
 Also, $K_s = (K_s^{\min}+K_s^{\text{max}})/2$ is the average number of required PRBs in slice s.
-Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
-The problem can be written as
+We aim to obtain the number of PRBs assigned to each slice $s$ ($\bar{K_s}$) by solving 
 \begin{subequations}\label{prob:prb}
@@
 \text{subject to} \quad  & \sum_s{\bar{K_s}} \leq K
- \label{prb0} \\
+ \label{prb0}, \\
 & K_s^{\min} \leq \bar{K_s}  \leq K_s^{\text{max}}  \quad \forall s \in S_1,\label{prb1} \\
@@
 \end{subequations}
-We used logarithms to assign PRBs to all slices to make them equally fair, since proportional fairness is achieved by maximizing the log utility function \cite{marabissi2019highly}.
+We use logarithms to assign PRBs to all slices to make them equally fair, since proportional fairness is achieved by maximizing the log utility function \cite{marabissi2019highly}.
 Equation \eqref{prb0} illustrates that the sum of PRBs of slices can not exceed the maximum number of PRBs ($K$).
@@
 By relaxing $\bar{K_s}$, the objective function and constraints become convex and can be solved using the Lagrangian function.
-
+\vspace{-3mm}
 \subsection{Slice Management}
+\vspace{-1mm}
 In this subsection, we will look at the life cycle of network slicing on a practical level. 
-The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages \cite{ETSI2};
+The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages \cite{ETSI2}:
 \begin{itemize}
@@
 %\vspace*{-1em}
+\vspace{-3mm}
 \section{Proposed Algorithm}\label{proAlg}
+\vspace{-1mm}
 In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
@@
 We repeat this procedure until the algorithm converges.
-
+\vspace{-3mm}
 \subsection{Sub-Problem 1}\label{sub1}
+\vspace{-1mm}
 Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
@@
 
-Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{P_{s}^{\text{max}}|{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$.
-we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
+Suppose $\hat{\rho}_{r,u(s,i)}^{k}\!\!=\!  P_{s}^{\text{max}}|{\bold{h}_{r,u(s,i)}^{H \: k}}\! \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2/(BN_0)$.
+We replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
 So, a lower bound for \eqref{eq11} is given that is a concave function.
@@
 \begin{alignat}{4}
-\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
-\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r},\\
- \hat{\zeta}_{u(s_j,i)}^{k} =& \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}),\\
- \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
+\bar{\mathcal{R}}_{u(s_j,i)}^{r} &\!\!=\!\!B\! \sum_{k=1}^{K_{\!s_j}}\!\!{e}_{u(s_j,i)}^{k} (\log_2({\!1\!+\! \bar{\rho}_{u(s_2,i)}^{k}})\!-\! \hat{\zeta}_{u(s_j,i)}^{k}\!),\!\\
+\bar{\mathcal{R}}_{u(s_j,i)} &\!\!= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r},\\
+ \hat{\zeta}_{u(s_j,i)}^{k} &\!\!= \log_2({e})Q^{-1}(\epsilon) \sqrt{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}/N_{u(s_j,i)}^{k}},\\
+ \hat{\mathfrak{C}}_{u(s_j,i)}^{k} &\!\!= 1 - 1/(1+\hat{\rho}_{u(s_j,i)}^{k})^2.
 \end{alignat}
@@
 Thus, if we restrict constraint \eqref{c16} to equality, constraint \eqref{c16} is still valid.
-Also, we have the following inequality.
+Also, we have the following inequality
 \begin{equation}\label{eqDelay}
-\frac{\alpha_s}{\mu_s} \leq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s.
-\end{equation}
-In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that
-the numerator and the denominator will both have the same sign.
-In the numerator, according to the \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
+\alpha_s / \mu_s \leq \mathtt{M}_{u(s,i)} \leq \mathfrak{M}_s,
+\end{equation}
+where $\mathtt{M}_{u(s,i)}=\frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s}\ge 0$ since
+the numerator and the denominator both have the same sign.
+In the numerator, according to \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
 If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{\max}_s \geq 1$, the numerator will be positive.
@@
 \begin{align}\label{RM}
-\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}, \\
-\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{\max}_s}+ \frac{3}{T^{\max}_s\mu_s-\alpha_s \frac{T^{\max}_s}{\mathfrak{M}_s}-3}.
+\mathcal{R}_{u(s,i)} \geq \lambda_{u(s,i)}+ 3/(T^{\max}_s&\mu_s-\alpha_s T^{\max}_s/\mathfrak{M}_s-3)+\nonumber\\
+&+ 1/T^{\max}_s=\varpi_{u(s,i)}.
 \end{align}
 %\end{subequations}
-In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
-So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
+%In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
+Thus, to obtain the optimal number of activated VNF in each slice, we need to find the maximum of the
 $\mathtt{M}_{u(s,i)}$ in each slice as $M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s $.
@@
 %\end{equation}
+\vspace{-3mm}
 \end{proof}
@@
 
-In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint
+In order to transform \eqref{problem} into a convex optimization problem in standard form, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint
 \eqref{c15} is changed to
@@
 \begin{equation}\label{RConstr}
-\mathcal{\bar{R}}_{u_{(s,i)}} \geq\eta_{u_{(s,i)}}= \max\{\mathcal{R}_{u_{(s,i)}}^{\min}, \lambda_{u_{(s,i)}}+\frac{1}{T^s_{\max}}, \varpi_{u(s,i)} \}. 
+\mathcal{\bar{R}}_{u_{(s,i)}}\!\!\geq\!\eta_{u_{(s,i)}}\!\!\!=\! \max\{\mathcal{R}_{u_{(s,i)}}^{\min}\!, \lambda_{u_{(s,i)}}\!\!+\frac{1}{T^s_{\max}}\!, \varpi_{u(s,i)} \}. 
 \end{equation}
@@
 &+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\nonumber\\
-&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\nonumber\\
-&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{\max}_{s}- p^k_{r,u(s,i)})\nonumber\\
-&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\nonumber\\
-&-  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)} -1)\nonumber\\
-&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R} \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}.
+&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\Big(\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\!-\!
+\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)}\!-\!1) \nonumber\\
+&+   \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}+ \mathfrak{q}^k_{r,u(s,i)} (P^{\max}_{s}- p^k_{r,u(s,i)})\Big)\nonumber\\
+&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}\Big(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1\Big).
 \end{align}
 %{\color{red} Motivate the lemma. separate proof and lemma}
+\vspace{-2mm}
 \begin{lemma}
@@
 \end{lemma}
+\vspace{-4mm}
 \begin{proof}
@@
 \begin{align}\label{deriveP}
-\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\nonumber\\
- &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0,
+\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}}\!\!=\!
+(\delta_s \!+\!
+\mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\!\!+\!
+(\mathfrak{s}^k_{r,u(s,i)}\!
+\!-\!\mathfrak{D}_{r,u(s,i)}^{k})\!=\!0,
 \end{align}
-where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follows:
+where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follows
 \begin{subequations}
 \begin{alignat}{4}
-\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
-\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
-\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.
+\mathfrak{D}_{r,u(s,i)}^{k} &\!\!= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
+\mathfrak{B}_{r,u(s,i)}^{k} &\!\!= \!B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}\mathfrak{S}_{r,u(s,i)}^{k}\!/\!\ln(2),\\
+\mathfrak{S}_{r,u(s,i)}^{k} &\!\!= ({|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}\!+\!BN_0\!+\! I_{r,u(s,i)}^{k})^{\!-1}.
 \end{alignat}
@@
 \begin{align}
-p_{r,u(s,i)}^{k} &= \bigg[\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ \text{Ln2} \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})} \nonumber\\
- &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}\bigg]^+.
+&p_{r,u(s,i)}^{k} =\nonumber\\ 
+&\bigg[\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ \ln(2) (\mathfrak{D}_{r,u(s,i)}^{k}\!\!-\!\mathfrak{s}^k_{r,u(s,i)})}\!
+-\!\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}\bigg]^+.
 \end{align}
@@
 \begin{align}\label{deriveE}
-\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\nonumber\\
-&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\nonumber\\
+\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} \!\!=\!
+&\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s\!+\!\mathfrak{h}_{u_{(s,i)}}\!)\!-\!
+\mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\nonumber\\
 &+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.
@@
 \begin{align}\label{deriveE1}
-e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\nonumber\\
-& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0,
+e_{r,u(s,i)}^{k}  (\mathfrak{F}^{k}_{r,u(s,i)} \!-\!\mathfrak{v}^{k}_{r,u(s,i)}\! -\! \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )\! =\! 0,
 \end{align}
@@
 The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
+\vspace{-3mm}
 \subsection{Sub-Problem 2}\label{sub2}
+\vspace{-1mm}
 After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.
-
-Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
+For this, assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, so we want to find $\boldsymbol{G}$.
 Next, we introduce a greedy algorithm that assigns an O-RU to each UE.
 
-\textit{Greedy Algorithm Assignment (GAA):}
-\textcolor{MidnightBlue}{Following is a reformulated version of the problem.}
-\begin{subequations}\label{problem2}
-\begin{alignat}{4}
-\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R} \delta_s g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
-\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r,
- \label{p11} \\
-& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{p12}\\
- & g^r_{u(s,i)} \in \{0,1\} \quad \forall s, i, \label{p13}
-\end{alignat}
-\end{subequations}
-where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
-and $\mathfrak{t}_r = \zeta_r- \sigma_r$  because of the equations \eqref{pr11} and \eqref{pr}.
-Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
-%The problem \eqref{problem2} is an integer linear programming.
-%By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
-The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.
-We solve this problem using heuristic method (GAA method \ref{alg1}), which is a greedy algorithm \cite{akccay2007greedy,lee2018dynamic}.
-Firstly, we set all the variables to zero ($g^r_{u(s,i)} = 0, \quad \forall s, i, r$).
-Then we define the parameter ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$.
-This parameter is used as a set of O-RUs that can be assigned to the UE $i$ in slice $s$, which initially includes all the O-RUs (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}, \forall s, i$ ).
-Also we introduce another parameter $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
-which is the knapsack capacity of each O-RU.
-Next, we sort all the slices based on their priority.
-Afterward, based on the sorting of the UEs,
-we assign the O-RU that provides the highest achievable data rate for each UE on the condition that the value of the desired UE ($\psi_{r,u(s,i)}$) does not exceed the knapsack capacity of each O-RU ($ \mathfrak{C}_r$).
-If it exceeds the capacity of the desired O-RU, we remove the specific O-RU from the set of O-RUs that can be assigned to that UE (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $).
-Then, the O-RU with the highest achievable data rate from the new set of O-RUs ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$ is selected.
-The complexity of sorting S slices based on their priority is $O(S\log(S))$.
-Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ as the whole number of UEs in the system.
-The complexity order of this algorithm is about $O(S\log(S)) + O(R\times \mathfrak{N})$.
-%$O(N\times \mathfrak{N})$
-\begin{algorithm}
+\begin{algorithm}[t!]
 \small
@@
 \end{algorithm}
-
- \begin{algorithm}
+%
+\textit{Greedy Algorithm Assignment (GAA):}
+The following is a reformulated version of the problem.
+\begin{subequations}\label{problem2}
+\begin{alignat}{4}
+\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R} \delta_s g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
+\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r,
+ \label{p11} \\
+& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{p12}\\
+ & g^r_{u(s,i)} \in \{0,1\} \quad \forall s, i, \label{p13}
+\end{alignat}
+\end{subequations}
+where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
+and $\mathfrak{t}_r = \zeta_r- \sigma_r$  because of the equations \eqref{pr11} and \eqref{pr}.
+Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
+%The problem \eqref{problem2} is an integer linear programming.
+%By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
+The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.
+We solve this problem using the heuristic GAA Algorithm~\ref{alg1}, which is a greedy algorithm \cite{akccay2007greedy,lee2018dynamic}.
+Firstly, we set all the variables to zero ($g^r_{u(s,i)} = 0, \quad \forall s, i, r$).
+Then we define the parameter ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$.
+This parameter is used as a set of O-RUs that can be assigned to the UE $i$ in slice $s$, which initially includes all the O-RUs (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}, \forall s, i$ ).
+Also we introduce another parameter $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
+which is the knapsack capacity of each O-RU.
+Next, we sort all the slices based on their priority.
+Afterward, based on the sorting of the UEs,
+we assign the O-RU that provides the highest achievable data rate for each UE on the condition that the value of the desired UE ($\psi_{r,u(s,i)}$) does not exceed the knapsack capacity of each O-RU ($ \mathfrak{C}_r$).
+If it exceeds the capacity of the desired O-RU, we remove the specific O-RU from the set of O-RUs that can be assigned to that UE (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $).
+Then, the O-RU with the highest achievable data rate from the new set of O-RUs ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$ is selected.
+The complexity of sorting S slices based on their priority is $O(S\log(S))$.
+Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ as the whole number of UEs in the system.
+The complexity order of this algorithm is about $O(S\log(S)) + O(R\times \mathfrak{N})$.
+%$O(N\times \mathfrak{N})$
+
+ \begin{algorithm}[t!]
  \small
@@
 \end{algorithm}
+\vspace{-3mm}
 \subsection{Iterative Proposed Algorithm}
+%\vspace{-1mm}
 In Sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted.
@@
  \small
-\caption{Fast Algorithm (FA) to Check the Convergence}\label{alg3}
+\caption{Fast Algorithm (FA) to check convergence}\label{alg3}
 \begin{algorithmic}[1]
@@
 \subsubsection{Convergence Analysis}
- \textcolor{MidnightBlue}{Due to limited system resources, we have limits on VNFs' power, UE or O-RU power, fronthaul capacity, etc.
+Due to limited system resources, we have limits on VNFs' power, UE or O-RU power, fronthaul capacity, etc.
 As a result, the objective function, which is the aggregate throughput, cannot exceed its optimal value and become infinite.
 Therefore, if the aggregate throughput is infinite and increases without limit, the resources must also be unlimited.
-Hence, the system has an optimal solution: its maximum aggregate throughput in the feasible region.}
-
- \textcolor{MidnightBlue}{Consequently, we can guarantee the convergence of the iterative algorithm if the objective function is the ascending function concerning the number of iterations and has an upper bound.
+Hence, the system has an optimal solution: its maximum aggregate throughput in the feasible region.
+
+Consequently, we can guarantee the convergence of the iterative algorithm if the objective function is the ascending function concerning the number of iterations and has an upper bound.
 Thus, it will converge to its optimum value if it is a strictly ascending function and to its local optimum if it is a non-monotonically ascending function.
-}
 % \cite{gholipoor2020resource}.
@@
 for the aggregate throughput.
-
-\textcolor{MidnightBlue}{ Thus,
+Thus,
 we can guarantee the local convergence of our iterative algorithm since the objective function $\mathcal{T}$ is the ascending function concerning the number of iterations
- and it has the upper bound which is not infinite.}
-
- \textcolor{MidnightBlue}{In addition, to extend our solution to the global optimum, we must prove that the algorithm monotonically increases in the non-optimal set of solutions and is Lipschitz monotone contraction mapping.
-Here, we briefly discussed our algorithm's global convergence for a low interference system.}
-
-  \textcolor{MidnightBlue}{ In the low interference system, the PRB and VNF assignment is obtained straightforwardly, and the first step's problem is power allocation.
-In the first step of our algorithm with the fixed O-RU association, we have
+ and it has the upper bound which is not infinite.
+
+In addition, to extend our solution to the global optimum, we must prove that the algorithm monotonically increases in the non-optimal set of solutions and is Lipschitz monotone contraction mapping.
+Here, we briefly discussed our algorithm's global convergence for a low interference system.
+
+In the low interference system, the PRB and VNF assignment is obtained straightforwardly, and the first step for solving the problem is power allocation. Given fixed O-RU association, we have
 $\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$ (strictly increase). 
-Because in this step, the problem is reformulated to the power allocation, and the objective function is convex, and the convex functions are Lipschitz monotone contractions. 
+Notice that for the power allocation problem, the objective function is convex, and the convex functions are Lipschitz monotone contractions. 
 However, in the second step of the algorithm, we can show as before that the algorithm is increased, but we can not talk about monotonically increases.
@@
 Consequently, the algorithm converges to the 
-global optimum solution in low interference.}
+global optimum solution in low interference.
 %\vspace*{-2em}
-\section{Numerical Results and The Feasible Region}\label{NE}
+%\vspace{-3mm}
+\section{Numerical Results}\label{NE}
+%\vspace{-1mm}
 In this section, firstly, we describe the initial points and the comparison algorithms.
@@
 %\vspace*{-1.7em}
+\vspace{-3mm}
 \subsection{The initial Points and The Comparison Algorithms}
+\vspace{-1mm}
 In this part, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method.
@@
   \centering
-    \includegraphics[scale = 0.30]{cell.pdf}
+    \includegraphics[scale = 0.30]{fig/cell.pdf}
     %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
     %\includegraphics[width=\textwidth]{finalDraw.pdf}
+    \vspace{-1mm}
   \caption{O-RU placement in a cell}
+  \vspace{-2mm}
   \label{fig:cell}
@@
 The figures in \cite{lee2018dynamic} show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area.
-The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.
-\vspace*{-0.9em}
+Notice that our proposed algorithm performs better than the DR scheme.
+\vspace{-3mm}
 \subsection{Feasible Region}\label{fr}
+\vspace{-1mm}
 Applying the correct initial point is crucial in making the system feasible and convergent.
@@
 Moreover, the allocation of PRBs to UEs is based on dividing the number of UEs by the total number of PRBs.
-\vspace*{-1.em}
-\subsection{Numerical Results}
+\vspace*{-3mm}
+\subsection{Performance Results}
+\vspace*{-1mm}
 In Fig.
-3, the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods.
+3, the aggregate throughput is plotted versus the number of UEs in each service for these three methods.
 Suppose we have one service instance for each type of service, so we have three various services in this figure.
@@
 	\label{label}
+	\vspace*{-3mm}
 \end{figure*}
@@
 	\end{tabular}}
+	\vspace*{-3mm}
 	%\caption{Global caption.}
@@
 Our solution is close to the optimal value in a small number of UEs.
-\textcolor{MidnightBlue}{Therefore, this figure numerically demonstrates that the proposed algorithm converges to the global optimal in low interference.}
+Therefore, this figure numerically demonstrates that the proposed algorithm converges to the global optimal in low interference.
 
@@
 
-\textcolor{MidnightBlue}{Table III shows the execution time given a number of UEs for one service for the three methods.
-We run our simulation on the system with configuration (RAM = 8 GB, CPU = Core i5, SSD Hard Disk).
+Table III shows the execution time given a number of UEs for one service for the three methods. We run our simulation on the system with configuration (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
  As the number of UEs in the system increases, the execution time increases polynomially for all three algorithms.
@@
 Power and PRB are allocated in the DR scheme, but O-RUs are associated based on distance.
-Therefore the execution time is less than the proposed algorithm.}
+Therefore the execution time is less than the proposed algorithm.
 \begin{table}%[H]
@@
 %\end{figure}
-\vspace*{-1.4em}
+%\vspace*{-1.4em}
 \section{Conclusion}\label{conc}
@@
 \bibliography{ref}
+\vspace*{-3em}
 %\bibliography{IEEEabrv,conf_short,ref}
+% \begin{IEEEbiography}
+% [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mojdeh.jpg}}]{ Mojdeh Karbalaee Motalleb} received her B.S.
+and M.S.
+degrees in electrical engineering from the Amirkabir University of Technology, Tehran, Iran in 2015 and 2017.
+She is working toward a Ph.D.
+with the Department of Computer and Electrical Engineering, University of Tehran, Tehran, Iran.
+She is also a Visiting Research Student with the Center for Wireless Communications, Oulu University, Oulu, Finland.
+Her research interests include optimization and machine learning in network and wireless communications.
+% \end{IEEEbiography}
+% \begin{IEEEbiography}
+% [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{onel.jpg}}]{ Onel L.
+A.
+López} (S'17-M'20) received the B.Sc.
+(1st class honors, 2013), M.Sc.
+(2017) and D.Sc.
+(with distinction, 2020) degree in Electrical Engineering from the Central University of Las Villas (Cuba),  the Federal University of Paraná (Brazil), and the University of Oulu (Finland), respectively.
+From 2013-2015, he served as a specialist in telematics at the Cuban telecommunications company (ETECSA).
+He is a collaborator to the 2016 Research Award given by the Cuban Academy of Sciences, a co-recipient of the 2019 IEEE EuCNC Best Student Paper Award, the author of the best doctoral thesis in engineering in Finland in 2020, and the recipient of the 2022 Young Researcher Award in the field of technology in Finland.
+He is co-author of the book entitled ``Wireless RF Energy Transfer in the massive IoT era: towards sustainable zero-energy networks'', Wiley, Dec 2021.
+He currently holds an Assistant Professorship (tenure track) in sustainable wireless communications engineering in the Centre for Wireless Communications (CWC), Oulu, Finland.
+His research interests include sustainable IoT, energy harvesting, wireless RF energy transfer, wireless connectivity, and machine-type communications.
+% \end{IEEEbiography}
+
+ \vskip 0pt plus -2fil
+ \begin{IEEEbiography}
+ [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/mojdeh.jpg}}]{ Mojdeh Karbalaee Motalleb} received her B.S.
+and M.S.
+degrees in electrical engineering from the Amirkabir University of Technology, Tehran, Iran in 2015 and 2017.
+She is working toward a Ph.D.
+with the Department of Computer and Electrical Engineering, University of Tehran, Tehran, Iran.
+She is also a Visiting Research Student with the Center of Wireless Communications, Oulu University, Oulu, Finland.
+Her research interests include optimization and machine learning in network and wireless system.
+ \end{IEEEbiography}
+  \vskip 0pt plus -1fil
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/Vahid}}]{Vahid Shah-Mansouri}%%%IEEEbiographynophoto
+(S’02–M’13) received the B.Sc. degree in electrical
+engineering from the University of Tehran, Tehran, Iran, in 2003,
+the M.Sc. degree in electrical engineering from Sharif University
+of Technology, Tehran, Iran, in 2005, and the Ph.D. degree from The
+University of British Columbia, Vancouver, BC, Canada, in 2011,
+respectively. Since 2013, he has been with the
+School of Electrical and Computer Engineering, University of Tehran,
+Tehran, Iran. His research interests include analysis and mathematical
+modeling of communication and computer networks.
+\end{IEEEbiography}
+ \vskip 0pt plus -1fil
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/Saeedeh}}]{Saeideh Parsaei Fard}%%%IEEEbiographynophoto
+ received the B.Sc.
+and M.Sc.
+degrees from the Amirkabir University of Technology (Tehran Polytechnic), Tehran, Iran, in 2003 and 2006, respectively, and the Ph.D.
+degree in electrical and computer engineering from Tarbiat Modares University, Tehran, in 2012.
+She is now part of Apple Cellular Platform Architecture team.
+Saeideh was a research scientist and lecturer from 2019 to 2021 at the University of Toronto, Canada.
+She was a Postdoctoral Research Fellow with the Telecommunication and Signal Processing Laboratory, Department of Electrical and Computer Engineering, McGill University, Canada, in 2013.
+From 2010 to 2011, she was a Visiting Ph.D.
+student with the Department of Electrical Engineering, the University of California at Los Angeles, Los Angeles, CA, USA.
+Her works are published in 3 books and 50 journals and conference papers, which are cited more than 1300 times with an h-index of 19 and i10-index of 31.
+She was awarded the “IEEE women in engineering award" in region 8 and Senior Member IEEE in 2018.
+Her background includes optimization theory, game theory, signal processing, and networking.
+Her current research focuses on distributed/federate learning, machine learning applications in next-generation wireless networks such as network automation and resource management, and robustness in both learning and communication.
+ \vspace{-1mm}
+\end{IEEEbiography}
+ \vskip 0pt plus -1fil
+ \begin{IEEEbiography}
+ [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/onel.jpg}}]{ Onel L.
+A.
+López} (S'17-M'20) received the B.Sc.
+(1st class honors, 2013), M.Sc.
+(2017) and D.Sc.
+(with distinction, 2020) degree in Electrical Engineering from the Central University of Las Villas (Cuba),  the Federal University of Paraná (Brazil), and the University of Oulu (Finland), respectively.
+From 2013-2015, he served as a specialist in telematics at the Cuban telecommunications company (ETECSA).
+He is a collaborator to the 2016 Research Award given by the Cuban Academy of Sciences, a co-recipient of the 2019 IEEE EuCNC Best Student Paper Award, the author of the best doctoral thesis in engineering in Finland in 2020, and the recipient of the 2022 Young Researcher Award in the field of technology in Finland.
+He is co-author of the book entitled ``Wireless RF Energy Transfer in the massive IoT era: towards sustainable zero-energy networks'', Wiley, Dec 2021.
+He currently holds an Assistant Professorship (tenure track) in sustainable wireless communications engineering in the Centre for Wireless Communications (CWC), Oulu, Finland.
+His research interests include sustainable IoT, energy harvesting, wireless RF energy transfer, wireless connectivity, and machine-type communications.
+ \end{IEEEbiography}
 \end{document}

### 2022-10-03 Code_journal1/paperTNSM/questions/biographyFolder/biography.tex
final version of magazine

--- 2022-09-08 Code_journal1/paperTNSM/pr.tex
@@
- %\pdfoutput=1
-%\documentclass[conference]{IEEEtran}
-\documentclass[lettersize,journal]{IEEEtran}
-%\normalsize
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{setspace}
-\usepackage{array,tabulary,tabularx,multirow}
-\usepackage[T1]{fontenc}
-\usepackage{cite}
-\usepackage{caption}
-\captionsetup{font=footnotesize}
-\usepackage{algcompatible}
-%\usepackage{subcaption}
-\usepackage{mathtools}
-\usepackage{stackengine}
-%\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
-\usepackage{graphicx}
-\usepackage{blindtext}
-\usepackage{textcomp}
-\usepackage[dvipsnames]{xcolor}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-%\usepackage{algorithmic,algorithm2e,float}
-\usepackage[noend]{algpseudocode}
-\usepackage{amsthm}
-\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\usepackage{balance}
-\usepackage{booktabs}
-\allowdisplaybreaks
-\newtheorem{remark}{Remark}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newcommand{\diag}{\mathop{\mathrm{diag}}}
-\DeclareMathOperator{\E}{\mathbb{E}}
-\usepackage[margin=0.7in]{geometry}
-\usepackage[export]{adjustbox}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\setlength{\columnsep}{11mm}
-\captionsetup{font=footnotesize}
-\captionsetup[figure]{font=small}
-\newcommand{\abstractnamefont}{\normalfont\small\bfseries}
-\newcommand{\abstracttextfont}{\normalfont\small}
-\setlength{\belowcaptionskip}{-10pt}
-\def\hlinewd#1{%
-\noalign{\ifnum0=`}\fi\hrule \@height #1 %
-\futurelet\reserved@a\@xhline} 
-%\setlength{\dbltextfloatsep}{-20pt}
-\begin{document}
-
-\title{Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
-}
-%%%%%%%%%%%%%%%
-%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
-%\IEEEauthorblockA{\textit{School of ECE} \\
-%\textit{Tehran University}\\
-%Tehran, Iran \\
-%mojdeh.karbalaee@ut.ac.ir}
-%\and
-%\IEEEauthorblockN{ Vahid Shah-Mansouri}
-%\IEEEauthorblockA{\textit{School of ECE} \\
-%\textit{Tehran University}\\
-%Tehran, Iran \\
-%vmansouri@ut.ac.ir}
-%\and
-%\IEEEauthorblockN{ Saeedeh Parsaeefard}
-%\IEEEauthorblockA{\textit{Department of ECE} \\
-%\textit{University of Toronto}\\
-%Toronto, Canada \\
-%saeede.parsaeefard@gmail.com}
-%}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  \author{
-%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
-%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
-%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
-%    \vspace{-.2cm}
-%  }
-%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
-%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
-%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
-%}
-\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, Saeede Parsaeefard$^\dagger$, and Onel Luis Alcaraz López$^\ddagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com, \{onel.alcarazlopez\}@oulu.fi\\
-\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada, $^\ddagger$University of Oulu, Oulu, Finland}
- }
-\maketitle
-\pagenumbering{gobble}
-%\vspace*{-4em}
-\begin{abstract}
-%\vspace*{-1.5em}
-The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks.
-Nevertheless, strictly satisfying quality-of-service requirements while establishing priorities and promoting balance between the significantly heterogeneous services remains a key research problem.
-In this paper, we use network slicing to study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems.
-The limited fronthaul capacity and end-to-end delay constraints are simultaneously considered.
-Optimizing baseband resources includes O-RAN radio unit (O-RU), physical resource block (PRB) assignment, and power allocation.
-The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve.
-Consequently, we break it down into two different steps and propose an iterative algorithm that finds a near-optimal solution.
-In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is resolved.
-The proposed method is validated via simulations, which achieve a higher data rate and lower end-to-end delay than existing methods.
-\end{abstract}
-\begin{IEEEkeywords}
-open radio access network (O-RAN), virtual network function (VNF), network slicing, knapsack problem, greedy algorithm, Karush-Kuhn-Tucker (KKT) Conditions.
-\end{IEEEkeywords}
-%
-\vspace{-3mm}
-\section{Introduction}
-\vspace{-1mm}
-%\subsection{State Of The Arts}
-Network slicing is a key technology in 5G wireless systems.
-Specifically, it isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various services\cite{shen2020ai,setayesh2020joint,popovski20185g}.
-
-There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC).
-Each service is assigned to a network slice depending on its corresponding quality of service (QoS) requirements.
-For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming.
-Meanwhile, the URLLC service provides ultra-reliable and low-latency connectivity, e.g., for autonomous vehicles, Tactile Internet, and remote surgeries.
-Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
-%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}
-%Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
-In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig.
-\ref{fig:c11}, is introduced to deal with these issues.
-%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture.
-We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
-%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
-%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems.
-The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence
-%A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV).
-Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
-%As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.
-\vspace{-3mm}
-\subsection{Motivation}
-\vspace{-1mm}
-The optimal resource allocation in 5G systems is crucial for reducing costs and improving the performance experienced by the user equipments (UEs).
-These systems face significant challenges, including interference alignment, limited capacity of the fronthaul links, energy restrictions on virtual machines (VMs), etc.\cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.
-
-Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering a single service's power, data rate, and delay limitations.
-%Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously.
-In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig.
-\ref{fig:c11}, is introduced to deal with these issues.
-Unfortunately, the existing radio access networks (RANs) currently lack adequate flexibility and openness to handle these simultaneous service demands. 
-Hence, a new RAN paradigm, called open RAN (O-RAN) architecture, has emerged.
-% as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost.
-Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges.
-Therefore, O-RAN can simultaneously support multiple services at a lower cost by being flexible, layered, and modular.  
-One of the fundamental problems lies in balancing services with different QoS, resource requirements, and priorities in O-RAN architecture
- \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.  
-%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
-%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
-%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}
-
-The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation.
-% Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
-\vspace{-3mm}
-\subsection{Main Contributions}
-\vspace{-1mm}
-This paper studies the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G services.
-We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
-%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
-%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
- The main contributions of this paper are summarized as follows:
-\begin{itemize}
-\item We examine the problem of baseband resource allocation, such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs, to maximize the weighted throughput of the O-RAN architecture.
-The three types of 5G service classes, i.e., eMBB, URLLC, and mMTC, together with their corresponding QoS requirements and service priorities, are considered.
-\item We propose a two-step resource management algorithm for solving the optimization problem.
-In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs.
-Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation.
-In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
-\item We analyze the complexity of the proposed algorithms and demonstrate their convergence.
-Additionally, we analyze the feasibility region of the problem and introduce a fast algorithm to check it numerically.
-\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay.
-Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
-\end{itemize}
-\vspace{-3mm}
-\subsection{Organization}
-\vspace{-1mm}
-%Table \ref{table:11a} lists the acronyms used throughout this paper, which
-This paper is organized as follows.
-Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
-The system model and the problem formulation are described in Section \ref{systemmodel} and Section \ref{prS}, respectively.
-The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}.
-In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm.
-Finally, Section \ref{conc} concludes the paper.
-For clarity, Table I lists the main acronyms used throughout the paper.
-
-\begin{table}%[H]
-\vspace*{-0em}
- \caption {List of Acronyms} \label{table:11a}
- \vspace*{-1em}
- \begin{center}
- \scalebox{0.9}{
-  \begin{tabular}{l  l }
-  \toprule
-  \vspace*{-0.3em}
-\textbf{Acronym} & \textbf{Definition} \\ [0.3ex]
-   \toprule
-  VNF & virtual network function\\[.3ex]
-
-  VM & virtual machine  \\[.3ex]
-  RAN &  radio access network \\[.3ex]
- O-RAN & open RAN  \\[.3ex]
- vRAN & virtual RAN \\[.3ex]
- CRAN & cloud RAN \\[.3ex]
-  RRH & radio remote head \\[.3ex]
-   BBU & baseband unit \\[.3ex]
-   QoS &  quality of service \\[.3ex]
-  MIMO & multiple input multiple output \\[.3ex]
-  PRB &  physical resource block \\[.3ex]
-  %SINR & signal to interference and noise ratio  \\[.3ex]
-  eMBB & enhanced mobile broadBand \\[.3ex]
-
-  URLLC  & ultra-reliable low latency communication \\[.3ex]
-
-  mMTC &  massive machine-to-machine communications \\[.3ex]
-
-  O-RU &  O-RAN radio unit \\[.3ex]
-
-   O-DU &  O-RAN distributed unit \\ [.3ex]
-
-   O-CU &  O-RAN central unit \\ [.3ex]
-
-     UPF &  user plane function \\ [.3ex]
-
-  UE &  user equipment \\ [.43ex]
-  SINR & signal-to-noise-plus-interference ratio \\ [.3ex]
-  CAPEX & capital expenditures  \\ [.3ex]
-  OPEX & operating expenses  \\ [.3ex]
-
-  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
- \toprule
- \end{tabular}}
- \end{center}
- \vspace*{-2.5em}
- \end{table}
-\vspace{-3mm}
-% \vspace*{-3em}
-\section{Related Literature}\label{RL}
-\vspace{-1mm}
-The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
-Two levels of dynamic network slicing in heterogeneous C-RAN (H-CRAN) are examined in \cite{lee2018dynamic}.
-The higher level manages user acceptance control, RRH association, and the allocation of BBU capacity.
-Meanwhile, PRB and power are allocated at lower levels.
-In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning.
-In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.
-In \cite{singh2022joint}, to provide 5G slicing services, the authors present a framework called O-RANFed that implements and optimizes federated learning tasks in O-RAN devices.
-Moreover, The authors of \cite{zhang2022federated} propose a federated deep reinforcement learning algorithm to achieve network slicing in O-RAN.
-
-Recent research has focused on multiplexing eMBB and URLLC services within a RAN.
-In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
-In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services.
-Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
-In \cite{alsenwi2021intelligent}, the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
-% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services.
-The system guarantees latency, service rate, and reliability maintenance.
-
-In \cite{SystemCostMinimization,guo2016exploiting}, VMs activation and beamforming allocation are discussed in C-RAN systems.
-Paper \cite{SystemCostMinimization} minimizes energy cost with system delay, fronthaul capacity, and rate constraints.
-To guarantee UE delays, M/M/1 queueing theory is used for transmission and processing delays.
-In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated.
-Also, the association of RRH to the UE is considered and solved using innovative methods.
-
-In \cite{ali2019energy,ali2018joint}, the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
-Finally, in \cite{amani2019power}, the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved. 
-%\vspace*{-1.8em}
-%\vspace{-3mm}
-\section{Background}\label{BG}
-\vspace{-1mm}
-\begin{figure}
-  \centering
-  \captionsetup{justification=centering}
-    \includegraphics[scale = 0.36]{fig/finalDraw1.pdf}
-    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-    \vspace{-6mm}
-  \caption{Network sliced O-RAN system}
-  \label{fig:c11}
-  \vspace{-2mm}
-\end{figure}
-O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence.
-
-O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).
-By virtualizing RANs, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to their networks more quickly.
-The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU).
-Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}.
-Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
-Mostly non-real-time baseband processing occurs in the O-CU layer, while real-time baseband processing occurs in the O-DU layer.
-
-In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN.
-As shown in Fig.
-\ref{fig:c11}, O-RU is a logical node that contains RF and low PHY.
-The former transmits or receives radio signals, while the latter includes digital beamforming.
-Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC.
-It contains a subfunction of the eNodeB and is deployed near the O-RU.
-Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
-In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
-
-The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP).
-The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).
-O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
-Moreover, O-CU-UP is connected to user plane function (UPF) via O-backhaul link.
-
-The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud.
-Orchestration and Automation include functions such as RIC Non-Real-Time.
-RIC is responsible for machine learning methods and making the system more intelligent.
-
- key feature of the O-
-RAN architecture is that the hardware is disaggregated from
-the software, leading to network function virtualization
-(NFV).
-Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
-As a result, as shown in Fig \ref{fig:c11}, O-RAN components, such as UPF, O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs
-\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
-%\vspace{-3mm}
-\section{System Model}\label{systemmodel}
-%\vspace{-1mm}
-We consider a downlink (DL) system, and an O-RAN architecture using RAN slicing as depicted in Fig. \ref{fig:c11}.
-In this section, we present the system and signal model, derive the achievable data rates, power of O-RU, and the fronthaul capacity  of the O-RAN system.
-Moreover, we discuss the mean delay and the power of VNFs.
-\vspace{-3mm}
-\subsection{System Model}
-\vspace{-1mm}
-Assume, there are three service types: eMBB, URLLC, and mMTC, which support different applications.
-Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
-Therefore, there are $S = S_1 + S_2 + S_3$ pre-allocated slices serving these services.
-Moreover, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have the set
-$\{1,2,...,S_1\}$ of eMBB service instances, the set $\{1,2,...,S_2\}$ of URLLC service instances, and the set
-$\{1,2,...,S_3\}$ of mMTC service instances.
-Each service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs requiring certain level of QoS. Notice that $j \in \{1,2,3\}$ indicates the service type.
-Based on the application and QoS request, UE may be admitted and allocated to the resources.
-
-Each pre-allocated slice contains reserved VNFs for the three logical nodes:
-\begin{itemize}
-\item MAC/RLC functions in the O-DU 
-\item PDCP/SDAP functions in the O-CU-UP
-\item UPF which is a functional layer
-\end{itemize}
-Each slice $s \in \{1,2,...,S \}$, consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP, and $M_s^{u}$ VNFs for the processing of UPF.
-The VNFs of O-DU, O-CU-UP, and UPF are interconnected, which is defined as the service function chain in the O-RAN system.
-Also, each VNF instance runs on a VM that uses resources from the data centers.
-
-%All $K$ PRBs can be assigned to all UEs in each service.
-Assume there are $K$ PRBs in this system. Suppose each slice $s$ consists of $\bar{K}_s$ pre-allocated virtual resource blocks that are mapped to PRBs. Therefore, we have $\sum_s \bar{K}_s \leq K$.
-In addition, there are $R$ multi-antenna O-RUs that are shared between the slices.
-Specifically, the O-RU $r \in \mathcal{R}=\{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data.
-Moreover, all O-RUs have access to all PRBs.
-\vspace{-3mm}
-%Coordinated multipoint (CoMP) system is considered here.
-%\subsection{The Achievable Rate}
-\subsection{Signal Model}
-\vspace{-1mm}
-Let $y_{u(s,i)} $ be the received signal of UE $i$ in the $s^{th}$ service such that
-\begin{equation}\label{eq2}
-y_{u(s,i)}\!\!=\!\!\sum_{r\!=\!1}^{R}\!\sum_{k\!=\!1}^{K_s} \!\boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r\! e^k_{r,u(s,i)}{x_Q}^k_{r,u(s,i)}\!\!+\!z_{u(s,i)},
-\end{equation}
-%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
-where ${x_Q}^k_{r,u(s,i)}\!=\!{x_P}^k_{r,u(s,i)}\!\!+\!
-\boldsymbol{q}_{r}$, ${x_P}^k_{r,u(s,i)}\!=\!
-\boldsymbol{w}^k_{r,u(s,i)}\!\sqrt{p^{k}_{r,u(s,i)}} x_{u(s,i)}$,  $ x_{u(s,i)}$ depicts the transmitted symbol vector, $z_{u(s,i)}\sim \mathcal{CN}(0,BN_0)$ is the receive additive Gaussian noise, and $BN_0$ is the noise power in a given bandwidth $B$.
-Here, ${x_P}$ denotes the precoded message before compression, while ${x_Q}$ illustrates the precoded message after compression.% as shown in Fig. \ref{fig:pq}.
-In addition, $\boldsymbol{q}_{r} \sim  \mathcal{CN}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$ indicates the quantization Gaussian noise which comes from the signal compression in O-DU.
-Furthermore, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether O-RU $r$ serves the $i^{th}$ UE that is allocated to the $s^{th}$ slice or not.
-Furthermore, $p_{r,u(s,i)}^{k}$ represents the transmission power of the O-RU $r$ serve the $i^{th}$ UE in slice $s$ and PRB $k$, while
-${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ corresponding channel vector.
-In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the associated transmit beamforming vector.
-%Here, it is assumed that each UE is served by the nearest o-RU
-Therefore, the SINR of the $i^{th}$ UE served at slice $s$ on PRB $k$ is given by
-\begin{equation}\label{eq1}
-\rho_{r,u(s,i)}^{k} =  \frac{p_{r,u(s,i)}^{k}|{\bold{h}_{r,u(s,i)}^{k \: H}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
-\end{equation}
-
-A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set $\mathcal{R}\backslash r$ that are using the same PRB $k$.
-Two types of interference occur between UEs in each slice: i) inter-slice interference between signals transmitted over different slices, and ii) intra-slice interference between signals transmitted over the same slice.%that is shown in Fig.
-\ref{fig:intf}.
-
-Network slicing techniques significantly reduce inter-service (inter-slice) interference.
-One way to leverage a two-time scale PRB scheduling is to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale).
-Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.
-In this paper, we assume that the PRB scheduling is performed.
-Also, in Section \ref{prb}, we briefly study the PRB scheduling between slices.
-Since there are limited resources, inter-service interference cannot be eliminated entirely.
-Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.
-%\begin{figure}
-%  \centering
-%  \captionsetup{justification=centering}
-%    \includegraphics[scale = 0.35]{Interference.png}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Type of Interference Signal}
-%  \label{fig:intf}
-%\end{figure}
-
-Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as 
-%{\color{red} use paranthesis in the following equation to clear +}
-%\begin{subequations}\label{eqI}
-%\begin{alignat}{4}
-%\begin{align}\label{eqI}
-%&I_{r,u(s,i)}^{k} =\nonumber\\
-% &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
-%&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
-%&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
-%\end{align}
-%\end{alignat}
-%\end{subequations}
-%{\color{red} $\gamma_1$ is constant used instead of variable. }
-\begin{align}\label{eqI}
-&I_{r,u(s,i)}^{k} =\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}} + \nonumber\\
- &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}}\!
-e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\!\!\sum_{\substack{r'=1 \\ r'\neq r}}^{R}\!|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
-\end{align}
-%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
-where $e^{k}_{u(s,i)}$ is a binary variable that indicates whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU, or not.
-%($\gamma_1$ and $\gamma_2$ are two variales.
-You  define on variable here.)
-Furthermore, there is no inter-slice interference, only intra-slice interference, since slices are assumed to be isolated.
-
-%To obtain SNR as formulated in \eqref{eq1}, 
-%\begin{figure}
-%  \centering
-%  \captionsetup{justification=centering}
-%    \includegraphics[scale = 0.45]{Qdiag.png}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Precoding and Quantization of Signal}
-%  \label{fig:pq}
-%\end{figure}
-
- Herein, we consider a zero forcing beamforming vector, which minimizes the experienced intra-slice interference, and is given by \cite{huang2013user}
-\begin{equation}
-\bold{w}_{r,u(s,i)}^{k} = \hat{\bold{h}}_{r,u(s,i)}^{k}(\hat{\bold{h}}_{r,u(s,i)}^{k \: H} \hat{\bold{h}}_{r,u(s,i)}^{k})^{-1}.
-\end{equation}
-\noindent where $\bold{h}_{r,u(s,i)}^{k}$ is the channel estimate, which is assumed imperfect. Mathematically,
-$\hat{\boldsymbol{h}}_{r,u(s,i)} = \boldsymbol{h}_{r,u(s,i)} + \Delta \boldsymbol{h}_{r,u(s,i)}$, where
-$\Delta \boldsymbol{h}_{r,u(s,i)}\sim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$ indicates the estimating error vector with a Gaussian distribution and $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$
-\vspace{-3mm}
-\subsection{Achievable Data Rate}
-\vspace{-1mm}
-The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as 
-\begin{equation}\label{eq3}
-\mathcal{R}_{u(s_1,i)} = \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},
-\end{equation}
-where
-\begin{equation}
-\mathcal{R}_{r, u(s_1,i)} = \sum_{k=1}^{K} \mathcal{{R}}_{r,u(s_1,i)}^{k} e^k_{r,u(s_1,i)}
-\end{equation}
-is the achievable data rate of RU $r$ to UE $i$ in slice $s_1$, which depends on the achievable data rate per PRB, i.e.,
-\begin{equation}
-\mathcal{{R}}_{r,u(s_1,i)}^{k} =  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}),
-\end{equation}
-%\begin{subequations}\label{eq3}
-%\begin{alignat}{4}
-%\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
-%\mathcal{R}_{r, u(s_1,i)} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
-%\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},
-%\end{alignat}
-%\end{subequations}
-Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the application of service type 2 (URLLC) and 3 (mMTC) is not achieved from the Shannon capacity formula.
-Instead, in a short packet transmission, the achievable data rate is approximated as \cite{setayesh2020joint}
-\begin{equation}\label{eq11}
-\mathcal{R}_{u(s_j,i)} = \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
-\end{equation}
-where
-\begin{equation}
-\mathcal{R}_{r,u(s_j,i)} = \mathcal{{R}}_{r,u(s_j,i)}^{k}{e}_{u(s_j,i)}^{k},
-\end{equation}
-is the achievable data rate of RU $r$ to UE $i$ in slice $s_1$, which depends on the achievable data rate per PRB, i.e.,
-\begin{equation}
-\mathcal{{R}}_{r,u(s_j,i)}^{k} = B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},
-\end{equation}
-%\begin{subequations}\label{eq11}
-%\begin{alignat}{4}
-%\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
-%\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
-%\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
-%\end{alignat}
-%\end{subequations}
-where %$j \in \{2,3\}$. Also we have $ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}},$.
-%{\color{red} check paranthesis. }
-\begin{equation}\label{shortPacket}
- \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\mathfrak{C}_{u(s_j,i)}^{k}/N_{u(s_j,i)}^{k}}.
-\end{equation}
-%{\color{red} what is transmission probability? }
-Here, $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of the Q function,
-$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$ and PRB $k$, while
-$N_{u(s_j,i)}^{k}$ represents the corresponding transmit blocklength.
-$\mathcal{R}_{r,u(s_j,i)}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.
-
-If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{\text{max}}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$.
-Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
-\subsection{Power of the O-RU and the Fronthaul Capacity}
-Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to all the UEs served by it. From \eqref{eq2}, the power of each O-RU $r$ is obtained as follows,
-%{\color{red} is this the sum rate of all users?}
-\begin{equation}\label{pr}
-P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2\alpha^k_{r,u(s,i)} + \sigma_{q}^2,
-\end{equation}
-where $\alpha^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$.
-Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
-%\cite{simeone2016cloud, 1111}
-\begin{align}\label{cr}
-C_{r} &= \log_2{\left(1+ \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} / \sigma_{q}^2\right)}\nonumber\\
-&= \log_2{\left(P_r/\sigma_{q}^2\right)}.
-\end{align}
-\vspace{-4mm}
-\subsection{Mean Delay}
-\vspace{-1mm}
-In this part, the end-to-end mean delay for each service is obtained.
-The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the total propagation delay ($T^{\text{pro}}$).
-\begin{subequations}
-\begin{alignat}{4}
-T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
-T^{\text{\text{proc}}} &=  T^{\text{RU}} + T^{\text{DU}} + T^{\text{CU}} + T^{\text{UPF}},\\
-T^{\text{tr}} &= T^{\text{fr},t} + T^{\text{mid},t} + T^{\text{b},t},  \\
-T^{\text{pro}} &= T^{\text{fr},p} + T^{\text{mid},p} + T^{b,p}.
-\end{alignat}
-\end{subequations}
-%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
-%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
-Mathematically, the total propagation delay ($T^{\text{pro}}$) is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
-In each link, the propagation delay is the time a signal to reach its destination.
-It is obtained based on the length of the fiber link and the capacity of the link (as $\text{T} = \text{L}/\text{c}$, where L is the length of the link and c is the propagation speed of the medium).
-Meanwhile, the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
-In each link, the transmission delay is the amount of time required to push all the packets into the transmission medium, and can formulated as
-$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the data-rate of the packet and $\mathcal{\alpha}$ is the mean packet size.
-Notice that taking the propagation and transmission delays into account in the formulation is straightforward, but we have avoided it for the sake of succinctness and simplicity.
-%It is worth highlighting that propagation delay must be specially considered when each O-RU can connect to several number of O-DUs and depending on the route, capacity, and priority. 
-%However, this would provide a new problem formulation, which could be added to our system model to extend our paper in the future.
-In the current paper, we assume that the connection between O-RUs and O-DUs is fixed and transparent, and we do not consider the problem of edge processing.
-Therefore, the propagation delay is fixed and does not affect the optimization problem.
-
-Next, we present a brief calculation of propagation delay.
-Assume a distance between the O-RU and O-DU around 10 km, the distance between O-DU and O-CU around 80 km, not greater than the distance from O-CU to the network around 200 km \cite{oranD1}.
-Then, assuming the fronthaul, midhaul and backhaul are connected with fiber optics and $c$ is the speed of like, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1$ ms.
-
-The following is a brief calculation of the transmission delay to show that its contribution to the total delay is negligible and does not affect the optimization.
-In URLLC and mMTC, the mean packet size may be between 20 to 32 bytes, while the minimum data rate is assumed to be $1\ bps/Hz \times BW (180\ KHz)$.
-Thus, the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{1 \times 180 \times 10^3} < 0.1\ ms$, and $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$.
-For eMBB, the packet size may be 100 times larger and the delay does not exceed 0.6 ms.
-Therefore, in the following, we assume that the total delay is approximate to the processing delay ($T^{\text{\text{tot}}} \approx T^{\text{proc}}$).
-%Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
-%\begin{equation}
-%T^{\text{\text{tot}}} \approx T^{\text{proc}}
-%\end{equation}
-\subsubsection{Processing Delay}
-Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ service (or slice).
-Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
-Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$), i.e., $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
-This is because the amount of data transferred along the route (regardless of frame changes) is constant.
-In fact, according to Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still Poisson with rate $\alpha_{s}$.
-It is assumed that there are load balancers in each layer for each service to divide equally the incoming traffic to VNFs. %\cite{frdl,luong2018novel,luong2018novel1}.
-Suppose the baseband processing of each VNF is modeled by an M/M/1 processing queue.
-%Since the system's arrival packets are from many independent sources.
-Moreover, the impact of a single packet on the system's performance is minimal.
-Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process.
-Therefore, we suppose that service times are exponentially distributed [36].
-In addition, since the services are isolated, the UEs in each service have the same priority, and the processing delays of each service are independent of the other services; Therefore, one service could have a higher priority, affecting the whole optimization, and the M/M/1 queue theory is still validated.
-Each packet is processed by one of the VNFs of the corresponding slice.
-Therefor, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, and can be respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
-\begin{align}
-T_{s}^{\text{DU}} &= 1/(\mu_s^d - \alpha_{s}/{M_s^{d}}),\\
-T_{s}^{\text{CU}} &= 1/(\mu_s^c - \alpha_{s}/{M_s^{c}}),\\
-T_{s}^{\text{UPF}} &= 1/(\mu_s^u - \alpha_{s}/{M_s^{u}}),
-\end{align}
-where $M_s^{d}$, $M_s^{c}$ and
-$M_s^{u}$ represent the number of VNFs in O-DU, O-CU-UP and UPF, respectively.
-Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service times of the O-DU, O-CU, and the UPF layers, respectively. The arrival rate of each VNF for each slice
-$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.
-
-On the other hand, arrival data rate of wireless link for each UE $i$ of service $s$ is $\lambda_{u(s,i)}$, thus $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
-Moreover, the service time of transmission queue for UE $i$ requesting service $s$ has
-an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.
-Therefore, the mean delay of the transmission layer for UE $i$ in slice $s$ is
-\begin{equation}
- T_{u(s,i)}^{\text{RU}} = 1/(R_{u(s,i)} - \lambda_{u(s,i)}).
-\end{equation}
-we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. %{\color{red} what results in this approximation?}
-%Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).
-\vspace{-3mm}
-\subsection{VNF Power}
-\vspace{-1mm}
-%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.}
-Assume the power consumption of each VNF in each logical node (O-DU, O-CU, and UPF) in the slice s, is represented by $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.
-Then, the system's total cost of energy of all the slices can be represented as $\textstyle \phi_{\text{\text{tot}}} = \sum_{s=1}^{S}\phi_{s}$,
-%\begin{equation*}
-%\textstyle \phi_{\text{\text{tot}}} = \sum_{s=1}^{S}\phi_{s},
-%\end{equation*} and $\phi_{s}$ is obtained from $\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d.$
-%\begin{equation}
-%\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d.
-%\end{equation}
-
-A significant issue facing the industry is reducing energy consumption.
-Data centers are one of the most energy-consuming.
-As a result, restrictions are placed on data centers' energy, including VMs.
-So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers.
-So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{\text{max}}$).
-\vspace{-3mm}
-\section{Problem Statement} \label{prS}
-\vspace{-1mm}
-Suppose the slice $s$ (which is assigned to service s) has a priority factor $\delta_s$ (based on the priority of its hosting service) where $\sum_{s=1}^S \delta_s =1$.
-The priority factor of each slice is obtained according to the service level agreement to promote a fairness in the system.
-%{\color{red} explain why you introduce priority factor.}
-This paper aims to maximize the sum-rate of all UEs subject to QoS constraints as follows %{\color{red} where did you define the objective? what is R bar?}
-\begin{subequations}\label{problem}
-\begin{alignat}{4}
-\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}} \ \\
-\text{subject to} \quad  &  P_r \leq P^{\text{max}}_{r} \quad \forall r,
- \label{c11} \\
-&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i, r, s, k,\label{c12} \\
-&p_{r,u(s,i)}^{k}  \leq P_{s}^{\text{max}}  \quad \forall i, r, s, k,\label{c12-1} \\
-&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{\min} \quad \forall s, \label{c13} \\
-%&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
-& C_r \leq C^{\text{max}}_r \quad \forall r, \label{c15}\\
-&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{\text{max}}_{s} \quad \forall i, s,\label{c16} \\
-& \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
-& \bar{\mathcal{R}}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i, s,\label{c16-2} \\
-& 0 \leq M_s \leq M^{\text{max}}_s  \quad \forall s,\label{c16-3}\\
-& \phi^{\text{\text{tot}}}  \leq \phi^{\text{max}}, \label{c19} \\
-%& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
-& \sum\nolimits_{\forall r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{c17}  \\
-& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s, i , r, \label{c18-1} \\
-& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s, i , r, \label{c18} \\
-& g^r_{u(s,i)} \in \{0,1\} \quad \forall s, i, \label{c20}  \\
-& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s, i. \label{c21}
-\end{alignat}
-\label{constraints}
-\end{subequations}
-Here, $\bar{\mathcal{R}}_{u_{(s,i)}}$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
-In addition, $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , i, r, k $, is the four-dimensional (4D) matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , i, r, k$ indicates the binary 4D matrix for the PRB association.
-Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , i, r$ is a binary three dimensional (3D) matrix for the O-RU association.
-Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is a matrix containing the number of VNFs in each layer of slice.
-Notice that
-\eqref{c11}, \eqref{c12} and \eqref{c12-1} limit the power of each O-RU and UE.
-Also, \eqref{c13} constrains the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and URLLC, to be greater than a threshold. Meanwhile,
-\eqref{c15} and \eqref{c16} represent the limited fronthaul capacity and the limited end-to-end delay of the received signal, respectively.
-\eqref{c16-1} and \eqref{c16-2} are related to the stability of the M/M/1 queue,
-\eqref{c16-3} restrictes the number of VNFs in each slice due to the limited resources, while
-%\eqref{c16} is a reliability condition that the delay in each layer should be less than the threshold.
-\eqref{c17} and \eqref{c18-1} guarantee that the O-RU and PRB are associated with the UE, respectively.
-Also, \eqref{c18} ensures that each PRB can not be assigned to more than one UE associated with the same O-RU, \eqref{c19} indicates that the fixed cost of energy of VNFs in each slice does not exceed the threshold, while \eqref{c20} and \eqref{c21} constrain $\boldsymbol{E}$ and $\boldsymbol{G}$ to be binary matrices.
-\vspace{-3mm}
-\subsection{PRB Scheduling}\label{prb}
-\vspace{-1mm}
-In this section, we provide a brief study on the problem of PRB scheduling which can be completed in two steps to eliminate the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
-Firstly, we should assign the PRBs to the slices.
-Secondly, we assign PRBs of slices to UEs, find the optimal number of VNFs for each slice, allocate power of UEs, and assign O-RU to UEs, which uses the proposed Algorithm \ref{proAlg}.
-Suppose, $\mathcal{R}_{{s}}^{\min}$, and $\mathcal{R}_{{s}}^{\text{max}}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
-Firstly, we need to find the average PRB number used by the UEs in each service.
-Since mMTC and URLLC require usually short packet transmissions, each UE in mMTC and URLLC requires 1 PRB.
-So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs.
-For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = B\log_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SINR of UEs in slice s.
-Therefore, the minimum number of PRBs that slice s with $U_s$ UEs requires is $K_s^{\min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\text{max}}}}\rceil$. 
-Moreover, the maximum number of PRB that the slice s with $U_s$ UEs requires is $K_s^{\text{max}} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\min}}}\rceil$.
-Also, $K_s = (K_s^{\min}+K_s^{\text{max}})/2$ is the average number of required PRBs in slice s.
-We aim to obtain the number of PRBs assigned to each slice $s$ ($\bar{K_s}$) by solving 
-\begin{subequations}\label{prob:prb}
-\begin{alignat}{4}
-\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s K_s \ln(\bar{K_s}) \ \\
-\text{subject to} \quad  & \sum_s{\bar{K_s}} \leq K
- \label{prb0}, \\
-& K_s^{\min} \leq \bar{K_s}  \leq K_s^{\text{max}}  \quad \forall s \in S_1,\label{prb1} \\
-&  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3.\label{prb2}
-\end{alignat}
-\label{constraints}
-\end{subequations}
-We use logarithms to assign PRBs to all slices to make them equally fair, since proportional fairness is achieved by maximizing the log utility function \cite{marabissi2019highly}.
-Equation \eqref{prb0} illustrates that the sum of PRBs of slices can not exceed the maximum number of PRBs ($K$).
-Equation \eqref{prb1} restricts the number of PRBs of eMBB slices and \eqref{prb2} limits the number of the PRBs of URLLC and mMTC slices.
-By relaxing $\bar{K_s}$, the objective function and constraints become convex and can be solved using the Lagrangian function.
-\vspace{-3mm}
-\subsection{Slice Management}
-\vspace{-1mm}
-In this subsection, we will look at the life cycle of network slicing on a practical level. 
-The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages \cite{ETSI2}:
-\begin{itemize}
-\item Preparation phase: the operator plans to create a network slice instance (NSI) by designing the its template, onboarding users, and preparing the environment.
-Also, the evaluation of requirements is performed in this step.
-\item Commissioning phase: the NSI is created, and the requirements are considered and allocated to the slice.
-\item Operation phase: the NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated.
-As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
-\item Decommissioning phase: an NSI that is decommissioned no longer exists after this phase.
-\end{itemize}
-Since the requirements evaluation is considered in the preparation phase, we need an algorithm to estimate the UE traffic in the system at different times.
-Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs, PRB assignment of UEs for each slice, and the total power requirements.
-In this phase, we use our algorithm to calculate resources after estimating the system's traffic.
-As shown in Fig.
-1, we have three different slices for eMBB, URLLC, and mMTC.
-The system must prepare VNFs for MAC/RLC functions in O-DU, PDCP/SDAP functions in O-CU, UPF, SMF, and AMF functionality layers for each slice.
-Moreover, O-RU, high PHY in O-DU, and O-CU-CP are shared between slices.
-Thus, we do not require evaluating and preparing for the share environments and platforms in the network slicing cycles.
-Moreover, the estimation of PRB and power is needed based on the proposed algorithm.
-After evaluating, assessing, and preparing the resources and environments for each slice, the commissioning phase is started.
-In this phase, the slices are created based on the previous phase estimation.
-These created slices are activated in the operation phase, and the actual resources are assigned based on the proposed algorithm.
-It is possible to modify the slice's resources even when the evaluation changes during the operation phase. 
-If we need to remove a slice or any service not used in a zone, the unshared resources are released in the decommissioning phase.
-%\vspace*{-1em}
-\vspace{-3mm}
-\section{Proposed Algorithm}\label{proAlg}
-\vspace{-1mm}
-In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
-We applied some simplifications and use an iterative heuristic algorithm to solve the problem.
-We solve this problem in two levels, iteratively, until it converges \cite{ali2018joint}.
-
-At the first level, the main purpose is to assign appropriate PRBs and power to the UEs.
-Furthermore, sufficient activated VNFs are assigned to each slice.
-Hence, at this level, we would like to obtain the variables $\boldsymbol{P}, \boldsymbol{E},$ and $\boldsymbol{M}$.
-Despite the simplification of the problem
-\eqref{problem}, it is still NP-hard and challenging to solve. Therefore,
-we relax the variable $\boldsymbol{E}$ \cite{lee2018dynamic,ali2018joint} and reformulating the constraint \eqref{c16},
-to turn them into a jointly-convex problem; Afterward, we solve this problem using a conventional dual Lagrangian method.
-In the second level, finding the optimal O-RU association, $ \boldsymbol{G}$, is concerned with the fixed parameter of power, PRB allocation, and the number of activated VNFs.
-We repeat this procedure until the algorithm converges.
-\vspace{-3mm}
-\subsection{Sub-Problem 1}\label{sub1}
-\vspace{-1mm}
-Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
-Here, we first simplify and relax the parameters to convexify the problem.
-As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{\text{max}}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
-for $\rho_{u(s,i)}^{k}$.
-Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.
-
-Suppose $\hat{\rho}_{r,u(s,i)}^{k}\!\!=\!  P_{s}^{\text{max}}|{\bold{h}_{r,u(s,i)}^{H \: k}}\! \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2/(BN_0)$.
-We replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
-So, a lower bound for \eqref{eq11} is given that is a concave function.
-\begin{subequations}\label{lb1}
-\begin{alignat}{4}
-\bar{\mathcal{R}}_{u(s_j,i)}^{r} &\!\!=\!\!B\! \sum_{k=1}^{K_{\!s_j}}\!\!{e}_{u(s_j,i)}^{k} (\log_2({\!1\!+\! \bar{\rho}_{u(s_2,i)}^{k}})\!-\! \hat{\zeta}_{u(s_j,i)}^{k}\!),\!\\
-\bar{\mathcal{R}}_{u(s_j,i)} &\!\!= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r},\\
- \hat{\zeta}_{u(s_j,i)}^{k} &\!\!= \log_2({e})Q^{-1}(\epsilon) \sqrt{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}/N_{u(s_j,i)}^{k}},\\
- \hat{\mathfrak{C}}_{u(s_j,i)}^{k} &\!\!= 1 - 1/(1+\hat{\rho}_{u(s_j,i)}^{k})^2.
-\end{alignat}
-\end{subequations}
-Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability.
-We notice that it makes the formulation simpler.
-However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner.
-Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $.
-Moreover, as mentioned before,
-the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$).
-So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$.
-Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
-These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
-As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
-Using the above assumption, we have $T^{\text{DU}}_{s} = T^{\text{CU}}_{s} = T^{\text{UPF}}_{s}$ and we have
-$T^{\text{proc}}_{s} =  T^{\text{RU}}_{s} + T^{\text{DU}}_{s} + T^{\text{CU}}_{s} + T^{\text{UPF}}_{s}$. So,
-$T^{\text{proc}}_{s}=  T^{\text{RU}}_{s} + 3\times T^{\text{DU}}_{s}.$
-%\begin{equation}
-%\begin{split}
-%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
-%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
-%\end{split}
-%\end{equation}
-
-The problem \eqref{problem} is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and by relaxing the variables, the problem is also non-convex; therefore, this problem is NP-hard.
-Solving the problem is not trivial.
-To solve the problem by inspiring Stackelberg, we reformulate the equation in \eqref{c16} to reduce one of the variables (i.e., $M_s$) that can be solved after obtaining the rate of UEs.
-We notice that $M_s$ is similar to the followers in Stackelberg Competition, and power and PRB assignment are identical to the leader.
-So, the new problem has two variables: power and PRB assignment.
-This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds \eqref{lb1}.
-The objective function and constraints of the problem are convex and can be solved by the Lagrangian function.
-After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs in each slice ($M_s$).
-
-In the following, we define a lemma to find the upper and lower bounds for the optimal number of VNFs based on the achievable rates.
-Afterward, we obtain the formula to attain the optimal number of VNFs.
-\begin{lemma}\label{lemma1}
-The optimal number of VNFs in each slice s can be achieved by the
-$M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s$.
-where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{\text{max}}_s R_{u(s,i)}-T^{\text{max}}_s\lambda_{u(s,i)} -1)}{(T^{\text{max}}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
-\end{lemma}
-%{\color{red} add one sentence before lemma to motivate why you need this lemma. The whole part is a lemma? It is too long. Where is the proof?}
-\begin{proof}
-In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as
-%$ \forall i,\forall s$
-\begin{subequations}
-\begin{alignat}{4}
-&T^{\max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}},  \\
-&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }.
-\end{alignat}
-\end{subequations}
-Also from equations in \eqref{c19}, \eqref{c16-1} and \eqref{c16-3}, we have
-\begin{equation}
-\alpha_s/\mu_s\leq M_s \leq \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}.
-\end{equation}
-We denote $ \mathfrak{M}_s= \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}$.
-Thus, if we restrict constraint \eqref{c16} to equality, constraint \eqref{c16} is still valid.
-Also, we have the following inequality
-\begin{equation}\label{eqDelay}
-\alpha_s / \mu_s \leq \mathtt{M}_{u(s,i)} \leq \mathfrak{M}_s,
-\end{equation}
-where $\mathtt{M}_{u(s,i)}=\frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s}\ge 0$ since
-the numerator and the denominator both have the same sign.
-In the numerator, according to \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
-If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{\max}_s \geq 1$, the numerator will be positive.
-$(R_{u(s,i)}-\lambda_{u(s,i)})T^{\max}_s \geq 1$ since the order of $T^{\max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{\max}_s$.
-Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{\max}_s$.
-So the numerator will be positive.
-In the denominator, we can say that $(T^{\max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,
-$\mu_s \geq 0$ and
-$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{\max}_s$ as mentioned above.
-%Therefore, we need to have the constraint below.
-%\begin{equation}\label{constraint16}
-%\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
-%\end{equation}
-The left side of the equation \eqref{eqDelay}, leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}.
-For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ given by
-%\begin{equation}\label{RM}
-%\begin{split}
-%\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
-% \mathit{\langle}_{u(s,i)}&=(T^{max}_s\mu_s-3)\lambda_{u(s,i)} + \mu_s,\\
-%\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
-%\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
-%\end{split}
-%\end{equation}
-%\begin{subequations}\label{RM}
-\begin{align}\label{RM}
-\mathcal{R}_{u(s,i)} \geq \lambda_{u(s,i)}+ 3/(T^{\max}_s&\mu_s-\alpha_s T^{\max}_s/\mathfrak{M}_s-3)+\nonumber\\
-&+ 1/T^{\max}_s=\varpi_{u(s,i)}.
-\end{align}
-%\end{subequations}
-%In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
-Thus, to obtain the optimal number of activated VNF in each slice, we need to find the maximum of the
-$\mathtt{M}_{u(s,i)}$ in each slice as $M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s $.
-%\begin{equation}
-%M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
-%\end{equation}
-\vspace{-3mm}
-\end{proof}
-Despite simplifying the problem in \eqref{problem}, it is still non-convex and hard to solve.
-Therefore, the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
-Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.
-
-In order to transform \eqref{problem} into a convex optimization problem in standard form, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint
-\eqref{c15} is changed to
- $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{\max}}$.
-The combination of equations \eqref{c11} and \eqref{c15} leads to the following equation
-\begin{equation} \label{pr11}
-P_r\leq \zeta_r= \min\{P_{\max}, \sigma_{q_r}^2\times 2^{C^r_{\max}} \}. 
-\end{equation}
-Moreover, the combination of equations in \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
-\begin{equation}\label{RConstr}
-\mathcal{\bar{R}}_{u_{(s,i)}}\!\!\geq\!\eta_{u_{(s,i)}}\!\!\!=\! \max\{\mathcal{R}_{u_{(s,i)}}^{\min}\!, \lambda_{u_{(s,i)}}\!\!+\frac{1}{T^s_{\max}}\!, \varpi_{u(s,i)} \}. 
-\end{equation}
-Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$, $\boldsymbol{\mathfrak{q}}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
-The Lagrangian function is written as
-\begin{align}\label{lagrang}
-&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\delta_s\mathcal{\bar{R}}_{u_{(s,i)}}\nonumber\\
-&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\nonumber\\
-&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\Big(\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\!-\!
-\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)}\!-\!1) \nonumber\\
-&+   \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}+ \mathfrak{q}^k_{r,u(s,i)} (P^{\max}_{s}- p^k_{r,u(s,i)})\Big)\nonumber\\
-&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}\Big(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1\Big).
-\end{align}
-%{\color{red} Motivate the lemma. separate proof and lemma}
-\vspace{-2mm}
-\begin{lemma}
-The derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{P}$ and $\boldsymbol{E}$ give the KKT conditions to obtain the optimal value of these two variables \cite{lee2018dynamic,ali2018joint}.
-\end{lemma}
-\vspace{-4mm}
-\begin{proof}
-Assume UE $i$ in slice $s$, associated with O-RU $r$, is allocated to PRB $k$  (i.e., $e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition
-\begin{align}\label{deriveP}
-\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}}\!\!=\!
-(\delta_s \!+\!
-\mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\!\!+\!
-(\mathfrak{s}^k_{r,u(s,i)}\!
-\!-\!\mathfrak{D}_{r,u(s,i)}^{k})\!=\!0,
-\end{align}
-where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follows
-\begin{subequations}
-\begin{alignat}{4}
-\mathfrak{D}_{r,u(s,i)}^{k} &\!\!= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
-\mathfrak{B}_{r,u(s,i)}^{k} &\!\!= \!B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}\mathfrak{S}_{r,u(s,i)}^{k}\!/\!\ln(2),\\
-\mathfrak{S}_{r,u(s,i)}^{k} &\!\!= ({|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}\!+\!BN_0\!+\! I_{r,u(s,i)}^{k})^{\!-1}.
-\end{alignat}
-\end{subequations}
-Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
-Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
-We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
-The optimal power is as follow.
-\begin{align}
-&p_{r,u(s,i)}^{k} =\nonumber\\ 
-&\bigg[\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ \ln(2) (\mathfrak{D}_{r,u(s,i)}^{k}\!\!-\!\mathfrak{s}^k_{r,u(s,i)})}\!
--\!\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}\bigg]^+.
-\end{align}
-
-Also $[a]^+ = \max(0,a)$.
-In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
-\begin{align}\label{deriveE}
-\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} \!\!=\!
-&\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s\!+\!\mathfrak{h}_{u_{(s,i)}}\!)\!-\!
-\mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\nonumber\\
-&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.
-\end{align}
-So, the optimal $\boldsymbol{E}$ is obtained using the KKT conditions, which require solving
-\begin{align}\label{deriveE1}
-e_{r,u(s,i)}^{k}  (\mathfrak{F}^{k}_{r,u(s,i)} \!-\!\mathfrak{v}^{k}_{r,u(s,i)}\! -\! \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )\! =\! 0,
-\end{align}
-where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
-Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follows
-\begin{equation}
-e_{r,u(s,i)}^{k} =
-  \begin{cases}
-      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S, \\
-      0 & \text{otherwise,}
-    \end{cases}
-\end{equation}
-where $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
- \end{proof}
-Thus, the user in slice $s$ that has  the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to PRB $k$.
-Since just one PRB can be allocated to a UE between those UEs (regardless of the services), that is associated to the same O-RU.
-The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
-The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
-\vspace{-3mm}
-\subsection{Sub-Problem 2}\label{sub2}
-\vspace{-1mm}
-After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.
-For this, assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, so we want to find $\boldsymbol{G}$.
-Next, we introduce a greedy algorithm that assigns an O-RU to each UE.
-
-\begin{algorithm}[t!]
-\small
-%\setstretch{1.}
-\caption{Greedy Algorithm for Assignment of O-RU to UEs (GAA)}\label{alg1}
-\begin{algorithmic}[1]
-\State Set $g^r_{u(s,i)} = 0$, $\mathfrak{C}_r = \mathfrak{t}_r,$ and ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$   $\forall s, \forall i, \forall r$.\label{31}
-\State Sort slices according to their $\delta_s$ in descending order
-\For {$s \gets 1$ to $S$}\label{33}
-\For {$i \gets 1$ to $U_s$}
-\State $RU = 0$
-\For {$r \gets 1$ to $R$}
-\State Acquire $\mathfrak{G}^r_{u_{(s,i)}} = \bar{\mathcal{R}}^r_{u_{(s,i)}}$
-\EndFor
-\State \textbf{end for}
-\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
-\While{$RU == 0$}
-\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$}
-\State Set $g^{r^*}_{u(s,i)} = 1$
-\State Set  $\mathfrak{C}_{r^*} = \mathfrak{C}_{r^*} - \psi_{{r^*},u(s,i)}$
-\State Set $RU = 1$
-\Else: ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $ 
-\EndIf
-\State \textbf{end if}
-\EndWhile
-\State \textbf{end while}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for} \label{34}
-\end{algorithmic}
-\end{algorithm}
-%
-\textit{Greedy Algorithm Assignment (GAA):}
-The following is a reformulated version of the problem.
-\begin{subequations}\label{problem2}
-\begin{alignat}{4}
-\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R} \delta_s g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
-\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r,
- \label{p11} \\
-& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{p12}\\
- & g^r_{u(s,i)} \in \{0,1\} \quad \forall s, i, \label{p13}
-\end{alignat}
-\end{subequations}
-where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
-and $\mathfrak{t}_r = \zeta_r- \sigma_r$  because of the equations \eqref{pr11} and \eqref{pr}.
-Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
-%The problem \eqref{problem2} is an integer linear programming.
-%By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
-The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.
-We solve this problem using the heuristic GAA Algorithm~\ref{alg1}, which is a greedy algorithm \cite{akccay2007greedy,lee2018dynamic}.
-Firstly, we set all the variables to zero ($g^r_{u(s,i)} = 0, \quad \forall s, i, r$).
-Then we define the parameter ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$.
-This parameter is used as a set of O-RUs that can be assigned to the UE $i$ in slice $s$, which initially includes all the O-RUs (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}, \forall s, i$ ).
-Also we introduce another parameter $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
-which is the knapsack capacity of each O-RU.
-Next, we sort all the slices based on their priority.
-Afterward, based on the sorting of the UEs,
-we assign the O-RU that provides the highest achievable data rate for each UE on the condition that the value of the desired UE ($\psi_{r,u(s,i)}$) does not exceed the knapsack capacity of each O-RU ($ \mathfrak{C}_r$).
-If it exceeds the capacity of the desired O-RU, we remove the specific O-RU from the set of O-RUs that can be assigned to that UE (${\mathfrak{B}}^{rem}_{u_{(s,i)}} = {\mathfrak{B}}^{rem}_{u_{(s,i)}} \setminus \{{r^*}\} $).
-Then, the O-RU with the highest achievable data rate from the new set of O-RUs ${\mathfrak{B}}^{rem}_{u_{(s,i)}}$ is selected.
-The complexity of sorting S slices based on their priority is $O(S\log(S))$.
-Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ as the whole number of UEs in the system.
-The complexity order of this algorithm is about $O(S\log(S)) + O(R\times \mathfrak{N})$.
-%$O(N\times \mathfrak{N})$
-
- \begin{algorithm}[t!]
- \small
-\caption{Iterative algorithm for the baseband resource allocation and VNF activation (IABV)}\label{alg2}
-\begin{algorithmic}[1]
-\State  Set the maximum num. of iter. ${\text{I}}_{\max}$, convergence condition $\epsilon > 0$ \label{a21}
-\State  Assign Users to O-RU randomly (Initialize $\boldsymbol{G}$) \label{a22}
-\For {$i \gets 1$ to ${\text{I}}_{\max}$}\label{23}
-\State Acquire $\boldsymbol{P}^{(i)}$, $\boldsymbol{E}^{(i)}$ and $\boldsymbol{M}^{(i)}$ using Lagrangian function and sub-gradient method based on \eqref{sub1}
-\State Update $\boldsymbol{G}^{(i)}$   based on algorithm GAAOU \eqref{alg1} in  \eqref{sub2}
-\If {the algorithm converged with the tolerence of $\epsilon$}
-\State Break
-\Else:   Continue the algorithm
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for} \label{24}
-\end{algorithmic}
-\end{algorithm}
-\vspace{-3mm}
-\subsection{Iterative Proposed Algorithm}
-%\vspace{-1mm}
-In Sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted.
-Here, the iterative algorithm for the whole problem is demonstrated.
-Firstly, we fixed $\boldsymbol{G}$ to achieve $\boldsymbol{P}$ and $\boldsymbol{E}$, using the Lagrangian method and the KKT conditions.
-Afterward, $\boldsymbol{G}$ is updated using the GAA algorithm. This process is repeated until it converges.
-The whole algorithm (IABV method) is depicted as follows (Algorithm \ref{alg2}).
-
-\subsubsection{Complexity Order}
-The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}U_S$.
-Also, assume that the algorithm converges after $T_{conv}$ times.
-As we mentioned before, the complexity order of the first sub-problem is about $O(T_{conv} \times \mathfrak{N} \times K)$
-and the complexity order of the second sub-problem is about $O(S\log(S)) + O(R\times \mathfrak{N})$.
-So the complexity of the main problem \eqref{problem} is $O(T_{conv} \times \mathfrak{N} \times K \times (S\log(S)+R\mathfrak{N}))$.
- \begin{algorithm}
- \small
-\caption{Fast Algorithm (FA) to check convergence}\label{alg3}
-\begin{algorithmic}[1]
-\State Set count = 0
-\State Set $p_{r,u(s,i)}^{k} = 0$, $e_{r,u(s,i)}^{k} = 0$ and $g_{u(s,i)}^{r} = 0$ $\forall r,k,s,i$
-\For{$s \gets 1$ to $S$}
-\For{$i \gets 1$ to $U_s$}
-\State count = count +1
-\State $r^* = \argmin_r d_{r,u(s,i)} \quad \forall r$
-\State $g_{u(s,i)} ^{r^*}=1$
-\State temp =mod(count, K)
-\If {temp=0 }
-\State $e_{r^*,u(s,i)}^{K} = 1 $
-\State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
-\Else: $e_{r^*,u(s,i)}^{\text{temp}} = 1 \quad \forall r$
-\State Set $p_{r^*,u(s,i)}^{\text{temp}} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
-\EndIf
-\State \textbf{end if}
-\EndFor
-\State \textbf{end for}
-\EndFor
-\State \textbf{end for}
-\end{algorithmic}
-\end{algorithm}
-\subsubsection{Convergence Analysis}
-Due to limited system resources, we have limits on VNFs' power, UE or O-RU power, fronthaul capacity, etc.
-As a result, the objective function, which is the aggregate throughput, cannot exceed its optimal value and become infinite.
-Therefore, if the aggregate throughput is infinite and increases without limit, the resources must also be unlimited.
-Hence, the system has an optimal solution: its maximum aggregate throughput in the feasible region.
-
-Consequently, we can guarantee the convergence of the iterative algorithm if the objective function is the ascending function concerning the number of iterations and has an upper bound.
-Thus, it will converge to its optimum value if it is a strictly ascending function and to its local optimum if it is a non-monotonically ascending function.
-% \cite{gholipoor2020resource}.
-
-Consider the aggregate throughput as $\mathcal{T(\bold{P},\bold{E},\bold{G})} =\sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}}$.
-In the first step of the iteration i of the algorithm \ref{alg2} (IABV), we have $\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1})$.
-In this step, optimal power and PRB allocation are obtained for the fixed O-RU association, so we have
-$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
-In the second step of the iteration i, the optimal O-RU association is achieved to maximize the aggregate throughput. So we have this inequality
-$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
-As a result, we have
-$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
-Hence, in each step of the iteration, the aggregate throughput increased.
-Note that $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*})$ is the achieved aggregate throughput
-for all the feasible resource allocation solutions of $\{\bold{P},\bold{E},\bold{G}\}$.
-So, $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i})$ and thus in each iteration, the aggregate throughput can not be larger than the optimal solution.
-
-In addition, if we assume that the interference is set to be zero ${I}_{r,u_{(s,i)}}^{k}=0$,
-and we suppose that each UE has the maximum power $p_{r,u_{(s,i)}}^k = P_{s}^{max}$,
-and we consider that all PRB is assigned to all UE $e_{r,u_{(s,i)}}^k = 1 \forall s,\forall i$
-and each UE is assigned to the nearest O-RU with the best channel quality. So, the solution of this allocation, is the upper bound
-for the aggregate throughput.
-Thus,
-we can guarantee the local convergence of our iterative algorithm since the objective function $\mathcal{T}$ is the ascending function concerning the number of iterations
- and it has the upper bound which is not infinite.
-
-In addition, to extend our solution to the global optimum, we must prove that the algorithm monotonically increases in the non-optimal set of solutions and is Lipschitz monotone contraction mapping.
-Here, we briefly discussed our algorithm's global convergence for a low interference system.
-
-In the low interference system, the PRB and VNF assignment is obtained straightforwardly, and the first step for solving the problem is power allocation. Given fixed O-RU association, we have
-$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$ (strictly increase). 
-Notice that for the power allocation problem, the objective function is convex, and the convex functions are Lipschitz monotone contractions. 
-However, in the second step of the algorithm, we can show as before that the algorithm is increased, but we can not talk about monotonically increases.
-Hence we have
-$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
-Nevertheless, the objective function is still Lipschitz monotone mapping. 
-Accordingly, we have 
-$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
-Therefore the objective function is the strictly ascending
-function concerning the number of iterations and has an
-upper bound.
-Consequently, the algorithm converges to the 
-global optimum solution in low interference.
-%\vspace*{-2em}
-%\vspace{-3mm}
-\section{Numerical Results}\label{NE}
-%\vspace{-1mm}
-In this section, firstly, we describe the initial points and the comparison algorithms.
-Then, we talk about the feasible region of our system model. Afterward, we illustrate the numerical results.
-%\vspace*{-1.7em}
-\vspace{-3mm}
-\subsection{The initial Points and The Comparison Algorithms}
-\vspace{-1mm}
-In this part, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method.
-We consider three network slices for eMBB, URLLC, and mMTC services.
-Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in Fig. \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
-
-\begin{figure}
-  \centering
-    \includegraphics[scale = 0.30]{fig/cell.pdf}
-    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-    \vspace{-1mm}
-  \caption{O-RU placement in a cell}
-  \vspace{-2mm}
-  \label{fig:cell}
-\end{figure}
-
-Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent.% \cite{gholipoor2020cloud}.
-Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
-We consider 25 PRBs in the network. The packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes \cite{ETSI1}.
-The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the URLLC  service is $\lambda  = 0.2Mbps$.
-Also, the quantization noise is assumed to be $10^{-13}$.
-Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
-and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.
-The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2,IMT, ETSI1}.%\cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.
-
-Finding a feasible initial value is almost tricky. We use a fast method discussed in \ref{fr} to overcome this challenge. 
-Two different methods are used to compare the performance of the proposed method (IABV) and show the optimality of our approach.
-The first one is a baseline scheme, which uses random PRB allocation.
-Therefore, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE.
-Also, the association of O-RU is carried out based on distance.
-It means that each UE is assigned to the nearest O-RU.
-The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
-After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma \eqref{lemma1}.
-\begin{table}%[H]
- \caption {Simulation Parameters} \label{table:1a}
- \begin{center}
- \scalebox{0.9}{
-  \begin{tabular}{l  l }
-  \toprule
-\textbf{Parameter} & \textbf{Value} \\ [0.5ex]
-  \toprule\toprule
-  noise power & -174 dBm\\
-
-  bandwidth & 180 KHz  \\
-
- maximum transmit power of each O-RU & 40 dBm \\
-
-  maximum delay for eMBB &  4 msec \\
-
-    maximum delay for URLLC &  1 msec \\
-
-  maximum delay for mMTC &  5 msec \\
-
-  maximum fronthaul capacity  & 46 bps \\
-
-  minimum data rate for eMBB &  20 bps \\
-
-   minimum data rate for URLLC and mMTC &  2 bps \\
-
-   maximum received power for mMTC &  20 dBm \\ [.5ex]
-
-    maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]
- \toprule
- \end{tabular}}
- \vspace*{-1.em}
- \end{center}
- \end{table}
-For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic} and named it the dynamic resource allocation scheme (DR scheme).
- We have services with different QoS in this work, similar to tenants with different QoS introduced in \cite{lee2018dynamic}.
-Therefore, we can use the DR scheme similar to the FBDR method adapted to our conditions for comparison.
-Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
- Since we do not talk about O-DU and O-CU capacity, we use the dynamic resource allocation scheme (DR scheme) algorithm and do not consider BBU capacity.
- In the DR scheme, PRB and power are dynamically allocated.
-The number of VNFs is obtained from the simulation.
-The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm \ref{alg1} (GAA algorithm) for O-RU assignment.
-The figures in \cite{lee2018dynamic} show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area.
-Notice that our proposed algorithm performs better than the DR scheme.
-\vspace{-3mm}
-\subsection{Feasible Region}\label{fr}
-\vspace{-1mm}
-Applying the correct initial point is crucial in making the system feasible and convergent.
-Therefore, we investigated the non-converging and converging simulation for models with fixed initial parameters and UE random channel gains.
-We experimentally found that in non-converged simulations, there are UEs at the edge of the boundaries or far away from the O-RU and have a weak channel gain.
-One solution is to eliminate UEs who undermine system convergence.
-For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interference.
-Another solution is to remove the simulations in the Monte-Carlo that do not converge using the fast algorithm (FA) to check the convergence before
-the proposed algorithm (IABV).
-Therefore, if more than half of the iterations have a feasible solution for the initial condition, the simulation can be displayed as a feasible model.
-If the conditions in \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
-Assume, the number of UEs is $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_s}1$,
-the number of PRBs is $K$, and the distance between the $r^{th}$ O-RU to the UE i in slice $s$ is $d_{r,u(s,i)}$.
-The FA algorithm is represented in Algorithm \ref{alg3}.
-The complexity order of this algorithm is $O(R\times \mathfrak{N})$ which is remarkably lower than the complexity order of the IABV method.
-In the FA algorithm, the O-RU association is based on the distance of the UE to the O-RU.
-Each UE is associated with the nearest O-RU.
-Also, the power of each UE is set to be the minimum of the maximum power of each UE and the maximum power of each O-RU divided by the total number of UEs ($\min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\}$).
-Moreover, the allocation of PRBs to UEs is based on dividing the number of UEs by the total number of PRBs.
-\vspace*{-3mm}
-\subsection{Performance Results}
-\vspace*{-1mm}
-In Fig.
-3, the aggregate throughput is plotted versus the number of UEs in each service for these three methods.
-Suppose we have one service instance for each type of service, so we have three various services in this figure.
-Also, we have between 6 to 48 UEs in the system.
-Here, we did not consider the priority. The figure presented that the proposed method, IABV, is $18.6\%$ higher throughput than the baseline scheme.
-As the number of UEs increases in each service, the aggregated throughput initially increases.
-Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
-
-\begin{figure*}[!htb]
-	\centerline{%
-		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.4]{fig/Arate_ue1_1n.eps} &
-			\includegraphics[scale = 0.4]{fig/vnfNum1n.eps} &
-			\includegraphics[scale = 0.4]{fig/RatePower1n.eps} \\
-			\scriptsize Fig.
-3~Aggr.
-throughput vs.
-number of UEs in each service & \scriptsize  Fig.
-4~Number of VNFs in each service vs.
-arrival rate & \scriptsize Fig.
-5~Aggr.
-throughput for eMBB vs.
-maximum  power
-	\end{tabular}}
-	%\caption{Global caption.}
-	\label{label}
-	\vspace*{-3mm}
-\end{figure*}
-
-Fig.
-4 depicts the number of activated VNFs for five different mean service times of one URLLC service vs.
-the mean arrival time for 12 UEs.
-This figure presents that as the mean arrival rate increases, the number of activated VNF increases.
-Moreover, the number of activated VNFs decreases when the mean service rate increases.
-
-In Fig.
-5, the aggregate throughput is depicted vs.
-the maximum power of UE for three different instances of eMBB service using proposed method (IABV), DR scheme and the baseline scheme.
-Here, we suppose that we have 12 UEs in each service.
-We assume that these three services require 5bits/sec/Hz, 10bits/sec/Hz, and 15bits/sec/Hz.
-%In addition, We suppose that each O-RU can transmit three times of the maximum power of the UEs.
-As you can see in the figure, increasing the maximum power increases the aggregate throughput.
-Moreover, the proposed method (IABV), gives higher aggregate rates in compared to the DR scheme and the baseline scheme.
-
-\begin{figure*}[!htb]
-	\centerline{%
-		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.4]{fig/delay_newn.eps} &
-			\includegraphics[scale = 0.4]{fig/delay1_newn.eps} &
-			\includegraphics[scale = 0.4]{fig/AmmTCpowern.eps} \\
-			\scriptsize Fig.
-6~~Total Delay of a URLLC vs.
-the arrival rate of a UE  & \scriptsize Fig.
-7~~ Total Delay of a URLLC vs.
-arrival rate of a UE  & \scriptsize Fig.
-8~~Aggr.
-throughput vs.
-the number of mMTC UEs
-	\end{tabular}}
-	\vspace*{-3mm}
-	%\caption{Global caption.}
-	\label{label}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%
-Fig. 6 illustrates the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE and the number of UEs in the service for the proposed method (IABV).
-It is shown that the delay is an ascending function of the mean arrival rate (when the mean service time is fixed) and the number of UEs in the service.
-% In this figure, we assume that the maximum number of VNF for each slice is 50 and the maximum delay of each UE in a URLLC service is $0.5ms$. 
-%Also, the maximum number of PRB is considered to be 50.
- Moreover, we can see that the mean delay of a URLLC service
-does not reach the maximum threshold of the delay.
-
-%Moreover, we can see that the mean delay of a URLLC service increases almost linearly with the mean arrival rate of the packet transmission.
-%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.47]{delay_new.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Mean Total Delay of a URLLC Service vs. the Mean Arrival Rate of a UE in the Service for various number of UEs}
-%  \label{fig:6}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%5
-Fig.
-7 is the same as Fig.
-6 that presented the mean total delay of a UE in a URLLC service regarding the mean arrival rate of the UE for 20 UEs using three different methods.
-As you can see, the proposed method (IABV) outperforms the other scenarios.
-
-Fig. 8, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances. 
-Assume each UE in each mMTC service instance requires 0.1 bits/sec/Hz data rate and is not sensitive to the end-to-end delay. There is no restriction on fronthaul link capacity and the number of VNFs.
-%Moreover, to make the simulation feasible, we assume that the number of PRBs is as large as the system has low interference.
-%so we suppose there is a fixed  PRB allocation in the simulation that each UE is allocated to one PRB. There is no PRB with more than one UE allocation.
-The figure depicts that by increasing the number of UEs in each instance of the service, or by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput increases.
-%Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
-
-%%%%%%%%%%%%
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.4]{AmmTCpower.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput for mMTC services vs. Number of UEs in each Service for three different mMTC service instances}
-%  \label{fig:8}
-%\end{figure}
-%%%%%%%%%%%%
-Assume we have two types of eMBB service instances.
-In Fig.
-9, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances.
-Here we consider 4 UEs in each service.
-%We assume that the the fronthaul link and the end-to-end delay have no restrictions.
-The Fig.
-9 presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa.
-Also, we can realize from this figure that the aggregate throughput has the most significant value at the same priority.
-
-\begin{figure*}[!htb]
-	\centerline{%
-		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.4]{fig/priorityLastn.eps} &
-			\includegraphics[scale = 0.4]{fig/itern.eps} &
-			\includegraphics[scale = 0.4]{fig/iterD.eps} \\
-			\scriptsize Fig.
-9~~Throughput of eMBB services vs.
-priority of the first one  & \scriptsize Fig.
-10~~Aggregate throughput vs.
-number of iterations  & \scriptsize Fig.
-11~~Mean Delay time vs.
-number of iterations
-	\end{tabular}}
-	\vspace*{-3mm}
-	%\caption{Global caption.}
-	\label{label}
-\end{figure*}
-
-%%%%%%%%%%5
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.4]{priorityLast.eps}
-%  \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
-%  \label{fig:9}
-%\end{figure}
-%%%%%%%%%%%
-%In the figure \ref{fig:10}, the aggregate throughput is presented vs. the number of UEs for one service in a system by considering two different cloud restrictions and fronthaul restrictions.
-%In the graph of cloud restriction, we have the restrictions in O-DU and O-CU.
-%In the graph of fronthaul restriction, we have the restrictions in O-RU.
-%In the O-RU restriction graph, we assume that the fronhaul link is set to be 47 bits/sec/Hz (the variance of quantization noise is $10^{-13}$) , and the maximum power of each O-RU is 40 dBm.
-Also, the maximum power of each UE is set to be 35 dBm.
-Moreover, the minimum data rate for each UE in this service is 6 bits/sec/Hz.
-In this graph, we assume that there is less restriction in the end-to-end delay (50 ms) and the VNF resources (the system has 100 reserved VNF).
-%In the graph of cloud restriction, we assume that there is no restriction on the fronthaul link.
-%The limitation on the power is less than the graph of fronthaul limitation, and it is set to be 45 dBm on the power of each O-RU, and the maximum power of each UE is 40 dBm.
-%The minimum data rate for each UE in this service is 10 bits/sec/Hz.
-%The end-to-end delay for each UE is 4ms and the mean arrival rate is 2Mbps.
-%and the mean service rate is 10Mbps.
-%In this figure, the consequence of cloud limitation and fronthaul limitation is depicted.
-%As the number of UEs increases, the aggregate throughput rises linearly, and the graph of cloud restriction increases more than the other graph of fronthaul limitation.
-
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.4]{AcloudVsFronthaul.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput vs. Number of UEs in a Service}
-%  \label{fig:10}
-%\end{figure}
-In Fig. 10, the aggregate throughput is shown according to the number of iteration (outer loop) of the
-proposed algorithm (IABV) for different numbers of UEs for one service. In this figure, the convergence of the IABV method is illustrated. The minimum data rate for each UE is assumed to be 2 Mbps.
-After four iterations, IABV converges to the fixed value.
-
-In Fig. 11, the mean total delay of URLLC service is indicated according to the number of iterations of the
-proposed algorithm (IABV) for different numbers of UEs for one URLLC service. This figure shows that the algorithm converged to the fixed value after four iterations.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%55
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.4]{iter.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput vs. Number of Iterations}
-%  \label{fig:11}
-%\end{figure}
-%%%%%%%%%%%%%%%%%5
-%\subsection{Summary of Simulation Results}
-In Fig. 12, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
-proposed algorithm (IABV) and the optimal method for URLLC service for the low interference.
-The minimum data rate is 5bits/sec/Hz for each UE and the maximum delay is $0.1$ms.
-Also the mean arrival rate is set to be $0.2$Mbps and the mean service rate is $0.5$Mbps.
-%The other parameters are depicted in Table \ref{table:1a}.
-The optimal approach is obtained from the two-step joint exhaustive search and using CVX.
-In each iteration in the first step, the PRB allocation and O-RU association are obtained from brute force, and in the second step, we use CVX to get optimal power.
-Our solution is close to the optimal value in a small number of UEs.
-Therefore, this figure numerically demonstrates that the proposed algorithm converges to the global optimal in low interference.
-
-\begin{figure*}[!htb]
-	\centerline{%
-		\begin{tabular}{c@{}c@{}c}			
-			\includegraphics[scale = 0.4]{fig/optimal1n.eps} &
-			\includegraphics[scale = 0.4]{fig/interF_newn.eps} &
-			\includegraphics[scale = 0.4]{fig/FAn.eps} \\
-			\scriptsize Fig. 12~~Aggregate throughput vs. number of UEs   & \scriptsize Fig. 13~~Aggregate throughput vs. maximum interference   & \scriptsize Fig. 14~~Aggregate throughput vs. number of UEs
-	\end{tabular}}
-	\vspace*{-3mm}
-	%\caption{Global caption.}
-	\label{label}
-\end{figure*}
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.4]{optimal1.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput vs. Number of UEs }
-%  \label{fig:12}
-%\end{figure}
-
-In Fig. 13, the aggregate throughput is depicted vs. the maximum interference for two different maximum power thresholds of O-RU. 
-%We suppose that the maximum power threshold of UEs is one-third of the maximum power of O-RU.
-%The minimum data bit rate is assumed to be 0.2Mbps for each UE.
-Here we assume that with the increase of every ten dBm of interference power, it is assumed that ten users have been added to the system.
-In -105 dBm, we have 5 UEs, and at the end, we have 55 UEs in the system.
-Since the amount of interference in the system is entered as a fixed value,
-the allocation of PRBs is not considered.
-The higher maximum power threshold leads to a greater aggregate throughput.
-The aggregate throughput first increases with the number of UEs and at the same time the amount of the maximum interference, then it becomes almost fixed and finally decreases so much.
-When the aggregate throughput decreases, the maximum interference is so high that it takes the system out of feasibility.
-%The aggregate throughput rises with the increases of UEs and the maximum interference and then remains almost constant.
-
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.4]{interF_new.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput vs. Maximum Interference }
-%  \label{fig:13}
-%\end{figure}
-
-In Fig. 14, the aggregate throughput is shown versus
-the number of UEs for an eMBB service with low interference for the IABV and FA methods in the feasible region.
-The minimum data rate for each UE is 1Mb/s/Hz.
-The maximum power for each O-RU is 34dBm, and the maximum power for each UE is 30dBm. We assume that the system is not sensitive to fronhaul capacity and end-to-end delay and has enough VNF resources.
-By increasing the number of UEs, the aggregate throughput raises.
-And we can see that the IABV method is better than the FA method.
-%\begin{figure}
-%  \centering
-%    \includegraphics[scale = 0.4]{FA.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  \caption{Aggregate Throughput vs. the Number of UEs }
-%  \label{fig:14}
-%\end{figure}
-
-Table III shows the execution time given a number of UEs for one service for the three methods. We run our simulation on the system with configuration (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
- As the number of UEs in the system increases, the execution time increases polynomially for all three algorithms.
-Since the baseline scheme is a simpler algorithm, with random PRB allocation and O-RU association based on distance, the execution time is less than the two other algorithms.
-Power and PRB are allocated in the DR scheme, but O-RUs are associated based on distance.
-Therefore the execution time is less than the proposed algorithm.
-\begin{table}%[H]
- \caption {Execution Time vs. Number of UEs} 
-\begin{center}
- \scalebox{0.75}{
-\begin{tabular}{ |l|l|l|l| }
-%\hline
-%\multicolumn{3}{|c|}{Country List} \\
-\hline
-\multirow{2}{*}{Number of UEs } &\multicolumn{3}{|c|}{Execution Time (usec)} \\
-\cline{2-4}
-{} &Proposed method & DR scheme & Baseline scheme \\
-\hline
-5 & 12.156 &8.9546 &6.6436\\
-10 & 19.156   & 12.3112& 8.7870\\
-15 &29.140 & 15.4778 &9.5648 \\
-20    &44.573 &  21.5342 &14.8334 \\
-25 & 67.912  & 32.7926 &21.5510 \\
-\hline
-\end{tabular}}
-\vspace*{-1.6em}
-\end{center}
-\end{table}
-%\begin{figure}[H]
-%  \centering
-%    \includegraphics[scale = 0.4]{fig/exec.eps}
-%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
-%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
-%  %\caption{Mean Total Delay (usec) vs. Number of iterations}
-%  \captionsetup{labelformat=empty}
-%  \caption{(15) Execution time vs. the number of UEs}
-%  \label{fig:2}
-%\end{figure}
-%\vspace*{-1.4em}
-\section{Conclusion}\label{conc}
-In this paper, we modeled the downlink of the O-RAN system using isolated network slicing for different 5G services, i.e., eMBB, mMTC, and URLLC.
-Our goal is to maximize aggregate throughput by activating VNFs in each service, associating RUs, allocating power, and PRBs.
-The limited fronthaul capacity and the mean delay for each service are considered.
-The problem is mixed-integer non-linear programming that is solved by a two-step iterative algorithm.
-In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then, we obtained PRB association and power allocation using the Lagrangian method.
-In the second step, the O-RU association is carried out.
-The performance of our proposed method (i.e., IABV) is compared with the baseline scheme and DR scheme in \cite{lee2018dynamic}.
-In addition, the feasible region is discussed, and the FA algorithm is introduced to check the feasibility of the initial values.
-Also, we assume distinct scenarios for each service, i.e., eMBB, mMTC, and URLLC, based on their requirement QoS.
-Simulation results show that the proposed method (i.e., IABV) achieves $18.6\%$ higher data rate than the baseline scheme.
-Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than DR scheme and the baseline scheme.
-\vspace*{-1.1em}
-\bibliographystyle{IEEEtran}
-\bibliography{ref}
-\vspace*{-3em}
-%\bibliography{IEEEabrv,conf_short,ref}
-% \begin{IEEEbiography}
-% [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mojdeh.jpg}}]{ Mojdeh Karbalaee Motalleb} received her B.S.
+ \vskip 0pt plus -2fil
+ \begin{IEEEbiography}
+ [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/mojdeh.jpg}}]{ Mojdeh Karbalaee Motalleb (Karbalaeimotaleb)} received her B.S.
 and M.S.
@@
 She is also a Visiting Research Student with the Center for Wireless Communications, Oulu University, Oulu, Finland.
-Her research interests include optimization and machine learning in network and wireless communications.
-% \end{IEEEbiography}
-% \begin{IEEEbiography}
-% [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{onel.jpg}}]{ Onel L.
-A.
-López} (S'17-M'20) received the B.Sc.
-(1st class honors, 2013), M.Sc.
-(2017) and D.Sc.
-(with distinction, 2020) degree in Electrical Engineering from the Central University of Las Villas (Cuba),  the Federal University of Paraná (Brazil), and the University of Oulu (Finland), respectively.
-From 2013-2015, he served as a specialist in telematics at the Cuban telecommunications company (ETECSA).
-He is a collaborator to the 2016 Research Award given by the Cuban Academy of Sciences, a co-recipient of the 2019 IEEE EuCNC Best Student Paper Award, the author of the best doctoral thesis in engineering in Finland in 2020, and the recipient of the 2022 Young Researcher Award in the field of technology in Finland.
-He is co-author of the book entitled ``Wireless RF Energy Transfer in the massive IoT era: towards sustainable zero-energy networks'', Wiley, Dec 2021.
-He currently holds an Assistant Professorship (tenure track) in sustainable wireless communications engineering in the Centre for Wireless Communications (CWC), Oulu, Finland.
-His research interests include sustainable IoT, energy harvesting, wireless RF energy transfer, wireless connectivity, and machine-type communications.
-% \end{IEEEbiography}
-
- \vskip 0pt plus -2fil
- \begin{IEEEbiography}
- [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bio/mojdeh.jpg}}]{ Mojdeh Karbalaee Motalleb} received her B.S.
-and M.S.
-degrees in electrical engineering from the Amirkabir University of Technology, Tehran, Iran in 2015 and 2017.
-She is working toward a Ph.D.
-with the Department of Computer and Electrical Engineering, University of Tehran, Tehran, Iran.
-She is also a Visiting Research Student with the Center of Wireless Communications, Oulu University, Oulu, Finland.
 Her research interests include optimization and machine learning in network and wireless system.
@@
  \end{IEEEbiography}
-\end{document}
